### 2020-09-16 asa/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{Journal of Geophysics and Engineering, 12, no. 12, 175–187, (2015)}

\title{Application of spectral decomposition using regularized non-stationary autoregression to random noise attenuation}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Wencheng Yang\footnotemark[1], Runqiu Wang\footnotemark[1], Yangkang Chen\footnotemark[2], Jian Wu\footnotemark[1], Shan Qu\footnotemark[1], Jiang Yuan\footnotemark[1] and Shuwei Gan\footnotemark[1]}
\address{
\footnotemark[1] State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
ziyouqishi\_2014@163.com

\footnotemark[2]Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
Email: ykchen@utexas.edu
}
\lefthead{Yang et al.}
\righthead{Denoising by SDRNAR}

% for multiple-revision
\DeclareRobustCommand{\dlo}[1]{\ifthenelse{\boolean{@revd}}{}{}}
\DeclareRobustCommand{\wen}[1]{%
  \ifthenelse{\boolean{@revd}}{\textcolor{black}{#1}}{#1}}

%\dlo means remove removing
%\wen means preserve
\begin{abstract}

We propose an application of spectral decomposition using regularized non-stationary autoregression (SDRNAR) to random noise attenuation. SDRNAR is a recently proposed signal-analysis method, which aims at decomposing the seismic signal into several spectral components, each of which has a smoothly variable frequency and smoothly variable amplitude. 
In the proposed novel denoising approach, random noise is deemed to be the residual part of decomposed spectral components because it is unpredictable. 
One unique property of this novel denoising approach is that the amplitude maps 
for different frequency components can also be obtained during the denoising process, which can be valuable for some interpretation tasks. Compared with spectral decomposition algorithm by empirical mode decomposition (EMD), SDRNAR has higher efficiency and better decomposition performance. Compared with $f$-$x$ deconvolution\wen{ and mean filter}, the proposed denoising approach can obtain higher signal-to-noise ratio (SNR) and preserve more useful energy.  \wen{The proposed approach can only be applied to seismic profiles with relatively flat events, which becomes its main limitation. However, because it is applied trace by trace, it can preserve spatial discontinuities}. We use both synthetic and field data examples to demonstrate the performance of the proposed method.

\end{abstract}

\section{Keywords}
\wen{Random noise attenuation, spectral decomposition using regularized non-stationary autoregression (SDRNAR), empirical mode decomposition, $f$-$x$ deconvolution}

\section{Introduction}
Random noise attenuation plays an indispensable role in seismic data processing. The useful signal that is smeared in the ambient random noise is often neglected and thus may cause fake discontinuity of seismic events and artifact in final migrated image. Enhancing the useful signal while preserving edge properties of the seismic profiles by attenuating random noise can help reduce interpretation difficulties and misleading risks for oil \& gas detection. There has been a bunch of random noise attenuation approaches.

The widely used $f-x$ deconvolution \cite[]{canales} can achieve good result for linear events but may fail in handling complex or hyperbolic events. The way to deal with this linear-events dependence limitation is to use local $f-x$ deconvolution with small windows. However, different window size\wen{s} will result in different denoising effects and \wen{the} window size is actually data dependent. Thus, localized $f-x$ deconvolution with small processing windows is often hard to be implemented in practice. \wen{In addition to the local $f-x$ deconvolution with small windows, forward-backward prediction method \cite[]{yanghua1999} is also effective, but is still limited to linear events.} A mean or median filter \cite[]{nlm,liuyang2009tvmf,yangkang2014svmf} is often used to attenuate specific types of random noise. For example, a mean filter is only effective to attenuate highly Gaussian white noise, and a median filter \cite[]{yangkang2014svmf,yangkang2014nmo} can only remove spike-like random noise with excellent performance. An eigen-image based approach \cite[]{bekara2007}, or sometimes referred as global singular value decomposition (SVD), is effective for horizontal-events seismic profiles, but can not be adapted to complex profile. Otherwise, much useful dipping energy will be removed. An enhanced version of this method turns global SVD to local SVD \cite[]{bekara2007}, where a dip steering process is performed in each local processing window to make the local events flat. The problem for local SVD is that only one slope component for each processing window is allowed, and also the size of each processing window is often difficult to select. Matrix completion via $f-x$ domain multichannel singular spectrum analysis (MSSA) can handle complex dipping events well by extracting the first several eigen components after SVD for each frequency slice. The $f-x$ MSSA approach is based on a pre-known rank of the seismic data. However, for complex seismic data, the rank is hard to select, and for curved events, the rank tends to be high and thus will involve a serious rank-mixing problem. One widely used denoising approach that has relative ease for controlling parameters is spectral decomposition. \wen{\cite{yangkang2014simi} proposed a post-processing strategy in order to guarantee no coherent signal is lost in the removed noise section.}

Spectral decomposition of seismic data into different components is often used in random noise attenuation because useful energy and random noise usually reside in different spectral bands. Once signal and random noise are separated in different spectral scales, the random noise can be effectively attenuated by simply removing the large scale components. Existing spectral decomposition schemes include the Fourier transform, wavelet transform \cite[]{mallat,wavelet}, curvelet transform \cite[]{curvelet}, seislet transform \cite[]{seislet,yangkang20142}\wen{, and matching pursuit method \cite[]{yanghua2007,yanghua2010}}. Each of them has some special properties.

\cite{emd} proposed a new signal decomposition method called Empirical Mode Decomposition (EMD). The original aim of EMD is to stabilize a complex signal, that is, to decompose a signal into a series of Intrinsic Mode Functions (IMF). Each IMF has a locally constant frequency. The frequency of each IMF is decreasing according to the sequence in which each IMF is separated out. EMD is a breakthrough in the analysis of linear and stable spectrum, because it can adaptively separate a\dlo{n} nonlinear and non-stationary signal, which is the feature of seismic data, into different frequency ranges. The random noise can be removed by removing the first IMF, which corresponds to the highest oscillatory components. \wen{EMD can also be utilized in each frequency slice in the $f-x$ domain to preserve horizontal energy, while leaving the dipping energy dealt with by other specific denoising approaches \cite[]{yangkang2014eage1,yangkang2014shemd}}.

\cite{sdrnar} proposed a novel spectral decomposition scheme termed spectral decomposition using regularized non-stationary autoregression (SDRNAR), which aims at decomposing a seismic signal into sub-signals with smoothly variable frequency and smoothly variable amplitude. This method differs from EMD in that it can more explicitly control the frequency and amplitude of different components and their smoothness than EMD.

The motivation for \cite{sdrnar} to propose this method is to provide a faster and more precise way to implement spectral analysis. Inspired by the application of EMD to random noise attenuation in the signal-processing field, in this paper, we apply SDRNAR to random noise attenuation in the $t-x$ domain. Instead of removing the first IMF, we remove the residual of SDRNAR, because the random noise is thought to be the highest oscillatory and thus unpredictably distributed.  The uniqueness of the proposed denoising approach is that all the spectral information as indicated by \cite{sdrnar} can be achieved during the denoising process. Compared with EMD, SDRNAR can separate the seismic data into different frequency component with much less frequency-component mixture. We show that SDRNAR can separate the useful signal components and noise effectively while EMD can not. We compared the proposed denoising approach with the well-known $f$-$x$ deconvolution and mean filter according to their denoising performance. Results show that, the proposed approach can preserve much more useful energy than $f$-$x$ deconvolution and mean filter.

We organize the paper as follows: we first introduce the basis of regression analysis, then we review the principle of SDRNAR and propose the application of SDRNAR to random noise attenuation, finally we use both synthetic and field data examples to demonstrate the performance of the proposed approach and make a comparison with the alternatives.

\section{Method}
\subsection{Regression analysis}

Let's first review the classic stationary regression theory. Let $d(t)$ be a time series, it can be represented in the norm of $b_n(t)(n=1,2,\cdots,N)$ (called basis function) in the least square criteria:

\begin{equation}
\label{eq:one}
\min\parallel d(t)-\sum_{n=1}^{N}a_nb_n(t)\parallel_2^2,
\end{equation}
where $a_n$ is the regressive coefficient and $\parallel \parallel_2^2$ denotes the squared \dlo{L-2}\wen{L2} norm of a function. In the non-stationary case, the regressive coefficients become variable with time, which can be expressed as:

\begin{equation}
\label{eq:two}
\min\parallel d(t)-\sum_{n=1}^{N}a_n(t)b_n(t)\parallel_2^2.
\end{equation}

The minimization of equation \ref{eq:two} is ill-posed for the reason that more unknown variables than given variables need to be found. In the theory of SDRNAR, \cite{sdrnar} used shaping regularization to constrain equation \ref{eq:two}.

\subsection{Denoising by spectral decomposition}

The non-stationary decomposition model for a complex signal $d(t)$ is:

\begin{equation}
\label{eq:three}
d(t)=\sum_{n=1}^{N}d_n(t)=\sum_{n=1}^{N}\hat{A}_n(t)e^{i\Phi_n(t)}+r(t),
\end{equation}

where $d_n(t)$, $\hat{A}_n(t)$, $\Phi_n(t)$, $r(t)$ stand for \dlo{sub-signal}\wen{decomposed signal}, local amplitude, local phase and residual respectively. $\hat{A}_n(t)$ can be found by following equation \ref{eq:four} using regularized non-stationary regression (RNR):

\begin{equation}
\label{eq:four}
\min\parallel d(t)-\sum_{n=1}^{N}\hat{A}_n(t)e^{i\Phi_n(t)}\parallel_2^2,
\end{equation}

and $\Phi_n(t)$ can be found by time integration of the instantaneous frequency $f_n(t)$ following equation \ref{eq:five}:

\begin{equation}
\label{eq:five}
\Phi_n(t)=2\pi\int_0^t f_n(\tau)d\tau.
\end{equation}

The instantaneous frequency $f_n(t)$ in equation \ref{eq:five} can be determined directly from the phase of different complex roots $\hat Z_n(t)$ of the polynomial function (shown in equation \ref{eq:poly}) following equation \ref{eq:instf}:

\begin{equation}
\label{eq:instf}
f_n(t)=-Re\left[ arg\left(\frac{\hat{Z}_n(t)}{2\pi\Delta t}\right)\right],
\end{equation}

\begin{eqnarray}
\label{eq:poly}
F(Z)=(1-Z/Z_1)(1-Z/Z_2)\cdots(1-Z/Z_N) \\ \nonumber
\quad=1+a_1Z+a_2Z^2+\cdots+a_nZ^N.
\end{eqnarray}

\wen{In non-stationary case, the filter coefficients $a_n$ becomes a smoothly varying functions of time $a_n(t)$ (shown in equation \ref{eq:two}), which makes the filter shown in equation \ref{eq:poly} adapt to non-stationary changes in the input data. The complex roots $\hat{Z}_n(t)$ can be found using a eigenvalue-based algorithm \cite[]{sdrnar}.}

The final denoised data can be got by: 
\begin{equation}
\label{eq:denoise}
\hat{d}(t)=\sum_{n=1}^{N}\hat{A}_n(t)e^{i\Phi_n(t)}.
\end{equation}

The decomposition is similar to empirical mode decomposition (EMD), but differs in that it has a mathematical formulation for controlling the decomposition. Figure \ref{fig:sig,sig1,sigemd1,sig2,sigemd2,cresid,sigemd3} gives a comparison between SDRNAR and EMD in decomposing a synthetic signal that has two oscillating frequency components. As can be seen from the demonstration, both SDRNAR and EMD successfully decompose the combined signal into individual monotonic component. The residuals using both methods are very close to zero. Figure \ref{fig:trace-sig,trace-sign1,trace-sigemd4,trace-sign2,trace-sigemd3,trace-sign3,trace-sigemd2} shows a comparison between SDRNAR and EMD in decomposing a noise free synthetic seismic trace.

A special property of the proposed approach is that, apart from the denoised data, we can also get other valuable information from the data, such as the instantaneous frequency $f_n(t)$ and amplitude of the instantaneous frequency $\hat{A}_n(t)$ of the $n$th component. The spectral information can be valuable in interpretation jobs like identifying the oil\&gas traps, which has already been shown by \cite{sdrnar}.\dlo{This abstract focuses on the denoising performance of the novel spectral decomposition approach.}

\subsection{Algorithm steps}
The algorithm steps can be summarized below:
\begin{enumerate}
\item Use non-stationary autoregression to compute $a_n(t)$ with \dlo{$b_n(t)=a_n(t-n)$}\wen{$b_n(t)=d(t-n\Delta t)$ ($\Delta t$ is the time interval)} according to equation \ref{eq:two};
\item Find the roots $Z_n(t)$ of each polynomial according to equation \ref{eq:poly};
\item Compute instantaneous frequency $f_n(t)$ according to equation \ref{eq:instf};
\item Compute local phase $\phi_n(t)$ according to equation \ref{eq:five};
\item Fit the data to compute the amplitude corresponding to each frequency component $\hat{A}_n(t)$ and the fitted denoised data $\hat{d}(t)$ according to equations \ref{eq:four} and \ref{eq:denoise}.
\end{enumerate}

\section{Examples}

\inputdir{sigsep}
\multiplot{7}{sig,sig1,sigemd1,sig2,sigemd2,cresid,sigemd3}{width=0.34\columnwidth}{Signal Separation using SDRNAR and EMD. (a) Original signal. (b) Frequency component 1 using SDRNAR. (c) Frequency component 1 using EMD. (d) Frequency component 2 using SDRNAR. (d) Frequency component 2 using EMD. (f) Residual using SDRNAR. (g) Residual using EMD.}

\inputdir{tracesep}
\multiplot{7}{trace-sig,trace-sign1,trace-sigemd4,trace-sign2,trace-sigemd3,trace-sign3,trace-sigemd2}{width=0.34\columnwidth}{Trace decomposition using SDRNAR and EMD. (a) Original noise free seismic trace. (b) First component using SDRNAR. (c) First component using EMD. (d) Second component using SDRNAR. (e) Second component using EMD. (f) Third component using SDRNAR.}

\inputdir{simple}
\plot{trace-disp}{width=\columnwidth}{Denoising demonstration using the proposed approach for single-trace synthetic data. (a) Noisy data. (b) First spectral component. (c) Second spectral component. (d) Third spectral component. (e) Fourth spectral component. (f) The residual after SDRNAR. (g) Denoised data. \wen{The SNR has increased from -10.17 to 0.9729.}}

The first example is a noisy single trace, shown in Figure \ref{fig:trace-disp}a. The clean synthetic trace is generated by convolving Ricker wavelet with four different central frequency (40 Hz, 30 Hz, 20 Hz, \wen{and} 10Hz, respectively) with the same reflectivity coefficients located at different temporal positions. After adding Gaussian white noise, the wavelet has been smeared in the noise. After spectral decomposition using SDRNAR, the decomposed signals are shown in Figures \ref{fig:trace-disp}b-\ref{fig:trace-disp}e. The residual or the random noise is shown in Figure \ref{fig:trace-disp}f. The denoised data, summation of \ref{fig:trace-disp}b-\ref{fig:trace-disp}e, is shown in Figure \ref{fig:trace-disp}g. A huge level of noise has been removed during the denoising process. \wen{In order to numerically compare the performances using the proposed approach, we use the signal-to-noise ratio (SNR) defined as: 
\begin{equation}
\label{eq:snr}
SNR=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2^2}{\Arrowvert \mathbf{s}-\hat{\mathbf{s}}\Arrowvert_2^2},
\end{equation}
where $\mathbf{s}$ is the noise-free signal and $\hat{\mathbf{s}}$ is the denoised signal. After using the proposed approach, the SNR has increased from -10.17 to 0.9729.}

The second example is a synthetic seismic profile with four horizontal events (Figures \ref{fig:synth0,synth}). Figures \ref{fig:synth0} and \ref{fig:synth} show the clean and noisy synthetic data, respectively. The central frequency of the Ricker wavelet used to synthesize the profile is decreasing as we can see from the original profile. Their corresponding central frequency are 40Hz, 30Hz, 20 Hz, and 10 Hz, from up to down, respectively. The denoised section and \wen{removed} noise section are shown in Figures \ref{fig:synth-cfit} and \ref{fig:synth-cdif}, respectively. As a reference, Figures \ref{fig:synth-fx} and \ref{fig:synth-fx-dif} show the denoised profile and removed noise section for $f$-$x$ deconvolution. Because of the application of spatial prediction filter in $f$-$x$ domain, there exist some boundary effects in the denoised section, as shown in Figure \ref{fig:synth-fx}. The clean denoised section and coherency-free noise sections using the proposed approach show an excellent denoising performance.

The original SNR of the noisy data (Figure \ref{fig:synth}) is $-23.94$. After using $f$-$x$ deconvolution (\ref{fig:synth-fx}), the SNR increases to $-1.91$. After using the proposed approach (\ref{fig:synth-cfit}), the SNR increases to $1.54$. In this example, we decompose the signal into four components. Figure \ref{fig:synth-sign0,synth-sign1,synth-sign2,synth-sign3} show\wen{s} the decomposed four components using SDRNAR. For comparison with EMD, we also demonstrate the four decomposed components using EMD in Figure \ref{fig:simf1,simf2,simf3,simf4}. As can be seen in Figure \ref{fig:synth-sign0,synth-sign1,synth-sign2,synth-sign3}, the decomposed components are clean, exhibiting smoothly-variable frequency. However, the EMD decomposed components have serious mode-mixing issues, as mentioned in \cite[]{kopecky2010,yangkang2014}, which made the removal of random noise by removing one mode difficult. The amplitude maps of instantaneous frequency are shown in Figure \ref{fig:synth-cwht0,synth-cwht1,synth-cwht2,synth-cwht3}. Figure \ref{fig:synth-cwht0,synth-cwht1,synth-cwht2,synth-cwht3} also confirms the observation from Figure \ref{fig:synth-sign0,synth-sign1,synth-sign2,synth-sign3} that the decomposed components contain smoothly-variable frequency.

The third example is a relatively more complex data, with dipping and conflicting events (Figure \ref{fig:complex,complex-cfit,complex-cdif,complex-mf,complex-mf-dif}). This example demonstrates the limitation of the proposed approach in dealing with complex seismic profiles. As we can see from the both denoised section and removed noise section as shown in Figures \ref{fig:complex-cfit} and \ref{fig:complex-cdif}, respectively, there is some damages to dipping energy. As the slope becomes larger, there are more damages to the useful energy. The horizontal events, however, are well preserved and denoised. The reason causing the limitation of the proposed approach comes from the fact that the SDRNAR method is applied trace by trace. The parameters selected for the decomposition should be relatively the same in order to be efficient, otherwise, we need to specify the parameters trace by trace, which make the SDRNAR method can not adapt to highly spatially variable components, e.g., steeply dipping event. \new{We also show the performance of the same example using the mean filter. Figure \ref{fig:complex-mf} is the denoised result using mean filter and Figure \ref{fig:complex-mf-dif} is the corresponding noise section. As we can see from Figures \ref{fig:complex-mf} and \ref{fig:complex-mf-dif}, the mean filter nearly remove all the dipping energy.}

The fourth example is a post-stack field data. It comes from part of the 2-D field land data from the open-source website Freeusp 
(http://www.freeusp.org/). The stacked data is shown in Figure \ref{fig:data-f}. After random noise attenuation using the proposed approach, the denoised data is shown in Figure \ref{fig:cfit-f}. Figure \ref{fig:cdif-f} shows the difference between the denoised section and original noise section. From the denoising performance, we conclude the proposed approach does an excellent job. We also apply $f$-$x$ deconvolution \wen{and mean filter} to the field dataset. The denoised section and removed noise section using $f-x$ deconvolution are shown in Figure \ref{fig:data-fx} and \ref{fig:data-fx-dif}, respectively. \wen{The denoised section and removed noise section using mean filter are shown in Figure \ref{fig:data-mf} and \ref{fig:data-mf-dif}, respectively.} Even though the denoised section using $f$-$x$ deconvolution \wen{and mean filter} seem\dlo{s} clean, there exist some coherent horizontal events in the noise section (Figures \ref{fig:data-fx-dif} \wen{and \ref{fig:data-mf-dif}}). Because in this example we do not know the true answer, we can not numerically compare the SNRs of two approaches, however, from the visual comparisons, it is enough to draw a conclusion that the proposed approach does a better job. \wen{In this example, the denoised section using mean filter is over smoothed. The two areas pointed out by the labels A and B show the over-smoothed places. The spatial discontinuities will cause a failure using mean filter because mean filter is based on the spatial coherency assumption. The lost information due to over smoothing can be found in the noise section, as pointed out by the label C. Thus, we conclude that the proposed approach can outperform the mean filter in preserving spatial discontinuities.} Figure \ref{fig:sign0,sign1,sign2,sign3} shows the four decomposed components using SDRNAR, from which we can see the smoothly-variable-frequency behavior for each component. For a referential comparison, the separated results using EMD are shown in Figure \ref{fig:imf1,imf2,imf3,imf4}. It is obvious that the separated components do not have constant or smoothly-variable frequency. Additionally, we obtain the spectral information shown in Figure \ref{fig:cwht0,cwht1,cwht2,cwht3}. From Figure \ref{fig:cwht3}, it seems that there is a low-frequency anomaly around 0.75\wen{ }s, which may indicate a trap of oil \& gas.

\inputdir{simple}
\multiplot{2}{synth0,synth}{width=0.45\columnwidth}{(a) Clean synthetic data. (b) Noisy synthetic data.}

\multiplot{4}{synth-cfit,synth-cdif,synth-fx,synth-fx-dif}{width=0.45\columnwidth}{Amplitudes of  different frequency components.}

\multiplot{4}{synth-sign0,synth-sign1,synth-sign2,synth-sign3}{width=0.45\columnwidth}{Amplitudes of  different frequency components.}

\inputdir{simpleemd}
\multiplot{4}{simf1,simf2,simf3,simf4}{width=0.45\columnwidth}{Different separated components for synthetic data using EMD. (a) First separated component. (b) Second separated component. (c) Third separated component. (d) Fourth separated component.}

\inputdir{simple}
\multiplot{4}{synth-cwht0,synth-cwht1,synth-cwht2,synth-cwht3}{width=0.45\columnwidth}{Amplitudes of  different frequency components.}

\inputdir{dipping}
\multiplot{5}{complex,complex-cfit,complex-cdif,complex-mf,complex-mf-dif}{width=0.45\columnwidth}{(a) Noisy synthetic example with dipping events. (b) Denoised result using the proposed approach. (c) Removed noise section using the proposed approach. Note that the damage to dipping events suggest a denoising failure. (d) Denoised result using mean filter. (e) Removed noise section using mean filter.}

\inputdir{freeusp}
\plot{data-f}{width=0.48\columnwidth}{Input noisy field data from Freeusp.}

\multiplot{6}{cfit-f,cdif-f,data-fx,data-fx-dif,data-mf,data-mf-dif}{width=0.34\columnwidth}{Different separated components for field data using SDRNAR. (a) First separated component. (b) Second separated component. (c) Third separated component. (d) Fourth separated component.}

\inputdir{freeusp}
\multiplot{4}{sign0,sign1,sign2,sign3}{width=0.4\columnwidth}{Different separated components for field data using SDRNAR. (a) First separated component. (b) Second separated component. (c) Third separated component. (d) Fourth separated component.}

\inputdir{freeuspemd}
\multiplot{4}{imf1,imf2,imf3,imf4}{width=0.4\columnwidth}{Different separated components for field data using EMD. (a) First separated component. (b) Second separated component. (c) Third separated component. (d) Fourth separated component.}

\inputdir{freeusp}
\multiplot{4}{cwht0,cwht1,cwht2,cwht3}{width=0.4\columnwidth}{Amplitudes of  different frequency components.}

\section{Discussions}

SDRNAR is a new spectral decomposition approach that can decompose a 1D signal into different spectral components. 
With exact mathematical formulation, SDRNAR can control its behavior by selecting different parameters. SDRNAR differs 
from EMD in that SDRNAR can be manually manipulated rather than empirically data dependent. The proposed denoising algorithm is 
based on applying SDRNAR to each seismic trace. Although there are other options of direction and domain for applying
SDRNAR, this paper focuses on the $t$-$x$ domain application of SDRNAR to each 1-D signal along temporal direction.

The proposed approach is more beneficial for post-stack or NMO corrected profiles where seismic events are mostly horizontal. We can 
understand this property by analyzing the implementation steps of SDRNAR. We apply SDRNAR to each trace of a profile with the same parameters. 
When seismic events are not horizontal, the optimal parameters used for each trace may not be equivalent. It can not be made possible for manually choosing the best parameters for each trace. 
However, an efficient and adaptive parameter selection algorithm for each trace can be developed in the future in order to handle the horizontal-events restriction. \wen{It can perform obviously better than those specific denoising approaches for horizontal events, e.g. mean filter, as it is applied based on the assumption of spatial coherency. There is danger in smoothing too much along spatial directions using other approaches. The proposed approach can be widely used in processing land post-stack data, where most of reflections are horizontal. The proposed approach can also be used to denoise microseismic trace, because many microseismic data can only be processed trace by trace. }

The efficiency and performance for SDRNAR to decompose seismic traces into local monotonic components are better than that of EMD. Because of the explicit 
mathematical formulation of SDRNAR, we can use fast iterative solver to handle the under-determined equations involved in SDRNAR. However, without any mathematical model to 
support EMD, we can not use fast algorithm to apply EMD. The cost of SDRNAR is $O(NN_tN_{iter})$, where $N_t$ is the number of time samples and $N_{iter}$ is the number of shaping iterations (typically between 10 and 100). As can be seen in the examples, the decomposition of seismic traces achieved by EMD are not applicable for removing
random noise, because of the serious mode-mixing problem. The separated components of SDRNAR, however, obtain excellent results for removing unpredictable random noise.

\section{Conclusions}
We have proposed a new method to attenuate random noise in $t-x$ domain, by applying the SDRNAR to each seismic trace and remove the residuals for each trace. 
SDRNAR can achieve better decomposition than EMD in that no mode mixture exists and no useful energy lays in the noise component. In addition to denoising, the amplitude maps 
for different frequency components can also be obtained, which can be used to aid in seismic interpretation and help in finding oil \& gas related low-frequency anomalies. We use both synthetic and field data examples to demonstrate the implementation and performance of the proposed denoising approach. \wen{The proposed approach can not be applied to complex seismic profile, which becomes its main limitation. However, compared with those filters that can be specifically used for horizontal events (e.g. mean filter), the proposed approach can get better result. Because it is applied trace by trace, and thus can preserve spatial discontinuities.}  Compared with $f$-$x$ 
deconvolution \wen{and mean filter}, the proposed approach can obtain higher SNR and preserve more useful energy.

\section{Acknowledgments}
We thank the Freeusp website for providing the open-source field data. We are grateful to developers of the Madagascar software package for providing corresponding codes for testing the algorithms and preparing the figures. We would like to thank three anonymous reviewers for helpful suggestions, which improves the manuscript a lot. This work is supported by the National Basic Research Program of China (grant NO: 2013 CB228600).

\bibliographystyle{seg}
\bibliography{asa}

\newpage
\listoffigures

### 2020-09-16 cs/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{Journal of Applied Geophysics, 130, 194–208, (2016)}

\title{Compressive sensing for seismic data reconstruction via fast projection onto convex sets based on seislet transform}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Shuwei Gan\footnotemark[1], Shoudong Wang\footnotemark[1], Yangkang Chen\footnotemark[2], Xiaohong Chen\footnotemark[1], Weiling Huang\footnotemark[1] and Hanming Chen\footnotemark[1]}
\address{
\footnotemark[1] State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
Email: gsw19900128@126.com\&swang104@ucsc.edu\&chenxh@cup.edu.cn \\
cup\_hwl@126.com \& huichanming@126.com \\
\footnotemark[2] Jackson School of Geosciences\\
The University of Texas at Austin\\
University Station, Box X\\
Austin, TX 78713-8924, USA \\
Email: ykchen@utexas.edu
}

\lefthead{Gan et al.}
\righthead{Compressive sensing with seislet}
%\footer{Iterative deblending using shaping regularization}

% for multiple-revision
\DeclareRobustCommand{\dlo}[1]{\ifthenelse{\boolean{@revd}}{}{}}
\DeclareRobustCommand{\wen}[1]{%
  \ifthenelse{\boolean{@revd}}{\textcolor{black}{#1}}{#1}}

\begin{abstract}
According to the compressive sensing (CS) theory in the signal-processing field, we proposed a new CS approach based on a fast projection onto convex sets (POCS) algorithm with sparsity constraint in the seislet transform domain. The seislet transform appears to be the sparest among the state-of-the-art sparse transforms. The FPOCS can obtain much faster convergence than conventional POCS (about two thirds of conventional iterations can be saved)\wen{, while maintaining the same recovery performance}. \wen{The FPOCS can obtain faster and better performance than FISTA for relatively cleaner data but will get slower and worse performance than FISTA, which becomes a reference to decide which algorithm to use in practice according the noise level in the seismic data.} The seislet transform based CS approach can achieve obviously better data recovery results than $f-k$ transform based scenarios, considering \dlo{both} signal-to-noise ratio (SNR)\wen{, local similarity comparison,} and visual observation, because of a much sparser structure in the seislet transform domain. We have used both synthetic and field data examples to demonstrate the \wen{superior} performance \wen{the proposed seislet-based FPOCS approach}. 
\end{abstract}

\newpage
\section{Keywords}
Compressive sensing, irregularly sampled seismic data, sparsity comparison, seislet transform, fast projection onto convex sets

\section{Introduction}
% It breaks the long-standing pillar of Nyquist-Shannon sampling theory, which assumes that information is naturally band-limited. Instead, CS assumes a model where the signal is sparse in some transform domain. This lets us sense a signal with far fewer samples. We then use $L_1$-optimization techniques to reconstruct the signal as if we had taken all of the samples.

Most of the time, seismic data processing need a regular and dense dataset input, which is of extreme importance for obtaining a high-resolution result.  However, during the data acquisition process, many different reasons may result in the missing traces\wen{, including economic reasons, ground surface limitations, and regulatory reasons}. Seismic data reconstruction is such a pre-condition procedure that can be used to remove sampling artifacts\wen{, filling the gaps}, and to improve amplitude analysis, which is indispensable for the subsequent processing steps including high-resolution processing, wave-equation migration, multiple suppression, amplitude-versus-offset (AVO) or amplitude-versus-azimuth (AVAZ) analysis, and time-lapse studies \cite[]{daniel2002,liubin2004,abma2005,abma2006,juefu2010,mostafa2010,yangkang2014halfthr,yangkang2015eage2}.

In recent years, because of the popularity of compressive sensing (CS) based applications \cite[]{candes20062}, there exists a new paradigm for seismic data acquisition that can potentially reduce the survey time and increase the data resolution \cite[]{herrmann2010}. Compressive sensing (CS) is a relatively new paradigm in signal processing that has recently received a lot of attention. The theory indicates that the signal which is sparse under some basis may still be recovered even though the number of measurements is deemed insufficient by Shannon's criterion. The principle of CS involves solving a least-square minimization problem with a $L_1$ norm penalty term of the reconstructed model, which requires compromising a least-square data-misfit constraint and a sparsity constraint over the reconstructed model. The iterative shrinkage thresholding (IST) and the projection onto convex sets (POCS) are two common approaches used to solve the minimization problem in the exploration geophysics field.

%In recent years, compressive sensing has raised a lot of attention among different kinds of areas, like compressive imaging, medical imaging, analog-to-information conversion, and geophysical data analysis, to name just a few. According to the Shannon/Nyquist sampling theorem, signal processing requires that a signal must be sampled at the rate of at least twice its highest frequency in order to be represented explicitly. While the compressive sensing theory can reconstruct the signal with much less sampling rate because its exploration of the sparsity-promotion in some transformed domain. The CS strategy is composed of three key steps: data acquisition through a randomized sensing matrix, sparsifying transform and a sparsity-promotion recovery by solving a least-square problem with a $L_1$ norm  penalty term of the reconstructed model, which requires compromising a least-square data-misfit constraint and a sparsity constraint over the reconstructed model. As the acquisition process is a starting point in seismic processing, how to obtain more information through as little survey time as possible has a great practical significance. A lot of researches have been done to explore the new acquisition strategy in the CS level. In this paper, we assume that the irregular acquisition surveys already satisfy the randomized sampling requirement approximately, which makes the missing traces harmless by turning them into incoherent Gaussian noise that can be attenuated easily.

Inspired from the fast iterative shrinkage-thresholding algorithm (FISTA) introduced in \cite{beck2009}, we propose a similar faster version of POCS (FPOCS).  Sparsity of seismic data has been explored utilizing different transforms, such as Fourier transform, curvelet \cite[]{candes20061} and synchrosqueezed wavelet transform \cite[]{yangkang2014sswt}. We compare the sparseness of different well-known sparse transforms by displaying the transform domain and drawing the transform domain coefficients decaying curves. The comparison shows that the seislet transform is obviously sparser than other alternative sparse transforms. Thus, we use the seislet transform \cite[]{seislet,yangkang20142} as the sparsity promoting transform in the compressive sensing data recovery framework in order to explore its related behaviors. Both synthetic and field data examples show that the proposed seislet based FPOCS can obtain better and faster data recovery than the $f$-$k$ transform based POCS method.

\wen{The contributions of the paper can be divided into three aspects. (1) We extend the acceleration strategy used previously in the IST approach to POCS approach, and compare the performance difference of IST and POCS (and related FISTA and FPOCS) in seismic data with different noise level and pointed out that the selection of IST or POCS depends on the noise level of seismic data. (2) We compare the transform domain sparsity of different well-known sparse transforms in terms of the plotted sparse coefficients and coefficients decaying diagrams, and find out that the seislet transform has a much sparser transform domain structure than Fourier transform, wavelet transform, and the curvelet transform. (3) The seislet-based CS approach for seismic data reconstruction is initially investigated and the performance of seislet-based approach and $f$-$k$ based approach are compared in terms of the reconstruction signal-to-noise ratio (SNR), local similarity comparison, and visual observation. }

\section{Methods}
\subsection{Problem statement}
The interpolation problem in a CS framework can be summarized in the following model:
\begin{equation}
\label{eq:int}
\mathbf{d}_{obs} = \mathbf{S}\mathbf{d}, \mathbf{m} = \mathbf{Ad}
\end{equation}
where $\mathbf{d}_{obs}$ is the observed data, $\mathbf{S}$ is the sampling operator, $\mathbf{d}$ is the unknown data we would like to
estimate, $\mathbf{A}$ is the sparsity-promoting transform, and $\mathbf{m}$ is the transform domain coefficients.

The synthesis based approach solves the following problem:
\begin{equation}
\label{eq:syn}
\min_{\mathbf{m}} \parallel\mathbf{d}_{obs}- \mathbf{SA}^{-1}\mathbf{m} \parallel_2^2 + \lambda \parallel \mathbf{m} \parallel_1,
\end{equation}
where $\mathbf{A}^{-1}$ denotes the inverse sparsity-promoting transform.

The analysis-based approach solves the following problem:
\begin{equation}
\label{eq:ana}
\min_{\mathbf{d}} \parallel \mathbf{d}_{obs} - \mathbf{S}\mathbf{d}  \parallel_2^2 + \lambda \parallel \mathbf{A} \mathbf{d} \parallel_1.
\end{equation}

The analysis-based approach emphasizes the sparsity of the
canonical transformed coefficients, so it tends to recover data with
smooth regions; while the synthesis-based approach finds the
sparsest approximation of the given data in the transformed domain \cite[]{jianwei2014}.

\subsection{Fast iterative shrinkage thresholding algorithm}
The iterative shrinkage thresholding (IST) is one of the most effective methods to solve problem \ref{eq:syn}:
\begin{equation}
\label{eq:ist}
\mathbf{m}_{n+1} = \mathbf{T}_{\tau}\left[\mathbf{m}_{n} + (\mathbf{S}\mathbf{A}^{-1})^H(\mathbf{d}_{obs}-(\mathbf{S}\mathbf{A}^{-1})\mathbf{m}_n)\right],
\end{equation}
where $\mathbf{m}_n$ denotes the coefficients model after $n$th iteration, $\mathbf{T}_{\tau}$ denotes a thresholding operator (which is a nonlinear operator) with an input parameter $\tau$, and $[\cdot]^H$ denotes the adjoint operator. It's worth noting that $\tau$ has different connections with $\lambda$ according to the thresholding type \cite[]{yangkang2014halfthr}.

Due to the $O(1/k)$ convergence of IST, implementing IST is usually very time-consuming in practice. \cite{beck2009} proposed the fast iterative shrinkage thresholding algorithm (FISTA) to improve the convergence rate:
\begin{equation}
\begin{split}
\mathbf{m}_{n}'  &= \mathbf{m}_n + \frac{v_n-1}{v_{n+1}}(\mathbf{m}_n-\mathbf{m}_{n-1}), \\
\mathbf{m}_{n+1} &= \mathbf{T}_{\tau}\left[\mathbf{m}_{n}' + (\mathbf{S}\mathbf{A}^{-1})^H\left(\mathbf{d}_{obs}-(\mathbf{S}\mathbf{A}^{-1})\mathbf{m}_n'\right)\right],
\end{split}
\end{equation}
where $v_n$ is a controlling parameter with the initial value $v_0=1$ and $\mathbf{v}_{n+1}=(1+\sqrt{1+4v_n^2})/2$.

The improved convergence rate is $O(1/k^2)$, and thus becomes widely used in the image-processing field since its invention.

\subsection{Projection onto convex sets and its fast version}
In exploration geophysics field, geophysicists prefer formulating the seismic data reconstruction problem as problem \ref{eq:ana}. The projection onto convex sets (POCS) algorithm is one of the most widely used methods for reconstructing missing seismic data, especially for those irregular sampled seismic data binned onto regular grids.  The POCS \cite[]{abma2006} aims to solve equation \ref{eq:ana} by the following framework:
\begin{equation}
\label{eq:pocs}
\mathbf{d}_{n+1} = \mathbf{d}_{obs} + (\mathbf{I}-\mathbf{S})\mathbf{A}^{-1}\mathbf{T}_{\tau}\left[\mathbf{A}(\mathbf{d}_n)\right],
\end{equation}
where $\mathbf{d}_n$ denotes the estimated data after $n$th iteration.

Inspired from the FISTA, we propose the following faster version of POCS (FPOCS):
\begin{equation}
\begin{split}
\mathbf{d}_{n}'  &= \mathbf{d}_n + \frac{v_n-1}{v_{n+1}}(\mathbf{d}_n-\mathbf{d}_{n-1}), \\
\mathbf{d}_{n+1} &= \mathbf{d}_{obs} + (\mathbf{I}-\mathbf{S})\mathbf{A}^{-1}\mathbf{T}_{\tau}\left[\mathbf{A}(\mathbf{d}_{n}')\right].
\end{split}
\end{equation}
An obvious difference between IST and POCS (or between FPOCS and FISTA) is whether we make use of the known data. Briefly speaking, the IST (FISTA) treats all the data components as unknown while POCS (FPOCS) only treats the missing data components as unknown. The comparison between IST (FISTA) and POCS (FPOCS) in terms of the reconstruction performance and convergence rate can be done from two cases: irregularly sampled noisy data and irregularly sampled clean data. We will implement such two comparisons in the section of examples. The general conclusion can be given in advance: for irregularly sampled noisy dataset, the IST (FISTA) method can be superior  because during the thresholding process, the extra random noise will be attenuated gradually; for irregularly sampled clean dataset, the POCS (FPOCS) method can be superior because the known sampled data help constrain the spatial coherency during the inversion. Here, the noisy level is relative. Those data acquired from the marine acquisition are much better than those data from land acquisition. In this paper, we only deal with the datasets from marine acquisition, thus we prefer the FPOCS instead of the FISTA.

\subsection{Review of seislet transform}
The construction of seislet transform \cite[]{seislet} follows the basics of the second-generation wavelet transform. The forward transform starts with the finest scale (the original sampling) and goes to the coarsest scale. The inverse transform starts with the coarsest scale and goes back to the finest scale \cite[]{yangkang20142}. The forward and inverse seislet transforms can be
expressed as:
\begin{equation}
\label{eq:one}
\mathbf{r}=\mathbf{o}-\mathbf{P\left[e\right]},
\end{equation}
\begin{equation}
\label{eq:two}
\mathbf{c}=\mathbf{e}+\mathbf{U\left[r\right]},
\end{equation}
\begin{equation}
\label{eq:three}
\mathbf{e}=\mathbf{c}-\mathbf{U\left[r\right]},
\end{equation}
\begin{equation}
\label{eq:four}
\mathbf{o}=\mathbf{r}+\mathbf{P\left[e\right]},
\end{equation}
where $\mathbf{P}$ is the prediction operator, $\mathbf{U}$ is the updating operator. $\mathbf{r}$ denotes the difference between true odd trace and predicted odd trace (from even trace), $\mathbf{c}$ denotes a coarse approximation of the data. At the start of forward transform, e and o correspond to the even and odd
traces of the data domain. At the start of the inverse transform, $\mathbf{c}$ and $\mathbf{r}$ will have just one
trace of the coarsest scale of the seislet domain. The seislet transform differs from the wavelet transform in that the prediction and updating operators utilize the local slope of seismic profiles to predict and update the even and odd traces. The above prediction and update operators can be defined as follows:
\begin{equation}
\label{eq:five}
\mathbf{P}\left[\mathbf{e}\right]_k=\left(\mathbf{P}^{(+)}_k\left[\mathbf{e}_{k-1}\right]+\mathbf{P}^{(-)}_k\left[\mathbf{e}_k\right]\right)/2,
\end{equation}
\begin{equation}
\label{eq:six}
\mathbf{U}\left[\mathbf{r}\right]_k=\left(\mathbf{P}^{(+)}_k\left[\mathbf{r}_{k-1}\right]+\mathbf{P}^{(-)}_k\left[\mathbf{r}_k\right]\right)/4,
\end{equation}
where $\mathbf{P}^{(+)}_k$ and $\mathbf{P}^{(-)}_k$ are operators that predict a trace from its left and right neighbors, correspondingly, by shifting seismic events according to their local slopes.
The local slope can be calculated using a robust algorithm as introduced in \cite{fomel2002pwd}.

\subsection{Comparison of sparsity-promoting transforms}
The well-known exited sparsity-promoting transforms in the exploration geophysics field include the Fourier\cite[]{chandrasekharan1949}, wavelet transform\cite[]{akansu2010}, and curvelet transform \cite[]{candes20061}.

In order to effectively compare the sparseness of different transforms, we first select an input dataset (here, we use the synthetic example shown in Figure \ref{fig:sigmoid-1} as the input dataset). Then we transform the input data into sparse transform domain using different sparse transforms. Figure \ref{fig:sig-fk,sig-dwt,sig-seis,sig-curv-img} shows different transformed domains for the input data. The 2-D Fourier transform in this case means the $f-k$ transform. The 2-D wavelet transform means implementing the 1-D wavelet transform along the temporal direction first and along the spatial direction second. The 2-D seislet transform means implementing the seislet transform along the spatial direction first and 1-D seislet transform along the temporal direction second. The 2-D curvelet transform refers to the 2-D wedge wrapping based fast discrete curvelet transform \cite[]{candes20061}. Next we sort the coefficients in the transform domains into decaying 1-D vectors according to the coefficient amplitude and scale the 1-D vectors. Finally we plot the decaying coefficients with respect to the sequence number for all the transforms in one plot. Figure \ref{fig:sig-c} shows a comparison between the decay of sorted coefficients in the 2-D Fourier transform, 2-D wavelet transform, 2-D seislet transform and 2-D curvelet transform domains. Our experiments show that the seislet coefficients decay significantly faster than coefficients of the other transforms, which indicates a more compact structure of the seislet domain. Thus, our FPOCS is preferred to use the 2-D seislet transform domain as the sparsity-promoting transform.

%Figure \ref{fig:slet,sletthr} shows what the seislet domain looks like for the blended seismic data shown in Figure \ref{fig:blendedsyn}. 
%Figure \ref{fig:slet} shows the seislet domain of Figure \ref{fig:blendedsyn}, Figure \ref{fig:sletthr} shows the thresholded seislet domain. Obviously much blending noise has been removed out after applying soft shresholding.

\inputdir{coef}
\multiplot{4}{sig-fk,sig-dwt,sig-seis,sig-curv-img}{width=0.45\textwidth}{Comparison among different sparsity-promoting transforms based on the synthetic example shown in Figure \ref{fig:sigmoid-1}. (a) 2-D Fourier transform domain. (b) 2-D Wavelet transform domain. (c) 2-D Seislet transform domain. (d) 2-D Curvelet transform domain.}
\plot{sig-c}{width=0.8\textwidth}{Coefficients decreasing diagram of different sparsity-promoting transforms.}

\section{Examples}
We use one synthetic example and one field data example to demonstrate the interpolation effect using the proposed approach. 
The first synthetic example is a combination of linear reflectors, curved reflectors and faults. The original data and decimated data with 30\% randomly removed traces are shown in Figures \ref{fig:sigmoid-1} and \ref{fig:sigmoid-zero-0}, respectively. \old{Figures \ref{fig:fk} and \ref{fig:fk-zero} show the corresponding spectrum of Figures \ref{fig:sigmoid-1} and \ref{fig:sigmoid-zero-0}.} After $f-k$ based POCS and FPOCS, and seislet based POCS and FPOCS, the reconstructed data and their corresponding error sections using different approaches are shown in Figures \ref{fig:data-pocs-fft-0,data-fpocs-fft-1,data-pocs-seis-0,data-fpocs-seis-1} and \ref{fig:diff-pocs-fft,diff-fpocs-fft,diff-pocs-seis,diff-fpocs-seis}, respectively. \wen{In this paper, we use the percentile thresholding strategy \cite[]{yangkang2014halfthr}. The percentile thresholding refers to using a constant percentage of maximum coefficients during the iterations. For the first example, 15 \% coefficients are preserved during the iterations. The percentile thresholding refers to using a constant percentage of maximum coefficients during the iterations.} \old{The corresponding spectrum for four methods are shown in Figure \ref{fig:fk-pocs-fft,fk-fpocs-fft,fk-pocs-seis,fk-fpocs-seis}.}  We zoom in the frame boxes as shown in Figures \ref{fig:sigmoid-1,sigmoid-zero-0} and \ref{fig:data-pocs-fft-0,data-fpocs-fft-1,data-pocs-seis-0,data-fpocs-seis-1}, and show the zoomed sections in Figure \ref{fig:data-z,data-zero-z,data-pocs-fft-z,data-fpocs-fft-z,data-pocs-seis-z,data-fpocs-seis-z} for better comparison. In order to numerically compare the performance, we use the signal-to-noise ratio (SNR): $SNR=10\log_{10}(\Arrowvert\mathbf{d}_{true}\Arrowvert_2^2/\Arrowvert\mathbf{d}_{true}-\mathbf{d}_{inter}\Arrowvert_2^2)$\dlo{.} \wen{, which is widely used in the literature to numerically measure the data recovery error \cite[]{guochang2009,wencheng2015asa}.} We plot the SNR diagram of the first example in Figure \ref{fig:snrs}.  As can be seen from the comparison of different approaches, the seislet based POCS and FPOCS obviously perform better than $f-k$ based POCS and FPOCS, according to both SNR comparison and visual observation. \new{It should be mentioned that the superior performance of FPOCS algorithm depends on the parameter selection (percentage of coefficients in the transformed domain) in the percentile thresholding strategy. Figure \ref{fig:snrs} shows the performances of different algorithms using the best selected parameter (the percentage is 15 \%), while Figure \ref{fig:snrs0} shows the performance of different algorithms using inappropriate parameter (the percentage is 20 \%). It is obvious that in Figure \ref{fig:snrs0}, both seislet based FPOCS and $f-k$ based FPOCS go through an SNR increasing and then decreasing process. Thus, when using the FPOCS algorithm in practice, we might need to have several parameters tuning process in order to select the best parameter.} The reconstructed results using FPOCS and POCS are nearly the same. From the convergence diagram, we can confirm that the FPOCS and POCS converge to the same SNR but FPOCS converges much faster. Figure \ref{fig:trace-comp} shows the amplitude comparison for the 175th trace (as highlighted in Figures \ref{fig:sigmoid-1}, \ref{fig:data-fpocs-fft-1} and \ref{fig:data-fpocs-seis-1}).  It is also obvious that the seislet based FPOCS approach can obtain better performance than the $f-k$ based FPOCS approach. \wen{In addition to the SNR comparison, we also use another newly developed way to measure the recovery performance: the local similarity. The local similarity was initially used to measure the signal reconstruction in the noise attenuation problem \cite[]{yangkang2015ortho}. Here, we borrow the same way to numerically measure the data reconstruction performance. Appendix A gives a short review of the local similarity and its calculation. We use the local similarity in two ways: 1) to calculate the local similarity between the true data and the reconstructed data; 2) to calculate the local similarity between the true data and the estimation error. The higher the former similarity is, the better reconstruction performance is, since such similarity measure the correctness. However, the higher the latter similarity is, the worse reconstruction performance is, since such similarity magnifies the error. Figure \ref{fig:simi-pocs-fft,simi-fpocs-fft,simi-pocs-seis,simi-fpocs-seis} shows the local similarity between the true dataset and the reconstructed data. The two similarity maps on the bottom row obviously contains fewer anomalies than that on the top row, indicating that the two $f$-$k$ based approaches cause more error than the seislet based approaches. Please note that the the maximum local similarity is 1, which means that the two compared signals are exactly the same. Figure \ref{fig:simi-diff-pocs-fft,simi-diff-fpocs-fft,simi-diff-pocs-seis,simi-diff-fpocs-seis} shows the local similarity between the true dataset and the reconstruction error. The two similarity maps on the bottom show small values while the two maps on the top row show high-value anomalies, further confirming the superior performance using the seislet-based approach.} \wen{Figure \ref{fig:tsimi-comp} shows the local similarity comparison (between the reconstructed trace and the true trace), which again confirms that the reconstructed trace using the seislet-based approach is much more similar to the true data.}

In order to compare the difference between IST and POCS (or between FPOCS and FISTA). We do two experiments with clean and noisy irregularly sampled datasets, respectively. For the clean data case, we use the same synthetic example as shown in Figure\wen{s} \ref{fig:sigmoid-1} \wen{and \ref{fig:sigmoid-zero}}. We reconstruct the missing data with seislet POCS, seislet FPOCS, seislet IST, seislet FISTA, and show the convergence diagrams in terms of SNR in Figure \ref{fig:istpocs-snrs}. It is obvious that both seislet POCS and seislet FPOCS obtain better converged results than seislet IST and seislet FISTA, which results from the fact that in POCS based methods the sampled clean data components help constrain the model during the inversion. However, for the noisy data case, as shown in Figure \ref{fig:sigmoidn-zero}, the convergence diagrams show opposite performance compared with the clean data case. Both seislet POCS and seislet FPOCS obtain better converged results than seislet IST and seislet FISTA. This phenomenon results from the fact that during the inversion, the IST based methods can help remove the random noise iteratively while the POCS based approaches maintain the random noise in the known data components. The conclusion from these two experiments can guide us to decide which type of method (POCS or IST) to use in practice according to the level of noise existing in the seismic data: for relatively noisier dataset, the IST (FISTA) method can be superior  because during the thresholding process, the extra random noise will be attenuated gradually; for relatively cleaner dataset, the POCS (FPOCS) method can be superior because the known sampled data help constrain the spatial coherency during the inversion. \new{Currently, we do not have ways to quantify the noise level acceptable for FPOCS. It might be an interesting topic for future investigation.}. The next field data example is from a marine survey, with high data quality, thus we keep using the POCS based approach for comparison

The second example is a field data example, as shown in Figures \ref{fig:sean-1}. The incomplete data by randomly removing 30\% traces is shown in Figure \ref{fig:sean-zero-0}. \old{Figures \ref{fig:sean-fk} and \ref{fig:sean-fk-zero} show the corresponding spectrum of Figures \ref{fig:sean-1} and \ref{fig:sean-zero-0}.} The reconstructed results for the field data example are shown in Figures \ref{fig:sean-pocs-fft-0,sean-fpocs-fft-1,sean-pocs-seis-0,sean-fpocs-seis-1}. \wen{For the field data example, 18 \% coefficients are preserved during the iterations.} The error sections using different approaches are shown in Figure \ref{fig:sean-diff-pocs-fft,sean-diff-fpocs-fft,sean-diff-pocs-seis,sean-diff-fpocs-seis}. It is obvious that the reconstructed data using seislet based approach are much more coherent than $f-k$ based and have less reconstruction error. We also show zoomed sections in Figure \ref{fig:sean-z,sean-zero-z,sean-pocs-fft-z,sean-fpocs-fft-z,sean-pocs-seis-z,sean-fpocs-seis-z} for better comparison. The SNR diagrams are shown in Figure \ref{fig:sean-snrs}. \wen{It also shows a similar conclusion that is consistent with that from the previous synthetic example: the seislet-based approaches can obtain better reconstruction performance and the the FPOCS can obtain much faster convergence.} Because $f-k$ transform is a global transform, $f-k$ based approaches will cause artifacts outside the main data structure, as can be seen at the top of Figure \ref{fig:sean-fpocs-fft-1}. Since the seislet transform is a local transform, it will not cause such artifacts.  Figure \ref{fig:sean-trace-comp} shows the amplitude comparison for the 48th trace (as highlighted in Figures \ref{fig:sean-1}, \ref{fig:sean-fpocs-fft-1} and \ref{fig:sean-fpocs-seis-1}). It is obvious that the seislet based FPOCS has less reconstruction error compared with the $f-k$ based FPOCS. \wen{Figure \ref{fig:sean-simi-pocs-fft,sean-simi-fpocs-fft,sean-simi-pocs-seis,sean-simi-fpocs-seis} shows the local similarity between the true field data and the reconstructed datasets. The two similarity maps on the bottom row have relatively smaller values than that on the top row, indicating that the seislet based approaches can obtain more accurate reconstructed results. The low-value anomalies in the deep-water part are caused by the low-amplitude (nearly zero) deep-water reflections and should not be taken into the consideration in evaluating different performance. Figure \ref{fig:sean-simi-diff-pocs-fft,sean-simi-diff-fpocs-fft,sean-simi-diff-pocs-seis,sean-simi-diff-fpocs-seis} shows the local similarity between the true dataset and the reconstruction error. The two similarity maps on the bottom show small values while the two maps on the top row show high-value anomalies, further confirming the superior performance using the seislet-based approach.} \wen{Figure \ref{fig:sean-tsimi-comp} shows the local similarity comparison for the field data example (between the reconstructed trace and the true trace), which further confirms the aforementioned conclusions.}

\section{Discussions}
\old{There exists a long-standing argument about the sparse transforms: what is the sparsest transform for seismic data? In this paper, we first compare the sparsity of different well-known transforms widely used in the seismic data processing community, including the Fourier transform, the wavelet transform, the curvelet transform, and the seislet transform. The plotted transform domains show that the seislet domain is a very compact domain that is suitable for some sparsity-based processing, such as signal-and-noise separation and sparsity-regularized seismic data interpolation. While the curvelet has been very popular in the general image-processing field since its invention more than one decade ago, it seems not superior in compress well-structured seismic data. For the very typical synthetic example used in this paper, the curvelet transform does not obtain a very compact compression, at least not as sparse as we thought about. The transform domain coefficients decaying curves can further confirm such observation in that the coefficients in the seislet domain decays the fastest, indicating the fact that the maximum amplitude of the compressed coefficients differ the most with the relatively low amplitude. The comparison, to the best of our knowledge, is never done in the literature. This sparse comparison offers us a new view in selecting the sparsest transform for related applications in seismic data processing.}

The seislet transform was proposed in \cite{seislet}.\old{, and} \new{In this paper, we first compare the sparsity of different well-known transforms widely used in the seismic data processing community, including the Fourier transform, the wavelet transform, the curvelet transform, and the seislet transform. The comparison, to the best of our knowledge, is never done in the literature. This sparse comparison offers us a new view in selecting the sparsest transform for related applications in seismic data processing.} \new{The seislet transform} has found successful applications in noise attenuation \cite[]{liuyang20091,seislet}. However, the successful application of the seislet transform in iterative interpolation, especially from the industry, is barely reported. One of the drawbacks that impede the wide application of seislet based interpolation is the efficiency. The seislet transform itself does not slow down the efficiency too much. The efficiency of seislet transform is about 2-4 times slower than the fast Fourier transform, and is about 4-8 times slower than the fast wavelet transform \cite{seislet}.  However, the slope estimation that is required by the seislet transform is much slower. In order to accelerate the process, the slope estimation is commonly estimated every several iterations. In this paper, the slope estimation is iterated every 5 iterations. Even though, the computational cost is still much heavier than the widely used Fourier transform. In this paper, the FPOCS approach can greatly accelerate the efficiency by reducing a large number of iterations. According to the performance of the two examples in the paper, about two thirds iterations can be saved using the fast iterative approach. The cost saving in the paper is only obtained from 2D data examples. The application of 3D seislet-based POCS approach can even offer more cost savings,  which will potentially allow the wide application of the seislet transform in the industry.

The widely used POCS and IST algorithms can be both considered as the simplest and most effective iterative approaches for seismic data interpolation. In a mathematical sense, the IST is a type of POCS, the multiple projections include the weighted projection (model update), the forward sparse transform, the soft thresholding, and the inverse sparse transform. However, in the community of exploration geophysics, the IST algorithm and the POCS algorithm are different. The most apparent difference is whether to use the known data as a part of the model.  However, there is no published literature discussing the performance difference using the two approaches. We use a group of two simple but convincing tests with and without strong random noise to show the slight difference between the two approaches. The selection of the two approach simply depends on the noise level in the seismic data. When the noise level is high, we should use the IST based approach (FIST), otherwise, we should use the POCS based approach (FPOCS).

How to measure data recovery performance is another long-standing argument in the seismic data processing community. In the case of simulated test, in which we know the true answer, the traditionally used signal-to-noise ratio (SNR) seems to be the best choice. However, the SNR can only obtain a global measurement of the recovery quality while the local performance is not measured effectively. For example, an extrema (or huge error) in a local area will also result in a small global average. We use the local similarity \cite[]{fomel2007localattr} as a way to measure the data reconstruction performance in this paper. This evaluation is based on the assumption that the true signal and the estimated should have high local similarity and the true signal and the estimation error should have low local similarity. From the local similarity maps, we can get more details of different approaches. We can observe clearly that, even in the case of very close SNRs, the local similarity can still show slight but obvious difference, which makes it more sensitive in comparing different state-of-the-art approaches.

\section{Conclusion}
We have proposed a novel fast\dlo{er} projection onto convex sets (FPOCS) solver for compressive sensing of seismic data via sparsity constraint in seislet transform domain. The seislet transform is demonstrated to be much sparser than other state-of-the-art sparse transforms and thus is more suitable for a compressive sensing based seismic data recovery approach. The FPOCS can obtain much faster convergence than conventional POCS\wen{, which can potentially make the seislet-based POCS approach applicable in practice according to the efficiency acceleration}. \wen{We have found that the the POCS based approach can be superior than the IST based approach in relatively cleaner dataset while can be slightly worse than the IST based approach in relatively noisier dataset. This conclusion can guide us to use different iterative approach according to the noise level in the data. In addition to the signal-to-noise ratio (SNR), the local similarity is also used to measure the data recovery performance. We are surprisingly to find out that even in the case of very close SNRs, the local similarity can still show slight but obvious difference, and thus the local similarity measurement is more sensitive in comparing different state-of-the-art approaches.} The seislet transform based compressive sensing can achieve obviously better data recovery results than $f-k$ transform based scenarios because of a much sparser structure in the seislet transform domain. We have used both synthetic and field data examples to demonstrate the superior performance of the proposed seislet-based FPOCS approach.

\section*{Acknowledgements}
We would like to thank Jianwei Ma and Sergey Fomel for fruitful discussions about compressive sensing and the seislet transform. \wen{We also thank Jyoti Behura and one anonymous reviewer for constructive suggestions that improve the manuscript greatly.} This research is supported by the National Natural Science Foundation of China (Grant No.41274137), the National Science and Technology of Major Projects of China (Grant No. 2011ZX05019-006), and National Engineering Laboratory of Offshore Oil Exploration.

\inputdir{synth}
\multiplot{4}{sigmoid-1,sigmoid-zero-0}{width=0.46\columnwidth}{(a) Synthetic data. (b) Decimated synthetic data with 30\% removed traces. \old{(c) \& (d) are the $f$-$k$ spectrum corresponding to (a) and (b).}}

\multiplot{4}{data-pocs-fft-0,data-fpocs-fft-1,data-pocs-seis-0,data-fpocs-seis-1}{width=0.46\columnwidth}{(a)-(d) Reconstructed sections corresponding to POCS with $f$-$k$ thresholding, FPOCS with $f$-$k$ thresholding, POCS with seislet thresholding and FPOCS with seislet thresholding.}

\multiplot{4}{simi-pocs-fft,simi-fpocs-fft,simi-pocs-seis,simi-fpocs-seis}{width=0.46\columnwidth}{\wen{Local similarity between the reconstructed sections with the true data using different approaches. (a) $f$-$k$ POCS. (b) $f$-$k$ FPOCS. (c) Seislet POCS. (d) Seislet FPOCS. } }

\multiplot{4}{diff-pocs-fft,diff-fpocs-fft,diff-pocs-seis,diff-fpocs-seis}{width=0.46\columnwidth}{(a)-(d) Reconstruction error sections corresponding to Figures \ref{fig:data-pocs-fft-0}-\ref{fig:data-fpocs-seis-1}, respectively. }

\multiplot{4}{simi-diff-pocs-fft,simi-diff-fpocs-fft,simi-diff-pocs-seis,simi-diff-fpocs-seis}{width=0.46\columnwidth}{\wen{Local similarity between the error sections with the true data using different approaches. (a) $f$-$k$ POCS. (b) $f$-$k$ FPOCS. (c) Seislet POCS. (d) Seislet FPOCS. } }

%\multiplot{4}{fk-pocs-fft,fk-fpocs-fft,fk-pocs-seis,fk-fpocs-seis}{width=0.46\columnwidth}{(a)-(d) $f$-$k$ spectrum corresponding to the reconstructed sections Figures \ref{fig:data-pocs-fft-0}-\ref{fig:data-fpocs-seis-1}.}

\multiplot{6}{data-z,data-zero-z,data-pocs-fft-z,data-fpocs-fft-z,data-pocs-seis-z,data-fpocs-seis-z}{width=0.46\columnwidth}{Zoomed sections. (a) True data. (b) Decimated data. (c) POCS with $f$-$k$ thresholding. (d) FPOCS with $f$-$k$ thresholding. (e) POCS with seislet thresholding. (f) FPOCS with seislet thresholding.}

\inputdir{./}
\plot{snrs}{width=0.8\textwidth}{SNR comparison of the synthetic example\old{.}\new{, when the best parameter is selected.}}

\plot{snrs0}{width=0.8\textwidth}{\new{SNR comparison of the synthetic example, when the inappropriate parameter is selected.}}

\inputdir{synth}
%\plot{trace-comp}{width=0.8\textwidth}{Amplitude comparison. Black solid line denotes the true trace. Red dot dash line denotes FPOCS with seislet thresholding. Green dash line denotes FPOCS using $f$-$k$ thresholding.  }

\multiplot{2}{trace-comp,tsimi-comp}{width=0.65\textwidth}{\dlo{Amplitude comparison. Black solid line denotes the true trace. Red dot dash line denotes FPOCS with seislet thresholding. Green dash line denotes FPOCS using $f$-$k$ thresholding.} \wen{(a) Amplitude comparison. (b) Local similarity comparison. Black solid line denotes the true trace. Red dot dashed line denotes FPOCS with seislet thresholding. Green dashed line denotes FPOCS using $f$-$k$ thresholding. Note that the amplitude using seislet thresholding is much closer to the true amplitude and the local similarity using seislet thresholding is much closer to the maximum similarity: 1.} }

\inputdir{./}
\multiplot{4}{sigmoid-zero,istpocs-snrs,sigmoidn-zero,istpocsnoise-snrs}{width=0.45\textwidth}{\dlo{(b) Noisy irregularly sampled synthetic example. (b) Comparison of POCS (FPOCS) and IST (FISTA) of noisy data in terms of SNR. ".,*,o,-" correspond to seislet FPOCS, seislet POCS, seislet FISTA, and seislet IST.}\wen{(a) Clean synthetic data. (b) Comparison of POCS (FPOCS) and IST (FISTA) of clean data in terms of SNR. (c) Noisy synthetic data. (d) Comparison of POCS (FPOCS) and IST (FISTA) of noisy data in terms of SNR.}}

\inputdir{sean}
\multiplot{4}{sean-1,sean-zero-0}{width=0.41\columnwidth}{\wen{Field data example.} (a)\dlo{Field data.}\wen{True field data.} (b) Decimated field data with  30 \% removed traces. \old{(c) \& (d) are the $f$-$k$ spectrum corresponding to (a) and (b).}}

\multiplot{4}{sean-pocs-fft-0,sean-fpocs-fft-1,sean-pocs-seis-0,sean-fpocs-seis-1}{width=0.41\columnwidth}{\wen{Field data example.} (a)-(d) Reconstructed sections corresponding to POCS with $f$-$k$ thresholding, FPOCS with $f$-$k$ thresholding, POCS with seislet thresholding and FPOCS with seislet thresholding. Note the artifacts caused by the $f$-$k$ based methods, as pointed out by the arrows.}

\multiplot{4}{sean-simi-pocs-fft,sean-simi-fpocs-fft,sean-simi-pocs-seis,sean-simi-fpocs-seis}{width=0.46\columnwidth}{\wen{Field data example.} \wen{Local similarity between the reconstructed sections with the true data using different approaches. (a) $f$-$k$ POCS. (b) $f$-$k$ FPOCS. (c) Seislet POCS. (d) Seislet FPOCS. } }

\multiplot{4}{sean-diff-pocs-fft,sean-diff-fpocs-fft,sean-diff-pocs-seis,sean-diff-fpocs-seis}{width=0.41\columnwidth}{\wen{Field data example.} (a)-(d) Reconstruction error sections corresponding to Figures \ref{fig:sean-pocs-fft-0}-\ref{fig:sean-fpocs-seis-1}, respectively.}

\multiplot{4}{sean-simi-diff-pocs-fft,sean-simi-diff-fpocs-fft,sean-simi-diff-pocs-seis,sean-simi-diff-fpocs-seis}{width=0.46\columnwidth}{\wen{Field data example.} \wen{Local similarity between the error sections with the true data using different approaches. (a) $f$-$k$ POCS. (b) $f$-$k$ FPOCS. (c) Seislet POCS. (d) Seislet FPOCS. } }

%\multiplot{4}{sean-fk-pocs-fft,sean-fk-fpocs-fft,sean-fk-pocs-seis,sean-fk-fpocs-seis}{width=0.41\columnwidth}{\wen{Field data example.} (a)-(d) $f$-$k$ spectrum corresponding to the reconstructed sections Figures \ref{fig:sean-pocs-fft-0}-\ref{fig:sean-fpocs-seis-1}.}

\multiplot{6}{sean-z,sean-zero-z,sean-pocs-fft-z,sean-fpocs-fft-z,sean-pocs-seis-z,sean-fpocs-seis-z}{width=0.41\columnwidth}{Zoomed sections \wen{of the field data example}. (a) True data. (b) Decimated data. (c) POCS with $f$-$k$ thresholding. (d) FPOCS with $f$-$k$ thresholding. (e) POCS with seislet thresholding. (f) FPOCS with seislet thresholding.}
\inputdir{./}
\plot{sean-snrs}{width=0.8\textwidth}{\dlo{SNR of field data (".,*,o,-" correspond to seislet FPOCS, seislet POCS, $f-k$ FPOCS and $f-k$ POCS).} \wen{SNR comparison of the field data example.}}
\inputdir{sean}
\multiplot{2}{sean-trace-comp,sean-tsimi-comp}{width=0.65\textwidth}{\dlo{Amplitude comparison. Black solid line denotes the true trace. Red dot dash line denotes FPOCS with seislet thresholding. Green dash line denotes FPOCS using $f$-$k$ thresholding.} \wen{Field data example. (a) Amplitude comparison. (b) Local similarity comparison. Black solid line denotes the true trace. Red dot dashed line denotes FPOCS with seislet thresholding. Green dashed line denotes FPOCS using $f$-$k$ thresholding. Note that the amplitude using seislet thresholding is much closer to the true amplitude and the local similarity using seislet thresholding is much closer to the maximum similarity: 1.} }

\wen{\append{Review of local similarity}
A common way to measure the similarity between two signals is to calculate the global correlation coefficient:
\begin{equation}
\label{eq:simi}
\gamma=\frac{\displaystyle\sum_{i=1}^Na(i)b(i)}{\displaystyle\sqrt{\sum_{i=1}^Na^2(i)\sum_{i=1}^Nb^2(i)}},
\end{equation}
where $r$ is the global correlation coefficient, $N$ denotes the number of samples of the signals $\mathbf{a}$ and $\mathbf{b}$. In order to calculate the similarity between two signals locally, one can use the localized correlation coefficient:
\begin{equation}
\label{eq:simi}
\gamma_m(t)=\frac{\displaystyle\sum_{i=t-m/2}^{t+m/2} a(i) b(i)}{\sqrt{\displaystyle\sum_{i=t-m/2}^{t+m/2} a^2(i) \displaystyle\sum_{i=t-m/2}^{t+m/2} b^2(i) }},
\end{equation}
where $\gamma_m(t)$ denotes the local correlation coefficient, $m$ is the local window size.}
\par
\wen{\cite{fomel2007localattr} designed an elegant way to calculate the local similarity: 
\begin{align}
\label{eq:local}
\gamma(t) & =\sqrt{\gamma_1(t)\gamma_2(t)}, \\
\label{eq:local1}
\gamma_1(t)&=\arg\min_{\gamma_1(t)} \left(\sum_{t}(a(t)-\gamma_1(t)b(t)) + R(\gamma_1(t)) \right), \\
\label{eq:local2}
\gamma_2(t)&=\arg\min_{\gamma_2(t)} \left(\sum_{t}(b(t)-\gamma_2(t)a(t)) + R(\gamma_2(t)) \right).
\end{align}
Equation \ref{eq:local} represents that the local similarity can be expressed as the product of two vectors that are the solutions of two minimization problems. $R$ is a regularization operator for constraining $\gamma_1$ and $\gamma_2$. $R$ can be chosen as a local triangular smoother to enforce the smoothness of vectors $\gamma_1$ and $\gamma_2$, and then equations \ref{eq:local1} and \ref{eq:local2} can be solved using the shaping regularization \cite[]{fomel2007shape}:
\begin{align}
\label{eq:local3}
\mathbf{\gamma}_1 &= [\lambda_1^2\mathbf{I} + \mathcal{S}(\mathbf{B}^T\mathbf{B}-\lambda_1^2\mathbf{I})]^{-1}\mathcal{S}\mathbf{B}^T\mathbf{a},\\
\label{eq:local4}
\mathbf{\gamma}_2 &= [\lambda_2^2\mathbf{I} + \mathcal{S}(\mathbf{A}^T\mathbf{A}-\lambda_2^2\mathbf{I})]^{-1}\mathcal{S}\mathbf{A}^T\mathbf{b},
\end{align}
where $\mathbf{A}$ is a diagonal operator composed from the elements of $\mathbf{a}$: $\mathbf{A}=diag(\mathbf{a})$ and $\mathbf{B}$ is a diagonal operator composed from the elements of $\mathbf{b}$: $\mathbf{B}=diag(\mathbf{b})$. $\mathbf{\mathcal{S}}$ is a smoothing operator, and $\lambda_1$ and $\lambda_2$ are two parameters controlling the physical dimensionality and enabling fast convergence when inversion is implemented iteratively. These two parameters can be chosen as the least-squares norms of $\mathbf{A}$ and $\mathbf{B}$ \cite[]{fomel2007localattr}. The local similarity algorithm can be used to calculate the local similarity of signal of any dimension. For 1D signals, the meanings of equations \ref{eq:local3} and \ref{eq:local4} are intuitive. For 2D or higher-dimensional signals, each signal is first reshaped into a 1D signal and then follows equations \ref{eq:local3} and \ref{eq:local4} to calculate the local similarity vector. The smoothing operator is applied to the 2D or multi-dimensional form of the original signal to enforce the smoothness in any dimension.}

\bibliographystyle{seg}
\bibliography{cs}

### 2020-09-16 dbdl/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\title{Learning the blending spikes using sparse dictionaries}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\author{Yangkang Chen\footnotemark[1], Shaohuan Zu\footnotemark[1], Wei Chen\footnotemark[2]\footnotemark[3], Mi Zhang\footnotemark[4],  and Zhe Guan\footnotemark[5]}
\ms{GJI-2020}

\address{
\footnotemark[1]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
yangkang.chen@zju.edu.cn \\
\footnotemark[2]Key Laboratory of Exploration Technology for Oil \\
and Gas Resources of Ministry of Education\\
Yangtze University\\
Daxue Road No.111\\
Caidian District, Wuhan, China, 430100\\
\footnotemark[3]Hubei Cooperative Innovation Center of Unconventional Oil and Gas\\
Daxue Road No.111\\
Caidian District, Wuhan, China, 430100\\
chenwei\_yangtze@126.com \\
\footnotemark[4]State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
cupmi@sina.com \\
\footnotemark[5]
Applied Physics Program\\
Rice University\\
Houston, TX, USA\\
Zhe.Guan@rice.edu\\
}

\lefthead{Chen et al.}
\righthead{Learning the spikes}

\begin{abstract}
Deblending plays an important role in preparing \dlo{the }high-quality seismic data from modern blended simultaneous-source seismic acquisition. \dlo{The s}\wen{S}tate-of-the-art deblending\dlo{ method} is based on the \old{sparsity-constraint}\new{sparsity-constrained} iterative inversion. \dlo{The inversion}\wen{Inversion} based deblending\dlo{ method} assumes that the ambient noise level is low and the data misfit during iterative inversion accounts for the random ambient noise. The traditional method becomes problematic when the random ambient noise becomes extremely strong and the inversion iteratively fits the random noise instead of the signal and blending interference. We propose a \dlo{novel }constrained inversion model that takes the strong random noise into consideration and can achieve satisfactory result even when strong random noise exists. The principle of \dlo{the}\wen{this} new method is that we use sparse dictionaries to learn the blending spikes and thus the learned dictionary atoms are able to distinguish between blending spikes and random noise. The separated signal and blending spikes can then be better fitted by the iterative inversion framework. \dlo{A set of synthetic}\wen{Synthetic} and field data examples are used to demonstrate the performance of the new approach. \\
\textbf{Keywords}\\
Geophysical methods, Time series analysis, Image processing, Seismology
\end{abstract}

%\section{Keywords}
%key1,key2,key3

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}

\section{Introduction}
Simultaneous-source acquisition technique is a breakthrough in modern seismic data acquisition \cite[]{beasleycj2008,berkhout2008,abma2009,beasley2012,berkhout2012,wapenaark2012,qushan2015,abma2015,shaohuan2017jag,asgedom2017rough,zhang2017improving,kim2017efficient,shaohuan2017jag,wang2017building,wujuan2018jse1,amundsen2017multi}. It removes the limit of large temporal/spatial interval between adjacent shots or consecutive shots by allowing multiple sources to be fired simultaneously. The technique can not only improve the quality of recorded seismic data by increasing the spatial sampling rate but also increase the acquisition efficiency by decreasing the shot interval between two consecutive shots. However, the simultaneous-source acquisition will cause strong crosstalk interference in the recorded data, which makes the subsequent seismic data processing challenging. Because of the benefits of the revolutionary acquisition concept and the challenges involved in the processing and imaging framework, the technique has attracted much attention from both industry and academia \cite[]{mahdad2011,mahdad2012,panagiotis20122,arazthesis2012,qushan2014,sixuethesis2014,yanhui2014,sixue2015,halliday2015,benfengpocs,sixuethesis2014,sixue2015,yangkang2016irr5d,Robertsson2016Signal,andersson2017flawless,yatong2018gji,baimin2018jse2,yatong2018dbi,yatong2018jse}.

The \dlo{blended }simultaneous-source seismic data can either be separated first and then be used for seismic imaging or be used directly for imaging. The former strategy is referred to as \dlo{the }deblending\dlo{ process} while the latter strategy is referred to as\dlo{ the} direct imaging\dlo{ method}. Deblending can provide a dataset that is similar to those datasets acquired from \dlo{the}\wen{a} traditional acquisition system, thus does not require the modification of the \wen{present} seismic imaging algorithms. However, due to its \dlo{dependency}\wen{dependence} on the pre-processing of massive blended data, it is more computationally expensive. The direct imaging method avoids the pre-processing step, but requires a carefully modified seismic imaging framework. A number of great breakthroughs have been made on direct imaging of simultaneous-source data recently \cite[]{verschuur2011,shuwei2016vscan,kui2016,kui20162,shaohuan2017,baimin2017jse1,yangkang2017lsrtm,wujuan2018cg1,baimin2018jse1,baimin2018cg,qingchen2018tgrs,qingchen2018gji,yangkang2019lsrtm}, thus in this paper we limit the discussion only on the deblending methods.

Among all the deblending methods, most are based on the spatial coherency of useful signals and incoherency of blending interference \cite[]{wujuan2019jse1}. To promote the coherency of useful signals, the seismic data should be sorted into the common receiver domain, common midpoint domain or common offset domain. In the ocean bottom node (OBN) seismic surveys, the seismic data is recorded in the common receiver domain, thus, it is straightforward to apply the deblending algorithms without domain transformation \cite[]{arazthesis2012}. \cite{kim2009} applied an offset-domain prediction and subtraction method to iteratively attenuate the blending spikes. The blending spikes refer to the blending noise. Because the blending noise is spatially discontinuous and has abnormal value, like spikes, we call the blending noise \old{as }blending spikes throughout the paper. \cite{yangkang20142} initially proposed a general iterative framework for iterative estimation and subtraction of blending spikes based on the shaping regularization method. In the shaping regularization framework, most iterative deblending methods can be understood in the same way except for a different constraint or assumption for the model.

A large group of deblending methods are based on the sparsity. \cite{akerberg2008} proposed an iterative deblending method based on the Radon transform. \cite{abma2009} used the Fourier transform to promote the sparsity of useful signals and developed an effective deblending method, which has now been widely applied in the industry. \cite{yangkang20142} used the seislet transform, which is assumed to be the sparest transform for seismic data, to promote the sparsity of useful signals and separate the crosstalk noise. \cite{yangkang2015dbortho} further extend the seislet constraint to a hybrid orthogonalization and seislet constraint to better separate the blended sources. \cite{shaohuan20161} used the curvelet transform as the sparse domain to separate the blended sources. They also pointed out that the traditional random dithering sequences are not optimal in practical deployment of the technique in the field and proposed a periodic shot scheduling sequence for blended acquisition. \cite{yaru20172} used the high-order sparse Radon transform to deal with the amplitude-variation-with-offset (AVO) phenomenon that is usually neglected in deblending frameworks. \cite{yatong2018seis} applied the seislet frame transform to filter out blending spikes in the presence of multiples. Because the multiples have different local slopes, the seislet frame transform\dlo{ instead of seislet transform} is used to sparsify multiples with different orders. In addition to the sparsity constraint \cite[]{mostafa2016geo,mostafa2016bssa}, the rank constraint is also used for the deblending purposes \cite[]{yaru2016dblend,zhangdong2016cseg,zhangdong2016seg,zhangdong2016eage,wujuan2018jge3,baimin2019jag}. \cite{jinkun2015} developed the iterative rank-reduction method for deblending simultaneous-source data, where the singular spectrum analysis (SSA) filter is applied as the shaping operator. \cite{yatong2017ieee} applied the structural rank-reduction method for attenuating the blending spikes, where the rank-one approximation filter is applied as the rank-reduction operator. Similar to the sparsity and rank constraints, the coherency constraint was proposed by \cite{shaohuan2017gji} to deal with the complicated situations where data structure is complex and the number of simultaneous sources is large.

%\cite{yatong2018seis} propose
Another mainstream method for deblending is not based on the coherency difference between useful signals and blending spikes. According to the local slope difference between signals and noise, \cite{hampson2008} applied a dip filter to remove the blending interference in common shot gathers. \cite{sixue2015} analyzed the disadvantage of the receiver-domain deblending methods and proposed a shot-domain deblending method based on the shot repetition concept. They argue that data in the receiver domain are usually under-sampled and is \dlo{easier}\wen{more prone} to cause the aliasing problem than the data in shot domain. \cite{shuwei20163} developed an iterative seislet frame thresholding method to separate simultaneous-source data in the shot domain. The seislet frame can compress the \dlo{master shot and interference shot}\wen{signal and interference} according to their individual slope maps, which can be calculated directly from the blended data in the shot domain. \cite{shaohuan2017} proposed a least-squares method for separating the \dlo{master shot and interferening shot}\wen{signal and interference} in the shot domain. The crux of the least-squares method is constructing two convolutional filters to set up a least-squares estimation problem. The convolutional filters are constructed based on the plane-wave approximation of wave equation.

In this paper, we address the problem of strong ambient noise in iterative inversion based deblending framework. It is known that the iterative inversion method is based on small random noise level, i.e., small and negligible data misfit. The source-separation inversion uses least-squares method to adjust the data misfit caused by random ambient noise. When the noise level is high, the least-squares method will try to fit the noise component instead of the blended signal components. To unravel the challenge in deblending when strong random noise exists, we propose a method to distinguish the blended signal components and the random noise by designing a dictionary that can best represent the waveform structure of both signal and blending spikes. By learning the structure of \wen{the} blending spikes, we are able to separate the blending spikes from random noise and thus make the iterative inversion robust. We first briefly introduce the sparse-inversion framework for the deblending problem and then introduce the dictionary learning constrained deblending framework in detail. To illustrate the philosophy of the presented method, we use \dlo{extensive }numerical examples to demonstrate the performance of the new method.

The concept of sparse dictionary learning \cite[]{mairal2009online}, originated from image processing field,  and is not new in geophysics. Many applications of the sparse dictionary learning algorithm have been investigated in the geophysics literature \cite[]{jianwei20142,yangkang2016dsd,amir2017geo,amir2017}. However, most of the applications are about representing spatially coherent reflection seismic events in a sparse way so that the spatially incoherent components can be easily separated during the sparse learning process. The application of the sparse dictionary learning algorithm here is somewhat contradicting with the mainstream studies, i.e., we want to represent the blending spikes using the sparse dictionary learning method. The benefit of the sparse representation of blending spikes is that we can relieve the influence of the random noise to iterative deblending of simultaneous-source data by separating the random noise based on the hybrid-sparsity constrained model for deblending. This type of application of dictionary learning is unusual not only in the deblending literature, but also in the whole seismic data processing community. Blending spikes, due to its spatial incoherency property, are thought to be excluded from being \old{learned into}\new{learned by} the dictionary atoms \cite[]{yanhui2014,yanhui2016}. However, in this paper, we have shown using extensive examples that the blending spikes can be learned via a normal sparse dictionary learning algorithm for being separated from random noise and their features can be well captured by the dictionary atoms. This phenomenon can be attributed to the fact that although the blending spikes are not spatially coherent, they are temporally coherent. The blending spikes share the same properties with the useful primary signals when viewed in the time \old{direction}\new{dimension}. We infer that the temporal coherency property of the blending spikes \old{make}\new{makes} them easy to be learned by a typical sparse dictionary learning algorithm, e.g., the K-SVD method \cite[]{aksvd2008}. From the experiments and results shown in this paper, we are questioning the possibility of using a sparse dictionary learning based algorithm to separate the blending interference from the primary reflection signals, e.g., the work from \cite{yanhui2014}. If we do want to apply the sparse dictionary learning method to separate the blending spikes only, we need to adjust the typical dictionary learning algorithm so that the blending spikes cannot be taken into consideration when constructing the dictionary atoms. For example, constraining the dictionary atoms not to contain spikes may be a potential solution.

\section{Method}
\subsection{Iterative deblending as an optimization problem}
Regularized iterative deblending is equivalent to solving the following optimization problem \cite[]{yangkang20142,shaohuan2015,shuwei2015seg1,qushan2016,shaohuan2016seg2}
\wen{	\begin{equation}
		\label{eq:db}
	\begin{split}
	&\arg\min\limits_\mathbf{m}\Vert \mathbf{d}-\mathbf{F}\mathbf{m}\Vert_2^2,\\
	&\text{s.t.}\quad \Omega(\mathbf{m}) \le T,
	\end{split}
	\end{equation}}
where $\Omega(\mathbf{m})$ denotes the regularization operator. \wen{$\mathbf{m}$ and $\mathbf{d}$ denote the unblended and blended data, respectively. Both $\mathbf{m}$ and $\mathbf{d}$ are in the data space. $\mathbf{F}$ is the blending operator, which maps the unblended data to the blended data. Detailed formulation of the forward operator $\mathbf{F}$ can be found in \cite{yangkang20142}. $T$ denotes a regularization constraint. $\Omega(\cdot)$ here is a generalized form of a regularization operator. $\Vert \cdot \Vert_2$ denotes the $L_2$ norm.  }

When a transform-domain sparsity constraint is chosen as the regularization ($\Omega(\cdot)$) \cite[]{yangkang20142,shaohuan20161}, equation \ref{eq:db2} becomes 
\wen{	\begin{equation}
		\label{eq:db2}
	\begin{split}
	&\arg\min\limits_\mathbf{m}\Vert \mathbf{d}-\mathbf{F}\mathbf{m}\Vert_2^2,\\
	&\text{s.t.}\quad \parallel \mathbf{A}\mathbf{m}\parallel_0 \le T,
	\end{split}
	\end{equation}}
	where $\mathbf{A}$ denotes the forward sparse transform, e.g., the seislet transform \cite[]{fomel2010seislet}, or the curvelet transform \cite[]{candes20061}.  \wen{$\Vert \cdot \Vert_0$ denotes the $L_0$ norm.  Here, $T$ constrains the number of non-zero entries in the transform domain smaller than or equal to T.}

%	Solving equation \ref{eq:db2} is NP-hard and thus an approximate solution, like the unconstrained $L_1$ norm regularized optimization problem as follows:
%	\begin{equation}
%		\label{eq:db2}
%	\begin{split}
%	&\arg\min\limits_\mathbf{m}\Vert \mathbf{y}-\mathbf{F}\mathbf{m}\Vert_F^2,\\
%	&\text{s.t.}\quad \parallel \mathbf{A}(\mathbf{m})\parallel_0 < T,
%	\end{split}
%	\end{equation}

The optimization problem shown in equations \ref{eq:db} and \ref{eq:db2} is based on the assumption that 
\begin{equation}
\label{eq:ass}
\mathbf{d}\approx \mathbf{F}\mathbf{m}.
\end{equation}
Equation \ref{eq:ass} holds in the case of weak random noise. However, when noise level is strong, the data-fitting term $\mathbf{d}-\mathbf{F}\mathbf{m}$ in equations \ref{eq:db} and \ref{eq:db2} will be problematic and will cause overfitting. The iterative minimization of the data misfit will make the strong random noise fitted by the model and the \dlo{resulted}\wen{resulting} solution far from accurate.

\subsection{Dictionary learning constrained optimization problem}
To take the influence of strong random noise into consideration, we propose the following optimization model:
\wen{	\begin{equation}
		\label{eq:db3}
	\begin{split}
	\arg&\min_{\mathbf{m},\mathbf{D},\mathbf{C} }\parallel\mathbf{R}^{-1}(\mathbf{DC})-\mathbf{F}\mathbf{m}\parallel_2^2 \\
	\text{s.t.}\quad & \Vert \mathbf{Y}-\mathbf{D}\mathbf{C}\Vert_F^2\le T_0,\\
	&\parallel\mathbf{C} \parallel_0\le T_1,\\
	& \parallel \mathbf{A}\mathbf{m}\parallel_0 \le T_2.
	\end{split}
	\end{equation}}

In equation \ref{eq:db3}, $\Vert \mathbf{Y}-\mathbf{D}\mathbf{C}\Vert_F^2\le T_0$ denotes the dictionary learning constraint. $\mathbf{Y}$ denotes the patches constructed from the raw blended data that contains extremely strong noise. $\mathbf{D}$ denotes the sparse dictionary. $\mathbf{C}$ denotes the sparse coefficients in the \wen{windowed} sparse dictionary domain. \wen{$T_1$ and $T_2$ denote the second and third constraints.} $\mathbf{R}^{-1}$ denotes the inverse mapping from the patch domain to data domain. \wen{$\parallel\cdot \parallel_F$ denotes the Frobenius norm.}

The learning process uses patch-based samples. In this paper, preparing the training samples from the seismological datasets is referred to as the patching process. Correspondingly, \old{reconstruct}\new{reconstructing} the seismological datasets from filtered patches is referred to as the unpatching process. The patching ($\mathbf{R}$) and unpatching ($\mathbf{R}^{-1}$) processes are illustrated in Figure \ref{fig:demo}. In the patching process, we slide a window of the patch size from the top to the bottom, and the left to the right, of the 2D seismic data. Thus, we obtain a patch in each sliding step. To avoid the discontinuity between patches when reconstructing, each pair of neighbor patches share an overlap. The size of the overlapping part is called the shift size. In this paper, we define the shift size as half of the patch size. A large patch size would make the learning process miss small-scale features while a small patch size would make the learning process incapable of learning meaningful waveform features. In this paper, we define the patch size as approximately half of the dominant wavelength of data. The patches obtained from the sliding process are arranged to be a 2D matrix, which is put into the learning process. In the unpatching process, we reinsert each filtered patch from the 2D data matrix back into the seismological datasets. In the overlapping part of the reconstructed trace, we take the average of the two neighbor patches.

We solve the problem in equation \ref{eq:db3} via a two-step strategy. We first divide the optimization problem into two sub-problems as follows:
\begin{equation}
\label{eq:opt1}
\text{1.}\quad \arg \min_{\mathbf{D},\mathbf{C}} \Vert \mathbf{Y}-\mathbf{D}\mathbf{C}\Vert_F^2\quad\text{s.t.}\quad\parallel\mathbf{C} \parallel_0\le T_1.
\end{equation}
\wen{\begin{equation}
\label{eq:opt2}
\text{2.} \quad \arg \min_{\mathbf{m}}\parallel\mathbf{R}^{-1}(\mathbf{DC})-\mathbf{F}\mathbf{m}\parallel_2^2 \quad \text{s.t.}\quad \parallel \mathbf{A}\mathbf{m}\parallel_0 \le T_2.
\end{equation}}
Equation \ref{eq:opt1} refers to the sparse dictionary learning problem. To solve it, two steps are taken iteratively. The first step is called sparse coding, meaning that given the dictionary matrix $\mathbf{D}$, we use \wen{a} sparse coding algorithm to update the coefficients
\wen{\begin{equation}
\label{eq:Code}
\forall_i \mathbf{c}_i ^n = \arg \min_{\mathbf{c}_i} \parallel \mathbf{Y} - \mathbf{D}\mathbf{C}^n \parallel_F^2,\quad \text{s.t.} \quad \forall_i \parallel \mathbf{c}_i \parallel_0 \le T.
\end{equation}
  The second step is called the dictionary updating, meaning that given the sparse coefficient matrix $\mathbf{C}$, we seek the optimal dictionary matrix $\mathbf{D}$ to fit the input data. 
\begin{equation}
\label{eq:Dic}
\mathbf{D}^{n+1} = \arg\min_{\mathbf{D}} \parallel \mathbf{Y} - \mathbf{D}^n\mathbf{C} \parallel_F^2.
\end{equation}}
\wen{The orthogonal matching pursuit (OMP) algorithm \cite[]{aksvd2008} is usually used to solve the sparse coding problem.} The OMP algorithm selects the atom with highest correlation with the current residual each time. The K-SVD algorithm \cite[]{aksvd2008} is often taken to update the dictionary given the sparse coefficients. In the K-SVD algorithm, updating the dictionary atoms aims to solve the minimizing the following misfit
	\begin{equation}
	\begin{array}{ccl}
	\left\Vert\mathbf{Y}-\mathbf{D}\mathbf{C}\right\Vert_F^2 &= &\left\Vert\mathbf{Y}- \sum\limits_{j=1}^{K}\mathbf{d}_j\mathbf{c}_j^T\right\Vert_F^2\\
	&=&\left\Vert\left(\mathbf{Y}- \sum\limits_{j\neq k}\mathbf{d}_j\mathbf{c}_j^T\right)-\mathbf{d}_k\mathbf{c}_k^T\right\Vert_F^2\\
	&=&\left\Vert \mathbf{E}_k-\mathbf{d}_k\mathbf{c}_k^T	\right\Vert_F^2,
	\end{array}
	\label{eq:ksvd}
	\end{equation}
where $\mathbf{E}_k$ denotes the error matrix when the $k$th atom is missing. $d_k$ and $a_k$ denote the $k$th atom vector and coefficient vector, respectively. Minimizing the misfit in equation \ref{eq:ksvd} can be sovled easily via the K-SVD algorithm \cite[]{aksvd2008,shaohuan2019ieee}. \dlo{Since K SVD decompositions are involved, the algorithm is thus called K-SVD algorithm.}The K-SVD algorithm is computationally demanding and faster algorithm for updating the dictionary matrix $\mathbf{D}$ is also possible \cite[]{yangkang2017sgk}.

The second subproblem can be solved using the iterative shaping regularization method
	\begin{equation}
	\mathbf{m}_{n+1}=\mathbf{S}\left[\mathbf{m}_n+\mathbf{B}\left(\mathbf{R}^{-1}\left(\mathbf{D}\mathbf{A}\right)-\mathbf{F}\mathbf{A}\mathbf{m}_n\right)\right],
	\label{eq:shape}
	\end{equation}
where the $\mathbf{B}$ is the backward operator and is defined as $\mathbf{B}=\Phi^*\mathbf{F}^*$. \wen{The backward operator provides an approximate inverse to the forward operator in an inverse problem.} The $\mathbf{S}$ is the shaping operator and can be defined as $\mathbf{S}=\mathbf{T}_\lambda$. \wen{$\mathbf{T}_\lambda$ denotes a soft-thresholding operator with an input threshold parameter $\lambda$.}

\section{Examples}
In this section, we define two metrics to evaluate denoising performance. First, we use signal-to-noise ratio (SNR) defined as follows \cite[]{weilin2016seg,weilin2016seg2,wujuan2018jge1,wujuan2018jge2,chenwei2018,shaohuan20183d}:
\begin{equation}
\label{eq:snr}
\text{SNR}=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2^2}{\Arrowvert \mathbf{s} -\hat{\mathbf{s}}\Arrowvert_2^2},
\end{equation}
where $\mathbf{s}$ denotes the noise-free data and $\hat{\mathbf{s}}$ denotes the denoised/deblended data.

Secondly, we use local similarity. We calculate the local similarity map between each reconstructed data and the exact solution. The local similarity is a way to evaluate the similarity between two vectors/matrices/cubes in a local manner so that the evaluation can be revealed immediately from the calculated local similarity maps. \dlo{The detailed introduction of mathematics behind the local similarity calculation can be found in ?. }\wen{The local similarity between two vectors are defined as:
\begin{equation}
\label{eq:local}
\mathbf{x}=\sqrt{\mathbf{x}_1\circ\mathbf{x}_2},
\end{equation}
where $\circ$ means elementwise product. $\mathbf{x}_1$ and $\mathbf{x}_2$ are calculated from the two target vectors $\mathbf{v}_1$ and $\mathbf{v}_2$.
\begin{align}
\label{eq:local1}
&\min_{\mathbf{x}_1}\Arrowvert \mathbf{v}_1-\mathbf{V}_2 \mathbf{x}_1 \Arrowvert_2^2, \\
\label{eq:local2}
&\min_{\mathbf{x}_2}\Arrowvert \mathbf{v}_2-\mathbf{V}_1 \mathbf{x}_2 \Arrowvert_2^2.
\end{align}
\dlo{where}\wen{Here,} $\mathbf{V}_1$ is a diagonal operator composed of the elements of $\mathbf{v}_1$, $\mathbf{V}_2$ is a diagonal operator composed of the elements of $\mathbf{v}_2$. Note that in equations \ref{eq:local}-\ref{eq:local2}, $\mathbf{v}_1$, $\mathbf{v}_2$, and $\mathbf{x}$  denote vectorized 2D matrices. Equations \ref{eq:local1} and \ref{eq:local2} can be solved using shaping regularization with a local-smoothness constraint:
\begin{align}
\label{eq:local3}
\mathbf{x}_1 &= [\lambda_1^2\mathbf{I} + \mathcal{T}(\mathbf{V}_1^T\mathbf{V}_1-\lambda_1^2\mathbf{I})]^{-1}\mathbf{TV}_1^T\mathbf{v}_2,\\
\label{eq:local4}
\mathbf{x}_2 &= [\lambda_2^2\mathbf{I} + \mathcal{T}(\mathbf{V}_2^T\mathbf{V}_2-\lambda_2^2\mathbf{I})]^{-1}\mathbf{TV}_2^T\mathbf{v}_1,
\end{align}
where $\lambda_1$ and $\lambda_2$ are two controlling parameters that enable fast convergence, and $\mathcal{T}$ is a smoothing operator. \wen{$\lambda_1$ and $\lambda_2$} are normally chosen as $\lambda_1  = \Arrowvert\mathbf{V}_1^T\mathbf{V}_1\Arrowvert_2$ and $\lambda_2  = \Arrowvert\mathbf{V}_2^T\mathbf{V}_2\Arrowvert_2$.}

\subsection{Denoising blending spikes}
We first test the ability of the sparse dictionary learning method in separating blending spikes and random noise. Figure \ref{fig:bn1,bnn1,bnn_dn1,bnn_re1} shows a synthetic example. Figure \ref{fig:bn1} shows the simulated blending spikes without random noise. Figure \ref{fig:bnn1} shows the random \old{nosie}\new{noise} corrupted blending spikes. The noise level in Figure \ref{fig:bnn1} is relatively weak and the SNR is computed as 12.99 dB.  Here, we treat the clean blending spikes as the exact solution for the SNR calculation. \dlo{Figure \ref{fig:bnn_dn1,bnn_rn1} shows the denoising results using the sparse dictionary learning method.} Figure \ref{fig:bnn_dn1} displays the denoised blending spikes and Figure \ref{fig:bnn_re1} displays the \dlo{removed random noise}\wen{denoising error}. It is clear that in this test, the sparse dictionary learning method does a very good job and the blending spikes and random noise are well separated. \wen{The error is negligible.} The SNR of the denoised blending spikes reaches 20.05 dB. Figure \ref{fig:H00,H0-0,H1-0,H0-z,H1-z} shows a comparison of dictionaries learned from different datasets. In this paper, we use a patch size of $10\times10$ for the training. Thus, each atom size in the learned dictionary is $100\times 1$. When reformulated into a 2D matrix, each dictionary atom is of size $10\times10$. A total of 256 dictionary atoms will generated during the training process. Figure \ref{fig:H00} shows the initial  basis dictionary atoms input for learning. The dictionary atoms are very regular and does not follow the pattern features in the seismic data. Figures \ref{fig:H0-0} and \ref{fig:H1-0} show the learned dictionaries from the clean and noisy blending spikes, respectively. Figures \ref{fig:H0-0} and \ref{fig:H1-0} are very similar except that the dictionary atoms learned from the clean blending spikes are a little cleaner than the dictionary atoms learned from the noisy blending spikes.  We can see that each dictionary atom in Figure \ref{fig:H0-0} or \ref{fig:H1-0} exhibits the shape of several blending spikes, which indicates that the features of blending spikes are successfully learned into the atoms and thus the learned atoms have the ability to distinguish between blending spikes and random noise. \dlo{Figure \ref{fig:H0-z,H1-z} shows the zoomed atoms from Figure \ref{fig:H00,H0-0,H1-0,H0-z,H1-z}. }The zooming areas are highlighted by the blue square frame boxes in Figure \ref{fig:H00,H0-0,H1-0,H0-z,H1-z}. In Figures \ref{fig:H0-z} and \ref{fig:H1-z} we can see more clearly the atoms learned from the clean and noisy blending spikes, respectively, and conclude that the sparse dictionary learning can successfully learn the features of blending spikes into the dictionary atoms.

To test the influence of stronger noise to the denoising performance, we increase the noise level to moderately strong and extremely strong and compare the denoising performance. \wen{The top row in Figure \ref{fig:bnn3,bnn_dn3,bnn_re3,bnn4,bnn_dn4,bnn_re4} shows the denoising performance for the blending spikes with moderately strong noise.} In this case, $\text{SNR}=0.95$ dB. Figure \ref{fig:bnn3} shows the random noise corrupted spikes and Figure \ref{fig:bnn_dn3} shows the separated spikes using the sparse dictionary learning method. Figure \ref{fig:bnn_re3} shows the denoising error, where \dlo{it is difficult to see observable leaked blending spikes}\wen{the amplitude is small compared with that of the spikes}. From Figure \ref{fig:bnn3,bnn_dn3,bnn_re3,bnn4,bnn_dn4,bnn_re4}, we see that sparse dictionary learning method can also be capable of separating moderately strong random noise from the blending spikes.  We further increase the noise level and decrease the SNR of the noisy spikes to -5.07 dB, where the added random noise is considered as extremely strong noise. Figure \ref{fig:bnn4} shows the blending spikes with extremely strong random noise, where the noise energy is much stronger than the blending spikes and the blending spikes are even hard to see. Figure \ref{fig:bnn_dn4} shows the denoised spikes using the sparse dictionary learning method, where the shapes of the blending spikes have become much more visible than when in the noisy data. Figure \ref{fig:bnn_re4} shows the \dlo{removed random noise}\wen{denoising error}, where \dlo{no blending spikes are discernable}\wen{some energy shows up but is still not strong}. Figure \ref{fig:H3-0,H4-0,H3-z,H4-z} shows a comparison of the learned dictionary atoms from the noise corrupted blending spikes with different noise levels. Figure \ref{fig:H3-0} shows the dictionary atoms learned from the noisy spikes with moderately strong random noise (Figure \ref{fig:bnn3}). Figure \ref{fig:H4-0} shows the dictionary atoms learned from the noisy spikes with extremely strong random noise (Figure \ref{fig:bnn4}). Figures \ref{fig:H3-z} and \ref{fig:H4-z} show the zoomed 16 atoms from Figures \ref{fig:H3-0} and \ref{fig:H4-0}, respectively. From the learned dictionary atoms and the zoomed atoms, we see that even in the case of moderately strong or extremely strong random noise, the dictionary learning algorithm can still learn the dominant features of the blending spikes. However, we do see that the shapes of the spikes shown in the atoms are becoming more vague as the noise level increases from moderately strong to extremely strong (from Figures \ref{fig:H3-z} to \ref{fig:H4-z}), meaning that stronger random noise indeed makes the learning algorithm more difficult to learn the features of the spikes. Figure \ref{fig:snr-n0} shows the diagrams of the input SNRs and output SNRs varied with the increased noise variance. Both diagrams drop fast \dlo{in the first nosie level}\wen{in the beginning} but the output SNR becomes more stable in the case of high noise variance, which indicates that when noise level is lower, the dictionary learning algorithm is more sensitive to noise level and when noise level is higher, the dictionary learning algorithm becomes less sensitive.

\subsection{Denoising blending spikes and primary signals}
We then test the ability of the sparse dictionary learning method in learning the features of blending spikes in the presence of primary signals. \dlo{Figure \ref{fig:s1,sn1,sn1-bn,sn1-bnn} shows the simulated primary signals in different noise circumstances. Figure \ref{fig:s1} shows 
the clean synthetic data with four hyperbolic events.} \dlo{Figure \ref{fig:sn1} shows the noisy synthetic data with some random noise. Figure \ref{fig:sn1-bn} shows the blended data with some blending spikes.} Figure \ref{fig:sn1-bnn} shows the noisy data with both blending spikes and random noise. In Figure \ref{fig:sn1-bnn}, we add relatively weak noise, with $\text{SNR}=9.94$ dB. \dlo{Note that here we use the clean blended data shown in Figure \ref{fig:sn1-bn} as the ground-truth solution to calculate the SNR. }Figure \ref{fig:sn1-bnn-dn} shows the result after separating the random noise from the primary signals and blending spikes. Figure \ref{fig:sn1-bnn-re} displays the \dlo{removed random noise}\wen{error}. The SNR of Figure \ref{fig:sn1-bnn-dn} has been increased to 17.59 dB.  From Figure \ref{fig:sn1-bnn,sn1-bnn-dn,sn1-bnn-re}, we conclude that in the presence of primary signals, we can still separate the random noise from the blending spikes and primary signals. Figure \ref{fig:signal-H1,signal-H2,signal-H3-0,signal-H4-0,signal-H3-z,signal-H4-z} shows a comparison of dictionary atoms learned from different datasets. Figure \ref{fig:signal-H1} shows the learned dictionary atoms from the clean synthetic data. Figure \ref{fig:signal-H2} shows the learned dictionary atoms from the noisy synthetic data with random noise. Figure \ref{fig:signal-H3-0} shows the learned dictionary atoms from the blended synthetic data with blending spikes. Figure \ref{fig:signal-H4-0} shows the learned dictionary atoms from the noisy blended data with both random noise and blending spikes. It is clear that Figures \ref{fig:signal-H1} and \ref{fig:signal-H2} are very similar, indicating that the weak random noise causes negligible influence to the learned dictionary atoms. The same conclusion also holds for Figures \ref{fig:signal-H3-0} and \ref{fig:signal-H4-0}, where the added weak random noise does not affect the learned dictionary atoms obviously. \wen{To see a clearer view of the learned spike features in the atoms, we zoom in the two areas highlighted by the blue square frame boxes in Figures \ref{fig:signal-H3-0} and \ref{fig:signal-H4-0} and show the zoomed atoms in Figures \ref{fig:signal-H3-z} and \ref{fig:signal-H4-z}.}

\dlo{To test the influence of stronger noise to the dictionary learning performance, we increase the noise level and decrease the SNR of the noisy blended data to -8.14 dB. Figure \ref{fig:sn4,sn4-bnn} shows a comparison between the noisy data with random noise and noisy blended data with both random noise and blending spikes. The random noise is too strong to easily see the blending spikes. Figure \ref{fig:sn4-bnn-dn,sn4-bnn-rn} shows the denoised blending spikes and primary signals using the sparse dictionary learning method. Figure \ref{fig:sn4-bnn-dn} shows the separated primary signals and blending spikes. Figure \ref{fig:sn4-bnn-rn} shows the removed random noise. It is salient that the removed noise is almost pure random noise and does not contain any discernible spikes or primary signals. From this test, we conclude that the sparse dictionary learning method can also be capable of separating strong random noise from blending spikes in the presence of primary signals. Figure \ref{fig:signal-H2-3-0,signal-H2-4-0,signal-H4-3-0,signal-H4-4-0} shows a comparison of learned dictionary atoms in different noise circumstances and noise levels. Figures \ref{fig:signal-H2-3-0} and \ref{fig:signal-H2-4-0} show the dictionary atoms learned from noisy data containing random noise with different noise variance.  Figure \ref{fig:signal-H2-3-0} is related with relatively weaker noise ($\text{variance}=0.4$). Figure \ref{fig:signal-H2-4-0} is related with relatively stronger noise ($\text{variance}=0.8$). Figures \ref{fig:signal-H4-3-0} and \ref{fig:signal-H4-4-0} show the dictionary atoms learned from noisy data containing both random noise and blending spikes with different noise variance ($\text{variance}=0.4$ for (c) and $\text{variance}=0.8$ for (d)). The zoomed comparison of the atoms is shown in Figure \ref{fig:signal-H2-3-z,signal-H2-4-z,signal-H4-3-z0,signal-H4-4-z0}. It is clear that as noise variance increases, the learned atoms becomes more affected by random noise. However, even in the case of strong random noise, the sparse dictionary learning method can still learn the features of the blending spikes into the atoms, as pointed out by the labelled arrows in Figures \ref{fig:signal-H4-3-z0} and \ref{fig:signal-H4-4-z0}. Comparing Figures \ref{fig:signal-H2-4-z} and \ref{fig:signal-H4-4-z0}, we can also conclude that because of the existence of the blending spikes, the dictionary learning algorithm is more robust to random noise. The existing blending spikes highly \dlo{decreases}\wen{decrease} the possibility of the algorithm to learn the feature from pure random noise.}

With the constraint\wen{s} and precondition\wen{ing} from the sparse dictionary learning, the denoised blending spikes with the primary signals are then put into an iterative deblending framework, and the resulted deblended data is shown Figure \ref{fig:h-dl}. The proposed algorithm is also compared with the state-of-the-art deblending algorithms, e.g., the iterative rank-reduction method \cite[]{jinkun2015} and the iterative curvelet thresholding method \cite[]{shaohuan20161}. The result from the rank-based method is shown in Figure \ref{fig:h-rr} and the result from the curvelet-based method is shown in Figure \ref{fig:h-curv}. Figures \ref{fig:h-rr-e}  to \ref{fig:h-dl-e} show the deblending error sections corresponding to rank-based method, curvelet-based method, and the proposed method, respectively. The calculated SNRs for these three results are 4.66 dB for the rank-based method, 4.55 dB for the curvelet-based method and 10.28 dB for the proposed method. \dlo{Here, the SNRs are calculated with the clean synthetic data shown in Figure \ref{fig:s1} as the exact solution. }The local similarity of the deblended results is shown in \wen{the bottom row of} Figure \ref{fig:h-rr,h-curv,h-dl,h-rr-e,h-curv-e,h-dl-e,h-simi-rr,h-simi-curv,h-simi-dl}. It is obvious that the result from the proposed method is more similar to the exact solution than the other two results.

\wen{In order to test the proposed method on more complex dataset, we create another synthetic example in Figure \ref{fig:msignal,m1svd1,m1cur1,m1com1,mblend_erratic,m1svderr1,m1curerr1,m1comerr1}. This synthetic example is generated from the Marmousi velocity model. The clean data is shown in Figure \ref{fig:msignal}. Figures \ref{fig:m1svd1}, \ref{fig:m1cur1}, and \ref{fig:m1com1} plot the deblended results using the rank-based method, curvelet-based method, and the proposed method. It is worth mentioning that we not only simulate strong random noise, but also simulate more realistic erratic noise and add them to the numerically blended data. The noisy data containing different types of noise is shown in Figure \ref{fig:mblend_erratic}. In the presence of erratic noise, the dictionary learning model (equation \ref{eq:opt1}), however, needs to be modified so that the misfit measurement is not sensitive to the outliers, e.g.,
\begin{equation}
\label{eq:erratic}
\quad \arg \min_{\mathbf{D},\mathbf{C}} \rho_c( \mathbf{Y}-\mathbf{D}\mathbf{C})\quad\text{s.t.}\quad\parallel\mathbf{C} \parallel_0\le T_1,
\end{equation} 
where $\rho_c$ denotes the Huber norm with a tuning parameter $c$. The Huber norm can be expressed as
\begin{equation}
\label{eq:huber}
\rho_c(y) = \left\{\begin{array}{ll}
\frac{1}{2} y^2 & |y|\le c,\\
c(|y|-\frac{1}{2}c^2) & |y|> c.
\end{array}
\right.
\end{equation}
To solve the robust estimate model \ref{eq:erratic}, we follow the robust algorithm introduced in \cite{zhaoqiang2018}. A detailed introduction of these robust algorithms can be found in \cite{zhaoqiang2018} and is beyond the scope of this paper. Figures \ref{fig:m1svderr1}-\ref{fig:m1comerr1} show the deblending error for different methods. To compare the performance in detail, we zoom the frame boxes in Figure \ref{fig:msignal,m1svd1,m1cur1,m1com1,mblend_erratic,m1svderr1,m1curerr1,m1comerr1} and plot them in Figure \ref{fig:signalzoom1,svdzoom1,curzoom1,comzoom1,blezoom1_erratic}.  Figures \ref{fig:signalzoom1}-\ref{fig:blezoom1_erratic} correspond to Figures \ref{fig:msignal}-\ref{fig:mblend_erratic}, respectively. It is clear that the result from the proposed method (Figure \ref{fig:comzoom1}) is much cleaner than the results from the other two methods (Figures \ref{fig:svdzoom1}-\ref{fig:curzoom1}).}

\subsection{Field data example}
We first test the sparse dictionary learning method on a 2D field data example. The common-offset gather is shown in Figure \ref{fig:f-bd-0,f-bd-z}. Figure \ref{fig:f-bd-0} shows the blended field data with extremely strong random ambient noise and Figure \ref{fig:f-bd-z} shows a zoomed section of the field data. The zooming area is highlighted by the green frame box in Figure \ref{fig:f-bd-0}. The blending spikes and the primary reflection events are almost buried in the strong ambient noise. Figure \ref{fig:f-rr-0,f-curv-0,f-dl-0} shows the results using different iterative methods. Figure \ref{fig:f-rr-0} shows the result from the iterative rank reduction method, which has a much higher quality compared with the raw blended data in Figure \ref{fig:f-bd-0} and still contains some remaining noise. Figure \ref{fig:f-curv-0} shows the result from the iterative curvelet thresholding method, which is even cleaner than the iterative rank reduction method. The result from the proposed method is shown in Figure \ref{fig:f-dl-0}. The result of the proposed method is \dlo{much }cleaner than the other two results in that the reflection seismic events are more continuous in the space direction. The zoomed sections (corresponding to the green frame boxes in Figure \ref{fig:f-rr-0,f-curv-0,f-dl-0}) are shown in Figure \ref{fig:f-rr-z,f-curv-z,f-dl-z} for detailed comparison. It seems that the the results from the rank-based method and the curvelet-based method both contain some residual random noise and residual blending spikes, while the result from the proposed method not only removes most random noise and blending spikes but also preserves well the fault edges in this zooming area. It can be inferred that the residual random noise and blending spikes are caused by the fact that the traditional iterative inversion method tries to fit the raw blended data containing strong ambient noise instead of fitting the pure signal blended components, i.e., the mixture of the primary signals and the blending spikes. \dlo{Figure \ref{fig:f-rr-n,f-curv-n,f-dl-n} shows a comparison of the removed noise section during iterative deblending to check if any method causes significant damges to the useful primary signals. Because the ambient noise is very strong, no discernable primary signal components are shown in the noise sections. It is difficult to compare by the noise sections.} \dlo{Instead, we}\wen{We} use the local similarity introduced previously to compare the performance. Figure \ref{fig:f-simi-rr,f-simi-curv,f-simi-dl} shows the comparison of local similarity between the deblended data and removed noise for different methods. It is clear to see from the local similarity comparison that the local similarity map using the proposed method exhibits the smallest value compared with the other two similarity maps, indicating the fact that the removed noise using the proposed method is least similar to the deblended data and thus the proposed method causes the least damage to the useful primary signals \cite[]{yangkang2015ortho}.

The next field data example is a simulated multi-receivers 2D simultaneous source separation test, where the exact solution is known and we can better evaluate the deblending performance regarding the deblending error. 
\dlo{Figure \ref{fig:geom} shows the acquisition geometry of the 2D test. The red dots denote 120 evenly spaced shot locations on the surface. The blue inverted triangles denote 120 evenly spaced receivers. Note that in this acquisition geometry, the simultaneous shooting and traditional shooting only differ in the shot schedule ?. Figure \ref{fig:shottime} shows the shot schedules for the traditional and the faster simultaneous source shooting. From the shot schedule, it is obvious that the shooting time for the simultaneous-source acquisition is almost half of the traditional acquisition and thus saves about half of the traditional acquisition cost.}
\wen{The acquisition geometry in this example is a simple equidistant setup, where source and receivers are equispaced. }In this example, we use a relatively realistic field dataset to mimic the unblended data, as shown in Figure \ref{fig:d3d}. \dlo{The data is a marine data set provided by BGP China.} The size of the data is $1500\times 120\times120$ (in time-shot-receiver domain). Figure \ref{fig:b3d} shows the blended data with extremely strong ambient random noise. \wen{In this example, the added strong random noise is used for a test.} It is clear that the blending spikes appears to be spatially incoherent in the common receiver domain (along the shot axis) and spatially coherent in the common shot domain (along the receiver axis). Because of the very strong random noise, a lot of effective reflection signals have been buried in the noise. Figure \ref{fig:m3d} shows iteratively deblended data using the rank-based method. Figure \ref{fig:c3d} shows iteratively deblended data using the curvelet-based method. The iterative deblending is carried out in each common receiver gather based on the coherency difference between useful signals and interfering noise. We obtain the result shown in Figure \ref{fig:m3d} with 40 iterations. Comparing the rank-based deblended data and the curvelet-based data with the blended data, it is clear that although some noise is removed, there is still a significant amount of residual random noise and blending spikes. In this case, the deblended data using these two methods are considered to be successful. However, the result from the proposed method, as shown in Figure \ref{fig:im3d}, is much better considering both signal preservation and noise removal. Figures \ref{fig:m3d-n} to \ref{fig:im3d-n} show the removed noise corresponding to the three methods, where we can see significant useful primary signals are lost in the removed noise cubes. It is worth noting that the interfering shots are coherent in the spatial dimension ``Receiver''. Figures \ref{fig:m3d-e} to \ref{fig:im3d-e} show the deblending error sections corresponding to the three methods, where we can see that the proposed method causes the least deblending error while the error caused by the other two methods are mostly caused by the strong residual noise. For evaluating the deblending performance, we calculate the local similarity between the exact solution and deblended data and show them in Figures \ref{fig:m3d-s} to \ref{fig:im3d-s}, where the largest local similarity anomalies are shown in the similarity map corresponding the proposed method, indicating that the result from the proposed method is the most similar to the exact solution. To compare the amplitude preservation in detail, we plot a trace-by-trace comparison in Figure \ref{fig:trace}. The black line is from the unblended data. The red line is from the blended data. The magenta line corresponds to the rank-based method. The cyan line corresponds to the curvelet-based method. The green line corresponds to the proposed method. It is salient that the black and green lines are the most close to each other, thus the deblending error using the proposed approach is much less than the other two traditional methods.

\wen{\section{Discussion}}
\dlo{The concept of sparse dictionary learning ?, originated from image processing field,  is not new in geophysics. Many applications of the sparse dictionary learning algorithm have been investigated in the geophysics literature. However, most of the applications are about representing spatially coherent reflection seismic events in a sparse way so that the spatially incoherent components can be easily separated during the sparse learning process. The application of the sparse dictionary learning algorithm here is somewhat contradicting with the mainstream studies, i.e., we are seeking a way to represent the spatially incoherent blending spikes via learning the optimal dictionary atoms in a sparse way. The benefit of the sparse representation of blending spikes is that we can relieve the influence of the random noise to iterative deblending of simultaneous-source data by separating the random noise based on the hybrid-sparsity constrained model for deblending. This type of application of dictionary learning is unusual not only in the deblending literature, but also in the whole seismic data processing community. Blending spikes, due to its spatial incoherency property, are thought to be excluded from being learned into the dictionary atoms ?. However, in this paper, we have shown using extensive examples that the blending spikes can be learned via a normal sparse dictionary learning algorithm for being separated from random noise and their features can be well captured by the dictionary atoms. This phenomenon can be attributed to the fact that although the blending spikes are not spatially coherent, they are temporally coherent, i.e., they are smooth functions in the time direction. The blending spikes share the same properties with the useful primary signals when viewed in the time direction. We infer that the temporal coherency property of the blending spikes make them easily to be learned by a typical sparse dictionary learning algorithm, e.g., the K-SVD method.}% From the experiments and results shown in this paper, we are questioning the possibility of using a sparse dictionary learning based algorithm to separate the blending interference from the primary reflection signals, e.g., the work from ?. If we do want to apply the sparse dictionary learning method to separate the blending spikes only, we need to adjust the typical dictionary learning algorithm so that the blending spikes cannot be taken into consideration when constructing the dictionary atoms. For example, constraining the dictionary atoms not to contain spikes may be a potential solution.}

Research on the topic of deblending simultaneous-source data has gained a lot of surprising advances during the past decade. Dozens of methods have been developed to separate the blending spikes from the primary reflection signals either in a filtering-based manner or in an iterative-inversion way. While most existing deblending methods assume the ambient noise level to be low \cite[]{berk2013} and focus on the difference between primary signals and blending spikes, \dlo{seldom }research projects \wen{seldom} pay attention to the issues caused by strong ambient noise. Except for the discussion regarding the noise issue in simultaneous-source acquisition by \cite{berk2013}, where the \dlo{author claims}\wen{authors claim} that the overall noise level in the blended shot records will be lower than the total noise level when collecting all the required data in the traditional way (because of the faster acquisition\dlo{ period}), there is no other investigation or discussion regarding noise published to date. However, when random ambient noise becomes strong, almost all existing deblending methods become invalid. For example, from the viewpoint of filtering based deblending methods, which are mostly based on special implementation of median filters \cite[]{mediandeblend,shuwei2016,baimin2017jse1,weilin2018grsl,sosvmf}, when noise becomes strong, most median filtering based deblending approaches are ineffective in suppressing the random noise, causing a significant amount of residual noise. From the perspective of inversion based deblending methods, which are almost based on the forward blending operator and the least-squares fitting of the blended data, when noise becomes strong, much information in the recorded data cannot be fitted and the iteratively inverted model is seriously distorted and unreasonable. In this paper, we bring the noise issue to attention of \dlo{the}\wen{our} peers, and investigate how the noise level will affect the performance in the state-of-the-art deblending framework. More importantly, we have introduced a novel way to precondition the blended data using sparse dictionary learning so that observed data term in the least-squares framework can be fitted well. In the current stage, learning the features of blending spikes for the separation of random ambient noise is the best strategy we can come up with to solve the noise issue in an iterative inversion framework for deblending.

\section{Conclusions}
The traditional iterative inversion based deblending framework fails when the random ambient noise becomes extremely strong. In the case of strong random ambient noise, the iterative optimization tries to fit the noise\dlo{ and thus the}\wen{, and so the} estimated model is far from being accurate. We have proposed a sparse dictionary learning constrained deblending method, in which the blending spikes can be adaptively learned via the dictionary learning process and thus the resulted dictionary atoms are capable of distinguishing the random ambient noise from the blending spikes and primary reflection signals. Since the blending spikes can be learned via the sparse dictionary method, we suggest that the traditional dictionary learning algorithm should not be used to remove blending spikes without proper adjustment. A set of synthetic and field seismic datasets have been used to demonstrate the superior performance of the propose method over the traditional methods.

\section{Acknowledgements}
The research is supported by the “Thousand Youth Talents Plan”, the Starting Funds from Zhejiang University, the National Natural Science Foundation of China (Grant No. 41804140, and the Open Fund of Key Laboratory of Exploration Technologies for Oil and Gas Resources (Yangtze University), Ministry of Education (Grant No. PI2018-02).

%\inputdir{test}
%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
%\multiplot{2}{test1,test2}{width=0.45\textwidth}{(a) Caption a. (b) Caption b.}

\inputdir{./}

\plot{demo}{width=0.8\textwidth}{Cartoons illustrating the principles of patching (a) and unpatching (b).}

\inputdir{hyper}

\multiplot{4}{bn1,bnn1,bnn_dn1,bnn_re1}{width=0.4\textwidth}{Synthetic test for data with relatively \dlo{weaker}\wen{weak} noise. (a) Blending spikes. (b) Blending spikes contaminated by random noise (with SNR=12.99 dB). \wen{(c) Separated blending spikes using sparse dictionary learning (with SNR=20.05 dB). (d) \wen{Separation error} using sparse dictionary learning.}}

%\multiplot{2}{bnn_dn1,bnn_rn1}{width=0.45\textwidth}{Test for data with relatively \dlo{weaker}\wen{weak} noise. (a) Separated blending spikes using sparse dictionary learning (with SNR=20.05 dB). (b) Separated random noise using sparse dictionary learning.}

\multiplot{3}{H00,H0-0,H1-0,H0-z,H1-z}{width=0.3\textwidth}{Test for data with relatively weaker noise. (a) Initial dictionary atoms. (b) Learned dictionary atoms from the clean blending spikes. (c) Learned dictionary atoms from the noisy blending spikes. The areas highlighted by the \dlo{pink}\wen{cyan} frame boxes in (b) and (c) are zoomed in (d) and (e). \wen{(d) Zoomed dictionary atoms learned from the clean blending spikes. (e) Zoomed dictionary atoms learned from the noisy blending spikes.}}
%\multiplot{2}{H0-z,H1-z}{width=0.45\textwidth}{Dictionary comparison for data with relatively weaker noise. (a) Zoomed dictionary atoms learned from the clean blending spikes. (b) Zoomed dictionary atoms learned from the noisy blending spikes.}

\multiplot{6}{bnn3,bnn_dn3,bnn_re3,bnn4,bnn_dn4,bnn_re4}{width=0.3\textwidth}{Test for data with \dlo{relatively }\dlo{stronger}\wen{moderately strong (top row) and extremely strong (bottom row)} noise. (a) Blending spikes contaminated by random noise (with SNR=0.95 dB). (b) Separated blending spikes using sparse dictionary learning (with SNR=9.13 dB). (c) \wen{Separation error} \dlo{using sparse dictionary learning}\wen{corresponding to (b).}. \wen{(d) Blending spikes contaminated by random noise (with SNR=-5.07 dB). (e) Separated blending spikes using sparse dictionary learning (with SNR=2.21 dB). (f) \wen{Separation error} corresponding to (d).}}

%\multiplot{3}{bnn4,bnn_dn4,bnn_rn4}{width=0.38\textwidth}{Test for data with extremely strong noise. (a) Blending spikes contaminated by random noise (with SNR=-5.07 dB). (b) Separated blending spikes using sparse dictionary learning (with SNR=2.21 dB). (c) Separated random noise using sparse dictionary learning.}
\multiplot{4}{H3-0,H4-0,H3-z,H4-z}{width=0.45\textwidth}{Dictionary comparison for data with stronger noise. (a) Learned dictionary atoms from the data with SNR=0.95 dB. (b) Learned dictionary atoms from the data with SNR=-5.07 dB. (c) Zoomed atoms from (a). (d) Zoomed atoms from (b).}

\plot{snr-n0}{width=\textwidth}{Relation between SNRs and the noise levels.}

%with signal
\inputdir{hyper_signal}
%\multiplot{4}{s1,sn1,sn1-bn,sn1-bnn}{width=0.4\textwidth}{Test for data with primary signals and relatively \dlo{weaker}\wen{weak} noise. (a) Primary signals. (b) Primary signals with random noise. (c) Primary  signals with blending spikes. (d) Primary signals with noise and blending spikes (SNR=9.94 dB with (c) as ground truth solution).}

\multiplot{3}{sn1-bnn,sn1-bnn-dn,sn1-bnn-re}{width=0.3\textwidth}{\wen{Denoising test for data with primary signals and noise. (a) Primary signals with noise and blending spikes (SNR=9.94 dB). (b) Denoised data of Figure \ref{fig:sn1-bnn} using sparse dictionary learning (SNR=17.59 dB)). (c) \dlo{Removed noise}\wen{Denoising error}.}}

\multiplot{6}{signal-H1,signal-H2,signal-H3-0,signal-H4-0,signal-H3-z,signal-H4-z}{width=0.2\textwidth}{Dictionary comparison for data with relatively weaker noise. (a) Learned dictionary atoms from the primary signals. (b) Learned dictionary atoms from the primary signals and random noise. (c) Learned dictionary atoms from the primary signals and blending spikes. (d) Learned dictionary atoms from the primary signals, blending spikes, and random noise. The areas highlighted by the cyan frame boxes in (c) and (d) are zoomed in Figures (c) and (d), respectively. \wen{Note the atoms contain significant features of the blending spikes, which makes the learned sparse dictionary capable of separating the random noise from the primary signals and blending spikes.}}

%\multiplot{2}{signal-H3-z,signal-H4-z}{width=0.45\textwidth}{Dictionary comparison for data with relatively weaker noise. (a) Learned dictionary atoms from the primary signals and blending spikes. (b) Learned dictionary atoms from the primary signals, blending spikes, and random noise. Note the atoms contain significant features of the blending spikes, which makes the learned sparse dictionary capable of separating the random noise from the primary signals and blending spikes.}

%\multiplot{4}{sn4,sn4-bnn}{width=0.45\textwidth}{Test for data with primary signals and very strong noise. (a) Primary signals with random noise. (d) Primary signals with both random noise and blending spikes. (SNR=-8.14 dB with Figure \ref{fig:sn1-bn} as ground truth solution).}

%\multiplot{2}{sn4-bnn-dn,sn4-bnn-rn}{width=0.45\textwidth}{Denoising test for data with primary signals and very strong noise. (a) Denoised data of Figure \ref{fig:sn4-bnn} using sparse dictionary learning (SNR=2.18 dB). (b) Removed noise.}

%\multiplot{4}{signal-H2-3-0,signal-H2-4-0,signal-H4-3-0,signal-H4-4-0}{width=0.45\textwidth}{Test for data with different strong noise. (a) Learned dictionary atoms from the data contaminated only by random noise (variance=0.4). (b) Learned dictionary atoms from the data contaminated only by random noise (variance=0.8). (c) Learned dictionary atoms from the data contaminated by blending spikes and random noise (variance=0.4). (d) Learned dictionary atoms from the data contaminated by blending spikes and random noise (variance=0.8).}

%\multiplot{4}{signal-H2-3-z,signal-H2-4-z,signal-H4-3-z0,signal-H4-4-z0}{width=0.45\textwidth}{Zoomed dictionary comparison for data with different strong noise. (a) Zoomed area from Figure \ref{fig:signal-H2-3-0}. (b) Zoomed area from Figure \ref{fig:signal-H4-3-0}. (c) Zoomed area from Figure \ref{fig:signal-H2-4-0}. (d) Zoomed area from Figure \ref{fig:signal-H4-4-0}.}

\inputdir{hyper_db}
\multiplot{9}{h-rr,h-curv,h-dl,h-rr-e,h-curv-e,h-dl-e,h-simi-rr,h-simi-curv,h-simi-dl}{width=0.23\textwidth}{Deblending comparison. (a) Deblended data using the iterative rank reduction method ($\text{SNR}= 4.66$ dB). (b) Deblending using the iterative curvelet thresholding method ($\text{SNR}= 4.52$ dB). (c) Deblended data using the dictionary learning constrained iterative inversion method ($\text{SNR}=10.28$ dB). (d) Deblending error corresponding to (a). (e) Deblending error corresponding to (b). (f) Deblending error corresponding to (c). (g)-(i) Local similarities corresponding to (a)-(c).}

%\multiplot{3}{h-simi-rr,h-simi-curv,h-simi-dl}{width=0.30\textwidth}{Local similarity comparison. (a) Local similarity between the exact solution and deblended data using the iterative rank reduction method. (b) Local similarity between the exact solution and deblended data using the iterative curvelet thresholding method.  (c) Local similarity between the exact solution and deblended data using the proposed method. Note that the result from the proposed method is obviously more similar to the exact solution.}
\inputdir{matfun_mar1}

\multiplot{8}{msignal,m1svd1,m1cur1,m1com1,mblend_erratic,m1svderr1,m1curerr1,m1comerr1}{width=0.2\textwidth}{\wen{Marmousi example. (a) Clean data. (b)-(d) Deblended data using the iterative rank reduction method, curvelet method, and proposed method, respectively. (e) Noisy blended data (with erratic noise). (f)-(h) Error corresponding to (b)-(d), respectively.} }

\multiplot{5}{signalzoom1,svdzoom1,curzoom1,comzoom1,blezoom1_erratic}{width=0.4\textwidth}{\wen{Zoomed comparison (highlighted by the frame boxes) from Figure \ref{fig:msignal,m1svd1,m1cur1,m1com1,mblend_erratic,m1svderr1,m1curerr1,m1comerr1}. (a)-(e) correspond to Figures \ref{fig:msignal}-\ref{fig:mblend_erratic}, respectively.} }

\inputdir{field1}
\multiplot{2}{f-bd-0,f-bd-z}{width=0.65\textwidth}{The first field data example. (a) Field data in the common offset domain. (b) Zoomed data from the highlighted area in (a).}

\multiplot{3}{f-rr-0,f-curv-0,f-dl-0}{width=0.60\textwidth}{Deblending comparison for the first field data example. (a) Deblended data using the iterative rank reduction method. (b) Deblending using the iterative curvelet thresholding method. (c) Deblended data using the dictionary learning constrained iterative inversion method.}

\multiplot{3}{f-rr-z,f-curv-z,f-dl-z}{width=0.60\textwidth}{Zoomed deblending comparison for the first field data example (the zooming areas are highlighted by the frame boxes in Figure \ref{fig:f-rr-0,f-curv-0,f-dl-0}.). (a) Deblended data using the iterative rank reduction method. (b) Deblending using the iterative curvelet thresholding method. (c) Deblended data using the dictionary learning constrained iterative inversion method.}

%\multiplot{3}{f-rr-n,f-curv-n,f-dl-n}{width=0.60\textwidth}{Comparison of removed blending spikes and random noise for the first field data example. (a) Removed noise using the iterative rank reduction method. (b) Removed noise using the iterative curvelet thresholding method. (c) Removed noise using the dictionary learning constrained iterative inversion method.}

\multiplot{3}{f-simi-rr,f-simi-curv,f-simi-dl}{width=0.60\textwidth}{Comparison of local similarity between deblended data and removed noise for the first field data example. (a) Local similarity using the iterative rank reduction method. (b) Local similarity using the iterative curvelet thresholding method. (c) Local similarity using the dictionary learning constrained iterative inversion method.}

%\inputdir{field2}
%\inputdir{./}
%\multiplot{2}{geom,shottime}{width=0.5\textwidth}{The second field example. (a) Acquisition geometry.  The red dots denote shot locations and blue inverted triangles denote receivers. The simultaneous shooting and the traditional shooting only differ in the shot schedule. (b) Shot schedule. Note that the shot schedule is just for testing purpose and does not represent a real field deployment. In the test, the speed of a shooting vessel is assumed to be sufficiently large. In practice, the shot sampling would be much higher than the testing case, which is 0.05 km.}

\inputdir{./field2}
\multiplot{2}{d3d,b3d}{width=0.3\textwidth}{The second field data example. (a) Unblended data. (b) Blended data with very strong ambient noise.}

\multiplot{6}{m3d,c3d,im3d,c3d-n,m3d-n,im3d-n}{width=0.3\textwidth}{Deblending comparison for the second field data example. (a) Deblended data using the iterative rank reduction method. (b) Deblending using the iterative curvelet thresholding method. (c) Deblended data using the dictionary learning constrained iterative inversion method. (d) Removed noise corresponding to (a). (e) Removed noise corresponding to (b). (f) Removed noise corresponding to (c).}

\multiplot{6}{m3d-e,c3d-e,im3d-e,m3d-s,c3d-s,im3d-s}{width=0.3\textwidth}{Deblending comparison for the second field data example. (a) Deblending error using the iterative rank reduction method. (b) Deblending error using the iterative curvelet thresholding method. (c) Deblending error using the dictionary learning constrained iterative inversion method. (d) Local similarity corresponding to (a). (e) Local similarity corresponding to (b). (f) Local similarity corresponding to (c).}

\inputdir{./}
\plot{trace}{width=0.8\textwidth}{Single trace comparison for the second field data example. The black line is from the unblended data. The red line is from the blended data. The magenta line corresponds to the rank-constrained method. The cyan line corresponds to the \dlo{rank-constrained}\wen{sparsity-constrained} method. The green line corresponds to the proposed method. Note that the black and green lines are closest to each other, thus the deblending error using the proposed approach is much less than the other two traditional methods. (a) Comparison in the original size. (b) Comparison in a zoomed view.}

\bibliographystyle{seg}
\bibliography{db}

%\AtEndDocument{}

%\newpage
%\listoffigures

%\begin{figure}[htb!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
%	\caption{Caption.}
%	\label{fig:fig}
%\end{figure}

%\begin{figure}[htb!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
%    \label{fig:fig1}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
%    \label{fig:fig2}}\\
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure}

%\begin{figure*}[ht!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
%    \label{fig:fig1}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
%    \label{fig:fig2}}\\
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure*}

%\begin{table}[h]
%\caption{Table caption}
%\begin{center}
%     \begin{tabular}{|c|c|c|c|c|c|} 
%	  \hline Column1 (unit)  & Column2 (unit) & Column3 (unit) \\ 
%	  \hline 1 & 2  & 3 \\
%       \hline
%    \end{tabular} 
%\end{center}
%\label{tbl:table1}
%\end{table}

### 2020-09-16 dealiase1/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{IEEE Geoscience and Remote Sensing Letters, 12, no. 10, 2150-2154, (2015)}

\title{De-aliased seismic data interpolation using seislet transform with low-frequency constraint}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\author{Shuwei Gan\footnotemark[1], Shoudong Wang\footnotemark[1], Yangkang Chen\footnotemark[2], Yizhuo Zhang\footnotemark[3], Zhaoyu Jin\footnotemark[4]}
\address{
\footnotemark[1]
State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
%331334826@qq.com
gsw19900128@126.com\\
\footnotemark[2] Jackson School of Geosciences\\
The University of Texas at Austin\\
University Station, Box X\\
Austin, TX 78713-8924, USA \\
Email: ykchen@utexas.edu\\
\footnotemark[3] Institut de Physique du Globe de Paris (IPGP)\\ 
1 Rue Jussieu\\
75005 Paris, France  \\
Email: yizhuozh@gmail.com\\
\footnotemark[3]School of Geosciences,
University of Edinburgh,
Edinburgh,UK, EH9 3JW,
Email: s1263999@sms.ed.ac.uk
}

\maketitle

\begin{abstract}
Interpolating regularly missing traces in seismic data is thought to be much harder than interpolating irregularly missing seismic traces, because many sparsity-based approaches can not be used due to the strong aliasing noise in the sparse domain. We propose to use seislet transform to perform a sparsity-based approach to interpolate highly under-sampled seismic data based on the classic projection onto convex sets (POCS) framework. Many numerical tests show that the local slope is the main factor that will affect the sparsity and anti-aliasing ability of seislet transform. By low-pass filtering the under-sampled seismic data with a very low bound frequency, we can get a precise dip estimation, which will make seislet transform capable for interpolating the aliased seismic data. In order to prepare the optimum local slope during iterations, we update the slope field every several iterations. We also use a percentile thresholding approach to better control the reconstruction performance. Both synthetic and field examples show better performance using the proposed approach than the traditional prediction based and the $F-K$ POCS based approaches.
\end{abstract}

%\begin{keywords}
%Seismic data interpolation, seislet transform, sparsity comparison, low-frequency constrained inversion, local slope
%\end{keywords}

\section{Introduction}
Due to different reasons, seismic data may have missing traces. Seismic data reconstruction is such a procedure to remove sampling artifacts, and to improve amplitude analysis, which are very important for subsequent processing steps including high-resolution processing, wave-equation migration, multiple suppression, amplitude-versus-offset (AVO) or amplitude-versus-azimuth (AVAZ) analysis, and time-lapse studies \cite{daniel2002,liubin2004,abma2005,juefu2010,mostafa2010,yangkang2015eage2}. In recent years, due to the development of compressive sensing framework, there are a lot of sparsity-based methods for interpolating irregularly sampled seismic data. However, for regularly missing traces, sparsity-based methods \cite{abma2006,chengbo2012,yangkang2014halfthr} can not obtain satisfying results because of the strong aliasing noise in the transform domain. Instead, the prediction-based approaches \cite{spitz1991,mostafa2007} are still the best approaches for interpolating regularly missing traces.

In this paper, we propose to use seislet transform to perform a sparsity-based reconstruction, based on the well-established projection onto convex sets (POCS) framework \cite{abma2006}. Many numerical studies show that the local slope is the main factor affecting the sparsity and anti-aliasing ability of the seislet transform. Even though with the original aliased data, we can not obtain precise dip estimation, we can use low-pass filtered data (below 15 Hz) to estimate local slope in order to construct the seislet transform of the full-band seismic data and perform thresholding. Synthetic data and field data examples show nearly perfect results using the proposed approach. The traditional prediction based approach and the $F-K$ based POCS approach are both compared with the proposed approach and are demonstrated to be less effective.

\section{Methods}
\subsection{Projection onto convex sets (POCS)}
The principal problem of seismic data reconstruction is to solve the under-determined inversion problem:
\begin{equation}
\label{eq:acq}
\mathbf{Fm}=\mathbf{d},
\end{equation}
where $\mathbf{m}$ is the well-sampled seismic data, $\mathbf{F}$ denotes the sampling operator, and $\mathbf{d}$ denotes the observed data \cite{yangkang2014halfthr}. Because of the missing traces, the operator $\mathbf{F}$ is highly singular and thus make equation \ref{eq:acq} highly under-determined.

There have existed many different algorithms for solving equation \ref{eq:acq} by adding different constraints. The POCS algorithm \cite{abma2006} is one of the most widely used methods to interpolate seismic data with irregularly missing traces, and has the following iterative expression:
\begin{equation} 
\label{eq:pocs}
\mathbf{m}_{n+1}=\mathbf{d}+(\mathbf{I}-\mathbf{F})\mathbf{A}^{-1}\mathbf{T}\mathbf{A}[\mathbf{m}_n],
\end{equation}
where $\mathbf{m}_n$ denotes the reconstructed data after $n$th iteration, $\mathbf{A}$ and $\mathbf{A}^{-1}$ are the forward and inverse sparsity-promoting transforms, $\mathbf{I}$ is an identity matrix and $\mathbf{T}$ is a thresholding operator. However, for regularly missing traces, POCS can not obtain satisfying results because of the strong aliasing noise in the sparse domain

\subsection{Seislet transform}
The construction of seislet transform \cite{seislet} follows the basics of the second-generation wavelet transform. The forward transform starts with the finest scale (the original sampling) and goes to the coarsest scale. The inverse transform starts with the coarsest scale and goes back to the finest scale \cite{yangkang20142}. The forward and inverse seislet transforms can be
expressed as:
\begin{equation}
\label{eq:one}
\mathbf{r}=\mathbf{o}-\mathbf{P\left[e\right]},
\end{equation}
\begin{equation}
\label{eq:two}
\mathbf{c}=\mathbf{e}+\mathbf{U\left[r\right]},
\end{equation}
\begin{equation}
\label{eq:three}
\mathbf{e}=\mathbf{c}-\mathbf{U\left[r\right]},
\end{equation}
\begin{equation}
\label{eq:four}
\mathbf{o}=\mathbf{r}+\mathbf{P\left[e\right]},
\end{equation}
where $\mathbf{P}$ is the prediction operator, $\mathbf{U}$ is the updating operator. $\mathbf{r}$ denotes the difference between true odd trace and predicted odd trace (from even trace), $\mathbf{c}$ denotes a coarse approximation of the data. At the start of the forward transform, e and o correspond to the even and odd traces of the data domain. At the start of the inverse transform, $\mathbf{c}$ and $\mathbf{r}$ will have just one
trace of the coarsest scale of the seislet domain. The seislet transform differs from the wavelet transform in that the prediction and updating operators utilize the local slope of seismic profiles to predict and update the even and odd traces. The above prediction and update operators can be defined as follows:
\begin{equation}
\label{eq:five}
\mathbf{P}\left[\mathbf{e}\right]_k=\left(\mathbf{P}^{(+)}_k\left[\mathbf{e}_{k-1}\right]+\mathbf{P}^{(-)}_k\left[\mathbf{e}_k\right]\right)/2,
\end{equation}
\begin{equation}
\label{eq:six}
\mathbf{U}\left[\mathbf{r}\right]_k=\left(\mathbf{P}^{(+)}_k\left[\mathbf{r}_{k-1}\right]+\mathbf{P}^{(-)}_k\left[\mathbf{r}_k\right]\right)/4,
\end{equation}
where $\mathbf{P}^{(+)}_k$ and $\mathbf{P}^{(-)}_k$ are operators that predict a trace from its left and right neighbors, correspondingly, by shifting seismic events according to their local slopes.
The local slope can be calculated using a robust algorithm as introduced in \cite{fomel2002pwd}.

\inputdir{coef}
\multiplot{4}{hyper-fk,hyper-dwt,hyper-seiss,hyper-curv-img}{width=0.45\columnwidth}{Comparison among different sparsity-promoting transforms based on the synthetic example shown in Figure \ref{fig:hyper}. (a) 2-D Fourier transform domain. (b) 2-D Wavelet transform domain. (c) 2-D Seislet transform domain. (d) 2-D Curvelet transform domain.}

\plot{hyper-c}{width=0.5\columnwidth}{Coefficients decaying diagram of different sparsity-promoting transforms.}

\inputdir{synth}

\multiplot{4}{hyper,hyper-zero,fk-hyper,fk-hyper-zero}{width=0.45\columnwidth}{(a) Original synthetic data. (b) Decimated data (50\% traces regularly removed). (c) $F-K$ spectrum of original synthetic data. (d)  $F-K$ spectrum of decimated data.}

\multiplot{4}{hyper-seis,hyper-fx,fk-hyper-seis,fk-hyper-fx}{width=0.45\columnwidth}{(a) Reconstructed data using the proposed approach. (b) Reconstructed data using Spitz's approach. (c)  $F-K$ spectrum of reconstructed data using the proposed approach. (d)  $F-K$ spectrum of reconstructed data using Spitz's approach. }

\multiplot{2}{hyper-seis-dif,hyper-fx-dif}{width=0.45\columnwidth}{(a) Reconstruction error using the proposed approach. (b) Reconstruction error using the Spitz's approach.}

\multiplot{3}{dip,dip1,dip2}{width=0.45\columnwidth}{(a) Accurate dip estimation. (b) Final dip estimation using 15 Hz low-pass filtering. (c) Final dip estimation using 30 Hz low-pass filtering. Note the aliased dip in (c).}

\plot{snrs-pocs}{width=0.5\columnwidth}{Convergence diagram of the first example using the proposed approach.}

\subsection{Comparison of sparsity-promoting transforms}
The well-known existing sparsity-promoting transforms in the exploration geophysics field include the Fourier\cite{chandrasekharan1949}, wavelet transform\cite{akansu2010}, and curvelet transform \cite{candes20061}.

In order to effectively compare the sparseness of different transforms, we first select an input dataset (here, we use the synthetic example shown in Figure \ref{fig:hyper} as the input dataset). Then we transform the input data into sparse transform domain using different sparse transforms. Figure \ref{fig:hyper-fk,hyper-dwt,hyper-seiss,hyper-curv-img} shows different transformed domains for the input data. The 2-D Fourier transform in this case means the $f-k$ transform. The 2-D wavelet transform means implementing the 1-D wavelet transform along the temporal direction first and along the spatial direction second. The 2-D seislet transform means implementing the seislet transform along the spatial direction first and 1-D seislet transform along the temporal direction second. The 2-D curvelet transform refers to the 2-D wedge wrapping based fast discrete curvelet transform \cite{candes20061}. Next we sort the coefficients in the transform domains into decaying 1-D vectors according to the coefficient amplitude and scale the 1-D vectors. Finally we plot the decaying coefficients with respect to the sequence number for all the transforms in one plot. Figure \ref{fig:hyper-c} shows a comparison between the decay of sorted coefficients in the 2-D Fourier transform, 2-D wavelet transform, 2-D seislet transform and 2-D curvelet transform domains. Our experiments show that the seislet coefficients decay significantly faster than coefficients of the other transforms, which indicates a more compact structure of the seislet domain. Thus, our POCS based interpolation approach is preferred to use the 2-D seislet transform domain as the sparsity-promoting transform. Although the sparsity comparison is based on the well-sampled data, the same conclusion can be extended to the under-sampled case. It is worth to be mentioned that most sparse transforms (in their original form) including the four mentioned transforms can not obtain acceptable reconstruction results for under-sampled data with regularly missing traces.

\subsection{De-aliased interpolation by low-frequency constrained local slope estimation}
It can be demonstrated by tests that the slope estimation is the main factor affecting the sparsity and anti-aliasing ability of the seislet transform. Thus, we can first filter the data using a simple low-pass filter with a very low bound frequency. The bound frequency can be different for different datasets, but is generally below 15 Hz. When interpolating the regularly missing traces using a POCS algorithm, there are three key factors that will affect the final reconstructed results: (1) Slope estimation. (2) Threshold value in the seislet transform. (3) Number of iterations. We re-estimate the dip about every 5 POCS iterations using the low-pass filtered data. In order to set the optimum threshold, we use a percentile strategy, assuming that a certain percentage of coefficients can represent the data. In order to obtain a very good reconstruction, the number of iterations should be relatively large (about 150 iterations). The main computational cost of the proposed approach lays on the forward and inverse seislet transforms \cite{seislet,yangkang20142}. The seislet transform can be more expensive than the fast Fourier transform and the digital wavelet transform, but still has an $O(N)$ cost and is still efficient in practice.

\section{Examples}
The first synthetic example is shown in Figures \ref{fig:hyper,hyper-zero,fk-hyper,fk-hyper-zero}, \ref{fig:hyper-seiss,hyper-fx,fk-hyper-seis,fk-hyper-fx}, \ref{fig:hyper-seis-dif,hyper-fx-dif}, \ref{fig:dip,dip1,dip2} and \ref{fig:snrs-pocs}. Figure \ref{fig:hyper} shows the original well-sampled data. By regularly removing 50 \% traces, we simulate the under-sampled data and show it in Figure \ref{fig:hyper-zero}. After using the proposed approach, we obtain a perfect reconstructed data as shown in Figure \ref{fig:hyper-seis}. The dip estimation is applied on the low-frequency data using 15 Hz low-pass filtering. During each iteration, we preserve 8\% coefficients. In order to numerically compare the denoising performances of different approaches,  we utilize the signal-to-noise ratio (SNR) \cite{yangkang2015}:
\begin{equation}
\label{eq:snr}
SNR_n=10\log_{10}\frac{\Arrowvert \mathbf{m} \Arrowvert_2^2}{\Arrowvert \mathbf{m}-\mathbf{m}_n\Arrowvert_2^2},
\end{equation}
where $\mathbf{m}$ is the original complete data and $\mathbf{m}_n$ is denotes the reconstructed data after $n$th iteration.
After 200 iterations, we obtain a well-reconstructed data with a high SNR: 28.02 dB. Figure \ref{fig:snrs-pocs} shows the convergence diagram in terms of SNR using the proposed approach. It is clear that the percentile thresholding strategy can help obtain a converged result with a high SNR. Figures \ref{fig:fk-hyper} and \ref{fig:fk-hyper-zero} show the $F-K$ spectrum of the original data and decimated data. It is obvious that the removed traces cause strong spatial aliasing in the spectrum (Figure \ref{fig:fk-hyper-zero}). We also use the traditional $F-X$ prediction based approach \cite{spitz1991} to interpolate the decimated data and show the result in Figure \ref{fig:hyper-fx}. The performance of $F-X$ prediction method also obtains a good recovery of the missing traces. However, when compared in the $F-K$ domain (Figures \ref{fig:fk-hyper-seis} and \ref{fig:fk-hyper-fx}), the proposed approach clearly does a better job because there is still some aliasing noise left in the spectrum from $F-X$ prediction method. It can be further confirmed from the interpolation error sections, as shown in Figure \ref{fig:hyper-seis-dif,hyper-fx-dif}. $F-X$ prediction method causes noticeable estimation error while the proposed approach causes nearly zero error.

As we can see, the spectrum of the reconstructed data using the proposed approach is exactly the same as the original data. If we use a filter with a somewhat higher low-pass frequency, we will obtain a much worse reconstructed result, because of the severe aliasing problem. Figure \ref{fig:dip} shows the precise dip estimation from the original data. Figure \ref{fig:dip1} shows the final dip estimation using 15 Hz low-pass filtering. The final dip estimation using 30 Hz low-pass filtering shows incorrect dips around 0.75 s at trace 250 (Figure \ref{fig:dip2}).

The second synthetic example is a linear-event example to test the performance of the proposed approach on post-stack data. The original data is shown in Figure \ref{fig:linear}. We also remove 50\% traces regularly. In this example, we compare the proposed approach with the $F-K$ based POCS approach. The reconstructed results using the proposed approach and the $F-K$ based POCS approach are shown in Figures \ref{fig:linear-seis} and \ref{fig:linear-fft}, respectively. It is obvious that the proposed can still obtain a perfect performance, while the $F-K$ based POCS approach cannot obtain any improvement because of the strong aliasing noise in the $F-K$ domain. This test confirms the fact that $F-K$ based POCS approach should not be used to interpolate regularly missing traces \cite{spitz1991,mostafa2007,mostafa2010}. In this example, we use 100 iterations to obtain the reconstructed results of both seislet and Fourier transforms. The final SNR of the proposed approach reaches 22.47 dB, and the SNR of the $F-K$ based POCS approach stays unchanged: 3.007 dB. The slightly worse performance of the proposed approach on this example than the first example is because the crossing seismic events cause some errors when estimating the local slope, which affect the final performance a bit.

\inputdir{linear}
\multiplot{4}{linear,linear-zero,linear-seis,linear-fft}{width=0.45\columnwidth}{Second synthetic example test. (a) Original synthetic data. (b) Decimated data (50\% traces regularly removed). (c) Reconstructed data using the proposed approach. (d) Reconstructed data using $F-K$ based POCS approach. Note that the $F-K$ based POCS approach cannot obtain any improvement because of the aliasing noise caused by the regularly missing traces.}

The field data example is a highly under-sampled common shot gather, as shown in Figure \ref{fig:field}. By manually adding zero traces between two neighbor traces, we obtain the zero-padded data, as shown in Figure \ref{fig:field-zero}. After interpolation, a much better sampled data can be obtained, as shown in Figure \ref{fig:field-seis}. In this example, we estimate the local slope using 5 Hz low-pass filtering. The corresponding $F-K$ spectrum are shown in Figures \ref{fig:fk-field}, \ref{fig:fk-field-zero} and \ref{fig:fk-field-seis}, respectively. For many real seismic data, we might have difficulties to get the low-frequency information because of the low SNR at low frequencies. Thus, the proposed approach set a relatively high demand for data quality. Fortunately, we only require the low-frequency data for slope estimation and the appropriate frequency range varies from 5 Hz to 20 Hz for different datasets, which is not a problem for most field dataset.

\inputdir{field}
\multiplot{6}{field,field-zero,field-seis,fk-field,fk-field-zero,fk-field-seis}{width=0.29\columnwidth}{(a) Original field data. (b) Zero-padded field data. (c) Interpolated field data. (d) $F-K$ spectrum of original field data. (e) $F-K$ spectrum of zero-padded field data. (f) $F-K$ spectrum of interpolated field data.}

\section{Conclusion}
In this paper, we propose to use seislet domain percentile thresholding to iteratively reconstruct the regularly missing seismic traces based on the well-established POCS framework. Numerical tests show that the local slope is the main factor affecting the sparsity and anti-aliasing ability of seislet transform. %In order to provide the optimum slope estimation,
We update the local slope every several iterations and use low-frequency constrained data to prepare the local slope. We use both synthetic and field data examples to show nearly perfect reconstruction results using the proposed approach for reconstructing regularly missing traces. However, the $F-K$ based POCS approach cannot interpolate the irregularly missing traces because of the strong aliasing noise in the $F-K$ domain. The performance of the proposed approach is better than the commonly used $F-X$ prediction based interpolation approach.

\section{Acknowledgements}
We would like to thank the associated editor Luis Gomez and two anonymous reviewers for constructive suggestions on the manuscript. This research is supported by the National Natural Science Foundation of China (Grant No.41274137), the National Science and Technology of Major Projects of China (Grant No. 2011ZX05019-006), and National Engineering Laboratory of Offshore Oil Exploration.

\bibliographystyle{seg}
\bibliography{dealiase}

### 2020-09-16 dealiase2/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{IEEE Geoscience and Remote Sensing Letters, 13, no. 11, 1462-1466, (2016)}

\title{One-step slope estimation for dealiased seismic data reconstruction via iterative seislet thresholding}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\author{Wei Liu\footnotemark[1], Siyuan Cao\footnotemark[1], Shuwei Gan\footnotemark[1], Yangkang Chen\footnotemark[2], Shaohuan Zu\footnotemark[1], Zhaoyu Jin\footnotemark[3]}
\address{
\footnotemark[1]
State Key Laboratory of Petroleum Resources and Prospecting, 
China University of Petroleum, 
Fuxue Road 18th,
Beijing, China, 102200, 
Email: liuwei\_upc@126.com \& csy@cup.edu.cn \& gsw19900128@126.com \& zushaohuan@qq.com\\
\footnotemark[2] Jackson School of Geosciences,
The University of Texas at Austin,
University Station, Box X,
Austin, TX 78713-8924, USA,
Email: ykchen@utexas.edu\\
\footnotemark[3]School of Geosciences,
University of Edinburgh,
Edinburgh,UK, EH9 3JW,
Email: s1263999@sms.ed.ac.uk
}

\maketitle

\begin{abstract}
The seislet transform can be used to interpolate regularly under-sampled seismic data if an accurate local slope map can be obtained. The dealiasing capability of such method highly depends on the accuracy of the estimated local slope, which can be achieved by using the low-frequency components of the aliased seismic data in an iterative manner. Previous approaches to solving this problem have been limited to the unstable estimation of local slope via a large number of iterations. Here, we propose a new way to obtain the slope estimation. We first estimate the NMO velocity and then use a velocity-slope transformation to get the optimal local slope. The new method allows us to avoid the iterative slope estimation and can obtain an accurate slope field in one step. The one-step slope estimation can significantly accelerate the iterative seislet domain thresholding process and can also stabilize the iterative inversion. Both synthetic and field data examples are used to demonstrate the performance by using the proposed approach compared with alternative approaches. 
\end{abstract}

%\begin{keywords}
%Seismic interpolation, seislet transform, velocity-slope transformation, one-step slope estimation
%\end{keywords}

\section{Introduction} 
Due to some physical limitations, such as the presence of obstacles in the field, feathering on the sea, and economical consideration, such as reducing recorded data intentionally in order to save acquisition cost, and other different reasons, seismic records are typically irregularly sampled, or regularly but under-sampled. Seismic data interpolation is such a crucial part in the whole seismic data processing workflow that deals with this problem. It can compensate for the acquisition limitation and help prepare a dense and regularly sampled seismic dataset for subsequent seismic imaging and inversion.  Meanwhile, seismic data reconstruction is also an important procedure to improve the amplitude quality and to remove sampling artifacts, which is of significant importance for subsequent processing workflows including high-resolution processing, amplitude preservation migration and amplitude-versus-offsets (AVO) analysis.

During the past decades, there have been several classical methods for seismic data reconstruction. A number of fixed basis sparsity-promoting transforms have been proposed for restoring seismic data, e.g. the Fourier transform \cite{sacchi,naghizadehfourier,yangkang2014halfthr,yangkang2015eage2}, the Radon transform \cite{trad,yu,wangradon}, the curvelet transform \cite{herrmann,shahidi,liuwei2015} and the seislet transform \cite{seislet,shuwei20153,shuwei20164}.  Spatial predication filters are capable of interpolating aliased data by utilizing non-aliased low frequency data \cite{porsani}. Wave equation methods always require prior distribution of underground parameters, which are computational expensive \cite{ronen}. Rank reduction methods are based on the fact that missing traces and random noise can increase the rank of matrix, such as multichannel singular spectrum analysis (MSSA) \cite{oropezamssa,gaomssa}.

Interpolation of irregularly sampled data has been well solved by using a number of methods belonging to the emerging research field: compressive sensing \cite{donoho2006}. The interpolation problem is transformed into a denoising problem in some sparse transform domains. %However, interpolation of regularly sampled data (or aliased data) is still a big concern. 
The commonly used approach for dealiased seismic interpolation is the prediction based approach \cite{spitz1991}, which uses the low-frequency components to design a prediction error filter for interpolating high-frequency missing components (Spitz's method).

\cite{shuwei20153} proposes a sparse transform based interpolation method based on the seislet transform. The under-sampled regularly sampled data will be sparse in the seislet domain provided that an accurate local slope field can be obtained. To get such accurate slope map, a lot of iterations should be carried out with low-frequency constraints. In this letter, we propose a new algorithm that does not require the iterative slope estimation. The slope map can be easily estimated through velocity-slope transformation \cite{liuyang2013}. In the new method, we can use a fairly small number of projection onto convex sets (POCS) iterations to get a very good interpolation result. Both synthetic and field data examples are used to show the performance. Since the velocity-slope transformation is valid only for prestack seismic data, where data structure is relatively simple and the slope is generally positive, the proposed method can only be used in prestack seismic data reconstruction.

\inputdir{hyper}
\multiplot{6}{hyper,hyper0,hyper-zero,hyper-seis,hyper-fx,hyper-seisvd}{width=0.3\textwidth}{(a) Original synthetic data. (b) Under-sampled data. (c) Zero padded data (50\% traces regularly removed). (d) Reconstructed data by using traditional iterative seislet thresholding. (e) Reconstructed data by using Spitz's method. (f) Reconstructed data by using the proposed approach.}

\section{Method}
\subsection{Projection onto convex sets (POCS)}
The principal problem of seismic data reconstruction is to solve the underdetermined inversion problem:
\begin{equation}
\label{eq:acq}
\mathbf{Sm}=\mathbf{d},
\end{equation}
where $\mathbf{m}$ is the well-sampled seismic data (or model), $\mathbf{S}$ denotes the sampling operator, and $\mathbf{d}$ denotes the observed data \cite{yangkang2014halfthr}. Because of the missing traces, the operator $\mathbf{S}$ is highly singular and thus makes equation \ref{eq:acq} highly underdetermined.

There have been many different algorithms for solving equation \ref{eq:acq} by imposing different constraints. In the seismic data processing field, the POCS algorithm \cite{abma2006} is one of the most widely used methods to interpolate seismic data with irregularly missing traces, and has the following iterative expression:
\begin{equation} 
\label{eq:pocs}
\mathbf{m}_{n+1}=\mathbf{d}+(\mathbf{I}-\mathbf{S})\mathbf{A}^{-1}\mathbf{T}\mathbf{A}[\mathbf{m}_n],
\end{equation}
where $\mathbf{m}_n$ denotes the reconstructed data after $n$th iteration, $\mathbf{A}$ and $\mathbf{A}^{-1}$ are the forward and inverse sparsity-promoting transforms, $\mathbf{I}$ is an identity matrix and $\mathbf{T}$ is a thresholding operator. However, for regularly missing traces, POCS can not obtain satisfied results because of the strong aliasing noise in the sparse domain. \cite{shuwei20153} has shown that the seislet-based POCS algorithm can still be effective for interpolating regularly missing traces provided that an accurate local slope map can be obtained. All the examples in this paper are based on the iterative framework \ref{eq:pocs}. The thresholding operator $\mathbf{T}$ is chosen as a soft-thresholding operator in the seislet domain:
\begin{equation}
\label{eq:soft}
%\mathbf{\mathcal{T}}_{\gamma_i} (\mathbf{x}) =
\mathbf{T}_{\gamma}(v(\mathbf{x})) = \left\{ \begin{array}{ll}
v(\mathbf{x})-\gamma \frac{v(\mathbf{x})}{|v(\mathbf{x})|} & \text{for}\quad  |v(\mathbf{x})| > \gamma  \\
0			      & \text{for}\quad  |v(\mathbf{x})| \le \gamma
\end{array}\right.,
\end{equation}
where $\mathbf{T}_{\gamma}$ corresponds to the soft thresholding operator with a threshold value $\gamma$.  $\mathbf{x}$ denotes the coordinates vector. $v(\mathbf{x})$ denotes the value the spatial point $\mathbf{x}$.

\subsection{Dealiased interpolation by low-frequency constrained iterative local slope estimation}
 When interpolating the regularly missing traces by using a seislet-based POCS algorithm, there are three key factors that can affect the final reconstruction results: (1) The slope estimation. (2) The threshold value in the seislet transform. (3) The number of iterations. For the traditional approach, we calculate the local slope every a small number of iterations using the low-frequency components of seismic data. The large number of iterations is also used to ensure an acceptable slope estimation. The threshold value is designed assuming that a constant percentage of transform coefficients can optimally represent the true data. In the next section, we propose a very effective and efficient way for improving the traditional interpolation by using a different slope estimation approach, which is efficient and accurate enough to allow us to obtain a successful interpolation performance through a fairly small number of iterations.

\subsection{Dealiased interpolation via one-step local slope estimation based on velocity-slope transformation}
The estimation of the local slope in highly under-sampled data is a challenging problem. Instead of estimating the local slope by using the plane-wave destruction (PWD) algorithm \cite{fomel2002pwd} directly, we first calculate the NMO velocity  by using simple NMO-correction based velocity analysis and then transform the NMO velocity to local slope \cite{liuyang2013} by using
\begin{equation}
\label{eq:vtop}
p(t,x)=\frac{x}{t(x)v_n^2(t_0,x)},
\end{equation}
where $t_0$ is the zero-offset traveltime, $t(x)$ is the traveltime recorded at offset $x$, $v_n(t_0,x)$ is the NMO velocity, and $p(t,x)=dt/dx$ is the local slope. It is salient that $p(t,x)>0$ when $x>0$, as shown by the example in Fig. \ref{fig:hyper,hyper0,hyper-zero,hyper-seis,hyper-fx,hyper-seisvd}. The detailed velocity-slope transformation was introduced in \cite{liuyang2013}. It should be mentioned that such velocity-slope transformation was used previously by \cite{liuyang2015} and \cite{shuwei2016} for signal and noise separation. We use the velocity-slope transformation here for iterative interpolation based on seislet thresholding. We admit here that since equation \ref{eq:vtop} is derived from prestack data, the iterative interpolation approach based on the velocity-slope transformation cannot be applied to poststack seismic data processing, where the data structure can be arbitrarily complex and local slope can vary rapidly. Although prestack data can also be complex, we limit our algorithm in a simpler case, where we assume that the prestack data structure is relatively simple and do not have negative slope. As far as we know, this assumption is satisfied in most situations.

The seislet transform has found successful applications in noise attenuation \cite{seislet,yangkang20142}. However, the successful application of the seislet transform in iterative interpolation, especially in the industry, is not reported often. One of the drawbacks that impede the wide application of seislet based interpolation is the efficiency. The seislet transform itself does not slow down the efficiency too much. However, the slope estimation that is required by the seislet transform is much slower. The efficiency of seislet transform is about 2-4 times slower than the fast Fourier transform, and is about 4-8 times slower than the fast wavelet transform \cite{seislet}.   In order to accelerate the process, the slope estimation is commonly estimated every several iterations.

In \cite{shuwei20153}, the slope estimation is iterated every 5 iterations. Even though, the computational cost is still much heavier than the widely used Fourier transform. In this letter, the one-step slope estimation from velocity-slope transformation (shown in equation \ref{eq:vtop}) can greatly improve the efficiency by reducing numerous cost in iterative slope estimation. According to the performance of the synthetic example in the letter, the more accurate slope can even make the finally reconstructed data more accurate.  Thus, the utilization of velocity-slope transformation in seislet-based interpolation could be of a huge influence on promoting the wide application of seislet based interpolation approach in the industry.

\section{Examples}
We present two examples to show the superior performance  by using the proposed algorithm and the significance of one-step slope estimation.  The first example is shown in Fig. \ref{fig:hyper,hyper0,hyper-zero,hyper-seis,hyper-fx,hyper-seisvd}. Fig. \ref{fig:hyper} shows the original data. Fig. \ref{fig:hyper0} shows the under-sampled data by removing 50\% traces. Fig. \ref{fig:hyper-zero} shows the zero-padded section. It is worth mentioning that in the interpolation based inverse problem, Fig. \ref{fig:hyper-zero} is treated as the observed data with preprocessing done on Fig. \ref{fig:hyper0} (adding the zero traces). Fig. \ref{fig:hyper} is treated as the true model. The reconstruction results are compared with Fig. \ref{fig:hyper} to evaluate the performance.  Figs. \ref{fig:hyper-seis}, \ref{fig:hyper-fx}, and \ref{fig:hyper-seisvd} show the interpolated results by using traditional iterative seislet thresholding approach, prediction based approach, and the proposed approach, respectively. All the three methods seem to obtain good results.   Fig. \ref{fig:hyper-seis-dif,hyper-fx-dif,hyper-seisvd-dif} shows the reconstruction error by using three different approaches. There is nearly no error in most portion of the profile except for some small ones between 1s and 1.5s for the proposed approach (Fig. 2(c)). However, the other two approaches will cause significantly more useful energy damages. Fig. \ref{fig:hyper-sdip,hyper-pdip,hyper-dipiter,hyper-vdip} shows the calculated slope for different datasets. The slope estimated by using the velocity-slope transformation is almost the same as the true slope, while the slope via iterative low-frequency constrained estimation has a much larger error.  In order to numerically compare the reconstruction performance, the signal-to-noise ratio (SNR) is also used here, which was defined as \cite{herrmann,yangkang2015ortho}:
\begin{equation}
\label{eq:snr}
SNR_n=10\log_{10}\frac{\Arrowvert \mathbf{m}_{true} \Arrowvert_2^2}{\Arrowvert \mathbf{m}_{true} -\mathbf{m}_n\Arrowvert_2^2}.
\end{equation}
where $\mathbf{m}_n$ denotes the reconstructed data after $n$th iteration, and $\mathbf{m}_{true}$ denotes the true model.
The SNRs comparison between the traditional seislet thresholding and the proposed seislet thresholding are shown in Figs. \ref{fig:snrs-pocs} and \ref{fig:snrs-pocsvd}. It is obvious that in addition to the tremendous computational cost reduced by the one-step estimation and less desired number of iterations, the proposed approach can also improve the final reconstructed result. The converged SNR by using the proposed approach after 40 iterations is about 27 dB, while the SNR by using the traditional approach after  200 iterations is only about 15 dB. Besides, from the SNR diagrams, we can also infer that the traditional approach might not be stable after a large number of iterations because of the error accumulation on the slope, since the SNR starts to decrease after about 150 iterations.

In order to test the influence of noise, we add some background noise to the synthetic example and conduct the same experiment as the clean data example. Figs. \ref{fig:hyper-n,hyper0-n,hyper-zero-n,hypern-seis,hypern-fx,hypern-seisvd} and \ref{fig:hypern-seis-dif,hypern-fx-dif,hypern-seisvd-dif} show the reconstruction performance for the noisy data.  Figs. \ref{fig:hyper-n}, \ref{fig:hyper0-n}, and \ref{fig:hyper-zero-n} show the noisy counterparts of Figs.  \ref{fig:hyper}, \ref{fig:hyper0}, and \ref{fig:hyper-zero}. Figs. \ref{fig:hypern-seis}, \ref{fig:hypern-fx}, and \ref{fig:hypern-seisvd} show the reconstructed results by using three different methods. Figs. \ref{fig:hypern-seis-dif}, \ref{fig:hypern-fx-dif}, and \ref{fig:hypern-seisvd-dif} show their corresponding error sections. In this noisy data experiment, the true model is still the clean data shown in Fig. \ref{fig:hyper}. By comparing the figures in Figs. \ref{fig:hyper-n,hyper0-n,hyper-zero-n,hypern-seis,hypern-fx,hypern-seisvd} and \ref{fig:hypern-seis-dif,hypern-fx-dif,hypern-seisvd-dif}, we can get a similar conclusion as the clean data experiment. The proposed approach can obtain the best performance, although the overall performance is worse than the clean data experiment. In this case, Spitz's method causes a lot of residual noise in the final result, since it is based on the prediction filter, which will inevitably predict the random noise.

The next example is a poorly sampled marine dataset, which is shown in Fig. \ref{fig:bei}. Fig. \ref{fig:bei-zero} shows the zero-padded data. Fig. \ref{fig:vscan} shows the NMO-based velocity analysis. The black string denotes the automatically picked NMO velocity. Fig. \ref{fig:bei-pdip} shows the local slope calculated directly from the noisy and incomplete data by using the PWD algorithm (Fig. \ref{fig:bei-zero}). Fig. \ref{fig:bei-vdip} shows the obtained local slope by using the velocity-slope transformation equation \ref{eq:vtop}. The slope calculated through PWD algorithm is far from reasonable to capture the true local slope information of the data while the slope from the velocity-slope transformation can be interpreted well. Thus the latter method can be more stable in dealing with highly incomplete and noisy field datasets. Figs. \ref{fig:bei-fx} shows the result by using Spitz's method. Fig. \ref{fig:bei-seisvd} shows the result by using the proposed approach, which is of higher quality than Spitz's method. Figs. \ref{fig:fk-bei,fk-bei-zero,fk-bei-fx,fk-bei-seisvd} shows the corresponding FK spectrum of different datasets, which also confirms that the aliasing problem is no longer existing after implementation of the proposed method.  If observed carefully, some low-frequency low-wavenumber components can be discerned in Fig. \ref{fig:fk-bei-seisvd}. In order to know exactly what these spectrum components represent in the time-space domain, we filter the final reconstructed result with a simple bandpass filter (with a bound frequency 9 Hz) and show the filtered result in Fig. \ref{fig:bei-seis-bp}. Although we can not see obvious differences between Figs. \ref{fig:bei-seisvd} and \ref{fig:bei-seis-bp}, we can find something in their difference section, as shown in Fig. \ref{fig:bei-dif-bp}. The data shown on Fig. \ref{fig:bei-dif-bp} corresponds to the low-frequency and low-wavenumber components of the field data, which is however very important to many seismic data processing tasks such as waveform inversion. Figs. \ref{fig:fk-bei-seis-bp} and \ref{fig:fk-dif-bp} show the FK spectrum of Figs. \ref{fig:bei-seis-bp} and \ref{fig:bei-dif-bp}, respectively. Figs. \ref{fig:fk-bei-seis-bp} and \ref{fig:fk-dif-bp} not only demonstrate the correctness of the bandpass filter, but also confirm the low-frequency data recovery property of the proposed algorithm.

\section{Conclusion}
The seislet-based POCS algorithm can be used to interpolate regularly missing traces, but requires a fairly accurate local slope estimation. The iterative slope estimation strategy may not always  be successful, which will degrade the final interpolation performance. We propose a more stable way for calculating the local slope by using the velocity-slope transformation, which reduces the number of iterations needed in interpolation and can significantly improve the interpolation performance. Results from both synthetic and field data examples show that the proposed seislet-based POCS algorithm with one-step slope estimation can efficiently and effectively reconstruct the regularly missing traces.

\inputdir{hyper}
\multiplot{3}{hyper-seis-dif,hyper-fx-dif,hyper-seisvd-dif}{width=0.3\textwidth}{(a) Reconstruction error by using the traditional iterative seislet thresholding. (b) Reconstruction error by using Spitz's method. (c) Reconstruction error by using the proposed approach. }

\multiplot{2}{snrs-pocs,snrs-pocsvd}{width=0.3\textwidth}{(a) SNRs by using the traditional iterative seislet thresholding. (b) SNRs by using the proposed approach. Please note that a large number of iterations can be saved and the performance can be improved.}

\multiplot{4}{hyper-sdip,hyper-pdip,hyper-dipiter,hyper-vdip}{width=0.45\textwidth}{(a) True slope. (b) Slope from PWD. (c) Slope estimated iteratively. (d) Slope from velocity-slope transformation. }

\inputdir{hypern}
\multiplot{6}{hyper-n,hyper0-n,hyper-zero-n,hypern-seis,hypern-fx,hypern-seisvd}{width=0.3\textwidth}{(a) Noisy synthetic data. (b) Under-sampled data. (c) Zero padded data (50\% traces regularly removed). (d) Reconstructed data by using traditional iterative seislet thresholding. (e) Reconstructed data by using Spitz's method. (f) Reconstructed data by using the proposed approach.}

\multiplot{3}{hypern-seis-dif,hypern-fx-dif,hypern-seisvd-dif}{width=0.3\textwidth}{Noisy data example. (a) Reconstruction error by using the traditional iterative seislet thresholding. (b) Reconstruction error by using Spitz's method. (c) Reconstruction error by using the proposed approach. }

\inputdir{bei}
\multiplot{7}{bei,bei-zero,vscan,bei-pdip,bei-vdip,bei-fx,bei-seisvd}{width=0.21\textwidth}{(a) Original under-sampled field data.  (b) Zero padded data (with 50\% traces regularly removed). (c) Velocity analysis result. (d) Local slope calculated directly from (b) by using the PWD algorithm. (e) Local slope calculated from the velocity-slope transformation. (f) Reconstructed data by using Spitz's method. (g) Reconstructed data by using the proposed approach. }

\multiplot{4}{fk-bei,fk-bei-zero,fk-bei-fx,fk-bei-seisvd}{width=0.45\textwidth}{FK spectrum of different sections. (a) Original under-sampled field data. (b) Zero padded data (with 50\% traces regularly removed). (c) Reconstructed data by using Spitz's method. (d) Reconstructed data by using the proposed approach. }

\multiplot{4}{bei-seis-bp,bei-dif-bp,fk-bei-seis-bp,fk-dif-bp}{width=0.45\textwidth}{(a) Bandpass filtered result after iterative seislet thresholding with a bound frequency 9 Hz. (b) Low frequency data of the reconstructed data in Fig. \ref{fig:bei-seisvd}. (c) FK spectrum of (a). (d) FK spectrum of (b). }

\section{Acknowledgments}
This research is partially supported by National Science and Technology Major Project of China under Grants No. 2011ZX05024-001-01 and Texas Consortium for Computational Seismology (TCCS). %Moreover, we are also grateful for the support of the Australian and Western Australian Governments and the North West Shelf Joint Venture Partners, as well as the Western Australian Energy Research Alliance.

\bibliographystyle{seg}
\bibliography{dealiase}

### 2020-09-16 demulemd/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{IEEE Geoscience and Remote Sensing Letters, 14, 18-22, (2017)}

\title{Multiple reflections noise attenuation using adaptive randomized-order empirical mode decomposition}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\author{Wei Chen\footnotemark[1]\footnotemark[2], Jianyong Xie\footnotemark[3]\footnotemark[4], Shaohuan Zu\footnotemark[3]\footnotemark[5], and Shuwei Gan\footnotemark[3], and Yangkang Chen\footnotemark[6]}
\address{
\footnotemark[1]
Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education, Yangtze University, Wuhan, Hubei, 430100, China \\
\footnotemark[2]
Hubei Cooperative Innovation Center of Unconventional Oil and Gas, Wuhan, Hubei 430100, China, Email: chenwei2014@yangtzeu.edu.cn \\
\footnotemark[3]State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
\footnotemark[4]
Department of Physics, 
University of Alberta, 
Edmonton Alberta, T6G 2E1, Canada,
Emails: xjyshl@sina.com\\
\footnotemark[5] Modeling and Imaging Laboratory\\
Earth and Planetary Sciences\\
University of California\\
Santa Cruz, CA 95064\\
zushaohuan@qq.com\\
\footnotemark[6]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
chenyk2016@gmail.com\\
}

\maketitle

\begin{abstract}
We propose a novel approach for removing multiple reflections noise based on an adaptive randomized-order empirical mode decomposition framework. We first flatten the primary reflections in common midpoint (CMP) gather using the automatically picked NMO velocities that correspond to the primary reflections and then randomly permutate all the traces. Next, we removed the spatially distributed random spikes that correspond to the multiple reflections using the EMD based smoothing approach that is implemented in the $f-x$ domain. The trace randomization approach can make the spatially coherent multiple reflections random along the space direction and can decrease the coherency of near-offset multiple reflections. The EMD based smoothing method is superior to median filter and prediction error filter in that it can help preserve the flattened signals better, without the need of exact flattening, and can preserve the amplitude variation much better. In addition, EMD is a fully adaptive algorithm and the parameterization for EMD based smoothing can be very convenient. 
\end{abstract}
%
%\begin{keywords}
%Multiple reflections noise attenuation, empirical mode decomposition, randomized-order EMD, adaptive algorithm
%\end{keywords}

\section{Introduction} 
Multiples are multiplicative events seen in seismic profiles, which undergoes more than one reflections \cite{wujiandemul2016}. Multiple attenuation is one of the most important steps in seismic data processing, especially for marine data processing. Instead of being incoherent along the spatial direction like random noise \cite{hongbo2015,yangkang2016dsd}, the multiple reflections are coherent and behave nearly the same as the primary reflections, which makes it very difficult to remove them using simple signal processing methods. The surface related multiple elimination (SRME) is one of the most appealing approaches to attenuate the multiple reflections, which includes two main steps: multiple prediction and adaptive subtraction \cite{verschuur1992,shoudong2009}.  The surface related multiple reflections are first predicted based on the SRME theory and then adaptively subtracted from the raw data record. The adaptive subtraction step is intended to adjust for the mismatch of amplitude and phase during the SRME prediction step. There have existed several ways for designing the adaptive subtraction filters. \cite{verschuur1992} proposed  the classic least-squares based method for building the adaptive subtraction filter, which is called the stationary matching filter \cite{shebao2015}. \cite{yanghua20031} proposed an expanded multiple multichannel matching filter, which exploits more local time and phase information to match the multiple reflections. The regularized optimization is also adopted for non-stationary matching filtering \cite{fomel20095,yangkang2015ortho}, which better appeals to the real non-stationary seismic data. Another widely used approach to attenuate multiple reflections is by dip filtering after normal moveout (NMO) of primary reflections. While the primary reflections are flattened after NMO, the multiple reflections cannot be flattened in the NMO corrected gather. Usually a Radon transform is used to remove the unflattened multiple reflections \cite{foster1992,yanghua2003,porsani2011,donno2011,zhuang2015,yarudemul2016}. The dip filtering based approach can not only attenuate the surface-related multiple reflections, but also can attenuate high-order multiple reflections or interbed multiple reflections. When processing the marine field seismic data, the SRME method and the dip filtering based method are usually combined to obtain the optimal suppression of all types of multiple reflections.

Empirical mode decomposition (EMD) \cite{huangemd} can adaptively decompose a non-stationary signal into different stationary components, which are called intrinsic mode functions (IMF). The oscillating frequency of each IMF decreases according to the separation sequence of each IMF.  EMD has found successful applications in seismic data processing \cite{yangkang20141,yangkang2016emd}.  EMD is commonly applied in each frequency slice in the frequency-space domain and the highest wavenumber component is removed.  The only parameter we need to define in such method is the number of dip components. Considering that, in practice, we commonly choose to remove the first EMD component in order to remove the highest oscillating components, the EMD based filtering is non-parametric. Because of the adaptivity and the superior performance of the EMD based smoothing in field seismic data processing, more and more researchers are turning to use this technique as a blind-processing tool in order to deal with the rapidly increasing data size in modern seismic data processing \cite{yangkang2015enhemd}.

In this letter, we propose a novel EMD based approach called randomized-order EMD to attenuate multiple reflections noise \cite{carvalho1992,fomel20095,weglein2003,weglein2013}. The common midpoint (CMP) gather is first flattened by using the automatically picked velocities \cite{fomel20091} corresponding to the primary reflections. Then, the primary reflections are flattened while the multiple reflections are not. Since the multiple reflections and primary reflections are much similar in the near-offset part, we propose to first randomize the data along the spatial direction and make the unflattened multiple reflections behave like random incoherent noise along the spatial direction. Then the EMD based smoothing algorithm is applied to remove such incoherent noise. After EMD based smoothing, an inverse randomization step is applied, which is followed by the inverse normal moveout. The proposed approach is compared with median filtering and prediction error filtering based approaches. The performance shows that the EMD based smoothing algorithm can have stronger capability in removing the incoherent noise while preserving more primary reflections energy. The randomized-order EMD approach can not only be used in attenuating multiple reflections noise, but also be used in attenuating other types of coherent noise. The proposed method solves two long-standing problems in existing demutiple algorithms. The first one is the difficulty in separating coherent signal and coherent noise in near-offset traces, because they have very close local slopes and curvatures. The second one is the difficulty in selecting optimal parameters when applying a denoising operator. In many traditional denoising algorithms, the parameters are highly dependent on the input data set. The proposed algorithm solves the first problem by shuffling the traces along the spatial direction that help best distinguish between signal and noise. The proposed algorithm solves the second problem by using the EMD based method to adaptively process the data, where we do not need to specify any input parameter regardless of the complexity of input data set.

\section{Method}
The dip filtering based multiple reflections noise attenuation approaches depend on the separation between multiple reflections and primary reflections in the NMO corrected CMP gather, especially in the near offset where the local slopes between primary reflections and multiple reflections are very close. In this letter, we propose two novel strategies to better separate the primary reflections and multiple reflections. The first strategy is based on a trace randomization procedure, where we can turn the unflattened multiple reflections into random noise and maximize the difference between primary reflections and multiple reflections in the near offset. The next strategy is a different spatial smoothing approach. The new smoothing approach is based on the empirical mode decomposition (EMD), where we can attenuate the random noise that corresponds to multiple reflections adaptively, and more importantly we can preserve the useful reflection energy even though the events are not exactly flattened.

\subsection{Brief review of EMD}
EMD is an adaptive signal analysis algorithm that decomposes a non-stationary 1D signal into multiple stationary sub-signals:
\begin{equation}
\label{eq:emd}
s(t) = \sum_{n=1}^N c_n(t) + r(t).
\end{equation}
where $s(t)$ is a non-stationary 1D signal and $c_n(t)$ is $n$th decomposed stationary signal, which is also called intrinsic mode function (IMF). $r(t)$ is the monotonic residual. $N$ is the number of IMFs.

The decomposition is achieved via a recursive process called sifting algorithm. There are four main steps in the sifting algorithm: firstly, finding the local maxima and minima of the signal, and then fitting those extrema by cubic spline interpolation in order to obtain the upper and lower envelopes; secondly, calculating the mean of upper and lower envelopes and subtracting it from the original signal; thirdly, recursively implementing the first two steps until the remaining signal satisfy the two criteria of IMF: (1) the number of extrema and the number of zero crossing points cannot differ by more than one; (2) the mean value of upper envelope and lower envelope must be zero \cite{huangemd}; fourthly, subtracting the obtained IMF from the original signal and implementing the aforementioned three steps recursively on the remaining signal until the residual $r(t)$ becomes either too small or a monotonic function.

\subsection{EMD based smoothing}
\cite{yangkang2014emdsum} provided an overall introduction of the applications of EMD in random noise attenuation of seismic data. The best way to utilize EMD to remove spatially incoherent noise is to apply EMD along the space direction in each frequency slice and to remove the first decomposed mode that contains the high-wavenumber noise.

The methodology can be summarized mathematically as:
\begin{equation}
\label{eq:fxemd}
\hat{s}(m,t) = \mathcal{F}^{-1}\left(\sum_{n=2}^{N}C_n(m,w)\right), 
\end{equation}
\begin{equation}
\label{eq:fxemd2}
\mathcal{F} d(m,t)  = \sum_{n=1}^{N} C_n(m,w),
\end{equation}
where $\hat{s}(m,t)$ and $d(m,t)$ denote the estimated signal and observed noisy signal, respectively. $\mathcal{F}$ and $\mathcal{F}^{-1}$ denote the forward and inverse Fourier transforms along the time axis, respectively. $C_n$ denotes the $n$th EMD decomposed component. $w$ denotes frequency.

The detailed workflow can be summarized as 
%The EMD based smoothing method was proposed by \cite{bekara} as:
\begin{enumerate}
\item 
Transform the data from $t-x$ domain to $f-x$ domain.
\item 
For each frequency slice, 
\begin{enumerate}
\item
separate real and imaginary parts in the spatial sequence,
\item
compute the first IMF, for the real signal and subtract it to obtain the filtered real signal,
\item
repeat for the imaginary part,
\item
combine to create the filtered complex signal.
\end{enumerate}
\item
Transform data back to the $t-x$ domain.
\end{enumerate}

Smoothing via EMD has two main advantages. The first is its adaptivity. One does not need to decide any parameter before using the EMD based smoothing approach. As can be seen in equation \ref{eq:fxemd}, the first component after EMD is removed in each frequency slice to attenuate any spatially incoherent noise, which is very convenient to implement and has a robust performance. Another advantage is that EMD based smoothing can preserve the spatial amplitude variation details well since it does not require the exactly horizontal data structure. Smoothing via EMD can get very smooth final results. Unlike some other spatial smoothing operators such as mean filter, median filter or KL filter, the EMD based smoothing can also perform well even when the events have small curvatures. The main difference between the EMD and other decomposition algorithms is that it is empirical and thus adaptive to different input data sets, while other algorithms are based on a carefully designed mathematical model that requires a time-consuming parameter setting process \cite{liuwei2016,liuwei2016vmd,huijian2016}.

\inputdir{syn}
\multiplot{6}{ncmp,back,nrand-emd-back,rand,dif,emd-dif}{width=0.45\textwidth}{(a) CMP gather. (b) Demultipled using PEF method. (c) Demultipled using the proposed approach. (d) Trace randomization result of (a). (e) Noise corresponding to (b). (f) Noise corresponding to (c).}

\inputdir{haskell}
\multiplot{2}{hask,nmo}{width=0.45\textwidth}{(a) Original synthetic example. (b) Flattened CMP gather by picking the primary reflections related velocity peaks.}

\subsection{Randomized-order EMD}
EMD was thought to be useful only in attenuating spatially incoherent noise. However, the multiple reflections noise in seismic data is spatially coherent. Here, we propose a novel randomized-order EMD in order to make EMD capable of attenuating spatially coherent noise. The randomized-order EMD can be summarized in five main procedures. Firstly, each common midpoint (CMP) gather is flattened according to the normal moveout (NMO) velocity of primary reflections. This step will require NMO velocity analysis \cite{yangkang2015vel,shuwei2016vscan}. An automatic velocity picking approach is used to pick the NMO velocities that corresponds to the primary reflections \cite{fomel20091}. After the first step, the primary reflections are flattened while the multiple reflections noise of different orders are not. Secondly, the traces are shuffled randomly in order to make the unflattened multiple reflections noise spatially random. Because the primary reflections have small spatial variations, a random trace randomization along the spatial direction will not change the shape of primary reflections too much but will greatly change the spatial coherency of multiple reflections noise. More specifically, the spatially coherent multiple reflections noise can be transformed into spatially incoherent random noise. Thirdly, EMD based smoothing is applied to the randomized CMP gather to attenuate all spatially incoherent noise. Finally, the inverse trace randomization is implemented to the smoothed CMP gather, which is followed by the inverse NMO.

In this letter, EMD is utilized to attenuate noise other than random noise. The randomized order EMD is used for attenuating multiple reflections noise. Since the randomized-order EMD is a generally framework, it can also be used to attenuate any types of unwanted spatially coherent noise, such as ground roll noise \cite{yangkang2015orthogroll} and point source diffraction.

Fig. \ref{fig:ncmp,back,nrand-emd-back,rand,dif,emd-dif} shows an example of the randomization process. Fig. \ref{fig:ncmp} is a NMO corrected CMP gather with multiple reflections not flattened. Fig.  \ref{fig:rand} shows the section after random permutation of all the traces along the spatial direction. It is obvious that after random shuffling, the multiple reflections turn into random spikes from the spatial view while the primary reflections are still coherent. The spikes can be removed using any type of coherency-based denoising approach. Fig. \ref{fig:back} shows demultipled data using a common PEF filter \cite{Abma1995}. Fig. \ref{fig:nrand-emd-back} shows the demultipled data using EMD based smoothing. Figs. \ref{fig:dif} and \ref{fig:emd-dif} show the removed multiple reflections using PEF and EMD based approaches, respectively. The performance using the PEF method is not acceptable since there is still some noise left. Since we know the true signal in this example, we can quantitively compare the denoising performance between two methods. We use the signal-to-noise ratio (SNR) defined below to measure the denoising performance \cite{yangkang20142,shuwei20153,weilin2016,shaohuan2016}:
\begin{equation}
\label{eq:diff}
SNR=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2^2}{\Arrowvert \mathbf{s} -\hat{\mathbf{s}}\Arrowvert_2^2},
\end{equation}
 where $\mathbf{s}$ and $\hat{\mathbf{s}}$ denote the true and estimated signals, respectively. 
The calculated SNRs of the original noisy data, denoised data using PEF and denoised data using EMD are 0.168 dB, 8.344 dB, and 9.061 dB, respectively. The SNR comparison confirms the better denoising performance using the EMD method.

\multiplot{6}{h-ncmp,h-rand,h-back,h-dif,h-nrand-emd-back,h-emd-dif}{width=0.3\textwidth}{(a) CMP gather. (b) Trace randomization result.  (c) Demultipled using the PEF method. (d) Noise corresponding to (c). (e) Demultipled using the proposed method.  (f) Noise corresponding to (e).}

\inputdir{haskell}
\multiplot{6}{h-ncmp,h-rand,h-back,h-dif,h-nrand-emd-back,h-emd-dif}{width=0.3\textwidth}{(a) CMP gather. (b) Trace randomization result.  (c) Demultipled using the PEF method. (d) Noise corresponding to (c). (e) Demultipled using the proposed method.  (f) Noise corresponding to (e).}

\inputdir{mobil}
\multiplot{6}{cmp0,vscan,demul-mf,vscan-mf,demul-emd,vscan-emd}{width=0.3\textwidth}{(a) CMP gather. (b) Velocity spectrum of (a). (c) Demultipled using MF. (d) Velocity spectrum of (c). (e) Demultipled using EMD.   (f) Velocity spectrum of (e). }

\multiplot{2}{dif-mf,dif-emd}{width=0.45\textwidth}{(a) Removed multiple reflections using MF. (b) Removed multiple reflections using EMD. }

\section{Example}
First we make a synthetic example, as shown in Fig. \ref{fig:hask,nmo}. Fig. \ref{fig:hask} shows the noisy data. Fig. \ref{fig:nmo} shows the NMO corrected data with multiple reflections not flattened.

We zoom a part from the data and show detailed comparison of demultiple performance using median filter (MF) based and EMD based approaches (Fig. \ref{fig:h-ncmp,h-rand,h-back,h-dif,h-nrand-emd-back,h-emd-dif}). Fig. \ref{fig:h-ncmp} shows the noisy zoomed CMP gather. Fig. \ref{fig:nmo} shows the data after randomization.  Fig. \ref{fig:h-back} is the demultipled data using MF. Fig. \ref{fig:h-dif} shows its corresponding noise. Fig. \ref{fig:h-nrand-emd-back} shows the demultipled data using EMD and Fig. \ref{fig:h-emd-dif} shows the corresponding noise. It is obvious that the EMD based approach can make the flattened primary reflections more coherent while the MF based approach will cause some abnormal features, since the MF based approach is more based on the spike-like property of noise. While the noise is just incoherent but not spiky, MF based approach cannot obtain a successful performance.

The second example is a field data example, which is shown in Fig. \ref{fig:cmp0}.
There exists strong internal multiple reflections in this CMP gather. Figs. \ref{fig:demul-mf} and \ref{fig:demul-emd} show the results using MF and EMD based approaches (here we omit the flattening, randomization, processes and just show the final performances). It is clear that the proposed approach can obtain more coherent primary reflections. The bottom row of Fig. \ref{fig:cmp0,vscan,demul-mf,vscan-mf,demul-emd,vscan-emd} shows the velocity spectra that corresponds to the top row of Fig. \ref{fig:cmp0,vscan,demul-mf,vscan-mf,demul-emd,vscan-emd}. The strong multiple reflections energy can be revealed from Fig. \ref{fig:vscan}. Figs. \ref{fig:vscan-mf} and \ref{fig:vscan-emd} confirm that significant multiple reflections energy has been removed while the EMD based approach obtain an obviously better preservation of the primary energy, since the velocity spectrum corresponding EMD has more focused and stronger velocity peaks. The removed multiple reflections using MF and EMD approaches are shown in Figs. \ref{fig:dif-mf} and \ref{fig:dif-emd}, respectively.

\section{Conclusions}
We propose a novel approach to attenuate multiple reflections using randomized-order empirical mode decomposition (EMD). EMD is applied in each frequency slice to obtain different oscillating wavenumber components. The several highest wavenumber components are then removed to remove the unflattened high wavenumber components. In order to make EMD based smoothing approach capable of attenuating spatially coherent noise, we propose to first apply a trace randomization procedure to the NMO-corrected CMP gather to make the unflattened multiple reflections spatially incoherent (like random noise) and thus easier for attenuation. Compared with the other denoising approaches that are based on spatial coherency, the proposed EMD based approach is non-parametric and can obtain a better demultiple performance with a better preservation of the flattened primary reflections. The proposed EMD based approach is also more adaptive than those more advanced EMD based approaches, like EEMD \cite{eemd}, CEEMD \cite{epsceemd}, or ICEEMD \cite{iceemd2014}, which require more input parameters.

\section{Acknowledgments}
We would like to thank Tingting Liu, Zhaoyu Jin, and Wei Liu for helpful comments and suggestions on the topic of EMD. We are grateful to developers of the Madagascar software package for providing corresponding codes for testing the algorithms and preparing the figures. This research is supported by Sinopec Key Laboratory of Geophysics (Grant No. 33550006-15-FW2099-0017) and Texas Consortium for Computational Seismology (TCCS).

\bibliographystyle{seg}
\bibliography{mulemd}

### 2020-09-16 diffrlrra/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\title{Separation and imaging of seismic diffractions using a localized rank-reduction method with adaptively selected ranks}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\author{Hang Wang \footnotemark[1], Xingye Liu \footnotemark[2] and Yangkang Chen\footnotemark[1]}

\ms{GEO-2020}

\address{
\footnotemark[1]
Key Laboratory of Geoscience Big Data and Deep Resource of Zhejiang Province\\
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
chenyk2016@gmail.com \& 18328504171@163.com\\
\footnotemark[2]
College of Geology and Environment\\
Xi’an University of Science and Technology\\
Xi’an, Shaanxi Province, China, 710054 \\
lwxwyh506673@126.com\\
Corresponding Author: Yangkang Chen (chenyk2016@gmail.com) 
}

\lefthead{Wang et al.}
\righthead{Separation and imaging of seismic diffractions}

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}

\begin{abstract}
Seismic diffractions are some weak seismic events hidden within the more dominant reflection events in a seismic profile. Separating diffraction energy from the post-stack seismic profiles can help infer the subsurface discontinuities that generate the diffraction events. The separated seismic diffractions can be migrated with a traditional seismic imaging method or a specifically designed migration method to highlight the diffractors, i.e., the diffraction image. Traditional diffraction separation methods based on the the underlying plane-wave assumption are limited by either the inaccurate slope estimation or the plane-wave assumption of the PWD filter, and thus will cause reflection leakage into the separated diffraction profile. The leaked reflection energy will deteriorate the resolution of the subsequent diffraction imaging result. Here, we propose a new diffraction separation method based on a localized rank-reduction method. The localized rank-reduction method assumes the reflection events to be locally low-rank and the diffraction energy can be separated by a rank-reduction operation. Compared with the global rank-reduction method, the localized rank-reduction method is more constrained in selecting the rank and is free of separation artifacts. We use a carefully designed synthetic example to demonstrate that the localized rank-reduction method can help separate the diffraction energy from a post-stack seismic profile with both kinematically and dynamically accurate performance. 
\end{abstract}

\maketitle

%\section{Keywords}
%key1,key2,key3

\section{Introduction}
Diffraction is a very common \dlo{type of seismic waves which}\wen{wave type that} can be observed in almost every \wen{seismic} data set. \dlo{The small-scale}\wen{Small-scale} geological bodies (such as \dlo{salt dome,} faults and fractures in carbonate rocks\dlo{, etc.}) are the main \dlo{reasons for the appearance of it}\wen{cause}. As the simple hydrocarbon reservoirs have been fully explored and exploited, the unconventional hydrocarbon reservoirs controlled by these small geological bodies \dlo{gradually draw}\wen{are now drawing} attentions of\dlo{ the} exploration geophysicists. The well-preserved diffraction can provide rich information about these reservoirs \cite[]{Gelius1995limit,Landa1998moni,decker2017diffraction}. However, in the traditional seismic exploration workflow, \dlo{the }diffractions \dlo{is}\wen{are} treated as a kind of noise and removed from the original data. \dlo{Additionally, because the amplitude of diffraction is usually weaker than that of reflection wave, it will create more difficulties in the final imaging of it.}\wen{In addition, the weakness of diffraction amplitudes leads to final imaging challenges.} Thus, \dlo{the}\wen{developing} effective and accurate methods for diffraction imaging \dlo{are badly needed by the oil industry in the future}\wen{would be a beneficial goal}.

Generally, the key of diffraction imaging is to \wen{accurately} separate the reflection and diffraction\dlo{ accurately}. Based on this idea, many separating methods have been proposed \dlo{in the past few years. These approaches, according to their mathematical algorithms, can be roughly divided into two}\wen{, which can be divided into two main categories according to their mathematical algorithms,} path-summation-based methods and \dlo{the other is the} wave-equation-based methods.  Additionally, some other approaches such as machine learning \cite[]{Tschannen2020dp} are also effective tools for imaging the diffraction \cite[]{Protasov2019spectral}.

For the path-summation-based methods, the traveltime (event shape) is of great importance to the separation of reflection and diffraction \cite[]{Kanasewich1988dis,Santos2012Tomo}. \cite{Berkovitch2009multi} \dlo{used}\wen{use} a multifocusing algorithm to separate \dlo{the diffraction and reflection}\wen{diffractions from reflections by designing}\dlo{. They designed} a novel time-correction formula\dlo{, which contains angle and radius parameters,} to approximate the diffraction events. This method can make the energy of diffraction more focused while scattering that of reflection in the stacking result. \cite{Dell2011crs} separate diffraction and reflection \wen{energy} in the time domain using a common-reflection-surface algorithm. Different synthetic examples showed the validity of this method. \cite{Waheed2013ti} propose a new method for fitting the \dlo{traveltime of the diffraction}\wen{diffraction traveltimes} in the TI media. This approach can accelerate the traditional process for solving equation and lower the computational complexity. Additionally, it adaptively selects the best parameters for the traveltime equation without complex modeling processes. \cite{Asgedom2013co} combine two novel algorithms, i.e., the modified common‐reflection‐surface method and the replacement‐media technique, to enhance the weak diffraction in the strong reflection background. \dlo{The stability of this method under different data qualities was also tested. }\cite{Coimbra2018fo} propose  \dlo{anew equation to describe the traveltime of diffraction called }\wen{the} finite-offset double-square-root diffraction traveltime equation\dlo{. Via this precise fitting result,}\wen{that can accurately separate} diffraction\dlo{ can be separated properly} from the background reflection. A simplified version was also proposed to accelerate the calculation of the equation parameters while keeping the quality of result unchanged. The synthetic and field data \wen{results} \dlo{showed}\wen{show} the outstanding performance of this improvement. \cite{bakhtiari2018common} compare the influence of pre-stack and post-stack diffraction separation to imaging performance, and showed that the \dlo{pre-stack}\wen{former} method based on the wavefront attributes can help improve the illumination compared with the \dlo{post-stack}\wen{latter} method.  \cite{Zhengwei2019vtd} design a vertical traveltime difference gather and its plus version. Compared with the traditional two-dimensional dip gather, this gather has the advantage of occupying less storage space. After Kirchhoff time migration, the diffraction is flattened, and the reflection events still have \dlo{the upward dip}\wen{upward dip}. By this difference, the reflection can be cut off, which will further strengthen \dlo{the amplitude of diffraction}\wen{recovered diffraction amplitudes}. \dlo{Finally, the result of diffraction imaging will be generated. }\cite{merzlikin2019least} introduce the separation of diffraction into an inversion framework, and designed a new decomposition algorithm by combining Kirchhoff modeling, plane-wave deconstruction and an integral operator. This method \wen{simultaneously} separates weak diffraction and strong reflection accurately, \dlo{and suppresses the noise sufficiently at the same time}\wen{while sufficiently supressing noise}. \cite{Benjamin2019cohe} design an adaptive filter to separate diffraction in the background of strong reflection. This method is mainly based on the summation of reflection data rather than diffraction data, and uses a variety of wavefront filters in the stacking domain to separate diffraction and reflection. \dlo{Through the examples of seismic data and GPR, they demonstrated}\wen{Using seismic and GPR data examples, they demonstrate} that this method could recover weak diffraction signals effectively.

\dlo{For the wave-equation-based}\wen{Wave-equation-based} methods\dlo{, they} take all the wavefield information into consideration \cite[]{Sava2005wave,Hemin2019gpr}. \cite{Klokov2012dip} \dlo{gave}\wen{derive} a novel analytical equation to accurately separate the diffraction and reflection. After the migration process, the Radon transform can distinguish the diffraction effectively by its shape feature. This method is very stable on both synthetic and field data examples. \cite{Zhang2014opening} image the weak diffraction in the shot and opening-angle gathers by muting the strong reflection and enhancing the weak diffraction. This method \dlo{keeps obtaining the}\wen{generates} satisfactory results even if the diffraction interferes with the reflection. The velocities for migration can be gradually updated based on the migrated results to achieve the best result. The real and synthetic data all showed the validity of this method. \cite{Liu2016wave} propose a fast migration method for the imaging of diffraction. They first use linear Radon transform to obtain the local plane waves\dlo{. Then, implemented}\wen{, and then implement} the zero-lag correlation between these plane waves and incident waves. The final diffraction image \dlo{was}\wen{is} generated after the energy of reflected wave was attenuated by a median filter. \cite{Dongliang2019wave} divide the wavefield into two parts, left and right, by using reverse time migration. Based on the fact that the reflection is always related to a specific dip angle, and can only exist in either the left or right wave field. However, due to the nature of diffraction, \dlo{it can}\wen{associated energy will simultaneously} appear in \dlo{two}\wen{both} components at \dlo{the same time. By the} point-by-point multiplication between two components\dlo{, the}\wen{ can suppress} reflection \dlo{can be suppressed }while the imaging result of diffraction\dlo{ will be highlighted}.

\cite{fomel2007} proposes a two-step diffraction separation and imaging framework. \dlo{In the first step, the}\wen{The first step separates} diffraction and reflection wavefields \dlo{are separated }based on the spatial coherence using the plane-wave destruction (PWD) method. The PWD method assumes that the reflection waves have better spatial coherence than the diffraction waves, and thus can be predicted by neighbor traces following the smooth local slope field. In the second step, the separated diffraction waves are migrated using different velocities. Their corresponding focusing performance on the images are measured to determine the \dlo{best }migration velocity \dlo{that results in the best focused image.}\wen{that optimally focuses the image.} In this way, one can achieve simultaneous velocity estimation and diffraction imaging. Based on this framework, the \dlo{separation of diffraction  waves}\wen{diffraction separation} becomes a pure signal processing task, where no prior subsurface velocity models are required. Thus, this method is easy to apply and sometimes can obtain very good performance in real data applications. \wen{In a similar framework, \cite{zhou2017enhancing} and \cite{zhou2018seismic} develop a method to extract diffractions from high-resolution coal seismic data using localized moving-average-error filter (MAEF) to flattened reflection seismic data and or along the reflection dips based on the estimated dip by gradient calculation.} However, the success of this method depends on  the accuracy of the estimated slope. Because of the smoothness of the local slope, \dlo{the reflection waves in complicated areas or with small dip angles can also be separated by the PWD method, which further results in a poor resolution of the migrated diffraction image}\wen{there is leakage of reflection energy into the diffraction estimate which contaminates the imaging results}.

In this paper, we propose a new diffraction separation method based on a localized rank-reduction method (LRR). The LRR method \dlo{is also based on the assumption of local plane waves}\wen{also uses a local plane-wave assumption}, but \dlo{can bypass}\wen{bypasses} the step of slope estimation. The compromise between the removal of diffractions and preservation of reflections is controlled by the rank in each local window. We propose an adaptive rank-selection method for each localized window to select the \dlo{best}\wen{optimal} cut-off rank that best distinguishes between reflections and diffractions. After the diffraction separation step, an migration operation is applied to obtain the migration diffraction image, e.g., by Kirchhoff migration \cite[]{fomel2002antialiasing}, velocity continuation \cite[]{fomel20037}\dlo{, etc}.

The paper is organized as follows: we first introduce the principles of the LRR method. Then, we introduce how we adaptively select the ranks in each local window. The hybrid LRR and adaptive rank selection method is referred to as the localized rank-reduction method with adaptively chosen ranks (LRRA). Next, we use several representative examples to demonstrate the performance of the proposed diffraction separation method, and more importantly how the new method can improve the resolution and fidelity of the final image. \dlo{We finally draw some key conclusions at the end.  }

\section{Methods for adaptively separating diffractions}
The ranks or the singular (characteristic) values of the matrix data are calculated by the SVD method and are measures of the different dipping events within the matrix data (seismic data). This approach is well-known as the matrix pencil method (MPM) \cite[]{jain1974filter,hua1991svd,sarkar1995using}. The MPM approach has been used for dispersion estimation of sonic logging data \cite[]{lang1987estimating,ekstrom1996dispersion}\dlo{. It is assumed}\wen{, and assumes} that the first a few characteristic values are associated with the reflection data while the rest are related to diffractions. Therefore, we can estimate or separate reflections and diffractions from recorded seismic data by matrix rank reduction or truncation. As the seismic events are not necessarily linear or follow plane wave assumption, we propose to apply the matrix rank reduction approach on windowed data to better approximate the \wen{plane-wave} assumption for the reflection data. We call this method a localized rank-reduction method.
\subsection{Localized rank-reduction method}
%For a given regular grid, the relationship between the complete earthquake data $\mathbf{d}\in\mathbb{R}^{N_tN_xN_y\times1}$
%
%$\mathbf{R}$ represents the reconstruction filter and is usually applied in the frequency-space domain in the rank-reduction methods \cite[]{Vicente2011Simultaneous}.
Without the loss of generalization, we introduce the theory of the rank-reduction method in the case of a 3D problem. The 2D problem is just special case of the 3D problem \dlo{when the number of crossline traces is 1}\wen{with a single crossline trace}. In the rank-reduction method, a pre-transformed matrix, e.g., the block Hankel matrix, is assumed to be of low rank. Then the goal becomes to extract the principal components of the pre-transformed matrix, i.e., the reflection signals, and separate the diffractions that usually corresponds to the inessential components due to \dlo{the less}\wen{lower} spatial coherence.

Assuming that the tensor form of the input 3D seismic data is $D(x,y,t)$, the corresponding form in frequency-space domain \dlo{be}\wen{is} obtained after Fourier transform and can be expressed as $D(x,y,f)$.  For each frequency slice, we map the frequency domain data into several block Hankel matrices. This process is referred as Hankelization \cite[]{mssa,weilin2016dmssa,amir2017grsl}. Given a frequency $f$, the Hankel matrix can be constructed as 
\wen{\begin{align} \label{eq:Rif} 
\mathbf{H}_i(f)=
\begin{bmatrix}
D(i,1,f)&D(i,2,f)&\cdots&D(i,Q_y,f)\\
D(i,2,f)&D(i,3,f)&\cdots&D(i,Q_y+1,f)\\
\vdots&\vdots&\ddots&\vdots\\
D(i,P_y,f)&D(i,P_y+1,f)&\cdots&D(i,N_y,f)
\end{bmatrix},
\end{align}
where the subscript $i$ is the row and $\mathbf{H}_i(f)$ is the Hankel matrix in frequency domain corresponding to the data matrix in frequency-space domain $D(x,y,f)$.
$P_y=\lfloor N_y/2\rfloor+1$, $Q_y=N_y-P_y+1$ and $\lfloor \cdot \rfloor$ \dlo{is reserving integer part operator}\wen{denotes the integer part of an input argument}. $N_y$ denotes the number of traces in the $y$ direction. }

\wen{Then, the corresponding block Hankel matrix can be inserted with equation \ref{eq:Rif}
\begin{align} \label{eq:H} 
\mathbf{B}(f)=
\begin{bmatrix}
\mathbf{H}_1(f)&\mathbf{H}_2(f)&\cdots&\mathbf{H}_{Q_x}(f)\\
\mathbf{H}_2(f)&\mathbf{H}_3(f)&\cdots&\mathbf{H}_{Q_x+1}(f)\\
\vdots&\vdots&\ddots&\vdots\\
\mathbf{H}_{P_x}(f)&\mathbf{H}_{P_x+1}(f)&\cdots&\mathbf{H}_{N_x}(f)
\end{bmatrix},
\end{align}
where $P_x=\lfloor N_x/2\rfloor+1$, $Q_x=N_x-P_x+1$.  $N_x$ denotes the number of traces in the $x$ direction.}

The rank-reduction can be achieved by minimizing the following objective function
\begin{align} \label{eq:obj} 
\begin{split}
\text{min} \quad &O=\|\mathbf{B}(f)-\mathbf{L}(f)\|^2_F\\
\text{subject to} \quad&\text{rank}(\mathbf{L}(f))=L,
\end{split}
\end{align} 
where $\mathbf{L}(f)$ denotes the low-rank section corresponding to $\mathbf{B}(f)$. $L$ denotes the optimal rank parameter. The above objective function can be conveniently minimized by the well-known singular value decomposition (SVD). Therefore, the SVD of block Hankel matrix $\mathbf{B}(f)$ can be expressed as
\begin{equation} \label{eq:svd}
\mathbf{B}(f)=\mathbf{U}\mathbf{\Sigma}\mathbf{V}^T,
\end{equation}
where $\mathbf{U}=[\mathbf{u}_1,\mathbf{u}_2,\cdots,\mathbf{u}_N]$ is a left singular matrix, $\mathbf{\Sigma}=[{\sigma}_1,{\sigma}_2,\cdots,{\sigma}_N]$ is a singular matrix and $\mathbf{V}=[\mathbf{v}_1,\mathbf{v}_2,\cdots,\mathbf{v}_N]$ is a right singular matrix. $\sigma_i$ represents the $i$th singular value, and $N$ represents the number of columns of $\mathbf{B}(f)$. Next, the rank-reduced matrix $\mathbf{L}(f)$ can be calculated by extracting the first $L$ principal components, i.e.,
\begin{equation}\label{eq:solution}
\mathbf{L}(f)=\sum^L \limits_{i=1} {\sigma}_i\mathbf{u}_i\mathbf{v}_i^T.
\end{equation}

Then, the solved low-rank Hankel matrix is rearranged to a vector form according to inverse Hankelization process. The rank-reduction method can be summarized as follows:
\begin{equation}
\label{eq:rr}
\begin{split}
\mathbf{R} &=\mathcal{F}^{-1}\mathbf{T}\mathcal{F}\mathbf{D},\\
\mathbf{T} &=\mathcal{A}\mathcal{L}\mathcal{H},
\end{split}
\end{equation}
where $\mathbf{R}$ denotes the separated reflections. The separated diffractions can directly obtained by $\mathbf{D}-\mathbf{R}$. $\mathcal{F}$ and $\mathcal{F}^{-1}$ denote forward and inverse Fourier transforms.

In equation \ref{eq:rr}, filter $\mathbf{T}$ is referred to as the frequency-domain rank-reduction operator, containing the Hankelization $\mathcal{H}$, principal component extraction $\mathcal{L}$ and inverse Hankelization process $\mathcal{A}$.   Because of the complexity of seismic data, the plane-wave assumption is only valid locally. Thus, it is more appropriate to apply the rank-reduction method locally, i.e., in local windows:
\begin{equation}
\label{eq:lrr}
\mathbf{R} =\mathcal{W}^{-1}\mathcal{F}^{-1}\mathbf{T}\mathcal{F}\mathcal{W}\mathbf{D},
\end{equation}
where $\mathcal{W}$ and $\mathcal{W}^{-1}$ denote a pair of windowing and reconstruction operators.

\subsection{Automatic rank selection}
In order to obtain a satisfactory result, an appropriate $L$, referred to the rank, should be cautiously selected.  A big value of $L$ will lead to preserving all components, while a small value of the rank will cause damage on the preserved reflections by the rank-reduction filter.  In the first case, negligible diffraction energy \dlo{could be}\wen{are} separated. In the second case, only the most coherent wave components, e.g., horizontal waves, \dlo{can be}\wen{are} preserved \cite[]{yangkang2017lsrtm,yangkang2019nc}. Thus, there will be a strong mixture between the separated reflections and diffractions. Therefore, the determination of rank parameter is difficult and traditional methods \dlo{such as the approaches based on the events that have distinct slowness}\wen{that exploit distinct event slowness} \cite[]{Vicente2011Simultaneous} cannot perform well in complicated situations.

For the rank-reduction filtering, an alternative method is to adaptively and automatically select the rank parameter based on the features and complexity of the data. In the singular spectrum, the singular values of signals and noise are discrepant. The cut-off rank in singular value spectrum can indicate the separation of signal and noise energy. On this basis, we use an adaptive strategy to optimize the rank \cite[]{yangkang2017lsrtm,yangkang2019nc}.  At first, we define a singular value ratio (SVR):
\begin{equation} 
\label{eq:svr}
m_i=\dfrac{\sigma_i}{\sigma_{i+1}},i=1,2,\cdots,N-1,
\end{equation}
where $\{m_i\}$ denotes the SVR sequence, and $N$ is the length of the singular spectrum. Then, the rank $L$ can be calculated by maximizing the  SVR sequence, i.e.,
\begin{equation} \label{eq:svr}
\hat{L}=\text{arg} \max\limits_i\quad m_i.
\end{equation}

A detailed analysis of the LRRA method on the diffraction separation problem is presented in the next section. In addition, we will aslo comprehensively analyze the reliability of the adaptive rank selection strategy in accurately separating diffractions from reflection waves in the next section.

\inputdir{synth}
\multiplot{3}{s-datai,s-diffr,s-data}{width=0.45\textwidth}{(a) Simulated reflection data. (b) Simulated diffraction data. (c) Simulated zero-offset data containing both reflections and diffractions.}

\multiplot{4}{s-pwd-s,s-pwd-n,s-lrra-s,s-lrra-n}{width=0.45\textwidth}{(a) Separated reflections using PWD method. (b) Separated diffractions using PWD method. (c) Separated reflections using LRRA method.  (d) Separated diffractions using LRRA method. }

\plot{s-dip0}{width=0.6\textwidth}{Estimated local slope from the zero-offset data shown in Figure \ref{fig:s-data}, which is used for \dlo{the plane-wave destruction}\wen{PWD analysis}. Note that both reflection and diffraction slopes are revealed in this map.}

\multiplot{4}{s-lrr-N2-s,s-lrr-N3-s,s-lrr-N4-s,s-lrr-N5-s}{width=0.45\textwidth}{Separated reflections using LRR method with (a) N=2, (b) N=3, (c) N=4, (d) N=5. }

\multiplot{4}{s-lrr-N2-n,s-lrr-N3-n,s-lrr-N4-n,s-lrr-N5-n}{width=0.45\textwidth}{Separated diffractions using LRR method with (a) N=2, (b) N=3, (c) N=4, (d) N=5. }

\multiplot{4}{s-grr-N5-s,s-grr-N10-s,s-grr-N16-s,s-grr-N25-s}{width=0.45\textwidth}{Separated reflections using GRR method with (a) N=5, (b) N=10, (c) N=16, (d) N=25. }

\multiplot{4}{s-grr-N5-n,s-grr-N10-n,s-grr-N16-n,s-grr-N25-n}{width=0.45\textwidth}{Separated diffractions using GRR method with (a) N=5, (b) N=10, (c) N=16, (d) N=25. }

\multiplot{4}{s-mig-true,s-mig0,s-mig-tra,s-mig}{width=0.45\textwidth}{True diffraction image (a) and migration results of (b) traditional method, (c) PWD method, and (d) LRRA method.}

\section{Comparison of Diffraction Imaging}
\subsection{Synthetic test}
In order to test the effective performance of the proposed localized rank-reduction method\dlo{. We}\wen{, we} use a synthetic and two real data examples to show the better diffraction separation performance of the LRRA method, and compare it with the state-of-the-art PWD based method. To demonstrate the advantages of the localized-processing and automatic rank selection strategies, we compare the rank-reduction methods in different cases, considering local or global processing, and fixed or adaptive rank selection.

\dlo{The first example is a synthetic test, as presented in Figure \ref{fig:s-datai,s-diffr,s-data}.} We first generate the reflection data from five reflection surfaces by \dlo{the }Kirchhoff modeling \dlo{, and plot it in Figure \ref{fig:s-datai}}\wen{(Figure \ref{fig:s-datai})}. Then, we generate the diffraction data from a set of diffraction points \dlo{, and plot it in Figure \ref{fig:s-diffr}}\wen{(Figure \ref{fig:s-diffr})}. We sum the reflection and diffraction data to output the simulated zero-offset data \dlo{, as shown in Figure \ref{fig:s-data}}\wen{(Figure \ref{fig:s-data})}. The size of the zero-offset dataset is 800$\times$501. The temporal sampling is 4 ms and \dlo{space}\wen{spatial} sampling is 0.02 km. Note that the same synthetic data \dlo{was}\wen{were} also used in \cite{merzlikin2019least}. We show the results from the PWD method \cite[]{fomel2007} and the proposed LRRA method in Figure \ref{fig:s-pwd-s,s-pwd-n,s-lrra-s,s-lrra-n}. \dlo{The left column of Figure \ref{fig:s-pwd-s,s-pwd-n,s-lrra-s,s-lrra-n} compares}\wen{Figures \ref{fig:s-pwd-s} and \ref{fig:s-lrra-s} compare} the separated reflections\dlo{ and the right column compares}\wen{while Figures \ref{fig:s-pwd-n} and \ref{fig:s-lrra-n} show} the separated diffractions. It is clear that the PWD method \dlo{(top row)}\wen{(Figures \ref{fig:s-pwd-s} and \ref{fig:s-pwd-n})} causes significantly more residual diffractions in the separated reflections than the proposed LRRA method \dlo{(bottom row)}\wen{(Figures \ref{fig:s-lrra-s} and \ref{fig:s-lrra-n})}. Correspondingly, the separated diffractions of the PWD method are much weaker than those from the proposed LRRA method. We attribute the unsatisfactory performance of the PWD method to the failure in distinguishing between the reflections and diffractions in the local slope map, as plotted in Figure \ref{fig:s-dip0}. Because the slope estimation method calculates the slope for both reflections and diffractions, it is difficult to separate them for PWD diffraction separation method that relies on the slope difference. In this test, we use a local window with 200 samples in time and 100 samples in space. The window size is chosen so as to \dlo{maximize}\wen{optimize} the \dlo{separation ability}\wen{separability of}\dlo{ between} diffractions\dlo{ and}\wen{from} reflections. Based on this criterion, we choose the optimal window size based on a try-and-error strategy in practice. We move the window by half of the window size in each directions, meaning that the overlap between two neighbor windows are 50\%. We take the automatic rank selection strategy as introduced previously so we do not need to specify the rank parameter in the LRRA method. The PWD algorithm \cite{fomel2002pwd} \dlo{used }in this paper is a local algorithm, but does not use local windows. \cite{fomel2002pwd} \dlo{avoided}\wen{avoids} the use of local window strategy by designing a non-stationary dip estimation method, where the window size is substituted by the smoothing radius. \dlo{So}\wen{Thus} the only parameter that affects the slope estimation is the smoothing radius (along time and space). A larger smoothing radius corresponds to a larger local window size, i.e., smoother, and vice versa. But the smoothing radius \dlo{can}\wen{does} not result in the same effect as the local window strategy. For example, when we increase the smoothing radius to a large level, the diffraction slope shown in Figure \ref{fig:s-dip0} will be weakened. But, at the same time, the accuracy of the reflection slope will \dlo{be deteriorated}\wen{deteriorate}, thereby making the reflection not fully separated. In the opposite way, if the smoothing radius is smaller, like in this paper, the diffraction slope shows up, then the diffraction is not easy to be separated. So, this is the contradiction in tuning the PWD algorithm. In this paper, we use a smoothing radius of \dlo{10}\wen{ten} samples along both horizontal and vertical directions.

To compare the performance of the automatic rank selection strategy and manual rank selection strategy, we perform several try-and-error tests by specifying different ranks based on the LRR method. Figure \ref{fig:s-lrr-N2-s}-\ref{fig:s-lrr-N5-s} shows four separated reflection sections based on the LRR method with a fixed rank of \dlo{$N=2$ (a), $N=3$ (b), $N=4$ (c), and $N=5$ (d)}\wen{$N=[2,3,4,5]$, respectively}. Correspondingly, Figure \ref{fig:s-lrr-N2-n}-\ref{fig:s-lrr-N5-n} shows four separated diffraction sections based on the LRR method with \dlo{a fixed rank of $N=2$ (a), $N=3$ (b), $N=4$ (c), and $N=5$ (d)}\wen{the same fixed rank as Figure \ref{fig:s-lrr-N2-s,s-lrr-N3-s,s-lrr-N4-s,s-lrr-N5-s}}. From Figures \ref{fig:s-lrr-N2-s,s-lrr-N3-s,s-lrr-N4-s,s-lrr-N5-s} and \ref{fig:s-lrr-N2-n,s-lrr-N3-n,s-lrr-N4-n,s-lrr-N5-n}, we can find that the residual diffraction energy in the separated reflection sections gradually increases, and the reflection energy in the separated diffraction sections decreases, as the fixed rank increases from $N=2$ to $N=5$. All these results from the LRR method with fixed ranks \dlo{seem to be worse}\wen{appear worse} than the result from the LRRA method. For example, when $N=2$, the separated reflection section (Figure \ref{fig:s-lrr-N2-s}) is clean and free of diffraction, but the separated diffraction contains very strong reflection energy, which will significantly deteriorate the resolution of migrated diffractors in the diffraction image. When $N=5$ (Figure \ref{fig:s-lrr-N5-s}), the separated diffraction section contains pure diffraction energy, but \dlo{its}\wen{the associated} reflection section contains significant diffraction energy, thus the resulted diffraction image will not be accurate. When $N=3$ and $N=4$, it seems that the LRR method obtains a better compromise, but is less \dlo{competent}\wen{powerful in removing the diffractions} \dlo{as}\wen{than} the LRRA method\dlo{ is better separating the two components}. The worse performance of the LRR method with a fixed rank compared with the LRRA method with automatically selected ranks is due to the rank inconsistency problem \cite[]{shaohuan2017gji}, i.e., the optimal ranks in each localized processing window are different and thus a globally defined rank cannot suit each localized window. In addition to the superior perfomance, LRRA method also avoids the try-and-error process for rank selection and is more convenient to apply.

We also compare the performance of diffraction separation based on a global rank reduction (GRR) method \cite[]{mssa,Chen2016Simultaneous,lin2020diffraction} with different rank choices. \dlo{Figure \ref{fig:s-grr-N5-s,s-grr-N10-s,s-grr-N16-s,s-grr-N25-s}}\wen{Figures \ref{fig:s-grr-N5-s}-\ref{fig:s-grr-N25-s}} show a comparison of separated reflection sections using the GRR method with a fixed rank of  \dlo{$N=5$ (a), $N=10$ (b), $N=16$ (c), and $N=25$ (d)}\wen{$N=[5,10,16,25]$, respectively}. Figure \ref{fig:s-grr-N5-n,s-grr-N10-n,s-grr-N16-n,s-grr-N25-n} shows a comparison of separated diffraction sections using the GRR method with \dlo{a fixed rank of  $N=5$ (a), $N=10$ (b), $N=16$ (c), and $N=25$ (d)}\wen{the same fixed ranks as Figure \ref{fig:s-grr-N5-s,s-grr-N10-s,s-grr-N16-s,s-grr-N25-s}}. From Figures \ref{fig:s-grr-N5-s,s-grr-N10-s,s-grr-N16-s,s-grr-N25-s} and \ref{fig:s-grr-N5-n,s-grr-N10-n,s-grr-N16-n,s-grr-N25-n}, it is \dlo{obvious}\wen{evident} that as the rank increases, the residual diffraction energy in the separated reflection sections\dlo{ becomes less and less}\wen{ reduces}\dlo{. In the meantime,}\wen{ while} the diffraction sections become cleaner and cleaner in the sense of less reflection energy. \dlo{The general observation of the GRR method is similar to the LRR method, but in the GRR method, it seems even more difficult to compromise between the cleanness and preservation of the reflection energy, e.g., when the separated reflection section (Figure \ref{fig:s-grr-N25-s}) contains the same level of residual diffraction energy as the LRR method (Figure \ref{fig:s-lrr-N5-s}), its diffraction section contains stronger reflection energy.}\wen{The general performance of the GRR method is similar to that of the LRR method, but it is more difficult to compromise between the cleanness and preservation of the reflection energy for the GRR method. For example, when the separated reflection section (Figure \ref{fig:s-grr-N25-s}) contains the same level of residual diffraction energy as the LRR method (Figure \ref{fig:s-lrr-N5-s}), its diffraction section contains stronger reflection energy.} The GRR method tends to fail because of the non-stationarity of both reflection and diffraction energy, while the GRR method is based on a global linear-event assumption \cite[]{mssa}.  To verify the diffraction imaging performance of the better separated diffractions using the proposed LRRA method, we plot four different diffraction images in Figure \ref{fig:s-mig-true,s-mig0,s-mig-tra,s-mig}. Figure \ref{fig:s-mig-true} shows a ground-truth diffraction image as a reference. Figure \ref{fig:s-mig0} shows the migrated image of the zero-offset dataset (Figure \ref{fig:s-data}), i.e., treating both reflections and diffractions as a whole and without special handling of the diffraction energy. Figure \ref{fig:s-mig0} is considered as a conventional image as compared with the more advanced diffraction image. Figure \ref{fig:s-mig-tra} shows the migrated image of the separated diffractions from the PWD method, where most diffraction points \dlo{have been}\wen{are} imaged well but with some blurry points \dlo{in a deeper area}\wen{at greater depths}. Figure \ref{fig:s-mig} shows the diffraction image using the proposed method, where all diffraction points are imaged clearly. Besides, because the separated diffraction energy of the proposed method is stronger than that of the PWD method, the resulted image has an obviously stronger amplitude of each diffraction point.

\inputdir{nankai_new}
\plot{k-dmo}{width=\textwidth}{Input Nankai seismic data.}

\multiplot{4}{k-pwd-ref,k-lrra-ref,k-pwd-dif0,k-lrra-dif0}{width=0.45\textwidth}{Separated reflection from (a) PWD method and (b) LRRA method. Separated diffraction from (c) PWD method and (d) LRRA method. }

%\multiplot{3}{k-post,k-pwd-s,k-pwd-n}{width=0.45\textwidth}{(a) Input Nankai seismic data. (b) Separated reflections using PWD. (c) Separated diffractions using PWD.. }

%\multiplot{4}{k-grr-N5,k-grr-N10,k-grr-N20,k-grr-N30}{width=0.45\textwidth}{Separated reflections using global rank-reduction method with N=5 (a), N=10 (b), N=20 (c), and N=30 (d). }

%\multiplot{4}{k-lrr,k-ldrr,k-lrra,k-ldrra}{width=0.45\textwidth}{Comparison of separated reflections. (a) Result from localized rank-reduction method with N=3. (b) Result from localized damped rank-reduction method N=3. (c) Result from localized rank-reduction method with the automatically chosen rank. (b) Result from localized damped rank-reduction method  the automatically chosen rank.  }
%\multiplot{4}{k-lrr-n,k-ldrr-n,k-lrra-n,k-ldrra-n}{width=0.45\textwidth}{Comparison of separated diffractions. (a) Result from localized rank-reduction method with N=3. (b) Result from localized damped rank-reduction method N=3. (c) Result from localized rank-reduction method with the automatically chosen rank. (b) Result from localized damped rank-reduction method  the automatically chosen rank.  }

\multiplot{4}{k-pwd-s0,k-lrra-s0,k-pwd-n0,k-lrra-n0}{width=0.38\textwidth}{Comparison of diffraction and reflection images.  (a) Reflection image from the PWD method. (b) Reflection image from the LRRA method. (c) Diffraction image from the PWD method. (d) Diffraction image from the LRRA method.}
\multiplot{6}{k-pwd-s-z1,k-pwd-s-z2,k-pwd-s-z3,k-lrra-s-z1,k-lrra-s-z2,k-lrra-s-z3}{width=0.3\textwidth}{Zoomed comparison of the reflection image. Top row: PWD method. Bottom row: LRRA method. \dlo{Left column corresponds}\wen{(a) and (d) correspond} to the frame box A in Figure \ref{fig:k-pwd-s0,k-lrra-s0,k-pwd-n0,k-lrra-n0}. \dlo{Middle column corresponds}\wen{(b) and (e) correspond} to the frame box B in Figure \ref{fig:k-pwd-s0,k-lrra-s0,k-pwd-n0,k-lrra-n0}. \dlo{Right column corresponds}\wen{(c) and (f) correspond} to the frame box C in Figure \ref{fig:k-pwd-s0,k-lrra-s0,k-pwd-n0,k-lrra-n0}.}

\multiplot{6}{k-pwd-n-z1,k-pwd-n-z2,k-pwd-n-z3,k-lrra-n-z1,k-lrra-n-z2,k-lrra-n-z3}{width=0.3\textwidth}{Zoomed comparison of the diffraction image. Top row: PWD method. Bottom row: LRRA method. \dlo{Left column corresponds}\wen{(a) and (d) correspond} to the frame box A in Figure \ref{fig:k-pwd-s0,k-lrra-s0,k-pwd-n0,k-lrra-n0}. \dlo{Middle column corresponds}\wen{(b) and (e) correspond} to the frame box B in Figure \ref{fig:k-pwd-s0,k-lrra-s0,k-pwd-n0,k-lrra-n0}. \dlo{Right column corresponds}\wen{(c) and (f) correspond} to the frame box C in Figure \ref{fig:k-pwd-s0,k-lrra-s0,k-pwd-n0,k-lrra-n0}. }

\multiplot{4}{k-lrr-N1-n,k-lrr-N2-n,k-lrr-N3-n,k-lrr-N4-n}{width=0.38\textwidth}{Diffraction images from localized rank-reduction method by manually chosen rank.  (a) N=1. (b) N=2. (c) N=3. (d) N=4. }
\multiplot{4}{k-grr-N5-n,k-grr-N10-n,k-grr-N20-n,k-grr-N30-n}{width=0.38\textwidth}{Diffraction images using global rank-reduction method with N=5 (a), N=10 (b), N=20 (c), and N=30 (d). }

\subsection{\dlo{Real}\wen{Field} data tests}
\dlo{The first field data example is shown in Figure \ref{fig:k-dmo}. This dataset is}\wen{The first field example (Figure \ref{fig:k-dmo}) is} a stacked dataset after \wen{applying} dip-moveout (DMO)\dlo{ stacking}. The size of the dataset is $1750\times 401$. The temporal sampling is 4 ms and spatial sampling is 0.0167 km. This dataset was also studied previously by \cite{decker2017diffraction}. Figure \ref{fig:k-pwd-ref,k-lrra-ref,k-pwd-dif0,k-lrra-dif0} plots a comparison of separated diffraction sections and reflection sections between the traditional PWD method and the proposed LRRA method. \dlo{The top row of }Figures \ref{fig:k-pwd-ref} and \ref{fig:k-lrra-ref} compare the separated reflections between the two methods\dlo{ and the bottom row of Figure \ref{fig:k-pwd-ref,k-lrra-ref,k-pwd-dif0,k-lrra-dif0} compares}\wen{, while Figures \ref{fig:k-pwd-dif0} and \ref{fig:k-lrra-dif0} show} the corresponding diffractions. From Figures \ref{fig:k-pwd-dif0} and \ref{fig:k-lrra-dif0}, it is clear that although the separated diffraction energy of the PWD method (Figure \ref{fig:k-pwd-dif0}) seems to be stronger than that of the LRRA method (Figure \ref{fig:k-lrra-dif0}), \dlo{there exists }significant reflection energy \dlo{in}\wen{remains in} the PWD result. The labels point out some areas with obvious reflection energy, indicating a serious reflection leakage phenomenon. The diffraction section separated by the LRRA method seems to be pure diffraction energy. In this test, we use a localized processing window with a size of 100 samples in time and 20 samples in space.

We then compare the migrated reflection and diffraction images using two aforementioned methods in Figure \ref{fig:k-pwd-s0,k-lrra-s0,k-pwd-n0,k-lrra-n0}. The \dlo{bottom}\wen{top} row of Figure \ref{fig:k-pwd-s0,k-lrra-s0,k-pwd-n0,k-lrra-n0} plots the corresponding reflection images using the velocity continuation method \cite[]{fomel20037} for the two methods\dlo{. The bottom row of Figure \ref{fig:k-pwd-s0,k-lrra-s0,k-pwd-n0,k-lrra-n0} plots}\wen{, while Figures \ref{fig:k-pwd-n0} and \ref{fig:k-lrra-n0} plot} the diffraction images. From Figure \ref{fig:k-pwd-s0,k-lrra-s0,k-pwd-n0,k-lrra-n0}, it is clear that the proposed LRRA method obtains a better diffraction image with an obviously higher resolution. Several distinct imaging areas are highlighted by the frame boxes A, B, and C. At the same time, the reflection image of the LRRA method is \dlo{spatially more}\wen{more spatially} continuous than the PWD method because the amplitude of reflection waves are less damaged during the diffraction separation process of the LRRA method. The migrated reflection images indicate a clear \dlo{over-thrusting}\wen{overthrust} structure, with the thrust-generated faults highlighted clearly in the diffraction images.  We zoom in the three areas referred to by the frame boxes and plot the zoomed sections in Figures \ref{fig:k-pwd-s-z1,k-pwd-s-z2,k-pwd-s-z3,k-lrra-s-z1,k-lrra-s-z2,k-lrra-s-z3} and \ref{fig:k-pwd-n-z1,k-pwd-n-z2,k-pwd-n-z3,k-lrra-n-z1,k-lrra-n-z2,k-lrra-n-z3}. Figure \ref{fig:k-pwd-s-z1,k-pwd-s-z2,k-pwd-s-z3,k-lrra-s-z1,k-lrra-s-z2,k-lrra-s-z3}  plots the detailed comparison of the reflection images and Figure \ref{fig:k-pwd-n-z1,k-pwd-n-z2,k-pwd-n-z3,k-lrra-n-z1,k-lrra-n-z2,k-lrra-n-z3} plots the comparison of the zoomed diffraction images. The top rows of Figures \ref{fig:k-pwd-s-z1,k-pwd-s-z2,k-pwd-s-z3,k-lrra-s-z1,k-lrra-s-z2,k-lrra-s-z3}   and \ref{fig:k-pwd-n-z1,k-pwd-n-z2,k-pwd-n-z3,k-lrra-n-z1,k-lrra-n-z2,k-lrra-n-z3} correspond to the PWD method while the bottom rows correspond to the proposed LRRA method. These detailed comparison further confirms that the proposed LRRA method can obtain a higher resolution in the diffraction image and a better continuity in the reflection image.

We vary the fixed rank from $N=1$ to $N=4$ for the LRR method gradually and show their corresponding diffraction images in Figure \ref{fig:k-lrr-N1-n,k-lrr-N2-n,k-lrr-N3-n,k-lrr-N4-n}. It is salient that the amplitude of diffraction images \dlo{becomes weaker and weaker as we increase}\wen{weakens as we incrase} the rank, which is explained by the fact that a larger rank causes less separated diffraction energy. When $N=1$, most discontinuities \dlo{can be}\wen{are} imaged well but with very low resolution because \dlo{a lot of}\wen{numerous} reflection structures also exist. When $N=2$, the resolution of the diffraction image becomes higher, but it also misses a lot of significant diffraction structures, e.g., around 7.5 s. When $N>2$, the \dlo{diffraction images have a poor quality and are not able to}\wen{poor diffraction quality does not} provide helpful indications of the subsurface discontinuity structures. \dlo{We also}\wen{Figures \ref{fig:k-grr-N5-n}-\ref{fig:k-grr-N30-n}} compare the diffraction images using the GRR method with ranks of \dlo{$N=5$, $N=10$, $N=20$, and $N=30$}\wen{$N=[5,10,20,30]$}, respectively, in Figure \ref{fig:k-grr-N5-n,k-grr-N10-n,k-grr-N20-n,k-grr-N30-n}. It is clear that when the rank is smaller, e.g., $N\le 10$, the diffraction images have low resolutions and more importantly contain a lot of artifacts. When the rank is larger, e.g., $N\ge 20$, the diffraction images fail \dlo{in depicting}\wen{to depict} all the discontinuities and also contain some reflection structures. In conclusion, the GRR method is much more difficult than the LRR method in \dlo{compromising the}\wen{determining an appropriate compromise between} resolution and completeness.

Next, we apply the proposed LRRA method to a real \wen{post-stack} dataset from the Gulf of Mexico \wen{Figure \ref{fig:bei-in}}. The post-stack seismic image of this dataset is plotted in Figure \ref{fig:bei-in}. There are 1000 temporal samples and 250 spatial samples in this dataset. The temporal sampling is 4 ms and the spatial sampling is 0.0335 km. We compare the separated diffraction sections using the PWD and LRRA methods in Figure \ref{fig:bei-tra-0,bei-rr-0}. In this test, we use a localized window with the size of $200\times 50$. It is clear from Figure \ref{fig:bei-tra-0,bei-rr-0} that the PWD method causes some reflection energy leakage in the separated diffractions while the LRRA method is less likely to cause the reflection leakage problem. The two frame boxes and the two labels in Figure \ref{fig:bei-tra-0,bei-rr-0} highlight some areas with distinct difference between two sections, e.g., more leaked reflection waves in the PWD result on the left. Figure \ref{fig:bei-tra-slc-0,bei-rr-slc-0} plots a comparison of the diffraction images using two methods, based on the velocity analysis and diffraction \dlo{image}\wen{imaging} framework introduced in \cite{fomel2007}. The comparison of diffraction images shows that the proposed LRRA method causes fewer reflection structures and a higher spatial migration resolution in the diffraction image, as indicated by the frame boxes and arrows. Figure \ref{fig:bei-tra-pik,bei-rr-pik} plots a comparison of the estimated velocity models by focusing the separated diffractions using the PWD method on the left and the LRRA method on the right based on the velocity continuation approach \cite[]{fomel20037}. According to the better focused diffraction image, we consider the velocity model from the LRRA method is more accurate. However, further verification of the velocity model requires more information.

\inputdir{fault}
\plot{bei-in}{width=\textwidth}{Input marine seismic data.}
\multiplot{2}{bei-tra-0,bei-rr-0}{width=0.45\textwidth}{(a) Separated diffractions by PWD. (b) Separated diffractions by LRRA. Note that the PWD method causes more leaked reflection energy as highlighted by the frame boxes and labels. }
\multiplot{2}{bei-tra-slc-0,bei-rr-slc-0}{width=0.45\textwidth}{(a) Migrated image using separated diffractions by PWD. (b) Migrated image using separated diffractions by LRRA. Note the less reflection structure and higher resolution obtained from the LRRA method compared with the PWD method.  }
\multiplot{2}{bei-tra-pik,bei-rr-pik}{width=0.45\textwidth}{(a) Picked velocity profile from separated diffractions by PWD. (b) Picked velocity profile from separated diffractions by LRRA. }

\section{Conclusions}
The diffraction separation performance of the traditional PWD filter is limited \dlo{when the geological structure is complicated}\wen{in complex geological structure}, thereby causing an inaccurate slope estimation and the inadequacy of the plane-wave assumption of the PWD filter. We have proposed a new effective diffraction separation method based on the localized rank-reduction method. The rank-reduction method assumes the diffractions to be high-rank and reflections to be low-rank locally, and thus the diffraction energy can be easily separated via a simple rank-reduction filter. The localized rank-reduction method shows great advantages over the global rank-reduction method because the rank to be chosen in a localized method  has a narrower range than in the global method and thus is easier to choose. More importantly, the localized rank-reduction is free of artifacts that \wen{commonly} exist in \dlo{the }global methods. The ranks of the localized rank-reduction method  can be either constant or better be adaptively chosen. The adaptive rank selection strategy is simple and convenient to use. The separated diffractions and reflections based on the localized rank-reduction method are accurate both kinematically and dynamically. \dlo{Both synthetic}\wen{Synthetic} and field examples demonstrate the effectiveness of the proposed method in diffraction separation and further in imaging of the separated diffractions.

\section{Acknowledgements}
The research is supported by the Starting Funds from Zhejiang University.

\section{DATA AND MATERIALS AVAILABILITY}
Data associated with this research are available and can be obtained by contacting the corresponding author.

\bibliographystyle{seg}
\bibliography{diffr}

### 2020-09-16 dipseis/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{Geophysical Journal International, 206, 457–469, (2016)}

\title{Dip-separated structural filtering using seislet transform and adaptive empirical mode decomposition based dip filter}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Yangkang Chen}

\address{
\footnotemark[1]Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
ykchen@utexas.edu
}

\lefthead{Chen}
\righthead{Dip-separated structural filtering}
\maketitle

% for multiple-revision
\DeclareRobustCommand{\dlo}[1]{\ifthenelse{\boolean{@revd}}{}{}}
\DeclareRobustCommand{\wen}[1]{%
  \ifthenelse{\boolean{@revd}}{\textcolor{black}{#1}}{#1}}

\begin{abstract}
The seislet transform has been demonstrated to have a better compression performance for seismic data compared with other well-known sparsity promoting transforms, thus it can be used to remove random noise by simply applying a thresholding operator in the seislet domain. Since the seislet transform compresses the seismic data along the local structures, the seislet thresholding can be viewed as \dlo{the simplest}\wen{a simple} structural filtering approach. Because of the dependence on a precise local slope estimation, the seislet transform usually suffers from low compression ratio and high reconstruction error for seismic profiles that have dip conflicts. In order to remove the limitation of seislet thresholding in dealing with conflicting-dip data, I propose a \dlo{semi-automatic} dip-separated filtering strategy. In this method, I first use an adaptive empirical mode decomposition based dip filter to separate the seismic data into several dip bands (5 or 6). Next, I apply seislet thresholding to each separated dip component to remove random noise. Then I combine all the denoised components to form the final denoised data. Compared with other dip filters, the empirical mode decomposition based dip filter is data-adaptive. Both complicated synthetic and field data examples show superior performance of my proposed approach than the traditional alternatives. The dip-separated structural filtering is not limited to seislet thresholding, and can also be extended to all those methods that require slope information.
\end{abstract}

\section{Keywords}
Dip-separated structural filtering, seislet thresholding, empirical mode decomposition, dip filter

\section{INTRODUCTION}
Random noise attenuation is \dlo{one of the principal problems}\wen{an important task} in seismic data processing \wen{\cite[]{fxydecon,ramesh2006,guochang20112,guochang2012,sanyi2012,wencheng2015asa,shuwei20152,weilin2015,qushan2015}}. Among different random noise attenuation approaches, the transform domain thresholding \wen{approach} is \wen{one of the most} widely-known \wen{approaches} \cite[]{yangkang2016dsd}. The principle of this type of approach is simple: seismic reflection has coherent structure and can be sparsely represented while random noise are spreading through the whole transform domain, thus random noise can be removed by applying a simple thresholding operator in the transformed domain. One of the most well-known \dlo{and robust} transforms might be \wen{the} Fourier transform, or $f$-$k$ transform. linear events are transformed into narrow strings in the $f$-$k$ domain. The basic assumption of using $f$-$k$ transform based thresholding is that the \dlo{seismic events should be linear}\wen{data is built of monochromatic plane waves}. To consolidate the assumption, windowed $f$-$k$ transform is usually used to ensure the linear property of local seismic events. Another emerging sparsity-promoting transform is Radon transform. According \wen{to} the shape of the integral operator in the Radon transform, Radon transform can be divided into different types. Among the most popular types are linear Radon transform (also known as slant stack), parabolic Radon transform, hyperbolic Radon transform, and polynomial Radon transform \wen{\cite[]{yaru2014,yaru2016demul}}. As the standard Radon transform operator is not unitary, least-squares and high-resolution version\wen{s} of Radon transform are often used to ensure a practical application of \wen{the} Radon transform. The basic assumption \dlo{beyond}\wen{behind the} Radon transform based thresholding is that the shape of seismic events follows the shape of the integral operator that is used in the Radon transform. \dlo{Curvelet}\wen{The curvelet} transform is becoming more and more popular in \dlo{exploration geophysics field}\wen{the field of exploration geophysics} because of its multi-dimensional and multi-scale \dlo{structures}\wen{properties} \cite[]{hennenfent2006,neelamani2008,neelamani2010,liuwei20162}. \wen{The curvelet transform can give a very sparse representation of a seismic wavefield which has advantages for interpolation and denoising of these data \cite[]{hermann2007}. Therefore it has become more and more popular in exploration geophysics in recent years.} Because \dlo{of the sophisticated construction of}\wen{the} curvelet transform takes both the direction and scale into account, \dlo{curvelet transform}\wen{it} can \dlo{be more adaptive}\wen{get sparser representation for complex data} than many other alternatives. \dlo{The assumption behind the curvelet transform is that the image should have local-symmetric structure.} \wen{The curvelet transform does not have any a prior knowledge of the seismic data, which is designed for a general image processing task. Recently popular shearlet transform is also a natural extension of wavelet transform to accommodate the fact that multivariate functions are typically governed by anisotropic features such as edges in images.} All of the aforementioned sparsity-promoting transforms are \dlo{parameters dependent}\wen{parameter-dependent}, rather than data dependent. \wen{For example, the good compression performance using curvelet transform depends on the input parameters, such as the scales and the directions, while the seislet transform only depends on the local slope that is estimated directly from the data.}

\dlo{Different from images from the digital signal processing field, seismic images have well-constructed geological structures (e.g. coherent along the spatial dimension), and thus are suitable for structural filtering in order to enhance useful signals and removing noise . However, structural filtering usually requires a precise local slope estimation, which can be demanding in complex seismic profiles because of the difficulty in calculating conflicting dips.}

\cite{seislet} propose a wavelet-like transform that is tailed especially \dlo{for}\wen{to} seismic data, called seislet transform. The seislet transform follows the lifting scheme \cite[]{sweldens1995} in constructing the second generation wavelet transform. The only difference between \wen{the} seislet transform and the general second-generation wavelet transform is that the prediction operator in the seislet transform framework is \wen{defined as} the prediction between different traces according to local slope. The key component of \wen{the} seislet transform is the estimation of local slope of seismic data using plane-wave destruction algorithm. The seislet transform is a\dlo{n} \dlo{outbreak}\wen{breakthrough} in the development of fixed basis sparsity promoting transforms because it can be data adaptive as long as the slope estimation is up to a certain degree of accuracy. \wen{The s}\dlo{S}eislet transform has been successfully used in random noise attenuation, seismic data interpolation, stacking without estimating \dlo{RMS}\wen{the normal-moveout} velocity \cite[]{seislet}, and separation of simultaneous-source seismic data. \wen{As the seislet transform compresses the seismic data along local structures, thus seislet thresholding \cite[]{seislet} can be considered as the simplest structural filtering approach.} \wen{Different from images from \wen{the} digital signal processing field, \dlo{the }seismic images have well-constructed geological structures (e.g. coherent along the spatial dimension), and thus are suitable for structural filtering in order to enhance useful signals and removing noise \cite[]{hale2011,shuwei2015,wencheng2015stack,zhiguang2016}. However, structural filtering usually requires a precise local slope estimation, which can be demanding in complex seismic profiles because of the difficulty in calculating conflicting dips. }

Because of the close \dlo{dependency}\wen{dependence} on slope estimation, \wen{the} seislet transform can be limited \dlo{sometimes} to \dlo{real}\wen{practical} application\wen{s} for some specific datasets when slope estimation is not acceptable, such as dip-conflicting profiles and highly noisy profiles. In order to solve this problem, several alternatives to \wen{the} plane-wave destruction based seislet transform have been proposed. \cite{liuyang2010} proposed the offset continuation based seislet transform. In \wen{the} offset continuation based seislet transform, \wen{the} offset continuation operator is used as \wen{a} replacement of \dlo{PWD}
\wen{plane-wave destruction} operator for the prediction between different traces. The offset continuation operator can only be used to predict traces along the offset direction because of the sole continuation direction \wen{but cannot be used to predict traces along the midpoint direction}, thus it can\dlo{ }not be used in image domain (common offset gathers). \cite{liuyang2013} introduced the velocity dependent seislet transform. \wen{The} \dlo{V}\wen{v}elocity dependent seislet transform use\wen{s} normal-moveout based velocity analysis to obtain velocity spectra and transform\wen{s} the normal-moveout velocity to local slope \dlo{that}\wen{which} is required by the plane-wave destruction based seislet transform. However, the velocity dependent seislet transform can only be applied in common midpoint gathers \wen{since one cannot apply NMO-based velocity analysis in common offset gathers}. The problem of estimating correct local slope in common offset gathers, or stacked image, is still an unsolved problem.

Empirical mode decomposition (EMD) based dip filter was first proposed by \cite{yangkang2014}. The EMD based dip filter is a data-driven adaptive dip filter. EMD based dip filter utilizes EMD in each frequency slices to separate different spatial oscillating (wavenumber) components that corresponds to different dip components. Because of the adaptive property, the only parameter\dlo{s} \dlo{I}\wen{one} need to define is the number of dip components. \cite{yangkang2014} utilized \dlo{EMDBDF}\wen{EMD based dip filter} to improve the \dlo{predictive}\wen{denoising} performance of $f$-$x$ predictive filtering. $f$-$x$ EMD filtering can also be understood \dlo{using}\wen{as} \wen{EMD based dip filter} considering that random noise\dlo{ and}\wen{,} steeply dipping coherent events and ground rolls can be removed by applying a high-cut \dlo{EMDBDF}\wen{EMD based dip filter}, as mentioned in \cite[]{yangkang2014}.

In this paper, I propose \dlo{a semi-automatic}\wen{an effective} way to solve the conflicting-dip problem of many structural filtering  by separating different dips of the seismic image first, and then applying the structural filtering to each dip-separated gather secondly. \dlo{We}\wen{I} take the seislet thresholding as \dlo{the simplest}\wen{an} example to show the philosophy of the proposed methodology. When dip conflicts exist, the seislet transform can\dlo{ }not get a good compression performance. For this case, I first apply an EMD based dip filter to separate the seismic data into different \dlo{initial} dip components\dlo{, then I manually combine the initially separated dip components to form smaller number of components (the final separated dip components)} such that no conflicting dips exist in each component. \dlo{The combination is used for saving the computational costs.} Then I apply the traditional seislet thresholding to each separated component to remove random noise and finally I combine all the denoised components together to obtain the output data. The proposed \dlo{semi-automatic} multi-step strategy is very efficient and convenient to implement because no local window is needed for the processing and the EMD based dip filter is data adaptive, without the need to select many parameters that required by other dip filters\dlo{, and there is only one manual step in the whole process: the manual combination of initial dip components}. The proposed approach is a general framework that can deal with the troubles in any structural filtering approaches by separating the dip components first and then filtering secondly. Since almost all the structural filtering approaches need the calculation of structural information, such as the local slope, and thus will encounter the similar problem as the seislet transform in estimating local slope. \wen{Although some novel transforms, such as shearlets, may have the potential to resolving conflicting dips without dip calculation, these transforms are relatively new to seismic data processing and their behaviors in seismic data processing still remains to be investigated. Thus, I only compare the proposed approach with the most widely used curvelet transform.}

I organize the paper as follows: I first give short reviews on seislet domain thresholding and point out its dip dependence problem, then I review the adaptive EMD based dip filter and propose the \dlo{semi-automatic} multi-step random noise attenuation by cascading EMD based dip filter and seislet thresholding and give detailed demonstration on how to implement the proposed framework, finally I use both synthetic and field data examples to demonstrate the performance of the proposed approach. \wen{The contribution of this paper can be summarized into two aspects. First, the paper relieves the slope dependence of the seislet transform in sparsifying seismic data by applying the seislet transform to EMD based dip-separated seismic images and thus slope estimation can be much more precise. Second, the paper proposes a general dip-separated image filtering framework  that can be extended to many other methods which depend on slope information, by utilizing the adaptive property of EMD in separating different dip components.}

\section{Method}
\subsection{Seislet transform and its dip \dlo{dependency}\wen{dependence}}
The seislet is defined with the help of the wavelet-lifting scheme \cite[]{sweldens1995} combined with local \dlo{PWD-based}\wen{plane-wave destruction} \cite[]{seislet}.% The wavelet-lifting utilizes predictability of even components from odd components and finds a difference $\mathbf{r}$ between them. 
The forward and inverse seislet transforms can be expressed as:
\begin{equation}
\label{eq:one}
\mathbf{r}=\mathbf{o}-\mathbf{P\left[e\right]},
\end{equation}
\begin{equation}
\label{eq:two}
\mathbf{c}=\mathbf{e}+\mathbf{U\left[r\right]},
\end{equation}
\begin{equation}
\label{eq:three}
\mathbf{e}=\mathbf{c}-\mathbf{U\left[r\right]},
\end{equation}
\begin{equation}
\label{eq:four}
\mathbf{o}=\mathbf{r}+\mathbf{P\left[e\right]},
\end{equation}
where $\mathbf{P}$ is the prediction operator, $\mathbf{U}$ is the updating operator. $\mathbf{r}$ denotes the difference between true odd trace and predicted odd trace (from even trace), $\mathbf{c}$ denotes a coarse approximation of the data. \wen{$\mathbf{e}$ and $\mathbf{o}$ correspond to the even and odd traces of the data domain. The foward transform starts with the finest scale and goes to the coarsest scale. Correspondingly, the inverse \dlo{transfrom}\wen{transform} starts with the coarsest scale and goes back to the finest scale \cite[]{seislet}.}

The above prediction and update operators can be defined as follows:
\begin{equation}
\label{eq:five}
\mathbf{P}\left[\mathbf{e}\right]_k=\left(\mathbf{P}^{(+)}_k\left[\mathbf{e}_{k-1}\right]+\mathbf{P}^{(-)}_k\left[\mathbf{e}_k\right]\right)/2,
\end{equation}
\begin{equation}
\label{eq:six}
\mathbf{U}\left[\mathbf{r}\right]_k=\left(\mathbf{P}^{(+)}_k\left[\mathbf{r}_{k-1}\right]+\mathbf{P}^{(-)}_k\left[\mathbf{r}_k\right]\right)/4,
\end{equation}
where $\mathbf{P}^{(+)}_k$ and $\mathbf{P}^{(-)}_k$ are operators that predict a trace from its left and right neighbors, correspondingly, by shifting seismic events according to their local slopes. \dlo{More details about the construction of the seislet transform can be found in.}

\wen{
It is easier for understanding the seislet transform by extending the regular wavelet transform to seislet transform. For example, in the simplest case of Haar transform, the Z-transform domain prediction filter for the Haar wavelet transform is 
\begin{equation}
\label{eq:haar}
P(Z)=Z,
\end{equation}
and the Z-transform domain Haar updating filter for wavelet transform is 
\begin{equation}
\label{eq:haaru}
U(Z)=Z/2.
\end{equation}
However, for seislet transform,
\begin{align}
\label{eq:haarseis}
P(Z)&=Z/Z_0, \\
\label{eq:haarseisu}
U(Z)&=1/2(Z/Z_0).
\end{align}
where $Z_0=e^{i\omega_0\Delta t}$. The prediction filter \ref{eq:haarseis} can perfectly characterize a sinusoid with $\omega_0$ circular frequency sampled on a $\Delta t$ grid.
Analogously, the prediction filter for biorthogonal transform can be expressed as:
\begin{equation}
\label{eq:linearseis0}
P(Z)=1/2(Z/Z_0+Z_0/Z),
\end{equation}
and its corresponding updating operator is
\begin{equation}
\label{eq:uplinearseis0}
U(Z)=1/4(Z/Z_0+Z_0/Z).
\end{equation}
}

Although \wen{the} seislet transform has been demonstrated to have a better compression performance for seismic data \cite[]{seislet} \wen{than other alternatives} \wen{given that an fairly acceptable local slope field can be obtained}, the limitation is that it heavily depends on the estimation of local slope. As shown in equations \ref{eq:five} and \ref{eq:six}, the only difference between \wen{the} seislet transform and \wen{the} traditional second-generation wavelet is the prediction operator. When the \dlo{PWD}\wen{plane-wave destruction} operator can obtain an accurate local slope, e.g. where seismic reflections are spatially coherent and no dip conflicts exist, the seismic data can be compressed by \wen{the} seislet transform with a high compression ratio. However, when the local slope is not appropriately estimated, e.g. the seismic profile is very complicated, the seislet transform will not obtain a better compression result than traditional wavelet transform.

Figures \ref{fig:sig,dip0,slet0}, \ref{fig:dip1,slet1,dip2,slet2,dip3,slet3} and \ref{fig:sigcoef} demonstrate the \dlo{dip-dependency}\wen{dip-dependence} problem of \wen{the} seislet transform. Figure \ref{fig:sig} shows the well-known Sigmoid model \cite[]{claerbout2010bei}. Figure \ref{fig:dip0} shows the dip estimation result using \dlo{PWD}\wen{plane-wave destruction} with the best parameters selection. The dip estimation is very accurate in that it is consistent with the structure and cause\wen{s} a sparse compression in the seislet domain, as shown in Figure \ref{fig:slet0}. I treat this dip estimation as the true local slope as a reference for the comparison shown later. And the corresponding seislet domain is treated as the true seislet domain. In order to test the compression performance using different slope estimations, I smooth the true local slope with different smoothing radii. The longer smoothing radius is, the higher error exists in \wen{the}\dlo{he} local slope. Figure \ref{fig:dip1,slet1,dip2,slet2,dip3,slet3} shows three local slope maps with different smoothing radii and their corresponding seislet domains. When the smoothing radius is 50, the slope map is still very similar to the true local slope, and the seislet transform can still get an acceptable result, though much worse than the true seislet domain. When the smoothing radius \dlo{is increased}\wen{increases} to 100, the slope map  can\dlo{ }not indicate the general structure of seismic data, \wen{the} seislet transform get\wen{s} an even worse result, as shown in Figure \ref{fig:slet2}. When the smoothing radius is 250, the slope map is nearly zero, and the seislet domain is not sparse any more. In order to numerically compare the sparseness, I sort the seislet domain coefficients according to the \wen{normalized} amplitude and draw their \dlo{amplitude}\wen{magnitude}-decreasing diagrams, as shown in Figure \ref{fig:sigcoef}. In Figure \ref{fig:sigcoef}, the faster the coefficients decrease, the sparser the seislet domain is. From this figure, I observe that the coefficients in the true seislet domain decreases fastest, and as the smoothing radius becomes longer and longer, the coefficients decrease slower and slower. \wen {I also plot the magnitude-decreasing diagram of the curvelet transform, which lays between $SR=50$ and $SR=100$ when $n$ is small and becomes almost constant when $n$ is large. It can be inferred that even when the local slope contains significant error, the seislet domain is still sparser than the curvelet domain.} In field data processing, when the subsurface structure is complicated, \wen{however,} \dlo{PWD}\wen{plane-wave destruction} operator can\dlo{ }not obtain acceptable local slope estimation because of the dip conflicts\wen{, which makes the seislet domain not optimally sparse}. Thus, for these seismic profiles, the performance of conventional seislet thresholding will be deteriorated.

\subsection{Dip separation using adaptive \dlo{EMD}\wen{empirical mode decomposition} based dip filter}
The special property of \dlo{EMD}\wen{empirical mode decomposition (EMD)} based dip filter \cite[]{yangkang2014} is adaptivity. In order to separate a seismic profile to obtain several dip components, the only parameter to define is the number of dip components. A brief review about \dlo{EMDBDF}\wen{EMD based dip filter} is shown in Appendix A. \dlo{it's}\wen{It is} worth \dlo{to }mention\wen{ing} that the total number of decomposed \wen{intrinsic mode functions} IMFs \wen{($N$)} of EMD is usually limited to be less than 10 and the detectable dip components usually lay in the first 5 or 6 IMFs. The horizontal components lay in the residual for an incomplete EMD (stop the decomposition after obtaining the first several IMFs). \dlo{The parameters to form a simple dip filter to obtain 5 dip components are also shown in Appendix A.}

In the following sections, I will use the \wen{EMD based dip filter} \dlo{parameters defined in Table \ref{tbl:filterpara1}} to decompose the synthetic and field data examples into 5 dip components\dlo{, as shown in Figures \ref{fig:dip1,dip2,dip3,dip4,dip5} and \ref{fig:field-dip1,field-dip2,field-dip3,field-dip4,field-dip5}}. Note that the number of dip components is not limited to 5. \dlo{The dip separation also follows the same way as shown in Table \ref{tbl:filterpara1} to parameterize equation \ref{eq:emdbdf}.} As \dlo{we}\wen{one} can see, the \dlo{EMDBDF}\wen{EMD based dip filter} can act as a data-driven dip components separator, without any parameters to be defined except for the separation number \dlo{$M$}\wen{$N$}.

\inputdir{sigmoid}
\multiplot{3}{sig,dip0,slet0}{width=0.39\columnwidth}{(a) Synthetic data. (b) True local slope. (c) True seislet domain.}

\multiplot{3}{dip1,slet1,dip2,slet2,dip3,slet3}{width=0.39\columnwidth}{Smoothed local slope maps using different smoothing radii (SR) and the corresponding seislet domain. (a) Local slope map with $SR=50$. (b) Seislet domain using local slope shown in (a). (c) Local slope map with $SR=100$. (d) Seislet domain using local slope shown in (c). (e) Local slope map with $SR=250$. (f) Seislet domain using local slope shown in (e).}

\plot{sigcoef}{width=0.8\columnwidth}{Seislet domain coefficients decreasing diagrams\wen{, compared with the curvelet domain coefficients decreasing diagram}.}

\dlo{The dip-separated filtering is not only benefiting the seislet thresholding.} Other structural filtering approaches that require a precise slope estimation will perform better when the dip estimation is applied on dip-separated profiles than the traditional implementation. The slope estimation after dip separation will be obviously superior than that without dip separation. \dlo{We}\wen{One} can use the slope estimation shown in Figure \ref{fig:dip1-emd0,dip2-emd0,dip3-emd0,dip4-emd0,dip5-emd0} as an example. The slope estimation\wen{s} in the separated dip components \dlo{(Figures \ref{fig:sep1-dip} and \ref{fig:sep2-dip})} \dlo{is}\wen{are} more precise than that of the original profile in the dip conflicting area. The separated slope is \dlo{more smooth}\wen{smoother} while the original slope is highly non-stationary when the events cross each other. The dip estimation error will transform into large filtering damages in any structural filtering approaches. Other structural filtering approaches that do not rely on the slope estimation will also benefit a lot because a reduced number of slope components will result in a much easier parameterization, such as choosing the prediction length in the prediction filtering \cite[]{yangkang2014} and choosing the minimum rank in the multichannel singular spectrum analysis (MSSA) \cite[]{mssa}.

\subsection{\dlo{Semi-automatic multi-step random noise attenuation}}
\subsection{\wen{Multi-step random noise attenuation}}
In order to overcome the problem of plane-wave destruction in estimating conflicting dips that is involved in traditional seislet thresholding, I propose a new \dlo{semi-automatic} multi-step processing algorithm.  I first use an adaptive \dlo{EMD}\wen{empirical mode decomposition (EMD)} based dip filter to separate the seismic data into several dip bands (5 or 6)\dlo{, and then I manually combine the decomposed dip components into a small number (2 or 3) of dip components in order to reduce computational cost}. Next, I apply seislet thresholding to each separated dip component \dlo{(after dip combination)} to remove random noise. Finally I combine all the denoised data to form the final denoised data. \dlo{There are two combination steps in the multi-step process: dip combination after EMD based dip filter and combination of denoised data to form output data.} In the step of denoising each dip component using the seislet transform, I first apply plane-wave destruction to each separated dip component to calculate the local slopes, and then apply the forward seislet transform, soft thresholding, and the inverse seislet transform on each dip component. Because of the dip separation\dlo{ and recombination}, there are no dip conflicts in the data, thus plane-wave destruction can obtain more precise dip estimation, which will result in better compression by the seislet transform and better thresholding-based denoising performance \wen{than the alternatives}. %Note that "multi-step" here means two things: multi-step slope estimation and multi-step seislet thresholding. 
\dlo{Figure \ref{fig:flowchart} shows the detailed workflows for the proposed semi-automatic multi-step approach.} \wen{Figure \ref{fig:flowchart_new} shows the detailed workflow chart of the proposed dip-separated denoising framework.} In Table \ref{tbl:denotes}, I give a detailed explanation for the meanings of different abbreviations.

\dlo{The dip separation and recombination fashion can vary slightly for different field datasets. We can first select a small portion of the whole dataset to choose an optimal number of initial dip components ($N$) and an optimal number of final dip recombined components ($M$).  However, one can generally set $N=5$ and $M=2$ to be more conveniently implemented, as I do in the paper. $M=2$ indicates that one only separate the steepest components and the near-horizontal components, which suits most field datasets.}
\inputdir{./}
\plot{flowchart_new}{width=\textwidth}{\dlo{Demonstration of the semi-automatic multi-step random noise attenuation approach.}\wen{Workflow chart of the proposed dip-separated denoising framework.} }
\tabl{denotes}{Explanation of abbreviations shown in Figure \ref{fig:flowchart_new}. }
 {
    \begin{center}
     \begin{tabular}{|c|c|}
      \hline Abbreviations      & Meanings\\ 
      \hline \wen{PWD}   & plane-wave destruction\\      
      \hline DipC   & Dip component after EMD based dip filter\\
      \hline Seis  & Seislet domain without thresholding \\
      \hline Dip  & Local slope map using plane-wave destruction  \\
      \hline TSeis  & Thresholded seislet domain \\
      \hline DC  & Denoised component after thresholding in the seislet domain \\
      \hline N  & Number of dip components after EMD based dip filter \\
      \hline
    \end{tabular} 
   \end{center}
}

\wen{In this paper, I choose the threshold value by a simple percentile strategy. I do not chose the exact threshold value. Instead, I choose a percentage of low amplitude coefficients to remove. For example, if I choose 10\%, I preserve the 90\% largest coefficients. Then, when tuning the parameters, I can only tune the percentage, which is convenient to implement in practice.}

In order to numerically measure the denoising performance for the synthetic data, I utilize signal-to-noise ratio (SNR) \cite[]{hennenfent2006,guochang2009,yangkang2015ortho}, as shown below :
\begin{equation}
\label{eq:snr}
SNR=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2^2}{\Arrowvert \mathbf{s}-\hat{\mathbf{s}}\Arrowvert_2^2},
\end{equation}
where $\mathbf{s}$ is the noise-free signal and $\hat{\mathbf{s}}$ is the denoised signal.
For the field data example, as I do not know the exact answer, I can\dlo{ }not judge by numerical measurement. Instead, I only evaluate by visual observation, which is still effective.

\section{Example}
In this section, I give \dlo{one}\wen{two} synthetic and one field data examples to demonstrate the implementation procedures and the denoising performances of the proposed \dlo{semi-automatic multi-step} random noise attenuation approach.

\subsection{Synthetic example}
I \wen{first} use a \dlo{complicated} synthetic example \wen{with linear events} to demonstrate the performance of the proposed approach. The synthetic data is composed of four linear events with different slopes. They cross each other and form four crossing points. I create this synthetic data in order to decrease the performance of dip estimation using plane-wave destruction as there are dip conflicts in those crossing points. After using the \dlo{EMD}\wen{empirical mode decomposition (EMD)} based dip filter, the decomposed dip components are shown in Figure \ref{fig:dip1,dip2,dip3,dip4,dip5}. %check and difference using the proposed approach and common seislet-domain thresholding as
\dlo{The parameters I choose in designing the \dlo{EMDBDF}\wen{EMD based dip filter} (equation \ref{eq:emdbdf}) in order to obtain the five decomposed dip components are shown in Table \ref{tbl:filterpara1}.}

After dip \wen{decomposition} \dlo{recombination, I obtain two separated dip components that have no dip conflicts, which are shown in Figure \ref{fig:sep1,sep2}. As \dlo{we}\wen{one} can see, after \dlo{the} \dlo{EMDBDF}\wen{applying the EMD based dip filter} and dip recombination,} I remove the crossing points and the local dip conflicts that affect performance of \wen{the} seislet transform. Figure \ref{fig:dip1-emd-p,dip2-emd-p,dip3-emd-p,dip4-emd-p,dip5-emd-p,plane-dip} shows the local slope maps using plane-wave destruction \wen{algorithm} on separated dip components and original seismic profile. \dlo{The seislet domain of the original data is shown in Figure \ref{fig:plane-recon}. The seislet domains after \dlo{EMDBDF}\wen{EMD} based dip separation are shown in Figures \ref{fig:sep1-seis} and \ref{fig:sep2-seis}, respectively. }
The reconstructed seismic data \wen{for each separated dip component} after thresholding are shown in Figure \ref{fig:dip1-emd0,dip2-emd0,dip3-emd0,dip4-emd0,dip5-emd0}. \dlo{Figures \ref{fig:sep1-recon} and \ref{fig:sep2-recon} correspond\dlo{s} to the two denoised seismic data for two separated dip components.} \dlo{Figure \ref{fig:plane-emdseis} is the summation of Figure \ref{fig:sep1-recon} and \ref{fig:sep2-recon}} \wen{Figure \ref{fig:plane-emdseis} is the summation of Figures \ref{fig:dip1-emd0}-\ref{fig:dip5-emd0}} and thus the output using the proposed approach. Figure \ref{fig:plane-recon} is the denoised result using conventional method. \wen{In order to demonstrate the superior performance of the proposed over other widely used denoising approaches, I also show the denoised results using the curvelet thresholding approach \cite[]{candes20061,candes20062} and the \dlo{FX}\wen{$f-x$} deconvolution method \cite[]{canales}. In order to have a fair comparison, I try different parameter combinations in order to obtain the best denoised results with the least loss of useful energy for all the methods. } The noise sections corresponding to the proposed approach and the conventional approach\wen{es} are shown in \dlo{Figure \ref{fig:plane-emdseis-dif,plane-seis-dif,plane-curv-dif,plane-fx-dif}}\wen{Figures \ref{fig:plane-emdseis-dif} and \ref{fig:plane-seis-dif}}. \dlo{Because of dip conflicts, conventional seislet thresholding cause\wen{s} some artifacts in the final denoised image.}\wen{Because of dip conflicts, the seislet domain of the original seismic image is not optimally sparse, and the threshold \dlo{we}\wen{one} use should be more conservative in order to avoid any possible damages to the signals. The resulted denoised image is a bit noisier and the noise section has a lower amplitude level.} Although the curvelet transform has directional property, the compactly \dlo{crosing}\wen{crossing} events make thresholding in the curvelet transform domain not easy to implement, thus \dlo{we}\wen{one} can only use a very \dlo{convervative}\wen{conservative} threshold value to obtain the optimum denoised result that leaves the least useful energy in the noise section. The noise section using curvelet thresholding is relatively less noisier than other methods, which indicates that more noise are still in the denoised result. The \dlo{FX}\wen{$f-x$} deconvolution method can obtain a good denoising performance but \wen{might} cause some useful dipping energy lost due to the boundary effects. However, using the proposed approach, I obtain an excellent result. \dlo{The SNR of original noise data is 3.685 dB. The SNR of the denoised data using conventional seislet thresholding is 20.41 dB. The SNRs of the denoised data using the curvelet thresholding and the \dlo{FX}\wen{$f-x$} deconvolution are 20.51 dB and 20.67 dB, respectively. The SNR of the denoised data using the proposed semi-automatic multi-step approach is 23.46 dB.}\wen{The SNR of original noise data is 3.685 dB. The SNR of the denoised data using conventional seislet thresholding is 22.21 dB. The SNRs of the denoised data using the curvelet thresholding and the $f-x$ deconvolution are 21.07 dB and 20.98 dB, respectively. The SNR of the denoised data using the proposed approach is 24.38 dB.} The comparison of SNRs also proves the better performance of the proposed approach \wen{than the other approaches}. \dlo{Please note that even though we do not manually combine the separated dip components, we can still get the same result. Figure \ref{fig:dip1-thr,dip2-thr,dip3-thr,dip4-thr,dip5-thr,dips-thr} shows a example of denoising on each separated dip components. Figures \ref{fig:dip1-thr}, \ref{fig:dip2-thr}, \ref{fig:dip3-thr}, \ref{fig:dip4-thr}, and \ref{fig:dip5-thr} show the denoised result of each dip component. Figure \ref{fig:dips-thr} show the final denoised result by summing the 5 dip components in Figures \ref{fig:dip1-thr}, \ref{fig:dip2-thr}, \ref{fig:dip3-thr}, \ref{fig:dip4-thr}, and \ref{fig:dip5-thr}. Compared with denoised result in two final dip components, the performance is quite similar. The estimated SNR of Figure \ref{fig:dips-thr} is 23.39 \wen{dB}, which is quite close to that of Figure \ref{fig:plane-emdseis}.}\wen{  In this example, I preserve 2\% coefficients for all the dip components. For the traditional seislet method, I choose a bit more coefficients, 3\%, to perform the denoising. For the curvelet method, I choose 6\% coefficients to perform the denoising. }

\wen{I then use a second synthetic example with curved events to further confirm the superior performance of the proposed approach, as shown in Figures \ref{fig:hyper-c,hyper-e,hyper-s-0,hyper,hyper-ct-0,hyper-fx-0} and \ref{fig:hyper-e-n,hyper-s-n-0,hyper-ct-n-0,hyper-fx-n-0}. This example is composed with three curved events with spatially variable slope. The clean and noisy data are shown in Figures \ref{fig:hyper-c} and \ref{fig:hyper}, respectively. Figures \ref{fig:hyper-e}, \ref{fig:hyper-s-0}, \ref{fig:hyper-ct-0}, and \ref{fig:hyper-fx-0} show the denoised performances using the proposed method, traditional seislet method, curvelet method, and \dlo{FX}\wen{$f-x$} deconvolution method, respectively. Figures \ref{fig:hyper-e-n}, \ref{fig:hyper-s-n-0}, \ref{fig:hyper-ct-n-0}, and \ref{fig:hyper-fx-n-0} show their corresponding removed noise sections. It is obvious that the proposed approach can obtain the cleanest denoised data while the other three methods cause a bit more random noise left in the denoised images. The SNR improvements using four different approaches are 10.18 dB, 9.54 dB, 9.27 dB, and 7.98 dB, respectively. In this example, I preserve 3\% coefficients for all the dip components, preserve 5 \% coefficients for the traditional seislet method, and 8\% for the curvelet method. }

\subsection{Field data example}
The field data example is shown in Figure \ref{fig:field,field-emdseis,field-recon,field-ct,field-fx}. There is a salt dome in the down middle part of the image. Because of random noise, the useful seismic reflections are not very clear. Because of the salt dome, there exists dip conflicts near the flanks of the salt dome, which will cause bad compression performance for \wen{the} seislet transform. I first use the EMD based dip filter to separate the profile into five dip components\dlo{, as shown in Figure \ref{fig:field-dip1,field-dip2,field-dip3,field-dip4,field-dip5}}. \wen{Then I apply seislet thresholding on each of the five separated dip components and finally add all the denoised components together. The denoised image using the proposed approach is shown in Figure \ref{fig:field-emdseis}. } \dlo{I then combine the separated dip components into two components to avoid dip conflicts. Two combined components are shown in Figure \ref{fig:field-sep1,field-sep2}. Figures \ref{fig:field-sep1-dip} and \ref{fig:field-sep2-dip} show the local slope map for two separated dip components using \wen{the} plane-wave destruction algorithm. Figure \ref{fig:field-dip} shows the local slope map of original seismic profile. As \dlo{we}\wen{one} can observe from the slope estimation\wen{s} of two separated dip components, dip estimation focus\wen{es} better on different slope bands \wen{than the original slope estimation}. The first dip component get\wen{s} better dip estimation for salt flanks while the second dip component get\wen{s} better dip estimation for horizontal components. Figure \ref{fig:field-seis,field-sep1-seis,field-sep2-seis} shows the seislet domains for the original seismic profile and two separated dip components. After \wen{forward seislet transform,} thresholding in the seislet domains of both separated components, and \wen{the} inverse seislet transform, I obtain the denoised results for two separated dip components, as show in Figures \ref{fig:field-sep1-recon} and \ref{fig:field-sep2-recon}. The final result summing the two separated denoised results is shown in Figure \ref{fig:field-emdseis}.} \wen{As a reference, the denoised result using conventional one-step seislet transform is shown in Figure \ref{fig:field-recon}. The denoised images using curvelet thresholding and \dlo{FX}\wen{$f-x$} deconvolution are shown in Figures \ref{fig:field-ct} and \ref{fig:field-fx}, respectively.} \dlo{Figure \ref{fig:field-emdseis-dif,field-seis-dif} show\wen{s} the two noise sections corresponding to the proposed and conventional methods. From the comparison of denoised result\wen{s} using two approaches, I find that the proposed semi-automatic multi-step approach can recover useful signal\wen{s} and enhance weak signals better \wen{than the traditional approach}, as shown by the arrows. I zoom two parts that corresponding to the two frame boxes A\&B in the denoised results using two approaches (Figures \ref{fig:field-emdseis} and \ref{fig:field-recon}), and show them in Figure \ref{fig:field-sep1-recon,field-sep2-recon,field-emdseis,field-recon}. The comparisons of zoomed sections show more obvious advantage of the proposed semi-automatic multi-step random noise attenuation approach in preserving more useful energy and enhancing weak signals that were smeared in traditional method.} \wen{The noise sections using four different approaches are shown in Figure \ref{fig:field-emdseis-dif,field-seis-dif,field-ct-dif,field-fx-dif}. While the \dlo{FX}\wen{$f-x$} deconvolution method fails to obtain acceptable result, the other three methods obtain much better performance in that seldom useful energy is damaged during the processing. However, it is obvious that the proposed approach remove the most random noise while preserving the useful signals. In this example, I preserve 10\% coefficients in the seislet domain for each dip component, 14\% coefficients in the seislet domain for the original image, and 20\% coefficients in the curvelet domain.} The comparisons of zoomed sections show more obvious advantage of the proposed approach in preserving more useful energy and enhancing weak signals that were smeared in traditional seislet method.

\wen{The main cost in the proposed approach is the computation in the sifting process of empirical mode decomposition \cite[]{emd}, which might require a large CPU cost. EMD process does not require a large memory cost since it is a recursive process and the memory required is in linear relation with the data size. The 3D version of the proposed approach may require a combination of 2D EMD along each frequency slice and a 3D version of seislet transform. Currently the proposed method is not applicable to 4D or 5D, since there are no 3D and 4D versions of EMD, or 4D and 5D versions of seislet transform. }

\inputdir{complex}
\multiplot{2}{plane-c,plane}{width=0.48\columnwidth}{\dlo{Complex}\wen{First} synthetic example. (a) Clean data. (b) Noisy data.}

\multiplot{5}{dip1,dip2,dip3,dip4,dip5}{width=0.29\columnwidth}{\dlo{Initial s}\wen{S}eparated dip components using \dlo{EMDBDF}\wen{EMD based dip filter} for synthetic data. (a) First dip component. (b) Second dip component. (c) Third dip component. (d) Fourth dip component. (e) Last dip component.}

\multiplot{6}{dip1-emd-p,dip2-emd-p,dip3-emd-p,dip4-emd-p,dip5-emd-p,plane-dip}{width=0.29\columnwidth}{Local slope comparison for synthetic data. \dlo{Local slope map before dip separation.} \wen{(a)} First local slope map. \wen{(b)} Second local slope map. \wen{(c) Third local slope map. (d) Fourth local slope map. (e) Fifth local slope map. (f) Local slope map before dip separation.}}

\multiplot{5}{dip1-emd0,dip2-emd0,dip3-emd0,dip4-emd0,dip5-emd0}{width=0.29\columnwidth}{\wen{(a) Denoised first dip component. (b) Denoised second dip component. (c) Denoised third dip component. (d) Denoised fourth dip component. (e) Denoised fifth dip component.}}

\multiplot{4}{plane-emdseis,plane-recon,plane-curv,plane-fx}{width=0.4\columnwidth}{Denoised results for \wen{the first} synthetic data. \dlo{(a) Denoised first component using seislet thresholding. (b) Denoised second component using seislet thresholding.} \wen{(a)}\dlo{(c)} Denoised result using the proposed method (summation of \dlo{(a) and (b)}\wen{(a)-(e) in Figure \ref{fig:dip1-emd0,dip2-emd0,dip3-emd0,dip4-emd0,dip5-emd0}}). \wen{(b)}\dlo{(d)} Denoised result using the conventional seislet thresholding method. \wen{(c)}\dlo{(e)} Denoised result using the curvelet thresholding method. \wen{(d)}\dlo{(f)} Denoised result using the \dlo{FX}\wen{$f-x$} deconvolution method.}

\multiplot{4}{plane-emdseis-dif,plane-seis-dif,plane-curv-dif,plane-fx-dif}{width=0.4\columnwidth}{Denoised results for \wen{the first} synthetic data. \dlo{(a) Denoised first component using seislet thresholding. (b) Denoised second component using seislet thresholding.} \wen{(a)}\dlo{(c)} Denoised result using the proposed method (summation of \dlo{(a) and (b)}\wen{(a)-(e) in Figure \ref{fig:dip1-emd0,dip2-emd0,dip3-emd0,dip4-emd0,dip5-emd0}}). \wen{(b)}\dlo{(d)} Denoised result using the conventional seislet thresholding method. \wen{(c)}\dlo{(e)} Denoised result using the curvelet thresholding method. \wen{(d)}\dlo{(f)} Denoised result using the \dlo{FX}\wen{$f-x$} deconvolution method.}

\inputdir{hyper}
\multiplot{6}{hyper-c,hyper-e,hyper-s-0,hyper,hyper-ct-0,hyper-fx-0}{width=0.29\columnwidth}{\wen{Second synthetic example. (a) Clean data. (b) Denoised data using the proposed approach.  (c) Denoised data using the traditional seislet thresholding approach. (d) Noisy data. (e) Denoised data using the curvelet transform. (f) Denoised data using $f-x$ deconvolution.}}

\multiplot{4}{hyper-e-n,hyper-s-n-0,hyper-ct-n-0,hyper-fx-n-0}{width=0.4\columnwidth}{\wen{Removed noise sections for the second synthetic example. (a) Noise section using the proposed method. (b) Noise section using the conventional seislet thresholding method. (c) Noise section using the curvelet thresholding approach. (d) Noise section using $f-x$ deconvolution.}}

\inputdir{field}
\multiplot{5}{field,field-emdseis,field-recon,field-ct,field-fx}{width=0.4\columnwidth}{\wen{(a) Field data. (b) Denoised data using the proposed approach. (c) Denoised data using the traditional seislet thresholding approach. (d) Denoised data using the curvelet transform. (e) Denoised data using $f-x$ deconvolution.}}

\multiplot{4}{field-emdseis-dif,field-seis-dif,field-ct-dif,field-fx-dif}{width=0.4\columnwidth}{Removed noise sections for field data. (a) Noise section using the proposed method. (b) Noise section using the conventional seislet thresholding method. \wen{(c) Noise section using the curvelet thresholding approach. (d) Noise section using $f-x$ deconvolution.}}

\multiplot{4}{zoom2-emdseis,zoom2-recon,zoom1-emdseis,zoom1-recon}{width=0.4\columnwidth}{Zoomed denoised results for field data (corresponding to the frame boxes A \& B in Figure \ref{fig:field,field-emdseis,field-recon,field-ct,field-fx}). (a) \& (c) correspond to the proposed method. (b) \& (d) correspond to the conventional seislet thresholding method.}

\section{Conclusion}
I have proposed a novel \dlo{semi-automatic} dip-separated structural filtering approach that cascades a new empirical mode decomposition based adaptive dip filter and one structural filtering approach. The seislet thresholding is used as a simple example for structural filtering. The principle idea of the proposed approach is to adaptively separate complicated seismic profiles that contain dip conflicts into separated profiles that contain no dip conflicts. \dlo{The separation is achieved by two steps. The first step is to adaptively decompose the data into many dip components using the empirical mode decomposition based dip filter, and then manually combine the initial decomposed dip components into a smaller number of recombined dip components.}\wen{The dip separation is achieved by the empirical mode decomposition based dip filter.} \dlo{This first-decomposition and second-recombination dip separation strategy using the empirical mode decomposition based dip filter enjoys the benefits of convenience of adaptivity and efficiency for later seislet thresholding.} Because of the dip decomposition\dlo{ and recombination}, plane-wave destruction can obtain more precise slope estimation on each \dlo{recombined} dip component and can help to obtain better compression performance for the seislet transform than the traditional implementation. Synthetic and field data examples show that the proposed approach\dlo{ can not only help to preserve more useful energy and enhance weak signals, but also can increase the stability when using seislet-based thresholding}\wen{can help remove more random noise while preserving the energy of useful signals}.

\section{Acknowledgment}
I would like to thank Karl Schleicher, Shuwei Gan, Zhaoyu Jin, Sergey Fomel and Jianwei Ma for fruitful discussions. I also thank Jean Virieux and two anonymous reviewers for very constructive suggestions that improve the manuscript greatly. The paper was prepared in the Madagascar \cite[]{mada2013} open-source software platform and all the examples shown in the paper are reproducible.

\append{Review of \wen{EMD}\dlo{empirical mode decomposition} based dip filter}
The \dlo{EMD}\wen{empirical mode decomposition (EMD)} based dip filter is implemented in $f$-$x$ domain. As EMD \cite[]{emd,yangkang2015enhemd,shuwei20152} can empirically decompose a 1 D signal into different components that corresponds to different oscillating frequency, \dlo{we}\wen{one} can apply EMD to each frequency slice in $f$-$x$ domain and gather the same oscillating component\wen{s} for each frequency slice for separated $f$-$x$ domain profile. \dlo{We}\wen{One} then can get different separated seismic section\wen{s} by transforming the separated $f$-$x$ data back to $t$-$x$ domain. As the different oscillating components in each frequency slice of $f$-$x$ domain correspond to different dip components, the separating process acts as an adaptive dip filter.

The formulation of the EMD based dip filter was given by \cite{yangkang2014}:
\wen{
\begin{equation}
\label{eq:emdbdf}
u(f,h)=\sum_{n=1}^{N}d_n(f,h),
\end{equation}
}
\dlo{where \dlo{$N$}\wen{$I$} is the number of decomposed \wen{intrinsic mode functions (IMFs)} \dlo{IMFs} in each frequency slice, $\Lambda(f,h)$ is the filtered data for frequency slice $f$ in the $f-x$ domain. \dlo{$u_i(f,h)(i=1,2,\cdots,N)$}\wen{$u_i(f,h)(i=1,2,\cdots,I)$} is the $i$th separated IMF such that $S(f,h)=\sum_{i=1}^{I}u_i(f,h)$, where $S(f,h)$ is the transformed $f-x$ domain seismic data. \dlo{$D_i(i=1,2,\cdots,M)$}\wen{$D_i(i=1,2,\cdots,N)$} is the $i$th dip band or component, and \dlo{$M$}\wen{$N$} is the number of dip bands or the number of dip components to be separated, and $\epsilon_i$ is the corresponding weighting coefficient. For a simple high-pass dip filter, we can choose \dlo{$M=2$, $\epsilon_1=1$, $\epsilon_2=0$ and $D_1=\{1,2\}$, $D_2=\{3,4,\cdots,N\}$.}\wen{$N=2$, $\epsilon_1=1$, $\epsilon_2=0$ and $D_1=\{1,2\}$, $D_2=\{3,4,\cdots,I\}$.} To form a dip filter that separates a seismic profile into five dip components, we can parameterize equation \ref{eq:emdbdf} as shown in Table \ref{tbl:filterpara1}. Note that, for every seismic data, we can use the same parameters as shown Table \ref{tbl:filterpara1} to obtained five dip components. To obtain a different number of dip components, we only need to specify the number of dip components \dlo{$M$}\wen{$N$} and parameterize equation \ref{eq:emdbdf} similarly.}
\wen{where $N$ is the number of dip components or the number of EMD decomposed components. $n$ denotes index, $f$ denotes frequency, and $h$ denotes spatial trace index. The decomposition is done in each frequency slice in the frequency-space domain via EMD. The details of EMD can be found in \cite{emd}. }

\wen{Equation \ref{eq:emdbdf} is formulated in the frequency domain in its original form. In the time-space domain, the EMD based dip filtering is simply
\begin{equation}
\label{eq:emdbdft}
\mathbf{u}=\sum_{n=1}^{N}\mathbf{d_n},
\end{equation}
where $\mathbf{u}$ is the vectorized seismic data, $\mathbf{d}_n$ is the $n$th dip component after using the EMD based dip filter. It is obvious that the EMD based dip filter is a linear transform and the summation of all the dip components is the original seismic image.
 }

\onecolumn
\bibliographystyle{seg}
\bibliography{emdseis}

\newpage

### 2020-09-16 dmssa/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{Geophysics, 81, V261-V270, (2016)}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\title{Damped multichannel singular spectrum analysis for 3D random noise attenuation}
\author{Weilin Huang\footnotemark[1], Runqiu Wang\footnotemark[1], Yangkang Chen\footnotemark[2], Huijian Li\footnotemark[1], and Shuwei Gan\footnotemark[1]}

\address{
\footnotemark[1] State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200\\
cup\_hwl@126.com \& wrq@cup.edu.cn \& lihuijian1117@163.com \& gsw19900128@126.com\\ 
\footnotemark[2]Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
ykchen@utexas.edu 
}

\ms{GEO-2015}

\lefthead{Huang et al.}
\righthead{Damped MSSA}

\maketitle

% for multiple-revision
\DeclareRobustCommand{\dlo}[1]{\ifthenelse{\boolean{@revd}}{}{}}
\DeclareRobustCommand{\wen}[1]{%
  \ifthenelse{\boolean{@revd}}{\textcolor{black}{#1}}{#1}}

\begin{abstract}
Multichannel singular spectrum analysis (MSSA) is an effective algorithm for random noise attenuation in seismic data, which decomposes the vector space of the Hankel matrix of the  noisy signal into a signal subspace and a noise subspace by the truncated singular value  decomposition (TSVD). However, this signal subspace actually still contains residual noise.  We derived a new formula of low-rank reduction, which is more powerful in  distinguishing between signal and noise compared with the traditional TSVD. By introducing a  damping factor into the traditional MSSA for damping the singular values, we proposed a new algorithm for random noise attenuation. The proposed modified MSSA is named as the damped MSSA. The denoising performance is controlled by the damping factor and the proposed approach reverts to the traditional MSSA approach when the damping factor is sufficiently large. Application of the damped MSSA algorithm on synthetic and field seismic data demonstrates a superior performance compared with the conventional MSSA algorithm.
\end{abstract}

\section{Introduction}
High signal-to-noise ratio (SNR) is necessary \old{to many tasks}\new{for many procedures} in seismic exploration such as amplitude \old{versus}\new{variation with} offset (AVO) analysis, seismic attribute analysis and microseismic monitoring. The attenuation of random noise is an important subject in improving the signal-to-noise ratio (SNR) \cite[]{yangkang20141}. \dlo{The useful signal that is smeared in the ambient random noise is often neglected and thus may cause fake discontinuity of seismic events and artifact in final migrated image.}\wen{If signal is eliminated with the noise, continuity of seismic events may be disrupted and the resulting image quality will be negatively affected.} Enhancing the useful signal while preserving edge properties of the seismic profiles by attenuating random noise can help reduce interpretation difficulties and risks for oil \& gas detection \cite[]{shuwei2015,wencheng2015asa}.

There are several classical ways for random\dlo{-} noise attenuation: prediction based noise-attenuation approaches \cite[]{abma1995,guochang20112} \wen{ such as the $f-x$ deconvolution \cite[]{canales1984,gulunay1986} and $f-xy$ deconcolution \cite[]{fxydecon,guochang2012}}, median filtering \cite[]{yike2013,yangkang2014svmf,shuwei2016}, Karhunen-Loeve transform \cite[]{jones1987}, sparse transform domain thresholding strategies \cite[]{donoho1995,neelamani2008,fomel2010seislet,yangkang20142,yangkang2016dsd} and \wen{Cadzow filtering \cite[]{trickett2008,trickett2009} or} multichannel singular spectrum analysis \cite[]{mssa,stephen2013,jianjun2013}. The principle of all these denoising approaches is to distinguish between noise and signal based on certain characteristics\wen{, such as the spatial coherency \dlo{and}\wen{or} the sparsity in a sparse transform domain}. \dlo{In order to compensate for the loss of useful energy during the noise-attenuation process,} \cite{yangkang2015ortho} proposed a two-step denoising approach in order to retrieve the lost useful information from the removed noise based on local signal-and-noise orthogonalization.

In this paper, we focus\new{ed} on attenuating random noise in 3D seismic data using the multichannel singular spectrum analysis (MSSA) algorithm. MSSA is a data-driven algorithm developed from research on alternative tools for the analysis of multichannel time series, which is based on the truncated singular value decomposition (TSVD) \cite[]{golub1996} of the Hankel matrix. MSSA is also an extension of singular spectrum analysis (SSA), which is used to analyze 1D time series. Like other noise-attenuation methods, MSSA transforms the data into a domain where signal and noise \wen{are mapped} \dlo{map} onto separate subspaces and then removes the noise. However, many numerical experiments suggest that the random noise can not be completely removed using the MSSA algorithm \cite[]{weilin2015}. \old{One of the reasons}\new{One perspective} is that the TSVD can only decompose the data into a noise subspace and a signal-plus-noise subspace. \old{In order to make the MSSA algorithm more robust, a modified version is strongly required. In this paper, we propose\new{d} a damped MSSA approach that can decompose the data into the signal subspace and noise subspace, thus significantly improving the denoising performance of the traditional MSSA approach.}\new{In this paper, we analyzed how to theoretically decompose the input data into signal subspace and noise subspace and proposed a  practical solution to apply a variable damping factor to different singular values to obtain results with higher SNR.} We used both synthetic and field 3D seismic datasets to demonstrate our proposed approach.

\section{Traditional MSSA by TSVD}
Consider a block of 3D data $\mathbf{D}_{time}(x,y,t)$ of $N_x$ by $N_y$ by $N_t$ samples $(x=1\cdots N_x,y=1\cdots N_y,t=1\cdots N_t)$. The MSSA \cite[]{mssa} operates on the data in the following way: first, MSSA transforms $\mathbf{D}_{time}(x,y,t)$ into $\mathbf{D}_{freq}(x,y,w)(w=1\cdots N_w)$ \dlo{of}\wen{with} complex values \dlo{of}\wen{in} the frequency domain. Each frequency slice of the data, at a given frequency $w_0$, can be represented by the following matrix:
\begin{equation}
\label{eq:mssa}
\mathbf{D}(w_0)=\left(\begin{array}{cccc}
D(1,1) & D(1,2) & \cdots &D(1,N_x) \\
D(2,1) & D(2,2)  &\cdots &D(2,N_x) \\
\vdots & \vdots &\ddots &\vdots \\
D(N_y,1)&D(N_y,2) &\cdots&D(N_y,N_x)
\end{array}
\right).
\end{equation}

To avoid notational clutter we omit the argument $w_0$. Second, MSSA constructs a Hankel matrix for each row of $\mathbf{D}$; the Hankel matrix $\mathbf{R}_i$ for row $i$ of $\mathbf{D}$ is as follows:
\begin{equation}
\label{eq:data}
\mathbf{R}_i=\left(\begin{array}{cccc}
D(i,1) & D(i,2) & \cdots &D(i,m) \\
D(i,2) & D(i,3)  &\cdots &D(i,m+1) \\
\vdots & \vdots &\ddots &\vdots \\
D(i,N_x-m+1)&D(i,N_x-m+2) &\cdots&D(i,N_x)
\end{array}
\right).
\end{equation}
Then MSSA constructs a block Hankel matrix $\mathbf{M}$ for $\mathbf{R}_i$ \new{as}:
\begin{equation}
\label{eq:hankel2}
\mathbf{M}=\left(\begin{array}{cccc}
\mathbf{R}_1 &\mathbf{R}_2 & \cdots &\mathbf{R}_n \\
\mathbf{R}_2 &\mathbf{R}_3 &\cdots &\mathbf{R}_{n+1} \\
\vdots & \vdots &\ddots &\vdots \\
\mathbf{R}_{N_y-n+1}&\mathbf{R}_{N_y-n+2} &\cdots&\mathbf{R}_{N_y}
\end{array}
\right).
\end{equation}
The size of $\mathbf{M}$ is $I\times J$, $I=(N_x-m+1)(N_y-n+1)$, \dlo{$J=mI$}\wen{$J=mn$}. $m$ and $n$ are predifined integers chosen such that the \wen{Hankel maxtrix $\mathbf{R}_i$ and the block Hankel matrix $\mathbf{M}$}  \dlo{block Hankel matrices $\mathbf{R}_i$ and $\mathbf{M}$} are close to square matrices, for example, $m=N_x-\lfloor\frac{N_x}{2}\rfloor$ and $n=N_y-\lfloor\frac{N_y}{2}\rfloor$, where $\lfloor\cdot\rfloor$ denotes the integer part of the \dlo{input}\wen{argument}. We assume that $I>J$. The filtered data are recovered with random noise attenuated by properly averaging along the anti-diagonals of the low-rank reduction matrix of $\mathbf{M}$ via TSVD. \old{Let us first focus on the TSVD.}\new{Next, we would like to briefly discuss the TSVD to introduce our work.} % for the purpose of random noise attenuated. 
 In general, the matrix $\mathbf{M}$ can be represented as
\begin{equation}
\label{eq:M}
\mathbf{M}=\mathbf{S}+\mathbf{N},
\end{equation}
where $\mathbf{S}$ and $\mathbf{N}$ denote the block Hankel matrix of signal and of random noise, respectively. We assume that $\mathbf{M}$ and $\mathbf{N}$ have full rank, $rank(\mathbf{M})$=$rank(\mathbf{N})=J$ and $\mathbf{S}$ has deficient rank, $rank(\mathbf{S})=K<J$. The singular value decomposition (SVD) of $\mathbf{M}$ can be represented as:
\begin{equation}
\label{eq:svdm}
\mathbf{M} = [\mathbf{U}_1^M\quad \mathbf{U}_2^M]\left[\begin{array}{cc} 
\Sigma_1^M & \mathbf{0}\\
\mathbf{0} & \Sigma_2^M
\end{array}
\right]\left[\begin{array}{c} 
(\mathbf{V}_1^M)^H\\
(\mathbf{V}_2^M)^H
\end{array}
\right],
\end{equation}
where $\Sigma_1^M$ ($K\times K$) and $\Sigma_2^M$ ($(I-K)\times(J-K)$) are diagonal matrices and contain, respectively, larger singular values and smaller singular values. $\mathbf{U}_1^M$ ($I\times K$), $\mathbf{U}_2^M$ ($I\times (I-K)$), $\mathbf{V}_1^M$ ($J\times K$) and $\mathbf{V}_2^M$ ($J\times (J-K)$) denote the associated matrices with singular vectors. The symbol $[\cdot]^H$ denotes the conjugate transpose of a matrix. \old{In general}\new{Generally,} the signal is more energy-concentrated and correlative than the random noise.  Thus, the larger singular values and their associated singular vectors represent the signal, \dlo{while the smaller represent the random noise.}\wen{while the smaller values and their associated singular vectors represent the random noise.} We let $\Sigma_2^M$ be $\mathbf{0}$ to achieve the goal of attenuating random noise as follows:
\begin{equation}
\label{eq:tsvd}
\tilde{\mathbf{M}} = \mathbf{U}_1^M\Sigma_1^M(\mathbf{V}_1^M)^H.
\end{equation}
Equation \ref{eq:tsvd} is referred to as the TSVD.

\section{Damped MSSA}
However, $\tilde{\mathbf{M}}$ is actually still mixed with residual noise. In the following part, we will first \old{introduce}\new{analyse} the reason why $\tilde{\mathbf{M}}$ also contains noise component, and then introduce the modified MSSA method by damping the singular values, which we call the damped MSSA.

The singular value decomposition (SVD) of $\mathbf{S}$ can be represented as:
\begin{equation}
\label{eq:svds}
\mathbf{S} = [\mathbf{U}_1^S\quad \mathbf{U}_2^S]\left[\begin{array}{cc} 
\Sigma_1^S & \mathbf{0}\\
\mathbf{0} & \Sigma_2^S
\end{array}
\right]\left[\begin{array}{c} 
(\mathbf{V}_1^S)^H\\
(\mathbf{V}_2^S)^H
\end{array}
\right].
\end{equation}
The corresponding matrices in equations \ref{eq:svdm} and \ref{eq:svds} have the same size.

Because of the deficient rank, the matrix $\mathbf{S}$ can be written as
\begin{equation}
\label{eq:S}
\mathbf{S}=\mathbf{U}_1^S\Sigma_1^S(\mathbf{V}_1^S)^H.
\end{equation}

Combining equations \ref{eq:M}, \ref{eq:svds}, and \ref{eq:S}, we can factorize $\mathbf{M}$ as follows:
\begin{equation}
\label{eq:factorm}
\mathbf{M} = [\mathbf{U}_1^S \quad \mathbf{U}_2^S]\left[\begin{array}{cc} 
\Sigma_{1} & \mathbf{0}\\
\mathbf{0} & \Sigma_{2}
\end{array}
\right]\left[\begin{array}{c} 
(\Sigma_{1})^{-1}(\mathbf{N}^H\mathbf{U}_1^S+\mathbf{V}_1^S\Sigma_1^S)^H\\
(\Sigma_{2})^{-1}(\mathbf{N}^H\mathbf{U}_2^S)^H
\end{array}
\right],
\end{equation}

where $\Sigma_1$ and $\Sigma_2$ denote diagonal and positive definite matrices. \wen{Please note that M is constructed such that it is close to a square matrix \cite[]{mssa}, and thus the $\Sigma_1$ and $\Sigma_2$ are assumed to be square matrices for derivation convenience.} The appendix A provides the derivation of how we factorize $\mathbf{M}$ into the form of equation \ref{eq:factorm}. We observe that the left \dlo{and right matrices}\wen{matrix} \dlo{have}\wen{has} orthonormal columns and the middle matrix is diagonal. \wen{It can be proven that the right matrix also has orthonormal columns. The proof is provided in appendix A.} Thus, equation \ref{eq:factorm} is an SVD of $\mathbf{M}$. According to the TSVD method, we let $\Sigma_2$ be $\mathbf{0}$ and then the following equation holds:
\begin{equation}
\label{eq:tsvd2}
\begin{split}
\tilde{\mathbf{M}} &= \mathbf{U}_1^S(\mathbf{U}_1^S)^H\mathbf{N} + \mathbf{U}_1^S\Sigma_1^S(\mathbf{V}_1^S)^H \\
 &=\mathbf{S} + \mathbf{U}_1^S(\mathbf{U}_1^S)^H\mathbf{N}.
\end{split}
\end{equation}

It is clear that $\tilde{\mathbf{M}}\neq\mathbf{S}$. Because the matrices $\mathbf{U}_1^S$ and $\mathbf{N}$ are unknown, \dlo{so }we cannot use equation \ref{eq:tsvd2} directly to attenuate the residual noise. However, by combining equations \ref{eq:tsvd}, \ref{eq:factorm} and \ref{eq:tsvd2}, we can derive $\mathbf{S}$ as:

\begin{equation}
\label{eq:S2}
\mathbf{S}=\mathbf{U}_1^M\left\{\Sigma_1^M(\mathbf{V}_1^M)^H- \left[\Sigma_1(\mathbf{V}_1^M)^H-\Sigma_1^S(\mathbf{V}_1^S)^H\right]\right\}
\end{equation}
The appendix B gives a detailed derivation to obtain equation \ref{eq:S2} from equations \ref{eq:tsvd}, \ref{eq:factorm} and \ref{eq:tsvd2}.

For simplification, we assume that there exist\dlo{s} such $\mathbf{A}$ and $\mathbf{B}$ that $\mathbf{V}_1^S=\mathbf{V}_1^M\mathbf{A}$ and $\Sigma_1= \Sigma_1^M\mathbf{B}$. $\mathbf{A}$ is a square matrix of \dlo{$J\times J$}\wen{$K\times K$} and $\mathbf{B}$ is a diagonal matrix of \dlo{$J\times J$}\wen{$K\times K$}. Then we can simplify $\mathbf{S}$ as:

\begin{align}
\label{eq:S3}
\mathbf{S} &= \mathbf{U}_1^M\Sigma_1^M\mathbf{T}\left(\mathbf{V}_1^M\right)^H.\\
\label{eq:T}
\mathbf{T} &= \mathbf{I} - \mathbf{B}\left(\mathbf{I}-(\Sigma_1)^{-1}\Sigma_1^S\mathbf{A}^H\right),
\end{align}
where $\mathbf{I}$ is a unit matrix and here we name $\mathbf{T}$ the damping operator. In fact, from equation \ref{eq:factorm}, we can also approximate $\mathbf{A}$ and $\mathbf{B}$ as follows:

\begin{align}
\label{eq:A}
\mathbf{A}&\approx(\mathbf{I}-\Gamma)\Sigma_1\left(\Sigma_1^S\right)^{-1},\\
\label{eq:B}
\mathbf{B} &=\mathbf{I}.
\end{align}
where \dlo{$\Gamma=(\mathbf{V}_1^M)^H\mathbf{N}^H\mathbf{U}_1^S$} \wen{$\Gamma=(\mathbf{V}_1^M)^{o}\mathbf{N}^H\mathbf{U}_1^S(\Sigma_1)^{-1}$} is an unknown matrix\dlo{, where}\wen{.} $(\mathbf{V}_1^M)^{o}$ \wen{can be regarded as an approximate inverse of $\mathbf{V}_1^M$, which }satisfies that $\parallel\mathbf{I}-\mathbf{V}_1^M(\mathbf{V}_1^M)^{o} \parallel\rightarrow 0$. The appendix B provides the detailed derivation for obtaining equations \ref{eq:A} and \ref{eq:B}.

Inserting equations \ref{eq:A} and \ref{eq:B} into equation \ref{eq:T}, we can obtain a simplified formula:

\begin{equation}
\label{eq:T1}
\begin{split}
\mathbf{T} &= \mathbf{I} - \mathbf{I}\left(\mathbf{I}-(\Sigma_1)^{-1}\Sigma_1^S\mathbf{A}^H\right)\\
		 &= (\Sigma_1)^{-1}\Sigma_1^S\mathbf{A}^H \\
		 &\approx(\Sigma_1)^{-1}\Sigma_1^S  \left((\mathbf{I}-\Gamma)\Sigma_1\left(\Sigma_1^S\right)^{-1}\right)^H \\
		 &=\mathbf{I}-\Gamma.
\end{split}		 
\end{equation}

Combing equations \ref{eq:S3} and \ref{eq:T1}, we can conclude that the true signal is a damped version of the previous TSVD method (equation \ref{eq:tsvd}), with the damping operator defined by equation \ref{eq:T1}. Right now, there \dlo{are}\wen{is} still one unknown parameter needed to be defined: $\Gamma$. Although we have a potential selection  $\Gamma=(\mathbf{V}_1^M)^{o}\mathbf{N}^H\mathbf{U}_1^S(\Sigma_1)^{-1}$, as defined during the derivation of $\mathbf{A}$, we cannot calculate it because we do not know $\mathbf{N}$ and $\mathbf{U}_1^S$.

\wen{
Instead, we seek the form of $\Gamma$ from a different way. We treat $\Gamma$ as a whole instead of paying attention to each detailed component in $\Gamma=(\mathbf{V}_1^M)^{o}\mathbf{N}^H\mathbf{U}_1^S(\Sigma_1)^{-1}$. We have known that the true signal is a damped version of the TSVD method from the previous derivation, and the damping operator equals to $\mathbf{I}-\Gamma$, \old{which acts}\new{acting} on the diagonal matrix $\Sigma_1^M$. We can begin our search for an approximation of $\Gamma$ based on the following conditions:
\begin{enumerate}
\item As we know from the previous derivation, the truncating point of TSVD is the rank of the signal matrix $\mathbf{S}$. In other words, the rank of $\tilde{\mathbf{M}}= \mathbf{U}_1^M\Sigma_1^M(\mathbf{V}_1^M)^H$ equals to the rank of $\mathbf{S}$. The rank of $\tilde{\mathbf{M}}$ should remain unchanged when we damp $\Sigma_1^M$. Therefore, the damping operator should be a diagonal and positive definite matrix.
\item Each element of the damping operator should be in the interval $(0,1]$.
\item The lower the SNR is, the stronger the damping should be, because the energy of random noise in the signal-noise space is relatively \old{more}\new{stronger}. \old{Therefore the damping operator should have a positive relationship with the SNR.}
\item In the case of zero random noise, the damping operator should be a unit matrix.
\item Since we always hope to preserve the main components of seismic data, the damping operator should have a weaker effect on the larger singular value.
\item The power of the damping operator can be controlled by one coefficient and the damped MSSA can revert to the traditional MSSA.
\end{enumerate}
From the above analysis, we \old{speculate that the $\Gamma$ should be a formula as}\new{propose to use a $\Gamma$ of the following form:}
		\begin{equation}
		\Gamma=
		\left(                 
		\begin{array}{cccc}  
		a_1/b_1 &         &        &   \\[3mm]
		        & a_2/b_2 &        &   \\[3mm]
		        &         & \ddots &   \\[3mm]
		        &         &        & a_K/b_K
		\end{array}
		\right),                 
		\end{equation}
where \old{the sequences $ \{a\} $ and $ \{b\} $ satisfy that} $ \{a\} $ contains the information of random noise, $ \{b\} $ contains the information of signal, $ a_1/b_1<a_2/b_2<\cdots<a_K/b_K $ and $ 0<a_i<b_i $, $i=1,2,\cdots,K $. 
}

\wen{We} \new{tried}\old{try} a lot \dlo{a}\wen{of} numerical experiments and found that a very pleasant denoising performance can be obtained when $\Gamma$ is chosen as
\begin{equation}
\label{eq:Gamma}
\Gamma \approx \hat{\delta}^N\left(\Sigma_1^M\right)^{-N},
\end{equation}
where $\hat{\delta}$ denotes the maximum element of $\Sigma_2^M$ and $N$ denotes the damping factor. \wen{We use such approximation because of three reasons. (1) $\hat{\delta}$ reflects the energy of random noise and $ \Sigma_1^M $ contains the information of signal. (2) Because the diagonal  elements of $ \Sigma^M $ are in a descending order, $\hat{\delta} $  is certainly smaller than every diagonal element of $ \Sigma_1^M $, and  $ \hat{\delta}/\delta_1<\hat{\delta}/\delta_2<\cdots<\hat{\delta}/\delta_K $, where $\delta_i$ denotes $i$th diagonal entry in $\Sigma_1^M$. (3) $\hat{\delta}$ is zero in the zero random noise situation. Besides, We introduce the parameter $ N $ to control the strength of damping operator, the greater the $ N $, the weaker the damping, and the damped MSSA reverts to the basic MSSA when $ N\to\infty $.
}

Combining equations \ref{eq:S3}, \ref{eq:T1}, and \ref{eq:Gamma}, we conclude the approximation of $\mathbf{S}$ as:
\begin{align}
\label{eq:S4}
\mathbf{S} & = \mathbf{U}_1^M \Sigma_1^M\mathbf{T}(\mathbf{V}_1^M)^H,\\
\label{eq:T2}
\mathbf{T} & =\mathbf{I}-(\Sigma_1^M)^{-N}\hat{\delta}^N.
\end{align} 
\dlo{The newly developed algorithm (equations \ref{eq:S4} and \ref{eq:T2}) is termed as the damped MSSA algorithm.}\wen{We call the newly developed algorithm (equations \ref{eq:S4} and \ref{eq:T2}) damped MSSA algorithm.} In the proposed algorithm, we only need to decide \old{the} two parameters: the rank $K$ and the damping factor $N$. \dlo{It is worth to be mentioned that the greater the $N$, the weaker the damping, and equation \ref{eq:S4} reverts to equation \ref{eq:tsvd} when $N\rightarrow +\infty$.} \wen{It is worth mentioning that the damping operator $\mathbf{T}$ (equation \ref{eq:T2}) also behaves as a soft-thresholding operator applied on the singular matrix $\mathbf{\Sigma_1^M}$. } The damping (thresholding) step may thus cause slight damage to useful signal while more noise is scaled down, and the final S/N can still be \old{much}\new{greatly} improved.

The parameterization for the DMSSA approach is \old{very}\new{quite} convenient. Although the traditional MSSA has a rank with \old{large}\new{broad} range according to the data size and data complexity, the damping factor is usually chosen between 2-5. When damping factor is chosen as 1, the damping is very strong and will cause some useful energy loss, but when the damping factor is chosen \new{as} 2, 3, or even larger value, the compromise between preservation of useful signals and removal of random noise are much improved. The implementation of the DMSSA approach can be straightforwardly based on the MSSA framework, except for the slight difference, \dlo{that}\wen{which} introduces the damping factor.

\section{Examples}
We first test the damped MSSA algorithm proposed in this paper on a 3D synthetic data \wen{set} which is composed of three linear events in $x-y-t$ domain. The data contain $N_x\times N_y$ traces, with $N_x=20$ and $N_y=20$. The size of the block Hankel matrix for this example is $121\times100$. The temporal length of the window is 600 ms. The sampling interval is 2ms. The clean and noisy data are shown in Figures \ref{fig:synth-clean} and \ref{fig:synth-noisy}, respectively. \wen{In this example, we add  bandlimited random noise with bandwidth close to the seismic bandwidth.} \wen{The lines indicate the displaying slices for the front, right, and top views.} After using the conventional MSSA and the damped MSSA, the results are shown in Figures \ref{fig:synth-mssa} and \ref{fig:synth-dmssa}, respectively. Figures \ref{fig:synth-n-mssa} and \ref{fig:synth-n-dmssa} show the removed noise that correspond to the conventional MSSA and the damped MSSA, respectively. Figure \ref{fig:synth-s-clean,synth-s-mssa,synth-sn-mssa,synth-s-noisy,synth-s-dmssa,synth-sn-dmssa} demonstrates the denoising comparison of the 5th crossline section of the synthetic example. Figure \ref{fig:synth-s-clean-i,synth-s-mssa-i,synth-sn-mssa-i,synth-s-noisy-i,synth-s-dmssa-i,synth-sn-dmssa-i} demonstrates the denoising comparison of the 5th inline section of the synthetic example. From Figures \ref{fig:synth-clean,synth-mssa,synth-n-mssa,synth-noisy,synth-dmssa,synth-n-dmssa}, \ref{fig:synth-s-clean,synth-s-mssa,synth-sn-mssa,synth-s-noisy,synth-s-dmssa,synth-sn-dmssa}, and \ref{fig:synth-s-clean-i,synth-s-mssa-i,synth-sn-mssa-i,synth-s-noisy-i,synth-s-dmssa-i,synth-sn-dmssa-i}, it is clear that although the traditional MSSA approach performs well and suppresses the random noise, the proposed damped MSSA approach obtains even better results. In this example, \dlo{we use}\wen{the rank} $K=3$ and \wen{the damping factor} \dlo{$N=3$}\wen{$N=4$}. \wen{Figure \ref{fig:synth-err1,synth-err2} show\wen{s} two denoising error comparison of the 5th inline section of the synthetic example. The error section denotes the difference section between the clean and denoised section. It is obvious that both MSSA and DMSSA approaches will not cause obvious damage to the useful events while the DMSSA approach cause less denoising error because of a larger amount of removed noise.} In order to test the sensitivity of the denoising performance on the damping factor $N$, we tried different $N$ and compared their performance. Figure \ref{fig:synth-s-dmssa-1,synth-s-dmssa-2,synth-s-dmssa-4,synth-s-dmssa-10,synth-s-dmssa-20,synth-s-dmssa-40} shows the denoising performance of the 5th crossline section using different $N$. It is clear that as $N$ increases, the residual noise becomes stronger and stronger. When $N=40$, the denoising performance is nearly the same as the traditional MSSA, as shown in Figure \ref{fig:synth-s-mssa}. When the $N$ is too small, say $N=1$, although the denoised section (Figure \ref{fig:synth-s-dmssa-1}) is very clean, \dlo{there causes some damages to the events.}\wen{there is some signal loss on the events.} We can increase $N$ from 1 to \dlo{3}\wen{4} to obtain a compromise between the removal of residual noise and the preservation of useful signals, as shown in Figures \ref{fig:synth-s-dmssa} and \ref{fig:synth-s-dmssa-4}.

To demonstrate how the proposed algorithm works in practice, we apply the damped MSSA algorithm on two 3D post-stack field datasets. The first field data is shown in Figure \ref{fig:field}. Figures \ref{fig:field-mssa} and \ref{fig:field-dmssa} show the denoised data using the traditional and damped MSSAs, respectively. Figures \ref{fig:field-n-mssa} and \ref{fig:field-n-dmssa} show the removed noise using the traditional and damped MSSAs, respectively. In this test, in order to preserve the main features of the original data, we use a more conservative combination of $K$ and $N$ ($K=25$ and $N=5$ in this example)\dlo{, in order to preserve all the potential useful components}.  A denoising comparison of the 5th crossline section is shown in Figure \ref{fig:field-s-0,field-s-mssa-0,field-s-dmssa-0,field-sn-mssa,field-sn-dmssa}. The top row of Figure \ref{fig:field-s-0,field-s-mssa-0,field-s-dmssa-0,field-sn-mssa,field-sn-dmssa} shows the comparison between the raw data and the denoised data using the traditional MSSA and the damped MSSA. The bottom row of Figure \ref{fig:field-s-0,field-s-mssa-0,field-s-dmssa-0,field-sn-mssa,field-sn-dmssa} shows a comparison of the removed noise sections using two methods. \dlo{In can be observed}\wen{It can be observed} that the denoised section using the damped MSSA (Figure \ref{fig:field-s-dmssa-0}) is cleaner than that of the traditional MSSA (Figure \ref{fig:field-s-mssa-0}). The noise section of the damped MSSA is obviously noisier than that of the traditional MSSA, which indicates that the damped MSSA can attenuate more random noise. Since there is \wen{almost} no coherent energy in the noise sections, \dlo{both denoising results can be acceptable}\wen{both denoising results would be acceptable}, but the proposed approach obtains a better performance. Figure \ref{fig:z-field,z-mssa,z-dmssa} shows three zoomed parts from the crossline sections of the raw data and two denoised data, as highlighted by the frameboxes in Figure \ref{fig:field-s-0,field-s-mssa-0,field-s-dmssa-0,field-sn-mssa,field-sn-dmssa}, which gives us a more detailed comparison.  \wen{The MSSA approach obtains a big improvement of the image considering the signal-to-noise ratio (S/N) while the DMSSA approach obtains a even better performance. The events  using the DMSSA approach become more continuous than the MSSA approach, without remaining any random noise, and both approaches well preserve the discontinuities in the image.}

The second field data example is shown in Figure \ref{fig:field2}. The reflectors in this example \dlo{have higher curvature}\wen{are more complex with steeper dips} compared with the first field data example. The two denoised results are shown in Figures \ref{fig:field2-mssa} and \ref{fig:field2-dmssa}. Figures \dlo{\ref{fig:field-sn-mssa} and \ref{fig:field-sn-dmssa}}\wen{\ref{fig:field2-n-mssa} and \ref{fig:field2-n-dmssa}} show the removed noise cubes using the traditional MSSA and the damped MSSA, respectively. It is clear that the proposed approach can remove stronger noise compared with the traditional MSSA approach, as can be see from Figure \ref{fig:field2,field2-mssa,field2-dmssa,field2-n-mssa,field2-n-dmssa}. In this example, because of the \wen{steeper dip} of reflectors, \wen{we use higher $K$ compared \old{to}\new{with} the previous field data example}. \wen{In practice, when the seismic data becomes more complicated, a higher $K$ value should be used to account for the higher rank caused by the larger number of dip components. } For this example, $K=40$ and $N=2$. The 10th crossline sections \dlo{are picked} from the raw data, \wen{the} denoised data using the traditional MSSA approach, and \wen{the} denoised data using the damped MSSA approach, are shown in Figures \ref{fig:field2-s-0}, \ref{fig:field2-s-mssa-0}, and \ref{fig:field2-s-dmssa-0}, respectively. The bottom row of Figure \ref{fig:field2-s-0,field2-s-mssa-0,field2-s-dmssa-0,z-field2,z-field2-mssa,z-field2-dmssa} shows the zoomed sections that correspond to the frameboxes in the top row. It is clear that the proposed approach can obtain smoother and cleaner reflections than the traditional MSSA approach. \wen{For all the three examples, we do not use local processing windows to apply the MSSA or DMSSA algorithm, because the data size is not big and data structure is not very complicated, which makes the performance using MSSA still acceptable.}

%\inputdir{synth2}
%\multiplot{6}{synth-clean,synth-mssa,synth-n-mssa,synth-noisy,synth-dmssa,synth-n-dmssa}{width=0.29\textwidth}{Denoising comparison of synthetic example. (a) \& (d) Clean and noisy data, respectively. (b) \& (e) Denoised data using the traditional MSSA and the damped MSSA, respectively. (c) \& (f) Removed noise using the traditional MSSA and the damped MSSA, respectively. In the example, $K=3$, \dlo{$N=3$}\wen{$N=4$}.}

%\multiplot{6}{synth-s-clean,synth-s-mssa,synth-sn-mssa,synth-s-noisy,synth-s-dmssa,synth-sn-dmssa}{width=0.29\textwidth}{Denoising comparison of the 5th crossline section of the synthetic example. (a) \& (d) Clean and noisy data, respectively. (b) \& (e) Denoised data using the traditional MSSA and the damped MSSA, respectively. (c) \& (f) Removed noise using the traditional MSSA and the damped MSSA, respectively. }

%\multiplot{6}{synth-s-clean-i,synth-s-mssa-i,synth-sn-mssa-i,synth-s-noisy-i,synth-s-dmssa-i,synth-sn-dmssa-i}{width=0.29\textwidth}{Denoising comparison of the 5th inline section of the synthetic example. (a) \& (d) Clean and noisy data, respectively. (b) \& (e) Denoised data using the traditional MSSA and the damped MSSA, respectively. (c) \& (f) Removed noise using the traditional MSSA and the damped MSSA, respectively. }

%\multiplot{2}{synth-err1,synth-err2}{width=0.29\textwidth}{\wen{Denoising error comparison of the 5th inline section of the synthetic example. (a) Error of the traditional MSSA. (b) Error of the damped MSSA.} }

%\multiplot{6}{synth-s-dmssa-1,synth-s-dmssa-2,synth-s-dmssa-4,synth-s-dmssa-10,synth-s-dmssa-20,synth-s-dmssa-40}{width=0.29\textwidth}{Demonstration of the performance with same $K=3$ and different $N$ for the 5th crossline section. (a) N=1. (b) N=2. (c) \dlo{N=3}\wen{N=4}. (d) N=10. (e) N=20. (f) N=40. }

\inputdir{synth3}
\multiplot{6}{synth-clean,synth-mssa,synth-n-mssa,synth-noisy,synth-dmssa,synth-n-dmssa}{width=0.29\textwidth}{Denoising comparison of synthetic example. (a) \& (d) Clean and noisy data, respectively. (b) \& (e) Denoised data using the traditional MSSA and the damped MSSA, respectively. (c) \& (f) Removed noise using the traditional MSSA and the damped MSSA, respectively. In the example, $K=3$, \dlo{$N=3$}\wen{$N=4$}.}

\multiplot{6}{synth-s-clean,synth-s-mssa,synth-sn-mssa,synth-s-noisy,synth-s-dmssa,synth-sn-dmssa}{width=0.29\textwidth}{Denoising comparison of the 5th crossline section of the synthetic example. (a) \& (d) Clean and noisy data, respectively. (b) \& (e) Denoised data using the traditional MSSA and the damped MSSA, respectively. (c) \& (f) Removed noise using the traditional MSSA and the damped MSSA, respectively. }

\multiplot{6}{synth-s-clean-i,synth-s-mssa-i,synth-sn-mssa-i,synth-s-noisy-i,synth-s-dmssa-i,synth-sn-dmssa-i}{width=0.29\textwidth}{Denoising comparison of the 5th inline section of the synthetic example. (a) \& (d) Clean and noisy data, respectively. (b) \& (e) Denoised data using the traditional MSSA and the damped MSSA, respectively. (c) \& (f) Removed noise using the traditional MSSA and the damped MSSA, respectively. }

\multiplot{2}{synth-err1,synth-err2}{width=0.29\textwidth}{\wen{Denoising error comparison of the 5th inline section of the synthetic example. (a) Error of the traditional MSSA. (b) Error of the damped MSSA.} }

\multiplot{6}{synth-s-dmssa-1,synth-s-dmssa-2,synth-s-dmssa-4,synth-s-dmssa-10,synth-s-dmssa-20,synth-s-dmssa-40}{width=0.29\textwidth}{Demonstration of the performance with same $K=3$ and different $N$ for the 5th crossline section. (a) N=1. (b) N=2. (c) \dlo{N=3}\wen{N=4}. (d) N=10. (e) N=20. (f) N=40. }

\inputdir{field}
\multiplot{5}{field,field-mssa,field-dmssa,field-n-mssa,field-n-dmssa}{width=0.29\textwidth}{Denoising comparison of first field data example. (a) Noisy 3D field data. (b) Denoised data using the traditional MSSA. (c) Denoised data using the damped MSSA. (d) Removed noise using the traditional MSSA. (e) Removed noise using the damped MSSA. In the example, $K=25$, $N=5$.}

\multiplot{5}{field-s-0,field-s-mssa-0,field-s-dmssa-0,field-sn-mssa,field-sn-dmssa}{width=0.29\textwidth}{Denoising comparison of the 5th crossline section of field data example. (a) Noisy 3D field data. (b) Denoised data using the traditional MSSA. (c) Denoised data using the damped MSSA. (d) Removed noise using the traditional MSSA. (e) Removed noise using the damped MSSA.}

\multiplot{3}{z-field,z-mssa,z-dmssa}{width=0.46\textwidth}{(a) Zoomed section from Figure \ref{fig:field-s-0}. (b) Zoomed section from Figure \ref{fig:field-s-mssa-0}. (c) Zoomed section from Figure \ref{fig:field-s-dmssa-0}.}

\inputdir{./}
\multiplot{5}{field2,field2-mssa,field2-dmssa,field2-n-mssa,field2-n-dmssa}{width=0.29\textwidth}{Denoising comparison of second field data example. (a) Noisy 3D field data. (b) Denoised data using the traditional MSSA. (c) Denoised data using the damped MSSA. (d) Removed noise using the traditional MSSA. (e) Removed noise using the damped MSSA. In the example, $K=40$, $N=2$.}

\multiplot{6}{field2-s-0,field2-s-mssa-0,field2-s-dmssa-0,z-field2,z-field2-mssa,z-field2-dmssa}{width=0.29\textwidth}{Denoising comparison of the 5th crossline section of field data example. (a) Noisy 3D field data. (b) Denoised data using the traditional MSSA. (c) Denoised data using the damped MSSA. (d) Zoomed section from (a). (e) Zoomed section from (b). (f) Zoomed section from (c).}

%\multiplot{6}{field2-s-0,field2-s-mssa-0,field2-s-dmssa-0,field2-sn-mssa,field2-sn-dmssa}{width=0.29\textwidth}{Denoising comparison of the 5th crossline section of field data example. (a) Noisy 3D field data. (b) Denoised data using the traditional MSSA. (c) Denoised data using the damped MSSA. (d) Removed noise using the traditional MSSA. (e) Removed noise using the damped MSSA.}

%\multiplot{3}{z-field2,z-field2-mssa,z-field2-dmssa}{width=0.46\textwidth}{(a) Zoomed section from Figure \ref{fig:field2-s-0}. (b) Zoomed section from Figure \ref{fig:field2-s-mssa-0}. (c) Zoomed section from Figure \ref{fig:field2-s-dmssa-0}.}

\section{Conclusion}
We have proposed a novel modified multichannel singular spectrum analysis (MSSA) algorithm to attenuate random noise with a new formula of low-rank reduction, which is named as the damped MSSA algorithm. Compared with the traditional truncated singular value decomposition (TSVD) formula, we introduce\new{d} a damping factor to damp the singular values that correspond to the signal in order to attenuate the residual noise appearing in the traditional approach. %\wen{The introduced damping operator may slightly scale down some of the signal energy, but will scale down much more residual noise, and thus the new approach can result in a larger SNR. }
\dlo{This formula is more suitable for random\dlo{-} noise attenuation compared with the traditional TSVD.} \wen{The preservation of useful signals and the removal of random noise are compromised through the introduced damping factor. While the rank in MSSA has a big range considering the data size and data complexity, the damping factor in the damped MSSA is usually chosen as an integer that is slightly larger than 1 (such as 2, 3, or 4) to obtain a sufficient improvement.} From the synthetic and field data examples, it is obvious that the proposed damped MSSA algorithm can obtain cleaner denoised image \dlo{and preserve signals better} compared with the traditional MSSA algorithm.

\section{Acknowledgement}
We would like to thank Ming Zhang, \wen{Valentina Socco, Kris Innanen\new{, Mauricio Sacchi}, and three anonymous reviewers} for constructive suggestions. This work is supported by the National Basic Research Program of China (grant NO: 2013 CB228602) and Texas Consortium for Computational Seismology (TCCS). \old{All the examples shown in this paper are reproducible in the Madagascar open-source platform.}

\newpage
\append{Factorization of the data matrix $\mathbf{M}$}
Because equation \ref{eq:svds} is a singular value decomposition (SVD) of the signal matrix $\mathbf{S}$, the left matrix in equation \ref{eq:svds} is a unitary matrix:
\begin{equation}
\label{eq:unit}
\mathbf{I}=\mathbf{U}^S(\mathbf{U}^S)^H=[\mathbf{U}_1^S\quad \mathbf{U}_2^S]\left[\begin{array}{c} 
(\mathbf{U}_1^S)^H \\
(\mathbf{U}_2^S)^H 
\end{array}
\right].
\end{equation}

Combining equations \ref{eq:M}, \ref{eq:S}, and \ref{eq:unit}, we can derive\new{:}
\begin{equation}
\label{eq:factorapp}
\begin{split}
\mathbf{M}&=\mathbf{S}+\mathbf{N} \\
&=\mathbf{S}+\mathbf{IN}\\
&=\mathbf{S}+[\mathbf{U}_1^S\quad \mathbf{U}_2^S]\left[\begin{array}{c} 
(\mathbf{U}_1^S)^H \\
(\mathbf{U}_2^S)^H
\end{array}
\right]\mathbf{N} \\
&=\mathbf{U}_1^S\Sigma_1^S(\mathbf{V}_1^S)^H + \left( 
\mathbf{U}_1^S(\mathbf{U}_1^S)^H+\mathbf{U}_2^S(\mathbf{U}_2^S)^H
\right)\mathbf{N}\\
&=\mathbf{U}_1^S \left(
(\mathbf{U}_1^S)^H\mathbf{N}+\Sigma_1^S(\mathbf{V}_1^S)^H
\right)+\mathbf{U}_2^S(\mathbf{U}_2^S)^H\mathbf{N}\\
&=\mathbf{U}_1^S\left(
\mathbf{N}^H\mathbf{U}_1^S+\mathbf{V}_1^S\Sigma_1^S
\right)^H + \mathbf{U}_2^S(\mathbf{N}^H\mathbf{U}_2^S)^H\\
&= [\mathbf{U}_1^S \quad \mathbf{U}_2^S]\left[\begin{array}{cc} 
\mathbf{I} & \mathbf{0}\\
\mathbf{0} & \mathbf{I}
\end{array}
\right]\left[\begin{array}{c} 
(\mathbf{N}^H\mathbf{U}_1^S+\mathbf{V}_1^S\Sigma_1^S)^H\\
(\mathbf{N}^H\mathbf{U}_2^S)^H
\end{array}
\right],\\
&= [\mathbf{U}_1^S \quad \mathbf{U}_2^S]\left[\begin{array}{cc} 
\Sigma_1 & \mathbf{0}\\
\mathbf{0} & \Sigma_2
\end{array}
\right]\left[\begin{array}{c} 
(\Sigma_1)^{-1}(\mathbf{N}^H\mathbf{U}_1^S+\mathbf{V}_1^S\Sigma_1^S)^H\\
(\Sigma_2)^{-1}(\mathbf{N}^H\mathbf{U}_2^S)^H
\end{array}
\right],
\end{split}
\end{equation}
where $\Sigma_1$ and $\Sigma_2$ are introduced  matrices and are diagonal and positive definite.

In order to make the right matrix orthonormal, we make two assumptions:
\begin{itemize}
\item The noise is close to white noise in the sense that $\mathbf{N}\mathbf{N}^H=\lambda\mathbf{I}$. 
\item The signal is orthogonal to the noise in the sense that $\mathbf{S}\mathbf{N}^H=\mathbf{0}$.
\end{itemize}

We let $\mathbf{P}^H$ denote\dlo{s} the right matrix of the last equation in \ref{eq:factorapp}, then
\begin{equation}
\label{eq:vhv}
\begin{split}
&\mathbf{P}^H\mathbf{P} \\
&=\left[\begin{array}{c} 
(\Sigma_1)^{-1}(\mathbf{N}^H\mathbf{U}_1^S+\mathbf{V}_1^S\Sigma_1^S)^H\\
(\Sigma_2)^{-1}(\mathbf{N}^H\mathbf{U}_2^S)^H
\end{array}
\right]\left[\begin{array}{cc} 
(\mathbf{N}^H\mathbf{U}_1^S+\mathbf{V}_1^S\Sigma_1^S)(\Sigma_1)^{-1} &(\mathbf{N}^H\mathbf{U}_2^S)(\Sigma_2)^{-1}
\end{array}\right] \\
&=\left[\begin{array}{c} 
(\Sigma_1)^{-1}((\mathbf{U}_1^S)^H\mathbf{N}+\Sigma_1^S(\mathbf{V}_1^S)^H)\\
(\Sigma_2)^{-1}((\mathbf{U}_2^S)^H\mathbf{N})
\end{array}
\right]\left[\begin{array}{cc} 
(\mathbf{N}^H\mathbf{U}_1^S+\mathbf{V}_1^S\Sigma_1^S)(\Sigma_1)^{-1} &(\mathbf{N}^H\mathbf{U}_2^S)(\Sigma_2)^{-1}
\end{array}\right]\\
&=\left[\begin{array}{cc} 
p_{11} & p_{12}\\
p_{21} & p_{22}
\end{array}
\right]
\end{split}
\end{equation}
where
\begin{equation}
\label{eq:p11}
\begin{split}
p_{11}&=(\Sigma_1)^{-1}((\mathbf{U}_1^S)^H\mathbf{N}+\Sigma_1^S(\mathbf{V}_1^S)^H) (\mathbf{N}^H\mathbf{U}_1^S+\mathbf{V}_1^S\Sigma_1^S)(\Sigma_1)^{-1} \\
& =(\Sigma_1)^{-1}((\mathbf{U}_1^S)^H\mathbf{N}\mathbf{N}^H\mathbf{U}_1^S+
\Sigma_1^S(\mathbf{V}_1^S)^H\mathbf{N}^H\mathbf{U}_1^S+ 
(\mathbf{U}_1^S)^H\mathbf{N}\mathbf{V}_1^S\Sigma_1^S+
\Sigma_1^S(\mathbf{V}_1^S)^H\mathbf{V}_1^S\Sigma_1^S)(\Sigma_1)^{-1}\\
&=(\Sigma_1)^{-1} (\lambda\mathbf{I}+\mathbf{0}+\mathbf{0}+(\Sigma_1^S)^2)(\Sigma_1)^{-1}\\
&=(\Sigma_1)^{-1} (\lambda\mathbf{I}+(\Sigma_1^S)^2)(\Sigma_1)^{-1} \\
&=\mathbf{I}
\end{split}
\end{equation}
when $\Sigma_1=\sqrt{\lambda\mathbf{I}+(\Sigma_1^S)^2}$.
\begin{equation}
\label{eq:p12}
\begin{split}
p_{12}&=(\Sigma_1)^{-1}((\mathbf{U}_1^S)^H\mathbf{N}+\Sigma_1^S(\mathbf{V}_1^S)^H) (\mathbf{N}^H\mathbf{U}_2^S)(\Sigma_2)^{-1} \\
&=(\Sigma_1)^{-1}((\mathbf{U}_1^S)^H\mathbf{N}\mathbf{N}^H\mathbf{U}_2^S + \Sigma_1^S(\mathbf{V}_1^S)^H\mathbf{N}^H\mathbf{U}_2^S  )(\Sigma_2)^{-1} 
\end{split}
\end{equation}
Since $\mathbf{U}^S$ is an orthogonal matrix, then $(\mathbf{U}_1^S)^H\mathbf{U}_2^S=\mathbf{0}$. Since $\mathbf{S}\mathbf{N}^H=\mathbf{0}$, then $\mathbf{U}_1^S\Sigma_1^S(\mathbf{V}_1^S)^H\mathbf{N}^H=\mathbf{0}$, thus $(\mathbf{V}_1^S)^H\mathbf{N}^H=\mathbf{0}$. In the same way, since $\mathbf{NS}^H=\mathbf{0}$,  thus $\mathbf{NV}_1^S=\mathbf{0}$.
Then, 
\begin{equation}
\label{eq:p122}
\begin{split}
p_{12}&=\mathbf{0}. 
\end{split}
\end{equation}
\begin{equation}
\label{eq:p21}
\begin{split}
p_{21}&=(\Sigma_2)^{-1}((\mathbf{U}_2^S)^H\mathbf{N}) (\mathbf{N}^H\mathbf{U}_1^S+\mathbf{V}_1^S\Sigma_1^S)(\Sigma_1)^{-1}\\
&=(\Sigma_2)^{-1}((\mathbf{U}_2^S)^H\mathbf{N})\mathbf{N}^H\mathbf{U}_1^S+(\mathbf{U}_2^S)^H\mathbf{N})\mathbf{V}_1^S\Sigma_1^S)(\Sigma_1)^{-1} \\
&=\mathbf{0}. 
\end{split}
\end{equation}
\begin{equation}
\label{eq:p22}
\begin{split}
p_{22}&=(\Sigma_2)^{-1}((\mathbf{U}_2^S)^H\mathbf{N}) (\mathbf{N}^H\mathbf{U}_2^S)(\Sigma_2)^{-1} \\
&=(\Sigma_2)^{-1}(\lambda\mathbf{I})(\Sigma_2)^{-1}\\
&=\mathbf{I},
\end{split}
\end{equation}
when $\Sigma_2=\sqrt{\lambda\mathbf{I}}$.
Thus, we prove that $\mathbf{P}^H\mathbf{P}=\mathbf{I}$ when $\Sigma_1$ and $\Sigma_2$ are appropriately chosen, and $\mathbf{P}$ is orthonormal.

\newpage
\append{Derivation for equations \ref{eq:S2}, \ref{eq:A} and \ref{eq:B}}
We first reformulate equation \ref{eq:tsvd2} as
\begin{equation}
\label{eq:tsvd22}
\mathbf{S} = \tilde{\mathbf{M}} -\mathbf{U}_1^S(\mathbf{U}_1^S)^H\mathbf{N}.
\end{equation}
Inserting equation \ref{eq:tsvd} into equation \ref{eq:tsvd22}, we can further derive 
\begin{equation}
\label{eq:tsvd222}
\begin{split}
\mathbf{S} = \mathbf{U}_1^M\Sigma_1^M(\mathbf{V}_1^M)^H -\mathbf{U}_1^S(\mathbf{U}_1^S)^H\mathbf{N}.
\end{split}
\end{equation}
Because equations \ref{eq:svdm} and \ref{eq:factorm} are both SVDs of $\mathbf{M}$, we let
\begin{equation}
\label{eq:equal1}
\mathbf{U}_1^S=\mathbf{U}_1^M,
\end{equation}
and
\begin{equation}
\label{eq:equal3}
\Sigma_1=\Sigma_1^M,
\end{equation}
and

\begin{equation}
\label{eq:equal2}
(\mathbf{N}^H\mathbf{U}_1^S+\mathbf{V}_1^S\Sigma_1^S)(\Sigma_1)^{-1}=\mathbf{V}_1^M.
\end{equation}
Considering $\Sigma_1= \Sigma_1^M\mathbf{B}$,
\begin{equation}
\label{eq:Bder}
\mathbf{B}=\mathbf{I}.
\end{equation}
From equation \ref{eq:equal2},

\begin{equation}
\label{eq:Ader0}
\begin{split}
\mathbf{V}_1^S&=(\mathbf{V}_1^M-\mathbf{N}^H\mathbf{U}_1^S(\Sigma_1)^{-1})\Sigma_1(\Sigma_1^S)^{-1}\\
&\approx \mathbf{V}_1^M(\mathbf{I}-(\mathbf{V}_1^M)^{o}\mathbf{N}^H\mathbf{U}_1^S(\Sigma_1)^{-1})\Sigma_1(\Sigma_1^S)^{-1}\\
&=\mathbf{V}_1^M\mathbf{A},
\end{split}
\end{equation}
where $(\mathbf{V}_1^M)^{o}$ satisfies that $\parallel\mathbf{I}-\mathbf{V}_1^M(\mathbf{V}_1^M)^{o} \parallel\rightarrow 0$.

Considering $\mathbf{V}_1^S=\mathbf{V}_1^M\mathbf{A}$,

\begin{equation}
\label{eq:Ader}
\begin{split}
\mathbf{A}&\approx (\mathbf{I}-(\mathbf{V}_1^M)^{o}\mathbf{N}^H\mathbf{U}_1^S(\Sigma_1)^{-1})\Sigma_1(\Sigma_1^S)^{-1}\\
&=(\mathbf{I}-\Gamma)\Sigma_1(\Sigma_1^S)^{-1},
\end{split}
\end{equation}
where \dlo{$\Gamma=(\mathbf{V}_1^M)^H\mathbf{N}^H\mathbf{U}_1^S$}\wen{$\Gamma=(\mathbf{V}_1^M)^{o}\mathbf{N}^H\mathbf{U}_1^S(\Sigma_1)^{-1}$}.

Inserting equations \ref{eq:equal1} and \ref{eq:equal2} into equation \dlo{\ref{eq:tsvd22}}\wen{\ref{eq:tsvd222}}, we can obtain:

\begin{equation}
\label{eq:S22}
\begin{split}
\mathbf{S} &= \mathbf{U}_1^M\Sigma_1^M(\mathbf{V}_1^M)^H - \mathbf{U}_1^S\left(\mathbf{U}_1^S\right)^H\mathbf{N}\\
 &= \mathbf{U}_1^M\Sigma_1^M(\mathbf{V}_1^M)^H - \mathbf{U}_1^M\left(\mathbf{U}_1^S\right)^H\mathbf{N}\\
&=\mathbf{U}_1^M\left[\Sigma_1^M(\mathbf{V}_1^M)^H-  (\mathbf{U}_1^S)^H\mathbf{N}\right]\\
&=\mathbf{U}_1^M\left[\Sigma_1^M(\mathbf{V}_1^M)^H-  (\mathbf{N}^H\mathbf{U}_1^S)^H\right]\\
&=\mathbf{U}_1^M\left[\Sigma_1^M(\mathbf{V}_1^M)^H-  (\mathbf{N}^H\mathbf{U}_1^S+\mathbf{V}_1^S\Sigma_1^S-\mathbf{V}_1^S\Sigma_1^S)^H\right]\\
&=\mathbf{U}_1^M\left[\Sigma_1^M(\mathbf{V}_1^M)^H- (\mathbf{V}_1^M\Sigma_1-\mathbf{V}_1^S\Sigma_1^S)^H\right]\\
&=\mathbf{U}_1^M\left\{\Sigma_1^M(\mathbf{V}_1^M)^H- \left[\Sigma_1(\mathbf{V}_1^M)^H-\Sigma_1^S(\mathbf{V}_1^S)^H\right]\right\}.
\end{split}
\end{equation}

\bibliographystyle{seg}
\bibliography{dmssa}

### 2020-09-16 drr3d/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{Computers \& Geosciences, 95, 59-66, (2016)}

\title{An open-source Matlab code package for improved  rank-reduction 3D  seismic data denoising and reconstruction}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Yangkang Chen\footnotemark[1], Weilin Huang\footnotemark[2], Dong Zhang\footnotemark[2], and Wei Chen\footnotemark[3]}
\address{
\footnotemark[1]Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
Email: ykchen@utexas.edu \\
\footnotemark[2] State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
cup\_hwl@126.com  \&  zhangdongconan@163.com \\
\footnotemark[3]
School of Geophysics and Oil Resource \\
Yangtze University\\
Jingzhou, Hubei Province, China, 434023\\
chenwei2014@yangtzeu.edu.cn 
}

\maketitle
\righthead{Matlab code for MSSA}

\begin{abstract}
Simultaneous seismic data denoising and reconstruction is a currently popular research subject in modern reflection seismology. Traditional rank-reduction based 3D seismic data denoising and reconstruction algorithm will cause strong residual noise in the reconstructed data and thus affect the following processing \new{and interpretation }tasks. In this paper, we propose an improved rank reduction method by \old{slightly} modifying the truncated singular value decomposition (TSVD) formula used in the traditional method. The proposed approach can help us obtain nearly perfect reconstruction performance even in the case of low signal-to-noise ratio (SNR). The proposed \old{improved }algorithm is tested via one synthetic and field data examples. Considering that seismic data interpolation and denoising source packages are seldom in the public domain, we also provide a program template for the rank reduction based simultaneous denoising and reconstruction algorithm by providing an open-source Matlab package. 
\end{abstract}

\section{Keywords}
Open-source Matlab code, rank reduction, 3D seismic data, reconstruction, denoising

\section{Introduction}
Seismic data interpolation plays a fundamental role in seismic data processing, which provides the regularly sampled seismic data for the following workflows like high-resolution processing, wave-equation migration, multiple suppression, amplitude-versus-offset (AVO) or amplitude-versus-azimuth (AVAZ) analysis, and time-lapse studies \cite[]{chiu2014,yangkang2015shape,benfeng2015,shuwei2015seg,zhongwei2016,zhangdong2016}. Three main types of interpolation approaches have been proposed in the literature for handling with the interpolation problem. The first type of approach is based on prediction \cite[]{spitz1991,porsani1999}. A prediction operator is designed from the low-frequency components of seismic data and is applied to high-frequency components. However, the predictive filtering method can only be applied to regularly sampled seismic data. The second type is a transformed domain method \cite[]{candes20061,yangkang20142,shuwei,liuwei2015}, which is based on compressive sensing theory \cite[]{candes20062,donoho2006} to achieve a successful recovery using highly incomplete available data \cite[]{sacchi1998,wang2003,yangkang2014halfthr}.  Compressive sensing (CS) is a relatively new paradigm \cite[]{candes20062,donoho2006,donoho20061,shuwei20164,liuwei20162} in signal processing that has recently received a lot of attention. The theory indicates that the signal which is sparse under some basis may still be recovered even though the number of measurements is insufficient as required by the Shannon's criterion. \cite{mostafa2007} propose a multistep autoregressive strategy which combines the first two types of methods to reconstruct irregular seismic data. The third type is based on the wave equation. This type of method utilizes the inherent constraint of the seismic data from wave equation to interpolate seismic data, thus it depends on the known velocity model, which also becomes its limitation \cite[]{canning1996,fomel2003}. Recently, an increasing number of researchers have developed algorithms connecting the interpolation and deblending \cite[]{berkhout2008} problems for the irregular sampled simultaneous-source data \cite[]{chengbo2013}, which provides new recipes for conventional seismic interpolation problem.

Recently, rank reduction based seismic interpolation algorithms become popular \cite[]{trickett2009,oropezamssa}.  The rank reduction methods for seismic data reconstruction can be divided into two main categories. The first category applies rank reduction to multilevel block Hankel/Toeplitz matrices formed from the entries of the tensor. In other words, multidimensional seismic data are rearranged into a block Hankel or Toeplitz matrix, and a rank reduction algorithm is used to improve the signal-to-noise ratio (SNR) and to reconstruct the data. Such algorithm is usually named as the Cadzow method \cite[]{trickett2009} or multichannel singular spectrum analysis (MSSA) method \cite[]{oropezamssa}.
The other category of rank reduction methods encompasses techniques that are based on dimensionality reduction of multi-linear arrays or tensors. In this case, the multichannel seismic data is viewed as a multi-linear array, and dimensionality reduction techniques are directly applied to the multi-linear array \cite[]{jianjun2015}. For example, \cite{kreimer2012} adopt the high-order singular value decomposition (HOSVD) to solve the 5D seismic data reconstruction problem in the frequency-space domain.

In this paper, we focus on simultaneous reconstruction and denoising of 3D seismic data using the MSSA algorithm. MSSA is a data-driven algorithm developed from research on alternative tools for the analysis of multichannel time series, which is based on the truncated singular value decomposition (TSVD) \cite[]{golub} of the Hankel matrix. MSSA is also an extension of singular spectrum analysis (SSA) \cite[]{vautard}, which is used to analyze 1D time series. Missing traces and random noise increase the rank of the appropriately constructed Hankel matrix that is composed of seismic data at a given frequency slice. To some extent, missing data in each frequency slice performs like random noise at the first iteration of weighted projection onto convex sets (POCS) \new{like framework}. Similar to other simultaneous seismic data reconstruction and denoising approaches, MSSA transforms the noisy data with missing traces into a domain where signal and noise are mapped onto separate subspaces and then removes the noise. Weighted POCS\new{-like} method, which is widely used for seismic data reconstruction and first introduced to the community of seismic exploration by \cite{abmapocs}, is in charge of the reconstruction procedure. Many numerical experiments, however, indicate that the random noise cannot be completely removed using the conventional MSSA algorithm and there still exist some reconstruction errors. The main reasons is that the traditional TSVD can only decompose the data into a noise subspace and a signal-plus-noise subspace. \cite{weilin2016} suggest using damped MSSA (DMSSA) algorithm to better decompose the data into the signal subspace and noise subspace for random noise attenuation. In order to overcome the defect mentioned above, we extend the DMSSA algorithm further to simultaneous reconstruction and denoising of 3D seismic data. We first review the theory of traditional MSSA algorithm, then we introduce the proposed DMSSA based reconstruction and denoising framework. Next, we introduce the main components in the Matlab package and correlate the interior functions with the mathematical symbols in the theory sections. Finally, one synthetic and one field data examples are used to demonstrate the performance using the proposed algorithm and the presented open-source Matlab package. The first synthetic example is reproducible from the provided Matlab package. The field data example is, however, not in the public domain, therefore we do not provide the \emph{segy} file of the field data in the package. But the field data example is just a straightforward application of the Matlab package.

\section{Rank reduction via MSSA}
Consider a block of 3D data $\mathbf{D}_{time}(t,x,y)$ of $N_t$ by $N_x$ by $N_y$ samples $(t=1\cdots N_t,x=1\cdots N_x,y=1\cdots N_y)$. The MSSA \cite[]{oropezamssa} operates on the data in the following way: first, MSSA transforms $\mathbf{D}_{time}(t,x,y)$ into $\mathbf{D}_{freq}(w,x,y)(w=1\cdots N_w)$ of complex values of the frequency domain. Each frequency slice of the data, at a given frequency $w_0$, can be represented by the following matrix:
\begin{equation}
\label{eq:mssa}
\mathbf{D}(w_0)=\left(\begin{array}{cccc}
D(1,1) & D(1,2) & \cdots &D(1,N_x) \\
D(2,1) & D(2,2)  &\cdots &D(2,N_x) \\
\vdots & \vdots &\ddots &\vdots \\
D(N_y,1)&D(N_y,2) &\cdots&D(N_y,N_x)
\end{array}
\right).
\end{equation}

To avoid notational clutter we omit the argument $w_0$. Second, MSSA constructs a Hankel matrix for each row of $\mathbf{D}$; the Hankel matrix $\mathbf{R}_i$ for row $i$ of $\mathbf{D}$ is as follows:
\begin{equation}
\label{eq:data}
\mathbf{R}_i=\left(\begin{array}{cccc}
D(i,1) & D(i,2) & \cdots &D(i,m) \\
D(i,2) & D(i,3)  &\cdots &D(i,m+1) \\
\vdots & \vdots &\ddots &\vdots \\
D(i,N_x-m+1)&D(i,N_x-m+2) &\cdots&D(i,N_x)
\end{array}
\right).
\end{equation}
Then MSSA constructs a block Hankel matrix $\mathbf{M}$ for $\mathbf{R}_i$:
\begin{equation}
\label{eq:hankel2}
\mathbf{M}=\left(\begin{array}{cccc}
\mathbf{R}_1 &\mathbf{R}_2 & \cdots &\mathbf{R}_n \\
\mathbf{R}_2 &\mathbf{R}_3 &\cdots &\mathbf{R}_{n+1} \\
\vdots & \vdots &\ddots &\vdots \\
\mathbf{R}_{N_y-n+1}&\mathbf{R}_{N_y-n+2} &\cdots&\mathbf{R}_{N_y}
\end{array}
\right).
\end{equation}
The size of $\mathbf{M}$ is $I\times J$, $I=(N_x-m+1)(N_y-n+1)$, $J=mn$. $m$ and $n$ are predifined integers chosen such that the block Hankel matrices $\mathbf{R}_i$ and $\mathbf{M}$ are close to square matrices. The transformation of the data matrix into a block Hankel matrix can be represented in operator notation as follows:
\begin{equation}
\label{eq:hankelopt}
\mathbf{M}=\mathcal{H}\mathbf{D},
\end{equation}
where $\mathcal{H}$ denotes the Hankelization operator.

In general, the block Hankel matrix $\mathbf{M}$ can be represented as:
\begin{equation}
\label{eq:M}
\mathbf{M}=\mathbf{S}+\mathbf{N},
\end{equation}
where $\mathbf{S}$ and $\mathbf{N}$ denote the block Hankel matrix of signal and of random noise, respectively.
%\emph{Here, missing signal can be regarded as a condition where signal and noise are summed to zero only for the first iteration of reconstruction process. After the first iteration, there are no missing data.}

We assume that $\mathbf{M}$ and $\mathbf{N}$ have full rank, $rank(\mathbf{M})$=$rank(\mathbf{N})=J$ and $\mathbf{S}$ has deficient rank, $rank(\mathbf{S})=N<J$. The singular value decomposition (SVD) of $\mathbf{M}$ can be represented as:
\begin{equation}
\label{eq:svdm}
\mathbf{M} = [\mathbf{U}_1^M\quad \mathbf{U}_2^M]\left[\begin{array}{cc} 
\Sigma_1^M & \mathbf{0}\\
\mathbf{0} & \Sigma_2^M
\end{array}
\right]\left[\begin{array}{c} 
(\mathbf{V}_1^M)^H\\
(\mathbf{V}_2^M)^H
\end{array}
\right],
\end{equation}
where $\Sigma_1^M$ ($N\times N$) and $\Sigma_2^M$ ($(I-N)\times(J-N)$) are diagonal matrices and contain, respectively, larger singular values and smaller singular values. $\mathbf{U}_1^M$ ($I\times N$), $\mathbf{U}_2^M$ ($I\times (I-N)$), $\mathbf{V}_1^M$ ($J\times N$) and $\mathbf{V}_2^M$ ($J\times (J-N)$) denote the associated matrices with singular vectors. The symbol $[\cdot]^H$ denotes the conjugate transpose of a matrix. In general the signal is more energy-concentrated and correlative than the random noise.  Thus, the larger singular values and their associated singular vectors represent the signal, while the smaller values and their associated singular vectors represent the random noise. We let $\Sigma_2^M$ be $\mathbf{0}$ to achieve the goal of attenuating random noise while recovering the missing data during the first iteration in reconstruction process as follows:
\begin{equation}
\label{eq:tsvd}
\tilde{\mathbf{M}} = \mathbf{U}_1^M\Sigma_1^M(\mathbf{V}_1^M)^H.
\end{equation}
Equation \ref{eq:tsvd} is referred to as the TSVD, which is used in the conventional MSSA approach.

\section{3D seismic data reconstruction via DMSSA}

Nevertheless, $\tilde{\mathbf{M}}$ is actually still contaminated  with residual random noise. \cite{weilin2016} suggest using damped MSSA (DMSSA) algorithm to attenuate the residual random noise that the conventional MSSA fails to. Here, we further extend the DMSSA algorithm to simultaneous reconstruction and denoising of 3D seismic data. Since the missing data at each frequency slice can be regarded as the random noise, the derivation are similar with \cite{weilin2016} except for the extra reconstruction process based on the weighted POCS\new{-like} method. Therefore, we conclude the approximation of $\mathbf{S}$ as:
\begin{align}
\label{eq:S4}
\mathbf{S} & = \mathbf{U}_1^M \Sigma_1^M\mathbf{T}(\mathbf{V}_1^M)^H,\\
\label{eq:T2}
\mathbf{T} & =\mathbf{I}-(\Sigma_1^M)^{-K}\hat{\delta}^K.
\end{align} 
where $\hat{\delta}$ denotes the maximum element of $\Sigma_2^M$ and $K$ denotes the damping factor. It is worth mentioning that the greater the $K$ is, the weaker the damping is, and equation \ref{eq:S4} degrades to equation \ref{eq:tsvd} when $K\rightarrow +\infty$.

The revised TSVD for DMSSA algorithm can be represented in operator notation as follows:
\begin{equation}
\label{eq:rankrdopt}
\mathbf{S}=\mathcal{R}_d\mathbf{M}
\end{equation}
where we use $\mathcal{R}_d$ as the rank reduction operator for DMSSA while $\mathcal{R}$ is used for conventional MSSA.

The filtered data is recovered with random noise attenuated and missing traces reconstructed by properly averaging along the anti-diagonals of the low-rank matrix $\mathbf{S}$ obtained via revised TSVD in DMSSA:\\ 
\begin{equation}
\label{eq:dmssaopt}
\hat{\mathbf{D}}=\mathcal{A}\mathbf{S}=\mathcal{A}\mathcal{R}_d\mathbf{M}=\mathcal{A}\mathcal{R}_d\mathcal{H}\mathbf{D}=\mathcal{F}_d\mathbf{D}
\end{equation}
$\mathcal{A}$ denotes the averaging operator. And the operator $\mathcal{F}_d$ represents DMSSA filter. If $\mathcal{R}_d$ is changed by the traditional TSVD rank reduction operator $\mathcal{R}$, $\mathcal{F}$ can represent conventional MSSA filter similarly:
\begin{equation}
\label{eq:F}
\mathcal{F}=\mathcal{A}\mathcal{R}\mathcal{H}.
\end{equation}

In this paper, we pay our attention to the reconstruction of noisy data, \new{more specifically, those noisy data with very low SNR}. \old{Therefore, the modified weighted POCS\new{-like} algorithm  is as follows:}\new{Here, we recall the traditional weighted POCS-like algorithm \cite[]{oropezamssa} as follows:}
\begin{equation}
\label{eq:mssapocs}
\mathbf{D}_n=a_n \mathbf{D}_{obs} + (1-a_n\mathcal{S})\circ \mathcal{F}\mathbf{D}_{n-1},\qquad n=1,2,3,\cdots,n_{max}
\end{equation}

\old{Revised}\new{Substituting the MSSA filter $\mathcal{F}$ with} \old{by} the DMSSA filter $\mathcal{F}_d$, \old{therefore} the \old{extended}\new{improved} DMSSA algorithm for simultaneous seismic data reconstruction and denoising can be formulated as follows:
\begin{equation}
\label{eq:dmssapocs}
\mathbf{D}_n=a_n \mathbf{D}_{obs} + (1-a_n\mathcal{S})\circ \mathcal{F}_d\mathbf{D}_{n-1},\qquad n=1,2,3,\cdots,n_{max}
\end{equation}
where $\mathbf{D}_0=\mathbf{D}_{obs}$. $a_n$ is an iteration-dependent scalar that linearly decreases from $a_1=1$ to $a_{n_{max}}=0$. $\mathcal{S}$ denotes the sampling factor. $\mathcal{S}$ equals 1 at the observation point while 0 at the missing traces. $\circ$ denotes the Hadamard product (entry-wise product) of two same size matrices. The algorithm stops when either a maximum number of iterations $n_{max}$ is reached or $\Arrowvert \mathbf{D}_n - \mathbf{D}_{n-1}\Arrowvert_F^2 \leq \epsilon$.

\new{The MSSA based approach is based on the assumption that seismic data is of low rank at each frequency slice in the frequency-space domain. Since seismic data are locally composed of plane-wave components, it intuitively satisfies such assumption. According to our experience, when the SNR is relatively high, in other words with less noise, the performance of MSSA and DMSSA based approaches is similar to each other. However, when the SNR is very low, the proposed DMSSA based approach will outperform the MSSA based approach a lot.}

\section{Code description}
There are two testing Matlab scripts and four main subroutines and three related subroutines that are required by the Matlab scripts in the Matlab package.

\begin{enumerate}
\item \texttt{test\_dmssa\_denoise.m} This script is used to run the denoising demonstration using the synthetic 3D seismic data. It is based on the algorithm described in \cite{weilin2016}.
\item \texttt{test\_dmssa\_recon.m} This script is used to run the simultaneous denoising and reconstruction of the incomplete and noisy synthetic 3D seismic data. It will generate all the required binary files for Figures 1,3,4. For quick look at the performance, some 2D image comparisons will also be generated automatically.
\end{enumerate}

The main source subroutines are listed below. All the input and output parameters are clearly annotated in the subroutines.

\begin{enumerate}
\item \texttt{fxymssa.m} This code is used for MSSA based denoising for 2D/3D seismic data.

\item \texttt{fxydmssa.m} This code is used for DMSSA based denoising for 2D/3D seismic data.

\item \texttt{fxymssa\_recon.m} This code is used for MSSA based simultaneous denoising and reconstruction for 2D/3D seismic data.

\item \texttt{fxydmssa\_recon.m} This code is used for DMSSA based simultaneous denoising and reconstruction for 2D/3D seismic data.
\end{enumerate}

The other source subroutines are listed below.
\begin{enumerate}
\item \texttt{genmask.m} This code is used for generating the random mask sampling operator \cite[]{yangkang2015shape} for the reconstruction test.

\item \texttt{rperm.m} This code is used for permutating the seismic traces randomly.

\item \texttt{snrcyk.m} This code is used to numerically measure the signal-to-noise ratio (SNR) of the reconstructed and denoised data based on the criteria introduced in \cite{yangkang2015ortho}.
\end{enumerate}

There are five different functions in the main subroutines
\begin{enumerate}
\item \texttt{P\_H()} This function corresponds to the Hankelization operator $\mathcal{H}$ in equations \ref{eq:dmssaopt} and \ref{eq:F}. 
\item \texttt{P\_R()} This function corresponds to the rank reduction operator $\mathcal{R}$ in equation \ref{eq:F}.
\item \texttt{P\_RD()} This function corresponds to the damped rank reduction operator $\mathcal{R}_d$ in equation \ref{eq:dmssaopt}.
\item \texttt{P\_A()} This function corresponds to the averaging operator $\mathcal{A}$ in equations \ref{eq:dmssaopt} and \ref{eq:F}.
\item \texttt{ave\_antid()} This function applies averaging along the anti-diagonals of an input matrix.
\end{enumerate}

The only difference between the traditional MSSA program and the proposed DMSSA program is the rank reduction operator. For a better comparison, we copy the interior functions \texttt{P\_R()} and \texttt{P\_RD()} as follows:
\begin{itemize}
\item \texttt{P\_R()} \\
\texttt{function} $[dout]$=\texttt{P\_R}$(din,N)$\\
$[U,D,V]$=\texttt{svd}$(din)$;\\
$dout=U(:,1:N)*D(1:N,1:N)*(V(:,1:N)')$;\\
\texttt{return}

\item \texttt{P\_RD()}\\
\texttt{function} $[dout]$=\texttt{P\_RD}$(din,N,K)$ \\
    $[U,D,V]$=\texttt{svd}$(din)$;\\
    \texttt{for} $j=1:N$\\
        $D(j,j)=D(j,j)*(1-D(N+1,N+1)^K/D(j,j)^K)$;\\
    \texttt{end}        \\
    $dout=U(:,1:N)*D(1:N,1:N)*(V(:,1:N)')$;\\
\texttt{return}
\end{itemize}
The second to fourth lines in \texttt{P\_RD()} correspond to applying the damping operator expressed in \ref{eq:T2}. It is worth mentioning that for truncated singular value decomposition, it is faster to use the Matlab function \texttt{svds()} instead 
of \texttt{svd()} when the size of the input matrix is large. However, \texttt{svd()} is faster than \texttt{svds()} when data size is small. Readers are encouraged to adjust such trivial modification according to specific tasks.

There is also a Python script called SConstruct. It is used for generating the final 2D/3D figures used in the paper. It should be run in the Madagascar software platform \cite[]{mada2013}, which is an open-source geophysical processing software package, which is available for download at $www.ahay.org$.

\section{Examples}
We use one synthetic example and one field data example to demonstrate the performances of the traditional and the improved MSSA algorithms from the Matlab package. 
The first synthetic example is shown in Figures \ref{fig:synth-clean,synth-noisy,synth-obs,synth-mssa,synth-dmssa2}, \ref{fig:synth-dmssa1,synth-dmssa}, \ref{fig:synth-s-clean,synth-s-noisy,synth-s-obs,synth-s-mssa,synth-s-dmssa2}, and \ref{fig:synth-s-clean-i,synth-s-noisy-i,synth-s-obs-i,synth-s-mssa-i,synth-s-dmssa2-i}. Since this example is a synthetic example, we have the clean dataset in Figure \ref{fig:synth-clean}. We add some bandlimited random noise to the clean data to simulate the noisy data, as shown in Figure \ref{fig:synth-noisy}. We then randomly remove 50\% traces from the noisy synthetic data, and obtain the simulated observed noisy data, as shown in Figure \ref{fig:synth-obs}. Figures \ref{fig:synth-mssa} and \ref{fig:synth-dmssa2} show the reconstructed and denoised data using the traditional MSSA and the proposed modified MSSA algorithms. It is obvious that the proposed approach can obtain a very accurate recovery (Figure \ref{fig:synth-dmssa2}) compared with the true clean data shown in Figure \ref{fig:synth-clean}. However, the traditional MSSA approach still causes some noticeable residual noise. Note that in Figure \ref{fig:synth-dmssa2}, we use $N=3,K=2$. We also show the reconstructed and denoised data using $K=1$ and $K=3$ in Figure \ref{fig:synth-dmssa1} and \ref{fig:synth-dmssa}, respectively. It is obvious that when $K=1$, as shown in Figure \ref{fig:synth-dmssa1}, the proposed algorithm causes too much damages to the useful signals. When $K=3$, as shown in Figure \ref{fig:synth-dmssa}, there is a bit more residual noise left in the data compared with that when $K=2$. Figure \ref{fig:synth-s-clean,synth-s-noisy,synth-s-obs,synth-s-mssa,synth-s-dmssa2} shows the comparison of 5th crossline section for all the figures in Figure \ref{fig:synth-clean,synth-noisy,synth-obs,synth-mssa,synth-dmssa2}.  Figure \ref{fig:synth-s-clean-i,synth-s-noisy-i,synth-s-obs-i,synth-s-mssa-i,synth-s-dmssa2-i} shows the comparison of 5th inline section for all the figures in Figure \ref{fig:synth-clean,synth-noisy,synth-obs,synth-mssa,synth-dmssa2}. From both Figures \ref{fig:synth-s-clean,synth-s-noisy,synth-s-obs,synth-s-mssa,synth-s-dmssa2} and \ref{fig:synth-s-clean-i,synth-s-noisy-i,synth-s-obs-i,synth-s-mssa-i,synth-s-dmssa2-i} we can confirm that the proposed improved MSSA algorithm can obtain a much better reconstruction and denoising performance than the traditional MSSA algorithm.

The field data example is shown in Figure \ref{fig:field-obs,field-mssa,field-dmssa,field-s-obs,field-s-mssa,field-s-dmssa}. In this example, we do not know the true answer and thus we can not judge the reconstruction and denoising performance by comparing the final results with the true model as used in the synthetic example. Instead, we can only judge the performance by the spatial coherency of the reconstructed data. Figure \ref{fig:field-obs} shows the observed noisy and incomplete data, which has been binned to regular grids. There are about 50\% missing traces in this example. Figures \ref{fig:field-mssa} and \ref{fig:field-dmssa} show the final results using the traditional and proposed improved MSSA algorithms. Figures \ref{fig:field-s-obs}, \ref{fig:field-s-mssa}, and \ref{fig:field-s-dmssa} show the 4th crossline slices of Figures \ref{fig:field-obs}, \ref{fig:field-mssa}, and \ref{fig:field-dmssa}, respectively. It can be seen that both methods can effectively reconstruct the missing data and attenuate the strong random noise, but the proposed improved MSSA algorithm can obtain even better performance since the events are more spatially coherent. \new{It is worth mentioning that since there is no true answer for the field data example, it is hard to use quantitive measure to compare the performance of different approaches. The visual observation on the spatial coherency, instead, is the most effective and straightforward way.}

Both examples are processed using the introduced Matlab packages. The binary files output from the Matlab packages are then put into the Madagascar platform to generate the final figures shown in Figures 1-5.

\inputdir{synth}
\multiplot{5}{synth-clean,synth-noisy,synth-obs,synth-mssa,synth-dmssa2}{width=0.29\textwidth}{(a) Clean data. (b) Noisy data. (c) Observed data with 50\% missing traces. (d) Denoised and reconstructed using the MSSA method. (e) Denoised and reconstructed using the proposed approach ($K=2$).}
\multiplot{2}{synth-dmssa1,synth-dmssa}{width=0.29\textwidth}{ (a) Denoised and reconstructed data using the proposed approach when $K=3$. (b) Denoised and reconstructed data using the proposed approach when $K=1$.}

\multiplot{5}{synth-s-clean,synth-s-noisy,synth-s-obs,synth-s-mssa,synth-s-dmssa2}{width=0.29\textwidth}{Single slice comparison (5th crossline section). (a) Clean data. (b) Noisy data. (c) Observed data with 50\% missing traces. (d) Denoised and reconstructed using the MSSA method. (e) Denoised and reconstructed data using the proposed approach ($K=2$). }

\multiplot{5}{synth-s-clean-i,synth-s-noisy-i,synth-s-obs-i,synth-s-mssa-i,synth-s-dmssa2-i}{width=0.29\textwidth}{Single slice comparison (5th inline section). (a) Clean data. (b) Noisy data. (c) Observed data with 50\% missing traces. (d) Denoised and reconstructed using the MSSA method. (e) Denoised and reconstructed using the proposed approach ($K=2$). }

\inputdir{field}
\multiplot{6}{field-obs,field-mssa,field-dmssa,field-s-obs,field-s-mssa,field-s-dmssa}{width=0.29\textwidth}{(a) Observed field data (binned to the regular grid). (b) Reconstructed data using the MSSA method. (c) Reconstructed data using the DMSSA method. (d) 4th crossline slice of the observed data. (e) 4th crossline slice of the MSSA reconstructed data. (f) 4th crossline slice of the reconstructed data using the proposed approach.  }

\section{Conclusions}
We have proposed an improved rank-reduction method by slightly modifying the truncated singular value decomposition (TSVD) formula used in the traditional method. The resulted new rank reduction method can obtain a significantly cleaner 3D data recovery result compared with the traditional method based on one synthetic and one field data examples. We have described how we write the Matlab code for traditional multichannel singular spectrum analysis (MSSA) method, \new{and }how we make the slight modification to the MSSA code in order to tremendously improve the performance. This Matlab code package can be used in research and industrial applications for effectively and efficiently reconstructing the missing seismic traces due to different reasons.

\section{Acknowledgements}
We would like to thank Ming Zhang, Zhaoyu Jin, Shaohuan Zu, Shuwei Gan for constructive suggestions and fruitful discussions that improve the manuscript and Matlab codes greatly. This work is partially supported by Texas Consortium for Computational Seismology (TCCS) and the National Basic Research Program of China (grant NO: 2013 CB228602) \new{and Sinopec Key Laboratory of Geophysics (Grant No. 33550006-15-FW2099-0017)}.

\bibliographystyle{seg}
\bibliography{dmssa}

### 2020-09-16 enhemd/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{Journal of Applied Geophysics, 119, 99-105, (2015)}

\title{Enhancing seismic reflections using empirical mode decomposition in the flattened domain}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Yangkang Chen\footnotemark[1], Guoyin Zhang\footnotemark[2], Shuwei Gan\footnotemark[2], and Chenglin Zhang\footnotemark[3]}
\address{
\footnotemark[1]Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
Email: ykchen@utexas.edu

\footnotemark[2] State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
guoyinzh@126.com
%guoyinzh@126.com  
%ziyouqishi\_2014@163.com

\footnotemark[3] Exploration and Development Institute of Southwest Oil \& Gasfield Company, \\
 PetroChina oil Company \\
  Jianshe North Road (Section 1), No. 83,
Chengdu, China, 610041 \\
zclcup@163.com \\

\footnotemark[4] School of Electronic and Information Engineering \\
Hebei University of Technology \\
Xiping Road No. 5340, Beichen District \\
Tianjin, China, 300401\\
zyt@hebut.edu.cn
}
\lefthead{Chen et al.}
\righthead{EMD in the flattened domain}

\maketitle

\begin{abstract}
Due to different reasons, the seismic reflections are not continuous even when no faults or \new{no} discontinuities exist. We propose a novel approach for enhancing the amplitude of seismic reflections and mak\old{e}\new{ing} \new{the} seismic reflections continuous. We use plane\new{-}wave flattening \new{technique} to provide \old{highly} horizontal events for the following empirical mode decomposition (EMD) based smoothing in the flattened domain. \old{An}\new{The} inverse plane\new{-}wave flattening can be used to obtain original curved events. The plane\new{-}wave flattening process requires a precise local slope estimation, which \old{was}\new{is} provided by the plane-wave destruction (PWD) algorithm. The EMD based smoothing filter is a non-parametric and adaptive filter, thus can be conveniently used. Both pre-stack and post-stack field data examples show tremendous improvement for the data quality, which \old{is especially interpretation friendly} \new{makes the following interpretation easier and more reliable}.  
\end{abstract}

\section{Keywords}
Empirical mode decomposition, smoothing, plane\new{-}wave flattening, flattened domain

\section{Introduction}
Modern exploration for hydrocarbon requires more advanced techniques for each steps of seismic acquisition, processing, and interpretation \cite[]{yangkang20142,qushan2015}. The key step that connects geophysics and geology is interpretation. A clean pre-stack dataset can aid AVO-related inversion. A clean post-migrated image will help geologists make right decisions and reduce the interpretation risks \cite[]{yangkang20141,zhiguang2014,yangkang2015image,wencheng2015stack}. Due to different reasons, e.g. unpredictable noise or sampling issues, the raw seismic data might not be clean or coherent enough.

To solve this problem, we can not use \old{a}\new{the} traditional random noise attenuation \old{technique}\new{techniques} to make the seismic reflections coherent, because \old{this type of }discontinuous noise is not randomly spreaded across the whole profile. \old{Using a}\new{The} traditional random noise attenuation technique\old{s} \cite[]{wencheng2015asa,yangkang2015}, such as the $f-x$ deconvolution \cite[]{canales1984}, $f-x$ singular spectrum analysis \cite[]{mssa}, Karhunen-loeve (KL) or singular value decomposition (SVD) filtering \cite[]{jones1987}, will harm much of the useful reflections. The discontinuous problem of some seismic dataset can be solved using a smoothing operator. A mean filter is usually used to smooth the seismic reflections instead of solely removing random noise. However, mean filter requires \old{a} exactly flattened reflections, otherwise much \new{of the} useful reflections will be lost. In addition, the parameters setting when utilizing the mean filter requires some effort in practice.  \cite{hale2011} proposed a bilateral filtering approach for improving the smoothness and coherency along the local structure of seismic data. Considering the damages to useful energy in many smoothing and denoising algorithms, \new{\cite{yangkang2014simi,yangkang2015ortho}} proposed a signal-compensation approach for reducing the damages to useful reflections during the initial denoising processing.

In this paper, we propose a novel approach for enhancing seismic signal either in pre-stack dataset or in post-stack (-migrated) image. The novel approach utilizes the \old{excellent}\new{good} smoothing ability of the empirical mode decomposition (EMD) based denoising approaches. Instead of using EMD to remove random noise \cite[]{yangkang2014emdsum}, here we only use EMD to enhance seismic reflections and to make seismic events more coherent. Because those EMD based denoising approaches are best used in horizontal reflections, a plane\new{-}wave flattening process is \old{applied}\new{implemented} before the traditional EMD based approach. Even though, the EMD based filtering approach does not require exactly flattened events. Unlike 1D mean and median filters, EMD based filtering can also preserve useful reflections with small dip angle. What is even more attractive is that EMD based denoising approach is \old{very} adaptive. The only parameter we need to define is the number of dip components. Considering that, in practice, we commonly choose to remove the first EMD component in order to remove the highest oscillating components, the EMD based filtering is non-parametric. Because of the adaptivity and the superior performance of the EMD based smoothing in field seismic data processing, more and more researchers are turning to use this techinique as a blind-processing tool in order to deal with the rapidly increasing data size in modern seismic data processing \new{\cite[]{jiajun2015eemd,shuwei20152}}. We use both pre-stack common midpoint (CMP) gather and post-stack image to demonstrate the performance of the proposed approach\old{es}. Results show that the amplitude and the coherency of seismic reflections can be tremendously enhanced.

\section{Method}
%For every frequency, 
The proposed processing workflow can be briefly summarized as: 1) Apply forward plane\new{-}wave flattening to the raw dataset. 2) Apply EMD filtering in $f-x$ domain. 3) Apply inverse plane\new{-}wave flattening to obtain curved seismic reflections.
In the following contexts, we \new{will} give some details about both EMD based smoothing and plane\new{-}wave flattening\old{ in the following contexts}.
\subsection{Smoothing by empirical mode decomposition}
Empirical mode decomposition (EMD) is used to empirically decompose a non-stationary signal into a finite set of subsignals, which are termed \new{as} intrinsic mode functions (IMF) and are considered to be \new{locally} \old{stable}\new{stationary}. The IMFs satisfy two conditions: (1) in the whole data set, the number of extrema and the number of zero crossings must either equal or differ at most by one; and (2) at any point, the mean value of the envelope defined by the local maxima and the envelope defined by the local minima is zero \cite[]{emd}. 
Let $s(t)$, $c_n(t)$, $r(t)$ and $N$ denote the original non-stationary signal, the separated IMF, the residual and the number of IMFs, respectively. The EMD can be expressed as:
\begin{equation}
\label{eq:emd}
s(t)=\sum_{n=1}^{N}c_n(t)+r(t).
\end{equation}
For a non-stationary signal $s(t)$, using equation \ref{eq:emd}, we get a finite set of subsignals $c_n(t)$,($n=1,2,\cdots,N$).

We can straightforwardly use the EMD to denoise each seismic trace because of the special frequency-decreasing property of IMF. IMFs represent\old{s} different oscillations embedded in the data, and the oscillating frequency for each subsignal $c_n(t)$ decreases as the sequence number of IMF \old{become}\new{gets} larger. This property results from the sifting algorithm to implement the decomposition. The sifting process can be summarized as a process in which low-frequency component is gradually removed out to generate a more local-constant-frequency mode, which is followed by generating the next mode.

\cite{yangkang2014emdsum} provided an overall introduction of the applications of EMD in random noise attenuation of seismic data. According to \cite{yangkang2014emdsum}, EMD can be used to denoise each 1-D signal from the 2-D seismic profile in time-space ($t$-$x$) domain either along the time direction or space direction. However, because of the mode-mixing problem, $t$-$x$ domain EMD along the time direction will cause some damage to useful seismic signal. A better way \new{utilize EMD to remove noise} is to apply EMD along the space direction and to remove the highly oscillating components. The frequency-space ($f$-$x$) domain EMD can help to obtain faster implementation and even better performances. 
%The EMD based smoothing method was proposed by \cite{bekara} as:
%\begin{enumerate}
%\item 
%Transform the data to the $f-x$ domain.
%\item 
%For every frequency, 
%\begin{enumerate}
%\item
%separate real and imaginary parts in the spatial sequence,
%\item
%compute IMF1, for the real signal and subtract it to obtain the filtered real signal,
%\item
%repeat for the imaginary part,
%\item
%combine to create the filtered complex signal.
%\end{enumerate}
%\item
%Transform data back to the $t-x$ domain.
%\end{enumerate}
$f-x$ EMD refers to applying EMD on
each frequency slice in the $f-x$ domain, and remov\old{e}\new{ing} the first IMF,
which mainly represent the high\old{er}\new{est} wavenumber components. The methodology can be summarized as \cite[]{yangkang2015}:
\begin{equation}
\label{eq:fxemd}
\begin{split}
\hat{s}(m,t) &= \mathcal{F}^{-1}\left(\sum_{n=2}^{N}C_n(m,w)\right), \\
\mathcal{F} d(m,t)  &= \sum_{n=1}^{N} C_n(m,w),
\end{split}
\end{equation}
where $\hat{s}(m,t)$ and $d(m,t)$ denote the estimated signal and observed noisy signal, respectively. $\mathcal{F}$ and $\mathcal{F}^{-1}$ denote the forward and inverse Fourier transforms along the time axis, respectively. $C_n$ denotes the $n$th EMD decomposed component. $w$ denotes frequency. In order to \old{maximize}\new{optimize} the effectiveness, the seismic events should \new{better} be flattened first.

It is worth to be mentioned here that the $f-x$ EMD does not require exactly flattened events. Unlike 1D mean and median filters, $f-x$ EMD can also preserve useful reflections with small dip angle. Compared with Karhunen-loeve (KL) or singular value decomposition (SVD) filtering, the $f-x$ EMD can be much more adaptive, because the horizontal events mainly lay in the first 1-3 IMFs after EMD in the $f-x$ domain, however, the number of singular values corresponding to the useful horizontal reflections for KL or SVD transforms have a large range and thus is not convenient to chose. The performance for preserving horizontal events of $f-x$ EMD is also much better than that of KL or SVD transforms \cite[]{yangkang2015}.

\subsection{plane\new{-}wave flattening}
Considering that the local plane wave can be described as the following differential equation: 
\begin{equation}
\label{eq:plane}
\frac{\partial u}{\partial x}+\sigma\frac{\partial u}{\partial t} = 0,
\end{equation}
where $\sigma$ is the local slope in continuous space, and $u$ denotes the wavefield. In the case of the constant local slope, equation \ref{eq:plane} has the following solution:
\begin{equation}
\label{eq:planesolu}
P(t,x) = f(t-\sigma),
\end{equation}
\new{where} $f$ is the waveform function. In order to flatten a seismic section, we need to first select a reference trace\old{. Then}\new{, and then} we flatten the whole profile by predicting each trace from the reference trace, following the local slope. Predicting trace $k$ from trace $r$ (reference trace) is simply:
\begin{equation}
\label{eq:pre}
\mathbf{P}_{r,k} = \mathbf{P}_{r,r+1}\cdots\mathbf{P}_{k-2,k-1}\mathbf{P}_{k-1,k}.
\end{equation}
The above recursive operator $\mathbf{P}_{r,k}$ is called predictive paining \cite[]{fomel2010painting}.
Each $\mathbf{P}_{i,j}$ denotes the prediction operator following the local slope $\sigma$.

%\subsection{plane\new{-}wave destruction}
The local slope can be obtained by solving the following equation:
\begin{equation}
\label{eq:pwd}
\mathbf{D}(\sigma)\mathbf{S} = \mathbf{0},
\end{equation}
where \old{$\mathbf{s}$}\new{$\mathbf{S}$} is the seismic section, $\mathbf{S}=[\mathbf{s}_1\quad\mathbf{s}_2\cdots\mathbf{s}_N]^T$, $\mathbf{s}_i$ denotes $i$th trace, $[\cdot]^T$ denotes the transpose of the input matrix,  and $\mathbf{D}$ is called plane\new{-}wave destruction (PWD) operator \cite[]{fomel2002pwd}, which has the following form:
\begin{equation}
  \label{eq:d}
  \mathbf{D}(\sigma) = 
  \left[\begin{array}{ccccc}
      \mathbf{I} & 0 & 0 & \cdots & 0 \\
      - \mathbf{P}_{1,2} & \mathbf{I} & 0 & \cdots & 0 \\
      0 & - \mathbf{P}_{2,3} & \mathbf{I} & \cdots & 0 \\
      \cdots & \cdots & \cdots & \cdots & \cdots \\
      0 & 0 & \cdots & - \mathbf{P}_{N-1,N} & \mathbf{I} \\
    \end{array}\right]\;.
\end{equation}
Equation \ref{eq:pwd} can be solved by iterative inversion using shaping regularization with a local smoothness constraint \cite[]{fomel2007shape}. \cite{shuwei2015} used a similar methodology to provide a flattened domain for attenuating random noise using truncated singular value decomposition.

Figure \ref{fig:sigmoid,sdip,sflat,flat-rec} shows a simple demonstration of the plane-wave flattening process. Figure \ref{fig:sigmoid} \old{is}\new{shows} a synthetic data, with dipping reflector, curved events, and faults in the profile. Figure \ref{fig:sdip} shows the corresponding local slope estimation using the PWD algorithm. Figure \ref{fig:sflat} shows the flattened domain of the synthetic data using the plane-wave flattening algorithm. The reference trace is selected as the 30th trace in the section, as highlighted by the blue line in Figures \ref{fig:sigmoid}, \ref{fig:sflat} and \ref{fig:flat-rec}. Figure \ref{fig:flat-rec} shows the reconstructed synthetic data using the inverse plane-wave flattening process.

\inputdir{sigmoid}
\multiplot{4}{sigmoid,sdip,sflat,flat-rec}{width=0.45\columnwidth}{\new{Demonstration of the plane\new{-}wave flattening algorithm.}(a) Synthetic example. (b) Local slope estimation. (c) Flattened domain. (d) Reconstructed data.}

%\subsection{Signal enhancing workflow}

\section{Field data examples}
The first example is a pre-stack CMP gather, as shown in Figure \ref{fig:gath0}. In order to apply the EMD based smoother, we first use plane\new{-}wave flattening \new{algorithm} to flatten the original CMP gather. The local slope used in the plane-wave flattening algorithm is \old{provided}\new{shown} in Figure \ref{fig:dip}. The flattened gather is shown in Figure \ref{fig:flat}. We can see some incoherence and some random noise appearing in the flattened gather. However, after applying EMD in the $f-x$ domain, we obtain a quite smooth gather, as shown in Figure \ref{fig:flat-emd}\old{,}\new{.} \old{a}\new{A}fter using \new{the} inverse plane\new{-}wave flattening \new{algorithm}, we \new{can} obtain the filtered data (Figure \ref{fig:flat-emd-rec0}). Figure \ref{fig:dif} shows the difference section between Figures \ref{fig:gath0} and \ref{fig:flat-emd-rec0}.  We can see a tremendous improvement from the zoomed sections, corresponding to the frame boxes A and B, in Figures \ref{fig:zooma-1,zooma-2} and \ref{fig:zoomb-1,zoomb-2}. The seismic reflections after signal enhancing are obviously much more coherent than the original data. The reference trace for flattening \new{in this example} is chosen as the middle trace of the section.

The second example is a post-stack section, as shown in Figure \ref{fig:post-gath0}. This data set has much more curved events than the first example. However, by using \new{the} plane\new{-}wave flattening \new{algorithm}, we can still get a well-fattened section that is suitable for applying an EMD based smoothing operator. The reflection-enhanced data is shown in Figure \ref{fig:post-emd-rec0}. Figure \ref{fig:post-dif} shows the difference section \new{before and after the smoothing}. We also zoom two parts from the original section and filtered section, and show them in Figure \ref{fig:post-zooma-1,post-zooma-2,post-zoomb-1,post-zoomb-2}. The comparison \new{also} \old{obviously} shows that the proposed seismic reflection enhancing process can help obtain much more continuous event\new{s}.

\section{Conclusions}
In this paper, we proposed a seismic reflection enhancing approach using \new{the} empirical mode decomposition \new{(EMD)} in the flattened domain. We use the plane\new{-}wave flattening algorithm to flatten the seismic data by predicting different traces from one reference trace.  The proposed approach is not intended to attenuate random noise, instead, it is used to enhance seismic reflections in order to make the events more continuous and thus easier for interpretation. The EMD based \old{filtering}\new{smoothing} is non-parametric and adaptive to different dataset, thus can be conveniently used in practice. Both pre-stack and post-stack examples show that the proposed approaches can successfully enhance the useful signals and make the seismic reflections more continuous.

\section{Acknowledgements}
We would like to thank the chief editor Jyoti Behura\new{, Ryan Swindeman, Jitao Ma, Tingting Liu, Karl Schleicher, Josef Paffenholz} and two anonymous reviewers for \new{helpful discussions and} constructive suggestions that improve the grammar and configuration of the paper a lot\old{, Tingting Liu for helpful discussions about EMD.} Yangkang Chen would like to thank Texas Consortium for Computational Seismology (TCCS) for financial support. This paper was prepared in the Madagascar open-source platform \cite[]{mada2013} and all the examples are reproducible.

\inputdir{prestack}

\multiplot{3}{gath0,flat,flat-emd}{width=0.45\columnwidth}{Pre-stack data example.  (a) Pre-stack data. (b) Flattened domain using plane\new{-}wave flattening. (c) EMD filter\old{ed}\new{ing} in the flattened domain.}
%\multiplot{4}{gath0,flat,flat-emd,flat-mf}{width=0.45\columnwidth}{Pre-stack data example.  (a) Pre-stack data. (b) Flattened domain using plane\new{-}wave flattening. (c) EMD filtered in the flattened domain. (d) MF filtered in the flattened domain.   }

\multiplot{2}{flat-emd-rec0,dif}{width=0.45\columnwidth}{Pre-stack data example. (a) Seismic reflection enhanced data using EMD. (c) Difference section between Figure\new{s} \ref{fig:gath0} and \ref{fig:flat-emd-rec0}.  }
%\multiplot{4}{flat-emd-rec0,flat-mf-rec0,dif,dif0-mf}{width=0.45\columnwidth}{Pre-stack data example. (a) Seismic reflection enhanced data using EMD. (b) Seismic reflection enhanced data using MF. (c) Difference section between Figure \ref{fig:gath0} and (a). (d) Difference section between Figure \ref{fig:gath0} and (b).   }

\plot{dip}{width=0.45\columnwidth}{Local slope of pre-stack data example for plane-wave flattening.  }

\multiplot{2}{zooma-1,zooma-2}{width=0.45\columnwidth}{Pre-stack data example. (a) Zoomed sections corresponding to the framebox A in Figure \ref{fig:gath0}. (b) Zoomed sections corresponding to the framebox A in Figure \ref{fig:flat-emd-rec0}.}
%\multiplot{3}{zooma-1,zooma-2,zooma-3}{width=0.45\columnwidth}{Pre-stack data example. (a) Zoomed sections corresponding to the framebox A in Figure \ref{fig:gath0}. (b) Zoomed sections corresponding to the framebox A in Figure \ref{fig:flat-emd-rec0}. (c) Zoomed sections corresponding to the framebox A in Figure \ref{fig:flat-mf-rec0}.}

\multiplot{2}{zoomb-1,zoomb-2}{width=0.45\columnwidth}{Pre-stack data example. (a) Zoomed sections corresponding to the framebox B in Figure \ref{fig:gath0}. (b) Zoomed sections corresponding to the framebox B in Figure \ref{fig:flat-emd-rec0}.}
%\multiplot{3}{zoomb-1,zoomb-2,zoomb-3}{width=0.45\columnwidth}{Pre-stack data example. (a) Zoomed sections corresponding to the framebox B in Figure \ref{fig:gath0}. (b) Zoomed sections corresponding to the framebox B in Figure \ref{fig:flat-emd-rec0}. (c) Zoomed sections corresponding to the framebox B in Figure \ref{fig:flat-mf-rec0}.}

\inputdir{postack}
\multiplot{3}{post-gath0,post-emd-rec0,post-dif}{width=0.45\columnwidth}{Post-stack data example. (a) \old{Postack}\new{Post-stack} data. (b) Signal enhanced data. (c) Difference.}

\multiplot{4}{post-zooma-1,post-zooma-2,post-zoomb-1,post-zoomb-2}{width=0.45\columnwidth}{Post-stack data example. (a) \& (b) Zoomed sections corresponding to the framebox C in Figure \ref{fig:post-gath0,post-emd-rec0,post-dif}. (c) \& (d) Zoomed sections corresponding to the framebox D in Figure \ref{fig:post-gath0,post-emd-rec0,post-dif}.}

\bibliographystyle{seg}
\bibliography{enhemd}

### 2020-09-16 eseis/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{Geophysics, 82, DOI: 10.1190/geo2017-0554.1}

\title{EMD-seislet transform}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Yangkang Chen\footnotemark[1] and Sergey Fomel\footnotemark[2]}

\ms{GEO-2017-0554}

\address{
\footnotemark[1]Previously: 
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin\\
University Station\\
Box X, Austin, TX 78713-8924\\
Currently: 
National Center for Computational Sciences\\
Oak Ridge National Laboratory\\
One Bethel Valley Road\\
Oak Ridge, TN 37831-6008\\
chenyk2016@gmail.com\&cheny@ornl.gov\\
\footnotemark[2]
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin\\
University Station\\
Box X, Austin, TX 78713-8924\\
sergey.fomel@beg.utexas.edu 
}

\lefthead{Chen \& Fomel}
\righthead{EMD-seislet transform}
\maketitle

\begin{abstract}
The seislet transform uses a prediction operator which is connected to the local slope or frequency of seismic events. In this paper, we propose combining \new{the} 1D non-stationary seislet transform with empirical mode decomposition (EMD) in the $f-x$ domain. We use \new{the} EMD to decompose data into smoothly variable frequency components for the following 1D seislet transform. The resultant representation shows remarkable sparsity.  We introduce the detailed algorithm and use \old{one}\new{a} field example to demonstrate the application of the new seislet transform for sparsity-promoting seismic data processing.
\end{abstract}

\section{Introduction}
\new{The sparse}\old{Sparse} approximation aims at extracting the most important information of the given data by a linear combination of pre-specified atom signals with sparse linear coefficients. \old{Sparse approximation}\new{The} theory has been a rapidly evolving field in digital image analysis, since many state-of-the-art signal and image processing tasks have been successfully handled with the concept of sparsity, including image inpainting and restoration \cite[]{elad2005,shuwei20153,shuwei2016cs,amir2017}, image denoising \cite[]{mostafa2016geo,mostafa2017geo,amir2017geo}, data compression \cite[]{bryt2008}, blind source separation \cite[]{zib2001}, etc.

Over the past several decades, different types of sparse transforms have been explored for seismic \old{data processing }applications, and promising results have been reported \cite[]{yangkang20142}. 
\cite{fomel2010seislet} introduced a data-adaptive \old{sparsity promoting }transform, called the \emph{seislet} transform. Following the lifting scheme used in the construction of second-generation digital wavelets, the seislet transform utilizes the \old{spatial }predictability\old{ property} of \new{the} seismic data to construct the predictive operator. \cite{fomel2010seislet} used plane-wave construction (PWD) to aid the prediction process. Instead of using PWD, \cite{liuyang2010} used differential offset continuation (OC) to construct \new{a} seislet transform for pre-stack reflection data. \new{The} OC-seislet transform can obtain better sparsity for conflicting-dip pre-stack seismic data in that \new{the} OC seislet uses offset continuation instead of local slopes to connect different common offset gathers. %however, at the expense of much higher computational cost. 
In order to relieve the dependence of \new{the} seislet transform on local slope estimation, \cite{liuyang2015} proposed a velocity-dependent (VD) seislet transform based on conventional velocity analysis. The seislet transform has also found a recent application in simultaneous-source separation. Instead of using a single slope or frequency map to sparsify the seismic data, \cite{fomel2010seislet} proposed to apply several seislet transforms with smoothly variable slopes or frequencies, which are referred to as seislet frames.

In this paper, we propose to use empirical mode decomposition (EMD) \cite[]{huangemd} to create sparse transforms for representing seismic data.  The essence of \new{the} EMD is to stabilize a highly non-stationary signal by decomposing it into smoothly variable frequency components, which are called  intrinsic mode functions (IMF). We first transform the input seismic data from \new{the} $t-x$ domain to \new{the} $f-x$ domain, then apply \new{the} EMD to each frequency slice to decompose \new{the} input data into smooth\old{ly variable} frequency components. Next, \new{the} 1D non-stationary seislet transform is applied independently to each component. We evaluate the sparsity of the new representation (EMD-seislet transform) and apply it to noise attenuation of a seismic image.
\section{Method}
\subsection{Empirical mode decomposition}
The process of EMD has the following simple expression: 
\begin{equation}
\label{eq:emd}
s(t)=\sum_{n=1}^{N}c_n(t)+r(t),
\end{equation}
where $s(t)$ is the original non-stationary signal, $c_n(t)$ ($n=1,2,\cdots,N$) denotes each separated IMF, $N$ denotes the number of separated IMF, and $r(t)$ denotes the residual after EMD. The process of EMD is to gradually remove the stable oscillations embedded in the original signal to arrive at a monotonic and smooth residual or trend at last. A special property of \new{the} EMD is that the IMFs represent different oscillations embedded in the data, where the oscillating frequency for each sub-signal $c_n(t)$ decreases with IMF order increasing \cite[]{huangemd}.

\subsection{1D seislet transform}
The seislet transform can be constructed by multi-scale prediction of the odd components $\mathbf{o}$ from the even components $\mathbf{e}$:
\begin{align}
\label{eq:r}
\mathbf{r}&=\mathbf{o}-\mathbf{P}(\mathbf{e}), \\
\label{eq:e}
\mathbf{c}&=\mathbf{e}+\mathbf{U}(\mathbf{r}).
\end{align}
\new{In the above equations,} $\mathbf{P}$ denotes the prediction operator and $\mathbf{U}$ denotes the updating operator at a particular scale. \new{$\mathbf{r}$ denotes the difference vector and $\mathbf{c}$ denotes the updated even component.} The inverse seislet transform follows the inverse process of equations \ref{eq:r} and \ref{eq:e} continuing from large to small scale. The difference between \new{the} 1D seislet transform and \new{the} 1D wavelet transform is whether the prediction is modulated by an appropriate frequency. In the simplest case of Haar transform, the Z-transform domain prediction filter for the Haar wavelet transform is 
\begin{equation}
\label{eq:haar}
P(Z)=Z,
\end{equation}
and the Z-transform domain Haar prediction filter for wavelet transform is 
\begin{equation}
\label{eq:haaru}
U(Z)=Z/2.
\end{equation}

However, for \new{the} seislet transform,
\begin{align}
\label{eq:haarseis}
P(Z)&=Z/Z_0, \\
\label{eq:haarseisu}
U(Z)&=1/2(Z/Z_0).
\end{align}
where $Z_0=e^{i\omega_0\Delta t}$. The prediction filter \new{in equation} \ref{eq:haarseis} can perfectly characterize\old{s} a sinusoid with $\omega_0$ \old{circular}\new{angular} frequency sampled on a $\Delta t$ grid.
Analogously, the prediction filter for biorthogonal 2/2 transform can be expressed as:
\begin{equation}
\label{eq:linearseis0}
P(Z)=1/2(Z/Z_0+Z_0/Z),
\end{equation}
and its corresponding updating operator is
\begin{equation}
\label{eq:uplinearseis0}
U(Z)=1/4(Z/Z_0+Z_0/Z).
\end{equation}

\subsection{1D non-stationary seislet transform}
%Let us take the linear prediction filter \ref{eq:linearseis} as an example.
When a 1D signal has a constant \old{circular}\new{angular} frequency, the prediction filter \new{in equation} \ref{eq:haarseis} can characterize a sinusoidal signal. When the 1D signal contains a sinusoid with a variable frequency, or in other words, is non-stationary, we can replace $Z_0$ with $Z_t$,  $Z_t=e^{i\omega(t)\Delta t}$ denotes the frequency modulation at time $t$. Let us modify equation \ref{eq:linearseis0} to the following form\new{:}
\begin{equation}
\label{eq:linearseis}
P_t(Z) = 1/2(Z/Z_t + Z_t/Z),
\end{equation}
in order to best characterize the non-stationary signal. $P_t(Z)$ denotes the prediction filter at time $t$.\old{, and $Z_t=e^{i\omega(t)\Delta t}$ denotes the frequency modulation at time $t$.} In the physical domain, the linear prediction and updating operators can be expressed as:
\begin{align}
\label{eq:linearseis-phy}
P_t(e)&=(S_t^{(+)}(e_{t-1}) + S_t^{(-)}(e_t))/2,\\
\label{eq:linearseisu-phy}
U_t(r)&=(S_t^{(+)}(r_{t-1}) + S_t^{(-)}(r_t))/4,
\end{align}
where $S_t^{(+)}$ and $S_t^{(-)}$ are operators that predict an element from its left and right neighbors by modulating each element according to their local frequency $\omega(t)$.

Figure \ref{fig:non-comp2} shows a comparison between \new{the} wavelet transform and \new{the} 1D stationary and non-stationary seislet transforms in compressing a 1D signal with smooth\old{ly variable} frequency components. The frequency ranges from 250 to 186 Hz. Both the wavelet transform and stationary seislet transform fail to compress the signal well while the non-stationary seislet transform obtains a perfectly sparse representation.

\subsection{Estimating local frequency by complex non-stationary autoregression}
According to the autoregressive spectral analysis theory \cite[]{marple}, a complex time series that has a constant frequency component is predictable by a two-point prediction-error filter $(1,-e^{i\omega_0\Delta t})$. Suppose a complex time series is $d(t)$. In Z-transform notation, the two-point prediction-error filter can be expressed as:
\begin{equation}
\label{eq:twopre}
F(Z)=1-Z/Z_0.
\end{equation} 
We assume that a 1D time series \old{have}\new{has} a smooth\old{ly variable} frequency component, then the 1D time series can be locally predicted using different local two-point prediction-error filters $(1,-e^{i\omega(t)\Delta t})$:
\begin{equation}
\label{eq:localpre}
d(t)=e^{i\omega(t)\Delta t}d(t-\Delta t).
\end{equation}

In order to estimate $\omega(t)$ using equation \ref{eq:localpre}, we need to first minimize the least-squares misfit of the true and predicted time series with a local-smoothness constraint:
\begin{equation}
\label{eq:mini}
\min_{\mathbf{a}} \parallel \mathbf{d} - \mathbf{D} \mathbf{a} \parallel_2^2 + \mathbf{R}(\mathbf{a}),
\end{equation}
where $\mathbf{d}$ and $\mathbf{a}$ are \old{vector}\new{vectors} composed of the entries $d(t)$ and $a(t)$, respectively, and $a(t)=e^{i\omega(t)\Delta t}$. $\mathbf{D}$ is a diagonal matrix composed of the entries $d(t-\Delta t)$. $\mathbf{R}$ denotes the local-smoothness constraint. Equation \ref{eq:mini} can be solved using shaping regularization:
\begin{equation}
\hat{\mathbf{a}} = [\lambda^2\mathbf{I}+\mathcal{T}(\mathbf{D}^T\mathbf{D}-\lambda^2\mathbf{I})]^{-1}\mathcal{T}\mathbf{D}^T\mathbf{d},
\end{equation}
where $\mathcal{T}$ is a triangle smoothing operator and $\lambda$ is a scaling parameter that controls the physical dimensionality and enables fast convergence. $\lambda$ can be chosen as the least-squares norm of $\mathbf{D}$. After the filter coefficient $a(t)$ is obtained, we can straightforwardly calculate the local \old{circular}\new{angular} frequency $\omega(t)$ by
\begin{equation}
\label{eq:circ}
\omega(t) = Re\left[\frac{\mbox{arg}(a(t))}{\Delta t}\right].
\end{equation}

\subsection{Preparing locally stationary frequency slice by EMD}
The aforementioned 1D non-stationary seislet transform adapts to 1D signals that have smoothly variable  frequency components since its compression performance is controlled by the predicting and updating procedures between the series elements according to a locally smooth modulation frequency. Correspondingly, when calculating the local frequency, we also assume the 1D signal to have smoothly variable frequency components.

We call the combined FFT-EMD-seislet workflow the \emph{EMD-seislet} transform. Figures \ref{fig:demo,demo-fz,demo,demo-fs-3} and \ref{fig:demo-f1z-0,demo-f1z-seis-0,demo-dip1-0,demo-f2z-0,demo-f2z-seis-0,demo-dip2-0,demo-f3z-0,demo-f3z-seis-0,demo-dip3-0} provide a detailed demonstration of the procedures involved in the EMD-seislet transform construction. Figure \ref{fig:demo} shows a synthetic data with hyperbolic events. Figure \ref{fig:demo-fz} shows the $f-x$ spectrum of the synthetic data. \new{Figure \ref{fig:demo-fs-3} shows a demonstration for preparing smoothly variable frequency components for each frequency slice using \new{the} EMD in the $f-x$ domain.} We can observe that each frequency slice in the $f-x$ domain is highly non-stationary. After EMD decomposition, the three decomposed $f-x$ domain components are shown in the left column of Figure \ref{fig:demo-f1z-0,demo-f1z-seis-0,demo-dip1-0,demo-f2z-0,demo-f2z-seis-0,demo-dip2-0,demo-f3z-0,demo-f3z-seis-0,demo-dip3-0}. Each component now has smoothly non-stationary frequency slices. After 1D non-stationary seislet transforms, the three $f-x$ domain components become highly compressed. The middle column in Figure \ref{fig:demo-f1z-0,demo-f1z-seis-0,demo-dip1-0,demo-f2z-0,demo-f2z-seis-0,demo-dip2-0,demo-f3z-0,demo-f3z-seis-0,demo-dip3-0} shows the compressed $f-x$ domain using the 1D non-stationary seislet transform. \new{The scale of the compressed coefficients is indicated by the horizontal axis.} The right column in Figure \ref{fig:demo-f1z-0,demo-f1z-seis-0,demo-dip1-0,demo-f2z-0,demo-f2z-seis-0,demo-dip2-0,demo-f3z-0,demo-f3z-seis-0,demo-dip3-0} shows the reconstructed $t-x$ domain data from the decomposed and compressed components in the middle column. The three decomposed components correspond to different parts of the input signal.% three different slopes. % The EMD-seislet transform domain appears sparse.

In order to compare the sparsity in compressing seismic data, we plot the reconstruction error curves with respect to the number of selected largest coefficients. The reconstruction error is defined as $E=\parallel\mathbf{d}-\mathbf{Am}_N\parallel_2^2$, where $\mathbf{m}_N$ denotes the largest $N$ coefficients in the transform domain. The faster the curve decays, the sparser the corresponding transform domain will be. As shown in Figure \ref{fig:sparse}, the EMD-seislet appears to be the sparsest compared with the PWD-seislet transform, wavelet transform, and Fourier transform.

\section{Application \old{to}\new{of} noise attenuation \old{of}\new{to} real data}
We use a \old{field}\new{real} data example shown in Figure \ref{fig:real-0} to demonstrate the performance of the proposed EMD-seislet in attenuating random noise. Figure \ref{fig:real-eseist-0} shows the denoised result by thresholding in the EMD-seislet transform domain. Figure \ref{fig:real-eseist-dif-g} shows the removed noise section using EMD-seislet thresholding. 2\% of EMD-seislet coefficients were retained. Despite the complicated structures of the seismic image, the proposed approach obtains a successful denoising performance. \new{Figure \ref{fig:real-seist-0} shows the denoised result using the traditional seislet thresholding method. Figure \ref{fig:real-fx-0} shows the denoised result using the FX Decon method. Figures \ref{fig:real-seist-dif-g} and \ref{fig:real-fx-dif-g} show the removed noise corresponding to the seislet thresholding method and the FX Decon method, respectively. Figures \ref{fig:real-z}, \ref{fig:real-eseist-z}, \ref{fig:real-seist-z}, and \ref{fig:real-fx-z} show the enlarged sections (corresponding to the frame boxes in Figure \ref{fig:real-eseist-0,real-eseist-dif-g,real-seist-0,real-seist-dif-g,real-fx-0,real-fx-dif-g}).} From the comparison in Figure \ref{fig:real-eseist-0,real-eseist-dif-g,real-seist-0,real-seist-dif-g,real-fx-0,real-fx-dif-g},  
the proposed approach obtains the best result, while \new{the} seislet thresholding is over-smoothing\new{,} and \new{the} FX Decon harms some of the signal energy. \new{The over-smoothing effect of the seislet thresholding method may be due to the over-smooth local slope calculated using the PWD algorithm. The signal-leakage problem of the FX Decon method has been widely studied in the literature, e.g., in \cite{yangkang20141}.} \new{The EMD-seislet domains before and after applying the thresholding operator are plotted in Figures \ref{fig:real-femdr-seis0-3d} and \ref{fig:real-femdr-seis-thr-3d}, respectively. It is clear that the thresholding removes most low-amplitude coefficients in the sparse EMD-seislet domain.}

\section{Conclusion}
We have proposed a novel approach for sparsifing seismic data: EMD-seislet transform. The approach relies on the ability of empirical mode decomposition (EMD) in the $f-x$ domain to provide smoothly non-stationary data, which we use in the following 1D non-stationary seislet transform. When applied to seismic data with multiple conflicting slopes, EMD-seislet is remarkably sparse. A \old{field}\new{real} data example shows an excellent performance of \new{the} EMD-seislet transform in attenuating random noise. \new{However, the large computational cost required by the EMD algorithm requires a careful design of the parallel computing framework in the future research. }

\new{
\section{Acknowledgments}
We appreciate the comments from three anonymous reviewers that greatly improved the manuscript.
}

\inputdir{nonseis}

\plot{non-comp2}{width=0.8\textwidth}{Demonstration of 1D non-stationary seislet transform for \new{a} non-stationary signal. \old{Upper}\new{From the top to the bottom: non-stationary chirp signal (frequency ranges from 250 to 186 Hz), compressed data using \new{the} 1D wavelet transform, compressed data using \new{the} 1D stationary seislet transform with the frequency of 250 Hz, and compressed data using \new{the} 1D non-stationary seislet transform.}}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.3\textwidth]{demo2/Fig/demo}
    \label{fig:demo}}
  \subfloat[]{\includegraphics[width=0.3\textwidth]{demo2/Fig/demo-fz}
    \label{fig:demo-fz}}\\
  \subfloat[]{\includegraphics[width=0.7\textwidth]{demo2/Fig/demo-fs-3}
    \label{fig:demo-fs-3}}
   \caption{(a) Synthetic example with hyperbolic events. (b) $f-x$ spectrum of (a). (c) Demonstration of preparing the smoothly variable frequency components by \new{the} EMD for the 15 Hz slice of the synthetic data in Figure \ref{fig:demo}.}
   \label{fig:demo,demo-fz,demo,demo-fs-3}
\end{figure}

\inputdir{demo4}
\multiplot{9}{demo-f1z-0,demo-f1z-seis-0,demo-dip1-0,demo-f2z-0,demo-f2z-seis-0,demo-dip2-0,demo-f3z-0,demo-f3z-seis-0,demo-dip3-0}{width=0.24\textwidth}{A demonstration of the EMD-seislet transform. The left column shows the decomposed $f-x$ domain spectrum using the EMD. The middle column shows the compressed $f-x$ domain using 1D non-stationary seislet transform. The right column shows the reconstructed $t-x$ domain data corresponding to different components.}

\inputdir{sparse}
\plot{sparse}{width=0.8\columnwidth}{Sparsity comparison. $E=\parallel\mathbf{d}-\mathbf{Am}_N\parallel_2^2$ denotes the reconstruction error with the largest $N$ coefficients in the transform domain.}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-0}
    \label{fig:real-0}}
  \subfloat[]{\includegraphics[width=0.2\textwidth]{field/Fig/real-z}
    \label{fig:real-z}}\\
  \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-eseist-0}
    \label{fig:real-eseist-0}}
  \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-eseist-dif-g}
    \label{fig:real-eseist-dif-g}} 
  \subfloat[]{\includegraphics[width=0.2\textwidth]{field/Fig/real-eseist-z}
    \label{fig:real-eseist-z}}\\
  \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-seist-0}
    \label{fig:real-seist-0}}
  \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-seist-dif-g}
    \label{fig:real-seist-dif-g}} 
  \subfloat[]{\includegraphics[width=0.2\textwidth]{field/Fig/real-seist-z}
    \label{fig:real-seist-z}}\\
  \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-fx-0}
    \label{fig:real-fx-0}}
  \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-fx-dif-g}
    \label{fig:real-fx-dif-g}}
  \subfloat[]{\includegraphics[width=0.2\textwidth]{field/Fig/real-fx-z}
    \label{fig:real-fx-z}}
   \caption{Denoising test. (a) Real seismic data. (c) Denoised data using EMD-seislet domain thresholding. (d) Noise section \old{corresponds}\new{corresponding}  to (c).  (f) Denoised data using seislet domain thresholding. (g) Noise section \old{corresponds}\new{corresponding} to (f). (i) Denoised data using FX Decon. (j) Noise section \old{corresponds}\new{corresponding} to (i). (b),(e),(h) and (k): Zoomed sections for the frame boxes \new{in (a), (c), (f), and (i), respectively}.}
   \label{fig:real-eseist-0,real-eseist-dif-g,real-seist-0,real-seist-dif-g,real-fx-0,real-fx-dif-g}
\end{figure}
\inputdir{field}
\multiplot{2}{real-femdr-seis0-3d,real-femdr-seis-thr-3d}{width=0.45\textwidth}{\new{(a) EMD-seislet domain before thresholding. (b) EMD-seislet domain after thresholding.}}

\bibliographystyle{seg}
\bibliography{eseis}

\newpage
\listoffigures

### 2020-09-16 halfthr/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{Journal of Geophysics and Engineering, 11, no. 6, 065001, (2014)}

\title{Irregular seismic data reconstruction using a percentile-half-thresholding algorithm}

\author{Yangkang Chen\footnotemark[1], Keling Chen\footnotemark[2], Peidong Shi\footnotemark[3] and Yanyan Wang\footnotemark[3]}

\address{
\footnotemark[1]Bureau of Economic Geology, \\
Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
USA \\
%+1-5125478899 \\
ykchen@utexas.edu \\
%\ead{ykchen@utexas.edu}
\footnotemark[2]Department of Earth and Atmospheric Sciences \\
University of Houston, \\
Houston, TX, 77004\\
USA \\
kxc124930@gmail.com\\
\footnotemark[3]State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
speedshi@126.com
%yanshan0425@126.com
}

%\maketitle

\lefthead{Chen et al.}
\righthead{percentile-half-thresholding algorithm}

% for multiple-revision
\DeclareRobustCommand{\dlo}[1]{\ifthenelse{\boolean{@revd}}{}{}}
\DeclareRobustCommand{\wen}[1]{%
  \ifthenelse{\boolean{@revd}}{\textcolor{black}{#1}}{#1}}

%\dlo means remove removing
%\wen means preserve

\begin{abstract}
%In this paper, we introduce a novel IST based iterative algorithm for reconstructing irregularly sampled seismic data. 
In this paper, a percentile-half-thresholding approach is proposed in the transformed domain thresholding process for iterative shrinkage thresholding (IST). The percentile-thresholding strategy is more convenient for implementing than the constant-value, linear-decreasing, or exponential-decreasing thresholding because it's data-driven. The novel half-thresholding strategy is inspired from the recent advancement in the researches on optimization using non-convex regularization. We summarize a general thresholding framework for IST and show that the only difference between half thresholding and the conventional soft or hard thresholding lays in the thresholding operator. Thus it's straightforward to insert the existing percentile-thresholding strategy to the half-thresholding iterative framework. We use both synthetic and field data examples to compare the performances using soft thresholding or half thresholding with constant threshold or percentile threshold. Synthetic and field data show consistent results that 
%half thresholding can achieve more precise reconstructed result than the conventional soft thresholding, and the percentile-thresholding approach can obtain better interpolated result than the constant-value thresholding. 
apart from the threshold-setting convenience, the percentile thresholding also has the possibility for improving the recovery performance. Compared with soft thresholding, half thresholding tends to have a more precise reconstructed result.
\end{abstract}

\section{Introduction}
Seismic data interpolation plays a fundamental role in seismic data processing, which provides the regularly sampled seismic data for the following jobs like 3D SRME and wave equation-based migrations \cite[]{shengxu2010}. There has been a number of effective methods to recover missing seismic traces, these methods can be generally divided into three types. The first kind is based on a convolution operator, which utilizes a prediction filter computed from the low-frequency parts to predict the high-frequency components \cite[]{spitz1991,porsani1999,wang2002}. However, the predictive filtering method can only be applied to regularly sampled seismic data \cite[]{mostafa2007}. The second type is a transformed domain method, which is based on a sparsity assumption and makes use of the theory of compressive sensing or compressive sampling (CS) \cite[]{candes20062,donoho2006,mallat2009,herrmann2010} to achieve a successful recovery using highly incomplete available data \cite[]{sacchi1998,wang2003,zwartjes20071,zwartjes20072,pengliang2012,pengliang2013}. \cite{mostafa2007} proposed a multistep autoregressive strategy which combines the first two types of methods to reconstruct irregular seismic data. The third type is based on the integral of continuation operators. This integral is performed based on the traveltime calculation from a velocity model, thus it depends on the known velocity model, which also becomes its limitation \cite[]{canning1996,bleistein2000,stolt2002,fomel2003}.

A recently very popular way for interpolating irregularly sampled seismic data is by using iterative thresholding, such as projection onto convex sets (POCS) and iterative shrinkage thresholding (IST), mainly because of their simple formulations and convenient implementations. Different thresholding approaches will lead to different performances for interpolation. 
%One simple way is constant-value thresholding. Other more efficient ways includes the linear-decreasing thresholding \cite[]{abma2006}, exponential decreasing \cite[]{jianjun2010}. 
Because of the advancement of the non-convex optimization algorithms, a half-thresholding algorithm has been proposed both in signal-processing and exploration geophysics communities \cite[]{pengliang20131,zongben2012}. In this paper, we summarize a general thresholding framework for IST algorithm. The only difference among soft, hard, and half thresholding lays in the thresholding operator. Thus, a percentile thresholding strategy, which is particularly useful in practice, can be straightforwardly applied to the case of half thresholding. We use both synthetic and field data examples to demonstrate the performance of our proposed percentile-half-thresholding algorithm, compared with other three existing approaches.

\section{Theory}
\subsection{Seismic interpolation}
The basic target of seismic interpolation is to solve the following equation:
\begin{equation}
\label{eq:int1}
\mathbf{d}_{obs}=\mathbf{Md},
\end{equation}
where $\mathbf{d}_{obs}$ is the observed data which is regularly or irregularly sampled, $\mathbf{d}$ is the unknown data we want to reconstruct and $\mathbf{M}$ is the sampling matrix. The sampling operator has a diagonal structure, which is composed by zero and identity matrix:
\begin{equation}
\label{eq:mask}
\mathbf{M} = \left[\begin{array}{cccccccc} 
\mathbf{I} & 	       & 	  & 	     &		 &	\\
	   &\mathbf{O} & 	  &	     &		 &	\\
	   &           &\mathbf{I}&	     &		 &	\\
	   &  	       &          &\mathbf{I}&	         & 	\\
	   &	       &	  &	     &\mathbf{\ddots} & \\
	   &	       &	  &	     &		 & \mathbf{I} 
\end{array}\right].
\end{equation}
Each $\mathbf{I}$ in equation \ref{eq:mask} corresponds to sampling a trace, and each $\mathbf{O}$ corresponds to missing a trace.

As equation \ref{eq:int1} is under-determined, additional constraint is required in order to solve the equation. By applying a regularization term, we get a least-squares minimization solution for solving equation \ref{eq:int1}:
\begin{equation}
\label{eq:int2}
\hat{\mathbf{d}}=\arg\min_{\mathbf{d}}\Arrowvert \mathbf{d}_{obs}-\mathbf{Md}\Arrowvert_2^2+\mathbf{R}(\mathbf{d}),
\end{equation}
where $\mathbf{R}$ is a regularization operator and $\Arrowvert\cdot\Arrowvert_2^2$ denotes the square of $L_2$ norm.

\subsection{Iterative shrinkage thresholding}
In order to reconstruct the missing traces in the seismic data, one can use a sparsity-promoting transform to precondition $\mathbf{d}$ in equation \ref{eq:int1}, that is:
\begin{equation}
\label{eq:precondition}
\mathbf{d}=\mathbf{Ax},
\end{equation}
where $\mathbf{A}$ is a tight frame such that $\mathbf{x}=\mathbf{A}^{H}\mathbf{d}$ and $\mathbf{A}^{-1}=\mathbf{A}^{H}$, and $[\cdot]^H$ denotes adjoint. A common selection for $\mathbf{A}$ is the Fourier transform.
Inserting equation \ref{eq:precondition} into equation \ref{eq:int1}, and let $\mathbf{K}=\mathbf{MA}$, we obtain 
\begin{equation}
\label{eq:forw2}
\mathbf{d}_{obs} = \mathbf{Kx}.
\end{equation}
Correspondingly, equation \ref{eq:int2} turns to:
\begin{equation}
\label{eq:int3}
\hat{\mathbf{x}} = \arg\min_{\mathbf{x}} \Arrowvert \mathbf{d}_{obs}-\mathbf{Kx} \Arrowvert_2 + \mathbf{R}'(\mathbf{x})
\end{equation}
The well-known IST algorithm is used for solving equation \ref{eq:int3} with a sparsity constraint:
\begin{equation}
\label{eq:ist}
\mathbf{x}_{n+1} = \mathbf{T}_{\gamma(\tau,p)}[\mathbf{x}_n+\mathbf{K}^{H}(\mathbf{d}_{obs}-\mathbf{Kx}_n)].
\end{equation}
Here $\mathbf{T}_{\gamma(\tau,p)}$ corresponds to a thresholding operator performed element-wise with threshold $\gamma(\tau,p)$ \cite[]{pengliang20131}. When $p=1$, $\gamma(\tau,1)=\tau$, $\mathbf{R}'(\cdot)=\tau \Arrowvert \cdot \Arrowvert_1$, where $\tau$ is a regularization parameter which controls the weight between misfit and constraint in the minimization problem, $\mathbf{T}_{\gamma(\tau,1)}$ corresponds to a soft-thresholding operator:
\begin{equation}
\label{eq:soft}
\mathbf{T}_{\gamma(\tau,1)}[v(\mathbf{x})] = \left\{ \begin{array}{ll}
v(\mathbf{x})-\gamma \frac{v(\mathbf{x})}{|v(\mathbf{x})|} & \text{for}\quad  |v(\mathbf{x})| > \gamma(\tau,1)  \\
0			      & \text{for}\quad  |v(\mathbf{x})| \le \gamma(\tau,1)
\end{array}\right.,
\end{equation} 
where $v(\mathbf{x})$ denotes the amplitude of each position-coordinate vector $\mathbf{x}$.
 When $p=0$, $\gamma(\tau,0)=\sqrt{2\tau}$, $\mathbf{R}'(\cdot)=\tau \Arrowvert \cdot \Arrowvert_0$, $\mathbf{T}_{\gamma(\tau,0)}$ corresponds to a hard\wen{-}thresholding operator:
\begin{equation}
\label{eq:hard}
\mathbf{T}_{\gamma(\tau,0)}[v(\mathbf{x})] = \left\{ \begin{array}{ll}
v(\mathbf{x}) 	 & \text{for}\quad  |v(\mathbf{x})| > \gamma(\tau,0)  \\
0			      & \text{for}\quad  |v(\mathbf{x})| \le \gamma(\tau,0)
\end{array}\right.,
\end{equation}
\subsection{Percentile half thresholding}
Recent research suggests that it's possible to reconstruct the seismic data using non-convex $L_p$-norm minimization, $0< p <1$. Particularly, iterative half thresholding has been developed both in signal processing and exploration geophysics communities \cite[]{zongben2012,pengliang20131}. The difference between half thresholding and the conventional soft thresholding is just the thresholding operator. When $p=1/2$, $\gamma(\tau,1/2)=\frac{3}{2}\tau^{2/3}$, $\mathbf{R}'(\cdot)=\tau \Arrowvert \cdot \Arrowvert_{1/2}^{1/2}$, $\mathbf{T}_{\gamma(\tau,1/2)}$ becomes a half-thresholding operator:
\begin{align}
\label{eq:half}
&\mathbf{T}_{\gamma(\tau,1/2)}[v(\mathbf{x})] = \\
&\left\{ \begin{array}{l}
\frac{2}{3}v(\mathbf{x})\left(1+\cos(\frac{2}{3}\pi - \frac{2}{3} \arccos(\frac{\tau}{8}(\frac{|v(\mathbf{x})|}{3})^{-\frac{3}{2}}))\right) \\
\quad\quad\quad  \text{for}\quad  |v(\mathbf{x})| > \gamma(\tau,1/2)  \\
0	\\
	\quad\quad\quad    \text{for}\quad  |v(\mathbf{x})| \le \gamma(\tau,1/2) \\
 %\quad &
\end{array}\right..
\end{align} 
The threshold $\gamma(\tau,p)$ can be constant, linear-decreasing \cite[]{abma2006} and exponential-decreasing \cite[]{jianjun2010}. However, all of these defining criterion are based on a prior knowledge about the data and is often not easy to choose. Instead, a processing-convenient percentile-thresholding strategy can be selected to overcome this inconvenience \cite[]{dian2008}. $\gamma(\tau,p)$ is selected as the $k$th largest absolute value among all $N$ values in the transformed domain, where the predefined percentile threshold $pc=k/N$ such that \dlo{$\gamma(\tau,p) = pc * MAX(|v(\mathbf{x})|)$. Here, $MAX$ denotes the maximum value of the transformed domain.}\wen{$\gamma(\tau,p)=prctile(|v(\mathbf{x})|,pc)$. Here, $prctile$ returns percentile $pc$ of the values in $|v(\mathbf{x})|$.}

\subsection{Signal-to-noise ratio}
In order to test the convergence performance, we use the widely used measurement\cite[]{hennenfent2006,guochang2009,sep}:
\begin{equation}
\label{eq:snr}
SNR=10\log_{10} \frac{\Arrowvert \mathbf{d} \Arrowvert_2^2}{\Arrowvert\mathbf{d}-\hat{\mathbf{d}}\Arrowvert_2^2},
\end{equation} 
where the unit for $SNR$ is $dB$, $\mathbf{d}$ and $\hat{\mathbf{d}}$ denote the true and estimated data, respectively.

\section{Examples}
We use two synthetic examples and one field data set to compare the performance of the aforementioned percentile-half-thresholding approach with the conventional thresholding approaches. For simplicity, we only compare half thresholding with soft thresholding in two cases: percentile and constant-value threshold.

%The two examples are shown in Figure \ref{fig:linear,linear-zero,sean,sean-zero}. Figures \ref{fig:linear} and \ref{fig:sean} show the original seismic sections. Figures \ref{fig:linear-zero} and \ref{fig:sean-zero} show the decimated sections with 30\% traces randomly removed. 
The first example is a synthetic example that is composed of four linear events, one of which crosses the other three events. The original data is shown in Figure \ref{fig:linear}. After randomly removing 30\% traces, we create the decimated section, as shown in Figure \ref{fig:linear-zero}. Figure \ref{fig:data2,data3,data5,data6,diff2,diff3,diff5,diff6,diff2_10,diff3_10,diff5_10,diff6_10} show the reconstruction results for the first synthetic example. From the result using percentile half thresholding (Figure \ref{fig:data6}) and constant-value half thresholding (Figure \ref{fig:data3}), and their corresponding estimation error sections (the difference between the true data and estimated data), we can observe that half thresholding nearly do a perfect job while the percentile thresholding strategy helps obtain a even better result. Both conventional constant-value and percentile soft-thresholding results seem to have significant estimation error.  We can also observe that the percentile soft thresholding outperforms the constant-value soft thresholding by obtaining slightly less estimation error.   \wen{In order to better compare the error sections using different approaches, we amplified the magnitude of each error section shown in Figures \ref{fig:diff2}, \ref{fig:diff3}, \ref{fig:diff5} and \ref{fig:diff6} by multiplying the magnitude by 10 times. The magnitude amplified error sections are shown in Figures \ref{fig:diff2_10}, \ref{fig:diff3_10}, \ref{fig:diff5_10} and \ref{fig:diff6_10}. It's much clearer that the percentile-half-thresholding strategy obtains a much better performance than any other approaches.} The diagrams shown in Figure \ref{fig:SNRs} further prove the observations in that the converged result for percentile half thresholding has the largest SNR, which is followed by constant-value half thresholding, and the constant-value soft thresholding obtains the smallest SNR.

The second example is a hyperbolic-events synthetic example. The original data and decimated data with 30 \% traces randomly removed traces are shown in Figure \ref{fig:hyper,hyper-zero}. We apply four different thresholding approaches as mentioned above to this example and get the reconstructed results and their corresponding reconstruction error sections, which are shown in Figure \ref{fig:hyper-data2,hyper-data3,hyper-data5,hyper-data6,hyper-diff2,hyper-diff3,hyper-diff5,hyper-diff6}. Similarly, the reconstructed result for the proposed percentile half thresholding (shown in Figure \ref{fig:hyper-data6}) obtains the best results, causing negligible reconstruction error (shown in Figure \ref{fig:hyper-diff6}). The constant-value \dlo{soft}\wen{half} thresholding also performs well because the error section (shown in Figure \ref{fig:hyper-data3}) contains small amount of coherent signals. The reconstruction results for soft thresholding using either percentile or constant-value strategy (shown in Figures \ref{fig:hyper-data2} and \ref{fig:hyper-data5} )are not pleasant. \dlo{Because they cause a significant energy loss in the error sections as shown in Figures \ref{fig:hyper-diff2} and \ref{fig:hyper-diff5}.} \wen{Because they still contain some zero or weak-amplitude traces and cause a significant energy loss in the error sections as shown in Figures \ref{fig:hyper-diff2} and \ref{fig:hyper-diff5}, which indicates a failure in interpolating the missing traces.} From the convergence diagram as shown in Figure \ref{fig:hyper-SNRs}, we can conclude that the half-thresholding approaches outperforms the conventional soft-thresholding approaches, while the percentile-thresholding strategy can helps obtain better results that the constant-value strategy.

The third example is a field marine data, which was investigated widely in the literature \cite[]{fomel2002pwd,liuyang2011rna}. We can obtain a similar conclusion as the previous two examples. However, from the reconstructed data and the estimation error sections, the conventional soft-thresholding (both constant-value and percentile) results (shown in Figures \ref{fig:sean-data2} and \ref{fig:sean-data5}) suffer from a heavy useful-energy loss as shown in Figures \ref{fig:sean-diff2} and \ref{fig:sean-diff5} \wen{and the reconstructed data as shown in Figures \ref{fig:sean-data2} and \ref{fig:sean-data5} still contain some obvious zero or weak-amplitude traces}, which is no longer acceptable. From the convergence diagrams shown in Figure \ref{fig:sean-SNRs}, the \wen{final} SNRs of conventional soft-thresholding approaches are \dlo{both less than 12 $dB$}\wen{lower than the half-thresholding approaches.}. \dlo{The half-thresholding algorithms get much higher SNRs compared with soft-thresholding algorithms. The proposed percentile-half-thresholding obtains the highest SNR: 20 $dB$.}\wen{Although the constant-value half thresholding can get slightly higher SNR than percentile half thresholding during the first several iterations, the percentile half thresholding converges to a higher final SNR than constant-value half thresholding.}

\section{Conclusions}
We have introduced a general thresholding framework for IST algorithm. The only difference between half thresholding and conventional soft or hard thresholding is owing to the thresholding operator, so the percentile-thresholding strategy can be easily inserted into the half-thresholding algorithm. We compared four different types of thresholding strategies by using two synthetic examples and one field data example. The results show that apart from the threshold-setting convenience, the percentile thresholding also has the possibility for improving the recovery performance. Compared with soft thresholding, half thresholding tends to have a more precise reconstructed result.

\section{Acknowledgments}
We thank \new{Sanyi Yuan, Shan Qu, and} \old{three}\new{two} anonymous reviewers for their constructive suggestions, which helped improve this paper. We are grateful to developers of the Madagascar software package for providing corresponding codes for testing the algorithms and preparing the figures.

\inputdir{linear}
\multiplot{2}{linear,linear-zero}{width=0.45\textwidth}{(a) Synthetic data (linear events). (b) Decimated synthetic data (created by randomly removing 30\% traces).}

\multiplot{12}{data2,data3,data5,data6,diff2,diff3,diff5,diff6,diff2_10,diff3_10,diff5_10,diff6_10}{width=0.21\textwidth}{Reconstructed results for synthetic data (linear events). (a) Using constant-value soft thresholding. (b) Using constant-value half thresholding.  (c) Using percentile soft thresholding. (d) Using percentile half thresholding.  (e)-(h) Reconstruction error sections corresponding to (a)-(d), respectively.  (i)-(l) Amplitude amplified error sections by $\times 10$, corresponding to (e)-(h), respectively.}

\plot{SNRs}{width=0.8\textwidth}{Convergence diagrams for synthetic data (linear events). "p" corresponds to percentile half thresholding. "o" corresponds to constant-value half thresholding. "s" corresponds to percentile soft thresholding. "*" corresponds to constant-value soft thresholding. }

\inputdir{hyper}
\multiplot{2}{hyper,hyper-zero}{width=0.45\textwidth}{(a) Synthetic data (hyperbolic events). (b) Decimated synthetic data (created by randomly removing 30\% traces). }

\multiplot{12}{hyper-data2,hyper-data3,hyper-data5,hyper-data6,hyper-diff2,hyper-diff3,hyper-diff5,hyper-diff6}{width=0.21\textwidth}{Reconstructed results for synthetic data (hyperbolic events). (a) Using constant-value soft thresholding. (b) Using constant-value half thresholding.  (c) Using percentile soft thresholding. (d) Using percentile half thresholding.  (e)-(h) Reconstruction error sections corresponding to (a)-(d), respectively.}

\plot{hyper-SNRs}{width=0.8\textwidth}{Convergence diagrams for synthetic data (hyperbolic events). "p" corresponds to percentile half thresholding. "o" corresponds to constant-value half thresholding. "s" corresponds to percentile soft thresholding. "*" corresponds to constant-value soft thresholding. }

\inputdir{sean}
\multiplot{2}{sean,sean-zero}{width=0.45\textwidth}{(a) Field data. (b) Decimated field data (created by randomly removing 30\% traces). }

\multiplot{12}{sean-data2,sean-data3,sean-data5,sean-data6,sean-diff2,sean-diff3,sean-diff5,sean-diff6}{width=0.21\textwidth}{Reconstructed results for field data.  (a) Using constant-value soft thresholding. (b) Using constant-value half thresholding.  (c) Using percentile soft thresholding. (d) Using percentile half thresholding.  (e)-(h) Reconstruction error sections corresponding to (a)-(d), respectively.}

\plot{sean-SNRs}{width=0.8\textwidth}{Convergence diagrams for field data. "p" corresponds to percentile half thresholding. "o" corresponds to constant-value half thresholding. "s" corresponds to percentile soft thresholding. "*" corresponds to constant-value soft thresholding. }

\bibliographystyle{seg}
\bibliography{halfthr}

### 2020-09-16 ieee_temp_groll/ieee_groll.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\title{Ground-roll noise attenuation using a simple and effective approach based on local bandlimited orthogonalization}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{\IEEEauthorblockN{Yangkang Chen$^1$, Shebao Jiao$^2$, Jianwei Ma$^3$, Hanming Chen$^2$, Yatong Zhou$^4$, and Shuwei Gan$^2$}\\
$^1$\IEEEauthorblockA{Jackson School of Geosciences,
The University of Texas at Austin,
University Station, Box X,
Austin, TX 78713-8924, USA,
Email: ykchen@utexas.edu}\\
$^2$\IEEEauthorblockA{State Key Laboratory of Petroleum Resources and Prospecting, 
China University of Petroleum, 
Fuxue Road 18th,
Beijing, China, 102200, 
Email: gsw19900128@126.com \& huichanming@126.com} \\
$^3$ \IEEEauthorblockA{Department of Mathematics,
Harbin Institute of Technology,
Harbin, China, 
jma@hit.edu.cn}\\
$^4$\IEEEauthorblockA{School of Electronic and Information Engineering,
Hebei University of Technology,
Xiping Road No. 5340, Beichen District,
Tianjin, China, 300401,
zyt@hebut.edu.cn}\\
}
\maketitle
%512375919@qq.com

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	Defined by myself 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
\newcommand{\dlo}[1]{}
\newcommand{\wen}[1]{#1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	Defined by myself 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
 The bandpass filtering is a common way for estimating the ground-roll noise in land seismic data because of the low-frequency property of ground-roll noise. However, the frequency-mixing problem makes bandpass filtering inconvenient or even impossible to achieve a successful removal of ground-roll noise.  In this paper, we propose a novel band-limited orthogonalization approach for removing ground-roll noise without harming useful primary reflections. We orthogonalize the initially denoised signal via bandpass filtering with a relatively high low-bound-frequency (LBF), and the corresponding noise section that contains loss of primary reflections, using local signal-and-noise orthogonalization.  The local orthogonalization guarantees that the least coherent primary reflections are lost in the noise section. The procedure of the proposed approach is very convenient to implement because only a bandpass filtering and a regularized division between the initially denoised signal and initial noise are used. An open-source field dataset demonstrates a successful performance using the proposed approach. 
\end{abstract}

\begin{keywords}
Ground-roll noise, bandpass filtering, local orthogonalization, regularized division
\end{keywords}

\section{Introduction} 
Ground-roll noise is a type of seismic noise, with a high amplitude, low frequency, and low velocity. Ground-roll noise is the main type of coherent noise for land seismic \dlo{survey}\wen{surveys}. Ocean bottom node (OBN) based marine seismic surveys may also contain this type of noise \cite{yangkang20142}. The ground-roll noise is a type of source-generated noise and can be scattered by near-surface heterogeneities.  The ground-roll noise usually mask the shallow reflections at short offset, and deep reflections at larger offset \cite{claerbout1983,saatilar1988,henley2003}, and must be removed before the subsequent processing tasks. Instead of being incoherent along the spatial direction like random noise \cite{wencheng2015asa,yangkang2015}, the ground-roll noise is \wen{usually} coherent \wen{along the spatial dimension} \dlo{and behave much similarly to the primary reflections}, which makes the removal of them very difficult using simple signal processing methods. 
There have been a lot of researches about removing ground-roll noise done in the literature and many researchers have proposed different methods for handling the ground-roll noise problem \cite{shieh1990,brown2000}. Most of the ground-roll noise removal approaches either fail to remove all the ground-roll noise or remove much useful primary reflections energy. An efficient and effective technique for removing ground-roll noise is always in demand.

The simplest and most straightforward way for removing ground-roll noise might be bandpass filtering. Because of the low-frequency property, a simple high-pass filter is usually applied to the seismic record to attenuate the ground-roll noise. However, the low-bound-frequency (LBF) for the bandpass filter is not easy to choose, because higher LBF will cause much damage to primary reflections while lower LBF will fail to remove enough ground-roll noise. This issue exists because of the coupling of primary reflections and ground-roll noise in the frequency bands. One way to solve this problem is to use matching filtering. The low-pass data is used as an initial guess for the ground-roll noise and then a least squares (LS) based matching filter is calculated to match the initial ground-roll noise to the raw seismic data best \cite{carson2006,stephen2007,halliday2010}. The matched ground-roll noise is then subtracted from raw seismic data to obtain the output. This adaptive subtraction method highly depends on the initial prediction of the ground-roll noise. Besides, in the case of highly non-stationary primary reflections and ground-roll noise, a conventional stationary matching filtering will fail to obtain an acceptable result.

%\cite{james1968} proposed the multichannel stacking filters for attenuating those types of noise which \dlo{occur}\wen{occurred} at relatively well-determined points on neighbor traces, such as the ground-roll noise. \cite{prasad1980} studied and compared the performance of the least-mean-squares (LMS) adaptive filter, the adaptive lattice filter, and the adaptive Kalman filter identifier.  \cite{cahit1983} proposed an effective surface wave removal approach termed as vibroseis whitening (VSW) approach, which was tailed specifically for vibroseis data. The VSW approach was based on the application of time-varying amplitude scaling before vibroseis crosscorrelation. This scaling resulted in a signal-to-noise ratio (SNR) improvement equal\dlo{s} to the gain expected from crosscorrelation. This approach \dlo{is}\wen{was} also termed as the spectral balancing approach. \cite{ruhi1988} proposed a one-dimensional, linear frequency-modulated matched filter for removing ground-roll noise. This approach works well when the frequency bands of seismic reflections and ground-roll noise overlap. \cite{carson2006} proposed to use curvelet transform to remove ground-roll noise by a two-step process. The first step is to identify the ground-roll noise from the seismic data using an appropriate approach and then separate the signal and ground-roll noise using a block-coordinate relaxation method that seeks the sparest set for weighted curvelet coefficients of the ground-roll noise and the sought-after reflectivity. \cite{ruhi1994} proposed an adaptive lattice filter for attenuating ground-roll noise. The lattice filter has the same order of computational complexity as the LMS adaptive filter but enjoys a faster convergence rate.  \wen{\cite{regone1998} and \cite{ozbek2000} proposed to use acquisition-based suppression schemes to attenuate the ground-roll noise based on the use of recording arrays. \cite{stephen2007} proposed a polarization filtering approach to attenuate ground-roll noise, in which they combined statics, signal-to-noise ratio, and eigenimages to construct the ground-roll noise model, followed by adaptive subtraction.}  \wen{There is a type of ground-roll noise attenuation approaches that are based on the seismic interferometry \cite{halliday20072,halliday20092}.} \cite{yanwei2009} proposed an interferometric method to predict and subtract surface waves in seismic data. Instead of the traditional frequency-based one-step prediction, the interferometric method uses a multi-prediction and subtraction strategy to attenuate more ground-roll noise and preserve more useful energy. However, the implementation requires a careful parameters designing and tuning process. \wen{\cite{halliday2010} also proposed an interferometric ground-roll removal approach. They used seismic interferometry to estimate scattered ground-roll noise between pairs of receiver locations.}   A recently proposed approach by \cite{liuyang2012} utilized a time-frequency decomposition technique to separate ground-roll noise and primary reflections. The basic principle of this method is that instead of using a global frequency difference between the primary reflections and ground-roll noise, it uses the local time-frequency property of ground-roll noise to achieve the noise free data. 
In this paper, we proposed a simple but effective way for removing all the ground-roll noise without harming useful reflections. We first apply a simple bandpass filtering to raw seismic data in order to remove all the ground-roll noise (thus the LBF should be a little bit high to guarantee no ground-roll noise left in the data), then because of loss of useful primary reflections, we use local signal-and-noise orthogonalization proposed recently by \cite{yangkang2015ortho} to orthogonalize the primary reflections and ground-roll noise in order to retrieve the lost useful signals back to the initial bandpass filtered data. The performance of the proposed approach on the pre-stack dataset shows successful performance.

\section{Method}
\subsection{Bandpass filtering and its frequency-mixing problem}
A bandpass filtering process can be simply summarized as:
\begin{equation}
\label{eq:bandpass}
\mathbf{\hat{d}} = \mathbf{F}^{-1} \mathbf{B}_{fl,fh} \left(\mathbf{F} \mathbf{d}\right),
\end{equation}
where $\mathbf{d}$ and $\mathbf{\hat{d}}$ denote the unfiltered and filtered data, respectively. $\mathbf{F}$  and $\mathbf{F}^{-1}$ denotes a pair of forward and inverse Fourier transforms. $\mathbf{B}_{fl,fh}$ denotes the bandpass filter with a high-bound-frequency (HBF) $fh$, and low-bound-frequency (LBF) $fl$. For the purpose of removing ground-roll noise, $fh$ is usually chosen as Nyquist frequency, the only parameter to choose is only the LBF.

The problem of bandpass filtering for removing ground-roll noise is the inconvenience, or impossibility to choose an optimal LBF, because of the frequency-mixing problem of ground-roll noise and primary reflections. Figure \ref{fig:field-1-0,dif-1-0,field-2-0,dif-2-0} shows a demonstration of the frequency-mixing problem. When $fl=25$ Hz, all the ground-roll noise have been removed, and denoised section (Figure \ref{fig:field-1-0}) does not contain any ground-roll noise. However, the noise section (Figure \ref{fig:dif-1-0}) contains a lot of coherent signals: both direct waves and primary reflections. When $fl=10$ Hz, the noise section (Figure \ref{fig:dif-2-0}) does not contains any coherent reflection or direct waves, however, the denoised section (Figure \ref{fig:field-2-0}) still contains a large amount of ground-roll noise.

One of the most commonly used approaches to solve the frequency-mixing problem is to use matching filtering. The removed ground-roll noise after a common bandpass filtering is used as an initial guess for the ground-roll noise. A least squares (LS) based matching filter is then calculated to match the initial ground-roll noise to the raw seismic data based on the least-energy assumption. The matched ground-roll noise is then subtracted from the raw seismic data to obtain the ground-roll noise attenuated profile. However, this adaptive subtraction method highly depends on the initial prediction of the ground-roll noise. Besides, in the case of highly non-stationary primary reflections and ground-roll noise, a conventional stationary matching filtering is not physically reasonable, and thus can not obtain a satisfactory performance. In the next sections, we will introduce a novel approach for attenuating ground-roll noise based on bandpass filtering, which can remove more ground-roll noise and preserve more useful primary reflections.

\subsection{Local signal-and-noise orthogonalization}
%\cite{yangkang2014ortho} proposed a local orthogonalization approach for retrieving useful signals from the noise section. 
The principle of local signal-and-noise orthogonalization is to locally orthogonalize the denoised signal and noise sections in order to make sure no coherent primary reflections will be lost in the noise section. %\cite{yangkang2014ortho} mainly dealt with random noise attenuation problem.
Here, we propose to use this algorithm to ground-roll noise removal problem. The orthogonalization based approach can be summarized as: 
\begin{align}
\label{eq:news}
\mathbf{s}&=(\mathbf{I}+\mathbf{W})\mathbf{\hat{d}},\\
\label{eq:newn}
\mathbf{n}&=\mathbf{\hat{d}}-(\mathbf{I}+\mathbf{W})\mathbf{\hat{d}}.
\end{align}
Here, $\mathbf{s}$ and $\mathbf{n}$ are the output denoised signal and noise sections.\wen{$\mathbf{I}$ denotes an identity matrix.} $\mathbf{W}$ denotes a diagonal operator composed of the local orthogonalization weight (LOW) vector. \dlo{The LOW closely follows the way calculating the global orthogonalization weight (GOW).} When $w=\frac{\mathbf{n}_0^T\mathbf{s}_0}{\mathbf{s}_0^T\mathbf{s}_0}$, \wen{$\mathbf{s}_0$ and $\mathbf{n}_0$ denoting the initial guess of signal and noise} , $w$ is the global orthogonalization weight (GOW), it can be proved that the following scaled signal $\mathbf{s}_0$ and corresponding noise $\mathbf{n}_0$ are orthogonal to each other in a global sense: %\cite{yangkang2014ortho}:
%\begin{figure}[htb!]
%  \centering
%  \includegraphics[width=0.32\columnwidth,height=0.32\columnwidth]{Fig/demo}
%  \caption{Demonsration of global orthogonalization.}
%   \label{fig:demo}
%\end{figure}

\begin{align}
\label{eq:ortho1}
\hat{\mathbf{n}} &= \mathbf{n}_0 - w\mathbf{s}_0, \\
\label{eq:ortho2}
\hat{\mathbf{s}} &= \mathbf{s}_0 + w\mathbf{s}_0.
\end{align}
In a local sense, the LOW can be define as:
      \begin{equation}
        \label{eq:eq2}
          w_m(t) = \frac{\displaystyle\sum_{i=t-m/2}^{t+m/2} s_0(i) n_0(i)}{\displaystyle\sum_{i=t-m/2}^{t+m/2} s_0^2(i)},
      \end{equation}
where $w_m(t)$ denotes the LOW for each temporal point $t$ with a local window length $m$. $s_0(t)$ and $n_0(t)$ here denote the initially estimated signal and noise for each point $t$.

In order to better control the locality and smoothness of LOW, we follow the local-attribute scheme introduced by \cite{fomel2007localattr}: %and first turn the orthogonalization problem into an optimization problem:
\begin{equation}
\label{eq:localortho}
\mathbf{w} = \arg\min_{\mathbf{\tilde{w}}} \parallel \mathbf{n}_0 - \mathbf{S}_0\mathbf{\tilde{w}}\parallel_2^2. %+ \mathbf{R}(\mathbf{w})
\end{equation}
Here, $\mathbf{w}$ is the LOW, $\mathbf{S}_0$ is a diagonal matrix composed of the initial estimated signal $\mathbf{s}_0$: $\mathbf{S}_0=diag(\mathbf{s}_0)$.
Then, we solve the least-squares problem \ref{eq:localortho} with the help of shaping regularization using a local-smoothness constraint:
\begin{equation}
\label{eq:shape}
\mathbf{w} = [\lambda^2\mathbf{I} + \mathcal{T}(\mathbf{S}_0^T\mathbf{S}_0-\lambda^2\mathbf{I})]^{-1}\mathcal{T}\mathbf{S}_0^T\mathbf{n}_0,
\end{equation}
where $\mathcal{T}$ is a triangle smoothing operator and $\lambda$ is a scaling parameter set as $\lambda  = \Arrowvert\mathbf{S}_0^T\mathbf{S}_0\Arrowvert_2$ \cite{fomel2007localattr}. The triangle smoothing operator was introduced in detailed in \cite{fomel2007shape}. It should be mentioned that solution of equation \ref{eq:localortho} corresponds to a regularized division between the two vectors $\mathbf{n}_0$ and $\mathbf{s}_0$ and it can be solved using any regularization approach, not limited to the shaping regularization strategy shown in equation \ref{eq:shape}. Thus it is fairly convenient to implement the local orthogonalization between initial signal and noise.

\subsection{Local bandlimited orthogonalization}
The basic principle of the proposed approach is to first apply a simple bandpass filtering to the raw common shot gather in order to obtain an initial guess of primary reflections and ground-roll noise. Then we orthogonalize the initial guess of primary reflections and ground-roll noise to obtain a signal compensated primary reflection gather, and a signal-free ground-roll noise section. In order to make the local orthogonalization robust, we need first use a relative high LBF such that all the ground-roll noise is removed initially. This proposed workflow for attenuating ground-roll noise is termed as the \emph{local bandlimited orthogonalization}. The detailed workflow of the proposed approach is shown in Figure \ref{fig:flowchart}. As we can see, the total workflow of the proposed approach is fairly convenient to implement, because there are only two steps involved in the processing. First, using a conventional bandpass filtering. Second, using local signal-and-noise orthogonalization. As we stated in the last section, the local signal-and-noise orthogonalization is no more than solving a regularized division problem (equations \ref{eq:eq2} and \ref{eq:localortho}). Thus, the proposed approach can be conveniently used as an alternative in the industry. In the next section, we will use a typical dataset for demonstrating the effective performance of the proposed approach.
\begin{figure}[htb!]
  \centering
    \includegraphics[width=0.8\columnwidth]{Fig/flowchart}
	\caption{Workflow of the proposed ground-roll noise attenuation approach based on local bandlimited orthogonalization.}
   \label{fig:flowchart}
\end{figure}
\section{Example}
The dataset that we use to demonstrate the effectiveness of our proposed denoising approach is \wen{an open-source dataset, which has been widely used in the geophysics community \cite{yilmaz1987,carson2006}.} \dlo{borrowed from  and }\wen{This data }is referred to as the OZ-25 dataset \cite{carson2006}. \wen{One can easily download it either from the Seismic Unix (SU) website ($http://www.cwp.mines.edu/cwpcodes/$) or from the Madagascar software website ($www.ahay.org$, \cite{mada2013}).} The raw data in common shot domain is shown in Figure \ref{fig:field}. \wen{The temporal sampling rate is 0.002s and the spatial sampling rate is 0.05km. The shot location is located at the middle of the receiver array, thus the shot record has a symmetric form. There are 81 traces (receivers) in the shot record and the offset ranges from -2km to 2km.} The OZ-25 dataset is a typical dataset suitable for testing the ground-roll noise attenuation performance because of several reasons. First,  there is a large amount of ground-roll noise contaminating this dataset. It is obvious that most of the primary reflections are covered by this coherent ground-roll noise. Secondly, the reflections are highly non-stationary. We can clearly see that the amplitude of the reflections are variable in the range of the whole gather. Because of the large amplitude range of primary reflections, it can be effectively used to test the primary reflections preservation properties of a certain denoising algorithm.

\dlo{Figures \ref{fig:field-ortho-0} and \ref{fig:dif-ortho-0} show the denoised section and noise section using the proposed approach.} We locally orthogonalize the denoised section and noise section that come from the bandpass filtering using $fl=25$ Hz. The initial guess of the primary reflections and ground-roll noise are shown in Figures \ref{fig:field-1-0} and \ref{fig:dif-1-0}. \wen{Figures \ref{fig:field-ortho-0} and \ref{fig:dif-ortho-0} show the denoised section and noise section using the proposed approach.} The denoised data using the proposed approach shows excellent result, because most of the ground-roll noise have been removed but no primary reflections energy is damaged.

\wen{We also apply the widely used adaptive subtraction method to the field data and show its performance in Figures \ref{fig:field-3-0} and \ref{fig:dif-3-0}. Figures \ref{fig:field-3-0} and \ref{fig:dif-3-0} correspond to the denoised data and removed noise, respectively. It is obvious that there is some residual ground-roll noise existing in the denoised data and the noise section contains significant useful reflections, especially for the shallow part.}

We zoom several parts from the denoised sections and noise sections using different approaches and show them in Figures \ref{fig:zooma-1,zooma-2,zooma-ortho,zooma-3} and \ref{fig:zoomb-1,zoomb-2,zoomb-ortho,zoomb-3}. Figure \ref{fig:zooma-1,zooma-2,zooma-ortho,zooma-3} shows the zoomed denoised sections for the frame box A, as shown in Figures \ref{fig:field-1-0},\ref{fig:field-2-0}\dlo{ and }\wen{, }\ref{fig:field-ortho-0}, \wen{and \ref{fig:field-3-0},} respectively. We can see there is an obvious primary reflections recovery using the proposed approach by comparing Figures \ref{fig:zooma-1} and \ref{fig:zooma-ortho}. There is also an obvious decrease of noise using the proposed approach by comparing Figures \ref{fig:zooma-2} and \ref{fig:zooma-ortho}. \wen{It is more obvious that the adaptive subtraction method causes some residual dipping ground-roll noise energy by comparing Figures \ref{fig:zooma-ortho} and \ref{fig:zooma-3}.}

Figure \ref{fig:zoomb-1,zoomb-2,zoomb-ortho,zoomb-3} shows the zoomed noise sections for frame box B, as shown in Figures \ref{fig:dif-1-0},\ref{fig:dif-2-0}\dlo{ and}\wen{, } \ref{fig:dif-ortho-0},\wen{and \ref{fig:dif-3-0},} respectively. Please note that there is a decrease of primary reflections using the proposed approach, comparing Figures \ref{fig:zoomb-1} and \ref{fig:zoomb-ortho}, and there is an increase of noise removal using the proposed approach, comparing Figures \ref{fig:zoomb-2} and \ref{fig:zoomb-ortho}. \wen{The proposed approach and the adaptive subtraction method are very similar in this selected region. There is a slight amount of useful energy in Figure \ref{fig:zoomb-ortho} but hopefully not significant, considering the overall denoising performance. The ground-roll noise energy in Figure \ref{fig:zoomb-ortho}, however, is a bit stronger than that in Figure \ref{fig:zoomb-3}.} These observations indicate that compared with bandpass filtering with $fl=25$ Hz, the proposed approach preserves much more useful energy, and compared with bandpass filtering with $fl=10$ Hz, the proposed method removes much more ground-roll noise. \wen{Compared with the traditional adaptive subtraction method, the proposed approach can obtain a generally better performance}.

Figure \ref{fig:field-fs} shows a comparison of the average spectrum of all the traces for different data. \dlo{The black solid line denotes the average spectrum of raw data. The green dash line corresponds to the proposed approach. The red dot dash line corresponds to $fl=25$ Hz. The yellow long dash line corresponds to $fl=10$ Hz. We can see obviously that there is a removal of ground-roll noise spectrum from the black solid and yellow long dash lines to the green dash line. There is also a spectrum boost of the primary reflections from the red dot dash line to green dash line.}\wen{The black solid line denotes the average spectrum of raw data. The green dashed line corresponds to the proposed approach. The red dot-dashed line corresponds to the high-pass filtering with $fl=25$ Hz. The yellow long-dashed line corresponds to the high-pass filtering with $fl=10$ Hz. The blue dotted line corresponds to the adaptive subtraction method. We can see obviously that there is a removal of ground-roll noise spectrum from the black solid and the yellow long-dashed lines to the green dashed line.  There is also a spectrum boost of the primary reflections from the red dot-dashed line to the green dashed line. There exists several spectrum notches in the blue dotted line, which indicates that there is still a mixture of useful reflections and ground-roll noise after applying the adaptive subtraction method.}

\section{Conclusions}
We have proposed a novel local bandlimited  orthogonalization approach for removing highly non-stationary ground-roll noise, which can remove most of ground-roll noise without harming the useful primary reflections. We orthogonalize the initial guess of primary reflections and ground-roll noise using local signal-and-noise orthogonalization. The initial guess of primary reflections and ground-roll noise are bandlimited data from a common bandpass filtering with a relatively high LBF such that all the ground-roll noise is removed during the initial guess. The proposed approach can solve the frequency-mixing problem when applying a simple bandpass filtering. The proposed approach can guarantee that the least amount of useful primary reflections is lost in the noise section. The procedure of the proposed approach is fairly convenient to implement because only a bandpass filtering and a regularized division between the initially denoised signal and initial noise are used. We have used an open-source field dataset to demonstrate the successful performance of the proposed approach in real data processing.

\begin{figure}[htb!]
  \centering
    \includegraphics[width=.42\columnwidth]{field/Fig/field}
	\caption{Raw OZ-25 field data, borrowed from \cite{carson2006}.}
   \label{fig:field}
\end{figure}

\begin{figure}[htb!]
  \centering
    \subfigure[]{\includegraphics[width=0.41\columnwidth]{field/Fig/field-1-0}
    \label{fig:field-1-0}}
    \subfigure[]{\includegraphics[width=0.41\columnwidth]{field/Fig/dif-1-0}
    \label{fig:dif-1-0}}   
    \subfigure[]{\includegraphics[width=0.41\columnwidth]{field/Fig/field-2-0}
    \label{fig:field-2-0}}
    \subfigure[]{\includegraphics[width=0.41\columnwidth]{field/Fig/dif-2-0}
    \label{fig:dif-2-0}}         
	\caption{(a) Bandpass filtered data (fl=25 Hz). (b) Difference section corresponding to (a). (c) Bandpass filtered data (fl=10 Hz). (d) Difference section corresponding to (c).}
   \label{fig:field-1-0,dif-1-0,field-2-0,dif-2-0}
\end{figure}

\begin{figure}[htb!]
  \centering
    \subfigure[]{\includegraphics[width=0.41\columnwidth]{field/Fig/field-ortho-0}
    \label{fig:field-ortho-0}}
    \subfigure[]{\includegraphics[width=0.41\columnwidth]{field/Fig/dif-ortho-0}
    \label{fig:dif-ortho-0}}   
    \subfigure[]{\includegraphics[width=0.41\columnwidth]{field/Fig/field-3-0}
    \label{fig:field-3-0}}
    \subfigure[]{\includegraphics[width=0.41\columnwidth]{field/Fig/dif-3-0}
    \label{fig:dif-3-0}}         
	\caption{(a) Denoised data using the proposed approach. (b) Noise section corresponding to (a). (c) Denoised data using the adaptive subtraction approach. (d) Noise section corresponding to (c).}
   \label{fig:field-ortho-0,dif-ortho-0,field-3-0,dif-3-0}
\end{figure}

\begin{figure}[htb!]
  \centering
    \subfigure[]{\includegraphics[width=0.38\columnwidth]{field/Fig/zooma-1}
    \label{fig:zooma-1}}
    \subfigure[]{\includegraphics[width=0.38\columnwidth]{field/Fig/zooma-2}
    \label{fig:zooma-2}}   
    \subfigure[]{\includegraphics[width=0.38\columnwidth]{field/Fig/zooma-ortho}
    \label{fig:zooma-ortho}}
    \subfigure[]{\includegraphics[width=0.38\columnwidth]{field/Fig/zooma-3}
    \label{fig:zooma-3}}         
	\caption{(a)-(d) Zoomed denoised section comparisons for frame box A (as shown in Figures \ref{fig:field-1-0},\ref{fig:field-2-0} , \ref{fig:field-ortho-0}, and \ref{fig:field-3-0}, respectively). Note the primary reflections recovery from (a) to (c) and the noise decrease from (b) to (c). There is obvious residual ground-roll noise existing in (d).}
   \label{fig:zooma-1,zooma-2,zooma-ortho,zooma-3}
\end{figure}

\begin{figure}[htb!]
  \centering
    \subfigure[]{\includegraphics[width=0.38\columnwidth]{field/Fig/zoomb-1}
    \label{fig:zoomb-1}}
    \subfigure[]{\includegraphics[width=0.38\columnwidth]{field/Fig/zoomb-2}
    \label{fig:zoomb-2}}   
    \subfigure[]{\includegraphics[width=0.38\columnwidth]{field/Fig/zoomb-ortho}
    \label{fig:zoomb-ortho}}
    \subfigure[]{\includegraphics[width=0.38\columnwidth]{field/Fig/zoomb-3}
    \label{fig:zoomb-3}}         
	\caption{(a)-(d) Zoomed noise section comparisons for frame box B (as shown in Figures \ref{fig:dif-1-0},\ref{fig:dif-2-0}, \ref{fig:dif-ortho-0}, and \ref{fig:dif-3-0}, respectively). Note the decrease of primary reflections from (a) to (c) and the increase of noise removal from (b) to (c). (c) and (d) are very similar in this zoomed region.}
   \label{fig:zoomb-1,zoomb-2,zoomb-ortho,zoomb-3}
\end{figure}

\begin{figure}[htb!]
  \centering
    \includegraphics[width=0.9\columnwidth]{field/Fig/field-fs}
	\caption{Comparisons of the average spectrum of all the traces. \dlo{Black solid line denotes the average spectrum of raw data. Green dash line corresponds to the proposed approach. Red dot dash line corresponds to $fl=25$ Hz. Yellow long dash line corresponds to $fl=10$ Hz. Note the removal of ground-roll noise spectrum from the black solid and yellow long dash lines to the green dash line, and the primary reflections spectrum boost from the red dot dash line to green dash line.}\wen{The black solid line denotes the average spectrum of raw data. The green dashed line corresponds to the proposed approach. The red dot-dashed line corresponds to $fl=25$ Hz. The yellow long-dashed line corresponds to $fl=10$ Hz. The blue dotted line corresponds to the adaptive subtraction method. Note the removal of ground-roll noise spectrum from the black solid and the yellow long-dashed lines to the green dashed line, and the primary reflections spectrum boost from the red dot-dashed line to the green dashed line. There exists several spectrum notches in the blue dotted line, indicating a mixture of useful reflections and ground-roll noise after applying the adaptive subtraction method.} }
   \label{fig:field-fs}
\end{figure}

\section{Acknowledgments}
We would like to thank Qun Luo, Shan Qu, Jiang Yuan for constructive suggestions \wen{that improved the manuscript greatly}. Yangkang Chen appreciate\wen{s} Sergey Fomel for the inspiring discussions about local orthogonalization. \wen{The paper is reproducible within the Madagascar open-source platform \cite{mada2013}.} We are grateful to developers of the Madagascar software package for providing corresponding codes for testing the algorithms and preparing the figures. \wen{This work is partially supported by the Natural Science Fund of China (grant nos.:91330108, 41374121, and 61327013), the fundamental Research Funds for the Central Universities (grant no.: HIT.BRETIV.201314), the Program for New Century Excellent Talents in University (grant no.: NCET-11-0804), the China Postdoctoral Science Foundation (grant no.: 2014M561053), the Natural Science Foundation of Hebei Province (grant no.: F2013202254), and the Texas Consortium for Computational Seismology (TCCS).}

\bibliographystyle{IEEEtran}
\bibliography{groll}

### 2020-09-16 ieee_temp_groll/ieee_groll_r1.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\title{Ground-roll noise attenuation using a simple and effective approach based on local bandlimited orthogonalization}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{\IEEEauthorblockN{Yangkang Chen$^1$, Shebao Jiao$^2$, Jianwei Ma$^3$, Hanming Chen$^2$, Yatong Zhou$^4$, and Shuwei Gan$^2$}\\
$^1$\IEEEauthorblockA{Jackson School of Geosciences,
The University of Texas at Austin,
University Station, Box X,
Austin, TX 78713-8924, USA,
Email: ykchen@utexas.edu}\\
$^2$\IEEEauthorblockA{State Key Laboratory of Petroleum Resources and Prospecting, 
China University of Petroleum, 
Fuxue Road 18th,
Beijing, China, 102200, 
Email: gsw19900128@126.com \& huichanming@126.com} \\
$^3$ \IEEEauthorblockA{Department of Mathematics,
Harbin Institute of Technology,
Harbin, China, 
jma@hit.edu.cn}\\
$^4$\IEEEauthorblockA{School of Electronic and Information Engineering,
Hebei University of Technology,
Xiping Road No. 5340, Beichen District,
Tianjin, China, 300401,
zyt@hebut.edu.cn}\\
}
\maketitle
%512375919@qq.com

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	Defined by myself 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
\DeclareRobustCommand{\old}[1]{}
\DeclareRobustCommand{\new}[1]{#1}
\DeclareRobustCommand{\old}[1]{\color{blue}{\sout{#1}}\color{black}{}}
\DeclareRobustCommand{\new}[1]{\color{red}{\textit{#1}}\color{black}{}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	Defined by myself 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
% The bandpass filtering is a common way for estimating the ground-roll noise in land seismic data because of the low-frequency property of ground-roll noise. However, the frequency-overlap problem makes bandpass filtering inconvenient or even impossible to achieve a successful removal of ground-roll noise.  In this paper, we propose a novel band-limited orthogonalization approach for removing ground-roll noise without harming useful primary reflections. We orthogonalize the initially denoised signal via bandpass filtering with a relatively high low-bound-frequency (LBF), and the corresponding noise section that contains loss of primary reflections, using local signal-and-noise orthogonalization.  The local orthogonalization guarantees that the least coherent primary reflections are lost in the noise section. The procedure of the proposed approach is very convenient to implement because only a bandpass filtering and a regularized division between the initially denoised signal and initial noise are used. An open-source field dataset demonstrates a successful performance using the proposed approach. 
Bandpass filtering is a common way to estimate ground-roll noise on land seismic data, because of the relatively low frequency content of ground-roll. However, there is usually a frequency overlap between ground-roll and the desired seismic reflections that prevents bandpass filtering alone from effectively removing ground-roll without also harming the desired reflections. We apply a bandpass filter with a relatively high upper bound to provide an initial, imperfect separation of ground-roll and reflection signal. We then apply a technique called 'local orthogonalization' to improve the separation. The procedure is easily implemented, since it involves only bandpass filtering and a regularized division of the initial signal and noise estimates. We demonstrate the effectiveness of the method on an open-source set of field data.
\end{abstract}

\begin{keywords}
Ground-roll noise, bandpass filtering, local orthogonalization, regularized division
\end{keywords}

\section{Introduction} 
Ground-roll noise is a type of coherent seismic noise, with a high amplitude, low frequency, and low velocity. It is often the strongest mode of coherent noise for land seismic surveys. Ocean bottom node (OBN) based marine seismic surveys may also contain this type of noise \cite{yangkang20142}. Ground-roll noise is a type of source-generated noise and can be scattered by near-surface heterogeneities.  The ground-roll noise often masks the shallow reflections at short offset, and deep reflections at larger offset \cite{claerbout1983,saatilar1988,henley2003}, and must be removed before the subsequent processing tasks. Instead of being incoherent along the spatial direction like random noise \cite{wencheng2015asa,yangkang2015}, the ground-roll noise is usually coherent along the spatial dimension, which can assist in its removal using simple signal processing methods.  There has been a lot of research about removing ground-roll noise published in the literature, and many researchers have proposed different methods for handling the ground-roll noise problem \cite{shieh1990,brown2000}. Most of the ground-roll noise removal approaches either fail to remove all the ground-roll noise or remove much useful primary reflection energy. An efficient and effective technique for removing ground-roll noise is always in demand.

The simplest and most straightforward way for removing ground-roll noise might be bandpass filtering. Because of the low-frequency property of ground-roll, a simple high-pass filter is often applied to the seismic record to attenuate the ground-roll noise. However, the low-bound-frequency (LBF) for the bandpass filter is not easy to choose, because higher LBF will damage primary reflections while lower LBF will fail to remove enough ground-roll noise. This issue exists because of the frequency overlap of primary reflections and ground-roll noise. One way to solve this problem is to use matched filtering. The low-pass data is used as an initial guess for the ground-roll noise and then a least squares (LS) based matching filter is calculated to match the initial ground-roll noise to the raw seismic data best \cite{carson2006,stephen2007,halliday2010}. The matched ground-roll noise is then subtracted from raw seismic data to obtain the output. This adaptive subtraction method depends highly on the initial prediction of the ground-roll noise. Besides, in the case of highly non-stationary primary reflections and ground-roll noise, a conventional stationary matched filtering will fail to obtain an acceptable result.

%\cite{james1968} proposed the multichannel stacking filters for attenuating those types of noise which \old{occur}\new{occurred} at relatively well-determined points on neighbor traces, such as the ground-roll noise. \cite{prasad1980} studied and compared the performance of the least-mean-squares (LMS) adaptive filter, the adaptive lattice filter, and the adaptive Kalman filter identifier.  \cite{cahit1983} proposed an effective surface wave removal approach termed as vibroseis whitening (VSW) approach, which was tailed specifically for vibroseis data. The VSW approach was based on the application of time-varying amplitude scaling before vibroseis crosscorrelation. This scaling resulted in a signal-to-noise ratio (SNR) improvement equal\old{s} to the gain expected from crosscorrelation. This approach \old{is}\new{was} also termed as the spectral balancing approach. \cite{ruhi1988} proposed a one-dimensional, linear frequency-modulated matched filter for removing ground-roll noise. This approach works well when the frequency bands of seismic reflections and ground-roll noise overlap. \cite{carson2006} proposed to use curvelet transform to remove ground-roll noise by a two-step process. The first step is to identify the ground-roll noise from the seismic data using an appropriate approach and then separate the signal and ground-roll noise using a block-coordinate relaxation method that seeks the sparest set for weighted curvelet coefficients of the ground-roll noise and the sought-after reflectivity. \cite{ruhi1994} proposed an adaptive lattice filter for attenuating ground-roll noise. The lattice filter has the same order of computational complexity as the LMS adaptive filter but enjoys a faster convergence rate.  \new{\cite{regone1998} and \cite{ozbek2000} proposed to use acquisition-based suppression schemes to attenuate the ground-roll noise based on the use of recording arrays. \cite{stephen2007} proposed a polarization filtering approach to attenuate ground-roll noise, in which they combined statics, signal-to-noise ratio, and eigenimages to construct the ground-roll noise model, followed by adaptive subtraction.}  \new{There is a type of ground-roll noise attenuation approaches that are based on the seismic interferometry \cite{halliday20072,halliday20092}.} \cite{yanwei2009} proposed an interferometric method to predict and subtract surface waves in seismic data. Instead of the traditional frequency-based one-step prediction, the interferometric method uses a multi-prediction and subtraction strategy to attenuate more ground-roll noise and preserve more useful energy. However, the implementation requires a careful parameters designing and tuning process. \new{\cite{halliday2010} also proposed an interferometric ground-roll removal approach. They used seismic interferometry to estimate scattered ground-roll noise between pairs of receiver locations.}   A recently proposed approach by \cite{liuyang2012} utilized a time-frequency decomposition technique to separate ground-roll noise and primary reflections. The basic principle of this method is that instead of using a global frequency difference between the primary reflections and ground-roll noise, it uses the local time-frequency property of ground-roll noise to achieve the noise free data. 
In this paper, we proposed a simple but effective way for removing all the ground-roll noise without harming useful reflections. We first apply a simple bandpass filter to raw seismic data in order to remove all the ground-roll noise (thus the LBF should be a little bit high to guarantee no ground-roll noise left in the data). Then because of loss of useful primary reflections, we use local signal-and-noise orthogonalization proposed recently by \cite{yangkang2015ortho} to orthogonalize the primary reflections and ground-roll noise in order to restore the lost useful signals to the initial bandpass filtered data. The local orthogonalization algorithm was initially proposed to compensate for the useful energy loss during a traditional random noise attenuation process. The basic principle of the local orthogonalization methodology is to assume that the useful signal and noise should be orthogonal to each other and then orthogonalize the two components by formulating a regularized inverse problem. We bring the same strategy to this paper to compensate for the energy loss in a simple bandpass filtering based ground-roll noise attenuation approach. The performance of the proposed approach on the pre-stack dataset appears successful and also indicate a broader application of the orthogonalization methodology in removing various types of noise.

\section{Method}
\subsection{Bandpass filtering and the frequency-overlap problem}
A bandpass filtering process can be simply summarized as:
\begin{equation}
\label{eq:bandpass}
\mathbf{\hat{d}} = \mathbf{F}^{-1} \mathbf{B}_{fl,fh} \left(\mathbf{F} \mathbf{d}\right),
\end{equation}
where $\mathbf{d}$ and $\mathbf{\hat{d}}$ denote the unfiltered and filtered data, respectively. $\mathbf{F}$  and $\mathbf{F}^{-1}$ denotes a pair of forward and inverse Fourier transforms. $\mathbf{B}_{fl,fh}$ denotes the bandpass filter with a high-bound-frequency (HBF) $fh$, and low-bound-frequency (LBF) $fl$. For the purpose of removing ground-roll noise, $fh$ is usually chosen as Nyquist frequency, the only parameter to choose is the LBF. The actual filtering in this paper is implemented by recursive  (Infinite Impulse Response) convolution in the time domain following the Butterworth algorithm.

The problem of bandpass filtering for removing ground-roll noise is the difficulty of choosing an optimal LBF, because of the frequency-overlap problem of ground-roll noise and primary reflections. Figure \ref{fig:field-1-0,dif-1-0,field-2-0,dif-2-0} shows a demonstration of the frequency-overlap problem. When $fl=25$ Hz, all the ground-roll noise has been removed, and the denoised section (Figure \ref{fig:field-1-0}) does not contain any ground-roll noise. However, the noise section (Figure \ref{fig:dif-1-0}) contains a lot of coherent signals: both direct waves and primary reflections. When $fl=10$ Hz, the noise section (Figure \ref{fig:dif-2-0}) does not contains any coherent reflection or direct waves, however, the denoised section (Figure \ref{fig:field-2-0}) still contains a large amount of ground-roll noise.

One of the most commonly used approaches to solve the frequency-overlap problem is to use matched filtering. The removed ground-roll noise after a common bandpass filtering is used as an initial guess for the ground-roll noise. A least squares (LS) based matching filter is then calculated to match the initial ground-roll noise to the raw seismic data based on the least-energy assumption. The matched ground-roll noise is then subtracted from the raw seismic data to obtain the ground-roll noise attenuated profile. However, this adaptive subtraction method depends highly on the initial prediction of the ground-roll noise. Besides, in the case of highly non-stationary primary reflections and ground-roll noise, a conventional stationary matched filtering is not physically reasonable, and thus will not likely provide a satisfactory performance. In the next sections, we will introduce a novel approach for attenuating ground-roll noise based on bandpass filtering, which can remove more ground-roll noise and preserve more useful primary reflections.

\subsection{Local signal-and-noise orthogonalization}
%\cite{yangkang2014ortho} proposed a local orthogonalization approach for retrieving useful signals from the noise section. 
The principle of our technique is to locally orthogonalize the denoised signal and noise sections in order to ensure no coherent primary reflections will be lost in the noise section. %\cite{yangkang2014ortho} mainly dealt with random noise attenuation problem.
Here, we propose to apply the algorithm to the ground-roll noise removal problem. The orthogonalization based approach can be summarized as: 
\begin{align}
\label{eq:news}
\mathbf{s}&=(\mathbf{I}+\mathbf{W})\mathbf{\hat{d}},\\
\label{eq:newn}
\mathbf{n}&=\mathbf{\hat{d}}-(\mathbf{I}+\mathbf{W})\mathbf{\hat{d}}.
\end{align}
Here, $\mathbf{s}$ and $\mathbf{n}$ are the output denoised signal and noise sections. $\mathbf{I}$ denotes an identity matrix. $\mathbf{W}$ denotes a diagonal operator composed of the local orthogonalization weight (LOW) vector.  When $w=\frac{\mathbf{n}_0^T\mathbf{s}_0}{\mathbf{s}_0^T\mathbf{s}_0}$, $\mathbf{s}_0$ and $\mathbf{n}_0$ denoting the initial guess of signal and noise, $w$ is the global orthogonalization weight (GOW), it can be proved \ref{eq:localortho} that the following scaled signal $\mathbf{s}_0$ and corresponding noise $\mathbf{n}_0$ are orthogonal to each other in a global sense: %\cite{yangkang2014ortho}:
%\begin{figure}[htb!]
%  \centering
%  \includegraphics[width=0.32\columnwidth,height=0.32\columnwidth]{Fig/demo}
%  \caption{Demonsration of global orthogonalization.}
%   \label{fig:demo}
%\end{figure}

\begin{align}
\label{eq:ortho1}
\hat{\mathbf{n}} &= \mathbf{n}_0 - w\mathbf{s}_0, \\
\label{eq:ortho2}
\hat{\mathbf{s}} &= \mathbf{s}_0 + w\mathbf{s}_0.
\end{align}
In a local sense, the LOW can be define as:
      \begin{equation}
        \label{eq:eq2}
          w_m(t) = \frac{\displaystyle\sum_{i=t-m/2}^{t+m/2} s_0(i) n_0(i)}{\displaystyle\sum_{i=t-m/2}^{t+m/2} s_0^2(i)},
      \end{equation}
where $w_m(t)$ denotes the LOW for each temporal point $t$ with a local window length $m$. $s_0(t)$ and $n_0(t)$ here denote the initially estimated signal and noise for each point $t$.

In order to better control the locality and smoothness of LOW, we follow the local-attribute scheme introduced by \cite{fomel2007localattr}: %and first turn the orthogonalization problem into an optimization problem:
\begin{equation}
\label{eq:localortho}
\mathbf{w} = \arg\min_{\mathbf{\tilde{w}}} \parallel \mathbf{n}_0 - \mathbf{S}_0\mathbf{\tilde{w}}\parallel_2^2. %+ \mathbf{R}(\mathbf{w})
\end{equation}
Here, $\mathbf{w}$ is the LOW, $\mathbf{S}_0$ is a diagonal matrix composed of the initial estimated signal $\mathbf{s}_0$: $\mathbf{S}_0=diag(\mathbf{s}_0)$.
Then, we solve the least-squares problem \ref{eq:localortho} with the help of shaping regularization (a novel regularization framework for obtaining a faster convergence and a better control on the model behavior, originated from the seismic data processing community \cite{fomel2007shape}) using a local-smoothness constraint:
\begin{equation}
\label{eq:shape}
\mathbf{w} = [\lambda^2\mathbf{I} + \mathcal{T}(\mathbf{S}_0^T\mathbf{S}_0-\lambda^2\mathbf{I})]^{-1}\mathcal{T}\mathbf{S}_0^T\mathbf{n}_0,
\end{equation}
where $\mathcal{T}$ is a triangle smoothing operator and $\lambda$ is a scaling parameter set as $\lambda  = \Arrowvert\mathbf{S}_0^T\mathbf{S}_0\Arrowvert_2$ \cite{fomel2007localattr}. The triangle smoothing operator was introduced in detail in \cite{fomel2007shape}. It should be mentioned that solution of equation \ref{eq:localortho} corresponds to a regularized division (an element-wise division between two vectors can be treated as an inverse problem with some constraints in order to ensure the stability) between the two vectors $\mathbf{n}_0$ and $\mathbf{s}_0$ and it can be solved using any regularization approach, not limited to the shaping regularization strategy shown in equation \ref{eq:shape}. Thus it is fairly convenient to implement the local orthogonalization between initial signal and noise. A more detailed mathematical description about the local orthogonalization methodology can be found in \cite{yangkang2015ortho} and a demonstration about the physical meaning of orthogonalization can be found in the Appendix A in \cite{yangkang2015ortho}.

\subsection{Local bandlimited orthogonalization}
The basic principle of the proposed approach is to first apply a simple bandpass filter to the raw common shot gather in order to obtain an initial guess of primary reflections and ground-roll noise. Then we orthogonalize the initial guess for primary reflections and ground-roll noise to obtain a signal compensated primary reflection gather, and a signal-free ground-roll noise section. In order to make the local orthogonalization robust, we need first use a relative high LBF such that all the ground-roll noise is removed initially. This proposed workflow for attenuating ground-roll noise is termed \emph{local bandlimited orthogonalization}. The detailed workflow of the proposed approach is shown in Figure \ref{fig:flowchart}. As we can see, the total workflow of the proposed approach is fairly convenient to implement, because there are only two steps involved in the processing. First, we apply a conventional bandpass filter. Second, local signal-and-noise orthogonalization is applied. As we stated in the last section, the local signal-and-noise orthogonalization is no more than solving a regularized division problem (equations \ref{eq:eq2} and \ref{eq:localortho}). Thus, the proposed approach can be conveniently implemented by the industry. In the next section, we will use a typical dataset for demonstrating the effective performance of the proposed approach.
\begin{figure}[htb!]
  \centering
    \includegraphics[width=0.8\columnwidth]{Fig/flowchart}
	\caption{Workflow of the proposed ground-roll noise attenuation approach based on local bandlimited orthogonalization.}
   \label{fig:flowchart}
\end{figure}
\section{Example}
The dataset that we use to demonstrate the effectiveness of our proposed denoising approach is \new{an open-source dataset, which has been widely used in the geophysics community \cite{yilmaz1987,carson2006}.} \old{borrowed from  and }\new{This data }is referred to as the OZ-25 dataset \cite{carson2006}. \new{One can easily download it either from the Seismic Unix (SU) website ($http://www.cwp.mines.edu/cwpcodes/$) or from the Madagascar software website ($www.ahay.org$, \cite{mada2013}).} The raw data in common shot domain is shown in Figure \ref{fig:field}. \new{The temporal sampling rate is 0.002s and the spatial sampling rate is 0.05km. The shot location is located at the middle of the receiver array, thus the shot record has a symmetric form. There are 81 traces (receivers) in the shot record and the offset ranges from -2km to 2km.} The OZ-25 dataset is a typical dataset suitable for testing the ground-roll noise attenuation performance because of several reasons. First,  there is a large amount of ground-roll noise contaminating this dataset. It is obvious that most of the primary reflections are covered by this coherent ground-roll noise. Secondly, the reflections are highly non-stationary. We can clearly see that the amplitudes of the reflections are variable in the range of the whole gather. 
%Because of the large amplitude range of primary reflections, it can be effectively used to test the primary reflections preservation properties of a certain denoising algorithm.

\old{Figures \ref{fig:field-ortho-0} and \ref{fig:dif-ortho-0} show the denoised section and noise section using the proposed approach.} We locally orthogonalize the denoised section and noise section that come from the initial bandpass filtering using $fl=25$ Hz. The initial guess of the primary reflections and ground-roll noise are shown in Figures \ref{fig:field-1-0} and \ref{fig:dif-1-0}. \new{Figures \ref{fig:field-ortho-0} and \ref{fig:dif-ortho-0} show the denoised section and noise section using the proposed approach.} The denoised data using the proposed approach shows excellent result, because most of the ground-roll noise has been removed, but no primary reflections energy is damaged.

We also apply the widely used adaptive subtraction method to the field data and show its performance in Figures \ref{fig:field-3-0} and \ref{fig:dif-3-0}. Figures \ref{fig:field-3-0} and \ref{fig:dif-3-0} correspond to the denoised data and removed noise, respectively. It is obvious that there is some residual ground-roll noise remaining in the denoised data and that the noise section contains significant reflection energy, especially for the shallow part.

We zoom several parts from the denoised sections and noise sections and show them in Figures \ref{fig:zooma-1,zooma-2,zooma-ortho,zooma-3} and \ref{fig:zoomb-1,zoomb-2,zoomb-ortho,zoomb-3}. Figure \ref{fig:zooma-1,zooma-2,zooma-ortho,zooma-3} shows the zoomed denoised sections for the frame box A, as shown in Figures \ref{fig:field-1-0},\ref{fig:field-2-0}\old{ and }\new{, }\ref{fig:field-ortho-0}, \new{and \ref{fig:field-3-0},} respectively. We can see there is good primary reflection recovery using the proposed approach, by comparing Figures \ref{fig:zooma-1} and \ref{fig:zooma-ortho}. There is also an obvious decrease of noise using the proposed approach by comparing Figures \ref{fig:zooma-2} and \ref{fig:zooma-ortho}. \new{It is more obvious that the adaptive subtraction method leaves some residual dipping ground-roll noise energy by comparing Figures \ref{fig:zooma-ortho} and \ref{fig:zooma-3}.}

Figure \ref{fig:zoomb-1,zoomb-2,zoomb-ortho,zoomb-3} shows the zoomed noise sections for frame box B, as shown in Figures \ref{fig:dif-1-0}, \ref{fig:dif-2-0},  \ref{fig:dif-ortho-0}, and \ref{fig:dif-3-0}, respectively. Please note that there is a decrease of primary reflections using the proposed approach, comparing Figures \ref{fig:zoomb-1} and \ref{fig:zoomb-ortho}, and there is an increase of noise removal using the proposed approach, comparing Figures \ref{fig:zoomb-2} and \ref{fig:zoomb-ortho}. \new{The proposed approach and the adaptive subtraction method are very similar in this selected region. There is a slight amount of useful energy in Figure \ref{fig:zoomb-ortho} but hopefully not significant, considering the overall denoising performance. The ground-roll noise energy in Figure \ref{fig:zoomb-ortho}, however, is a bit stronger than that in Figure \ref{fig:zoomb-3}.} These observations indicate that compared with bandpass filtering with $fl=25$ Hz, the proposed approach preserves much more useful energy, and compared with bandpass filtering with $fl=10$ Hz, the proposed method removes much more ground-roll noise. \new{Compared with the traditional adaptive subtraction method, the proposed approach can obtain a generally better performance}.

Figure \ref{fig:field-fs} shows a comparison of the average spectrum of all the traces for different data. The black solid line denotes the average spectrum of raw data. The green line corresponds to the proposed approach. The red line corresponds to the high-pass filtering with $fl=25$ Hz. The pink line corresponds to the high-pass filtering with $fl=10$ Hz. Blue corresponds to the adaptive subtraction method. We can see obviously that there is a removal of ground-roll noise spectrum from the black and yellow lines to the green line.  There is also a spectrum boost of the primary reflections between red and green. There exists several spectral notches for the blue spectrum, which indicates that there is still an overlap of reflections and ground-roll noise after applying the adaptive subtraction method.

\section{Conclusions}
We have proposed a novel local bandlimited  orthogonalization approach for removing highly non-stationary ground-roll noise, which can remove most ground-roll noise without harming the useful primary reflections. We orthogonalize the initial guess of primary reflections and ground-roll noise using local signal-and-noise orthogonalization. The initial guess of primary reflections and ground-roll noise are bandlimited data from a common bandpass filtering with a relatively high LBF such that all the ground-roll noise is removed during the initial guess. The proposed approach can solve the frequency-overlap problem when applying a simple bandpass filtering. The proposed approach can guarantee that the least amount of useful primary reflections is lost in the noise section. The procedure of the proposed approach is fairly convenient to implement because only a bandpass filtering and a regularized division between the initially denoised signal and initial noise are used. We have used an open-source field dataset to demonstrate the successful performance of the proposed approach in real data processing.

\begin{figure}[htb!]
  \centering
    \includegraphics[width=.42\columnwidth]{field/Fig/field}
	\caption{Raw OZ-25 field data, borrowed from \cite{carson2006}.}
   \label{fig:field}
\end{figure}

\begin{figure}[htb!]
  \centering
    \subfigure[]{\includegraphics[width=0.40\columnwidth]{field/Fig/field-1-0}
    \label{fig:field-1-0}}
    \subfigure[]{\includegraphics[width=0.40\columnwidth]{field/Fig/dif-1-0}
    \label{fig:dif-1-0}}   
    \subfigure[]{\includegraphics[width=0.40\columnwidth]{field/Fig/field-2-0}
    \label{fig:field-2-0}}
    \subfigure[]{\includegraphics[width=0.40\columnwidth]{field/Fig/dif-2-0}
    \label{fig:dif-2-0}}         
	\caption{(a) Bandpass filtered data (fl=25 Hz). (b) Difference section corresponding to (a). (c) Bandpass filtered data (fl=10 Hz). (d) Difference section corresponding to (c).}
   \label{fig:field-1-0,dif-1-0,field-2-0,dif-2-0}
\end{figure}

\begin{figure}[htb!]
  \centering
    \subfigure[]{\includegraphics[width=0.40\columnwidth]{field/Fig/field-ortho-0}
    \label{fig:field-ortho-0}}
    \subfigure[]{\includegraphics[width=0.40\columnwidth]{field/Fig/dif-ortho-0}
    \label{fig:dif-ortho-0}}   
    \subfigure[]{\includegraphics[width=0.40\columnwidth]{field/Fig/field-3-0}
    \label{fig:field-3-0}}
    \subfigure[]{\includegraphics[width=0.40\columnwidth]{field/Fig/dif-3-0}
    \label{fig:dif-3-0}}         
	\caption{(a) Denoised data using the proposed approach. (b) Noise section corresponding to (a). (c) Denoised data using the adaptive subtraction approach. (d) Noise section corresponding to (c).}
   \label{fig:field-ortho-0,dif-ortho-0,field-3-0,dif-3-0}
\end{figure}

\begin{figure}[htb!]
  \centering
    \subfigure[]{\includegraphics[width=0.35\columnwidth]{field/Fig/zooma-1}
    \label{fig:zooma-1}}
    \subfigure[]{\includegraphics[width=0.35\columnwidth]{field/Fig/zooma-2}
    \label{fig:zooma-2}}   
    \subfigure[]{\includegraphics[width=0.35\columnwidth]{field/Fig/zooma-ortho}
    \label{fig:zooma-ortho}}
    \subfigure[]{\includegraphics[width=0.35\columnwidth]{field/Fig/zooma-3}
    \label{fig:zooma-3}}         
	\caption{(a)-(d) Zoomed denoised section comparisons for frame box A (as shown in Figures \ref{fig:field-1-0},\ref{fig:field-2-0} , \ref{fig:field-ortho-0}, and \ref{fig:field-3-0}, respectively). Note the primary reflections recovery from (a) to (c) and the noise decrease from (b) to (c). There is obvious residual ground-roll noise existing in (d).}
   \label{fig:zooma-1,zooma-2,zooma-ortho,zooma-3}
\end{figure}

\begin{figure}[htb!]
  \centering
    \subfigure[]{\includegraphics[width=0.35\columnwidth]{field/Fig/zoomb-1}
    \label{fig:zoomb-1}}
    \subfigure[]{\includegraphics[width=0.35\columnwidth]{field/Fig/zoomb-2}
    \label{fig:zoomb-2}}   
    \subfigure[]{\includegraphics[width=0.35\columnwidth]{field/Fig/zoomb-ortho}
    \label{fig:zoomb-ortho}}
    \subfigure[]{\includegraphics[width=0.35\columnwidth]{field/Fig/zoomb-3}
    \label{fig:zoomb-3}}         
	\caption{(a)-(d) Zoomed noise section comparisons for frame box B (as shown in Figures \ref{fig:dif-1-0},\ref{fig:dif-2-0}, \ref{fig:dif-ortho-0}, and \ref{fig:dif-3-0}, respectively). Note the decrease of primary reflections from (a) to (c) and the increase of noise removal from (b) to (c). (c) and (d) are very similar in this zoomed region.}
   \label{fig:zoomb-1,zoomb-2,zoomb-ortho,zoomb-3}
\end{figure}

\begin{figure}[htb!]
  \centering
    \includegraphics[width=0.8\columnwidth]{field/Fig/field-fs}
	\caption{Comparisons of the average spectrum of all the traces. The black line denotes the average spectrum of raw data. The green line corresponds to the proposed approach. The red line corresponds to $fl=25$ Hz. The pink line corresponds to $fl=10$ Hz. The blue line corresponds to the adaptive subtraction method. Note the removal of ground-roll noise spectrum from the black and pink lines to the green line, and the primary reflections spectrum boost from the red line to the green line. There exists several spectrum notches in the blue line, indicating a mixture of useful reflections and ground-roll noise after applying the adaptive subtraction method. }
   \label{fig:field-fs}
\end{figure}

\section{Acknowledgments}
We would like to thank Qun Luo, Shan Qu, Jiang Yuan, and two anonymous reviewers for constructive suggestions that improved the manuscript greatly. Yangkang Chen appreciates Sergey Fomel for the inspiring discussions about local orthogonalization. The paper is reproducible within the Madagascar open-source platform \cite{mada2013}. We are grateful to developers of the Madagascar software package for providing corresponding codes for testing the algorithms and preparing the figures. This work is partially supported by the Natural Science Fund of China (grant nos.:91330108, 41374121, and 61327013), the fundamental Research Funds for the Central Universities (grant no.: HIT.BRETIV.201314), the Program for New Century Excellent Talents in University (grant no.: NCET-11-0804), the China Postdoctoral Science Foundation (grant no.: 2014M561053), the Natural Science Foundation of Hebei Province (grant no.: F2013202254), and the Texas Consortium for Computational Seismology (TCCS).

\bibliographystyle{IEEEtran}
\bibliography{groll}

### 2020-09-16 ieee_temp_groll/reply_grsl.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\begin{center}
Reply to the reviews  of manuscript \\
\textbf{"Ground-roll noise attenuation using a simple and effective approach based on local bandlimited orthogonalization"} \\
by Yangkang Chen, Shebao Jiao, Jianwei Ma, Hanming Chen, Yatong Zhou, and Shuwei Gan
\end{center}

We thank the two referees for constructive suggestions. We have taken into account all the recommendations and have changed the paper accordingly.

\section{Referee 1}
\begin{enumerate}
\item \emph{line 14 page 2, please delete ‘only’ as it has already appeared in line 13.}\\
\textbf{Reply: We have removed "only".}

\item \emph{Please change ‘LFB’ in the workflow from figure 1 to ‘LBF’.}\\
\textbf{Reply: Thanks for pointing out the typo. We have corrected it in the workflow.}

\item \emph{How would you determine the LBF to find out if the fl (e.g. 25 Hz in this article) is enough to
remove all the ground rolls? Is it by trial and error or is there other ways to do it?}\\
\textbf{Reply: We determined the LBF by trials. Fortunately it is convenient to implement, and can obtain much more superior performance than simple bandpass filtering.}

\item \emph{In this article, you choose to use 25 Hz as the LBF. Will other values of LBF affect the
performance?}\\
\textbf{Reply: We have tried several different values of the LBF, and found out that the 25 Hz can obtain the best performance.}

\item \emph{It looks like you haven’t explain figure 3c and figure 3d in the first place, although they are then
used for the comparisons for several times.}\\
\textbf{Reply: Figures 3c and 3d denote the denoised and noise sections when $fl=10$ Hz. We have added an extra explanation for Figures 3c and 3d.}

\item \emph{Please further check grammar problems.}\\
\textbf{Reply: We have rechecked the grammar to minimize the inappropriate wording.}
\end{enumerate}

\section{Referee 2}
\begin{enumerate}
\item\emph{I noted that the principle author has just published a paper in Geophysics demonstrating this same technique applied to random noise. Because of the existence of this paper, I would like to see you refer to it more heavily, particularly in your introduction, and in the theory section, where you present the mathematics in a rather abbreviated form. If you're not going to go into more detail, then you should reference the Geophysics paper, particularly Appendix A, so that readers can satisfy themselves about the theoretical soundness of your work.}\\
\textbf{Reply: We have added the introduction about the previously published work and also significance of this paper. Since the page limit of the IEEE geosciences and remote sensing letters, we are not possible for going into detail the mathematical principles, but we do refer to the previously published methodology more heavily. For example: "The local orthogonalization algorithm was initially proposed to compensate for the useful energy loss during a traditional random noise attenuation process. The basic principle of the local orthogonalization methodology is to assume that the useful signal and noise should be orthogonal to each other and then orthogonalize the two components by formulating a regularized inverse problem. We bring the same strategy to this paper to compensate for the energy loss in a simple bandpass filtering based ground-roll noise attenuation approach." "A more detailed mathematical description about the local orthogonalization methodology can be found in [12] and a demonstration about the physical meaning of orthogonalization can be found in the Appendix A in [12]." Other unfamiliar nomenclatures are also given brief introduction.}

\item\emph{I have supplied an annotated pdf for your use. In most cases, I am suggesting alternate words or phrases to improve the style and the clarity for general readers.}\\
\textbf{Reply:  Thanks very much for your patient check. We have followed all the suggestions from you and have modified the paper accordingly. Besides, we recheck the paper in order to minimize the grammar mistakes and to make the paper more understandable to general readers. }

\item\emph{Your abstract needs to be completely rewritten to make it understandable by a general reader...I have supplied a possible alternative.}\\
\textbf{Reply:  We have rewritten the abstract following your suggestions.}

\item\emph{Your Figure 7 needs to be redone with much heavier lines and more visible colors. Also, it is not necessary to use different line types, if you use different colors for each plot line...that just confuses the issue. As an alternative, you could use black for all spectra and use different line types to distinguish them...}\\
\textbf{Reply: We have replotted Figure 7 to make the lines heavier and color more visible. We have made all the line types the same and re-describe each lines. }

\item\emph{When you talk about high-bound and low-bound frequencies here, you imply a sharp frequency cutoff, or 'boxcar' filter, whereas most actual filters have filter slopes, and thus need two 'high-bound' frequencies and two 'low-bound' frequencies. For a low-bound frequency cutoff, you would typically specify the lowest frequency for which the filter response is unity, as well as the even lower frequency for which the filter response is zero. This defines the filter taper zone.}\\
\textbf{Reply: The bandpass filtering algorithm used in the paper is the Butterworth algorithm. The desired bandwidth is specified by low and high frequencies. The actual filtering is implemented by recursive  (Infinite Impulse Response) convolution in the time domain. The frequency domain response is like a boxcar filter. The description of the bandpass filtering algorithm can also be found in}\\
\begin{url}
http://ahay.org/rsflog/index.php?/archives/313-Program-of-the-month-sfbandpass.html
\end{url}.\textbf{We also add some details in the main context.}

\item\emph{It's not clear to me what you mean here. The amplitude range of the reflections should not affect the noise separation}\\
\textbf{Reply: We have removed the sentence in order to avoid misunderstanding.}

\item\emph{It's not obvious to me what you mean by nonstationary, in this context. The usual meaning is that reflection amplitude and bandwidth diminishes with recording time. Variation of reflection amplitude with offset is not normally considered an aspect of stationarity.}\\
\textbf{Reply: Here, the "nonstationary" simply means that the seismic energy varies a lot for different parts of the data.}

\end{enumerate}

%\bibliographystyle{seg}
%\bibliography{halfthr}

### 2020-09-16 ndip/ieee.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\title{Robust non-stationary local slope estimation}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{H. Wang, G. Huang, and Y. Chen
\thanks{Y. Chen, G. Huang, and Y. Chen are with Zhejiang University.}
\thanks{The research is supported by the starting fund from Zhejiang University.}}
\maketitle

\DeclareRobustCommand{\old}[1]{}
\DeclareRobustCommand{\new}[1]{#1}
\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}

\begin{abstract}
The plane-wave destruction (PWD) method has been a widely used local slope estimation method in the seismic community. It is based on the discretization of the plane-wave partial differential equation (PWD) and the linearization of the PDE with respect to the local slope. Solving the linearized inverse problem for the slope perturbation is equivalent to solving a smoothness constrained optimization based on a shaping regularization method. The smoothness constraint in the shaping regularization is important in that it not only controls the stability and smoothness of the solution, i.e., slope perturbation, but also affects the accuracy and resolution of the solution. Traditional PWD algorithm is not easy to compromise the smoothness and resolution of the estimated local slope because it uses a stationary triangle smoothing operator as the shaping operator. Here, we propose to improve the robustness of the PWD algorithm by introducing a non-stationary triangle smoothing operator into the shaping regularization framework in order to adaptively constrain the solution according to the local signal reliability. The smoothing is weak in areas with a higher probability of signals and is strong in areas with a higher likelihood of noise. The smoothing radius can be adaptively estimated based on an optimization model, which is solved by a line-search method. The proposed new slope estimation method is referred to as a non-stationary method compared with the traditional stationary one. The effectiveness and benefits of the new slope estimation method are validated via several synthetic and field data examples.
\end{abstract}

\begin{keywords}
Seismic signal analysis, structural filtering, local slope
\end{keywords}

\section{Introduction}
The local slope is a seismic attribute that can be extracted from the raw data. It has been successfully applied in several geophysical processing and inverse problems, e.g., wavefield separation \cite{harlan1984signal,fomel2002pwd}, predictive painting \cite{fomel2010predictive}, velocity-independent seismic imaging \cite{fomel2007velocity}, regularized geophysical inversion \cite{fomel2007shape}, etc.

\new{The local slope is closely related with the seismic dip angle. Researchers have started the seismic dip estimation from last century. There are at least three-generations methods for calculating the seismic dip \cite{chopra2007volumetric}, e.g., (1) cross-correlation based methods \cite{browaeys2010local,aqrawi2012hybrid,aarre2013consistent}, (2) semblance-based discrete scanning methods \cite{marfurt19983,lou2019accurate}, (3) structure tensor-based methods \cite{hale2007local,wu2017directional,wang2018robust}.}

In the past decades, there have been a variety of slope estimation methods \new{based on the plane-wave theory}. The plane-wave destruction (PWD) method was originally proposed by \cite{claerbout1992pvi}. Fomel (2002) \cite{fomel2002pwd} proposed to use an implicit finite difference scheme to discretize the plane-wave equation, where an infinite impulse response (IIR) filter (also known as the all-pass filter) to approximate the phase-shift operator and transforms the plane-wave equation into a non-linear inverse problem. Hale (2007) \cite{hale2007local} proposed the structure-tensor, also known as the gradient tensor \cite{van1995estimators}, \old{based slope estimation method based}\new{where the slope estimation is based} on the assumption that eigenvector corresponding to the largest eigenvalue of the structure tensor \old{point}\new{points} to the structural direction.  Liu et al. (2015) \cite{liuyang2015} took advantage of the relation between 2D Hilbert transform and the derivatives of the seismic data and derive a fast non-iterative dip estimation method, which turns to be more robust than the PWD based slope estimation method in the case of noisy data \cite{yangkang2018gji3}. Chen et al. (2013) \cite{zhonghuan2013accelerated} accelerated the PWD method by deriving an analytical solution to the non-linear inverse problem based on the three-point all-pass approximation filter, thus the PWD method no longer requires outer-loop non-linear iterations and thus is significantly accelerated. Chen et al. (2013) \cite{zhonghuan2013omnidirectional} further improved the conventional PWD algorithm by proposing a circle-interpolating model that makes the PWD method avoid the aliasing issues, thereby well handling both vertical and horizontal structures.

The local slope of a seismic data can be used to compress the seismic events along the slope direction, i.e., to obtain an optimally sparse representation of the seismic data. This sparsification process is referred to as the seislet transform \cite{fomel2010seislet}. Since the seislet transform is based on the structure direction to compress the data, its sparsity in the transform domain highly depends on the accuracy of the estimated local slope. Chen (2016) \cite{yangkang2016emd} discussed the influence of the error of local slope estimation in the sparsity performance of the seislet transform, and developed a dip-separated processing strategy to deal with the limitation of the PWD algorithm in the estimation of conflicting dips.

One important application of slope is structural filtering. The basics of the structural filtering is to create a local window along the structural direction and then apply a mean/median filter within this local window. \new{Liu et al. (2010)} \cite{liuyang2010} proposed a trace-prediction way to create local windows along the structure direction by creating a third dimension with predicted traces following the slope. Gan et al. (2016) \cite{shuwei2016somf} developed a structure-oriented median filtering method to suppress the blending noise arise from the simultaneous-source acquisition, where the slope is estimated by transforming the NMO-picked velocities to the slope. Chen et al. (2019) \cite{sosvmf} developed a structure-oriented space-varying median filtering method to deal with the problem of unflattened events in the third  dimension when the slope of seismic data is not accurately estimated.

Another important application of slope is to regularize the inversion-based seismic imaging approaches, e.g., the least-squares reverse time migration (LSRTM) and full waveform inversion (FWI). Xue et al. (2016) \cite{zhiguang2016} developed a constrained LSRTM method to deal with the intense migration artifacts caused by the simultaneous-source shooting or insufficient spatial data sampling, where the smoothing operator along the structural direction is used as a shaping operator to constrain the smoothness of the geological structures. Qu et al. (2019) \cite{qushan2019geo} developed a directional total variation (DTV) method to constrain the velocity model during the FWI iteration so as to avoid being trapped into a local minimum. The DTV constraint is equivalent to the rotated traditional total variation following the dip angle of the geological structure.

Generally speaking, the PWD method has been a well-known slope estimation method in the exploration seismic community. However, the low anti-noise ability of the PWD method still limits its wide application in challenging situations where the random noise is strong \cite{curveletieee2016,yanan2014,weilin2017dlsp,shaohuan2018ieee,zhaoqiang2019tgrs,wang2019hankel}. From the parameter setting perspective, it is usually required to choose a large smoothing radius when dealing with a low signal-to-noise ratio so that the resulted local slope is sufficiently smooth, i.e., avoiding the unstable solution. However, a larger smoothing radius could degrade the fidelity of the estimated slope, resulting in a poor structural processing or constraint when applied subsequently for other tasks. Thus, the stationary fixed smoothing radius is rigid in tuning the performance of the PWD method. In this paper, we developed a novel non-stationary slope estimation method, where the triangle smoother used to regularize the smoothness of the slope is stretched and squeezed according to the signal reliability and complexity. For areas with higher signal reliability or a simpler structural complexity, we use a relatively smaller radius, and vice versa. More importantly, we introduce an adaptive smoothing radius estimation method based on an iterative optimization model. The non-stationary slope estimation with the adaptively estimated smoothing radius is tested via several synthetic and field datasets, which demonstrate a great potential of the proposed method in obtaining better performance in structurally filtering complex seismic data.

\subsection{Plane-wave destruction (PWD)}
The PWD algorithm is based on the plane-wave approximation of the wave equation:
\begin{equation}
\label{eq:plane}
\sigma \frac{\partial d}{\partial t} + \frac{\partial d}{\partial x} = 0,
\end{equation}
where $d$ is the wavefield, $t$ and $x$ denotes time and space, respectively, and $\sigma$ denotes the local slope.

A general solution to equation \ref{eq:plane} can be expressed as: 
\begin{equation}
\label{eq:plane}
d(t,x) = f(t-\sigma x),
\end{equation}
which indicates a two-point prediction filter in the frequency domain, i.e.,
\begin{equation}
\label{eq:plane1}
D(w,x) = e^{iw\sigma x}F(w),
\end{equation}
and
\begin{equation}
\label{eq:plane2}
D(w,x) = e^{iw\sigma }D(w,x-1) ,
\end{equation}
where $D(w,x)$ and $F(w)$ denote the spectrum of $d(t,x)$ and $f(t)$ in the frequency domain. It is clear that the two-point prediction filter to destruct equation \ref{eq:plane2} takes the form $[1,-e^{iw\sigma }]$.

Equation \ref{eq:plane2} can be further transformed into the Z-transform notation as: 
\begin{equation}
\label{eq:Z}
A(Z_t,Z_x) D(Z_t,Z_x) = 0,
\end{equation}
where 
\begin{equation}
\label{eq:Z1}
A(Z_t,Z_x) = (1-Z_x\frac{L(Z_t)}{L(1/Z_t)}),
\end{equation}
or 
\begin{equation}
\label{eq:Z2}
H(Z_t,Z_x) D(Z_t,Z_x) = 0,
\end{equation}
where 
\new{\begin{equation}
\label{eq:Z3}
H(Z_t,Z_x) = (L(1/Z_t)-Z_xL(Z_t)),
\end{equation}}
$A(Z_t,Z_x)$ and $H(Z_t,Z_x)$ are two different forms of the plane-wave destruction filter in the Z-transform domain. $L(Z_t)/L(1/Z_t)$ is referred to as the Thiran all-pass filter \cite{thiran1971recursive,fomel2002pwd,zhonghuan2013accelerated}.

\subsection{\old{Gaussian-Newton's}\new{Gauss-newton} method}
Thanks to the all-pass filter, the plane-wave equation is then transformed into a non-linear inverse problem. Thus, slope estimation is essentially to solve the non-linear inverse problem as expressed below:
\begin{equation}
\label{eq:nonlinear}
\mathbf{H}(\boldsymbol{\sigma})\mathbf{d}=\mathbf{0},
\end{equation}
where $\mathbf{H}(\boldsymbol{\sigma})$ denotes a convolutional operator and is a non-linear function with respect to the slope vector $\boldsymbol{\sigma}$. According to \old{Gaussian-Newton's}\new{Gauss-newton} method, equation \ref{eq:nonlinear} can be solved via
\begin{equation}
\label{eq:nonlinear2}
\boldsymbol{\sigma}_{n+1}=\boldsymbol{\sigma}_n-(\mathbf{J}^T\mathbf{J})^{-1}\mathbf{J}^T\mathbf{H}(\boldsymbol{\sigma}_n)\mathbf{d},
\end{equation}
where $\mathbf{J}$ is the Jacobian matrix with respect to variable vector $\boldsymbol{\sigma}$ corresponding to $\mathbf{H}(\boldsymbol{\sigma})\mathbf{d}$. Equation \ref{eq:nonlinear} indicates that during each non-linear iteration, there is an embedded iteration that aims to solve $(\mathbf{J}^T\mathbf{J})^{-1}$, which is the inversion of the \old{Hession matrix}\new{approximated Hessian matrix}. It is also equivalent to solving the following linear equation via a least-squares method:
\begin{equation}
\label{eq:nonlinear3}
\mathbf{H}(\boldsymbol{\sigma}_n)\mathbf{d} = \mathbf{J} \Delta \boldsymbol{\sigma}_n,
\end{equation}
where $\mathbf{J}$ can be expressed \old{\new{$\mathbf{J}=\mathbf{H}'(\boldsymbol{\sigma}_n)$}}\new{$\mathbf{J}=\mathbf{H}'(\boldsymbol{\sigma}_n)\mathbf{d}$}, $ \Delta \boldsymbol{\sigma}_n$ denotes the slope update during each non-linear iteration.  Here, $\mathbf{H}'$ denotes the derivative form of the PWD filter, e.g., each coefficient of $\mathbf{H}$ is taken a derivative.

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hyper}
   \label{fig:hyper}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hyper-n}
   \label{fig:hyper-n}}
\caption{Synthetic test. (a) Clean data. (b) Noisy data (SNR=1.56 dB). }
\label{fig:hyper,hyper-n}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hyper-dip}
  \label{fig:hyper-dip}}
  \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-dip}
  \label{fig:hypern-dip}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-dip2}
  \label{fig:hypern-dip2}}
  \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-dip3}
  \label{fig:hypern-dip3}}
\caption{Slope estimation results. (a) Estimated slope from the clean data with a constant smoothing radius $R=5$. (b) Estimated slope from the noisy data with a constant smoothing radius $R=8$. (c) Estimated slope from the noisy data with a constant smoothing radius $R=50$. (d) Estimated slope from the noisy data with the non-stationary smoothing radius map shown in Fig. \ref{fig:rectdip1}. Note that (b) and (c) use the smallest and largest smoothing radii of the non-stationary smoothing radius map. }
\label{fig:hyper-dip,hypern-dip,hypern-dip2,hypern-dip3}
\end{figure}

\begin{figure}[htb!]
 \centering
 \includegraphics[width=\columnwidth]{hyper/Fig/rectdip1}
  \caption{Adaptively estimated smoothing radius for non-stationary dip estimation.}
  \label{fig:rectdip1}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm1}
   \label{fig:hypern-sm1}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm2}
   \label{fig:hypern-sm2}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm3}
   \label{fig:hypern-sm3}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm4}
   \label{fig:hypern-sm4}}\\
\caption{Smoothing test. (a) Structurally smoothed using the slope estimated from the clean data (SNR=13.73 dB). (b) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius (SNR=11.80 dB). (c) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius (SNR=10.71 dB). (d) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius (SNR=13.11 dB).}
\label{fig:hypern-sm1,hypern-sm2,hypern-sm3,hypern-sm4}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm1-n}
   \label{fig:hypern-sm1-n}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm2-n}
   \label{fig:hypern-sm2-n}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm3-n}
   \label{fig:hypern-sm3-n}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm4-n}
   \label{fig:hypern-sm4-n}}\\
\caption{Smoothing test. (a)-(d) Removed noise corresponding to Figs. \ref{fig:hypern-sm1}-\ref{fig:hypern-sm4}.}
\label{fig:hypern-sm1-n,hypern-sm2-n,hypern-sm3-n,hypern-sm4-n}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-0}
   \label{fig:g-0}}
   \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-z-a}
   \label{fig:g-z-a}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-z-b}
   \label{fig:g-z-b}}
\caption{Field data example. (a) Raw field data. (b) Zoomed section A. (c) Zoomed section B.}
\label{fig:g-0,g-z-a,g-z-b}
\end{figure}

\begin{figure}[htb!]
\centering
\includegraphics[width=0.45\textwidth]{real2d/Fig/g-rectdip1}
\caption{Field data example. Non-stationary smoothing radius.}
\label{fig:g-rectdip1}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-dip1}
   \label{fig:g-dip1}}
   \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-dip2}
   \label{fig:g-dip2}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-dip3}
   \label{fig:g-dip3}}
\caption{Smoothing test of the field data example. (a) Slope estimated from the noisy data with a small constant smoothing radius $R=8$. (b) Slope estimated from the noisy data with a large constant smoothing radius $R=100$. (c) Slope estimated from the noisy data with non-stationary smoothing radius.}
\label{fig:g-dip1,g-dip2,g-dip3}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-0}
  \label{fig:g-sm1-0}}
  \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-0}
  \label{fig:g-sm2-0}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-0}
  \label{fig:g-sm3-0}}
\caption{Smoothing test of the field data example. (a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius. (b) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius. (c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius.}
\label{fig:g-sm1-0,g-sm2-0,g-sm3-0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-n}
  \label{fig:g-sm1-n}}
  \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-n}
  \label{fig:g-sm2-n}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-n}
  \label{fig:g-sm3-n}}
\caption{Smoothing test of the field data example. (a)-(c) Removed noise corresponding to Figs. \ref{fig:g-sm1-0}-\ref{fig:g-sm3-0}.}
\label{fig:g-sm1-n,g-sm2-n,g-sm3-n}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-z-a0}
 \label{fig:g-sm1-z-a0}}
 \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-z-a0}
 \label{fig:g-sm2-z-a0}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-z-a0}
 \label{fig:g-sm3-z-a0}}
\caption{Zoomed comparison of the field data example (frame box A). (a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius. (b) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius. (c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius.}
\label{fig:g-sm1-z-a0,g-sm2-z-a0,g-sm3-z-a0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-z-b0}
  \label{fig:g-sm1-z-b0}}
  \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-z-b0}
  \label{fig:g-sm2-z-b0}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-z-b0}
  \label{fig:g-sm3-z-b0}}
\caption{Zoomed comparison of the field data example (frame box B). (a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius. (b) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius. (c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius.}
\label{fig:g-sm1-z-b0,g-sm2-z-b0,g-sm3-z-b0}
\end{figure}

\subsection{Shaping regularization with non-stationary smoothing}
To ensure the smoothness and stability of the slope update, we use the following shaping regularization to solve the linear inverse problem expressed in equation \ref{eq:nonlinear3}:
\begin{equation}
\label{eq:linear}
\Delta \boldsymbol{\sigma}_n^{m} = \mathbf{S}\left[ \Delta \boldsymbol{\sigma}_n^{m-1} + \mathbf{J}^T\left( \mathbf{H}(\boldsymbol{\sigma}_n)\mathbf{d} - \mathbf{J}\Delta \boldsymbol{\sigma}_n^{m-1}\right)\right],
\end{equation}
where $\Delta \boldsymbol{\sigma}_n^{m}$ denotes the estimated $\Delta \boldsymbol{\sigma}_n$ after $m$th linear iteration. $\mathbf{S}$ is a shaping operator used to constrain the model behavior and ensure a fast convergence. The converged model based on the shaping regularization method is given as:
\begin{equation}
\label{eq:shape}
\hat{\Delta \boldsymbol{\sigma}_n} = \mathbf{T}[\lambda^2\mathbf{I} + \mathbf{T}^T(\mathbf{J}^T\mathbf{J}-\lambda^2\mathbf{I})\mathbf{T}]^{-1}\mathbf{T}^T\mathbf{J}^T\mathbf{H}(\boldsymbol{\sigma}_n)\mathbf{d},
\end{equation}
where $\mathbf{T}$ denotes a triangle smoothing operator. \new{In equation \ref{eq:linear}, the shaping operator is chosen as $\mathbf{S}=\mathbf{T}\mathbf{T}^T$. $\lambda$ is a scaling parameter that controls the relative scaling of the forward operator $\mathbf{J}$ \cite{fomel2007shape}. } The triangle smoothing operator takes the following form in the Z transform domain:
\begin{equation}
\label{eq:T}
T(Z) = B(Z)B(Z),
\end{equation} 
where $T(Z)$ and $B(Z)$ denote the triangle and rectangle smoothers in the Z-transform notations, respectively. The rectangle smoother can be expressed in the following way:
\begin{equation}
\label{eq:BZ}
B(Z)=\frac{1-Z^N}{1-Z} = 1 + Z + Z^2 +\cdots + Z^{N-1}.
\end{equation} 
Implementation of the rectangle smoothing \ref{eq:BZ} can be efficient when using a recursive strategy. For example, division by $1-Z$ corresponds to a causal integration operation in the time domain; multiplying \new{by} $1-Z^N$ in the numerator of equation \ref{eq:BZ} is equivalent to implementing the following recursion:
\begin{equation}
\label{eq:recur}
y_n = x_1 - x_{N},
\end{equation}
where $N$ denotes the smoothing radius. Thus, given a non-stationary distribution map of the smoothing radius, we can obtain a very fast implementation of the non-stationary smoothing following equations \ref{eq:T}-\ref{eq:recur}.

The non-stationary smoothing radius can either be defined with help of a priori information, or be calculated by utilizing the concept of signal reliability, e.g., introduced in \cite{liuyang2009tvmf} and \cite{sosvmf}. The signal reliability simply means the possibility of a point as a signal point. In the signal point, it is helpful to use a smaller smoothing radius for better signal preservation, and for a noise point, it is better to use a long smoothing radius for an exclusive removal of the noise.  Here, we introduce a new method for adaptively estimating the non-stationary smoothing radius based on optimization.

We can formulate the following optimization method in order to estimate the adaptive smoothing radius:
\new{\begin{equation}
\label{eq:nsm}
O= \parallel \mathcal{L}\left(\mathbf{T}(\mathbf{n})\mathbf{d}\right) - \mathcal{L}(\mathbf{d}_B) \parallel_2^2, 
\end{equation}}
where $O$ denotes the objective function of the optimization problem \cite{greer2018matching}. $\mathcal{L}$ denotes a local attribute estimator, e.g., the local frequency attribute \cite{fomel2007localattr}, $\mathbf{T}(\mathbf{n})$ denotes the triangle smoothing operator that is a function of the non-stationary smoothing radius vector $\mathbf{n}$, $\mathbf{d}$ denotes the input data, and $\mathbf{d}_B$ denotes a lowpass filter\new{, where the cut-off frequency could be chosen as the dominant frequency of the seismic data}. %The idea is similar to that was proposed in , where the low-frequency legacy seismic data is merged to the high-resolution data with a non-stationary smoothing. 
\new{The local attribute estimator is chosen as the local frequency operator, which is a local version of the instantaneous frequency operator. It transforms the direct division of the instantaneous frequency operator as a regularized inverse problem, which is then solved via the shaping regularization method. The smoothing operator $\mathbf{T}$ is expressed in equation \ref{eq:T} as a Z-transform form.  }

We use a simple line-search method for minimizing the objective function expressed in equation \ref{eq:nsm}:
\begin{equation}
\label{eq:nsm2}
\mathbf{n}_{m} = \mathbf{n}_{m-1} + \alpha_m \left( \mathcal{S}\left(\mathbf{T}(\mathbf{n})\mathbf{d}\right) - \mathcal{S}(\mathbf{d}_B) \right),
\end{equation}
where $\alpha_m$ denotes a step size, gradually decreasing a larger value, e.g., 0.8, to a smaller value, e.g., 0.05, for a fast convergence.

Note that the adaptive smoothing radius estimation method introduced here is an option to obtain a rough estimate of the optimal smoothing radius from a raw seismic data. In later examples, we will demonstrate the effectiveness of the optimization in estimating plausible smoothing radius distribution. However, an in-depth analysis of the optimization in terms of the theoretical implications, stability, and convergence is beyond the scope of this paper. Other options on obtaining non-stationary smoothing radius are worth investigating. To summarize, incorporating this adaptive smoothing radius estimation method into the recursion-based fast non-stationary smoothing can help better constrain the slope estimation by better compromising the smoothness of the result and the fidelity of the estimated slope.

\section{Examples}
We use several synthetic and field data examples to demonstrate how the new slope estimation with non-stationary smoothing radius help improve the accuracy of the slope estimation, especially in the case of strong random noise.

The first example is a synthetic test. The synthetic data is shown in Fig. \ref{fig:hyper,hyper-n} with the clean data on the left and the noisy data on the right. The signal-to-noise ratio (SNR) of the noisy data is 1.56 dB, based on the definition expressed below \cite{benfeng2019efficient}:
\begin{equation}
\label{eq:diff}
\text{SNR}=10\log_{10}\frac{\Arrowvert \mathbf{d} \Arrowvert_2^2}{\Arrowvert \mathbf{d} -\mathbf{d}_t\Arrowvert_2^2},
\end{equation}
where $\mathbf{d}$ denotes the ground-truth solution, i.e., the clean data in Fig. \ref{fig:hyper}, \new{and} $\mathbf{d}_t$ denotes the target signal to be evaluated.

A comparison of different slope estimation results is shown in Fig. \ref{fig:hyper-dip,hypern-dip,hypern-dip2,hypern-dip3}. Fig. \ref{fig:hyper-dip} shows the estimated slope from the clean data with a constant smoothing radius $R=5$, which is considered as the ground-truth solution for the slope. Here, we use the traditional PWD algorithm \cite{fomel2002pwd} for the slope estimation. \new{To numerically compare the accuracy of slope, we treat the slope calculated from the clean data as the ground truth, and also use the SNR metric (defined in equation \ref{eq:diff}) for the evaluation.} Fig. \ref{fig:hypern-dip} shows the estimated slope from the noisy data with a constant smoothing radius $R=8$. It is clear that when using a smoothing radius $R=8$, the estimated local slope is highly unstable. There are a lot of artifacts in the slope map caused by the strong random noise. Note that a smaller smoothing radius will result in an even more unstable slope estimation result. \new{The accuracy of this slope result is 0.48 dB. } Fig. \ref{fig:hypern-dip2} shows the slope estimation result using a much larger smoothing radius $R=50$. \new{The accuracy of this slope result is 8.40 dB. } The resultant slope becomes stable and smooth across the whole profile, but the accuracy of the slope value in each point is significantly decreased. In addition, because of the larger smoothing radius, the PWD algorithm loses the resolution in distinguishing between seismic events. From the two results plotted in Figs. \ref{fig:hypern-dip} and \ref{fig:hypern-dip2}, we conclude that the resolution is maintained when the smoothing radius is small and is deteriorated when the radius becomes large. However, when the smoothing radius is small, the slope estimation is more unstable. Thus, the smoothing radius affects greatly the resolution and the stability of the estimated slope. It is always a compromise to achieve a balance between the smoothness and resolution of the slope map. Fig. \ref{fig:hypern-dip3} shows the estimated slope using the proposed method, which obtains a good compromise between the smoothness and the resolution of the slope map. \new{The accuracy of proposed slope result is 10.44 dB. } It is clear that the estimated slope using the proposed method is very close to the ground-truth solution of the slope estimation.

Based on the aforementioned adaptive radius estimation method, we calculate the non-stationary radius map and show it in Fig. \ref{fig:rectdip1}. The minimum radius in this non-stationary radius map is about 8 and the maximum radius is about 50. Comparing the non-stationary radius map and the seismic data (Fig. \ref{fig:hyper}), we find that the adaptive smoothing radius estimation method correctly finds the areas of the signal components and output smaller radius for these signal areas and output a larger radius for other areas. It is clear that the proposed method adjusts the smoothing radius between the largest one (e.g., 50) and the smallest one (e.g., 8) in an adaptive way, and thus obtain a good compromise between the resolution (signal areas) and smoothness (noise areas) when estimating the local slope based on the PWD algorithm. Then, to compare the accuracy of the estimated local slope maps, we conduct a structure-oriented smoothing test. In the structure-oriented smoothing method \cite{sosvmf}, we first flat the seismic data based on a trace prediction strategy, and then apply a common triangle smoothing operator to the flattened dimension. 
The smoothed data using the four slope maps (Fig. \ref{fig:hyper-dip,hypern-dip,hypern-dip2,hypern-dip3}) are plotted in Fig. \ref{fig:hypern-sm1,hypern-sm2,hypern-sm3,hypern-sm4}. Fig. \ref{fig:hypern-sm1} plots the smoothed data using the ground-truth slope (Fig. \ref{fig:hyper-dip}). Fig. \ref{fig:hypern-sm2} corresponds to the local slope using a constant smoothing radius $R=8$ (Fig. \ref{fig:hypern-dip}). Because of the highly unstable artifacts in the local slope shown in Fig. \ref{fig:hypern-dip}, there are also some artifacts in the smoothed data, e.g., around 1.5s at the 100th trace.  Fig. \ref{fig:hypern-sm3} shows the smoothed data using the local slope with a constant smoothing radius $R=50$. It is clear that because of the low accuracy of the slope value caused by an over-large smoothing radius, the smoothing damages the signal amplitude significantly, e.g., the first seismic event. Fig.  \ref{fig:hypern-sm4} plots the smoothed data using the local slope estimated based on the proposed method. The result is very close to the smoothing result based on the ground-truth slope (Fig. \ref{fig:hypern-sm1}), and there are no observable artifacts and signal damages. Thus, we deem the smoothing result based on the proposed method accurate. The calculated SNRs for Figs. \ref{fig:hypern-sm1}-\ref{fig:hypern-sm4} are 13.73 dB, 11.80 dB, 10.71 dB, and 13.11 dB, respectively. It indicates \new{that} the smoothed data based on the proposed method obtains the highest SNR.  The removed noise sections caused by different smoothing operations are plotted in Fig. \ref{fig:hypern-sm1-n,hypern-sm2-n,hypern-sm3-n,hypern-sm4-n}. All the noise sections except for Fig. \ref{fig:hypern-sm3-n} shows no observable signal energy. However, there is \new{a} clear spatially coherent energy in Fig. \ref{fig:hypern-sm3-n}, which indicates a strong damage to the useful signals caused by the over-smoothed slope estimation when using a large constant smoothing radius $R=50$.

The second example is a \new{2D} field data test. The field data is shown in Fig. \ref{fig:g-0}. This field data has 2501 time samples and \old{2000}\new{1000} traces. The sampling rate is 2ms. Figs. \ref{fig:g-z-a} and \ref{fig:g-z-b} are two zoomed sections from the raw data for a detailed comparison. The two zooming areas are pointed by the two pink rectangles A and B. We show the adaptively estimated smoothing radius map in Fig. \ref{fig:g-rectdip1}. The non-stationary smoothing radius map successfully classifies the whole seismic section into signal areas where the smoothing radius is large and noise areas where the smoothing radius is small. The smallest smoothing radius on the map is about 8 and the largest smoothing radius is about 100. We apply different slope estimation methods to the noisy field data and get the slope maps in Fig. \ref{fig:g-dip1,g-dip2,g-dip3}. Fig. \ref{fig:g-dip1} shows the estimated slope using a small constant smoothing radius $R=8$, which is highly non-stable. Fig. \ref{fig:g-dip2} shows the estimated slope using a large constant smoothing radius $R=100$, which is somewhat over-smoothing. Fig. \ref{fig:g-dip3} shows the slope estimation result using the proposed method with the non-stationary smoothing radius presented in Fig. \ref{fig:g-rectdip1}. It is obvious the estimated slope using the proposed method is both smooth and \old{high-resolution}\new{with a high resolution}, maintaining the most subtle structures in the whole section. We then apply the structure-oriented smoothing based on different slope maps shown in Fig. \ref{fig:g-dip1,g-dip2,g-dip3}. The three smoothed profiles are plotted in Fig. \ref{fig:g-sm1-0,g-sm2-0,g-sm3-0}, with the top two results corresponding to the stationary slope estimation with a small smoothing radius \old{(left)}\new{(up)} and a large smoothing radius \old{(right)}\new{(down)}. The bottom \old{Fig.}\new{figure} corresponds to the result of the proposed method. The removed noise sections corresponding to the smoothed data are plotted in Fig. \ref{fig:g-sm1-n,g-sm2-n,g-sm3-n} for better evaluation. For a clearer comparison, we zoom in two sections from each \old{subFig.}\new{subfigure} in Fig. \ref{fig:g-sm1-0,g-sm2-0,g-sm3-0}. Fig. \ref{fig:g-sm1-z-a0,g-sm2-z-a0,g-sm3-z-a0} shows a comparison of the zoomed frame box A. From Fig. \ref{fig:g-sm1-z-a0,g-sm2-z-a0,g-sm3-z-a0}, it is clear that the top two results are both over-smoothed, causing either smoothing artifacts across the section \old{(left)}\new{(up)}, or damaged energy in areas with large dips \old{(right)}\new{(down)}. For example, several arrows point out the obvious distortion and damages to the useful seismic events in the top two panels. The smoothed data in the bottom panel seems to well preserve the key structures.  Fig. \ref{fig:g-sm1-z-b0,g-sm2-z-b0,g-sm3-z-b0} shows a comparison of the zoomed frame box B.  In this comparison, it is much more obvious that the top two results are over-smoothed seriously, as indicated by the white arrows. The result from the proposed method, however, still maintains the main geological structures.

\new{The third example is a 3D field data test. The 3D field data is shown in Fig. \ref{fig:real}. The size of this dataset is $512\times 128\times 32$. This field data contains strong random noise. The adaptively calculated non-stationary smoothing radius is plotted in Fig. \ref{fig:rect1}. We apply different slope estimation methods to the noisy field data and get the slope maps in Fig. \ref{fig:real-s2dip1,real-s1dip1,real-ndip1}. The top two results correspond to the traditional PWD algorithm with constant smoothing radii. Fig. \ref{fig:real-s2dip1} shows the estimated slope using a small constant smoothing radius $R=2$, which is highly non-stable. Fig. \ref{fig:real-s1dip1} shows the estimated slope using a large constant smoothing radius $R=20$, which is over-smoothed. Fig. \ref{fig:real-ndip1} shows the slope estimation result using the proposed method with the non-stationary smoothing radius presented in Fig. \ref{fig:rect1}. It is obvious the estimated slope using the proposed method is both smooth and high-resolution, maintaining the most subtle structures in the whole section. We then apply the structure-oriented smoothing based on different slope maps. The three smoothed profiles are plotted in Fig. \ref{fig:real-pws2-0,real-pws1-0,real-pws3-0}, with the top two results corresponding to the stationary slope estimation with a small smoothing radius (up) and a large smoothing radius (down). The bottom figure corresponds to the result of the proposed method. The removed noise sections corresponding to the smoothed data are plotted in Fig. \ref{fig:real-pws2-n-0,real-pws1-n-0,real-pws3-n-0} for better evaluation.  As highlighted by the arrows in Fig. \ref{fig:real-pws2-0,real-pws1-0,real-pws3-0}. The proposed slope estimation method helps obtain the best denoising result. As highlighted by the arrows in Fig. \ref{fig:real-pws2-n-0,real-pws1-n-0,real-pws3-n-0}, a large smoothing radius would cause a over-smoothing in the denoised result and a small smoothing radius would cause an insufficient amount of removed noise. The proposed method, however, obtains the best compromise between noise removal and signal preservation.}

\section{Conclusion}
The traditional PWD method is based on a stationary smoothing shaping operator. The stationary smoothing shaping operator constrains the slope perturbation during each non-linear iteration. The constant smoothing radius is not convenient to choose in order to compromise the smoothness of the estimated slope field and its resolution. The unsatisfactory choice of the constant smoothing radius will result in unacceptable slope estimation results, which further deteriorate the structural filtering based on the accuracy of the local slope. The non-stationary smoothing based slope estimation method can overcome the limitation in choosing the fixed smoothing radius because the smoothing radius can be adaptively calculated based on an optimization method. We have shown that the smoothing radius plays an important role in the accuracy of the estimated slope and the proposed non-stationary slope estimation method can obtain a fairly accurate slope field in an adaptive way. Both synthetic and field data examples show the proposed non-stationary method can work effectively well in the case of strong random noise. The structure-oriented smoothing based upon the estimated local slope maps further verifies the advantages of the non-stationary smoothness constrained iterative slope estimation over the traditional PWD method.

\begin{figure}[htb!]
\centering
\includegraphics[width=0.45\textwidth]{real3d/Fig/real}
\caption{\new{3D field data example.} }
\label{fig:real}
\end{figure}

\begin{figure}[htb!]
\centering
\includegraphics[width=0.45\textwidth]{real3d/Fig/rect1}
\caption{\new{3D field data example. Non-stationary smoothing radius.}}
\label{fig:rect1}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-s2dip1}
   \label{fig:real-s2dip1}}
   \subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-s1dip1}
   \label{fig:real-s1dip1}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-ndip1}
   \label{fig:real-ndip1}}
\caption{\new{Slope comparison of the 3D field data example. (a) Slope estimated from the noisy data with a small constant smoothing radius $R=2$. (b) Slope estimated from the noisy data with a large constant smoothing radius $R=20$. (c) Slope estimated from the noisy data with non-stationary smoothing radius.}}
\label{fig:real-s2dip1,real-s1dip1,real-ndip1}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws2-0}
  \label{fig:real-pws2-0}}
  \subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws2-0}
  \label{fig:real-pws2-0}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws3-0}
  \label{fig:real-pws3-0}}
\caption{\new{Smoothing test of the field data example. (a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius. (b) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius. (c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius. Note the difference highlighted by the arrows.}}
\label{fig:real-pws2-0,real-pws1-0,real-pws3-0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws2-n-0}
  \label{fig:real-pws2-n-0}}
  \subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws1-n-0}
  \label{fig:real-pws1-n-0}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws3-n-0}
  \label{fig:real-pws3-n-0}}
\caption{\new{Smoothing test of the field data example. (a)-(c) Removed noise corresponding to Figs. \ref{fig:real-pws2-0}-\ref{fig:real-pws3-0}. Note the difference highlighted by the arrows.}}
\label{fig:real-pws2-n-0,real-pws1-n-0,real-pws3-n-0}
\end{figure}

\section{Acknowledgments} 
We would like to thank S. Zu, D. Zhang, and S. Fomel for inspiring discussions. \new{We also thank two anonymous reviewers for constructive suggestions.}

\bibliographystyle{IEEEtran}
\bibliography{dip}

%\begin{figure}[htb!]
%	\centering
%	\subfigure[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
%	\caption{Caption.}
%	\label{fig:fig}
%\end{figure}

%\begin{figure}[htb!]
%	\centering
%	\subfigure[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}}\\
%    \subfigure[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}}
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure}

%\begin{table}[h]
%\caption{Table caption}
%\begin{center}
%     \begin{tabular}{|c|c|c|c|c|c|} 
%	  \hline Column1 (unit)  & Column2 (unit) & Column3 (unit) \\ 
%	  \hline 1 & 2  & 3 \\
%       \hline
%    \end{tabular} 
%\end{center}
%\label{tbl:table1}
%\end{table}

### 2020-09-16 npm/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{Geophysical Prospecting, 66, 85-97 (2018)}

\title{Data-driven time-frequency analysis of seismic data using 
non-stationary Prony method} 
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\address{
\footnotemark[1] The College of Science\\
China University of Petroleum\\
Beijing, China
\footnotemark[2] Bureau of Economic Geology,\\
John A. and Katherine G. Jackson School of Geosciences\\
The University of Texas at Austin\\
University Station, Box X\\
Austin, TX, USA, 78731-8924\\
\footnotemark[3] Previously:  The University of Texas at Austin; Currently: Oak Ridge National Laboratory
}

\author{Guoning Wu\footnotemark[1], Sergey Fomel\footnotemark[2], Yangkang Chen\footnotemark[3]}

%\footer{GEO-2016}
%\lefthead{Wu etc.}
\righthead{Time-frequency analysis}
\maketitle

\begin{abstract}
The empirical mode decomposition aims to decompose the input signal 
into a small number of components named intrinsic mode functions 
with slowly varying amplitudes and frequencies. In spite of its simplicity
and usefulness, however, the empirical mode decomposition lack 
solid mathematical foundation. In this paper, we describe a method to 
extract the intrinsic mode functions of the input signal using 
non-stationary Prony method. The proposed method captures the 
philosophy of the empirical mode decomposition, but use a different 
method to compute the intrinsic mode functions. 
Having the intrinsic mode functions obtained, we then compute 
the spectrum of the input signal using Hilbert transform. Synthetic and field data 
validate the proposed method can correctly compute the 
spectrum of the input signal, and could be used in seismic data analysis to facilitate 
interpretation.
\end{abstract}

\section{INTRODUCTION}

Time-frequency analysis maps an 1D time signal into 2D time and frequency domains, 
which can capture the non-stationary character of seismic data. Time-frequency 
analysis is a fundamental tool for seismic data analysis and geological 
interpretation \cite[]{Castagna2003,Reine2009,yangkang2014sswt,liuwei2016}. 
Conventional time-frequency methods, such as short time Fourier transform \cite[]{Cohen1989}, 
wavelet transform \cite[]{Mallat1989} and S-transform \cite[]{Stockwell1996} 
are under the control of Heisenberg/Gabor uncertainty principle, which states 
that we cannot have the energy arbitrarily located in both time and frequency 
domains \cite[]{mallat}. Moreover, short time Fourier transform, wavelet transform 
and S-transform are using a windowing process, which often brings smearing and 
leakage \cite[]{Tary2014}. Therefore spurious frequencies are often generated, 
which will "color" the real time-frequency map and affects the interpretation. 
In recent years, many new methods were proposed such as matching pursuit \cite[]{Mallat1993}, 
basis pursuit \cite[]{basispursuit}, empirical mode decomposition \cite[]{emd,emdseis}, 
the synchrosqueezing wavelet transform \cite[]{daubechies} and its variants such as the 
synchrosqueezing short time Fourier transform \cite[]{Oberlin2014}, 
the synchrosqueezing S-transform \cite[]{Synchrostran}. The matching pursuit and basis pursuit methods 
represent the energies of the input signal by the energies of atoms found using 
different methods, which prevents smearing and leakage, creating highly 
localized time-frequency decompositions. The efficiency of these two methods depend
on the predefined dictionary \cite[]{Tary2014}. The empirical mode decomposition 
method decomposes a signal into symmetric, narrow-band waveforms named intrinsic 
mode functions to compress artificial spectra caused by sudden changes and to 
therefore improve the time-frequency resolution \cite[]{han}. However, the empirical mode
decomposition also suffers from mode mixing and splitting problems. 
In order to solve the above problems, alternative methods were developed 
based on empirical mode decomposition: ensemble empirical mode decomposition\cite[]{eemd}, 
complete ensemble empirical mode decomposition \cite[]{ceemd}. However, these two methods, 
like the empirical mode decomposition, are still "empirical" because 
their sketchy mathematical justifications. The synchrosqueezing wavelet 
transform \cite[]{daubechies} and its variants capture the philosophy of 
empirical mode decomposition, but use a different method to compute the 
intrinsic mode functions providing a rigorous mathematical framework.

Similar to the Fourier transform, the Prony method \cite[]{prony} decomposes 
a signal into a series of damped exponentials or sinusoids in a data-driven manner, 
which allows for the estimation of frequencies, amplitudes, phases and damping 
components of a signal. \citet[]{fomel2013} proposed the non-stationary Prony method (NPM)
based on regularized non-stationary auto-regression. The NPM decomposes a signal into 
intrinsic mode functions with controlled smoothness of amplitudes and frequencies 
like the empirical mode decomposition does, but uses NPM instead.
Unlike Fourier transform, the coefficients of the extracted intrinsic mode functions 
for the Prony method do not clearly define the energy distribution for the input 
signal in the time-frequency domain. Therefore, the NPM used by Fomel does not clearly
define a "real" time-frequency map but a "time-component" map. In this paper, we couple the NPM 
\cite[]{fomel2013} and the Hilbert transform to give a time-frequency decomposition. 
The proposed method has a rigorous mathematical framework. Furthermore, 
synthetic and real data tests confirm that the intrinsic mode functions derived by the proposed 
method are more smooth with respect to the amplitudes and frequencies
than the intrinsic mode functions of ensemble empirical mode decomposition \cite[]{eemd}. 
Synthetic and real data tests also confirm that the proposed method
has a higher time-frequency resolution than the ensemble empirical mode decomposition.
The proposed method can be used to facilitate seismic interpretation.

\section{THEORY}
We give a short description of the theories for empirical mode decomposition, Prony, and 
NPM. For details of the Prony and NPM see Appendix.
\subsection{Empirical Mode Decomposition}
Empirical mode decomposition is a data-driven method, which is a powerful 
tool for non-stationary signal analysis \cite[]{emd}. This method decomposes 
a signal into slowly varying time dependent amplitudes and phases components named intrinsic 
mode functions. The time-frequency decomposition for the input signal is attributed to 
the Hilbert transform of the intrinsic mode functions extracted by the sifting process\cite[]{han}. 
If $s(t)$ is the input signal, the empirical mode decomposition can be written as:
\begin{equation}
    \label{eq:eq1}
    s(t) =\sum_{k=1}^{K} s_k (t)= \sum_{k=1}^{K} A_k (t)\cos (\phi_k(t)),
\end{equation}
where $A_k(t)$ measures amplitude modulation, and $\phi_k(t)$ measures 
phase oscillation. Each $s_k(t)$ has a narrow-band 
waveform and an instantaneous frequency that is smooth and positive. 
The empirical mode decomposition is powerful, but its mathematical theory is sketchy.

\subsection{Prony Method}
Prony method extracts damped complex exponential functions (or sinusoids) 
from a given signal by solving a set of linear equations 
\cite[]{prony,prony2003,ThomasPeter2013,Mitrofanov2015}. 
The Prony method allows for estimation of frequencies, amplitudes and phases 
of a signal (For details see Appendix). Assume we want to solve the problem:
\begin{equation}
    \label{eq:eq2}
     x[n] = \sum_{k=1}^{M}A_k e^{(\alpha_k + j\omega_k)(n-1)\Delta t + j\phi_k},
\end{equation}
if let $h_k = A_k e^{j\phi_k}, z_k = e^{(\alpha_k + j\omega_k)\Delta t}$, we derive the concise form
\begin{equation}
    \label{eq:eq3}
     x[n] = \sum_{k=1}^{M}h_k z_k^{n-1}.
\end{equation}
The above M equations can be written in a matrix form:
\begin{equation}
    \label{eq:eq4}
    \left[ \begin{array}{cccc}
        z_1^0 & z_2^0 & \cdots & z_M^0\\
        z_1^1 & z_2^1 & \cdots & z_M^1\\
        \vdots & \vdots & & \vdots\\
        z_1^{M-1} & z_2^{M-1} & \cdots & z_M^{M-1}
    \end{array} \right]
    \left[ \begin{array}{c} h_1\\ h_2\\ \vdots \\ h_M
    \end{array} \right] =
    \left[ \begin{array}{c} x[1]\\ x[2]\\ \vdots \\ x[M]
    \end{array} \right].
\end{equation}
The above $z_k, k=1,2, \cdots , M$ of equation~\ref{eq:eq4} 
can be computed by solving a polynomial of the form:
\begin{equation}
    \label{eq:eq5}
    \mathbf{P}(z)  = \prod_{k=1}^{M}(z-z_k),
\end{equation}
equation~\ref{eq:eq5} can also be written in a form:
\begin{equation}
    \label{eq:eq6}
    \mathbf{P}(z) = a_0 z^M + a_1 z^{M-1} + \cdots + a_{M-1}z + a_M.
\end{equation}
The coefficients $a_k$ of the polynomial can be computed by solving the following equation:
\begin{equation}
    \label{eq:eq7}
    \sum_{m=0}^{M}a_mx[n-m] = 0.
\end{equation}
We use the method proposed by \citet[]{roots} to compute the roots $z_k$ of equation~\ref{eq:eq6}. 
If the roots are solved, 
the $h_k$ can be computed using equation~\ref{eq:eq3}.
Finally, the components are 
computed based on the equation below(For details see Appendix):
\begin{equation}
    c_k[n] = h_kz_k^{n-1} = h_kz_k^{n-1}, k=1,2,\cdots,M.
\end{equation}

\subsection{Non-stationary Prony method}
Equation~\ref{eq:eq7} can be written as:
\begin{equation}
    \label{eq:eq9}
    \sum_{m=1}^{M}\hat{a}_m x[n-m] = x[n].
\end{equation}
If the $\hat{a}_m$ in equation~\ref{eq:eq9} are time dependent, then we have:
\begin{equation}
    \label{eq:eq10}
    \sum_{m=1}^{M}\hat{a}_m[n] x[n-m] \approx x[n],
\end{equation}
which is an under-determined linear system. There are many methods for solving under-determined 
linear system, such as Tikhonov method \cite[]{tikhonov}.
In this paper, we apply shaping regularization \cite[]{shape,lpf} to regularize
the under-determined linear system, and obtain (for details see Appendix):
\begin{equation}
    \label{eq:eq11}
    \mathbf{\hat{a}} = \mathbf{F}^{-1}\mathbf{\eta},
\end{equation}
where $\mathbf{\hat{a}}$ is a vector composed of $\hat{a}_m [n]$, 
the elements of vector $\mathbf{\eta}$ are 
$\eta_i[n] = \mathbf{S}[x_i^* [n] x[n]] $, where $x_i[n] = x[n-i]$, $x_i^*[n]$ stands for the complex conjugate of $x_i[n]$
and $\mathbf{S}$ is the shaping operator. 
The elements of matrix $\mathbf{F}$ are:
\begin{equation}
    \label{eq:eq12}
    {F}_{ij}[n] = \sigma^2 \delta_{ij} + \mathbf{S}[x_i^*[n]x_j[n] - \sigma^2 \delta_{ij}],
\end{equation}
where $\sigma$ is the regularization parameter.
Solving equation~\ref{eq:eq11}, we obtain the 
coefficients vector $\hat{a}_m[n]$ and form a polynomial below:
\begin{equation}
    \mathbf{P}(z) = z^M + \hat{a}_1[n] z^{M-1} + \cdots + \hat{a}_M[n].
\end{equation}
For the roots computation $\hat{z}_m[n], m=1,2,\cdot,M$ of the above polynomial, we 
use the method proposed by \citet[]{roots}. 
The instantaneous frequency of each different component is derived from the following equation:
\begin{equation}
    f_m[n] = \Re \left[ \arg \left( \frac{\hat{z}_m[n]}{2\pi \Delta t} \right) \right].
\end{equation}
From the instantaneous frequency, we compute the local phase according to the following equation:
\begin{equation}
    \Phi_m[n] = 2\pi\sum_{k=0}^{n}f_m[k]\Delta t.
\end{equation}
Solving the following equation using 
regularized non-stationary regression method \cite[]{fomel2013}:
\begin{equation}
    \label{eq:eq13}
    x[n] = \sum_{m=1}^{M} \hat{A}_m[n]e^{j \Phi_m[n]} =
     \sum_{m=1}^{M} c_m[n].
\end{equation} 
Finally the narrow-band intrinsic mode functions $c_m[n]$ are computed based on equation~\ref{eq:eq13}

\section{EXAMPLES}
We use synthetic signals and real field data to test the proposed method.
\subsection{Benchmark examples}
We use a simple synthetic signal to test the proposed method. 
Figure~\ref{fig:hsig} is a synthetic signal from \citet[]{hou}. 
The three components of the signal are shown in Figure~\ref{fig:sigs}. 
Figure~\ref{fig:emd} and Figure~\ref{fig:nar} show the intrinsic mode functions 
extracted respectively by ensemble empirical mode decomposition and NPM methods. 
From the figures, we see that the NPM method 
accurately identifies the three components that the signal has. 
The intrinsic mode functions derived by the NPM are 
more smooth with respect to amplitudes and frequencies 
compared with the intrinsic mode functions obtained by ensemble empirical mode decomposition. 
For ensemble empirical mode decomposition, we repeat the empirical mode decomposition 25 times with different level of noises 
to generate the ensemble empirical mode decomposition results.
The time-frequency distributions of the input signal are the 
Hilbert transform of the intrinsic mode functions. 
Figure~\ref{fig:htf},~\ref{fig:htfemd} and~\ref{fig:htfnar} 
are respectively the time-frequency distributions using local attribute \cite[]{guochang2011}, 
ensemble empirical mode decomposition \cite[]{eemd} and the proposed method for the synthetic 
signal of Figure~\ref{fig:hsig}. 
Figure~\ref{fig:msig} is an another synthetic signal. 
Figure~\ref{fig:mtf},~\ref{fig:mtfemd} and~\ref{fig:mtfnar}
are respectively the time-frequency maps using local attribute 
\cite[]{guochang2011}, ensemble empirical mode decomposition \cite[]{eemd} and the proposed method. 
From the figures, we see that the energies compactly spread over the instantaneous 
frequencies for the ensemble empirical mode decomposition. 
However, the energies are not steadily distributed for the ensemble empirical mode decomposition. 
The proposed method provides a steady and compact energies distribution, which 
sharpen the time-frequency distribution.
\inputdir{hou}
\plot{hsig}{width=0.7\columnwidth}{Synthetic signal.}

\plot{sigs}{width=0.7\columnwidth} {Components of the synthetic 
signal of Figure~\ref{fig:hsig} .}
\plot{emd}{width=0.7\columnwidth} {Components of the synthetic 
signal of Figure~\ref{fig:hsig} using ensemble empirical mode decomposition.}
\plot{nar}{width=0.7\columnwidth} {Components of the synthetic 
signal of Figure~\ref{fig:hsig} using NPM.}
\multiplot{3}{htf,htfemd,htfnar}{width=0.7\columnwidth}
  {(a) Time-frequency map for synthetic signal of Figure~\ref{fig:hsig} using local attribute. 
  (b) Time-frequency map for synthetic signal of Figure~\ref{fig:hsig} using ensemble empirical mode decomposition. 
  (c) Time-frequency map  for synthetic signal of Figure~\ref{fig:hsig} using the proposed method.}

\inputdir{mirko}
\plot{msig}{width=0.7\columnwidth}{Synthetic signal.}
\multiplot{3}{mtf,mtfemd,mtfnar}{width=0.7\columnwidth}
  {(a) Time-frequency map for synthetic signal of Figure~\ref{fig:msig} using local attribute. 
  (b) Time-frequency map for synthetic signal of Figure~\ref{fig:msig} using ensemble empirical mode decomposition. 
  (c) Time-frequency map  for synthetic signal of Figure~\ref{fig:msig} using the proposed method.}

\subsection{Field examples}
Figure~\ref{fig:trace} is a seismic trace from marine survey. 
Figure~\ref{fig:stf},~\ref{fig:tfemd} and~\ref{fig:tfnar} are the time-frequency 
distributions of the trace using local attribute \cite[]{guochang2011}, 
ensemble empirical mode decomposition and the proposed method.
We can see that the energies distributions for ensemble empirical mode decomposition and the proposed method 
are much like each other. Both the ensemble empirical mode decomposition and the proposed method using 
the Hilbert transform of the intrinsic mode functions to represent the time-frequency distributions 
for the input signal. The results confirm that they both reveal the time-frequency
character of the input signal.

\inputdir{trace}
\plot{trace}{width=0.7\columnwidth}{Seismic trace from marine survey.}
\multiplot{3}{stf,tfemd,tfnar}{width=0.7\columnwidth}
  {(a) Time-frequency map for synthetic signal of Figure~\ref{fig:trace} using local attribute. 
  (b) Time-frequency map for synthetic signal of Figure~\ref{fig:trace} using ensemble empirical mode decomposition. 
  (c) Time-frequency map  for synthetic signal of Figure~\ref{fig:trace} using the proposed method.}
Low-frequency anomalies are often attributed to abnormally high attenuation
in gas-filled reservoirs and can be used as a hydrocarbon indicator \cite[]{Castagna2003}.
The mechanisms of low-frequency anomalies associated with hydrocarbon reservoirs 
are not clearly understood \cite[]{Ebrom2004, Kazemeini2009}.
Figure~\ref{fig:data} is a 2D field seismic data. 
Figure~\ref{fig:LC_TimeFreqSlice3} and~\ref{fig:LC_TimeFreqSlice6}, 
~\ref{fig:GasSmoothSliceEmd3} and~\ref{fig:GasSmoothSliceEmd6},
~\ref{fig:GasSmoothSliceNar3} and~\ref{fig:GasSmoothSliceNar6} are
the 30Hz and 60Hz constant frequency slices using local attribute, ensemble empirical mode decomposition and 
the proposed method.
From the above figures, we see that there is a low frequency anomaly 
in the upper left part of the data section indicated by the text boxes
"Gas?" for the ensemble empirical mode decomposition and the proposed methods, 
which may correspond to gas presentation.
\inputdir{vecta-stlc}
\plot{data}{width=0.7\columnwidth}
{2D seismic data section.}

\inputdir{vecta-nar}
\multiplot{6}{LC_TimeFreqSlice3,LC_TimeFreqSlice6,GasSmoothSliceEmd3,GasSmoothSliceEmd6,GasSmoothSliceNar3,GasSmoothSliceNar6}{width=0.45\columnwidth}
{
   (a) 30Hz slice time-frequency map using local attribute method.
   (b) 60Hz slice time-frequency map using local attribute method.
   (c) 30Hz slice time-frequency map using ensemble empirical mode decomposition method.
   (d) 60Hz slice time-frequency map using ensemble empirical mode decomposition method.
   (e) 30Hz slice time-frequency map of the proposed method. 
   (f) 60Hz slice time-frequency map of the proposed method. 
}

Figure~\ref{fig:TimeFreqCube_LC},~\ref{fig:TimeFreqCubeEmd} and~\ref{fig:TimeFreqCubeNar} are the 
full time-frequency cubes computed respectively using local attribute, ensemble empirical mode decomposition and the proposed 
methods. The main panels show constant frequency slices. 
The right hand side panels show the time-frequency maps of the 150th trace. 
The top panels show the time-frequency maps of 0.6s time-depth signal. 
From the right and top side panels we see that there are a lot of noise in the high 
frequency domain for the ensemble empirical mode decomposition and local attribute methods compared with the proposed method. 
\inputdir{vecta-nar}
\multiplot{4}{TimeFreqCube_LC,TimeFreqCubeEmd,TimeFreqCubeNar}{width=0.4\columnwidth}
{
   (a) Time-frequency cube using local attribute method. 
   (b) Time-frequency cube using ensemble empirical mode decomposition method. 
   (c) Time-frequency cube using NPM method. 
}

\section{CONCLUSION}
We proposed to compute the time-frequency map of an input signal based on 
NPM coupled with Hilbert spectral analysis. 
The proposed method is an empirical mode decomposition-like method, but using NPM 
to compute its intrinsic mode functions. Compared with the Fourier 
transform, the proposed method is data-driven and needs much less base functions 
to approximate the original signal. Since the NPM 
results an under-determined linear system, we use shaping regularization to 
regularize it. The regularization makes the intrinsic mode functions more 
smooth with respect to the amplitudes and frequencies 
compared with the intrinsic mode functions of the empirical mode decomposition. 
There are many time-frequency methods, which one is the best? This is a difficult 
question to answer. Methods are good for some type signals, maybe not good for 
other type signals.

\citet[]{eemd_comp} pointed out that the complexity of empirical mode decomposition/ensemble
empirical mode decomposition is $41*\mathbf{N}_E*\mathbf{N}_S*n(\log_2n)=O(n\log n)$
, where $n$ is the data length and the parameters $\mathbf{N}_E$ and $\mathbf{N}_S$ are the
ensemble and sifting numbers respectively. For the non-stationary Prony method, the computation
complexity is mainly attributed to the polynomial zero-finding. We used the pseudo-zeros 
method to compute the pseudo-spectra of the associated balanced 
companion matrix \cite[]{roots}, which requires approximate $\mathbf{N}^3$ works, where $\mathbf{N}$
is the polynomial degree number. Therefore, the total computation complexity is 
$\mathbf{N}^3*\frac{n}{\mathbf{N}}=n*\mathbf{N}^2$, where $n$ is the data length.
In this paper, we choose $\mathbf{N}=5$, and therefore the total computation complexity is approximate 
$n*5^2 = O(n)$.
\section{ACKNOWLEDGMENTS}
We would like to thank Zhiguang Xue, and Junzhe Sun for their constructive 
suggestions. The first author thanks China University of Petroleum-Beijing 
for supporting his visiting to the Bureau of Economic Geology at UT Austin. 
The work is partially supported by Youth Science Foundation of China 
University of Petroleum at Beijing (Grant NO. 01jb0508) and Science Foundation 
of China University of Petroleum-Beijing (Grant NO.2462015YQ0604).

\newpage
\appendix
\section{Appendix A}
\section{Prony method}
Prony method can extract damped complex exponential signals 
from a given data by solving a set of linear equations 
\cite[]{prony,prony2003,ThomasPeter2013,Mitrofanov2015}. 
Assume the N complex data samples $x[1],x[2],\cdots x[N]$,
 we approximate the data by $M$ exponential functions:
\begin{equation}
    \label{eqa:eq0}
     x[n] \approx \sum_{k=1}^{M}A_k e^{(\alpha_k + j\omega_k)(n-1)\Delta t + j\phi_k},
\end{equation}
where $A_k$ is the amplitude, $\Delta t$ is the sampling period, 
$\alpha_k$ is the damping factor, $\omega_k$ is the angular frequency, $\phi_k$ is 
the initial phase.
If we let $h_k = A_k e^{j\phi_k}, z_k = e^{(\alpha_k + j\omega_k)\Delta t}$, 
we then derive the concise form below:
\begin{equation}
    \label{eqa:eq1}
     x[n] \approx \sum_{k=1}^{M}h_k z_k^{n-1}.
\end{equation}
The approximation problem above can be solved based on the error minimization:
\begin{equation}
    \label{eqa:eq2}
    \mathbf{min} \sum_{n=1}^{N} \left|\epsilon[n]\right|^2 = 
    \mathbf{min}\sum_{n=1}^{N}\left | x[n] - \sum_{k=1}^{M}h_k z_k^{n-1}\right|^2.
\end{equation}
This turns to be a nonlinear problem. It can be solved using 
Prony method that utilizes linear equation solutions.
If there are as many data samples as parameters of the approximation problem,
the above M equations\textbf{~\ref{eqa:eq1}} can be expressed:
\begin{equation}
    \label{eqa:eq3}
     x[n] = \sum_{k=1}^{M}h_k z_k^{n-1}.
\end{equation}
\textbf{~\ref{eqa:eq3}} can be written in a matrix form as below:
\begin{equation}
    \label{eqa:eq4}
    \left[ \begin{array}{cccc}
        z_1^0 & z_2^0 & \cdots & z_M^0\\
        z_1^1 & z_2^1 & \cdots & z_M^1\\
        \vdots & \vdots & & \vdots\\
        z_1^{M-1} & z_2^{M-1} & \cdots & z_M^{M-1}
    \end{array} \right]
    \left[ \begin{array}{c} h_1\\ h_2\\ \vdots \\ h_M
    \end{array} \right] =
    \left[ \begin{array}{c} x[1]\\ x[2]\\ \vdots \\ x[M]
    \end{array} \right].
\end{equation}
Prony proposed to define the polynomial that has the 
above $z_k, k=1,2, \cdots , M$ as its roots \cite[]{prony}:
\begin{equation}
    \label{eqa:eq5}
    \mathbf{P}(z)  = \prod_{k=1}^{M}(z-z_k).
\end{equation}
Equation \textbf{~\ref{eqa:eq5}} can be rewritten in the form below:
\begin{equation}
    \label{eqa:eq6}
    \mathbf{P}(z) = a_0 z^M + a_1 z^{M-1} + \cdots + a_{M-1}z + a_M.
\end{equation}
Shifting the index on equation\textbf{~\ref{eqa:eq3}} from $n$ to $n-m$
, and multiplying by parameter $a[m]$, then we derive:
\begin{equation}
    \label{eqa:eq7}
    \sum_{m=0}^{M}a_mx[n-m] = \sum_{k=1}^{M}h_kz_k^{n-M-1}
    \sum_{m=0}^M a[m]z_{k}^{M-m}.
\end{equation}
Notice $z_k, k=1,2,\cdots, M$ are roots of equation\textbf{~\ref{eqa:eq6}},
then equation\textbf{~\ref{eqa:eq7}} be written as:
\begin{equation}
    \label{eqa:eq8}
    \sum_{m=0}^{M}a_mx[n-m] = 0.
\end{equation}
Solving equation\textbf{~\ref{eqa:eq8}} for the polynomial coefficients.
In subsequent steps we compute the frequencies, damping factors 
and the phases according to Algorithm 1. 
After all the parameters are computed, we then
compute the components of the input signal. For details see 
Algorithm 1 as follows:
%\begin{algorithm}
%   \caption{Prony method} 
%   \label{pro:pronyalgorithm}
% \begin{algorithmic}[1]
%     \State \textit{Find coefficients:} $\displaystyle a_k,k=1,2,\cdots,M \gets \sum_{m=0}^{M}a_mx[n-m] = 0.$
%     \State \textit{Find roots:} $\displaystyle z_k,k=1,2,\cdots,M \gets \sum_{m=0}^{M}a_mz^{M-m}= 0.$
%     \State \textit{Compute frequencies:} $\displaystyle
%     \omega_k, k=1,2,\cdots,M \gets \Re\left\{\mathbf{arg}\left(\frac{z_k}{(k-1)\Delta t}\right)\right\}, k=1,2,\cdots,M.$
%     \State \textit{Compute:} $\displaystyle
%     A_k e^{\alpha_k (n-1)\Delta t + j\phi_k}, k=1,2,\cdots,M \gets 
%     x[n] = \sum_{k=1}^{M}A_k e^{(\alpha_k + j\omega_k)(n-1)\Delta t + j\phi_k}.$
%     \State \textit{Compute components:} $\displaystyle
%     A_k e^{(\alpha_k + j\omega_k)(n-1)\Delta t + j\phi_k}.$
% \end{algorithmic}
%\end{algorithm}

\begin{algorithm}{Algorithm 1: Prony method}{}
     \text{Find coefficients:}  \\
     \displaystyle a_k,k=1,2,\cdots,M \gets \sum_{m=0}^{M}a_mx[n-m] = 0. \\
     \text{Find roots:} \displaystyle z_k,k=1,2,\cdots,M \gets \sum_{m=0}^{M}a_mz^{M-m}= 0.\\
     \text{Compute frequencies:} \\  
     \displaystyle
     \omega_k, k=1,2,\cdots,M \gets \Re\left\{\mathbf{arg}\left(\frac{z_k}{(k-1)\Delta t}\right)\right\}, k=1,2,\cdots,M.\\
     \text{Compute:} \displaystyle \\
     A_k e^{\alpha_k (n-1)\Delta t + j\phi_k}, k=1,2,\cdots,M \gets  \\
     x[n] = \sum_{k=1}^{M}A_k e^{(\alpha_k + j\omega_k)(n-1)\Delta t + j\phi_k}.\\
     \text{Compute components:} \\
     \displaystyle  
     A_k e^{(\alpha_k + j\omega_k)(n-1)\Delta t + j\phi_k}. \\
\end{algorithm}

\section{non-stationary Prony method and shaping regularization}
The equation\textbf{~\ref{eqa:eq8}} can be rewritten as
\begin{equation}
    \label{eqa:eq9}
\sum_{m=1}^{M}\hat{a}_m x[n-m] = x[n].
\end{equation}
If the $\hat{a}_m, m=1,2,\cdots,M$ in equation\textbf{~\ref{eqa:eq9}} are time dependent, then we have
\begin{equation}
    \label{eqa:eq10}
    \sum_{m=1}^{M}\hat{a}_m[n] x[n-m] \approx x[n],
\end{equation}
which is under-determined. There many methods for the solving 
under-determined linear system. For example, \citet[]{tikhonov} 
used the regularization method for making the under-determined 
problem well-posed by adding constraints on the estimated model.
\subsection{Shaping regularization}
\citet[]{shape,lpf} introduces shaping regularization in inversion problem, 
which regularizes the under-determined linear system by mapping the model
to the space of acceptable models.
Consider a linear system given as $\mathbf{Fx = \mathbf{b}}$,
where $\mathbf{F}$ is the forward-modeling map, $\mathbf{x}$
is the model vector, and $\mathbf{b}$ is the data vector.
Tikhonov regularization method amounts to minimize the least square problem bellow 
\cite[]{tikhonov}:
\begin{equation}
    \label{eqa:eq11}
    \mathbf{min} \|\mathbf{Fx}-\mathbf{b}\|^2+\epsilon^2\|\mathbf{Dx}\|^2,
\end{equation}
where $\mathbf{D}$ is the regularization operator, and $\epsilon$ is a scalar parameter.
The solution for equation\textbf{~\ref{eqa:eq11}} is:
\begin{equation}
    \label{eqa:eq12}
    \mathbf{\hat{x}} = \left(\mathbf{F}^T\mathbf{F}+\epsilon^2 \mathbf{D}^T\mathbf{D}\right)^{-1}\mathbf{F}^T\mathbf{b},
\end{equation}
Where $\mathbf{\hat{x}}$ is the least square approximated of $\mathbf{x}$, $\mathbf{F}^T$
is the adjoint operator.
If the forward operator $\mathbf{F}$ is simply the identity operator, the solution of 
equation\textbf{~\ref{eqa:eq12}} is the form below:
\begin{equation}
    \label{eqa:eq13}
    \mathbf{\hat{x}} = \left(\mathbf{I}+\epsilon^2 \mathbf{D}^T\mathbf{D}\right)^{-1}\mathbf{b},
\end{equation}
which can be viewed as a smoothing process. If we let:
\begin{equation}
    \label{eqa:eq14}
    \mathbf{S} = \left(\mathbf{I}+\epsilon^2 \mathbf{D}^T\mathbf{D}\right)^{-1},
\end{equation}
or 
\begin{equation}
    \label{eqa:eq15}
    \epsilon^2 \mathbf{D}^T\mathbf{D} = \mathbf{S}^{-1} - \mathbf{I}.
\end{equation}
Substituting equation \textbf{~\ref{eqa:eq15}} into equation \textbf{~\ref{eqa:eq12}}
yields a solution by shaping regularization:
\begin{equation}
    \label{eqa:eq16}
    \mathbf{\hat{x}} = \left(\mathbf{F}^T\mathbf{F}+\mathbf{S}^{-1}-\mathbf{I}\right)^{-1}\mathbf{F}^T\mathbf{b}
     = \left[\mathbf{I} + \mathbf{S}\left(\mathbf{F}^T\mathbf{F}-\mathbf{I}\right)\right]^{-1}\mathbf{SF}^T\mathbf{b}.
\end{equation}
The forward operator $\mathbf{F}$ may has physical units that require scaling. Introducing 
scaling $\lambda$ into $\mathbf{F}$, equation \textbf{\ref{eqa:eq16}} be written as:
\begin{equation}
    \label{eqa:eq17}
    \mathbf{\hat{x}} = \left[\lambda^2\mathbf{I} + \mathbf{S}\left(\mathbf{F}^T\mathbf{F}-\lambda^2\mathbf{I}\right)\right]^{-1}\mathbf{SF}^T\mathbf{b}.
\end{equation}
If $\mathbf{S}=\mathbf{HH}^T$ with square and invertible $\mathbf{H}$. Equation \textbf{~\ref{eqa:eq17}} can be written as:
\begin{equation}
    \label{eqa:eq18}
    \mathbf{\hat{x}} = \mathbf{H}\left[\lambda^2\mathbf{I} + \mathbf{H}^T\left(\mathbf{F}^T\mathbf{F}-\lambda^2\mathbf{I}\right)\mathbf{H}\right]^{-1}\mathbf{H}^T\mathbf{F}^T\mathbf{b}.
\end{equation}
The conjugate gradient algorithm can be used for the solution of the equation\textbf{~\ref{eqa:eq18}}.

\subsection{Non-stationary Prony method}
Equation \textbf{\ref{eqa:eq10}} can be written as a matrix form:
\begin{equation}
    \label{eqa:eq19}
    \sum_{m=1}^{M}\mathbf{\hat{a}}_m(t)\mathbf{x}_m(t) \approx \mathbf{d}(t),
\end{equation}
where $\mathbf{d}(t) = \mathbf{x}(t)$, $\mathbf{x}_m(t) = \mathbf{x}(t-m\Delta t)$ is the time shift
of the input signal $\mathbf{x}(t)$ and $\mathbf{\hat{a}}_m(t)$ is the time-dependant coefficients.
We solve the under-determined linear system by using the shaping regularization method.
The solution is the form below:
\begin{equation}
    \label{eqa:eq20}
    \mathbf{a = F^{-1}\eta},
\end{equation}
where $\mathbf{a}$ is a vector of $\hat{a}(t)$, the elements of vector $\mathbf{\eta}$ is:
\begin{equation}
    \label{eqa:eq21}
    \mathbf{\eta}_i(t) = \mathbf{S}\left[\mathbf{x}_i^*(t)\mathbf{d}(t)\right],
\end{equation}
the elements of the matrix $\mathbf{F}$ is:
\begin{equation}
    \label{eqa:eq22}
    \mathbf{F}_{ij}= \sigma^2 \mathbf{\delta}_{ij} + S[\mathbf{x}_i^*(t)\mathbf{x}_j(t) - \sigma^2 \mathbf{\delta}_{ij}]
\end{equation}
where $\sigma$ is the regularization parameter, $\mathbf{S}$ is a shaping operator,
and $\mathbf{x}_i^*(t)$ stands for the complex conjugate of $\mathbf{x}_i(t)$.
We can use the conjugate gradient method to find the solution of the linear system.
The NPM \cite[]{fomel2013} can be summarized as follows:
%\begin{algorithm}
%   \caption{non-stationary Prony method} 
%   \label{pro:nopronyalgorithm}
% \begin{algorithmic}[1]
%     \State \textit{Find time dependent coefficients using auto-regression method:} 
%       $\displaystyle \hat{a}_k[n],k=1,\cdots,M \gets \sum_{m=0}^{M}\hat{a}_m[n]x[n-m] = 0.$
%     \State \textit{Find time dependent roots:} 
%        $\displaystyle \hat{z}_k[n],k=1,2,\cdots,M \gets \sum_{m=0}^{M}\hat{a}_m[n]z^{M-m}= 0.$
%     \State \textit{Compute time dependent frequencies:}
%        $\displaystyle \hat{\omega}_k[n], k=1,\cdots,M\gets\Re\left\{\mathbf{arg}\left(\frac{\hat{z}_k[n]}{\Delta t}\right)\right\}, k=1,\cdots,M.$
%     \State \textit{Compute the time dependent phase:} 
%      $\displaystyle \hat{\phi}_k[n] = \sum_{k=0}^{n}\hat{\omega}_k[n]\Delta t.$ 
%     \State \textit{Compute components using auto-regression method:} 
%       $\displaystyle \hat{c}_m[n], m=1,\cdots M \gets \mathbf{x}[n] \approx \sum_{m=1}^M \hat{A}_m[n]e^{j\hat{\phi}_m[n]}=\sum_{m=1}^M\hat{c}_m[n]$
% \end{algorithmic}
%\end{algorithm}

\begin{algorithm}{Algorithm 2: non-stationary Prony method}{}
     \text{Find time dependent coefficients using auto-regression method:}  \\
     \displaystyle \hat{a}_k[n],k=1,\cdots,M \gets \sum_{m=0}^{M}\hat{a}_m[n]x[n-m] = 0. \\
     \text{Find time dependent roots:}  \\
     \displaystyle \hat{z}_k[n],k=1,2,\cdots,M \gets \sum_{m=0}^{M}\hat{a}_m[n]z^{M-m}= 0.\\
     \text{Compute time dependent frequencies:}  \\
     \displaystyle \hat{\omega}_k[n], k=1,\cdots,M\gets\Re\left\{\mathbf{arg}\left(\frac{\hat{z}_k[n]}{\Delta t}\right)\right\}, k=1,\cdots,M.\\
     \text{Compute the time dependent phase:}   \\
     \displaystyle \hat{\phi}_k[n] = \sum_{k=0}^{n}\hat{\omega}_k[n]\Delta t.\\
     \text{Compute components using auto-regression method:}   \\
     \displaystyle \hat{c}_m[n], m=1,\cdots M \gets \mathbf{x}[n] \approx \sum_{m=1}^M \hat{A}_m[n]e^{j\hat{\phi}_m[n]}=\sum_{m=1}^M\hat{c}_m[n]
\end{algorithm}

After we decompose the input signal into narrow-band components, 
we compute the time-frequency distribution of the input signal 
using the Hilbert transform of the intrinsic mode functions.

\newpage
\bibliographystyle{seg}
\bibliography{npm}

### 2020-09-16 odrr3d/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\title{Seismic signal enhancement based on the lowrank methods}
\author{Min Bai\footnotemark[1]\footnotemark[2], Guangtan Huang\footnotemark[1], Hang Wang\footnotemark[1], and Yangkang Chen\footnotemark[1]}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

%\author{Yangkang Chen\footnotemark[1] et al.}

\ms{GP-2020} %\ms{GJI-2018}

\address{
\footnotemark[1]School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
baimin2016@126.com \\
\footnotemark[2]
Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
Yangtze University\\
Wuhan, Hubei Province, China, 430100 \\
}

\lefthead{Bai et al., 2020}
\righthead{LR methods}

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}

\begin{abstract}
Based on the fact that the Hankel matrix constructed by noise-free seismic data is lowrank (LR), LR approximation (or rank-reduction) methods have been widely used for removing noise from seismic data. Due to the linear-event assumption of the traditional LR approximation method, it is difficult to define a rank that optimally separates the data subspace into signal and noise subspaces. For preserving the most useful signal energy, a relatively large rank threshold is often chosen, which inevitably leaves residual noise. To reduce the energy of residual noise, we propose an optimally damped rank-reduction method. The optimal damping is applied via two steps. In the first step, a set of optimal damping weights is derived. In the second step, we derive an optimal singular-value damping operator. We review several traditional lowrank methods and compare their performance with the new one. We also compare these lowrank methods with two sparsity-promoting transform methods. Examples demonstrate that the proposed optimally damped rank-reduction method could get significantly cleaner denoised images compared with the state-of-the-art methods.  \par
\textbf{Key words:} Random noise attenuation, multidimensional seismic data, lowrank approximation, optimal damping
\end{abstract}

\section{Introduction}
Random noise can seriously affect the stability and precision of seismic data processing and imaging steps including inversion-based migration, full waveform inversion, AVO inversion, and \dlo{also }post-stack seismic interpretation\dlo{, and thus}\wen{. Thus,} \dlo{the removal of it}\wen{its removal} is \old{indispensable}\new{very important} \cite[]{galbraith1991,block3d2017,zhaoqiang2018,shucai2020}.

\dlo{In the past decades, many algorithms have been proposed to attenuate the random noise in the seismic data. One widely used seismic denoising strategy is based on transforming the noisy data into another domain in order to concisely represent the signal with a few number of selected components that capture the useful information.}  The sparse transform based denoising methods assume the seismic data to be sparse in the transform domain and the spreading noise in the transform domain can be suppressed by applying a thresholding operation. These \wen{methods} include\dlo{ approaches} \dlo{that are}\wen{those} based on the \wen{Fourier transform \cite[]{fourier1986}}, Radon transform \cite[]{beylkin1987discrete}, seislet transform \cite[]{fomel2010seislet,yangkang2018eseis}, curvelet transform \cite[]{candes20061}, wavelet transform \cite[]{gilles2013,mostafa2016geo}, dreamlet transform \cite[]{huang2018damped}, dictionary-learning based sparse transform \cite[]{yanhui2016,amir2017sp,amir2017geo,shaohuan2019dl}. \dlo{Another type of methods utilizes the predictable property of seismic data}\wen{Prediction based methods are another group of popular denoising methods}, such as \dlo{the }time-space domain prediction method \cite[]{abma1995}, frequency-space predictive filtering \cite[]{canales1984}, regularized non-stationary prediction method \cite[]{guochang2012,guochang2013}, and the polynomial fitting method \cite[]{guochang20112}. The decomposition based denoising methods consider the separability of seismic signal and random noise and attempt to extract useful information from the principal components of the noisy data. Typical methods include the empirical-mode decomposition (EMD) related methods \cite[]{huangemd}, e.g., the ensemble EMD \cite[]{eemd}, complete ensemble empirical-mode decomposition \cite[]{epsceemd}, improved complete ensemble empirical-mode decomposition \cite[]{epsceemd}, \dlo{etc.} singular-value decomposition (SVD) related methods \cite[]{bekara2007}, \wen{and} non-stationary decomposition with regularization \cite[]{li2018multidimensional}.

\dlo{In this paper we’re going to improve on the multi-spatial-dimensional Cadzow filter}\wen{In this paper, we aim to improve on the multi-dimensional Cadzow filter} applied to constant-frequency slices \cite[]{cadzow1988,trickett2008}, also referred to as multichannel singular spectrum analysis (MSSA) \cite[]{mssa,stephen2013,curveletieee2016}. This filter
has been widely adopted for seismic data processing due to its \dlo{superb}\wen{good} performance \cite[]{ginolhac2013performance,gao2017five,wang2018hankel}. This algorithm is based on lowrank (LR) matrix approximation. \dlo{Among the denoising approaches, the lowrank (LR) approximation and optimization based approaches have been widely adopted for seismic data denoising because of their superb performance ?. }The \dlo{basic}\wen{main requirement}\dlo{ assumption} of the LR methods is the low rank of the frequency-domain Hankel matrix. \dlo{The rank of such Hankel matrix equals to the number of distinct dips}\wen{The rank of the Hankel matrix equals the number of distinct dips}  \cite[]{mssa,yangkang2016irr5d,wang2020low}. However, the real seismic data are complicated, where the linear-events assumption is not met. To apply the LR methods, one needs to divide the field data into small time-space windows for separate processing \cite[]{zhangdong2017,shaohuan2017gji}. Nevertheless, it will cause another problem in local processing window\wen{s}, i.e., if we use a fixed rank for all the local windows, then it is \dlo{very }possible that this rank is too large for some windows (so that the LR approximation keeps too much noise) and is too small for some other windows (such that the method loses the useful information). Thus, to optimize the denoising performance, it is desirable to find the appropriate rank for each local window. The rank can also be adaptively selected according to the ratio of two consecutive singular-values \cite[]{wujuan2018jge}. However, all these strategies work only when the data structure is not complex and may not be applicable when noise is extremely strong.

In practice, the predefined rank is usually set large enough to preserve the useful signals without damaging weak and curving energy. The selection of a large rank \wen{could} leave significant \dlo{amount of }residual noise in the filtered data. One possible solution is to use a threshold to further suppress the residual noise after the rank-reduction step. This second-step thresholding can be understood conveniently in the framework of nuclear norm minimization \wen{\cite[]{yatong2017nuclear}}. This strategy brings another challenging question on how to optimally choose the threshold for damping the residual noise. Considering that the thresholding step can be interpreted as a re-weighting process for the singular-values, we apply an adaptive singular-value weighting method following \cite{optshrink2013}. This weighting method is an adaptive to shrinkage the singular values as compared with the direct truncation strategy. \cite{aharchaou2017singular} introduced this adaptive weighting method to seismic data reconstruction problems. Some other alternatives to the presented approach in this paper, such as  those automated methods in \cite[]{gavish2014optimal} or \cite{trickett2015preserving}. One can further improve the optimal weighting based rank-reduction method by cascading the weighting strategy into the damed rank-reduction framework. The \dlo{resulted}\wen{resulting} algorithm is referred to as the optimal damped rank-reduction \wen{(ODRR)} method. It has the potential to make the damped rank-reduction method effective for a wide range of rank selection in an adaptive way.  We use different synthetic and field seismic datasets to show the \dlo{superiority}\wen{advantages} of the presented algorithm.

\section{Theory}
\dlo{It is known that the following optimization model can be applied to express the noise suppression problem $\hat{\mathbf{x}} = \arg \min_{\mathbf{x}} \parallel \mathbf{y} - \mathbf{x} \parallel_2^2,\text{subject to}\quad \mathbf{C}(\mathbf{x}) \le t$}

\dlo{where $\mathbf{y}$ denotes the noisy data, $\mathbf{x}$ denotes the noise-free data. $\hat{\mathbf{x}}$ denotes the estimation of the noise-free data, and $\mathbf{C}$ denotes a constraint for the model, i.e., the noise-free data. The constraint $\mathbf{C}(\mathbf{x})\le t$ represents the priori knowlege of the model. }

\dlo{We can also denoise data data by minimizing the constraint operator of the model, given that the data misfit is bounded by a limit $\epsilon$: $\hat{\mathbf{x}} = \arg \min_{\mathbf{x}} \mathbf{C}(\mathbf{x}) , \text{subject to} \quad \parallel \mathbf{y} - \mathbf{x} \parallel_2^2 \le \epsilon.$}

\dlo{Because it is difficult to have priori information for both data misfit and model constraint, in realistic situations, it is more flexible to use the following unconstrained model to denoise seismic data: $\hat{\mathbf{x}} = \arg \min_{\mathbf{x}} \parallel \mathbf{y} - \mathbf{x} \parallel_2^2 + \lambda  \mathbf{C}(\mathbf{x})$ where we use a regularization parameter $\lambda$ to balance the data misfit and model constraint. }

\subsection{Hankel matrix embedding}
The rank-reduction based methods discussed in this paper \dlo{construct a block Hankel matrix from a 2D spatial matrix (Inline and Xline) in the frequency domain}\wen{deal with a block Hankel matrix (Inline and Xline) in the frequency-space domain}. Let $\mathbf{D}(t,x,y)$ (of size $N_t\times N_x\times N_y$) represent a 3D seismic dataset. \dlo{Consider a block of 3D data $\mathbf{D}(t,x,y)$ of $N_t$ by $N_x$ by $N_y$ samples. } First, we transform $\mathbf{D}(t,x,y)$ in time-space domain to $\mathbf{D}(w,x,y)(w=1\cdots N_w)$ in the frequency-space domain. At a given frequency $w_0$ slice, the 2D data can be expressed as \cite[]{mssa}:
\begin{equation}
\label{eq:mssa3d}
\mathbf{D}(w_0)=\left(\begin{array}{cccc}
D(1,1) & D(1,2) & \cdots &D(1,N_y) \\
D(2,1) & D(2,2)  &\cdots &D(2,N_y) \\
\vdots & \vdots &\ddots &\vdots \\
D(N_x,1)&D(N_x,2) &\cdots&D(N_x,N_y)
\end{array}
\right).
\end{equation}
\dlo{In the following context}\wen{From here on}, $w_0$ is omitted for notational convenience. \dlo{Then, a}\wen{A} Hankel matrix is \wen{then} constructed from \dlo{each row of }$\mathbf{D}$. We first construct a Hankel matrix $\mathbf{R}_i$ as:
\new{\begin{equation}
\label{eq:data}
\mathbf{R}_i=\left(\begin{array}{cccc}
D(i,1) & D(i,2) & \cdots &D(i,m) \\
D(i,2) & D(i,3)  &\cdots &D(i,m+1) \\
\vdots & \vdots &\ddots &\vdots \\
D(i,N_y-m+1)&D(i,N_y-m+2) &\cdots&D(i,N_y)
\end{array}
\right),
\end{equation}}
and then construct the block Hankel matrix as:
\begin{equation}
\label{eq:hankel2}
\mathbf{M}=\left(\begin{array}{cccc}
\mathbf{R}_1 &\mathbf{R}_2 & \cdots &\mathbf{R}_n \\
\mathbf{R}_2 &\mathbf{R}_3 &\cdots &\mathbf{R}_{n+1} \\
\vdots & \vdots &\ddots &\vdots \\
\mathbf{R}_{N_x-n+1}&\mathbf{R}_{N_x-n+2} &\cdots&\mathbf{R}_{N_x}
\end{array}
\right).
\end{equation}
\wen{Parameters} $m$ and $n$ are chosen to make $\mathbf{R}_i$ and $\mathbf{M}$ close to square matrices, e.g., $m=N_y-\lfloor\frac{N_y}{2}\rfloor$ and $n=N_x-\lfloor\frac{N_x}{2}\rfloor$. The symbol $\lfloor\cdot \rfloor$ outputs the integer of an input value. The matrix $\mathbf{M}$ is of size $I\times J$, with $I=(N_y-m+1)(N_x-n+1)$, $J=mn$. The block Hankel matrix $\mathbf{M}$ is considered to be lowrank \cite[]{trickett2008,mssa,weilin2016dmssa,yangkang2019nc}\wen{, i.e., it can be approximated by a small number of eigen-images}.

\wen{\subsection{Rank-reduction method}
Regularization can be implemented as a rank-based constraint \wen{\cite[]{trickett2008,mssa,jinkun2015}}:
\begin{equation}
\label{eq:regu2}
\begin{split}
\hat{\mathbf{X}} &= \arg \min_{\mathbf{x}} \parallel\mathbf{D}-\mathbf{X} \parallel_F^2, \\ \text{subject to}&\quad \text{rank} (\mathcal{H}(\mathbf{X})) =N,
\end{split}
\end{equation}
%or in an unconstrained version as
%\begin{equation}
%\label{eq:regu2}
%\hat{\mathbf{X}} = \arg \min_{\mathbf{X}} \parallel\mathbf{D}-\mathbf{X} \parallel_F^2 + %\epsilon^2\text{rank} (\mathcal{H}(\mathbf{X})),
%\end{equation}
\wen{where} $\parallel\cdot\parallel_F$ denotes the Frobenius norm. $\mathbf{D}$ denotes a matrix constructed \dlo{by}\wen{from} the frequency slice corresponding to $w_0$. $\mathbf{X}$ denotes the noise-free data to be estimated. $\hat{\mathbf{X}}$ denotes the estimated signal. $\mathcal{H}(\mathbf{X})$ denotes the Hankel matrix constructed from $\mathbf{X}$. Let $\mathbf{M}=\mathcal{H}(\mathbf{D})$, the singular value decomposition of $\mathbf{M}$ can be expressed as 
\begin{equation}
\label{eq:svd}
\mathbf{M} = \mathbf{U}\boldsymbol{\Sigma}\mathbf{V}^H,
\end{equation}
where $\mathbf{U}$ and $\mathbf{V}$ are referred to as the left and right singular vector matrices, respectively. $\boldsymbol{\Sigma}$ is the singular value matrix. $(\cdot)^H$ denotes complex tranpose. According to equation \ref{eq:regu2}, the rank of the signal component that is embedded in the Hankel matrix $\mathbf{M}$ is assumed to be $N$. The traditional rank-reduction method based on the truncated singular value decomposition (TSVD) \cite[]{mssa} can be briefly expressed as
\begin{equation}
\label{eq:tsvd}
\hat{\mathbf{S}} = \mathbf{U}_N\boldsymbol{\Sigma}_N\mathbf{V}_N^H,
\end{equation}
which is a solution to equation \ref{eq:regu2} according to the Eckart-Young-Mirsky theorem \cite[]{eckart1936approximation}. $\hat{\mathbf{S}}$ denotes the denoised signal. $\mathbf{U}_N$ and $\mathbf{V}_N$ are matrices composed of the left $N$ singular vectors in $\mathbf{U}$ and $\mathbf{V}$, respectively. $\boldsymbol{\Sigma}_N$ is the truncated singular value matrix with the first $N$ singular values preserved.  Although theoretically $N$ equals to the number of distinct dipping components, it is practically defined as a relatively large number considering data complexity, otherwise signal energy can be damaged. The algorithm workflow for the traditional rank-reduction method (RR) is outlined in Algorithm \ref{alg:alg1}. $\mathcal{A}$ in the algorithm workflow denotes an averaging operator along anti-diagonals.}

\wen{\subsection{Damped rank-reduction method}
The estimated signal using the TSVD method, however, \dlo{is still containing}\wen{still contains} non-negligible residual noise components, as explained in \cite{weilin2016dmssa}. The problem of residual noise can be solved to some extent by further applying a thresholding operator to the singular value matrix according to the nuclear-norm minimization model \cite[]{yatong2017nuclear}:
\begin{equation}
\label{eq:nuclear}
\hat{\mathbf{S}} =\mathbf{U}_N\mathcal{T}(\boldsymbol{\Sigma}_N,\tau)\mathbf{V}_N^H,
\end{equation}
where $\mathcal{T}$ denotes the thresholding operator for the singular-values, and $\tau$ denotes the threshold of the operator. Defining an optimal threshold $\tau$, however, is often challenging because a constant threshold is inadequate to handle an inhomogeneous distribution of noise energy. \cite{weilin2016dmssa} developed a more elegant way to shrinkage the singular values by deriving a damping operator:
\begin{align}
\label{eq:damp}
\mathbf{P} &= \mathbf{I} - \boldsymbol{\Gamma}, \\
\label{eq:damp2}
\boldsymbol{\Gamma} &= \hat{\sigma}^K\left(\boldsymbol{\Sigma_N}\right)^{-K},
\end{align}
where $\mathbf{P}$ is called the damping matrix, $\mathbf{I}$ is an identity matrix, and $\boldsymbol{\Gamma}$ is referred to as the damping threshold matrix. $\hat{\sigma}$ is the $(N+1)$th singular value in the un-truncated singular matrix $\boldsymbol{\Sigma}$. \new{$K$ in equation \ref{eq:damp2} is called the damping factor}, which is used to control the strength of the damping operator. In a special case, when $K\rightarrow \infty$, $\mathbf{P}\rightarrow\mathbf{I}$, indicating that the damped rank-reduction method reverts to the traditional rank-reduction method. The mathematical details to derive the damping operator can be found in \cite{weilin2016dmssa} and \cite{weilin2017dlsp}. The damping operator is used to shrinkage the singular values in the TSVD formula to reduce the residual noise:
\begin{equation}
\label{eq:drr}
\hat{\mathbf{S}} = \mathbf{U}_N\mathbf{P}\boldsymbol{\Sigma}_N\mathbf{V}_N^H.
\end{equation}
Compared with the thresholding method in equation \ref{eq:nuclear}, where a rigid threshold $\tau$ is used to shrinkage the singular values, the damping operator applies variable thresholds to different singular values. According to equation \ref{eq:damp}, the threshold decreases as the residual noise becomes less dominant, i.e., the singular value becomes larger. The algorithm workflow for the damped rank-reduction method (DRR) is outlined in Algorithm \ref{alg:alg2}.}

\wen{\subsection{Optimally damped rank-reduction method}
A shortcoming of the traditional rank-eduction and damped rank-reduction methods is that the output perfomance is quite sensitive to the input parameter $N$. The rank parameter varies greatly for different datasets, especially for field datasets. In order to alleviate the influence of the rank parameter, we take advantage of an adaptive singular-value weighting algorithm developed by \cite{Benaych2012The} and \cite{optshrink2013}. An adaptive singular-value weighting matrix can be obtained by solving the following problem:
\begin{equation}
\label{eq:opt}
\hat{\boldsymbol{\omega}}=\arg\min_{\boldsymbol{\omega}} \parallel \sum_{i=1}^{N} \sigma_i\mathbf{u}_i^S(\mathbf{v}_i^S)^H - \omega_i\sigma_i\mathbf{u}_i\mathbf{v}_i^H \parallel_F,
\end{equation}
where $\mathbf{u}_i^S$ and $\mathbf{v}_i^S$ denote $i$th left and right singular vectors corresponding to the estimated signal component, $\sigma_i$ denotes the $i$th singular value in $\boldsymbol{\Sigma}$. $\boldsymbol{\omega}$ is the adaptive weight vector, which can be used to construct the adaptive weighting matrix $\hat{\mathbf{W}}=\text{diag}(\hat{\boldsymbol{\omega}})$. The solution to the optimization problem can be obtained as:
\begin{equation}
\label{eq:optw}
\hat{w}_i=\left(-\frac{2}{\sigma_i}\frac{\mathcal{D}(\sigma_i;\boldsymbol{\Sigma})}{\mathcal{D}'(\sigma_i;\boldsymbol{\Sigma})}\right).
\end{equation}
where $\mathcal{D}$ represents a transform expressed as:
\begin{equation}
\label{eq:D1}
\mathcal{D}(\sigma;\boldsymbol{\Sigma})= \frac{1}{N^2} \text{Tr}\left(\sigma(\sigma^2\mathbf{I}-\boldsymbol{\Sigma}\boldsymbol{\Sigma}^H)^{-1}\right) \text{Tr}\left(\sigma(\sigma^2\mathbf{I}-\boldsymbol{\Sigma}^H\boldsymbol{\Sigma})^{-1}\right),
\end{equation}
and $\mathcal{D}'$ denotes its derivative. \dlo{Its expression can be found in.}\wen{The expression of $\mathcal{D}'$  can be expressed as:} 
\wen{
\begin{equation}
\label{eq:D2}
\begin{split}
D'(\sigma;\boldsymbol{\Sigma})&= 2\left[\frac{1}{N} \text{Tr}\left(\sigma(\sigma^2\mathbf{I}-\boldsymbol{\Sigma}^2)^{-1}\right)\right]\left[\frac{1}{N} \text{Tr}\left((\sigma^2\mathbf{I}-\boldsymbol{\Sigma}^2)^{-1}-2\sigma(\sigma^2\mathbf{I}-\boldsymbol{\Sigma}^2)^{-2}\sigma\right)\right] \\
&=\frac{2}{N^2}\left[ \text{Tr}\left(\sigma(\sigma^2\mathbf{I}-\boldsymbol{\Sigma}^2)^{-1}\right)\right]\left[ \text{Tr}\left((\sigma^2\mathbf{I}-\boldsymbol{\Sigma}^2)^{-1}-2\sigma^2(\sigma^2\mathbf{I}-\boldsymbol{\Sigma}^2)^{-2}\right)\right].
\end{split}
\end{equation}
}
The symbol $\text{Tr}(\cdot)$ denotes the trace of the input. \wen{The trace of a square matrix $\mathbf{X}$ is defined to be the sum of elements on the main diagonal of $\mathbf{X}$.}
\wen{
\begin{equation}
\label{eq:tr}
\text{Tr}(\mathbf{X}) = \sum_{i=1}^{N}X_{i,i},
\end{equation}
where $X_{i,i}$ denotes the main diagonal elements of $\mathbf{X}$.
}

 The adaptive weighting operator can be applied to make the traditional rank-reduction method adaptive:
\begin{equation}
\label{eq:opts}
\hat{\mathbf{S}}=\mathbf{U}_N\hat{\mathbf{W}}\boldsymbol{\Sigma}_N\mathbf{V}_N^H.
\end{equation}
To incorporate the adaptive weighting operator into the damped rank-reduction framework, we can introduce intermediate variables as 
\begin{align}
\label{eq:svds_qu}
\mathbf{U}_N^{Q} = \mathbf{U}_N,\\
\label{eq:svds_qs}
\boldsymbol{\Sigma}_N^{Q} = \hat{\mathbf{W}}\boldsymbol{\Sigma}_N,\\
\label{eq:svds_qv}
\mathbf{V}_N^{Q} = \mathbf{V}_N,
\end{align}
then equation \ref{eq:opts} turns into 
\begin{equation}
\label{eq:opts2}
\hat{\mathbf{S}}=\mathbf{U}_N^{Q}\boldsymbol{\Sigma}_N^{Q}\mathbf{V}_N^{Q}.
\end{equation}
It can be derived that the damping formula (equation \ref{eq:damp}) also holds for equation \ref{eq:opts2} but with the damping threshold matrix expressed as
\begin{equation}
\label{eq:dampt}
\boldsymbol{\Gamma} = \hat{\sigma}^K\left(\boldsymbol{\Sigma_N^Q}\right)^{-K},
\end{equation}
where the subscript $N$ denotes a sufficiently large rank parameter, as required by the derivations detailed in \cite{yangkang2019gji5d}.  The resulted final form of the optimally damped rank-reduction method then can be expressed as 
\begin{equation}
\label{eq:odrr}
\hat{\mathbf{S}} = \mathbf{U}_N\mathbf{P}\hat{\mathbf{W}}\boldsymbol{\Sigma}_N\mathbf{V}_N^H.
\end{equation}
The algorithm workflow for the optimally damped rank-reduction method (ODRR) is outlined in Algorithm \ref{alg:alg3}. Due to the existence of a weighting matrix in the proposed method, it is more convenient to choose the input rank parameter $N$ empirically in practice. As mentioned previously, the rank parameter $N$ is in practice set to a relatively large value to forestall damaging the signal. But in the proposed algorithm, even if a large $N$ is used, the algorithm can adaptively shrink the singular-values. Thus, \dlo{the}\wen{its} performance is not sensitive to the input rank parameter, in contrast to other related approaches \cite[]{mssa}. Because of the insensitivity, one can use a sufficiently large $N$ in processing complicated datasets without leaving strong residual noise in the result. The convenience in tuning parameters makes the rank-reduction related methods more computationally feasible in large-scale data processing, e.g., the 5D reconstruction problem \cite[]{yangkang2019gji5d}, since one no longer needs to tune the parameters many times while one trial is already computationally demanding.  A glossary describing the main mathematical notations are presented in Table \ref{tbl:glo}. The three methods are all variations of how the singular-values are thresholded. Simply speaking, the DRR method improves the RR method by introducing a damping operation and the ODRR method improves DRR method by further introducing a weighting operation.}

\AtEndDocument{
\begin{table}[ht!]
\caption{Glossary of \dlo{the }main mathematical notations \wen{used} in this paper.}
\begin{center}
     \begin{tabular}{|c|c|} 
	  \hline Symbols  &  Meanings \\ 
	  \hline $\mathbf{D}(t/w,x,y)$  & 3D noisy seismic data \\
	  \hline $\mathbf{D}(w_0)$ or $\mathbf{D}$  & \dlo{brief}\wen{abbreviated} notation of 2D frequency slice \\
	  \hline $\mathbf{R}_i$ &  $i$th Hankel matrix\\
	  \hline $\mathbf{M}$ &  block Hankel matrix\\
	  \hline $\mathbf{S}$ & signal\dlo{ and noise} component\\
	  \hline $\hat{\mathbf{S}}$ & estimated signal component\\
%	  \hline $\mathbf{N}$ & \dlo{signal and }noise component\\
	  \hline $\mathbf{U}$ & left singular vector matrix\\
	  \hline $\boldsymbol{\Sigma}$ & singular-value matrix\\
	  \hline $\mathbf{V}$ & right singular vector matrix\\
	  \hline $\hat{\mathbf{W}}$ & weighting matrix \\
	  \hline  $\mathbf{P}$ &  damping matrix\\
	  \hline $\boldsymbol{\Gamma}$ & damping threshold matrix\\	 
	  	  	  \hline $\mathbf{Q}$ & temporary variable\\	
	  	  	  	  \hline $\mathcal{D}$ & D-transform\\	
	  \hline $\mathcal{H}$ &  Hankelization operator\\
	  \hline $\mathcal{T}$ &  thresholding operator\\
	  \hline $\mathcal{A}$ &  averaging operator\\
		 \hline $N$ & rank\\	
		\hline  $K$ & damping factor\\	
          \hline
    \end{tabular} 
\end{center}
\label{tbl:glo}
\end{table}

\begin{table}[ht!]
\caption{Comparison of SNRs in dB for different rank-reduction based methods. \wen{RR denotes the \dlo{traditional }rank-reduction method. DRR denotes the damped rank-reduction method. \dlo{Proposed}\wen{ODRR} denotes the optimally damped rank-reduction method.}}
\begin{center}
     \begin{tabular}{|c|c|c|c|c|} 
	  \hline Tests  &  Noisy (dB) & RR (dB)  &  DRR (dB)  &  \dlo{Proposed}\wen{ODRR} (dB) \\ 
	  \hline \wen{Linear synthetic} (N=3) & -8.39 & 6.57 & 10.29 & 11.27 \\
      \hline \wen{Linear synthetic} (N=6) & -8.39 & 3.45 & 8.35 & 10.86\\
	  \hline \wen{Hyperbolic synthetic (N=10)} & -2.17 & 8.27 & 9.58 & 9.65 \\
      \hline \wen{Hyperbolic synthetic (N=20)} & -2.17 & 7.04 & 10.08 & 11.00\\
          \hline
    \end{tabular} 
\end{center}
\label{tbl:snrs}
\end{table}

\begin{table}[ht!]
\caption{\wen{Comparison of computational costs in seconds for different rank-reduction based methods.}}
\begin{center}
     \begin{tabular}{|c|c|c|c|c|c|c|} 
	  \hline Tests  & FK (s) & RR (s)  &  DRR (s) &  \dlo{Proposed}\wen{ODRR} (s) \\ 
	  \hline \dlo{First example}\wen{Linear synthetic} (N=3) & 0.13 & 2.27 & 2.45 & 2.43 \\
      \hline \dlo{First example}\wen{Linear synthetic} (N=6) & 0.17  &3.02 & 3.04 & 3.17 \\
	  \hline \dlo{Second example}\wen{Hyperbolic synthetic} (N=10)   &0.43 &1.69 & 1.71 & 1.83 \\
      \hline \dlo{Second example}\wen{Hyperbolic synthetic} (N=20)   &0.49 & 2.75 & 2.69 & 2.83\\
          \hline
    \end{tabular} 
\end{center}
\label{tbl:times}
\end{table}
}

\wen{
  \begin{algorithm}
   \caption{Seismic denoising \dlo{seismic data via}\wen{based on} rank-reduction method. }
   \textbf{Require:} Input \dlo{seismic }data $\mathbf{D}(t,x,y)$ and predefined rank $N$.
    \begin{algorithmic}[1]
    \State \textbf{Fourier transform along the time axis}: $\text{FFT}\left(\mathbf{D}(t,x,y)\right)\rightarrow \mathbf{D}(\omega,x,y)$, \wen{for a frequency slice $\omega$}
        \For{$w$ = $1,\cdots,N_{\omega}$}
     \State \textbf{Construct block Hankel matrix}: $\mathcal{H}(\mathbf{D}(\omega))\rightarrow \mathbf{M}$
     \State \textbf{Singular value decomposition}: $\text{SVD}(\mathbf{M},N)\rightarrow [\mathbf{U},\boldsymbol{\Sigma},\mathbf{V}]$
     \State \textbf{Rank reduction}: $\mathbf{U}\boldsymbol{\Sigma}\mathbf{V}^T\rightarrow \hat{\mathbf{S}}$
     \State \textbf{Averaging}: $\mathcal{A}(\hat{\mathbf{S}})\rightarrow \hat{\mathbf{D}}(\omega)$
        \EndFor 
         \State \textbf{Inverse Fourier transform}: $\text{IFFT}\left(\hat{\mathbf{D}}(\omega,x,y)\right)\rightarrow \hat{\mathbf{D}}(t,x,y)$
\end{algorithmic}
\label{alg:alg1}
\end{algorithm}
  \begin{algorithm}
   \caption{Seismic denoising based on the damped rank-reduction method. }
   \textbf{Require:} \wen{Input seismic data $\mathbf{D}(t,x,y)$, predefined rank $N$, and damping factor $K$.}
    \begin{algorithmic}[1]
    \State \textbf{Fourier transform along the time axis}: $\text{FFT}\left(\mathbf{D}(t,x,y)\right)\rightarrow \mathbf{D}(\omega,x,y)$, \wen{for a frequency slice $\omega$}
        \For{$w$ = $1,\cdots,N_{\omega}$}
     \State \textbf{Construct block Hankel matrix}: $\mathcal{H}(\mathbf{D}(\omega))\rightarrow \mathbf{M}$
     \State \textbf{Singular value decomposition}: $\text{SVD}(\mathbf{M},N)\rightarrow [\mathbf{U},\boldsymbol{\Sigma},\mathbf{V}]$
     \State \textbf{Rank reduction with the damping operation}: $\mathbf{U}\mathbf{P}\boldsymbol{\Sigma}\mathbf{V}^T\rightarrow \hat{\mathbf{S}}$
     \State \textbf{Averaging}: $\mathcal{A}(\hat{\mathbf{S}})\rightarrow \hat{\mathbf{D}}(\omega)$
        \EndFor 
         \State \textbf{Inverse Fourier transform}: $\text{IFFT}\left(\hat{\mathbf{D}}(\omega,x,y)\right)\rightarrow \hat{\mathbf{D}}(t,x,y)$
\end{algorithmic}
\label{alg:alg2}
\end{algorithm}
  \begin{algorithm}
   \caption{Seismic denoising based on the optimally damped rank-reduction method. }
   \textbf{Require:} \wen{Input seismic data $\mathbf{D}(t,x,y)$, predefined rank $N$, and damping factor $K$.}
    \begin{algorithmic}[1]
    \State \textbf{Fourier transform along the time axis}: $\text{FFT}\left(\mathbf{D}(t,x,y)\right)\rightarrow \mathbf{D}(\omega,x,y)$, \wen{for a frequency slice $\omega$}
        \For{$w$ = $1,\cdots,N_{\omega}$}
     \State \textbf{Construct block Hankel matrix}: $\mathcal{H}(\mathbf{D}(\omega))\rightarrow \mathbf{M}$
     \State \textbf{Singular value decomposition}: $\text{SVD}(\mathbf{M},N)\rightarrow [\mathbf{U},\boldsymbol{\Sigma},\mathbf{V}]$
     \State \textbf{Rank reduction with both weighting and damping operations}: $\mathbf{U}\mathbf{P}\hat{\mathbf{W}}\boldsymbol{\Sigma}\mathbf{V}^T\rightarrow \hat{\mathbf{S}}$
     \State \textbf{Averaging}: $\mathcal{A}(\hat{\mathbf{S}})\rightarrow \hat{\mathbf{D}}(\omega)$
        \EndFor 
         \State \textbf{Inverse Fourier transform}: $\text{IFFT}\left(\hat{\mathbf{D}}(\omega,x,y)\right)\rightarrow \hat{\mathbf{D}}(t,x,y)$
\end{algorithmic}
\label{alg:alg3}
\end{algorithm}}

\wen{\section{Results}}
In this section, several \dlo{typical}synthetic and \dlo{real}\wen{field} data examples will be used to test the validity of the proposed method. We will use examples containing both crossing linear events and hyperbolic events to test the sensitivity of methods to different data structures. \wen{For synthetic examples}, we use the \wen{signal-to-noise} ratio (SNR) metric for quantitative evaluation, which is defined as follows:
\wen{\begin{equation}
\label{eq:snr}
\text{SNR(dB)}=10\log_{10}\frac{\Arrowvert \mathbf{S} \Arrowvert_F^2}{\Arrowvert \mathbf{S} -\hat{\mathbf{S}}\Arrowvert_F^2}.
\end{equation}}
where $\hat{\mathbf{S}}$ and $\mathbf{S}$ denote the estimated signal and exact solution, respectively. \dlo{Besides}\wen{In addition},  we use the local similarity attribute \cite[]{yangkang2015ortho} to measure the \dlo{damages}\wen{damage} that a denoising method \dlo{causes}\wen{can cause} to seismic data. \dlo{Generally speaking}\wen{In general}, higher local similarity between the denoised data and removed noise indicates \dlo{larger damages}\wen{greater damages}. The local similarity attribute \dlo{lets one quantify}\wen{allows to quantify} the effectiveness of a denoising algorithm on datasets \dlo{for which one does not have ground truth}\wen{when the exact solution is unknown}. The local similarity can also measure the local orthogonality between the separated signal and noise components \cite[]{yangkang2015ortho}. Here, we assume that the signal and noise components should be locally \dlo{orthogonally}\wen{orthogonal}, which is \dlo{revealed}\wen{indicated} by low anomalies in the local similarity maps. Processing pre-stack seismic data is much more challenging than that for post-stack seismic data. \dlo{There can be subtle diffraction signals that could be attenuated as noise and potentially damage images along faults. Here, we only consider processing of post-stack seismic data.} Subtle diffraction signals could be treated \dlo{by the algorithm as noise}\wen{as noise by the algorithm} and be attenuated, potentially damaging images along faults. \wen{ In this paper, we only focus on the denoising of post-stack seismic data, but further work could focus on noise attenuation of pre-stack data.}

\wen{\subsection{Synthetic examples}}
The first example is shown in Figure \ref{fig:syn3d-cn} \dlo{, where (a) is the clean data and (b) is the noisy data}\wen{including both clean and noisy data}.\dlo{ We add some random noise to the clean data (Figure \ref{fig:syn3d-c}) to simulate the noisy data.} The noisy data has an SNR of -8.39 dB. In this test, we compare the denoising performance of four different methods\dlo{, i.e.,}\wen{:} the frequency-wavenumber (FK) domain thresholding method \cite[]{arazthesis,abma2015}, the \dlo{traditional }rank-reduction method (RR), the damped rank-reduction method (DRR), and the proposed method \wen{(ODRR)}. \wen{In this example, we do not use local windows. We use the Ricker wavelet with a dominant frequency of 40 Hz to generate the clean data. We add Gaussian white noise with variance of 0.2 (as compared with the normalized clean data).  } Since the proposed method is an improved version of the DRR method, we compare the proposed method \dlo{of}\wen{with}\dlo{ the} two other rank-reduction methods. Since the FK method is one of most commonly used \dlo{methods}\wen{approaches} to attenuate high-frequency high-wavenumber random noise, we also treat it as a competing method for \dlo{the}\wen{this} comparison. Figure \ref{fig:syn3d-comp} shows denoised data using \wen{different methods.} The top row of Figure \ref{fig:syn3d-comp} shows the \dlo{four denoised data using four methods}\wen{the dataset denoised by the four methods}\dlo{ and}\wen{, while} the \dlo{bottom}\wen{middle} row of Figure \ref{fig:syn3d-comp} \dlo{shows}\wen{presents} the noise \dlo{reduced}\wen{extracted} by the four methods. In this test, we preserve the 10\% largest coefficients for the FK method to obtain Figure \ref{fig:syn3d-fk}. We use \wen{a rank of} $N=3$ for all three rank-reduction based methods. By observing Figure \ref{fig:syn3d-fk}, it is clear that the FK thresholding causes strong artifacts around the edges. Both FK thresholding\dlo{ method} and the \dlo{traditional }rank-reduction \dlo{method}\wen{methods} \dlo{cause}\wen{leaves} a large amount of residual noise in the denoised results. \dlo{The damped rank-reduction method and the proposed method both obtain pleasant results but the proposed method is a little better because it removes slightly more noise.} \wen{The calculated SNRs of the four methods are 6.03 dB for the FK thresholding method, 6.57 dB for the rank-reduction method, 10.29 dB for the damped rank-reduction method, and 11.27 dB for the proposed method.} It is clear that the SNR comparison quantitatively \dlo{confirm}\wen{confirms} our initial observation that the proposed method obtains the best result among the four methods. \dlo{It is wroth mentioning that in}\wen{In} this test we use a very simple synthetic example that contains three planar components. In the rank-reduction method, it can be proved that the number of the planar/linear events is equal to the \dlo{appealing rank}\wen{input rank parameter}, i.e., $N=3$ in this test \cite[]{Trickett2009,mssa}. Because we know the ground truth in this test, we \dlo{choose $N=3$}\wen{the same rank} for all methods, and the proposed method obtains the best performance but is slightly better than the damped method. However, in the case of the more \dlo{complicated}\wen{complex} data, where the exact number of events \wen{with distinct dips} is unknown, we prefer to choose a more conservative rank \dlo{for fear of losing}\wen{to avoid losing} too many useful details. \dlo{In a more realistic case, it is interesting to know how the proposed method behaves compared with the competing methods.}\wen{The bottom row of Figure \ref{fig:syn3d-comp} shows the comparison of local similarity, where we can find that the local similarity of the ODRR method is much smaller.} \wen{The spectrum comparison when $N=3$ is plotted in Figure \ref{fig:syn3d-comp-fk}, which further verify the best performance of the proposed method. }

Next, based on the same example, we use a larger rank $N=6$. We also use a more conservative threshold value for the FK thresholding method, e.g., we preserve the 20\% largest coefficients in the transformed domain. The results of the four methods are shown in the top row of Figure \ref{fig:syn3d-6-comp}. The \dlo{bottom}\wen{middle} row of Figure \ref{fig:syn3d-6-comp} shows the corresponding noise cubes. It is clear that the denoised results of FK thresholding method, rank-reduction method, damped rank-reduction method are all noisier than \dlo{those}\wen{the corresponding results presented} in Figure \ref{fig:syn3d-comp}. However, the result from the proposed method, as shown in Figure \ref{fig:syn3d-6-olr}, is less affected\dlo{ and is even untouched}. \wen{The calculated SNRs in this case are 4.31 dB for the FK method, 3.45 dB for the RR method, 8.35 dB for the DRR method, and 10.86 dB for the proposed method. The differences of SNR with respect to the previous example for the three methods are 1.72 dB for the FK thresholding method, 3.12 dB for the rank-reduction method, 1.94 dB for the damped rank-reduction method, and 0.41 dB for the proposed method.} Comparison \dlo{in SNR}\wen{of SNRs} demonstrates that while the other three methods are sensitive to the input parameter, the proposed method is much less sensitive\wen{, because it can still find the appropriate rank by using weights}. The bottom row of Figure \ref{fig:syn3d-6-comp} shows the comparison of local similarity, where we \dlo{can }find that the local similarity of the presented method is distinctly smaller. \wen{The spectrum comparison when $N=6$ is plotted in Figure \ref{fig:syn3d-6-comp-fk}, which further verify the best performance of the proposed method.}

For a better comparison, we extract the 5th Xline slice from Figures \ref{fig:syn3d-cn} and \ref{fig:syn3d-6-comp} and show the slices in Figure \ref{fig:syn3d-6-comp-s}. \dlo{It is more obvious  to show that the proposed method \dlo{gets}\wen{produces} the cleanest result while not causing any signal damage.}\wen{In this display, it is even more evident that the proposed method produces the cleanest result while minimizing \dlo{any }signal damage.} Figure \ref{fig:snrs} plots the SNR diagrams of \wen{the} different \dlo{approaches}\wen{methods} with respect to the input parameters. \dlo{The input parameter for the rank-reduction based methods is the selected rank, and the input parameter for the transform based methods is the percentage of sparse coefficients.}\wen{The input parameters for the rank-reduction based methods and transform based methods are the selected rank and the percentage of sparse coefficients, respectively. } \wen{When the rank is chosen large enough, e.g., larger than 8, the} proposed method is less sensitive in all methods. The two transform based methods are also sensitive to the percentage of \wen{selected} coefficients.

\wen{To test the performance of the proposed method in denoising high-frequency band. We create a slightly different example shown in Figure \ref{fig:syn3dhf-cn}. We increase the dominant frequency of the Ricker wavelet to 60 Hz and then extract the frequency band of 60-100 Hz. We also extract the same frequency band of the Gaussian white noise, and add the high-frequency noise to the clean data to generate the noisy data. The denoising comparison of different methods for the high-frequency band is shown in Figure \ref{fig:syn3dhf-comp}. The spectrum comparison is shown in Figure \ref{fig:syn3dhf-comp-fk}. This test demonstrates the lowrank methods also work well in high-frequency band. }

The next example is a synthetic dataset with hyperbolic events. \wen{In this example, we use the Ricker wavelet with a dominant frequency of 10 Hz to generate the clean data. We add Gaussian white noise with variance of 0.2 (as compared with the normalized clean data).} The clean and noisy data are shown in Figures \ref{fig:hyp3d-c} and \ref{fig:hyp3d-n}, respectively. The SNR of the noisy data is \dlo{4.29}\wen{-2.17} dB. We apply FK thresholding method and the three rank-reduction based methods to this example and show the results in Figure \ref{fig:hyp3d-comp}. For the FK thresholding method, we preserve 20\% largest coefficients in the transformed domain. For all the rank-reduction based methods, we use \dlo{$N=3$}\wen{$N=10$}. Since the hyperbolic events no longer \dlo{meet}\wen{satisfy} the assumption, i.e., \dlo{bing}\wen{being} lowrank, the hyperbolic events in this example are \dlo{obviously }over-smoothed when \dlo{$N=3$}\wen{$N=10$}. It is also clear that both FK thresholding and the rank-reduction \dlo{method}\wen{methods} have significant residual noise. The damped rank-reduction method and the proposed method are both very clean, but the proposed method is slightly smoother. In this example, because of the hyperbolic events and \dlo{the}\wen{their} small rank, the removed noise cubes as shown in the bottom row of Figure \ref{fig:hyp3d-comp} contain \dlo{small}\wen{a small amount of} spatially coherent energy, which indicates \dlo{the }signal leakage \cite[]{yangkang2015ortho}.  The calculated SNRs in this example are \dlo{10.86}\wen{7.05} dB for the FK thresholding method, \dlo{11.05}\wen{8.27} dB for the \dlo{traditional }rank-reduction method, \dlo{11.08}\wen{9.58} dB for the damped rank-reduction method, and \dlo{11.64}\wen{9.65} dB for the \dlo{new method}\wen{proposed method}. \wen{In this example, we do not use local windows to locally pretend that hyperbolic events act as linear events. When applying local windows, \dlo{more}\wen{additional} parameters (e.g., the window size) need to be compared and considered. To avoid the this step, we can use a relatively large rank to avoid the signal damage.} From the comparison of local similarity, significant \dlo{damages are}\wen{damage is} highlighted as \dlo{the }high similarity anomalies. \dlo{Then we}\wen{We} increase the rank from \dlo{$N=3$}\wen{$N=10$} to \dlo{$N=9$}\wen{$N=20$} and show the results in Figure \ref{fig:hyp3d-20-comp}. For the FK thresholding method, we increase the threshold percentage from 20\% to 40\%. We find that in this test, both FK thresholding method and the \dlo{traditional }rank-reduction method \dlo{cause}\wen{leave} more residual noise while the results from the damped rank-reduction method and the proposed method are still very smooth.  However, when \dlo{$N=9$}\wen{$N=20$}, \dlo{none of the rank-reduction methods cause damages to useful signals}\wen{the rank-reduction methods do not produce significant damage to useful signals} \wen{but they also do not attenuate the noise very well}. In addition, when \dlo{$N=9$}\wen{$N=20$}, the proposed method becomes obviously smoother than the damped rank-reduction method. The comparison \dlo{if}\wen{is} more noticeable when observing the local similarity maps. The calculated SNRs in this example are \dlo{13.43}\wen{5.85} dB for the FK thresholding method, \dlo{15.36}\wen{7.04} dB for the \dlo{traditional }rank-reduction method, \dlo{20.06}\wen{10.08} dB for the damped rank-reduction method, and \dlo{21.25}\wen{11.00} dB for the proposed method.  \wen{Figure \ref{fig:hyp3d-20-comp-s} shows a} single slice comparison of this example (5th Xline slice) when \dlo{$N=9$}\wen{$N=20$}, where it is more \dlo{salient}\wen{noticeable} that the proposed method obtains the best result.  \dlo{Besides, the}\wen{The} SNRs for all the aforementioned tests are \wen{given} in Table \ref{tbl:snrs} for a detailed comparison. %\wen{Based on this example, we test the performance of different methods in the presence of band-limited noise. The added noise has been bandpass filtered within the frequency range of 0-40 Hz. The calculated SNRs of the noisy data, FK method, RR method, DRR method, and the proposed method are 9.15 dB, 19.97 dB, 21.21 dB, and 21.91 dB, respectively. Though the proposed method is derived based on the assumption of white noise, it can also adapt to band-limited noise.}
Figure \ref{fig:snrs_hyp} plots the SNR diagrams of \wen{the} different \dlo{approaches}\wen{methods} with respect to the input parameters for the hyperbolic example. When the rank is sufficiently large, e.g., larger than 18, the proposed approach is clearly more insensitive to the rank when compared to the other rank-reduction based methods \wen{due to the calculation of adaptive weights for the singular-values}. \dlo{We}\wen{Table \ref{tbl:times}} compares the computational costs for all these tests. \dlo{ The three rank-reduction methods have similar computational costs, while the proposed method is slightly more expensive.}\wen{All three methods are comprable but the proposed method is slightly more expensive.}

\wen{\subsection{Field data example}}
\wen{Next we apply the proposed method to the real migrated 3D land seismic dataset shown in Figure \ref{fig:r3d}. }\dlo{Next, we apply the proposed method to real 3D seismic data. }\dlo{The real seismic dataset is shown in Figure \ref{fig:r3d}} The 3D seismic image \dlo{is from a land data after}\wen{corresponds to a land dataset after} time migration. \wen{The field dataset goes through a normal seismic processing workflow, e.g., muting the dead traces, ground roll removal, surface-consistent deconvolution, pre-stack noise attenuation by the FX method, NMO-based velocity analysis, and kirchhoff time migration.} \dlo{The shallow structures are simple plane layers (above 1 s) and the deep structures are complex curved layers (below 1 s). }The temporal sampling \dlo{rate}\wen{interval} is 4 ms. \dlo{There are 200 Inline traces and 50 Xline traces. The Inline \dlo{sampling rate}\wen{trace spacing} is 5m and the Xline \dlo{sampling rate}\wen{trace spacing} is 10m. } There are 200 inlines and 50 crosslines\dlo{ traces}, with trace spacings of 5 m and 10 m, respectively. Figure \ref{fig:r3d-comp} shows the denoising comparison \wen{using different methods}. From the previous synthetic examples, we \dlo{have known}\wen{understand} the differences for different rank-reduction related methods\dlo{, so in this example, we examine the denoising}\wen{. Therefore, in this example we examine the denoising} performance using the seislet transform \cite[]{fomel2010seislet}. The seislet transform is deemed to be the sparsest transform for seismic data. The denoised data using the seislet thresholding method, the \dlo{traditional }rank-reduction method, and the proposed method are shown in the left column of Figure \ref{fig:r3d-comp}\wen{, respectively}. The middle column of Figure \ref{fig:r3d-comp} shows the corresponding noise cubes of the three methods. Since for the \dlo{real}\wen{field} data example\dlo{,} \dlo{we do not have ground-truth solution (clean data)}\wen{we do not have the pure signal} for calculating the SNR, we \wen{can only} \dlo{utilize}\wen{use} the local similarity metric to evaluate the denoising performance. The general criterion is that the local similarity between the denoised data and removed noise should be negligible \dlo{provided that the removed noise \wen{does not include part of the signal}}\wen{provided that there is no signal leakage in the removed noise}. The local similarity cubes corresponding to the three methods are shown in the right column of Figure \ref{fig:r3d-comp}. To make the removed noise comparably strong, we preserve 8\% largest coefficients in the seislet domain. We use rank $N=21$ for the \dlo{traditional }rank-reduction method and use rank $N=30$ for the proposed method. Comparison of the local similarity shows that the \dlo{thresholding}\wen{seislet transform} and the rank-reduction methods both cause significant signal leakage, while the proposed method is almost damage-free for the useful signals. It is clear that \wen{ when removing the same amount of random noise}, it is able to preserve the most \dlo{useful}\wen{signal} energy for the proposed method. \dlo{In}\wen{At} the same time, the \dlo{proposed}\wen{new} method can get a \dlo{much }smoother result than the rank-reduction method, and same smoothness level compared with the seislet thresholding method. \wen{The spectrum comparison for the field data example is plotted in Figure \ref{fig:real-fks}, where the proposed method preserves more signal spectra than the seislet method, but removes more noise spectra than the rank-reduction method.} \wen{The zoomed comparison in Figure \ref{fig:real-z} makes this even more obvious.}

%\section{Discussions}

\section{Conclusions}
The rank-reduction method for seismic noise suppression based on the nuclear norm minimization requires a carefully selected threshold value. We have developed an optimal weighting strategy to obtain better shrinkage of the singular-values, bypassing the need for manual selection of the rank \dlo{a}\wen{as a} priori \wen{information}. Considering the issue of residual noise after the optimal rank-reduction method, we further \dlo{derive a theoretically}\wen{introduce an} optimal way to damp the remaining noise. The proposed method can separate \wen{the} noise subspace and the signal subspace in an optimal way. Detailed \dlo{analysis}\wen{analyses} on the proposed algorithm via two synthetic datasets and one \dlo{real}\wen{field} example demonstrate that the proposed method can obtain better denoising performance regarding the noise removal and signal preservation \wen{than the widely used methods in terms of SNR and local similarity measurements}. More importantly, because of the optimally damped singular-values, the proposed method is an adaptive method, i.e., the performance is not sensitive to the predefined rank parameter.

\section{DATA AVAILABILITY STATEMENT}
Datasets and source codes associated with this research will be made available online (www.ahay.org) in the format of reproducible research.

%\section{Acknowledgements}
%We  thank Dong Zhang, Weilin Huang, and Wei Chen for constructive comments.  The research is supported by the starting fund from Zhejiang University and ``Thousand Youth Talents Plan of China''.

\bibliographystyle{seg}
\bibliography{odrr}

\newpage
\listoffigures
\newpage

\newpage
\listoftables
\newpage

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.4\textwidth]{syn3d/Fig/syn3d-c}  \label{fig:syn3d-c}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{syn3d/Fig/syn3d-n}	\label{fig:syn3d-n}}\\
	\caption{Synthetic \wen{data} examples with linear/\dlo{planer}\wen{planar} events. (a) Clean \dlo{synthetic }data. (b) Noisy\dlo{ synthetic} data. \wen{The events shown on the outside of the cube are situated at the blue lines within the cube.}}
	\label{fig:syn3d-cn}
\end{figure}

\begin{figure*}[ht!]
	\centering
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d/Fig/syn3d-fk}   \label{fig:syn3d-fk}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d/Fig/syn3d-lr}	  \label{fig:syn3d-lr}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d/Fig/syn3d-dlr}  \label{fig:syn3d-dlr}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d/Fig/syn3d-olr}  \label{fig:syn3d-olr}}\\
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d/Fig/syn3d-n-fk}   \label{fig:syn3d-n-fk}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d/Fig/syn3d-n-lr}	  \label{fig:syn3d-n-lr}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d/Fig/syn3d-n-dlr}  \label{fig:syn3d-n-dlr}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d/Fig/syn3d-n-olr}  \label{fig:syn3d-n-olr}}\\
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d/Fig/syn3d-simi1}   \label{fig:syn3d-simi1}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d/Fig/syn3d-simi2}	  \label{fig:syn3d-simi2}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d/Fig/syn3d-simi3}  \label{fig:syn3d-simi3}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d/Fig/syn3d-simi4}  \label{fig:syn3d-simi4}}\\
	\caption{Denoising comparison ($N=3$). \dlo{(a) Result using the FK thresholding method. (b) Result using the rank-reduction method. (c) Result using the damped rank-reduction method. (d) Result using the proposed method. (e) Removed noise using the FK thresholding method. (f) Removed noise using the rank-reduction method. (g) Removed noise using the damped rank-reduction method. (h) Removed noise using the proposed method.}\wen{Top row: denoised results using (a) FK method with 10\% largest coefficients, (b) rank-reduction method, (c) damped rank-reduction method, and (d) the proposed method. Middle row: separated noise corresponding to the top row. Bottom row: local similarity corresponding to the top row. }}
	\label{fig:syn3d-comp}
\end{figure*}

\begin{figure*}[ht!]
	\centering
	\subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d/Fig/syn3d-c-fkk}   \label{fig:syn3d-c-fkk}}
	\subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d/Fig/syn3d-n-fkk}   \label{fig:syn3d-n-fkk}}
    \subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d/Fig/syn3d-fk-fkk}	  \label{fig:syn3d-fk-fkk}}\\
    \subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d/Fig/syn3d-lr-fkk}	  \label{fig:syn3d-lr-fkk}}
	\subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d/Fig/syn3d-dlr-fkk}  \label{fig:syn3d-dlr-fkk}}
    \subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d/Fig/syn3d-olr-fkk}  \label{fig:syn3d-olr-fkk}}
	\caption{\wen{Spectrum comparison ($N=3$). FK spectrum of (a) clean data, (b) noisy data, (c) FK method, (d) rank-reduction method, (e) damped rank-reduction method, and (f) the proposed method.}}
	\label{fig:syn3d-comp-fk}
\end{figure*}

\begin{figure*}[ht!]
	\centering
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-fk}   \label{fig:syn3d-6-fk}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-lr}	  \label{fig:syn3d-6-lr}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-dlr}  \label{fig:syn3d-6-dlr}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-olr}  \label{fig:syn3d-6-olr}}\\
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-n-fk}   \label{fig:syn3d-6-n-fk}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-n-lr}	  \label{fig:syn3d-6-n-lr}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-n-dlr}  \label{fig:syn3d-6-n-dlr}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-n-olr}  \label{fig:syn3d-6-n-olr}}\\
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-simi1}   \label{fig:syn3d-6-simi1}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-simi2}	  \label{fig:syn3d-6-simi2}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-simi3}  \label{fig:syn3d-6-simi3}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-simi4}  \label{fig:syn3d-6-simi4}}\\
	\caption{Denoising comparison ($N=6$). \dlo{(a) Result using the FK thresholding method. (b) Result using the rank-reduction method. (c) Result using the damped rank-reduction method. (d) Result using the proposed method. (e) Removed noise using the FK thresholding method. (f) Removed noise using the rank-reduction method. (g) Removed noise using the damped rank-reduction method. (h) Removed noise using the proposed method.}\wen{Top row: denoised results using (a) FK method with 20\% largest coefficients, (b) rank-reduction method, (c) damped rank-reduction method, and (d) the proposed method. Middle row: separated noise corresponding to the top row. Bottom row: local similarity corresponding to the top row. }}
	\label{fig:syn3d-6-comp}
\end{figure*}

\begin{figure*}[ht!]
	\centering
	\subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d_N6/Fig/syn3d-6-c-fkk}   \label{fig:syn3d-6-c-fkk}}
	\subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d_N6/Fig/syn3d-6-n-fkk}   \label{fig:syn3d-6-n-fkk}}
    \subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d_N6/Fig/syn3d-6-fk-fkk}	  \label{fig:syn3d-6-fk-fkk}}\\
    \subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d_N6/Fig/syn3d-6-lr-fkk}	  \label{fig:syn3d-6-lr-fkk}}
	\subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d_N6/Fig/syn3d-6-dlr-fkk}  \label{fig:syn3d-6-dlr-fkk}}
    \subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d_N6/Fig/syn3d-6-olr-fkk}  \label{fig:syn3d-6-olr-fkk}}
	\caption{\wen{Spectrum comparison ($N=6$). FK spectrum of (a) clean data, (b) noisy data, (c) FK method, (d) rank-reduction method, (e) damped rank-reduction method, and (f) the proposed method.}}
	\label{fig:syn3d-6-comp-fk}
\end{figure*}

\begin{figure*}[ht!]
	\centering
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-c-s}   \label{fig:syn3d-6-c-s}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-fk-s}   \label{fig:syn3d-6-fk-s}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-lr-s}	  \label{fig:syn3d-6-lr-s}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-dlr-s}  \label{fig:syn3d-6-dlr-s}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-olr-s}  \label{fig:syn3d-6-olr-s}}\\
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-n-s}   \label{fig:syn3d-6-n-s}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-n-fk-s}   \label{fig:syn3d-6-fk-s}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-n-lr-s}	  \label{fig:syn3d-6-lr-s}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-n-dlr-s}  \label{fig:syn3d-6-dlr-s}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-n-olr-s}  \label{fig:syn3d-6-olr-s}}\\
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-simi1-s}   \label{fig:syn3d-6-simi1-s}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-simi2-s}	  \label{fig:syn3d-6-simi2-s}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-simi3-s}  \label{fig:syn3d-6-simi3-s}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_N6/Fig/syn3d-6-simi4-s}  \label{fig:syn3d-6-simi4-s}}\\
	\caption{\wen{2D slice view of denoising}\dlo{Denoising} comparison ($N=6$). (a) Clean data. \dlo{(b) Result using the FK thresholding method. (c) Result using the rank-reduction method. (d) Result using the damped rank-reduction method. (e) Result using the proposed method. (f) Noisy data. (g) Removed noise using the FK thresholding method. (h) Removed noise using the rank-reduction method. (i) Removed noise using the damped rank-reduction method. (j) Removed noise using the proposed method.}\wen{(b)-(e): denoised results using FK method, (b) rank-reduction method, (c) damped rank-reduction method, and the proposed method, respectively. (f) Noisy data. (g)-(j) Separated noise corresponding to (b)-(e), respectively. (k)-(n) Local similarity corresponding to (b)-(e), respectively. }}
	\label{fig:syn3d-6-comp-s}
\end{figure*}

\begin{figure}[htb!]
	\centering
\includegraphics[width=0.8\textwidth]{Fig/snrs}	
	\caption{\dlo{SNR diagrams of different approaches with respect to the input parameters the linear synthetic example, i.e., selected rank for the rank-reduction based methods and percentage of sparse coefficients for the transform based methods.}\wen{SNR diagrams of different lowrank approaches with respect to the selected rank parameters for the linear synthetic example.} }
	\label{fig:snrs}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.4\textwidth]{syn3d_hf/Fig/syn3dhf-c}  \label{fig:syn3dhf-c}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{syn3d_hf/Fig/syn3dhf-n}	\label{fig:syn3dhf-n}}\\
	\caption{\wen{Synthetic \wen{data} examples with linear/\dlo{planer}\wen{planar} events  for the high-frequency denoising test (60-100 Hz). (a) Clean \dlo{synthetic }data. (b) Noisy\dlo{ synthetic} data. \wen{The events shown on the outside of the cube are situated at the blue lines within the cube.}}}
	\label{fig:syn3dhf-cn}
\end{figure}

\begin{figure*}[ht!]
	\centering
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_hf/Fig/syn3dhf-fk}   \label{fig:syn3dhf-fk}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_hf/Fig/syn3dhf-lr}	  \label{fig:syn3dhf-lr}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_hf/Fig/syn3dhf-dlr}  \label{fig:syn3dhf-dlr}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_hf/Fig/syn3dhf-olr}  \label{fig:syn3dhf-olr}}\\
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_hf/Fig/syn3dhf-n-fk}   \label{fig:syn3dhf-n-fk}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_hf/Fig/syn3dhf-n-lr}	  \label{fig:syn3dhf-n-lr}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_hf/Fig/syn3dhf-n-dlr}  \label{fig:syn3dhf-n-dlr}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_hf/Fig/syn3dhf-n-olr}  \label{fig:syn3dhf-n-olr}}\\
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_hf/Fig/syn3dhf-simi1}   \label{fig:syn3dhf-simi1}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_hf/Fig/syn3dhf-simi2}	  \label{fig:syn3dhf-simi2}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_hf/Fig/syn3dhf-simi3}  \label{fig:syn3dhf-simi3}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{syn3d_hf/Fig/syn3dhf-simi4}  \label{fig:syn3dhf-simi4}}\\
	\caption{\wen{Denoising comparison ($N=6$)  for the high-frequency denoising test (60-100 Hz). \dlo{(a) Result using the FK thresholding method. (b) Result using the rank-reduction method. (c) Result using the damped rank-reduction method. (d) Result using the proposed method. (e) Removed noise using the FK thresholding method. (f) Removed noise using the rank-reduction method. (g) Removed noise using the damped rank-reduction method. (h) Removed noise using the proposed method.}\wen{Top row: denoised results using (a) FK method with 10\% largest coefficients, (b) rank-reduction method, (c) damped rank-reduction method, and (d) the proposed method. Middle row: separated noise corresponding to the top row. Bottom row: local similarity corresponding to the top row. }}}
	\label{fig:syn3dhf-comp}
\end{figure*}

\begin{figure*}[ht!]
	\centering
	\subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d_hf/Fig/syn3dhf-c-fkk}   \label{fig:syn3dhf-c-fkk}}
	\subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d_hf/Fig/syn3dhf-n-fkk}   \label{fig:syn3dhf-n-fkk}}
    \subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d_hf/Fig/syn3dhf-fk-fkk}	  \label{fig:syn3dhf-fk-fkk}}\\
    \subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d_hf/Fig/syn3dhf-lr-fkk}	  \label{fig:syn3dhf-lr-fkk}}
	\subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d_hf/Fig/syn3dhf-dlr-fkk}  \label{fig:syn3dhf-dlr-fkk}}
    \subfloat[]{\includegraphics[width=0.3\textwidth]{syn3d_hf/Fig/syn3dhf-olr-fkk}  \label{fig:syn3dhf-olr-fkk}}
	\caption{\wen{Spectrum comparison ($N=6$) for the high-frequency denoising test (60-100 Hz). FK spectrum of (a) clean data, (b) noisy data, (c) FK method, (d) rank-reduction method, (e) damped rank-reduction method, and (f) the proposed method.}}
	\label{fig:syn3dhf-comp-fk}
\end{figure*}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.4\textwidth]{hyp3d/Fig/hyp3d-c}  \label{fig:hyp3d-c}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{hyp3d/Fig/hyp3d-n}	\label{fig:hyp3d-n}}\\
	\caption{Synthetic \wen{data} examples with hyperbolic events. (a) Clean \dlo{synthetic }data. (b) Noisy\dlo{ synthetic} data. \wen{The gray scales for all of the images shown in Figures \ref{fig:hyp3d-cn}-\ref{fig:hyp3d-20-comp-s} are the same.}}
	\label{fig:hyp3d-cn}
\end{figure}

\begin{figure*}[ht!]
	\centering
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d/Fig/hyp3d-fk}   \label{fig:hyp3d-fk}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d/Fig/hyp3d-lr}	  \label{fig:hyp3d-lr}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d/Fig/hyp3d-dlr}  \label{fig:hyp3d-dlr}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d/Fig/hyp3d-olr}  \label{fig:hyp3d-olr}}\\
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d/Fig/hyp3d-n-fk}   \label{fig:hyp3d-fk}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d/Fig/hyp3d-n-lr}	  \label{fig:hyp3d-lr}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d/Fig/hyp3d-n-dlr}  \label{fig:hyp3d-dlr}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d/Fig/hyp3d-n-olr}  \label{fig:hyp3d-olr}}\\
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d/Fig/hyp3d-simi1}   \label{fig:hyp3d-simi1}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d/Fig/hyp3d-simi2}	  \label{fig:hyp3d-simi2}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d/Fig/hyp3d-simi3}  \label{fig:hyp3d-simi3}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d/Fig/hyp3d-simi4}  \label{fig:hyp3d-simi4}}\\
	\caption{Denoising comparison (\dlo{$N=3$}\wen{$N=10$}). \dlo{(a) Result  using the FK thresholding method. (b) Result using the rank-reduction method. (c) Result using the damped rank-reduction method. (d) Result using the proposed method. (d) Removed noise using the FK thresholding method. (e) Removed noise using the rank-reduction method. (f) Removed noise using the damped rank-reduction method. (g) Removed noise using the proposed method.}\wen{The top row: denoised results using (a) FK method, (b) rank-reduction method, (c) damped rank-reduction method, and (d) the proposed method. The middle row: separated noise corresponding to the top row. The bottom row: local similarity corresponding to the top row.}}
	\label{fig:hyp3d-comp}
\end{figure*}

\begin{figure*}[ht!]
	\centering
	\subfloat[]{\includegraphics[width=0.3\textwidth]{hyp3d/Fig/hyp3d-c-fkk}   \label{fig:hyp3d-c-fkk}}
	\subfloat[]{\includegraphics[width=0.3\textwidth]{hyp3d/Fig/hyp3d-n-fkk}   \label{fig:hyp3d-n-fkk}}
    \subfloat[]{\includegraphics[width=0.3\textwidth]{hyp3d/Fig/hyp3d-fk-fkk}	  \label{fig:hyp3d-fk-fkk}}\\
    \subfloat[]{\includegraphics[width=0.3\textwidth]{hyp3d/Fig/hyp3d-lr-fkk}	  \label{fig:hyp3d-lr-fkk}}
	\subfloat[]{\includegraphics[width=0.3\textwidth]{hyp3d/Fig/hyp3d-dlr-fkk}  \label{fig:hyp3d-dlr-fkk}}
    \subfloat[]{\includegraphics[width=0.3\textwidth]{hyp3d/Fig/hyp3d-olr-fkk}  \label{fig:hyp3d-olr-fkk}}
	\caption{\wen{Spectrum comparison ($N=10$). FK spectrum of (a) clean data, (b) noisy data, (c) FK method, (d) rank-reduction method, (e) damped rank-reduction method, and (f) the proposed method.}}
	\label{fig:hyp3d-comp-fk}
\end{figure*}

\begin{figure*}[ht!]
	\centering
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-fk}   \label{fig:hyp3d-20-fk}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-lr}	  \label{fig:hyp3d-20-lr}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-dlr}  \label{fig:hyp3d-20-dlr}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-olr}  \label{fig:hyp3d-20-olr}}\\
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-n-fk}   \label{fig:hyp3d-20-fk}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-n-lr}	  \label{fig:hyp3d-20-lr}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-n-dlr}  \label{fig:hyp3d-20-dlr}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-n-olr}  \label{fig:hyp3d-20-olr}}\\
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-simi1}   \label{fig:hyp3d-20-simi1}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-simi2}	  \label{fig:hyp3d-20-simi2}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-simi3}  \label{fig:hyp3d-20-simi3}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-simi4}  \label{fig:hyp3d-20-simi4}}\\
	\caption{Denoising comparison (\dlo{$N=10$}\wen{$N=20$}). \dlo{(a) Result using the FK thresholding method. (b) Result using the rank-reduction method. (c) Result using the damped rank-reduction method. (d) Result using the proposed method. (d) Removed noise using the FK thresholding method. (e) Removed noise using the rank-reduction method. (f) Removed noise using the damped rank-reduction method. (g) Removed noise using the proposed method.}\wen{The top row: denoised results using (a) FK method, (b) rank-reduction method, (c) damped rank-reduction method, and (d) the proposed method. The middle row: separated noise corresponding to the top row. The bottom row: local similarity corresponding to the top row.}}
	\label{fig:hyp3d-20-comp}
\end{figure*}

\begin{figure*}[ht!]
	\centering
	\subfloat[]{\includegraphics[width=0.3\textwidth]{hyp3d_N20/Fig/hyp3d-20-c-fkk}   \label{fig:hyp3d-20-c-fkk}}
	\subfloat[]{\includegraphics[width=0.3\textwidth]{hyp3d_N20/Fig/hyp3d-20-n-fkk}   \label{fig:hyp3d-20-n-fkk}}
    \subfloat[]{\includegraphics[width=0.3\textwidth]{hyp3d_N20/Fig/hyp3d-20-fk-fkk}	  \label{fig:hyp3d-20-fk-fkk}}\\
    \subfloat[]{\includegraphics[width=0.3\textwidth]{hyp3d_N20/Fig/hyp3d-20-lr-fkk}	  \label{fig:hyp3d-20-lr-fkk}}
	\subfloat[]{\includegraphics[width=0.3\textwidth]{hyp3d_N20/Fig/hyp3d-20-dlr-fkk}  \label{fig:hyp3d-20-dlr-fkk}}
    \subfloat[]{\includegraphics[width=0.3\textwidth]{hyp3d_N20/Fig/hyp3d-20-olr-fkk}  \label{fig:hyp3d-20-olr-fkk}}
	\caption{\wen{Spectrum comparison ($N=20$). FK spectrum of (a) clean data, (b) noisy data, (c) FK method, (d) rank-reduction method, (e) damped rank-reduction method, and (f) the proposed method.}}
	\label{fig:hyp3d-20-comp-fk}
\end{figure*}

\begin{figure*}[ht!]
	\centering
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-c-s}   \label{fig:hyp3d-20-c-s}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-fk-s}   \label{fig:hyp3d-20-fk-s}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-lr-s}	  \label{fig:hyp3d-20-lr-s}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-dlr-s}  \label{fig:hyp3d-20-dlr-s}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-olr-s}  \label{fig:hyp3d-20-olr-s}}\\
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-n-s}   \label{fig:hyp3d-20-n-s}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-n-fk-s}   \label{fig:hyp3d-20-fk-s}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-n-lr-s}	  \label{fig:hyp3d-20-lr-s}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-n-dlr-s}  \label{fig:hyp3d-20-dlr}-s}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-n-olr-s}  \label{fig:hyp3d-20-olr-s}}\\
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-simi1-s}   \label{fig:hyp3d-20-simi1-s}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-simi2-s}	  \label{fig:hyp3d-20-simi2-s}}
	\subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-simi3-s}  \label{fig:hyp3d-20-simi3-s}}
    \subfloat[]{\includegraphics[width=0.18\textwidth]{hyp3d_N20/Fig/hyp3d-20-simi4-s}  \label{fig:hyp3d-20-simi4-s}}\\
	\caption{Denoising comparison (\dlo{$N=10$}\wen{$N=20$}). (a) Clean data. \wen{(b)-(e): denoised results using FK method, (b) rank-reduction method, (c) damped rank-reduction method, and the proposed method, respectively. (f) Noisy data. (g)-(j) Separated noise corresponding to (b)-(e), respectively. (k)-(n) Local similarity corresponding to (b)-(e), respectively. }}
	\label{fig:hyp3d-20-comp-s}
\end{figure*}

\begin{figure}[htb!]
	\centering
\includegraphics[width=0.8\textwidth]{Fig/snrs_hyp2}	
	\caption{\dlo{SNR diagrams of different approaches with respect to the input parameters for the hyperbolic synthetic example, i.e., selected rank for the rank-reduction based methods \wen{(solid lines)} and percentage of sparse coefficients for the transform based methods \wen{(dashed lines)}.}\wen{SNR diagrams of different lowrank approaches with respect to the selected rank parameters for the hyperbolic synthetic example.} }
	\label{fig:snrs_hyp}
\end{figure}

\begin{figure}[htb!]
	\centering
%	\subfloat[]{\includegraphics[width=0.6\textwidth]{real3d/Fig/real}
	\subfloat[]{\includegraphics[width=0.5\textwidth]{Fig/r3d}
	\label{fig:r3d}}
	\caption{Real 3D seismic data. \wen{The green box highlights the zooming area for detailed comparison.}}
	\label{fig:r3d}
\end{figure}

\begin{figure*}[ht!]
	\centering
%	\subfloat[]{\includegraphics[width=0.22\textwidth]{real3d/Fig/r3d-seis}
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/r3d-seis}
	\label{fig:r3d-seis}}
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/r3d-seis-n}
	\label{fig:r3d-seis-n}}	
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/r3d-simi3}
	\label{fig:r3d-simi3}}	\\

%    \subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/r3d-lr}
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/r3d-lr}	
    \label{fig:r3d-lr}}
    \subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/r3d-lr-n}	\label{fig:r3d-lr-n}}    
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/r3d-simi1}
	\label{fig:r3d-simi1}}\\

%    \subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/r3d-olr}
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/r3d-olr}
    	\label{fig:r3d-olr}}
    \subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/r3d-olr-n}	\label{fig:r3d-olr-n}}
    \subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/r3d-simi2}	\label{fig:r3d-simi2}}\\
	\caption{Denoising comparison. (a) Result using the seislet thresholding method.  (b) Removed noise corresponding to (a). (c) Local similarity between (a) and (b). (d) Removed noise using the rank-reduction method. (e) Removed noise corresponding to (d). (f) Local similarity between (d) and (e).  (g) Result using the proposed method.  (h) Removed noise using the proposed method. (i) Local similarity between (g) and (h). }
	\label{fig:r3d-comp}
\end{figure*}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.40\textwidth]{Fig/r3d-fk}  \label{fig:r3d-fk}}
    \subfloat[]{\includegraphics[width=0.40\textwidth]{Fig/r3d-seis-fk}	\label{fig:r3d-seis-fk}}\\
	\subfloat[]{\includegraphics[width=0.40\textwidth]{Fig/r3d-lr-fk}  \label{fig:r3d-lr-fk}}
    \subfloat[]{\includegraphics[width=0.40\textwidth]{Fig/r3d-olr-fk}	\label{fig:r3d-olr-fk}}\\
	\caption{Spectrum comparison for the field data example. Spectrum of (a) real seismic data, (b) result using the seislet thresholding method, (c) result using the rank-reduction method, and (d) result using the proposed method. }
	\label{fig:real-fks}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.40\textwidth]{Fig/r3d-z}  \label{fig:r3d-z}}
    \subfloat[]{\includegraphics[width=0.40\textwidth]{Fig/r3d-seis-z0}	\label{fig:r3d-seis-z}}\\
	\subfloat[]{\includegraphics[width=0.40\textwidth]{Fig/r3d-lr-z}  \label{fig:r3d-lr-z}}
    \subfloat[]{\includegraphics[width=0.40\textwidth]{Fig/r3d-olr-z0}	\label{fig:r3d-olr-z}}\\
	\caption{Zoomed denoising comparison for the \dlo{real}\wen{field} data example. (a) Real seismic data. (b) Result using the seislet thresholding method. (c) Result using the rank-reduction method. (d) Result using the proposed method. \wen{The arrows highlight the difference between (b) and (d).}}
	\label{fig:real-z}
\end{figure}

### 2020-09-16 pcastack/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{IEEE Geoscience and Remote Sensing Letters, 14, no. 8, 1213-1217, (2015)}

\title{Application of principal component analysis in weighted stacking of seismic data}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\author{Jianyong Xie\footnotemark[1], Wei Chen\footnotemark[2], Dong Zhang\footnotemark[1], Shaohuan Zu\footnotemark[1], and Yangkang Chen\footnotemark[3]}

\address{
\footnotemark[1]
State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
%331334826@qq.com
gsw19900128@126.com\\
\footnotemark[2]
Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education, Yangtze University, Wuhan, Hubei, China, 430100, Hubei Cooperative Innovation Center of Unconventional Oil and Gas, Wuhan, Hubei, China, 430100, and State Key Laboratory of Geodesy and Earth's Dynamics, Institute of Geodesy and Geophysics, Chinese Academy of Sciences, Wuhan, China, 430077, chenwei2014@yangtzeu.edu.cn.\\
gsw19900128@126.com\\
\footnotemark[3] Jackson School of Geosciences\\
The University of Texas at Austin\\
University Station, Box X\\
Austin, TX 78713-8924, USA \\
Email: ykchen@utexas.edu\\
}

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}

\maketitle

\begin{abstract}
Optimal stacking of multiple datasets plays a significant role in many scientific domains. The quality of stacking will affect the signal-to-noise ratio (SNR) and amplitude fidelity of the stacked image. In seismic data processing, the similarity-weighted stacking makes use of the local similarity between each trace and a reference trace as the weight to stack the flattened prestack seismic data after normal moveout (NMO) correction. The traditional reference trace is an approximated zero-offset trace that is calculated from a direct arithmetic mean of the data matrix along the spatial direction. However, in the case that the data matrix contains abnormal mis-aligned trace, erratic and non-gaussian random noise, the accuracy of the approximated zero-offset trace would be greatly affected, thereby further influence the quality of stacking. We propose a novel weighted stacking method that is based on principal component analysis (PCA). The principal components of the data matrix, namely the useful signals, are extracted based on a low-rank decomposition method by solving an optimization problem with a low-rank constraint. The optimization problem is solved via a common singular value decomposition algorithm. The low-rank decomposition of the data matrix will alleviate the influence of abnormal trace, erratic and non-gaussian random noise, thus will be more robust than the traditional alternatives.  We use both synthetic and field data examples to show the successful performance of the proposed approach.
\end{abstract}
%The selection of reference trace plays a significant role in the final performance.

%the data matrix may contain abnormal mis-aligned trace, erratic and non-gaussian random noise, which will greatly affect the accuracy of the approximated zero-offset trace.

%The traditional similarity-weighted stacking approach uses the traditionally stacked trace as the reference, which is not plausible when there is abnormal trace in the data. 
%We proposed a new criteria for selecting the reference trace, which is based on the stacked trace after applying a truncated singular value decomposition to the NMO-corrected data. The TSVD aims to reduce the impact of the abnormal trace in the stacked trace, and thus can make the similarity-weighted stacking more robust.

\section{Keywords}
Weighted stacking, principal component analysis, low-rank decomposition, singular value decomposition, local similarity

\section{Introduction} 
Stacking of multiple datasets to output a final smoothed data is a common research subject in many scientific fields. The stacking can be viewed as the simplest form of random noise attenuation for enhancing multi-dimensional remote sensing datasets \cite{yanan2014,zhuang2015}. 
In seismic data processing, stacking simply means the summation of a collection of seismic traces from different records into a single trace. The quality of stacking greatly affect the performance of many seismic data processing tasks. It can be considered as the simplest way for improving the SNR \cite{elad2006,candes20062} in prestack seismic data processing. It can quickly obtain a meaningful post-stack seismic image without wavefield continuation. The three steps in the stacking process are \wen{normal moveout} (NMO) velocity analysis, NMO correction and trace summation.

The original weighted stacking used an SNR-based weighted stacking strategy to minimize random noise. \wen{Schoenberger} \cite{Schoenberger96} proposed a different weighted stacking approach that can suppress the multiples effectively by solving a set of optimization equations in order to determine the stacking weights. \wen{Neelamani et al.} \cite{Neelamani06} took the signal structures into consideration and proposed a simultaneous stacking and denoising approach (SAD). %\cite{Zhang06} made use of the wavelet transformation theory and the high-order statistics theory when proposing a high-order weighted stacking approach. 
Based on the statistics theory, \wen{Trickett} \cite{Trickett07} proposed to use a maximum-likelihood estimator for weighted stacking by estimating the probability distribution of random noise. \wen{Tang} \cite{Tang07} calculated the stacking weights as functions of angle and azimuth and proposed a selective stacking approach.

\wen{Li and Gao} \cite{stackgrsl2014} proposed a novel method for stacking seismic data in time-frequency domain \cite{liuwei2016ewt,hongbo2015}. %\cite{dengpan2016} took the amplitude-versus-offset (AVO) effect into consideration and proposed a weighted stacking method which can handle the amplitude variation phenomenon of CMP gathers. 
\wen{Liu et al.} \cite{Liu09} proposed a similarity-weighted stacking approach that designs the weights of each trace by calculating the local similarity between each trace and a reference trace, and the method was demonstrated to be superior to the state-of-the-art weighted stacking approaches. %However, the selection of the reference trace plays an important role in the final stacking performance. %The traditionally stacked trace is not plausible to be the reference trace when there are abnormal traces in the NMO-corrected gather. We propose to use a stacked trace from a denoised NMO-corrected gather after truncated singular value decomposition (TSVD) as the reference for calculating the similarity-based stacking weights. 
The reference trace in the traditional similarity-weighted stacking method is an approximated zero-offset trace directly calculated from the spatial arithmetic mean of data matrix \cite{ron2010}. When the data matrix contains mis-aligned trace, erratic and non-gaussian random noise, the spatial arithmetic mean of the data matrix is of low fidelity to approximate the zero-offset trace. In this letter, we propose a novel principal component analysis (PCA) \cite{farrell2005,duqian2007} based weighted stacking method. Considering the complicated situations of field seismic data as mentioned above, we propose to extract the principal components of seismic data to approximate a highly accurate zero-offset trace. The principal components of the data matrix are extracted via solving an optimization problem with low-rank constraint. A singular value decomposition can be used to efficiently solve the optimization problem and then the low-rank approximation of the data matrix, which has a high SNR and is close to the ideal NMO-corrected common midpoint (CMP) gather, can be easily obtained. The new stacking method is easy to implement and can obtain significantly better stacked profile with cleaner geological structures. %, since the TSVD step can reduce the influences of both abnormal traces and random noise on the final performance. 
We first use a simple synthetic example to show the \dlo{principal}\wen{principle} and then use a real pre-stack field data example to further demonstrate the tremendous improvement over the traditional approaches.

\section{Method}
\subsection{Equal-weight stacking}
In order to enhance the SNR of the zero-offset trace, all traces in a prestack CMP gather are summed. The traditional equal-weight stacking is the average of all traces in a prestack CMP gather.
\begin{equation}
\label{eq:stack}
\hat{s}(t)= \frac{1}{N}\sum_{i=1}^{N} s_i(t),
\end{equation} 
where $t$ is time, $s_i(t)$ denotes the $i$th trace. $\hat{s}(t)$ is the stacked zero-offset trace, and $N$ is the number of traces.

\subsection{Weighted stacking}
However, the quality of each trace is different and each trace should contribute differently to the final stacked trace. A better stacking approach is to weight each trace before stacking based on certain criteria. The weighted stacking process can be formulated as
\begin{equation}
\label{eq:simistack}
\hat{s}_w(t)= \frac{1}{\sum_{i=1}^{N}w_{i}(t)}\sum_{i=1}^{N}w_{i}(t)\cdot s_i(t) 
\end{equation} 
where $w_{i}(t)$ is the weight applied to trace $i$ and time $t$ in a CMP gather. $\hat{s}_w(t)$ is the stacked trace after weighting.

Different methods have been proposed to apply weights according to different criteria. For example, the smart stacking proposed by \cite{Rashed08} is based on sign difference between sample point and the alpha-trimmed mean to remove frequency distortions. \cite{Neelamani06} uses an iterative algorithm called \emph{leave me out} (LMO) to estimate noise variances from data. The desired signal is assumed to be flat with constant amplitude across all the traces within a gather in the LMO method.

\subsection{Similarity-weighted stacking}
The similarity-weighted stacking method was proposed by \cite{Liu09} to weight each trace according to the time-variant local similarity between each trace and the mean trace.

To implement the similarity-weighted stacking, we first apply the equal-weight stack to the NMO-corrected CMP gather to obtain the reference trace. Then we compute the local similarity \cite{yangkang2015orthogroll} between the reference trace and the NMO-corrected CMP gather and apply soft thresholding \cite{donoho1995} to all local similarity values. Finally, we apply the weighted stack to the CMP gather using local similarity based weights to get the final stacked trace. %The mathematical principal of similarity-weighted stacking can be summarized as:
%\begin{equation}
%\label{eq:simistack}
%\hat{s}_w(t)= \frac{1}{\sum_{i=1}^{N}w_{i}(t)}\sum_{i=1}^{N}w_{i}(t)\cdot s_i(t) 
%\end{equation} 
% $w_i$ denotes the weight of the $i$th trace in a CMP gather, which
The local similarity based weighting criteria is defined as:
\begin{align}
\label{eq:weight}
w_i(t)=\left\{\begin{array}{cl}
\eta_{i}(t)-\epsilon, & \quad \eta_i>\epsilon \\
0 & \quad  \eta_i \le \epsilon
\end{array},\right.
\end{align}
where $\epsilon$ is the threshold value, $\eta_i(t)$ is the local similarity between $i$th prestack trace and the reference trace:
\begin{equation}
\label{eq:eta}
\eta_i(t) = \mathcal{S}(s_i(t),\hat{s}(t)).
\end{equation}
where $\mathcal{S}(a,b)$ denotes the local similarity between traces $a$ and $b$. $\hat{s}(t)$ is the arithmetic mean as introduced \dlo{above}\wen{in (\ref{eq:stack})}. \wen{$\epsilon$ can be intelligently chosen by defining a percentage. The percentage is used to preserve or reject the values during thresholding. For example, a percentage of 10 means that we preserve 10\% largest value of the local similarity $\eta$. The result is not very sensitive to $\epsilon$. We usually keep a 50\% of largest $\eta$ values to obtain the stacking result. }

\subsection{Low-rank approximation of the data matrix}
In the similarity-weighted stacking approaches \dlo{(equations \ref{eq:simistack}-\ref{eq:eta})}\wen{(\ref{eq:simistack})-(\ref{eq:eta})}, $\hat{s}(t)= \frac{1}{N}\sum_{i=1}^{N} s_i(t)$ is not an appropriate zero-offset approximation. The spatial arithmetic mean of the data matrix is the true zero-offset trace only if the random noise is statistically white, and all traces after NMO correction are aligned well. Furthermore, no existing abnormal traces should exist in the data matrix. These requirements are seldom met due to the extremely complicated features of real seismic data and seismic data are always contaminated with different types of noise, e.g. erratic noise and colored noise.

A better way for calculating the approximation of the zero-offset trace is to calculate the spatial arithmetic mean of a low-rank approximated data matrix using principal component analysis (PCA). PCA is an important tool for multivariate analysis in statistics. The idea is to reduce the dimensionality
of a data set while preserving as much variability of data variables as possible \cite{jolliffe2010}.

Suppose the data matrix $\mathbf{D}$ is composed of signal component $\mathbf{S}$, random noise $\mathbf{N}$, erratic noise $\mathbf{E}$, and mis-aligned data components $\mathbf{M}$:
\begin{equation}
\label{eq:pca1}
\mathbf{D} = \mathbf{S} + \mathbf{N} + \mathbf{E} + \mathbf{M}.
\end{equation}
\wen{For seismic stacking in this paper, $\mathbf{D}$ is simply a common midpoint gather.}
 If we assume the error components $ \mathbf{N} + \mathbf{E} + \mathbf{M}$ are composed of small random perturbations, an optimal estimate of $\mathbf{S}$ can be acquired via the following optimization problem:
 \begin{equation}
 \label{eq:pca2}
 \begin{split}
 &\min \parallel \mathbf{N} + \mathbf{E} + \mathbf{M} \parallel_F^2, \\
 s.t. &\quad rank(\mathbf{S})=k, \quad \mathbf{D} = \mathbf{S} + \mathbf{N} + \mathbf{E} + \mathbf{M},
 \end{split}
 \end{equation}
 where $k$ denotes the rank constraint applied to the target signal components. The problem can be efficiently solved via singular value decomposition (SVD).  The observed data matrix $\mathbf{D}$ can be decomposed into a group of eigen-images via the SVD. The low-rank component $\mathbf{S}$ can be described with a few eigen-images that are associated with the largest singular values. The other noise items $ \mathbf{N}$, $\mathbf{E}$, $\mathbf{M}$, however, will have energy spread over all the eigen-images.

\subsection{Weighted stacking based on PCA} 
After the low-rank approximation of the data matrix $\hat{\mathbf{S}}$ is obtained, a better zero-offset reference trace can be obtained via calculating the arithmetic mean of the data matrix along the spatial direction:
 \begin{equation}
 \label{eq:ave}
\hat{s}_{lr}(t)= \hat{S}\mathbf{a},
 \end{equation}
 where $\mathbf{a}$ is an averaging column vector $[\frac{1}{N},\frac{1}{N},\cdots,\frac{1}{N}]_{1\times N}^T$. Here $[\cdot]$ denotes the transpose of the input matrix/vector.
Substituting $\hat{s}(t)$ in \dlo{equation \ref{eq:eta}}\wen{(\ref{eq:eta})} with $\hat{s}_{lr}(t)$, we can obtain a new weighting criteria:
\begin{align}
\label{eq:weight1}
\omega_i(t)=\left\{\begin{array}{cl}
\beta_{i}(t)-\epsilon, & \quad \beta_i>\epsilon \\
0 & \quad \beta_i \le \epsilon
\end{array},\right.
\end{align}
where $\beta_i(t)$ is the local similarity between $i$th prestack trace and the low-rank approximated reference trace:
\begin{equation}
\label{eq:beta}
\beta_i(t) = \mathcal{S}(s_i(t),\hat{s}_{lr}(t)).
\end{equation}
Inserting the new weighting criteria, as shown in \dlo{equation }\wen{(\ref{eq:weight1})}, into \dlo{equation }\wen{(\ref{eq:simistack})}, we obtain the new PCA-based weighted stacking approach. The detailed algorithm workflow of the proposed weighted stacking approach can be expressed as:

\begin{enumerate}
\item Calculate the SVD of data matrix $\mathbf{D}$:
\begin{equation}
\label{eq:svd}
[\mathbf{U},\Sigma,\mathbf{V}]=\text{SVD}(\mathbf{D})
\end{equation}
\item Calculate the low-rank approximated singular value matrix by selecting the $k$ largest diagonal elements and setting others zero:
\begin{equation}
\label{eq:singular}
\hat{\Sigma} = \Sigma(1:k,1:k)
\end{equation}
\item Calculate the low-rank approximated data matrix
\begin{equation}
\label{eq:lr}
\hat{\mathbf{S}} = \mathbf{U}\hat{\Sigma}\mathbf{V}^T.
\end{equation}
\item Calculate the arithmetic mean of the low-rank approximated data matrix according to \dlo{equation }\wen{(\ref{eq:ave})}.
\item Calculate the local similarity between each trace and the low-rank approximated zero-offset reference trace.
\item Calculate the PCA-based weighting function $w_i(t)$ according to \dlo{equation }\wen{(\ref{eq:weight1})}.
\item Stack the CMP gather using the calculated weighting function according to \dlo{equation }\wen{(\ref{eq:simistack})}.
\end{enumerate}
For more complicated cases, the nonlinear equivalent of standard PCA (NPCA) can be used to potentially obtain even better performance. The NPCA reduces the observed variables to a number of uncorrelated principal components. The most important advantages of nonlinear over linear PCA are that it incorporates nominal and ordinal variables, and that it can handle and discover nonlinear relationships between variables, which may indicates the the traces may not need to be exactly flattened before stacking.

\section{Examples}
%The abnormal trace in the NMO-corrected gather will make the traditionally stacked trace suffering from energy loss. In order to reduce the effect of abnormal trace to the reference trace. We propose to apply a truncated singular value decomposition to the NMO-corrected data in order to make the energy equally distributed in all the traces. As shown in Fig. \ref{fig:syncomp}a, there is an abnormal trace in the NMO-corrected gather. Fig. \ref{fig:syncomp}b shows the cleaner data after TSVD. The energy of the abnormal trace is greatly decreased.

We first use a simple synthetic example to show the logic of the proposed approach. Fig. \ref{fig:syncomp} shows an NMO-corrected CMP gather \wen{on the left}. It is salient that there is an abnormal trace in the CMP gather. Besides, there is a significant amount of random noise in the data. For this data set, it is not plausible to directly take the arithmetic mean of the traces to stand for the zero-offset trace, since the abnormal trace will greatly degrade the fidelity of the equal-weight stacked trace and the non-gaussian random noise will cause a lot of residual noise in the stacked trace. However, the low-rank approximated data matrix (as shown in \dlo{Fig. 1b}\wen{the right subfigure in Fig. 1}) that alleviates the influence of the abnormal trace and non-Gaussian random noise is much cleaner and close to the ideal NMO-corrected CMP gather.

\dlo{Figs. 2b,2c,2d,2e}\wen{The second to fifth subfigures (from left to right) in Fig. 2} show the stacked traces using traditional stacking, smart stacking \cite{Rashed08}, SNR stacking \cite{Neelamani06} and similarity weighted stacking  \cite{Liu09}, respectively. Despite the existence of the abnormal first trace, the similarity-weighted trace obtains the best stacking performance as shown in \cite{Liu09}. \dlo{We zoom in Figs. 2a and 2e and show them in Figs. 3a and 3b.}\wen{We zoom in the last figure in Fig. 2 and show it in the middle of Fig. 3.} In addition, we show \wen{the clean signal on the left of Fig. 3 and}the stacked \dlo{trace}\wen{signal} using the proposed method on the right of Fig. 3. It is obvious that the abnormal trace makes the stacked trace based on local similarity deviate from the true signal a lot around 0.175s, as pointed out by the arrow. The proposed method, however, obtains a \dlo{nearly perfect}\wen{successful} stacked signal.  \wen{The SNR of the similarity based method is 8.85 dB and the SNR of the PCA based method is 9.38 dB.} We can conclude from the synthetic example that the proposed method can not only help improve the SNR, but also can help better preserve the amplitude of the useful signals. %Instead of using the Fig. 2b as the reference trace, we first apply TSVD to the NMO-corrected data, shown in Fig. 1b, and then obtain an equal-weight stacked trace, then using this trace as the reference for calculating the local similarity. After both TSVD and similarity-weighted stacking, the stacked trace (Fig. 3b) is even better than that of the similarity stacking approach (Fig. 3c).

\wen{The number of stacking signals may be large, e.g., more than 50. The number of abnormal traces can also be larger than 1. Actually, when the number of stacking signals becomes larger, the method becomes more appealing, since more signals also implies more complicated signal features, more noise, and more abnormal traces. The superiority of the proposed method will become more practically beneficial when the data size and structure becomes more complicated, e.g., the field data example discussed next.}
%This combined TSVD and local similarity weighted stacking can make the stacking more robust in field applications.

We then apply the proposed method to a field data example, as shown in Fig. \ref{fig:cmps}. The second field data is a 2-D line from the Blake Outer Ridge area offshore Florida and Georgia\dlo{ (Figure~\ref{fig:map2})}. \dlo{It was collected by USGS in order to study the occurrence of methane hydrates. The presence of gas hydrates is manifested by a so-called BSR (bottom-simulating reflector).} Fig. \ref{fig:nmo} shows a demonstration of flattening one CMP gather (Fig. \ref{fig:nmo}a) using NMO velocity analysis (Fig. \ref{fig:nmo}b) and NMO correction (Fig. \ref{fig:nmo}c). The white line overlaying Fig. \ref{fig:nmo}b denotes the automatically picked NMO velocity used for flattening the gather. \dlo{Fig. \ref{fig:blake-simi-cube} shows all the NMO corrected gathers in a 3D cube.} Fig. \ref{fig:blake-weight} shows the weight calculated using the proposed method (equations \ref{eq:weight1} and \ref{eq:beta}). The stacked seismic images using different methods are shown in Fig. \ref{fig:blake-stack0,blake-simistack0,blake-simistack-tsvd0}.

As shown in Fig. \ref{fig:blake-stack0,blake-simistack0,blake-simistack-tsvd0}, the three sections (a),(b),(c) correspond to the stacked images of this field data example using three different methods: equal-weight stacking, similarity-weighted stacking, and PCA-based stacking. The proposed approach obtains a more satisfying stacking performance, as shown in Fig. \ref{fig:blake-simistack-tsvd}. The amplitude of seismic reflections becomes obviously stronger using the proposed approach (Fig. \ref{fig:blake-simistack-tsvd}). Fig. \ref{fig:zoom1,zoom2,zoom3} shows zoomed sections that correspond to the pink frame boxes shown in Fig. \ref{fig:blake-stack0,blake-simistack0,blake-simistack-tsvd0}. It further confirms that the proposed method can help obtain cleaner stacked image and better preserve the amplitude of the useful signals. \wen{In order to quantitatively compare the stacking performance of different methods, we plot the average spectrum (1D FFT along the time axis) of all the traces of the stacked images for three methods and show them in Fig. \ref{fig:field-fs}. The black line denotes the average spectrum of equal-weight stacking method. The green line corresponds to similarity stacking method. The red line corresponds to the proposed approach. It is very obvious that the energy of the proposed algorithm is stronger than that of the equal-weight stacking method and similarity stacking method, indicating that the proposed algorithm helps best preserve the amplitude of seismic reflection events. We also calculate the maximum frequency energy (MFE), i.e., the maximum amplitude of the average frequency spectrum, for three methods. MFE is 231.83 for the equal-weight method, 415.24 for the similarity method, and 504.77 for the proposed method. The proposed method improve the equal-weight method by 117.33\% and improve the similarity method by 21.56\% in terms of MFE. }

\new{It is worth mentioning that there is no 100\% reliable way to compare the stacking performance of real seismic data in the literature, since there is no ground truth for real data. When judging the stacking performance by human observation, we care about the "large amplitude/energy" of those key reflectors since stronger amplitude/energy makes us see clearer the reflectors, as highlighted by the ellipses and arrows in Fig. 8. When interpreting the seismic profiles, the No 1 principle is to detect those critical reflectors, the No 2 principle is the coherency of those reflectors since it is related to the horizon tracking in seismic interpretation. The "accuracy" or "fidelity" of amplitude is not very important in interpretation of time-migrated seismic images. However, the modern seismic imaging techniques such as true-amplitude least-squares migration \cite{yangkang2017lsrtm}, seek to obtain true-amplitude subsurface image where the amplitude correctness is of vital importance. However, this is beyond the scope of the letter For judging the stacking performance of field data, we highly recommend to judge by "observing" and "interpreting".  }

\section{Conclusion}
The similarity-weighted stacking approach can obtain a much improved stacking result than the equal-weight stacking considering the increased SNR, however, will still cause
energy damage when an inappropriate reference trace is used to calculate the similarity based weights. %We propose a combined TSVD and local similarity stacking technique that can mitigate the influence of abnormal traces to the amplitude of reference trace. 
We proposed a new weighted stacking method that is based on principal component analysis (PCA). The principal of the method is to prepare an ideal NMO-corrected data matrix via low-rank approximation. The low-rank approximation, or in other words the principal components, is obtained via solving a low-rank constrained optimization problem via singular value decomposition (SVD). The proposed PCA-based stacking method can help alleviate the negative effects caused from abnormal trace, erratic and non-gaussian random noise existing in the data matrix, and thus is robust in field data processing.  The proposed approach is tested via a synthetic CMP gather and a field data example, which shows very promising performance. \wen{Future research topics include substituting the current PCA framework with more sophisticated algorithms to make the obtained components statistically as independent as possible, such as Independent Component Analysis (ICA), where higher-order statistics rather than second-order moments are used to determine basic vectors and is proven to be stronger than PCA \cite{ica2001}.}

%\begin{figure}[htb!]
%\centering
%\includegraphics[width=0.5\columnwidth]{field/Fig/blake-simi-cube}
%\caption{NMO-corrected 3D data cube. }
%\label{fig:blake-simi-cube}
%\end{figure}

\inputdir{synth}
\plot{syncomp}{width=\columnwidth}{Left: Original NMO-corrected data. Right: Low-rank approximated data matrix. }

\plot{compare}{width=\columnwidth}{\dlo{(a) NMO-corrected data. (b) Conventional stack. (c) Smart stack. (d) SNR stack. (e) Similarity stack .} \wen{From left to right: NMO-corrected data, conventional stack, smart stack \cite{Rashed08}, SNR stack \cite{Neelamani06}, and similarity stack  \cite{Liu09}.} }

\plot{simi-combine}{width=\columnwidth}{From left to right: true signal, stacked signal using the similarity-weighted stacking \wen{(SNR=8.85 dB)}, and stacked signal based on the PCA method \wen{SNR=9.38 dB}.}

\inputdir{field}

\plot{cmps}{width=\columnwidth}{Field data example.  }

\plot{nmo}{width=\columnwidth}{Demonstration of NMO correction for the field data example. }

\plot{blake-weight}{width=\columnwidth}{PCA-based weights for each time and space indices.}

\multiplot{3}{blake-stack0,blake-simistack0,blake-simistack-tsvd0}{width=0.7\columnwidth}{(a) Stacked result using equal-weight method. (b) Stacked result using local similarity based weight. (c) Stacked result using the proposed method.}

\inputdir{./}
\multiplot{3}{zoom1,zoom2,zoom3}{width=0.7\columnwidth}{Zoomed sections from Fig. \ref{fig:blake-stack0,blake-simistack0,blake-simistack-tsvd0}. (a) Stacked result using equal-weight method. (b) Stacked result using local similarity based weight. (c) Stacked result using the proposed method.}

\plot{field-fs}{width=\columnwidth}{Comparisons of the average spectrum of all the traces. The black line denotes the average spectrum of equal-weight stacking method. The green line corresponds to similarity stacking method. The red line corresponds to the proposed approach. Note that energy of the proposed algorithm is obviously stronger than the other two methods.}

\section{Acknowledgments}
This research is supported by Supported by State Key Laboratory of Geodesy and Earth's Dynamics (Institute of Geodesy and Geophysics, CAS, Grant No. SKLGED2017-4-3-E) and Sinopec Key Laboratory of Geophysics (Grant No. 33550006-15-FW2099-0017). J. Xie is supported by China Scholarship Council (201606440091). J. Xie also thanks the Shell Ph.D Scholarship to support excellence in geophysical research.

\bibliographystyle{seg}
\bibliography{svdstack}

### 2020-09-16 q/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{Geophysical Journal International, 218, 655–665, (2019)}

\title{Multi-channel quality factor Q estimation}
\author{Yangkang Chen}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\author{Yangkang Chen\footnotemark[1]}

\ms{GJI-2019}

\address{
\footnotemark[1]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
yangkang.chen@zju.edu.cn 
}

\lefthead{Chen, 2019}
\righthead{Multi-channel Q estimation}

\begin{abstract}
The estimation of quality factor, Q, plays an important role in many geophysical problems, including Q-compensated seismic imaging, geophysical interpretation, and fluid characterization. One of the most widely used approaches for estimating Q is the spectral ratio method (SRM). However, the spectral division in SRM may not be stable due to the spectral nulls. The shaping regularized inversion that treats the spectral division as a regularized least-squares inversion problem can help solve the spectral-nulls problem and make the spectral division stable. In the case of very noisy seismic data, the time-frequency maps can not be optimally obtained and thus the Q estimation performance will be strongly affected and unstable even with the regularized inversion method. We propose a multi-channel Q estimation approach that takes advantage of the multi-channel spatial coherence to constrain the inversion so that the estimated Q is spatially continuous. We use a set of synthetic and real data examples to demonstrate the performance of the multi-channel Q estimation method. Results show that the proposed method can obtain accurate and more importantly stable Q estimation result even in the case of strong random noise.
\end{abstract}

\section{Introduction}
Because of the anelasticity and heterogeneity of earth medium, seismic waves experience absorption when traveling through the earth \cite[]{ricker1953,futterman1962,wright1981,kneib1995,changjun2002,yanghua2002,patro2006,youyi2010,youyi2012,shuwei2016vscan,yufeng2018geo}. The attenuation of seismic waves is a property of the earth, and is quantified by Q, the quality factor. Seismic attenuation affects both amplitude and waveforms of the recorded seismic data. The accuracy and stability when estimating the quality factor have effects on processing quality, seismic imaging, amplitudes interpretation and reservoir description \cite[]{guorui2014,yufeng2018l12}. 
Q can be used to enhance seismic resolution by inverse Q filtering or Q-compensated migration \cite[]{Kjartansson1979Constant,Carcione2002Time,toverud2005comparison,carcione2007wave,zhang2007seismic,wang2011attenuation,prudencio2013spatial,delle2014frequency,dutta2014attenuation,zhu2014time,li2015efficient,matsushima2015seismic,wang2015q,tieyuan2015Implementation,zhu2017viscoelastic,jingnan2018}, and can also be used to aid AVO analysis because the attenuation effects are superimposed on AVO signature and can be corrected if accurate Q values are available for compensation. Besides, Q can be potentially used as a hydrocarbon indicator \cite[]{hedlin2001,yanghua2004,yanghua2014}. In addition, Q can be used to provide information about lithology, porosity, and fluid or gas saturation of subsurface to facilitate seismic interpretation \cite[]{pengcheng2012}.

The algorithm for estimating Q from recorded seismic data has been investigated exclusively in the literature. Q can be estimated in time domain, frequency domain and time-frequency domain, each domain has its own advantage and limitation. In time domain, the pulse amplitude decay (PAD) \cite[]{brzostowski1992}, pulse rising time (PRT) \cite[]{Kjartansson1979Constant}, and pulse broadening (PB) \cite[]{wright1981} are the most common approaches. In the frequency domain, those approaches include spectral ratio method (SRM) \cite[]{hauge1981,raikes1984}, centroid frequency shifting (CFS) \cite[]{quan1997} and peak frequency shifting (PFS) \cite[]{changjun2002,jinghuai2007}. All these frequency domain approaches require Fourier transforms to calculate the frequency spectra of seismic records sampled within a time window \cite[]{senlin2009}.  The time-frequency domain approach includes peak scale variations (PSV) \cite[]{li2006} in the wavelet domain to estimate Q by assuming an idealized pulse as the seismic source wavelet. However, the difference between the real source wavelet and an idealized pulse may be substantial, which is the limitation of the PSV method. There also exists a type of Q estimation approaches based on the instantaneous frequency (IF) of seismic record. In this type of method, Q can be estimated by inversion from the relationship between the measured instantaneous spectra and the seismic attenuation \cite[]{tonn1991,barnes1991,engelhard1996}. \cite{matheney1995} proposed a IF matching (IFM) method, which can iteratively modifies the causal attenuation operator \cite[]{akirichards.2002} so that the IF at the envelope peak of the reference pulse is the closest to that of the target pulse and thus Q can be estimated. Although IFM requires a time-window and an iterative procedure, it does not have the requirement of selecting variable frequency bands as required by SRM.

Several researchers compared different Q estimation methods in the literature. \cite{jannsen1985} compared PRT, SRM, spectrum modeling method and wavelet modeling method, and concluded that the wavelet modeling method is relatively better. \cite{tonn1991} compared the Q estimation approaches based on zero-offset VSP data, and concluded that no single method is generally superior. The performance of different Q estimation approaches depends on the specific situation where they are used. For example, analytical signal method is better for true amplitude recording, and SRM is the best for noise free data. \cite{senlin2009} compared four Q estimation methods, including SRM, CFS, PFS and wavelet envelope peak instantaneous frequency (WEPIF) methods according to their performance regarding wavelet independence, noise resistance and resolution of thin beds. Their comparison results showed that SRM is the best in both wavelet independence and noise resistance. WEPIF is the best in obtaining a highest resolution for a wedge model. \cite{reine2009} compared four time-frequency transforms used for SRM. Their results show that time-frequency transforms with a systematically varying time window, such as the S transform and continuous wavelet transform (CWT), can obtain more robust estimation of Q \cite[]{guochang2010}.

By reformulating the SRM in the time domain, \cite{pengcheng2012} proposed a matching filtering method  (MFM). Instead of calculating a spectral ratio, the Q estimation turns to finding a convolution operator in the time domain. The MFM is theoretically same to the SRM because the inverse Fourier transform of a spectral ratio is a matching filter. However, the time domain MFM is more robust in the presence of noise than direct spectral division in the frequency domain. Based on the concept of frequency down-shift, \cite{raji2013} proposed a new mathematical model to achieve a reliable Q estimation, which shows less sensitivity to noise interference and change of frequency bandwidth. Their inversion process mainly consist of two stages: (1) computation of the centroid frequency for the individual signal using variable window length and fast Fourier transform; (2) estimation of the difference in the centroid frequency and traveltime for a paired incident and transmitted signals.

From the literature review, we can conclude that the noise level existing in the seismic records is the main effect on the Q estimation performance. In this paper, we propose a multi-channel Q estimation approach using a regularized spectral ratio method, which can utilize the spatial coherence of useful reflection signals to alleviate the influence of strong random noise. The proposed method can help obtain an accurate Q estimation result even from the raw seismic data without the need of denoising. We formulate the spectral division as a regularized inversion problem and use shaping regularization with a local smoothing constraint to solve the optimization problem. The smoothness constraint is applied both along the frequency and space directions. According to the conclusion from \cite{reine2009} and \cite{guochang2010}, we propose to use the S transform \cite[]{stockwell1996} as the optimal time-frequency transform for the Q estimation. We organize the paper as follows: we first introduce the state-of-the-art single-channel Q estimation method based on the spectral ratio method. Then, we introduce the multi-channel Q estimation method based on the regularized spectral division framework, and we also introduce the shaping regularization method to solve the inversion-based regularized spectral division problem. Next, we test the proposed multi-channel Q estimation method on several synthetic and real data examples in the section of EXAMPLES. We also discuss the issues regarding the influence of noise and denoising, and computational complexity in the section of INTRODUCTION. Finally, we draw some key conclusions at the end of the paper.

\section{Theory}

\subsection{Single-channel spectral ratio method}
The  seismic wave amplitude spectrum after propagating from traveltime $t_1$ to $t_2$ in a homogeneous attenuating medium are given by:
\begin{align}
\label{eq:sp1}
Y(f,t_1) &= A(t_1)Y(f,t_0)e^{-\frac{\pi f(t_1-t_0)}{Q}},\\
\label{eq:sp2}
Y(f,t_2) &= A(t_2)Y(f,t_0)e^{-\frac{\pi f(t_2-t_0)}{Q}},
\end{align}
where $f$ is the frequency, $Y(f,t_1)$ and $Y(f,t_2)$ are the seismic wave amplitude spectrum after propagating traveltime $t_1$ and $t_2$, respectively, $Y(f,t_0)$ is the initial amplitude spectrum, and $A(t)$ is a factor independent of frequency. Combining equations \ref{eq:sp1} and \ref{eq:sp2}, we can obtain:
\begin{equation}
\label{eq:sp}
\frac{Y(f,t_2)}{Y(f,t_1)} = \frac{A(t_2)e^{-\frac{\pi ft_2}{Q}}}{A(t_1)e^{-\frac{\pi ft_1}{Q}}} = d(f).
\end{equation}
Take a natural log of each side of equation \ref{eq:sp}, we obtain:
\begin{equation}
\label{eq:log}
\ln[d(f)] = A+Bf,
\end{equation} 
where $A$ and $B$ are both constants, and $A=\ln(A(t_2)/A(t_1))$, $B=-(\pi(t_2-t_1)/Q)$. Here, $B$ can be estimated by the slope of linear regression line. Then, $Q$ can be estimated by 
\begin{equation}
\label{eq:q}
Q=\frac{\pi(t_1-t_2)}{B}.
\end{equation}

\subsection{Multi-channel Q estimation method}
The method introduced above refers to the single-channel method for Q estimation. In the single channel method, Q is estimated trace-by-trace, which does not consider the spatial coherence of the Q model. In the multi-channel method, we introduce the spatial coordinate $x$ into equations \ref{eq:sp1} and \ref{eq:sp2}:
\begin{align}
\label{eq:sp1x}
Y(f,t_1,x) &= A(t_1,x)Y(f,t_0,x)e^{-\frac{\pi f(t_1-t_0)}{Q(x)}},\\
\label{eq:sp2x}
Y(f,t_2,x) &= A(t_2,x)Y(f,t_0,x)e^{-\frac{\pi f(t_2-t_0)}{Q(x)}},
\end{align}
where $x$ indicates that $Y(f,t_1,x)$, $A(t_1,x)$, $Q(x)$ vary with spatial coordinate $x$. Dividing equation \ref{eq:sp1x} by equation \ref{eq:sp2x}, equation \ref{eq:spx} becomes:
\begin{equation}
\label{eq:spx}
\frac{Y(f,t_2,x)}{Y(f,t_1,x)} = \frac{A(t_2,x)e^{-\frac{\pi ft_2}{Q(x)}}}{A(t_1,x)e^{-\frac{\pi ft_1}{Q(x)}}} = d(f,x).
\end{equation}

\subsection{Spectral division by shaping regularization}
The key step in the SRM is the division between $Y(f,t_2,x)$ and $Y(f,t_1,x)$. The division may be unstable when denominator $Y(f,t_1,x)$ is very small or the spectrum is not smooth. \cite{fomel2007localattr} and \cite{guochang2010} treated the division of two vectors ($\mathbf{a}$ and $\mathbf{b}$) as a regularized least-squares minimization problem:
\begin{equation}
\label{eq:opti}
\min_{\mathbf{c}} \parallel \mathbf{a} -\mathbf{B}\mathbf{c} \parallel_2^2 + \mathbf{R}(\mathbf{c}),
\end{equation}  
where $\mathbf{B}=diag(\mathbf{b})$, $diag$ denotes the diagonal matrix composed of $\mathbf{b}$, $\mathbf{R}$ is the regularization operator. Shaping regularization \cite[]{fomel2007shape} can provide a convenient way for enforcing the smoothness of the solution in equation \ref{eq:opti} and the solution of equation \ref{eq:opti} has the following form:
\begin{equation}
\label{eq:solu}
\mathbf{c} = [\lambda^2\mathbf{I} + \mathcal{T}(\mathbf{B}^T\mathbf{B}-\lambda_1^2\mathbf{I})]^{-1}\mathcal{T}\mathbf{B}^T\mathbf{a},
\end{equation}
where $\mathbf{\mathcal{T}}$ is a two-dimensional smoothing operator, which controls the smoothness along the frequency and space axes. $\lambda$ is a parameter controlling the physical dimensionality and enabling fast convergence when inversion is implemented iteratively. It can be chosen as $\lambda  = \Arrowvert\mathbf{B}^T\mathbf{B}\Arrowvert_2$ \cite[]{fomel2007localattr}.

Here, in order to obtain a stable division between $Y(f,t_2,x)$ and $Y(f,t_1,x)$, we only need to substitute $\mathbf{a}$ and $\mathbf{b}$ with $Y(f,t_2,x)$ and $Y(f,t_1,x)$, where $f\in(f_{min},f_{max})$, respectively.

When the spectral ratio $d(f,x)$ is calculated, we can do the least-squares line-fitting by taking the natural log of each side of equation \ref{eq:spx}:
\begin{equation}
\label{eq:logx}
\ln[d(f,x)] = A(x)+B(x)f,
\end{equation} 
where $A(x)$ and $B(x)$ are both varying with the space coordinate $x$, and 
\begin{align}
\label{eq:Ax}
A(x)&=\ln(A(t_2,x)/A(t_1,x)),\\
\label{eq:Bx}
B(x)&=\frac{-\pi(t_2-t_1)}{Q(x)}.
\end{align}
The least-squares line-fitting for estimating $A(x)$ and $B(x)$ can be expressed as 
\begin{equation}
\left(\hat{A}(x),\hat{B}(x) \right) = \displaystyle \arg \min_{\left(A(x),B(x)\right)}\left\|
\left[\begin{array}{cc}
1 & f_1\\
1 & f_2\\
\vdots & \vdots\\
1 & f_n\\
\end{array}\right]\left[\begin{array}{c}
A(x)\\
B(x)
\end{array}\right]-\left[\begin{array}{cc}
\ln[d(f1,x)]\\
\ln[d(f2,x)]\\
\vdots \\
\ln[d(fn,x)]\\
\end{array}\right] \right\|_2^2.
\end{equation}
After the least-squares line-fitting, Q can be calculated as
\begin{equation}
\label{eq:qx}
Q(x)=\frac{\pi(t_1-t_2)}{B(x)}.
\end{equation}

The proposed method requires a time-frequency mapping to obtain $Y(f,t,x)$ for the subsequent calculation. \cite{reine2009} showed that the time-frequency transform used to calculate the spectrum of the seismic wave affects the accuracy of estimated Q, and the S transform and CWT decrease the variability of the attenuation estimate, specifically at the high and low ends of the spectrum because of a variable window function used in the definition. Because of the success of the S transform in estimating Q as shown in \cite{reine2009} and \cite{guochang2010}, we continue to use the S transform as the time-frequency transform in our multi-channel Q estimation framework. In the appendix, we provide a brief review of the S transform.

The proposed method is convenient to implement and its parameters are easy to control. The proposed multi-channel Q estimation method is developed based on the state-of-the-art spectral ratio method framework. The difference between the proposed method and the traditional method lies in the way we calculate the spectral division. The regularized spectral division is an elegant way to avoid the problem of spectral nulls when doing a spectral division conventionally. The shaping regularization method has also been a state-of-the-art algorithm in recent years. A detailed algorithm framework of the iterative shaping regularization can be found in \cite{fomel2007shape}. The smoothness constraint is very straightforward to apply, i.e., two smoothing operators along the frequency and space directions individually. The smoothing operators can be a triangle operator or a Gaussian smoothing operator, both of which are very typical in the signal processing literature. In the whole algorithm framework, the only parameters we need to set are the smoothing radii along the frequency and space axes and the frequency range for least-squares line fitting. The larger smoothing radius, the smoother spectral ratio we will get. The frequency range is related with the dominant frequency range of the useful signals. We have mentioned the parameter selection in detail for each example. In practice, one need to adjust these parameters several times. Since there parameters have very straightforward implications, the adjustment of the parameters is still easy to control.

\section{Examples}
In this section, we use two synthetic examples to demonstrate the performance of the proposed multi-channel Q estimation method. In the first example, we use a spatially constant Q to simulate the example. In the second example, we use a spatially varying Q. Then, we apply the proposed method to a field data example.

The first synthetic example is shown in Figure \ref{fig:traces,trace-15}. We apply band-limited random noise to the clean data to simulate a realistic data that contains random ambient noise, as shown in Figure \ref{fig:traces}. The signal-to-noise ratio (SNR) of the noisy data is -4.5 dB. We use the following SNR definition \cite[]{yangkang2016irr5d,mostafa2016geo,mostafa2016bssa,mostafa2017geo,yangkang2017sgk}:
\begin{equation}
\label{eq:snr}
\text{SNR}=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2^2}{\Arrowvert \mathbf{s} -\hat{\mathbf{s}}\Arrowvert_2^2}.
\end{equation}
where $\mathbf{s}$ denotes the noise-free data and $\hat{\mathbf{s}}$ denotes the denoised data.

The random noise is very strong and the the useful reflection signals are almost buried in the strong noise. Figure \ref{fig:trace-15} shows a single trace (the middle trace) that is extracted from the multi-channel seismic section.  To apply the spectral ratio method (SRM), we first transform the seismic data from time-space domain to time-frequency-space domain using the S transform. We show the time-frequency cube of the seismic data in Figure \ref{fig:trace-st-N}. Because of the strong random noise, the 2D time-frequency analysis becomes highly affected and resulted time-frequency map is highly irregular, as revealed by the front panel in Figure \ref{fig:trace-st-N}. However, when time-frequency maps are arranged section by section in a 3D cube, the peaks (high amplitude anomaly) on the time-frequency maps become continuous along the space direction in the time-frequency cube. Thus, by taking the 3D time-frequency cube into consideration when computing the spectral ratio, the spatial coherence can be well utilized. Figure \ref{fig:trace-f-t2-N,trace-f-t1-N} shows two multi-channel time slice. Figure \ref{fig:trace-f-t2-N} shows the time slice corresponding to time $t_2$ and Figure \ref{fig:trace-f-t1-N} shows the time slice of $t_1$. The 2D matrix in Figure \ref{fig:trace-f-t2-N} is equivalent to the numerator $A(t_2,x)e^{-\frac{\pi ft_2}{Q(x)}}$ in equation \ref{eq:spx} while the 2D matrix in Figure \ref{fig:trace-f-t1-N} corresponds to the denominator $A(t_1,x)e^{-\frac{\pi ft_2}{Q(x)}}$. In a vector form, Figure \ref{fig:trace-f-t2-N} corresponds to vector $\mathbf{a}$ in equation \ref{eq:opti} and Figure \ref{fig:trace-f-t1-N} denotes the vector $\mathbf{b}$ that constructs the diagonal matrix $\mathbf{B}$ in equation \ref{eq:opti}.

The calculated the spectral ratio is shown in Figure \ref{fig:trace-ratio-N}. Because of the two-dimensional smoothness contraint, the calculated spectral ratio is smooth on both axes and is not affected seriously by the random noise in the raw data. Figure \ref{fig:trace-lsfits} shows the predicted spectral ratio using the least-squares line-fitting. Figure \ref{fig:trace-coef-N} shows  the calculated slope ($B$ in equation \ref{eq:log}) of the fitted line.  Figure \ref{fig:trace-comp} shows the comparison of the estimated Q using single-channel and multi-channel methods, respectively. The blue line shows the exact Q that is used to generate the synthetic example. The red line shows the estimated Q using the proposed multi-channel Q estimation method. The pink line shows the estimated Q using the single-channel Q estimation method. The exact Q used for simulating the example is 60 and the estimated Q is very close to the exact Q and is almost spatially constant. However, due to the strong noise, the single-channel method obtains very unstable Q results, which are obviously not acceptable. In this example, we use a 5-point radius for the frequency direction smoothing and a 10-point radius for the space direction smoothing to obtain the result. We use the frequency range $f\in(20 \text{Hz},80 \text{Hz})$ for the least-squares line-fitting.

The second example with spatially varying Q is shown in Figure \ref{fig:linear-0,linear-15}. Figure \ref{fig:linears} shows the multi-channel seismic section. Figure \ref{fig:linear-15} shows a single trace extracted from the seismic section. In this example, the quality factor, Q, varies from 40 to 80 from left to right. The SNR of this example is -1.53 dB. The time-frequency cube using the S transform is shown in Figure \ref{fig:linear-st-N}. Figure \ref{fig:linear-f-t2-N,linear-f-t1-N} shows the two constant time slices. Figure \ref{fig:linear-f-t2-N} and \ref{fig:linear-f-t1-N} correspond to $t_2=0.8$ s and $t_1=0.5$ s, respectively. Figure \ref{fig:linear-ratio-N} displays the spectral ratio result using the proposed shaping regularization method, which is smooth along both frequency and space directions. Figure \ref{fig:linear-lsfits} shows the predicted spectral ratio using the least-squares line-fitting method. It is clear that the smoothness regularized spectral ratio is close to the predicted spectral ratio by least-squares line-fitting. Figure \ref{fig:linear-comp} shows a comparison of different estimated Q results. The pink line from the single-channel Q estimation is highly oscillating, while the estimated space-varying Q curve as denoted by the red line is very close to the exact Q curve denoted by the blue line. In this example, we use a 5-point radius for the frequency direction smoothing and a 15-point radius for the space direction smoothing to obtain the result. We use the frequency range $f\in(20\text{Hz},80 \text{Hz})$ for the least-squares line-fitting.

We then apply the proposed method to a real seismic data. The seismic section is shown in Figure \ref{fig:field-0}. It is clear that the field data is very noisy, not only containing strong random noise, but also corrupted by strong high-frequency linear noise. The highlighted area by the blue dashed lines and the frame box correspond to a hydrocarbon reservoir. We focus on studying the spatial variation of the quality factor in the reservoir area, which can provide insight on the viscosity and fluid property in this area. Figure \ref{fig:field-single} shows a single trace (first trace in the gather). Because of the strong noise and poor SNR of this dataset, it is difficult to distinguish between the reflections signals and noise in purely from the single trace.
Figure \ref{fig:field-st-N} shows the time-frequency cube of this example using the S transform. It is salient that the time-frequency maps help reveal the seismic events more clearly than the original amplitude profile. Figure \ref{fig:field-f-t2-N,field-f-t1-N} shows the two time-slices used for calculating the space-varying spectral ratio.  Figure \ref{fig:field-f-t2-N} corresponds to $t_2=1.18$ s and Figure \ref{fig:field-f-t1-N} corresponds to $t_1=0.71$ s. Figure \ref{fig:field-ratio-N} shows the spectral ratio using the proposed method. Figure \ref{fig:field-lsfits} shows the predicted spectral ratio by least-squares line-fitting. Figure \ref{fig:field-comp} shows the comparison of estimated space-varying Q using the single-channel method and the proposed multi-channel method. The red line corresponds to the single-channel method, which is highly unstable while the blue line corresponds the multi-channel method, which is much smoother. In this example, we use a 5-point radius for the frequency direction smoothing and a 10-point radius for the space direction smoothing to obtain the result. To alleviate the influence of high-frequency noise, we use a relatively narrower frequency range $f\in(20 \text{Hz},50 \text{Hz})$ for the least-squares line-fitting.

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.45\textwidth]{simple/Fig/traces}
    \label{fig:traces}}
   \subfloat[]{\includegraphics[width=0.435\textwidth]{simple/Fig/trace-15}
    \label{fig:trace-15}}
	\caption{The synthetic example. (a) The multi-channel seismic section with $\text{SNR}=-4.5$ dB. (b) The middle trace in (a).}
	\label{fig:traces,trace-15}
\end{figure}

\begin{figure}[htb!]
	\centering
	\includegraphics[width=\textwidth]{simple/Fig/trace-st-N}
	\caption{Time-frequency cube of the multi-channel seismic section. Note that although the time-frequency map of a single-trace is irregular, the time-frequency map along the position direction is coherent. }
	\label{fig:trace-st-N}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.6\textwidth]{simple/Fig/trace-f-t2-N}
    \label{fig:trace-f-t2-N}}\\
   \subfloat[]{\includegraphics[width=0.6\textwidth]{simple/Fig/trace-f-t1-N}
    \label{fig:trace-f-t1-N}}
	\caption{The multi-channel time slice of time $t_2$ (a) and time $t_1$ (b). In equation \ref{eq:spx}, (a) denotes the numerator and (b) denotes the denominator. In equation \ref{eq:opti}, (a) denotes the vector $\mathbf{a}$ and (b) denotes the vector $\mathbf{b}$.}
	\label{fig:trace-f-t2-N,trace-f-t1-N}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.6\textwidth]{simple/Fig/trace-ratio-N}
    \label{fig:trace-ratio-N}}\\
   \subfloat[]{\includegraphics[width=0.6\textwidth]{simple/Fig/trace-lsfits}
    \label{fig:trace-lsfits}}
	\caption{(a) The calculated spectral division. (b) The predicted spectral ratio via line fitting.}
	\label{fig:trace-ratio-N,trace-lsfits}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.5\textwidth]{simple/Fig/trace-coef-N}
    \label{fig:trace-coef-N}}\\
   \subfloat[]{\includegraphics[width=0.5\textwidth]{simple/Fig/trace-comp}
    \label{fig:trace-comp}}
	\caption{(a) The slope ($B$ in equation \ref{eq:log}) of the fitted line. (b) The estimated quality factor, compared with the result of single-channel method, and the exact solution. The blue line in (b) corresponds to the exact Q that is used to generate the synthetic data. The pink line denotes the estimated result using the single-channel method.  The blue line denotes the estimated Q using the proposed multi-channel method. Note that the estimated Q using the proposed method is very close to the exact solution while the Q estimated from the single-channel method is highly unstable. }
	\label{fig:trace-coef-N,trace-comp}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.45\textwidth]{var/Fig/linears}
    \label{fig:linears}}
   \subfloat[]{\includegraphics[width=0.435\textwidth]{var/Fig/linear-15}
    \label{fig:linear-15}}
	\caption{The synthetic data example  with spatially varying quality factor. (a) The multi-channel seismic profile with $\text{SNR}=-1.53$ dB. (b) The middle trace in (a).}
	\label{fig:linear-0,linear-15}
\end{figure}

\begin{figure}[htb!]
	\centering
	\includegraphics[width=\textwidth]{var/Fig/linear-st-N}
	\caption{Time-frequency cube of the synthetic example  with spatially varying quality factor. Note that the time-frequency map along the position direction is coherent. }
	\label{fig:linear-st-N}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.6\textwidth]{var/Fig/linear-f-t2-N}
    \label{fig:linear-f-t2-N}}\\
   \subfloat[]{\includegraphics[width=0.6\textwidth]{var/Fig/linear-f-t1-N}
    \label{fig:linear-f-t1-N}}
	\caption{The multi-channel time slice of time $t_2$ (a) and time $t_1$ (b) for the synthetic data example  with spatially varying quality factor. In equation \ref{eq:spx}, (a) denotes the numerator and (b) denotes the denominator. In equation \ref{eq:opti}, (a) denotes the vector $\mathbf{a}$ and (b) denotes the vector $\mathbf{b}$.}
	\label{fig:linear-f-t2-N,linear-f-t1-N}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.6\textwidth]{var/Fig/linear-ratio-N}
    \label{fig:linear-ratio-N}}\\
   \subfloat[]{\includegraphics[width=0.6\textwidth]{var/Fig/linear-lsfits}
    \label{fig:linear-lsfits}}
	\caption{Synthetic data example with spatially varying quality factor. (a) The calculated spectral division. (b) The predicted spectral ratio via line fitting.}
	\label{fig:linear-ratio-N,linear-lsfits}
\end{figure}

\begin{figure}[htb!]
	\centering
	\includegraphics[width=0.8\textwidth]{var/Fig/linear-comp}
	\caption{The estimated Q using the proposed multi-channel method compared with the single-channel method and the exact solution for the synthetic example with spatially varying quality factor. The blue line corresponds to the exact Q that is used to generate the synthetic data. The pink line denotes the estimated result using the single-channel method.  The red line denotes the estimated Q using the proposed multi-channel method. Note that the estimated Q using the proposed method is very close to the exact solution while the Q estimated from the single-channel method is highly unstable. }
	\label{fig:linear-comp}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.45\textwidth]{field/Fig/field-0}
    \label{fig:field-0}}
   \subfloat[]{\includegraphics[width=0.435\textwidth]{field/Fig/field-single}
    \label{fig:field-single}}
	\caption{The field data example. (a) The field seismic profile. (b) The first trace in (a).}
	\label{fig:field-0,field-single}
\end{figure}

\begin{figure}[htb!]
	\centering
	\includegraphics[width=\textwidth]{field/Fig/field-st-N}
	\caption{Time-frequency cube of the field seismic profile. Note that the time-frequency map along the position direction is coherent. }
	\label{fig:field-st-N}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.6\textwidth]{field/Fig/field-f-t2-N}
    \label{fig:field-f-t2-N}}\\
   \subfloat[]{\includegraphics[width=0.6\textwidth]{field/Fig/field-f-t1-N}
    \label{fig:field-f-t1-N}}
	\caption{The multi-channel time slice of time $t_2$ (a) and time $t_1$ (b) for the field data example. In equation \ref{eq:spx}, (a) denotes the numerator and (b) denotes the denominator. In equation \ref{eq:opti}, (a) denotes the vector $\mathbf{a}$ and (b) denotes the vector $\mathbf{b}$.}
	\label{fig:field-f-t2-N,field-f-t1-N}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.6\textwidth]{field/Fig/field-ratio-N}
    \label{fig:field-ratio-N}}\\
   \subfloat[]{\includegraphics[width=0.6\textwidth]{field/Fig/field-lsfits}
    \label{fig:field-lsfits}}
	\caption{Field data example. (a) The calculated spectral division. (b) The predicted spectral ratio via line fitting.}
	\label{fig:field-ratio-N,field-lsfits}
\end{figure}

\begin{figure}[htb!]
	\centering
	\includegraphics[width=0.8\textwidth]{field/Fig/field-comp}
	\caption{The estimated Q using the proposed multi-channel method compared with the single-channel method. The pink line denotes the estimated result using the single-channel method.  The red line denotes the estimated Q using the proposed multi-channel method. Note that the estimated Q using the proposed method is spatially smooth while the Q estimated from the single-channel method is highly oscillating. }
	\label{fig:field-comp}
\end{figure}

\section{Discussions}
The Q estimation problem is a long-standing problem and has been investigated extensively for several decades. However, it is the first time that a multi-channel method is proposed for estimating the quality factor from surface-recorded reflection seismic data. The main advantage of the proposed method is that it can be applied to the raw reflection seismic data directly without the need of denoising. Although the seismic data can be denoised first and be used to estimate the quality factor secondly, the reliability of the Q estimation heavily depends on the effectiveness of the denoising algorithm. Although a lot of denoising algorithm have been developed in the seismic community, because of the inappropriate parameter selection or inadequacy of denoising assumption, damage to the useful reflection signals is almost unavoidable \cite[]{yangkang2015ortho}. As long as the signal energy is damaged, the subsequent Q estimation that depends on the accuracy of signal amplitude cannot be convincing. Besides, separating the quality factor estimation into two steps in the traditional seismic data processing framework, i.e., denoising and Q estimation, is not elegant. By developing the multi-channel Q estimation algorithm, we make Q estimation an entity that only depends on the raw data itself. The independency of the proposed method from this perspective also makes it conveniently to be embeded into an automatic seismic data processing and inversion workflow.

Although robust in the presence of strong noise, as can be concluded from the field data example, it is still instructive to see how the result from the proposed method is compared with the result from denoised data in a single-channel framework. Comparing the denoising-based traditional processing framework and the denoising-free multi-channel Q estimation framework can also be informative to evaluate the reliability of the new algorithm. For the raw field data shown in Figure \ref{fig:field-0}, we use the state-of-the-art $f-x$ predictive filtering (or FX Decon) method \cite[]{canales1984} to remove the noise first. The denoised data is shown in Figure \ref{fig:field-dn}. Figure \ref{fig:field-dn-n} shows the removed noise from the raw data.
Comparing the denoised data in Figure \ref{fig:field-dn} and the raw data in Figure \ref{fig:field-0}, it is clear to see the huge improvement. However, it is also possible to see some leaked signal energy, especially around the time slice of 0.6 s and 0.7 s. Figure \ref{fig:field-dn-st-N} shows the time-frequency cube of the denoised field data. It is obvious that because of the removal of much random and coherent linear noise, the time-frequency cube of the denoised data becomes much clearer and smoother. Figure \ref{fig:field-dn-Q1s-esti} shows the estimated Q from the denoised data using the single-channel method. The axes on Figure \ref{fig:field-dn-Q1s-esti} are set the same as on Figure \ref{fig:field-comp} for a easier comparison. From Figure \ref{fig:field-dn-Q1s-esti} we observe that the estimated Q from the denoised data can be less oscillating compared with that from the raw data using the traditional single-channel framework. It indicates that the denoising step can indeed make the Q estimation more stable. However, the Q is still not continuous along the space direction and many abrupt changes in Q between neighbor channels still exist. It is surprising to see that the estimated Q from raw data using the new method and the estimated Q from denoised data using the traditional method are pretty close, indicating the fact that the new method can avoid a denoising step without much affecting the accuracy of the estimated Q.

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.45\textwidth]{field/Fig/field-dn}
    \label{fig:field-dn}}
   \subfloat[]{\includegraphics[width=0.45\textwidth]{field/Fig/field-dn-n}
    \label{fig:field-dn-n}}
	\caption{Denoising test. (a) Denoised field data using the $f-x$ predictive filtering method. (b) Removed noise using the $f-x$ predictive filtering method.}
	\label{fig:field-dn,field-dn-n}
\end{figure}

\begin{figure}[htb!]
	\centering
	\includegraphics[width=\textwidth]{field/Fig/field-dn-st-N}
	\caption{Time-frequency cube of the denoised field data. Note that the time-frequency map is much smoother than that from the raw data (Figure \ref{fig:field-st-N}). }
	\label{fig:field-dn-st-N}
\end{figure}

\begin{figure}[htb!]
	\centering
	\includegraphics[width=0.8\textwidth]{field/Fig/field-dn-Q1s-esti}
	\caption{The estimated Q from the denoised data using the single-channel method.}
	\label{fig:field-dn-Q1s-esti}
\end{figure}

To understand the computational complexity of the proposed multi-channel Q estimation method, we need to analyse its implementation in detail. The main computational steps in the multi-channel Q estimation method are the forward S transform, regularization spectral division, and least-squares line-fitting. Let the target multi-channel seismic section be of the size $N_tN_x$. When transformed into the time-frequency domain, the 3D time-frequency cube is of the size $N_fN_tN_x$. The number of iterations during the regularized spectral division is $N_{iter}$, which is normally less than 50. The smoothing radii for the frequency and space directions are $R_f$ and $R_x$, respectively. The computational cost of the typical forward S transform on the raw 2D seismic section is $O(N_xN_fN_t\log(N_t))$. With iterative solver, the inversion-based spectral division takes $O(N_{iter}N_fN_x+N_{iter}N_fR_f+N_{iter}N_xR_x)$, where the first term comes from the iterative conjugate gradient solver, and the latter two terms come from the smoothing regularization in the frequency and space directions. The least-squares line-fitting takes only $O(N_f)$. Overall, since normally the computational cost of the regularized spectral division is much smaller than that of the S transform, the main computational cost of the proposed algorithm framework comes from the forward S transform. The traditional single-channel Q estimation method differs with the regularized one only in the second step, i.e., the inversion-based spectral division. In traditional single channel method, the cost is $O(N_xN_f)$. In the case of single-channel regularized spectral division, the cost is $O(N_{iter}N_fN_x+N_{iter}N_fR_f)$, which is only smaller than the proposed multi-channel method by $O(N_{iter}N_xR_x)$. Considering that the smoothing radius in the proposed method is not chosen too large to avoid over-smoothing, the extra computational cost from the multi-channel method is not significant. In summary, the computational cost of the spectral ratio method is mainly from the S transform and improving the efficiency of the S transform is beneficial in increasing the efficiency of the overall algorithm framework.

\section{Conclusions}
Q estimation is highly affected when the noise is strong. We have proposed a novel multi-channel Q estimation algorithm based on the commonly used spectral ratio method. In order to deal with the spectral nulls, we formulate the spectral division as an inversion problem and solve it using the shaping regularization method with a smoothness constraint. In order to deal with the instability of the solution when the random noise is very strong, we propose to use an extra spatial smoothness constraint in the shaping regularization framework. The synthetic examples with spatially constant and varying Q demonstrate that the proposed method can obtain very accurate Q estimation results. The real seismic data example with strong noise demonstrates that the proposed method can help obtain stable Q estimation performance in the presence of high noise level.

\section{Acknowledgements}
The research is supported by the starting fund from Zhejiang University.

\bibliographystyle{seg}
\bibliography{q}

\newpage
\append{S transform}
For non-stationary data, time-frequency transforms are useful, as they can produce a spectral estimate centered at each time element of the data. In this respect, a 1D data trace is mapped into a 2D spectrogram, which has dimensions of time and frequency \cite[]{reine2009}. To introduce the S transform, we first briefly introduce the short-time Fourier transform (STFT).

The STFT is a Fourier-related transform used to determine the sinusoidal frequency and phase content of local sections of a signal as it changes over time
\begin{equation}
\label{eq:constft}
X_F(\tau,f)=\text{STFT}\{x(\tau)\}=\int_{-\infty}^{\infty}x(t)w(t-\tau)e^{-i2\pi ft}dt,
\end{equation}
where $f$ is the frequency, $\tau$ is a parameter that controls the position of the window function along the $t$ axis.

The STFT might be the most recognized time-frequency transform. It can be understood in such way that the data trace $x$ is gated by a sliding window function $w$, and the Fourier transform \cite[]{bracewell1978}. The sliding window function is commonly chosen as a Hanning window or Gaussian window.

When $w(t)$ is chosen as a Gaussian window function:
\begin{equation}
\label{eq:gauss}
w(t)=e^{-t^2/2\sigma^2},
\end{equation}
where $\sigma$ is the distribution width, the STFT transforms to the definition of Gabor transform \cite[]{carmona1998}.

The S transform was proposed by \cite{stockwell1996} as an extension to the Morlet wavelet transform. Instead of a fixed time length for each frequency in the window functions chosen for STFT, the S transform analyzes shorter data segments as the frequencies increase. Related with the Gaussian window function as shown in equation \ref{eq:gauss}, the distribution width $\sigma$ is substituted with:
\begin{equation}
\label{eq:inversesigma}
\sigma=\frac{1}{|f|}.
\end{equation}
Besides, the Gaussian window function used in the S transform is normalized with respect to the amplitude. Thus, the width of the Gaussian window scales inversely with frequency and amplitude scales linearly with the frequency:
\begin{equation}
\label{eq:Sgauss}
w(t,f)=\frac{|f|}{\sqrt{2\pi}}e^{-t^2f^2/2}.
\end{equation}
Combining equation \ref{eq:constft} with equation \ref{eq:Sgauss} we can obtain the definition of the S transform (ST):
\begin{equation}
\label{eq:strans}
X_S(\tau,f)=\text{ST}\{x(\tau)\}=\frac{|f|}{2\pi}\int_{-\infty}^{\infty}x(t)e^{-(t-\tau)^2f^2/2}e^{-i2\pi ft}dt.
\end{equation}
The S transform use a frequency-dependent window similar to that of wavelet transform, which allows a better resolution of low frequency components and enables a better time resolution of high frequency components.

\newpage
\listoffigures
\newpage

### 2020-09-16 qcomp/ieee_r1.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\title{Q-compensated denoising of seismic data}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Hang Wang, Guangtan Huang, Yangkang Chen, and Wei Chen
\thanks{H. Wang, G. Huang, Y. Chen are with Zhejiang University.}
\thanks{W. Chen is with Yangtze University (corresponding author).}
\thanks{The research is supported by the National Natural Science Foundation of China (Grant No. 41804140).}}
\maketitle

\begin{abstract}
It is widely known that strong noise can decrease the quality of seismic data. However, the anelastic attenuation could be more important to account for the weak amplitude and low quality of seismic data. Here, we develop an inversion framework to simultaneously compensate for the attenuation of seismic data and remove noise, thereby enhancing the quality of seismic data. Instead of directly applying a compensation operator to the input seismic data, we formulate an inverse problem that connects the sparse reflectivity model and the raw seismic data % that is attenuated and noisy 
via the convolution and attenuation functions. The random noise is assumed to be the unpredicted part \old{in}\new{of} the forward modeling process. We use the L2-norm regularization for the data misfit and impose a sparsity constraint onto the reflectivity series, e.g., using the L1-norm constraint. We use an iterative preconditioned conjugate gradient method to solve the L1-norm constrained least-squares optimization problem and obtain the  reflectivity series. The denoised and compensated data is obtained by applying the convolution operator to the reflectivity. We use several synthetic and field seismic data to illustrate the effectiveness of the presented method.
\end{abstract}

\begin{keywords}
Q-compensation, denoising, and seismic data
\end{keywords}

\section{Introduction}
Recovering the seismic signals from the strong background seismic noise, also known as seismic denoising, is of great importance of the whole seismic data processing chain \cite{yanan2014,yanhui2016,amir2017ieee,li2018multidimensional,wang2019hankel}.  There have been a lot of classic denoising algorithms in the literature, e.g., the prediction-based denoising methods \cite{canales1984,abma1995}, \new{the sparse transform based denoising methods \cite{fomel2010seislet,mostafa2016geo,mostafa2016bssa,mousavi2017automatic}}, the mode decomposition based denoising methods \cite{chenwei2012}, the rank-reduction based denoising methods \cite{mssa,weilin2016dmssa,zhaoqiang2019tgrs}, etc. Despite \old{of }the reported success in the field of seismic denoising, the traditional methods cannot resolve the problem of amplitude loss due to the anelastic attenuation when seismic waves are propagated in subsurface media. \new{The amplitude loss could make the recorded seismic data contain very weak events.} This limitation makes all traditional seismic denoising methods fail in dealing with highly attenuated seismic data, e.g., the weak seismic signals. What is worse is that due to the weak energy of those attenuated seismic events, the spatial correlation is also mitigated, thereby causing a high probability in damaging the weak events during the denoising process. \new{Besides, most denoising methods also affect the amplitude, thus causing a high chance that the attenuation estimation using denoised signal results in overestimation of the quality factor, Q.} In this paper, we will focus on the challenging problem of simultaneous denoising and attenuation compensation (Q-compensation). The goal is to develop an inversion framework that \old{can }not only \new{can} attenuate the random noise, but also compensate for the anelastic amplitude loss and thus increase the vertical resolution.

The anelastic attenuation is usually described by the quality factor (Q). Kjartansson (1979) \cite{kjartansson1979constant} proposed a constant Q-model, which describes an attenuation medium \cite{bickel1985plane,wang2002stable,shen2018q,shen2018q2}. In the constant Q-model, the quality factor does not vary with frequency \cite{braginsky1989quality,dai2012multi}. The estimation of Q is important in a variety of geophysical inverse problems, e.g., Q-compensated seismic migration, high-fidelity seismic interpretation, reservoir fluid characterization, and seismic risk estimation \cite{mousavi2014jgr,shank2018image,cheng2018q,jyothi2017seismic,luo2019q,chen2019multichannel}. Q-compensation, a widely used method to seismic imaging, is becoming a \old{heated}\new{hot} researching topic in exploration geophysics \cite{guo2017adjoint,zhou2019viscoacoustic,aharchaou2019prestack}. \new{Besides, Q can also be used to interpret the large-scale geological features \cite{zhao2018lateral}.}

Reverse time migration (RTM) is thought as one of the most effective seismic imaging methods \cite{baysal1983reverse,yoon2004challenges,dai2012multi}. In recent years, Q-compensation research for different forms of reverse time migration has emerged. \cite{zhang2010compensating} proposed a Q-compensated RTM, where a \old{viscoelastic}\new{viscoacoustic} wave equation is used for compensating amplitude attenuation and phase dispersion effects.  Researchers also used the separated fractional Laplace equation to approximate the constant-Q wave equation for viscous acoustic medium modeling and imaging tasks \cite{zhu2014q,fathalian2020approach}, which plays an important role in effectively using constant-Q in data processing \cite{harris2014q,wang2018adaptive}.\old{ The viscoelastic least-square inverse time migration (also known as Q-LSRTM) is a linear inversion of \new{a} subsurface reflectance model from lossy data ?. Compared with the traditional migration method, it could compensate for the amplitude loss of the migration image caused by the strong underground attenuation, and can produce the reflector accurately located at the depth. Researchers have developed different algorithms and demonstrate the Q-LSRTM method converges significantly faster than least-square reserve time migration ?.} Q-compensation can be utilized in full waveform inversion (FWI) as well. FWI provides a reliable method for the establishment of \new{a} high-resolution underground model, especially for the construction of \new{a} complex geological structure model, which has been \old{fully}\new{extensively} studied\old{ and developed} in the past decades \cite{tarantola2005inverse,virieux2009overview}. Q-compensated FWI has been proved to be highly effective \new{for building a reliable subsurface velocity model} \cite{xue2018accelerating}. \old{By comparing the convergence rates of FWI with Q-compensated gradient and without Q-compensated gradient, we can know that the Q-compensation strategy can obviously improve the convergence of FWI, which is helpful for the fast inversion of \new{the} deep structure of velocity model ?. \old{However, attenuation reconstruction is always an ill-posed problem. Because the reliability of attenuation reconstruction depends on the precision of \new{the} initial velocity model to a great extent, FWI has the advantages of being more robust and stable, but the calculation cost is very high ?.} ? proposed a ray based Q-tomography, which can be incorporated into the traditional depth velocity modeling process. In order to compensate for the attenuation in RTM and FWI imaging, it is necessary to estimate the spatial change rate of attenuation from the dataset. Q-tomography based on frequency shift data is very useful in estimating the uniform attenuation rate ?.}

%Q-compensation can be utilized in full waveform inversion (FWI) as well. FWI provides a reliable method for the establishment of \new{a} high-resolution underground model, especially for the construction of \new{a} complex geological structure model, which has been \old{fully}\new{extensively} studied\old{ and developed} in the past decades \cite{tarantola2005inverse,virieux2009overview}. Q-compensated FWI has been proved to be highly effective \new{for building a reliable subsurface velocity model} \cite{xue2017visco,xue2018accelerating}. By comparing the convergence rates of FWI with Q-compensated gradient and without Q-compensated gradient, we can know that the Q-compensation strategy can obviously improve the convergence of FWI, which is helpful for the fast inversion of \new{the} deep structure of velocity model \cite{alasmri2019towards,li2016application,xue2016q,wang2019q}. \old{However, attenuation reconstruction is always an ill-posed problem. Because the reliability of attenuation reconstruction depends on the precision of \new{the} initial velocity model to a great extent, FWI has the advantages of being more robust and stable, but the calculation cost is very high ?.} \cite{xin20093} proposed a ray based Q-tomography, which can be incorporated into the traditional depth velocity modeling process. In order to compensate for the attenuation in RTM and FWI imaging, it is necessary to estimate the spatial change rate of attenuation from the dataset. Q-tomography based on frequency shift data is very useful in estimating the uniform attenuation rate \cite{harris2014q,he2012q,xin2014robust}.

\old{Furthermore, Q-compensation is useful for non-linear reconstruction of seismic reflection data, which has been proved for its the concept and numerical feasibility, and also with more robustness ?. What is more, Q-compensation technology could contribute to tomography for complex near-surface condition. Since the Q-compensation strategy can significantly boost the energy that is lost due to the attenuation of the high-frequency components in the shallow to middle layers ?.} \new{While the Q-compensation problem has been extensively studied in either an independent processing step or in the wave-equation based imaging step via RTM and FWI, it is seldom investigated in conjuction with the seismic denoising process. As we know, seismic attenuation affects the seismic denoising since it could extra-weak seismic reflections while denoising also affects Q compensation greatly because denoising could weaken the seismic signals that are closely related with the Q estimation. Here, we propose an integrated framework for simultaneously denoising and Q compensation. } In this paper, we will start from the basic convolution model and then introduce the forward operator in the frequency domain that incorporates the anelastic attenuation. We will introduce a preconditioned conjugate gradient method to solve for the Q-compensated reflectivity inversion, after which we can obtain the Q-compensated amplitude recovery with the random noise simultaneously removed.

\subsection{Convolution model with anelastic attenuation}
The convolution model is well known as:
\begin{equation}
\label{eq:conv}
\mathbf{d} = \mathbf{Wr},
\end{equation}
where $\mathbf{d}$ denotes the seismic data, $\mathbf{W}$ denotes the convolution matrix that is composed of the source wavelet $\mathbf{w}$, and $\mathbf{r}$ denotes the reflectivity. When considering the subsurface seismic anelastic attenuation, the convolution model \ref{eq:conv} can be modified as:
\begin{equation}
\label{eq:conva}
\mathbf{d} = \mathbf{WAr},
\end{equation}
where $\mathbf{A}$ denotes the attenuation operator. In an integral form, equation \ref{eq:conva} can be expressed as \cite{margrave2011gabor,yufeng2018l12}:
\begin{equation}
\label{eq:int}
d(\omega) = w(\omega) \int r(t)a(\omega,t)e^{-i\omega t}dt,
\end{equation}
where $d(\omega)$ and $w(\omega)$ denote the spectrum of the seismic data $d(t)$ and wavelet function $w(t)$ in the frequency domain, respectively. $a(\omega,t)$ corresponds to an attenuation function. $r(t)$ is the reflectivity function in the time domain. The attenuation function can be defined based on the constant-Q theory as follows \cite{zhu2014q,yufeng2018l12}:
\begin{equation}
\label{eq:af}
a(\omega, t) = e^{-\frac{\omega t}{2Q}\left | \frac{\omega}{\omega_h} \right |^{-\gamma}}e^{i \omega t \left | \frac{\omega}{\omega_h} \right |^{-\gamma}},
\end{equation}
where $\gamma=\frac{1}{\pi Q}$, and $\omega_h$ is a reference frequency \new{e.g., 30 Hz}.

According to equation \ref{eq:int}, the explicit expression of equation \ref{eq:conva} can be written as:
\begin{equation}
\label{eq:exp}
\begin{split}
&\left[ \begin{array}{ccc}
e^{-i \omega_1 t_1}w(\omega_1)a(\omega_1, t_1) & \ldots & e^{-i \omega_1 t_N}w(\omega_1)a(\omega_1, t_N) \\
\vdots & \ddots & \vdots \\
e^{-i \omega_M t_1}w(\omega_M)a(\omega_M, t_1) & \ldots & e^{-i \omega_M t_N}w(\omega_M)a(\omega_M, t_N)
\end{array} \right] \\
&\left[\begin{array}{c} r_1 \\ \vdots \\ r_N \end{array} \right] = \left[\begin{array}{c} d(\omega_1) \\ \vdots \\ d(\omega_M) \end{array} \right] .
\end{split}
\end{equation}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-dc}
   \label{fig:syn-dc}}\\
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-da}
   \label{fig:syn-da}}
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-dn}
   \label{fig:syn-dn}}
  \caption{Synthetic data example. \old{(a) Clean data. (b) Noisy data with attenuated amplitude. (c) Enhanced data using fx method. (d) Enhanced data using the proposed method.}\new{(a) Clean data. (b) Clean data with attenuated amplitude. (c) Noisy data with attenuated amplitude.}}
  \label{fig:syn-dc,syn-da,syn-dn}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d2}
   \label{fig:syn-d2}}
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d1}
   \label{fig:syn-d1}}
  \caption{Synthetic data example. (a) Denoised data using FX method. (d) Q-compensated and denoised data using the proposed method.}
  \label{fig:syn-d2,syn-d1}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-da-simi}
   \label{fig:syn-da-simi}}
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-dn-simi}
   \label{fig:syn-dn-simi}}\\
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d2-simi}
   \label{fig:syn-d2-simi}}
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d1-simi}
   \label{fig:syn-d1-simi}}
  \caption{Similarity comparison between the target data and the ground truth for (a) attenuated data, (b) noisy data, (c) denoised data using FX method, and (d) the proposed method.}
  \label{fig:syn-da-simi,syn-dn-simi,syn-d2-simi,syn-d1-simi}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.5\textwidth]{synth/Fig/syn-ss0}
   \label{fig:syn-ss0}}
 \subfigure[]{\includegraphics[width=0.5\textwidth]{synth/Fig/syn-ss-z}
   \label{fig:syn-ss-z}}
  \caption{Trace-by-trace (3rd trace in Figs. \ref{fig:syn-dc,syn-da,syn-dn} and \ref{fig:syn-d2,syn-d1}) comparison for the synthetic data example, in the original scale (a), and in the zoomed scale (b). The red line denotes the clean attenuated data. The pink line corresponds to the noisy attenuated data. The green line corresponds to the Q-compensated denoising method. The blue line corresponds to the FX method.  The black line corresponds to the ground truth. It is clear that the black and green lines are close to each other.}
  \label{fig:syn-ss0,syn-ss-z}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-dn-0}
   \label{fig:real-dn-0}}\\
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d2-0}
   \label{fig:real-d2-0}}
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d1-0}
   \label{fig:real-d1-0}}   
  \caption{Field data example. (a) Raw data. (b) Enhanced data using fx method. (c) Enhanced data using the proposed method.}
  \label{fig:real-dn-0,real-d2-0,real-d1-0}
\end{figure}

\subsection{Q-compensated seismic denoising}
%The nonstationary convolution in the frequency domain, we can solve the following optimization problem for the sparse reflectivity. 
Let $\mathbf{F}=\mathbf{WA}$, then equations \ref{eq:conva} and \ref{eq:exp} can be briefly expressed as
\begin{equation}
\label{eq:inv}
\mathbf{d} = \mathbf{Fr},
\end{equation}
which can be solved via the regularized optimization method
\begin{equation}
\label{eq:cost1}
\hat{\mathbf{r}} = \arg \min_{\mathbf{r}} \ \frac{1}{2} \parallel \mathbf{F} \mathbf{r}-\mathbf{d}\parallel_2^2+ \lambda \parallel\mathbf{r}\parallel_1,
\end{equation}
where $\parallel\cdot \parallel_2$ denotes the $L_2$-norm data misfit and $\parallel\cdot \parallel_1$ denotes the $L_1$-norm model constraint. $\lambda$ denotes a the compromising parameter that controls the weight between the data misfit and model constraint.

Note that 
\begin{equation}
\label{eq:l1l2}
\parallel \mathbf{r} \parallel_1 = \sum_{i} |r_i| =  \sum_{i} |r_i| |r_i|^{-1} |r_i| = \parallel \mathbf{W}_r\mathbf{r} \parallel_2^2,
\end{equation}
where $[\mathbf{W}_r]_{ii}=|r_i|^{-1/2}$. To avoid the singularity caused by too small $r_i$, a threshold needs to be defined \cite{amr2014}.

Substituting equation \ref{eq:l1l2} into equation \ref{eq:cost1}, we obtain
\begin{equation}
\label{eq:cost2}
\hat{\mathbf{r}} = \arg \min_{\mathbf{r}} \ \frac{1}{2} \parallel \mathbf{F} \mathbf{r}-\mathbf{d}\parallel_2^2+ \lambda \parallel \mathbf{W}_r\mathbf{r} \parallel_2^2,
\end{equation}
which can then be transformed as
\begin{equation}
\label{eq:cost2}
\hat{\mathbf{m}} = \arg \min_{\mathbf{m}} \ \frac{1}{2} \parallel \mathbf{F} \mathbf{W}_r^{-1}\mathbf{m}-\mathbf{d}\parallel_2^2+ \lambda \parallel \mathbf{m} \parallel_2^2,
\end{equation}
by defining $\mathbf{r}=\mathbf{W}_r^{-1}\mathbf{m}$.

Equation \ref{eq:cost2} can be solved via the classic conjugate gradient method. In summary, when solving equation \ref{eq:cost1}, we need to iteratively solve for $\mathbf{m}$ and $\mathbf{W}_r$. $\mathbf{W}_r$ needs to be re-calculated during the iterations. \new{Following Daniel (2003) \cite{daniel2003}}, we ease the inconvenience in selecting the balancing parameter $\lambda$ by adjusting the sparsity constraint through the number of re-weighting iterations. A higher number of re-weighting iterations corresponds to a higher trade-off parameter $\lambda$ and vice versa. The detailed preconditioned conjugate gradient algorithm to solve equation \ref{eq:cost1} is provided in Algorithm \ref{alg:alg1}, where the input are the forward operator $\mathbf{F}$, raw data $\mathbf{d}$, and initial guess of $\mathbf{m}_0$, inner and outer iterations $N_i$ and $N_o$. When the  reflectivity $\hat{\mathbf{r}}=\mathbf{r}_{N_i}$ is solved through algorithm \ref{alg:alg1}, the Q-compensated and denoised data can be obtained by $\hat{\mathbf{s}} = \mathbf{W}\hat{\mathbf{r}}$.

\new{The proposed method is based on 1D assumption, which means that we need to apply the Q-compensation algorithm in post-stack data. Besides, in this paper, we do not seek a theoretically correct Q-compensation result. Instead, we seek an improved version of denoising, where the Q effect is taken into consideration. Also, we demonstrate that even thorough a roughly assumed constant Q value, we can obtain significant improvement of the SNR and resolution of the result, as detailed in the next section. }
\begin{algorithm}
   \caption{Iterative preconditioned conjugate gradient algorithm}
   \textbf{Input:} $\mathbf{d}$,$\mathbf{m}_0$,$N_o$,$N_i$,$\mathbf{F}$ \\
   \textbf{Output:} $\hat{\mathbf{r}}$ 
    \begin{algorithmic}[1]
    \State $\mathbf{W}_r=\mathbf{I}$
    \State $\mathbf{r}_0=\mathbf{W}_r\mathbf{m}_0$ 
    \For {$t = 1:N_o$}
    \State $\mathbf{r}_0=\mathbf{d}-\mathbf{F}\mathbf{W}_r\mathbf{m}_0$
    \State $\mathbf{W}_r=\text{diag}(\mathbf{r}_0^{1/2})$
    \State $\mathbf{p}_0=\mathbf{W}_r^T\mathbf{F}^T\mathbf{r}_0$;$\quad$$\mathbf{p}_1=\mathbf{p}_0$ 
    \State $\mathbf{u}_0=\mathbf{p}_0$;$\quad$$\mathbf{u}_1=\mathbf{u}_0$ 
    \For {$k = 1:N_i$}
    \State $\mathbf{q}_{N_i}=\mathbf{F}\mathbf{W}_r\mathbf{u}_{N_i}$
    \State $\alpha=\mathbf{p}_{N_i}^T\mathbf{p}_{N_i}/\mathbf{q}_{N_i}^T\mathbf{q}_{N_i}$
    \State $\mathbf{m}_{N_i}=\mathbf{m}_{k-1}+\alpha\mathbf{p}_{N_i}$
    \State $\mathbf{r}_{N_i}=\mathbf{r}_{k-1}-\alpha\mathbf{q}_{N_i}$ 
    \State $\mathbf{p}_{N_i}=\mathbf{W}_r^T\mathbf{F}^T\mathbf{r}_{N_i}$
    \State $\beta=\mathbf{r}^T_{k}\mathbf{r}_{k}/\mathbf{r}^T_{k-1}\mathbf{r}_{k-1}$ 
    \State $\mathbf{u}_{N_i}=\mathbf{p}_{N_i}+\beta\mathbf{u}_{N_i}$
%    \If {$\textbf{w}(k)==1$}%\\
%    \% Selected multi-scale components.
%    \State $\textbf{C} \leftarrow diag(\textbf{c}\{k+1\})$
%    \EndIf
    \EndFor
    \State $\mathbf{r}_{N_i}=\mathbf{W}_r\mathbf{m}_{N_i}$;
    \State $\mathbf{r}_0=\mathbf{r}_{N_i}$;$\quad$ $\mathbf{m}_0=\mathbf{m}_{N_i}$
    \EndFor
    \State $\hat{\mathbf{r}}=\mathbf{r}_{N_i}$ 
\end{algorithmic}
\label{alg:alg1}
\end{algorithm}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-dn-z1}
   \label{fig:real-dn-z1}}\\
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d2-z1}
   \label{fig:real-d2-z1}}
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d1-z1}
   \label{fig:real-d1-z1}}   
  \caption{Zoomed comparison for the field data example (corresponding to the pink boxes in Fig. \ref{fig:real-dn-0,real-d2-0,real-d1-0}). (a) Raw data. (b) Enhanced data using fx method. (c) Enhanced data using the proposed method.}
  \label{fig:real-dn-z1,real-d2-z1,real-d1-z1}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-dn-z2}
   \label{fig:real-dn-z2}}\\
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d2-z2}
   \label{fig:real-d2-z2}} 
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d1-z2}
   \label{fig:real-d1-z2}}   
  \caption{Zoomed comparison for the field data example (corresponding to the red boxes in Fig. \ref{fig:real-dn-0,real-d2-0,real-d1-0}). (a) Raw data. (b) Enhanced data using fx method. (c) Enhanced data using the proposed method (Q=50).}
  \label{fig:real-dn-z2,real-d2-z2,real-d1-z2}
\end{figure}

\begin{figure*}[ht!]
 \centering
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q60-0}
   \label{fig:real-d1-q60-0}}
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q70-0}
   \label{fig:real-d1-q70-0}}   
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q80-0}
   \label{fig:real-d1-q80-0}}  \\
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q90-0}
   \label{fig:real-d1-q90-0}}
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q100-0}
   \label{fig:real-d1-q100-0}}   
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q120-0}
   \label{fig:real-d1-q120-0}}   
  \caption{Field data example with different Q. (a) Q=60. (b) Q=70. (c) Q=80. (d) Q=90. (e) Q=100. (f) Q=120. The areas highlighted by the frame boxes is zoomed in Fig. \ref{fig:real-d1-q60-z1,real-d1-q70-z1,real-d1-q80-z1,real-d1-q90-z1,real-d1-q100-z1,real-d1-q120-z1}.}
  \label{fig:real-d1-q60-0,real-d1-q70-0,real-d1-q80-0,real-d1-q90-0,real-d1-q100-0,real-d1-q120-0}
\end{figure*}

\begin{figure*}[ht!]
 \centering
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q60-z1}
   \label{fig:real-d1-q60-z1}}
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q70-z1}
   \label{fig:real-d1-q70-z1}}   
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q80-z1}
   \label{fig:real-d1-q80-z1}}  \\
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q90-z1}
   \label{fig:real-d1-q90-z1}}
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q100-z1}
   \label{fig:real-d1-q100-z1}}   
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q120-z1}
   \label{fig:real-d1-q120-z1}}   
  \caption{Zoomed comparison of the field data example with different Q. (a) Q=60. (b) Q=70. (c) Q=80. (d) Q=90. (e) Q=100. (f) Q=120.}
  \label{fig:real-d1-q60-z1,real-d1-q70-z1,real-d1-q80-z1,real-d1-q90-z1,real-d1-q100-z1,real-d1-q120-z1}
\end{figure*}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.23\textwidth]{Fig/real3}
   \label{fig:real3}}\\
 \subfigure[]{\includegraphics[width=0.23\textwidth]{Fig/real3-d2}
   \label{fig:real3-d2}}   
 \subfigure[]{\includegraphics[width=0.23\textwidth]{Fig/real3-d1}
   \label{fig:real3-d1}}   
  \caption{3D seismic data example. (a) Raw data. (b) Denoised data using the FX method. (c) Q-compensated and denoised data using the proposed method.}
  \label{fig:real3,real3-d2,real3-d1}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.23\textwidth]{Fig/real3-z}
   \label{fig:real3-z}}\\
 \subfigure[]{\includegraphics[width=0.23\textwidth]{Fig/real3-d2-z}
   \label{fig:real3-d2-z}}   
 \subfigure[]{\includegraphics[width=0.23\textwidth]{Fig/real3-d1-z}
   \label{fig:real3-d1-z}}   
  \caption{Zoomed comparison of the 3D seismic data example. (a) Raw data. (b) Denoised data using the FX method. (c) Q-compensated and denoised data using the proposed method.}
  \label{fig:real3-z,real3-d2-z,real3-d1-z}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.33\textwidth]{Fig/real3-s-0}
   \label{fig:real3-s-0}}\\
 \subfigure[]{\includegraphics[width=0.33\textwidth]{Fig/real3-d2-s-0}
   \label{fig:real3-d2-s-0}} \\  
 \subfigure[]{\includegraphics[width=0.33\textwidth]{Fig/real3-d1-s-0}
   \label{fig:real3-d1-s-0}}   
  \caption{Constant-time ($t=0.4s$) comparison of the 3D seismic data example. (a) Raw data. (b) Denoised data using the FX method. (c) Q-compensated and denoised data using the proposed method.}
  \label{fig:real3-s-0,real3-d2-s-0,real3-d1-s-0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.5\textwidth]{Fig/real3-traces-0}}
\caption{\new{Trace-by-trace comparison (middle traces of the zoomed seismic cubes in Fig. \ref{fig:real3-z,real3-d2-z,real3-d1-z}). Black denotes the raw data. Pink denotes the FX method. Cyan denotes the proposed method. Note the obviously enhanced resolution.} }
\label{fig:real3-traces-0}
\end{figure}

\section{Examples}
We use several datasets to show the performance of the new Q-compensated denoising method, including a synthetic and two field data examples. First, the synthetic example is shown in Fig. \ref{fig:syn-dc}, which is a clean seismic section containing several linear events. Some of the events are crossing each other. We apply a forward attenuating operator ($\mathbf{A}$) introduced above with $Q=50$ to the clean seismic section, and show the attenuated data in Fig. \ref{fig:syn-da}. The wavelet we use here is a Ricker wavelet with 30 Hz dominant frequency. The deep seismic signals are of very weak amplitude due to the attenuation. We then add some band-limited random noise into the attenuated data and show the noisy and attenuated data in Fig. \ref{fig:syn-dn}. We apply the FX method \cite{canales1984} and the proposed signal enhancing method to the noisy and attenuated data, and then show the results in Fig. \ref{fig:syn-d2,syn-d1}.

As can be seen from Fig. \ref{fig:syn-d2,syn-d1}, the FX method can suppress some random noise but cannot recover the amplitude loss. What is worse is that the FX method almost removes all the weak signals around 1.5s. The proposed method, however, can obtain an almost correct result with amplitude compensated and noise removed. The recovered seismic signals are very close to the ground-truth solution shown in Fig. \ref{fig:syn-dc}. To evaluate the denoising and Q-compensation performance, we use the local similarity metric \cite{fomel2007localattr,yangkang2015ortho}. We calculate the local similarity between the ground-truth solution (Fig. \ref{fig:syn-dc}) and all other data in Figs. \ref{fig:syn-dc,syn-da,syn-dn} and \ref{fig:syn-d2,syn-d1}. A higher local similarity value indicates a higher quality of the data to be evaluated since the signals are more similar to the ground-truth signals. The local similarity maps are plotted in Fig. \ref{fig:syn-da-simi,syn-dn-simi,syn-d2-simi,syn-d1-simi}. The local similarity comparison clearly shows that the proposed method obtains obviously higher local similarity values, and thus the proposed method obtains a very accurate recovery of the seismic signals. We then extract a single trace (the 3rd trace) from each seismic sections from Figs. \ref{fig:syn-dc,syn-da,syn-dn} and \ref{fig:syn-d2,syn-d1} and plot them in Fig. \ref{fig:syn-ss0,syn-ss-z}. Fig. \ref{fig:syn-ss0} plots the trace-by-trace comparison in the original scale, where the ground-truth solution is denoted by the black line. The red line denotes the clean attenuated data. The pink line corresponds to the noisy attenuated data.  The green line corresponds to the proposed Q-compensated denoising method. The blue line corresponds to the FX method. It is clear that the black and green lines are almost overlapping, indicating an excellent amplitude recovery performance. We zoom a waveform and show the comparison in Fig. \ref{fig:syn-ss-z}. The zooming part is stressed by the cyan frame box in Fig. \ref{fig:syn-ss0}.

The first field data example is a 2D section, as shown in Fig. \ref{fig:real-dn-0}. The seismic data contains several representative features, e.g., many fault structures in the shallow area and some highly dipping structures in the deep area probably caused by abrupt uplifting of deep stratas. However, due to \new{the} strong random noise and existence of the wave attenuation phenomenon, the seismic events are highly discontinuous, affecting the interpretation challenges in this geological area.  Traditionally, we apply a denoising operator to the raw seismic data and obtain an improved seismic section. For example, we can apply the FX method to the raw data and obtain the denoised data shown in Fig. \ref{fig:real-d2-0}. The seismic events become more continuous but still have some sporadic weak-amplitude patterns which are caused by the strong wave attenuation. We apply the proposed Q-compensated denoising method to the raw data and obtain a much improved section, as shown in Fig. \ref{fig:real-d1-0}. It is clear that the amplitude loss is recovered well and the signal-to-noise ratio is increased dramatically. In this field data test, we assume a constant $Q=50$ for the convenient processing. For a better comparison, we zoomed two parts from each sub-figure in Fig. \ref{fig:real-dn-0,real-d2-0,real-d1-0}.  The zooming sections highlighted by the pink frame box are plotted in Fig. \ref{fig:real-dn-z1,real-d2-z1,real-d1-z1}. It becomes very clear that the proposed approach can obtain a good amplitude recovery and denoising. The seismic events become obviously continuous and the fault structures become very clearly depicted. Because of the Q-compensation, the resolution of the processed data is also dramatically enhanced, which is beneficial to interpret the thin-bed structures. Another area that is stressed using the red rectangles in Fig. \ref{fig:real-dn-0,real-d2-0,real-d1-0} is zoomed and compared in Fig. \ref{fig:real-dn-z2,real-d2-z2,real-d1-z2}. It is more obvious that some thin layers that have \new{a} very weak amplitude in the raw seismic data have been revealed clearly after the Q-compensated and denoising processing, e.g., in areas around 2.4 sec and between 200th and 250th traces. To evaluate the influence of different Q values to the result, we use six different Qs, i.e., Q=60, 70, 80, 90, 100, and 120, to process the data based on the same aforementioned framework, and show the results in Fig. \ref{fig:real-d1-q60-0,real-d1-q70-0,real-d1-q80-0,real-d1-q90-0,real-d1-q100-0,real-d1-q120-0}. For a better view, we zoom the area pointed out by the pink frame boxes and show the comparison in Fig. \ref{fig:real-d1-q60-z1,real-d1-q70-z1,real-d1-q80-z1,real-d1-q90-z1,real-d1-q100-z1,real-d1-q120-z1}. It is obvious that as Q increases, the amplitude compensation effect becomes weaker, and the seismic events become less continuous. It is easy to infer that as Q becomes very large, there is little effect on improving the quality of the seismic data. According to our experience, when Q becomes very small, e.g., less than 40, the proposed method is more likely to cause instability due to much boosted noise energy.  In practice, we are recommending starting tuning the proposed algorithm with Q=50, and then gradually increase the Q value to see which result best serves the geological interpretation.

Finally, we use a 3D seismic dataset to demonstrate the proposed method. Fig. \ref{fig:real3} demonstrates the raw seismic data. Fig. \ref{fig:real3-d2} shows the result from \old{a}\new{the} FX method. For simplicity, we only use the 2D version of the predictive filtering method to denoise this data, i.e., process the data in a 2D section. Although the simple denoising method can attenuate some random noise, it cannot compensate for the amplitude loss due to seismic attenuation. The amplitude of the deep area is still weak. We apply the proposed Q-compensated denoising method to the raw data and show the result in Fig. \ref{fig:real3-d1}. The amplitude of the deep areas \old{have}\new{has} been enhanced significantly. We zoomed a 3D cube from each dataset in the original scale and show the comparison in Fig. \ref{fig:real3-z,real3-d2-z,real3-d1-z}, where we can better see that the proposed method not only suppress random noise, but also compensate for the amplitude loss and enhance the vertical resolution.  We also extract a constant-time slice of $t=0.4$s from each dataset in Fig. \ref{fig:real3,real3-d2,real3-d1} and show the comparison in Fig. \ref{fig:real3-s-0,real3-d2-s-0,real3-d1-s-0}. It is clear that the proposed method \old{unveil}\new{unveils} several hidden signals from the raw data thanks to the Q compensation, as indicated by the arrows \new{in Fig. \ref{fig:real3-d1-s-0}}.  \new{A trace-by-trace comparison is plotted in Fig. \ref{fig:real3-traces-0}, where the black line denotes the raw data. The pink line corresponds to the result from the FX method. The cyan line corresponds to the proposed method. It is clear that the proposed method significantly enhance the resolution. }

%\section{Discussions}
\section{Conclusions}
Both seismic noise and seismic attenuation can cause the low-quality issue of many reflection seismic data. We have introduced an inversion framework to simultaneously remove seismic noise and compensate for the amplitude absorption and phase distortion, thereby enhancing the resolution and signal-to-noise ratio (SNR) of the seismic data. We theoretically introduce the forward operator in the inverse problem, and use the L1-norm constrained optimization problem to solve the inverse problem. A preconditioned conjugate gradient method is used to solve the optimization problem with superb performance. \new{Due to the inversion process, the computational cost of the proposed method is higher than a traditional denoising algorithm. However, the computational complexity can be controlled by the numbers of inner and outer iterations, i.e., $N_i$ and $N_o$. Since the attenuation compensation could boost the high-frequency energy, thus it could be more sensitive to the noise levels than a standard denoising algorithm.} All synthetic, 2D and 3D real post-stack seismic data containing strong random noise are tested with the proposed method to demonstrate its validity in industrial applications.

%\inputdir{synth}
%%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
%\multiplot{3}{syn-dc,syn-da,syn-dn}{width=0.4\textwidth}{Synthetic data example. (a) Clean data. (b) Noisy data with attenuated amplitude. (c) Enhanced data using fx method. (d) Enhanced data using the proposed method.}
%

%\section{Discussions}
%\section{Conclusions}
%\section{Acknowledgements}

\bibliographystyle{IEEEtran}
\bibliography{q}

%\begin{figure}[htb!]
%	\centering
%	\subfigure[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
%	\caption{Caption.}
%	\label{fig:fig}
%\end{figure}

%\begin{figure*}[ht!]
%  \centering
%  \subfigure[]{\includegraphics[width=0.45\textwidth]{path/Fig/fig1}
%    \label{fig:fig1}}
%  \subfigure[]{\includegraphics[width=0.35\textwidth]{path/Fig/fig2}
%    \label{fig:fig2}}    
%   \caption{caption goes here}
%   \label{fig:fig1,fig2}
%\end{figure*}

%\begin{table}[h]
%\caption{Table caption}
%\begin{center}
%     \begin{tabular}{|c|c|c|c|c|c|} 
%	  \hline Column1 (unit)  & Column2 (unit) & Column3 (unit) \\ 
%	  \hline 1 & 2  & 3 \\
%       \hline
%    \end{tabular} 
%\end{center}
%\label{tbl:table1}
%\end{table}

### 2020-09-16 qrtm/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{Geophysics, 84(1), F1-F15, (2019)}

\title{CuQ-RTM: A CUDA-based code package for stable and efficient Q-compensated reverse time migration}
\author{Yangkang Chen}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\author{Yufeng Wang\footnotemark[1], Hui Zhou\footnotemark[1], Xuebin Zhao\footnotemark[1], Qingchen Zhang\footnotemark[2], Poru Zhao\footnotemark[3], Xiance Yu\footnotemark[3], and Yangkang Chen\footnotemark[4]}

%\ms{GJI-2019}

\address{
\footnotemark[1] State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
\footnotemark[2]Research Center for Computational and Exploration Geophysics\\
 State Key Laboratory of Geodesy and Earth’s Dynamics\\
  Institute of Geodesy and Geophysics\\
   Chinese Academy of Sciences\\
    Wuhan, Hubei Province, China, 430077\\
%qczh@whigg.ac.cn \\
\footnotemark[3]
China National Petroleum Corporation\\
Beijing, China. \\
%zpru@hotmail.com; xiance\_yu@hotmail.com.  \\
\footnotemark[4]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
yangkang.chen@zju.edu.cn 
}

\lefthead{Wang et al, 2019}
\righthead{CUDA-based Q-RTM}

\begin{abstract}
Reverse time migration (RTM) in attenuating media should take the absorption and dispersion effects into consideration. The latest proposed viscoacoustic wave equation with decoupled fractional Laplacians (DFLs) facilitates separate amplitude compensation and phase correction in $Q$-compensated RTM ($Q$-RTM). However, intensive computation and enormous storage requirements of $Q$-RTM prevent it from being extended into practical application, especially for large-scale 2D or 3D case. The emerging graphics processing unit (GPU) computing technology, built around a scalable array of multithreaded Streaming Multiprocessors (SMs), presents an opportunity for greatly accelerating $Q$-RTM by appropriately exploiting GPU's architectural characteristics. We present the cu$Q$-RTM, a CUDA-based code package that implements $Q$-RTM based on a set of stable and efficient strategies, such as streamed CUFFT, checkpointing-assisted time-reversal reconstruction (CATRC) and adaptive stabilization. The cu$Q$-RTM can run in a multi-level parallelism (MLP) fashion, either synchronously or asynchronously, to take advantages of all the CPUs and GPUs available, while maintaining impressively good stability and flexibility. We mainly outline the architecture of the cu$Q$-RTM code package and some program optimization schemes. The speedup ratio on a single GeForce GTX760 GPU card relative to a single core of Intel Core i5-4460 CPU can reach above 80 in large-scale simulation. The strong scaling property of multi-GPU parallelism is demonstrated by performing $Q$-RTM on a Marmousi model with one to six GPU(s) involved. Finally, we further verify the feasibility and efficiency of the cu$Q$-RTM on a field data set. The ``living'' package is available from GitHub at \url{https://github.com/Geophysics-OpenSource/cuQRTM}, and peer-reviewed code related to this article can be found at \url{http://software.seg.org/2019/0001}.
\end{abstract}

Seismic wave absorption and dispersion, resulting from the presence of intrinsic anelasticity in subsurface media, has been considered one of the most important factors degrading the quality of seismogram and decreasing the resolution of migrated images, which affects the reliability of seismic interpretation \citep{Wang2004Seismic, carcione2007wave, wang2018L}. Many models have been proposed to characterize this frequency-dependent attenuation, which can be roughly classified into two categories: mechanical models and mathematical models. The former includes standard spring-pot models such as the Maxwell body, Kelvin-Voigt model, standard linear solid (SLS) model \citep{carcione2007wave, mainardi2010fractional}, their generalizations such as the generalized Maxwell body (GMB) and generalized Zener body (GZB) \citep{moczo2005rheological, cao2014equivalence}, and their fractional extensions such as the fractional Kelvin model (FKM), fractional Zener model (FZM) \citep{rossikhin2010application, nasholm2013fractional}. Generally, the attenuation of seismic waves appears to be adequately modeled by a power law \citep{strick1967determination, szabo1994time, szabo1995causal} or linear dependence on frequency over a finite bandwidth (a special case of power-law attenuation with a power of 1) \citep{mcdonal1958attenuation, futterman1962dispersive, kjartansson1979constant}. Therefore, another category of models is established on the assumption of power-law attenuation, which includes the Kolsky-Futterman model \citep{kolsky1956lxxi, futterman1962dispersive}, the power-law model and Kjartansson's constant-$Q$ model \citep{kjartansson1979constant}.

The attenuation models mentioned above are designed for mathematically characterizing frequency-dependent attenuation effects of subsurface media and further paving the way to mitigate these effects during seismic wave propagation. Early attempts to compensate for the $Q$ effect (attenuation and dispersion effects) are mostly conducted in the framework of one-way wave-equation migration (OWWEM) \citep{Dai1994Inverse, mittet1995prestack, Wang2004Seismic, mittet2007simple, zhang2012compensation}. In recent years, $Q$-RTM has received increasing attention from the geophysical community \citep{Causse2000Viscoacoustic, Zhang2010Compensating, Zhu2014Q, Li2016Efficient, sun2016q, guo2016comparison, wang2018adaptive}, which generalizes acoustic RTM by considering viscoacoustic propagation and compensating amplitude loss and phase distortion during source and receiver wavefields extrapolation.  \cite{Zhu2014Modeling} proposed a novel viscoacoustic wave equation with decoupled fractional Laplacians (DFLs) which separately dominate amplitude attenuation and phase dispersion, and they further applied this viscoacoustic wave equation in RTM so as to improve the resolution and quality of the image \citep{Zhu2014Q}. This decoupled viscoacoustic wave equation is attractive for $Q$-RTM due to its flexibility for separate amplitude compensation and phase correction, which can be achieved by simply reversing the absorption proportionality coefficient in sign while leaving the equivalent dispersion parameter unchanged \citep{Treeby2010Photoacoustic, Zhu2014Q}.

Although the basic paradigm of $Q$-RTM has been well-established in recent years, there are still some problems and limitations in the process of the implementation, i.e., intensive computation, huge storage requirements and frequent disk I/O, and the difficult issue of stability. The emerging graphics processing unit (GPU) computing technology, built around a scalable array of multithreaded Streaming Multiprocessors (SMs), presents an opportunity for accelerating $Q$-RTM much further by appropriately exploiting the GPU's architectural characteristics \citep{tan2016faster, farquhar2016gpu}. As a booming technology, the GPU computing technology has been widely applied into seismic modeling \citep{micikevicius20093d, zhang2014time}, imaging \citep{zhang2009accelerating, foltinek2009industrial, liu2012fourier, Liu20133D, Yang2014RTM}, and inversion \citep{shin20143d, Yang2015A}. In this chapter, we present a CUDA-based code package named cu$Q$-RTM, which aims to tackle these problems so as to achieve an efficient, storage-saving and stable $Q$-RTM. Next, we will briefly introduce how cu$Q$-RTM is designed to deal with these challenges and then outline the architecture of the cu$Q$-RTM code package.

Specifically, in order to avoid intensive computation, we implement $Q$-RTM in a multi-level parallel (MLP) fashion, either synchronously or asynchronously, to take advantage of all the CPUs and GPUs available. In the framework of cu$Q$-RTM, the basic forward and backward modeling modules, based on viscoacoustic wave equations with DFLs, are efficiently simulated using the Fourier pseudospectral method (PSM) \citep{Carcione2010A, Zhu2014Modeling, chen2016two}. Discrete Fourier transforms (DFTs) of complex wavefields are the most time-consuming parts of these modules. Fortunately, DFTs can be efficiently computed by calling the CUFFT library API \citep{guide2013cuda}, which provides a simple interface for computing parallel FFTs on the GPU, and a simple configuration mechanism called a plan that completely specifies the optimal plan of execution. The use of a CUFFT standard library brings two obvious benefits: the configuration mechanism allows us to create the plans once and execute the plans multiple times (at every time step of the iteration) without recalculation of the configuration. Every CUFFT plan can be associated with a specified CUDA stream. Streaming the CUFFT execution allows for potential overlap between transforms and memory copies and provides a balanced calculation load on each card of the GPUs. CUFFT library functions can only be executed on the device and called from the host, so we have to split my customized kernel functions into k-space components and x-space components. From the brief codes in Appendix A, one can clearly figure out how these components are interconnected.

Apart from the issue of intensive computation, extensive data storage and burdensome disk I/O are another two bottlenecks for conventional RTM, especially for CUDA-based RTM which demands frequent memory copying between host and device \citep{Liu20133D, Yang2014RTM}. In the past three decades, several wavefield reconstruction strategies have been developed to reach a reasonable compromise between the computer memory requirement and computational complexity, for example, reverse propagation coupled with effective boundary saving \citep{Yang2014RTM}, the optimal checkpointing scheme \citep{Griewank2000Algorithm, Symes2007Reverse}, and their combinations such as the time-reversal checkpointing method \citep{Anderson2012Time} and the checkpointing-assisted reverse-forward simulation (CARFS) method \citep{yang2016wavefield}. \cite{yang2016wavefield} proposed a novel viscoacoustic wavefield reconstruction algorithm referred as CARFS, which is implemented by monitoring the energy errors of the reconstruction, and taking it as a criterion to decide whether forward simulation or reverse simulation will be performed at the next time step. \cite{wang2017wavefield} proposed a robust viscoacoustic wavefield reconstruction scheme using time-reversal checkpointing (TRC) and k-space filtering (KSF). In this hybrid scheme, TRC serves as a time-domain regularization to eliminate accumulating errors by replacing the reconstructed wavefield with the stored wavefield at checkpoints, whereas KSF further suppresses high-wavenumber artifacts introduced during time-reversal reconstruction. In the cu$Q$-RTM package, we adopt the checkpointing-assisted time-reversal reconstruction (CATRC) scheme to reconstruct source wavefields, which combines the efficiency of reverse propagation and the stability of checkpointing. Unlike CARFS, the proposed CATRC scheme keeps the reconstruction errors within an acceptable range by imposing low-pass filtering on the time-reversal reconstructed wavefield so as to maintain a fixed recomputation ratio of two.

Finally, amplitude compensation in $Q$-RTM suffers from numerical instability because of it boosts high-frequency noise arising from high-frequency noise in seismic data and numerical errors from the finite machine precision \citep{wang2009seismic, Zhu2014Q, yang2016wavefield, zhao2017method}. Therefore stabilization needs to be introduced either in the frequency or wavenumber domain \citep{Kalimeris2012Photoacoustic, Ammari2013Time}. Since the forward and backward modeling modules are simulated by PSM in cu$Q$-RTM, it is more natural to conduct stabilization in the wavenumber domain. In some literature concerning $Q$ compensation, high-frequency noises are suppressed by utilizing a low-pass Tukey filter with its cutoff frequency identified by the noise level of measured data \citep{Treeby2010Photoacoustic, Zhu2014Q,Li2016Efficient}. However, conventional time-invariant filtering fails to adapt with $Q$ distribution and compensation depth (travel time). \cite{wang2018adaptive} developed an adaptive stabilization for Q-RTM by analytically deriving k-space Green's functions for the constant-$Q$ wave equation with DFLs and its compensated equation, where the stabilization factor can be explicitly identified by the specified gain limit according to an empirical formula. In the provided package, we utilize the proposed adaptive stabilization method to deal with numerical instability in $Q$-RTM, which exhibits superior properties of time-variance and $Q$-dependence over conventional low-pass filtering.

In this chapter, we present an open-source code package cu$Q$-RTM, which overcomes several problems commonly existing in conventional $Q$-RTM such as intensive computation, data storage and numerical stability, by adopting stable and efficient strategies like streamed CUFFT, CATRC and adaptive stabilization. The general architecture of the cu$Q$-RTM code package consists of memory manipulation, modules, kernels, and multi-level parallelism. Each component plays an indispensable role in GPU-CPU cooperative computing. We further demonstrate the validity and efficiency of cu$Q$-RTM with both synthetic and field examples.

\section{Overview of $Q$-RTM}

In this section, we first review the general principle of $Q$-RTM in the framework of viscoacoustic wave equation with DFLs, which includes viscoacoustic propagation, compensation, and imaging. Besides that, two stable and efficient strategies, CATRC and adaptive stabilization, are also provided to improve the computation and stability performance of $Q$-RTM.

\subsection{Propagation, compensation, and imaging}

The viscoacoustic wave equation with DFLs was first proposed by \cite{Zhu2014Modeling} to characterize frequency-dependent attenuation and dispersion separately, which can be written as
\begin{equation}  
\left\{  
             \begin{array}{lr}  
             \dfrac{1}{c^2}\dfrac{\partial^2p}{\partial t^2}(\mathbf{x},t)-\eta(-\nabla^2)^{\gamma+1}p(\mathbf{x},t)-\tau \dfrac{\partial}{\partial t}					
             (-\nabla^2)^{\gamma+\frac{1}{2}}p(\mathbf{x},t) = \delta(\mathbf{x}_s)f(t),  &  \\  
             p(\mathbf{x},t)=\dfrac{\partial p}{\partial t}(\mathbf{x},t)=0,   \qquad \mathbf{x} \in \Omega, t<0 , & 
             \end{array}  
\right.  
\label{eq:forward}
\end{equation} 
where $\Omega$ is a bounded domain in $d$-dimensional space $\mathbb{R}^d$, $\mathbf{x}_s$ denotes the source position, and $f(t)$ is the point source signature enforced at $\mathbf{x}_s$. The dimensionless parameter $\gamma=\mathrm{arctan}(1/\pi Q)$ ranges within $[0, 1/2)$, and $c^2=c_0^2\mathrm{cos}^2(\pi \gamma /2)$, where $c_0$ is the velocity model defined at the reference frequency $\omega_0$. The proportionality coefficients of two fractional Laplacians, separately representing dispersion and absorption, are given by $\eta =-c_0^{2\gamma}\omega_0^{-2\gamma} \mathrm{cos}(\pi \gamma)$ and $\tau=-c_0^{2\gamma-1}\omega_0^{-2\gamma}\mathrm{sin}(\pi \gamma)$. Equation \ref{eq:forward} seems to be attractive for $Q$-RTM owing to its flexibility for separately compensating amplitude loss and correcting phase distortion. \cite{Treeby2010Photoacoustic} and \cite{Zhu2014Q} stated that attenuation compensation based on this equation can be achieved by reversing the absorption proportionality coefficient in sign but leaving the equivalent dispersion parameter unchanged. My latest work (in Chapters 4 and 5) has analytically proved that Green's function of equation \ref{eq:forward} is exponentially decreasing, whereas reversing the absorption proportionality coefficient in sign signifies replacing the Green's function with a phase-conjugated Green's function that is exponentially increasing \citep{wang2018adaptive, wang2017k}.

The novel paradigm of $Q$-RTM first proposed by \cite{Zhu2014Q}, where the source wavefield $p_s(\mathbf{x},t)$ and receiver wavefield $p_r(\mathbf{x},t)$ are compensated during forward extrapolation and time-reversal extrapolation simultaneously, coupled with a zero-lag crosscorrelation imaging condition, has proven to be a promising approach for generating high-resolution images and high-fidelity amplitude reflectors. Following the spirit of \cite{Treeby2010Photoacoustic} and \cite{Zhu2014Q}, the $Q$-compensated source wavefield $p_s(\mathbf{x},t)$ is the solution of the following equation:
\begin{equation}  
\left\{  
             \begin{array}{lr}  
             \dfrac{1}{c^2}\dfrac{\partial^2p_s}{\partial t^2}(\mathbf{x},t)-\eta(-\nabla^2)^{\gamma+1}p_s(\mathbf{x},t)+\tau \dfrac{\partial}{\partial t}					
             (-\nabla^2)^{\gamma+\frac{1}{2}}p_s(\mathbf{x},t) = \delta(\mathbf{x}_s)f(t),  &  \\  
             p_s(\mathbf{x},t)=\dfrac{\partial p_s}{\partial t}(\mathbf{x},t)=0,   \qquad \mathbf{x} \in \Omega, t<0, & 
             \end{array}  
\right.  
\label{eq:Qpforward}
\end{equation} 
and the $Q$-compensated receiver wavefield $p_r(\mathbf{x},t)$ satisfies the following equation
\begin{equation}
\left\{  
            \begin{array}{lr}
			\dfrac{1}{c^2}\dfrac{\partial^2p_r}{\partial t^2}(\mathbf{x},t)-\eta(-\nabla^2)^{\gamma+1}p_r(\mathbf{x},t)+\tau \dfrac{\partial}{\partial t}		
			(-\nabla^2)^{\gamma+\frac{1}{2}}p_r(\mathbf{x},t) = \delta(\mathbf{x}_r)g(\mathbf{x},T-t), &  \\ 
			g(\mathbf{x},t)=p(\mathbf{x},t), \qquad \mathbf{x} \in \mathbf{x}_r, t \in [0,T], & 
            \end{array}  
\right.  
\label{eq:Qpbackward}
\end{equation} 
where $\mathbf{x}_r$ denotes the receiver positions, $g(\mathbf{x},t)$ stands for the recorded seismic data at $\mathbf{x}_r$, which are reversed in time and enforced as the Dirichlet boundary condition. Finally, we realize $Q$-RTM via the following zero-lag crosscorrelation imaging condition:
\begin{equation}
I(\mathbf{x})= \int_0^T p_s(\mathbf{x},t) p_r(\mathbf{x},t) dt.
\label{eq:ic}
\end{equation}
However, an inevitable issue imposed by the crosscorrelation algorithm is that the forward wavefields need to be accessible at every time step \citep{Anderson2012Time, yang2016wavefield}. Saving all forward wavefields requires tremendous memory and frequent disk I/O, which makes it impractical for large-scale 2D or 3D RTM \citep{Symes2007Reverse, Tan2014Reducing}, especially for CUDA-based RTM that demands data transfer between host and device \citep{Yang2014RTM}.

\subsection{CATRC}

In order to relieve extensive data storage and burdensome disk I/O and thus reach a reasonable compromise between the computer memory requirement and computational complexity, we propose an efficient wavefield reconstruction strategy named CATRC, which combines the efficiency of reverse propagation and the stability of checkpointing. Therefore source wavefields used in imaging condition in equation \ref{eq:ic} can be well-reconstructed during time-reversal simulation. Here we denote the reconstructed wavefields as $q(\mathbf{x},t)$, which is the solution of
\begin{equation}  
\left\{  
             \begin{array}{lr}  
             \dfrac{1}{c^2}\dfrac{\partial^2q}{\partial t^2}(\mathbf{x},t)-\eta(-\nabla^2)^{\gamma+1}q(\mathbf{x},t)-\tau \dfrac{\partial}{\partial t}			
             (-\nabla^2)^{\gamma+\frac{1}{2}}q(\mathbf{x},t) = \delta(\mathbf{x}_{\partial \Omega})h(\mathbf{x},T-t),  &  \\  
             h(\mathbf{x},t)=p_s(\mathbf{x},t),   \qquad \mathbf{x} \in \partial \Omega, t \in [0,T] , &  \\
             q(\mathbf{x},t)=p_s(\mathbf{x},t),  \qquad  t \in \big \{C_i \mid i \in [0, N_c-1]\big \} \bigcup \big \{T, T-\Delta t\big \}, &
             \end{array}  
\right.  
\label{eq:catrc}
\end{equation} 
where $\partial \Omega$ is the boundary of space $\Omega$, $h(\mathbf{x},t)$ are forward wavefields distributed on $\partial \Omega$, which are reversed in time and enforced as the Dirichlet boundary condition for source wavefield reconstruction. $C_i$ denotes a checkpoint, and $N_c$ is the number of checkpoints. According to equation \ref{eq:catrc}, the implementation of CATRC can be briefly summarized as two processes. Firstly, we compute forward wavefield $p_s(\mathbf{x},t)$ by solving the compensated viscoacoustic wave equation in \ref{eq:Qpforward}, and we save the forward wavefield at the outermost layer boundary of the simulation domain at every time step. At the same time, we also save the complete forward wavefield $p_s(\mathbf{x},t)$ at the predefined checkpoints ($t \in C_i, i=0, \cdots , N_c-1$) and the last two time steps. The checkpoints can be equally distributed or logarithmically distributed \citep{Griewank2000Algorithm, Symes2007Reverse}. Next, we compute the backward wavefield $q(\mathbf{x},t)$ in reverse time (from $t=T$ to $t=0$) by solving the reconstructed viscoacoustic wave equation (equation \ref{eq:catrc}), and replacing the calculated backward wavefield $q(\mathbf{x},t)$ with the recorded forward wavefield $p_s(\mathbf{x},t)$ at checkpoints ($t \in C_i, i=N_c-1, \cdots , 0$).

It is remarkable that reconstruction by equation \ref{eq:catrc} is a mathematically stable process, given that the source wavefield is compensated while the reconstructed wavefield from boundary is attenuated. However, this stable reconstruction still suffers from insufficient accuracy due to the fact that we utilize PSM to solve equation \ref{eq:catrc} with only the recorded forward wavefield at the outermost layer boundary of simulation domain at every time step. This mismatch of simulation accuracy inevitably degrades the performance of the wavefield reconstruction. Fortunately, the time-reversal checkpointing scheme acts as a time-domain regularization that eliminates accumulating errors by replacing the reconstructed wavefield with the stored wavefield at checkpoints \citep{wang2017wavefield}.

\subsection{Adaptive stabilization}

Mathematically speaking, the compensated viscoacoustic wave equations \ref{eq:Qpforward} and \ref{eq:Qpbackward} are severely ill-posed due to the presence of the compensating term $+\tau \partial_t (-\nabla^2)^{\gamma+1/2} p(\mathbf{x},t)$. That is to say, amplitude compensation is a nonstationary process with energy exponentially amplified over travel time, which boosts high-frequency ambient noise and can even result in numerical instability. In the package, we apply an adaptive stabilization scheme for $Q$-RTM to suppress unwanted high-frequency artifacts, which is discussed in my previous work \citep{wang2018adaptive}. Here we briefly summarize the process.

I derive a k-space Green's function of equation \ref{eq:forward} by enforcing a point source at time $t=t_0$ and $\mathbf{x}=\mathbf{x}_s$. The time-space harmonic Green's function $G(\mathbf{k},\omega)$ is the solution of the following Helmholtz equation
\begin{equation}  
\left(\frac{\omega^2}{c^2}+\eta |\mathbf{k}|^{2\gamma+2}+i\omega\tau|\mathbf{k}|^{2\gamma+1}\right)G(\mathbf{k},\omega)=\frac{1}{(2\pi)^{d+1}}e^{-i \omega t_0} e^{i\mathbf{k} \mathbf{x}_s}.
\label{eq:kwgreen}
\end{equation} 
Solving for Green's function $G(\mathbf{k},\omega)$, applying $d+1$ dimensional inverse Fourier transformation, and then integrating the kernel function with respect to $\omega$ based on Cauchy's residue theorem, we have the following time-domain attenuated Green's function 
\begin{equation}  
G_{att}(\mathbf{x},t)=\frac{c^2}{(2\pi)^{d}} \int_{\mathbb{C}^d} \frac{\mathrm{sin} (\xi_1 t)e^{-\xi_2 t}}{\xi_1} d\mathbf{k}.
\label{eq:attgreen}
\end{equation}
The compensated Green's function can be obtained by reversing the absorption-related term $\tau$ in sign but leaving the other term $\eta$ unchanged:
\begin{equation}  
G_{comp}(\mathbf{x},t)=\frac{c^2}{(2\pi)^{d}} \int_{\mathbb{C}^d} \frac{\mathrm{sin} (\xi_1 t)e^{\xi_2 t}}{\xi_1} d\mathbf{k},
\label{eq:compgreen}
\end{equation}
where $G_{att}$ and $G_{comp}$ represent attenuated and compensated Green's functions, respectively. These two Green's functions lay the foundation for designing an adaptive stabilization operator.  Inspired by stabilization in inverse $Q$ filtering \citep{Wang2002A, Irving2003Removal, wang2006inverse}, we proposed a similar adaptive stabilization for $Q$-RTM, which can be defined as
\begin{equation}
\Lambda (\mathbf{k}, t)= \frac{\beta (\mathbf{k}, t)}{\beta^2 (\mathbf{k}, t)+\sigma^2} = \frac{e^{\xi_2 t}}{1+\sigma^2e^{2\xi_2 t}},
\label{eq:staampcomp}
\end{equation}
where the amplitude-attenuated operator $\beta(\mathbf{k}, t)=e^{-\xi_2 t}$. The final form of the proposed stabilization operator can be given by
\begin{equation}
s(\mathbf{k}, l \Delta t)  = \left\{ 
\begin{array}{lll}
 \frac{1}{1+\sigma^2e^{2\xi_2(\mathbf{k}) \Delta t}}, & l=1, \\
\frac{1+\sigma^2e^{2\xi_2 (l-1) \Delta t}}{1+\sigma^2e^{2\xi_2 l \Delta t}}, & l=2,3, \dots, n. \\
\end{array}
\right.
\label{eq:stabl}
\end{equation}

\section{Architecture of the cu$Q$-RTM code package}

In this section, we outline the architecture of cu$Q$-RTM code package and some program optimization schemes. From an overall perspective, this package can be roughly separated into four components: memory manipulation, modules, kernels, and multi-level parallelism. As shown in Figure \ref{fig:Fig1}, each component plays an indispensable role in GPU-CPU cooperative computing. The following is a brief description of each component and how it interacts with the others.

\subsection{Memory manipulation}

The CUDA programming model assumes that both the host and the device maintain their own separate memory spaces in DRAM, referred to as host memory and device memory, respectively. Before we introduce the details about the architecture of the cu$Q$-RTM code package, we need to clarify the variable definition and figure out which variables need to be transferred between host memory and device memory. Table \ref{tbl:tab1} presents some important variables allocated on host and device, which fall into three memory types: pageable host memory, page-locked host memory, and global device memory. The philosophy of choosing host variable types is that variables to be frequently copied between host and device, such as $seismogram\_rms$ and $image\_cor$, are allocated in page-locked host memory, whereas the rest of the host variables are allocated as regular pageable host memory. Because copies between page-locked host memory and device memory can be performed concurrently with kernel execution, data transfer can be overlapped during kernel execution leading to a more efficient streaming execution on cluster nodes with multiple GPUs.

\texttt{struct MultiGPU} contains page-locked host variables and global device variables (with $d$ as a prefix) on every stream. From this struct variable, we can estimate the total device memory usage before execution and ensure that the memory usage will not exceed the memory limit. CUDA threads (kernel functions) execute on a physically separate device (GPUs), whereas the rest of the C program executes on the host (CPUs). Therefore, a program manages the global memory accessible to kernels through calls to the CUDA runtime such as device memory allocation \texttt{cuda\_Device\_malloc($\ldots$)}, deallocation \texttt{cuda\_Device\_free($\ldots$)}, and initialization \texttt{cuda\_Host\_initialization($\ldots$)} as well as data transfer between host and device memory.

\inputdir{./}

%\begin{figure}
%\begin{center} 
%\includegraphics[width=0.8\linewidth]{Fig1.pdf} 
%\caption{The architecture of the cuQ-RTM code package. \label{fig:Fig1}} 
%\end{center} 
%\end{figure}

\plot{Fig1}{width=0.8\linewidth}{The architecture of the cuQ-RTM code package. }

\begin{table}
\begin{center}
\caption{Some important variables allocated on host and device.}
\label{tbl:tab1}
\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}
\begin{tabular}{|c|c|c|c|}
\hline {} & Memory type & \tabincell{c}{ Allocation \& Free} & Variables \\
\hline 
\multirow{2}*{Host} & pageable & \tabincell{c}{ \texttt{malloc()} \\ \texttt{free()}} &
 \tabincell{c}{\emph{ricker, vp, Qp, Gamma, t\_cp} \\ \emph{kfilter, kstabilization} \\  \emph{Final\_image\_cor, Final\_image\_cor}} \\
\cline{2-4}
                     & page-locked  & \tabincell{c}{ \texttt{cudaMallocHost()} \\ \texttt{cudaFreeHost()} } & \tabincell{c}{\emph{u0, u1, u2} \\ \emph{seismogram\_obs, seismogram\_rms}  \\  \emph{image\_cor, image\_nor}}  \\
\hline
Device & global & \tabincell{c}{ \texttt{cudaMalloc()} \\ \texttt{cudaFree()} } & \tabincell{c}{\emph{d\_ricker, d\_vp, d\_Gamma, d\_t\_cp, d\_u\_cp} \\ \emph{d\_u0, d\_u1,d\_u2, d\_seimogram\_rms} \\ \emph{d\_image\_cor, d\_image\_nor}  \\  \emph{d\_uk, d\_Lap\_uk, d\_amp\_uk, d\_pha\_uk}  \\ \emph{d\_borders\_up, d\_u2\_final0, d\_u2\_final1} }\\
\hline
\end{tabular} 
\end{center}
\end{table}

\subsection{Kernel}

Kernels, the most basic unit of cu$Q$-RTM to accomplish a series of specific tasks such as variable initialization and applying an absorbing boundary condition (ABC), can further be integrated into a fully functional module.  Different variables are initialized with distinct kernels \texttt{cuda\_kernel\_initialization($\ldots$)},  \texttt{cuda\_kernel\_initialization\_images($\ldots$)}, and \texttt{cuda\_kernel\_initialization\_Finals($\ldots$)} based on their scope in modules.  Wavefield variables are updated by \texttt{cuda\_kernel\_update($\ldots$)}.

In the framework of cu$Q$-RTM, the basic forward and backward modules based on viscoacoustic wave equation with DFLs are efficiently simulated by PSM coupled with the CUFFT library. However, CUFFT library functions can only be executed on the device and called from the host, so we split the customized kernel functions into a k-space component and x-space component. The Fourier transform function \texttt{cufftExecC2C($\ldots$, CUFFT\_FORWARD)} and inverse Fourier transform function \texttt{cufftExecC2C($\ldots$, CUFFT\_INVERSE)} serve as the link between the x-space operator \texttt{cuda\_kernel\_visco\_PSM\_2d\_forward\_x\_space($\ldots$)} and the k-space operator \texttt{cuda\_kernel\_visco\_PSM\_2d\_forward\_k\_space($\ldots$)}. Absorbing boundary conditions for these modeling operators are conducted by the multiple transmitting formula (MTF) \texttt{cuda\_kernel\_MTF\_2nd($\ldots$)} \citep{liao1984transmitting}.

In the cu$Q$-RTM package, we adopt the CATRC scheme to reconstruct source wavefields, which combines the efficiency of reverse propagation and the stability of checkpointing. Kernel functions \texttt{cuda\_kernel\_checkpoints\_Out($\ldots$)} and \texttt{cuda\_kernel\_checkpoints\_In($\ldots$)} are designed to record and fetch forward wavefields at predefined checkpoints. Furthermore,  wavefields on the outermost layer boundary of simulation domain at each time step are also recorded in global device variables $d\_borders\_up,\ d\_borders\_bottom,\ d\_borders\_left$, and $d\_borders\_right$.  The total memory storage for 2D reconstruction can be estimated as
\begin{equation}
\label{eq:Mem2d}
Storage_{2D}\ [GB] \approx \frac{2(nx+nz) nt + (N_c+2) (nx \times nz)}{1024^3/4},
\end{equation}
and for the 3D case, 
\begin{equation}
\label{eq:Mem3d}
Storage_{3D}\ [GB] \approx \frac{2(nx \times ny + nx \times nz + ny \times nz) nt + (N_c+2) (nx \times ny \times nz)}{1024^3/4},
\end{equation}
where $nx,\ ny,\ nz$ and $nt$ are spatial and temporal grid sizes. Figure \ref{fig:Fig2a_v} shows memory storage against the scale of the model (where we denote size of the simulation as $nx = ny = nz = 0.1 nt = 10 Nc$) for 2D and 3D cases. Figure \ref{fig:Fig2b_v} presents the memory ratio between boundary savings and checkpointing savings for 2D and 3D cases. Such a large amount of memory storage is  unacceptable for the 3D case, so we have to output the boundary savings to the disk and then read the borders by memory copying between host and device memory.

\multiplot{2}{Fig2a_v,Fig2b_v}{width=0.8\textwidth}{(a) Memory storage and (b) memory ratio of boundary wavefield to checkpointing wavefield (B/C) for both 2D and 3D cases.}

I develop an adaptive stabilization method to deal with numerical instability in $Q$-RTM, which exhibits superior properties of time-variance and $Q$-dependence over conventional low-pass filtering. Both the adaptive stabilization scheme \texttt{cuda\_kernel\_AdaSta($\ldots$)} and low-pass filtering scheme \texttt{cuda\_kernel\_filter2d($\ldots$)} are provided in this package. Users can choose either of these two stabilizing methods to suppress high-frequency noises as they like.

\subsection{Module}

Much as the kernel layer insulates the user from the programming details of a series of specific tasks, the module layer insulates the user from the implementation details of the module of $Q$-RTM, which contains forward extrapolation, wavefield reconstruction, backward extrapolation and imaging. Each of them is made up of several kernel functions and streams. A stream is defined by creating a stream object using \texttt{cudaStreamCreate($\ldots$)} and specifying it as the stream parameter to a sequence of kernel launches and host-device memory copies. Streams are released by calling \texttt{cudaStreamDestroy($\ldots$)}, which waits for all preceding commands in the given stream to complete before destroying the stream and returning control to the host thread. THe forward module \texttt{cuda\_visco\_PSM\_2d\_forward($\ldots$)} in cu$Q$-RTM is designed in a splitting fashion and called by the main function to conduct forward wavefield extrapolation. As wavefield reconstruction, backward extrapolation and imaging are conducted during time-reversal simulation, these three modules can be merged into one module \texttt{cuda\_visco\_PSM\_2d\_backward($\ldots$)}. Both forward and backward modules are presented by brief codes in Appendix A.

\subsection{Multi-level parallelism}

The code package described above is implemented for multiple NVIDIA GPUs using MPI, C, and CUDA in an MLP fashion. The execution is divided into two components. The first is responsible for the coarse-grained parallelization between nodes of the clusters, which is parallelized using MPI. The second performs calculations within each GPU using CUDA. One of the most important issues arising when working with a hybrid MPI/CUDA code is the proper mapping of MPI processes and threads to GPUs and nodes. Thus, we can evenly distribute all shots among every node and every GPU, while being aware of the precise index of each shot during simulation. In the package, we provide two distributing schemes to allow the framework to run on both uniform clusters (i.e., each node with the same number of integrated GPUs) and non-uniform clusters (i.e., a mixture of nodes with the different number and the types of integrated GPUs). Every MPI process (rank) \texttt{MPI\_Comm\_rank(comm,\&myid)} inspects the configuration of the node being executed on, and all GPUs of each node are launched by streaming execution. Algorithms 1 and 2 provide shot distributing schemes to ensure load balancing on each node and device. All threads on host are synchronized by \texttt{MPI\_Barrier(comm)} before migrated images from all shots are reduced by \texttt{MPI\_Allreduce($\ldots$)}, which further guarantees less thread blocking time.

\begin{algorithm}{Algorithm 1: Shot distribution for uniform clusters}{}
     \textbf{Input:} \text{The number of shots} ns, \text{nodes} np, \text{GPUs per node} ng. \\
     \textbf{Output:} \text{Index of each shot}  is. \\
     nsid=ns/(np\times ng)\\
     modsr=ns\%(np\times ng) \\
     prcs=modsr/ng \\
    \begin{IF}{myid<prcs} 
     eachsid=nsid+1;\\
     \text{offset} = myid\times (nsid+1)\times ng;\\
    \ELSE
    eachsid=nsid;\\
    \text{offset}=prcs\times (nsid+1)\times ng+(myid-prcs)\times nsid\times ng;
    \end{IF} \\
    \begin{FOR}{iss\=0\cdots eachsid-1} \\
    \text{offsets} = \text{offset} + iss\times ng; \\ 
    \begin{FOR}{i\=0\cdots ng-1} \\
    is=\text{offsets}+i;  
    \end{FOR}
    \end{FOR}
\end{algorithm}

\begin{algorithm}{Algorithm 2: Shot distribution for non-uniform clusters}{}
     \textbf{Input:} \text{The number of shots} ns, \text{nodes} np, \text{GPUs per node} ng^{(id)}. \\
     \textbf{Output:} \text{Index of each shot}  is. \\
     nsid=ns/\sum_{id=0}^{np-1}{ng^{(id)}}\\
     modsr=ns\%\sum_{id=0}^{np-1}{ng^{(id)}} \\
    \begin{FOR}{j\=1\cdots np-1} \\
    prcs=modsr/\sum_{id=0}^{np-1-j}{ng^{(id)}}; \\ 
    \begin{IF}{prcs>0} 
		break;
    \end{IF} \\
    \end{FOR}
    \begin{IF}{myid<np-j} 
     eachsid=nsid+prcs;\\
     \text{offset} = (nsid+prcs)\times \sum_{id=0}^{myid}{ng^{(id)}};\\
    \ELSE
    eachsid=nsid;\\
    \text{offset}== (nsid+prcs)\times \sum_{id=0}^{np-1-j}{ng^{(id)}}+nsid\times \sum_{id=np-j}^{myid}{ng^{(id)}};
    \end{IF} \\
    \begin{FOR}{iss\=0\cdots eachsid-1} \\
    \text{offsets} = \text{offset} + iss\times ng^{(myid)}; \\ 
    \begin{FOR}{i\=0\cdots ng^{(myid)}-1} \\
    is=\text{offsets}+i; 
    \end{FOR}
    \end{FOR}
\end{algorithm}

\section{Examples}

In this section, we use both synthetic and field examples to demonstrate the superior performance of the presented cu$Q$-RTM package over traditional CPU-based computational models in terms of efficiency, memory storage and stability. All of the following examples are reproducible when the C, CUDA, Matlab and Madagascar platforms \citep{Fomel2013Madagascar} are available.

\subsection{Viscoacoustic modeling on a layered model}

In the first synthetic example, we perform viscoacoustic modeling on a multi-scale layered model with a single GeForce GTX760 GPU and a single core of Intel Core i5-4460 CPU for speedup comparison. As is shown in Figure \ref{fig:Fig3_v}, the scale of these layered models varies from $128\times 128$ to $2048\times 2048$ grids. We record the mean runtime per time step of viscoacoustic modeling using a single CPU core and a single GPU at each model scale, and their corresponding speedup ratio, which are presented in Table \ref{tbl:tab2}. CPU-based simulation is compiled by GNU C++ compiler (g++ 4.8.4) with FFTW 3.3.2. GPU-based simulation is compiled by CUDA C with the CUFFT library API. Figure \ref{fig:Fig4_v} shows the mean runtime per time step and the corresponding speedup ratio against model scale. It indicates that the presented cu$Q$-RTM package running on a single GPU card can nearly be 50-80 times faster than the conventional CPU implementation with a single CPU core. Furthermore, simulation on a larger model scale tends to achieve a greater speedup ratio.

\plot{Fig3_v}{width=0.6\linewidth}{Velocity  models for multi-scale layered model.}

\begin{table}
\caption{The mean runtime per time step of viscoacoustic modeling using  a single GTX760 GPU relative to a four-core Intel Core i5-4460 CPU and the corresponding speedup ratio against model scale.}
\label{tbl:tab2}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline Model Scale (grids) & 128 $\times$ 128  & 256 $\times$ 256 & 512 $\times$ 512 & 1024 $\times$ 1024 & 2048 $\times$ 2048\\
\hline CPU Runtime (ms) & 9.7170 & 43.5925 & 101.3938 & 359.0682 & 1855.8382\\
\hline GPU Runtime (ms) & 0.1839 & 0.8195 & 1.8262 & 6.3267 & 22.3263\\
\hline Speedup Ratio & 52.8385 & 53.1940 & 55.5217 & 56.7544 & 83.1234\\
\hline
\end{tabular} 
\end{center}
\end{table}

\plot{Fig4_v}{width=0.6\linewidth}{The mean runtime per time step of viscoacoustic modeling using a single GTX760 GPU relative to a four-core Intel Core i5-4460 CPU and the corresponding speedup ratio against model scale.}

\subsection{$Q$-RTM on Marmousi model}

The second synthetic example presented here is CUDA-based $Q$-RTM for the Marmousi model. Figures \ref{fig:vp} and \ref{fig:qp} show its velocity and $Q$ models, which contains a high-attenuation zone with a low $Q$ value. The model has 234 nodes with a sampling interval of $dz=10$ m in depth and 663 nodes with a sampling interval of $dx=10$ m  in the horizontal direction. In the observation system, 60 sources are distributed laterally with a shot interval $ds=100$ m, and each shot has 301 double-sided receivers with a maximum offset of 1500 m.  The point source is a Ricker wavelet with a dominant frequency $f_d=20$ Hz. The synthetic seismic data are modeled by the PSM with time interval $dt=0.001$ s, and the records last 2 s.

Figure \ref{fig:img0,img1,img2,img3} shows the migrated image using conventional RTM from acoustic data (Figure \ref{fig:img0}) and viscoacoustic data without compensation (Figure \ref{fig:img1}), and $Q$-RTM from viscoacoustic data (Figures \ref{fig:img2} and \ref{fig:img3}), respectively. The acoustic imaging result shown in Figure \ref{fig:img0} serves as a reference for comparison. Due to the presence of a high-attenuation zone,  the imaging result of the structure beneath high-attenuation zone shown in the blue frame in Figure \ref{fig:img1} exhibits attenuated amplitudes and blurred structures. The attenuation also severely affects the migrated image of the anticlinal structure, shown in the green frame in Figure \ref{fig:img1} below the unconformity. Figures \ref{fig:img2} and \ref{fig:img3} show compensated images from $Q$-RTM using conventional low-pass filtering and the proposed adaptive stabilization scheme. The compensated images exhibit a clear anticlinal structure and recovered amplitudes compared with the non-compensated image. For another comparison, Figure \ref{fig:Fig7a_v,Fig7b_v,Fig7c_v} shows migrated seismic traces, which are selected arbitrarily at three distances of 1500 m, 3600 m and 5200 m from the imaging results shown in Figure \ref{fig:img0,img1,img2,img3}. From these traces, one find that the compensated traces match well with the reference traces. It indicates that the developed cu$Q$-RTM package is capable of improving imaging quality.

The strong scaling plot shows how the execution time decreases with an increasing number of computing resources. During large-scale imaging, the proportion of computational time  spent to simulate wave propagation mandates that the solver must be efficient and scale well. In this regard, 60 shots of $Q$-RTM are evenly distributed among every GPU card with the number of GPUs (Tesla K10) varying from one to six. We record scheduling runtime and computational runtime during every test and present them in Table \ref{tbl:tab3}. Figure \ref{fig:Fig8_v} shows the results of a strong scaling test of cu$Q$-RTM on the Marmousi model. It demonstrates that very close to ideal efficiency can be achieved with a balanced load on each GPU. Thus, the code package exhibits excellent scalability and can be run with almost ideal code performance, in part because communications are almost entirely overlapped with calculations.

\inputdir{marm}
\multiplot{2}{vp,qp}{width=0.6\linewidth}{(a) Velocity and (b) $Q$ of the Marmousi model.}

\multiplot{4}{img0,img1,img2,img3}{width=0.45\linewidth}{Migrated images of the Marmousi model using (a) conventional RTM from acoustic data, (b) conventional RTM from viscoacoustic media without compensation, (c) $Q$-RTM using low-pass filtering and (d) $Q$-RTM using adaptive stabilization scheme.}

\inputdir{./}

%\begin{figure}
%\begin{center} 
%\subfigure[]{ 
%\includegraphics[width=0.6\linewidth]{Fig7a_v.pdf} 
%}
%\subfigure[]{ 
%\includegraphics[width=0.6\linewidth]{Fig7b_v.pdf} 
%}
%\subfigure[]{ 
%\includegraphics[width=0.6\linewidth]{Fig7c_v.pdf} 
%}
%\caption{Migrated seismic traces selected at three distances of (a) 1500 m, (b) 3600 m and (c) 5200 m from migration results shown in Figure \ref{fig:img0,img1,img2,img3}.  \label{fig:Fig7a_v,Fig7b_v,Fig7c_v}}
%\end{center} 
%\end{figure}

\multiplot{3}{Fig7a_v,Fig7b_v,Fig7c_v}{width=0.45\linewidth}{Migrated seismic traces selected at three distances of (a) 1500 m, (b) 3600 m and (c) 5200 m from migration results shown in Figure \ref{fig:img0,img1,img2,img3}.}

\begin{table}
\caption{runtime of cu$Q$-RTM using multiple Tesla K10 GPUs and the corresponding speedup ratio against the number of GPUs. The model has 234 nodes with in depth and 663 nodes in the horizontal direction.}
\label{tbl:tab3}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline The number of GPUs & 1  & 2 & 3 & 4 & 5 & 6\\
\hline Manipulational Runtime (s) & 7.62 & 10.07 & 10.52 & 11.02 & 11.41 & 11.92\\
\hline Computational Runtime (s) & 2639.29 & 1329.40 & 889.82 & 672.78 & 539.21 & 449.97\\
\hline Total Runtime (s) & 2646.91 & 1339.50 & 900.34 & 683.80 & 550.62 & 461.89\\
\hline Speedup Ratio & 1.0000 & 1.9761 & 2.9399 & 3.8709 & 4.8071 & 5.7306\\
\hline
\end{tabular}
\end{center}
\end{table}

%\begin{figure}
%\begin{center} 
%\includegraphics[width=0.6\linewidth]{Fig8_v.pdf} 
%\caption{Strong scaling for cu$Q$-RTM on the Marmousi model using multiple Tesla K10 GPUs. Speedup ratios are plotted against the number of GPUs. The model has 234 nodes with in depth and 663 nodes in the horizontal direction. \label{fig:Fig8_v}}
%\end{center} 
%\end{figure}

\plot{Fig8_v}{width=0.6\linewidth}{Strong scaling for cu$Q$-RTM on the Marmousi model using multiple Tesla K10 GPUs. Speedup ratios are plotted against the number of GPUs. The model has 234 nodes with in depth and 663 nodes in the horizontal direction. }

\subsection{$Q$-RTM on field data}

The field data example shown in Figures \ref{fig:Fig9a_v,Fig9b_v}-\ref{fig:Fig11a_v,Fig11b_v} aims to further verify the feasibility and applicability of the proposed package. Velocity and $Q$ models are presented in Figure \ref{fig:Fig9a_v,Fig9b_v}, which were obtained by migration velocity analysis \citep{sava2008numeric} and $Q$ tomography \citep{shen2015image}. The size of the model is 8.0 km $\times$ 15.6 km with the spatial interval $dx = dz = 10$ m. There are 77 shots horizontally distributed on the surface of the model. We perform $nt = 10000$ time steps for each shot with the temporal interval $dt = 0.0005$ s. In order to eliminate the diffraction artifacts from long offset, we set the stacking aperture of 2.0 km around the shot. Figure \ref{fig:Fig10a_v,Fig10b_v} shows the migrated image using conventional RTM without compensation (Figure \ref{fig:Fig10a_v}) and $Q$-RTM from real data (Figure \ref{fig:Fig10b_v}), respectively. For a clearer comparison, we display the zoomed in seismic images in Figure \ref{fig:Fig11a_v,Fig11b_v} corresponding to the marked area from Figure \ref{fig:Fig10a_v,Fig10b_v}. From Figures \ref{fig:Fig10a_v} and \ref{fig:Fig10b_v}, one can conclude that the $Q$-compensated image using the proposed package exhibits sharper reflections and more balanced amplitude.

\multiplot{2}{Fig9a_v,Fig9b_v}{width=0.45\linewidth}{(a) Velocity and (b) $Q$ models for field data.}

\multiplot{2}{Fig10a_v,Fig10b_v}{width=0.45\linewidth}{Migrated images of the field data using (a) conventional RTM from viscoacoustic media without compensation, (b) $Q$-RTM.}

\multiplot{2}{Fig11a_v,Fig11b_v}{width=0.45\linewidth}{Zoom view of the images shown in the boxs in (a) Figure \ref{fig:Fig10a_v} and (b) Figure \ref{fig:Fig10b_v}.}

\section{Discussion}

An open-source code package cu$Q$-RTM presented in this chapter is designed for efficient and stable viscoacoustic imaging in attenuating media. The package utilizes streamed CUFFT, CATRC scheme and adaptive stabilization to pertinently tackle some well known problems in viscoacoustic imaging such as intensive computations, large storage requirements and frequent disk I/O, and instability. Each of these issues has been discussed in the literature, notably an efficient implementation of 3D FFTs across multiple-GPU systems \citep{nandapalan2012implementation, czechowski2012communication}, memory-saving reconstruction schemes \citep{Anderson2012Time, yang2016wavefield, wang2017wavefield}, and stabilized compensation strategies \citep{Zhu2014Q, sun2015stable, wang2017regularized}. The proposed package aims at utilizing a set of the state-of-art strategies to achieve an efficient, storage-saving and stable $Q$-RTM. Here we discuss the superior performance of the CATRC scheme and adaptive stabilization over conventional methods. Unlike conventional effective boundary-saving strategy using finite-differences (FD) ($2Lc+1$ grid points FD stencil), which requires $Lc$ layers of boundary wavefields at each time step, the proposed CATRC scheme stores the outermost layers of boundary wavefields at each time step plus states at the checkpoints and the last two time steps to the reconstructed source wavefield for performing crosscorrelating imaging condition, without much loss of precision. Figure \ref{fig:Fig12a_v,Fig12b_v,Fig12c_v,Fig12d_v,Fig12e_v,Fig12f_v} shows source snapshots, reconstructed snapshots and their differences from the Marmousi model at two propagation times. It demonstrates that the reconstructed wavefields from CATRC are accurate enough for $Q$-RTM.

\multiplot{6}{Fig12a_v,Fig12b_v,Fig12c_v,Fig12d_v,Fig12e_v,Fig12f_v}{width=0.45\linewidth}{Forward snapshots, reconstructed snapshots and their differences from Marmousi model (see Figure \ref{fig:vp,qp}) at two propagation times: (a)-(c) $t=0.82$ s and (d)-(f) $t=1.22$ s.}

%\begin{figure}
%\begin{center} 
%\subfigure[]{ 
%\includegraphics[width=0.3\linewidth]{Fig12a_v.pdf} 
%}
%\subfigure[]{ 
%\includegraphics[width=0.3\linewidth]{Fig12b_v.pdf} 
%}
%\subfigure[]{ 
%\includegraphics[width=0.3\linewidth]{Fig12c_v.pdf} 
%}
%\subfigure[]{ 
%\includegraphics[width=0.3\linewidth]{Fig12d_v.pdf} 
%}
%\subfigure[]{ 
%\includegraphics[width=0.3\linewidth]{Fig12e_v.pdf} 
%}
%\subfigure[]{ 
%\includegraphics[width=0.3\linewidth]{Fig12f_v.pdf} 
%}
%\caption{Forward snapshots, reconstructed snapshots and their differences from Marmousi model (see Figure \ref{fig:vp,qp}) at two propagation times: (a)-(c) $t=0.82$ s and (d)-(f) $t=1.22$ s. \label{fig:Fig12a_v,Fig12b_v,Fig12c_v,Fig12d_v,Fig12e_v,Fig12f_v}} 
%\end{center} 
%\end{figure}

As this chapter mainly focuses on $Q$-RTM and its GPU implementation, we do not pay much attention to the numerical simulation of spatially varying fractional power of Laplacian operators. There are effective proposed schemes to handle spatial variable-order fractional Laplacians \citep{Sun2014Viscoacoustic, Li2016Efficient, chen2016two, Wangning2018A, wang2018adaptive}. \cite{chen2016two} proposed two efficient methods to calculate spatial variable-order fractional Laplacians, i.e., Taylor-expansion approximation scheme and Low-rank decomposition scheme. \cite{Wangning2018A} extended the Taylor-expansion approximation scheme to the viscoelastic case. All of these methods come at the expense of computational efficiency. In this code package, the averaged strategy \citep{Zhu2014Q} is used to achieve a quick solution. Improving the accuracy of the code package will be my future work.

Another critical issue is the constructed architecture and parallelism strategy of the cu$Q$-RTM code package. The architecture of the cu$Q$-RTM code package has been discussed in detail, which can be separated into four components: memory manipulation, kernel, module and multi-level parallelism. Task-oriented kernels form several fully functional modules, and these modules are further integrated into a complete process of $Q$-RTM. The package contains 2D seismic imaging schemes on both compensated and non-compensated frames with adaptive stabilization and low-pass filtering strategies. We can execute $Q$-RTM in a flexible manner by choosing a series of flags responsible for switching among different scenarios without any code modifications. In this sense, cu$Q$-RTM provides a general GPU-based framework to ensure a time- and memory-efficient implementation. The proposed cu$Q$-RTM is implemented in an MLP manner to take advantages of all the CPUs and GPUs available, while maintaining impressively good stability and flexibility. Whether for a single shot test or a complete simulation, with only a single machine containing seven Nvidia GPU cards, cu$Q$-RTM consistently provides speedup factors approaching or exceeding 50 times compared to conventional CPU-only implementations. My package is particularly well suited to $Q$-RTM where multiple shots are run on clusters with multiple GPUs per node.

Shared memory is expected to be much faster than global memory, which enables direct GPU-to-GPU transfers \citep{nandapalan2012implementation, jaros2012use}. Many researchers proposed shared memory strategy for GPU parallel computing to improve computational efficiency \citep{micikevicius20093d, liu2012fourier, jaros2012use, nandapalan2012implementation, Liu20133D}. In the cu$Q$-RTM code package, we adopt streamed CUFFT to improve computational efficiency with no domain decomposition and GPU-to-GPU transfers involved. For this reason we do not take shared memory strategy into considersation, which might be considered as an improvment in a future version.

Apart from outlining the architecture of the cu$Q$-RTM code package and underlining some program optimization schemes, we also provide speedup analysis and strong scaling test on synthetic models. With only a single Nvidia GPU card, the presented cu$Q$-RTM code package can be 50-80 times faster than the state-of-art distributed CPU implementation running on a single CPU core. We also find that GPU-based simulation on larger model scale tends to reach higher speedup ratio compared with that of small-scale simulation. Objectively speaking, an abusolute speedup ratio without considering the hardware that we used is not really a ``fair'' comparison. In this study, we test the package on a GeForce GTX760 GPU and comapre it with the conventional CPU implementation running on a single core of Intel Core i5-4460 CPU. If a more modern CPU system or a better GPU card is used, the speedup ratio would be much lower or higher than that we claimed in this study. Regarding the scaling test on multi-GPUs, the provided code package exhibits excellent scalability and can be run with almost ideal code performance in part because communications are almost entirely overlapped with calculations. My package's architecture is designed to mimic how a geophysicist writes down a seismic processing module such as modeling, imaging, and inversion. By utilizing the streamed CUFFT, the most time-consuming part of the pseudo-spectral simulation can be computed synchronously on each device, which improves performance and lends itself naturally to the future implementation of more complicated ($Q$-compensated) LSRTM and FWI \citep{Yang2015A, jaros2016full} on the GPU. Future work may also generalize to the 3D case and incorporate more efficient reconstruction scheme, while a further investigation of alternative or improved 2D and 3D FFTs techniques across multiple GPUs \citep{jaros2012use, jaros2016spectral} may also prove worthwhile.

\section{Summary}

In this chapter, we have presented an open-source code package cu$Q$-RTM, equipped with a set of the state-of-art strategies such as streamed CUFFT, the CATRC scheme, and adaptive stabilization, to achieve an efficient and robust $Q$-RTM. The architecture of the cu$Q$-RTM code package is composed of four components: memory manipulation, kernel, module, and multi-level parallelism. Task-oriented kernels are consolidated into several fully functional modules, which are further integrated into the complete process of $Q$-RTM. The package is implemented in an MLP manner to take advantages of all the CPUs and GPUs available, while maintaining impressively good stability and flexibility. We have demonstrated the effectiveness and applicability of the developed package by performing $Q$-RTM on both synthetic and field data. Either synthetic or field migrated images with $Q$ compensation exhibit sharper reflections and more balanced amplitude. Furthermore, speedup tests via viscoacoustic modeling on layered models indicates that the presented cu$Q$-RTM can be 50-80 times faster, compared with  conventional CPU-based implementation with only a single GPU card. The strong scaling analysis of $Q$-RTM across multiple GPUs demonstrates the excellent scalability of the package.

\bibliographystyle{seg}
\bibliography{qrtm}

\newpage

### 2020-09-16 sgk/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{Geophysical Journal International, 209, 21-31, (2017)}

\title{Fast dictionary learning for \old{enhancing multidimensional seismic data}\new{noise attenuation of multidimensional seismic data}}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Yangkang Chen}
\address{
\footnotemark[1]Previously: Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
ykchen@utexas.edu \\
Currently: National Center for Computational Sciences \\
Oak Ridge National Laboratory \\
One Bethel Valley Road, \\
Oak Ridge, TN 37831-6008 \\
chenyk2016@gmail.com
}

\lefthead{GJI - Chen 2017}
\righthead{Fast Dictionary Learning}

\maketitle

\begin{abstract}
The K-SVD algorithm has been successfully utilized for adaptively learning the sparse dictionary in 2D seismic denoising. Because of the high computational cost of many SVDs in the K-SVD algorithm, it is not applicable in practical situations, especially in 3D or 5D problems. In this paper, I extend the dictionary learning based denoising approach from 2D to 3D. To address the computational efficiency problem in K-SVD, I propose a fast dictionary learning approach based on the sequential generalized K-means (SGK) algorithm for denoising multidimensional seismic data. The SGK algorithm updates each dictionary atom by taking an arithmetic average of several training signals instead of calculating a SVD as used in K-SVD algorithm. I summarize the sparse dictionary learning algorithm using K-SVD, and introduce SGK algorithm together with its detailed mathematical implications. 3D synthetic, 2D and 3D field data examples are used to demonstrate the performance of both K-SVD and SGK algorithms. It has been shown that SGK algorithm can significantly increase the computational efficiency while only slightly degrading the denoising performance. 
\end{abstract}

\section{Introduction}
Seismic data is inevitably corrupted by random noise in field acquisition, with important consequences for oil and gas exploration. Thus, random noise attenuation plays a fundamental role in seismic data processing and interpretation \cite[]{fxydecon,zhuang2015,qushan2015,shuwei2016vscan,huijian20161,huijian20162}. Over the past few decades, a large number of denoising methods for random noise have been developed.  
Prediction based methods utilize the predictable property of useful signals to construct prediction filters for enhancing signals and rejecting noise, for example, t-x predictive filtering \cite[]{abma1995}, f-x deconvolution \cite[]{canales1984}, the forward-backward prediction approach \cite[]{yanghua1999}, the polinomial fitting based approach \cite[]{guochang20112}, non-stationary predictive filtering \cite[]{guochang2012,guochang2013}. Mean and median filters utilize the statistical difference between signal and noise to reject the Gaussian white noise or impulsive noise \cite[]{liuyang2009tvmf,yike2013,shuwei2016}.  Decomposition based approaches decompose the noisy seismic data into different components and then select the principal components to represent the useful signals. Empirical mode decomposition and its variations \cite[]{huangemd}, singular value decomposition based approaches \cite[]{bekara2007,yangkang20141,shuwei2015}, regularized non-stationary decomposition based approaches \cite[]{fomel20132} are usually used to extract the useful components in multidimensional seismic data. Rank-reduction based approaches assume the seismic data to be low-rank after some data rearrangement steps, such methods include the Cadzow filtering \cite[]{trickett2008}, principal component analysis \cite[]{weilin2016seg2}, singular spectrum analysis \cite[]{mssa,weilin2017}, damped  singular spectrum analysis \cite[]{weilin2016,zhangdong2016,yangkang2016irr3d,yangkang2016irr5d}.

The sparse transform based random noise attenuation is one of the most widely used \old{approach}\new{approaches} \cite[]{zhangchao2015,yangkang2016emd}. Not only in seismic data processing, but also in all image processing fields, transform\new{ed} domain thresholding approach has achieved very successful performance \cite[]{protter2009,jianfeng2013}. The denoising step can be implemented by simply applying a thresholding operator in the transformed sparse domain, followed by an inverse sparse transform.  Sparse transform can be divided into two types:  analytical transform, which has an exact basis, and learning-based dictionary, which iteratively updates the basis by learning \cite[]{yangkang2016dsd}. I will use \emph{transform} and \emph{dictionary} to refer to these two types of sparse transform, respectively, in this paper.

A lot of transforms have been used in denoising seismic data. \cite{jinghuai2006} used the wavelet transform to denoise prestack seismic data. \cite{dian2008} used the second-generation wavelet transform, which is based on the lifting scheme, to denoise seismic data with a percentile thresholding strategy. \cite{hennenfent2006} and \cite{neelamani2008}  applied the curvelet transform to attenuate both random and coherent noise in seismic data. \cite{shaohuan2016} applied the curvelet transform to separate simultaneous sources based on the iterative soft-thresholding algorithm. \cite{fomel2010seislet} designed a sparse transform that is \old{tailed}\new{tailored} specifically for seismic data, which is called seislet transform, for sparse representation based processing of seismic data, including seismic denoising \cite[]{yangkang2016emd,wujiandemul2016}, seismic deblending \cite[]{yangkang20142,shuwei20163},  and data restoration \cite[]{shuwei20153,shuwei20164,liuwei2016dealiase}. \cite{emdseis} used the adaptive separation properties of empirical mode decomposition (EMD) \cite[]{huangemd} for preparing the stable input for the non-stationary 1D seislet transform and proposed a new EMD-seislet transform to denoise seismic data with strong spatial heterogeneity. Recently, \cite{dehui2015} applied the shearlet transform to seismic random noise attenuation.

The learning-based dictionaries are becoming more and more popular for seismic data processing in recent years since \old{its}\new{their} superior performance\new{s} in adaptively learning the basis that can sparsely represent the complicated seismic data  \cite[]{sgk2013}. \cite{kaplan2009} used a data-driven sparse-coding algorithm to adaptively learn basis functions in order to sparsely represent seismic data and then perform\old{ed} denoising in the transformed domain. Based on a variational sparse-representation model, \cite{jianwei20142} proposed a denoising approach by adaptively learning dictionaries from noisy seismic data. \cite{yangkang2016dsd} combined the learning based dictionaries and the fixed-basis transforms and proposed a double-sparsity dictionary to better handle the special features of seismic data, which can \old{be better in separating signals and noise}\new{can separate signals and noise more precisely}.

K-SVD is one of the most effective dictionary learning algorithms \cite[]{aharon2006}. However, the computational cost which requires thousands of SVD \old{decomposition} hinders its wide application \old{for}\new{in} seismic data processing, especially in practical 3D or 5D problems. In this paper, I propose to apply a fast dictionary learning algorithm, which is called sequential generalized K-means (SGK) algorithm \cite[]{sgk2013}, to denoise \old{multi-dimensional}\new{multidimensional} seismic data. Since sparse code is relatively new to the seismic community, I introduce the basic formulation of a sparse representation problem and mathematically analyze the principle of K-SVD algorithm and clarify its computational bottleneck. Then, I also introduce the SGK algorithm in detail and apply both K-SVD and SGK algorithms to denoise \old{multi-dimensional}\new{multidimensional} seismic data. Three examples show that the SGK algorithm can significantly accelerate the dictionary learning process and cause no observably worse denoising performance.

\section{Method}
\subsection{Problem formulation}
Sparse representation via learning based dictionary \old{is consisted}\new{consists} of two main steps.
\begin{itemize}
\item Sparse coding. Given the observed data $\mathbf{d}$, sparse coding aims at solving the optimization problem:
\begin{equation}
\label{eq:code}
\mathbf{m}^n = \arg \min_{\mathbf{m}} \parallel \mathbf{d} - \mathbf{F}^n\mathbf{m} \parallel_2^2, s.t. \parallel \mathbf{m} \parallel_0 \le T,
\end{equation}
where \new{$\parallel\cdot\parallel_2$ and $\parallel\cdot\parallel_0$ denote the $L_2$ and $L_0$ norms of an input vector, respectively.} $T$ is the number of non-zero coefficients. \new{$\mathbf{F}$ is the learned dictionary and $\mathbf{m}$ is the sparse representation of $\mathbf{d}$.}
\item Dictionary updating.
For the obtained $\mathbf{m}^n$, update $\mathbf{F}^n$ such that
\begin{equation}
\label{eq:dic}
\mathbf{F}^{n+1} = \arg \min_{\mathbf{F}} \parallel \mathbf{d} - \mathbf{Fm}^n \parallel _2^2.
\end{equation}
\end{itemize}
Equations \ref{eq:code} and \ref{eq:dic} are iterated $Niter$ times to learn the optimal dictionary and \new{the} sparest representation.

The multidimensional seismic data is first reformulated into patch form $\mathbf{D}$. Each column vector in $\mathbf{D}$ is extracted from the multidimensional seismic data matrix. An example is given in \cite{siwei2015} and \cite{yangkang2016dsd}.
Equations \ref{eq:code} and \ref{eq:dic} then become 
\begin{align}
\label{eq:Code}
\forall_i \mathbf{m}_i ^n &= \arg \min_{\mathbf{m}_i} \parallel \mathbf{D} - \mathbf{F}^n\mathbf{M} \parallel_F^2, s.t. \forall_i \parallel \mathbf{m}_i \parallel_0 \le T, \\
\label{eq:Dic}
\mathbf{F}^{n+1} &= \arg\min_{\mathbf{F}} \parallel \mathbf{D} - \mathbf{FM}^n \parallel_F^2,
\end{align}
\new{where $\parallel\cdot\parallel_F$ denotes the Frobenius norm of an input matrix.}

Problem \ref{eq:Code} is a NP-hard problem, and directly finding the truly optimal $\mathbf{M}$ is impossible and is usually solved by an approximation pursuit method, such as the orthogonal matching pursuit (OMP) algorithm. To solve problem \ref{eq:Dic} for the adaptive dictionary $\mathbf{F}$, there are several different algorithms.

\subsection{Dictionary learning by K-SVD}
The K-SVD method \cite[]{aharon2006} is one approach that solves equation \ref{eq:Dic} with good performance. The dictionaries in $\mathbf{F}$ are not obtained at a time. Instead, $K$ columns in $\mathbf{F}$ are updated one by one while fixing $\mathbf{M}$. In order to update the $k$th column, one can first write the objective function in \new{equation} \ref{eq:Dic} as
\begin{equation}
\label{eq:Dic2}
\begin{split}
\parallel \mathbf{D} - \mathbf{FM} \parallel_F^2  & = \parallel \mathbf{D} - \sum_{j=1}^{K}\mathbf{f}_j\mathbf{m}_T^j \parallel_F^2, \\
&= \parallel \mathbf{D} - \sum_{j\ne k}\mathbf{f}_j\mathbf{m}_T^j - \mathbf{f}_k\mathbf{m}_T^k \parallel_F^2, \\
& =  \parallel\mathbf{E}_k- \mathbf{f}_k\mathbf{m}_T^k \parallel_F^2 ,
\end{split}
\end{equation}
where \old{$a_j$}\new{$\mathbf{f}_j$} is the $j$th column vector in $\mathbf{F}$, $\mathbf{m}_T^j$ is the $j$th row vector in $\mathbf{M}$. \new{Here, $[\cdot]_T$ simply indicates a row vector.} For simplicity, in equation \ref{eq:Dic2} and the following derivations, I omit the superscript $n$ shown in equation \ref{eq:Dic}. $\mathbf{E}_k$ is the fitting error using all column vectors other than the $k$th dictionary and their corresponding coefficients row vectors.   
\old{Please note}\new{Note} that in equation \ref{eq:Dic2}, $\mathbf{D}$ and $\mathbf{E}_k$ are of size $M\times N$, $\mathbf{F}$ is of size $M\times K$, and $\mathbf{M}$ is of size $K\times N$. \new{Here, $M$ is the length of each training signal, $N$ is the number of training signals, and $K$ is the number of atoms in the dictionary.}

It is now obvious that the $k$th dictionary in $\mathbf{F}$ is updated by minimizing the misfit between the rank-1 approximation of $\mathbf{f}_k\mathbf{m}_T^k$ and the $\mathbf{E}_k$ term. The rank-1 approximation is then solved using the singular value decomposition (SVD).

A problem in the direct use of SVD for rank-1 approximation of $\mathbf{E}_k$ is the loss of sparsity in $\mathbf{m}_T^k$. After SVD on $\mathbf{E}_k$, $\mathbf{m}_T^k$ is likely to be filled. In order to solve such problem, K-SVD restricts minimization of equation \ref{eq:Dic2} to a small set of training signals $\mathbf{D}_k=\{\mathbf{d}_i: \mathbf{m}_T^k(i)\ne 0\}$. To achieve this goal, one can define a transformation matrix $\mathbf{R}_k$ to \old{shrinks}\new{shrink} $\mathbf{E}_k$ and $\mathbf{m}_T^k$ by rejecting the zero columns in $\mathbf{E}_k$ and zero entries in $\mathbf{m}_T^k$. First one can define a set $r_k=\{i| 1\le i \le N, \mathbf{m}_T^k(i)\ne 0 \}$, which selects the entries in $\mathbf{m}_T^k$ that are non-zero. One then \old{construct}\new{constructs} $\mathbf{R}_k$ as a matrix of size $N\times N_r^k$ with ones on the $(r_k(i),i)$ entries and zeros otherwise.

Applying $\mathbf{R}_k$ to both $\mathbf{E}_k$ and $\mathbf{m}_T^k$, then the \old{objection}\new{objective} function in \new{equation} \ref{eq:Dic2} becomes
\begin{equation}
\label{eq:Dic3}
\parallel\mathbf{E}_k\mathbf{R}_k- \mathbf{f}_k\mathbf{m}_T^k\mathbf{R}_k \parallel_F^2  = \parallel\mathbf{E}^R_k- \mathbf{f}_k\mathbf{m}_R^k \parallel_F^2
\end{equation}
and can be minimized by directly using SVD:
\begin{equation}
\label{eq:svd}
\mathbf{E}^R_k  = \mathbf{U}\Sigma\mathbf{V}^T. 
\end{equation}
$\mathbf{f}_k$ is then set as the first column in $\mathbf{U}$, the coefficient vector $\mathbf{m}_R^k$ as the first column of $\mathbf{V}$ multiplied by first diagonal entry $\sigma_1$. After $K$ columns are all updated, one \old{turn}\new{turns} to solve equation \ref{eq:Code} for $\mathbf{M}$.

\subsection{Fast dictionary learning by sequential generalized K-means}
Although K-SVD can obtain very successful performance in a number of sparse representation based approaches, since there involves many SVD operations in the K-SVD algorithm, it is very computationally expensive. Especially when utilized in \old{multi-dimensional}\new{multidimensional} seismic data processing (e.g. 3D or 5D processing), the computational cost is not tolerable. The sequential generalized K-means algorithm (SGK) was proposed to increase the computational efficiency \cite[]{sgk2013}. SGK tries to solve slightly different iterative optimization problem in sparse coding as \old{equations}\new{equation} \ref{eq:Code}:
%\begin{equation}
%\label{eq:Code2}
%\forall_i \mathbf{m}_i ^n = \arg \min_{\mathbf{m}_i} \parallel \mathbf{D} - \mathbf{F}^n\mathbf{M} \parallel_F^2, s.t. \forall_i \parallel \mathbf{m}_i \parallel_0 = 1,
%\end{equation}
\begin{equation}
\label{eq:Code2}
\forall_i \mathbf{m}_i ^n = \arg \min_{\mathbf{m}_i} \parallel \mathbf{D} - \mathbf{F}^n\mathbf{M} \parallel_F^2, s.t. \forall_i \mathbf{m}_i = \mathbf{e}_t.% for some t,
\end{equation}
\new{$t$ indicates that $\mathbf{m}_i$ has all 0s except 1 in the $t$th position.} %which means the sparse coding in SGK algorithm needs to be sparser than that in K-SVD.  
The dictionary updating in SGK algorithm is also different. 
In SGK, equation \ref{eq:Dic3} also holds. Instead of using SVD to minimize the objective function, which is computationally expensive, SGK turns to use least-squares method to solve the minimization problem. Taking the derivative of $J=\parallel\mathbf{E}^R_k- \mathbf{f}_k\mathbf{m}_R^k \parallel_F^2$ with respect to $\mathbf{f}_k$ and setting the result to 0 gives the following equation:
\begin{equation}
\label{eq:deri}
\frac{\partial J}{\partial \mathbf{f}_k} = -2(\mathbf{E}^{R}_k-\mathbf{f}_k\mathbf{m}_R^k)(\mathbf{m}_R^k)^T = 0
\end{equation}
solving equation \ref{eq:deri} leads to
\begin{equation}
\label{eq:deriso}
\mathbf{f}_k = \mathbf{E}^R_k (\mathbf{m}_R^k)^T \left( \mathbf{m}_R^k (\mathbf{m}_R^k)^T \right)^{-1}.
\end{equation}

It can be derived further that
\begin{equation}
\label{eq:em0}
\begin{split}
\mathbf{E}^R_k (\mathbf{m}_R^k)^T &= \left(\mathbf{D}_R-\sum_{j\ne k}\mathbf{f}_j\mathbf{m}_R^j\right) (\mathbf{m}_R^k )^T \\
&= \mathbf{D}_R (\mathbf{m}_R^k )^T  + \sum_{j\ne k}\mathbf{f}_j\mathbf{m}_R^j (\mathbf{m}_R^k ).^T
\end{split}
\end{equation}
\new{Here, $\mathbf{D}_R$ has the same meaning as $\mathbf{D}$ shown in equation \ref{eq:Dic2} except for a smaller size due to the selection set $r_k$ that selects the entries in $\mathbf{m}_T^k$ that are non-zero.}

Since $\forall_i,\parallel \mathbf{m}_i \parallel_0=1$, \new{as constrained in equation \ref{eq:Code2}} then 
\begin{equation}
\label{eq:ortho}
\forall_{j\ne k} \mathbf{m}_R^j (\mathbf{m}_R^k )^T =  0.
\end{equation}
\new{
Since $\mathbf{m}_R^k$ is a smaller version of row vector $\mathbf{m}_T^k$ and all its entries are all equal to 1, $\mathbf{D}_R (\mathbf{m}_R^k )^T$ is simply a summation over all the column vectors in $\mathbf{D}_R$. Considering that $\mathbf{D}_R=\{\mathbf{d}_i: i\in r_k\}$, 
\begin{equation}
\label{eq:sum}
\mathbf{D}_R (\mathbf{m}_R^k )^T=\sum_{i\in r_k}\mathbf{d}_i
\end{equation}
}
\old{Since $\mathbf{D}_R (\mathbf{m}_R^k )^T=\sum_{i\in r_k}\mathbf{d}_i$,}\new{Following equation \ref{eq:sum},} equation \ref{eq:em0} becomes
\begin{equation}
\label{eq:em}
\mathbf{E}^R_k (\mathbf{m}_R^k)^T = \sum_{i\in r_k}\mathbf{d}_i.
\end{equation}
It is simple to derive that $\mathbf{m}_R^k(\mathbf{m}_R^k)^T=N_r^k$, %diag(N_r^k,N_r^k,\cdots)
 where $N_r^k$ denotes the number of elements in the set $r_k$, or the number of training signals associated with the atom $\mathbf{f}_k$. The $k$th atom in \old{$\mathbf{D}_R$}\new{$\mathbf{F}$} is
\begin{equation}
\label{eq:fk}
\mathbf{f}_k =\frac{\sum_{i\in r_k}\mathbf{d}_i}{N_r^k}.
\end{equation}
Thus, in SGK, one can avoid the use of SVD. Instead the trained dictionary can be simply expressed as an average of several training signals. In this way, SGK can obtain significantly higher efficiency than K-SVD. In the next section, I will use several examples to show that the overall denoising performance does not degrade when one can obtain a much faster implementation.

\section{Examples}
I will use three different examples to show the performance of SGK in denoising \old{multi-dimensional}\new{multidimensional} seismic data. Please note that when using equations \ref{eq:Code} (or \ref{eq:Code2}) and \ref{eq:Dic} for dictionary learning, the \old{multi-dimensional}\new{multidimensional} seismic \new{data} is first mapped from the original form to a 2D matrix according to some patching criteria. Some details about the patching method can be found in \cite{siwei2015} or \cite{yangkang2016dsd}.  After iteratively solving equations \ref{eq:Code} (or \ref{eq:Code2}) and \ref{eq:Dic} several times, the denoised data is expressed as 
\begin{equation}
\label{eq:final}
\hat{\mathbf{D}} = \mathbf{F}^{Niter}\mathbf{M}^{Niter}.
\end{equation}
An inverse mapping is then applied to $\hat{\mathbf{D}}$ to output the finally denoised data.

\new{
For measuring the denoising performance of synthetic data examples, where one knows the clean data, I use the signal-to-noise ratio (SNR) \cite[]{guochang2009,weilin2016} measurement and the formula is expressed as follows:
\begin{equation}
\label{eq:snr}
SNR=10\log_{10}\frac{\Arrowvert \mathbf{D}_{true} \Arrowvert_F^2}{\Arrowvert \mathbf{D}_{true} -\hat{\mathbf{D}}\Arrowvert_F^2},
\end{equation}
where $\mathbf{D}_{true}$ denotes the clean data and $\hat{\mathbf{D}}$ denotes the denoised data.}

\new{
In addition to the commonly used SNR measurement, one can also use local similarity \cite[]{fomel2007localattr,yangkang2015ortho} as a convenient tool to evaluate denoising performance. The abnormal area in the local similarity map with high similarity indicates the area that contains significant signal leakage in the removed noise. A local similarity map with values that are close to zero, as well as the observed significant amount of removed noise, provides a valid support of a successful denoising performance. In addition, the local similarity measurement can be used in many cases since the input data of local similarity calculation are just the denoised data and removed noise. It provides an alternative in the case of field data processing, where the clean data is unknown and the SNR based evaluation becomes unavailable. Besides, local similarity is a local measurement of denoising performance, whereas the SNR is a global measurement, which cannot guide us to pick out the areas with poor denoising performances.}

\old{The first example is a 2D field data example, as shown in Figure \ref{fig:field2d}. Figures \ref{fig:field2d-ksvd} and \ref{fig:field2d-sgk} show the denoised result using K-SVD and SGK, respectively. Figures \ref{fig:field2d-n-ksvd} and \ref{fig:field2d-n-sgk} show their corresponding noise sections. The data size of this example is $512\times 512$ . In this example, I chose a patch size of $8\times8$. The overlap between different patches is $7$ points in both vertical and horizontal directions. Thus the atom size $M=8\times8=64$, and the number of sample signals is thus $N=(512-7)\times(512-7)=255025$. The size of $\mathbf{D}$ is $64\times255025$. For K-SVD, the dictionary updating process takes about 1232.23s, while for SGK, the dictionary updating process takes only 51.37s, which shows a great speedup. Figure \ref{fig:dicfield0} shows the initial input dictionary. Figures \ref{fig:dicfieldksvd} and \ref{fig:dicfieldsgk} show the learned dictionaries using K-SVD and SGK, respectively. The two learned dictionaries show some similarities but are not exactly the same. }

\subsection{Synthetic example}

The \old{second}\new{first} example is a 3D synthetic example, as shown in Figure \ref{fig:syn3d,syn3d-ksvd,syn3d-sgk,syn3d-n,syn3d-ksvd-n,syn3d-sgk-n}. Figure \ref{fig:syn3d} is the clean data and Figure \ref{fig:syn3d-n} is the noisy data. Figures \ref{fig:syn3d-ksvd} and \ref{fig:syn3d-sgk} show the denoised results using K-SVD and SGK, respectively. Figures \ref{fig:syn3d-ksvd-n} and \ref{fig:syn3d-sgk-n} show the removed noise cubes of two approaches. It seems that the denoised results using both methods are very successful while the denoised result using SGK algorithm shows a little bit more residual noise, which is however negligible. The size of this example is $64\times 16\times 16$. I use a 3D patch of size $4\times 4\times 4$ and the overlap between neighbor patches is 3 points in all time, inline, xline directions. In this example, the sample signals $\mathbf{D}$ is of size $64\times 10309$. The K-SVD takes \old{195.71s}\new{192.60s} while SGK takes only \old{9.30s}\new{9.27s}. The SNRs of noisy data, K-SVD result and SGK result are 0.68 dB, 9.61dB and 9.32dB respectively. While the SNRs using the K-SVD and SGK are very similar, the SGK method obtains about 5 times acceleration. \new{To further demonstrate the denoising performance and compare the two methods regarding the tiny differences, I plot the local similarity between denoised data and removed noise in Figure \ref{fig:syn3d-simi1,syn3d-simi2,syn3d-simi3,syn3d-simi4}. Figures \ref{fig:syn3d-simi1} and \ref{fig:syn3d-simi2} show the local similarity cubes without amplification that correspond to K-SVD and SGK methods, respectively. It can be seen that both methods cause negligible local similarity, or correlation, between denoised data and removed noise, confirming the extremely successful performance of the two methods. Figures \ref{fig:syn3d-simi3} and \ref{fig:syn3d-simi4} show the amplified local similarity cubes (similarity $\times$ 2) corresponding to K-SVD and SGK methods, respectively. It can be observed that there are some non-zero amplified similarity values around the events, indicating these tiny damages to the signal caused by both methods. It can also be observed that the amplified local similarity of SGK method is slightly higher than K-SVD method. Considering the slightly low SNR using SGK method, I conclude that SGK method might cause slightly worse performance than the K-SVD method while obtaining a huge improvement on computational efficiency.  I also show some learned atoms of this example in Figure \ref{fig:dic0,dicksvd,dicsgk}. Figures \ref{fig:dic0}, \ref{fig:dicksvd}, and \ref{fig:dicsgk} show the atoms from initial dictionary, K-SVD learned dictionary, and SGK learned dictionary, respectively. I set up the initial dictionary using the discrete cosine transform. It can be seen from Figure \ref{fig:dic0} that the shapes of the atoms in the initial dictionary are rigid, which are not optimal to represent the highly-nonstationary seismic data. After dictionary learning, the updated dictionaries as shown in Figures \ref{fig:dicksvd} and \ref{fig:dicsgk} contain atoms with much varied shapes. These various atoms are more likely to capture the non-stationary features in the seismic data and thus can potentially improve the sparse representation of the observed noisy seismic data. Please note that each atom has been reshaped into a 3D cube and only 16 atoms are shown here. }

\new{In order to test the denoising performances of the two methods in different noise levels, I calculate the SNRs of two methods in four different cases with increasing noise levels (or decreasing input SNRs). The denoising performances of different input SNRs are compared in table \ref{tbl:snrcomp}. The SNR of input noisy data drops from 3.18 dB to -5.33 dB. Correspondingly, the SNRs of the best results using two methods drop from above 10 dB to around 1 dB. Besides, the K-SVD method consistently obtains a slightly higher SNR than SGK method. }

In this paper, I compare the speed of SGK with the classic version of K-SVD algorithm (exact SVD calculation). Recently, there are a lot of new algorithms proposed to approximate SVD instead of exactly computing it, e.g., \cite{aksvd2008}, \cite{gpuksvd}, and \cite{fksvd}. These methods can hopefully improve the efficiency of K-SVD algorithm, but at the expense of slightly degrading the performance. Both K-SVD and SGK use the fast OMP algorithm for sparse coding in the whole dictionary learning process. In order to compare the computing time fairly, I repeat the same calculation three times for each model size and calculate the average time as the final measured computing time.

\tabl{snrcomp}{\new{Comparison of denoising performances  with different input SNRs between K-SVD and SGK methods.}}
 {
    \begin{center}
     \begin{tabular}{|c|c|c|} 
	  \hline Input SNR (dB) & K-SVD (dB)  & SGK (dB)			       		 \\ 
	  \hline 3.18 & 10.60 & 10.60 \\
	  \hline 0.68 & 9.61 & 9.32 \\
	  \hline -2.84 & 2.17 & 2.08 \\	  
      \hline -5.33 & 1.27 & 1.11  \\ 
      \hline
    \end{tabular} 
   \end{center}
}

\subsection{\new{Field data example}}
I first use a 2D field data example to compare the difference between K-SVD and SGK methods, as shown in Figure \ref{fig:field2d}.  The data size of this example is $512\times 512$ . In this example, I choose a patch size of $8\times8$. The overlap between different patches is $7$ points in both vertical and horizontal directions. Thus the atom size $M=8\times8=64$, and the number of sample signals is thus $N=(512-7)\times(512-7)=255025$. The size of $\mathbf{D}$ is $64\times255025$. For K-SVD, the dictionary updating process takes about 1590.2s, while for SGK, the dictionary updating process takes only 87.23s, which shows a great speedup. Figure \ref{fig:dicfield0} shows the initial input dictionary. Figures \ref{fig:dicfieldksvd} and \ref{fig:dicfieldsgk} show the learned dictionaries using K-SVD and SGK, respectively. The two learned dictionaries show some similarities but are not exactly the same. As can be seen in either Figure \ref{fig:dicfieldksvd} or \ref{fig:dicfieldsgk} that there are some atoms in the middle part of the dictionary map containing linear patterns, indicating a better representation of the locally linear events. In this example, I also compare the K-SVD and SGK methods with two other widely known methods, i.e. the DDTF method \cite[]{jianfeng2013} and the seislet transform method \cite[]{fomel2010seislet}. The denoised results using four methods are shown in Figure \ref{fig:field2d-ksvd,field2d-sgk,field2d-ddtf,field2d-seis}. The corresponding noise sections are shown in Figure \ref{fig:field2d-n-ksvd,field2d-n-sgk,field2d-n-ddtf,field2d-n-seis}. Comparing the results in both Figures \ref{fig:field2d-ksvd,field2d-sgk,field2d-ddtf,field2d-seis} and \ref{fig:field2d-n-ksvd,field2d-n-sgk,field2d-n-ddtf,field2d-n-seis}, I can roughly get some conclusions that K-SVD, SGK, and DDTF methods all seem to obtain successful denoised results while the result from seislet transform is a bit over-smoothed, which causes some observable low-frequency coherent energy in the noise section (Figure \ref{fig:field2d-n-seis}). A better evaluation of denoising performance can be obtained using the local similarity measurement and is shown in Figure \ref{fig:field2d-simi1,field2d-simi2,field2d-simi3,field2d-simi4}. The local similarity confirms my observation in that the local similarity corresponding to seislet method is very high, which is followed by the DDTF method. The DDTF method obtains a successful performance in most part of the data but causes some damages to the highly curved signals around the 2s near the left boundary, as indicated from the local similarity map (Figure \ref{fig:field2d-simi3}). The K-SVD and SGK methods obtain very close results but SGK results in a slightly higher local similarity in right part of the data.

\old{The last example is a 3D field data example}\new{I next use a 3D field data example to demonstrate the performance}, as shown in Figure \ref{fig:field3d,field3d-ksvd,field3d-sgk,field3d-ksvd-n,field3d-sgk-n}. Figures \ref{fig:field3d}, \ref{fig:field3d-ksvd}, and \ref{fig:field3d-sgk} show noisy data, K-SVD denoised data and SGK denoised data, respectively. Figures \ref{fig:field3d-ksvd-n} and \ref{fig:field3d-sgk-n} show the noise sections of two approaches. It is clear that both approach\new{es} obtain \old{close}\new{approximate} performance. It is \old{too} computationally expensive to use K-SVD to learn the dictionary for this example. While it takes about half an hour to learn the dictionary using SGK algorithm\new{, it takes more than half a day to learn the dictionary using the K-SVD algorithm. The local similarity cubes between denoised data cubes and removed noise cubes using two methods are shown in Figure \ref{fig:field3d-simi1,field3d-simi2}, which confirms the successful and comparable performance of both methods in that most part of the data is close to zero}.

\inputdir{synth}
\multiplot{6}{syn3d,syn3d-ksvd,syn3d-sgk,syn3d-n,syn3d-ksvd-n,syn3d-sgk-n}{width=0.3\columnwidth}{3D synthetic example. (a) Clean data. (b) Denoised data using K-SVD. (c) Denoised data using SGK. (d) Noisy data. (e) Noise using K-SVD. (f) Noise using SGK. }

\multiplot{4}{syn3d-simi1,syn3d-simi2,syn3d-simi3,syn3d-simi4}{width=0.4\columnwidth}{(a) \& (b) Local similarity between denoised data and removed noise using  K-SVD and SGK. (c) \& (d) Amplified local similarity ($\times$2) between denoised data and removed noise using  K-SVD and SGK.}

\inputdir{./}
\multiplot{3}{dic0,dicksvd,dicsgk}{width=0.45\columnwidth}{(a) Initial overcomplete DCT dictionary. (b) Learned dictionary using K-SVD. (c) Learned dictionary using SGK. Only the first 16 atoms in the dictionary are displayed and each dictionary has been reshaped into a 3D cube. It can see from (a) that the shapes of the atoms in the initial dictionary (discrete cosine transform) are rigid, which are not optimal to represent the highly-nonstationary seismic data. After dictionary learning, the updated dictionaries as shown in (b) and (c) contain atoms with much varied shapes. These various atoms are more likely to capture the non-stationary features hidden in the seismic data.}

\plot{field2d}{width=0.8\columnwidth}{Noisy 2D field data.}
\multiplot{3}{dicfield0,dicfieldksvd,dicfieldsgk}{width=0.45\columnwidth}{(a) Initial overcomplete DCT dictionary. (b) Learned dictionaries using K-SVD. (c) Learned dictionaries using SGK. Each atom in the dictionary has been reshaped into a 2D matrix. As can be seen in either (b) or (c) that there are some atoms in the middle part of the dictionary map containing linear patterns, indicating a better representation of the locally linear events. }

\multiplot{4}{field2d-ksvd,field2d-sgk,field2d-ddtf,field2d-seis}{width=0.45\columnwidth}{(a) Denoised data using K-SVD. (b) Denoised data using SGK. (c) Denoised data using DDTF. (d) Denoised data using seislet thresholding.}

\multiplot{4}{field2d-n-ksvd,field2d-n-sgk,field2d-n-ddtf,field2d-n-seis}{width=0.45\columnwidth}{(a) Removed noise using K-SVD. (b) Removed noise using SGK. (c) Removed noise using DDTF. (d) Removed noise using seislet thresholding. }

\multiplot{4}{field2d-simi1,field2d-simi2,field2d-simi3,field2d-simi4}{width=0.45\columnwidth}{Local similarity between denoised data and removed noise using (a)  K-SVD, (b) SGK, (c) DDTF and (d) seislet thresholding.  }

\multiplot{5}{field3d,field3d-ksvd,field3d-sgk,field3d-ksvd-n,field3d-sgk-n}{width=0.3\columnwidth}{(a) Noisy 3D field data. (b) \& (c) Denoised data using K-SVD and SGK. (d) \& (e) Noise cubes using K-SVD and SGK. }

\multiplot{2}{field3d-simi1,field3d-simi2}{width=0.45\columnwidth}{(a) Local similarity between denoised data using K-SVD and the corresponding noise cube. (b) Local similarity between denoised data using SGK and the corresponding noise cube. }

\section{Conclusion}
In this paper, I proposed a fast dictionary-learning based seismic denoising approach using the  sequential generalized K-means (SGK) algorithm. In the SGK algorithm, each atom in the dictionary is updated by an average of several sample signals while K-SVD uses computationally expensive SVD to update each atom. Thus, the SGK algorithm can be much faster than K-SVD algorithm for adaptively learning the dictionary. I applied both K-SVD and SGK to dictionary learning of seismic data for random noise attenuation. The results from three different examples show that SGK is much faster than K-SVD without sacrificing \old{any}\new{much} denoising performance. I suggest substituting the \old{KSVD}\new{K-SVD} with SGK in any applications that require sparse coding. Future research direction may include applying the SGK based dictionary learning for \old{multi-dimensional}\new{multidimensional} seismic data reconstruction.

\section{Acknowledgments}
\new{I would like to thank editors Jorg Renner, Lapo Boschi, and two anonymous reviewers for providing critical comments that improve the manuscript greatly.} I also thank Shuwei Gan, Shaohuan Zu, Weilin Huang for helpful comments and suggestions on the topic of seismic signal processing, and Jianwei Ma, Sergey Fomel, Siwei Yu for inspiring discussions on sparse transform.

\newpage
\new{
\append{Local similarity}
Let $\mathbf{x}_1$ and $\mathbf{x}_2$ denote the two signal vectors that are reshaped from a 2D matrix or 3D tensor. In the case of evaluating denoising performance, $\mathbf{x}_1$ and $\mathbf{x}_2$ simply means signal and noise.}
\new{
The simplest way to measure the similarity between two signals is to calculate the correlation coefficient,
\begin{equation}
\label{eq:corr}
c=\frac{\mathbf{x}_1^T\mathbf{x}_2}{\parallel \mathbf{x}_1 \parallel_2 \parallel \mathbf{x}_2 \parallel_2},
\end{equation}
where $c$ is the correlation coefficient, $\mathbf{x}_1^T\mathbf{x}_2$ denotes the dot product between $\mathbf{x}_1$ and $\mathbf{x}_2$. $\parallel \cdot \parallel_2$ denotes the $L_2$ norm of the input vector. A locally calculated correlation coefficient can be used to measure the local similarity between two signals,
\begin{equation}
\label{eq:localcorr}
c(i) =  \frac{\sum_{i_w=-N_w/2}^{N_w/2} x_1(i+i_w)x_2(i+i_w)}{\sqrt{\sum_{i_w=-N_w/2}^{N_w/2} x_1(i+i_w)^2}\sqrt{\sum_{i_w=-N_w/2}^{N_w/2} x_2(i+i_w)^2}},
\end{equation}
where $x_1(i)$ and $x_2(i)$ denote the $i$the entries of vectors $\mathbf{x}_1$ and $\mathbf{x}_2$, respectively. $i_w$ denotes the index in a local window. $N_w+1$ denotes the length of each local window. The windowing is sometime troublesome, since the measured similarity is largely dependent on the windowing length and the measured local similarity might be discontinuous because of the separate calculations in windows. To avoid the negative performance caused by local windowing calculations, \cite{fomel2007localattr} proposed an elegant way for calculating smooth local similarity via solving two inverse problems.} 
\new{
The local similarity I use to evaluate denoising performance in this paper is defined as 
\begin{equation}
\label{eq:cc}
\mathbf{s}=\sqrt{\mathbf{s}_1\circ\mathbf{s}_2},
\end{equation}
where $\mathbf{s}$ is the calculated local similarity, $\circ$ denotes Hadamard (or Schur) product, and $\mathbf{s}_1$ and $\mathbf{s}_2$ come from two least-squares inverse problem:
\begin{align}
\label{eq:local1}
\mathbf{s}_1 &=\arg\min_{\tilde{\mathbf{s}}_1}\Arrowvert \mathbf{x}_1-\mathbf{X}_2\tilde{\mathbf{s}}_1 \Arrowvert_2^2, \\
\label{eq:local2}
\mathbf{s}_2 &=\arg\min_{\tilde{\mathbf{s}}_2}\Arrowvert \mathbf{x}_2-\mathbf{X}_1\tilde{\mathbf{s}}_2 \Arrowvert_2^2,
\end{align}
where $\mathbf{X}_1$ is a diagonal operator composed from the elements of $\mathbf{x}_1$: $\mathbf{X}_1=diag(\mathbf{x}_1)$ and $\mathbf{X}_2$ is a diagonal operator composed from the elements of $\mathbf{x}_2$: $\mathbf{X}_2=diag(\mathbf{x}_2)$.
Equations \ref{eq:local1} and \ref{eq:local2} are solved via shaping regularization
\begin{align}
\label{eq:local3}
\mathbf{s}_1 &= [\lambda_1^2\mathbf{I} + \mathcal{T}(\mathbf{X}_2^T\mathbf{X}_2-\lambda_1^2\mathbf{I})]^{-1}\mathcal{T}\mathbf{X}_2^T\mathbf{x}_1,\\
\label{eq:local4}
\mathbf{s}_2 &= [\lambda_2^2\mathbf{I} + \mathcal{T}(\mathbf{X}_1^T\mathbf{X}_1-\lambda_2^2\mathbf{I})]^{-1}\mathcal{T}\mathbf{X}_1^T\mathbf{x}_2,
\end{align}
where $\mathbf{\mathcal{T}}$ is a smoothing operator, and $\lambda_1$ and $\lambda_2$ are two parameters controlling the physical dimensionality and enabling fast convergence when inversion is implemented iteratively. These two parameters can be chosen as $\lambda_1  = \Arrowvert\mathbf{X}_2^T\mathbf{X}_2\Arrowvert_2$ and $\lambda_2  = \Arrowvert\mathbf{X}_1^T\mathbf{X}_1\Arrowvert_2$ \cite[]{fomel2007localattr}.
}

\bibliographystyle{seg}
\bibliography{sgk}

\newpage
\listoffigures

### 2020-09-16 sosvmf/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{Geophysical Journal International, 216, 1214-1232, (2019)}

\title{Deblending of simultaneous-source data using a structure-oriented space-varying median filter}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\author{Yangkang Chen\footnotemark[1], Shaohuan Zu\footnotemark[2]\footnotemark[3], Yufeng Wang\footnotemark[3], and Xiaohong Chen\footnotemark[3]}
\address{
\footnotemark[1]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
chenyk2016@gmail.com\\
\footnotemark[2] Modeling and Imaging Laboratory\\
Earth and Planetary Sciences\\
University of California\\
Santa Cruz, CA 95064\\
zushaohuan@qq.com\\
\footnotemark[3]State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
hellowangyf@163.com \& chenxh@cup.edu.cn \\
}

\lefthead{Chen et al.}
\righthead{SOSVMF}

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}

\begin{abstract}
In seismic data processing, the median filter\dlo{ (MF)} is usually applied along the structural direction of seismic data in order to attenuate erratic or spike-like noise. The performance of a structure-oriented median filter\dlo{ (SOMF)} highly depends on the accuracy of \new{the} estimated local slope from the noisy data. When local slope contains significant error, which is usually the case for noisy data, the \dlo{SOMF}\wen{structure-oriented median filter} will still cause severe damages to useful energy. \dlo{In this paper, we}\wen{We} propose a type of \dlo{SOMF}\wen{structure-oriented median filter} that can effectively attenuate spike-like noise even when the local slope is not accurately estimated, which we call \dlo{SOSVMF}\wen{structure-oriented space-varying median filter}. \wen{A structure-oriented space-varying median filter} can adaptively squeeze and stretch the window length of the \dlo{MF }\wen{median filter }when applied in the locally flattened dimension of an input seismic data in order to deal with the dipping events caused by inaccurate slope estimation. We show the key difference among different types of median filters in detail and demonstrate the principle of the \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} method. We apply the \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} method to remove the spike-like blending noise arising from the simultaneous source acquisition. Synthetic and real data examples show that \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} can significantly improve the signal preserving performance for curving events in the seismic data. The \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} can also be easily embedded into an iterative deblending procedure based on the shaping regularization framework and can help obtain much improved deblending performance. 
\end{abstract}

\section{Keywords}
Seismic signal processing, noise attenuation, median filter

\maketitle

\section{Introduction}
Simultaneous shooting has been a long-standing research topic in the industry, aiming at boosting the acquisition efficiency by significantly shortening the acquisition time period as well as improving subsurface sampling by increased shot density \cite[]{beasleycj2008,wapenaark2012,abma2014,amundsen2017multi,shaohuan2017jag,asgedom2017rough,zhang2017improving,kim2017efficient,wang2017building,wujuan2018jse1}. Because of the \dlo{much saved}\wen{reduced} acquisition cost, it supports more frequent\dlo{ly periodical} data recording in time-lapse seismic monitoring. Due to the \dlo{tremendously }improved spatial shot sampling, it makes the high-resolution subsurface imaging and inversion more achievable.  All the aforementioned benefits, however, are compromised by the intense \dlo{crosstalk}\wen{interference} noise introduced during simultaneous shooting \cite[]{panagiotis20122,arazthesis2012,qushan2014,sixuethesis2014,sixue2015,yangkang2016irr5d,yatong2018gji,baimin2018jse2,yatong2018dbi,yatong2018jse}. To deal with the strong blending noise in simultaneous source data, one can either develop new algorithms to separate the blended records so that the subsequent processing and workflows do not need to be changed, which is called deblending, or to design new workflows for migrating the blended data directly regardless of the intense interference, which is called direct imaging \cite[]{verschuur2011,shuwei2016vscan,shaohuan2017,baimin2017jse1,wujuan2018cg1,baimin2018cg,baimin2018jse1,qingchen2018gji,qingchen2018tgrs}.

There are two main types of deblending approaches. The first is based on filtering, which simply treats the blending interference as noise and uses denoising algorithms to remove it \cite[]{mostafa2016geo,mostafa2016jag,mostafa2016bssa,mostafa2017geo}. These methods include the median filtering based approaches \cite[]{mediandeblend,yangkang2015svmf,shuwei2016,weilin2018grsl}, adaptive subtraction methods \cite[]{spitz2008,kim2009}, and dip filtering based methods \cite[]{hampson2008}.
The second is based on inversion.  The inversion based algorithms take advantage of iterative solvers to solve the ill-posed inverse problem in deblending.  Regularization strategies should be used to \dlo{guarantee the convergence during iteration}\wen{constrain the model to be the desired solution}. A number of methods based on different types of constraints have been developed in the literature, e.g., the seislet constraint \cite[]{yangkang20142}, the curvelet constraint \cite[]{kumar2015source,qushan2016,shaohuan2016}, the Fourier constraint \cite[]{abma2015}, the rank constraint \cite[]{jinkun2016,yatong2017ieee}, the hybrid rank-sparsity constraint \cite[]{shaohuan2017gji}, and the hybrid mask-sparsity constraint \cite[]{yatong2017pocs}. \wen{Here ``seislet constrint'' denote ``seislet-domain sparsity constraint''. } While the filtering based methods are more computational efficient and easier to implement, the inversion-based approaches usually lead to better deblending performance \cite[]{borselen2012,shaohuan2016}.

To date, there are also \dlo{a lot of}\wen{many} reported trials for directly migrating the simultaneous source data. Because of the strong \dlo{crosstalk}\wen{interference} noise, the migrated images might contain distinct artifacts if no extra implementation step is introduced into the migration process. \dlo{?  utilized the inversion based migration strategy, i.e., the least-squares migration to suppress the migration artifacts to some extent. To further attenuate the artifacts, they carefully designed a deblurring filter to constrain the least-squares migration to be structurally smooth.} \cite{berkhout2012} discussed the illumination aspect of direct imaging of simultaneous source data. \cite{zhiguang2016} proposed a new direct imaging method that is based on least-squares reverse time migration\dlo{ (LSRTM)} and structural enhancing operator \cite[]{liuyang2010}. Different from the preconditioning constraint that was used in \cite{daiwei2011}, \cite{zhiguang2016} developed a new iterative solver to solve the \dlo{LSRTM}\wen{least-squares reverse time migration} related inverse problem, which is based on the shaping regularization framework. To tackle the smearing problem of structural smoothing operator in the \dlo{LSRTM}\wen{least-squares reverse time migration} method proposed by \cite{zhiguang2016}, \cite{yangkang2017lsrtm} developed a local singular spectrum analysis (SSA) constraint to preserve the edges and discontinuities on the image. While those imaging methods are promising to make the future imaging framework more flexible, most reported successes are stuck on the synthetic test. A lot of researchers are still working hard to push the direct imaging technique from simulation to practical applications \cite[]{dutta2017lsrtm,lichuang2018}.

In this paper, we are aiming at introducing a novel median filtering method for either separating the simultaneous sources in a fast one-step way, or iteratively improving the traditional shaping regularized deblending approaches by constructing a more powerful shaping operator. Since the new method is \dlo{in}\wen{by} nature a type of median filter, it is worth mentioning some existing\dlo{ ways} \wen{methods} that use median filtering\dlo{ methods} for deblending. \cite{mediandeblend} proposed a multi-dimensional vector median filter for separating \dlo{blended }simultaneous-source data. A dip scanning step is first performed so that a vector median filter can be applied along the structural direction. \cite{yangkang2015svmf} developed a space-varying median filter to deal with curved events in seismic data. The filter length varies spatially so that noise is removed using a long filter length and the signal is preserved using a relatively smaller filter length. \cite{shuwei2016} proposed a structure-oriented median filter to maximize the effectiveness of a median filter when processing a complicated dataset. Both methods in either \cite{mediandeblend} or \cite{shuwei2016} can be considered as structure-oriented filtering, which requires an sufficiently-accurate slope estimation. However, when the slope is not properly estimated, e.g., in the case of strong ambient noise and blending noise, the structural filtering strategy would fail because those filters will tend to damage signal energy.

We investigate the reason why the structural filtering fails when the slope is not accurate enough. The principle of the structural filtering is to create a local window along the structural direction, or in other words, to create a locally flattened gather to apply the 1D median or mean filter. When the slope is accurate, e.g., using the plane-wave destruction\dlo{ (PWD)} algorithm \cite[]{fomel2002pwd}, the local gather is exactly flattened. However, when the slope is not precise enough, the local gather still contains curved events. In this case, we take advantage of the \dlo{space varying}\wen{spatially varying} median filter to deal with the slightly curved events in the flattened dimension. The proposed method is thus capable of preserving more useful energy than the traditional structural filtering method.

The paper is organized as follows, we first introduce the basics of median filtering\dlo{ (MF)} and structure-oriented filtering\dlo{ (SOMF)}. Then, we focus on introducing the proposed structure-oriented space-varying median filtering method\dlo{ (SOSVMF)}. We also introduce the way we imbed the proposed filtering method in the shaping regularized iterative deblending framework. Next, we use several synthetic and real data examples to show the potential of the proposed method, either in obtaining a fast simultaneous source separation, or in improving the deblending performance \dlo{through}\wen{in} an iterative fashion. Finally, we draw some key conclusions at the end of the paper.

\section{Structural-oriented space-varying median filter (SOSVMF)}
\subsection{Median filter}
A median filter\dlo{ (MF)} can be used to obtain successful performance in rejecting \dlo{impulse}\wen{impulsive} (spiky) noise, which has \dlo{extreme}\wen{anomalous} value compared with neighboring values. Compared with the commonly known smoothing filter, the median filter enjoys several advantages such as preserving edges, being less sensitive to \dlo{extreme}\wen{anomalous} values and being able to be applied repeatedly. Given a 2D signal, e.g., the waveform\wen{s} recorded by \dlo{Laser Doppler interferometer receiver}\wen{geophone arrays}, a 1D median filter is applied along the spatial direction and each row of the waveform matrix is filtered one by one. Mathematically, a median filter can be expressed using the following formula \cite[]{yangkang2015svmf} when applied to a 2D signal: \dlo{$\hat{u}_{i,j}=\arg\min_{u_m\in U_{i,j}}\sum_{l=1}^{L}\Arrowvert u_m-u_l \Arrowvert_1$}
\wen{\begin{equation}
\label{eq:mf1}
\min_{u_m\in U_{i,j}}\sum_{l=1}^{L}\Arrowvert u_m-u_l \Arrowvert_1,
\end{equation}}
\dlo{where $\hat{u}_{i,j}$ is the}\wen{The solution of minimization problem \ref{eq:mf1} is the} output value for location $x_{i,j}$. $U_{i,j}=\{u_1,u_2,\cdots,u_L\}$ denotes the 1D \dlo{filering}\wen{filtering} window. $i,j$ are the position indices in a 2D profile. $l$ and $m$ are both indices in the filtering window. \wen{Both $u_l$ and $u_m$ are temporary variables.} $L$ is the length of the filtering window. \wen{Simply speaking, for each point in the 2D data, the median filter substitutes it with the median of neighbor points included by the window with size $L$. The process of $\min_{u_m}\sum_{l=1}^{L}\Arrowvert u_m-u_l \Arrowvert_1$ corresponds to finding the median in the window constructed by $\{u_1,u_2,u_3,\cdots,u_L\}$.  }

\subsection{Median filter along the structural direction}
Median filtering has a remarkable capability for attenuating spike-like noise. However, the median filter might still cause some damage\dlo{s} to useful components when the data is highly non-stationary in the space direction. Considering that the recorded waveforms may have structural patterns, if the median filter is applied along the structural direction, the damage can be minimized. We utilize a way that is used in reflection seismic data processing to flatten the recorded waveform data in a local manner. \wen{The flattening process is based on the predictability between neighbor traces. In the following context, we will introduce in details the flattening process.} Then, the median filter can be applied in the flattened dimension to maximize its effectiveness.

%Structure-oriented filtering has obtained much attention recently because it takes advantage of the structure information of seismic data when applying a common smoothing or median filter. The structure-oriented filter requires a pre-calculated local slope field of the seismic data in order to apply a 1D mean or median filter in the flattened dimension. However, in the case of low signal-to-noise ratio, the local slope is difficult to obtain, which will affect the subsequent filtering along the structure direction. In this study, we show that inaccurate slope estimation will make the flattened dimension slightly curved. These curved events will make 1D median filter incapable of attenuating spike noise while preserving useful energy.

Flattening the waveforms is basically a data mapping process. We perform the data mapping by a \dlo{recursive predicting strategy}\wen{recursive prediction strategy}. We recall that the target of the data mapping is to create a flattened gather in each local window centered at each trace. Let the width of the window to be $2N+1$, then the central trace $\mathbf{d}_i$ can be predicted from its $j$th ($j\le N$) right trace $\mathbf{d}_{i+j}$ in such a recursive manner,
\begin{equation}
\label{eq:recur}
\mathbf{d}_i=\mathbf{P}_{i+1,i}\cdots\mathbf{P}_{i+j-1,i+j-2}\mathbf{P}_{i+j,i+j-1}\mathbf{d}_{i+j}, 
\end{equation}
\wen{where $\mathbf{P}_{i,j}$ denotes a prediction operator to predict trace $\mathbf{d}_i$ from trace $\mathbf{d}_j$.} For predicting trace $\mathbf{d}_i$ from its left trace, we use a similar recursive formula,
\begin{equation}
\label{eq:recur}
\mathbf{d}_i=\mathbf{P}_{i-1,i}\cdots\mathbf{P}_{i-j+1,i-j+2}\mathbf{P}_{i-j,i-j+1}\mathbf{d}_{i-j}. 
\end{equation}

Figure \ref{fig:demo} shows a sketch of the trace prediction process \wen{for $N=1$}. Each trace is associated with a local flattened window. The prediction process transforms the curving event in the local window to a flattened event. More details regarding the trace prediction and the flattening operator can be found in \cite{liuyang2010}. Figure \ref{fig:synth0,synth-cube} shows a demonstration of the structure-oriented processing. Figure \ref{fig:synth0} is the data with clear structural patterns. Figure \ref{fig:synth-cube} shows the locally flattened data \wen{in the third dimension} by predicting each trace from its left and right neighboring traces. The median filter is then applied along the third dimension (prediction axis) to remove erratic or spike-like noise. The 2D section defined by the axes ``Time (ms)'' and ``Position (m)'' indicates the original profile so it contains curving events. \wen{It is the same as the profile shown in Figure \ref{fig:synth0}.} The 2D section defined by the axes ``Time (ms)'' and ``\dlo{Position (m)}\wen{Prediction (trace)}'' indicates the flattened data. \wen{The 2D section defined by the axes ``Prediction (trace)'' and ``Position (m)'' indicates the constant Time slice.} \wen{The data shown in Figure \ref{fig:synth0,synth-cube} can be considered as a common offset data or a migrated image. The curving events denote the curving subsurface reflectors.} It is worth noting that the flattening strategy also works for crossing events\wen{, but the median filters may damage the useful energy due to the anomalous amplitude when crossing events exist.}

\subsection{Median filter along the structural direction with a variable window length}
When the data is not flattened well, e.g., when the local slope of the waveform profile is not estimated accurately due to the strong spike-like noise \wen{(e.g., using the plane-wave destruction algorithm \cite[]{fomel2002pwd})}, the traditional median filter with a constant filter length will still cause some damages. Figures \ref{fig:dip} and \ref{fig:dip-n} show two estimated slope sections from the clean data and noisy data respectively. It is obvious that the two local slope maps have distinct differences. \wen{The color indicates the slope value. Warm (red) color indicates high positive slope and cool (blue) color indicates high negative slope. Positive slope and negative slope mean opposite dipping directions.} Figures \ref{fig:synths-cube} and \ref{fig:synths-cuben} show the flattened data using true and estimated local slopes. For a better comparison, we select three flattened gathers for different space locations from Figures \ref{fig:synths-cube} and \ref{fig:synths-cuben}, respectively, and show them in Figure \ref{fig:flat1,flat2,flat3,flat1-n,flat2-n,flat3-n}. When using the true local slope, we can clearly observe that the data are exactly flattened and events in the prediction dimension are exactly horizontal. However, when we use the inaccurate local slope that is estimated from the observed noisy data, the prediction based flattening operator cannot obtain a perfect performance. The events in the prediction dimension are not exactly horizontal, but are more or less curved. \new{Note that in Figures \ref{fig:flat3} and \ref{fig:flat3-n}, the first blank trace is caused by the boundary trace prediction. For example, if a seismic section contains 98 traces, then the predicted 90th trace from its 9th right neighbor trace is a zero trace.}

The space-varying median filter \dlo{(SVMF) }can be used in such case where the events are not perfectly flattened. For \dlo{SVMF}\wen{space-varying median filter}, $L$ becomes $L_{i,j}$, varying with respect to location $x_{i,j}$. The new filtering expression is, \dlo{$\hat{v}_{i,j} = \arg\min_{v_{m}\in U_{i,j} }\sum_{l=1}^{L_{i,j}} \Arrowvert v_{m} -v_l \Arrowvert_p$}
\wen{\begin{equation}
\label{eq:svmf1}
\min_{v_{m}\in U_{i,j} }\sum_{l=1}^{L_{i,j}} \Arrowvert v_{m} -v_l \Arrowvert_1.
\end{equation}}
\dlo{where }\wen{The solution} $\hat{v}_{i,j}$ is the output value for location $x_{i,j}$ after applying a \dlo{SVMF}\wen{space-varying median filter}, $U_{i,j}=\{v_1,v_2,\cdots,v_{L_{i,j}}\}$ denotes the local filtering window in the case of \dlo{SVMF}\wen{space-varying median filter}. The filter length $L_{i,j}$ can be \dlo{chosen based on the criterion proposed in}\wen{adaptively chosen according to the signal reliability $s^L_{i,j}$ \cite[]{yangkang2015svmf}. Signal reliability is a local attribute to indicate how reliable a data point is considered as a signal point. The signal reliability can be defined as the local similarity \cite[]{fomel2007localattr} between the initially filtered data $u^L_{i,j}$ with a window length $L$ and the original data $u_{i,j}$, \dlo{$s^L_{i,j} = \mathbf{S} [u^L_{i,j}, u_{i,j}]$}
\wen{\begin{equation}
\label{eq:simi}
s^L_{i,j} = S (u^L_{i,j}, u_{i,j}).
\end{equation}}
Here, \wen{$S(\mathbf{x},\mathbf{y})$} denotes the local similarity between $\mathbf{x}$ and $\mathbf{y}$.} \wen{Here, the operator $S$ denotes the process of calculating the local similarity between two data sets: $u^L_{i,j}$ and $u_{i,j}$. The selection of the initial filter length requires some human experience and trials. } \wen{The initially filtered data means the filtered data using a conventional median filtering method.} \wen{Later, we will illustrate how the signal reliability/local similarity looks like. }The criterion for defining the filter length is expressed as follows: 
\begin{equation}
\label{eq:svmf2}
L_{i,j}=\left\{\begin{array}{ll}
L+l_1,\quad 0\quad \le |s^L_{i,j}|\le s_1 \\
L+l_2,\quad s_1 < |s^L_{i,j}|< s_2 \\
L,\quad \quad\quad s_2 \le |s^L_{i,j}|\le s_3 \\
L-l_3,\quad s_3 <|s^L_{i,j}| < s_4\\
L-l_4,\quad s_4 \le|s^L_{i,j}| \le s_{max}
\end{array}\right.,
\end{equation}
where $l_1$, $l_2$, $l_3$, and $l_4$ are predefined parameters corresponding to the increments or decrements of the length of filter window and are generally chosen as 4, 2, 2, and 4 in default, respectively. \dlo{, $s^L_{i,j}$ is the \emph{signal reliability} (SR) for point $x_{i,j}$, which can be defined as the local similarity ? between the initially filtered data $u^L_{i,j}$ with a window length $L$ and the original data $u_{i,j}$, }$s_1$, $s_2$, $s_3$, and $s_4$ are four thresholds, and are empirically chosen as $s_1=0.15s_{max}$, $s_2=0.25s_{max}$, $s_3=0.75s_{max}$, and $s_4=0.85s_{max}$.  $s_{max}$ denotes the maximum value of the similarity map. \dlo{Appendix A}\wen{The appendix} provides a brief review of the calculation of local similarity.

\wen{To facilitate an easier understanding of the space-varying median filtering, more specifically the relation among initially filtered data, local similarity, variable filter length, we draw an illustrative picture shown in Figure \ref{fig:svmf}. Figure \ref{fig:svmf}(a) denotes the noisy data. Figure \ref{fig:svmf}(b) shows the map of constant filter length.  Figures \ref{fig:svmf}(a) and  \ref{fig:svmf}(b) are used to generate the  initially filtered data shown in  \ref{fig:svmf}(c). Using equation \ref{eq:simi}, from the original data and the initially filtered data, we can calculate the local similarity map. Utilizing equation \ref{eq:svmf2}, we can calculated the map of variable filter length. With the map of variable filter length, we can obtain the finally filtered data shown in Figure  \ref{fig:svmf}(f). From this illustration, it is clear that the local similarity clearly detect the main distribution of the useful reflection energy. Those areas with better signal preservation after the initial median filtering are revealed by higher local similarity. The map of variable filter length clearly shows that those noise areas are dealt with very longer filter length while those signal areas correspond to relatively shorter (safer) filter length. }

Applying the \dlo{SVMF}\wen{space-varying median filter} in the imperfectly flattened gathers, we can preserve much useful energy that remains curved. Figure \ref{fig:flat1-n-mf,flat2-n-mf,flat3-n-mf,flat1-n-svmf,flat2-n-svmf,flat3-n-svmf} shows a comparison between \dlo{MF }\wen{median filter }and \dlo{SVMF}\wen{space-varying median filter} in attenuating the spike-like noise when applied to the flattened gathers as shown in Figure \ref{fig:flat1,flat2,flat3,flat1-n,flat2-n,flat3-n} from (d) to (f). It is obvious that \dlo{SVMF}\wen{space-varying median filter} helps preserve the energy much better than the \dlo{MF}\wen{median filter}. \wen{To further confirm this conclusion, we also plot the removed noise sections in Figure \ref{fig:flat1-n-mf-dif,flat2-n-mf-dif,flat3-n-mf-dif,flat1-n-svmf-dif,flat2-n-svmf-dif,flat3-n-svmf-dif}. It is more salient that the median filter damages more useful energy than the space-varying median filter.}

\subsection{Including the \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} into an inversion framework}
The blending process can be summarized as the following equation: 
\begin{equation}
\label{eq:blend}
\mathbf{d}=\Gamma\mathbf{m},
\end{equation}
where $\mathbf{d}$ is the blended data, $\Gamma$ is the blending operator, and $\mathbf{m}$ is the unblended data.
The formulation of $\Gamma$ has been introduced in \cite{arazthesis2012} in detail. When considered in time domain, $\Gamma$ corresponds to blending different \dlo{shot records onto one receiver record}\wen{receiver signals into one channel} according to the shot schedules of different shots. Deblending amounts to inverting equation \ref{eq:blend} and recovering $\mathbf{m}$ from $\mathbf{d}$.

%The deblending process refers to solving equation \ref{eq:blend} for $\mathbf{m}$. One approximation of the solution would be simply approximating the inverse of $\Gamma$ by its adjoint $\Gamma^T$:
%\begin{equation}
%\label{eq:deblend}
%\hat{\mathbf{m}}_{pseudo}=\Gamma^T\mathbf{d}.
%\end{equation} 
%Equation \ref{eq:deblend} refers the commonly known \emph{pseudo-deblending}, \emph{passive separation}, and \emph{combing}. The three terms are widely used in the literature to denote the same process.

%There have been many methods in the literature for seeking the true solution of equation \ref{eq:blend} based on inversion. 
Because of the ill-posed property of this problem, all inversion methods require some constraints. \cite{yangkang20142} proposed a general iterative deblending framework via shaping regularization \cite{fomel2007shape}. The iterative deblending is expressed as:
\wen{
\begin{equation}
\label{eq:iter}
\mathbf{m}_{n+1} = \mathbf{C}[\mathbf{m}_n+\mathbf{B}[\mathbf{d}-\Gamma\mathbf{m}_n]],
\end{equation}
where $\mathbf{C}$ is the shaping operator}, which provides some constraints on the model, and $\mathbf{B}$ is the backward operator, which approximates the inverse of $\Gamma$. The shaping regularization framework offers us much freedom in constraining an under-determined problem by allowing different types of constraints.  In this paper, the backward operator is simply chosen as $\lambda\Gamma^*$, where $\lambda$ is a scale coefficient closely related with the blending fold, and $\Gamma^*$ stands for the adjoint operator of $\Gamma$ (or the pseudo-deblending operator). For example, $\lambda$ can be optimally chosen as $1/2$ in a two-source dithering configuration \cite[]{yangkang20142,arazthesis2012}. %In the next two sections, we will first introduce the conventional way for choosing the $\mathbf{S}$ and then propose a novel way for designing the $\mathbf{S}$.

Given a sparsity or rank constraint based shaping operator, we are proposing the hybrid shaping operator, which is constructed by cascading the  structure-oriented space-varying median filter and the rank constraint based shaping operators. \wen{During the iterations, we need to vary the filter length $L$ with each iteration, e.g., starting from a relatively large $L$ and decreasing it to 1.} \wen{It is worth noting that the median filter based methods can only be effective in filtering but not effective in inversion if not combined with other constraints. It is because the median filter is very powerful in rejecting impulsive noise but is not convenient to control for signal preservation.}

\inputdir{./}
\plot{demo}{width=0.9\textwidth}{Sketch of the trace prediction process \wen{for $N=1$}.}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.5\columnwidth]{Fig/synth0}
    \label{fig:synth0}}  \\
  \subfloat[]{\includegraphics[width=0.5\columnwidth]{jy/Fig/synth-cube}
    \label{fig:synth-cube}}          
   \caption{A simple demonstration of structure-oriented processing. (a) Input data. (b) Locally flattened domain. The 2D section defined by the axes ``Time (ms)'' and ``Position (m)'' indicates the original profile so it contains curving events. The 2D section defined by the axes ``Time (ms)'' and ``\dlo{Position (m)}\wen{Prediction (trace)}'' indicates the flattened data. \wen{The 2D section defined by the axes ``Prediction (trace)'' and ``Position (m)'' indicates the constant Time slice.} }
   \label{fig:synth0,synth-cube}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.25\columnwidth]{jy/Fig/synth}
    \label{fig:sig}}  
  \subfloat[]{\includegraphics[width=0.25\columnwidth]{jy/Fig/dip}
    \label{fig:dip}} 
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{jy/Fig/synth-cube}
    \label{fig:synths-cube}} \\    
  \subfloat[]{\includegraphics[width=0.25\columnwidth]{jy/Fig/synth-n}
    \label{fig:sig-n}} 
  \subfloat[]{\includegraphics[width=0.25\columnwidth]{jy/Fig/dip-n}
    \label{fig:dip-n}}   
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{jy/Fig/synths-cuben}
    \label{fig:synths-cuben}}           
   \caption{(a) Clean data. (b) Slope estimated from (a). (c) Flattened domain of (a). (d) Noisy data. (e) Slope estimated from (d). (f) Flattened domain of (d).}
   \label{fig:sig,dip,synth-cube,sig-n,dip-n,synths-cube}
\end{figure}

\inputdir{jy}

\multiplot{6}{flat1,flat2,flat3,flat1-n,flat2-n,flat3-n}{width=0.29\textwidth}{A comparison of ``flattened" local windows (predicted dimension) for different space locations. (a)-(c) Flattened gathers for traces 9, 50, 90, using the accurate slope. (d)-(f) ``Flattened" gathers for traces 9, 50, 90, using the estimated slope.}

\inputdir{.}
\plot{svmf}{width=0.9\textwidth}{\wen{An illustration of the space-varying median filter. (a) Raw noisy data. (b) A map of constant filter length. (c) Initially filtered data using the constant filter length shown in (b). (d) Calculated local similarity map from (a) and (c) using equation \ref{eq:simi}. (e) Calculated map of variable filter length using equation \ref{eq:svmf2}. (f) Filtered data using the variable filter length shown in (e).}  }

\inputdir{jy}
\multiplot{6}{flat1-n-mf,flat2-n-mf,flat3-n-mf,flat1-n-svmf,flat2-n-svmf,flat3-n-svmf}{width=0.29\textwidth}{A denoising comparison of ``flattened" local windows (predicted dimension) using estimated slope for different space locations. (a)-(c) Denoised gathers for traces 9, 50, 90, using the \wen{median filter}. (d)-(f) \dlo{``Flattened"}\wen{Denoised} gathers for traces 9, 50, 90, using the \dlo{SVMF}\wen{space-varying median filter}. \wen{Note that although (c) is cleaner, the curving signals are serious damaged.}}

\multiplot{6}{flat1-n-mf-dif,flat2-n-mf-dif,flat3-n-mf-dif,flat1-n-svmf-dif,flat2-n-svmf-dif,flat3-n-svmf-dif}{width=0.29\textwidth}{\wen{A comparison of removed noise. (a)-(c) Removed noise for traces 9, 50, 90, using the median filter. (d)-(f) Removed noise for traces 9, 50, 90, using the space-varying median filter. Note that the median filter removes more coherent energy.}}

\inputdir{hyper}
\multiplot{4}{hyper,hyper-n,hdip,hdip-n}{width=0.4\textwidth}{(a) Clean data. (b) Noisy data with spike-like blending noise. (c) Estimated slope from the clean data. (d) Estimated slope from the noisy data. }

\multiplot{2}{hflat0,hflat-n0,hflat-n-mf0,hflat-n-svmf0}{width=0.45\textwidth}{(a) Flattened dimension of the clean data using the accurate slope. (b) Flattened dimension of the noisy data using the inaccurate slope. (c) Filtered data using \dlo{MF }\wen{median filter }in the flattened domain. (b) Filtered data using \dlo{SVMF}\wen{space-varying median filter} in the flattened domain.  }

\multiplot{2}{hflat-z0,hflat-n-z0,hflat-n-mf-z0,hflat-n-svmf-z0}{width=0.45\textwidth}{\wen{Zoomed comparison of Figure \ref{fig:hflat0,hflat-n0,hflat-n-mf0,hflat-n-svmf0}. (a) Flattened dimension of the clean data using the accurate slope. (b) Flattened dimension of the noisy data using the inaccurate slope. (c) Filtered data using median filter in the flattened domain. (b) Filtered data using space-varying median filter in the flattened domain. } }

\multiplot{4}{hyper-mf0,hyper-svmf0,hyper-somf0,hyper-sosvmf0}{width=0.38\textwidth}{(a) Deblended data using \dlo{MF}\wen{median filter}. (b) Deblended data using \dlo{SVMF}\wen{space-varying median filter}. (c) Deblended data using \dlo{SOMF}\wen{structure-oriented median filter}. (d) Deblended data using \dlo{SOSVMF}\wen{structure-oriented space-varying median filter}. \wen{Note that since all median filters are only applied once, so there are several spikes left. The one-step processing is efficient but can be improved through multiple iterations (e.g., in iterative deblending). }  }

\multiplot{4}{hyper-mf-z0,hyper-svmf-z0,hyper-somf-z0,hyper-sosvmf-z0}{width=0.4\textwidth}{\wen{Zoomed comparison of Figure \ref{fig:hyper-mf0,hyper-svmf0,hyper-somf0,hyper-sosvmf0}. (a) Deblended data using median filter. (b) Deblended data using space-varying median filter. (c) Deblended data using structure-oriented median filter. (d) Deblended data using structure-oriented space-varying median filter.}  }

\multiplot{4}{hyper-mf-n,hyper-svmf-n,hyper-somf-n,hyper-sosvmf-n}{width=0.35\textwidth}{(a)-(d) Removed blending noise sections corresponding to Figure\wen{s} \ref{fig:hyper-mf0,hyper-svmf0,hyper-somf0,hyper-sosvmf0} (a)-(c), respectively. }

\inputdir{field}
\multiplot{2}{shot-n,sdip-n}{width=0.48\textwidth}{(a) Simultaneous source data.  (b) Slope estimated from the raw data.  }

\multiplot{4}{shot-mf,shot-svmf,shot-somf,shot-sosvmf}{width=0.38\textwidth}{(a) Deblended data using \dlo{MF}\wen{median filter}. (b) Deblended data using \dlo{SVMF}\wen{space-varying median filter}. (c) Deblended data using \dlo{SOMF}\wen{structure-oriented median filter}. (d) Deblended data using \dlo{SOSVMF}\wen{structure-oriented space-varying median filter}.}

\multiplot{4}{shot-mf-n-0,shot-svmf-n-0,shot-somf-n-0,shot-sosvmf-n-0}{width=0.38\textwidth}{(a) Removed blending noise using \dlo{MF}\wen{median filter}. (b) Removed blending noise using \dlo{SVMF}\wen{space-varying median filter}.  (c) Removed blending noise using \dlo{SOMF}\wen{structure-oriented median filter}. (d) Removed blending noise using \dlo{SOSVMF}\wen{structure-oriented space-varying median filter}.}

\multiplot{4}{shot-mf-s,shot-svmf-s,shot-somf-s,shot-sosvmf-s}{width=0.38\textwidth}{A comparison of local similarity between deblended data and removed blending noise. (a) Local similarity using \dlo{MF}\wen{median filter}. (b) Local similarity using \dlo{SVMF}\wen{space-varying median filter}.  (c) Local similarity using \dlo{SOMF}\wen{structure-oriented median filter}. (d) Local similarity using \dlo{SOSVMF}\wen{structure-oriented space-varying median filter}.}

\section{Examples}
%In this section, we not only show the performance of the SOSVMF in attenuating blending noise
%that results from the simultaneous source acquisition, we also show an example on rejecting general spike-like noise.

%We first test the performance of the SOSVMF in attenuating general spike-like noise. 
We first test the \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} method on a simple synthetic example. Figure \ref{fig:hyper} shows a simple hyperbolic synthetic example. \wen{We create the data using the Kirchhoff 2-D/2.5-D modeling method with analytical Green's functions, introduced in \cite{haddon1981use}.} Figure \ref{fig:hyper-n} shows the noisy data with some
blending noise. Figure \ref{fig:hdip} shows the slope estimated from the clean data and Figure \ref{fig:hdip-n} shows the slope estimated from the noisy data. The strong noise makes the slope estimation inaccurate. Figures \ref{fig:hflat0} and \ref{fig:hflat-n0} show a comparison between the flattened unblended data using accurate slope and flattened blended data using inaccurate local slope, respectively. From Figure \ref{fig:hflat0}, we can observe that the data is flattened well locally using the accurate local estimation (from the unblended data). From Figure \ref{fig:hflat-n0}, it is obvious that the events in the flattened dimension are not horizontal, which indicates an imperfect local flattening.  Figures \ref{fig:hflat-n-mf0} and \ref{fig:hflat-n-svmf0} show a comparison between the filtered data using the \dlo{MF }\wen{median filter }and \dlo{SVMF}\wen{space-varying median filter}, respectively. Both \dlo{MF }\wen{median filter }and \dlo{SVMF}\wen{space-varying median filter} are applied along the flattened dimension (along the ``prediction'' axis). It is clear that some energy is damaged using the \dlo{MF }\wen{median filter }and the signals are preserved well using the \dlo{SVMF}\wen{space-varying median filter} method, as indicated by the white arrow in Figure \ref{fig:hflat0,hflat-n0,hflat-n-mf0,hflat-n-svmf0}. \wen{For a clearer comparison, we show the zoomed data of Figure \ref{fig:hflat0,hflat-n0,hflat-n-mf0,hflat-n-svmf0} in Figure \ref{fig:hflat-z0,hflat-n-z0,hflat-n-mf-z0,hflat-n-svmf-z0}.} Figure \ref{fig:hyper-mf0,hyper-svmf0,hyper-somf0,hyper-sosvmf0} shows a deblending comparison between the \dlo{MF,}\wen{median filter,} \dlo{SVMF}\wen{space-varying median filter}, \dlo{SOMF}\wen{structure-oriented median filter}, and \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} methods, respectively. From Figure \ref{fig:hyper-mf0,hyper-svmf0,hyper-somf0,hyper-sosvmf0}, we can see that the traditional \dlo{MF }\wen{median filter }results in the \dlo{lagest}\wen{largest} damages, which is followed by \dlo{SVMF}\wen{space-varying median filter}. \dlo{SOMF}\wen{structure-oriented median filter} preserves most signals but still causes some damages, as indicated by the white arrow. Among the four results, the \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} result is the best in preserving dipping energy and rejecting spike-like blending noise. \wen{A zoomed comparison of Figure \ref{fig:hyper-mf0,hyper-svmf0,hyper-somf0,hyper-sosvmf0} is shown in Figure \ref{fig:hyper-mf0,hyper-svmf0,hyper-somf0,hyper-sosvmf0}.} Figure \ref{fig:hyper-mf-n,hyper-svmf-n,hyper-somf-n,hyper-sosvmf-n} shows the removed blending noise corresponding to the four aforementioned methods, which confirms the observation from Figure \ref{fig:hyper-mf0,hyper-svmf0,hyper-somf0,hyper-sosvmf0} that \dlo{MF,}\wen{median filter,} \dlo{SVMF}\wen{space-varying median filter}, and \dlo{SOMF}\wen{structure-oriented median filter} all result in more or less signal leakage \cite[]{yangkang2015ortho} to the noise sections. In this example, we use the signal-to-noise ratio (SNR) to quantitatively compare the deblending performance using different methods:
\begin{equation}
\label{eq:diff}
SNR=10\log_{10}\frac{\Arrowvert \mathbf{m}_{clean} \Arrowvert_2^2}{\Arrowvert \mathbf{m}_{clean} -\mathbf{m}\Arrowvert_2^2},
\end{equation}
where $\mathbf{m}_{clean}$ denotes the exact solution, or the unblended data. $\mathbf{m}$ denotes the deblended data. Using this metic, we calculate the SNRs of the blended data, deblended data using \dlo{MF,}\wen{median filter,} \dlo{SVMF}\wen{space-varying median filter}, \dlo{SOMF}\wen{structure-oriented median filter}, and \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} methods as 1.62 dB, 5.46 dB, 8.63 dB, 12.46 dB, and 16.55 dB, respectively. The \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} method obtains the highest SNR.

The next example is a field data test. Figure \ref{fig:shot-n} shows the a common receiver gather that contains blending noise. \wen{The data is a benchmark testing data shared by BGP, China.} Figure \ref{fig:sdip-n} shows the local slope map calculated from the raw data using the \dlo{PWD}\wen{plane-wave destruction} algorithm. The deblended results using four methods are shown in Figure \ref{fig:shot-mf,shot-svmf,shot-somf,shot-sosvmf}. The removed blending noise corresponding to the four methods are shown in Figure \ref{fig:shot-mf-n-0,shot-svmf-n-0,shot-somf-n-0,shot-sosvmf-n-0}. Combining Figures \ref{fig:shot-mf,shot-svmf,shot-somf,shot-sosvmf} and \ref{fig:shot-mf-n-0,shot-svmf-n-0,shot-somf-n-0,shot-sosvmf-n-0}, it is easy to conclude that both \dlo{MF }\wen{median filter }and \dlo{SVMF}\wen{space-varying median filter} methods cause a large amount of damaged energy, the \dlo{SOMF}\wen{structure-oriented median filter} method causes relatively less damaged energy around the large-offset areas, and the \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} method causes negligible damaged energy. Note that the signal damages are highlighted by the white arrows in Figure \ref{fig:shot-mf-n-0,shot-svmf-n-0,shot-somf-n-0,shot-sosvmf-n-0}. In this example, the exact solution is unknown, thus we cannot use the quantitative metric that is used previously to compare the performance quantitatively. But we use the local similarity to measure the signal damage. The local similarity between the denoised (deblended) and removed noise sections are calculated to detect the signal damage for a denoising (deblending) algorithm, as proposed in \cite{yangkang2015ortho}. High anomalies in the local similarity map indicates a more servere signal damage. The most distinct advantage of the local similarity measure is that it can measure the signal damage in a local and vivid way. Figure \ref{fig:shot-mf-s,shot-svmf-s,shot-somf-s,shot-sosvmf-s} show the four local similarity maps for the four methods. The comparison of local similarity shows vividly that all \dlo{MF,}\wen{median filter,} \dlo{SVMF}\wen{space-varying median filter}, and \dlo{SOMF}\wen{structure-oriented median filter} methods cause a large amount of damaged signals in the noise and the signal damage using the \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} method is the least. \wen{It is worth mentioning that some shallow reflections are not well predicted.  This is likely because of the curvature of the events and the linearity of the process.}

Next, we simulate a multi-receivers 2D simultaneous source separation test. In this test, we want to test how the \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} method performs when embedded into an iterative deblending framework. Figure \ref{fig:geom} shows the acquisition geometry of the 2D test. The red dots denote 120 evenly spaced shot locations on the surface. \dlo{The red strings denote the ray paths underneath the surface.} The blue inverted triangles denote 120 evenly spaced receivers. Note that in this acquisition geometry, the simultaneous shooting and traditional shooting only differ in the shot schedule \cite[]{abma2014}. Figure \ref{fig:shottime} shows the shot schedules for the traditional and the faster simultaneous source shooting. It is worth mentioning here that although there is only one source in this test, the faster shooting scheduling results in an overlapping subsurface reflection responses in time, which is still considered as simultaneous shooting \cite[]{abma2015}. From the shot schedule, it is obvious that the shooting time for the simultaneous source acquisition is almost half of the traditional acquisition and thus saves about half of the traditional acquisition cost. In this example, we use a relatively realistic field dataset to mimic the unblended data ($\mathbf{m}$ in equation \ref{eq:blend}), as shown in Figure \ref{fig:d3d}. \wen{The data is a marine data set provided by BGP China.} The size of the data is $1500\times 120\times120$ \wen{(in time-shot-receiver domain)}. Figure \ref{fig:b3d} shows the blended data ($\mathbf{d}$ in equation \ref{eq:blend}). It is clear that the blending noise appears to be spatially incoherent in the common receiver domain (along the shot axis) and spatially coherent in the common shot domain (along the receiver axis). Figure \ref{fig:m3d} shows iteratively deblended data using the rank-constrained shaping regularization framework \dlo{(equation \ref{eq:iter})} \cite[]{yangkang20142,shaohuan2017gji}. The iterative deblending is carried out in each common receiver gather based on the coherency difference between useful signals and interfering noise. For the rank-constrained inversion, we use local windows with the size of $200\times 20$ \wen{($\text{time} \times \text{space}$)}. A constant rank strategy is used for each window with $rank=2$. We obtain the result shown in Figure \ref{fig:m3d} with 40 iterations. Comparing the rank-constrained deblended data with the blended data, it is clear that most blending noise is removed. However, there is still \dlo{a lot of}\wen{much} residual noise. By cascading the \dlo{SOSVMF}\wen{structure-oriented space-varying median filter}\dlo{ filter} and the rank filter based on the iterative shaping regularization framework, as expressed by equations \ref{eq:iter}, we obtain a much improved deblended result, as shown in Figure \ref{fig:im3d}. During the inversion, we linearly decrease the filter length from 11 points to 0. A comparison between the two deblended data in Figure \ref{fig:m3d,im3d} confirms the effectiveness of the \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} method in improving iterative deblending. Figure \ref{fig:m3d-e,im3d-e} shows the deblending error for the traditional method and the proposed method. The deblending error means the difference between the unblended data (exact solution) and the deblended data. From Figure \ref{fig:m3d-e,im3d-e}, it is obvious that the deblending error for the proposed method is negligible while the error for the \dlo{traditional}\wen{rank-reduction} method is very large. Figure \ref{fig:m3d-n,im3d-n} shows the removed noise corresponding to the two methods\wen{, note that the interfering shots are coherent in the second spatial dimension.}. For evaluating the signal damages of this example, we calculate the local similarity between the deblended data and \dlo{removed}\wen{the} noise and show them in Figure \ref{fig:m3d-s,im3d-s}, where much larger local similarity anomalies are shown in the similarity map corresponding the traditional method. To compare the amplitude preservation in detail, we plot a trace-by-trace comparison in Figure \ref{fig:trace}. The black line is from the unblended data. The red line is from the blended data. The \dlo{blue}\wen{magenta} line corresponds to the rank-constrained method. The green line corresponds to the proposed \dlo{SOSVMF-rank-constrained }method. It is salient that the black and green lines are very close to each other, thus the deblending error using the proposed approach is much less than the traditional method for most parts. \wen{In order to compare the hybrid method with the structure-oriented space-varying median filter and the hybrid with the structure-oriented median filter, we also have a inversion test using the structure-oriented median filter. The deblended data is shown in Figure \ref{fig:im3d-2,im3d-e-2}. It is obvious that the hybrid method with the structure-oriented median filter causes much higher deblending error. }

\inputdir{./}
\multiplot{2}{geom,shottime}{width=0.5\textwidth}{(a) Acquisition geometry. \dlo{The red strings denote the ray paths underneath the surface.} The red dots denote shot locations and blue inverted triangles denote receivers. The simultaneous shooting and the traditional shooting only differ in the shot schedule. (b) Shot schedule. Note that the shot schedule is just for testing purpose and does not represent a real field deployment. In the test, the speed of a shooting vessel is assumed to be sufficiently large. In practice, the shot sampling would be much higher than the testing case, which is 0.05 km.}

\multiplot{2}{d3d,b3d}{width=0.6\textwidth}{Shot-receiver data example. (a) Unblended data. (b) Blended data.}
\multiplot{2}{m3d,im3d}{width=0.6\textwidth}{A comparison between \wen{iterative} deblending performance. (a) \dlo{Traditionally}\wen{Iteratively} deblended data using the rank-constrained method. (b) Deblended data using the \dlo{SOSVMF-rank-constrained}\wen{proposed} method.}

\multiplot{2}{m3d-e,im3d-e}{width=0.6\textwidth}{A comparison between deblending error. (a) Error corresponding to the traditional rank-constrained method. (b) Error corresponding to the \dlo{SOSVMF-rank-constrained}\wen{proposed} method.}

\multiplot{2}{m3d-n,im3d-n}{width=0.6\textwidth}{A comparison between removed blending noise. (a) Removed blending noise corresponding to the traditional rank-constrained method. (b) Removed blending noise corresponding to the \dlo{SOSVMF-rank-constrained}\wen{proposed} method.}

\multiplot{2}{m3d-s,im3d-s}{width=0.5\textwidth}{A comparison between local similarity comparison. (a) Local similarity corresponding to the traditional rank-constrained method. (b) Local similarity corresponding to the \dlo{SOSVMF-rank-constrained}\wen{proposed} method. Note the much larger similarity anomaly shown in (a).}

\multiplot{2}{trace,trace-z}{width=0.5\textwidth}{Single trace comparison. The black line is from the unblended data. The red line is from the blended data. The \dlo{blue}\wen{magenta} corresponds to the rank-constrained method. The green line corresponds to the proposed \dlo{SOSVMF-rank-constrained}\wen{proposed} method. Note that the black and green lines are very close to each other, thus the deblending error using the proposed approach is much less than the traditional method for most parts. \wen{(a) Comparison in the original size. (b) Comparison in a zoomed view.}}

\multiplot{2}{im3d-2,im3d-e-2}{width=0.5\textwidth}{\wen{Deblending performance using the hybrid method with structure-oriented median filter. (a) Deblended data. (b) Deblending error. Note that the deblending error in this case is much higher than the hybrid method with structure-oriented space-varying median filter (Figure \ref{fig:im3d-e}).}}

\wen{\section{Discussion}}
\wen{Two main research tracks of deblending are the filtering method, which is fast and easy to control, and the inversion method, which is more computationally demanding but can obtain better result. Two main existing challenges for deblending are 1) damaging signals for the filtering method and 2) lacking extra constraints during inversion in order to deal with high blending fold \cite[]{arazthesis2012}. The paper mainly discusses the filtering based deblending methods, so let us first focus on the drawbacks of the filtering method. To date, the filtering based deblending methods are mainly based on some types of median filtering, e.g., \cite{mediandeblend}, \cite{yangkang2015svmf}, \cite{shuwei2016}, and etc. Median filtering is a classic method. However, when we dig into the median filtering method further and further, we find that the implementation of a traditional median filter affects the result significantly. For example, \cite{mediandeblend} propose to apply the median filter to the dip direction of the seismic events, which can preserve the useful energy well. \cite{yangkang2015svmf} proposes to apply the median filter with different filter lengths, which can also preserve the useful energy well. \cite{shuwei2016} propose a similar method  as \cite{mediandeblend} but with a different structural filtering strategy and a different slope/dip estimation strategy. However, both \cite{mediandeblend}  and \cite{shuwei2016} depend  on accurate slope/dip estimation. What if slope/dip is not estimated accurately, e.g., in extremely noisy blended data or not in CMP gathers (as required by \cite{shuwei2016})? Then, both methods fail. In addition, for \cite{yangkang2015svmf}'s method, what if there exists steeply dipping events? No matter what thresholds of the method we use, it fails. The structure-oriented space-varying median filter is not a seemingly simple concatenation. It relieves the influence of slope/dip estimation on the following median filtering (traditional). So the dependency of an accurate slope/dip estimation no longer exists. Besides, because of the flattening (or approximate flattening when slope/dip is not accurate), the events are guaranteed to be not steeply dipping. The combination of the two methods is elegant, which solves two long-existing and fundamental problems for the ``median filtering'' based deblending  methods. The straightforward benefit is that we can deal with the massive blended data in a very fast and amplitude-preserving way.}

%First, we would like to discuss the computational cost of the SOSVMF filter. 
The \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} is not computationally expensive. To understand the computational cost of the \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} better, we can first split \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} into two components: \dlo{SVMF}\wen{space-varying median filter} and \dlo{SOMF}\wen{structure-oriented median filter}. Compared with the traditional \dlo{MF}\wen{median filter}, the \dlo{SVMF}\wen{space-varying median filter} uses a \dlo{MF}\wen{median filter} twice, each with different filter length criterion, thus the computational cost of \dlo{SVMF}\wen{space-varying median filter} is about the twice of the cost of the \dlo{MF}\wen{median filter} plus the calculation of the local similarity between the initially filtered data and a removed noise section. Calculation of the local similarity is also an efficient algorithm thanks to the fast implementation of the shaping regularization framework \cite[]{fomel2007localattr}. The \dlo{SOMF}\wen{structure-oriented median filter} adds an extra flattening (or trace prediction) step into the traditional \dlo{MF}\wen{median filter} and the extra computational cost is composed of local slope calculation and spatial neighbor trace prediction. According to our experience, the 2D calculation is still acceptable. More details of slope calculation are referred to \cite{fomel2002pwd} and more explanations regarding the trace prediction can be found in \cite{liuyang2010}. The main computational cost of \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} comes from calculation of the local slope, trace prediction, and local similarity calculation required by \dlo{SVMF}\wen{space-varying median filter} in each flattened local gather. All these extra computational steps can be implemented via efficient algorithms based on shaping regularization \cite[]{fomel2007shape}, thus the application of the \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} is not expensive. Here, we compare the computational cost in time for four different filtering methods in Table \ref{tbl:time}. The computation is done on a PC station equipped with an Intel Core i7 CPU clocked at 3.1 GHz and 16 GB of RAM. With a small data size, the computational cost for four methods are comparable. For a large data size (e.g., $800 \times 400$), the computational cost for the \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} is roughly 3 times that of the \dlo{SOMF}\wen{structure-oriented median filter}. It is also worth noting that the actual calculation time is usually data dependent. The exact calculation time for the local slope estimation and similarity computation may vary according to the input data but are not expensive.

%\tabl{time}{Comparison of computational time. MF denotes median filter. SVMF denotes space-varying median filter. SOMF denotes structure-oriented median filter. SOSVMF denotes structure-oriented space-varying median filter. }
% {

%}

The \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} is close to an adaptive method. The only parameter that needs to be chosen is the filter length. Once the filter length $L$ is fixed, the filter can adaptively adjust according to the complicated seismic structure via the two-step cascaded structure-oriented filtering and variable window strategy. Traditionally, the performance of the structure-oriented filtering highly depends on the local slope calculated from the noisy data. While adjusting the the parameters for the \dlo{PWD}\wen{plane-wave destruction} algorithm, e.g., the smoothing radius, regularization parameters, and the number of iterations, can somewhat improve the performance of slope estimation, it is still almost impossible to output an optimal slope map. As shown in the beginning part of the paper, a roughly calculated local slope map will result in unflattened local gathers and are not suitable for a simple median filtering. The \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} eases the dependency of the performance on the input slope field in that the following \dlo{SVMF}\wen{space-varying median filter} can deal with the unflattened energy via the variable window strategy. From a different aspect, the traditional \dlo{SVMF}\wen{space-varying median filter} does not account for the structure patterned existing in seismic data and is only effective to events with smaller dip angle. The local flattening process in structural filtering helps the \dlo{SVMF}\wen{space-varying median filter} prepare events with small dip angle. Combining the strategies of structural filtering and variable window length, the \dlo{SOSVMF}\wen{structure-oriented space-varying median filter} \dlo{is almost adaptive to any}\wen{is adaptive to almost any} input data with an arbitrary level of structural complexity. \new{For example, in the supplementary data, we show the results of a crossing-event dataset, where we can find that the proposed method also adapts to dataset containing crossing events.}

%Secondly, parameterization of the SOSVMF is not not complicated. 
\dlo{The SOSVMF is not limited to seismic data processing. Due to the strong signal-preserving ability of SOSVMF, it has the potential to be widely applied to remove spike-like noise in any type of datasets that contain structural patterns. Here, we want to mention an interesting application of the SOSVMF method in improving the waveforms recorded from the laser interferometor, which is usually used to study the anisotropy of organic-rich shale in rock physics. 
The laser ultrasonic approach has outstanding advantages in measuring elastic and anisotropic parameters and seismic physical modeling compared with the transducers ultrasonic approach in (1) no coupling and ring problems, (2) denser sampling, (3) fast and automatic acquisition, (4) exact group velocity.  The principle is to obtain the waveforms in each direction to the bedding plane in a horizontal cored shale sample, from which we can acquire a large number of diagonal group velocities versus group angle to invert the elastic constants and anisotropic parameters.  However, due to the extreme complexity of diagenetic overprints (temperature, overlying pressure, time), lithology and intrinsic properties (porosity, permeability, mineral components, etc) of organic-rich shale, the conversion efficiency of laser-ultrasonic is usually too low to be discerned when the laser pulse hits the surface of sample directly, which makes it difficult to obtain signals with high signal-to-noise ratio (SNR). Figure ? shows a recorded data from the  laser interferometor, which contains significant amount of noise. Figure ? shows the denoised data using the proposed SOSVMF method, and Figure ? shows the corresponding removed noise, which is generally spatially incoherent and does not contain obvious useful waveform signal.}
%The SOSVMF is not limited to seismic data processing. Due to the strong signal-preserving ability of SOSVMF, it has the potential to be widely applied to remove spike-like noise in any type of datasets that contain structural patterns. Here, we want to mention an interesting application of the SOSVMF method in improving the waveforms recorded from the laser interferometor, which is usually used to study the anisotropy of organic-rich shale in rock physics. The laser ultrasonic approach has outstanding advantages in measuring elastic and anisotropic parameters \cite[]{Aussel1989, Pouet1993,Lebedev2011, Carson2014} and seismic physical modeling \cite[]{blum2010, Bretaudeau2011} compared with the transducers ultrasonic approach in (1) no coupling and ring problems, (2) denser sampling, (3) fast and automatic acquisition, (4) exact group velocity \cite[]{blum2013,jianyong2016}.  The principle is to obtain the waveforms in each direction to the bedding plane in a horizontal cored shale sample, from which we can acquire a large number of diagonal group velocities versus group angle to invert the elastic constants and anisotropic parameters.  However, due to the extreme complexity of diagenetic overprints (temperature, overlying pressure, time), lithology and intrinsic properties (porosity, permeability, mineral components, etc) of organic-rich shale, the conversion efficiency of laser-ultrasonic is usually too low to be discerned when the laser pulse hits the surface of sample directly, which makes it difficult to obtain signals with high signal-to-noise ratio (SNR). Figure \ref{fig:data} shows a recorded data from the laser interferometor, which contains significant amount of noise. Figure \ref{fig:data-somf} shows the denoised data using the proposed SOSVMF method, and Figure \ref{fig:data-somf-n} shows the corresponding removed noise, which is generally spatially incoherent and does not contain obvious useful waveform signal.

%\inputdir{laser}
%\multiplot{3}{data,data-somf,data-somf-n}{width=0.7\textwidth}{(a) Recorded data from the laser interferometor. (b) Denoised data using the SOSVMF method. (c) Removed noise using the SOSVMF method.}

\section{Conclusion}
The signal preserving ability of a median filter\dlo{ (MF)} has been improved from the classic implementation to a space-varying median filter\dlo{ (SVMF)}, and further to a structure-oriented median filter\dlo{ (SOMF)}. However, the performance of \dlo{SOMF}\wen{structure-oriented median filter} highly depends on the accuracy of \dlo{the }estimated local slope\wen{s} of the input seismic data. We have proposed a variant of MF\wen{, named structure-oriented space-varying median filter,} that preserves signal energy even in \wen{cases with} complicated structure\wen{,} and can adapt to the inaccurate slope estimation in a structure-oriented filtering framework by applying a \dlo{SVMF}\wen{space-varying median filter} along the imperfectly flattened dimension. The proposed \dlo{SOSVMF }method can be applied to \dlo{reject}\wen{remove} spike-like noise in datasets that contain structural patterns. \dlo{The application of the SOSVMF in simultaneous source separation demonstrates a successful performance and shows distinct advantages over traditional alternative MFs.} \dlo{SOSVMF}\wen{Structure-oriented space-varying median filter} can also be conveniently used as an extra constraint during iterative deblending to improve the deblending performance based on the shaping regularization framework. Both synthetic and field data examples demonstrate the great advantages and potential of the \dlo{SOSVMF}\wen{the proposed method}.

\section{Acknowledgements}
The authors would like to thank Sergey Fomel, Shan Qu, Yaru Xue, Wei Chen, Min Bai, Dong Zhang, Jianyong Xie, Josef Paffenholz, Araz Mahdad, Ray Abma, Min Zhou, Qie Zhang, \wen{and} Zhiyong Jiang for \dlo{better }inspiring discussions on the simultaneous source separation problem. Yangkang Chen \dlo{is appreciated to}\wen{appreciates} FairfieldNodal and BP America for offering \dlo{his }summer internships during his PhD study at UT Austin. %The authors also thank editors Jeffrey Shragge and Guy Drijkoningen, reviewer Ying Wang, and \wen{three} other anonymous reviewers for constructive comments.  
\new{The authors also thank Herve Chauris, S.Mostafa Mousavi, and an anonymous reviewers for constructive comments.} The research is partially supported by \wen{the “Thousand Youth Talents Plan”, the starting fund from Zhejiang University, }National Natural Science Foundation of China (Grant No. U1262207), National Engineering Laboratory of Offshore Oil Exploration, 973 Program of China (Grant No. 2013CB228603), \wen{and} the National Science and Technology Program (Grant No. 2016ZX05010002-002).

\section{Appendix: Local similarity}
 Local similarity between vectors $\mathbf{a}$ and $\mathbf{b}$ is defined as:
\begin{equation}
\label{eq:local}
\mathbf{c}=\sqrt{\mathbf{c}_1\circ\mathbf{c}_2},
\end{equation}
where $\circ$ denotes element-wise product\dlo{,}\wen{.} $\mathbf{c}_1$ and $\mathbf{c}_2$ come from two least-squares minimization problems:
\begin{align}
\label{eq:local1}
&\min_{\mathbf{c}_1}\Arrowvert \mathbf{a}-\mathbf{B} \mathbf{c}_1 \Arrowvert_2^2, \\
\label{eq:local2}
&\min_{\mathbf{c}_2}\Arrowvert \mathbf{b}-\mathbf{A} \mathbf{c}_2 \Arrowvert_2^2.
\end{align}
\dlo{where}\wen{Here,} $\mathbf{A}$ is a diagonal operator composed of the elements of $\mathbf{a}$, $\mathbf{B}$ is a diagonal operator composed of the elements of $\mathbf{b}$. Note that in equations \ref{eq:local}-\ref{eq:local2}, $\mathbf{a}$, $\mathbf{b}$, and $\mathbf{c}$  denote vectorized 2D matrices. Equations \ref{eq:local1} and \ref{eq:local2} can be solved using shaping regularization with a local-smoothness constraint:
\begin{align}
\label{eq:local3}
\mathbf{c}_1 &= [\lambda_1^2\mathbf{I} + \mathbf{T}(\mathbf{B}^T\mathbf{B}-\lambda_1^2\mathbf{I})]^{-1}\mathbf{TB}^T\mathbf{b},\\
\label{eq:local4}
\mathbf{c}_2 &= [\lambda_2^2\mathbf{I} + \mathbf{T}(\mathbf{A}^T\mathbf{A}-\lambda_2^2\mathbf{I})]^{-1}\mathbf{TA}^T\mathbf{a},
\end{align}
where $\mathbf{T}$ is a smoothing operator\dlo{ and}\wen{,} $\lambda_1$ and $\lambda_2$ are two parameters controlling the physical dimensionality and enabling fast convergence when inversion\wen{s} \wen{for $\mathbf{c}_1$ and $\mathbf{c}_2$ expressed in equations \ref{eq:local3} and \ref{eq:local4}} are implemented iteratively. \wen{$\lambda_1$ and $\lambda_2$} can be chosen as $\lambda_1  = \Arrowvert\mathbf{B}^T\mathbf{B}\Arrowvert_2$ and $\lambda_2  = \Arrowvert\mathbf{A}^T\mathbf{A}\Arrowvert_2$.

\bibliographystyle{seg}
\bibliography{mf}

\newpage
\listoftables
\newpage
\begin{table}[!ht]
\caption{Comparison of computational time. MF denotes median filter. SVMF denotes space-varying median filter. SOMF denotes structure-oriented median filter. SOSVMF denotes structure-oriented space-varying median filter.}
    \begin{center}
     \begin{tabular}{|c|c|c|c|c|} 
	  \hline Model size & 50$\times$50  &  100$\times$100 & 200$\times$200 & 800$\times$ 400\\ 
	  \hline MF (s) & 0.442 & 0.460 & 0.471 & 0.591\\
      \hline SVMF (s) & 0.473	& 0.491	   & 0.527   & 0.962	 \\ 
      \hline SOMF (s) & 0.491 & 0.508 	&0.600	 & 1.525\\
      \hline SOSVMF (s) & 0.660  & 0.848 	&1.769	 & 4.237\\
      \hline
    \end{tabular} 
   \end{center}
   \label{tbl:time}
\end{table}

### 2020-09-16 sswtapp/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{Interpretation, 4, No.4, T541-T550, (2016)}

\title{Probing the subsurface karst features using time-frequency decomposition}

\author{Yangkang Chen\footnotemark[1]}
\address{
\footnotemark[1]Previously: Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
chenyk2016@gmail.com,
Currently: National Center for Computational Sciences \\
Oak Ridge National Laboratory \\
One Bethel Valley Road, \\
Oak Ridge, TN 37831-6008 \\
cheny@ornl.gov }
%INT-2016-0030

\lefthead{Chen}
\righthead{Probing the karst}
\maketitle

\DeclareRobustCommand{\dlo}[1]{\ifthenelse{\boolean{@revd}}{}{}}
\DeclareRobustCommand{\wen}[1]{%
\ifthenelse{\boolean{@revd}}{\textcolor{black}{#1}}{#1}}

\begin{abstract}
The high-resolution mapping of karst features is of great importance to \old{the} hydrocarbon discovery and recovery in the resource exploration field. However, currently, there are few effective methods specifically tailored for such mission. The 3D seismic data can reveal the existence of karsts to some extent but cannot obtain a precise characterization. I propose an effective framework for accurately probing the subsurface karst features using a well-developed time-frequency decomposition algorithm. More specifically, I introduce a frequency interval analysis approach for obtaining the best karsts detection result using an optimal frequency interval. A high resolution time-frequency transform is preferred in the proposed framework to capture the inherent frequency components hidden behind the amplitude map. Although the single frequency slice cannot provide a reliable karst depiction result, the summation over the selected frequency interval can obtain a high-resolution and high-fidelity delineation of subsurface karsts. I use a publicly available 3D field seismic dataset as an example to show the performance of the proposed method.  
\end{abstract}

%\begin{keywords}
%karst, time-frequency decomposition, synchrosqueezing wavelet transform
%\end{keywords}

\section{Introduction} 
Karst is a type of solutional caves that are usually formed in \old{the} soluble rock limestone when an aggressive fluid dissolves the rock. Subsurface karsting can produce a range of different structures, such as widened fissures and different types of cavities at all scales.  These may locally be partly or completely filled by
speleothems, sediments deposited by streams or breccia derived from stoping or collapse of the cave roof and walls \wen{\cite[]{karstthesis}}. \new{Commonly known karst features are fluid-enhanced faults \cite[]{su2005}, eroded caves, and sinkholes.} %incised valleys
The karst features are usually related with big petroleum reservoirs \wen{\cite[]{karstford}}. Understanding the spatial distribution of the karsts is of great importance to the discovery of hydrocarbons and their optimal recovery from these reservoirs. However, this can be very difficult \old{because of}\new{due to} several reasons. One reason is that the karsts are not uniformly distributed and exhibit an extreme spatial variability. Another reason is that the karst features are usually below seismic resolution\new{,} which makes them difficult to map. In this paper, I propose a high-resolution characterization approach for mapping the karst features by utilizing time-frequency decomposition of 3D seismic data.

Time-frequency decomposition offers extra information when analyzing seismic data, which has been extensively used in seismic data processing and interpretation \cite[]{jiajun2013,reine2009,rodriguez2012,fomel20132,tfpeak2015,yangkang2015sswt,liuwei20162,zhangdong20162}.
One of the most commonly used applications of time-frequency analysis is that deeper channels are usually \wen{of} stronger \wen{amplitude} at lower frequency in the time-frequency map\new{,} and the shallower flank of the channel has \dlo{stronger}\wen{larger} amplitude\dlo{s} at higher frequencies \wen{in the time-frequency map} \wen{\cite[]{liuwei2016,zixiang2016eage,liuwei2016eage}}. In addition, \dlo{TF}\wen{time-frequency} analysis can be used in estimating attenuation, pore-pressure prediction, detecting seismic unconformities, and some implementation of seismic chronostratigraphy \wen{\cite[]{tengfei2013}}. \wen{Over the past decades, time-frequency decomposition has found a panoply of applications in seismic data processing and interpretation \cite[]{jianlei2007}. Most time-frequency decomposition approaches are used in detecting low-frequency shadow \cite[]{castagna2003}, detecting paleochannels \cite[]{guochang20112}, reservoir characterization \cite[]{guoyin2015}, structural and stratigraphic delineation \cite[]{liuwei2016,yangkang2016eage}, arrivals picking of P or S wave modes \cite[]{pinnegar2003}.} In this paper, I  propose \dlo{a novel}\wen{an} application of the time-frequency decomposition in probing the subsurface karst features.  \dlo{Two}\wen{Four} \dlo{different} approaches with different analyzing resolutions are compared to offer more practical guidelines for utilizing the proposed approach.

 Some researchers have mentioned the application of time-frequency decomposition approaches in delineating the subsurface karst feature, but most applications are not introduced in detail\old{s} \cite[]{satinder2007,gaynor2010}. The karst features are depicted based on the criteria that they are discontinuous in spatial domain and show frequency anomalies. The challenge in delineating karst feature lays in the fact that high-resolution delineation may result \new{in} many spurious frequency anomalies while low-resolution delineation may fail to depicted such valuable details. A method that can offer us freedom to control the characterization resolution and fidelity is \old{ strongly demanded}\new{in strong demand}.

\section{Method}
Time-frequency decomposition maps a 1-D signal in the time domain into a 2-D image in time-frequency space, which can describe the local time-frequency variations
of geophysical properties. There have \dlo{existed}\wen{been} many different approaches for such decomposition mission, such as the continuous wavelet transform \wen{\cite[]{daubechies1992}}, S transform \wen{\cite[]{stockwell1996}}, and synchrosqueezing wavelet transform \wen{\cite[]{daubechies2011}}. I will not promote a new algorithmic advance here for better time-frequency decomposition, but instead, I will propose a novel and effective way for mapping the subsurface karst features based \new{on} a simple frequency interval analysis approach using 3D seismic data recorded at the surface of the targeted area.

The algorithm can be summarized in three simple steps:  
\begin{itemize}
\item Step 1: Input the 3D seismic data, and define the minimum and maximum analyzing frequency $\omega_{\min}$ and $ \omega_{\max}$ and frequency interval distance $\Delta \omega$.
\item Step 2: Apply time-frequency decomposition to each trace of the 3D seismic data and sum the frequency components in each frequency interval $<\omega_i,\omega_{i}+\Delta \omega>$, $i=1,2,\cdots,N$, where $N$ denotes the number of frequency intervals, then reform the summed frequency components of different intervals into several 3D cubes that correspond to different frequency intervals.
\item Step 3: Output the different frequency cubes and analyze the results to pick the best frequency interval that can best depicts the karst features.
\end{itemize}

$\omega_{\min}$ and $\omega_{\max}$ are chosen based on the bandwidth of seismic data. A reference value can be $\omega_{\min}=1$Hz and $\omega_{\max}=100$Hz. The $\Delta \omega$ is the only parameter that may need several trials. One can test the $\Delta \omega$ from 5Hz to 30 Hz, and updating $\Delta \omega$ every 5Hz. The choice of $\Delta \omega$ is a compromise between analysis complexity and the characterization resolution.

It is worth mentioning that time-frequency based karst delineation approach is not new in geophysical study. A typical and standard way to extract subsurface karst features based on time-frequency decomposition is to extract different constant frequency slices, and then to select a certain frequency slice to best represent the karst features based on a prior knowledge and good correlation between the frequency slice and the amplitude map. However, the single frequency slice depiction is sometimes not  reliable since higher frequency may provide fine-scale delineation with higher resolution\new{,} while lower-frequency may provide large-scale result with lower resolution. The result of the contradiction in traditional approaches is that there might be spurious bright spots or unclear karsts representation. I will just mention the problem here and will show it in detail in the data example. The frequency interval analysis approach provides us a convenient way to control the resolution and reliability of finally depicted karsts by simply adjusting the frequency interval. Although determining the frequency interval still requires some efforts in its current version, \old{the}\new{my} experience shows that frequency interval is usually chosen as 5, 10, or 20Hz\old{, which is still not too many options to choose}.

\section{Study Area and Dataset}
The studied dataset is a 3D dataset that was a significant part of the total data base amassed during a two-year study of the Bend Conglomerate reservoir system in Boonsville Field in north-central Texas. The 3D Boonsville field dataset \wen{\cite[]{hardage1996,hardage1996b}} was made publicly available for educational training purposes for a broad range of industry and academic interests since 1996 by Bob Hardage from the Bureau of economic Geology at The University of Texas at Austin. A special property of this dataset is that it shows interesting karst phenomenon of deep Ellenburger carbonates, which generate collapse structures that have compartmentalized clastic Bend Conglomerate reservoirs 620 to 760 meters above the depths where collapse structures originate. The demonstration of the study area is shown in Figure \ref{fig:boons}. \wen{Figure \ref{fig:barnett-strat} shows the strati-graphic column of the Fort Worth Basin \cite[]{Pollastro07}. The formation of \old{interset}\new{interest} is the Ordovician-age Ellenburger carbonate section. The Ellenburger carbonate section creates near-vertical chimneys-like karst collapses. } The 3D seismic dataset is shown in Figure \ref{fig:old3d} and a selected 2D profile (crossline=75) is shown in Figure \ref{fig:old}. \dlo{If one looks carefully at Figure \ref{fig:old}, one can see some karst collapses around the depth of 1.75s, but the phenomenon is not very clear.} \wen{It can be observed that around the depth of 1.25s, there are some karst collapses, which is however, not very clear. In the next section, I will show a much better delineation result using time-frequency decomposition.  }

\plot{boons}{width=\columnwidth}{Middle Pennsylvanian paleogeographic map showing the Fort Worth Basin and other basins related to the Ouachita orogony and the
Boonsville project area. The solid rectangle on the Wise-Jack county line designates the site of the 3-D seismic survey, curtersy of \cite{hardage1996}.}

\plot{barnett-strat}{width=0.5\columnwidth}{Strati-graphic column of the Fort Worth Basin, curtersy of \cite{Pollastro07}. The target horizon is the deep Ordovician-age Ellenburger carbonate section which causes numerous karst collapses and significant disruptions in the overlaying strata.}

\inputdir{boonsville}
\plot{old3d}{width=\columnwidth}{3D \dlo{time-migrated} Boonsville dataset \wen{after time migration}.}

\multiplot{4}{tfsswt1-2d3d-0,tfsswt2-2d3d-0,tfsswt3-2d3d-0,tfsswt4-2d3d-0}{width=0.4\columnwidth}{3D karst features delineation result using SSWT with different frequency intervals.}

\multiplot{5}{old,lowf-st,lowf-tfsswt2,lowf-stft,lowf-ltft}{width=0.4\columnwidth}{2D seismic section (crossline=75) and its karst mapping results. (a) Amplitude section. (b) Low frequency slice of ST. (c) Low frequency slice of SSWT. (d) Low frequency slice of STFT. (e) Low frequency slice of LTFT.}

\multiplot{5}{old-z,lowf-st-z,lowf-sswt-z,lowf-stft-z,lowf-ltft-z}{width=0.4\columnwidth}{Zoomed 2D seismic section (crossline=75) and its zoomed karst mapping results. (a) Amplitude section. (b) Low frequency slice of ST. (c) Low frequency slice of SSWT. (d) Low frequency slice of STFT. (e) Low frequency slice of LTFT.}

\multiplot{4}{tf-s,tf-ss,tf-stft,tf-ltft}{width=0.4\columnwidth}{Time-frequency maps of the 80th trace in the 2D seismic section as shown in Figure \ref{fig:old}, using (a) ST and using (b) SSWT. (c) STFT. (d) LTFT. The selected trace is highlighted by the blue line in Figure \ref{fig:old}.}

\multiplot{16}{sswt-0,sswt-1,sswt-2,sswt-3,sswt-4,sswt-5,sswt-6,sswt-7,sswt-8,sswt-9,sswt-10,sswt-11,sswt-12,sswt-13,sswt-14,sswt-15}{width=0.21\columnwidth}{Constant frequency slices using SSWT. The frequency range is from 21 to 81 Hz. Frequency interval is 4 Hz.}

Some structure-related anomalies, such as the faults, discontinuities, karst collapses, are not always easily viewed from the original amplitude-based seismic profile. There \old{have existed}\new{are} many approaches in the literature \old{for better viewing}\new{which better highlights} the structural anomalies. One of the most \old{used}\new{common} methods is to define \new{a} new seismic attribute which is sensitive to the structural anomalies\old{ to show clear delineation of the structural anomalies} \cite[]{wenkai2015,xieqian2015eage2}. The 3D dataset from the Boonsville field contains typical karst phenomenon, as shown in Figures \ref{fig:old3d} and \ref{fig:old}. But\new{,} from the original seismic reflections, the phenomenon is not obvious.

\section{Results}
By utilizing the proposed frequency interval analysis method, one can divide the total frequency \old{band}\new{range} into different sub-bands\new{,} and analyze the structural behaviors delineated from the sub-bands. In this paper, \wen{I use the synchrosqueezing wavelet transform (SSWT) \cite[]{daubechies2011,yangkang2014sswt,xieqian2015eage} for the time-frequency delineation of the karsts. } \dlo{I define the}\wen{I let} $\omega_{\min}=1$\new{Hz}, $\omega_{\max}=80$\new{Hz}, and $\Delta \omega=20$\new{Hz}, which \dlo{are}\wen{is} the optimal parameter combination for this dataset. \new{I choose $\omega_{\min}=1$ Hz and $\omega_{\max}=80$ Hz by looking at the averaged frequency spectrum of the seismic data and finding out that amplitude spectrum beyond 80 Hz or below 1 Hz is almost negligible. $\Delta \omega=20$\new{Hz} is decided by comparing the delineation results (as shown in Figure \ref{fig:tfsswt2-2d3d-0}) with $\Delta \omega=5,10,20$ Hz, respectively, and founding out that $\Delta \omega=20$Hz gives the best performance. }  The four 3D cubes that correspond to four different frequency intervals ($<1,20>$ Hz, $<21,40>$ Hz, $<41,60>$ Hz, and $<61,80>$ Hz) are shown in Figures \ref{fig:tfsswt1-2d3d-0} to \ref{fig:tfsswt4-2d3d-0}, respectively. \dlo{Please focus}\wen{Focusing} on the target layer from 1.0 s to 1.4 s, it is obvious that the result of the frequency interval $<21,40>$ clearly shows the distribution of the karsts. Please note that the closer the color is to blue, the higher possibility that area is karst. \new{The collapsed karsts are not formed during continuous sedimentation and thus is usually composed of complicated components. There are no layered structures inside the karsts, which will make seismic wave go through a strong scattering process when traveling through the karst media. The strong scattering will be revealed in seismic image as discontinuities, which will be further revealed in time-frequency maps as low amplitude phenomenon in the dominant frequency range. Thus, the blue (close to zero) is of higher likehood of karst.} I then select the best 3D karst characterization result of the frequency interval $<21,40>$ Hz and show it in detail in Figure \ref{fig:tfsswt2-2d3d,tfsswt2-2d3d-2,tfsswt2-2d3d-3,tfsswt2-2d3d-4} and will discuss about the details later.

\multiplot{2}{tfsswt2-2d3d,tfsswt2-2d3d-2,tfsswt2-2d3d-3,tfsswt2-2d3d-4}{width=0.45\columnwidth}{3D karst features mapping results (flat view) using SSWT with different time (top), crossline (left) and inline (right) slices. (a) Crossline=75, inline=80, time=1.2s. (b) Crossline=45, inline=80, time=1.2s. (c) Crossline=75, inline=50, time=1.2s. (d) Crossline=75, inline=80, time=1.1s.}

\inputdir{strata}
\multiplot{2}{stra-int,stra-tf}{width=\columnwidth}{Different strata slices from the time-frequency delineation result, shown in Figure \ref{fig:stra-tf}. (a) Top of Caddo. (b) Strata slice between Caddo and Vineyard. (c) Top of Vineyard. (d) Strata slice between Vineyard and the base.}

\multiplot{4}{stra1,stra2,stra3,stra4}{width=0.45\columnwidth}{Different strata slices from the time-frequency delineation result, shown in Figure \ref{fig:stra-tf}. (a) Top of Caddo. (b) Strata slice between Caddo and Vineyard. (c) Top of Vineyard. (d) Strata slice between Vineyard and the base.}

I then take the selected 2D section for further analysis. I compare the performance using \dlo{two}\wen{four} different time-frequency decomposition approaches: \wen{the} S transform\dlo{ and }\wen{, the} SSWT transform\wen{, the short time Fourier transform (STFT), and the local attribute based time-frequency transform (LTFT) \cite[]{guochang20113} }.  The delineation results using \dlo{ST and SSWT}\wen{ST, SSWT, STFT, and LTFT} are shown in Figures \dlo{\ref{fig:lowf-st} and \ref{fig:lowf-tfsswt2}}\wen{\ref{fig:lowf-st}, \ref{fig:lowf-tfsswt2} , \ref{fig:lowf-stft} , and \ref{fig:lowf-ltft} }, respectively. The result from SSWT is very appealing because those karst collapses are all depicted by the time-frequency decomposition (see those \wen{pink} frame boxes)\new{,} and \old{those}\new{the} collapse areas are all corresponding to small amplitude in the low frequency slice. However, \dlo{ST}\wen{all other time-frequency transforms} cannot decompose the seismic data in such way.  In order to make the comparison clearer, I zoom a part from each figure in Figure \ref{fig:old,lowf-st,lowf-tfsswt2,lowf-stft,lowf-ltft} and show them in Figure \ref{fig:old-z,lowf-st-z,lowf-sswt-z,lowf-stft-z,lowf-ltft-z}. The zoomed area is highlighted by the black frame boxes in Figure \ref{fig:old,lowf-st,lowf-tfsswt2,lowf-stft,lowf-ltft}. In Figure \ref{fig:old-z,lowf-st-z,lowf-sswt-z,lowf-stft-z,lowf-ltft-z}, the blue color in Figure \ref{fig:lowf-sswt-z} correlates well with the collapsed area in Figure \ref{fig:old-z}. The best mapping of karsts using SSWT is due to its high resolution property when analyzing 1D non-stationary seismic signals. Figure \ref{fig:tf-s,tf-ss,tf-stft,tf-ltft} shows time-frequency decomposition results of the 80th trace of the 2D seismic section as shown in Figure \ref{fig:old}\new{,} using four different approaches (ST, SSWT, STFT, and LTFT). The selected trace is highlighted by blue in Figure \ref{fig:old}.  From the comparison, one can see that SSWT has a much higher frequency resolution than ST, STFT, and LTFT. From the single-trace time-frequency slice one can judge roughly in which depth the data show abnormal frequency, and what their corresponding dominant frequency components are. In order to show superior performance of the frequency interval analysis approach as introduced in \old{the}\new{this} paper\new{,} over the traditional single frequency slice analysis approach, I plot 16 single frequency slices in Figure \ref{fig:sswt-0,sswt-1,sswt-2,sswt-3,sswt-4,sswt-5,sswt-6,sswt-7,sswt-8,sswt-9,sswt-10,sswt-11,sswt-12,sswt-13,sswt-14,sswt-15}. The frequency range is from 21 Hz to 81 Hz, and I plot the frequency slices every 4 Hz. It can be observed that the time-frequency decomposition results of subsurface properties are either of too low resolution\new{,} as shown in the low frequency slices, or of too high resolution as shown in high frequency slices. \old{The depicted results via constant single frequency slice do not correlate with the karst collapses and thus no frequency slice can be reliable to depicted the subsurface karst features.}

Figure \ref{fig:tfsswt2-2d3d,tfsswt2-2d3d-2,tfsswt2-2d3d-3,tfsswt2-2d3d-4} shows 3D karst delineation results (flat view) using SSWT with different time (top), crossline (left) and inline (right) slices. Figure \ref{fig:tfsswt2-2d3d} differs from \ref{fig:tfsswt2-2d3d-2} by different crossline sections. From the comparison between Figures \ref{fig:tfsswt2-2d3d} and \ref{fig:tfsswt2-2d3d-2}, one can see clearly how the karst varies along the crossline direction: the karst becomes weaker from crossline 75 to crossline 50. In the same way, one can study the karst variation along the inline direction by comparing Figures \ref{fig:tfsswt2-2d3d} and \ref{fig:tfsswt2-2d3d-3}. %From the comparison between Figures \ref{fig:tfsswt2-2d3d} and \ref{fig:tfsswt2-2d3d-4}, one can conclude that the karstification becomes weaker from 1.2 s to 1.1 s. 
It is also possible to evaluate the volume of the karst controlled area by looping along different directions in the 3D volume (Figure \ref{fig:tfsswt2-2d3d-0}), which is closely related with the karst controlled reserve.  Figure \ref{fig:stra-int} shows an interpreted 3D seismic section with three key stratas highlighted. The top pink line, middle green line, and bottom blue line denote the Caddo strata,  the Vineyard strata, and the Ellenburger strata, respectively. Figure \ref{fig:stra-tf} shows the time-frequency delineation result of the karsts overlaid by the picked three horizons. The Upper Caddo is the top boundary of the productive Bend Conglomerate section, and the Upper Vineyard is a sequence near the base of the Bend Conglomerate section. The Bend Conglomerate section is of Middle Pennsylvanian age (also known as Atokan) and is targeted throughout the 1980s and 1990s as it contains several oil\&gas bearing reservoirs. \old{It has a}\new{The} thickness \new{is} around 300-360 meters in this area\new{,} with a depth from 1370 to 1830 meters \cite[]{hardage1996,hardage1996b}.   It can be observed from the karsts mapping result shown in Figure \ref{fig:stra-tf} that the karsts spreads a deep range from the Upper Caddo to the base of Ellenburger. %As the general karsts delineation result correlates very well with the amplitude section, blue color under the Ellenburger strata even indicates that the collapses start even earlier than the Ellenburger carbonate. 
I also selected different strata slices from Figure \ref{fig:stra-tf} and show them in Figure \ref{fig:stra1,stra2,stra3,stra4}. Figure \ref{fig:stra1} shows a structure surface of the top of Caddo. Figure \ref{fig:stra2} shows a structure surface between Caddo and Vineyard. Figure \ref{fig:stra3} shows a structure surface on the top of Vineyard. Figure \ref{fig:stra4} shows a structure surface between Vineyard and the base of Ellenburger carbonate section. It can be observed that from up to down, the main color turns from cool (blue) to warm (red), indicates that the karstification weakens as the depth increases, which is consistent with the fact that the consolidation becomes stronger as the depth increases and make the deeper strata has stronger collapses and less karsts.

\new{The Boonsville 3D dataset consolidate the proposed frequency interval analysis method in delineating subsurface karst collapses. When I use the term \emph{karst collapses}, I intend to refer to all those commonly seen karst features, such as incised valleys, eroded caves, sinkholes, and so on. While the reasons causing these karst features are different, they will all cause more or less depressions or collapses to the overburden strata and have a similar situation as the one presented in the Boonsville example. There is a large potential that the proposed framework can be successfully used in any type of karst features, and future validation of the framework on more field datasets are worth being done. The sediment or mud-filled collapse features may not cause significant differences of anomalies in amplitude spectrum and they will both show irregularities on the 3D seismic images since seismic wave will experience strong scattering effects when traveling through the collapsed area. But future investigation should be done to validate this inference. }

\section{Conclusion}
Accurate\old{ly} mapping \new{of}\old{the} karst features is crucial for the resources exploration and recovery. The 3D seismic data can offer some insights in the spatial distribution of the karsts\new{,} but with low resolution, since the boundary of karst caves cannot be clearly delineated and the small-scale kart features are smeared in the seismic reflections. I propose to use time-frequency decomposition via a frequency interval analysis approach to accurately map the subsurface karst features with high resolution and accuracy. The time-frequency resolution can affect the final depicted result\new{,} and I suggest\dlo{ to use} \wen{using} the high-resolution synchrosqueezing wavelet transform (SSWT) to perform such task. The frequency interval analysis approach can provide us with more freedom in controlling the resolution and reliability of the \old{finally}\new{final} depicted result\new{,} compared with the traditional single frequency slice based approach. The proposed method is easy to implement and \dlo{should be paid}\wen{deserves} more attention to assist in geological research on the topic of karst evolution.

\section{Acknowledgements}
I would like to thank Summer Li, Qian Xie, Shuwei Gan, Wei Liu, Zixiang Cheng, Tingting Liu for helpful discussions\new{,} and Bob Hardage for making the Boonsville dataset publicly available.  I also thank associate editor Hongliu Zeng, \new{Victor Aarre}, and two anonymous reviewers for constructive suggestions that improved the manuscript greatly\new{.}\old{ and}\new{ Finally, thanks to} Dmytro Iatsenko for sharing the SSWT code\old{s} online: 
\begin{verbatim}
http://www.physics.lancs.ac.uk/research/nbmphysics/diats/tfr/.
\end{verbatim}
\newpage

\listoffigures
\bibliographystyle{seg}
\bibliography{sswt}

### 2020-09-16 strsvd/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{Journal of Geophysics and Engineering, 12, 262-272, (2015)}

\title{Structure-oriented singular value decomposition for random noise attenuation of seismic data}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\author{Shuwei Gan\footnotemark[1], Yangkang Chen\footnotemark[2], Shaohuan Zu \footnotemark[1], Shan Qu\footnotemark[1] and Wei Zhong \footnotemark[1]}

\address{
\footnotemark[1] State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
gsw19900128@126.com\\
\footnotemark[2]Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
ykchen@utexas.edu
}

\lefthead{Gan et al.}
\righthead{Structure-oriented SVD}
\maketitle

\begin{abstract}
Singular value decomposition (SVD) can be used both globally and locally to remove random noise in order to improve the signal-to-noise ratio (SNR) of seismic data. However, they can only be applied to seismic data with simple structure such that there is only one dip component in each processing window. We introduce a novel denoising approach that utilizes a structure-oriented SVD and this approach can enhance seismic reflections with continuous slopes. We create a third dimension for a 2D seismic profile by using the plane-wave prediction operator to predict each trace from its neighbour traces and apply SVD along this dimension. The added dimension is equal to flattening the seismic reflections within a neighbouring window. The third dimension is then averaged to decrease the dimension. We use two synthetic examples with different complexities and one field data example to demonstrate the performance of the proposed structure-oriented SVD. Compared with global and local SVDs, and $f-x$ deconvolution, the structure-oriented SVD can obtain much clearer reflections and preserve more useful energy. 
\end{abstract}

\section{Keywords}
Singular value decomposition, random noise attenuation, global SVD, local SVD, structure-oriented SVD

\section{Introduction}
The attenuation of random noise is an important subject in seismic data processing. The enhanced seismic signals with higher signal-to-noise ratio (SNR) can help interpreters to make more accurate decisions. There are generally four different categories of random noise attenuation approaches that exist in the exploration geophysics literatures. The first is based on the predictive property of useful signals in small spatial-temporal windows, such as $f-x$ deconvolution \cite[]{canales,yangkang2014}, $f-x-y$ prediction filtering \cite[]{yanghua1999,yanghua2002}, $t-x$ prediction error filtering \cite[]{abma1995}, and $f-x$ non-stationary polynomial fitting \cite[]{guochang20112}. \new{\cite{wencheng2015asa} proposed a novel trace-by-trace random noise attenuation approach based on the predictable spectral components property of useful seismic reflections using regularized non-stationary autoregression \cite[]{fomel20132}. This approach does not require the spatial coherency assumption and has the potential to be widely used to denoise microseismic signal, the SNR of which is very low.}  The second is based on the statistical property of seismic profile, such as the mean filter \cite[]{nlm}, median filter \cite[]{yike2013,yangkang2014svmf,yangkang2014nmo}. The third is based on extracting the principal components of seismic data, such as multichannel singular spectrum analysis (MSSA) \cite[]{mssa,yangkang2015} and EMD based approaches \cite[]{yangkang2014emdsum}. This type of approach is also related with those rank-reduction based approaches, eigenimage-based approaches. The fourth is based on a transformed domain thresholding strategy \cite[]{curvelet,seislet,yangkang20142}. The transform operator can be a fixed-basis sparsity-promoting transform, and can also be an adaptively-learned dictionary, while the fixed-basis transform enjoys better efficiency and learning-based dictionary enjoys better adaptivity. Apart from those aforementioned one-step noise attenuation, \cite{yangkang2015ortho} proposed a two-step approach for retrieving the lost useful signals from the noise section, which can be seen as the residual random noise attenuation.

\cite{freire1988svdsnr} proposed to carry out rank reduction of seismic images in the $t-x$ domain via singular value decomposition (SVD). They applied SVD to the seismic data matrix and extracted the first singular value in order to remove random noise based on the assumption that the seismic data with only horizontal events have a rank of one. We refer to this method as the global SVD (GSVD), because this SVD method does not require to be implemented in small windows. The GSVD does not require regularly sampled data because no convolutional operator is used. As long as the seismic profiles are composed with horizontal events, GSVD can obtain a good denoising performance. However, the seismic profiles do not necessarily meet the requirement that there are no dipping events. For those complex profiles, GSVD cannot be applied. \cite{freire1988svdsnr} also demonstrated that the GSVD is actually equivalent to Karhunen-Loeve (KL) (or principal component transformation) approach \cite[]{jones1987}. Because of the horizontal-energy selective property of GSVD, \cite{milton2009} proposed to use GSVD filtering to remove dipping interference, such as ground-rolls.

The $f-x$ domain rank reduction approaches are independent from dip, and therefore, do not require flattening. They require an eigen-decomposition of the spectral matrix of data, which is connected with Cadzow filtering \cite[]{cadzow1988} and multichannel singular spectrum analysis (MSSA) \cite[]{vautard1992,mssa}.
Although MSSA and Cadzow filtering are equivalent, they come from different signal analysis subfields. Cadzow filtering was proposed to denoise images, whereas MSSA was proposed to decompose time series arising in the study of dynamical systems \cite[]{oropeza2010}. Cadzow filtering and MSSA are also referred to as the $f-x$ SVD (FXSVD). For FXSVD, the eigen-decomposition of spectral matrix is usually done by applying an SVD to a pre-constructed (block) Hankel matrix. However, this type of methods depends on the low-rank property of seismic data, in other words, the seismic profile should contain few linear events (2D) or few plane-wave components (3D). The low-rank and linear-events assumptions of the FXSVD are not always met, which enforces the FXSVD to be implemented in local processing windows. The division of local windows and decision of rank value, however, are sometimes an empirical and user-unfriendly process.

In this paper, we propose a novel SVD approach for enhancing useful reflections by removing random noise. The novel SVD is implemented obeying the structural information.
We first flatten the seismic reflections according to the local slopes by trace prediction. In the flattened domain, we apply a GSVD to horizontal events in order to remove random noise. The flattened traces are then transformed back to the original structural shape by stacking the traces in the flattened domain. We refer to the proposed novel SVD denoising approach as structure-oriented SVD (SOSVD). The SOSVD does not require local processing windows as LSVD and FXSVD do, and it can distinguish signal and noise better than GSVD. Flattened events make the largest singular value components mainly correspond to useful events, which are much easier to be separated. However, GSVD may not be applied to flattened events.

We organize the paper as follows: we first introduce the well-known GSVD, LSVD along with dip steering, and the theoretical aspects of SOSVD. \new{A brief review of the basic theory of the commonly used $f-x$ deconvolution is also provided in the appendix.} We then \old{compare}\new{apply} three different SVDs and \old{commonly used} $f-x$ deconvolution onto three different synthetic examples (with increasing complexity) and one field data example that comes from the \old{Gulf of Mexico}\new{North Sea}, and compare their performances. The comparisons show that the SOSVD can obtain much better performance in removing noise and preserving useful signals.

\section{Theory}
\subsection{Noise attenuation using SVD}
2D seismic data can be expressed as a data matrix $\mathbf{D}$ ($M\times N$), consisting of $N$ traces and $M$ time samples. The SVD of the data matrix $\mathbf{D}$ can be expressed as:
\begin{equation}
\label{eq:svd}
\mathbf{D}=\mathbf{U\Sigma V}^T.
\end{equation}
Here, $\mathbf{U}$ is composed of the eigenvectors of $\mathbf{DD}^T$. $\mathbf{V}$ is composed of the eigenvectors of $\mathbf{D}^T\mathbf{D}$. $\mathbf{\Sigma}$ is a diagonal matrix composed of the decreasing singular values. Let us denote $\mathbf{U}$, $\mathbf{\Sigma}$, and $\mathbf{V}$ in the following form:
\begin{equation}
\label{eq:svdu}
\begin{array}{l}
\mathbf{U}=[u_1,u_2,\cdots,u_r],\\
\mathbf{\Sigma}=diag(\sigma_1,\sigma_,\cdots,\sigma_r),\\
\mathbf{V}=[v_1,v_2,\cdots,v_r],
\end{array}
\end{equation}
where $r$ is the rank of $\mathbf{D}$. The vectors $\mathbf{u}_k$ and $\mathbf{v}_k$ are also called the propagation vectors and the eigen-wavelets, respectively \cite[]{vrabie2004}. The singular values $\sigma_k$ are sorted such that $\sigma_1\ge\sigma_2\ge\cdots\ge\sigma_r$. They can be obtained by calculating the positive square roots of the eigenvalues of the data covariance matrix $\mathbf{D}\mathbf{D}^T$.

Equation \ref{eq:svd} can be expressed as:
\begin{equation}
\label{eq:svd2}
\mathbf{D} = \sum_{k=1}^{r}\lambda_k\mathbf{u}_k\mathbf{v}^T_{k},
\end{equation}
where $\mathbf{u}_k\mathbf{v}^T$ is the rank-one matrix called the $k$th eigenimage of $\mathbf{D}$. Thus, from equation \ref{eq:svd2}, the seismic image can be decomposed into $r$ eigenimages, %Matrix $\mathbf{D}$ can be decomposed into $r$ parts, 
the energy of which corresponds to the value of each element in matrix $\mathbf{\Sigma}$.

We can remove the random noise in seismic data in order to enhance the seismic reflections by only selecting the first several eigenimages \cite[]{freire1988svdsnr}:
\begin{equation}
\label{eq:svddenoise}
\hat{D}_{svd} = \sum_{k=1}^{p} \sigma_k\mathbf{u}_k\mathbf{v}_k^T.
\end{equation}

Random noise attenuation approach by SVD utilizes the property that useful seismic signals are horizontally coherent to separate signal and noise. %Let $\mathbf{D}$ denotes the seismic profile with $N$ traces and $M$ temporal samplings. 
The decomposition is based on the criterion of horizontal coherency. The energy of coherent signals lays in the first several parts of the decomposition, which is represented by the value of bigger values in $\mathbf{\Sigma}$. For seismic data, the horizontal coherent part corresponds to useful signal while random noise or coherent dipping events are not horizontally coherent. Thus, by choosing the first several elements in $\mathbf{\Sigma}$ and making the others equal to zero, we can remove the noise and enhance seismic data quality. SVD acts as a data-driven, low-pass filter by rejecting highly uncorrelated traces \cite[]{bekara2007}. Here, we refer to those denoising approaches that simply apply SVD to the original seismic data in order to remove random noise as global SVD (GSVD).

\subsection{Dip steering and local SVD}
Supposing the events in a processing window have one slope, dip steering algorithm aims to flatten the dipping events by shifting each trace such that the flattened events are suitable for applying a GSVD based denoising approach, as shown in equation \ref{eq:svddenoise}. This flattening strategy is called dip steering \cite[]{bekara2007}. After removing noise, applying an inverse flattening to the data in the processing window can obtain the denoised data. We refer to those denoising approaches that apply a GSVD in the dip-steering flattened domain as local SVD (LSVD).
The time shifts for each trace in order to flatten the events are obtained by selecting the time delays that can maximize cross-correlation between each trace and a reference trace.  
\begin{equation}
\label{eq:steer}
\tau_n = \arg\max_{\tau} \sum_{m=\min(1-\tau,1)}^{\max(M_w,M_w-\tau)} r(m)d(m+\tau,n),
\end{equation}
where $\tau_n$ is the optimal time shift for $n$th trace in the processing window, $M_w$ denotes the number of time samples in the processing window and $r(m)$ denotes the $m$th sample of the reference trace and $d(m,n)$ denotes the data value in $m$th sample and $n$th trace.
$\tau_n>0$ corresponds to shifting trace downward with respect to the reference trace, and $\tau_n<0$ corresponds to shifting trace upward.

As can be seen from the equation \ref{eq:steer}, the selection of reference trace is crucial for the effectiveness of LSVD. It can be chosen as random trace in the processing window if the noise level is not high, or can be chosen as a stacked trace after normal-moveout (NMO) of common-midpoint gathers. \cite{bekara2007} proposed an iterative strategy for selecting the optimal reference trace stating that the resulting shifted traces are stacked after each cross-correlation pass for updating the new reference traces and the process of cross-correlation, shifting, and stacking is repeated until the process converges.
Figure \ref{fig:dn,dh,dhc,dc} shows a demonstration for dip steering and the processes of LSVD. Figure \ref{fig:dn} is the original noisy dipping event. Figure \ref{fig:dh} denotes the flattened event after forward dip steering. Figure \ref{fig:dhc} shows the LSVD denoised result by choosing only one singular value. The final denoised result after inverse dip steering on Figure \ref{fig:dhc} is shown in Figure \ref{fig:dc}. The time shifts after the optimizing equation \ref{eq:steer} are shown in Figure \ref{fig:shift}. The reference trace is simply chosen as the first trace of the original data, as shown in Figure \ref{fig:dn}.

\inputdir{dipsteer}
\multiplot{4}{dn,dh,dhc,dc}{width=0.45\textwidth}{Demonstration for dip steering and LSVD. (a) Noisy dip reflector. (b) Flattened event using dip steering. (c) SVD denoised result by selecting only one eigen-image. (d) Denoised data after inverse dip steering.}

\plot{shift}{width=0.6\textwidth}{Time shifts for each trace for the forward dip steering as shown in Figure \ref{fig:dn,dh,dhc,dc} (reference trace selected as the left trace in Figure \ref{fig:dn}).}

\subsection{Structure-oriented SVD}
The structure-oriented SVD (SOSVD) refers to two processes: flattening along the local structure in a local  spatial window and applying GSVD in the flattened local spatial window. The procedures can be summarized as:
\begin{equation}
\label{eq:proc}
\mathbf{D} \rightarrow \mathbf{D}_j^R (j=1,2,\cdots,N) \rightarrow \overline{\mathbf{D}}_j^R \rightarrow \overline{\overline{D}}_j^R \rightarrow \mathbf{d}_j \rightarrow \hat{\mathbf{D}}_{sosvd}.
\end{equation}

Here, $\mathbf{D}_j^R$ denotes the $j$th spatial window (corresponding to $j$th trace) with a radius of $R$, $\overline{\mathbf{D}}_j^R$ denotes the flattened local spatial window, $\overline{\overline{D}}_j^R$ denotes the SVD denoised local spatial window, $\mathbf{d}_j$ denotes the averaged local spatial window, and $\hat{\mathbf{D}}_{sosvd}$ denotes the output data using SOSVD.

As we can see from the workflow, the key step that distinguishes SOSVD with other types of SVD approaches is the flattening in the local spatial window. The flattening corresponds to applying a flattening operator to the data (here we use a prediction operator according to local slope) so that the output data have horizontal events:
\begin{equation}
\label{eq:flatten}
 \mathbf{P}_j \mathbf{D}_j^R= \overline{\mathbf{D}}_j^R.
\end{equation}
where $\mathbf{P}_j$ is the $j$th flattening operator. Here, the flattening operator is chosen as a plane-wave prediction operator related with the local slope. 
Equation \ref{eq:flatten} has the following detailed form:
\begin{equation}
\label{eq:detail}
\begin{split}
& \left[
\begin{array}{cccccc}
\mathbf{P}_{(1,j)\rightarrow(1+R,j)}(\sigma_{1,j}) &  & & & & \\
 &  & \ddots & & & \\
 &  & & \mathbf{P}_{(1+R,j)\rightarrow(1+R,j)}(\sigma_{1+R,j}) & & \\
 &  & & & \ddots & \\
 &  & & & & \mathbf{P}_{(1+2R,j)\rightarrow(1+R,j)}(\sigma_{1+2R,j})\\
\end{array}
\right]\\
&[\mathbf{d}_{1,j},\cdots,\mathbf{d}_{1+R,j}, \cdots, \mathbf{d}_{1+2R,j}]\\
&=[\overline{\mathbf{d}}_{1,j},\cdots,\overline{\mathbf{d}}_{1+R,j}, \cdots, \overline{\mathbf{d}}_{1+2R,j}]. 
\end{split}
\end{equation}
Here, $\mathbf{P}_{(i,j)\rightarrow(k,j)}(\sigma_{i,j})$ denotes the prediction operator from trace $i$ to trace $k$ in $j$th spatial window, which is connected with the local slope of $i$th trace.  Prediction of a trace consists of shifting the original trace along dominant event slopes \cite[]{fomel2010painting}.  
Prediction of a trace from a distant neighbour can be accomplished by simple recursion \cite[]{liuyang2010}, i.e., predicting trace $k$ from trace $1$ is simply
\begin{equation}
\label{eq:recur}
\mathbf{P}_{(1,j)\rightarrow(k,j)} (\sigma_{1,j})= \mathbf{P}_{(k-1,j)\rightarrow(k,j)}(\sigma_{k-1,j})\cdots\mathbf{P}_{(2,j)\rightarrow(3,j)}(\sigma_{2,j})\mathbf{P}_{(1,j)\rightarrow(2,j)}(\sigma_{1,j}).
\end{equation}

The prediction operator is a numerical solution of the local plane differential equation 
\begin{equation}
\label{eq:plane}
\frac{\partial P}{\partial x} + \sigma \frac{\partial P}{\partial t} = 0,
\end{equation}
for local plane wave propagation in the $x$ direction.

The dominant slopes are estimated by solving the following least-square minimization problem using regularized least-squares optimization:
\begin{equation}
\label{eq:mini}
\hat{\mathbf{\sigma}} = \arg\min_{\sigma} \parallel \mathbf{W}(\sigma)\mathbf{D} \parallel_2^2,
\end{equation}
where \old{$\mathbf{D}$}\new{$\mathbf{W}$} is the destruction operator defined as

\begin{displaymath} 
\mathbf{W} = \left[
\begin{array}{ccccc} 
\mathbf{I} & 0 & 0 & \cdots & 0\\
-\mathcal{\mathbf{P}}_{1\rightarrow 2} &\mathbf{I} & 0 &\cdots &0\\
0 &-\mathcal{\mathbf{P}}_{2\rightarrow 3} & \mathbf{I} & \cdots & 0 \\
\cdots & \cdots & \cdots & \cdots & \cdots \\
0& 0 & \cdots & - \mathcal{\mathbf{P}}_{N-1\rightarrow N} & \mathbf{I}
\end{array}\right]\;, 
\end{displaymath}
where $\mathbf{I}$ stands for the identity operator, and $\mathcal{\mathbf{P}}_{i\rightarrow k}$ describes prediction of trace $k$ from trace $i$ (same as the previous version $\mathbf{P}_{(i,j)\rightarrow(k,j)}(\sigma_{i,j})$ except for not in a specific spatial window). The optimization approach as shown in equation \ref{eq:mini} for obtaining local slope estimation is called plane wave destruction (PWD) \cite[]{fomel2002pwd}.

\section{Examples}
In this section, we first use two synthetic examples with different complexities. Then a field data example is presented for better demonstration of the proposed approach. \new{For all the three examples, we compare the denoising performances for GSVD, LSVD,SOSVD, and the commonly used $f-x$ deconvolution. A brief review of the theory of $f-x$ deconvolution is provided in the appendix.}

The first synthetic example is a simple seismic profile that has hyperbolic events. It is generated from the SeismicLab library. The clean data and noisy data with simulated Gaussian white noise are shown in Figure \ref{fig:hyper,hyper-noise}. There are three hyperbolic events in the synthetic data. Two events have small slopes and the other one has high slope. The denoised results using GSVD, LSVD, and SOSVD are shown in Figures \ref{fig:hyper-gsvd}, \ref{fig:hyper-lsvd}, and \ref{fig:hyper-svd}, respectively. As a reference, we also show the denoised result using $f-x$ deconvolution in Figure \ref{fig:hyper-fx}. From the comparison of denoised results shown in Figure \ref{fig:hyper-gsvd,hyper-lsvd,hyper-fx,hyper-svd}, we can initially conclude that the GSVD removes the least noise, there are some damages to the events for LSVD, $f-x$ deconvolution does a little damage to the dipping hyperbolic event, and the denoised result using the proposed SOSVD obtains a nearly perfect result. The removed noise sections are shown in Figure \ref{fig:hyper-n-gsvd,hyper-n-lsvd,hyper-n-fx,hyper-n-svd}. From the noise sections, we can confirm the observation made from the denoised results shown in Figure \ref{fig:hyper-gsvd,hyper-lsvd,hyper-fx,hyper-svd}. The GSVD cannot remove too much random noise because we cannot remove too many eigen images, otherwise the damages to useful events are very large. The GSVD causes some damages to the steep event, LSVD causes some damages to areas that have conflicting slopes, $f-x$ deconvolution causes damages to both steep event and more horizontal events. There are nearly no coherent signals lost in the noise section for the proposed SOSVD.

The second synthetic example is a linear-event section. Figure \ref{fig:complex,complex-noise} shows the clean and noisy data. There are one horizontal and three dipping events in this section. Two of the dipping events cross with each other. After using the GSVD, LSVD, $f-x$ deconvolution, and the proposed SOSVD, we obtain four denoised sections, as shown in Figure \ref{fig:complex-gsvd,complex-lsvd,complex-fx,complex-svd}. The GSVD still does a bad job because of the dipping events. The LSVD seems to cause more damages to the useful events than the previous example because almost in each processing window there are more than one slopes, which makes the dip steering strategy fail. $f-x$ deconvolution damages both horizontal and dipping events. The proposed SOSVD removes the most noise and preserves the useful energy best. From the noise sections as shown in Figure \ref{fig:complex-n-gsvd,complex-n-lsvd,complex-n-fx,complex-n-svd}, we conclude that the SOSVD gets an excellent performance except for small damage to the crossing point of the original noisy data. The damage for the crossing point comes from the fact that the PWD algorithm cannot obtain a precise slope estimation in the region and thus causes the flattening along the structure more difficult. \new{In fact, the only disadvantage of the proposed approach is the incapability to handle crossing seismic events. The crossing points will appear in the noise section. The problem can be handled by slope-separated processing using the same approach. However, as a byproduct, the proposed approach may has potential to be used as a diffraction detector, which will be helpful for other important tasks in seismic data processing and imaging. This topic regarding to the crossing point may be the subject of future investigation.}

The third example is a field data example. This example is a part extracted from a 3D North Sea data \cite[]{lomask2006,fomel2010painting}.  The original image is shown in Figure \ref{fig:field-noise}. As we can see, the seismic data contain a lot of \old{in-continuous}\new{dis-continuous} events caused by a low SNR, which makes the interpretation and evaluation of the useful signals impossible. After using GSVD, LSVD, $f-x$ deconvolution and SOSVD, we obtain four denoised sections that are shown in Figure \ref{fig:field-gsvd,field-lsvd,field-fx,field-svd}. It's obvious that GSVD and LSVD both cause some damages to the useful signals. Although $f-x$ deconvolution preserves the useful reflections well, there seems no improvement for SNR of the data. By using SOSVD, we can obtain a very good denoised image (Figure \ref{fig:field-svd}). The image becomes clean and seismic reflections becomes continuous, which is beneficial for the following interpretation. From the noise sections shown in Figure \ref{fig:field-n-gsvd,field-n-lsvd,field-n-fx,field-n-svd}, we can get the similar conclusion that  SOSVD preserves the most useful energy while removing the most noise.

\inputdir{hyper}
\multiplot{2}{hyper,hyper-noise}{width=0.45\textwidth}{Hyperbolic-events synthetic seismic profile. (a) Clean data. (b) Noisy data.}

\multiplot{4}{hyper-gsvd,hyper-lsvd,hyper-fx,hyper-svd}{width=0.45\textwidth}{Comparison of denoised data for the hyperbolic-events synthetic example. (a) Using GSVD. (b) Using LSVD. (c) Using $f-x$ deconvolution. (d) Using SOSVD.}

\multiplot{4}{hyper-n-gsvd,hyper-n-lsvd,hyper-n-fx,hyper-n-svd}{width=0.45\textwidth}{Comparison of removed noise for the hyperbolic-events synthetic example. (a) Using GSVD. (b) Using LSVD. (c) Using $f-x$ deconvolution. (d) Using SOSVD.}

\inputdir{complex}
\multiplot{2}{complex,complex-noise}{width=0.45\textwidth}{Complex-events synthetic seismic profile. (a) Clean data. (b) Noisy data.}

\multiplot{4}{complex-gsvd,complex-lsvd,complex-fx,complex-svd}{width=0.45\textwidth}{Comparison of denoised data for the complex-events synthetic example. (a) Using GSVD. (b) Using LSVD. (c) Using $f-x$ deconvolution. (d) Using SOSVD.}

\multiplot{4}{complex-n-gsvd,complex-n-lsvd,complex-n-fx,complex-n-svd}{width=0.45\textwidth}{Comparison of removed noise for the complex-events synthetic example. (a) Using GSVD. (b) Using LSVD. (c) Using $f-x$ deconvolution. (d) Using SOSVD.}

\inputdir{fieldstrsvd}
\plot{field-noise}{width=0.45\textwidth}{Field data example.}
\multiplot{4}{field-gsvd,field-lsvd,field-fx,field-svd}{width=0.45\textwidth}{Comparison of denoised data for field data. (a) Using GSVD. (b) Using LSVD. (c) Using $f-x$ deconvolution. (d) Using SOSVD.}
\multiplot{4}{field-n-gsvd,field-n-lsvd,field-n-fx,field-n-svd}{width=0.45\textwidth}{Comparison of removed noise for field data. (a) Using GSVD. (b) Using LSVD. (c) Using $f-x$ deconvolution. (d) Using SOSVD.}

\section{Conclusions}
We have proposed a novel structure-oriented singular value decomposition (SOSVD) for enhancing useful reflections by removing random noise of seismic data. The SOSVD locally flattens the useful reflections by predicting each trace from its neighbouring traces. The plane-wave destruction (PWD) operator serves as the slope estimator for the prediction operator. In the flattened local processing window, we can apply a traditional SVD to remove incoherent noise. The SVD denoised windows are then stacked to output the denoised trace. Compared with GSVD, the SOSVD can preserve much more dipping events by slope flattening. Compared with LSVD, the SOSVD skips the use of dip steering that depends on a\old{n} uniform shift for each trace and assumes a uniform-slope processing window, thus is more robust and effective in handling complex structures. Compared with $f-x$ deconvolution, the SOSVD can be significantly more effective both in the removal of random noise and the preservation of useful reflections.

\new{\section{Acknowledgement}}
\new{We would like to thank three anonymous reviewers for very constructive suggestions, which help us improve the manuscript greatly.}

\append{\new{Review of $f-x$ deconvolution}}
$f-x$ deconvolution is one of the most widely used approaches for random noise attenuation. In this appendix, we briefly review the theory of $f-x$ deconvolution. Let $s_t(x)$ be the seismic signal located at trace $x$ and time $t$. If the slope of a linear event with constant amplitude in a seismic section is $\psi$, then:
\begin{equation}
\label{eq:first}
s_t(x+1)=s_{t-x\psi\Delta h}(1),
\end{equation}
where $\Delta h$ denotes the spatial interval. Equation \ref{eq:first} can be directly transformed into the frequency domain utilizing the time-shift property of the Fourier transform:
\begin{equation}
\label{eq:second}
S_f(x+1)=S_f(1)e^{-i2\pi fx\psi\Delta h}.
\end{equation}
For a specific frequency $f_0$,  from equation \ref{eq:second} we can  obtain a linear recursion, which is given by:
\begin{equation}
\label{eq:third}
S_{f_0}(x+1)=a_{f_0}(1)S_{f_0}(x),
\end{equation}
where  $a_{f_0}(1)=e^{-i2\pi f_0\psi\Delta h}$. 
This recursion is also known as an auto-regressive (AR) model of order 1 \cite[]{canales}. Similarly, superposition of $p$ linear events in the $t-x$ domain can be represented by an AR model of order $p$ \cite[]{tufts,har} as the following equation:
\begin{equation}
\label{eq:fifth}
S_{f_0}(x+1)=a_{f_0}(1)S_{f_0}(x)+a_{f_0}(2)S_{f_0}(x-1)+\cdots+a_{f_0}(p)S_{f_0}(x+1-p),
\end{equation}
Equation \ref{eq:fifth} can be formulated as a convolutional form:
\begin{equation}
\label{eq:sixth}
\mathbf{d}=\mathbf{f}*\mathbf{a},
\end{equation}
where $\mathbf{d}$ denotes the vector composed of $S_{f_0}(x+1)(x=1,2,\cdots,X)$, $\mathbf{f}$ denotes the vector composed of $S_{f_0}(x)(x=1,2,\cdots,X)$, $\mathbf{a}$ denotes the vector composed of $a_{f_0}(x)(x=1,2,\cdots,X)$, and $X$ denotes the number of traces.

Equation \ref{eq:sixth} can be formulated as a matrix vector form:
\begin{equation}
\label{eq:seventh}
\mathbf{d}=\mathbf{Fm},
\end{equation}
where $\mathbf{F}$ is the covolution matrix composed by $\mathbf{f}$. Suppose $p=4$, the detailed form of equation \ref{eq:seventh} can be expressed as:

\begin{equation}
\label{eq:eigth}
\left[ \begin{array}{c}
f_2\\
f_3\\
\vdots\\
f_{X}\\
0\\
0\\
0\\
\end{array}\right]
=
\left[\begin{array}{cccc} 
f_1 & 0 & 0 & 0 \\
f_2 & f_1 & 0 & 0 \\
\vdots &f_2&f_1 & 0 \\
f_{X-1}& \vdots &f_2&f_1\\ 
0&f_{X-1}&\vdots& f_2 \\
0&0&f_{X-1}&\vdots \\
0&0&0&f_{X-1} \\
\end{array}\right] 
\left[ \begin{array}{c}
a_1\\
a_2\\
a_3\\
a_{4}\\
\end{array}\right].
\end{equation}

However, equation \ref{eq:seventh} is based on clean signal model. In reality, the seismic data is composed of random noise. Thus, we have to solve $\mathbf{a}$ from the noise corrupted observation $\mathbf{d}$ based on some optimization schemes. Based on equation \ref{eq:fifth}, we can formulate an optimization problem based on the minimum prediction error energy assumption. The predictive error filter can be solved by minimizing the following objective function:
\begin{equation}
\label{eq:objective}
J={\Arrowvert \mathbf{Fm}-\mathbf{d} \Arrowvert}_2^2,
\end{equation}
where $\Arrowvert\cdot\Arrowvert_2^2$ denotes the squares of $L_2$ norm.

Taking derivatives of the cost function \ref{eq:objective} with respect to $\mathbf{m}$, and setting the result to zero, we can obtain the following equation:
\begin{equation}
\label{eq:derivative}
\mathbf{F}^T\mathbf{d}=\mathbf{F}^{T}\mathbf{Fm},
\end{equation}
where $[\cdot]^T$ denotes transpose. Note that $\mathbf{F}^T\mathbf{F}$ is a Toeplitz form and thus can be efficiently solved using Levinson's recursion. In order to stabilize the recursion for solving $\hat{\mathbf{a}}$, we need to add a small perturbation to the diagonal of the Toeplitz matrix:
\begin{equation}
\label{eq:solution}
\hat{\mathbf{a}}= (\mathbf{F}^{T}\mathbf{F}+\mu\mathbf{I})^{-1}\mathbf{F}^T\mathbf{d}.
\end{equation}
Finally, the estimated clean data (denoised data) can be expressed as:

\begin{equation}
\label{eq:solution1}
\hat{\mathbf{d}}= \mathbf{F}\hat{\mathbf{a}}.
\end{equation}

It is worth to be mentioned that, the $f-x$ deconvolution approach introduced here only applies a forward AR model to estimate the signal. A hybrid forward and backward version of AR model was proposed in \cite{yanghua1999}.

\bibliographystyle{seg}
\bibliography{strsvd}

### 2020-09-16 svscan/paper.tex
2020年 9月16日 星期三 15时46分34秒 CDT

\published{Geophysical Journal International, 204, 768-779, (2016)}

\title{Velocity analysis of simultaneous-source data using high-resolution semblance - coping with the strong noise}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\author{Shuwei Gan\footnotemark[1], Shoudong Wang\footnotemark[1], Yangkang Chen\footnotemark[2], Shan Qu\footnotemark[3] and Shaohuan Zu\footnotemark[1]}

\address{
\footnotemark[1] State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
gsw19900128@126.com \\
\footnotemark[2]Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX, USA, 78713-8924  \\
ykchen@utexas.edu\\
\footnotemark[3]Department of Imaging Physics \\
Faculty of Applied Sciences \\
Delft University of Technology, \\
2600 CD Delft, Netherlands,   \\
S.Qu@tudelft.nl \\
%+86-18810415565 
}

\lefthead{Gan et al.}
\righthead{Velocity analysis of simultaneous-source data}

\maketitle

% for multiple-revision
\DeclareRobustCommand{\dlo}[1]{\ifthenelse{\boolean{@revd}}{}{}}
\DeclareRobustCommand{\wen}[1]{%
  \ifthenelse{\boolean{@revd}}{\textcolor{black}{#1}}{#1}}

\begin{abstract}
Direct imaging of simultaneous-source (or blended) data, without the need of deblending, requires a precise subsurface velocity model. In this paper, we focus on the velocity analysis of simultaneous-source data using the NMO-based velocity picking approach. We demonstrate that it is possible to obtain a precise velocity model directly from the blended data in the common-midpoint (CMP) domain. The similarity-weighted semblance can help us obtain much better velocity spectrum with higher resolution and higher reliability compared with the traditional semblance. The similarity-weighted semblance enforces an inherent noise attenuation solely in the semblance calculation stage, thus is not sensitive to the intense interference. We use both simulated synthetic and field data examples to demonstrate the performance of the similarity-weighted semblance in obtaining reliable subsurface velocity model for direct migration of simultaneous-source data. \new{The migrated image of blended field data using prestack kirchhoff time migration (PSKTM) approach based on the picked velocity from the similarity-weighted semblance is very close to the migrated image of unblended data.}
\end{abstract}

\newpage
\section{Keywords}
Velocity analysis, simultaneous-source acquisition, similarity-weighted semblance, direct imaging of blended data

\section{Introduction}
Simultaneous-source shooting is a breakthrough in modern seismic acquisition, which can tremendously increase the acquisition efficiency and improve the data quality \cite[]{beasleycj1998,berkhout2008,abma2009}. In blended acquisition, more than one source is shot simultaneously, regardless of \dlo{their interactive}\wen{the} interference. When more than one source is involved in acquisition, either a denser or a wider shot coverage can be obtained for a given constant acquisition period. The \emph{wider} coverage (Figure \ref{fig:demo2}) here refers to a higher acquisition efficiency while the \emph{denser} coverage (Figure \ref{fig:demo1}) refers to a better-sampled seismic dataset. The attractive benefits are compromised by the challenges in dealing with strong interference from simultaneous sources in the acquired seismic data. We can either separate the blended sources into individual ones as if they were acquired independently, which is also called deblending \cite[]{yangkang2014svmf,shuwei2016}, or directly migrate the blended data using \dlo{some} newly-developed imaging schemes \cite[]{verschuur2011,yaxun2009}. Deblending can provide similar data as the conventional acquisition and thus not require a change in post-processing and imaging algorithms, but need specific computationally expensive technique for the pre-processing \cite[]{abma2009,abma2014}. Direct imaging does not require any pre-processing steps for observed data and thus enjoys the benefit of \wen{high} efficiency, but calls for a tremendously different processing workflow \cite[]{zhiguang2014,yangkang2015image}. 
\inputdir{./}
\multiplot{2}{demo1,demo2}{width=0.45\textwidth}{Demonstration of the simultaneous-source geometry. (a) Two-source shooting for denser coverage. (b) Two-source shooting for wider coverage. Red points denote shot positions for source 1. Green points denote shot positions for source 2. Blue points denote receiver positions. Red and green strings denote the shooting rays. Arrows denote the shooting directions. Borrowed from \cite{yangkang2014nmo}.}

Because of many reported success of deblending, more and more focus is now moved towards the direct imaging of blended data.  However, one of the most important components in the direct imaging of simultaneous-source data is the macro subsurface velocity model of the targeted area. In this paper, we focus on the velocity analysis \dlo{problem} of the simultaneous-source data. We demonstrate that it is possible to directly apply the common velocity scanning procedures to the blended data in the common-midpoint (CMP) domain. We also propose to use the newly developed similarity-weighted semblance \cite[]{yangkang2015vel,shuwei2015vel} to perform \wen{the} velocity analysis. Both synthetic and field data examples show that the similarity-weighted semblance can help obtain higher-resolution and more reliable velocity spectrum than the conventional semblance, especially in the case of simultaneous-source data. \new{The direct imaging of simultaneous-source data based on the directly picked velocity is also carried out via the prestack kirchhoff time migration (PSKTM) approach. The performance shows that the migrated image from blended data based on the picked velocity from similarity-weighted semblance is very close to the migrated image from unblended data. }

\section{Method}
\subsection{Blended acquisition and direct imaging}
For a constant-receiver survey, the simultaneous-source data can be expressed as:
\begin{equation}
\label{eq:blend}
\mathbf{d}=\Gamma\mathbf{m},
\end{equation}
where $\mathbf{d}$ is the blended data, $\Gamma$ is the blending operator, and $\mathbf{m}$ is the unblended data. The formulation of $\Gamma$ has been introduced in \cite{arazthesis} in detail. When considered in time domain, the $\Gamma$ corresponds to blending different shot records onto one receiver record \wen{(node)} according to the shot schedules of different shots.
\dlo{Considering the}\wen{The} Born modeling from seismic reflectivity to the primary reflections \wen{can be expressed as}:
\begin{equation}
\label{eq:born}
\mathbf{m}=\mathbf{L}\mathbf{r},
\end{equation}
where $\mathbf{r}$ denotes the subsurface reflectivity model and $\mathbf{L}$ denotes the Born modeling operator.
One way to remove the effect\wen{s} caused by the blending operator $\Gamma$ is first solving equation \ref{eq:blend} and then solving equation \ref{eq:born}, which is referred to as \dlo{deblending}\wen{\emph{deblending}}. The general deblending framework can be summarized as \cite[]{yangkang20142,yangkang2015pnmo}:
\old{$\mathbf{m}_{n+1} = \mathbf{S} (\mathbf{m}_n+\lambda (\mathbf{d}-\Gamma\mathbf{m}_n))$}
\new{
\begin{equation}
\label{eq:shape}
\mathbf{m}_{n+1} = \mathbf{S} (\mathbf{m}_n+\lambda \Gamma^* (\mathbf{d}-\Gamma\mathbf{m}_n)), 
\end{equation}}
where $\mathbf{S}$ is \dlo{a coherency constraining shaping operator} \wen{called the shaping operator, which is used to constrain the current model,} and $\lambda$ is the step size of the \dlo{updating}\wen{updated} misfit. $\Gamma^*$ denotes the adjoint of $\Gamma$. $\mathbf{m}_n$ denotes the deblended data after $n$th iteration.

Another way for deal\wen{ing} with the simultaneous-source data is to solve the following equation for $\mathbf{r}$ directly, which is known as direct imaging of blended data,
\begin{equation}
\label{eq:direct}
\mathbf{d}= \mathbf{Fr}, 
\end{equation}
where $\mathbf{F}=\Gamma\mathbf{L}$.

Equation \ref{eq:direct} can be best solved using a least-squares (LS) based migration approach. More robust LS solvers involve adding \dlo{some} constraints of structural coherency when inverting $\mathbf{r}$, either in a preconditioned LS formulation \cite[]{daiwei2011,yangkang2015image} or in a shaping-regularized LS iterative framework \cite[]{fomel2007shape,zhiguang2014}.

Because of the great success of deblending reported in the literature \cite[]{abma2010,mahdad2011,beasley2012,chengbo2013,shuwei2015seg,shaohuan2015,yangkang2015dbortho} in the recent years, more and more focus is \wen{currently} moving towards the direct imaging of blended data, which can be more efficient and can illuminate the surface better \cite[]{verschuur2011,berkhout2012}. \new{It is worth mentioning that the deblending step for the massive blended data requires large computational resources (mainly for the parallel processing of a huge number of common receiver gathers) and a long processing period because of the thousands of iterations used for each common receiver gather. If the direct imaging can obtain a good result, we can obtain a big saving in both computational resources and processing period.} However, a key aspect for the success of direct imaging is the macro velocity model of subsurface. Either tomography based velocity analysis or \wen{Born-approximation} wave-equation based velocity inversion, requires an initial acceptable velocity model from the \old{highly-corrupted}\new{very noisy} blended data (Figure \old{1b}\new{\ref{fig:comp2}a} shows an example). In the next section, we will introduce a way for obtaining high-resolution and high-fidelity velocity spectrum from blended data, using the recently developed similarity-weighted semblance.

\subsection{Velocity analysis of blended data using similarity-weighted semblance}
The conventional semblance is defined by \cite{neidell1971} as:
\begin{equation}
\label{eq:semb}
C[i] = \frac{\displaystyle\sum_{j=i-M}^{i+M}\left(\sum_{k=0}^{N-1}s[j,k]\right)^2}{\displaystyle N\sum_{j=i-M}^{i+M}\sum_{k=0}^{N-1}s^2[j,k]},
\end{equation}
where $i$ and $j$ are time sample indices, $C[i]$ denotes the conventional semblance for time index $i$, $2M+1$ is the length of the smoothing window along the time axis, and $s[j,k]$ is the trace amplitude at time index $j$ and trace number $k$ of the NMO-corrected CMP gather.

The weighted semblance introduced in \cite{yangkang2015vel} can be summarized as:
\begin{equation}
\label{eq:semb-weight}
W[i] = \frac{\displaystyle\sum_{j=i-M}^{i+M}\left(\sum_{k=0}^{N-1}s[j,k]w[j,k]\right)^2}{\displaystyle \sum_{j=i-M}^{i+M}\left(\sum_{k=0}^{N-1}s^2[j,k]\sum_{k=0}^{N-1}w^2[j,k]\right)},
\end{equation}
where $W[i]$ denotes the weighted semblance, $w[j,k]$ denotes the weighting function for time index $j$ and trace number $k$.

There have existed several weighting criteria, such as the AB semblance \cite[]{fomel20091}, offset-prior semblance \cite[]{luosimon2012}, and the similarity-weighted semblance \cite[]{yangkang2015vel}. As the similarity-weighted semblance can improve the resolution of velocity spectrum greatly, and has the possibility to subtract noise effect, we choose the local similarity \cite[]{fomel2007localattr} to weight different traces:
\begin{equation}
\label{eq:simiweight}
w[j,k]=\mathcal{L}(s[j,k],r[j]),
\end{equation}
where $\mathcal{L}(\mathbf{x},\mathbf{y})$ denotes the local similarity between traces $\mathbf{x}$ and $\mathbf{y}$, $r[j]$ denotes the $j$th time point for a selected reference trace $\mathbf{r}$. In this paper, the reference trace is chosen as the stacked trace using a conventional stacking technique. Figure \ref{fig:synth-comp} shows a demonstration of \wen{the} \dlo{similarity-semblance calculated} velocity spectrum \wen{calculated using the similarity-weighted semblance} compared with the \wen{velocity spectrum calculated using the traditional semblance}\dlo{traditional-semblance calculated velocity spectrum}. The left panel in Figure \ref{fig:synth-comp} shows a simple synthetic data with four hyperbolic events. The middle and right panels show the velocity spectrum calculated using the traditional and the proposed semblance, respectively. It is obvious that the similarity-weighted semblance is of \dlo{very} high resolution.

%The open-source code ("Msimivscan.c") is provided as an appendix to teach the readers how we program the aforementioned algorithm. We formed our code by modifying the original template code ("Mvscan.c"). The original template code is also provided as an appendix. Both source codes can be found in the Madagascar open-source platform \cite[]{mada2013}. The only difference between the similarity-weighted semblance and conventional semblance is the weighs calculated from the local similarity between each trace and a reference trace. Thus, we only modify the original template velocity scanning code by implementing the weighting part. The difference is commented in the source code.

\inputdir{class}
\plot{synth-comp}{width=\textwidth}{A brief comparison between the similarity-weighted semblance and the conventional semblance. Left: simple synthetic data. Middle: semblance map using the conventional semblance. Right: semblance map using the similarity-weighted semblance.}

It is worth \old{to mention}\new{mentioning} that, the selection of the reference trace needs several iterations in practice. It is obvious that the similarity-weighted semblance is calculated with an inherent denoising ability. The noise \dlo{subtraction}\wen{attenuation} involved in the similarity-weighted semblance is much similar to that used in \cite{guochang2009} for attenuating random noise in the stacking process. Because of intense interference \dlo{involved}\wen{existing} in the simultaneous-source data, conventional semblance will decrease the resolution because of the corruption by \wen{the blending} interference. However, the beauty of the similarity-weighted semblance is that it enforces an inherent noise attenuation solely in the semblance calculation stage, without any extra process specifically designed for noise attenuation. The key element that enables the anti-noise ability of the similarity-weighted semblance is the local similarity based weights. In the next part, we will review the basic theory of the local similarity.

\subsection{Local similarity}
A common way to measure the similarity between two signals is to calculate the global correlation coefficient:
\begin{equation}
\label{eq:simi}
\gamma=\frac{\displaystyle\sum_{i=1}^Na(i)b(i)}{\displaystyle\sqrt{\sum_{i=1}^Na^2(i)\sum_{i=1}^Nb^2(i)}},
\end{equation}
where \old{$r$}\new{$\gamma$} is the global correlation coefficient, $N$ denotes the number of samples of the signals $\mathbf{a}$ and $\mathbf{b}$. In order to calculate the similarity between two signals locally, one can use the localized correlation coefficient:
\begin{equation}
\label{eq:simi}
\gamma_m(t)=\frac{\displaystyle\sum_{i=t-m/2}^{t+m/2} a(i) b(i)}{\sqrt{\displaystyle\sum_{i=t-m/2}^{t+m/2} a^2(i) \displaystyle\sum_{i=t-m/2}^{t+m/2} b^2(i) }},
\end{equation}
where $\gamma_m(t)$ denotes the local correlation coefficient, $m$ is the local window size. \\
\cite{fomel2007localattr} designed an elegant way to calculate the local similarity: 
\begin{align}
\label{eq:local}
\gamma(t) & =\sqrt{\gamma_1(t)\gamma_2(t)}, \\
\label{eq:local1}
\gamma_1(t)&=\arg\min_{\gamma_1(t)} \left(\sum_{t}(a(t)-\gamma_1(t)b(t)) + R(\gamma_1(t)) \right), \\
\label{eq:local2}
\gamma_2(t)&=\arg\min_{\gamma_2(t)} \left(\sum_{t}(b(t)-\gamma_2(t)a(t)) + R(\gamma_2(t)) \right).
\end{align}
Equation \ref{eq:local} represents that the local similarity can be expressed as the product of two vectors that are the solutions of two minimization problems. $R$ is a regularization operator for constraining $\gamma_1$ and $\gamma_2$. $R$ can be chosen as a local triangular smoother to enforce the smoothness of vectors $\gamma_1$ and $\gamma_2$, and then equations \ref{eq:local1} and \ref{eq:local2} can be solved using the shaping regularization \cite[]{fomel2007shape}:
\begin{align}
\label{eq:local3}
\mathbf{\gamma}_1 &= [\lambda_1^2\mathbf{I} + \mathcal{S}(\mathbf{B}^T\mathbf{B}-\lambda_1^2\mathbf{I})]^{-1}\mathcal{S}\mathbf{B}^T\mathbf{a},\\
\label{eq:local4}
\mathbf{\gamma}_2 &= [\lambda_2^2\mathbf{I} + \mathcal{S}(\mathbf{A}^T\mathbf{A}-\lambda_2^2\mathbf{I})]^{-1}\mathcal{S}\mathbf{A}^T\mathbf{b},
\end{align}
where $\mathbf{A}$ is a diagonal operator composed from the elements of $\mathbf{a}$: $\mathbf{A}=diag(\mathbf{a})$ and $\mathbf{B}$ is a diagonal operator composed from the elements of $\mathbf{b}$: $\mathbf{B}=diag(\mathbf{b})$. $\mathbf{\mathcal{S}}$ is a smoothing operator, and $\lambda_1$ and $\lambda_2$ are two parameters controlling the physical dimensionality and enabling fast convergence when inversion is implemented iteratively. These two parameters can be chosen as the least-squares norms of $\mathbf{A}$ and $\mathbf{B}$ \cite[]{fomel2007localattr}.

The local similarity algorithm can be used \dlo{to}\wen{for the} \dlo{calculate}\wen{calculation of signals} \dlo{the local similarity of signal} of any dimension. For 1D signals, the meanings of equations \ref{eq:local3} and \ref{eq:local4} are intuitive. For 2D or higher-dimensional signals, each signal is first reshaped into a 1D signal and then follows equations \ref{eq:local3} and \ref{eq:local4} to calculate the local similarity vector. The smoothing operator is applied to the 2D or multi-dimensional form of the original signal to enforce the smoothness in any dimension. Figures \ref{fig:trace-comp} and \ref{fig:flat-comp} show demonstrations for both 1D and 2D signals. Figures \ref{fig:trace-comp}a and \ref{fig:trace-comp}b show the same trace with different level of noise. Figure \ref{fig:trace-comp}c shows the calculated local similarity for the 1D signal. Figures \ref{fig:flat-comp}a and \ref{fig:flat-comp}b show the same flattened gather with different level of noise. Figure \ref{fig:flat-comp}c shows the calculated local similarity for the 2D signal.  From the two examples, we can conclude that the local similarity can effectively obtain smooth and reasonable measurements for both 1D and 2D signals. The peaks in the calculated local similarity indicate the position of useful wavelets correctly.
\inputdir{simi}
\plot{trace-comp}{width=\textwidth}{Local similarity for 1D signal. (a) \& (b) The same trace with different level of noise. (c) Calculated local similarity.}
\plot{flat-comp}{width=\textwidth}{Local similarity for 2D signal. (a) \& (b) The same flattened gather with different level of noise. (c) Calculated local similarity.}

\section{Examples}
The first example is a synthetic example. Figure \ref{fig:simple-comp-dat} shows the unblended and blended data in the CMP domain. The blending fold is very high and thus the blended data is very noisy. \new{It should be mentioned that before the processing, we need to apply the domain transformation. That is to say: transform the data from shot domain to midpoint domain. The domain transformation corresponds to the following transformation relation: 
\begin{equation}
\label{eq:trans}
\begin{split}
\mathbf{m} &= \frac{1}{2}(\mathbf{s}+\mathbf{r}),\\
\mathbf{h} &= \frac{1}{2}(\mathbf{s}-\mathbf{r}), 
\end{split}
\end{equation}
where $\mathbf{m}$ and $\mathbf{h}$ denotes the midpoint and offset locations, $\mathbf{s}$ and $\mathbf{r}$ denotes the source and receiver locations.} Here, we leave out the domain transformation \cite[]{yangkang2014nmo} between common shot point (CSP) domain and CMP domain, and just show the data in the CMP domain. Figure \ref{fig:simple-comp-scn} shows the comparison of the velocity spectrum using conventional semblance and similarity-weighted semblance. As we know the exact velocity of this synthetic example, we can compare the velocity spectrum with the true velocity in order to judge the performance of different semblance approaches. As we can see from the comparison, the similarity-weighted semblance can obtain obviously higher resolution and more reliable spectrum. The black strings on the top of the spectrum maps denote the true velocity. The two frame boxes highlight two regions of obvious difference. From the two highlighted frame boxes, it is much clearer that the similarity-weighted semblance can get more reliable result.

%We provide a Python script that can regenerate Figures \ref{fig:simple-comp-dat} and \ref{fig:simple-comp-scn} of the first example. The Python script (SConstruct) should be run in the Madagascar open-source environment \cite[]{mada2013}, which can be downloaded at $www.ahay.org$.

The second example is a field data example with multiples. Figure \ref{fig:comp-dat} shows the unblended and blended data in the CMP domain. Figure \ref{fig:comp} shows a comparison between different velocity spectrum for both unblended and blended data. Because in this case, we do not have the true velocity model, we can only use the spectrum of unblended data as a reference. The left and middle left figures in Figure \ref{fig:comp} correspond to the velocity spectrum of unblended data using conventional semblance and similarity-weighted semblance, respectively. The middle right and right figures in Figure \ref{fig:comp} correspond to the velocity spectrum of blended data using conventional semblance and similarity-weighted semblance, respectively. In this case, we also have the spectrum of multiples. It is obvious that the similarity-weighted semblance can obtain higher resolution for both unblended and blended data. Comparing the middle right and right figures, we can conclude that the similarity-weighted semblance can be more reliable for velocity picking.

The third example is \wen{a} numerically blended field data example in the case of high blending ratio (the interference is very strong). The numerically blended data is shown in Figure \ref{fig:comp2}a. Because of the strong blended interference, it is hard to detect the useful reflections. In this example, the conventional semblance can not obtain an acceptable velocity spectrum, as shown in Figure \ref{fig:comp2}b. The peaks in the velocity spectrum map are nearly smeared in the background noise. However, \dlo{using the proposed high-resolution similarity-weighted semblance,} we can still obtain well-behaved velocity peaks, \wen{using the proposed high-resolution similarity-weighted semblance,} which distinguish themselves with the background noise. The peaks can be picked either manually or automatically.

The fourth example is a numerically blended \old{pre-stack}\new{prestack} field data. Figures \ref{fig:gulf} and \ref{fig:gulf-b} show the unblended and blended data that have been sorted from CSP gathers to CMP gathers. This example is used to simulate the independent marine-streamer simultaneous shooting (IMSSS) acquisition \cite[]{yangkang2014nmo}.
The blending interference is so strong that the useful reflections are nearly smeared in the noise. Figure \ref{fig:vscan-gulf} shows the velocity spectrum of the unblended data using the traditional semblance. Figure \ref{fig:vscan-b} shows the velocity spectrum of the blended data using the traditional semblance. Figure \ref{fig:vscan-simi-b} shows the velocity spectrum of the blended data using the proposed high-resolution semblance. 
It is obvious that the traditional semblance can obtain good performance for clean unblended data. However, the traditional \new{semblance} \old{can not}\new{cannot} obtain \dlo{an}\wen{a} reasonable velocity spectrum for the blended data. Because of the strong blending interference, the traditional semblance cannot \dlo{form}\wen{generate} \new{energy} peaks in the spectrum that can be easily picked. Fortunately, the high-resolution similarity-weighted semblance can help obtain much focused peaks in the velocity spectrum that can be picked. With the automatically picked velocity \cite[]{fomel20091} from the velocity spectrum shown in Figure \ref{fig:vscan-gulf,vscan-b,vscan-simi-b}, we can obtain their corresponding migration results. \new{Here, it is worth giving a brief introduction about the automatic velocity picking algorithm. Although the automatic velocity picking problem was mentioned by several researchers in the literature \cite[]{SEG-1999-11621165,SEG-2000-02360238,harlan,SEG-2004-16271629}, we use the approach proposed in \cite{fomel20091}. The main principle of the approach is to solve the following eikonal equation
\begin{equation}
\label{eq:eik}
\left(\frac{\partial T}{\partial v}\right)^2 + \frac{1}{\alpha^2} \left(\frac{\partial T}{\partial t}\right)^2 = e^{-2w(t,v)},
\end{equation}
where $T$ is the traveltime, $w(t,v)$ corresponds to the semblance spectrum, and $\alpha$ denotes a scaling parameter. After obtaining a finite-difference solution of equation \ref{eq:eik}, we can extract the picking trajectory $v(t)$ by tracking backward along the traveltime gradient direction.}

The migrated profiles using the prestack kirchhoff time migration (PSKTM) \new{algorithm} for different cases are shown in Figure \ref{fig:pstm,pstm-b,pstm-simi-b}. Figure \ref{fig:pstm} shows the migrated profile for unblended data using the traditional semblance method. Figures \ref{fig:pstm-b} and \ref{fig:pstm-simi-b} \old{shows}\new{show} the migrated profiles for blended data using the traditional semblance and the proposed high-resolution semblance, respectively. In this example, we can consider \dlo{the} Figure \ref{fig:pstm} as the true answer, and judge the performance of different approaches by comparing the migrated results with Figure \ref{fig:pstm}. We can observe huge difference between Figures \ref{fig:pstm} and \ref{fig:pstm-b}. However, Figures \ref{fig:pstm} and \ref{fig:pstm-simi-b} are more similar. We can confirm this observation by zooming a part from the original migrated profiles. Figure \ref{fig:pstmzoom,pstm-bzoom,pstm-simi-bzoom} shows the zoomed sections that correspond to the frame boxes shown in Figure \ref{fig:pstm,pstm-b,pstm-simi-b}. It is more obvious that Figures \ref{fig:pstmzoom} and \ref{fig:pstm-simi-bzoom} show very similar reflections, while Figure \ref{fig:pstm-bzoom} \old{are}\new{is} much different from the other two cases. The erroneous reflections in Figure \ref{fig:pstm-bzoom} indicate erroneous picked velocities using the traditional semblance.

\section{Conclusion}
We have demonstrated that it is possible to use NMO-based velocity analysis approach to obtain an acceptable velocity model \old{for}\new{from} the \new{very noisy} simultaneous-source data. The similarity-weighted semblance can obtain a better velocity spectrum than the conventional semblance, with higher resolution and reliability. When the blending interference \dlo{becomes}\wen{is} so strong that the seismic reflections can not be observed, the similarity-weighted semblance can still show plausible \new{energy} peaks in the velocity spectrum, and the peaks can \dlo{then} be picked easily. \old{The picked velocities from the similarity-weighted semblance can make the direct migration result of the blended data close to the unblended data, which makes the separation of simultaneous sources not necessary.} We use both simulated synthetic and field data examples to show the potential of the similarity-weighted semblance in velocity analysis of simultaneous-source data. \new{We also compare the migrated images of unblended field data, and numerically blended field data using different picked velocities. The migrated image of blended data using the picked velocity from the similarity-weighted semblance is very close to the migrated image of unblended data, which shows great potential that the separation of simultaneous sources is no longer necessary.}

\inputdir{simple}
\plot{simple-comp-dat}{width=\columnwidth}{Synthetic data example. Left: Unblended CMP gather. Right: Blended CMP gather.}
\plot{simple-comp-scn}{width=\columnwidth}{Left: Velocity spectrum of blended data using the conventional semblance. Right: Velocity spectrum of blended data using the high-resolution semblance.}
\inputdir{field}
\plot{comp-dat}{width=\columnwidth}{Field data example.  Left: Unblended CMP gather. Right: Blended CMP gather.}
\plot{comp}{width=\columnwidth}{Left: Velocity spectrum of unblended data  using conventional semblance. Middle left: Velocity spectrum of unblended data using similarity-weighted semblance. Middle right: Velocity spectrum of blended data using the conventional semblance. Right: Velocity spectrum of blended data using the high-resolution semblance.}

\inputdir{bei}
\plot{comp2}{width=\columnwidth}{(a) Blended CMP gather with strong blending interference. (b) Velocity spectrum using the conventional semblance. (c) Velocity spectrum using the high-resolution semblance.}

\section{Acknowledgement}
We would like to thank Pan Deng and Keling Chen for helpful discussions about similarity-weighted semblance, Jiang Yuan, Zhaoyu Jin, Ray Abma, Min Zhou, Araz Mahdad and Sergey Fomel for inspiring discussions about simultaneous-source acquisition. \new{We also thank Ingo Grevemeyer, and two anonymous reviewers for constructive suggestions that improve the original manuscript greatly.} This work is partially supported by the National Natural Science Foundation of China (Grant No.41274137), the National Science and Technology of Major Projects of China (Grant No. 2011ZX05019-006), National Engineering Laboratory of Offshore Oil Exploration, and the Texas Consortium for Computational Seismology (TCCS).

\inputdir{beicmps}
\multiplot{2}{gulf,gulf-b}{width=0.45\textwidth}{Gulf of Mexico data example. (a) Unblended field data. (b) Numerically simulated field data. }

\multiplot{3}{vscan-gulf,vscan-b,vscan-simi-b}{width=0.45\textwidth}{Comparison of velocity spectrum. (a) Velocity analysis of unblended data using the traditional approach. (b) Velocity analysis of blended data using the traditional approach. (c) Velocity analysis of blended data using the proposed approach.}

\multiplot{3}{pstm,pstm-b,pstm-simi-b}{width=0.45\textwidth}{Comparison of migration results. (a) PSKTM of unblended data using the traditional picked velocities. (b) PSKTM of blended data using the traditional approach. (c) PSKTM of blended data using the proposed approach.}

\multiplot{3}{pstmzoom,pstm-bzoom,pstm-simi-bzoom}{width=0.45\textwidth}{Comparison of zoomed migration results. (a) PSKTM of unblended data using the traditional approach. (b) PSKTM of blended data using the traditional approach. (c) PSKTM of blended data using the proposed approach.}

\bibliographystyle{seg}
\bibliography{vscan}

### 2020-09-16 diffrlrra/matfun/FAULTS.m

@@ -1,0 +1,34 @@
+function FAULTS(din,dout)
+% Author      : Hang Wang, Xingye Liu, and Yangkang Chen
+% Date        : March, 2020
+
+% Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
+
+%  Copyright (C) 2020 Zhejiang University
+%  Copyright (C) 2020 Hang Wang, Xingye Liu, and Yangkang Chen
+%
+%  This program is free software; you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published by
+%  the Free Software Foundation; either version 2 of the License, or
+%  (at your option) any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, write to the Free Software
+%  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307
+
+
+d=zeros(1000,250);
+rsf_read(d,din);
+
+d1=fxymssa_win_auto2(d,0,120,0.004,3,6,0,200,50,1,0.5,0.5,0.5,2);
+
+rsf_create(dout,size(d1)');
+rsf_write(d1,dout);
+
+
+    

### 2020-09-16 diffrlrra/matfun/LDRR.m

@@ -1,0 +1,65 @@
+function LDRR(din,d_lrr,d_lrra,n1,n2,n3,dt,lf,hf,N,NN,n1win,n2win,n3win,r1,r2,r3,ifdamp,verb)
+% Author      : Yangkang Chen
+% Date        : March, 2020
+
+% Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
+
+%  Copyright (C) 2020 Zhejiang University
+%  Copyright (C) 2020 Yangkang Chen
+%
+%  This program is free software; you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published by
+%  the Free Software Foundation; either version 2 of the License, or
+%  (at your option) any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, write to the Free Software
+%  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307
+
+%%from Madagascar to Matlab
+d=zeros(n1,n2*n3);
+rsf_read(d,din)
+d=reshape(d,n1,n2,n3);
+
+%%% Main program goes here !
+
+if ~ifdamp
+    %% LRR
+    d1=fxymssa_win(d,lf,hf,dt,N,verb,n1win,n2win,n3win,r1,r2,r3);
+    %% LDRR
+    d2=fxymssa_win_auto(d,lf,hf,dt,N,verb,n1win,n2win,n3win,r1,r2,r3,2);
+    
+    d1=reshape(d1,n1,n2,n3);
+    d2=reshape(d2,n1,n2,n3);
+else
+    %% LRRA
+    d3=fxydmssa_win(d,lf,hf,dt,N,NN,verb,n1win,n2win,n3win,r1,r2,r3);
+    %% LDRRA
+    d4=fxydmssa_win_auto(d,lf,hf,dt,N,NN,verb,n1win,n2win,n3win,r1,r2,r3,2);
+
+    d3=reshape(d3,n1,n2,n3);
+    d4=reshape(d4,n1,n2,n3);
+end
+
+%% from Matlab to Madagascar
+if ~ifdamp
[…]

### 2020-09-16 nonMada/cnncwt_pick/f.py

@@ -1,0 +1,827 @@
+# -*- coding: utf-8 -*-
+"""
+# Copyright (C) 2019 Guoyin Zhang and Yangkang Chen
+# Python version: python 3 
+#
+# Reference:
+# Chen, Y., G. Zhang, M. Bai, S. Zu, Z. Guan, and M. Zhang, 2019, Automatic Wave- form Classification and Arrival Picking Based on Convolutional Neural Network, Earth and Space Science, 6, 1244-1261.
+# Zhang, G., C. Lin, and Y. Chen, 2020, Convolutional Neural Networks for Microseismic Waveform Classification and Arrival Picking, Geophysics, 85, WA227–WA240.
+# Zhang, G., Z. Wang, and Y. Chen, 2018, Deep Learning for Seismic Lithology Prediction, Geophysical Journal International, 215, 1368–1387.
+"""
+
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.colors import ListedColormap
+import struct
+ 
+from sklearn.metrics import accuracy_score, f1_score
+from sklearn.cluster import KMeans, SpectralClustering
+from sklearn import preprocessing
+
+import skfuzzy as fuzz
+
+import f_time_frequency as tf
+
+#%% function defination
+def read_bin(fpath):
+    with open(fpath, 'rb') as f:  data = f.read()
+    #len(data)
+    data = struct.unpack("=2901000f", data)
+    data = np.array(data)
+    data = data.reshape(967,3000).T
+    return data
+
+
+def rickerz(f=20, length=0.1, dt=0.004):
+    t = np.linspace(-length/2, (length)/2, length/dt)
+    y = (1-2*(np.pi**2)*(f**2)*(t**2))*np.exp(-(np.pi**2)*(f**2)*(t**2))
+    return t, y
+
+
+def snrz(g, f):
+    '''
+    To calculate the signal-to-noise_ratio.
+    
+    g: ground truth image
+    f: noisy/restored image
+    g,f: 1D or 2D array
+    
+    according to:
+        Yangkang, Chen;
+        https://en.wikipedia.org/wiki/Signal-to-noise_ratio
+    '''
+    g=np.array(g)
+    f=np.array(f)
+    
+    if g.shape != f.shape: print('Dimesion of two images don''t match!')
+    else:
+        psnr = 20*np.log10(np.linalg.norm(g,'fro')/np.linalg.norm(g-f,'fro'))
+    
[…]

### 2020-09-16 nonMada/cnncwt_pick/main_obs.py

@@ -1,0 +1,494 @@
+# -*- coding: utf-8 -*-
+"""
+# Copyright (C) 2019 Guoyin Zhang and Yangkang Chen
+# Python version: python 3 
+#
+# Reference:
+# Chen, Y., G. Zhang, M. Bai, S. Zu, Z. Guan, and M. Zhang, 2019, Automatic Wave- form Classification and Arrival Picking Based on Convolutional Neural Network, Earth and Space Science, 6, 1244-1261.
+# Zhang, G., C. Lin, and Y. Chen, 2020, Convolutional Neural Networks for Microseismic Waveform Classification and Arrival Picking, Geophysics, 85, WA227–WA240.
+# Zhang, G., Z. Wang, and Y. Chen, 2018, Deep Learning for Seismic Lithology Prediction, Geophysical Journal International, 215, 1368–1387.
+"""
+
+#%% Package import
+
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.colors import ListedColormap
+import pandas as pd
+
+from sklearn.model_selection import train_test_split
+from sklearn.neural_network import MLPClassifier 
+from sklearn.metrics import accuracy_score, f1_score
+from sklearn import preprocessing
+
+from keras.utils import np_utils
+from keras.optimizers import Adam
+from keras.models import Model
+
+import f_nnclassifier as classifier
+import f_time_frequency as tf
+import f
+
+#%% Data import and parameter defination
+
+'''import observed and synthetic data'''
+#Syn = f.read_bin(fpath='data/syn2d_3000_967_fhi10.bin')
+Obso = f.read_bin(fpath='data/obs2d_3000_967_fhi10.bin')
+#Obs = pd.read_csv("data/micro.csv", header=None)
+
+# add normally random noise
+np.random.seed(20180319)
+Obs = Obso  + np.random.randn(Obso.shape[0],Obso.shape[1])*0.04
+
+ssnr = f.snrz(Obso,Obs)
+print('The signal to noise ratio is:', ssnr)
+
+nt = Obs.shape[0]  # the number of time records of a trace
+dt = 0.0015  # time interval
+
+t = np.arange(nt)*dt*1000
[…]

### 2020-09-16 nonMada/dlmtask/MTSNMF.m

@@ -1,0 +1,198 @@
+function [A, S] = MTSNMF(X, r, lambda, opts)
+%MTSNMF multi-task sparse NMF.
+%
+% Description:
+%    Multi-task sparse NMF solves the problem:
+%    (A_1,...,A_K,S) = argmin sum_k (||X_k-A_k*S||_F^2 + lambda_k*||S||_1).
+%
+%    [A, S] = MTSNMF(X, r, lambda) performs a multi-task sparse NMF with
+%    rank R on all M-by-N data matrices in the K-by-1 cell array X,
+%    resulting in K M-by-R basis matrices included in K-by-1 cell array A
+%    and a common R-by-N coefficient matrix S.
+%
+% Syntax:
+%    [A, S] = MTSNMF(X, r, lambda, opts)
+%
+% Inputs:
+%    X      - K-by-1 cell array containing K M-by-N data matrices to be
+%               factorized.
+%    r      - Rank of approximation (number of basis atoms in A_1,...,A_K)
+%    lambda - Regularization parameter. K-by-1 vector containing lambda_1,
+%               lambda_2,...,lambda_K.
+%    opts   - Options:
+%               opts.maxit   - Maximal iteration number. Default is 3000.
+%               opts.tol     - Convergence tolerance. The convergence is
+%                                achieved when C(t)-C(t-1) < C(t)*opts.tol.
+%                                Default is 1e-5.
+%               opts.verbose - Verbose or not. Default is true.
+%
+% Outputs:
+%    A      - K-by-1 cell array containing K M-by-R basis matrices.
+%    S      - R-by-N coefficient matrix shared by all tasks.
+
+
+error(nargchk(3, 4, nargin, 'struct'));
+
+maxit = 3000;
+tol = 1e-5;
+alpha = 1;
+tau = 0.2;
+verbose = true;
+
+if exist('opts', 'var')
+    if isfield(opts, 'maxit')
+        maxit = opts.maxit;
+    end
+    if isfield(opts, 'tol')
+        tol = opts.tol;
+    end
+    if isfield(opts, 'tau')
+        tau = opts.tau;
+    end
+    if isfield(opts, 'alpha')
+        alpha = opts.alpha;
+    end
+    if isfield(opts, 'verbose')
+        verbose = opts.verbose;
+    end
+end
+
+
+if ~iscell(lambda)
[…]

### 2020-09-16 nonMada/dlmtask/MTSNMF_MU.m

@@ -1,0 +1,153 @@
+function [A, S] = MTSNMF_MU(X, r, LA, lambda, opts)
+%MTSNMF multi-task sparse NMF.
+%
+% Description:
+%    Multi-task sparse NMF solves the problem:
+%    (A_1,...,A_K,S) = argmin sum_k (||X_k-A_k*S||_F^2 + lambda_k*||S||_1).
+%
+%    [A, S] = MTSNMF(X, r, lambda) performs a multi-task sparse NMF with
+%    rank R on all M-by-N data matrices in the K-by-1 cell array X,
+%    resulting in K M-by-R basis matrices included in K-by-1 cell array A
+%    and a common R-by-N coefficient matrix S.
+%
+% Syntax:
+%    [A, S] = MTSNMF(X, r, lambda, opts)
+%
+% Inputs:
+%    X      - K-by-1 cell array containing K M-by-N data matrices to be
+%               factorized.
+%    r      - Rank of approximation (number of basis atoms in A_1,...,A_K)
+%    lambda - Regularization parameter. K-by-1 vector containing lambda_1,
+%               lambda_2,...,lambda_K.
+%    opts   - Options:
+%               opts.maxit   - Maximal iteration number. Default is 3000.
+%               opts.tol     - Convergence tolerance. The convergence is
+%                                achieved when F(t)-F(t-1) < F(t)*opts.tol.
+%                                Default is 1e-5.
+%               opts.verbose - Verbose or not. Default is true.
+%
+% Outputs:
+%    A      - K-by-1 cell array containing K M-by-R basis matrices.
+%    S      - R-by-N coefficient matrix shared by all tasks.
+%
+
+error(nargchk(4, 5, nargin, 'struct'));
+
+maxit = 3000;
+tol = 1e-5;
+alpha = 1;
+tau = 0.2;
+verbose = true;
+
+if exist('opts', 'var')
+    if isfield(opts, 'maxit')
+        maxit = opts.maxit;
+    end
+    if  isfield(opts, 'tol')
+        tol = opts.tol;
+    end
+    if  isfield(opts, 'tau')
+        tau = opts.tau;
+    end
+    if  isfield(opts, 'alpha')
+        alpha = opts.alpha;
+    end
+    if  isfield(opts, 'verbose')
[…]

### 2020-09-16 nonMada/dlmtask/Norm.m

@@ -1,0 +1,7 @@
+function [NDnorm,min_val,max_val] = Norm(ND)
+
+min_val=min(min(min(ND)));
+max_val=max(max(max(ND)));
+NDnorm=(ND-min_val)/(max_val-min_val);
+
+return

### 2020-09-16 nonMada/dlmtask/est_noise.m

@@ -1,0 +1,11 @@
+function sigma = est_noise(DataCube)
+[m,n,p]=size(DataCube);
+data=reshape(DataCube,[p,m*n])';
+sigma=zeros(p,1);
+
+for i=1:p
+    y=data(:,i);
+    X=data;
+    X(:,i)=[];
+    sigma(i)=std(X*((X'*X)\(X'*y))-y);
+end

### 2020-09-16 nonMada/dlmtask/test_dl_multitask.m

@@ -1,0 +1,70 @@
+clc;clear;close all;
+%% DEMO script for the Multitask dictionary learning algorithm
+% Written by Yangkang Chen
+% March, 2020
+% 
+% Key Reference:
+% Siahsar, M. A. N., Gholtashi, S., Kahoo, A. R., W. Chen, and Y. Chen, 2017, Data-driven multi-task sparse dictionary learning for noise attenuation of 3D seismic data, Geophysics, 82, V385-V396.
+%
+% Some subroutines introduced in:
+% Siahsar, M. A. N., V. Abolghasemi, and Y. Chen, 2017, Simultaneous denoising and interpolation of 2D seismic data using data-driven non-negative dictionary learning, Signal Processing, 141, 309-321.
+% Chen, Y., 2020, Fast dictionary learning for noise attenuation of multidimensional seismic data, Geophysical Journal International, 222, 1717?1727.
+% Chen, Y., M. Zhang, M. Bai, and W. Chen, 2019, Improving the signal-to-noise ratio of seismological datasets by unsupervised machine learning, Seismological Research Letters, 90, 1552-1564.
+% Chen, Y., S. Zu, W. Chen, M. Zhang, and Z. Guan, 2020, Learning the blending spikes using sparse dictionaries, Geophysical Journal International, 222, 1846?1863. 
+% Wang, H., Q. Zhang, G. Zhang, J. Fang, and Y. Chen, 2020, Self-training and learning the waveform features of microseismic data using an adaptive dictionary, Geophysics, 85, KS51?KS61.
+% Chen, Y., S. Fomel, 2015, Random noise attenuation using local signal-and-noise orthogonalization, Geophysics, 80, WD1-WD9.
+% Chen, Y., J. Ma, and S. Fomel, 2016, Double-sparsity dictionary for seismic noise attenuation, Geophysics, 81, V17-V30.
+% Zu, S., H. Zhou, R. Wu, M. Jiang, and Y. Chen, 2019, Dictionary learning based on dip patch selection training for random noise attenuation, Geophysics, 84, V169?V183.
[…]

### 2020-09-16 nonMada/dlmtask/yc_wigb.m

@@ -1,0 +1,118 @@
+function yc_wigb(a,scal,x,z,amx)
+%YC_WIGB: Plot seismic data using wiggles.
+%
+%  YC_WIGB(a,scal,x,z,amx) 
+%
+%  IN  a:     seismic data (a matrix, traces are columns)
+%      scale: multiple data by scal
+%      x:     horizontal axis (often offset)
+%      z:     vertical axis (often time)
+%
+%  Note
+%
+%    If only 'a' is enter, 'scal,x,z,amn,amx' are set automatically; 
+%    otherwise, 'scal' is a scalar; 'x, z' are vectors for annotation in 
+%    offset and time, amx are the amplitude range.
+%
+%
+%  Author(s): Xingong Li (Intseis, Integrated Seismic Solutions)
+%  Copyright 1998-2003 Xingong 
+% 
+%  Modified by Yangkang Chen, Nov, 2016
+%  
+
+ if nargin == 0, nx=10;nz=10; a = rand(nz,nx)-0.5; end;
+
+ [nz,nx]=size(a);
+
+ trmx= max(abs(a));
+ if (nargin <= 4); amx=mean(trmx);  end;
+ if (nargin <= 2); x=[1:nx]; z=[1:nz];  end;
+ if (nargin <= 1); scal =1; end;
+
+ if nx <= 1; disp(' ERR:PlotWig: nx has to be more than 1');return;end;
+
+ % take the average as dx
+
+	dx1 = abs(x(2:nx)-x(1:nx-1));
+ 	dx = median(dx1);
+
+
+ dz=z(2)-z(1);
+ xmx=max(max(a)); xmn=min(min(a)); 
+
+ if scal == 0; scal=1; end;
+ a = a * dx /amx; 
+ a = a * scal;
+
+ fprintf(' PlotWig: data range [%f, %f], plotted max %f \n',xmn,xmx,amx);
+ 
+% set display range 
+
+ x1=min(x)-2.0*dx; x2=max(x)+2.0*dx;
+ z1=min(z)-dz; z2=max(z)+dz;
+ 
+ set(gca,'NextPlot','add','Box','on', ...
+  'XLim', [x1 x2], ...
+  'YDir','reverse', ...
+  'YLim',[z1 z2]);
+
+ 
+
+	fillcolor = [0 0 0];
+	linecolor = [0 0 0];
+	linewidth = 1.;
+
[…]

### 2020-09-16 nonMada/mdl/test_real.m

@@ -1,0 +1,290 @@
+clc;clear;close all;
+%Demo for microseismic data denoising using 1D dictionary learning
+%Prepared By Yangkang Chen and Hang Wang
+%Dec, 09, 2018
+%
+% Key Reference
+% Wang, H., Q. Zhang, G. Zhang, J. Fang, and Y. Chen, 2020, Self-training and learning the waveform features of microseismic data using an adaptive dictionary, Geophysics, 85, KS51-KS61.
+%
+% For more details about dictionary learning and denoising, please refer to
+% Siahsar, M. A. N., Gholtashi, S., Kahoo, A. R., W. Chen, and Y. Chen, 2017, Data-driven multi-task sparse dictionary learning for noise attenuation of 3D seismic data, Geophysics, 82, V385-V396.
+% Siahsar, M. A. N., V. Abolghasemi, and Y. Chen, 2017, Simultaneous denoising and interpolation of 2D seismic data using data-driven non-negative dictionary learning, Signal Processing, 141, 309-321.
+% Chen, Y., 2020, Fast dictionary learning for noise attenuation of multidimensional seismic data, Geophysical Journal International, 222, 1717?1727.
+% Chen, Y., M. Zhang, M. Bai, and W. Chen, 2019, Improving the signal-to-noise ratio of seismological datasets by unsupervised machine learning, Seismological Research Letters, 90, 1552-1564.
+% Chen, Y., S. Zu, W. Chen, M. Zhang, and Z. Guan, 2020, Learning the blending spikes using sparse dictionaries, Geophysical Journal International, 222, 1846?1863. 
+% Wang, H., Q. Zhang, G. Zhang, J. Fang, and Y. Chen, 2020, Self-training and learning the waveform features of microseismic data using an adaptive dictionary, Geophysics, 85, KS51-KS61.
[…]

### 2020-09-16 nonMada/mdl/test_syn.m

@@ -1,0 +1,433 @@
+clc;clear;close all;
+% Demo for microseismic data denoising using 1D dictionary learning
+% Prepared By Yangkang Chen and Hang Wang
+% Dec, 09, 2018
+%
+% Key Reference
+% Wang, H., Q. Zhang, G. Zhang, J. Fang, and Y. Chen, 2020, Self-training and learning the waveform features of microseismic data using an adaptive dictionary, Geophysics, 85, KS51-KS61.
+%
+% For more details about dictionary learning and denoising, please refer to
+% Siahsar, M. A. N., Gholtashi, S., Kahoo, A. R., W. Chen, and Y. Chen, 2017, Data-driven multi-task sparse dictionary learning for noise attenuation of 3D seismic data, Geophysics, 82, V385-V396.
+% Siahsar, M. A. N., V. Abolghasemi, and Y. Chen, 2017, Simultaneous denoising and interpolation of 2D seismic data using data-driven non-negative dictionary learning, Signal Processing, 141, 309-321.
+% Chen, Y., 2020, Fast dictionary learning for noise attenuation of multidimensional seismic data, Geophysical Journal International, 222, 1717?1727.
+% Chen, Y., M. Zhang, M. Bai, and W. Chen, 2019, Improving the signal-to-noise ratio of seismological datasets by unsupervised machine learning, Seismological Research Letters, 90, 1552-1564.
+% Chen, Y., S. Zu, W. Chen, M. Zhang, and Z. Guan, 2020, Learning the blending spikes using sparse dictionaries, Geophysical Journal International, 222, 1846?1863. 
+% Wang, H., Q. Zhang, G. Zhang, J. Fang, and Y. Chen, 2020, Self-training and learning the waveform features of microseismic data using an adaptive dictionary, Geophysics, 85, KS51-KS61.
[…]

### 2020-09-16 nonMada/mdl/yc_mf.m

@@ -1,0 +1,78 @@
+function [ D1 ] = yc_mf(D,nfw,ifb,axis)
+%YC_MF: median filter along first or second axis for 2D profile
+%  IN   D:   	intput data 
+%       nfw:    window size 
+%       ifb:    if use padded boundary (if not, zero will be padded)
+%       axis:    temporal sampling interval
+%      
+%  OUT   D1:  	output data
+% 
+%  Copyright (C) 2014 The University of Texas at Austin
+%  Copyright (C) 2014 Yangkang Chen
+%
+% Example: dsp/test_yc_meanf_repeat.m
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details: http://www.gnu.org/licenses/
+%
+% REFERENCE
+% For more details about median filtering in seismics, please refer to 
+% Chen, Y., J. Yuan, Z. Jin, K. Chen and L. Zhang, 2014, Deblending using normal moveout and median filtering in common-midpoint gather, Journal of Geophysics and Engineering, 11, 045012.
+% Chen, Y., 2015, Deblending using a space-varying median filter, Exploration Geophysics, 46, 332-341.
+% Gan, S., S. Wang, Y. Chen, X. Chen, and Kui Xiang, 2016, Separation of simultaneous sources using a structural-oriented median filter in the flattened dimension, Computers & Geosciences, 86, 46-54.
+% Huang, W., R. Wang, X. Gong, and Y. Chen, 2018, Iterative deblending of simultaneous- source seismic data with structuring median constraint, IEEE Geoscience and Remote Sensing Letters, 15, 58-62.
[…]

### 2020-09-16 nonMada/mdl/yc_mfs.m

@@ -1,0 +1,65 @@
+function [ dout ] = yc_mfs(din,nfw,ifb,axis,ntimes)
+%YCMFS: median filter along first or second axis for 2D profile
+%  IN   D:   	intput data 
+%       nfw:    window size
+%       ifb:    if use padded boundary (if not, zero will be padded)
+%       axis:    temporal sampling interval
+%       tmes:   number of filtering times
+%      
+%  OUT   D1:  	output data
+% 
+%  Copyright (C) 2018 The University of Texas at Austin
+%  Copyright (C) 2018 Yangkang Chen
+%
+% Example: dsp/test_yc_meanf_repeat.m
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details: http://www.gnu.org/licenses/
+%
+% REFERENCE
+% For more details about median filtering in seismics, please refer to 
+% Chen, Y., J. Yuan, Z. Jin, K. Chen and L. Zhang, 2014, Deblending using normal moveout and median filtering in common-midpoint gather, Journal of Geophysics and Engineering, 11, 045012.
+% Chen, Y., 2015, Deblending using a space-varying median filter, Exploration Geophysics, 46, 332-341.
+% Gan, S., S. Wang, Y. Chen, X. Chen, and Kui Xiang, 2016, Separation of simultaneous sources using a structural-oriented median filter in the flattened dimension, Computers & Geosciences, 86, 46-54.
+% Huang, W., R. Wang, X. Gong, and Y. Chen, 2018, Iterative deblending of simultaneous- source seismic data with structuring median constraint, IEEE Geoscience and Remote Sensing Letters, 15, 58-62.
+% Chen, Y., S. Zu, Y. Wang, and X. Chen, 2020, Deblending of simultaneous-source data using a structure-oriented space varying median filter, Geophysical Journal International, 222, 1805?1823.
[…]

### 2020-09-16 nonMada/mdl/yc_micro_emd.m

@@ -1,0 +1,18 @@
+function d1 = yc_micro_emd(d)
+% Simple EMD denoise
+% by Hang Wang and Yangkang Chen
+% Zhejiang University
+% 
+% Reference:
+% Wang, H., Q. Zhang, G. Zhang, J. Fang, and Y. Chen, 2020, Self-training and learning the waveform features of microseismic data using an adaptive dictionary, Geophysics, 85, KS51-KS61.
+
+[n1,n2]=size(d);
+
+d1=zeros(size(d));
+for i2=1:n2
+   tmp=emd(d(:,i2)); 
+   d1(:,i2)=sum(tmp(2:end,:),1)'; 
+end
+
+end
+

### 2020-09-16 nonMada/mdl/yc_patch_inv.m

@@ -1,0 +1,91 @@
+function [ A ] = yc_patch_inv( X,mode,n1,n2,l1,l2,o1,o2 )
+% insert patches into the image
+%  
+% by Yangkang Chen
+% Oct, 2017
+%
+% Input: 
+%   D: input image
+%   mode: patching mode
+%   l1: first patch size
+%   l2: second patch size
+%   o1: first shifting size
+%   o2: second shifting size
+%   
+% Output:
+%   X: patches
+% 
+% Modified on Dec 12, 2018 (the edge issue, arbitrary size for the matrix)
+% 		      Dec 31, 2018 (tmp1=mod(n1,l1) -> tmp1=mod(n1-l1,o1))
+% 
+% References:
+% Siahsar, M. A. N., Gholtashi, S., Kahoo, A. R., W. Chen, and Y. Chen, 2017, Data-driven multi-task sparse dictionary learning for noise attenuation of 3D seismic data, Geophysics, 82, V385-V396.
+% Siahsar, M. A. N., V. Abolghasemi, and Y. Chen, 2017, Simultaneous denoising and interpolation of 2D seismic data using data-driven non-negative dictionary learning, Signal Processing, 141, 309-321.
+% Chen, Y., 2020, Fast dictionary learning for noise attenuation of multidimensional seismic data, Geophysical Journal International, 222, 1717?1727.
+% Chen, Y., M. Zhang, M. Bai, and W. Chen, 2019, Improving the signal-to-noise ratio of seismological datasets by unsupervised machine learning, Seismological Research Letters, 90, 1552-1564.
+% Chen, Y., S. Zu, W. Chen, M. Zhang, and Z. Guan, 2020, Learning the blending spikes using sparse dictionaries, Geophysical Journal International, 222, 1846?1863. 
+% Wang, H., Q. Zhang, G. Zhang, J. Fang, and Y. Chen, 2020, Self-training and learning the waveform features of microseismic data using an adaptive dictionary, Geophysics, 85, KS51-KS61.
[…]

### 2020-09-16 qcomp/matfun/time_absorp_wavelet_matrix.m

@@ -1,0 +1,72 @@
+function [FW,TW] = time_absorp_wavelet_matrix_real(nt,dt,fdom,Q);
+
+%  IN   nt:     lenght of the trace
+%       dt:       sampling interval in secs
+%       fdom:     dominant frequency in Hz 
+%       Q:        quality factor
+%
+%  OUT  TW:  time_absorp_wavelet_matrix
+
+sign = mod(nt,2);
+if(sign == 1)
+    df = 1/(nt*dt);  
+else
+   nt=nt+1;
+   df = 1/(nt*dt);   
+end 
+ 
+% create a time vector
+  t=-ceil((nt-1)/2)*dt:dt:floor((nt-1)/2)*dt;
+  
+% create the Ricker wavelet
+  pf=pi^2*fdom^2;
+  w=(1-2.*pf*t.^2).*exp(-pf*t.^2);
+  w=w./max(abs(w));
+  
+% the wavelet in frequency domain
+  nn=ceil((nt-1)/2)+1;
+  ww=[w(nn:end),w(1:nn-1)];
+  W=fft(ww);
+  W(1,1)=0;
+  
+  f_ref=10*fdom;
+  
+% the wavelet absorption in frequency domain
+  A=zeros(nn,nt);
+  for i=2:nn
+      for k=1:nt
+          A(i,k)=exp(-(pi*df*(i-1)*(k-1)*dt)/Q(k))...
+                     *exp(j*2*log((i-1)*df/f_ref)*(i-1)*df*(k-1)*dt/Q(k));
+      end
+  end 
+  
+   FW=A;
+    
+  A1=A(2:nn,:);   
+  A1=conj(A1);
+  A1=flipud(A1);
+  WA=[A;A1]; 
+      
+% translate to the time domain
+  TWA=zeros(nt,nt);
+  for i=1:nt
+      TWA(:,i)=ifft(WA(:,i));
+  end
+      
+  TW=zeros(nt,nt);
+  ss=[TWA(nn+1:end,:);TWA(1:nn,:)];
+  for i=1:nn
+      TW(1:nn+i-1,i)=ss(nn-i+1:end,i);
+  end
+  for i=1:nn-1
+      TW(i+1:end,i+nn)=ss(1:end-i,i+nn);
+  end 
+  
+  if(sign == 1)
+      return;
+  else
+      TW=TW(1:end-1,1:end-1);
+  end
+  
+
+return;

### 2020-10-10 dtv/paper.tex
2020年10月 9日 星期五 21时53分48秒 CDT

%\documentclass[manuscript]{geophysics}
%	\usepackage{amsmath}
%	\usepackage{amssymb}
%	\usepackage{graphicx}
%	\usepackage{indentfirst}
%	\usepackage{lineno}
%	\usepackage{algorithm,algorithmic}
%	\usepackage{float}
%\begin{document}

\title{Full waveform inversion and joint migration inversion with an automatic directional total variation constraint}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\author{Shan Qu\footnotemark[1], Eric Verschuur\footnotemark[1] Yangkang Chen\footnotemark[2]}
\address{
\footnotemark[1] Delft University of Technology, Delphi consortium, \\
Mekelweg 5, 2628 CD Delft, Netherlands \\
\footnotemark[2] School of Earth Sciences, \\
Zhejiang University\\
 Hangzhou, Zhejiang Province, 310027
}

\lefthead{Qu et al.}
\righthead{Directional TV}

\maketitle

%\begin{center}
%\huge{\textbf{Full waveform inversion and joint migration inversion with an automatic directional total variation constraint}} 
%\end{center}

\begin{abstract}
\old{As full waveform inversion (FWI) is a non-unique and typically ill-posed inversion problem, it needs proper regularization. To reduce the non-linearity of FWI, Joint Migration Inversion (JMI) is proposed as an alternative, explaining the data with decoupled velocity and reflectivity parameters, however, the velocity update may also suffer from being trapped in local minima. To optimally include geologic information, we propose FWI/JMI with directional total variation as an L1-norm regularization on the velocity. We design the directional total variation (TV) operator based on the local dip field, instead of ignoring the local structural direction and only using horizontal/vertical gradients in the traditional TV. With two complex synthetic examples, based on the Marmousi model, we demonstrate that the proposed method is much more effective compared to both FWI/JMI without regularization and FWI/JMI with the conventional TV regularization. In the JMI-based example, we also show that L1 directional TV works better than L2 directional Laplacian smoothing.}
\new{As full waveform inversion (FWI) is a non-unique and typically ill-posed inversion problem, it needs proper regularization to avoid cycle-skipping. To reduce the non-linearity of FWI, Joint Migration Inversion (JMI) is proposed as an alternative, explaining the reflection data with decoupled velocity and reflectivity parameters. However, the velocity update may also suffer from being trapped in local minima. To optimally include geologic information, we propose FWI/JMI with directional total variation as an L1-norm regularization on the velocity. We design the directional total variation operator based on the local dip field, instead of ignoring the local structural direction of the subsurface and only using horizontal- and vertical- gradients in the traditional TV. The local dip field is estimated using plane-wave destruction based on a raw reflectivity model, which is usually calculated from the initial velocity model. With two complex synthetic examples, based on the Marmousi model, we demonstrate that the proposed method is much more effective compared to both FWI/JMI without regularization and FWI/JMI with the conventional TV regularization. In the JMI-based example, we also show that L1 directional TV works better than L2 directional Laplacian smoothing. In addition, by comparing these two examples, it can be seen that the impact of regularization is larger for FWI than for JMI, because in JMI the velocity model only explains the propagation effects and, thereby, makes it less sensitive to the details in the velocity model.} \par
\textbf{Key words:} FWI, JMI, regularization, total variation, directional
\end{abstract}

\section{Introduction}
Seismic full waveform inversion (FWI) is a powerful method for providing a quantitative description of
the \new{subsurface} properties by iteratively minimizing an objective function that measures the misfit between observed and predicted data in the least-squares sense \citep{tarantola1984inversion}. However, FWI is a non-linear and ill-posed inverse problem and its objective function may suffer from local minima that are not informative about the true parameters \citep{Virieux09,yangkang2016fwi,fu2017adaptive,fu2017discrepancy}. Using regularization methods is \new{an}\old{one} effective way to mitigate this ill-posedness and non-uniqueness of FWI.

Joint Migration Inversion (JMI) was proposed as one of the methods to overcome the \new{above-mentioned}\old{above mentioned} limitations in FWI \citep{Berkhout14b,Staalthesis,verschuur2016joint}. It is an inverse algorithm to automatically derive both velocity and reflectivity based on the full wavefield modeling (FWMod) process \citep{Berkhout14a} that takes into account transmission effects and surface/internal multiples. In the FWMod procedure, the velocity only affects the kinematics without any scattering effect in the modeling operators and the reflectivity only deals with scattering effects. These characteristics lead to a reduced non-linearity in the inversion process. Even though not as severe as FWI, the velocity update may still \old{slightly }suffer from being trapped in local minima. With the help of regularization, JMI can get a \old{better and smoothed}\new{more accurate} inverted velocity, and thus achieve a better inverted reflectivity \citep{qu161,qu2017i4d}.

The popular regularization methods include: quadratic \new{L2-norm-based}\old{L2-norm based} regularization, such as Tikhonov regularization \citep{Hu09}, and laplacian smoothing \citep{guitton2012constrained,qu162,qu2017simultaneous}, which tend to produce models with blurred discontinuities; non-quadratic \new{L1-norm-based}\old{L1-norm based} regularization, such as total variation (TV) \citep{anagaw2011full,qu161}, smooths the model by enhancing the sparsity of the spatial gradient of the velocity, thereby\old{,} preserving its edges. However, regular TV regularization only tends to reduce the horizontal and vertical gradients of each gridpoint in the model regardless of their structural direction. Thus, TV is not suitable where the local geologic structure has a dominant structural direction. Unlike general digital images, the spatial changes of the seismic model always have some specific geological structures, like tilted layers, faults, or edges of a salt body \citep{yangkang2017lsrtm,wujuan2018cg1,baimin2018cg,yangkang2018gji3}. \cite{bayram2012directional} proposed a directional TV method and applied it to digital image denoising. However, they only consider one single dominant direction for all pixels, which is obviously ineffective for \new{complex-textured}\old{complex textured} geologies. \new{Therefore, we propose a directional TV constraint based on a rough estimate of the subsurface image.}

The paper is organized as follows: we first briefly introduce the basics of FWI and JMI. Next, we formulate the conventional TV and the proposed directional TV. Finally, \new{using}\old{with} two complex Marmousi-model-based examples, we show that the proposed method is more effective than the alternative methods, when the model contains tilted layers and steep faults. \new{At}\old{In} the end, \new{using the JMI-based example, }we also show that\new{ the} L1 directional TV works better than\new{ the} L2 directional Laplacian smoothing regarding \new{the preservation of}\old{persevering} edges and \new{the} steering \new{of the} update \new{away} from\new{ the} local minimum\old{with the JMI-based example}. \new{Note}\old{Please note} that this paper is an extended version of work published in \cite{qu2017full}.

\section{Theory of FWI}
Mathematically, regular FWI can be formulated as a minimization problem with the following objective function:
\begin{equation}
\begin{split}
      J_{FWI} &=|| \mathbf{d} - f\left(\mathbf{m}\right) ||_2^2 + constraint,
\label{eq1:FWI}
\end{split}
\end{equation}
where $\mathbf{m}$ represents the model, $\mathbf{d}$ is the observed dataset, $f\left(.\right)$ is the corresponding \new{modeling}\old{modelling} operator, and $||.||_2^2$ stands for the L2-norm. In most FWI implementations, $\mathbf{m}$ consists of a gridded velocity distribution that explains both propagation and reflection of the seismic data\new{ and forward modeling is done via a finite-difference implementation of the two-way wave equation} \citep{Virieux09}. Note that in most FWI implementations, density variations are neglected. Minimizing this misfit function is likely to suffer from ill-posedness and non-uniqueness because of limited input data and non-linearity of the forward \new{modeling}\old{modelling} operator. Adding regularization to the objective function can be one effective way to mitigate the ill-posedness and non-uniqueness of this inverse problem.

\section{Theory of JMI}
Joint Migration Inversion (JMI) was proposed as one of the methods to overcome the \new{above-mentioned}\old{above mentioned} limitations in FWI. In \new{Figure}\old{figure}~\ref{fig:jmi_scheme} the flow diagram of the JMI process is shown. The main engine of the JMI method is a \new{forward-modeling}\old{forward modeling} process, called Full Wavefield Modeling (FWMod) based on \new{the} parameters reflectivity and velocity, which is described in \cite{Berkhout12}, \cite{Davydenko12a}\new{,} and \cite{Berkhout14a}. With this recursive and iterative two-way modeling process, from the current estimate of the reflectivities and the velocity model, the seismic reflection responses are being generated. In this modeling process, multiples and transmission effects are included. Next, the modeled responses are compared to the measured ones and the resulting difference data, being the residual of the inversion, is back-projected into the parameter space via reverse extrapolation of the residual into the medium and a subsequent transformation of this residual energy into updates of reflectivity and velocity. The parameters are updated, from which new seismic responses are modeled, yielding the next version of the residual data. In this way, the residual is slowly driven to zero \cite[]{Berkhout12,Staal12,Staal13,Berkhout14c}. We can treat the whole procedure as minimizing the following objective function:
\begin{equation}
J_{JMI} = \sum\limits_{\omega} || \mathbf{D}^-\left(z_0\right) - \mathbf{P}^-_{mod} \left( z_0,\mathbf{r}, \mathbf{v} \right) ||_2 ^2  + constraint,
\label{eq1:JMI inversion}
\end{equation}
where the $|| . ||^2$ describes the sum of the squares of the values (i.e.\new{,} the energy), $\mathbf{D}^-\left(z_0\right)$ is the collection of all recorded surface seismic shot records in the $\left( x,\omega \right)$ domain, and $\mathbf{P}^-_{mod} \left( z_0,\mathbf{r}, \mathbf{v} \right)$ describes the \new{modeled}\old{modelled} surface shot records as a function of reflectivity $\mathbf{r}$ and velocity $\mathbf{v}$\old{ respectively}. Note that by using \new{the} reflectivity and propagation velocity as parameters, density variations are implicitly included in $\mathbf{r}$. Even though JMI has a reduced non-linearity, the velocity update still \old{to some extend }suffers from local minima. With a proper constraint, JMI can lead to a \old{better and smoothed}\new{more accurate} inverted velocity, and therefore a better inverted reflectivity.

\section{FWI/JMI with TV and Directional TV}
In this paper, we consider anisotropic TV as the basic regularization method, since TV can smooth the model and at the same time preserve edges by enhancing the sparsity of the spatial gradient of the velocity difference. In addition, the anisotropic version is easier to minimize compared to the isotropic one. \new{Furthermore, we restrict ourselves to the 2D case, although extension to the full 3D situation is relatively straightforward.}

The extended misfit function with a TV constraint can be expressed as
\begin{equation}
\begin{split}
      J_{tot} = \mu J + \lambda C_{TV} \left(\mathbf{p} \right) = \mu J + \lambda ||\nabla_x \mathbf{p}||_1 + \lambda ||\nabla_z \mathbf{p}||_1.
\label{eq2:J with TV}
\end{split}
\end{equation}
Here, $J$ is $J_{FWI}$ or $J_{JMI}$. $\mathbf{p}$ is the parameter constrained by TV( $\mathbf{p}=\mathbf{m}$ for FWI, and $\mathbf{p} = \mathbf{v}$ for JMI). $\nabla_x$ and $\nabla_z$ represent \new{horizontal- and vertical-}\old{horizontal and vertical }gradient operator, respectively. For one gridpoint $\left(i,j\right)$ in a cartesian coordinate $\left(x,z\right)$, $\nabla_x \mathbf{p}\left(i,j\right) = p_{i+1,j} - p_{i,j}$ and $\nabla_z \mathbf{p}\left(i,j\right) = p_{i,j+1} - p_{i,j}$ (illustrated in figure~\ref{fig:FWI_fig1-01}a with the black dashed arrows). $\mu$ is the weight parameter of the fidelity term. $\lambda$ is the coefficient of the constraint term. \new{The latter two}\old{They} together control the balance between the regularization and the misfit function.

However, this conventional TV regularization only tends to reduce the \new{horizontal- and vertical-}\old{horizontal and vertical }gradients of each gridpoint in the model, regardless of the geological direction of the model. Therefore, TV is not suitable where the local structure has a dominant direction. Unlike general digital images, the spatial changes in the subsurface always follow some specific geological structures, e.g., tilted layers, faults, and edges of a salt body. In this case, we propose FWI/JMI with directional TV and we design the directional TV based on the local dip estimated\new{ from a rough reflection image} using the plane-wave destruction (PWD) algorithm \citep{fomel2002applications}.

The misfit function with directional TV can be formulated as
\begin{equation}
\begin{split}
      J_{tot} = \mu J + \lambda C_{DTV} \left(\mathbf{p} \right) = \mu J + \lambda ||\nabla_1 \mathbf{p}||_1 + \lambda ||\nabla_2 \mathbf{p}||_1,
\label{eq3:J with DTV}
\end{split}
\end{equation}
where $\nabla_1$ and $\nabla_2$ \new{are}\old{is} the gradient \new{operators}\old{operator} of the dominant direction and the direction perpendicular to the dominant direction, respectively. From the viewpoint of physical meaning, $\nabla_1$ and $\nabla_2$ are the rotated and scaled version of $\nabla_x$ and $\nabla_z$, according to the estimated local dip and a weighting parameter. Mathematically, for one point $\left(i,j\right)$, $\nabla_1 \mathbf{p}\left(i,j\right)$ and $\nabla_2 \mathbf{p}\left(i,j\right)$ can be represented as
\begin{equation}
\begin{split}
      \begin{pmatrix}
      \nabla_1 \mathbf{p}\left(i,j\right)\\\nabla_2 \mathbf{p}\left(i,j\right)
      \end{pmatrix} 
      &=\Lambda \mathbf{R} \begin{pmatrix}\nabla_x \mathbf{p}\left(i,j\right)\\\nabla_z \mathbf{p}\left(i,j\right)\end{pmatrix}\\
       \text{Here~} \Lambda &= 
      \begin{pmatrix}
      \alpha_1 & 0 \\
      0 & \alpha_2
	  \end{pmatrix}, \mathbf{R} = 
      \begin{pmatrix}
      \cos \theta & -\sin \theta \\
      \sin \theta & \cos \theta
	  \end{pmatrix},
\label{eq4:DTV}
\end{split}
\end{equation}
where $\Lambda$ and $\mathbf{R}$ represent scaling matrix and rotation matrix, respectively. $\alpha_1$ and $\alpha_2$ represent the weight on the gradient of the dominant direction and its perpendicular direction, respectively, and $\theta$ is the dip of the local structure. An illustration of such \new{a} directional TV is shown in figure~\ref{fig:FWI_fig1-01}a with the red solid arrows.

Please note that if we assume $\alpha_1 = \alpha_2 = 1$ and $\theta = 0^o$, then $\Lambda$ turns into \new{an}\old{a} identity matrix, which means the same weights are put on both directions, and $\mathbf{R}$ also becomes \new{an}\old{a} identity matrix, indicating that the target directions are horizontal and vertical. Therefore, we can see that the conventional TV is actually a special case of \new{the} directional TV, and in turn, \new{the} directional TV is a more general version of \new{the conventional} TV and more suitable to a model with complex geologic structures. In this paper, we solve both FWI/JMI with \new{the} conventional TV and FWI/JMI with \new{the} directional TV effectively using the split-Bregman iterative algorithm \citep{goldstein2009split}. We only show the framework of solving FWI with \new{the} directional TV in Algorithm 1, because, as mentioned before, we treat \new{the} conventional TV as a special case of directional \new{the} TV, and JMI with \new{the conventional} TV/directional TV will follow a similar algorithm.

\begin{algorithm}
\caption{FWI with directional total variation}
\begin{algorithmic}[1]
  \scriptsize
  \STATE Initialize: $\mathbf{m}^0=\mathbf{m}_0$, and $\mathbf{a}_1^0=\mathbf{a}_2^0=\mathbf{b}_1^0=\mathbf{b}_2^0=0$\\
  \STATE While Iter $<$ MaxIter \\
  ~$\mathbf{m}^{k+1}=\min\limits_\mathbf{m} \mu || \mathbf{d} - f\left(\mathbf{m}\right) ||_2^2 + \lambda|| \mathbf{a}_1^k-\nabla_1 \mathbf{m}-\mathbf{b}_1^k||_2^2 + \lambda|| \mathbf{a}_2^k-\nabla_2 \mathbf{m}-\mathbf{b}_2^k||_2^2$  \\
  ~~~~~(Hint: we solve this subproblem using gradient method, and the gradient is: \\
  ~~~~~~~~$\mu f^{*} \left( f\left(\mathbf{m}^{k}\right) - \mathbf{d} \right) - \lambda \nabla^{T}_1 \left( \mathbf{a}_1^k-\nabla_1 \mathbf{m}^{k}-\mathbf{b}_1^k \right) - \lambda \nabla^{T}_2 \left( \mathbf{a}_2^k-\nabla_2 \mathbf{m}^{k}-\mathbf{b}_2^k \right)$) \\
  ~$\mathbf{a}_1^{k+1}=shrink\left(\nabla_1 \mathbf{m}^{k+1}+\mathbf{b}_1^k, \frac{1}{\lambda}\right)$ \\
  \new{~~~~~($shrink\left(x, \gamma\right) = \frac{x}{|x|} * max\left(|x| - \gamma, 0\right)$, a soft-thresholding operator \citep{donoho1995noising})} \\

  ~$\mathbf{a}_2^{k+1}=shrink\left(\nabla_2 \mathbf{m}^{k+1}+\mathbf{b}_2^k, \frac{1}{\lambda}\right)$ \\
  ~$\mathbf{b}_1^{k+1}=\mathbf{b}_1^{k} + \left(\nabla_1 \mathbf{m}^{k+1}-\mathbf{a}_1^{k+1}\right)$  \\
  ~$\mathbf{b}_2^{k+1}=\mathbf{b}_2^{k} + \left(\nabla_2 \mathbf{m}^{k+1}-\mathbf{a}_2^{k+1}\right)$  \\
  end
\end{algorithmic}
\end{algorithm}

\section{FWI Example}
In order to demonstrate the effectiveness of FWI with directional TV, we consider the velocity model shown in \new{Figure}\old{figure}~\ref{fig:FWI_fig1-01}a, which is scaled from the top half of the Marmousi model. \new{To avoid cycle-skipping, a}\old{A} Ricker wavelet with a dominant frequency of \new{$14$ Hz}\old{$14 Hz$} is used as the source wavelet. Using a \new{constant-density}\old{constant density} acoustic \new{finite-difference modeling}\old{finite difference modelling}, we generated 23 shots with 334 receivers for each shot. The shot spacing is \new{$180$ m}\old{$180 m$} and \new{the} receiver spacing is \new{$12$ m}\old{$12 m$}. \new{The horizontal and vertical grid size are $12$ m}. In addition, some random noise with $SNR = 10$ is added to the \new{modeled}\old{modelled} data. The middle shot gather is shown in \new{Figure}\old{figure}~\ref{fig:shots_orig}. The initial velocity \new{model} is shown in \new{Figure}\old{figure}~\ref{fig:FWI_fig1-01}b, which is a smoothed version of \new{the model in Figure}\old{figure}~\ref{fig:FWI_fig1-01}a.

First, with the initial model, we apply 6 iterations of Full Wavefield Migration  \citep{Berkhout14b,davydenko2016full} at a maximum frequency of \new{$25$ Hz}\old{$25 Hz$} to the dataset and then denoise the inverted image via a simple soft-thresholding in the curvelet domain (\new{Figure}\old{figure}~\ref{fig:FWI_fig2}a, \cite{donoho1995noising}). Note that full wavefield  migration can be considered as a JMI process in which the velocity is assumed known and fixed. It will honour all multiples and transmission effects properly. Now, with this inverted reflectivity, we can estimate the dip field using plane-wave destruction algorithm proposed by \cite{fomel2002applications}, shown in \new{Figure}\old{figure}~\ref{fig:FWI_fig2}b. This estimated dip field is used to build the directional TV operator for each gridpoint.

Next, we compare three methods: regular FWI without any regularization, FWI with conventional TV, and FWI with directional TV. We use the same $\mu$ and $\lambda$ for TV and directional TV. We choose a relaxation strategy to set $\mu$, which is increasing exponentially. $\lambda$ is chosen as $0.005$, which depends on the scale of data. For directional TV, $\alpha_1 : \alpha_2 = 3 : 1$ and $\alpha_1 + \alpha_2 = 2$. For TV, $\Lambda$ is an identity matrix. After 100 iterations, the inverted results are shown in \new{Figure}\old{figure}~\ref{fig:FWI_fig3}. Note that the regular FWI without any regularization is trapped into local minima very quickly, despite the accurate starting model (\new{Figure}\old{figure}~\ref{fig:FWI_fig3}a). With the help of TV regularization, FWI with TV achieves a better result by smoothing the model via enhancing the sparsity of the spatial gradient of the velocity difference, which allows us to steer away from local minima. However, we can observe that the structures still remain vague in \new{Figure}\old{figure}~\ref{fig:FWI_fig3}b, especially in the deeper area, since traditional TV only uses \new{horizontal- and vertical-}\old{horizontal/vertical } and ignores the local structure. Compared to \new{the} regular TV, much weaker artifacts can be observed in the result of FWI with \new{the} directional TV, shown in \new{Figure}\old{figure}~\ref{fig:FWI_fig3}c, because we consider the structural directions of the spatial gradient and their weights according to the local dip. The convergence diagrams of the misfit function with iteration number corresponding to the three methods are shown in \new{Figure}\old{figure}~\ref{fig:FWI_fig3}d, in which it is visible that FWI with TV works well to mitigate the ill-posedness and non-uniqueness of FWI, and FWI with directional TV behaves clearly better than FWI with \new{the conventional} TV. Figure~\ref{fig:vel_profile-01} shows a comparison between \new{the} different velocities at three different locations. The locations are annotated in \new{Figure}\old{figure}~\ref{fig:FWI_fig3}a-c. We can see the obvious improvement using directional TV.

\new{To further illustrate the contribution of regularization in the inversion, we show the gradients from the residual at the first iteration based on the different methods in Figure~\ref{fig:FWI_gradient}. Compared to Figure~\ref{fig:FWI_gradient}a, Figure~\ref{fig:FWI_gradient}b has sharper structures, especially in the deeper part, by preserving the edges via the TV constraint. The gradient in Figure~\ref{fig:FWI_gradient}c shows even more blocky structures that correspond to the geologic information. Note that, in Figure~\ref{fig:FWI_gradient}c, there are imprints introduced by the imperfect raw reflectivity model and dip field (Figure~\ref{fig:FWI_fig2}). However, these imprints have been compensated and suppressed during inversion, and the proposed method ends up with a decent result shown in Figure~\ref{fig:FWI_fig3}c, which shows the proposed method is insensitive to the locally-incorrect dip field. Figure~\ref{fig:FWI_fig4} and~\ref{fig:FWI_CIGs} demonstrate the corresponding depth migration images and common image gathers calculated using full wavefield migration. We can see that the reflectivity based on the velocity from FWI with directional TV has the best focusing resolution and less imprints, and their corresponding common image gathers are flatter than the alternative methods. Please note some obvious improvements pointed out by the red arrows. In the end, we show in Figure~\ref{fig:FWI_shots-01} the modeled data generated from each of the final inverted velocities and the corresponding differences with the observed data.}
\old{Figure~\ref{fig:FWI_shots-01} shows the modelled data generated from the final inverted velocities and the corresponding differences between them and the observed data (figure~\ref{fig:shots_orig}).} From this figure, we note that FWI with directional TV approach can restore the observed data much better than \old{other}\new{the} alternatives.

\section{JMI Example}
In this part, we use the same model as in the previous example to demonstrate the effectiveness of JMI with directional TV. \new{Because the forward modeling in JMI is computationally less expensive that in FWI, w}\old{W}e \new{are able to }use a Ricker wavelet with a \new{higher} dominant frequency of \new{$20$ Hz}\old{$20 Hz$}\old{ as the source wavelet} \new{to acquire higher-resolution reflectivities and velocity. The shot spacing is $200$ m and the receiver spacing is $20$ m.} \new{The horizontal and vertical grid size are $20$ m and $10$ m, respectively. }Surface multiples are excluded in the \new{modeling}\old{modelling}, but internal multiples and transmission effects are included. \new{The direct wave is removed, as it cannot be explained by JMI. }Initially, reflectivities are zero and the initial velocity is a very simple vertical gradient (shown in \new{Figure}\old{figure}~\ref{fig:JMI_fig1}). First, with the initial model, we apply 30 iterations of JMI with \new{$5$ Hz $-$ $25$ Hz}\old{$5 Hz - 25 Hz$} \new{frequency bandwidth of}\old{band-width of frequency} to the dataset and then preprocess the inverted image via a simple soft-thresholding in the curvelet domain. Then, with this preprocessed inverted reflectivity, we estimate the dip field to build the directional TV operator. Meanwhile, the inverted velocity can be used as initial velocity model for the next step.

\new{Next, w}\old{W}e compare\new{results from} the regular JMI without any regularization, JMI with conventional TV, and JMI with directional TV. The \new{frequency bandwidth}\old{band-width of frequency} during \new{the second step of} JMI is \new{$5$ Hz $-$ $40$ Hz}\old{$5 Hz - 40 Hz$}. We use the same $\mu$ and $\lambda$ for both \new{the conventional} TV and directional TV. $\mu$ is also increasing with iteration and $\lambda = 1.2$. For directional TV, $\alpha_1 : \alpha_2 = 3 : 1$ and $\alpha_1 + \alpha_2 = 2$. For \new{the conventional} TV, $\Lambda$ is an identity matrix. After 50 iterations for each method, the inverted results are shown in \new{Figure}\old{figure}~\ref{fig:JMI_fig3} and \new{Figure}\old{figure}~\ref{fig:JMI_fig2}. Because of the inversion process included in JMI, all the images in \new{Figure}\old{figure}~\ref{fig:JMI_fig2} are quite accurate compared to the true reflectivity structures. Furthermore, all the estimated velocity models in \new{Figure}\old{figure}~\ref{fig:JMI_fig3} are also surprisingly stable and show some details.

In \new{Figure}\old{figure}~\ref{fig:JMI_fig3}a, the regular JMI without any regularization is slightly trapped in a local minimum, \old{i.e.}\new{e.g.,} in the lower right area pointed by the red arrow. With the help of TV regularization, JMI with \new{conventional} TV in \new{Figure}\old{figure}~\ref{fig:JMI_fig3}b achieves a better result by smoothing the model via enhancing the sparsity of the spatial gradient of the velocity difference, which allows us to steer away from the local minimum. Instead of using \new{the conventional} TV, \new{a }much better inverted velocity with clearer edges of structures \new{is obtained}\old{are shown} in \new{Figure}\old{figure}~\ref{fig:JMI_fig3}c using JMI with directional TV. This is because we consider the structural directions of the spatial gradient and their weights according to the local dip from the associated image. Please note some obvious improvements pointed out by the white arrows. In addition, compared to L1 directional \old{total variation}\new{TV}, L2 directional Laplacian smoothing results in a \new{smoother}\old{more smooth} velocity model (\new{Figure}\old{figure}~\ref{fig:JMI_fig3}d)\new{;}\old{,} however, it intensifies the local minima issue and tends to produce models with blurred discontinuities. That is because \new{the} directional Laplacian smoothing may over-smooth the velocity and cannot preserve edges very well\new{;}\old{, and} it is also more sensitive to the accuracy of the estimated dip field, compared to L1 directional \old{total variation}\new{TV}.  As a result of the improvement of the inverted velocity, the inverted reflectivity also becomes more accurate (\new{Figure}\old{figure}~\ref{fig:JMI_fig2}): The inverted reflectivities highlighted with white arrows in \new{Figure}\old{figure}~\ref{fig:JMI_fig2}c have better focussing and less distortions than the other alternatives\old{ do}.

Note that the velocity field estimated from JMI has less details compared to that from FWI, as it only needs to describe propagation, not reflection. \new{Similar as in the FWI example, we show in Figure~\ref{fig:JMI_shots-01} the modeled data generated from each of the final inverted velocities and the corresponding differences with the observed data. From this figure, we can see that regularizations on velocity do not make much difference in the data residual, because the velocity in JMI only explains propagation effects, and the reflectivities explain the scattering effects, which makes JMI less sensitive to the details in the velocity model compared to FWI.}

\section{Discussion}
FWI/JMI with directional TV has been demonstrated to be a more effective method than the alternatives. We design the directional TV based on the dip field calculated from an initial image. By considering the local structural directions of the spatial gradient and their weights according to the local dip, the proposed method achieves a better result compared to FWI/JMI without regularization or with conventional TV. In the case of complex subsurface structures, the local dip map \new{cannot}\old{is not able to} be estimated properly. However, directional TV regularization is not sensitive to the accuracy of the estimated dip, because even using an arbitrary dominant direction would not be worse than using \new{horizontal- and vertical-}\old{horizontal/vertical }gradients like \new{using conventional} TV in a complex area.

In terms of the parameter selection, we choose a relaxation strategy for $\mu$, which is increasing exponentially. In this way, we relax the strength of \new{the} L1 constraint gradually to make the inversion converge. $\lambda$ is a constant which depends on the scale of \new{the} data. We can set a proper $\lambda$ to make sure around $60\% - 70\%$ of \new{the} energy is passed through the \old{shrink}\new{shrinkage} step in Algorithm 1, in order to improve the stability of the algorithm. Regarding the weights on the dominant direction and its perpendicular direction of gradients, it depends on the accuracy of \new{the} estimated dip field and the bias of the subsurface structures. Usually, $\alpha_1 : \alpha_2 = 2 : 1$ is a safe choice. \new{In this paper, we use  $\alpha_1 : \alpha_2 = 3 : 1$ for both examples, which puts more weight on the dominant spatial direction of the velocity gradient, because the structures of the Marmousi model are quite tilted and biased.}

\new{Regarding the calculation efficiency of JMI, JMI is more cost-effective than FWI. First, it doesn't require a good initial model to start with due to its linearization; Second, it is implemented in the frequency domain and no finite-difference-based method is used, therefore the horizontal and vertical grid size do not have to satisfy a frequency dispersion condition, but are defined by the spatial Nyquist criterion. For instance, in the JMI example, the frequency range is upto $40$ Hz and the chosen horizontal and vertical grid size is $20$ m and $10$ m, respectively.}

\section{Conclusions}
\new{
Full waveform inversion (FWI) and Joint migration inversion (JMI) with the directional total variation (TV) has been demonstrated to be a more effective method than the alternatives (i.e., FWI/JMI without regularization, with the conventional TV, or directional Laplacian smoothing). We design the directional TV based on the dip field calculated from an initial image. By considering the local structural directions of the spatial gradient and their weights according to the local dip, the proposed method achieves a better result compared to FWI/JMI without regularization or with conventional TV. Finally, it can be concluded that the impact of directional TV is larger for FWI than for JMI, because in JMI the velocity model only explains the propagation effects and, thereby, makes it less sensitive to the details in the velocity model. }
\old{FWI/JMI with directional TV has been demonstrated to be a more effective method than the alternatives. We design the directional TV based on the dip field calculated from an initial image. By considering the local structural directions of the spatial gradient and their weights according to the local dip, the proposed method achieves a better result compared to FWI/JMI without regularization or with conventional TV. Finally, it can be concluded that the impact of directional TV is larger for FWI than for JMI, confirming the robustness of the JMI methodology. }

\section{ACKNOWLEDGEMENTS}
S. Qu and E. Verschuur thank the sponsors of the Delphi consortium for their support. Y. Chen is supported by the “Thousand Youth Talents Plan” of China, and the Starting Funds from Zhejiang University.

%\new{Furthermore, they thank the anonymous reviewers, the associate and assistant editors for their constructive comments.}
%\new{The authors thank the anonymous reviewers, the associate and assistant editors for their constructive comments.}

\renewcommand{\figdir}{Fig} % figure directory

\plot{jmi_scheme}{width=1\textwidth}{JMI flow chart.}
\plot{FWI_fig1-01}{width=1\textwidth}{FWI example: (a) Real velocity model, at specific gridpoint $\left(i,j\right)$. The black dash arrows illustrate $\nabla_x \mathbf{p}\left(i,j\right)$ and $\nabla_z \mathbf{p}\left(i,j\right)$, the red solid arrows illustrate $\nabla_1 \mathbf{p}\left(i,j\right)$ and $\nabla_2 \mathbf{p}\left(i,j\right)$, based on the structural dip at $\left(i,j\right)$. (b) Initial velocity model.}

\plot{shots_orig}{width=0.3\textwidth}{FWI example: Recorded middle shot gather at \new{$X = 2000$ m}\old{$X = 2000 m$} }

\plot{FWI_fig2}{width=0.9\textwidth}{FWI example: (a) The inverted reflectivity model after denoising using thresholding in the curvelet domain. (b) The estimated dip field (in degrees).}

\plot{FWI_fig3}{width=0.9\textwidth}{FWI example: The inverted velocity using (a) regular FWI without any regularization, (b) FWI with conventional TV, and (c) FWI with directional TV. (d) The convergence diagrams of the data misfit as a function of iteration. The blue line denotes the inverted velocity using regular FWI without any regularization. The red line denotes the inverted velocity using FWI with conventional TV. The yellow line denotes the inverted velocity using FWI with directional TV.}

\plot{vel_profile-01}{width=0.9\textwidth}{FWI example: Comparison of different velocities at three locations. Velocity comparison at (a) \new{$X = 1000$ m}\old{$X = 1000 m$}, (b) \new{$X = 2000$ m}\old{$X = 2000 m$}, (c) \new{$X = 3000$ m}\old{$X = 3000 m$}. The purple line denotes the true velocity. The green line denotes the initial velocity. The blue line denotes the inverted velocity using regular FWI without any regularization. The red line denotes the inverted velocity using FWI with conventional TV. The yellow line denotes the inverted velocity using FWI with directional TV. The three locations are highlighted by the black dash lines in \new{Figure}\old{figure}~\ref{fig:FWI_fig3}a-c}.

\new{\plot{FWI_gradient}{width=0.9\textwidth}{FWI example: The velocity gradient from the residual at the first iteration using (a) regular FWI without any regularization, (b) FWI with conventional TV, and (c) FWI with directional TV.}}

\new{\plot{FWI_fig4}{width=0.9\textwidth}{FWI example: The corresponding reflectivity based on the inverted velocity using (a) regular FWI without any regularization, (b) FWI with conventional TV, and (c) FWI with directional TV.}}

\new{\plot{FWI_CIGs}{width=0.9\textwidth}{FWI example: The corresponding angle gathers generated at $X = 1000$ m, $X = 2000$ m, and $X = 3000$, based on the inverted velocity using (a, b, c) regular FWI without any regularization, (d, e, f) regular FWI with conventional TV, and (g, h, i) regular FWI with directional TV.}}

\plot{FWI_shots-01}{width=0.9\textwidth}{FWI example: The modeled data \new{ generated at $X = 2000$ m} \old{generated from the inverted velocity} and the corresponding difference with the observed data based on the inverted velocity using (a, b) regular FWI without any regularization\old{figure~\ref{fig:FWI_fig3}a)}, (c, d) regular FWI with conventional TV\old{ (figure~\ref{fig:FWI_fig3}b)}, and (e, f) regular FWI with directional TV\old{ (figure~\ref{fig:FWI_fig3}c).}}

\plot{JMI_fig1}{width=0.9\textwidth}{JMI example: (a) Initial reflectivity model. (b) Initial velocity model.}

\plot{JMI_fig3}{width=0.9\textwidth}{JMI example: The inverted velocity using (a) regular JMI without any regularization, (b) JMI with conventional TV, (c) JMI with directional TV, and (d) JMI with L2 directional laplacian smoothing.}

\plot{JMI_fig2}{width=0.9\textwidth}{JMI \new{example}: The inverted reflectivity using (a) regular JMI without any regularization, (b) JMI with conventional TV, (c) JMI with directional TV, and (d) JMI with L2 directional laplacian smoothing.}

\new{\plot{JMI_shots-01}{width=0.9\textwidth}{JMI example: the modeled data generated at $X = 2000$ m and the corresponding difference with the observed data based on the inverted velocity and reflectivity using (a, b) regular JMI without any regularization, (c, d) regular JMI with conventional TV , and (e, f) regular JMI with directional TV.}}

%\append{The source of the bibliography}
%\verbatiminput{2016_seg.bib}

\bibliographystyle{seg}  % style file is seg.bst
\bibliography{2017_seg}

%\end{document}

### 2020-10-10 dtv/marm/fdmod.c
2020年10月 9日 星期五 22时22分12秒 CDT

@@ -1,0 +1,1250 @@
+/* Simple acoustic wave propagation code
+#
+# Originally written by Yangkang Chen
+# Modified by Shan Qu
+# 
+# CODE for DTV regularized FWI
+# Reference:
+# Qu, S., E. Verschuur, and Y. Chen, 2019, FWI/JMI with an automatic directional total variation constraint, Geophysics, 84, R175-R183.
+#
+*/
+
+#include <stdio.h>
+#include <math.h>
+#include <stdio.h>
+#include <stdlib.h>
+#include <rsf.h>
+
+// #include <iostream>
+// #include <complex>
+// #include <sstream>
+// #include <assert.h>
+
+#define M_PI 3.1415926535897932385E0
+// typedef struct { float Re; float Im; }  complex;         /* for complex number */
+
+float **alloc2D(int size_x, int size_y);
+void delete2D(float **arr, int size_x, int size_y);
+void sg_position(int *sxz, int sxbeg, int jsx, int ns);
+void step_forward(float **p0, float **p1, float **p2, float **vv, float dt, float dz, float dx, int nz, int nx, int nb, int nd, bool iffree);
+void oneway_abc(float **uo, float **um, float **vv, int nx, int nz, int nb, int nd, float dx, float dz, float dt, bool iffree);
+void save_2d_float(float **p, int n1, int n2, char *filename);
+void save_1d_float(float *p, int n1, char *filename);
+void save_1d_int(int *p, int n1, char *filename);
+void rw_boundary(float *bd, float **p, int nz, int nx, int nb, int nd, bool write);
+void step_backward(float **illum, float **lap, float **p0, float **p1, float **p2, float **vv, float dt, float dz, float dx, int nz, int nx, int nb, int nd);
+void pre_gradient(float **grad, float **vv, float **illum, int nz, int nx, int nb, int nd, float stab, bool precon);
[…]

### 2020-10-10 dtv/paper.tex
2020年10月 9日 星期五 22时22分12秒 CDT
2020年10月10日 星期六 09时57分00秒 CDT

@@
-%\documentclass[manuscript]{geophysics}
-%	\usepackage{amsmath}
-%	\usepackage{amssymb}
-%	\usepackage{graphicx}
-%	\usepackage{indentfirst}
-%	\usepackage{lineno}
-%	\usepackage{algorithm,algorithmic}
-%	\usepackage{float}
-%\begin{document}
+\published{Geophysics, 84, no. 2, (2019)}
 
@@
 \maketitle
-
-%\begin{center}
-%\huge{\textbf{Full waveform inversion and joint migration inversion with an automatic directional total variation constraint}} 
-%\end{center}
 
@@
 Thus, TV is not suitable where the local geologic structure has a dominant structural direction.
-Unlike general digital images, the spatial changes of the seismic model always have some specific geological structures, like tilted layers, faults, or edges of a salt body \citep{yangkang2017lsrtm,wujuan2018cg1,baimin2018cg,yangkang2018gji3}.
+Unlike general digital images, the spatial changes of the seismic model always have some specific geological structures, like tilted layers, faults, or edges of a salt body \citep{yangkang2017lsrtm,wujuan2018cg1,baimin2018cg,yangkang2020gji3}.
 \cite{bayram2012directional} proposed a directional TV method and applied it to digital image denoising.
@@
 
-\plot{FWI_fig3}{width=0.9\textwidth}{FWI example: The inverted velocity using (a) regular FWI without any regularization, (b) FWI with conventional TV, and (c) FWI with directional TV.
+%original files
+%\plot{FWI_fig3}{width=0.9\textwidth}{FWI example: The inverted velocity using (a) regular FWI without any regularization, (b) FWI with conventional TV, and (c) FWI with directional TV.
+(d) The convergence diagrams of the data misfit as a function of iteration.
+The blue line denotes the inverted velocity using regular FWI without any regularization.
+The red line denotes the inverted velocity using FWI with conventional TV.
+The pink line denotes the inverted velocity using FWI with directional TV.}
+
+\inputdir{marm}
+\multiplot{4}{vinv,vinv_tv,vinv_dtv,objs}{width=0.45\textwidth}{FWI example: The inverted velocity using (a) regular FWI without any regularization, (b) FWI with conventional TV, and (c) FWI with directional TV.
 (d) The convergence diagrams of the data misfit as a function of iteration.
@@
 
+\inputdir{./}
 \plot{vel_profile-01}{width=0.9\textwidth}{FWI example: Comparison of different velocities at three locations.
@@
 \bibliographystyle{seg}  % style file is seg.bst
-\bibliography{2017_seg}
-
-%\end{document}
+\bibliography{dtv}

### 2020-10-10 sgk5d/paper.tex
2020年10月10日 星期六 14时54分48秒 CDT

\title{Fast dictionary learning for high-dimensional seismic reconstruction}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
%\author{Hang Wang, Quan Zhang, Wei Chen, Xingye Liu, Shaohuan Zu, and Yangkang Chen
\author{Hang Wang, Wei Chen, Quan Zhang, Xingye Liu, Shaohuan Zu, and Yangkang Chen
\thanks{H. Wang, Q. Zhang, and Y. Chen are with the Key Laboratory of Geoscience Big Data and Deep Resource of Zhejiang Province, School of Earth Sciences, Zhejiang University (chenyk2016@gmail.com).}
\thanks{W. Chen is with the Key Laboratory of Exploration Technology for Oil and Gas Resources, Ministry of Education, Yangtze University, and also with the Hubei Cooperative Innovation Center of Unconventional Oil and Gas, Yangtze University.}
\thanks{X. Liu is with College of Geology and Environment, Shaanxi Provincial Key Laboratory of Geological Support for Coal Green Exploitation, Xi'an University of Science and Technology.}
\thanks{S. Zu is with College of Geophysics, Chengdu University of Technology.}
\thanks{The research is supported by the starting fund from Zhejiang University and the National Natural Science Foundation of China (Grant No. 41804140), the Open Fund of Key Laboratory of Exploration Technologies for Oil and Gas Resources (Yangtze University), Ministry of Education (Grant No. PI2018-02). (Corresponding author: Yangkang Chen.)}}
\maketitle

%, college of geology and enviroment
%58 Yanta road
%Beilin district

\begin{abstract}
A sparse dictionary is more adaptive than a sparse fixed-basis transform since it can learn the features directly from the input data in a data-driven way.  However, learning a sparse dictionary is time consuming because a large number of iterations are required in order to obtain the dictionary atoms that best represent the features of input data. The computational cost becomes unaffordable when it comes to high-dimensional problems, e.g., 3D or even 5D applications. We propose an efficient high-dimensional dictionary learning method by avoiding the singular value decomposition (SVD) calculation in each dictionary update step that is required by the classic K-singular value decomposition (KSVD) algorithm. Besides, due to the special structure of the sparse coefficient matrix, it requires a much less expensive sparse coding process. The overall computational advantage of the new dictionary learning method is very decent while the results are still comparable or event better than those from the traditional KSVD method. We apply the proposed method to both 3D and 5D seismic data reconstructions and demonstrate the successful and efficient performance.
\end{abstract}

\begin{keywords}
Seismic data reconstruction, signal processing, dictionary learning, high-dimensional problem
\end{keywords}

\section{Introduction}
The seismic acquisition in the field will inevitably come across many problems that affect the completeness of collected data \cite{Chao2018Adap}. The huge expense of acquisition is one of the most important reasons for this degradation. In order to minimize the cost, the acquisition system is always not dense enough, which will generate a too sparse data set. Additionally, the topography in working area is usually complex, and the deployment of receivers will be limited in certain places. As a result, the reflection information from these areas cannot be sufficiently obtained. In addition to the problems mentioned above, there are many anomalous traces caused by the defective instruments and erratic noise in the raw data. Simply removing them will also lead to the considerable loss of seismic traces. This information loss may cause some troubles in the following processes, such as inversion and migration. Reconstructing these missing traces is very meaningful to the accurate imaging of subsurface structures. The original data from field acquisition are usually five-dimension volumes \cite{yangkang2016irr5d,jianjun2017five}, including inline, xline, azimuth, offset and time dimensions. The reconstruction of the missing traces can provide much more information than the conventional 2D or 3D data interpolation.

\old{The random noise is another important reason for decreasing data quality, and will also cause problems in the subsequent processes ?. Thus, the random noise should also be eliminated properly to generate a good imaging result. Fortunately, the interpolation and denoising of seismic data have some similar features and can be dealt with by the similar mathematical methods, such as prediction-based method ?, transform-based method ? and rank-reduction-based method ?, and so on.}Prediction-based method is often used as an effective tool for the denoising and interpolation of seismic data. It designs a prediction filter in the frequency-space domain. Then, in each frequency slice, the filter is applied to suppress random noise or interpolate the missing traces \cite{Spitz1991fx,Guochang2019Multi}. \old{? first proposed the idea that the linear events are predictable. He used the Wiener method to derive a filter and applied it to attenuate the random noise in each frequency-space slice. ? continued applying this idea to interpolate the under-sampled seismic data. This method shows good robustness even if the seismic data contains non-linear events and unstable amplitude. ? utilized a narrow-band model to interpolate the sparse data collected in the field, aiming at saving the cost of acquisition. Different examples all demonstrated the validity of this method. ? treated the seismic data as two parts, i.e., non-aliased part and aliased part. The low-frequency components corresponding to the non-aliased part are reconstructed first by the minimum-weighted norm method. Then, this part was used to extract the prediction filter. The method in this step is called multistep autoregression. The extracted filter is then applied to the whole data to interpolate the missing traces in all frequency components. This algorithm shows outstanding performance in reconstructing irregular data. ? designed a non-stationary method to interpolate the near offset data. Compared to the traditional method that simply uses pseudo-primaries to replace the missing data, this method can effectively reduce the negative artifacts caused by the multiples. Both 3D synthetic data and 2D examples showed its superiority over the conventional method.}Transform-based methods are commonly used approaches for seismic interpolation and denoising \cite{Trad2002rt,Abma2006pocs,Side2010damped}. \old{? proposed a two-step method based on the Fourier transform. Firstly, it reconstructs the data in the low and non-aliased frequencies. This reconstructed part is then used as a prior information to recover the high and aliased frequency components. This process is implemented in an inversion framework with a penalty. To meet the linear assumption, this algorithm needs to be implemented in local windows. ? added the sparseness constraint to the frequency slices of the five-dimensional data. This high-dimensional reconstruction algorithm can preserve the variation information of reflected amplitude and minimize the artifacts caused by the method itself.  ? regarded the interpolation of seismic data as an inversion problem. They used dreamlet transform to interpolate the missing traces, based on the projection onto convex sets (POCS) framework. The data examples showed that the dreamlet-based method has better ability to recover the missing signals than the curvelet-based one. ? used seislet transform as the sparse constraint, and analyzed the difference between the POCS and iterative shrinkage thresholding (IST) methods in different cases. Some real marine data and synthetic examples demonstrated its good performance in the sparse representation of the under-sampled data.} Rank-reduction-based methods are mainly based on the assumption that the complete and incomplete data correspond to the low-rank and high-rank features, respectively. A good separation of the rank values can provide proper reconstructed results of under-sampled seismic data \cite{Jianjun2013rank,Yangkang2016drr,yangkang2019nc}. \old{? formed the high-order tensor using the noisy and under-sampled high-dimensional data, and obtained the singular value decomposition of this tensor to reduce the rank of it. This method can effectively recover the synthetic and field data with random noise and missing traces even if the event shapes of them are complex. ? reconstructed the noisy and incomplete five-dimensional data by the damping operator which can better distinguish the noise and recover the missing traces more accurately. ? continued to propose an optimally damped operator which simultaneously keeps the advantages of both optimal weighted and damping operators. The simultaneous interpolation and denoising result of it is more accurate than the conventional method that just has one operator.}

In addition to the popular methods mentioned above, dictionary-learning-based (DL) methods are recently developed rapidly for the denoising and reconstruction of seismic data \cite{lingchen2015multiscale,Siahsar2017multitask,yangkang2020sgk}. This novel method can commonly be divided into two steps: the sparse coding and the dictionary update. The two parts are implemented alternately to form the final best sparse representation and updated dictionary. Like the transform-based methods, the DL method also has the advantage that the signal can be represented by few sparse coefficients, which can decrease the computing cost and separate the wanted and other components in the sparse domain. The difference between DL and traditional transform is that the DL method has a variable dictionary while the traditional transform keeps the dictionary (such as wavelet) fixed. \cite{Beckouche2014dl} divided the seismic data into many small patches and used them to train the dictionary. After enough iterations, the dictionary can effectively represent the reflection signals and suppress the noise. \cite{yangkang2016double} proposed a double-sparsity dictionary to attenuate the random noise. This method takes the advantages of both analytic and learned atoms to enhance the efficiency and flexibility. The synthetic and field data examples showed a good performance in separating the noise and signals. \cite{zhouy2016patchwise} used the DL method in a sparse inversion frame to suppress the blending noise. The alternating direction method of multipliers is used as the updating algorithm to form the final dictionary. The separated simultaneous-source data is more precise than the result from the traditional mathematical transform. \cite{turquais2017coherence} proposed a coherence-constrained dictionary learning algorithm to alleviate the problem that the prior information of noise is not stable in different locations. This modification makes the denoised result more satisfactory than that resulted from the conventional KSVD method. \old{? utilized Laplacian matrix to test the similarity between different data patches, and designed two updating algorithms to realize the DL method.} \cite{Turquais2017morphology} proposed to use the morphology features to distinguish the coherent noise and signals. They established a redundant dictionary that contains atoms of both coherent noise and signals, then used statistical method to divide them into two sub-dictionaries. This method shows superb performance in separating the coherent noise from reflected signals on real marine data set. \cite{shaohuan2019dippatch} designed a dip-based DL approach to suppress the random noise. They used the curvelet method to roughly get noise-free dip field, and, based on this information, selected the training patches. This algorithm has obvious superiority over the conventional random-selection strategy.

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.3\columnwidth]{synth/Fig/synth-clean}
\label{fig:synth-clean}}
   \subfigure[]{\includegraphics[width=0.3\columnwidth]{synth/Fig/synth-noisy}
   \label{fig:synth-noisy}}
   \subfigure[]{\includegraphics[width=0.3\columnwidth]{synth/Fig/synth-obs}
   \label{fig:synth-obs}}
\caption{Synthetic example with planar events. (a) Clean data. (b) Noisy data (SNR=-0.05 dB). (c) Observed data with 50\% randomly missing traces (SNR=-0.03 dB).}
\label{fig:synth-clean,synth-noisy,synth-obs}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.3\columnwidth]{synth/Fig/synth-ksvd}
\label{fig:synth-ksvd}}
   \subfigure[]{\includegraphics[width=0.3\columnwidth]{synth/Fig/synth-ddtf}
   \label{fig:synth-ddtf}}
   \subfigure[]{\includegraphics[width=0.3\columnwidth]{synth/Fig/synth-sgk}
   \label{fig:synth-sgk}}
\caption{Reconstructed data using (a) KSVD (SNR=8.89 dB), (b) DDTF (SNR=5.42 dB), and (c) SGK (SNR=9.74 dB).}
\label{fig:synth-ksvd,synth-ddtf,synth-sgk}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\columnwidth]{Fig/atom_dct}
\label{fig:atom_dct}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{Fig/atom_ksvd}
   \label{fig:atom_ksvd}}\\
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{Fig/atom_ddtf}
   \label{fig:atom_ddtf}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{Fig/atom_sgk}
   \label{fig:atom_sgk}}
\caption{Comparison of different dictionary atoms. (a) Dictionary atoms of the discrete cosine transform. (b) Dictionary atoms of the KSVD method. (c) Dictionary atoms of the DDTF method.  (d) Dictionary atoms of the SGK method. }
\label{fig:atom_dct,atom_ksvd,atom_ddtf,atom_sgk}
\end{figure}

To date, the KSVD based method is one of the most widely used dictionary learning methods. However, the KSVD method requires computationally expensive dictionary update and sparse coding due to many singular value decomposition (SVD) and orthogonal matching pursuit (OMP) operations. The high computational cost of KSVD method limits its wide application in high-dimensional problems, e.g., 3D/5D seismic reconstruction. In this paper, we develop an efficient dictionary learning method based on a different learning model, which is referred to as the sequential generalized K-means (SGK) model \cite{sgk2013,yangkang2020sgk}. The SGK model is inspired from the work in \cite{sgk2013}, and is an extension of the previous work in \cite{yangkang2020sgk} for high-dimensional seismic reconstruction. The SGK model is applied to the patches created from the high-dimensional seismic data by the patching method \cite{wanghang2020}. Then, the computed denoised/reconstructed patches are concatenated to output the high-dimensional seismic data by the unpatching method \cite{wanghang2020}. We introduce in detail the accelerating principles in both dictionary update and sparse coding processes of the SGK method, and introduce the detailed algorithms. The computational speedup of the proposed SGK method is very appealing, i.e., at least 6 times speedup for small problems and more than 10 (or higher) times for larger problems. We use exclusive seismic data examples for both 3D and 5D reconstructions to demonstrate the comparable performance of the proposed method with the state-of-the-art KSVD method and the much accelerated computational performance.

\section{Theory}
The traditional DL is usually realized by the KSVD method which includes two parts. The first step is to represent the signal with sparse coefficients by a given dictionary. The later one updates the dictionary based on the fixed sparse coefficients. These two steps are alternately carried out until the best representation of signals is obtained.

\subsection{Sparse coding}
We use $\mathbf{x}$ to represent the observed field data. After dividing it into different sample patches $\mathbf{x}_j$, the data used to train the dictionary can be expressed as $\mathbf{X}$ ($M\times N$) whose $j$th column is $\mathbf{x}_j$ ($M\times 1$). Assuming that the rearranged data can be sparsely represented by the matrix multiplication of the dictionary $\mathbf{D}^{n}$ ($M\times L$) and sparse coefficients $\mathbf{S}$ ($L\times N$). The superscript $n$ means that it is the generated dictionary after $n$th iteration. Each column of $\mathbf{D}^{n}$ stands for an atom that is variable in every iteration step. To make this representation relationship sensible, the three matrices should meet the following requirement:
\new{
\begin{equation}
\forall_{j}\mathbf{s}_j^{n}=\mathop{\text{argmin}}_{\mathbf{s}_j} \parallel \mathbf{X}-\mathbf{D}^{n}\mathbf{S} \parallel_{F}^{2},\,\,\text{s.t.}\,\, \forall_{j}\parallel \mathbf{s}_j \parallel_{0} \,\leq P.
\label{eq:eq1}
\end{equation}}
$\forall_{j}$ is a symbol meaning that it is suitable for all the $\mathbf{s}_j$. $\mathbf{s}_j$ ($L\times 1$) means the sparse coefficients of $j$th sample in $\mathbf{X}$, which also corresponds to the $j$th column of the sparse matrix $\mathbf{S}$. \new{Here, a sample in $\mathbf{X}$ means a column in $\mathbf{X}$. The matrix $\mathbf{X}$ is a collection of all available samples for learning.} $\parallel \cdot \parallel_{F}$ and $\parallel \cdot \parallel_{0}$ stand for the Frobenius norm and the $L_0$ norm, respectively. \old{$T$}\new{$P$} is a sparsity requirement that the number of non-zero elements in $\mathbf{s}_j$ should not exceed \old{$T$}\new{$P$}.

Solving above equation is a very difficult task because it is NP-hard. To directly find the precise solution is almost impossible without using tremendous computing resources. Therefore, OMP is proposed as an alternative approach to effectively find a suitable solution of sparse coefficients.

OMP algorithm can provide an optimal linear combination of the selected atoms to represent the signals. First, one can select an atom and find its corresponding sparse coefficient. Then, the residual signal is calculated and will be decomposed by the new atom and coefficient. This procedure keeps going until the requirement of \old{$T$}\new{$P$} non-zero coefficients is satisfied.

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.30\columnwidth]{synth/Fig/synth-ksvd-simi}
\label{fig:synth-ksvd-simi}}
   \subfigure[]{\includegraphics[width=0.30\columnwidth]{synth/Fig/synth-ddtf-simi}
   \label{fig:synth-ddtf-simi}}
   \subfigure[]{\includegraphics[width=0.30\columnwidth]{synth/Fig/synth-sgk-simi}
   \label{fig:synth-sgk-simi}}
\caption{Similarity comparison of reconstructed data using (a) KSVD, (b) DDTF, and (c) SGK.}
\label{fig:synth-ksvd-simi,synth-ddtf-simi,synth-sgk-simi}
\end{figure}

\begin{figure}[htb!]
\centering
	\subfigure[]{\includegraphics[width=0.31\columnwidth]{synth/Fig/synth-s-clean}
	\label{fig:synth-s-clean}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth/Fig/synth-s-noisy}
   \label{fig:synth-s-noisy}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth/Fig/synth-s-obs}
   \label{fig:synth-s-obs}}\\
\subfigure[]{\includegraphics[width=0.31\columnwidth]{synth/Fig/synth-s-ksvd}
\label{fig:synth-s-ksvd}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth/Fig/synth-s-ddtf}
   \label{fig:synth-s-ddtf}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth/Fig/synth-s-sgk}
   \label{fig:synth-s-sgk}}
\caption{\new{2D slice comparison of the synthetic example. (a) Clean data. (b) Noisy data. (c) Observed data. (d) Reconstructed data using KSVD. (e) Reconstructed data using DDTF. (f) Reconstructed data using SGK.}}
\label{fig:synth-s-clean,synth-s-noisy,synth-s-obs,synth-s-ksvd,synth-s-ddtf,synth-s-sgk}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=\columnwidth]{synth/Fig/synth-ss}}
\caption{Single-trace comparison. The black line corresponds to the ground-truth solution. The green line corresponds to the noisy data. The pink line corresponds to the proposed method, which is closest to the black line. The red line corresponds to the KSVD method. The blue line corresponds to the DDTF method.}
\label{fig:synth-ss}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.30\columnwidth]{synth/Fig/synth-mssa}
\label{fig:synth-mssa}}
   \subfigure[]{\includegraphics[width=0.30\columnwidth]{synth/Fig/synth-mssasgk}
   \label{fig:synth-mssasgk}}
\caption{Reconstructed data using (a) MSSA (SNR=9.51 dB), and (b) SGK with (a) as the initialization model (SNR=12.22 dB).}
\label{fig:synth-mssa,synth-mssasgk}
\end{figure}

\subsection{Dictionary update via KSVD}

When one get the matrix of sparse coefficients after the sparse coding process, the dictionary should be updated to better approximate the data features. This new process can be expressed as:
\begin{equation}
\mathbf{D}^{n+1}=\mathop{\text{argmin}}_{\mathbf{D}} \parallel \mathbf{X}-\mathbf{D}\mathbf{S}^{n} \parallel_{F}^{2}.
\end{equation}
Note that the sparse coefficients are fixed in this step. This equation can be solved in the following form:
\begin{equation}
\begin{aligned}
\parallel \mathbf{X}-\mathbf{D}\mathbf{S} \parallel_{F}^{2}&=\parallel \mathbf{X}-\sum_{j=1}^{L} \mathbf{d}_{j}\mathbf{s}_{T}^{j} \parallel_{F}^{2}\\
&=\parallel \mathbf{X}-\sum_{j\neq k}^{L} \mathbf{d}_{j}\mathbf{s}_{T}^{j}-\mathbf{d}_{k}\mathbf{s}_{T}^{k} \parallel_{F}^{2}\\
&=\parallel \mathbf{Q}_{k}-\mathbf{d}_{k}\mathbf{s}_{T}^{k} \parallel_{F}^{2}
\end{aligned},
\label{eq:ksvd}
\end{equation}
where $\mathbf{d}_{j}$ is the $j$th column of dictionary $\mathbf{D}$. $\mathbf{s}_{T}^{k}$ is the $k$th row of sparse matrix $\mathbf{S}$. \new{Here, the subscript $T$ simply indicates a row vector.} $\mathbf{Q}_{k}$ is a $M\times N$ matrix representing the error between the real data and the sparse representation of atoms except the $k$th column.

By making the low-rank approximations of the two terms closer, the above equation can be solved and the atom $\mathbf{d}_{k}$ can be obtained. By repeating this procedure, all the atoms in $\mathbf{D}$ can be updated. It is worth mentioning that if $\mathbf{s}_{T}^{k}$ contains some zero elements, the equation needs to be changed into a more flexible form. That is to say, if the $m$th coefficient in $\mathbf{s}_{T}^{k}$ is 0, the $\mathbf{s}_{T}^{k}$ can be rewritten as $\mathbf{s}_{new}^{k}$ which discards the $m$th element and has the size of $1\times N_{new}$. The $\mathbf{Q}_{k}$ will also correspondingly delete the $m$th column and get the new size $M\times N_{new}$. \new{Deleting the $m$th column in $Q_k$ is required by the sparsity of the coefficient vector $s_T^k$. Suppose that the $m$th entry in $s_T^k$ is zero, if $m$th column in $Q_k$ is not deleted, then the $m$th entry of the updated $s_T^k$ after the rank-one decomposition ($\mathbf{Q}_k=\mathbf{d}_k\mathbf{s}_T^k$) will be filled with an non-zero value. It will damage the sparse structure of the coefficients vector $s_T^k$.} We use $\mathbf{Q}_{k}^{new}$ to stand for the new error term. The equation then can be formulated as:
\begin{equation}
\label{eq:err}
\parallel \mathbf{Q}_{k}-\mathbf{d}_{k}\mathbf{s}_{T}^{k} \parallel_{F}^{2}=\parallel \mathbf{Q}_{k}^{new}-\mathbf{d}_{k}\mathbf{s}_{new}^{k} \parallel_{F}^{2}.
\end{equation}
Solving this equation can save more calculation resources and generate the same satisfactory results as equation \ref{eq:ksvd}.

\subsection{Dictionary update via SGK}
Inspired from \cite{sgk2013}, here we introduce a different dictionary learning model:
\begin{equation}
\label{eq:modelsgk}
\forall_{j}\mathbf{s}_j^{n}=\mathop{\text{argmin}}_{\mathbf{s}_j} \parallel \mathbf{X}-\mathbf{D}^{n}\mathbf{S} \parallel_{F}^{2},\,\,\text{s.t.}\,\, \forall_{j} \mathbf{s}_j = \mathbf{e}_p,
\end{equation}
where $\mathbf{e}_p$ denotes a unit vector with $t$th element being 1 and other elements being 0. The constraint on $\mathbf{s}_j$, i.e., $\mathbf{s}_j = \mathbf{e}_p$, can be taken into consideration during the sparse coding process, which will be introduced in detail later. During the dictionary update processing, $\mathbf{D}$ needs to be updated like the way in KSVD method. It is natural to use the KSVD method here to solve the same dictionary update problem, but we turn to use a more efficient way, which is enabled due to the constraint of the unit vector applied onto the sparse coefficients.  Following equation \ref{eq:err}, we define the following objective function as:
\begin{equation}
\label{eq:obj}
J=\parallel \mathbf{Q}_{k}^{new}-\mathbf{d}_{k}\mathbf{s}_{new}^{k} \parallel_{F}^{2}.
\end{equation}
Taking the derivative of $J$ with respect to the coefficient vector $\mathbf{d}_k$ and setting it to zero, we obtain
\begin{equation}
\label{eq:err2}
\frac{\partial J}{\partial  \mathbf{d}_k}=-2( \mathbf{Q}_{k}^{new}-\mathbf{d}_{k}\mathbf{s}_{new}^{k} )(\mathbf{s}_{new}^{k})^T=0.
\end{equation}
The solution to equation \ref{eq:err2} can be given as:
\begin{equation}
\label{eq:err3}
\mathbf{d}_{k}=\mathbf{Q}_{k}^{new}(\mathbf{s}_{new}^{k})^T(\mathbf{s}_{new}^{k}(\mathbf{s}_{new}^{k})^T)^{-1}.
\end{equation}

Supposing there are $N^k$ non-zero elements in the row vector $\mathbf{s}_{new}^{k}$, then 
\begin{equation}
\label{eq:N}
\mathbf{s}_{new}^{k}(\mathbf{s}_{new}^{k})^T =N^k,
\end{equation}
then
\begin{equation}
\label{eq:err3}
\mathbf{d}_{k}=\frac{1}{N^k}\mathbf{Q}_{k}^{new}(\mathbf{s}_{new}^{k})^T.
\end{equation}
$\mathbf{Q}_{k}^{new}(\mathbf{s}_{new}^{k})^T$ can be expressed as:
\begin{equation}
\label{eq:Qk}
\begin{split}
\mathbf{Q}_{k}^{new}(\mathbf{s}_{new}^{k})^T & = \left( \mathbf{X}^{new}-\sum_{j\ne k}^{L} \mathbf{d}_{j}\mathbf{s}_{new}^{j} \right)(\mathbf{s}_{new}^{k})^T \\
&= \mathbf{X}^{new}(\mathbf{s}_{new}^{k})^T - \sum_{j\ne k}^{L} \mathbf{d}_{j}\mathbf{s}_{new}^{j}(\mathbf{s}_{new}^{k})^T.
\end{split}
\end{equation}
$\mathbf{X}^{new}$ has the same meaning as $\mathbf{Q}^{new}$, i.e., selecting only the columns in  $\mathbf{X}$ according to the non-zero element indices in $\mathbf{s}_{new}^k$. Since $\mathbf{s}_{new}^{k}$ is a row vector containing ones for all its entries, then $\mathbf{X}^{new}(\mathbf{s}_{new}^{k})^T$ denotes a summation across all the columns of $\mathbf{X}^{new}$:
\begin{equation}
\label{eq:sum}
 \mathbf{X}^{new}(\mathbf{s}_{new}^{k})^T = \sum_{i=1}^{N^k}\mathbf{x}_i.
\end{equation}
Since $\forall_{j} \mathbf{s}_j = \mathbf{e}_p$ (with $\mathbf{s}_j$ being a column vector), 
\begin{equation}
\label{eq:jk}
\forall_{j\ne k} \mathbf{s}_{new}^{j}(\mathbf{s}_{new}^{k})^T =0.
\end{equation}
Inserting equations \ref{eq:sum} and \ref{eq:jk} into equation \ref{eq:Qk}, and then into equation \ref{eq:err3}, we obtain
\begin{equation}
\label{eq:dk}
\mathbf{d}_{k}=\frac{1}{N^k}\sum_{i=1}^{N^k}\mathbf{x}_i.
\end{equation}
Equation \ref{eq:dk} corresponds to the whole process of dictionary update in the SGK method. It is intuitive that in SGK, the low-rank approximation of $k$th dictionary atom via singular value decomposition (SVD) operation has been replaced by a simple summation across the training samples.
\subsection{Sparse coding in SGK}
In the SGK method, sparse coding can also be efficiently accelerated  due to the special structure of the coefficient vectors, i.e., the unit vector. The traditional OMP algorithm solves the sparse coding problem recursively. Assuming that there are \old{$T$}\new{$P$} non-zero elements in each coefficient vector, the OMP algorithm iterates \old{$T$}\new{$P$} times to get the optimal representation of the target data sample by a linear combination of the dictionary atoms. Thus, the higher \old{$T$}\new{$P$} is, the larger speedup is due to the efficient sparse coding in SGK. Besides, calculation of the pseudo-inverse of the selected representative dictionary matrix in each iteration becomes larger when a larger number of non-zero coefficients need to be computed.  In the SGK algorithm, however, we only need one-time sparse coding. It means that we require one iteration instead of \old{$T$}\new{$P$} to compute the optimal sparse coefficients. We only need to select one atom in the dictionary that best matches the target data sample $\mathbf{x}_i$.  Thus, the sparse coding in SGK is also much accelerated.

The traditional OMP algorithm can be detailed in Algorithm \ref{alg:alg1}, where $I$ denotes a set of indices that correspond to the non-zero sparse coefficients. $\mathbf{D}_I$ denotes the representative dictionary matrix composed of the selected atoms. $(\mathbf{D}_I)^{\dagger}=(\mathbf{D}_I^T\mathbf{D}_I)^{-1}\mathbf{D}_I^T$ denotes the pseudo-inverse of the representative dictionary matrix.

\begin{algorithm}
   \caption{OMP algorithm in KSVD method}
   \textbf{Input:} Dictionary $\mathbf{D}$, Training samples $\mathbf{X}$, Sparse coding parameter $T$. \\
   \textbf{Output:} Sparse coefficients $\mathbf{S}$. 
    \begin{algorithmic}[1]
 \For{$n$ = $1,\cdots,N$}
 \State $n$th column in $\mathbf{X}$ is set as $\mathbf{x}$
 \State  $\mathbf{r}=\mathbf{x}$
 \For{\new{$p$ = $1,\cdots,P$}}
     \State $\hat{k}  = \displaystyle\arg\max_{k} |\mathbf{d}_k^T\mathbf{r}|$ 
     \State $I=(I,\hat{k})$
     \State $\mathbf{s}_I=\left(\mathbf{D}_I\right)^{\dagger}\mathbf{x}$
     \State $\mathbf{r}=\mathbf{x} - \mathbf{D}_I \mathbf{s}_I$ 
 \EndFor
  \State  $n$th column of $\mathbf{S}$ is set by $\mathbf{s}_I$ with the indices defined by $I$ chosen as the non-zero coefficients.
 \EndFor

\end{algorithmic}
\label{alg:alg1}
\end{algorithm}
\new{$I = (I , \hat{k})$ means that each time one finds a sparse coefficient, the index $k$ is inserted into the index vector that is a collection of the indices of non-zero elements in the sparse coefficient vector.} As a comparison, the accelerated sparse coding algorithm in the SGK method can be detailed in Algorithm \ref{alg:alg2}.

\begin{algorithm}
   \caption{Sparse coding algorithm in SGK method}
   \textbf{Input:} Dictionary $\mathbf{D}$, Training samples $\mathbf{X}$. \\
   \textbf{Output:} Sparse coefficients $\mathbf{S}$. 
    \begin{algorithmic}[1]
 \For{$n$ = $1,\cdots,N$}
 \State $n$th column in $\mathbf{X}$ is set as $\mathbf{x}$
     \State $\hat{k}  = \displaystyle\arg\max_{k} |\mathbf{d}_k^T\mathbf{x}|$ 
  \State  $\hat{k}$th entry in $n$th column of $\mathbf{S}$ is set by $\mathbf{d}_k^T\mathbf{x}/(\mathbf{d}_k^T\mathbf{d}_k)$.
 \EndFor       
\end{algorithmic}
\label{alg:alg2}
\end{algorithm}

%\subsection{Comparison between KSVD, DDTF and SGK}

\subsection{Reconstruction based on the POCS method}
The reconstruction of seismic data can be expressed as the following inverse problem:
\begin{equation}
\label{eq:inv}
\mathbf{d}_{obs}= \mathbf{M}\mathbf{d},
\end{equation}
where $\mathbf{d}_{obs}$ is the observed incomplete data, $\mathbf{d}$ denotes the complete data to be reconstructed. $\mathbf{M}$ is the sampling operator. The structure of $\mathbf{M}$ has been introduced in many published papers, e.g., in \cite{mostafa2011}. We use an iterative POCS method to solve the inverse problem:
\begin{equation}
\label{eq:iter}
\mathbf{d}_{m+1} = \mathbf{M}\mathbf{d}_{obs} + (\mathbf{I}-\mathbf{M})\mathcal{F}(\mathbf{d}_m),
\end{equation}
where $m$ denotes iteration number, $\mathcal{F}$ denotes a reconstruction operator. In this paper, we use the dictionary learning based reconstruction operator, which can be expressed as:
\begin{equation}
\label{eq:Fdm}
\mathbf{F}(\mathbf{d}_m) = \mathcal{P}^{-1}(\hat{\mathbf{D}}\hat{\mathbf{S}}),
\end{equation}
where $\hat{\mathbf{D}}$ and $\hat{\mathbf{S}}$ are solution to the following problem:
\begin{equation}
\label{eq:pro}
\{\hat{\mathbf{D}},\hat{\mathbf{S}}\}=\arg\min_{\mathbf{D},\mathbf{S}} \parallel \mathcal{P}(\mathbf{d}_m)-\mathbf{D}\mathbf{S} \parallel_{F}^{2},\,\,\text{s.t.}\,\, \mathcal{C}(\mathbf{S}).
\end{equation}
$\mathcal{C}(\mathbf{S})$ denotes the constraint on the coefficient matrix $\mathbf{S}$, according to the KSVD method ($\forall_{j} \mathbf{s}_j \le P$) or the SGK method ($\forall_{j} \mathbf{s}_j = \mathbf{e}_p$). $\mathcal{P}$ and $\mathcal{P}^{-1}$ denote the patching and unpatching operators \cite{wanghang2020}, i.e., creating patches from the high-dimensional seismic data and reconstructing the high-dimensional seismic data from the patches.

Equation \ref{eq:iter} is effective only when the seismic data contains no/little random nosie \cite{shuwei2016cs}. When there is strong random noise, we propose to use the following weighted POCS\new{-like} iteration:\old{$\mathbf{d}_{m+1} =\alpha_m\mathbf{M}\mathbf{d}_{obs} +  (1-\alpha_m) \mathbf{M} \mathcal{F}(\mathbf{d}_m)+(\mathbf{I}-\mathbf{M})\mathcal{F}(\mathbf{d}_m)$}
\begin{equation}
\label{eq:iter2}
\mathbf{d}_{m+1} =\alpha_m\mathbf{M}\mathbf{d}_{obs} +  (\mathbf{I}-\alpha_m\mathbf{M})  \mathcal{F}(\mathbf{d}_m),
\end{equation}
where $\alpha_m$ is a relaxing parameter that linearly decreases from 1 to 0 through iterations.

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-clean}
\label{fig:hyper-clean}}
  \subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-noisy}
  \label{fig:hyper-noisy}}
  \subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-obs}
  \label{fig:hyper-obs}}
\caption{Synthetic example with hyperboloid events. (a) Clean data. (b) Noisy data (SNR=6.93 dB). (c) Observed data with 50\% randomly missing traces (SNR=2.21 dB).}
\label{fig:hyper-clean,hyper-noisy,hyper-obs}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-mssa}
\label{fig:hyper-mssa}}
\subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-ksvd}
\label{fig:hyper-ksvd}}\\
  \subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-ddtf}
  \label{fig:hyper-ddtf}}
  \subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-sgk}
  \label{fig:hyper-sgk}}
\caption{Reconstructed data using (a) Rank-reduction method (SNR=9.68 dB), (b) KSVD (SNR=10.84 dB), (c) DDTF (SNR=11.45 dB), and (d) SGK (SNR=11.00 dB). All DL based methods use the result from the rank-reduction method as the initial model.}
\label{fig:hyper-mssa,hyper-ksvd,hyper-ddtf,hyper-sgk}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-ksvd-simi}
\label{fig:hyper-ksvd-simi}}
  \subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-ddtf-simi}
  \label{fig:hyper-ddtf-simi}}
  \subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-sgk-simi}
  \label{fig:hyper-sgk-simi}}
\caption{Similarity comparison of reconstructed data using (a) KSVD, (b) DDTF, and (c) SGK.}
\label{fig:hyper-ksvd-simi,hyper-ddtf-simi,hyper-sgk-simi}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\columnwidth]{hyper/Fig/hyper-s-clean}
\label{fig:hyper-s-clean}}
  \subfigure[]{\includegraphics[width=0.31\columnwidth]{hyper/Fig/hyper-s-noisy}
  \label{fig:hyper-s-noisy}}
  \subfigure[]{\includegraphics[width=0.31\columnwidth]{hyper/Fig/hyper-s-obs}
  \label{fig:hyper-s-obs}}\\
\subfigure[]{\includegraphics[width=0.31\columnwidth]{hyper/Fig/hyper-s-ksvd}
\label{fig:hyper-s-ksvd}}
  \subfigure[]{\includegraphics[width=0.31\columnwidth]{hyper/Fig/hyper-s-ddtf}
  \label{fig:hyper-s-ddtf}}
  \subfigure[]{\includegraphics[width=0.31\columnwidth]{hyper/Fig/hyper-s-sgk}
  \label{fig:hyper-s-sgk}}
\caption{\new{2D slice comparison of the synthetic example. (a) Clean data. (b) Noisy data. (c) Observed data. (d) Reconstructed data using KSVD. (e) Reconstructed data using DDTF. (f) Reconstructed data using SGK.}}
\label{fig:hyper-s-clean,hyper-s-noisy,hyper-s-obs,hyper-s-ksvd,hyper-s-ddtf,hyper-s-sgk}
\end{figure}

%\begin{figure}[htb!]
%\centering
%\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper_regu/Fig/hyper2-obs}
%\label{fig:hyper2-obs}}
%  \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper_regu/Fig/hyper2-sgk}
%  \label{fig:hyper2-sgk}}
%\caption{\new{A reconstruction test for regularly missing traces. (a) Observed data. (b) Reconstructed data.}}
%\label{fig:hyper2-obs,hyper2-sgk}
%\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-clean}
\label{fig:syn5d-clean}}
  \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-noisy}
  \label{fig:syn5d-noisy}}
  \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-obs}
  \label{fig:syn5d-obs}}\\
\subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-ksvd}
\label{fig:syn5d-ksvd}}
  \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-ddtf}
  \label{fig:syn5d-ddtf}}
  \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-sgk}
  \label{fig:syn5d-sgk}}
\caption{\new{Comparison of 5D seismic reconstruction in a common midpoint gather. (a) Clean data. (b) Noisy data (SNR=-0.65 dB). (c) Decimated data with 70\% randomly removed traces  (SNR=-0.21 dB). (d) Reconstructed data using KSVD  (SNR=6.58 dB). (e) Reconstructed data using DDTF  (SNR=3.22 dB). (f) Reconstructed data using SGK (SNR=6.58 dB).}}
\label{fig:syn5d-clean,syn5d-noisy,syn5d-obs,syn5d-ksvd,syn5d-ddtf,syn5d-sgk}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-clean2}
\label{fig:syn5d-clean2}}
  \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-noisy2}
  \label{fig:syn5d-noisy2}}
  \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-obs2}
  \label{fig:syn5d-obs2}}\\
\subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-ksvd2}
\label{fig:syn5d-ksvd2}}
  \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-ddtf2}
  \label{fig:syn5d-ddtf2}}
  \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-sgk2}
  \label{fig:syn5d-sgk2}}
\caption{\new{Comparison of 5D seismic reconstruction in a common offset gather. (a) Clean data. (b) Noisy data (SNR=-0.65 dB). (c) Decimated data with 70\% randomly removed traces  (SNR=-0.21 dB). (d) Reconstructed data using KSVD  (SNR=6.58 dB). (e) Reconstructed data using DDTF  (SNR=3.22 dB). (f) Reconstructed data using SGK (SNR=6.58 dB).}}
\label{fig:syn5d-clean2,syn5d-noisy2,syn5d-obs2,syn5d-ksvd2,syn5d-ddtf2,syn5d-sgk2}
\end{figure}

\new{Despite of the highly incomplete sampling of the raw dataset, it is not difficult to learn dictionaries.  In the proposed framework, one can use two options to learn dictionaries from observed data. First, one can directly learn the dictionaries from incomplete data with missing traces. Secondly, one can also learn the dictionaries for initially reconstructed data (e.g., using a rank-based method). Both strategies will be illustrated later. }

\new{An interesting note is that enforcing $\mathbf{s}_j =\mathbf{e}_p$ ($P=1$) helps deriving the SVD-free dictionary updating scheme, as an averaged form of the training samples (e.g., in equation \ref{eq:dk}). $P=1$ is only required in the dictionary learning process. When applied to denoising or reconstruction, the sparse coding process expressed in equation \ref{eq:eq1}, (given the learned dictionary $\mathbf{D}$ from the SGK method), can be taken for the denoising or reconstruction purpose.}

\section{Examples}
To evaluate the performance of different methods, we use two metrics. The first one is the commonly used signal-to-noise ratio (SNR) metric, which is defined as:
\begin{equation}
\label{eq:snr}
\text{SNR}=20\log_{10}\frac{\Arrowvert \mathbf{d}_{true} \Arrowvert_2}{\Arrowvert \mathbf{d}_{true} -\mathbf{d}_{esti}\Arrowvert_2},
\end{equation}
where $\mathbf{d}_{true}$ denotes the ground-truth solution, i.e., clean data, and $\mathbf{d}_{esti}$ denotes the reconstructed/noisy data to estimate the SNR. Another quantitive metric is the local similarity metric \cite{fomel2007localattr,yangkang2015ortho}. A higher local similarity value between the clean and reconstructed/incomplete data means a more accurate reconstruction or a higher quality. All comparisons of computational costs are based on a Mac Pro Laptop with a 2.5 Ghz Intel Core i7 processor, and 16 GB LPDDR3 memory. In addition to the KSVD method, we also compare the performance of the proposed SGK method with the data-driven tight frame (DDTF) method \cite{siwei2016}.

We first test the performance of different algorithms to a 3D synthetic data with plane waves. The clean data of this example is plotted in Fig. \ref{fig:synth-clean}. We add some band-limited noise to the clean data and obtain the noisy data, as plotted in Fig. \ref{fig:synth-noisy}. We randomly remove 50\% of the total traces from the noisy data to generate the noisy and incomplete data, as shown in Fig. \ref{fig:synth-obs}. The SNRs of the noisy and incomplete data are -0.05 dB and -0.03 dB, respectively. The three reconstructed data using KSVD, DDTF, and the proposed methods are plotted in Fig. \ref{fig:synth-ksvd,synth-ddtf,synth-sgk}. The SNRs of KSVD, DDTF, and the proposed methods are 8.89 dB, 5.42 dB, 9.74 dB, respectively. It is clear that the SGK method obtains an obviously better result than the other two methods. Both KSVD and DDTF methods seem to leave significant residual noise while the SGK method causes the smallest amount of residual noise. Note that for all three methods, we use 10 iterations for dictionary update, and 12 iterations for the POCS method. The KSVD and DDTF methods use \new{$P=3$} for the sparse coding. The size of this dataset is $175\times 20\times20$. During the patching and unpatching steps, the patch size is $6\times 4\times 4$, and the shift size is the same for all three dimensions, i.e., 2 points. The KSVD method takes 313.41 s, DDTF method takes 255.05 s, and the proposed method takes only 51.30s, which is more than 6 times faster than the traditional KSVD method. The learned atoms of different methods are plotted in Fig. \ref{fig:atom_dct,atom_ksvd,atom_ddtf,atom_sgk}. The atoms of the initial dictionary refer to the discrete cosine transform, as plotted in Fig. \ref{fig:atom_dct}. The atoms learned from the KSVD, DDTF, and SGK methods are plotted in Figs. \ref{fig:atom_ksvd}, \ref{fig:atom_ddtf}, and \ref{fig:atom_sgk}, respectively. We further use the local similarity to evaluate the reconstruction performance. The local similarity between the ground-truth solution and all these three reconstructed data are shown in Fig. \ref{fig:synth-ksvd-simi,synth-ddtf-simi,synth-sgk-simi}, where the local similarity corresponding to the proposed method is obviously higher than the other two methods, indicating a higher reconstruction accuracy. The local similarity corresponding to the DDTF method seems to have lower values. A 2D slice comparison of different data are plotted in Fig. \ref{fig:synth-s-clean,synth-s-noisy,synth-s-obs,synth-s-ksvd,synth-s-ddtf,synth-s-sgk}.  The top row of Fig. \ref{fig:synth-s-clean,synth-s-noisy,synth-s-obs,synth-s-ksvd,synth-s-ddtf,synth-s-sgk} shows the clean data (left), noisy data (middle), and decimated data (right). The bottom row of Fig. \ref{fig:synth-s-clean,synth-s-noisy,synth-s-obs,synth-s-ksvd,synth-s-ddtf,synth-s-sgk} shows the results from KSVD (left), DDTF (middle), and SGK (right) methods. It is clear that the KSVD and SGK methods obtain obviously better results than the DDTF method, e.g., better signal preservation. A single-trace comparison is plotted in Fig. \ref{fig:synth-ss}. In Fig. \ref{fig:synth-ss}, the ground-truth solution is plotted as the black line. The green line corresponds to the noisy data, which clearly shows that the noise level is very strong. The results from the KSVD, DDTF, and SGK methods are plotted as pink, red, and blue lines, respectively. The pink line seems to be closest to the black line, demonstrating that the proposed method is best in preserving the amplitude as well as removing the strong random noise. All three methods use the discrete cosine transform as the initial dictionary atoms. The incomplete data are used directly as the initial guess in the POCS iteration. A better initial guess of the ground truth can help obtain a better reconstructed result in the proposed iterative framework. For example, we also conduct a benchmark comparison with the state-of-the-art multi-channel singular spectrum analysis (MSSA) method and show the result in Fig. \ref{fig:synth-mssa}, where the rank is chosen as three, since three corresponds to the number of plane-wave components in this dataset. The SNR of the MSSA result is 9.51 dB. Then, we use the result from the MSSA method as the initial model of the proposed framework, and obtain an even better result with a SNR equal to 12.22 dB, as shown in Fig. \ref{fig:synth-mssasgk}.

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/f-obs}
\label{fig:f-obs}}
\subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/f-ksvd}
\label{fig:f-ksvd}}\\
  \subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/f-ddtf}
  \label{fig:f-ddtf}}
  \subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/f-sgk}
  \label{fig:f-sgk}}
\caption{\new{3D Field data example. (a) Observed data. Reconstructed data using (b) KSVD, (c) DDTF, and (d) SGK.} }
\label{fig:f-obs,f-ksvd,f-ddtf,f-sgk}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/f-s-obs0}
\label{fig:f-s-obs0}}
\subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/f-s-ksvd0}
\label{fig:f-s-ksvd0}}\\
  \subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/f-s-ddtf0}
  \label{fig:f-s-ddtf0}}
  \subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/f-s-sgk0}
  \label{fig:f-s-sgk0}}
\caption{2D slice comparison of the field data example. (a) Observed data. (b) Reconstructed data using KSVD. (c) Reconstructed data using DDTF. (d) Reconstructed data using SGK. The frame boxes are zoomed and shown in Figure \ref{fig:fz-obs,fz-ksvd,fz-ddtf,fz-sgk}. }
\label{fig:f-s-obs0,f-s-ksvd0,f-s-ddtf0,f-s-sgk0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/fz-obs}
\label{fig:fz-obs}}
\subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/fz-ksvd}
\label{fig:fz-ksvd}}\\
  \subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/fz-ddtf}
  \label{fig:fz-ddtf}}
  \subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/fz-sgk}
  \label{fig:fz-sgk}}
\caption{Zoomed 2D slice comparison of the field data example. (a) Observed data. (b) Reconstructed data using KSVD. (c) Reconstructed data using DDTF. (d) Reconstructed data using SGK. }
\label{fig:fz-obs,fz-ksvd,fz-ddtf,fz-sgk}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\columnwidth]{field5d/Fig/f5d-obs}
\label{fig:f5d-obs}}
\subfigure[]{\includegraphics[width=0.45\columnwidth]{field5d/Fig/f5d-ksvd}
\label{fig:f5d-ksvd}}\\
  \subfigure[]{\includegraphics[width=0.45\columnwidth]{field5d/Fig/f5d-ddtf}
  \label{fig:f5d-ddtf}}
  \subfigure[]{\includegraphics[width=0.45\columnwidth]{field5d/Fig/f5d-sgk}
  \label{fig:f5d-sgk}}
\caption{5D seismic reconstruction example. A common offset gather is displayed for comparison. The 3D common offset gather has been reformulated as 2D matrix. (a) Observed data with approximately 70\% missing traces. (b) Reconstructed data using KSVD. (c) Reconstructed data using DDTF. (d) Reconstructed data using SGK. }
\label{fig:f5d-obs,f5d-ksvd,f5d-ddtf,f5d-sgk}
\end{figure}

\begin{figure}[ht!]
\centering
\subfigure[]{\includegraphics[width=0.45\columnwidth]{field5d/Fig/z-obs}
\label{fig:z-obs}}
\subfigure[]{\includegraphics[width=0.45\columnwidth]{field5d/Fig/z-ksvd}
\label{fig:z-ksvd}}\\
  \subfigure[]{\includegraphics[width=0.45\columnwidth]{field5d/Fig/z-ddtf}
  \label{fig:z-ddtf}}
  \subfigure[]{\includegraphics[width=0.45\columnwidth]{field5d/Fig/z-sgk}
  \label{fig:z-sgk}}
\caption{Zoomed comparison of the 5D seismic reconstruction example. The zooming area is stressed by the frame boxes in Figure \ref{fig:f5d-obs,f5d-ksvd,f5d-ddtf,f5d-sgk}. (a) Observed data with approximately 70\% missing traces. (b) Reconstructed data using KSVD. (c) Reconstructed data using DDTF. (d) Reconstructed data using SGK. The SGK result is obviously better than the other two methods.}
\label{fig:z-obs,z-ksvd,z-ddtf,z-sgk}
\end{figure}

The second example is a 3D synthetic data with a hyperboloid event. The clean data are plotted in Fig. \ref{fig:hyper-clean}. The noisy data by adding band-limited noise and the decimated data by randomly removing 50\% traces are plotted in Figs. \ref{fig:hyper-noisy} and \ref{fig:hyper-obs}. The SNRs of the noisy and decimated data are 6.93 dB and 2.21 dB, respectively. In this test, the reconstructed data using four different methods, i.e., MSSA (9.68 dB), KSVD (10.84 dB), DDTF (11.45 dB), SGK (11.00 dB) methods, are plotted in Fig. \ref{fig:hyper-mssa,hyper-ksvd,hyper-ddtf,hyper-sgk}. \new{In this example, the MSSA is not applied in small windows. We use a rank parameter of 20 for the MSSA method.} All dictionary learning based methods use the result from the MSSA method as the initial model in the POCS method. Although in this case, the DDTF method obtains a higher SNR than the SGK method, the SGK method takes much less computing time. The size of this synthetic dataset is $50\times 32\times 32$. The patch size is $4\times 4 \times 4$. The shift size is 2 points for all dimensions  In this test, the sparse coding parameter is larger, i.e., \old{$T=30$}\new{$P=30$}, because of the curving structure. We use 10 iterations to update the dictionary in each method and use 10 iterations for the POCS method. The KSVD and DDTF method take 4,132.23s and 3,801.04s, respectively. The SGK method, however, takes 353.03s. The speedup compared with the KSVD method is almost 12 times. The local similarity maps between clean and reconstructed data for each dictionary learning method are plotted in Fig. \ref{fig:hyper-ksvd-simi,hyper-ddtf-simi,hyper-sgk-simi}, which demonstrates that the performance of the three dictionary learning methods are comparable. A 2D slice is extracted from each dataset and plotted in Fig. \ref{fig:hyper-s-clean,hyper-s-noisy,hyper-s-obs,hyper-s-ksvd,hyper-s-ddtf,hyper-s-sgk}, where the top row shows the clean data (left), noisy data (middle), and decimated data (right), and the bottom row shows the reconstructed data using KSVD (left), DDTF (middle), and SGK (right). The 2D slices demonstrate that all three dictionary learning methods obtain successful recovery of the hyperboloid seismic event. The DDTF and SGK methods are slightly better than the KSVD method in terms of residual noise. 
%\new{Based on this dataset, we also conduct a test for reconstructing regularly missing traces. As shown in Fig. \ref{fig:hyper2-obs,hyper2-sgk}, the proposed method is also effective in reconstructing the regularly missing traces.}

%\section{Discussions}

The third example is a 5D synthetic dataset. Since it is not convenient to plot 5D dataset, we extract a 3D cube (e.g., a common midpoint gather or a common offset gather) from the 5D datasets for comparison. A comparison of different datasets in the common midpoint domain is shown in Fig. \ref{fig:syn5d-clean,syn5d-noisy,syn5d-obs,syn5d-ksvd,syn5d-ddtf,syn5d-sgk}. The top row in Fig. \ref{fig:syn5d-clean,syn5d-noisy,syn5d-obs,syn5d-ksvd,syn5d-ddtf,syn5d-sgk} plots the clean data (left), the noisy data with band-limited random noise (middle), and the decimated data by randomly removing 70\% traces (right). The bottom row plots the reconstructed data by the KSVD (left), DDTF (middle), and the SGK (right) methods. The SNRs of the noisy and decimated data are -0.65 dB and -0.21 dB, respectively. After reconstruction, the KSVD, DDTF, and SGK methods obtain SNRs of 6.58 dB, 3.22 dB, and 6.58 dB, respectively. For this dataset, the SNR of the DDTF is however much lower than the other two methods, which indicates a somewhat unstable performance of the DDTF method. Note that we have tuned the parameters by a try-and-error method but could not obtain a better result for the DDTF method. When observing the reconstructed data in Fig. \ref{fig:syn5d-clean,syn5d-noisy,syn5d-obs,syn5d-ksvd,syn5d-ddtf,syn5d-sgk}, it also shows that the DDTF method causes obvious amplitude damages since the energy of the reconstructed seismic events is much weaker compared with the ground-truth solution shown in Fig. \ref{fig:syn5d-clean}. Both KSVD and SGK methods, however, are comparable and perform successfully. The size of this dataset is $100\times10\times10\times10\times10$. We use a sparse coding parameter \old{$T=3$}\new{$P=3$} for all dictionary learning methods. The patch size of the first dimension is 6 points and the patch sizes for all the spatial dimensions are 4 points. The shift sizes for all dimensions are all 2 points. 
We use 10 iterations for dictionary update and 5 iterations for the POCS reconstruction. In this test, the SGK method takes only 1,232.21s, while the KSVD method takes 7,348.99s and the DDTF method takes 6,503.32s.  The speedup is almost 6 times. In a similar way, Fig. \ref{fig:syn5d-clean2,syn5d-noisy2,syn5d-obs2,syn5d-ksvd2,syn5d-ddtf2,syn5d-sgk2} plots a comparison of different datasets in the common offset domain, where we can observe a similar phenomenon as in the common midpoint domain.

The fourth example is a 3D field dataset. \new{Fig. \ref{fig:f-obs} shows the observed data with 56\% traces missing. There is a large gap (about 10 continuous traces) in the front slice. It is a post-stack dataset. The two space dimensions mean midpoint number in X and midpoint number in Y, respectively.} Figs. \ref{fig:f-ksvd}-\ref{fig:f-sgk} plot the reconstructed data using KSVD, DDTF, and SGK methods respectively. It is clear that all three dictionary learning methods obtain satisfactory results. The size of this dataset is $300\times 100\times 10$. Because of the complexity of this field dataset, we use a relatively high sparse-coding parameter, i.e., \old{$T=20$}\new{$P=20$}. We use 10 iterations for dictionary update and 5 iterations for the POCS reconstruction. Due to a larger \old{$T$}\new{$P$}, the KSVD and DDTF methods take a very long time, i.e., 6800.67 s for KSVD and 6300.34 s for DDTF. The SGK method, however, takes only 645.31 s, which is more than 10 times faster than the KSVD method. We extract a 2D slice from each dataset in Fig. \ref{fig:f-obs,f-ksvd,f-ddtf,f-sgk} and show the corresponding results in Fig. \ref{fig:f-s-obs0,f-s-ksvd0,f-s-ddtf0,f-s-sgk0}. We further zoom in the sections for a better evaluation of the reconstruction and show the zoomed data in Fig. \ref{fig:fz-obs,fz-ksvd,fz-ddtf,fz-sgk}. It is clear from Fig. \ref{fig:fz-obs,fz-ksvd,fz-ddtf,fz-sgk} that the proposed SGK method seems to obtain the best recovery of the shallow weak signals. The DDTF method, however, shows weakest energy of the shallow seismic events. \new{From this example, we also conclude that a continuously missing 10\% of the whole traces can be reconstructed with good performance.}

The final example is a 5D field dataset. \new{The four spatial dimensions of this field dataset are midpoint X, midpoint Y, offset X, and offset Y. This dataset has not gone through any pre-processing steps, except for the binning from irregular spatial coordinates onto regular grids. } Here, we extract a common offset gather from the 5D dataset and plot the common offset gather as a 2D matrix, which clearly shows the reconstruction performance. Fig. \ref{fig:f5d-obs} plots the observed 5D dataset in a 2D matrix, with a significant portion (roughly 70\%) of the data not recorded. Figs. \ref{fig:f5d-ksvd}-\ref{fig:f5d-sgk} show the reconstructed data using KSVD, DDTF, and SGK methods.  It is obvious that all three methods reconstruct most of the missing data and make the seismic waveforms much more coherent in the spatial dimension. However, in this dataset, the KSVD method seems to cause the worst result since the energy is obviously weaker compared with the other two methods. Besides, it fails in reconstructing the big gap as highlighted by the pink frame boxes. The size of this dataset is $100\times 4\times 4\times 20\times 20$. The patch size is $6\times 2 \times 2\times 4\times 4$. The shift size is 1 point for the first dimension and 2 points for all other dimensions. In this dataset, the sparse coding parameter \old{$T=3$}\new{$P=3$}. We use 10 iterations for dictionary update and 5 iterations for POCS reconstruction. The SGK method takes 1,203.53s, while the KSVD and DDTF take 8,766.97s and 7,793.12s, respectively. The speedup is about 7 times.  A zoomed comparison of different data is plotted in Fig. \ref{fig:z-obs,z-ksvd,z-ddtf,z-sgk} for a better view, which further demonstrates that the proposed SGK method seems to obtain the best result, and the DDTF method still causes some discontinuous reconstructed traces. From this test and the aforementioned numerical tests, it becomes clear that the KSVD and DDTF methods are less stable than the SGK method. It is difficult to predict which of the two methods (KSVD or DDTF) is better for a specific dataset, but we can conclude that the SGK method normally gives a stable and acceptable result with a high efficiency. \new{All the computation time comparisons are listed in Table \ref{tbl:timecomp}.}
%\new{
%\tabl{timecomp}{\new{Comparison of computation time among different dictionary learning methods.}}
% {
%    \begin{center}
%     \begin{tabular}{|c|c|c|c|} 
%	  \hline Tests & KSVD (s) &DDTF (s) & Proposed (s)			       		 \\ 
%	  \hline First synthetic & 313.41 &255.05 & 51.30 \\
%	  \hline Second synthetic & 4132.23 &3801.04 & 353.03 \\
%	  \hline Third synthetic  & 7348.99 & 6503.32 & 1232.21  \\
%	  \hline First field  &  6800.67 & 6300.34 &  645.31\\
%	  \hline Second field  & 8766.97 & 7793.12& 1203.53 \\
%      \hline 
%    \end{tabular} 
%   \end{center}
%}}
\new{
\begin{table}[h]
\caption{\new{Comparison of computation time among different dictionary learning methods.}}
\begin{center}
    \begin{tabular}{|c|c|c|c|} 
	  \hline Tests & KSVD (s) &DDTF (s) & Proposed (s)			       		 \\ 
	  \hline First synthetic & 313.41 &255.05 & 51.30 \\
	  \hline Second synthetic & 4132.23 &3801.04 & 353.03 \\
	  \hline Third synthetic  & 7348.99 & 6503.32 & 1232.21  \\
	  \hline First field  &  6800.67 & 6300.34 &  645.31\\
	  \hline Second field  & 8766.97 & 7793.12& 1203.53 \\
      \hline 
   \end{tabular} 
\end{center}
\label{tbl:timecomp}
\end{table}}

\section{Conclusions}
Dictionary learning (DL) uses an iterative process to update the sparse dictionary and the sparse coefficients in a data-driven way, thus is an adaptive approach in sparsity-promoting applications in seismic processing. We have introduced an efficient DL algorithm to deal with the computational bottleneck in high-dimensional seismic reconstructions based on the DL framework. Compared with the classic KSVD method, the proposed SGK method reduces the computational cost in the dictionary update step by replacing the SVD calculation with the calculation of mean of several input samples, and thus is less expensive. Besides, the SGK method saves significant cost by a special sparse coding that is free of the OMP algorithm, which further improves the computational efficiency. The proposed DL framework can not only be used as a standalone processing method, but also be combined with a conventional method. For example, it is applicable to learn the initial dictionary from the result of a first-step reconstruction method, e.g., the rank-reduction method, to obtain an even better result. We test the effectiveness and efficiency by both 3D and 5D examples, which both demonstrate promising performance. \new{Future research will focus on reconstructing regularly missing data based on the proposed method.}

\bibliographystyle{IEEEtran}
\bibliography{dl}

%\begin{figure}[htb!]
%	\centering
%	\subfigure[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
%	\caption{Caption.}
%	\label{fig:fig}
%\end{figure}

%\begin{figure}[htb!]
%	\centering
%	\subfigure[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}}\\
%    \subfigure[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}}
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure}

%\begin{table}[h]
%\caption{Table caption}
%\begin{center}
%     \begin{tabular}{|c|c|c|c|c|c|} 
%	  \hline Column1 (unit)  & Column2 (unit) & Column3 (unit) \\ 
%	  \hline 1 & 2  & 3 \\
%       \hline
%    \end{tabular} 
%\end{center}
%\label{tbl:table1}
%\end{table}

### 2020-10-10 sgk5d/matfun/Field5d.m

@@ -1,0 +1,141 @@
+function Field5d(clean,noisy,obs,sgk,ksvd,ddtf,T,niter,nniter,K,ll1,ll2,ll3,ss1,ss2,ss3,perc)
+% Author      : Yangkang Chen
+%               Zhejiang University
+%         
+% Date        : April, 2020
+
+% Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
+    
+%  Copyright (C) 2020 Zhejiang University
+%  Copyright (C) 2020 Yangkang Chen
+%  
+%  This program is free software; you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published by
+%  the Free Software Foundation; either version 2 of the License, or
+%  (at your option) any later version.
+%  
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%  
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, write to the Free Software
+%  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  
+
+addpath(genpath('~/chenyk.data3/'));
+addpath(genpath('~/chenyk/matlibcyk'));
+%clc;clear;close all;
+% DEMO script for 3D denoising and reconstruction based on KSVD
+% By Yangkang Chen
+% March, 2020
+
+load field5d.mat
+d=data5d;d=d/max(max(max(max(max(d)))));
+%% make it smaller
+d=d(46:145,1:4,1:4,:,:);
+[nt,nhx,nhy,nx,ny]=size(d);
+dt=0.004;
+%% exploring the data
+%1) ploting CMP gather
[…]

### 2020-10-10 sgk5d/matfun/Hyper.m

@@ -1,0 +1,194 @@
+function Hyper(clean,noisy,obs,sgk,ksvd,ddtf,mssa,mssasgk,T,niter,nniter,K,ll1,ll2,ll3,ss1,ss2,ss3,perc)
+% Author      : Yangkang Chen
+%               Zhejiang University
+%         
+% Date        : April, 2020
+
+% Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
+    
+%  Copyright (C) 2020 Zhejiang University
+%  Copyright (C) 2020 Yangkang Chen
+%  
+%  This program is free software; you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published by
+%  the Free Software Foundation; either version 2 of the License, or
+%  (at your option) any later version.
+%  
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%  
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, write to the Free Software
+%  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  
+
+addpath(genpath('~/chenyk/matlibcyk'));
+%clc;clear;close all;
+% DEMO script for 3D denoising and reconstruction based on KSVD
+% By Yangkang Chen
+% March, 2020
+
+%% create data
+cmp=zeros(50,32,32);
+[nz,nx,ny]=size(cmp);
+
+x=[1:32];
+y=[1:32];
+[x,y]=meshgrid(x,y);
+z=10*(sqrt(1+((x-16)./10).^2+((y-16)./10).^2)-1)+20;
+% figure;surf(y);set(gca,'ydir','reverse');
+
+for ix=1:nx
+    for iy=1:ny
[…]

### 2020-10-10 sgk5d/matfun/Hyper2.m

@@ -1,0 +1,201 @@
+function Hyper(clean,noisy,obs,sgk,ksvd,ddtf,mssa,mssasgk,T,niter,nniter,K,ll1,ll2,ll3,ss1,ss2,ss3,perc)
+% Author      : Yangkang Chen
+%               Zhejiang University
+%         
+% Date        : April, 2020
+
+% Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
+    
+%  Copyright (C) 2020 Zhejiang University
+%  Copyright (C) 2020 Yangkang Chen
+%  
+%  This program is free software; you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published by
+%  the Free Software Foundation; either version 2 of the License, or
+%  (at your option) any later version.
+%  
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%  
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, write to the Free Software
+%  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  
+
+addpath(genpath('~/chenyk/matlibcyk'));
+%clc;clear;close all;
+% DEMO script for 3D denoising and reconstruction based on KSVD
+% By Yangkang Chen
+% March, 2020
+
+%% create data
+cmp=zeros(50,32,32);
+[nz,nx,ny]=size(cmp);
+
+x=[1:32];
+y=[1:32];
+[x,y]=meshgrid(x,y);
+z=10*(sqrt(1+((x-16)./10).^2+((y-16)./10).^2)-1)+20;
+% figure;surf(y);set(gca,'ydir','reverse');
+
+for ix=1:nx
+    for iy=1:ny
[…]

### 2020-10-10 sgk5d/matfun/plotatom3d.m

@@ -1,0 +1,66 @@
+function plotatom3d(d0,L1,L2,L3)
+% yc_plotatom3d: plot atoms in 3D cubes
+% 
+% 
+% DEMO
+% test/test_ksvd3d.m
+% 
+l1=L3;
+l2=L2;
+l3=L1;
+
+n1 = size(d0,1);
+n2 = size(d0,2);
+% n = round(n1^(1.0/3.0));      
+d0(n1,:)=d0(n1,:)*1.00001;
+newd = zeros(l1+1,l1+1,l3+1);
+% tm =[1 2 5 17 6 18 21 22];  % 4
+% tm =[1 2 9 65 10 66 73 74]; % 8
+% tm =[1 2 3 4 5 6 7 8]; % 8
+% tm =[1 2 4 6 8 9 10 11 24 25 26 28 31 32 41 44] ;%8-di-elf
+tm =[1 2 3 4 6 8 9 12 20 21 22 27 32 54 56 58] ;%8-d-X
+% tm=[1:64];
+tm=[1,2,3,5,13,17,18,21,22,25,29,30,33,34,37,38,39,40,41,42,43,45,46,47,49,55,57,58,59,63];
+tm=[1,2,3,5,17,18,29,33,39,40,46,47,49,58,59,63];
+% tm = [1 2 8 50 9 51 57 58]; % 7
+% tm = [1 2 4 5 8 10 11 18 19 23 24 25 26 30 31 32 33 52 53 54]; % 7-2
+%   tm = 1:64;
+for m = 1:1
+    figure;
+    for i=1:length(tm)
+
+        subplot(4,4,i);
+%                 subplot(8,8,i);
+        newd = zeros(l1+1,l2+1,l3+1);
+        % DisplayH3d( reshape(d0(:,16/16*(i-1)+1),n,n,n));
+%         p = (m-1)*n*n+(i-1)+1;
+        p = tm(i) ;
+        newd(1:l1,1:l2,1:l3) = yc_transp(reshape(d0(:,p),L1,L2,L3),13);
+        newd(:,:,l3+1) = newd(:,:,l3);
+        newd(:,l2+1,:) = newd(:,l2,:);
+        newd(l1+1,:,:) = newd(l1,:,:);
+        slice(newd,[1,l1+1],[1,l2+1],[1,l3+1]);caxis([-0.15,0.15]);%colormap gray;
+        
+        h=findobj(gca,'linestyle','-');
+        h(1)=h(2);
[…]

### 2020-10-21 dtv/paper.tex
2020年10月20日 星期二 23时13分33秒 CDT

@@
 
-\begin{algorithm}
-\caption{FWI with directional total variation}
-\begin{algorithmic}[1]
-  \scriptsize
-  \STATE Initialize: $\mathbf{m}^0=\mathbf{m}_0$, and $\mathbf{a}_1^0=\mathbf{a}_2^0=\mathbf{b}_1^0=\mathbf{b}_2^0=0$\\
-  \STATE While Iter $<$ MaxIter \\
-  ~$\mathbf{m}^{k+1}=\min\limits_\mathbf{m} \mu || \mathbf{d} - f\left(\mathbf{m}\right) ||_2^2 + \lambda|| \mathbf{a}_1^k-\nabla_1 \mathbf{m}-\mathbf{b}_1^k||_2^2 + \lambda|| \mathbf{a}_2^k-\nabla_2 \mathbf{m}-\mathbf{b}_2^k||_2^2$  \\
-  ~~~~~(Hint: we solve this subproblem using gradient method, and the gradient is: \\
-  ~~~~~~~~$\mu f^{*} \left( f\left(\mathbf{m}^{k}\right) - \mathbf{d} \right) - \lambda \nabla^{T}_1 \left( \mathbf{a}_1^k-\nabla_1 \mathbf{m}^{k}-\mathbf{b}_1^k \right) - \lambda \nabla^{T}_2 \left( \mathbf{a}_2^k-\nabla_2 \mathbf{m}^{k}-\mathbf{b}_2^k \right)$) \\
-  ~$\mathbf{a}_1^{k+1}=shrink\left(\nabla_1 \mathbf{m}^{k+1}+\mathbf{b}_1^k, \frac{1}{\lambda}\right)$ \\
-  \new{~~~~~($shrink\left(x, \gamma\right) = \frac{x}{|x|} * max\left(|x| - \gamma, 0\right)$, a soft-thresholding operator \citep{donoho1995noising})} \\
-
-  ~$\mathbf{a}_2^{k+1}=shrink\left(\nabla_2 \mathbf{m}^{k+1}+\mathbf{b}_2^k, \frac{1}{\lambda}\right)$ \\
-  ~$\mathbf{b}_1^{k+1}=\mathbf{b}_1^{k} + \left(\nabla_1 \mathbf{m}^{k+1}-\mathbf{a}_1^{k+1}\right)$  \\
-  ~$\mathbf{b}_2^{k+1}=\mathbf{b}_2^{k} + \left(\nabla_2 \mathbf{m}^{k+1}-\mathbf{a}_2^{k+1}\right)$  \\
-  end
-\end{algorithmic}
-\end{algorithm}
+% Algorithm is not available in Madagascar online version (please refer to the journal version)
+%\begin{algorithm}
+%\caption{FWI with directional total variation}
+%\begin{algorithmic}[1]
+%  \scriptsize
+%  \STATE Initialize: $\mathbf{m}^0=\mathbf{m}_0$, and $\mathbf{a}_1^0=\mathbf{a}_2^0=\mathbf{b}_1^0=\mathbf{b}_2^0=0$\\
+%  \STATE While Iter $<$ MaxIter \\
+%  ~$\mathbf{m}^{k+1}=\min\limits_\mathbf{m} \mu || \mathbf{d} - f\left(\mathbf{m}\right) ||_2^2 + \lambda|| \mathbf{a}_1^k-\nabla_1 \mathbf{m}-\mathbf{b}_1^k||_2^2 + \lambda|| \mathbf{a}_2^k-\nabla_2 \mathbf{m}-\mathbf{b}_2^k||_2^2$  \\
+%  ~~~~~(Hint: we solve this subproblem using gradient method, and the gradient is: \\
+%  ~~~~~~~~$\mu f^{*} \left( f\left(\mathbf{m}^{k}\right) - \mathbf{d} \right) - \lambda \nabla^{T}_1 \left( \mathbf{a}_1^k-\nabla_1 \mathbf{m}^{k}-\mathbf{b}_1^k \right) - \lambda \nabla^{T}_2 \left( \mathbf{a}_2^k-\nabla_2 \mathbf{m}^{k}-\mathbf{b}_2^k \right)$) \\
+%  ~$\mathbf{a}_1^{k+1}=shrink\left(\nabla_1 \mathbf{m}^{k+1}+\mathbf{b}_1^k, \frac{1}{\lambda}\right)$ \\
+%  \new{~~~~~($shrink\left(x, \gamma\right) = \frac{x}{|x|} * max\left(|x| - \gamma, 0\right)$, a soft-thresholding operator \citep{donoho1995noising})} \\
+%  
+%  ~$\mathbf{a}_2^{k+1}=shrink\left(\nabla_2 \mathbf{m}^{k+1}+\mathbf{b}_2^k, \frac{1}{\lambda}\right)$ \\
+%  ~$\mathbf{b}_1^{k+1}=\mathbf{b}_1^{k} + \left(\nabla_1 \mathbf{m}^{k+1}-\mathbf{a}_1^{k+1}\right)$  \\
+%  ~$\mathbf{b}_2^{k+1}=\mathbf{b}_2^{k} + \left(\nabla_2 \mathbf{m}^{k+1}-\mathbf{a}_2^{k+1}\right)$  \\
+%  end
+%\end{algorithmic}
+%\end{algorithm}
 

### 2020-10-21 odrr3d/paper.tex
2020年10月20日 星期二 23时13分33秒 CDT

@@
+\published{Geophysical Prospecting, 68, 2783-2807, (2020)}
+
 \title{Seismic signal enhancement based on the lowrank methods}
@@
 Although theoretically $N$ equals to the number of distinct dipping components, it is practically defined as a relatively large number considering data complexity, otherwise signal energy can be damaged.
-The algorithm workflow for the traditional rank-reduction method (RR) is outlined in Algorithm \ref{alg:alg1}.
+The algorithm workflow for the traditional rank-reduction method (RR) is outlined in Algorithm 1.
 $\mathcal{A}$ in the algorithm workflow denotes an averaging operator along anti-diagonals.}
@@
 According to equation \ref{eq:damp}, the threshold decreases as the residual noise becomes less dominant, i.e., the singular value becomes larger.
-The algorithm workflow for the damped rank-reduction method (DRR) is outlined in Algorithm \ref{alg:alg2}.}
+The algorithm workflow for the damped rank-reduction method (DRR) is outlined in Algorithm 2.}
 
@@
 \end{equation}
-The algorithm workflow for the optimally damped rank-reduction method (ODRR) is outlined in Algorithm \ref{alg:alg3}.
+The algorithm workflow for the optimally damped rank-reduction method (ODRR) is outlined in Algorithm 3.
 Due to the existence of a weighting matrix in the proposed method, it is more convenient to choose the input rank parameter $N$ empirically in practice.
@@
 
-\wen{
-  \begin{algorithm}
-   \caption{Seismic denoising \dlo{seismic data via}\wen{based on} rank-reduction method. }
-   \textbf{Require:} Input \dlo{seismic }data $\mathbf{D}(t,x,y)$ and predefined rank $N$.
-    \begin{algorithmic}[1]
-    \State \textbf{Fourier transform along the time axis}: $\text{FFT}\left(\mathbf{D}(t,x,y)\right)\rightarrow \mathbf{D}(\omega,x,y)$, \wen{for a frequency slice $\omega$}
-        \For{$w$ = $1,\cdots,N_{\omega}$}
-     \State \textbf{Construct block Hankel matrix}: $\mathcal{H}(\mathbf{D}(\omega))\rightarrow \mathbf{M}$
-     \State \textbf{Singular value decomposition}: $\text{SVD}(\mathbf{M},N)\rightarrow [\mathbf{U},\boldsymbol{\Sigma},\mathbf{V}]$
-     \State \textbf{Rank reduction}: $\mathbf{U}\boldsymbol{\Sigma}\mathbf{V}^T\rightarrow \hat{\mathbf{S}}$
-     \State \textbf{Averaging}: $\mathcal{A}(\hat{\mathbf{S}})\rightarrow \hat{\mathbf{D}}(\omega)$
-        \EndFor 
-         \State \textbf{Inverse Fourier transform}: $\text{IFFT}\left(\hat{\mathbf{D}}(\omega,x,y)\right)\rightarrow \hat{\mathbf{D}}(t,x,y)$
-\end{algorithmic}
-\label{alg:alg1}
-\end{algorithm}
-  \begin{algorithm}
-   \caption{Seismic denoising based on the damped rank-reduction method. }
-   \textbf{Require:} \wen{Input seismic data $\mathbf{D}(t,x,y)$, predefined rank $N$, and damping factor $K$.}
-    \begin{algorithmic}[1]
-    \State \textbf{Fourier transform along the time axis}: $\text{FFT}\left(\mathbf{D}(t,x,y)\right)\rightarrow \mathbf{D}(\omega,x,y)$, \wen{for a frequency slice $\omega$}
-        \For{$w$ = $1,\cdots,N_{\omega}$}
-     \State \textbf{Construct block Hankel matrix}: $\mathcal{H}(\mathbf{D}(\omega))\rightarrow \mathbf{M}$
-     \State \textbf{Singular value decomposition}: $\text{SVD}(\mathbf{M},N)\rightarrow [\mathbf{U},\boldsymbol{\Sigma},\mathbf{V}]$
-     \State \textbf{Rank reduction with the damping operation}: $\mathbf{U}\mathbf{P}\boldsymbol{\Sigma}\mathbf{V}^T\rightarrow \hat{\mathbf{S}}$
-     \State \textbf{Averaging}: $\mathcal{A}(\hat{\mathbf{S}})\rightarrow \hat{\mathbf{D}}(\omega)$
-        \EndFor 
-         \State \textbf{Inverse Fourier transform}: $\text{IFFT}\left(\hat{\mathbf{D}}(\omega,x,y)\right)\rightarrow \hat{\mathbf{D}}(t,x,y)$
-\end{algorithmic}
-\label{alg:alg2}
-\end{algorithm}
-  \begin{algorithm}
-   \caption{Seismic denoising based on the optimally damped rank-reduction method. }
-   \textbf{Require:} \wen{Input seismic data $\mathbf{D}(t,x,y)$, predefined rank $N$, and damping factor $K$.}
-    \begin{algorithmic}[1]
-    \State \textbf{Fourier transform along the time axis}: $\text{FFT}\left(\mathbf{D}(t,x,y)\right)\rightarrow \mathbf{D}(\omega,x,y)$, \wen{for a frequency slice $\omega$}
-        \For{$w$ = $1,\cdots,N_{\omega}$}
-     \State \textbf{Construct block Hankel matrix}: $\mathcal{H}(\mathbf{D}(\omega))\rightarrow \mathbf{M}$
-     \State \textbf{Singular value decomposition}: $\text{SVD}(\mathbf{M},N)\rightarrow [\mathbf{U},\boldsymbol{\Sigma},\mathbf{V}]$
-     \State \textbf{Rank reduction with both weighting and damping operations}: $\mathbf{U}\mathbf{P}\hat{\mathbf{W}}\boldsymbol{\Sigma}\mathbf{V}^T\rightarrow \hat{\mathbf{S}}$
-     \State \textbf{Averaging}: $\mathcal{A}(\hat{\mathbf{S}})\rightarrow \hat{\mathbf{D}}(\omega)$
-        \EndFor 
-         \State \textbf{Inverse Fourier transform}: $\text{IFFT}\left(\hat{\mathbf{D}}(\omega,x,y)\right)\rightarrow \hat{\mathbf{D}}(t,x,y)$
-\end{algorithmic}
-\label{alg:alg3}
-\end{algorithm}}
+% Algorithm is not available in Madagascar online version (please refer to the journal version)
+%\wen{
+%  \begin{algorithm}
+%   \caption{Seismic denoising \dlo{seismic data via}\wen{based on} rank-reduction method. }
+%   \textbf{Require:} Input \dlo{seismic }data $\mathbf{D}(t,x,y)$ and predefined rank $N$.
+%    \begin{algorithmic}[1]
+%    \State \textbf{Fourier transform along the time axis}: $\text{FFT}\left(\mathbf{D}(t,x,y)\right)\rightarrow \mathbf{D}(\omega,x,y)$, \wen{for a frequency slice $\omega$}
+%        \For{$w$ = $1,\cdots,N_{\omega}$}
+%     \State \textbf{Construct block Hankel matrix}: $\mathcal{H}(\mathbf{D}(\omega))\rightarrow \mathbf{M}$
+%     \State \textbf{Singular value decomposition}: $\text{SVD}(\mathbf{M},N)\rightarrow [\mathbf{U},\boldsymbol{\Sigma},\mathbf{V}]$
+%     \State \textbf{Rank reduction}: $\mathbf{U}\boldsymbol{\Sigma}\mathbf{V}^T\rightarrow \hat{\mathbf{S}}$
+%     \State \textbf{Averaging}: $\mathcal{A}(\hat{\mathbf{S}})\rightarrow \hat{\mathbf{D}}(\omega)$
+%        \EndFor 
+%         \State \textbf{Inverse Fourier transform}: $\text{IFFT}\left(\hat{\mathbf{D}}(\omega,x,y)\right)\rightarrow \hat{\mathbf{D}}(t,x,y)$
+%\end{algorithmic}
+%\label{alg:alg1}
+%\end{algorithm}
+%  \begin{algorithm}
+%   \caption{Seismic denoising based on the damped rank-reduction method. }
+%   \textbf{Require:} \wen{Input seismic data $\mathbf{D}(t,x,y)$, predefined rank $N$, and damping factor $K$.}
+%    \begin{algorithmic}[1]
+%    \State \textbf{Fourier transform along the time axis}: $\text{FFT}\left(\mathbf{D}(t,x,y)\right)\rightarrow \mathbf{D}(\omega,x,y)$, \wen{for a frequency slice $\omega$}
+%        \For{$w$ = $1,\cdots,N_{\omega}$}
+%     \State \textbf{Construct block Hankel matrix}: $\mathcal{H}(\mathbf{D}(\omega))\rightarrow \mathbf{M}$
+%     \State \textbf{Singular value decomposition}: $\text{SVD}(\mathbf{M},N)\rightarrow [\mathbf{U},\boldsymbol{\Sigma},\mathbf{V}]$
+%     \State \textbf{Rank reduction with the damping operation}: $\mathbf{U}\mathbf{P}\boldsymbol{\Sigma}\mathbf{V}^T\rightarrow \hat{\mathbf{S}}$
+%     \State \textbf{Averaging}: $\mathcal{A}(\hat{\mathbf{S}})\rightarrow \hat{\mathbf{D}}(\omega)$
+%        \EndFor 
+%         \State \textbf{Inverse Fourier transform}: $\text{IFFT}\left(\hat{\mathbf{D}}(\omega,x,y)\right)\rightarrow \hat{\mathbf{D}}(t,x,y)$
+%\end{algorithmic}
+%\label{alg:alg2}
+%\end{algorithm}
+%  \begin{algorithm}
+%   \caption{Seismic denoising based on the optimally damped rank-reduction method. }
+%   \textbf{Require:} \wen{Input seismic data $\mathbf{D}(t,x,y)$, predefined rank $N$, and damping factor $K$.}
+%    \begin{algorithmic}[1]
+%    \State \textbf{Fourier transform along the time axis}: $\text{FFT}\left(\mathbf{D}(t,x,y)\right)\rightarrow \mathbf{D}(\omega,x,y)$, \wen{for a frequency slice $\omega$}
+%        \For{$w$ = $1,\cdots,N_{\omega}$}
+%     \State \textbf{Construct block Hankel matrix}: $\mathcal{H}(\mathbf{D}(\omega))\rightarrow \mathbf{M}$
+%     \State \textbf{Singular value decomposition}: $\text{SVD}(\mathbf{M},N)\rightarrow [\mathbf{U},\boldsymbol{\Sigma},\mathbf{V}]$
+%     \State \textbf{Rank reduction with both weighting and damping operations}: $\mathbf{U}\mathbf{P}\hat{\mathbf{W}}\boldsymbol{\Sigma}\mathbf{V}^T\rightarrow \hat{\mathbf{S}}$
+%     \State \textbf{Averaging}: $\mathcal{A}(\hat{\mathbf{S}})\rightarrow \hat{\mathbf{D}}(\omega)$
+%        \EndFor 
+%         \State \textbf{Inverse Fourier transform}: $\text{IFFT}\left(\hat{\mathbf{D}}(\omega,x,y)\right)\rightarrow \hat{\mathbf{D}}(t,x,y)$
+%\end{algorithmic}
+%\label{alg:alg3}
+%\end{algorithm}}
 

### 2020-10-21 odrr3d/matfun/yc_optshrink.m

@@ -14,7 +14,7 @@ function [dout] = yc_optshrink(din,N)
 % test_odrr_denoise.m
 %
 % REFERENCE
-% Bai et al., 2020, Seismic signal enhancement based on the lowrank methods, Geophysical Prospecting.
+% Bai et al., 2020, Seismic signal enhancement based on the lowrank methods, Geophysical Prospecting, 68, 2783-2807.
 % Chen et al., 2020, Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method, Geophysical Journal International, 222, 1824-1845.
 % Nadakuditi, R. R., 2013, Optshrink: An algorithm for improved low-rank signal matrix denoising by optimal, data-driven singular value shrinkage: IEEE Transactions on Information Theory, 60, 3002?3018.
 % 

### 2020-10-21 odrr3d/matfun/yc_optshrink_damp.m

@@ -14,13 +14,14 @@ function [dout] = yc_optshrink_damp(din,N,K)
 % test_odrr_denoise.m
 %
 % REFERENCE
-% Bai et al., 2020, Seismic signal enhancement based on the lowrank methods, Geophysical Prospecting.
+%  Bai et al., 2020, Seismic signal enhancement based on the lowrank methods, Geophysical Prospecting, 68, 2783-2807.
 % Chen et al., 2020, Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method, Geophysical Journal International, 222, 1824-1845.
 % Nadakuditi, R. R., 2013, Optshrink: An algorithm for improved low-rank signal matrix denoising by optimal, data-driven singular value shrinkage: IEEE Transactions on Information Theory, 60, 3002?3018.
 % Huang, W., R. Wang, Y. Chen, H. Li, and S. Gan, 2016, Damped multichannel singular spectrum analysis for 3D random noise attenuation, Geophysics, 81, V261-V270.
 % Chen, Y., W. Huang, D. Zhang, W. Chen, 2016, An open-source matlab code package for improved rank-reduction 3D seismic data denoising and reconstruction, Computers & Geosciences, 95, 59-66.
 % Chen, Y., D. Zhang, Z. Jin, X. Chen, S. Zu, W. Huang, and S. Gan, 2016, Simultaneous denoising and reconstruction of 5D seismic data via damped rank-reduction method, Geophysical Journal International, 206, 1695-1717.
-
+% Chen et al., 2017, Preserving the discontinuities in least-squares reverse time migration of simultaneous-source data, Geophysics, 82, S185-S196.
+% Chen et al., 2019, Obtaining free USArray data by multi-dimensional seismic reconstruction, Nature Communications, 10:4434.
 
 [n1,n2]=size(din);
 [U,S,V]=svd(din);

### 2020-10-27 drr5d/paper.tex
2020年10月27日 星期二 15时05分00秒 CDT

\title{Simultaneous denoising and reconstruction of 5D seismic data via damped rank-reduction method}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Yangkang Chen\footnotemark[1], Dong Zhang\footnotemark[2], Zhaoyu Jin\footnotemark[3], Xiaohong Chen\footnotemark[2], Shaohuan Zu\footnotemark[2], Weilin Huang\footnotemark[2] , and Shuwei Gan\footnotemark[2]}
\address{
\footnotemark[1]Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
Email: ykchen@utexas.edu \\
\footnotemark[2] State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
zhangdongconan@163.com\&chenxh@cup.edu.cn \& shaohuanzu@gmail.com \&  cup\_hwl@126.com\&gsw19900128@126.com  \\ 
\footnotemark[3]School of Geosciences \\
University of Edinburgh \\
Edinburgh,UK, EH9 3JW \\
s1263999@sms.ed.ac.uk
}

\lefthead{GJI - Chen et al.}
\righthead{5D interpolation}

\maketitle

\begin{abstract}
The Cadzow rank-reduction method can be effectively utilized in simultaneously denoising and reconstructing 5D seismic data that depends on four spatial dimensions. The classic version of Cadzow rank-reduction method arranges the 4D spatial data into a level-four block Hankel/Toeplitz matrix and then applies truncated singular value decomposition (TSVD) for rank-reduction. When the observed data is extremely noisy, which is often the feature of real seismic data, traditional TSVD cannot be adequate for attenuating the noise and reconstructing the signals. The reconstructed data tends to contain a significant amount of residual noise using the traditional TSVD method, which can be explained by the fact that the reconstructed data space is a mixture of both signal subspace and noise subspace. In order to better decompose the block Hankel matrix into signal and noise  components, we introduce\new{d} a damping operator into the traditional TSVD formula, which we call the damped rank-reduction method. The damped rank-reduction method  can obtain a perfect reconstruction performance even when the observed data has extremely low signal-to-noise ratio (SNR).  %The improvement is achieved by introducing a damping factor into the traditional rank-reduction formula following the recent research advances on damped multichannel singular spectrum analysis (MSSA). 
The feasibility of the improved 5D seismic data reconstruction method \old{is}\new{was} validated via both 5D synthetic and field data examples. We present\new{ed} comprehensive analysis of the data examples and obtain\new{ed} valuable experience and guidelines in better utilizing the proposed method in practice. Since the proposed method is convenient to implement and can achieve immediate improvement, we suggest its wide application in the industry. 
\end{abstract}

\section{Keywords}
5D seismic data, denoising, data reconstruction, rank-reduction method

\section{Introduction}
Field obstacles and economic costs in seismic acquisition often result in irregular and incomplete seismic field data \cite[]{chiu2014}. Seismic interpolation is such a processing step to provide the regularly sampled seismic data for the following workflows like high-resolution processing, wave-equation migration, multiple suppression, amplitude-versus-offset (AVO) or amplitude-versus-azimuth (AVAZ) analysis, and time-lapse studies, thus plays a fundamental role in seismic data processing \cite[]{porsani1999,abma2005,abma2006,juefu2010,chengbo2012,yangkang2015shape,shuwei20164,shuwei20153}.

During the past several decades of continuous research from both academia and industry, there have been many effective methods for seismic data interpolation. In prediction based approaches, a prediction error filter is designed such that the predicted data and the existing data has the minimum misfit by solving a least-squares linear inverse problem \cite[]{spitz1991,fomel2002pwd}. Considering that the irregularly sampled seismic data with large number of missing traces usually suffers from the aliasing problem, the prediction error filter is obtained by solving the inverse problem from low-frequency data that is less aliasing and then applied to high-frequency components \cite[]{mostafa2007}. The sparse transform based interpolation assumes that the seismic data is sparse in a certain transformed domain. By iteratively thresholding the transformed domain of the incomplete seismic data, one can gradually attenuate the artifacts in the sparse domain that are caused by the missing traces in the time-space domain, and then gradually recover the missing information \cite[]{yangkang2014halfthr,shuwei2015seg,shuwei20153,benfengpocs,benfeng2015}. An important component in this type of methods is the sparse transform. Generally speaking, sparse transforms can be divided into two categories \cite[]{yangkang2016dsd}: analytical transforms, which have fixed basis, and learning-based dictionaries, which iteratively update the basis. A number of fixed basis sparse transforms have been proposed in the literature for restoring seismic data, which include Fourier transform \cite[]{sacchi,duijndam,yangkang2014halfthr}, Radon transform \cite[]{trad,yu,wangradon}, curvelet transform \cite[]{herrmann,shahidi,liuwei2015,liuwei20162} and seislet transform \cite[]{fomel2010seislet,yangkang20142,shuwei20153}. The learning-based approach usually utilizes machine learning techniques to construct the dictionary. Another group of methods is based on wave equation. The wave equation theory inherently connects the seismic trace recorded at a specific location from a known shot position to all the other traces assuming the subsurface velocity model is known. Thus, it depends on a prior information that is usually difficult to obtain and it is also limited by the large computational cost aroused from solving the wave equation \cite[]{ronen,canning1996,fomel2003}.

Recently, rank-reduction based seismic interpolation algorithms become popular \cite[]{trickett2009,mssa,jianjun2015}.  The rank-reduction methods for seismic data reconstruction can be divided into two main categories. The first category applies rank-reduction to multilevel block Hankel/Toeplitz matrices formed from the entries of the tensor. In other words, multidimensional seismic data is rearranged into a block Hankel or Toeplitz matrix, and a rank-reduction algorithm is used to improve the signal-to-noise ratio (SNR) and to reconstruct the data. Such algorithm is usually named as the Cadzow method \cite[]{trickett2009} or multichannel singular spectrum analysis (MSSA) method \cite[]{mssa,weilin2015,weilin}. The other category of rank-reduction methods encompasses techniques that are based on dimensionality reduction of multi-linear arrays or tensors. In this case, the multichannel seismic data is viewed as a multi-linear array, and dimensionality reduction techniques are directly applied to the multi-linear array \cite[]{jianjun2015}. Simply speaking, rank-reduction methods are based on the fact that missing traces and random noise will increase the rank of a matrix or tensor. By applying a rank-reduction step, such as truncated singular value decomposition (TSVD), we can intuitively reduce the negative effects caused by the missing traces and random noise. It is worth noting that rank-reduction or low-rank matrix recovery is closely related to sparse transform and compressed sensing (CS) theory because of their utilization of low-dimensional signal structures \cite[]{recht,power,Yaniv}. Specifically, \cite{recht} discussed the bridge between CS and low-rank matrix recovery. \new{Considering that the multi-dimensional seismic data usually contains significant amount of random noise. A lof of efforts have been put in the area of simultaneous interpolation and denoising of seismic data. \cite{mssa} introduced a POCS-like iteration into the MSSA algorithm with a variable "alpha" to weight the addition of original data with estimated signal. While this method is effective in attenuating noise while interpolating seismic records, the mathematical relationship between "alpha" and the SNR was not properly understood.  Following \cite{mssa}, the weighting strategy was also adopted by \cite{kreimer2012}.  Recently the connection between parameter "alpha" and a trade-off parameter "mu" was made in \cite{jianjun2015}. \cite{sternfels2015} solved the simultaneous interpolation and denoising problem via convex optimization, where the problem was formulated as a regularized inverse problem with a sparsity promotion term and solved using the alternating direction method of multipliers (ADMM) algorithm.}

In recent years, 5D seismic interpolation has become popular since it takes all physical dimensions of seismic data into consideration for the interpolation, which brings us a stronger constraint when inverting a highly underdetermined inverse problem and thus helps us obtain a much improved reconstruction performance in the case of high missing-traces ratio compared with 2D and 3D interpolation \cite[]{liubin2004,kreimer2013,chiu2014,jianjun2015}.
The rank-reduction based seismic interpolation has been shown to be an effective method for 5D seismic data interpolation \cite[]{jianjun2015}. Our recent study shows that when the observed data is extremely noisy, which is often the feature of real seismic data, the reconstructed data using the rank-reduction based algorithm still contains significant residual noise. The residual noise is caused from the fact that the rank-reduced signal space via TSVD is a mixture of signal and noise subspace.  We propose an effective method for improving the traditional Cadzow rank-reduction method by modifying the TSVD formula. In order to better decompose the noisy data space into signal and noise subspace, we propose to apply a damping operator to the block Hankel matrix after TSVD.  The damping operator is controlled by adjusting an introduced parameter called damping factor. In the special case, when the damping factor is sufficiently large, the improved rank-reduction method reverts the traditional Cadzow rank-reduction method. The proposed method is compared with the traditional method via both synthetic and field  5D seismic dataset and is demonstrated to obtain much better performance.

\section{Theory}
\subsection{Block Hankel matrix formulation for 5D seismic data}
Consider a block of 5D data $\mathbf{D}_{time}(t,hx,hy,x,y)(t=1\cdots N_t)$, where $hx$, $hy$, $x$, $y$ denote $x$ and $y$ offsets and $x$ and $y$ midpoints. The rank-reduction method operates on the 5D seismic data in the following way: first, rank-reduction method transforms $\mathbf{D}_{time}(t,hx,hy,x,y)$ into $\mathbf{D}_{freq}(w,hx,hy,x,y)(w=1\cdots N_w)$ of complex values in the frequency domain. In the condition that the spatial variables are regularly sampled, each observation at a given frequency slice can be represented via a 4D spatial hypercube $\mathbf{D}_{k1,k2,k3,k4}$ with $k_i=1\cdots X_i$, $i=1,2,3,4$. In order to make our target matrices close to square matrices, parameters $Y_i$ are defined as $\lfloor \frac{X_i}{2} \rfloor +1$, $i=1,2,3,4$. \new{\cite{jianjun20152} outlined the usefulness of square Hankel matrices in rank reduction based regularization and described why square matrices are preferred.} The symbol $\lfloor\cdot\rfloor$ denotes the integer part of its argument. %As we have already known, SSA transforms the 1D time series into a level-one Hankel matrix while MSSA transforms the 2D frequency slice of a 3D seismic dataset into a level-two block Hankel matrix \cite[]{oropezamssa}.
The 4D spatial hypercube $\mathbf{D}_{k1,k2,k3,k4}$ can be embedded in a level-four block Hankel matrix as follows. We have to address in advance that each frequency slice of data is operated the exactly same way. We first embed the seismic data in a level-one Hankel matrix using all data components in the first dimension of the tensor $\mathbf{D}_{k1,k2,k3,k4}$ at a given frequency $w_0$. This generates the following Hankel matrices,
\begin{equation}
\label{eq:levelone}
\mathbf{M}_{k2,k3,k4}^{(1)}=\left(\begin{array}{cccc}
D_{1,k2,k3,k4} & D_{2,k2,k3,k4} & \cdots &D_{X_1-Y_1+1,k2,k3,k4} \\
D_{2,k2,k3,k4} & D_{3,k2,k3,k4}  &\cdots &D_{X_1-Y_1+2,k2,k3,k4} \\
\vdots & \vdots &\ddots &\vdots \\
D_{Y_1,k2,k3,k4}&D_{Y_1+1,k2,k3,k4} &\cdots&D_{X_1,k2,k3,k4}
\end{array}
\right).
\end{equation}

Matrices in Equation \ref{eq:levelone} are of size $Y_1 \times (X_1-Y_1+1)$. These matrices are embedded in a level-two block Hankel matrix:
\begin{equation}
\label{eq:leveltwo}
\mathbf{M}_{k3,k4}^{(2)}=\left(\begin{array}{cccc}
M_{1,k3,k4}^{(1)} & M_{2,k3,k4}^{(1)} & \cdots &M_{X_2-Y_2+1,k3,k4}^{(1)} \\
M_{2,k3,k4}^{(1)} & M_{3,k3,k4}^{(1)}  &\cdots &M_{X_2-Y_2+2,k3,k4}^{(1)} \\
\vdots & \vdots &\ddots &\vdots \\
M_{Y_2,k3,k4}^{(1)}&M_{Y_2+1,k3,k4}^{(1)} &\cdots&M_{X_2,k3,k4}^{(1)}
\end{array}
\right).
\end{equation}

Matrices in Equation \ref{eq:leveltwo} are of size $(Y_1 Y_2) \times (X_1-Y_1+1)(X_2-Y_2+1)$. These matrices are now embedded in a level-three block Hankel matrix:
\begin{equation}
\label{eq:levelthree}
\mathbf{M}_{k4}^{(3)}=\left(\begin{array}{cccc}
M_{1,k4}^{(2)} & M_{2,k4}^{(2)} & \cdots &M_{X_3-Y_3+1,k4}^{(2)} \\
M_{2,k4}^{(2)} & M_{3,k4}^{(2)}  &\cdots &M_{X_3-Y_3+2,k4}^{(2)} \\
\vdots & \vdots &\ddots &\vdots \\
M_{Y_3,k4}^{(2)}&M_{Y_3+1,k4}^{(2)} &\cdots&M_{X_3,k4}^{(2)}
\end{array}
\right).
\end{equation}

Matrices in Equation \ref{eq:levelthree} are of size $(Y_1 Y_2 Y_3) \times (X_1-Y_1+1)(X_2-Y_2+1)(X_3-Y_3+1)$. At last, these matrices are embedded in our final target level-four block Hankel matrix:
\begin{equation}
\label{eq:levelfour}
\mathbf{M}^{(4)}=\left(\begin{array}{cccc}
M_{1}^{(3)} & M_{2}^{(3)} & \cdots &M_{X_4-Y_4+1}^{(3)} \\
M_{2}^{(3)} & M_{3}^{(3)}  &\cdots &M_{X_4-Y_4+2}^{(3)} \\
\vdots & \vdots &\ddots &\vdots \\
M_{Y_4}^{(3)}&M_{Y_4+1}^{(3)} &\cdots&M_{X_4}^{(3)}
\end{array}
\right).
\end{equation}

Equation \ref{eq:levelfour} is the target matrix of our problem. The size of level-four block Hankel matrix $\mathbf{M}^{(4)}$ is $(Y_1 Y_2 Y_3 Y_4) \times (X_1-Y_1+1)(X_2-Y_2+1)(X_3-Y_3+1)(X_4-Y_4+1)$. If $X_i$ is an odd integer, the size of $\mathbf{M}^{(4)}$ is $(Y_1 Y_2 Y_3 Y_4) \times(Y_1 Y_2 Y_3 Y_4) $.

\subsection{Rank-reduction method for 5D seismic data restoration}
The transformation of the 4D data hypercube at a single frequency into a level-four block Hankel matrix can be represented in operator notation as follows:
\begin{equation}
\label{eq:hankelopt}
\mathbf{M}^{(4)}=\mathcal{H}\mathbf{D},
\end{equation}
where $\mathcal{H}$ denotes the Hankelization operator.  To avoid notational clutter, we omit the argument $k1,k2,k3,k4$ of $\mathbf{D}_{k1,k2,k3,k4}$ for convenience. In general, the level-four block Hankel matrix $\mathbf{M}^{(4)}$ can be represented as:
\begin{equation}
\label{eq:M}
\mathbf{M}^{(4)}=\mathbf{S}+\mathbf{N},
\end{equation}
where $\mathbf{S}$ and $\mathbf{N}$ denote the level-four block Hankel matrices of signal and random noise, respectively. Here, missing signal can be regarded as  a condition where signal and noise are summed to zero, and is distributed randomly due to the irregular sampling. Therefore, missing data represents itself by the noise-like characteristics.

We assume that $\mathbf{M}^{(4)}$ and $\mathbf{N}$ have full rank. The size of $\mathbf{M}^{(4)}$ is $I\times J,\quad J<I$. $rank(\mathbf{M}^{(4)})$=$rank(\mathbf{N})=J$, $I=Y_1 Y_2 Y_3 Y_4$, $J=(X_1-Y_1+1)(X_2-Y_2+1)(X_3-Y_3+1)(X_4-Y_4+1)$, and $\mathbf{S}$ has deficient rank, $rank(\mathbf{S})=K<J$. The singular value decomposition (SVD) of $\mathbf{M}^{(4)}$ can be represented as:
\begin{equation}
\label{eq:svdm}
\mathbf{M}^{(4)} = [\mathbf{U}_1^{M^{(4)}}\quad \mathbf{U}_2^{M^{(4)}}]\left[\begin{array}{cc}
\Sigma_1^{M^{(4)}} & \mathbf{0}\\
\mathbf{0} & \Sigma_2^{M^{(4)}}
\end{array}
\right]\left[\begin{array}{c}
(\mathbf{V}_1^{M^{(4)}})^H\\
(\mathbf{V}_2^{M^{(4)}})^H
\end{array}
\right],
\end{equation}
where $\Sigma_1^{M^{(4)}}$ ($K\times K$) and $\Sigma_2^{M^{(4)}}$ ($(I-K)\times(J-K)$) are diagonal matrices and contain, respectively, larger singular values and smaller singular values. $\mathbf{U}_1^{M^{(4)}}$ ($I\times K$), $\mathbf{U}_2^{M^{(4)}}$ ($I\times (I-K)$), $\mathbf{V}_1^{M^{(4)}}$ ($J\times K$) and $\mathbf{V}_2^{M^{(4)}}$ ($J\times (J-K)$) denote the associated matrices with singular vectors. The symbol $[\cdot]^H$ denotes the conjugate transpose of a matrix. Generally, the signal is more energy-concentrated and correlative than the random noise. Thus, the larger singular values and their associated singular vectors represent the signal, while the smaller values and their associated singular vectors represent the random noise. We substitute $\Sigma_2^{M^{(4)}}$ with $\mathbf{0}$ to achieve the goal of attenuating random noise while recovering the missing data during the first iteration in reconstruction process as follows:
\begin{equation}
\label{eq:tsvd}
\tilde{\mathbf{M}}^{(4)} = \mathbf{U}_1^{M^{(4)}}\Sigma_1^{M^{(4)}}(\mathbf{V}_1^{M^{(4)}})^H.
\end{equation}
Equation \ref{eq:tsvd} is referred to as the TSVD, which is used in the conventional rank-reduction approach for 5D seismic data interpolation.

Nevertheless, $\tilde{\mathbf{M}}^{(4)}$ is actually still contaminated  with residual random noise. Following \cite{weilin}, here we briefly clarify the reason why the $\tilde{\mathbf{M}}^{(4)}$ is still corrupted with some residual random noise. We first consider the SVD of the signal component $\mathbf{S}$ in a way similar to equation \ref{eq:svdm}: 
\begin{equation}
\label{eq:svds}
\mathbf{S} = [\mathbf{U}_1^{S}\quad \mathbf{U}_2^{S}]\left[\begin{array}{cc}
\Sigma_1^{S} & \mathbf{0}\\
\mathbf{0} & \Sigma_2^{S}
\end{array}
\right]\left[\begin{array}{c}
(\mathbf{V}_1^{S})^H\\
(\mathbf{V}_2^{S})^H
\end{array}
\right].
\end{equation}
Different from $\tilde{\mathbf{M}}^{(4)}$, the signal matrix should be of deficient rank, then $\Sigma_2^S$ is a zero diagonal matrix, and $\mathbf{S}$ can be denoted in a concise form:
\begin{equation}
\label{eq:signal}
\mathbf{S}=\mathbf{U}_1^S\Sigma_1^S(\mathbf{V}_1^S)^H.
\end{equation}
Combining equations \ref{eq:M}, \ref{eq:svds}, and \ref{eq:signal}, it straightforwardly derive the following equation:
\begin{equation}
\label{eq:contra}
\tilde{\mathbf{M}}^{(4)} = \mathbf{S} + \mathbf{U}_1^S(\mathbf{U}_1^S)^H\mathbf{N}.
\end{equation}
The appendix A gives a detailed derivation for obtaining equation \ref{eq:contra}, which we call exact formulation of the block Hankel matrix. From equation \ref{eq:contra}, we can intuitively know that TSVD result $\tilde{\mathbf{M}}^{(4)}$ still contains significant random noise $\mathbf{U}_1^S(\mathbf{U}_1^S)^H\mathbf{N}$, or in other words, the traditional TSVD can only decompose the data space into a mixture of signal and noise subspace.

\subsection{Damped rank-reduction method for 5D seismic data restoration}
\cite{weilin} introduced a damping factor into TSVD to effectively attenuate the residual random noise for 3D dataset. Here, we further extend this damped algorithm to rank-reduction method for 5D seismic data interpolation in the presence of random noise. Since the missing data at each frequency slice can be regarded as the random noise, the derivation is similar to \cite{weilin} except for the extra reconstruction process based on the weighted projection onto convex set (POCS) like method in a level-four block Hankel matrix. Appendix B
gives a detailed introduction on how to derive a damped TSVD in order to reduce the residual noise
existing in the rank-reduced matrix $\tilde{\mathbf{M}}^{(4)}$ . Here, we just conclude the approximation of $\mathbf{S}$ as follows:
\begin{align}
\label{eq:S4_m}
\mathbf{S} & = \mathbf{U}_1^{M^{(4)}} \Sigma_1^{M^{(4)}}\mathbf{T}(\mathbf{V}_1^{M^{(4)}})^H,\\
\label{eq:T2_m}
\mathbf{T} & =\mathbf{I}-(\Sigma_1^{M^{(4)}})^{-N}\hat{\delta}^N,
\end{align}
where $\hat{\delta}$ denotes the maximum element of $\Sigma_2^{M^{(4)}}$ and $N$ denotes the damping factor. It is worth mentioning that the greater the $N$, the weaker the damping is, and equation \ref{eq:S4_m} degrades to equation \ref{eq:tsvd} when $N\rightarrow +\infty$.

The damped TSVD of rank-reduction algorithm for 5D seismic data interpolation can be represented in operator notation as follows:
\begin{equation}
\label{eq:rankrdopt}
\mathbf{S}=\mathcal{R}_d\mathbf{M}^{(4)}.
\end{equation}
where we use $\mathcal{R}_d$ as the rank-reduction operator using the damped TSVD (equations \ref{eq:S4_m} and \ref{eq:T2_m}) while $\mathcal{R}$ is used for conventional TSVD. According to our experience, the damped TSVD is powerful for attenuating random noise while interpolating missing data. However, it is still SVD-based algorithm that takes the largest portion of computational time. The randomized singular value decomposition (RSVD) strategy \cite[]{rokhlin,halko11,mssa} can be used to accelerate the proposed method for better efficiency. Specifically according to our numerical tests, RSVD can save at least 45\% computational cost compared with the classic TSVD, and cost saving is different with data dimensions, the bigger the dimension is, the faster the RSVD is. Thus RSVD can increase the efficiency significantly.

The filtered data is recovered with random noise attenuated and missing traces reconstructed by properly averaging along the anti-diagonals of the low-rank matrix $\mathbf{S}$ obtained via the damped TSVD:\\
\begin{equation}
\label{eq:dmssaopt}
\hat{\mathbf{D}}=\mathcal{A}\mathbf{S}=\mathcal{A}\mathcal{R}_d\mathbf{M}^{(4)}=\mathcal{A}\mathcal{R}_d\mathcal{H}\mathbf{D}=\mathcal{F}_d\mathbf{D}.
\end{equation}
$\mathcal{A}$ denotes the averaging operator. The operator $\mathcal{F}_d$ represents improved rank-reduction filter. If $\mathcal{R}_d$ is substituted by the traditional TSVD operator $\mathcal{R}$, $\mathcal{F}$ can represent conventional rank-reduction filter similarly.

In this paper, we pay our attention to the reconstruction of noisy data. Our final goal is to recover the useful signal from the observed noisy and incomplete data. It is worth mentioning that this type of problem often arises in the field of collaborative filtering ($\mathbf{CF}$). Similarly to those arising in the field of $\mathbf{CF}$, seismic data reconstruction can be interpreted as a matrix completion problem. Missing traces in seismic data will introduce missing value in the observed data $\mathbf{D}_{k1,k2,k3,k4}$. The corresponding level-four block Hankel matrix $\mathbf{M}^{(4)}$ is expected to have rank $K$. Random noise and missing data will increase the rank of $\mathbf{M}^{(4)}$. Consequently, rank-reduction via the damped TSVD with the damping factor can be implemented to recover the useful signal and to reconstruct the missing records for 5D seismic volumes.

The modified weighted \old{POCS like}\new{POCS-like} algorithm based on conventional rank-reduction method for 5D seismic data interpolation can be shown as
$\mathbf{D}_n=a_n \mathbf{D}_{obs} + (1-a_n\mathcal{S})\circ \mathcal{F}\mathbf{D}_{n-1},\quad n=1,2,3,\cdots,n_{max}$.
Revised by the improved rank-reduction filter $\mathcal{F}_d$, therefore our proposed improved rank-reduction algorithm for simultaneous 5D seismic data reconstruction and denoising can be formulated as follows:
\begin{equation}
\label{eq:dmssapocs}
\mathbf{D}_n=a_n \mathbf{D}_{obs} + (1-a_n\mathcal{S})\circ \mathcal{F}_d\mathbf{D}_{n-1},\qquad n=1,2,3,\cdots,n_{max}
\end{equation}
where $\mathbf{D}_0=\mathbf{D}_{obs}$. $a_n$ is an iteration-dependent scalar that linearly decreases from $a_1=1$ to $a_{n_{max}}=0$. $\mathcal{S}$ denotes the sampling factor. $\mathcal{S}$ equals 1 at the observation point while 0 at the missing traces. Symbol $\circ$ denotes the Hadamard product (entry-wise product) of two matrices with the same size.

A complete and detailed algorithm workflow of the proposed damped rank-reduction algorithm for 5D seismic data reconstruction and denoising is provided as follows: %We adopt the following algorithm for reconstructing 5D noisy seismic data with missing traces:
\begin{algorithm}{Improved 5D seismic data rank-reduction algorithm}{\mathcal{S},\mathcal{F}_d,\mathbf{D}_{obs},a_n,\epsilon,n_{max},F}
  \mathbf{D}_{obs}(f,hx,hy,x,y) \= \mathbf{D}_{obs}(t,hx,hy,x,y) \text{by 1D forward FFT} \\
  \mathbf{D}_0 \= \mathbf{D}_{obs} \\
  \begin{FOR}{f \= 1, 2, \ldots, F} \\	
      \begin{FOR}{n \= 1, 2, \ldots, n_{max}} \\
          \mathbf{D}_n^f \= a_n \mathbf{D}_{obs}^f + (1-a_n) \mathcal{S} \mathcal{F}_d \mathbf{D}_{n-1}^f + (1-\mathcal{S}) \mathcal{F}_d \mathbf{D}_{n-1}^f\\
      \begin{IF}{\Arrowvert \mathbf{D}_n^f - \mathbf{D}_{n-1}^f \Arrowvert_F^2 \leq \epsilon} 
      \RETURN \mathbf{D}_n^f
      \end{IF}     
      \end{FOR} \\
      \RETURN \mathbf{D}_N^f
   \end{FOR}\\ 
  \RETURN \mathbf{D}_{recoverd}\\
  \mathbf{D}_{recoverd}(t,hx,hy,x,y) \= \mathbf{D}_{recoverd}(f,hx,hy,x,y) \text{by 1D inverse FFT}
\end{algorithm}
The iteration terminates after all $F$ frequencies are finished. For each frequency slice, the algorithm stops when either a maximum number of iterations $n_{max}$ is reached or $\Arrowvert \mathbf{D}_n - \mathbf{D}_{n-1}\Arrowvert_F^2 \leq \epsilon$, where $\parallel \cdot \parallel_F$ denotes the Frobenius norm and $\epsilon$ denotes a small tolerance value.%the iteration terminates after $n_{max}$ iterations or upon reaching convergence to the specified tolerance $tol$.

\section{Examples}
We apply the proposed improved rank-reduction method on a 5D synthetic seismic dataset, as shown in Figures \ref{fig:synth-clean-xy,synth-noisy-xy,synth-obs-xy,synth-rr-xy,synth-irr-xy} and \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-irr-hxhy}. Figure \ref{fig:synth-clean-xy,synth-noisy-xy,synth-obs-xy,synth-rr-xy,synth-irr-xy} shows the performance in one common offset gather ($hx=5,hy=5$) and Figure \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-irr-hxhy} shows the performance in one common midpoint gather ($x=5,y=5$). Figures \ref{fig:synth-clean-xy} and \ref{fig:synth-clean-hxhy} show the true data. Figures \ref{fig:synth-noisy-xy} and \ref{fig:synth-noisy-hxhy} show the noisy data by adding some bandlimited noise to the clean data. The noise is so strong that the useful signals can be hardly detected. Figures \ref{fig:synth-obs-xy} and \ref{fig:synth-obs-hxhy} show the observed incomplete and noisy data. 70\% of total traces are missing in this example. The signal-to-noise ratio (SNR) of the observed data is exetremely low and we can hardly see any coherent useful events in the observed data. Figures \ref{fig:synth-rr-xy} and \ref{fig:synth-rr-hxhy} show the reconstructed data using traditional method, which is quite acceptable since almost all useful signals are recovered and the noise has been greatly suppressed. However, there is still some residual noise in the reconstructed data, which can be explained by the non-optimal decomposition via traditional TSVD as analyzed in the theoretic section. Figures \ref{fig:synth-irr-xy} and \ref{fig:synth-irr-hxhy} show the reconstructed data using the proposed method. In this example, the rank $K=3$ and the damping factor $N=3$, and we use 10 weighted \old{POCS like}\new{POCS-like} iterations. It is obvious that the proposed method obtains a much cleaner result, and to some extent, the recovery of the useful signals are nearly perfect.  Figure \ref{fig:synth-rr-xy-e,synth-irr-xy-e} shows two reconstruction error cubes in common offset domain (the difference between the true data and the recovered data) using the traditional and the proposed approaches, respectively. Similarly, Figure \ref{fig:synth-rr-hxhy-e,synth-irr-hxhy-e} shows the reconstruction error cubes in common midpoint domain. Both Figures \ref{fig:synth-rr-xy-e,synth-irr-xy-e} and \ref{fig:synth-rr-hxhy-e,synth-irr-hxhy-e} clearly show that the proposed approach can obtain the least reconstruction error, while the error in the traditional approach is mainly due to the residual noise. In order to compare the amplitude between different datasets in detail, we conduct a single trace amplitude comparison for each data cubes shown in Figure \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-irr-hxhy}. The single trace is chosen as the middle trace in each cubes of Figure \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-irr-hxhy}. The comparison is presented in Figure \ref{fig:synth-ss}. The black
line is from the clean data. The red line is from the noisy data. The observed data in this case is zero and thus cannot be seen from the figure. The blue line corresponds to the traditional rank-reduction method. The green line corresponds to the proposed method. It is apparent that the green line is very close to the black line while the blue line deviates from the black line too much in most areas. This trace amplitude comparison  further confirms the superior performance of the proposed algorithm.

In order to show how the rank-reduced block Hankel matrix looks like and to more intuitively demonstrate the influence of the introduced damping operator to the target level-four block Hankel matrix in the first 5D seismic data example, we plot the 26 Hz block Hankel matrix for different  cases in Figures \ref{fig:H_clean-0,H_obs-0,H_rr10-0,H_irr10-0}, \ref{fig:H-z-clean,H-z-obs,H-z-rr10,H-z-irr10}, and \ref{fig:H_rr1-0,H_irr1-0,H-z-rr1,H-z-irr1}. Figure \ref{fig:H_clean-0} shows the 26 Hz block Hankel matrix for the clean data.  Figure \ref{fig:H_obs-0} shows the 26 Hz block Hankel matrix for the observed data, which is very different from that of the true data due to the 70\% missing traces. Figure \ref{fig:H_rr10-0} shows rank-reduced block Hankel matrix via the traditional TSVD after 10 iterations.  The rank-reduced block Hankel matrix via the damped TSVD is shown in Figure \ref{fig:H_irr10-0}. Figures \ref{fig:H_rr10-0} and \ref{fig:H_irr10-0} are both close to the true block Hankel matrix and are very similar to each other. If we look carefully or zoom in the figure a bit, we can see that the block Hankel matrix via the traditional TSVD is much rougher than the Hankel matrix via the damped TSVD. Considering that each subfigure in Figure \ref{fig:H_clean-0,H_obs-0,H_rr10-0,H_irr10-0} is a 1296$\times$625 matrix, which contains a lot of information, we zoom one block Hankel matrix, as highlighted by the black frame boxes in Figure \ref{fig:H_clean-0,H_obs-0,H_rr10-0,H_irr10-0} and make a more detailed comparison in Figure \ref{fig:H-z-clean,H-z-obs,H-z-rr10,H-z-irr10}. Figure \ref{fig:H-z-clean,H-z-obs,H-z-rr10,H-z-irr10} clearly shows that the rank-reduced block Hankel matrix via traditional TSVD still contains some artifacts, especially on the right bottom side, when compared with the true block Hankel matrix. The block Hankel matrix from the proposed approach is, however, much smoother, and closer to the true block Hankel matrix. We also show the comparison of two block Hankel matrices using rank-reduction methods after the first iteration and their zoomed matrices in Figure \ref{fig:H_rr1-0,H_irr1-0,H-z-rr1,H-z-irr1}. It can be observed that even after 1 iteration, the rank-reduced block Hankel matrix via the damped TSVD is much smoother, which indicates that more noise in each frequency slice
is suppressed. Please note that all figures in Figures \ref{fig:H_clean-0,H_obs-0,H_rr10-0,H_irr10-0}, \ref{fig:H-z-clean,H-z-obs,H-z-rr10,H-z-irr10}, and \ref{fig:H_rr1-0,H_irr1-0,H-z-rr1,H-z-irr1} use the same plotting scale. It can also be seen that the block Hankel matrix after 1 iteration is far from the true block Hankel matrix, however, during the weighted \old{POCS like}\new{POCS-like} iterations, the block Hankel matrix is gradually converging to the true block Hankel matrix.

In order to numerically compare the denoising performance, we use the commonly used SNR defined as follows to quantitatively measure the performance \cite[]{yangkang2015ortho,wencheng2015asa,shuwei2015}:
\begin{equation}
\label{eq:dsnr}
SNR=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2^2}{\Arrowvert \mathbf{s} -\hat{\mathbf{s}}\Arrowvert_2^2}.
\end{equation}
where $\mathbf{s}$ denotes the vectorized clean data and $\hat{\mathbf{s}}$ denotes the vectorized reconstructed data. In this example, the SNRs of the observed data, the reconstructed result via the traditional rank-reduction method, and the reconstructed result via the damped rank-reduction method are -4.59 dB, 8.22 dB, and 11.62dB, respectively. The SNR comparison shows that the damped rank-reduction can result in a huge reconstruction improvement.  In addition to SNR comparison, we also use the local similarity to measure the reconstruction performance. As claimed in \cite{yangkang2015ortho}, reconstruction performance via local similarity has several advantages than the commonly used SNR measure, such as the local measurement of the reconstruction performance. Since the local similarity is seldom used in evaluating seismic data reconstruction, we provide a brief review of the theory of local similarity in Appendix C. The range of local similarity is between 0 and 1.  The higher local similarity corresponds to the better reconstruction performance. Figure \ref{fig:synth-noisy-xy-simi,synth-obs-xy-simi,synth-rr-xy-simi,synth-irr-xy-simi} shows the local similarity comparison in common offset domain and Figure \ref{fig:synth-noisy-hxhy-simi,synth-obs-hxhy-simi,synth-rr-hxhy-simi,synth-irr-hxhy-simi} shows the local similarity comparison in common midpoint domain. Figures \ref{fig:synth-noisy-xy-simi}, \ref{fig:synth-obs-xy-simi}, \ref{fig:synth-rr-xy-simi}, and \ref{fig:synth-irr-xy-simi} show the local similarity between the true data and the noisy data, observed data, result from the traditional method, and result from the proposed method, respectively, in common offset domain. Figures \ref{fig:synth-noisy-hxhy-simi}, \ref{fig:synth-obs-hxhy-simi}, \ref{fig:synth-rr-hxhy-simi}, and \ref{fig:synth-irr-hxhy-simi} show the counterpart comparisons in common midpoint domain. Because of the strong random noise in the noisy data, the local similarity between noisy data and the true data is relatively low. It is surprising that the local similarity successfully captures the position of the useful signals, which is however not possible from the original amplitude cubes. A potential application of such byproduct in future research may be utilizing the detected useful signals from the noisy data as a prior information that can be put into the inversion framework to improve the final inversion performance. The local similarity between the observed data and the true data correlates well with the position of the available traces, since all missing traces have a zero local similarity with the true data. The local similarity between the result from traditional rank-reduction method is much higher than that of the noisy data and the similarity value is approaching 1, which is the highest possible value of local similarity. The proposed approach can make the local similarity between the result and true data even higher, as can be seen from Figures \ref{fig:synth-noisy-xy-simi,synth-obs-xy-simi,synth-rr-xy-simi,synth-irr-xy-simi} and \ref{fig:synth-noisy-hxhy-simi,synth-obs-hxhy-simi,synth-rr-hxhy-simi,synth-irr-hxhy-simi} that the similarity color that corresponds to the proposed method is redder than that of the traditional approach.

In order to demonstrate the reconstruction performance of the two rank-reduction methods with respect to noise level. We conduct 6 experiments of the 5D data reconstruction based on the first synthetic example, in which we use different noise level in different experiments. We plot the final SNRs using two different approaches after 10 iterations with respect to the noise variances in Figure \ref{fig:snr-n}. The red line shows the SNR diagram of the proposed approach and green line shows the SNR diagram of the traditional approach. The noise variance of 6 experiments are 0.05, 0,1, 0.25, 0.5, 0.75, and 1. Please note that all presented examples above are based on the noise variance 0.25. It can be intuitively inferred that noise variance above 0.25 can make the data even noisier. From Figure \ref{fig:snr-n}, it is clear that the proposed approach is always superior than the traditional approach in terms of SNR. It is more important to observe that as the noise level increases, the difference in terms of SNR of the two approaches also increases. It offers us a practical guideline that the proposed approach can be best utilized in the condition of strong noise corruption (or in other words on observed data with low SNR), which is usually the feature of most land seismic data. In order to demonstrate the reconstruction performance with respect to sampling ratio of the observed data, we did 8 experiments with different sampling ratios. The SNRs using two approaches after 10 iterations with respect to the sampling ratios are shown in Figure \ref{fig:snr-r}. Red line denotes the proposed approach and green line denotes the traditional approach. The proposed approach is always better than the traditional approach and as the sampling ratio increases (in other words we get more and more available traces), the difference between the proposed and traditional approaches increases too.

In order to test the effectiveness of the rank-reduction method on data containing curved events and to compare the performances of different methods in this case, we then use the second example to show the performance. In Figure \ref{fig:hyper-clean2d-1,hyper-obs2d-1,hyper-rr2d-1,hyper-irr2d-1}, we show a common midpoint gather comparison of the second synthetic example. Here we reshape the 3D data cube into a 2D matrix and compare the performance based on the 2D matrix. Figure \ref{fig:hyper-clean2d-1} shows the clean data. Figure \ref{fig:hyper-obs2d-1} shows the observed data with 70\% missing traces and strong random noise. The useful signals are hardly seen from the observed data. After reconstruction using the traditional rank-reduction method with 10 \old{POCS like}\new{POCS-like} iterations, we obtain the reconstructed result as shown in Figure \ref{fig:hyper-rr2d-1}. The result using the proposed approach is shown in Figure \ref{fig:hyper-irr2d-1}. The reconstruction result using the traditional method seems to have significant residual noise and even causes  artifacts in some parts of the data. The data highlighted by the green frame boxes are zoomed and shown in Figure \ref{fig:hyper-z-clean,hyper-z-obs,hyper-z-rr,hyper-z-irr}, where we can have a better view to compare the performance in detail and to see how the proposed method helps recover almost the true model.  The data highlighted by the black frame boxes are zoomed and shown in Figure \ref{fig:hyper-z1-clean,hyper-z1-obs,hyper-z1-rr,hyper-z1-irr}, where we can see the artifacts caused by the traditional approach clearly and see the almost perfect performance from the proposed approach.  We apply the proposed approach with $K=12$ and $N=3$ for this example. In this dataset, the original SNR of the observed is 0.34 dB. The SNR of the result from traditional rank-reduction approach is 13.56 dB while the SNR of the reconstruction result from the proposed damped rank-reduction method approach is 17.23 dB. In this example, we also calculate the local similarity between different datasets and the clean dataset and show them in Figure \ref{fig:hyper-obs-simi,hyper-rr-simi,hyper-irr-simi}. Figure \ref{fig:hyper-obs-simi} shows the local similarity between the observed data and the clean data. Figure \ref{fig:hyper-rr-simi} shows the local similarity between the result from traditional method and the clean data and Figure \ref{fig:hyper-irr-simi} shows the local similarity between the result from the proposed method and the clean data. The local similarity vividly demonstrates that the proposed approach can obtain the most similar result to the true model.

The next example is a field data example. The data has been binned onto a regular grid and a common offset gather of the field data is shown in Figure \ref{fig:field-obs2d-0}. Although we are only allowed to show a small portion of the field data and to give a limited discussion based on the performance, the comparison between traditional and proposed rank-reduction methods is adequate to show the superior performance of our proposed method. In the example, about 80\% traces are missing from the regular grids. It is obvious that the traditional rank-reduction method obtains a very successful recovery of the missing data, as shown in Figure \ref{fig:field-rr2d0-0}. However, there are still some residual noise in the reconstructed data, since we use a relatively large $K=15$ to account for the curved events. We apply the proposed approach with $K=15$ and $N=3$ and obtain an almost perfect reconstruction performance, as shown in Figure \ref{fig:field-irr2d-0}. The events become more coherent and the data becomes much cleaner. We zoom a part from each subfigure in Figure \ref{fig:field-obs2d-0,field-rr2d0-0,field-irr2d-0} and show the comparison in Figure \ref{fig:z-obs,z-rr,z-irr}. The zoomed data are highlighted by the red frame boxes shown in Figure \ref{fig:field-obs2d-0,field-rr2d0-0,field-irr2d-0}. The zoomed sections shown in Figure \ref{fig:z-obs,z-rr,z-irr} show a clearer comparison between the traditional and the proposed methods, and confirm that the proposed method can obtain a very clean and spatially coherent reconstruction result.

\new{The selection of rank affects the performance of the traditional rank-reduction based approaches greatly in that smaller value of rank will cause significant damages to the useful signals while larger value of rank will cause serious residual noise left in the reconstructed data. However, it is even impossible to choose an optimal value of rank to stand for the exact signals in practice.  In order to preserve as many useful signals as possible, we tend to set a relatively higher value of rank. The proposed approach relieves the dependence of the rank-reduction method on the rank selection since we can use a safe value of rank without compromising the SNR of the final reconstructed data by damping the residual noise that is caused from the increase of rank. In a nutshell, the proposed approach is less sensitive to the value of rank.}

\inputdir{synth}
\multiplot{5}{synth-clean-xy,synth-noisy-xy,synth-obs-xy,synth-rr-xy,synth-irr-xy}{width=0.29\textwidth}{Common offset 3D cubes comparison ($hx=5,hy=5$). (a) Clean synthetic data. (b) Noisy synthetic data. (c) Observed synthetic data (with 70\% missing traces). (d) Reconstructed data using the traditional approach. (e) Reconstructed data using the proposed approach. }

\multiplot{2}{synth-rr-xy-e,synth-irr-xy-e}{width=0.29\textwidth}{Reconstruction error comparison of common offset 3D cubes ($hx=5,hy=5$). (a) Reconstruction error using the traditional approach. (b) Reconstruction error using the proposed approach. }

\multiplot{5}{synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-irr-hxhy}{width=0.29\textwidth}{Common midpoint 3D cubes comparison ($x=5,y=5$). (a) Clean synthetic data. (b) Noisy synthetic data. (c) Observed synthetic data (with 70\% missing traces). (d) Reconstructed data using the traditional approach. (e) Reconstructed data using the proposed approach. }

\multiplot{2}{synth-rr-hxhy-e,synth-irr-hxhy-e}{width=0.29\textwidth}{Reconstruction error comparison of common midpoint 3D cubes ($x=5,y=5$). (a) Reconstruction error using the traditional approach. (b) Reconstruction error using the proposed approach. }

\plot{synth-ss}{width=0.9\columnwidth}{Comparison of the middle trace amplitude of each cubes in Figure \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-irr-hxhy}. The black line is from the clean data.  The red line is from the noisy data. The observed data in this case is zero and thus cannot be seen from the figure.%The yellow long-dashed line corresponds to $fl=10$ Hz. 
	The blue line corresponds to the traditional rank-reduction method. The green line corresponds to the proposed method. Note that the black and green lines are very close to each other, thus the reconstruction error using the proposed approach is much less than the traditional method for most parts.}

\inputdir{hankel}
\multiplot{4}{H_clean-0,H_obs-0,H_rr10-0,H_irr10-0}{width=0.45\textwidth}{26 Hz block Hankel matrix comparison. (a) Hankel matrix of the clean data. (b) Hankel matrix of the noisy data. (c) Hankel matrix of traditional method after 10 iterations. (d) Hankel matrix of the proposed method after 10 iterations. Please note the erratic artifacts shown in (c), which cannot be handled using the traditional rank-reduction method. The Hankel matrix of the proposed approach is, however, much closer to the true Hankel matrix.}

\multiplot{4}{H-z-clean,H-z-obs,H-z-rr10,H-z-irr10}{width=0.45\textwidth}{A close up look of the Hankel matrix (corresponding to the block Hankel matrix highlighted by the green frame box in Figure \ref{fig:H_clean-0,H_obs-0,H_rr10-0,H_irr10-0}.  (a) Hankel matrix of the clean data. (b) Hankel matrix of the noisy data. (c) Hankel matrix of traditional method after 10 iterations. (d) Hankel matrix of the proposed method after 10 iterations. }

\multiplot{4}{H_rr1-0,H_irr1-0,H-z-rr1,H-z-irr1}{width=0.45\textwidth}{26 Hz block Hankel matrix comparison after 1 iteration between two approaches. (a) Hankel matrix of traditional method after 1 iteration. (b) Hankel matrix of the proposed method after 1 iteration. (c)\&(d) A close up look of the two frame boxes in (a) and (b).  }

\inputdir{synth}
\multiplot{4}{synth-noisy-xy-simi,synth-obs-xy-simi,synth-rr-xy-simi,synth-irr-xy-simi}{width=0.32\textwidth}{Local similarity comparison of common offset 3D cubes comparison ($hx=5,hy=5$). (a) Noisy synthetic data. (b) Observed synthetic data (with 70\% missing traces). (c) Reconstructed data using the traditional approach. (d) Reconstructed data using the proposed approach. }

\multiplot{4}{synth-noisy-hxhy-simi,synth-obs-hxhy-simi,synth-rr-hxhy-simi,synth-irr-hxhy-simi}{width=0.32\textwidth}{Local similarity comparison of common midpoint 3D cubes ($x=5,y=5$). (a) Noisy synthetic data. (b) Observed synthetic data (with 70\% missing traces). (c) Reconstructed data using the traditional approach. (d) Reconstructed data using the proposed approach. }

\inputdir{snrs_sigma}
\plot{snr-n}{width=\textwidth}{SNR diagrams of the different approaches with respect to the noise level (variance value). Note that the proposed approach outperforms the traditional methods more and more as the noise level increases.}

\inputdir{snrs_ratio}
\plot{snr-r}{width=\textwidth}{SNR diagrams of the different approaches with respect to the sampling ratio (in percent). }

%\begin{figure}[htb!]
%  \centering    
%    \subfigure[]{\includegraphics[width=0.29\textwidth]{synth/Fig/synth-noisy-xy-simi}
%    \label{fig:synth-noisy-xy-simi}}
%    \subfigure[]{\includegraphics[width=0.29\textwidth]{synth/Fig/synth-obs-xy-simi}
%    \label{fig:synth-obs-xy-simi}}   
%    \subfigure[]{\includegraphics[width=0.29\textwidth]{synth/Fig/synth-rr-xy-simi}
%    \label{fig:synth-rr-xy-simi}}   
%    \subfigure[]{\includegraphics[width=0.29\textwidth]{synth/Fig/synth-irr-xy-simi}
%    \label{fig:synth-irr-xy-simi}}           
%	\caption{Local similarity comparison of common offset 3D cubes comparison %($hx=5,hy=5$). (a) Noisy synthetic data. (b) Observed synthetic data (with 70\% missing traces). (c) Reconstructed data using the traditional approach. (d) Reconstructed data using the proposed approach.}
 %  \label{fig:synth-noisy-xy-simi,synth-obs-xy-simi,synth-rr-xy-simi,synth-irr-xy-simi}
%\end{figure}

%\begin{figure}[htb!]
%  \centering    
%    \subfigure[]{\includegraphics[width=0.29\textwidth]{synth/Fig/synth-noisy-hxhy-simi}
%    \label{fig:synth-noisy-hxhy-simi}}
%    \subfigure[]{\includegraphics[width=0.29\textwidth]{synth/Fig/synth-obs-hxhy-simi}
%    \label{fig:synth-obs-hxhy-simi}}   
%    \subfigure[]{\includegraphics[width=0.29\textwidth]{synth/Fig/synth-rr-hxhy-simi}
%    \label{fig:synth-rr-hxhy-simi}}   
%    \subfigure[]{\includegraphics[width=0.29\textwidth]{synth/Fig/synth-irr-hxhy-simi}
%    \label{fig:synth-irr-hxhy-simi}}           
%	\caption{Local similarity comparison of common midpoint 3D cubes ($x=5,y=5$). (a) Noisy synthetic data. (b) Observed synthetic data (with 70\% missing traces). (c) Reconstructed data using the traditional approach. (d) Reconstructed data using the proposed approach.}	
   %\label{fig:synth-noisy-hxhy-simi,synth-obs-hxhy-simi,synth-rr-hxhy-simi,synth-irr-hxhy-simi}
%\end{figure}

\inputdir{hyper}
\multiplot{4}{hyper-clean2d-1,hyper-obs2d-1,hyper-rr2d-1,hyper-irr2d-1}{width=0.8\textwidth}{Common midpoint gather comparison (reshaped into a 2D matrix). (a) Clean synthetic data with curved events. (b) Observed synthetic data (with 70\% missing traces and strong noise). (c) Reconstructed data using the traditional approach. (d) Reconstructed data using the proposed approach. }

\multiplot{4}{hyper-z-clean,hyper-z-obs,hyper-z-rr,hyper-z-irr}{width=0.45\textwidth}{Zoomed sections from Figure \ref{fig:hyper-clean2d-1,hyper-obs2d-1,hyper-rr2d-1,hyper-irr2d-1} (the green frame box). (a) Clean data. (b) Observed data. (b) Reconstructed data using the traditional approach. (c) Reconstructed data using the proposed approach.}

\multiplot{4}{hyper-z1-clean,hyper-z1-obs,hyper-z1-rr,hyper-z1-irr}{width=0.45\textwidth}{Zoomed sections from Figure \ref{fig:hyper-clean2d-1,hyper-obs2d-1,hyper-rr2d-1,hyper-irr2d-1} (the black frame box). (a) Clean data. (b) Observed data. (b) Reconstructed data using the traditional approach. (c) Reconstructed data using the proposed approach. Note the strong artifacts caused from the traditional approach.}

\multiplot{3}{hyper-obs-simi,hyper-rr-simi,hyper-irr-simi}{width=0.8\textwidth}{Local similarity comparison with respect to the clean data. (a) Similarity of the Observed synthetic data. (b) Similarity of the reconstructed data using the traditional approach. (c) Similarity of the reconstructed data using the proposed approach.}

\inputdir{field}
\multiplot{3}{field-obs2d-0,field-rr2d0-0,field-irr2d-0}{width=\textwidth}{Common offset gather comparison (reshaped into a 2D matrix). (a) Observed field data (with 80\% missing traces). (b) Reconstructed data using the traditional approach. (c) Reconstructed data using the proposed approach. }

\multiplot{3}{z-obs,z-rr,z-irr}{width=0.45\textwidth}{Zoomed sections from Fig \ref{fig:field-obs2d-0,field-rr2d0-0,field-irr2d-0}. (a) Observed field data. (b) Reconstructed data using the traditional approach. (c) Reconstructed data using the proposed approach.}

%\multiplot{3}{field-obs2d-h,field-rr2d-h,field-irr2d-h}{width=0.8\textwidth}{Common midpoint 3D cubes comparison. (a) Observed field data (with 80\% missing traces). (b) Reconstructed data using the traditional approach. (c) Reconstructed data using the proposed approach. }

%\section{Discussions}

%The improvement in terms of signal-to-noise ratio of finally interpolated and denoised data is tremendous, not trivial. The damping factor, in other words "stability factor", is indeed very effective and in a very simple mathematical form.  The implementation of the proposed method is super convenient. Given the traditional 5D or 3D rank-reduction codes, one can test our algorithm in seconds.

%5D seismic data interpolation and denoising has been a newly emerging research field thanks to the SAIG consortium. While most researches (SAIG) from the academia are focusing on the acceleration, we actually add more flavors to it. We investigate the problem from a different perspective, and investigate the performance in the case of extremely low signal-to-noise ratio, in which case signals are hardly seen from the data. The method is proposed to solve the noise problem in traditional rank-reduction method. The noise problem is one of the biggest problems (to some extent the biggest)  existing in land seismic data processing. Unlike those seismic data from modern marine seismic acquisition, which usually have high SNR,  the raw data from land acquisition is almost full of garbage. Our proposed approach aims to provide a beginning step in the new paradigm which is intended to extract information from extremely noisy seismic dataset.

\section{Conclusion}
Traditional rank-reduction method cannot obtain acceptable result for 5D seismic data denoising and reconstruction when the signal-to-noise ratio (SNR) is extremely low. The traditional truncated singular value decomposition (TSVD) formula will cause residual noise in the seismic data after iterative reconstruction since the denoised data space is a mixture of the signal subspace and noise subspace. In order to better decompose the noisy data into signal and noise components, we introduce a damping operator into the traditional TSVD formula to dampen the singular values that contain significant information of residual noise.   %We have proposed an improved method that slightly modifies the traditional TSVD formula. 
The improvement via the damped rank-reduction method is shown to be very appealing from both 5D synthetic and field data examples and can be achieved conveniently following the introduced damped TSVD formula. As shown from the comprehensive analysis of different 5D seismic data examples, we get some extra insightful conclusions in addition to the reconstruction result itself. First, the block Hankel matrix after damped rank-reduction is smoother than that of traditional rank-reduction, which is caused by damping the singular values and matches with the overall superior performance of the proposed approach well when the block Hankel matrix is transformed back to time-space domain. Second, the advantage of the proposed rank-reduction method over the traditional method becomes more dominant as the noise level in the observed data increases, which makes the proposed approach very attractive in processing 5D land seismic data.  We suggest to replace the current 5D seismic data interpolation framework with our proposed framework for better dealing with the highly noisy incomplete dataset.

\section{Acknowledgments}
We would like to thank Shan Qu, Jiang Yuan, Mauricio Sacchi, \new{Jean Virieux and Aaron Stanton} for constructive suggestions that improved the manuscript greatly. We are grateful to developers of the Madagascar software package for providing corresponding codes for testing the algorithms and preparing the figures. This work is partially supported by National Basic Research Program of China (Grant NO: 2013 CB228602), National Natural Science Foundation of China (Grant No.41274137), National Science and Technology of Major Projects of China (Grant No. 2011ZX05019-006), National Engineering Laboratory of Offshore Oil Exploration, and the Texas Consortium for Computational Seismology (TCCS).

\newpage
\appendix
\section{Appendix A: EXACT FORMULATION OF THE BLOCK HANKEL MATRIX}
The block Hankel matrix $\mathbf{M}^{(4)}$ can be expressed as
\begin{equation}
\label{eq:M_a}
\mathbf{M}^{(4)}=\mathbf{S}+\mathbf{N},
\end{equation}
where $\mathbf{S}$ and $\mathbf{N}$ denote signal component and the random noise component that are both in $\mathbf{M}^{(4)}$, respectively. The singular value decomposition (SVD) of $\mathbf{S}$ can be represented as:
\begin{equation}
\label{eq:svds_a}
\mathbf{S} = [\mathbf{U}_1^{S}\quad \mathbf{U}_2^{S}]\left[\begin{array}{cc}
\Sigma_1^{S} & \mathbf{0}\\
\mathbf{0} & \Sigma_2^{S}
\end{array}
\right]\left[\begin{array}{c}
(\mathbf{V}_1^{S})^H\\
(\mathbf{V}_2^{S})^H
\end{array}
\right].
\end{equation}
Because of the deficient rank, the matrix $\mathbf{S}$ can be written as
\begin{equation}
\label{eq:S_a}
\mathbf{S}=\mathbf{U}_1^S\Sigma_1^S(\mathbf{V}_1^S)^H.
\end{equation}
Because equation \ref{eq:svds_a} is a SVD of the signal matrix $\mathbf{S}$, the left matrix in equation \ref{eq:svds_a} is a unitary matrix:
\begin{equation}
\label{eq:unit}
\mathbf{I}=\mathbf{U}^S(\mathbf{U}^S)^H=[\mathbf{U}_1^S\quad \mathbf{U}_2^S]\left[\begin{array}{c} 
(\mathbf{U}_1^S)^H \\
(\mathbf{U}_2^S)^H 
\end{array}
\right].
\end{equation}
Combining equations \ref{eq:M_a}, \ref{eq:S_a}, and \ref{eq:unit}, we can derive:
\begin{equation}
\label{eq:factorapp}
\begin{split}
\mathbf{M}^{(4)}&=\mathbf{S}+[\mathbf{U}_1^S\quad \mathbf{U}_2^S]\left[\begin{array}{c} 
(\mathbf{U}_1^S)^H \\
(\mathbf{U}_2^S)^H
\end{array}
\right]\mathbf{N} \\
&=\mathbf{U}_1^S\Sigma_1^S(\mathbf{V}_1^S)^H + \left( 
\mathbf{U}_1^S(\mathbf{U}_1^S)^H+\mathbf{U}_2^S(\mathbf{U}_2^S)^H
\right)\mathbf{N}\\
&=\mathbf{U}_1^S \left(
(\mathbf{U}_1^S)^H\mathbf{N}+\Sigma_1^S(\mathbf{V}_1^S)^H
\right)+\mathbf{U}_2^S(\mathbf{U}_2^S)^H\mathbf{N}\\
&=\mathbf{U}_1^S\left(
\mathbf{N}^H\mathbf{U}_1^S+\mathbf{V}_1^S\Sigma_1^S
\right)^H + \mathbf{U}_2^S(\mathbf{N}^H\mathbf{U}_2^S)^H\\
&= [\mathbf{U}_1^S \quad \mathbf{U}_2^S]\left[\begin{array}{cc} 
\mathbf{I} & \mathbf{0}\\
\mathbf{0} & \mathbf{I}
\end{array}
\right]\left[\begin{array}{c} 
(\mathbf{N}^H\mathbf{U}_1^S+\mathbf{V}_1^S\Sigma_1^S)^H\\
(\mathbf{N}^H\mathbf{U}_2^S)^H
\end{array}
\right],
\end{split}
\end{equation}
%where $\Sigma_1$ and $\Sigma_2$ are introduced  matrices and are diagonal and positive definite.
we can further derive equation \ref{eq:factorapp} and factorize $\mathbf{M}^{(4)}$ as follows:
\begin{equation}
\label{eq:factorm}
\mathbf{M}^{(4)} = [\mathbf{U}_1^S \quad \mathbf{U}_2^S]\left[\begin{array}{cc} 
\Sigma_{1} & \mathbf{0}\\
\mathbf{0} & \Sigma_{2}
\end{array}
\right]\left[\begin{array}{c} 
(\Sigma_{1})^{-1}(\mathbf{N}^H\mathbf{U}_1^S+\mathbf{V}_1^S\Sigma_1^S)^H\\
(\Sigma_{2})^{-1}(\mathbf{N}^H\mathbf{U}_2^S)^H
\end{array}
\right],
\end{equation} 
where $\Sigma_1$ and $\Sigma_2$ denote diagonal and positive definite matrices. Please note that $\mathbf{M}^{(4)}$ is constructed such that it is close to a square matrix \cite[]{mssa}, and thus the $\Sigma_1$ and $\Sigma_2$ are assumed to be square matrices for derivation convenience.  We observe that the left matrix has orthonormal columns and the middle matrix is diagonal. It can be shown that the right matrix also has orthonormal columns.  Thus, equation \ref{eq:factorm} is an SVD of $\mathbf{M}^{(4)}$. According to the TSVD method, we let $\Sigma_2$ be $\mathbf{0}$ and then the following equation holds:
\begin{equation}
\label{eq:tsvd2}
\begin{split}
\tilde{\mathbf{M}}^{(4)} &= \mathbf{U}_1^S(\mathbf{U}_1^S)^H\mathbf{N} + \mathbf{U}_1^S\Sigma_1^S(\mathbf{V}_1^S)^H \\
 &=\mathbf{S} + \mathbf{U}_1^S(\mathbf{U}_1^S)^H\mathbf{N}.
\end{split}
\end{equation}

\newpage
\appendix
\section{Appendix B: Damped TSVD formula}
We first reformulate equation \ref{eq:tsvd2} as
\begin{equation}
\label{eq:tsvd22}
\mathbf{S} = \mathbf{M}^{(4)} -\mathbf{U}_1^S(\mathbf{U}_1^S)^H\mathbf{N}.
\end{equation}
Inserting equation \ref{eq:tsvd} into equation \ref{eq:tsvd22}, we can further derive 
\begin{equation}
\label{eq:tsvd222}
\begin{split}
\mathbf{S} = \mathbf{U}_1^{M^{(4)}}\Sigma_1^{M^{(4)}}(\mathbf{V}_1^{M^{(4)}})^H -\mathbf{U}_1^S(\mathbf{U}_1^S)^H\mathbf{N}.
\end{split}
\end{equation}
The SVD of $\mathbf{M}^{(4)}$ can be expressed as
\begin{equation}
\label{eq:svdm_a}
\mathbf{M}^{(4)} = [\mathbf{U}_1^{M^{(4)}}\quad \mathbf{U}_2^{M^{(4)}}]\left[\begin{array}{cc}
\Sigma_1^{M^{(4)}} & \mathbf{0}\\
\mathbf{0} & \Sigma_2^{M^{(4)}}
\end{array}
\right]\left[\begin{array}{c}
(\mathbf{V}_1^{M^{(4)}})^H\\
(\mathbf{V}_2^{M^{(4)}})^H
\end{array}
\right].
\end{equation}

Because equations \ref{eq:svdm_a} and \ref{eq:factorm} are both SVDs of $\mathbf{M}^{(4)}$, we let
\begin{align}
\label{eq:equal1}
\mathbf{U}_1^S&=\mathbf{U}_1^{M^{(4)}}, \\
\label{eq:equal3}
\Sigma_1&=\Sigma_1^{M^{(4)}}, \\
\label{eq:equal2}
(\mathbf{N}^H\mathbf{U}_1^S+\mathbf{V}_1^S\Sigma_1^S)(\Sigma_1)^{-1}&=\mathbf{V}_1^{M^{(4)}}.
\end{align}

Inserting equations \ref{eq:equal1} and \ref{eq:equal2} into equation \ref{eq:tsvd222}, we can derive:
\begin{equation}
\label{eq:S22}
\mathbf{S} =\mathbf{U}_1^{M^{(4)}}\left\{\Sigma_1^{M^{(4)}}(\mathbf{V}_1^{M^{(4)}})^H- \left[\Sigma_1(\mathbf{V}_1^{M^{(4)}})^H-\Sigma_1^S(\mathbf{V}_1^S)^H\right]\right\}.
\end{equation}
For simplification, we assume that there exist such $\mathbf{A}$ and $\mathbf{B}$ that $\mathbf{V}_1^S=\mathbf{V}_1^{M^{(4)}}\mathbf{A}$ and $\Sigma_1= \Sigma_1^{M^{(4)}}\mathbf{B}$. $\mathbf{A}$ is a square matrix and $\mathbf{B}$ is a diagonal matrix. Then we can simplify $\mathbf{S}$ as:
\begin{align}
\label{eq:S3}
\mathbf{S} &= \mathbf{U}_1^{M^{(4)}}\Sigma_1^{M^{(4)}}\mathbf{T}\left(\mathbf{V}_1^{M^{(4)}}\right)^H.\\
\label{eq:T}
\mathbf{T} &= \mathbf{I} - \mathbf{B}\left(\mathbf{I}-(\Sigma_1)^{-1}\Sigma_1^S\mathbf{A}^H\right),
\end{align}
where $\mathbf{I}$ is a unit matrix and here we name $\mathbf{T}$ the damping operator.

From equation \ref{eq:equal3}, $\mathbf{B}=\mathbf{I}$.
%\begin{equation}
%\label{eq:Bder}
%\end{equation}
From equation \ref{eq:equal2}, it is straightforward to derive
\begin{equation}
\label{eq:Ader0}
\begin{split}
\mathbf{V}_1^S&=(\mathbf{V}_1^{M^{(4)}}-\mathbf{N}^H\mathbf{U}_1^S(\Sigma_1)^{-1})\Sigma_1(\Sigma_1^S)^{-1}\\
&\approx \mathbf{V}_1^{M^{(4)}}(\mathbf{I}-(\mathbf{V}_1^{M^{(4)}})^{o}\mathbf{N}^H\mathbf{U}_1^S(\Sigma_1)^{-1})\Sigma_1(\Sigma_1^S)^{-1}
\end{split}
\end{equation}
where $(\mathbf{V}_1^{M^{(4)}})^{o}$ satisfies that $\parallel\mathbf{I}-\mathbf{V}_1^{M^{(4)}}(\mathbf{V}_1^{M^{(4)}})^{o} \parallel\rightarrow 0$. Considering $\mathbf{V}_1^S=\mathbf{V}_1^{M^{(4)}}\mathbf{A}$, then the following relation holds
\begin{equation}
\label{eq:Ader}
\begin{split}
\mathbf{A}&\approx (\mathbf{I}-(\mathbf{V}_1^{M^{(4)}})^{o}\mathbf{N}^H\mathbf{U}_1^S(\Sigma_1)^{-1})\Sigma_1(\Sigma_1^S)^{-1}\\
&=(\mathbf{I}-\Gamma)\Sigma_1(\Sigma_1^S)^{-1},
\end{split}
\end{equation}
where $\Gamma=(\mathbf{V}_1^{M^{(4)}})^{o}\mathbf{N}^H\mathbf{U}_1^S(\Sigma_1)^{-1}$.

Inserting equation \ref{eq:Ader} and  $\mathbf{B}=\mathbf{I}$  into equation \ref{eq:T}, we can obtain a simplified formula:
\begin{equation}
\label{eq:T1}
\mathbf{T} = \mathbf{I}-\Gamma.
\end{equation}

Combing equations \ref{eq:S3} and \ref{eq:T1}, we can conclude that the true signal is a damped version of the previous TSVD method (equation \ref{eq:tsvd}), with the damping operator defined by equation \ref{eq:T1}. Right now, there is still one unknown parameter needed to be defined: $\Gamma$. Although we have a potential selection  $\Gamma=(\mathbf{V}_1^{M^{(4)}})^{o}\mathbf{N}^H\mathbf{U}_1^S(\Sigma_1)^{-1}$, as defined during the derivation of $\mathbf{A}$, we cannot calculate it because we do not know $\mathbf{N}$ and $\mathbf{U}_1^S$. A very pleasant denoising performance can be obtained when $\Gamma$ is chosen as
\begin{equation}
\label{eq:Gamma}
\Gamma \approx \hat{\delta}^N\left(\Sigma_1^{M^{(4)}}\right)^{-N},
\end{equation}
where $\hat{\delta}$ denotes the maximum element of $\Sigma_2^{M^{(4)}}$ and $N$ denotes the damping factor. We use such approximation because of three reasons. (1) $\hat{\delta}$ reflects the energy of random noise and $ \Sigma_1^{M^{(4)}} $ contains the information of signal. (2) Because the diagonal  elements of $ \Sigma^{M^{(4)}} $ are in a descending order, $\hat{\delta} $  is certainly smaller than every diagonal element of $ \Sigma_1^{M^{(4)}} $, and  $ \hat{\delta}/\delta_1<\hat{\delta}/\delta_2<\cdots<\hat{\delta}/\delta_K $, where $\delta_i$ denotes $i$th diagonal entry in $\Sigma_1^{M^{(4)}}$. (3) $\hat{\delta}$ is zero in the zero random noise situation. Besides, we introduce the parameter $ N $ to control the strength of damping operator, the greater the $ N $, the weaker the damping, and the damped MSSA reverts to the basic MSSA when $ N\to\infty $.

Combining equations \ref{eq:S3}, \ref{eq:T1}, and \ref{eq:Gamma}, we conclude the approximation of $\mathbf{S}$ as:
\begin{align}
\label{eq:S4}
\mathbf{S} & = \mathbf{U}_1^{M^{(4)}} \Sigma_1^{M^{(4)}}\mathbf{T}(\mathbf{V}_1^{M^{(4)}})^H,\\
\label{eq:T2}
\mathbf{T} & =\mathbf{I}-(\Sigma_1^{M^{(4)}})^{-N}\hat{\delta}^N.
\end{align}

\newpage
\appendix
\section{Appendix C: Review of local similarity}
We begin our review based on 1D vectors $\mathbf{a}$ and $\mathbf{b}$. A common way to measure the similarity between two signals is to calculate the correlation coefficient,
\begin{equation}
\label{eq:corr}
c=\frac{\mathbf{a}^T\mathbf{b}}{\parallel \mathbf{a} \parallel_2 \parallel \mathbf{b} \parallel_2},
\end{equation}
where $c$ is the correlation coefficient, $\mathbf{a}^T\mathbf{b}$ denotes the dot product of $\mathbf{a}$ and $\mathbf{b}$. $\parallel \cdot \parallel_2$ denotes the $L_2$ norm of the input vector. The correlation coefficient $c$ can measure the correlation, or in other words similarity, between two vectors within the selected window in a global manner. However, in some specific applications, a local measurement for the similarity is more demanded. In order to 
measure the local similarity of two vectors, it is straightforwardly to apply local windows to the target vectors: 
\begin{equation}
\label{eq:localcorr}
c(i) =  \frac{\mathbf{a}_i^T\mathbf{b}_i}{\parallel \mathbf{a}_i \parallel_2 \parallel \mathbf{b}_i \parallel_2},
\end{equation}
where $\mathbf{a}_i$ and $\mathbf{b}_i$ denote the localized vectors centered on the $i$th entry of input long vectors $\mathbf{a}$ and $\mathbf{b}$, respectively. The windowing is sometime troublesome, since the measured similarity is largely dependent on the windowing length and the measured local similarity might be discontinuous because of the separate calculations in windows. To avoid the negative performance caused by local windowing calculations, \cite{fomel2007localattr} proposed an elegant way for calculating smooth local similarity via solving two inverse problems.

Let us first rewrite equation \ref{eq:corr} in a different form. Getting the absolute value of both sides of equation \ref{eq:corr}, considering $\mathbf{a}^T\mathbf{b}=\mathbf{b}^T\mathbf{a}$, we have
\begin{equation}
\label{eq:absc}
|c|=\sqrt{ \frac{(\mathbf{a}^T\mathbf{b})(\mathbf{b}^T\mathbf{a})}{\parallel \mathbf{a} \parallel_2^2 \parallel\mathbf{b} \parallel_2^2} }=
\sqrt{\frac{\mathbf{a}^T\mathbf{b}}{\mathbf{a}^T\mathbf{a}} \frac{\mathbf{b}^T\mathbf{a}}{\mathbf{b}^T\mathbf{b}}} % = \sqrt{\left|\frac{\mathbf{a}^T\mathbf{b}}{\mathbf{a}^T\mathbf{a}}\right|}\sqrt{\left|\frac{\mathbf{b}^T\mathbf{a}}{\mathbf{b}^T\mathbf{b}}\right|}
\end{equation}
We let $c_1=\frac{\mathbf{a}^T\mathbf{b}}{\mathbf{a}^T\mathbf{a}}$ and $c_2=\frac{\mathbf{b}^T\mathbf{a}}{\mathbf{b}^T\mathbf{b}}$, equation \ref{eq:absc} turns to 
\begin{equation}
\label{eq:cc}
|c|=\sqrt{c_1c_2}.
\end{equation}
It is obvious that scalars $c_1$ and $c_2$ come from two least-squares inverse problem:
\begin{align}
\label{eq:ls1}
c_1 = \arg \min_{\tilde{c}} \parallel \mathbf{a}-\mathbf{b}\tilde{c} \parallel_2^2 \\
\label{eq:ls2}
c_2 = \arg\min_{\tilde{c}} \parallel \mathbf{b}-\mathbf{a}\tilde{c} \parallel_2^2 
\end{align}
The local similarity attribute is based on equations \ref{eq:ls1} and \ref{eq:ls2}, but is in a localized version: 
\begin{align}
\label{eq:local1}
\mathbf{c}_1 &=\arg\min_{\tilde{\mathbf{c}}_1}\Arrowvert \mathbf{a}-\mathbf{B}\tilde{\mathbf{c}}_1 \Arrowvert_2^2, \\
\label{eq:local2}
\mathbf{c}_2 &=\arg\min_{\tilde{\mathbf{c}}_2}\Arrowvert \mathbf{b}-\mathbf{A}\tilde{\mathbf{c}}_2 \Arrowvert_2^2,
\end{align}
where $\mathbf{A}$ is a diagonal operator composed from the elements of $\mathbf{a}$: $\mathbf{A}=diag(\mathbf{a})$ and $\mathbf{B}$ is a diagonal operator composed from the elements of $\mathbf{b}$: $\mathbf{B}=diag(\mathbf{b})$.
Equations \ref{eq:local1} and \ref{eq:local2} are solved via shaping regularization
\begin{align}
\label{eq:local3}
\mathbf{c}_1 &= [\lambda_1^2\mathbf{I} + \mathcal{T}(\mathbf{B}^T\mathbf{B}-\lambda_1^2\mathbf{I})]^{-1}\mathcal{T}\mathbf{B}^T\mathbf{a},\\
\label{eq:local4}
\mathbf{c}_2 &= [\lambda_2^2\mathbf{I} + \mathcal{T}(\mathbf{A}^T\mathbf{A}-\lambda_2^2\mathbf{I})]^{-1}\mathcal{T}\mathbf{A}^T\mathbf{b},
\end{align}
where $\mathbf{\mathcal{T}}$ is a smoothing operator, and $\lambda_1$ and $\lambda_2$ are two parameters controlling the physical dimensionality and enabling fast convergence when inversion is implemented iteratively. These two parameters can be chosen as $\lambda_1  = \Arrowvert\mathbf{B}^T\mathbf{B}\Arrowvert_2$ and $\lambda_2  = \Arrowvert\mathbf{A}^T\mathbf{A}\Arrowvert_2$ \cite[]{fomel2007localattr}.

After the $\mathbf{c}_1$ and $\mathbf{c}_2$ are solved, the localized version of $|c|$ is
\begin{equation}
\label{eq:lsimi}
\mathbf{c} = \sqrt{\mathbf{c}_1\circ\mathbf{c}_2},
\end{equation}
where $\mathbf{c}$ is the output local similarity and $\circ$ denotes element-wise product.

To calculate the 2D and 3D versions of local similarity, as used in demonstrating the reconstruction performance in the main contents of the paper, one needs to first reshape a 2D matrix or a 3D tensor into a 1D vector and then to use the formula shown above to calculate the local similarity vector. Since the local similarity is of the same size of the input two vectors, it can be easily reshaped into the 2D or 3D form for display purposes.

\bibliographystyle{seg}
\bibliography{irr}

### 2020-11-01 drr5d/paper.tex
2020年11月 1日 星期日 01时54分38秒 CDT

@@
+\published{Geophysical Journal International, 206, 1695-1717, (2016)}
+
 \title{Simultaneous denoising and reconstruction of 5D seismic data via damped rank-reduction method}
@@
 \section{Examples}
-We apply the proposed improved rank-reduction method on a 5D synthetic seismic dataset, as shown in Figures \ref{fig:synth-clean-xy,synth-noisy-xy,synth-obs-xy,synth-rr-xy,synth-irr-xy} and \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-irr-hxhy}.
-Figure \ref{fig:synth-clean-xy,synth-noisy-xy,synth-obs-xy,synth-rr-xy,synth-irr-xy} shows the performance in one common offset gather ($hx=5,hy=5$) and Figure \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-irr-hxhy} shows the performance in one common midpoint gather ($x=5,y=5$).
+We apply the proposed improved rank-reduction method on a 5D synthetic seismic dataset, as shown in Figures \ref{fig:synth-clean-xy,synth-noisy-xy,synth-obs-xy,synth-rr-xy,synth-drr-xy} and \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-drr-hxhy}.
+Figure \ref{fig:synth-clean-xy,synth-noisy-xy,synth-obs-xy,synth-rr-xy,synth-drr-xy} shows the performance in one common offset gather ($hx=5,hy=5$) and Figure \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-drr-hxhy} shows the performance in one common midpoint gather ($x=5,y=5$).
 Figures \ref{fig:synth-clean-xy} and \ref{fig:synth-clean-hxhy} show the true data.
@@
 However, there is still some residual noise in the reconstructed data, which can be explained by the non-optimal decomposition via traditional TSVD as analyzed in the theoretic section.
-Figures \ref{fig:synth-irr-xy} and \ref{fig:synth-irr-hxhy} show the reconstructed data using the proposed method.
+Figures \ref{fig:synth-drr-xy} and \ref{fig:synth-drr-hxhy} show the reconstructed data using the proposed method.
 In this example, the rank $K=3$ and the damping factor $N=3$, and we use 10 weighted \old{POCS like}\new{POCS-like} iterations.
 It is obvious that the proposed method obtains a much cleaner result, and to some extent, the recovery of the useful signals are nearly perfect.
-Figure \ref{fig:synth-rr-xy-e,synth-irr-xy-e} shows two reconstruction error cubes in common offset domain (the difference between the true data and the recovered data) using the traditional and the proposed approaches, respectively.
-Similarly, Figure \ref{fig:synth-rr-hxhy-e,synth-irr-hxhy-e} shows the reconstruction error cubes in common midpoint domain.
-Both Figures \ref{fig:synth-rr-xy-e,synth-irr-xy-e} and \ref{fig:synth-rr-hxhy-e,synth-irr-hxhy-e} clearly show that the proposed approach can obtain the least reconstruction error, while the error in the traditional approach is mainly due to the residual noise.
-In order to compare the amplitude between different datasets in detail, we conduct a single trace amplitude comparison for each data cubes shown in Figure \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-irr-hxhy}.
-The single trace is chosen as the middle trace in each cubes of Figure \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-irr-hxhy}.
+Figure \ref{fig:synth-rr-xy-e,synth-drr-xy-e} shows two reconstruction error cubes in common offset domain (the difference between the true data and the recovered data) using the traditional and the proposed approaches, respectively.
+Similarly, Figure \ref{fig:synth-rr-hxhy-e,synth-drr-hxhy-e} shows the reconstruction error cubes in common midpoint domain.
+Both Figures \ref{fig:synth-rr-xy-e,synth-drr-xy-e} and \ref{fig:synth-rr-hxhy-e,synth-drr-hxhy-e} clearly show that the proposed approach can obtain the least reconstruction error, while the error in the traditional approach is mainly due to the residual noise.
+In order to compare the amplitude between different datasets in detail, we conduct a single trace amplitude comparison for each data cubes shown in Figure \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-drr-hxhy}.
+The single trace is chosen as the middle trace in each cubes of Figure \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-drr-hxhy}.
 The comparison is presented in Figure \ref{fig:synth-ss}.
@@
 
-In order to show how the rank-reduced block Hankel matrix looks like and to more intuitively demonstrate the influence of the introduced damping operator to the target level-four block Hankel matrix in the first 5D seismic data example, we plot the 26 Hz block Hankel matrix for different  cases in Figures \ref{fig:H_clean-0,H_obs-0,H_rr10-0,H_irr10-0}, \ref{fig:H-z-clean,H-z-obs,H-z-rr10,H-z-irr10}, and \ref{fig:H_rr1-0,H_irr1-0,H-z-rr1,H-z-irr1}.
+In order to show how the rank-reduced block Hankel matrix looks like and to more intuitively demonstrate the influence of the introduced damping operator to the target level-four block Hankel matrix in the first 5D seismic data example, we plot the 26 Hz block Hankel matrix for different  cases in Figures \ref{fig:H_clean-0,H_obs-0,H_rr10-0,H_drr10-0}, \ref{fig:H-z-clean,H-z-obs,H-z-rr10,H-z-drr10}, and \ref{fig:H_rr1-0,H_drr1-0,H-z-rr1,H-z-drr1}.
 Figure \ref{fig:H_clean-0} shows the 26 Hz block Hankel matrix for the clean data.
@@
 Figure \ref{fig:H_rr10-0} shows rank-reduced block Hankel matrix via the traditional TSVD after 10 iterations.
-The rank-reduced block Hankel matrix via the damped TSVD is shown in Figure \ref{fig:H_irr10-0}.
-Figures \ref{fig:H_rr10-0} and \ref{fig:H_irr10-0} are both close to the true block Hankel matrix and are very similar to each other.
+The rank-reduced block Hankel matrix via the damped TSVD is shown in Figure \ref{fig:H_drr10-0}.
+Figures \ref{fig:H_rr10-0} and \ref{fig:H_drr10-0} are both close to the true block Hankel matrix and are very similar to each other.
 If we look carefully or zoom in the figure a bit, we can see that the block Hankel matrix via the traditional TSVD is much rougher than the Hankel matrix via the damped TSVD.
-Considering that each subfigure in Figure \ref{fig:H_clean-0,H_obs-0,H_rr10-0,H_irr10-0} is a 1296$\times$625 matrix, which contains a lot of information, we zoom one block Hankel matrix, as highlighted by the black frame boxes in Figure \ref{fig:H_clean-0,H_obs-0,H_rr10-0,H_irr10-0} and make a more detailed comparison in Figure \ref{fig:H-z-clean,H-z-obs,H-z-rr10,H-z-irr10}.
-Figure \ref{fig:H-z-clean,H-z-obs,H-z-rr10,H-z-irr10} clearly shows that the rank-reduced block Hankel matrix via traditional TSVD still contains some artifacts, especially on the right bottom side, when compared with the true block Hankel matrix.
+Considering that each subfigure in Figure \ref{fig:H_clean-0,H_obs-0,H_rr10-0,H_drr10-0} is a 1296$\times$625 matrix, which contains a lot of information, we zoom one block Hankel matrix, as highlighted by the black frame boxes in Figure \ref{fig:H_clean-0,H_obs-0,H_rr10-0,H_drr10-0} and make a more detailed comparison in Figure \ref{fig:H-z-clean,H-z-obs,H-z-rr10,H-z-drr10}.
+Figure \ref{fig:H-z-clean,H-z-obs,H-z-rr10,H-z-drr10} clearly shows that the rank-reduced block Hankel matrix via traditional TSVD still contains some artifacts, especially on the right bottom side, when compared with the true block Hankel matrix.
 The block Hankel matrix from the proposed approach is, however, much smoother, and closer to the true block Hankel matrix.
-We also show the comparison of two block Hankel matrices using rank-reduction methods after the first iteration and their zoomed matrices in Figure \ref{fig:H_rr1-0,H_irr1-0,H-z-rr1,H-z-irr1}.
+We also show the comparison of two block Hankel matrices using rank-reduction methods after the first iteration and their zoomed matrices in Figure \ref{fig:H_rr1-0,H_drr1-0,H-z-rr1,H-z-drr1}.
 It can be observed that even after 1 iteration, the rank-reduced block Hankel matrix via the damped TSVD is much smoother, which indicates that more noise in each frequency slice
 is suppressed.
-Please note that all figures in Figures \ref{fig:H_clean-0,H_obs-0,H_rr10-0,H_irr10-0}, \ref{fig:H-z-clean,H-z-obs,H-z-rr10,H-z-irr10}, and \ref{fig:H_rr1-0,H_irr1-0,H-z-rr1,H-z-irr1} use the same plotting scale.
+Please note that all figures in Figures \ref{fig:H_clean-0,H_obs-0,H_rr10-0,H_drr10-0}, \ref{fig:H-z-clean,H-z-obs,H-z-rr10,H-z-drr10}, and \ref{fig:H_rr1-0,H_drr1-0,H-z-rr1,H-z-drr1} use the same plotting scale.
 It can also be seen that the block Hankel matrix after 1 iteration is far from the true block Hankel matrix, however, during the weighted \old{POCS like}\new{POCS-like} iterations, the block Hankel matrix is gradually converging to the true block Hankel matrix.
@@
 The higher local similarity corresponds to the better reconstruction performance.
-Figure \ref{fig:synth-noisy-xy-simi,synth-obs-xy-simi,synth-rr-xy-simi,synth-irr-xy-simi} shows the local similarity comparison in common offset domain and Figure \ref{fig:synth-noisy-hxhy-simi,synth-obs-hxhy-simi,synth-rr-hxhy-simi,synth-irr-hxhy-simi} shows the local similarity comparison in common midpoint domain.
-Figures \ref{fig:synth-noisy-xy-simi}, \ref{fig:synth-obs-xy-simi}, \ref{fig:synth-rr-xy-simi}, and \ref{fig:synth-irr-xy-simi} show the local similarity between the true data and the noisy data, observed data, result from the traditional method, and result from the proposed method, respectively, in common offset domain.
-Figures \ref{fig:synth-noisy-hxhy-simi}, \ref{fig:synth-obs-hxhy-simi}, \ref{fig:synth-rr-hxhy-simi}, and \ref{fig:synth-irr-hxhy-simi} show the counterpart comparisons in common midpoint domain.
+Figure \ref{fig:synth-noisy-xy-simi,synth-obs-xy-simi,synth-rr-xy-simi,synth-drr-xy-simi} shows the local similarity comparison in common offset domain and Figure \ref{fig:synth-noisy-hxhy-simi,synth-obs-hxhy-simi,synth-rr-hxhy-simi,synth-drr-hxhy-simi} shows the local similarity comparison in common midpoint domain.
+Figures \ref{fig:synth-noisy-xy-simi}, \ref{fig:synth-obs-xy-simi}, \ref{fig:synth-rr-xy-simi}, and \ref{fig:synth-drr-xy-simi} show the local similarity between the true data and the noisy data, observed data, result from the traditional method, and result from the proposed method, respectively, in common offset domain.
+Figures \ref{fig:synth-noisy-hxhy-simi}, \ref{fig:synth-obs-hxhy-simi}, \ref{fig:synth-rr-hxhy-simi}, and \ref{fig:synth-drr-hxhy-simi} show the counterpart comparisons in common midpoint domain.
 Because of the strong random noise in the noisy data, the local similarity between noisy data and the true data is relatively low.
@@
 The local similarity between the result from traditional rank-reduction method is much higher than that of the noisy data and the similarity value is approaching 1, which is the highest possible value of local similarity.
-The proposed approach can make the local similarity between the result and true data even higher, as can be seen from Figures \ref{fig:synth-noisy-xy-simi,synth-obs-xy-simi,synth-rr-xy-simi,synth-irr-xy-simi} and \ref{fig:synth-noisy-hxhy-simi,synth-obs-hxhy-simi,synth-rr-hxhy-simi,synth-irr-hxhy-simi} that the similarity color that corresponds to the proposed method is redder than that of the traditional approach.
+The proposed approach can make the local similarity between the result and true data even higher, as can be seen from Figures \ref{fig:synth-noisy-xy-simi,synth-obs-xy-simi,synth-rr-xy-simi,synth-drr-xy-simi} and \ref{fig:synth-noisy-hxhy-simi,synth-obs-hxhy-simi,synth-rr-hxhy-simi,synth-drr-hxhy-simi} that the similarity color that corresponds to the proposed method is redder than that of the traditional approach.
 
@@
 In order to test the effectiveness of the rank-reduction method on data containing curved events and to compare the performances of different methods in this case, we then use the second example to show the performance.
-In Figure \ref{fig:hyper-clean2d-1,hyper-obs2d-1,hyper-rr2d-1,hyper-irr2d-1}, we show a common midpoint gather comparison of the second synthetic example.
+In Figure \ref{fig:hyper-clean2d-1,hyper-obs2d-1,hyper-rr2d-1,hyper-drr2d-1}, we show a common midpoint gather comparison of the second synthetic example.
 Here we reshape the 3D data cube into a 2D matrix and compare the performance based on the 2D matrix.
@@
 After reconstruction using the traditional rank-reduction method with 10 \old{POCS like}\new{POCS-like} iterations, we obtain the reconstructed result as shown in Figure \ref{fig:hyper-rr2d-1}.
-The result using the proposed approach is shown in Figure \ref{fig:hyper-irr2d-1}.
+The result using the proposed approach is shown in Figure \ref{fig:hyper-drr2d-1}.
 The reconstruction result using the traditional method seems to have significant residual noise and even causes  artifacts in some parts of the data.
-The data highlighted by the green frame boxes are zoomed and shown in Figure \ref{fig:hyper-z-clean,hyper-z-obs,hyper-z-rr,hyper-z-irr}, where we can have a better view to compare the performance in detail and to see how the proposed method helps recover almost the true model.
-The data highlighted by the black frame boxes are zoomed and shown in Figure \ref{fig:hyper-z1-clean,hyper-z1-obs,hyper-z1-rr,hyper-z1-irr}, where we can see the artifacts caused by the traditional approach clearly and see the almost perfect performance from the proposed approach.
+The data highlighted by the green frame boxes are zoomed and shown in Figure \ref{fig:hyper-z-clean,hyper-z-obs,hyper-z-rr,hyper-z-drr}, where we can have a better view to compare the performance in detail and to see how the proposed method helps recover almost the true model.
+The data highlighted by the black frame boxes are zoomed and shown in Figure \ref{fig:hyper-z1-clean,hyper-z1-obs,hyper-z1-rr,hyper-z1-drr}, where we can see the artifacts caused by the traditional approach clearly and see the almost perfect performance from the proposed approach.
 We apply the proposed approach with $K=12$ and $N=3$ for this example.
@@
 The SNR of the result from traditional rank-reduction approach is 13.56 dB while the SNR of the reconstruction result from the proposed damped rank-reduction method approach is 17.23 dB.
-In this example, we also calculate the local similarity between different datasets and the clean dataset and show them in Figure \ref{fig:hyper-obs-simi,hyper-rr-simi,hyper-irr-simi}.
+In this example, we also calculate the local similarity between different datasets and the clean dataset and show them in Figure \ref{fig:hyper-obs-simi,hyper-rr-simi,hyper-drr-simi}.
 Figure \ref{fig:hyper-obs-simi} shows the local similarity between the observed data and the clean data.
-Figure \ref{fig:hyper-rr-simi} shows the local similarity between the result from traditional method and the clean data and Figure \ref{fig:hyper-irr-simi} shows the local similarity between the result from the proposed method and the clean data.
+Figure \ref{fig:hyper-rr-simi} shows the local similarity between the result from traditional method and the clean data and Figure \ref{fig:hyper-drr-simi} shows the local similarity between the result from the proposed method and the clean data.
 The local similarity vividly demonstrates that the proposed approach can obtain the most similar result to the true model.
@@
 However, there are still some residual noise in the reconstructed data, since we use a relatively large $K=15$ to account for the curved events.
-We apply the proposed approach with $K=15$ and $N=3$ and obtain an almost perfect reconstruction performance, as shown in Figure \ref{fig:field-irr2d-0}.
+We apply the proposed approach with $K=15$ and $N=3$ and obtain an almost perfect reconstruction performance, as shown in Figure \ref{fig:field-drr2d-0}.
 The events become more coherent and the data becomes much cleaner.
-We zoom a part from each subfigure in Figure \ref{fig:field-obs2d-0,field-rr2d0-0,field-irr2d-0} and show the comparison in Figure \ref{fig:z-obs,z-rr,z-irr}.
-The zoomed data are highlighted by the red frame boxes shown in Figure \ref{fig:field-obs2d-0,field-rr2d0-0,field-irr2d-0}.
-The zoomed sections shown in Figure \ref{fig:z-obs,z-rr,z-irr} show a clearer comparison between the traditional and the proposed methods, and confirm that the proposed method can obtain a very clean and spatially coherent reconstruction result.
+We zoom a part from each subfigure in Figure \ref{fig:field-obs2d-0,field-rr2d0-0,field-drr2d-0} and show the comparison in Figure \ref{fig:z-obs,z-rr,z-drr}.
+The zoomed data are highlighted by the red frame boxes shown in Figure \ref{fig:field-obs2d-0,field-rr2d0-0,field-drr2d-0}.
+The zoomed sections shown in Figure \ref{fig:z-obs,z-rr,z-drr} show a clearer comparison between the traditional and the proposed methods, and confirm that the proposed method can obtain a very clean and spatially coherent reconstruction result.
 
@@
 \inputdir{synth}
-\multiplot{5}{synth-clean-xy,synth-noisy-xy,synth-obs-xy,synth-rr-xy,synth-irr-xy}{width=0.29\textwidth}{Common offset 3D cubes comparison ($hx=5,hy=5$).
+\multiplot{5}{synth-clean-xy,synth-noisy-xy,synth-obs-xy,synth-rr-xy,synth-drr-xy}{width=0.29\textwidth}{Common offset 3D cubes comparison ($hx=5,hy=5$).
 (a) Clean synthetic data.
@@
 
-\multiplot{2}{synth-rr-xy-e,synth-irr-xy-e}{width=0.29\textwidth}{Reconstruction error comparison of common offset 3D cubes ($hx=5,hy=5$).
+\multiplot{2}{synth-rr-xy-e,synth-drr-xy-e}{width=0.29\textwidth}{Reconstruction error comparison of common offset 3D cubes ($hx=5,hy=5$).
 (a) Reconstruction error using the traditional approach.
@@
 
-\multiplot{5}{synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-irr-hxhy}{width=0.29\textwidth}{Common midpoint 3D cubes comparison ($x=5,y=5$).
+\multiplot{5}{synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-drr-hxhy}{width=0.29\textwidth}{Common midpoint 3D cubes comparison ($x=5,y=5$).
 (a) Clean synthetic data.
@@
 
-\multiplot{2}{synth-rr-hxhy-e,synth-irr-hxhy-e}{width=0.29\textwidth}{Reconstruction error comparison of common midpoint 3D cubes ($x=5,y=5$).
+\multiplot{2}{synth-rr-hxhy-e,synth-drr-hxhy-e}{width=0.29\textwidth}{Reconstruction error comparison of common midpoint 3D cubes ($x=5,y=5$).
 (a) Reconstruction error using the traditional approach.
@@
 
-\plot{synth-ss}{width=0.9\columnwidth}{Comparison of the middle trace amplitude of each cubes in Figure \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-irr-hxhy}.
+\plot{synth-ss}{width=0.9\columnwidth}{Comparison of the middle trace amplitude of each cubes in Figure \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-rr-hxhy,synth-drr-hxhy}.
 The black line is from the clean data.
@@
 \inputdir{hankel}
-\multiplot{4}{H_clean-0,H_obs-0,H_rr10-0,H_irr10-0}{width=0.45\textwidth}{26 Hz block Hankel matrix comparison.
+\multiplot{4}{H_clean-0,H_obs-0,H_rr10-0,H_drr10-0}{width=0.45\textwidth}{26 Hz block Hankel matrix comparison.
 (a) Hankel matrix of the clean data.
@@
 
-\multiplot{4}{H-z-clean,H-z-obs,H-z-rr10,H-z-irr10}{width=0.45\textwidth}{A close up look of the Hankel matrix (corresponding to the block Hankel matrix highlighted by the green frame box in Figure \ref{fig:H_clean-0,H_obs-0,H_rr10-0,H_irr10-0}.
+\multiplot{4}{H-z-clean,H-z-obs,H-z-rr10,H-z-drr10}{width=0.45\textwidth}{A close up look of the Hankel matrix (corresponding to the block Hankel matrix highlighted by the green frame box in Figure \ref{fig:H_clean-0,H_obs-0,H_rr10-0,H_drr10-0}.
 (a) Hankel matrix of the clean data.
@@
 
-\multiplot{4}{H_rr1-0,H_irr1-0,H-z-rr1,H-z-irr1}{width=0.45\textwidth}{26 Hz block Hankel matrix comparison after 1 iteration between two approaches.
+\multiplot{4}{H_rr1-0,H_drr1-0,H-z-rr1,H-z-drr1}{width=0.45\textwidth}{26 Hz block Hankel matrix comparison after 1 iteration between two approaches.
 (a) Hankel matrix of traditional method after 1 iteration.
@@
 \inputdir{synth}
-\multiplot{4}{synth-noisy-xy-simi,synth-obs-xy-simi,synth-rr-xy-simi,synth-irr-xy-simi}{width=0.32\textwidth}{Local similarity comparison of common offset 3D cubes comparison ($hx=5,hy=5$).
+\multiplot{4}{synth-noisy-xy-simi,synth-obs-xy-simi,synth-rr-xy-simi,synth-drr-xy-simi}{width=0.32\textwidth}{Local similarity comparison of common offset 3D cubes comparison ($hx=5,hy=5$).
 (a) Noisy synthetic data.
@@
 
-\multiplot{4}{synth-noisy-hxhy-simi,synth-obs-hxhy-simi,synth-rr-hxhy-simi,synth-irr-hxhy-simi}{width=0.32\textwidth}{Local similarity comparison of common midpoint 3D cubes ($x=5,y=5$).
+\multiplot{4}{synth-noisy-hxhy-simi,synth-obs-hxhy-simi,synth-rr-hxhy-simi,synth-drr-hxhy-simi}{width=0.32\textwidth}{Local similarity comparison of common midpoint 3D cubes ($x=5,y=5$).
 (a) Noisy synthetic data.
@@
 %    \label{fig:synth-rr-xy-simi}}   
-%    \subfigure[]{\includegraphics[width=0.29\textwidth]{synth/Fig/synth-irr-xy-simi}
-%    \label{fig:synth-irr-xy-simi}}           
+%    \subfigure[]{\includegraphics[width=0.29\textwidth]{synth/Fig/synth-drr-xy-simi}
+%    \label{fig:synth-drr-xy-simi}}           
 %	\caption{Local similarity comparison of common offset 3D cubes comparison %($hx=5,hy=5$).
@@
 (d) Reconstructed data using the proposed approach.}
- %  \label{fig:synth-noisy-xy-simi,synth-obs-xy-simi,synth-rr-xy-simi,synth-irr-xy-simi}
+ %  \label{fig:synth-noisy-xy-simi,synth-obs-xy-simi,synth-rr-xy-simi,synth-drr-xy-simi}
 %\end{figure}
@@
 %    \label{fig:synth-rr-hxhy-simi}}   
-%    \subfigure[]{\includegraphics[width=0.29\textwidth]{synth/Fig/synth-irr-hxhy-simi}
-%    \label{fig:synth-irr-hxhy-simi}}           
+%    \subfigure[]{\includegraphics[width=0.29\textwidth]{synth/Fig/synth-drr-hxhy-simi}
+%    \label{fig:synth-drr-hxhy-simi}}           
 %	\caption{Local similarity comparison of common midpoint 3D cubes ($x=5,y=5$).
@@
 (d) Reconstructed data using the proposed approach.}
-   %\label{fig:synth-noisy-hxhy-simi,synth-obs-hxhy-simi,synth-rr-hxhy-simi,synth-irr-hxhy-simi}
+   %\label{fig:synth-noisy-hxhy-simi,synth-obs-hxhy-simi,synth-rr-hxhy-simi,synth-drr-hxhy-simi}
 %\end{figure}
@@
 \inputdir{hyper}
-\multiplot{4}{hyper-clean2d-1,hyper-obs2d-1,hyper-rr2d-1,hyper-irr2d-1}{width=0.8\textwidth}{Common midpoint gather comparison (reshaped into a 2D matrix).
+\multiplot{4}{hyper-clean2d-1,hyper-obs2d-1,hyper-rr2d-1,hyper-drr2d-1}{width=0.8\textwidth}{Common midpoint gather comparison (reshaped into a 2D matrix).
 (a) Clean synthetic data with curved events.
@@
 
-\multiplot{4}{hyper-z-clean,hyper-z-obs,hyper-z-rr,hyper-z-irr}{width=0.45\textwidth}{Zoomed sections from Figure \ref{fig:hyper-clean2d-1,hyper-obs2d-1,hyper-rr2d-1,hyper-irr2d-1} (the green frame box).
+\multiplot{4}{hyper-z-clean,hyper-z-obs,hyper-z-rr,hyper-z-drr}{width=0.45\textwidth}{Zoomed sections from Figure \ref{fig:hyper-clean2d-1,hyper-obs2d-1,hyper-rr2d-1,hyper-drr2d-1} (the green frame box).
 (a) Clean data.
@@
 
-\multiplot{4}{hyper-z1-clean,hyper-z1-obs,hyper-z1-rr,hyper-z1-irr}{width=0.45\textwidth}{Zoomed sections from Figure \ref{fig:hyper-clean2d-1,hyper-obs2d-1,hyper-rr2d-1,hyper-irr2d-1} (the black frame box).
+\multiplot{4}{hyper-z1-clean,hyper-z1-obs,hyper-z1-rr,hyper-z1-drr}{width=0.45\textwidth}{Zoomed sections from Figure \ref{fig:hyper-clean2d-1,hyper-obs2d-1,hyper-rr2d-1,hyper-drr2d-1} (the black frame box).
 (a) Clean data.
@@
 
-\multiplot{3}{hyper-obs-simi,hyper-rr-simi,hyper-irr-simi}{width=0.8\textwidth}{Local similarity comparison with respect to the clean data.
+\multiplot{3}{hyper-obs-simi,hyper-rr-simi,hyper-drr-simi}{width=0.8\textwidth}{Local similarity comparison with respect to the clean data.
 (a) Similarity of the Observed synthetic data.
@@
 
-\inputdir{field}
-\multiplot{3}{field-obs2d-0,field-rr2d0-0,field-irr2d-0}{width=\textwidth}{Common offset gather comparison (reshaped into a 2D matrix).
+\inputdir{./}
+\multiplot{3}{field-obs2d-0,field-rr2d0-0,field-drr2d-0}{width=\textwidth}{Common offset gather comparison (reshaped into a 2D matrix).
 (a) Observed field data (with 80\% missing traces).
@@
 
-\multiplot{3}{z-obs,z-rr,z-irr}{width=0.45\textwidth}{Zoomed sections from Fig \ref{fig:field-obs2d-0,field-rr2d0-0,field-irr2d-0}.
+\multiplot{3}{z-obs,z-rr,z-drr}{width=0.45\textwidth}{Zoomed sections from Fig \ref{fig:field-obs2d-0,field-rr2d0-0,field-drr2d-0}.
 (a) Observed field data.
@@
 
-%\multiplot{3}{field-obs2d-h,field-rr2d-h,field-irr2d-h}{width=0.8\textwidth}{Common midpoint 3D cubes comparison.
+%\multiplot{3}{field-obs2d-h,field-rr2d-h,field-drr2d-h}{width=0.8\textwidth}{Common midpoint 3D cubes comparison.
 (a) Observed field data (with 80\% missing traces).
@@
 \bibliographystyle{seg}
-\bibliography{irr}
+\bibliography{drr}

### 2020-11-01 drr5d/matfun/Hyper.m

@@ -21,7 +21,7 @@ function Hyper(clean,noisy,obs,rr,drr)
 %  along with this program; if not, write to the Free Software
 %  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  
 % 
-%  Reference:   Chen et al., GJI, 2016
+%  Reference:   Chen et al., GJI, 2016; Chen et al., GJI, 2020
 
 %% load data
 load yc_hyper5d.mat

### 2020-11-01 drr5d/matfun/SNRS_SIGMA.m

@@ -131,6 +131,7 @@ snrs2=[snr1_2 snr2_2 snr3_2 snr4_2 snr5_2 snr6_2];
 %plot(vars,snrs2,'bv');
 
 %% from Matlab to Madagascar
+snrs=[vars',snrs1',snrs2'];
 rsf_create(synth_drr_snrs,size(snrs)');
 rsf_write(snrs,synth_drr_snrs);
 

### 2020-11-01 drr5d/matfun/drr5d_lb_recon_H.m

@@ -34,9 +34,13 @@ function [ D1,H,H0,H1,H2] = drr5d_lb_recon_H(D,D_true,MASK,flow,fhigh,Hf,dt,N,NN
 %  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
 %  GNU General Public License for more details: http://www.gnu.org/licenses/
 %
-%  Reference:   Chen et al, 2016;Chen et al, 2020. 
-%
-% Example: test_lr_5d_recon_H.m
+%  [1] Bai et al., 2020, Seismic signal enhancement based on the lowrank methods, Geophysical Prospecting, 68, 2783-2807.
+%  [2] Chen et al., 2020, Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method, Geophysical Journal International, 222, 1824-1845.
+%  [3] Chen, Y., W. Huang, D. Zhang, W. Chen, 2016, An open-source matlab code package for improved rank-reduction 3D seismic data denoising and reconstruction, Computers & Geosciences, 95, 59-66.
+%  [4] Chen, Y., D. Zhang, Z. Jin, X. Chen, S. Zu, W. Huang, and S. Gan, 2016, Simultaneous denoising and reconstruction of 5D seismic data via damped rank-reduction method, Geophysical Journal International, 206, 1695-1717.
+%  [5] Huang, W., R. Wang, Y. Chen, H. Li, and S. Gan, 2016, Damped multichannel singular spectrum analysis for 3D random noise attenuation, Geophysics, 81, V261-V270.
+%  [6] Chen et al., 2017, Preserving the discontinuities in least-squares reverse time migration of simultaneous-source data, Geophysics, 82, S185-S196.
+%  [7] Chen et al., 2019, Obtaining free USArray data by multi-dimensional seismic reconstruction, Nature Communications, 10:4434.
 
 if nargin==0
     error('Input data must be provided!');

### 2020-11-02 odrr5d/paper.tex
2020年11月 2日 星期一 15时33分23秒 CST

\published{Geophysical Journal International, 222, 1824–1845, (2020)}

\title{Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method}
\author{Yangkang Chen\footnotemark[1], Min Bai\footnotemark[1], Zhe Guan\footnotemark[2], Qingchen Zhang\footnotemark[1], Mi Zhang\footnotemark[3], and Hang Wang\footnotemark[1]}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

%\author{Yangkang Chen\footnotemark[1] et al.}

\ms{GJI-2020} %\ms{GJI-2018}

\address{
\footnotemark[1]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
yangkang.chen@zju.edu.cn \\
%908352517@qq.com (hang)
\footnotemark[2]
Applied Physics Program\\
Rice University\\
Houston, TX, USA\\
%zg10@rice.edu
Zhe.Guan@rice.edu\\
\footnotemark[3]State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
cupmi@sina.com \\
}

\lefthead{Chen et al., 2019}
\righthead{ORR}

\begin{abstract}
\old{We continue our previous work on simultaneous denoising and reconstruction of five-dimensional seismic data and propose a new algorithm, which is called optimal rank reduction method.} \old{The traditional rank reduction method is difficult to separate noise from signal by a typical truncated singular value decomposition (TSVD) strategy due to the mixture of the signal and the noise subspaces after the decomposition.} \new{It is difficult to separate additive random noise from spatially coherent signal using a rank-reduction method that is based on the truncated singular value decomposition (TSVD) operation. This problem is due to the mixture of the signal and the noise subspaces after the TSVD operation.} This drawback can be partially conquered \old{via}\new{using} a damped rank reduction method, where the singular values corresponding to effective signals are adjusted via a carefully designed damping operator. The damping operator works most powerfully in the case of a small rank and a small damping factor. However, for complicated seismic data, \new{e.g., multi-channel reflection seismic data containing highly curved events}, the rank should be large enough to preserve the details in the data, which makes the damped rank reduction method less effective. In this paper, we develop an optimal \old{weighting}\new{damping} strategy for adjusting the singular values \new{when a large rank parameter is selected} so that the estimated signal can best approximate the exact signal. \old{The optimal weighting strategy is inspired by the random matrix theory and can compute the optimal weighting coefficients directly from the observed data.}\new{We first weight the singular values using optimally calculated weights. The weights are theoretically derived by solving an optimization problem that minimizes the Frobenius-norm difference between the approximated signal components and the exact signal components. The damping operator is then derived based on the initial weighting operator to further reduce the residual noise after the optimal weighting. The resulted optimally damped rank reduction method is nearly an adaptive method, i.e., insensitive to the rank parameter.} We demonstrate the performance of the \old{optimal rank reduction method}\new{proposed method} on a group of synthetic and real five-dimensional seismic data.  \\
\textbf{Keywords}\\
Seismic noise, image processing, time-series analysis
\end{abstract}
%\section{Keywords}
%key1,key2,key3

\section{Introduction}
With the increasing demand for exploration accuracy, wide azimuth seismic (WAZ) exploration technology has received more and more attention and development. The seismic data obtained by WAZ acquisition contains rich wavefield information with high illumination \cite[]{yangkang20142,shuwei2016vscan,shaohuan2017gji,kim2017efficient,lu2017coal,tian2017characteristics,fly2017jse,kirchdepth2017jse,qushan2017eage,chenwei2018,qingchen2018gji,qingchen2018tgrs,yufeng2018geo}. However, due to the influence of surface environments, the shot, receiver, azimuth and offset of the original data tend to be unevenly distributed, which is adverse to the subsequent processing and interpretation such as migration, pre-stack attribute analysis, reservoir prediction and fluid identification. Seismic data interpolation is such a processing step to regularize the irregularly sampled seismic traces onto regular grids \cite[]{fomel2003,yangkang2016irr5d,shaohuan2016seg,yatong2018dbi,zhangdong2016seg,yangkang2016fwieage,yangkang2016fwi,zhangdong2016cseg,zhangdong2016eage}. In the past decades, a number of methods have been developed to reconstruct the missing seismic traces on regular grids. One widely used seismic reconstruction strategy is to transform the noisy seismic data into different domains in order to concisely represent the signal with a few number of selected components that capture the useful information and recover the missing components. These include the methods based on the Fourier transform \cite[]{yatong2017pocs,baimin2018jse2}, Radon transform \cite[]{beylkin1987discrete}, seislet transform \cite[]{shuwei20153,shuwei2015seg1,shuwei2015seg2,liuwei2016dealiase,zhiguang2017fwi,yatong2018seis,yatong2018jse,yangkang2018eseis,baimin2019jse1}, curvelet transform \cite[]{jianwei20093,candes20061,shaohuan2015,shaohuan2016seg2}, dreamlet transform \cite[]{benfengpocs}, wavelet transform \cite[]{rioul1991wavelets,gilles2013,xieqian2015eage,liuwei2016,mostafa2016bssa}, dictionary-learning based adaptive transform \cite[]{yangkang2016dsd,amir2017ieee,amir2017sp,amir2017geo,wujuan2018jge2,wujuan2018cg1,shaohuan2019ieee,shaohuan2019dl}. Another type of methods utilize the predictable property of seismic data. In the prediction-based approaches, a prediction error filter is designed such that the predicted data and the existing data have the minimum misfit by solving a least-squares linear inverse problem \cite[]{spitz1991,fomel2002pwd,yangkang2016irr5d}.  Considering the aliasing issue in reconstructing regularly sampled seismic data, a prediction error filter is first estimated from the aliasing-free low-frequency components and then applied to aliased high-frequency components \cite[]{mostafa2007}. The wave equation based methods can also be used to reconstruct highly incomplete seismic data. These methods connect the seismic record and the subsurface elastic properties via the elastic wave equation. However, these methods depend on a prior information about the subsurface elastic properties and are strictly not data-driven methods. In addition, these methods suffer from losing computational efficiency when applied in the interpolation methods \cite[]{ronen,canning1996,fomel2003}. A review of the latest methods on reconstructing low-dimensional seismic data is given in \cite{yangkang2019sg}.

However, the amplitude and phase variations of the WAZ seismic data are often not accurately recovered by conventional three-dimensional data reconstruction. More accurate reconstruction results can be obtained by simultaneously interpolating in five dimensions of inline, crossline, time, azimuth and offset because sampling along any particular subset of all dimensions is often less than ideal. The pre-stack seismic gathers processed by the five-dimensional (5D) interpolation have higher quality, which can not only improve the imaging accuracy, but also improve the capabilities of fracture prediction and fluid identification. Therefore, a large number of 5D seismic data reconstruction methods and techniques have emerged in the past decade.

The minimum weighted norm interpolation (MWNI) is a constrained inversion algorithm that was successfully applied to 5D seismic data interpolation \citep{Liubin2004, Trad2007, Trad2009}. \cite{Trad2007} employed this algorithm to regularize the data in the inline-crossline-azimuth-offset frequency domain and obtained pre-stack interpolated results for the migration input. This work proved that the results after 5D interpolation help to improve the fidelity of the migration, which laid the foundation for the subsequent promotion of five-dimensional seismic data reconstruction. \cite{Downton2008} confirmed the validity of the MWNI for 5D interpolation and found that the 5D interpolation can preserve the amplitude and improve the signal-to-noise ratio. The MWNI did successfully interpolate sparse data and reduced migration artifacts \citep{Trad2009}, but it had difficulty to deal regularly missing data with spatial aliasing. Chiu (2012) proposed an anti-aliasing MWNI method to improve the deficiency of conventional MWNI in processing aliased data. 
In addition, some other multidimensional interpolation algorithms are also available for the five dimensions \citep{Chopra2013}. \cite{Jin2010} proposed a 5D interpolation method based on a damped least-norm Fourier inversion (DLNFI). Benefiting from the use of nonuniform discrete Fourier transform, DLNFI breaks the limitation in MWNI that the input data must be binned into the regular grid.

Another alternative 5D interpolation method utilizes wavefront attributes such as wavefront curvatures and propagation angles. \cite{Xie2017} proposed a wavefront-attribute-based 5D interpolation (5D WABI) via a global optimization strategy instead of pragmatic search approach, which can take advantage of the wide, rich, or full azimuth acquisitions. Application on a synthetic seismic data have shown that the 5D WABI method is better at preserving diffractions than the damped rank-reduction method but at the expense of significantly lower computational efficiency.
In recent years, dictionary learning and machine learning are applied to the reconstruction of 5D simple data \citep{YuSiwei2015, Jia2017, Jia2018}. Data driven tight frame (DDTF) is a kind of dictionary-learning method, which can simultaneously denoise and interpolate 5D seismic data \citep{YuSiwei2015}. In DDTF, a sparsity-promoting algorithm is used to build the dictionary which can represent the observed data and estimate the complete data. \cite{Jia2017} combined the DDTF with a classic machine learning method named support vector regression (SVR) to optimize the learning, which obtained better performance than the Gauss SVR method. With the continuous improvement of intelligent methods, learning-based 5D data reconstruction will be a hot research topic in the future.

Rank-reduction based algorithms have great potentials for 5D seismic data interpolation. \old{The starting point is that the fully sampled noise-free seismic data can be characterized as a low-rank matrix or tensor and the rank of the matrix or tensor increases when the missing traces and noise occur.}
\new{The basic assumption of these methods is that the fully sampled noise-free seismic data can be characterized as a low-rank matrix or tensor and the rank of the matrix or tensor increases when there are missing traces or noise in the data \cite[]{yatong2018gji}. The missing traces denote the zero-value seismic traces when the seismic data is binned from irregular station positions to regular grids.} 
By solving a low-rank tensor completion problem via convex optimization, the missing traces can be accurately recovered with the information of all dimensions \citep{Kreimer2013}. In addition, this method has stronger denoising ability than the previous methods. From other perspectives of rank minimization, \cite{Ely2015} estimated the complete data tensor via tensor singular value decomposition (SVD) and parallel matrix factorization, respectively. Subsequently, \cite{GaoJianjun2017} further developed a new and fast low-rank tensor completion method based on parallel square matrix factorization and advocated that reshaping the complete data tensor into almost square or square matrices can improve the reconstruction quality. However, when the signal-to-noise ratio of the observed seismic data is very low, \old{conventional}\new{the Cadzow} rank-reduction method\old{s} via truncated singular value decomposition (TSVD) do\new{es} not achieve \old{perfect}\new{reasonable} reconstruction result\old{, which is still filled with a large amount of residual noise}\new{, i.e., the result may still contains a large amount of residual noise}. \cite{yangkang2016irr5d} proposed a damped rank-reduction method to further suppress the residual noise by introducing a damping operator to the block Hankel matrix after TSVD. In the 5D reconstruction of field seismic data, the damped rank-reduction method achieved better performance than the \old{traditional }Cadzow rank-reduction method \citep{Trickett2009, mssa}. \new{Throughout the paper, the Cadzow rank-reduction method is referred to as the traditional rank-reduction method.}

The basic assumption of the rank-reduction methods is that the Hankel matrix formulated from the useful seismic signal is of low rank and its rank is equal to the number of linear/planar events (or dipping components) in the seismic data \cite[]{mssa,weilin2016,amir2017grsl,yangkang2017lsrtm,yatong2018inter,wujuan2018jge1,wujuan2018jse1,wujuan2018jge3,baimin2018jse1,baimin2018cg,baimin2019jag,wujuan2019jse1}. However, in general the real seismic data is composed of nonlinear events, which are more complicated than the linear events. A common strategy for addressing this issue is to implement the algorithm in local patches since the events can be approximately viewed as linear in small patches \cite[]{zhangdong2017}. However, this strategy poses another difficulty of choosing an appropriate rank for each local processing window.  A practical implementation of the rank-reduction method may require the predefined rank to be relatively large in order to avoid the damage of useful signal due to inappropriate assumption of the structural complexity. This conservative selection of rank would make the resulted data contain a significant amount of residual noise. \old{In this paper, we develop an adaptive singular value weighting method by solving an optimization problem, by which we can suppress the strong residual noise even when using a large rank.}\new{In this paper, we develop a relatively adaptive rank-reduction method, by which we can suppress the strong residual noise even when using a large rank. We first calculate a set of optimal weighting coefficients to weight the singular values as a first step by solving an optimization problem that minimizes the Frobenius-norm difference between the approximated signal components and the exact signal components.} The rank-reduction method based on the optimal weighting strategy can be further improved when connected with the damped rank-reduction method. The resulted method is named as the \old{optimal}\new{optimally damped} rank-reduction method, and can \old{hopefully}\new{potentially} provide the \old{optimal}\new{best} solution to the rank-reduction based high-dimensional seismic reconstruction problem in an adaptive way. We will use comprehensive numerical tests and detailed analysis to demonstrate the superiority of the presented algorithm based on several synthetic examples and a real seismic data.

\section{Theory}
\subsection{Construction of the block Hankel matrix for 5-D seismic data}
Let $D(t,hx,hy,x,y)$ denote the 5-D seismic data in the time domain, and $D(f,hx,hy,x,y)$ be the data in the frequency domain. For notation convenience, we omit $f$ in the following context and use $D_{k1,k2,k3,k4}$ to denote $D(f,hx,hy,x,y)$. The \new{traditional} rank-reduction based methods require the construction of a level-four block Hankel matrix for 5-D seismic data to meet the low-rank assumption. \new{A level-four block Hankel matrix means that we treat a series of level-three block Hankel matrix as elements and arrange them into a Hankel matrix. In a similar way, a level-three block Hankel matrix is constructed from a series of level-two block Hankel matrices while a level-two block Hankel matrix is formed from several standard Hankel matrices. }

The level-four block Hankel matrix has the following explicit expression:
\begin{equation}
\label{eq:levelfour}
\mathbf{H}^{(4)}=\left(\begin{array}{cccc}
\mathbf{H}_{1}^{(3)} & \mathbf{H}_{2}^{(3)} & \cdots & \mathbf{H}_{X_4-Y_4+1}^{(3)} \\
\mathbf{H}_{2}^{(3)} & \mathbf{H}_{3}^{(3)}  &\cdots & \mathbf{H}_{X_4-Y_4+2}^{(3)} \\
\vdots & \vdots &\ddots &\vdots \\
\mathbf{H}_{Y_4}^{(3)}&\mathbf{H}_{Y_4+1}^{(3)} &\cdots& \mathbf{H}_{X_4}^{(3)}
\end{array}
\right),
\end{equation}
where 
\begin{equation}
\label{eq:levelthree}
\mathbf{H}_{k4}^{(3)}=\left(\begin{array}{cccc}
\mathbf{H}_{1,k4}^{(2)} & \mathbf{H}_{2,k4}^{(2)} & \cdots &\mathbf{H}_{X_3-Y_3+1,k4}^{(2)} \\
\mathbf{H}_{2,k4}^{(2)} & \mathbf{H}_{3,k4}^{(2)}  &\cdots &\mathbf{H}_{X_3-Y_3+2,k4}^{(2)} \\
\vdots & \vdots &\ddots &\vdots \\
\mathbf{H}_{Y_3,k4}^{(2)}&\mathbf{H}_{Y_3+1,k4}^{(2)} &\cdots&\mathbf{H}_{X_3,k4}^{(2)}
\end{array}
\right),
\end{equation}
and 
\begin{equation}
\label{eq:leveltwo}
\mathbf{H}_{k3,k4}^{(2)}=\left(\begin{array}{cccc}
\mathbf{H}_{1,k3,k4}^{(1)} & \mathbf{H}_{2,k3,k4}^{(1)} & \cdots &\mathbf{H}_{X_2-Y_2+1,k3,k4}^{(1)} \\
\mathbf{H}_{2,k3,k4}^{(1)} & \mathbf{H}_{3,k3,k4}^{(1)}  &\cdots &\mathbf{H}_{X_2-Y_2+2,k3,k4}^{(1)} \\
\vdots & \vdots &\ddots &\vdots \\
\mathbf{H}_{Y_2,k3,k4}^{(1)}&\mathbf{H}_{Y_2+1,k3,k4}^{(1)} &\cdots&\mathbf{H}_{X_2,k3,k4}^{(1)}
\end{array}
\right),
\end{equation}
and

\begin{equation}
\label{eq:levelone}
\mathbf{H}_{k2,k3,k4}^{(1)}=\left(\begin{array}{cccc}
D_{1,k2,k3,k4} & D_{2,k2,k3,k4} & \cdots &D_{X_1-Y_1+1,k2,k3,k4} \\
D_{2,k2,k3,k4} & D_{3,k2,k3,k4}  &\cdots &D_{X_1-Y_1+2,k2,k3,k4} \\
\vdots & \vdots &\ddots &\vdots \\
D_{Y_1,k2,k3,k4}&D_{Y_1+1,k2,k3,k4} &\cdots&D_{X_1,k2,k3,k4}
\end{array}
\right).
\end{equation}

In order to make all target matrices (from equation \ref{eq:levelfour} to \ref{eq:levelone}) close to square matrices, parameters $Y_i$ are defined as $\lfloor \frac{X_i}{2} \rfloor +1$, $i=1,2,3,4$, where $X_i$ denotes the size of the $i$th dimension. Here, $\lfloor\cdot\rfloor$ denotes the integer part of an input argument.

The process of transforming a four-dimensional hypercube $D_{k1,k2,k3,k4}$ to the block Hankel matrix $\mathbf{H}^{(4)}$ is referred to as the Hankelization process. We can briefly denote this process as: 
\begin{equation}
\label{eq:hankel}
\mathbf{H}^{(4)}=\mathcal{H}D_{k1,k2,k3,k4}.
\end{equation}

Another important step in the rank-reduction based method is the rank reduction process, which can be denoted as $\mathcal{F}$.

Reconstructing the missing data aims at solving \old{this problem}\new{the following equation}:
\begin{equation}
\label{eq:inv}
\mathcal{S} \circ \mathbf{M} = \mathbf{M}_{0},
\end{equation}
where $\mathcal{S}$ is a sampling matrix, $\mathbf{M}=\mathbf{H}^{(4)}$, and $\mathbf{M}_{0}$ denotes the block Hankel
matrix with missing entries. $\circ$ denotes element-wise product.

Equation \ref{eq:inv} is seriously ill-posed and the low-rank assumption is applied to constrain the model,
\begin{equation}
\label{eq:inv2}
\begin{split}
\min_{\mathbf{M}} &\parallel \mathcal{S} \circ \mathbf{M}-\mathbf{M}_{0}\parallel_F, \\
\text{s.t.}&\quad \text{rank}(\mathbf{M})=N.
\end{split}
\end{equation}
\new{$\parallel \cdot \parallel_F$ denotes the Frobenius norm of an input matrix. The constraint in equation \ref{eq:inv2} means that we constrain the rank of the block Hankel matrix to be $N$.}

The problem expressed in equation \ref{eq:inv2} can be solved via the following iterative solver:
\begin{equation}
\label{eq:iter}
\mathbf{M}_n=a_n \mathbf{M}_{0} + (1-a_n\mathcal{S})\circ \mathcal{F}\mathbf{M}_{n-1},
\end{equation}
$a_n$ is an iteration-dependent scalar that linearly decreases from $a_1=1$ to $a_{n_{max}}=0$. $a_n$ is used to alleviate the influence of random noise existing in the observed data.

\subsection{Optimal weighting for rank reduction}
The observed data $\mathbf{M}$ can be expressed as:
\begin{equation}
\label{eq:msn}
\mathbf{M}=\mathbf{S}+\mathbf{N},
\end{equation}
where $\mathbf{S}$ and $\mathbf{N}$ denote the signal and noise components. \new{It is worth noting that for the derivation convenience, we assume the noise component $\mathbf{N}$ to be white. Although not exactly correct for seismic data, the denoising model also works for seismic data with band-limited noise.} In the following analysis, we assume $\mathbf{M}$ and $\mathbf{N}$ have full rank and $\mathbf{S}$ has deficient rank. $\mathbf{M}$, $\mathbf{S}$ and $\mathbf{N}$ are all of size $I\times J$.

The singular value decomposition (SVD) of $\mathbf{S}$ can be represented as:
\begin{equation}
\label{eq:svds_a}
\mathbf{S} = [\mathbf{U}_1^{S}\quad \mathbf{U}_2^{S}]\left[\begin{array}{cc}
\boldsymbol{\Sigma}_1^{S} & \mathbf{0}\\
\mathbf{0} & \boldsymbol{\Sigma}_2^{S}
\end{array}
\right]\left[\begin{array}{c}
(\mathbf{V}_1^{S})^H\\
(\mathbf{V}_2^{S})^H
\end{array}
\right].
\end{equation}
Because of the deficient rank, the matrix $\mathbf{S}$ can be written as:
\begin{equation}
\label{eq:S_a}
\mathbf{S}=\mathbf{U}_1^S\boldsymbol{\Sigma}_1^S(\mathbf{V}_1^S)^H.
\end{equation}

The singular value decomposition (SVD) of $\mathbf{M}$ can be represented as:
\begin{equation}
\label{eq:svdm_a}
\mathbf{M} = [\mathbf{U}_1^{M}\quad \mathbf{U}_2^{M}]\left[\begin{array}{cc}
\boldsymbol{\Sigma}_1^{M} & \mathbf{0}\\
\mathbf{0} & \boldsymbol{\Sigma}_2^{M}
\end{array}
\right]\left[\begin{array}{c}
(\mathbf{V}_1^{M})^H\\
(\mathbf{V}_2^{M})^H
\end{array}
\right].
\end{equation}
The rank-reduction method by TSVD refers to 
\begin{equation}
\label{eq:M_a}
\tilde{\mathbf{M}}=\mathbf{U}_1^M\boldsymbol{\Sigma}_1^M(\mathbf{V}_1^M)^H.
\end{equation}
Here, $\tilde{\mathbf{M}}$ is the estimated signal component via TSVD. We assume the \old{appealing rank}\new{rank} of $\mathbf{M}$ is $N$, and thus the size of $\mathbf{U}_1^M$ is $I\times N$. $\boldsymbol{\Sigma}_1^M$ is of size $N\times N$. $\mathbf{V}_1^M$ is of size $J\times N$.

However, the $\tilde{\mathbf{M}}$ is still a mixture of the signal and noise subspaces. Combining equations \ref{eq:msn}, \ref{eq:svds_a}, and \ref{eq:S_a}, it is easy to derive that \cite[]{yangkang2016irr5d}
\begin{equation}
\label{eq:msn2}
\tilde{\mathbf{M}}=\mathbf{S}+\mathbf{U}_1^S(\mathbf{U}_1^S)^H\mathbf{N},
\end{equation}
where we can see that the estimated signal component via TSVD is still corrupted by the noise component, which is the projection of the noise component to the signal component.

This problem can be partially alleviated by a singular value thresholding step:
\begin{equation}
\label{eq:M_a}
\tilde{\tilde{\mathbf{M}}}=\mathbf{U}_1^M\tilde{\boldsymbol{\Sigma}}_1^M(\mathbf{V}_1^M)^H,
\end{equation}
where $\tilde{\boldsymbol{\Sigma}}_1^M$ is the thresholded singular values such that:
\begin{equation}
\label{eq:thr}
\tilde{\boldsymbol{\Sigma}}_1^M = \mathbf{T}(\boldsymbol{\Sigma}_1^M,\tau).
\end{equation}
where $\mathbf{T}$ denotes a singular value thresholding operator and $\tau$ denotes the threshold. However, defining an optimal threshold is inconvenient and sometimes even difficult. It is because the noise component contributes differently to each singular value and a constant threshold is not plausible to deal with the inhomogeneous noise distribution.

Thus, in this paper, we propose an adaptive weighting algorithm to optimally define the singular values in order to best reconstruct the signal component. We introduce a weighting operator $\mathbf{W}$ to adjust the $\boldsymbol{\Sigma}_1^M$ after applying SVD to the observed noisy signal. To calculate the optimal weighting operator is equivalent to solving the following optimization problem:
\begin{equation}
\label{eq:opt}
\hat{\mathbf{W}} = \arg \min_{\mathbf{W}} \parallel \mathbf{U}_1^S\boldsymbol{\Sigma}_1^S(\mathbf{V}_1^S)^H - \mathbf{U}_1^M\mathbf{W}\boldsymbol{\Sigma}_1^M(\mathbf{V}_1^M)^H \parallel_F.
\end{equation}
By an optimally weighted combination of estimated left and right singular vectors, the optimization problem \ref{eq:opt} can yield the optimally adjusted singular values to obtain the closest low-rank estimates of signal component.

The optimal solution for the optimization problem was given in \cite{Benaych2012The} and \cite{optshrink2013}:
\begin{equation}
\label{eq:optW}
\hat{\mathbf{W}} = \text{diag}(\hat{w}_1,\hat{w}_2,\cdots,\hat{w}_N),
\end{equation}
where
\begin{equation}
\label{eq:optw}
\hat{w}_i=\left(-\frac{2}{\sigma_i^M}\frac{D(\sigma_i^M;\boldsymbol{\Sigma})}{D'(\sigma_i^M;\boldsymbol{\Sigma})}\right).
\end{equation}
$\sigma_i^M$ denotes the $i$th diagonal entry of $\boldsymbol{\Sigma}_1^M$ ($\boldsymbol{\Sigma}_1^M\in\mathbb{R}^{N\times N}$). $D$ denotes the D-transform:
\begin{equation}
\label{eq:D1}
\begin{split}
D(\sigma;\boldsymbol{\Sigma})&= \frac{1}{N} \text{Tr}\left(\sigma(\sigma^2\mathbf{I}-\boldsymbol{\Sigma}\boldsymbol{\Sigma}^H)^{-1}\right)\frac{1}{N} \text{Tr}\left(\sigma(\sigma^2\mathbf{I}-\boldsymbol{\Sigma}^H\boldsymbol{\Sigma})^{-1}\right)\\
&=\left[\frac{1}{N} \text{Tr}\left(\sigma(\sigma^2\mathbf{I}-\boldsymbol{\Sigma}^2)^{-1}\right)\right]^2
\end{split},
\end{equation}
where $D'$ is the derivative of $D$ with respect to $\sigma$, and $\text{Tr}(\cdot)$ is the trace of the input:
\begin{equation}
\label{eq:D2}
\begin{split}
D'(\sigma;\boldsymbol{\Sigma})&= 2\left[\frac{1}{N} \text{Tr}\left(\sigma(\sigma^2\mathbf{I}-\boldsymbol{\Sigma}^2)^{-1}\right)\right]\left[\frac{1}{N} \text{Tr}\left((\sigma^2\mathbf{I}-\boldsymbol{\Sigma}^2)^{-1}-2\sigma(\sigma^2\mathbf{I}-\boldsymbol{\Sigma}^2)^{-2}\sigma\right)\right] \\
&=\frac{2}{N^2}\left[ \text{Tr}\left(\sigma(\sigma^2\mathbf{I}-\boldsymbol{\Sigma}^2)^{-1}\right)\right]\left[ \text{Tr}\left((\sigma^2\mathbf{I}-\boldsymbol{\Sigma}^2)^{-1}-2\sigma^2(\sigma^2\mathbf{I}-\boldsymbol{\Sigma}^2)^{-2}\right)\right].
\end{split}
\end{equation}
Using the optimally estimated weighting operator expressed in equation \ref{eq:optW}, we can expressed the optimally estimated signal component as:
\begin{equation}
\label{eq:M_a}
\hat{\mathbf{M}}=\mathbf{U}_1^M\hat{\mathbf{W}}\boldsymbol{\Sigma}_1^M(\mathbf{V}_1^M)^H.
\end{equation}

\new{The optimal weighting strategy of the singular values is a substitute to directly truncating the singular values as used in the traditional rank-reduction method. An early investigation of the strategy to improve the rank-reduction performance in seismic data denoising and reconstruction is presented in \cite{aharchaou2017singular}. Besides, there are also a number of alternatives to these two approaches (weighting and truncating) such as  automatic rank determination \cite[]{gavish2014optimal,trickett2015preserving} and randomized approaches such as the randomized SVD and randomized QR factorizations \cite[]{jinkun2016}.}

\new{\subsection{Optimally damped rank-reduction method}}
\new{In this section, we will derive a damping operator for the optimally estimated signal components to further reduce the residual noise after rank reduction.}
Let 
\begin{equation}
\label{eq:svds_q}
\mathbf{Q} = [\mathbf{U}_1^{Q}\quad \mathbf{U}_2^{Q}]\left[\begin{array}{cc}
\boldsymbol{\Sigma}_1^{Q} & \mathbf{0}\\
\mathbf{0} & \boldsymbol{\Sigma}_2^{Q}
\end{array}
\right]\left[\begin{array}{c}
(\mathbf{V}_1^{Q})^H\\
(\mathbf{V}_2^{Q})^H
\end{array}
\right].
\end{equation} to be an SVD of matrix $\mathbf{Q}$,
and let
\begin{align}
\label{eq:svds_qu}
\mathbf{U}_1^{Q} = \mathbf{U}_1^{M},\\
\label{eq:svds_qs}
\boldsymbol{\Sigma}_1^{Q} = \hat{\mathbf{W}}\boldsymbol{\Sigma}_1^{M},\\
\label{eq:svds_qv}
\mathbf{V}_1^{Q} = \mathbf{V}_1^{M},
\end{align}
then equation \ref{eq:M_a} can be understood as a TSVD of the matrix $Q$:
\begin{equation}
\label{eq:tsvdq}
\tilde{\mathbf{Q}}=\mathbf{U}_1^{Q}\boldsymbol{\Sigma}_1^{Q}{\mathbf{V}_1^{Q}}^H.
\end{equation}
 Analogous to equation \ref{eq:msn2}, 
equation \ref{eq:M_a} can be re-formulated as 
\begin{equation}
\label{eq:M_a3}
\tilde{\mathbf{Q}}=\hat{\mathbf{M}}=\tilde{\mathbf{S}}+\mathbf{U}_1^{\tilde{\mathbf{S}}}{\mathbf{U}_1^{\tilde{\mathbf{S}}}}^H\tilde{\mathbf{N}},
\end{equation}

When the \old{appealing rank}\new{rank} is sufficiently large, we assume the estimated signal contains all signal components of the originally observed noisy data and contains less noise than the observed data. To further suppress the residual noise in the estimated signal, we re-analyze $\hat{\mathbf{M}}$ in detail. We can express the newly estimated signal as:
\begin{equation}
\label{eq:M_a2}
\tilde{\mathbf{Q}}=\hat{\mathbf{M}}=\mathbf{S}+\mathbf{U}_1^{S}{\mathbf{U}_1^{S}}^H\tilde{\mathbf{N}},
\end{equation}
where $\mathbf{U}_1^{S}{\mathbf{U}_1^{S}}^H\tilde{\mathbf{N}}$ denotes the residual noise component after the step using equation \ref{eq:M_a}.

Following \cite{yangkang2016irr5d} and \cite{weilin2016}, $\mathbf{S}$ can be approximated as:
\begin{align}
\label{eq:S3}
\mathbf{S} &= \mathbf{U}_1^{Q}\boldsymbol{\Sigma}_1^{Q}\mathbf{T}\left(\mathbf{V}_1^{Q}\right)^H,\\
\label{eq:T}
\mathbf{T} &= \mathbf{I}-\boldsymbol{\Gamma},
\end{align}
where $\mathbf{I}$ is a unit matrix and here we name $\mathbf{T}$ the damping operator. The damping relation $\boldsymbol{\Gamma}$ is expressed as:
\begin{equation}
\label{eq:Gamma}
\boldsymbol{\Gamma} \approx \hat{\delta}^N\left(\boldsymbol{\Sigma}_1^{Q}\right)^{-N},
\end{equation}
where $\hat{\delta}$ denotes the maximum element of $\boldsymbol{\Sigma}_2^{Q}$ and $N$ denotes the damping factor.

Considering that $\mathbf{U}_1^{Q} = \mathbf{U}_1^{M}$, $\boldsymbol{\Sigma}_1^{Q}= \hat{\mathbf{W}}\boldsymbol{\Sigma}_1^{M}$, and $\mathbf{V}_1^{Q} = \mathbf{V}_1^{M}$,  equation \ref{eq:S3} can be expressed as:
\begin{align}
\label{eq:S33}
\mathbf{S} = \mathbf{U}_1^{M} \mathbf{T} \hat{\mathbf{W}}\boldsymbol{\Sigma}_1^{M} \left(\mathbf{V}_1^{M}\right)^H,
\end{align}
which is referred to as the \old{optimal rank reduction}\new{optimally damped rank reduction} method. The $\mathcal{F}$ can thus be chosen as the operation defined in equation \ref{eq:S33}, and through iterations we can reconstruct and denoise the 5D frequency-domain seismic data.

\new{There are two main advantages of the optimally damped rank reduction method.  First, compared with the traditional and damped rank-reduction methods, the optimally damped rank reduction method is insensitive to the rank parameter, making it nearly an adaptive method for rank reduction based seismic denoising and reconstruction. This advantage is important because one of the most troublesome problems in processing complicated seismic data is the selection of the rank. A large rank tends to result in significant residual noise while a small rank tends to damage useful signals. This parameterization problem becomes more seriously when the rank reduction method is applied locally in windows. Because of the insensitivity to rank of the proposed method, one can choose a relatively large rank for all complicated datasets or local patches. Secondly, compared with the optimal weighting based rank reduction method, the proposed method can further suppress the noise components that reside mostly in the smaller singular values. The damping operator is data-driven and can adaptively separate signal and noise in the singular value spectrum further after the optimal weighting.  }

\new{In the rank-reduction methods, construction of the level-four Hankel matrix is very computationally expensive.  Recent advances in the rank reduction based methods show that the construction of the block Hankel matrix is not required. These methods exploit the structure of such matrices to avoid explicitly forming these matrices prior to factorization \cite[]{lu2015fast,cheng2016fast}. When factorizing data using only 1 or 2 spatial dimensions these approaches are not necessary, but moving to 3 or 4 spatial dimensions is not computationally feasible without considering matrix free approaches. In the current stage, we cannot move from the SVD-based method to SVD-free method because the damping operation has not been derived for the SVD-free case. Although it takes a large computational cost and is not very practically for the time being, it is still a promising algorithm. We will keep on investigating the acceleration of the current algorithm and make it computationally feasible in the future.}

\section{Examples}
We first apply the proposed optimal rank-reduction method to a 5D synthetic data with linear/planar events, as shown in Figure \ref{fig:syn}. Figure \ref{fig:syn}(a) shows the clean synthetic data in a common offset gather. The 3D common offset gather ($t-x-y$) has been arranged into a 2D matrix. Figure \ref{fig:syn}(b) shows the noisy data with extremely strong band-limited random noise. The useful signals are almost buried in the strong noise. Figure \ref{fig:syn}(c) shows the incomplete data, where 75\% traces have been randomly decimated. The reconstructed and denoised data using three different methods, i.e., the traditional rank-reduction method (RR), the damped rank-reduction method (DRR), and the \old{optimal}\new{optimally damped} rank-reduction method (ORR), are shown in Figure \ref{fig:syn_dn}. All three methods successfully recovered most of the signals.  It is clear that the RR method causes significant residual noise, the result from the DRR method is much cleaner than that from the RR method but still contains some residual noise. The proposed ORR method, however, obtains the cleanest result among the three results shown in Figure \ref{fig:syn_dn}. To evaluate the quality of the three reconstructed data, given the exact solution in Figure \ref{fig:syn}(a), we calculate the local similarity map between each reconstructed data and the exact solution. The local similarity is a way to evaluate the similarity between two vectors/matrices/cubes in a local manner so that the evaluation can be revealed immediately from the calculated local similarity maps. The detailed introduction of mathematics behind the local similarity calculation can be found in \cite{yangkang2015ortho}. From the local similarity comparison, it is quite obvious that from the top panel (RR method) to the bottom panel (ORR method), the similarity becomes higher and higher, which indicates that the proposed method obtains the most accurate solution.

To examine the amplitude recovery quality, we select the 22nd traces from the clean data in Figure \ref{fig:syn}(a) and from the three reconstructed data in Figure \ref{fig:syn_dn}, and draw them in Figure \ref{fig:syn_amp}. Figure \ref{fig:syn_amp}(a) shows the trace-by-trace comparison in the range of the whole trace and Figure \ref{fig:syn_amp}(b) shows the zoomed trade-by-trace comparison. The zooming part is highlighted by the red transparent rectangle shown in Figure \ref{fig:syn_amp}(a). From Figure \ref{fig:syn_amp} we can see that both RR and DRR methods (blue and red lines) cause strong fluctuations in the front part of the trace, while the proposed method obtains a result (the green line) that is the closest to the exact solution (the black line). The observation is even clearer in the zoomed comparison shown in Figure \ref{fig:syn_amp}(b). Figure \ref{fig:syn_e} shows the comparison of reconstruction error. The reconstruction error is calculated as the difference between the exact solution (Figure \ref{fig:syn}(a)) and each reconstructed data shown in Figure \ref{fig:syn_dn}. From Figure \ref{fig:syn_e} we can observe that both RR and DRR cause significant error and the proposed ORR method causes negligible reconstruction error except for some observable signal energy. The reconstruction error of RR method is higher than the DRR method, mostly because of the stronger residual noise caused by the RR method. Since the reconstruction error for the proposed method is mostly negligible, the error caused by the leakage signal energy becomes more apparent. To compare the leakage signal energy among three methods, we calculate the extra noise section of the RR and DRR methods. The extra noise section refers to the extra noise compared with the reference noise section from the ORR method (Figure \ref{fig:syn_e}(c)), thus is calculated as the difference between the error from either RR or DRR method and the error from the ORR method. The extra noise sections corresponding to the RR and DRR methods are shown in Figure \ref{fig:syn_ee}. It is obvious that by calculating the extra error sections, the leakage useful energy from RR/DRR method and ORR method counteract each other and the resulting sections are mostly random noise. This observation indicates that the energy of the leakage signal for the three methods are nearly the same. We conclude from this test that despite the same damage to useful signals, the proposed method causes the least residual noise and thus obtains the cleanest reconstruction result.

We also compare the level-four block Hankel matrices of different methods. Figures \ref{fig:H} and \ref{fig:H0} shows the Hankel matrices for the clean and incomplete data for the frequency slice of 30Hz. Figures \ref{fig:H_z} and \ref{fig:H0_z} show the zoomed Hankel matrices for the clean and incomplete data. The zooming areas are highlighted by the red rectangles shown in Figures \ref{fig:H} and \ref{fig:H0}. Because of the missing traces, the Hankel matrix contains a number of blank areas. Figure \ref{fig:Hs} shows the Hankel matrices for different methods. The left column correspond to the Hankel matrices after 1 iteration. The right column correspond to the Hankel matrices after 10 iterations. We only conclude from Figure \ref{fig:Hs} that after 10 iterations all three methods obtain similar Hankel matrices as the exact solution shown in Figure \ref{fig:H} but we cannot see the difference between different methods clearly. The differences between different methods can be clearly observed from the zoomed Hankel matrices, as shown in Figure \ref{fig:Hsz}. It is clear that from the top to bottom in Figure \ref{fig:Hsz}, the Hankel matrix becomes smoother and smoother and is closer to the exact solution shown in Figure \ref{fig:H_z}.

In addition to the local similarity mentioned above, we also use the signal-to-noise ratio (SNR) defined as follows to quantitatively measure the performance \cite[]{weilin2016,yangkang2017sgk,weilin2017gji}:
\begin{equation}
\label{eq:dsnr}
SNR=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2^2}{\Arrowvert \mathbf{s} -\hat{\mathbf{s}}\Arrowvert_2^2}.
\end{equation}
where $\mathbf{s}$ denotes the vectorized clean data and $\hat{\mathbf{s}}$ denotes the vectorized reconstructed data. In this example, the SNRs of the observed data, the reconstructed results via the RR method, the DRR method, and ORR method are -4.59 dB, 5.51 dB, 9.54 dB, and 11.83 dB, respectively. In this test, we use $rank=10$, assuming that we do not have a prior information about the structural complexity of the data and thus needing to set a relatively high rank. We then test the performance when the rank is chosen smaller. The reconstructed data when $rank=5$ are shown in Figure \ref{fig:syn_dn_N5}. Their corresponding error sections are shown in Figure \ref{fig:syn_e_N5}. From Figures \ref{fig:syn_dn_N5} and \ref{fig:syn_e_N5}, we can reach almost the same conclusion as the last test. In this case, the SNRs of the reconstructed results via the RR method, the DRR method, and ORR method are 8.01 dB, 10.87 dB, and 11.97 dB, respectively. The detailed SNR comparison is shown in Table \ref{tbl:plane}, including the case when $rank=3$.

\AtEndDocument{
\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/syn}
	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix). (a) Clean data. (b) Noisy data. \new{Note that because of the strong random noise, the useful signals are almost buried in the noise.} (c) Incomplete data with 70\% randomly removed traces. \new{The blanks in (c) indicate where there are missing traces.} \new{The strong noise and missing traces make the data quality extremely low.} }
	\label{fig:syn}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/syn_dn}
	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix). (a) Reconstructed data using the RR method. (b) Reconstructed data using the DRR method. (c) Reconstructed data using the ORR method.  In this case, $rank=10$.}
	\label{fig:syn_dn}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/syn_dn_simi}
	\caption{Local similarity comparison for the synthetic example (reshaped into a 2-D matrix). (a) Local similarity using the RR method. (b) Local similarity using the DRR method. (c) Local similarity using the ORR method. \new{It is obvious that the local similarity of the ORR method is much larger than the other two methods, indicating a more accurate reconstruction performance.}  }
	\label{fig:syn_dn_simi}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/syn_amp}
	\caption{\old{Trace-by-trace comparison. (a) The whole trace. (b) Zoomed trace.}\new{Trace-by-trace comparison.  (a) Comparison in the whole trace. The black line denotes the exact solution. Green line denotes the result from the proposed method. Red line denotes the result from the DRR method. Blue line denotes the result from the RR method. (b) Zoomed trace from (a). The transparant red window highlight the zooming area.}  }
	\label{fig:syn_amp}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/syn_e}
	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix). (a) Reconstruction error using the RR method. (b) Reconstruction error using the DRR method. (c) Reconstruction error using the ORR method. In this case, $rank=10$. }
	\label{fig:syn_e}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/syn_ee}
	\caption{Extra error comparison compared with the ORR method for the synthetic example (reshaped into a 2-D matrix) when $rank=10$. (a) Extra error caused by RR method (the difference between \ref{fig:syn_e}(a) and \ref{fig:syn_e}(c)). (b) Extra error caused by RR method (the difference between \ref{fig:syn_e}(b) and \ref{fig:syn_e}(c)). }
	\label{fig:syn_ee}
\end{figure}

\begin{figure}
	\centering
	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H}
    \label{fig:H}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H0}
    \label{fig:H0}}\\
	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H_z}
    \label{fig:H_z}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H0_z}
    \label{fig:H0_z}}
	\caption{Hankel matrices for the clean and observed data for frequency slice of 30Hz. (a) Hankel matrix of the clean data. (b) Hankel matrix of the observed data. (c) \& (d) Zoomed Hankel matrices of (a) \& (b). The zooming area is highlighted by the red rectangles.}
	\label{fig:HH}
\end{figure}

\begin{figure}
	\centering
	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_1}
    \label{fig:H1_1}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_1}
    \label{fig:H2_1}}\\
	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_2}
    \label{fig:H1_2}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_2}
    \label{fig:H2_2}}\\
	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_3}
    \label{fig:H1_3}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_3}
    \label{fig:H2_3}}
	\caption{Hankel matrices for different methods for frequency slice of 30Hz. Left column: Hankel matrix after 1 iteration. Right: Hankel matrix after 10 iterations. Top row: Hankel matrices for the RR method. Middle row: Hankel matrix for the DRR method. Bottom row: Hankel matrix for the ORR method.}
	\label{fig:Hs}
\end{figure}

\begin{figure}
	\centering
	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_1_z}
    \label{fig:H1_1_z}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_1_z}
    \label{fig:H2_1_z}}\\
	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_2_z}
    \label{fig:H1_2_z}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_2_z}
    \label{fig:H2_2_z}}\\
	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_3_z}
    \label{fig:H1_3_z}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_3_z}
    \label{fig:H2_3_z}}
	\caption{Zoomed Hankel matrices for different methods for frequency slice of 30Hz. Left column: Hankel matrix after 1 iteration. Right: Hankel matrix after 10 iterations. Top row: Hankel matrices for the RR method. Middle row: Hankel matrix for the DRR method. Bottom row: Hankel matrix for the ORR method.}
	\label{fig:Hsz}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/syn_dn_N5}
	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix). (a) Reconstructed data using the RR method. (b) Reconstructed data using the DRR method. (c) Reconstructed data using the ORR method.  In this case, $rank=5$.}
	\label{fig:syn_dn_N5}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/syn_e_N5}
	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix). (a) Reconstruction error using the RR method. (b) Reconstruction error using the DRR method. (c) Reconstruction error using the ORR method. In this case, $rank=5$. }
	\label{fig:syn_e_N5}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Fig/synth_vars}
	\caption{SNR diagrams of the different approaches with respect to the noise level (variance value). Note that the proposed approach outperforms the traditional methods more and more as the noise level increases.}
	\label{fig:synth_vars}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Fig/synth_ratios}
	\caption{SNR diagrams of the different approaches with respect to the sampling ratio (in percent). \new{It is obvious that the difference between the ORR method and the DRR method becomes larger as the sampling ratio increases. The ORR method always outperforms the other methods for all sampling ratios. }}
	\label{fig:synth_ratios}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Fig/synth_ranks}
	\caption{SNR diagrams of the different approaches with respect to the selected rank. \new{The ORR method is obviously much less sensitive to the rank compared with other two methods. This phenomenon indicates that the ORR method can be applied as an adaptive method by setting a relatively large rank.}}
	\label{fig:synth_ranks}
\end{figure}

\begin{figure}
	\centering
	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d_3v}
    \label{fig:hyper_d_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_dn_3v}
    \label{fig:hyper_dn_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d0_3v}
    \label{fig:hyper_d0_3v}} \\   
	\caption{Common midpoint gather comparison for the synthetic example with hyperbolic events. (a) Clean data. (b) Noisy data. (c) Incomplete data. \new{The blanks in (c) indicate where there are missing traces.} }
	\label{fig:hyper_N12}
\end{figure}

\begin{figure}
	\centering
	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_N12_3v}
    \label{fig:hyper_d1_N12_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_N12_3v}
    \label{fig:hyper_d2_N12_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_N12_3v}
    \label{fig:hyper_d3_N12_3v}} \\ 
	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_N24_3v}
    \label{fig:hyper_d1_N24_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_N24_3v}
    \label{fig:hyper_d2_N24_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_N24_3v}
    \label{fig:hyper_d3_N24_3v}} \\    
	\caption{Common midpoint gather comparison for the synthetic example with hyperbolic events. Top row shows results when $rank=12$. Bottom row shows results when $rank=24$. Left: Reconstructed data using the RR method. Middle: Reconstructed data using the DRR method. Right Reconstructed data using the ORR method. The SNR comparisons are shown in Table \ref{tbl:hyper}.}
	\label{fig:hyper_dn_N12}
\end{figure}

\begin{figure}
	\centering
	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_simi_N12_3v}
    \label{fig:hyper_d1_simi_N12_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_simi_N12_3v}
    \label{fig:hyper_d2_simi_N12_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_simi_N12_3v}
    \label{fig:hyper_d3_simi_N12_3v}} \\ 
	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_simi_N24_3v}
    \label{fig:hyper_d1_simi_N24_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_simi_N24_3v}
    \label{fig:hyper_d2_simi_N24_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_simi_N24_3v}
    \label{fig:hyper_d3_simi_N24_3v}} \\    
	\caption{Local similarity comparison for the synthetic example with hyperbolic events. Top row shows results when $rank=12$. Bottom row shows results when $rank=24$. Left: Reconstructed data using the RR method. Middle: Reconstructed data using the DRR method. Right Reconstructed data using the ORR method. The introduction of local similarity is given in \cite{yangkang2015ortho}. }
	\label{fig:hyper_simi_N12}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Fig/field_d0_0}
	\caption{Real data example \new{with a lot of missing traces}. \new{Because of the difficulty in display a 5D dataset, only one common midpoint gather is extracted and rearranged into a 2D matrix, and is plotted here. The two transparent colored windows denote two zooming areas for an amplified comparison.}}
	\label{fig:field_d0_0}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{Fig/field_dn_N12_0}
	\caption{Real data example. (a) Reconstructed data using the RR method. (b) Reconstructed data using the DRR method. (c) Reconstructed data using the ORR method.  In this case, $rank=20$. \new{It is obvious that all three methods obtain dramatic improvement from the raw data. The ORR method obtains cleaner and spatially more coherent seismic events compared with other two methods.}}
	\label{fig:field_dn_N12_0}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Fig/field_dn_N12_z1}
	\caption{Zoomed comparison for the field data example (the blue frame box). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method. }
	\label{fig:field_dn_N12_z1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Fig/field_dn_N12_z2}
	\caption{Zoomed comparison for the field data example (the red frame box). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method. }
	\label{fig:field_dn_N12_z2}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Fig/field_dn_N12_t80}
	\caption{Comparison for constant time slice for the field data example ($t=0.32$s). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method. }
	\label{fig:field_dn_N12_t80}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Fig/field_dn_N12_t160}
	\caption{Comparison for constant time slice for the field data example ($t=0.64$s). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method. }
	\label{fig:field_dn_N12_t160}
\end{figure}

}

To test the sensitivities of each method to input noise level, we vary the variance of the additive random noise from 0.1 to 0.9 and calculate the output SNRs corresponding to different methods and draw the diagrams in Figure \ref{fig:synth_vars}. The black line corresponds to the input SNR curve. The blue, red, and green lines correspond to the RR, DRR, and ORR methods, respectively. As the noise variance increases, the input SNR decreases, and so do the output SNRs of the three methods. However, the proposed method always outperforms the other two methods. It is worth noting that as the noise variance becomes larger, the differences between the proposed method and the other methods are also larger, which indicates that the proposed method is more effective for stronger noise.

To test the effectiveness of each method in situations with different sampling ratios, we vary the sampling ratio from 10\% to 90\%, and draw the input and output SNR curves in Figure \ref{fig:synth_ratios}. The colorful lines have the same meaning in this case. As we can see from Figure \ref{fig:synth_ratios}, the input SNR decreases with increasing sampling ratio. The output SNRs increase with increasing sampling ratios. It is clear that the output SNR curve of the proposed method is always above the other curves. The proposed method outperforms other two methods more when sampling ratio is higher.

To test the sensitivities of different methods to the input parameter, i.e., the predefined \old{appealing rank}\new{rank}, we vary the rank from 4 to 15 and draw the SNR curves in Figure \ref{fig:synth_ranks}. Both RR and DRR methods decrease fast as the predefined rank increases while the SNR curve of the proposed ORR method is almost flat and is also above the other two curves. This test indicates that while the RR and DRR are more or less sensitive to the predefined rank, the proposed method is almost parameter-free, which makes the ORR method convenient to use in realistic situations.

To compare the computational cost of different methods, we measure the computing time for the synthetic example with linear events. The computation is done on a MacBook Pro laptop equipped with an Intel Core i7 CPU clocked at 2.5 GHz and 16 GB of RAM. The detailed computing time comparison is shown in Table \ref{tbl:time}. It shows that the computational cost of the ORR method is higher than the other two methods.  The RR and DRR methods have almost the same computational cost while the proposed method costs 2-5 times more than the other two methods.

In order to test the effectiveness of the three methods on data containing curved events and to compare the performances of different methods in this case, we then use the second example to show the performance.  Figure \ref{fig:hyper_N12} shows the clean data, noisy data, and incomplete data with 70\% traces randonly missing in a common midpoint gather. Figure \ref{fig:hyper_dn_N12} shows the reconstructed data using different methods. Because this dataset no longer meet the linear-event assumption of the rank-reduction based methods, we use a relatively higher rank in this example. The top row in Figure \ref{fig:hyper_dn_N12} shows results when $rank = 12$. The bottom row in Figure \ref{fig:hyper_dn_N12} shows results when $rank = 24$. It is clear that the three methods also work when there are curving events. The proposed method obtains obviously cleaner result than the other two methods. The SNRs of the incomplete data, data from the RR method, DRR method, and ORR method are 0.59, 14.11, 16.46, and 16.86 dB when $rank=12$ and are 0.59, 13.88, 16.01, and 16.83 dB when $rank=24$. We also calculate the local similarity between the exact solution shown in Figure \ref{fig:hyper_d_3v} and each reconstructed data and show the similarity cubes in Figure \ref{fig:hyper_simi_N12}. The local similarity corresponding to the proposed method is obviously higher than those from the  other two methods, indicating a more accurate reconstruction result using the proposed method.

Finally, we apply the three methods to a 5D field data. We use the data previously used in \cite{yangkang2016irr5d}.  The data have been binned onto a regular grid and a common offset gather of the field data is shown in Figure \ref{fig:field_d0_0}. \new{In Figure \ref{fig:field_d0_0}, the colored stripes are the recorded seismic traces. The white blanks denote the missing traces, which means that we do not observe seismic data in these positions. Because of the difficulty in displaying a 5D dataset, we only show a common midpoint gather here. The 3D common midpoint gather is rearranged into a 2D matrix for a better view. The two transparent colored windows denote two zooming areas for an amplified comparison. } %Although we are only allowed to show a small portion of the field data and to give a limited discussion based on the performance, the comparison between traditional and proposed rank-reduction methods is adequate to show the superior performance of our proposed method. 
In this example, roughly 80\% traces are missing from the regular grids. \new{Because of the high ratio of missing traces, the observed seismic traces do not show any spatial coherency. It is difficult to see the waveforms from the raw data. }
The results from the three aforementioned methods are shown in Figure \ref{fig:field_dn_N12_0}. \new{After 5D reconstruction, the white blanks in the raw data have been filled with seismic traces. The waveforms become well aligned along the spatial direction. Compared with the raw data, all methods seem to obtain a dramatic improvement on the data quality.} It is salient that both DRR and ORR methods obtain \old{very encouraging}\new{much smoother and cleaner} results while the traditional RR method obtain a result that is noisier. \new{Because of the strong residual noise in the result from the traditional RR method, the spatial coherency of the seismic events are deteriorated, which may affect the subsequent processing tasks like imaging, inversion, and interpretation. } When zooming the data in \old{two areas, as highlighted by }the \new{two} transparent blue and red rectangles in both Figures \ref{fig:field_d0_0} and \ref{fig:field_dn_N12_0}, the comparison among different methods becomes much clearer. From Figures \ref{fig:field_dn_N12_z1} and \ref{fig:field_dn_N12_z2}, we observe that although the DRR method obtain a much smoother result compared with the RR result, as already discussed from \cite{yangkang2016irr5d}, the ORR method obtains a even smoother result, with energy spatially more correlative. We also extract two constant time slices at $t=0.32s$ and $t=0.64s$, respectively, and show them in Figures \ref{fig:field_dn_N12_t80} and \ref{fig:field_dn_N12_t160}. The pixels corresponding to the proposed method are obviously smoother from the proposed method. \new{The two reconstructed time slices from the proposed method show obvious shapes of a dome.  }

%\section{Discussions}
\section{Conclusions}
We have introduced a new rank-reduction (RR) method for interpolating and denoising five-dimensional seismic data based on a \new{cascaded }optimal weighting \old{strategy}\new{ and damping operations}. The proposed \new{optimally damped} rank-reduction (ORR) method can further improve \old{our previously developed}\new{the} damped rank-reduction (DRR) method in causing less residual noise and making the result smoother. The proposed ORR method works effectively in various data examples including data with linear/planar events, data with hyperbolic events, and field data. While in the case of low SNR, all rank-reduction methods tend to damage some useful energy, the proposed ORR method does not cause extra damage but can remove more noise than the other rank-reduction methods. The waveforms reconstructed from the proposed method are more similar to the ground-truth solution in the synthetic tests. The block Hankel matrix from the proposed method in each frequency slice is smoother than other rank-reduction method, which accounts for why it is more capable of suppressing residual noise. The proposed method outperforms the other rank-reduction methods more in stronger noise and higher sampling ratios. The effectiveness is almost unchanged for different predefined ranks, meaning that the proposed method is almsot parameter-free. One drawback of the proposed method is that the computational cost is 2-5 times higher than the other rank-reduction methods, which can be potentially tackled in future research.

\section{Acknowledgements}
We would like to thank Dong Zhang and Weilin Huang for inspiring discussions. \new{We also thank Frederik Simons and two anonymous reviewers for constructive suggestions that greatly improved the manuscript.} The research is supported by the starting fund from Zhejiang University and the ``Thousand Youth Talents Plan of China''.

%\subsection{Appendix: local similarity}
% Local similarity between vectors $\mathbf{a}$ and $\mathbf{b}$ is defined as:
%\begin{equation}
%\label{eq:local}
%\mathbf{c}=\sqrt{\mathbf{c}_1\circ\mathbf{c}_2}
%\end{equation}
%where $\circ$ denotes dot product, $\mathbf{c}_1$ and $\mathbf{c}_2$ come from two least-squares minimization problems:
%\begin{align}
%\label{eq:local1}
%\mathbf{c}_1 &=\arg\min_{\mathbf{c}_1}\Arrowvert \mathbf{a}-\mathbf{B} \mathbf{c}_1 \Arrowvert_2^2 \\
%\label{eq:local2}
%\mathbf{c}_2 &=\arg\min_{\mathbf{c}_2}\Arrowvert \mathbf{b}-\mathbf{A} \mathbf{c}_2 \Arrowvert_2^2
%\end{align}
%where $\mathbf{A}$ is a diagonal operator composed of the elements of $\mathbf{a}$, $\mathbf{B}$ is a diagonal operator composed of the elements of $\mathbf{b}$. Note that in equations \ref{eq:local}-\ref{eq:local2}, $\mathbf{a}$, $\mathbf{b}$, and $\mathbf{c}$  denote vectorized 2D matrices. Equations \ref{eq:local1} and \ref{eq:local2} can be solved using shaping regularization with a local-smoothness constraint:
%\begin{align}
%\label{eq:local3}
%\mathbf{c}_1 &= [\lambda_1^2\mathbf{I} + \mathbf{T}(\mathbf{B}^T\mathbf{B}-\lambda_1^2\mathbf{I})]^{-1}\mathbf{TB}^T\mathbf{b},\\
%\label{eq:local4}
%\mathbf{c}_2 &= [\lambda_2^2\mathbf{I} + \mathbf{T}(\mathbf{A}^T\mathbf{A}-\lambda_2^2\mathbf{I})]^{-1}\mathbf{TA}^T\mathbf{a},
%\end{align}
%where $\mathbf{T}$ is a smoothing operator and $\lambda_1$ and $\lambda_2$ are two parameters controlling the physical dimensionality and enabling fast convergence when inversion is implemented iteratively. These two parameters can be chosen as $\lambda_1  = \Arrowvert\mathbf{B}^T\mathbf{B}\Arrowvert_2$ and $\lambda_2  = \Arrowvert\mathbf{A}^T\mathbf{A}\Arrowvert_2$.
%
\bibliographystyle{seg}
\bibliography{dos5d}

\newpage
\listoftables

\newpage
\listoffigures
\newpage

\begin{table}[h]
\caption{SNRs comparison in dB for the synthetic example with linear events.}
\begin{center}
     \begin{tabular}{|c|c|c|c|c|} 
	  \hline &Incomplete & RR  & DRR  & ORR \\ 
	  \hline N=3    & -4.59 & 9.96 & 11.68 & 12.03 \\	  
	  \hline N=5    & -4.59 & 8.01 & 10.87 & 11.99 \\
	  \hline N=10 & -4.59 & 5.51 & 9.54 & 11.83 \\
%	  \hline N=15 &  &  &  &  \\
       \hline
    \end{tabular} 
\end{center}
\label{tbl:plane}
\end{table}

\begin{table}[h]
\caption{Computing time comparison in seconds for the synthetic example with linear events. The computation is done on a MacBook Pro laptop equipped with an Intel Core i7 CPU clocked at 2.5 GHz and 16 GB of RAM.}
\begin{center}
     \begin{tabular}{|c|c|c|c|c|} 
	  \hline  & RR  & DRR  & ORR \\ 
	  \hline N=3    &246.39  & 249.63 & 656.33   \\	  
	  \hline N=5    &249.37  & 252.52 &    923.45\\
	  \hline N=10  &250.28  &  255.27 & 1226.63 \\
%	  \hline N=15 &  &  &  &  \\
       \hline
    \end{tabular} 
\end{center}
\label{tbl:time}
\end{table}

\begin{table}[h]
\caption{SNRs comparison in dB for the synthetic example with hyperbolic events.}
\begin{center}
     \begin{tabular}{|c|c|c|c|c|} 
	  \hline &Incomplete  & RR  & DRR & ORR \\ 
	  \hline N=12& 0.59 & 14.11 & 16.46 & 16.86 \\
	  \hline N=24& 0.59 & 13.88 & 16.01 & 16.83 \\
       \hline
    \end{tabular} 
\end{center}
\label{tbl:hyper}
\end{table}
\newpage
%\inputdir{test}
%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
%\multiplot{2}{test1,test2}{width=0.45\textwidth}{(a) Caption a. (b) Caption b.}

%In equation \ref{eq:M_a}, because $\mathbf{U}_1^M$ and $\mathbf{V}_1^M$ both have orthonormal columns (as they come from the SVD of $\mathbf{M}$), thus equation \ref{eq:M_a} is an SVD of $\hat{\mathbf{M}}$. Let 
%\begin{equation}
%\label{eq:Sigma_new}
%\hat{\boldsymbol{\Sigma}}_1^M=\hat{\mathbf{W}}\boldsymbol{\Sigma}_1^M,
%\end{equation}
%and thus $\hat{\boldsymbol{\Sigma}}_1^M$ denotes the new singular values of the the estimated signal component after weighting.

%\AtEndDocument{}

%\begin{figure}
%	\centering
%	\subfloat[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
%	\caption{Caption.}
%	\label{fig:fig}
%\end{figure}

%\begin{figure}
%	\centering
%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
%    \label{fig:fig1}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
%    \label{fig:fig2}}\\
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure}

%\begin{table}[h]
%\caption{Table caption}
%\begin{center}
%     \begin{tabular}{|c|c|c|c|c|c|} 
%	  \hline Column1 (unit)  & Column2 (unit) & Column3 (unit) \\ 
%	  \hline 1 & 2  & 3 \\
%       \hline
%    \end{tabular} 
%\end{center}
%\label{tbl:table1}
%\end{table}

### 2020-11-02 odrr5d/matfun/Hyper.m

@@ -1,0 +1,112 @@
+function Hyper(clean,noisy,obs,rr,drr,odrr,rr2,drr2,odrr2)
+% Author      : Yangkang Chen
+% Date        : Feb, 2020
+% 
+% Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
+%    
+%  Copyright (C) 2019 The University of Texas at Austin
+%  Copyright (C) 2019 Yangkang Chen
+%  
+%  This program is free software; you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published by
+%  the Free Software Foundation; either version 2 of the License, or
+%  (at your option) any later version.
+%  
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%  
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, write to the Free Software
+%  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  
+% 
+%  Reference:   Chen et al., GJI, 2016; Chen et al., GJI, 2020
+
+%% load data
+load yc_hyper5d.mat
+d=hyper5d;d=d/max(max(max(max(max(d)))));
+[nt,nhx,nhy,nx,ny]=size(d);
+
+%% simultaneous denoising and reconstruction
+randn('state',201314);
+var=0.25;
+dn=d+var*randn(size(d));
+
+%% decimate
+[nt,nhx,nhy,nx,ny]=size(d);
+ratio=0.3;
+mask=yc_genmask(reshape(d,nt,nhx*nhy*nx*ny),ratio,'c',201415);
+mask=reshape(mask,nt,nhx,nhy,nx,ny);
+d0=dn.*mask;
+
+% RR
+flow=0;fhigh=100;dt=0.004;N=12;Niter=10;mode=1;verb=1;iflb=0;
[…]

### 2020-11-03 odrr5d/paper.tex
2020年11月 2日 星期一 19时07分54秒 CST

@@
 \section{Examples}
-We first apply the proposed optimal rank-reduction method to a 5D synthetic data with linear/planar events, as shown in Figure \ref{fig:syn}.
-Figure \ref{fig:syn}(a) shows the clean synthetic data in a common offset gather.
+We first apply the proposed optimal rank-reduction method to a 5D synthetic data with linear/planar events, as shown in Figure \ref{fig:figure1}.
+Figure \ref{fig:figure1}(a) shows the clean synthetic data in a common offset gather.
 The 3D common offset gather ($t-x-y$) has been arranged into a 2D matrix.
-Figure \ref{fig:syn}(b) shows the noisy data with extremely strong band-limited random noise.
+Figure \ref{fig:figure1}(b) shows the noisy data with extremely strong band-limited random noise.
 The useful signals are almost buried in the strong noise.
-Figure \ref{fig:syn}(c) shows the incomplete data, where 75\% traces have been randomly decimated.
-The reconstructed and denoised data using three different methods, i.e., the traditional rank-reduction method (RR), the damped rank-reduction method (DRR), and the \old{optimal}\new{optimally damped} rank-reduction method (ORR), are shown in Figure \ref{fig:syn_dn}.
+Figure \ref{fig:figure1}(c) shows the incomplete data, where 75\% traces have been randomly decimated.
+The reconstructed and denoised data using three different methods, i.e., the traditional rank-reduction method (RR), the damped rank-reduction method (DRR), and the \old{optimal}\new{optimally damped} rank-reduction method (ORR), are shown in Figure \ref{fig:figure2}.
 All three methods successfully recovered most of the signals.
 It is clear that the RR method causes significant residual noise, the result from the DRR method is much cleaner than that from the RR method but still contains some residual noise.
-The proposed ORR method, however, obtains the cleanest result among the three results shown in Figure \ref{fig:syn_dn}.
-To evaluate the quality of the three reconstructed data, given the exact solution in Figure \ref{fig:syn}(a), we calculate the local similarity map between each reconstructed data and the exact solution.
+The proposed ORR method, however, obtains the cleanest result among the three results shown in Figure \ref{fig:figure2}.
+To evaluate the quality of the three reconstructed data, given the exact solution in Figure \ref{fig:figure1}(a), we calculate the local similarity map between each reconstructed data and the exact solution.
 The local similarity is a way to evaluate the similarity between two vectors/matrices/cubes in a local manner so that the evaluation can be revealed immediately from the calculated local similarity maps.
@@
 
-To examine the amplitude recovery quality, we select the 22nd traces from the clean data in Figure \ref{fig:syn}(a) and from the three reconstructed data in Figure \ref{fig:syn_dn}, and draw them in Figure \ref{fig:syn_amp}.
-Figure \ref{fig:syn_amp}(a) shows the trace-by-trace comparison in the range of the whole trace and Figure \ref{fig:syn_amp}(b) shows the zoomed trade-by-trace comparison.
-The zooming part is highlighted by the red transparent rectangle shown in Figure \ref{fig:syn_amp}(a).
-From Figure \ref{fig:syn_amp} we can see that both RR and DRR methods (blue and red lines) cause strong fluctuations in the front part of the trace, while the proposed method obtains a result (the green line) that is the closest to the exact solution (the black line).
-The observation is even clearer in the zoomed comparison shown in Figure \ref{fig:syn_amp}(b).
-Figure \ref{fig:syn_e} shows the comparison of reconstruction error.
-The reconstruction error is calculated as the difference between the exact solution (Figure \ref{fig:syn}(a)) and each reconstructed data shown in Figure \ref{fig:syn_dn}.
-From Figure \ref{fig:syn_e} we can observe that both RR and DRR cause significant error and the proposed ORR method causes negligible reconstruction error except for some observable signal energy.
+To examine the amplitude recovery quality, we select the 22nd traces from the clean data in Figure \ref{fig:figure1}(a) and from the three reconstructed data in Figure \ref{fig:figure2}, and draw them in Figure \ref{fig:figure4}.
+Figure \ref{fig:figure4}(a) shows the trace-by-trace comparison in the range of the whole trace and Figure \ref{fig:figure4}(b) shows the zoomed trade-by-trace comparison.
+The zooming part is highlighted by the red transparent rectangle shown in Figure \ref{fig:figure4}(a).
+From Figure \ref{fig:figure4} we can see that both RR and DRR methods (blue and red lines) cause strong fluctuations in the front part of the trace, while the proposed method obtains a result (the green line) that is the closest to the exact solution (the black line).
+The observation is even clearer in the zoomed comparison shown in Figure \ref{fig:figure4}(b).
+Figure \ref{fig:figure5} shows the comparison of reconstruction error.
+The reconstruction error is calculated as the difference between the exact solution (Figure \ref{fig:figure1}(a)) and each reconstructed data shown in Figure \ref{fig:figure2}.
+From Figure \ref{fig:figure5} we can observe that both RR and DRR cause significant error and the proposed ORR method causes negligible reconstruction error except for some observable signal energy.
 The reconstruction error of RR method is higher than the DRR method, mostly because of the stronger residual noise caused by the RR method.
@@
 To compare the leakage signal energy among three methods, we calculate the extra noise section of the RR and DRR methods.
-The extra noise section refers to the extra noise compared with the reference noise section from the ORR method (Figure \ref{fig:syn_e}(c)), thus is calculated as the difference between the error from either RR or DRR method and the error from the ORR method.
-The extra noise sections corresponding to the RR and DRR methods are shown in Figure \ref{fig:syn_ee}.
+The extra noise section refers to the extra noise compared with the reference noise section from the ORR method (Figure \ref{fig:figure5}(c)), thus is calculated as the difference between the error from either RR or DRR method and the error from the ORR method.
+The extra noise sections corresponding to the RR and DRR methods are shown in Figure \ref{fig:figure6}.
 It is obvious that by calculating the extra error sections, the leakage useful energy from RR/DRR method and ORR method counteract each other and the resulting sections are mostly random noise.
@@
 \AtEndDocument{
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\textwidth]{Fig/syn}
-	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix).
+
+\inputdir{synth}
+\plot{figure1}{width=0.8\textwidth}{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix).
 (a) Clean data.
@@
 \new{The blanks in (c) indicate where there are missing traces.} \new{The strong noise and missing traces make the data quality extremely low.} }
-	\label{fig:syn}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\textwidth]{Fig/syn_dn}
-	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix).
+\plot{figure2}{width=0.8\textwidth}{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix).
 (a) Reconstructed data using the RR method.
@@
 In this case, $rank=10$.}
-	\label{fig:syn_dn}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\textwidth]{Fig/syn_dn_simi}
-	\caption{Local similarity comparison for the synthetic example (reshaped into a 2-D matrix).
+\plot{figure3}{width=0.8\textwidth}{Local similarity comparison for the synthetic example (reshaped into a 2-D matrix).
 (a) Local similarity using the RR method.
@@
 \new{It is obvious that the local similarity of the ORR method is much larger than the other two methods, indicating a more accurate reconstruction performance.} }
-	\label{fig:syn_dn_simi}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\textwidth]{Fig/syn_amp}
-	\caption{\old{Trace-by-trace comparison.
+\plot{figure4}{width=0.8\textwidth}{\old{Trace-by-trace comparison.
 (a) The whole trace.
@@
 The transparant red window highlight the zooming area.} }
-	\label{fig:syn_amp}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\textwidth]{Fig/syn_e}
-	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix).
+\plot{figure5}{width=0.8\textwidth}{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix).
 (a) Reconstruction error using the RR method.
@@
 (c) Reconstruction error using the ORR method.
-In this case, $rank=10$.
+In this case, $rank=10$.}
+\plot{figure6}{width=0.8\textwidth}{Extra error comparison compared with the ORR method for the synthetic example (reshaped into a 2-D matrix) when $rank=10$.
+(a) Extra error caused by RR method (the difference between \ref{fig:figure5}(a) and \ref{fig:figure5}(c)).
+(b) Extra error caused by RR method (the difference between \ref{fig:figure5}(b) and \ref{fig:figure5}(c)).
 }
-	\label{fig:syn_e}
-\end{figure}
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\textwidth]{Fig/syn_ee}
-	\caption{Extra error comparison compared with the ORR method for the synthetic example (reshaped into a 2-D matrix) when $rank=10$.
-(a) Extra error caused by RR method (the difference between \ref{fig:syn_e}(a) and \ref{fig:syn_e}(c)).
-(b) Extra error caused by RR method (the difference between \ref{fig:syn_e}(b) and \ref{fig:syn_e}(c)).
-}
-	\label{fig:syn_ee}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H}
-    \label{fig:H}}
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H0}
-    \label{fig:H0}}\\
-	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H_z}
-    \label{fig:H_z}}
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H0_z}
-    \label{fig:H0_z}}
-	\caption{Hankel matrices for the clean and observed data for frequency slice of 30Hz.
+%
+%\begin{figure}
+%	\centering
+%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H}
+%    \label{fig:H}}
+%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H0}
+%    \label{fig:H0}}\\
+%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H_z}
+%    \label{fig:H_z}}
+%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H0_z}
+%    \label{fig:H0_z}}
+%	\caption{Hankel matrices for the clean and observed data for frequency slice of 30Hz.
 (a) Hankel matrix of the clean data.
@@
 The zooming area is highlighted by the red rectangles.}
-	\label{fig:HH}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_1}
-    \label{fig:H1_1}}
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_1}
-    \label{fig:H2_1}}\\
-	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_2}
-    \label{fig:H1_2}}
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_2}
-    \label{fig:H2_2}}\\
-	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_3}
-    \label{fig:H1_3}}
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_3}
-    \label{fig:H2_3}}
-	\caption{Hankel matrices for different methods for frequency slice of 30Hz.
+%	\label{fig:HH}
+%\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_1}
+%    \label{fig:H1_1}}
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_1}
+%    \label{fig:H2_1}}\\
+%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_2}
+%    \label{fig:H1_2}}
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_2}
+%    \label{fig:H2_2}}\\
+%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_3}
+%    \label{fig:H1_3}}
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_3}
+%    \label{fig:H2_3}}
+%	\caption{Hankel matrices for different methods for frequency slice of 30Hz.
 Left column: Hankel matrix after 1 iteration.
@@
 Bottom row: Hankel matrix for the ORR method.}
-	\label{fig:Hs}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_1_z}
-    \label{fig:H1_1_z}}
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_1_z}
-    \label{fig:H2_1_z}}\\
-	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_2_z}
-    \label{fig:H1_2_z}}
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_2_z}
-    \label{fig:H2_2_z}}\\
-	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_3_z}
-    \label{fig:H1_3_z}}
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_3_z}
-    \label{fig:H2_3_z}}
-	\caption{Zoomed Hankel matrices for different methods for frequency slice of 30Hz.
+%	\label{fig:Hs}
+%\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_1_z}
+%    \label{fig:H1_1_z}}
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_1_z}
+%    \label{fig:H2_1_z}}\\
+%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_2_z}
+%    \label{fig:H1_2_z}}
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_2_z}
+%    \label{fig:H2_2_z}}\\
+%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_3_z}
+%    \label{fig:H1_3_z}}
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_3_z}
+%    \label{fig:H2_3_z}}
+%	\caption{Zoomed Hankel matrices for different methods for frequency slice of 30Hz.
 Left column: Hankel matrix after 1 iteration.
@@
 Bottom row: Hankel matrix for the ORR method.}
-	\label{fig:Hsz}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\textwidth]{Fig/syn_dn_N5}
-	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix).
+%	\label{fig:Hsz}
+%\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=0.8\textwidth]{Fig/syn_dn_N5}
+%	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix).
 (a) Reconstructed data using the RR method.
@@
 In this case, $rank=5$.}
-	\label{fig:syn_dn_N5}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\textwidth]{Fig/syn_e_N5}
-	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix).
+%	\label{fig:syn_dn_N5}
+%\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=0.8\textwidth]{Fig/syn_e_N5}
+%	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix).
 (a) Reconstruction error using the RR method.
@@
 }
-	\label{fig:syn_e_N5}
-\end{figure}
+%	\label{fig:syn_e_N5}
+%\end{figure}
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{Fig/synth_vars}
-	\caption{SNR diagrams of the different approaches with respect to the noise level (variance value).
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=\textwidth]{Fig/synth_vars}
+%	\caption{SNR diagrams of the different approaches with respect to the noise level (variance value).
 Note that the proposed approach outperforms the traditional methods more and more as the noise level increases.}
-	\label{fig:synth_vars}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{Fig/synth_ratios}
-	\caption{SNR diagrams of the different approaches with respect to the sampling ratio (in percent).
+%	\label{fig:synth_vars}
+%\end{figure}
+%
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=\textwidth]{Fig/synth_ratios}
+%	\caption{SNR diagrams of the different approaches with respect to the sampling ratio (in percent).
 \new{It is obvious that the difference between the ORR method and the DRR method becomes larger as the sampling ratio increases.
@@
 }}
-	\label{fig:synth_ratios}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{Fig/synth_ranks}
-	\caption{SNR diagrams of the different approaches with respect to the selected rank.
+%	\label{fig:synth_ratios}
+%\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=\textwidth]{Fig/synth_ranks}
+%	\caption{SNR diagrams of the different approaches with respect to the selected rank.
 \new{The ORR method is obviously much less sensitive to the rank compared with other two methods.
 This phenomenon indicates that the ORR method can be applied as an adaptive method by setting a relatively large rank.}}
-	\label{fig:synth_ranks}
-\end{figure}
+%	\label{fig:synth_ranks}
+%\end{figure}
 
-\begin{figure}
-	\centering
-	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d_3v}
-    \label{fig:hyper_d_3v}}
-    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_dn_3v}
-    \label{fig:hyper_dn_3v}}
-    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d0_3v}
-    \label{fig:hyper_d0_3v}} \\   
-	\caption{Common midpoint gather comparison for the synthetic example with hyperbolic events.
+%\begin{figure}
+%	\centering
+%	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d_3v}
+%    \label{fig:hyper_d_3v}}
+%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_dn_3v}
+%    \label{fig:hyper_dn_3v}}
+%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d0_3v}
+%    \label{fig:hyper_d0_3v}} \\   
+%	\caption{Common midpoint gather comparison for the synthetic example with hyperbolic events.
 (a) Clean data.
@@
 \new{The blanks in (c) indicate where there are missing traces.} }
-	\label{fig:hyper_N12}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_N12_3v}
-    \label{fig:hyper_d1_N12_3v}}
-    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_N12_3v}
-    \label{fig:hyper_d2_N12_3v}}
-    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_N12_3v}
-    \label{fig:hyper_d3_N12_3v}} \\ 
-	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_N24_3v}
-    \label{fig:hyper_d1_N24_3v}}
-    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_N24_3v}
-    \label{fig:hyper_d2_N24_3v}}
-    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_N24_3v}
-    \label{fig:hyper_d3_N24_3v}} \\    
-	\caption{Common midpoint gather comparison for the synthetic example with hyperbolic events.
+%	\label{fig:hyper_N12}
+%\end{figure}
+%
+%
+%\begin{figure}
+%	\centering
+%	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_N12_3v}
+%    \label{fig:hyper_d1_N12_3v}}
+%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_N12_3v}
+%    \label{fig:hyper_d2_N12_3v}}
+%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_N12_3v}
+%    \label{fig:hyper_d3_N12_3v}} \\ 
+%	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_N24_3v}
+%    \label{fig:hyper_d1_N24_3v}}
+%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_N24_3v}
+%    \label{fig:hyper_d2_N24_3v}}
+%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_N24_3v}
+%    \label{fig:hyper_d3_N24_3v}} \\    
+%	\caption{Common midpoint gather comparison for the synthetic example with hyperbolic events.
 Top row shows results when $rank=12$.
@@
 The SNR comparisons are shown in Table \ref{tbl:hyper}.}
-	\label{fig:hyper_dn_N12}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_simi_N12_3v}
-    \label{fig:hyper_d1_simi_N12_3v}}
-    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_simi_N12_3v}
-    \label{fig:hyper_d2_simi_N12_3v}}
-    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_simi_N12_3v}
-    \label{fig:hyper_d3_simi_N12_3v}} \\ 
-	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_simi_N24_3v}
-    \label{fig:hyper_d1_simi_N24_3v}}
-    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_simi_N24_3v}
-    \label{fig:hyper_d2_simi_N24_3v}}
-    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_simi_N24_3v}
-    \label{fig:hyper_d3_simi_N24_3v}} \\    
-	\caption{Local similarity comparison for the synthetic example with hyperbolic events.
+%	\label{fig:hyper_dn_N12}
+%\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_simi_N12_3v}
+%    \label{fig:hyper_d1_simi_N12_3v}}
+%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_simi_N12_3v}
+%    \label{fig:hyper_d2_simi_N12_3v}}
+%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_simi_N12_3v}
+%    \label{fig:hyper_d3_simi_N12_3v}} \\ 
+%	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_simi_N24_3v}
+%    \label{fig:hyper_d1_simi_N24_3v}}
+%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_simi_N24_3v}
+%    \label{fig:hyper_d2_simi_N24_3v}}
+%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_simi_N24_3v}
+%    \label{fig:hyper_d3_simi_N24_3v}} \\    
+%	\caption{Local similarity comparison for the synthetic example with hyperbolic events.
 Top row shows results when $rank=12$.
@@
 }
-	\label{fig:hyper_simi_N12}
-\end{figure}
+%	\label{fig:hyper_simi_N12}
+%\end{figure}
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{Fig/field_d0_0}
-	\caption{Real data example \new{with a lot of missing traces}.
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=\textwidth]{Fig/field_d0_0}
+%	\caption{Real data example \new{with a lot of missing traces}.
 \new{Because of the difficulty in display a 5D dataset, only one common midpoint gather is extracted and rearranged into a 2D matrix, and is plotted here.
 The two transparent colored windows denote two zooming areas for an amplified comparison.}}
-	\label{fig:field_d0_0}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.9\textwidth]{Fig/field_dn_N12_0}
-	\caption{Real data example.
+%	\label{fig:field_d0_0}
+%\end{figure}
+%
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=0.9\textwidth]{Fig/field_dn_N12_0}
+%	\caption{Real data example.
 (a) Reconstructed data using the RR method.
@@
 The ORR method obtains cleaner and spatially more coherent seismic events compared with other two methods.}}
-	\label{fig:field_dn_N12_0}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{Fig/field_dn_N12_z1}
-	\caption{Zoomed comparison for the field data example (the blue frame box).
+%	\label{fig:field_dn_N12_0}
+%\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=\textwidth]{Fig/field_dn_N12_z1}
+%	\caption{Zoomed comparison for the field data example (the blue frame box).
 (a) Incomplete data.
@@
 }
-	\label{fig:field_dn_N12_z1}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{Fig/field_dn_N12_z2}
-	\caption{Zoomed comparison for the field data example (the red frame box).
+%	\label{fig:field_dn_N12_z1}
+%\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=\textwidth]{Fig/field_dn_N12_z2}
+%	\caption{Zoomed comparison for the field data example (the red frame box).
 (a) Incomplete data.
@@
 }
-	\label{fig:field_dn_N12_z2}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{Fig/field_dn_N12_t80}
-	\caption{Comparison for constant time slice for the field data example ($t=0.32$s).
+%	\label{fig:field_dn_N12_z2}
+%\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=\textwidth]{Fig/field_dn_N12_t80}
+%	\caption{Comparison for constant time slice for the field data example ($t=0.32$s).
 (a) Incomplete data.
@@
 }
-	\label{fig:field_dn_N12_t80}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{Fig/field_dn_N12_t160}
-	\caption{Comparison for constant time slice for the field data example ($t=0.64$s).
+%	\label{fig:field_dn_N12_t80}
+%\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=\textwidth]{Fig/field_dn_N12_t160}
+%	\caption{Comparison for constant time slice for the field data example ($t=0.64$s).
 (a) Incomplete data.
@@
 }
-	\label{fig:field_dn_N12_t160}
-\end{figure}
+%	\label{fig:field_dn_N12_t160}
+%\end{figure}
 

### 2020-11-03 odrr5d/paper.tex
2020年11月 2日 星期一 21时31分03秒 CST

@@
 We also compare the level-four block Hankel matrices of different methods.
-Figures \ref{fig:H} and \ref{fig:H0} shows the Hankel matrices for the clean and incomplete data for the frequency slice of 30Hz.
-Figures \ref{fig:H_z} and \ref{fig:H0_z} show the zoomed Hankel matrices for the clean and incomplete data.
-The zooming areas are highlighted by the red rectangles shown in Figures \ref{fig:H} and \ref{fig:H0}.
+Figures \ref{fig:H_clean} and \ref{fig:H_obs} shows the Hankel matrices for the clean and incomplete data for the frequency slice of 30Hz.
+Figures \ref{fig:H-z-clean} and \ref{fig:H-z-obs} show the zoomed Hankel matrices for the clean and incomplete data.
+The zooming areas are highlighted by the red rectangles shown in Figures \ref{fig:H_clean} and \ref{fig:H_obs}.
 Because of the missing traces, the Hankel matrix contains a number of blank areas.
-Figure \ref{fig:Hs} shows the Hankel matrices for different methods.
+Figure \ref{fig:H_rr1,H_rr10,H_drr1,H_drr10,H_odrr1,H_odrr10} shows the Hankel matrices for different methods.
 The left column correspond to the Hankel matrices after 1 iteration.
 The right column correspond to the Hankel matrices after 10 iterations.
-We only conclude from Figure \ref{fig:Hs} that after 10 iterations all three methods obtain similar Hankel matrices as the exact solution shown in Figure \ref{fig:H} but we cannot see the difference between different methods clearly.
-The differences between different methods can be clearly observed from the zoomed Hankel matrices, as shown in Figure \ref{fig:Hsz}.
-It is clear that from the top to bottom in Figure \ref{fig:Hsz}, the Hankel matrix becomes smoother and smoother and is closer to the exact solution shown in Figure \ref{fig:H_z}.
+We only conclude from Figure \ref{fig:H_rr1,H_rr10,H_drr1,H_drr10,H_odrr1,H_odrr10} that after 10 iterations all three methods obtain similar Hankel matrices as the exact solution shown in Figure \ref{fig:H_clean} but we cannot see the difference between different methods clearly.
+The differences between different methods can be clearly observed from the zoomed Hankel matrices, as shown in Figure \ref{fig:H-z-rr1,H-z-rr10,H-z-drr1,H-z-drr10,H-z-odrr1,H-z-odrr10}.
+It is clear that from the top to bottom in Figure \ref{fig:H-z-rr1,H-z-rr10,H-z-drr1,H-z-drr10,H-z-odrr1,H-z-odrr10}, the Hankel matrix becomes smoother and smoother and is closer to the exact solution shown in Figure \ref{fig:H-z-clean}.
 
@@
 We then test the performance when the rank is chosen smaller.
-The reconstructed data when $rank=5$ are shown in Figure \ref{fig:syn_dn_N5}.
-Their corresponding error sections are shown in Figure \ref{fig:syn_e_N5}.
-From Figures \ref{fig:syn_dn_N5} and \ref{fig:syn_e_N5}, we can reach almost the same conclusion as the last test.
+The reconstructed data when $rank=5$ are shown in Figure \ref{fig:figure10}.
+Their corresponding error sections are shown in Figure \ref{fig:figure11}.
+From Figures \ref{fig:figure10} and \ref{fig:figure11}, we can reach almost the same conclusion as the last test.
 In this case, the SNRs of the reconstructed results via the RR method, the DRR method, and ORR method are 8.01 dB, 10.87 dB, and 11.97 dB, respectively.
@@
 
-%
-%\begin{figure}
-%	\centering
-%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H}
-%    \label{fig:H}}
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H0}
-%    \label{fig:H0}}\\
-%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H_z}
-%    \label{fig:H_z}}
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H0_z}
-%    \label{fig:H0_z}}
-%	\caption{Hankel matrices for the clean and observed data for frequency slice of 30Hz.
+\inputdir{hankel}
+\multiplot{4}{H_clean,H_obs,H-z-clean,H-z-obs}{width=0.45\textwidth}{Hankel matrices for the clean and observed data for frequency slice of 30Hz.
 (a) Hankel matrix of the clean data.
@@
 The zooming area is highlighted by the red rectangles.}
-%	\label{fig:HH}
-%\end{figure}
-%
-%\begin{figure}
-%	\centering
-%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_1}
-%    \label{fig:H1_1}}
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_1}
-%    \label{fig:H2_1}}\\
-%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_2}
-%    \label{fig:H1_2}}
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_2}
-%    \label{fig:H2_2}}\\
-%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_3}
-%    \label{fig:H1_3}}
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_3}
-%    \label{fig:H2_3}}
-%	\caption{Hankel matrices for different methods for frequency slice of 30Hz.
+
+\multiplot{6}{H_rr1,H_rr10,H_drr1,H_drr10,H_odrr1,H_odrr10}{width=0.35\textwidth}{Hankel matrices for different methods for frequency slice of 30Hz.
 Left column: Hankel matrix after 1 iteration.
@@
 Bottom row: Hankel matrix for the ORR method.}
-%	\label{fig:Hs}
-%\end{figure}
-%
-%\begin{figure}
-%	\centering
-%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_1_z}
-%    \label{fig:H1_1_z}}
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_1_z}
-%    \label{fig:H2_1_z}}\\
-%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_2_z}
-%    \label{fig:H1_2_z}}
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_2_z}
-%    \label{fig:H2_2_z}}\\
-%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_3_z}
-%    \label{fig:H1_3_z}}
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_3_z}
-%    \label{fig:H2_3_z}}
-%	\caption{Zoomed Hankel matrices for different methods for frequency slice of 30Hz.
+
+\multiplot{6}{H-z-rr1,H-z-rr10,H-z-drr1,H-z-drr10,H-z-odrr1,H-z-odrr10}{width=0.35\textwidth}{Zoomed Hankel matrices for different methods for frequency slice of 30Hz.
 Left column: Hankel matrix after 1 iteration.
@@
 Bottom row: Hankel matrix for the ORR method.}
-%	\label{fig:Hsz}
-%\end{figure}
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=0.8\textwidth]{Fig/syn_dn_N5}
-%	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix).
+
+\inputdir{synth2}
+\plot{figure10}{width=0.8\textwidth}{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix).
 (a) Reconstructed data using the RR method.
@@
 (c) Reconstructed data using the ORR method.
-In this case, $rank=5$.}
-%	\label{fig:syn_dn_N5}
-%\end{figure}
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=0.8\textwidth]{Fig/syn_e_N5}
-%	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix).
+In this case, $rank=5$.
+}
+\plot{figure11}{width=0.8\textwidth}{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix).
 (a) Reconstruction error using the RR method.
@@
 }
-%	\label{fig:syn_e_N5}
-%\end{figure}
 

### 2020-11-03 odrr5d/paper.tex
2020年11月 3日 星期二 01时14分36秒 CST

@@
 
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=\textwidth]{Fig/synth_vars}
-%	\caption{SNR diagrams of the different approaches with respect to the noise level (variance value).
+\inputdir{snrs_sigma}
+\plot{snr-n}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the noise level (variance value).
 Note that the proposed approach outperforms the traditional methods more and more as the noise level increases.}
-%	\label{fig:synth_vars}
-%\end{figure}
-%
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=\textwidth]{Fig/synth_ratios}
-%	\caption{SNR diagrams of the different approaches with respect to the sampling ratio (in percent).
+
+\inputdir{snrs_ratio}
+
+\plot{snr-r}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the sampling ratio (in percent).
 \new{It is obvious that the difference between the ORR method and the DRR method becomes larger as the sampling ratio increases.
@@
 }}
-%	\label{fig:synth_ratios}
-%\end{figure}
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=\textwidth]{Fig/synth_ranks}
-%	\caption{SNR diagrams of the different approaches with respect to the selected rank.
+
+\inputdir{snrs_rank}
+\plot{snr-rank}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the selected rank.
 \new{The ORR method is obviously much less sensitive to the rank compared with other two methods.
-This phenomenon indicates that the ORR method can be applied as an adaptive method by setting a relatively large rank.}}
-%	\label{fig:synth_ranks}
-%\end{figure}
+This phenomenon indicates that the ORR method can be applied as an adaptive method by setting a relatively large rank.}
 
@@
 
-To test the sensitivities of each method to input noise level, we vary the variance of the additive random noise from 0.1 to 0.9 and calculate the output SNRs corresponding to different methods and draw the diagrams in Figure \ref{fig:synth_vars}.
+To test the sensitivities of each method to input noise level, we vary the variance of the additive random noise from 0.1 to 0.9 and calculate the output SNRs corresponding to different methods and draw the diagrams in Figure \ref{fig:snr-n}.
 The black line corresponds to the input SNR curve.
@@
 
-To test the effectiveness of each method in situations with different sampling ratios, we vary the sampling ratio from 10\% to 90\%, and draw the input and output SNR curves in Figure \ref{fig:synth_ratios}.
+To test the effectiveness of each method in situations with different sampling ratios, we vary the sampling ratio from 10\% to 90\%, and draw the input and output SNR curves in Figure \ref{fig:snr-r}.
 The colorful lines have the same meaning in this case.
-As we can see from Figure \ref{fig:synth_ratios}, the input SNR decreases with increasing sampling ratio.
+As we can see from Figure \ref{fig:snr-r}, the input SNR decreases with increasing sampling ratio.
 The output SNRs increase with increasing sampling ratios.
@@
 
-To test the sensitivities of different methods to the input parameter, i.e., the predefined \old{appealing rank}\new{rank}, we vary the rank from 4 to 15 and draw the SNR curves in Figure \ref{fig:synth_ranks}.
+To test the sensitivities of different methods to the input parameter, i.e., the predefined \old{appealing rank}\new{rank}, we vary the rank from 4 to 15 and draw the SNR curves in Figure \ref{fig:snr-rank}.
 Both RR and DRR methods decrease fast as the predefined rank increases while the SNR curve of the proposed ORR method is almost flat and is also above the other two curves.
@@
 We would like to thank Dong Zhang and Weilin Huang for inspiring discussions.
-\new{We also thank Frederik Simons and two anonymous reviewers for constructive suggestions that greatly improved the manuscript.} The research is supported by the starting fund from Zhejiang University and the ``Thousand Youth Talents Plan of China''.
+\new{We also thank Frederik Simons and two anonymous reviewers for constructive suggestions that greatly improved the manuscript.} The research is supported by the starting fund from Zhejiang University.
 
@@
 \bibliographystyle{seg}
-\bibliography{dos5d}
+\bibliography{odrr}
 

### 2020-11-03 odrr5d/matfun/SNRS_RATIO.m

@@ -1,4 +1,4 @@
-function Hankel(H_clean,H_obs,H_rr,H_drr,H_odrr,H_rr10,H_drr10,H_odrr10)
+function SNRS_RATIO(synth_drr_rs)
 % Author      : Yangkang Chen
 % Date        : Oct, 2020
 % 
@@ -35,49 +35,48 @@ var=0.25;
 dn=d+var*randn(size(d));
 
 %% decimate
-[nt,nhx,nhy,nx,ny]=size(d);
-ratio=0.3;
+
+ratios=0.1:0.1:0.9;
+
+snrs0=zeros(length(ratios),1);
+snrs1=zeros(length(ratios),1);
+snrs2=zeros(length(ratios),1);
+snrs3=zeros(length(ratios),1);
+
+fprintf('N_ratios is %d\n',length(ratios));
+for i=1:length(ratios)
+ratio=ratios(i);
 mask=yc_genmask(reshape(d,nt,nhx*nhy*nx*ny),ratio,'c',201415);
 mask=reshape(mask,nt,nhx,nhy,nx,ny);
 d0=dn.*mask;
 
-%% reconstruct
-flow=0;fhigh=100;dt=0.004;N=10;NN=4;Niter=10;mode=1;verb=1;iflb=0;
+%% parameters
+flow=5;fhigh=100;dt=0.004;N=10;Niter=10;mode=1;verb=1;iflb=0;
 a=(Niter-(1:Niter))/(Niter-1); %linearly decreasing
-tic
-[d1,M_c,M_obs,M_rr,M_rr10]=drr5d_lb_recon_H(d0,d,mask,flow,fhigh,30,dt,N,Inf,Niter,eps,verb,mode,iflb,a);
-toc
 
-tic
-[d2,M_c,M_obs,M_drr,M_drr10]=drr5d_lb_recon_H(d0,d,mask,flow,fhigh,30,dt,N,NN,Niter,eps,verb,mode,iflb,a);
-toc
+%% reconstruct (RR)
+NN=Inf;
+d1=drr5d_lb_recon(d0,mask,flow,fhigh,dt,N,NN,Niter,eps,verb,mode,iflb,a);
 
-tic
-[d3,M_c,M_obs,M_odrr,M_odrr10]=drr5d_lb_recon_H(d0,d,mask,flow,fhigh,30,dt,N,NN,Niter,eps,verb,mode,2,a);
-toc
+%% reconstruct (DRR)
+NN=4;
[…]

### 2020-11-03 odrr5d/paper.tex
2020年11月 3日 星期二 15时01分00秒 CST

@@
 
-\inputdir{snrs_sigma}
-\plot{snr-n}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the noise level (variance value).
+%\inputdir{snrs_sigma}
+%\plot{snr-n}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the noise level (variance value).
 Note that the proposed approach outperforms the traditional methods more and more as the noise level increases.}
-
-\inputdir{snrs_ratio}
-
-\plot{snr-r}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the sampling ratio (in percent).
+%
+%\inputdir{snrs_ratio}
+%
+%\plot{snr-r}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the sampling ratio (in percent).
 \new{It is obvious that the difference between the ORR method and the DRR method becomes larger as the sampling ratio increases.
@@
 }}
+%
+%
 
-\inputdir{snrs_rank}
-\plot{snr-rank}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the selected rank.
+%\inputdir{snrs_rank}
+%\plot{snr-rank}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the selected rank.
 \new{The ORR method is obviously much less sensitive to the rank compared with other two methods.
-This phenomenon indicates that the ORR method can be applied as an adaptive method by setting a relatively large rank.}
-
-%\begin{figure}
-%	\centering
-%	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d_3v}
-%    \label{fig:hyper_d_3v}}
-%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_dn_3v}
-%    \label{fig:hyper_dn_3v}}
-%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d0_3v}
-%    \label{fig:hyper_d0_3v}} \\   
-%	\caption{Common midpoint gather comparison for the synthetic example with hyperbolic events.
+This phenomenon indicates that the ORR method can be applied as an adaptive method by setting a relatively large rank.}}
+%
+%
+%\inputdir{hyper}
+%\multiplot{3}{hyper-clean-xy,hyper-noisy-xy,hyper-obs-xy}{width=0.3\textwidth}{Common midpoint gather comparison for the synthetic example with hyperbolic events.
 (a) Clean data.
@@
 (c) Incomplete data.
-\new{The blanks in (c) indicate where there are missing traces.} }
-%	\label{fig:hyper_N12}
-%\end{figure}
-%
-%
-%\begin{figure}
-%	\centering
-%	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_N12_3v}
-%    \label{fig:hyper_d1_N12_3v}}
-%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_N12_3v}
-%    \label{fig:hyper_d2_N12_3v}}
-%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_N12_3v}
-%    \label{fig:hyper_d3_N12_3v}} \\ 
-%	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_N24_3v}
-%    \label{fig:hyper_d1_N24_3v}}
-%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_N24_3v}
-%    \label{fig:hyper_d2_N24_3v}}
-%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_N24_3v}
-%    \label{fig:hyper_d3_N24_3v}} \\    
-%	\caption{Common midpoint gather comparison for the synthetic example with hyperbolic events.
+The blanks in (c) indicate where there are missing traces.
+}
+%\multiplot{6}{hyper-rr-xy,hyper-drr-xy,hyper-odrr-xy,hyper-rr2-xy,hyper-drr2-xy,hyper-odrr2-xy}{width=0.3\textwidth}{Common midpoint gather comparison for the synthetic example with hyperbolic events.
 Top row shows results when $rank=12$.
@@
 Right Reconstructed data using the ORR method.
-The SNR comparisons are shown in Table \ref{tbl:hyper}.}
-%	\label{fig:hyper_dn_N12}
-%\end{figure}
+The SNR comparisons are shown in Table \ref{tbl:hyper}.
+}
 %
-%\begin{figure}
-%	\centering
-%	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_simi_N12_3v}
-%    \label{fig:hyper_d1_simi_N12_3v}}
-%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_simi_N12_3v}
-%    \label{fig:hyper_d2_simi_N12_3v}}
-%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_simi_N12_3v}
-%    \label{fig:hyper_d3_simi_N12_3v}} \\ 
-%	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_simi_N24_3v}
-%    \label{fig:hyper_d1_simi_N24_3v}}
-%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_simi_N24_3v}
-%    \label{fig:hyper_d2_simi_N24_3v}}
-%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_simi_N24_3v}
-%    \label{fig:hyper_d3_simi_N24_3v}} \\    
-%	\caption{Local similarity comparison for the synthetic example with hyperbolic events.
+%\multiplot{6}{hyper-rr-xy-simi,hyper-drr-xy-simi,hyper-odrr-xy-simi,hyper-rr2-xy-simi,hyper-drr2-xy-simi,hyper-odrr2-xy-simi}{width=0.3\textwidth}{Local similarity comparison for the synthetic example with hyperbolic events.
 Top row shows results when $rank=12$.
@@
 }
-%	\label{fig:hyper_simi_N12}
-%\end{figure}
 
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=\textwidth]{Fig/field_d0_0}
-%	\caption{Real data example \new{with a lot of missing traces}.
+%\inputdir{./}
+%\plot{field_d0_0}{width=0.8\textwidth}{Real data example \new{with a lot of missing traces}.
 \new{Because of the difficulty in display a 5D dataset, only one common midpoint gather is extracted and rearranged into a 2D matrix, and is plotted here.
 The two transparent colored windows denote two zooming areas for an amplified comparison.}}
-%	\label{fig:field_d0_0}
-%\end{figure}
 %
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=0.9\textwidth]{Fig/field_dn_N12_0}
-%	\caption{Real data example.
+%\plot{field_dn_N12_0}{width=0.8\textwidth}{Real data example.
 (a) Reconstructed data using the RR method.
@@
 The ORR method obtains cleaner and spatially more coherent seismic events compared with other two methods.}}
-%	\label{fig:field_dn_N12_0}
-%\end{figure}
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=\textwidth]{Fig/field_dn_N12_z1}
-%	\caption{Zoomed comparison for the field data example (the blue frame box).
+%\plot{field_dn_N12_z1}{width=0.8\textwidth}{Zoomed comparison for the field data example (the blue frame box).
+(a) Incomplete data.
+(b) Reconstructed data using the RR method.
+(c) Reconstructed data using the DRR method.
+(d) Reconstructed data using the ORR method.}
+%\plot{field_dn_N12_z2}{width=0.8\textwidth}{Zoomed comparison for the field data example (the red frame box).
+(a) Incomplete data.
+(b) Reconstructed data using the RR method.
+(c) Reconstructed data using the DRR method.
+(d) Reconstructed data using the ORR method.}
+%\plot{field_dn_N12_t80}{width=0.8\textwidth}{Comparison for constant time slice for the field data example ($t=0.32$s).
+(a) Incomplete data.
+(b) Reconstructed data using the RR method.
+(c) Reconstructed data using the DRR method.
+(d) Reconstructed data using the ORR method.}
+%\plot{field_dn_N12_t160}{width=0.8\textwidth}{Comparison for constant time slice for the field data example ($t=0.64$s).
 (a) Incomplete data.
@@
 }
-%	\label{fig:field_dn_N12_z1}
-%\end{figure}
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=\textwidth]{Fig/field_dn_N12_z2}
-%	\caption{Zoomed comparison for the field data example (the red frame box).
-(a) Incomplete data.
-(b) Reconstructed data using the RR method.
-(c) Reconstructed data using the DRR method.
-(d) Reconstructed data using the ORR method.
-}
-%	\label{fig:field_dn_N12_z2}
-%\end{figure}
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=\textwidth]{Fig/field_dn_N12_t80}
-%	\caption{Comparison for constant time slice for the field data example ($t=0.32$s).
-(a) Incomplete data.
-(b) Reconstructed data using the RR method.
-(c) Reconstructed data using the DRR method.
-(d) Reconstructed data using the ORR method.
-}
-%	\label{fig:field_dn_N12_t80}
-%\end{figure}
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=\textwidth]{Fig/field_dn_N12_t160}
-%	\caption{Comparison for constant time slice for the field data example ($t=0.64$s).
-(a) Incomplete data.
-(b) Reconstructed data using the RR method.
-(c) Reconstructed data using the DRR method.
-(d) Reconstructed data using the ORR method.
-}
-%	\label{fig:field_dn_N12_t160}
-%\end{figure}
-
 }
@@
 In order to test the effectiveness of the three methods on data containing curved events and to compare the performances of different methods in this case, we then use the second example to show the performance.
-Figure \ref{fig:hyper_N12} shows the clean data, noisy data, and incomplete data with 70\% traces randonly missing in a common midpoint gather.
-Figure \ref{fig:hyper_dn_N12} shows the reconstructed data using different methods.
+Figure \ref{fig:hyper-clean-xy,hyper-noisy-xy,hyper-obs-xy} shows the clean data, noisy data, and incomplete data with 70\% traces randonly missing in a common midpoint gather.
+Figure \ref{fig:hyper-rr-xy,hyper-drr-xy,hyper-odrr-xy,hyper-rr2-xy,hyper-drr2-xy,hyper-odrr2-xy} shows the reconstructed data using different methods.
 Because this dataset no longer meet the linear-event assumption of the rank-reduction based methods, we use a relatively higher rank in this example.
-The top row in Figure \ref{fig:hyper_dn_N12} shows results when $rank = 12$.
-The bottom row in Figure \ref{fig:hyper_dn_N12} shows results when $rank = 24$.
+The top row in Figure \ref{fig:hyper-rr-xy,hyper-drr-xy,hyper-odrr-xy,hyper-rr2-xy,hyper-drr2-xy,hyper-odrr2-xy} shows results when $rank = 12$.
+The bottom row in Figure \ref{fig:hyper-rr-xy,hyper-drr-xy,hyper-odrr-xy,hyper-rr2-xy,hyper-drr2-xy,hyper-odrr2-xy} shows results when $rank = 24$.
 It is clear that the three methods also work when there are curving events.
@@
 The SNRs of the incomplete data, data from the RR method, DRR method, and ORR method are 0.59, 14.11, 16.46, and 16.86 dB when $rank=12$ and are 0.59, 13.88, 16.01, and 16.83 dB when $rank=24$.
-We also calculate the local similarity between the exact solution shown in Figure \ref{fig:hyper_d_3v} and each reconstructed data and show the similarity cubes in Figure \ref{fig:hyper_simi_N12}.
+We also calculate the local similarity between the exact solution shown in Figure \ref{fig:hyper-clean-xy} and each reconstructed data and show the similarity cubes in Figure \ref{fig:hyper-rr-xy-simi,hyper-drr-xy-simi,hyper-odrr-xy-simi,hyper-rr2-xy-simi,hyper-drr2-xy-simi,hyper-odrr2-xy-simi}.
 The local similarity corresponding to the proposed method is obviously higher than those from the  other two methods, indicating a more accurate reconstruction result using the proposed method.

### 2020-11-03 odrr5d/matfun/SNRS_RATIO.m

@@ -76,7 +76,7 @@ end
 
 
 %% from Matlab to Madagascar
-snrs=[ratios',snrs1',snrs2',snrs3'];
+snrs=[ratios(:),snrs1(:),snrs2(:),snrs3(:)];
 rsf_create(synth_drr_rs,size(snrs)');
 rsf_write(snrs,synth_drr_rs);
 

### 2020-11-04 odrr5d/paper.tex
2020年11月 4日 星期三 10时44分00秒 CST

@@
 
-%\inputdir{snrs_sigma}
-%\plot{snr-n}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the noise level (variance value).
+\inputdir{snrs_sigma}
+\plot{snr-n}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the noise level (variance value).
 Note that the proposed approach outperforms the traditional methods more and more as the noise level increases.}
-%
-%\inputdir{snrs_ratio}
-%
-%\plot{snr-r}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the sampling ratio (in percent).
+
+\inputdir{snrs_ratio}
+
+\plot{snr-r}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the sampling ratio (in percent).
 \new{It is obvious that the difference between the ORR method and the DRR method becomes larger as the sampling ratio increases.
@@
 }}
-%
-%
 
-%\inputdir{snrs_rank}
-%\plot{snr-rank}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the selected rank.
+\inputdir{snrs_rank}
+\plot{snr-rank}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the selected rank.
 \new{The ORR method is obviously much less sensitive to the rank compared with other two methods.
 This phenomenon indicates that the ORR method can be applied as an adaptive method by setting a relatively large rank.}}
-%
+
 %

### 2020-11-06 odrr5d/paper.tex
2020年11月 6日 星期五 01时36分29秒 CST

@@
 
-%\inputdir{./}
-%\plot{field_d0_0}{width=0.8\textwidth}{Real data example \new{with a lot of missing traces}.
+\inputdir{./}
+\plot{field_d0_0}{width=0.8\textwidth}{Real data example \new{with a lot of missing traces}.
 \new{Because of the difficulty in display a 5D dataset, only one common midpoint gather is extracted and rearranged into a 2D matrix, and is plotted here.
 The two transparent colored windows denote two zooming areas for an amplified comparison.}}
-%
-%\plot{field_dn_N12_0}{width=0.8\textwidth}{Real data example.
+
+\plot{field_dn_N12_0}{width=0.8\textwidth}{Real data example.
 (a) Reconstructed data using the RR method.
@@
 The ORR method obtains cleaner and spatially more coherent seismic events compared with other two methods.}}
-%\plot{field_dn_N12_z1}{width=0.8\textwidth}{Zoomed comparison for the field data example (the blue frame box).
+\plot{field_dn_N12_z1}{width=0.8\textwidth}{Zoomed comparison for the field data example (the blue frame box).
 (a) Incomplete data.
@@
 (d) Reconstructed data using the ORR method.}
-%\plot{field_dn_N12_z2}{width=0.8\textwidth}{Zoomed comparison for the field data example (the red frame box).
+\plot{field_dn_N12_z2}{width=0.8\textwidth}{Zoomed comparison for the field data example (the red frame box).
 (a) Incomplete data.
@@
 (d) Reconstructed data using the ORR method.}
-%\plot{field_dn_N12_t80}{width=0.8\textwidth}{Comparison for constant time slice for the field data example ($t=0.32$s).
+\plot{field_dn_N12_t80}{width=0.8\textwidth}{Comparison for constant time slice for the field data example ($t=0.32$s).
 (a) Incomplete data.
@@
 (d) Reconstructed data using the ORR method.}
-%\plot{field_dn_N12_t160}{width=0.8\textwidth}{Comparison for constant time slice for the field data example ($t=0.64$s).
+\plot{field_dn_N12_t160}{width=0.8\textwidth}{Comparison for constant time slice for the field data example ($t=0.64$s).
 (a) Incomplete data.

### 2020-11-06 odrr5d/paper.tex
2020年11月 6日 星期五 10时11分21秒 CST

@@
 
-%
-%\inputdir{hyper}
-%\multiplot{3}{hyper-clean-xy,hyper-noisy-xy,hyper-obs-xy}{width=0.3\textwidth}{Common midpoint gather comparison for the synthetic example with hyperbolic events.
+\inputdir{hyper}
+\multiplot{3}{hyper-clean-hxhy,hyper-noisy-hxhy,hyper-obs-hxhy}{width=0.3\textwidth}{Common midpoint gather comparison for the synthetic example with hyperbolic events.
 (a) Clean data.
@@
 }
-%\multiplot{6}{hyper-rr-xy,hyper-drr-xy,hyper-odrr-xy,hyper-rr2-xy,hyper-drr2-xy,hyper-odrr2-xy}{width=0.3\textwidth}{Common midpoint gather comparison for the synthetic example with hyperbolic events.
+\multiplot{6}{hyper-rr-hxhy,hyper-drr-hxhy,hyper-odrr-hxhy,hyper-rr2-hxhy,hyper-drr2-hxhy,hyper-odrr2-hxhy}{width=0.3\textwidth}{Common midpoint gather comparison for the synthetic example with hyperbolic events.
 Top row shows results when $rank=12$.
@@
 }
-%
-%\multiplot{6}{hyper-rr-xy-simi,hyper-drr-xy-simi,hyper-odrr-xy-simi,hyper-rr2-xy-simi,hyper-drr2-xy-simi,hyper-odrr2-xy-simi}{width=0.3\textwidth}{Local similarity comparison for the synthetic example with hyperbolic events.
+
+\multiplot{6}{hyper-rr-hxhy-simi,hyper-drr-hxhy-simi,hyper-odrr-hxhy-simi,hyper-rr2-hxhy-simi,hyper-drr2-hxhy-simi,hyper-odrr2-hxhy-simi}{width=0.3\textwidth}{Local similarity comparison for the synthetic example with hyperbolic events.
 Top row shows results when $rank=12$.

### 2020-11-08 sgk5d/matfun/Field.m
2020年11月 8日 星期日 17时47分27秒 CST

@@ -1,13 +1,13 @@
 function Field(clean,noisy,obs,sgk,ksvd,ddtf,mssa,mssasgk,T,niter,nniter,K,ll1,ll2,ll3,ss1,ss2,ss3,perc)
-% Author      : Yangkang Chen
+% Author      : Hang Wang and Yangkang Chen
 %               Zhejiang University
 %         
 % Date        : April, 2020
-
+%
 % Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
-    
+%
 %  Copyright (C) 2020 Zhejiang University
-%  Copyright (C) 2020 Yangkang Chen
+%  Copyright (C) 2020 Hang Wang and Yangkang Chen
 %  
 %  This program is free software; you can redistribute it and/or modify
 %  it under the terms of the GNU General Public License as published by
@@ -22,15 +22,13 @@ function Field(clean,noisy,obs,sgk,ksvd,ddtf,mssa,mssasgk,T,niter,nniter,K,ll1,l
 %  You should have received a copy of the GNU General Public License
 %  along with this program; if not, write to the Free Software
 %  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  
-
-addpath(genpath('~/chenyk/matlibcyk'));
-%clc;clear;close all;
-% DEMO script for 3D denoising and reconstruction based on KSVD
-% By Yangkang Chen
-% March, 2020
+%  
+%  Reference:
+%  Wang et al., 2020, Fast dictionary learning for high-dimensional seismic reconstruction, IEEE TGRS, doi: 10.1109/TGRS.2020.3030740
+%  Chen, 2020, Fast dictionary learning for noise attenuation of multidimensional seismic data, GJI, 222, 1717??1727.
 
 %% create data
-fid=fopen('~/chenyk.open/reproduce/drr3d/matfun/real3d.bin','r');
+fid=fopen('./real3d.bin','r');
[…]

### 2020-11-08 sgk5d/matfun/Synth.m

@@ -1,13 +1,13 @@
 function Synth(clean,noisy,obs,sgk,ksvd,ddtf,mssa,mssasgk,T,niter,nniter,K,ll1,ll2,ll3,ss1,ss2,ss3,perc)
-% Author      : Yangkang Chen
+% Author      : Hang Wang and Yangkang Chen
 %               Zhejiang University
 %         
 % Date        : April, 2020
-
+%
 % Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
-    
+%
 %  Copyright (C) 2020 Zhejiang University
-%  Copyright (C) 2020 Yangkang Chen
+%  Copyright (C) 2020 Hang Wang and Yangkang Chen
 %  
 %  This program is free software; you can redistribute it and/or modify
 %  it under the terms of the GNU General Public License as published by
@@ -22,12 +22,10 @@ function Synth(clean,noisy,obs,sgk,ksvd,ddtf,mssa,mssasgk,T,niter,nniter,K,ll1,l
 %  You should have received a copy of the GNU General Public License
 %  along with this program; if not, write to the Free Software
 %  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  
-
-addpath(genpath('~/chenyk/matlibcyk'));
-%clc;clear;close all;
-% DEMO script for 3D denoising and reconstruction based on KSVD
-% By Yangkang Chen
-% March, 2020
+%  
+%  Reference:
+%  Wang et al., 2020, Fast dictionary learning for high-dimensional seismic reconstruction, IEEE TGRS, doi: 10.1109/TGRS.2020.3030740
+%  Chen, 2020, Fast dictionary learning for noise attenuation of multidimensional seismic data, GJI, 222, 1717-1727.
 
 %% create data
 a1=zeros(300,20);
@@ -69,7 +67,6 @@ end
 plane3d=shot;
 dc=yc_scale(plane3d,3);
 dc=dc(51:225,:,:);
[…]

### 2020-11-08 sgk5d/matfun/fxymssa_recon.m

@@ -1,0 +1,220 @@
+function [ D1 ] = fxymssa_recon(D,MASK,flow,fhigh,dt,N,Niter,eps,verb,mode,a)
+%  FXYMSSA_RECON: F-XY domain multichannel singular spectrum analysis (MSSA) for
+%  simultaneous denoising and reconstruction
+%
+%  IN   D:   	intput 3D data
+%       MASK:   sampling mask (consistent with the POCS based approaches)
+%       flow:   processing frequency range (lower)
+%       fhigh:  processing frequency range (higher)
+%       dt:     temporal sampling interval
+%       N:      number of singular value to be preserved
+%       Niter:  number of maximum iteration
+%       eps:    tolerence (||S(n)-S(n-1)||_F<eps)
+%       verb:   verbosity flag (default: 0)
+%       mode:   mode=1: denoising and reconstruction
+%               mode=0: reconstruction only
+%       a:      weight vector
+%
+%  OUT  D1:  	output data
+%
+%  Copyright (C) 2015 The University of Texas at Austin
+%  Copyright (C) 2015 Yangkang Chen
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details: http://www.gnu.org/licenses/
+%
+%  References:   
+%
+%  Chen, Y., W. Huang, D. Zhang, W. Chen, 2016, An open-source matlab code package for improved rank-reduction 3D seismic data denoising and reconstruction, Computers & Geosciences, 95, 59-66.
[…]

### 2020-11-08 sgk5d/matfun/plotatom3d.m

@@ -1,66 +1,0 @@
-function plotatom3d(d0,L1,L2,L3)
-% yc_plotatom3d: plot atoms in 3D cubes
-% 
-% 
-% DEMO
-% test/test_ksvd3d.m
-% 
-l1=L3;
-l2=L2;
-l3=L1;
-
-n1 = size(d0,1);
-n2 = size(d0,2);
-% n = round(n1^(1.0/3.0));      
-d0(n1,:)=d0(n1,:)*1.00001;
-newd = zeros(l1+1,l1+1,l3+1);
-% tm =[1 2 5 17 6 18 21 22];  % 4
-% tm =[1 2 9 65 10 66 73 74]; % 8
-% tm =[1 2 3 4 5 6 7 8]; % 8
-% tm =[1 2 4 6 8 9 10 11 24 25 26 28 31 32 41 44] ;%8-di-elf
-tm =[1 2 3 4 6 8 9 12 20 21 22 27 32 54 56 58] ;%8-d-X
-% tm=[1:64];
-tm=[1,2,3,5,13,17,18,21,22,25,29,30,33,34,37,38,39,40,41,42,43,45,46,47,49,55,57,58,59,63];
-tm=[1,2,3,5,17,18,29,33,39,40,46,47,49,58,59,63];
-% tm = [1 2 8 50 9 51 57 58]; % 7
-% tm = [1 2 4 5 8 10 11 18 19 23 24 25 26 30 31 32 33 52 53 54]; % 7-2
-%   tm = 1:64;
-for m = 1:1
-    figure;
-    for i=1:length(tm)
-
-        subplot(4,4,i);
-%                 subplot(8,8,i);
-        newd = zeros(l1+1,l2+1,l3+1);
-        % DisplayH3d( reshape(d0(:,16/16*(i-1)+1),n,n,n));
-%         p = (m-1)*n*n+(i-1)+1;
-        p = tm(i) ;
-        newd(1:l1,1:l2,1:l3) = yc_transp(reshape(d0(:,p),L1,L2,L3),13);
-        newd(:,:,l3+1) = newd(:,:,l3);
-        newd(:,l2+1,:) = newd(:,l2,:);
-        newd(l1+1,:,:) = newd(l1,:,:);
-        slice(newd,[1,l1+1],[1,l2+1],[1,l3+1]);caxis([-0.15,0.15]);%colormap gray;
-        
-        h=findobj(gca,'linestyle','-');
-        h(1)=h(2);
[…]

### 2020-11-08 sgk5d/matfun/yc_ddtf_recon.m

@@ -1,0 +1,140 @@
+function [dout]=yc_ddtf_recon(d0,mask,mode,l,s,perc,niter,a,param)
+%yc_ddtf_recon: DDTF algorithm for 2D/3D reconstruction
+% BY Yangkang Chen and Hang Wang
+% Jan, 2020
+%
+% INPUT
+%   mode: patching mode
+%   l: [l1,l2,l3]
+%   l1: first patch size
+%   l2: second patch size
+%   l3: third patch size
+%   s: [s1,s2,s3]
+%   s1: first shifting size
+%   s2: second shifting size
+%   s3: third shifting size
+%   perc: percentage
+% param: parameter struct for DL
+%   param.mode=1;   %1: sparsity; 0: error
+%   param.niter=10; %number of SGK iterations to perform; default: 10
+%   param.D=DCT;    %initial D
+%   param.T=3;      %sparsity level
+%
+% OUTPUT
+% dout:
+%
+% for X=DG
+% size of X: MxN
+% size of D: MxK
+% size of G: KxN
+%
+% DEMO:
+% test/test_yc_sgk_recon.m
+% test/test_yc_sgk_recon3d.m
+%
+% References:
+% Wang et al., 2020, Fast dictionary learning for high-dimensional seismic reconstruction, IEEE Transactions on Geoscience and Remote Sensing, % Chen, Y., 2020, Fast dictionary learning for noise attenuation of multidimensional seismic data, Geophysical Journal International, 222, 1717-1727.
+
+[n1,n2,n3,n4,n5]=size(d0);
+
+if isfield(param,'d0')
+    d1=param.d0;
+    fprintf('Using given model as the initilization\n');
+else
+    if isfield(param,'init') && (param.init==1)
+        d1=yc_dlrecon_init(d0,mask,'nearest');
+    fprintf('Using linear interpolation as the initilization\n');
+    else
+    d1=d0;
+    fprintf('Using the input as the initilization\n');
+    end
+end
+
+
+l1=l(1);
+l2=l(2);
+l3=l(3);
+
+s1=s(1);
+s2=s(2);
+s3=s(3);
+
+%initialization
+%[c1,c2,c3]: redundancy of the initial atom in 1st,2nd,3rd dimensions
[…]

### 2020-11-08 sgk5d/matfun/yc_ksvd_recon.m

@@ -1,0 +1,141 @@
+
+function [dout]=yc_ksvd_recon(d0,mask,mode,l,s,perc,niter,a,param)
+%yc_ksvd_recon: K-SVD algorithm for 2D/3D reconstruction
+% BY Yangkang Chen and Hang Wang
+% Jan, 2020
+%
+% INPUT
+%   mode: patching mode
+%   l: [l1,l2,l3]
+%   l1: first patch size
+%   l2: second patch size
+%   l3: third patch size
+%   s: [s1,s2,s3]
+%   s1: first shifting size
+%   s2: second shifting size
+%   s3: third shifting size
+%   perc: percentage
+% param: parameter struct for DL
+%   param.mode=1;   %1: sparsity; 0: error
+%   param.niter=10; %number of K-SVD iterations to perform; default: 10
+%   param.D=DCT;    %initial D
+%   param.T=3;      %sparsity level
+%
+% OUTPUT
+% dout:
+%
+% for X=DG
+% size of X: MxN
+% size of D: MxK
+% size of G: KxN
+%
+% DEMO: 
+% test/test_yc_ksvd_recon.m
+% test/test_yc_ksvd_recon3d.m
+%
+% References:
+% Wang et al., 2020, Fast dictionary learning for high-dimensional seismic reconstruction, IEEE Transactions on Geoscience and Remote Sensing, % Chen, Y., 2020, Fast dictionary learning for noise attenuation of multidimensional seismic data, Geophysical Journal International, 222, 1717-1727.
+
+[n1,n2,n3,n4,n5]=size(d0);
+if isfield(param,'d0')
+    d1=param.d0;
+    fprintf('Using given model as the initilization\n');
+else
+    if isfield(param,'init') && (param.init==1)
+        d1=yc_dlrecon_init(d0,mask,'nearest');
+    fprintf('Using linear interpolation as the initilization\n');
+    else
+    d1=d0;
+    fprintf('Using the input as the initilization\n');
+    end
+end
+
+
+l1=l(1);
+l2=l(2);
+l3=l(3);
+
+s1=s(1);
+s2=s(2);
+s3=s(3);
+
+%initialization
[…]

### 2020-11-08 sgk5d/matfun/yc_ksvd_recon5d.m

@@ -1,0 +1,151 @@
+function [dout]=yc_ksvd_recon5d(d0,mask,mode,l,s,perc,niter,a,param)
+%yc_ksvd_recon: K-SVD algorithm for 2D/3D reconstruction
+% BY Yangkang Chen and Hang Wang
+% Jan, 2020
+% March, 2020
+% Modified on April, 2020 (3D-4D/5D)
+%
+% INPUT
+%   mode: patching mode
+%   l: [l1,l2,l3,l4,l5]
+%   l1: first patch size
+%   l2: second patch size
+%   l3: third patch size
+%   l4: fourth patch size
+%   l5: fifth patch size
+%   s: [s1,s2,s3,s4,s5]
+%   s1: first shifting size
+%   s2: second shifting size
+%   s3: third shifting size
+%   s4: fourth shifting size
+%   s5: fifth shifting size
+%   perc: percentage
+%   param: parameter struct for DL
+%   param.mode=1;   %1: sparsity; 0: error
+%   param.niter=10; %number of K-SVD iterations to perform; default: 10
+%   param.D=DCT;    %initial D
+%   param.T=3;      %sparsity level
+%
+% OUTPUT
+% dout:
+%
+% for X=DG
+% size of X: MxN
+% size of D: MxK
+% size of G: KxN
+%
+% DEMO:
+% test/test_yc_ksvd_recon.m
+% test/test_yc_ksvd_recon3d.m
+%
+% References:
+% Wang et al., 2020, Fast dictionary learning for high-dimensional seismic reconstruction, IEEE Transactions on Geoscience and Remote Sensing, % Chen, Y., 2020, Fast dictionary learning for noise attenuation of multidimensional seismic data, Geophysical Journal International, 222, 1717-1727.
+
+[n1,n2,n3,n4,n5]=size(d0);
+d1=d0;
+
+l1=l(1);
+l2=l(2);
+l3=l(3);
+l4=l(4);
+l5=l(5);
+
+s1=s(1);
+s2=s(2);
+s3=s(3);
+s4=s(4);
+s5=s(5);
+
+%initialization
+%[c1,c2,c3,c4,c5]: redundancy of the initial atom in 1st,2nd,3rd,4th,5th dimensions
+%[l1,l2,l3,l4,l5]: patch sizes and the atom sizes in each dimension
+if ~isfield(param,'D')
[…]

### 2020-11-08 sgk5d/matfun/yc_ompN.m

@@ -2,6 +2,10 @@ function [ G ] = yc_ompN( D, X, K )
 %multi-column sparse coding
 % BY Yangkang Chen
 % Jan, 2020
+%
+% References:
+% Wang et al., 2020, Fast dictionary learning for high-dimensional seismic reconstruction, IEEE Transactions on Geoscience and Remote Sensing, % Chen, Y., 2020, Fast dictionary learning for noise attenuation of multidimensional seismic data, Geophysical Journal International, 222, 1717-1727.
+
 [n1,n2]=size(X);
 [n1,n3]=size(D);
 G=zeros(n3,n2);

### 2020-11-08 sgk5d/matfun/yc_patch.m

@@ -1,4 +1,4 @@
-function [ X ] = yc_patch( A,mode,l1,l2,o1,o2 )
+function [ X ] = yc_patch( A,mode,l1,l2,s1,s2 )
 %decompose the image into patches:
 %  
 % by Yangkang Chen
@@ -9,14 +9,14 @@ function [ X ] = yc_patch( A,mode,l1,l2,o1,o2 )
 %   mode: patching mode
 %   l1: first patch size
 %   l2: second patch size
-%   o1: first shifting size
-%   o2: second shifting size
+%   s1: first shifting size
+%   s2: second shifting size
 %   
 % Output:
 %   X: patches
 % 
 % Modified on Dec 12, 2018 (the edge issue, arbitrary size for the matrix)
-% 		      Dec 31, 2018 (tmp1=mod(n1,l1) -> tmp1=mod(n1-l1,o1))
+% 		      Dec 31, 2018 (tmp1=mod(n1,l1) -> tmp1=mod(n1-l1,s1))
 % 
 % References:
 % Wang et al., 2020, Fast dictionary learning for high-dimensional seismic reconstruction, IEEE Transactions on Geoscience and Remote Sensing, doi: 10.1109/TGRS.2020.3030740
@@ -41,28 +41,28 @@ function [ X ] = yc_patch( A,mode,l1,l2,o1,o2 )
 if mode==1 %possible for other patching options
 
 if nargin==2
-   l1=8;l2=8;o1=4;o2=4; 
+   l1=8;l2=8;s1=4;s2=4; 
 end
 
 if nargin==4
-   o1=round(l1/2);o2=round(l2/2);
+   s1=round(l1/2);s2=round(l2/2);
 end
 
-tmp=mod(n1-l1,o1);
+tmp=mod(n1-l1,s1);
 if tmp~=0
-   A=[A;zeros(o1-tmp,n2)]; 
+   A=[A;zeros(s1-tmp,n2)]; 
 end
-tmp=mod(n2-l2,o2);
+tmp=mod(n2-l2,s2);
 if tmp~=0
-   A=[A,zeros(size(A,1),o2-tmp)]; 
+   A=[A,zeros(size(A,1),s2-tmp)]; 
 end
 
 
 
 [N1,N2]=size(A);
  X=[];
-for i1=1:o1:N1-l1+1
-    for i2=1:o2:N2-l2+1
+for i1=1:s1:N1-l1+1
[…]

### 2020-11-08 sgk5d/matfun/yc_patch3d.m

@@ -1,23 +1,25 @@
-function [ X ] = yc_patch( A,mode,l1,l2,o1,o2 )
-%decompose the image into patches:
-%  
-% by Yangkang Chen
-% Oct, 2017
+function [ X ] = yc_patch3d( A,mode,l1,l2,l3,s1,s2,s3)
+%decompose 3D data into patches:
 %
-% Input: 
+% by Yangkang Chen
+% March, 2020
+%
+% Input:
 %   D: input image
 %   mode: patching mode
 %   l1: first patch size
 %   l2: second patch size
-%   o1: first shifting size
-%   o2: second shifting size
-%   
+%   l3: third patch size
+%   s1: first shifting size
+%   s2: second shifting size
+%   s3: third shifting size
+%
 % Output:
 %   X: patches
-% 
+%
 % Modified on Dec 12, 2018 (the edge issue, arbitrary size for the matrix)
-% 		      Dec 31, 2018 (tmp1=mod(n1,l1) -> tmp1=mod(n1-l1,o1))
-% 
+% 		      Dec 31, 2018 (tmp1=mod(n1,l1) -> tmp1=mod(n1-l1,s1))
+%
 % References:
 % Wang et al., 2020, Fast dictionary learning for high-dimensional seismic reconstruction, IEEE Transactions on Geoscience and Remote Sensing, doi: 10.1109/TGRS.2020.3030740
 % Siahsar, M. A. N., Gholtashi, S., Kahoo, A. R., W. Chen, and Y. Chen, 2017, Data-driven multi-task sparse dictionary learning for noise attenuation of 3D seismic data, Geophysics, 82, V385-V396.
@@ -30,43 +32,55 @@ function [ X ] = yc_patch( A,mode,l1,l2,o1,o2 )
 % Chen, Y., J. Ma, and S. Fomel, 2016, Double-sparsity dictionary for seismic noise attenuation, Geophysics, 81, V17-V30.
 % Zu, S., H. Zhou, R. Wu, M. Jiang, and Y. Chen, 2019, Dictionary learning based on dip patch selection training for random noise attenuation, Geophysics, 84, V169?V183.
[…]

### 2020-11-08 sgk5d/matfun/yc_patch3d_inv.m

@@ -1,0 +1,102 @@
+function [ A ] = yc_patch3d_inv( X,mode,n1,n2,n3,l1,l2,l3,s1,s2,s3 )
+% insert patches into the 3D data
+%
+% by Yangkang Chen
+% March, 2020
+%
+% Input:
+%   D: input image
+%   mode: patching mode
+%   n1: first dimension size
+%   n1: second dimension size
+%   n3: third dimension size
+%   l1: first patch size
+%   l2: second patch size
+%   l3: third patch size
+%   s1: first shifting size
+%   s2: second shifting size
+%   s3: third shifting size
+%
+% Output:
+%   X: patches
+%
+% Modified on Dec 12, 2018 (the edge issue, arbitrary size for the matrix)
+% 		      Dec 31, 2018 (tmp1=mod(n1,l1) -> tmp1=mod(n1-l1,s1))
+%             Marich, 31, 2020, 2D->3D
+%
+% References:
+% Chen, Y., M. Zhang, M. Bai, and W. Chen, 2019, Improving the signal-to-noise ratio of seismological datasets by unsupervised machine learning, Seismological Research Letters, 90, 1552-1564.
+% Wang, H., Q. Zhang, G. Zhang, J. Fang, and Y. Chen, 2020, Self-training and learning the waveform features of microseismic data using an adaptive dictionary, Geophysics, 85, KS51?KS61.
+% Chen, Y., S. Zu, W. Chen, M. Zhang, and Z. Guan, 2019, Learning the blending spikes using sparse dictionaries, Geophysical Journal International, 218, 1379?1397. 
+% Chen, Y., 2017, Fast dictionary learning for noise attenuation of multidimensional seismic data, Geophysical Journal International, 209, 21-31.
+% Chen, Y., J. Ma, and S. Fomel, 2016, Double-sparsity dictionary for seismic noise attenuation, Geophysics, 81, V17-V30.
+% Siahsar, M. A. N., Gholtashi, S., Kahoo, A. R., W. Chen, and Y. Chen, 2017, Data-driven multi-task sparse dictionary learning for noise attenuation of 3D seismic data, Geophysics, 82, V385-V396.
[…]

### 2020-11-08 sgk5d/matfun/yc_patch5d.m

@@ -1,22 +1,34 @@
-function [ X ] = yc_patch( A,mode,l1,l2,o1,o2 )
-%decompose the image into patches:
-%  
-% by Yangkang Chen
-% Oct, 2017
+function [ X ] = yc_patch5d( A,mode,l1,l2,l3,l4,l5,s1,s2,s3,s4,s5)
+%decompose 4D/5D data into patches:
 %
-% Input: 
+% by Yangkang Chen
+% March, 2020
+%
+% Input:
 %   D: input image
 %   mode: patching mode
 %   l1: first patch size
 %   l2: second patch size
-%   o1: first shifting size
-%   o2: second shifting size
-%   
+%   l3: third patch size
+%   l4: fourth patch size
+%   l5: fifth patch size    (when n5=1, l5=1, s5=0)
+%   s1: first shifting size
+%   s2: second shifting size
+%   s3: third shifting size
+%   s4: fourth shifting size
+%   s5: fifth shifting size (when n5=1, l5=1, s5=0)
+%
 % Output:
 %   X: patches
-% 
+%
 % Modified on Dec 12, 2018 (the edge issue, arbitrary size for the matrix)
-% 		      Dec 31, 2018 (tmp1=mod(n1,l1) -> tmp1=mod(n1-l1,o1))
+% 		      Dec 31, 2018 (tmp1=mod(n1,l1) -> tmp1=mod(n1-l1,s1))
+%             April 2, 2020 (3D-5D)
+%
+% Examples:
+%    ~/test/test_yc_ksvd_denoise3d.m
+%    ~/test/test_yc_ksvd_denoise5d.m
+%    ~/test/test_yc_ksvd_recon5d.m
 % 
 % References:
 % Wang et al., 2020, Fast dictionary learning for high-dimensional seismic reconstruction, IEEE Transactions on Geoscience and Remote Sensing, doi: 10.1109/TGRS.2020.3030740
@@ -32,41 +44,61 @@ function [ X ] = yc_patch( A,mode,l1,l2,o1,o2 )
[…]

### 2020-11-08 sgk5d/matfun/yc_patch_inv.m

@@ -1,5 +1,5 @@
-function [ X ] = yc_patch( A,mode,l1,l2,o1,o2 )
-%decompose the image into patches:
+function [ A ] = yc_patch_inv( X,mode,n1,n2,l1,l2,s1,s2 )
+% insert patches into the image
 %  
 % by Yangkang Chen
 % Oct, 2017
@@ -9,14 +9,14 @@ function [ X ] = yc_patch( A,mode,l1,l2,o1,o2 )
 %   mode: patching mode
 %   l1: first patch size
 %   l2: second patch size
-%   o1: first shifting size
-%   o2: second shifting size
+%   s1: first shifting size
+%   s2: second shifting size
 %   
 % Output:
 %   X: patches
 % 
 % Modified on Dec 12, 2018 (the edge issue, arbitrary size for the matrix)
-% 		      Dec 31, 2018 (tmp1=mod(n1,l1) -> tmp1=mod(n1-l1,o1))
+% 		      Dec 31, 2018 (tmp1=mod(n1,l1) -> tmp1=mod(n1-l1,s1))
 % 
 % References:
 % Wang et al., 2020, Fast dictionary learning for high-dimensional seismic reconstruction, IEEE Transactions on Geoscience and Remote Sensing, doi: 10.1109/TGRS.2020.3030740
@@ -36,39 +36,55 @@ function [ X ] = yc_patch( A,mode,l1,l2,o1,o2 )
 %l1=8;l2=8;
 %
 
-[n1,n2]=size(A);
-
 if mode==1 %possible for other patching options
 
-if nargin==2
-   l1=8;l2=8;o1=4;o2=4; 
-end
-
 if nargin==4
-   o1=round(l1/2);o2=round(l2/2);
+   l1=8;l2=8;s1=4;s2=4; 
 end
 
-tmp=mod(n1-l1,o1);
-if tmp~=0
-   A=[A;zeros(o1-tmp,n2)]; 
-end
-tmp=mod(n2-l2,o2);
-if tmp~=0
-   A=[A,zeros(size(A,1),o2-tmp)]; 
+if nargin==6
+   s1=round(l1/2);s2=round(l2/2);
 end
 
+tmp1=mod(n1-l1,s1);
[…]

### 2020-11-08 sgk5d/matfun/yc_sgk_recon.m

@@ -1,0 +1,144 @@
+function [dout]=yc_sgk_recon(d0,mask,mode,l,s,perc,niter,a,param)
+%yc_sgk_recon: SGK algorithm for 2D/3D reconstruction
+% BY Yangkang Chen
+% Jan, 2020
+%
+% INPUT
+%   mode: patching mode
+%   l: [l1,l2,l3]
+%   l1: first patch size
+%   l2: second patch size
+%   l3: third patch size
+%   s: [s1,s2,s3]
+%   s1: first shifting size
+%   s2: second shifting size
+%   s3: third shifting size
+%   perc: percentage
+% param: parameter struct for DL
+%   param.mode=1;   %1: sparsity; 0: error
+%   param.niter=10; %number of SGK iterations to perform; default: 10
+%   param.D=DCT;    %initial D
+%   param.T=3;      %sparsity level
+%   param.d0=d0;    %initial guess
+%   param.init=1;   %init=1: using linear interpolation for initialization
+%
+% OUTPUT
+% dout:
+%
+% for X=DG
+% size of X: MxN
+% size of D: MxK
+% size of G: KxN
+%
+% DEMO:
+% test/test_yc_sgk_recon.m
+% test/test_yc_sgk_recon3d.m
+% 
+% References:
+% Wang et al., 2020, Fast dictionary learning for high-dimensional seismic reconstruction, IEEE Transactions on Geoscience and Remote Sensing, % Chen, Y., 2020, Fast dictionary learning for noise attenuation of multidimensional seismic data, Geophysical Journal International, 222, 1717-1727.
+
+
+[n1,n2,n3,n4,n5]=size(d0);
+
+if isfield(param,'d0')
+    d1=param.d0;
+    fprintf('Using given model as the initilization\n');
+else
+    if isfield(param,'init') && (param.init==1)
+        d1=yc_dlrecon_init(d0,mask,'nearest');
+    fprintf('Using linear interpolation as the initilization\n');
+    else
+    d1=d0;
+    fprintf('Using the input as the initilization\n');
+    end
+end
+
+
+
+l1=l(1);
+l2=l(2);
+l3=l(3);
+
+s1=s(1);
+s2=s(2);
+s3=s(3);
+
+%initialization
[…]

### 2020-11-09 sgk5d/paper.tex
2020年11月 8日 星期日 17时47分27秒 CST
2020年11月 9日 星期一 11时05分45秒 CST

@@
-\title{Fast dictionary learning for high-dimensional seismic reconstruction}
+\published{IEEE Transactions on Geoscience and Remote Sensing, xxx, xxx, (2021)}
+
+\title{Fast Dictionary Learning for High-Dimensional Seismic Reconstruction}
+\author{Hang Wang\footnotemark[1], Wei Chen\footnotemark[2]\footnotemark[3], Quan Zhang\footnotemark[1], Xingye Liu\footnotemark[4], Shaohuan Zu\footnotemark[5], and Yangkang Chen\footnotemark[1]}
+
 \renewcommand{\thefootnote}{\fnsymbol{footnote}}
-%\author{Hang Wang, Quan Zhang, Wei Chen, Xingye Liu, Shaohuan Zu, and Yangkang Chen
-\author{Hang Wang, Wei Chen, Quan Zhang, Xingye Liu, Shaohuan Zu, and Yangkang Chen
-\thanks{H. Wang, Q. Zhang, and Y. Chen are with the Key Laboratory of Geoscience Big Data and Deep Resource of Zhejiang Province, School of Earth Sciences, Zhejiang University (chenyk2016@gmail.com).}
-\thanks{W.
-Chen is with the Key Laboratory of Exploration Technology for Oil and Gas Resources, Ministry of Education, Yangtze University, and also with the Hubei Cooperative Innovation Center of Unconventional Oil and Gas, Yangtze University.}
-\thanks{X. Liu is with College of Geology and Environment, Shaanxi Provincial Key Laboratory of Geological Support for Coal Green Exploitation, Xi'an University of Science and Technology.}
-\thanks{S. Zu is with College of Geophysics, Chengdu University of Technology.}
-\thanks{The research is supported by the starting fund from Zhejiang University and the National Natural Science Foundation of China (Grant No.
-41804140), the Open Fund of Key Laboratory of Exploration Technologies for Oil and Gas Resources (Yangtze University), Ministry of Education (Grant No.
-PI2018-02).
-(Corresponding author: Yangkang Chen.)}}
+
+\ms{TGRS-2021}
+
+\address{
+\footnotemark[1]
+School of Earth Sciences\\
+Zhejiang University\\
+Hangzhou, Zhejiang Province, China, 310027\\
+%908352517@qq.com (hang)
+%yangkang.chen@zju.edu.cn \\
+\footnotemark[2]
+Key Laboratory of Exploration Technology for Oil and Gas Resources\\
+Ministry of Education\\
+Yangtze University\\
+\footnotemark[3]
+Hubei Cooperative Innovation Center of Unconventional Oil and Gas\\
+Yangtze University \\
+\footnotemark[4]College of Geology and Environment\\
+Shaanxi Provincial Key Laboratory of Geological Support for Coal Green Exploitation\\
+Xi'an University of Science and Technology\\
+\footnotemark[5] College of Geophysics\\
+Chengdu University of Technology
+}
+
+\lefthead{Wang et al., 2021}
+\righthead{SGK5D}
+
 \maketitle
-
-%, college of geology and enviroment
-%58 Yanta road
-%Beilin district
 
@@
 The overall computational advantage of the new dictionary learning method is very decent while the results are still comparable or event better than those from the traditional KSVD method.
-We apply the proposed method to both 3D and 5D seismic data reconstructions and demonstrate the successful and efficient performance.
+We apply the proposed method to both 3D and 5D seismic data reconstructions and demonstrate the successful and efficient performance.\\
+\textbf{Keywords}\\
+Seismic data reconstruction, signal processing, dictionary learning, high-dimensional problem
 \end{abstract}
-
-\begin{keywords}
-Seismic data reconstruction, signal processing, dictionary learning, high-dimensional problem
-\end{keywords}
 
@@
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.3\columnwidth]{synth/Fig/synth-clean}
-\label{fig:synth-clean}}
-   \subfigure[]{\includegraphics[width=0.3\columnwidth]{synth/Fig/synth-noisy}
-   \label{fig:synth-noisy}}
-   \subfigure[]{\includegraphics[width=0.3\columnwidth]{synth/Fig/synth-obs}
-   \label{fig:synth-obs}}
-\caption{Synthetic example with planar events. (a) Clean data. (b) Noisy data (SNR=-0.05 dB). (c) Observed data with 50\% randomly missing traces (SNR=-0.03 dB).}
-\label{fig:synth-clean,synth-noisy,synth-obs}
-\end{figure}
+\inputdir{synth}
+\multiplot{3}{synth-clean,synth-noisy,synth-obs}{width=0.3\columnwidth}{Synthetic example with planar events.
+(a) Clean data.
+(b) Noisy data (SNR=-0.05 dB).
+(c) Observed data with 50\% randomly missing traces (SNR=-0.03 dB).}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.3\columnwidth]{synth/Fig/synth-ksvd}
-\label{fig:synth-ksvd}}
-   \subfigure[]{\includegraphics[width=0.3\columnwidth]{synth/Fig/synth-ddtf}
-   \label{fig:synth-ddtf}}
-   \subfigure[]{\includegraphics[width=0.3\columnwidth]{synth/Fig/synth-sgk}
-   \label{fig:synth-sgk}}
-\caption{Reconstructed data using (a) KSVD (SNR=8.89 dB), (b) DDTF (SNR=5.42 dB), and (c) SGK (SNR=9.74 dB).}
-\label{fig:synth-ksvd,synth-ddtf,synth-sgk}
-\end{figure}
+\multiplot{3}{synth-ksvd,synth-ddtf,synth-sgk}{width=0.3\columnwidth}{Reconstructed data using (a) KSVD (SNR=8.89 dB), (b) DDTF (SNR=5.42 dB), and (c) SGK (SNR=9.74 dB).}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{Fig/atom_dct}
-\label{fig:atom_dct}}
-   \subfigure[]{\includegraphics[width=0.45\columnwidth]{Fig/atom_ksvd}
-   \label{fig:atom_ksvd}}\\
-   \subfigure[]{\includegraphics[width=0.45\columnwidth]{Fig/atom_ddtf}
-   \label{fig:atom_ddtf}}
-   \subfigure[]{\includegraphics[width=0.45\columnwidth]{Fig/atom_sgk}
-   \label{fig:atom_sgk}}
-\caption{Comparison of different dictionary atoms.
+\inputdir{./}
+\multiplot{4}{atom_dct,atom_ksvd,atom_ddtf,atom_sgk}{width=0.45\columnwidth}{Comparison of different dictionary atoms.
 (a) Dictionary atoms of the discrete cosine transform.
@@
 (c) Dictionary atoms of the DDTF method.
-(d) Dictionary atoms of the SGK method.
-}
-\label{fig:atom_dct,atom_ksvd,atom_ddtf,atom_sgk}
-\end{figure}
+(d) Dictionary atoms of the SGK method.}
 
@@
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.30\columnwidth]{synth/Fig/synth-ksvd-simi}
-\label{fig:synth-ksvd-simi}}
-   \subfigure[]{\includegraphics[width=0.30\columnwidth]{synth/Fig/synth-ddtf-simi}
-   \label{fig:synth-ddtf-simi}}
-   \subfigure[]{\includegraphics[width=0.30\columnwidth]{synth/Fig/synth-sgk-simi}
-   \label{fig:synth-sgk-simi}}
-\caption{Similarity comparison of reconstructed data using (a) KSVD, (b) DDTF, and (c) SGK.}
-\label{fig:synth-ksvd-simi,synth-ddtf-simi,synth-sgk-simi}
-\end{figure}
+\inputdir{synth}
+\multiplot{3}{synth-ksvd-simi,synth-ddtf-simi,synth-sgk-simi}{width=0.3\columnwidth}{Similarity comparison of reconstructed data using (a) KSVD, (b) DDTF, and (c) SGK.}
 
-\begin{figure}[htb!]
-\centering
-	\subfigure[]{\includegraphics[width=0.31\columnwidth]{synth/Fig/synth-s-clean}
-	\label{fig:synth-s-clean}}
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth/Fig/synth-s-noisy}
-   \label{fig:synth-s-noisy}}
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth/Fig/synth-s-obs}
-   \label{fig:synth-s-obs}}\\
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{synth/Fig/synth-s-ksvd}
-\label{fig:synth-s-ksvd}}
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth/Fig/synth-s-ddtf}
-   \label{fig:synth-s-ddtf}}
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth/Fig/synth-s-sgk}
-   \label{fig:synth-s-sgk}}
-\caption{\new{2D slice comparison of the synthetic example.
+\multiplot{6}{synth-s-clean,synth-s-noisy,synth-s-obs,synth-s-ksvd,synth-s-ddtf,synth-s-sgk}{width=0.3\columnwidth}{\new{2D slice comparison of the synthetic example.
 (a) Clean data.
@@
 (f) Reconstructed data using SGK.}}
-\label{fig:synth-s-clean,synth-s-noisy,synth-s-obs,synth-s-ksvd,synth-s-ddtf,synth-s-sgk}
-\end{figure}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=\columnwidth]{synth/Fig/synth-ss}}
-\caption{Single-trace comparison.
+\plot{synth-ss}{width=\columnwidth}{width=0.3\columnwidth}{Single-trace comparison.
 The black line corresponds to the ground-truth solution.
@@
 The blue line corresponds to the DDTF method.}
-\label{fig:synth-ss}
-\end{figure}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.30\columnwidth]{synth/Fig/synth-mssa}
-\label{fig:synth-mssa}}
-   \subfigure[]{\includegraphics[width=0.30\columnwidth]{synth/Fig/synth-mssasgk}
-   \label{fig:synth-mssasgk}}
-\caption{Reconstructed data using (a) MSSA (SNR=9.51 dB), and (b) SGK with (a) as the initialization model (SNR=12.22 dB).}
-\label{fig:synth-mssa,synth-mssasgk}
-\end{figure}
+\multiplot{2}{synth-mssa,synth-mssasgk}{width=0.30\columnwidth}{Reconstructed data using (a) MSSA (SNR=9.51 dB), and (b) SGK with (a) as the initialization model (SNR=12.22 dB).}
 
@@
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-clean}
-\label{fig:hyper-clean}}
-  \subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-noisy}
-  \label{fig:hyper-noisy}}
-  \subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-obs}
-  \label{fig:hyper-obs}}
-\caption{Synthetic example with hyperboloid events. (a) Clean data. (b) Noisy data (SNR=6.93 dB). (c) Observed data with 50\% randomly missing traces (SNR=2.21 dB).}
-\label{fig:hyper-clean,hyper-noisy,hyper-obs}
-\end{figure}
+\inputdir{hyper}
+\multiplot{3}{hyper-clean,hyper-noisy,hyper-obs}{width=0.30\columnwidth}{Synthetic example with hyperboloid events.
+(a) Clean data.
+(b) Noisy data (SNR=6.93 dB).
+(c) Observed data with 50\% randomly missing traces (SNR=2.21 dB).}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-mssa}
-\label{fig:hyper-mssa}}
-\subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-ksvd}
-\label{fig:hyper-ksvd}}\\
-  \subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-ddtf}
-  \label{fig:hyper-ddtf}}
-  \subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-sgk}
-  \label{fig:hyper-sgk}}
-\caption{Reconstructed data using (a) Rank-reduction method (SNR=9.68 dB), (b) KSVD (SNR=10.84 dB), (c) DDTF (SNR=11.45 dB), and (d) SGK (SNR=11.00 dB).
+\multiplot{4}{hyper-mssa,hyper-ksvd,hyper-ddtf,hyper-sgk}{width=0.30\columnwidth}{Reconstructed data using (a) Rank-reduction method (SNR=9.68 dB), (b) KSVD (SNR=10.84 dB), (c) DDTF (SNR=11.45 dB), and (d) SGK (SNR=11.00 dB).
 All DL based methods use the result from the rank-reduction method as the initial model.}
-\label{fig:hyper-mssa,hyper-ksvd,hyper-ddtf,hyper-sgk}
-\end{figure}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-ksvd-simi}
-\label{fig:hyper-ksvd-simi}}
-  \subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-ddtf-simi}
-  \label{fig:hyper-ddtf-simi}}
-  \subfigure[]{\includegraphics[width=0.30\columnwidth]{hyper/Fig/hyper-sgk-simi}
-  \label{fig:hyper-sgk-simi}}
-\caption{Similarity comparison of reconstructed data using (a) KSVD, (b) DDTF, and (c) SGK.}
-\label{fig:hyper-ksvd-simi,hyper-ddtf-simi,hyper-sgk-simi}
-\end{figure}
+\multiplot{3}{hyper-ksvd-simi,hyper-ddtf-simi,hyper-sgk-simi}{width=0.30\columnwidth}{Similarity comparison of reconstructed data using (a) KSVD, (b) DDTF, and (c) SGK.}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{hyper/Fig/hyper-s-clean}
-\label{fig:hyper-s-clean}}
-  \subfigure[]{\includegraphics[width=0.31\columnwidth]{hyper/Fig/hyper-s-noisy}
-  \label{fig:hyper-s-noisy}}
-  \subfigure[]{\includegraphics[width=0.31\columnwidth]{hyper/Fig/hyper-s-obs}
-  \label{fig:hyper-s-obs}}\\
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{hyper/Fig/hyper-s-ksvd}
-\label{fig:hyper-s-ksvd}}
-  \subfigure[]{\includegraphics[width=0.31\columnwidth]{hyper/Fig/hyper-s-ddtf}
-  \label{fig:hyper-s-ddtf}}
-  \subfigure[]{\includegraphics[width=0.31\columnwidth]{hyper/Fig/hyper-s-sgk}
-  \label{fig:hyper-s-sgk}}
-\caption{\new{2D slice comparison of the synthetic example.
+\multiplot{6}{hyper-s-clean,hyper-s-noisy,hyper-s-obs,hyper-s-ksvd,hyper-s-ddtf,hyper-s-sgk}{width=0.30\columnwidth}{\new{2D slice comparison of the synthetic example.
 (a) Clean data.
@@
 (f) Reconstructed data using SGK.}}
-\label{fig:hyper-s-clean,hyper-s-noisy,hyper-s-obs,hyper-s-ksvd,hyper-s-ddtf,hyper-s-sgk}
-\end{figure}
+
+\inputdir{synth5d}
+\multiplot{6}{syn5d-clean,syn5d-noisy,syn5d-obs,syn5d-ksvd,syn5d-ddtf,syn5d-sgk}{width=0.30\columnwidth}{\new{Comparison of 5D seismic reconstruction in a common midpoint gather.
+(a) Clean data.
+(b) Noisy data (SNR=-0.65 dB).
+(c) Decimated data with 70\% randomly removed traces  (SNR=-0.21 dB).
+(d) Reconstructed data using KSVD  (SNR=6.58 dB).
+(e) Reconstructed data using DDTF  (SNR=3.22 dB).
+(f) Reconstructed data using SGK (SNR=6.58 dB).}}
+\multiplot{6}{syn5d-clean2,syn5d-noisy2,syn5d-obs2,syn5d-ksvd2,syn5d-ddtf2,syn5d-sgk2}{width=0.30\columnwidth}{\new{Comparison of 5D seismic reconstruction in a common offset gather.
+(a) Clean data.
+(b) Noisy data (SNR=-0.65 dB).
+(c) Decimated data with 70\% randomly removed traces  (SNR=-0.21 dB).
+(d) Reconstructed data using KSVD  (SNR=6.58 dB).
+(e) Reconstructed data using DDTF  (SNR=3.22 dB).
+(f) Reconstructed data using SGK (SNR=6.58 dB).}}
 
@@
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-clean}
-\label{fig:syn5d-clean}}
-  \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-noisy}
-  \label{fig:syn5d-noisy}}
-  \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-obs}
-  \label{fig:syn5d-obs}}\\
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-ksvd}
-\label{fig:syn5d-ksvd}}
-  \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-ddtf}
-  \label{fig:syn5d-ddtf}}
-  \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-sgk}
-  \label{fig:syn5d-sgk}}
-\caption{\new{Comparison of 5D seismic reconstruction in a common midpoint gather.
-(a) Clean data.
-(b) Noisy data (SNR=-0.65 dB).
-(c) Decimated data with 70\% randomly removed traces  (SNR=-0.21 dB).
-(d) Reconstructed data using KSVD  (SNR=6.58 dB).
-(e) Reconstructed data using DDTF  (SNR=3.22 dB).
-(f) Reconstructed data using SGK (SNR=6.58 dB).}}
-\label{fig:syn5d-clean,syn5d-noisy,syn5d-obs,syn5d-ksvd,syn5d-ddtf,syn5d-sgk}
-\end{figure}
-
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-clean2}
-\label{fig:syn5d-clean2}}
-  \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-noisy2}
-  \label{fig:syn5d-noisy2}}
-  \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-obs2}
-  \label{fig:syn5d-obs2}}\\
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-ksvd2}
-\label{fig:syn5d-ksvd2}}
-  \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-ddtf2}
-  \label{fig:syn5d-ddtf2}}
-  \subfigure[]{\includegraphics[width=0.31\columnwidth]{synth5d/Fig/syn5d-sgk2}
-  \label{fig:syn5d-sgk2}}
-\caption{\new{Comparison of 5D seismic reconstruction in a common offset gather.
-(a) Clean data.
-(b) Noisy data (SNR=-0.65 dB).
-(c) Decimated data with 70\% randomly removed traces  (SNR=-0.21 dB).
-(d) Reconstructed data using KSVD  (SNR=6.58 dB).
-(e) Reconstructed data using DDTF  (SNR=3.22 dB).
-(f) Reconstructed data using SGK (SNR=6.58 dB).}}
-\label{fig:syn5d-clean2,syn5d-noisy2,syn5d-obs2,syn5d-ksvd2,syn5d-ddtf2,syn5d-sgk2}
-\end{figure}
-
-\new{Despite of the highly incomplete sampling of the raw dataset, it is not difficult to learn dictionaries.
+Despite of the highly incomplete sampling of the raw dataset, it is not difficult to learn dictionaries.
 In the proposed framework, one can use two options to learn dictionaries from observed data.
@@
 Both strategies will be illustrated later.
-}
 
-\new{An interesting note is that enforcing $\mathbf{s}_j =\mathbf{e}_p$ ($P=1$) helps deriving the SVD-free dictionary updating scheme, as an averaged form of the training samples (e.g., in equation \ref{eq:dk}).
+An interesting note is that enforcing $\mathbf{s}_j =\mathbf{e}_p$ ($P=1$) helps deriving the SVD-free dictionary updating scheme, as an averaged form of the training samples (e.g., in equation \ref{eq:dk}).
 $P=1$ is only required in the dictionary learning process.
-When applied to denoising or reconstruction, the sparse coding process expressed in equation \ref{eq:eq1}, (given the learned dictionary $\mathbf{D}$ from the SGK method), can be taken for the denoising or reconstruction purpose.}
+When applied to denoising or reconstruction, the sparse coding process expressed in equation \ref{eq:eq1}, (given the learned dictionary $\mathbf{D}$ from the SGK method), can be taken for the denoising or reconstruction purpose.
 
@@
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/f-obs}
-\label{fig:f-obs}}
-\subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/f-ksvd}
-\label{fig:f-ksvd}}\\
-  \subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/f-ddtf}
-  \label{fig:f-ddtf}}
-  \subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/f-sgk}
-  \label{fig:f-sgk}}
-\caption{\new{3D Field data example. (a) Observed data. Reconstructed data using (b) KSVD, (c) DDTF, and (d) SGK.} }
-\label{fig:f-obs,f-ksvd,f-ddtf,f-sgk}
-\end{figure}
-
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/f-s-obs0}
-\label{fig:f-s-obs0}}
-\subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/f-s-ksvd0}
-\label{fig:f-s-ksvd0}}\\
-  \subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/f-s-ddtf0}
-  \label{fig:f-s-ddtf0}}
-  \subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/f-s-sgk0}
-  \label{fig:f-s-sgk0}}
-\caption{2D slice comparison of the field data example.
+\inputdir{field}
+\multiplot{4}{f-obs,f-ksvd,f-ddtf,f-sgk}}{width=0.30\columnwidth}{\new{3D Field data example. (a) Observed data. Reconstructed data using (b) KSVD, (c) DDTF, and (d) SGK.}}
+\multiplot{4}{f-s-obs0,f-s-ksvd0,f-s-ddtf0,f-s-sgk0}{width=0.30\columnwidth}{2D slice comparison of the field data example.
 (a) Observed data.
@@
 (d) Reconstructed data using SGK.
-The frame boxes are zoomed and shown in Figure \ref{fig:fz-obs,fz-ksvd,fz-ddtf,fz-sgk}.
+The frame boxes are zoomed and shown in Figure \ref{fig:fz-obs,fz-ksvd,fz-ddtf,fz-sgk}.}
+
+\multiplot{4}{fz-obs,fz-ksvd,fz-ddtf,fz-sgk}{width=0.30\columnwidth}{Zoomed 2D slice comparison of the field data example.
+(a) Observed data.
+(b) Reconstructed data using KSVD.
+(c) Reconstructed data using DDTF.
+(d) Reconstructed data using SGK.
 }
-\label{fig:f-s-obs0,f-s-ksvd0,f-s-ddtf0,f-s-sgk0}
-\end{figure}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/fz-obs}
-\label{fig:fz-obs}}
-\subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/fz-ksvd}
-\label{fig:fz-ksvd}}\\
-  \subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/fz-ddtf}
-  \label{fig:fz-ddtf}}
-  \subfigure[]{\includegraphics[width=0.30\columnwidth]{field/Fig/fz-sgk}
-  \label{fig:fz-sgk}}
-\caption{Zoomed 2D slice comparison of the field data example. (a) Observed data. (b) Reconstructed data using KSVD. (c) Reconstructed data using DDTF. (d) Reconstructed data using SGK. }
-\label{fig:fz-obs,fz-ksvd,fz-ddtf,fz-sgk}
-\end{figure}
-
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{field5d/Fig/f5d-obs}
-\label{fig:f5d-obs}}
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{field5d/Fig/f5d-ksvd}
-\label{fig:f5d-ksvd}}\\
-  \subfigure[]{\includegraphics[width=0.45\columnwidth]{field5d/Fig/f5d-ddtf}
-  \label{fig:f5d-ddtf}}
-  \subfigure[]{\includegraphics[width=0.45\columnwidth]{field5d/Fig/f5d-sgk}
-  \label{fig:f5d-sgk}}
-\caption{5D seismic reconstruction example.
+\inputdir{./}
+\multiplot{4}{f5d-obs,f5d-ksvd,f5d-ddtf,f5d-sgk}{width=0.45\columnwidth}{5D seismic reconstruction example.
 A common offset gather is displayed for comparison.
@@
 }
-\label{fig:f5d-obs,f5d-ksvd,f5d-ddtf,f5d-sgk}
-\end{figure}
 
-\begin{figure}[ht!]
-\centering
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{field5d/Fig/z-obs}
-\label{fig:z-obs}}
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{field5d/Fig/z-ksvd}
-\label{fig:z-ksvd}}\\
-  \subfigure[]{\includegraphics[width=0.45\columnwidth]{field5d/Fig/z-ddtf}
-  \label{fig:z-ddtf}}
-  \subfigure[]{\includegraphics[width=0.45\columnwidth]{field5d/Fig/z-sgk}
-  \label{fig:z-sgk}}
-\caption{Zoomed comparison of the 5D seismic reconstruction example.
+\multiplot{4}{z-obs,z-ksvd,z-ddtf,z-sgk}{width=0.45\columnwidth}{Zoomed comparison of the 5D seismic reconstruction example.
 The zooming area is stressed by the frame boxes in Figure \ref{fig:f5d-obs,f5d-ksvd,f5d-ddtf,f5d-sgk}.
@@
 (d) Reconstructed data using SGK.
-The SGK result is obviously better than the other two methods.}
-\label{fig:z-obs,z-ksvd,z-ddtf,z-sgk}
-\end{figure}
+The SGK result is obviously better than the other two methods.
+}
 
@@
 
+\section{Acknowledgement}
+The research is supported by the starting fund from Zhejiang University and the National Natural Science Foundation of China (Grant No.
+41804140), the Open Fund of Key Laboratory of Exploration Technologies for Oil and Gas Resources (Yangtze University), Ministry of Education (Grant No.
+PI2018-02).
+
 \bibliographystyle{IEEEtran}

### 2020-11-09 sgk5d/paper.tex
sgk

@@
 
-\plot{synth-ss}{width=\columnwidth}{width=0.3\columnwidth}{Single-trace comparison.
+\plot{synth-ss}{width=\columnwidth}{Single-trace comparison.
 The black line corresponds to the ground-truth solution.
@@
 
-\multiplot{4}{hyper-mssa,hyper-ksvd,hyper-ddtf,hyper-sgk}{width=0.30\columnwidth}{Reconstructed data using (a) Rank-reduction method (SNR=9.68 dB), (b) KSVD (SNR=10.84 dB), (c) DDTF (SNR=11.45 dB), and (d) SGK (SNR=11.00 dB).
+\multiplot{4}{hyper-mssa,hyper-ksvd,hyper-ddtf,hyper-sgk}{width=0.40\columnwidth}{Reconstructed data using (a) Rank-reduction method (SNR=9.68 dB), (b) KSVD (SNR=10.84 dB), (c) DDTF (SNR=11.45 dB), and (d) SGK (SNR=11.00 dB).
 All DL based methods use the result from the rank-reduction method as the initial model.}
@@
 \inputdir{field}
-\multiplot{4}{f-obs,f-ksvd,f-ddtf,f-sgk}}{width=0.30\columnwidth}{\new{3D Field data example. (a) Observed data. Reconstructed data using (b) KSVD, (c) DDTF, and (d) SGK.}}
-\multiplot{4}{f-s-obs0,f-s-ksvd0,f-s-ddtf0,f-s-sgk0}{width=0.30\columnwidth}{2D slice comparison of the field data example.
+\multiplot{4}{f-obs,f-ksvd,f-ddtf,f-sgk}{width=0.40\columnwidth}{\new{3D Field data example. (a) Observed data. Reconstructed data using (b) KSVD, (c) DDTF, and (d) SGK.}}
+\multiplot{4}{f-s-obs0,f-s-ksvd0,f-s-ddtf0,f-s-sgk0}{width=0.40\columnwidth}{2D slice comparison of the field data example.
 (a) Observed data.
@@
 
-\multiplot{4}{fz-obs,fz-ksvd,fz-ddtf,fz-sgk}{width=0.30\columnwidth}{Zoomed 2D slice comparison of the field data example.
+\multiplot{4}{fz-obs,fz-ksvd,fz-ddtf,fz-sgk}{width=0.40\columnwidth}{Zoomed 2D slice comparison of the field data example.
 (a) Observed data.

### 2020-12-17 usarray/paper.tex
2020年12月16日 星期三 18时06分01秒 CST

%\documentclass[fleqn,10pt]{wlscirep}
%\usepackage{amsmath,timet,bm,subfigure,graphicx,epstopdf,amsfonts,amssymb,mathrsfs,algorithm,algpseudocode,multirow,cite,color}
%\usepackage[normalem]{ulem}
%\usepackage{lineno}

%\begin{document}
%Paper('sr',lclass='wlscirep',options='fleqn,10pt',use='amsmath,timet,bm,subfigure,graphicx,epstopdf,amsfonts,amssymb,mathrsfs,algorithm,algpseudocode,multirow,cite')

%\newcommand{\old}[1]{\color{blue}{\sout{#1}}\color{black}{}}
%\newcommand{\new}[1]{\color{red}{\textit{#1}}\color{black}{}}

\newcommand{\dlo}[1]{}
\newcommand{\wen}[1]{#1}

%\newcommand{\old}[1]{}
%\newcommand{\new}[1]{#1}

\published{Nature Communications, 10, 4434, (2019)}

\title{Obtaining free USArray data by multi-dimensional seismic reconstruction}

\author{Yangkang Chen\footnotemark[1], Min Bai\footnotemark[2], and Yunfeng Chen\footnotemark[3]}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\ms{NC-2019} %\ms{GJI-2018}

\address{
\footnotemark[1]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
yangkang.chen@zju.edu.cn \\
%908352517@qq.com (hang)
\footnotemark[2]
Key Laboratory of Exploration Technology for Oil\\
and Gas Resources of Ministry of Education\\
Yangtze University, Wuhan\\
Hubei Province, 430100, China\\
\footnotemark[3]Deep Earth Imaging\\
Future Science Platform\\
CSIRO, Kensington\\
WA, Australia, 6151
}

\lefthead{Chen et al., 2019}
\righthead{LRR}

%\author[1,*]{Yangkang Chen}
%\author[2,1]{Min Bai}
%\author[3]{Yunfeng Chen}
%%\affil[1]{Modeling and Imaging Laboratory, Earth and Planetary Sciences, University of California, Santa Cruz, CA, USA, 95064}
%\affil[1]{School of Earth Sciences, Zhejiang University, Hangzhou, Zhejiang Province, 310027, China}
%\affil[2]{\new{Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education, Yangtze University, Wuhan, Hubei Province, 430100, China}}
%\affil[3]{Deep Earth Imaging, Future Science Platform, CSIRO, Kensington, WA, Australia, 6151}
%\affil[*]{chenyk2016@gmail.com}

%\affil[+]{these authors contributed equally to this work}

%\keywords{USArray data, earthquake data, reconstruction}

\begin{abstract}
% Microseismic signal is typically weak, compared with the strong background noise. This is an issue, because weak signal detection is necessary in microseismic data processing. Classic approaches such as frequency filtering are limited, or even invalid when the signal and noise share the same frequency band. In order to effectively detect the weak signal in microseismic data, we propose a mathematical morphology based approach. 
\dlo{The emergence of large seismic networks equipped with dense broadband seismometers has opened a new chapter for the acquisition of earthquake data. One of the pioneering examples is USArray of EarthScope project that provides a semi-uniform sampling of the seismic wavefield beneath its footprint and greatly advances the understanding of the structure and dynamics of Earth. Despite the continuing effort in improving the network design, the station deployment of USArray is still irregular and unbalanced due to concerns such as logistics.  As a result, the spatial sampling alias and contaminating noise from the incomplete data impose great challenges in array-based data analysis and seismic imaging.  Here we utilize an iterative rank-reduction method to simultaneously reconstruct the missing traces and suppress the noise in the array data, i.e., obtaining free USArray recordings as well as enhancing the existing data. This method exploits the spatial coherency of the three-dimensional data in the frequency domain and extracts the principal components from the incomplete data, which enables  recovering the missing elements in an iterative manner. The application of a localized rank-reduction scheme is critical to preserve the small-scale and weak-amplitude phases that are otherwise severely damped by the traditional methods. We demonstrate the merits of our method using synthetic data and teleseismic earthquake recordings from USArray. The reconstructed data improves the quality of P-wave travel time measurements as demonstrated by 1) a better spatial correlation of the travel time pattern with the velocity structures and 2) a significantly reduced travel time measurement uncertainty. This study provides a new tool to reconstruct the irregular seismic wavefield recorded by the large-aperture array and demonstrates great potential to improve the array-based seismic imaging techniques.}
\wen{USArray, a pioneering project for dense acquisition of earthquake data, provides a semi-uniform sampling of the seismic wavefield beneath its footprint and greatly advances the understanding of the structure and dynamics of Earth.  Despite continuing efforts in improving the acquisition design, network irregularity still causes spatial sampling alias and incomplete, noisy data, which imposes great challenges in array-based data analysis and seismic imaging.  Here we employ an iterative rank-reduction method to simultaneously reconstruct the missing traces and suppress noise, i.e., obtaining free USArray recordings as well as enhancing the existing data.  This method exploits the spatial coherency of three-dimensional data and recover the missing elements via the principal components of the incomplete data.  We examine its merits using simulated and teleseismic earthquake recordings.  The reconstructed P wavefield enhances the spatial coherency and accuracy of tomographic travel time measurements, which demonstrates great potential to benefit seismic investigations based on array techniques.}
\end{abstract}

%\flushbottom
\maketitle
% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
%
%  Click the title above to edit the author information and abstract
%
%\thispagestyle{empty}

%\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.

\section*{Introduction}

The past two decades have witnessed a major proliferation of broadband seismic arrays around the globe.  One excellent example is USAarry, the seismology component of the national Earth science program EarthScope, that \dlo{had been migrating}\wen{migrated} continuously across the North American continent (year 2004-2013\wen{; now deployed in Alaska and northwestern Canada}), providing a dense sampling of the seismic wavefield beneath its footprint. The availability of a large amount \wen{of} high-quality \dlo{array }data offers unique opportunities for \dlo{conducting }high-resolution seismic imaging, which leads to \wen{a} \dlo{much improved}\wen{much-improved} understanding of \wen{the} Earth's structure at various scales \cite{van2005surface,moschetti2007surface,yang2008structure,lin2009eikonal,yuan2010lithospheric,sigloch2011mantle,porritt2014seismic,schaeffer2014imaging,schmandt2014p,bao2016imaging,burdick2017model}. The relatively even-spaced sensors, with an average spacing of $ \sim $70 km, form an ideal network configuration for \dlo{applying the} \wen{the application of} array-based \dlo{method}\wen{methods} \cite{rost2002array,gu2010arrays}. While the quantity of array data is continuously growing, \dlo{its quality is still limited}\wen{the improvement of data quality is hampered} by the presence of noise and a biased spatial sampling \dlo{resulting}\wen{that results} from \dlo{the }unevenly distributed earthquake sources and stations. Both factors (i.e., quantity and quality) play an important role in exploiting the \dlo{information from the }data and achieving robust imaging outputs. Most \dlo{resolution}\wen{data} improvement efforts have been focusing on increasing the data volume whereas generally less attention was paid to improve the quality of \dlo{the }existing \dlo{data}\wen{recordings}. The high-quality data with a regular spatial sampling can greatly benefit data analysis, processing and visualization, and also improve the numerical stability and accuracy for grid-based seismic imaging techniques (e.g., Eikonal \cite{lin2009eikonal} and Helmholtz tomography \cite{lin2011helmholtz}). As a result, \dlo{the }regularization approach\wen{es} that suppress\dlo{es} the noise and interpolate\dlo{s} the missing traces of array data \dlo{is}\wen{are} highly demanded \cite{mostafa2016geo,mostafa2016bssa,schneider2017improvement}.

\dlo{There are some}\wen{Some} effective methods for seismic data reconstruction \dlo{from}\wen{have been proposed in} the exploration seismology community. One type of the most widely used methods is based on \wen{a} sparse transform that maps the seismic signals to certain domains (e.g., Fourier \cite{abma2006}, curvelet \cite{yu2017mapping}, \wen{slant stacklet \cite{ventosa2015extraction}, }and seislet domains \cite{fomel2010seislet}), where the useful information can be sparsely represented and separated from the missing data and random noise. Another type of mainstream \wen{methods} is based on the Cadzow filtering or the Singular Spectrum Analysis (SSA) \cite{ssa}, which is a rank-reduction based method that transforms the data to frequency-wavenumber or frequency-space domains to extract the spatial coherency of the entire data set for reconstructing the missing information. Oropeza and Sacchi (2011) \cite{mssa} extended the SSA method to multi-channel version to tackle the 3-D seismic data reconstruction challenge and later on Kreimer et al. (2013) \cite{kreimer2013} formulated the high-dimensional reconstruction as a nuclear-norm constrained tensor completion problem in the frequency-space domain. More recently, Chen et al. (2016) \cite{yangkang2016irr5d} improved the traditional truncated singular value decomposition (TSVD) method by deriving a new rank-reduction formula\dlo{, which}\wen{ that} better decomposes the data space into signal and noise subspaces. All aforementioned reconstruction methods are commonly applied to seismic data from exploration-scale surveys, while their applications to earthquake data, especially the multidimensional data recorded by large-scale seismic \dlo{array}\wen{arrays}, have been seldom reported.

In global seismology community, several methods have been proposed to interpolate the irregularly sampled seismic data. Most earlier studies have been concentrating on interpolating the receiver functions \cite{langston1977effect} that consist of P to S converted waves based on a certain form of spatial smoothing \dlo{such as}\wen{, including, for example,} weighted stacking with either linear \cite{chengping2015}, gaussian \cite{neal1999imaging, song2017moho} or cubic spline functions \cite{sheldrake2002regional, zhang2014receiver}. Also implemented are methods based on high-resolution Radon transform \cite{wilson2007teleseismic}, \dlo{sigular}\wen{singular} spectrum analysis \cite{gu2015sharp, dokht2016singular} and, more recently, non-linear waveform stretching-and-squeezing \cite{hu2018wavefield}.  Aside from interpolating the receiver functions, Schneider et al. (2017) \cite{schneider2017improvement} reconstruct\wen{ed} the weak-amplitude under-side reflections from the mantle transition zone (i.e., PP precursors) while utilizing a compressive sensing based approach that seeks the sparsity of dominating \dlo{energies}\wen{energy} in the frequency-wavenumber domain.  A recent study also \dlo{applies}\wen{applied} the idea of compressive sensing to reconstruct the synthetic surface wavefields via a sparse representation using a plane wave basis \cite{zhan2018application}.  These earlier studies represent \dlo{continuous}\wen{continuing} efforts of the global seismology community in improving the earthquake data towards a regularly sampled wavefield\dlo{, yet}\wen{. However,} challenge still exists in view that 1) only a specific type of data (e.g, receiver functions, PP precursors), which is typically structurally simple, is reconstructed, and 2) the energy of useful signals tends \wen{to} be excessively smoothed by the ad hoc interpolation schemes, which limits the data resolution thereby the resolvability of small-scale structures.

In this study, we \dlo{intend to }develop an effective framework to reconstruct the three-dimensional (3D) \dlo{full wavefields}\wen{data} of \wen{an} earthquake \dlo{from USArray data}\wen{recorded by USArray}. We propose a localized rank-reduction method to simultaneously reconstruct the missing traces and improve the weak-amplitude phase arrivals. Compared with the regular global rank-reduction method, our localized approach is superior at preserving the small-scale features in the array data, which is critical for high-resolution imaging of subsurface structures. We \dlo{investigate}\wen{demonstrate} \dlo{this}\wen{its} \dlo{amplitude-preserving}\wen{signal-improvement} capability via a synthetic dataset and then apply the proposed method to \dlo{the }January 18, 2009, Kermadec Islands Mw 6.4  earthquake recorded by USArray\dlo{ (Figure \ref{fig:station_earthquake})}, where a significant portion of the recordings is \dlo{the }missing due to deployment limitations.  The  reconstructed earthquake wavefield provides the virtual recordings at the missing locations as if they had been acquired by the actual stations during the earthquake. We demonstrate the merits of the proposed method and data improvement by conducting cross-correlation measurements of  P-wave \dlo{travel}\wen{arrival} times, a fundamental step in \wen{body-wave} travel time tomography.

\section*{Results}
\subsection*{Synthetic test}
We first conduct a synthetic test to demonstrate the performance of the proposed methodology. The model is designed to honor  the complex Moho structure in central US \cite{schmandt2015distinct} that is characterized by \dlo{a large depth variation}\wen{large depth variations} by as much as 20 km (Figure \ref{fig:syn}).  The elastic properties (velocity and density) of the crust and upper mantle are obtained from the average values of AK135 continental model\cite{kennett1995constraints} (Figures 1a-1c).  We synthesize the recorded wavefield by solving the 3D elastic wave equation based on a finite-difference method\dlo{ with a GPU implementation}\old{ (see Supplementary material for mathematical detail)}. We simulate plane-wave incidence of teleseismic earthquake by simultaneously injecting energy from multiple point sources located on a plane in the upper mantle (Figure \ref{fig:obs}). %\wen{The direction of wavefront is determined from the epicenter distance and azimuth of the earthquake investigated in this study. The stacked P-wave of actual earthquake recordings is employed as the effective source-time function to ensure a similar frequency content and signal energy of the synthetics. The frequency band  of the synthetic data as revealed by the spectrum plots in the Supplementary material is 0-0.3 Hz.}
\wen{The physical parameters of an earthquake (e.g., epicenter and magnitude) are implicitly considered in our simulation. The direction of wavefront is determined from the epicenter distance and azimuth of the earthquake investigated in this study. The stacked P-wave of actual earthquake recordings is employed as the effective source-time function to honor the actual earthquake source parameters and ensure a similar frequency content and signal energy of the synthetics. }

The 3D seismic data consists of 200 time samples with a sampling rate of 0.5 sec and 100 equally spaced spatial samples in both longitudinal \new{(X) and  latitudinal (Y)} directions (Figure \ref{fig:syn-clean}).  The simulated wavefield shows clear P and Moho converted phases (Ps) (Figure \ref{fig:syn-clean}). To mimic the realistic signal-to-noise ratio (SNR), we add real noise that \dlo{proceeds}\wen{precedes} the first arrivals (i.e., P waves) from the USArray data to the synthetics (Figure \ref{fig:syn-noisy}). The missing traces are generated by applying the sampling matrix (Figure \ref{fig:syn-mask}) to the noisy data. The final simulated data contains 30\% missing traces (Figure \ref{fig:syn-obs}). To quantitatively evaluate the data quality, we use a SNR criterion defined as follows: $\text{SNR}=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2^2}{\Arrowvert \mathbf{s} -\hat{\mathbf{s}}\Arrowvert_2^2}$, where $\mathbf{s}$ denotes the exact solution (i.e., the clean data), and $\hat{\mathbf{s}}$ is the noise contaminated or incomplete data. The respective data quality \dlo{factors}\wen{metrics} (SNR) for the noisy and  incomplete data are \dlo{7.51}\wen{10.12} and \dlo{4.64}\wen{4.35} dB, suggesting a significantly decreased data quality caused by missing traces. \wen{This criterion is also applied to assess the quality of reconstruction, where $\hat{\mathbf{s}}$ represents the recovered data using the global or local reconstruction algorithms. Thus, the SNR measures the deviation of an estimated data from its true solution.}

%The maximum amplitude of the second event varies at different coordinates $(X,Y)$. We generate the second event by shifting a flat event according to the shift-time table, shown in Figures \ref{fig:syn_how}(a) and \ref{fig:syn_how}(b). The values in the shift-time table denote the corresponding time shifts of the second event in the synthetic data example. The amplitude variation of the second event is shown in Figures \ref{fig:syn_how}(c) and \ref{fig:syn_how}(d). The left column in Figure \ref{fig:syn_how} shows the ``SURF" plots while the right column in Figure \ref{fig:syn_how} shows the ``GREY" plots. ``SURF" and ``GREY" correspond to the two different plotting functions in the MATLAB software platform. From Figure \ref{fig:syn_how} we can see that the maximum and minimum time shifts differ by a bout 15 seconds. The curvature becomes the largest when the time shifts become largest or smallest. It is also clear that the amplitude of the second event decreases from about 1.5 at the four corners to about 0.6 in the center.  Figures \ref{fig:syn-rr} and \ref{fig:syn-rr-e} show the reconstructed data and its corresponding reconstruction error using the global rank-reduction method. Figures \ref{fig:syn-lrr} and \ref{fig:syn-lrr-e} plot the reconstructed data using the localized rank-reduction method and its corresponding reconstruction error.
The global rank-reduction method assumes that the seismic data are composed of several plane waves, \dlo{while}\wen{however,} this assumption is often violated due to the presence of  non-planar wavefield\wen{s} in realistic models (see Figure \ref{fig:syn}). Thus, we improve the global rank-reduction \dlo{based MSSA}\wen{method} using a localized scheme. This method divides the data cube into several smaller volumes to minimize the curvature of seismic waves, which essentially imposes a local plane-wave constraint to alleviate the non-planar effect\wen{s}.  More sophisticated methods based on non-plane-wave assumption\wen{s} (e.g.,  non-stationary principal component analysis \cite{zhao2016principal}) may offer better solutions to the curved wavefronts. To implement the localized rank-reduction method, we apply a 3D moving window with \wen{a} size of $50\times 50\times 50$ to the data volume. We \dlo{also }\dlo{allows}\wen{allow} \dlo{an}\wen{a} 25-points \wen{(i.e., 50\%)} overlap in each direction between successive windows to suppress the edge effects. For each subset of the data volume within the moving window, we use a \wen{reference} rank of three to \dlo{synthesize}\wen{compute} the trajectory matrix \wen{(see Methods)}, \dlo{whereas the rank used in the global rank-reduction method is nine.}\wen{whereas a reference value of nine is adopted in global rank-reduction method.}  In the global case, the two plane waves are well reconstructed (Figure \ref{fig:syn-rr}), but the curved wavefront exhibits significant reconstruction errors, particularly in \dlo{the }areas with large curvatures (Figure \ref{fig:syn-rr-e}). \dlo{On the other hand}\wen{In comparison}, the localized rank-reduction method does not cause obvious damages to the signal (Figure \ref{fig:syn-lrr}) and the reconstruction error is almost zero everywhere (Figure \ref{fig:syn-lrr-e}). Based on SNR metric, the respective quality \dlo{factors}\wen{metrics} for the global and localized reconstructions are \dlo{7.51 dB and 14.38 dB}\wen{17.34 dB and 21.53 dB}, suggesting a better performance of \dlo{localized reconstruction than the global algorithm}\wen{the latter approach}. We extract a single trace at \dlo{the}\wen{a} location where large curvature exists (Figure \ref{fig:syn-trace}). \dlo{It is clear that the}\wen{The} reconstructed trace using localized rank-reduction method (green) almost fully recovers the input (black; Figure \ref{fig:syn-ss-z}), whereas an obvious time shift is present in the trace obtained from the global method (blue; see Figure \ref{fig:syn-ss-z}).

We also use local similarity \cite{fomel2007localattr}, which measures the similarity between two signals in a local sense, to evaluate the reconstruction performance. A mathematical introduction of the local similarity metric is provided in the Supplementary \old{material}\new{Note 2}. In our case, we intend to obtain a reconstruction result that is as close to the clean data as possible.  The local similarity between the clean and the reconstructed data using the global rank-reduction method shows obvious low values along the curved wavefront (Figure \ref{fig:syn-rr-simi}). \dlo{The}\wen{In comparison, the} local similarity of localized reconstruction is high throughout the data volume regardless of the shape of the wavefront (Figure \ref{fig:syn-lrr-simi}). We \dlo{also}\wen{further} investigate the effects of sampling ratios (i.e., the percentage of missing data) on the reconstruction.  To this end, we vary the sampling ratios from 90\% to 10\% and randomly remove the traces. The test results show that 1) the reconstruction performance, \wen{which is defined as SNR using equation 8,} improves with an increasing sampling ratio, 2) the proposed algorithm is robust even at the low end \wen{(30-40\%)} of the sampling range, and 3) the localized rank-reduction implementation always achieves superior reconstruction performance than the global method \wen{(Figure \ref{fig:snr-n})}.

The parameters for both strategies are fine-adjusted to achieve the best reconstruction results. The only parameter for the global rank-reduction method is the rank. To determine the optimal value, we linearly increase the rank and select the one that maximizes the SNR of the reconstructed data.  On the other hand, a two-step process is adopted to determine a pair of parameters (i.e., rank and window size) for the localized rank-reduction method.  As a first step, we optimize the window size while considering a relatively large reference rank (e.g., five). The exact choice of reference rank is not critical at this stage since the rank selection will be further optimized by the automatic rank selection\dlo{ method}\wen{ process}. We fix the overlapping between two neighboring windows to \dlo{be }half of the window size. The length of window in each dimension \dlo{should be chosen so as to segment the data}\wen{needs to be determined properly such that the data is segmented} into patches with the smallest extension. For example, for a dimension of length 100, the recommended window sizes are 10, 20, 50 or 100, since other choices will all cause an extension of dimension. With all possible combinations of the window sizes considering all three dimensions, we select the best window size leading to the largest SNR. In the second step, we further optimize the reference rank for the selected window size.  We decrease the reference rank and adopt the new value if \dlo{it can further improve the SNR}\wen{SNR can be further improved}. In real data processing, we use the same strategy except for the criterion to evaluate the output performance, which is prohibited by a lack of \dlo{ground truth}\wen{ground-truth} solution (i.e., term $\mathbf{s}$ in the equation of SNR). Instead, we define the maximum cross-correlation value between a reconstructed missing trace and its nearest observed trace as the criterion.

To investigate the influence of frequency content to the reconstruction performance of the presented methodology, we extract different frequency contents of the incomplete synthetic data for the reconstruction. \dlo{The bandwidth of the simulated seismic data is mainly confined between 0 and 0.3 Hz (Supplementary Figure \color{blue}{9}\color{black}{}), similar to that of the observed teleseismic P wave.} We linearly increase the frequency band from 0.05 to 0.4 Hz at an interval of 0.05 Hz and perform reconstruction at each frequency slice (Supplementary Figure \color{blue}{10}\color{black}{}). The seismic signals are well recovered in the reconstructed data for frequencies up to 0.3 Hz, showing more coherent P and Ps arrivals. The reconstruction performance degrades at higher frequencies ($>$0.3 Hz) with a lower degree of recovery of the missing traces.  The performance of reconstruction is mainly limited by the weak high-frequency seismic signals with energy that is close to (or below) the noise level (see Supplementary Figures 10g and 10h). We further perform a quantitative assessment of the reconstruction quality by computing the SNR of the output signal at each frequency (Supplementary Figure \color{blue}{11}\color{black}{}). Compared with the raw data, the reconstruction improves the SNRs by a factor of two at all frequencies except for the \dlo{higher}\wen{high} end ($>$0.3 Hz) of the frequency spectrum, where the SNRs fall below the level of input values. In summary, our test results suggest that the frequency content of the signal largely controls the performance of reconstruction, and high-quality results are achievable within the \dlo{dominating frequency band of signal}\wen{dominant frequency band (0-0.3 Hz) of the signal (Supplementary Figure \color{blue}{9}\color{black}{})}.  As a result, a careful frequency analysis of the data is recommended prior to applying the reconstruction algorithm.

%\begin{figure*}[ht!]
%	\centering
%	\subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-vp}
%    \label{fig:syn-jw-vp}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-vs}
%    \label{fig:syn-jw-vs}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-rho}
%    \label{fig:syn-jw-rho}}\\
%    \subfigure[]{\includegraphics[width=0.6\textwidth]{Fig/observation}
%    \label{fig:obs}}
%	\caption{Wavefield simulation of plane-wave incidence beneath a regional array. The synthetic model is constructed using real Moho constraints\cite{schmandt2015distinct} and\dlo{ and} elastic parameters of (a) P-wave velocities, (b) S-wave velocities and (c) densities from a 1D reference model\cite{kennett1995constraints}. The blue lines mark the location of horizontal and vertical slices, where the values of model parameters are demonstrated and projected onto the corresponding sides of the model cube. (d) Observation system demonstrating the positions of planar source and receivers. The stars at the surface denote the evenly distributed receivers and symbols on the dipping plane denote the injected source positions. }
%	\label{fig:syn}
%\end{figure*}
%
%\begin{figure*}[ht!]
%	\centering
%	\subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-clean}
%    \label{fig:syn-clean}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-noisy}
%    \label{fig:syn-noisy}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-mask}
%    \label{fig:syn-mask}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-obs}
%    \label{fig:syn-obs}}
%	\caption{The \dlo{input synthetic}\wen{synthesized} data. (a) The clean data \dlo{containing two main seismic phases. The colors at zero time slice indicate the relative time perturbations of the second phase arrivals.  The cross-hair marks the location of the sample trace shown in Figure 6.}\wen{obtained from elastic wave simulation.} (b) The noisy data with \old{SNR=}\new{signal-to-noise ratio equals to} 10.12 dB. (c) The sampling matrix with a sampling ratio of \dlo{80}\wen{70}\% (d) The final data after applying the sampling matrix to noisy data in (b). The SNR of the \wen{input} data is \dlo{4.64}\wen{4.35} dB.}
%	\label{fig:syns}
%\end{figure*}
%
%\begin{figure*}[ht!]
%	\centering
%	\subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-rr}
%    \label{fig:syn-rr}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-lrr}
%    \label{fig:syn-lrr}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-rr-e}
%    \label{fig:syn-rr-e}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-lrr-e}
%    \label{fig:syn-lrr-e}}
%	\caption{Synthetic test results. (a) Reconstructed data using the global rank-reduction method.  The \old{SNR}\new{signal-to-noise ratio} of the reconstructed data is 17.34 dB. (b) Reconstructed data using the localized rank-reduction method (\old{SNR=}\new{signal-to-noise ratio is }21.53 dB). (c) and (d) Reconstruction errors corresponding to (a) and (b). }
%	\label{fig:syns-rn}
%\end{figure*}
%
%\begin{figure*}[ht!]
%	\centering
%	\subfigure[]{\includegraphics[width=0.4\textwidth]{Fig/syn-jw-ss-0}
%    \label{fig:syn-ss-0}}
%    \subfigure[]{\includegraphics[width=0.4\textwidth]{Fig/syn-jw-ss-z}
%    \label{fig:syn-ss-z}}
%	\caption{Comparison of the single trace amplitude (X=225,Y=225) in \new{different scales.}\old{ (a) original and (b) zoomed-in scales .} \new{(a) Comparison in the original scale. (b) Comparison in the zoomed-in scale.} The black and pink lines represent \dlo{the }clean and noisy data, respectively. The trace processed using global and localized rank-reduction methods are shown by the blue and green lines, respectively. The black line (localized reconstruction) is almost completely overlapped with the green line (true solution), indicating that the error of reconstruction is \dlo{very small}\wen{minimal} for the proposed approach.}
%	\label{fig:syn-trace}
%\end{figure*}
%
%\begin{figure*}[ht!]
%	\centering
%	\subfigure[]{\includegraphics[width=0.25\textwidth]{Fig/syn-jw-rr-simi}
%    \label{fig:syn-rr-simi}}
%    \subfigure[]{\includegraphics[width=0.25\textwidth]{Fig/syn-jw-lrr-simi}
%    \label{fig:syn-lrr-simi}}
%	\caption{\old{Reconstruction performance comparison between (a) global and (b) localized rank-reduction methods using local similarity matrix.}\new{A comparison of reconstruction performance in terms of local similarity metric. (a) Local similarity using the global rank-reduction method. (b) Local similarity using the localized rank-reduction method.} Note that local similarity around curved wavefronts is noticeably lower in the global reconstruction results.}
%	\label{fig:syn-simi}
%\end{figure*}
%
%\begin{figure*}[ht!]
%	\centering
%	\includegraphics[width=0.4\textwidth]{Fig/snr-jw-n}
%	\caption{Reconstruction results at different sampling ratios. The reconstruction performance (SNR) improves with the increasing sampling ratio. The localized rank-reduction method always outperforms the global algorithm.}
%	\label{fig:snr-n}
%\end{figure*}

\subsection*{USArray data test} A more challenging test is performed using the real data from January 18, 2009, Kermadec Islands, Newzealand, Mw 6.4 earthquake recorded by the Transportable Array (TA) component of USArray (\dlo{see }Figure \ref{fig:station_earthquake}). Despite the best effort in acquisition design, earthquake data is rarely recorded on a perfectly even-spaced seismic array. Similar to earlier  interpolation methods \cite{neal1999imaging,dokht2016singular,schneider2017improvement}, the first step of our reconstruction algorithm is to bin the data onto a regular grid. To this end, we use a weighted interpolation method for the binning process. At each node location, the waveforms from nearby stations that are located within one grid distance are stacked and subsequently assigned to the node, whereas the node remains empty if no neighboring stations \dlo{is}\wen{are} available.  We use a grid \dlo{size of $ \sim $70 km}\wen{with respective dimensions of 1.0 deg and 0.5 deg in latitude and longitude directions}, which is comparable to the station spacing of USArray, to minimize the effect of spatial smoothing while preserving small-scale features \wen{(Supplementary Figure \color{blue}{1}\color{black}{})}. Future study would focus on interpolating an arbitrary geometry given a randomly distributed data set. \wen{The degree of data completeness after the binning process is demonstrated by the sampling matrix (Supplementary Figure \color{blue}{2}\color{black}{}), where empty and data-filled grid points are indicated by zero and one, respectively.} We obtain a regular grid with \wen{a} dimension of $16\times 28$ (longitude $\times$  latitude) that comprises a total of 448 sampling points.  Among them 253 nodes are filled with the recorded earthquake data while the remaining 164 points \dlo{are required to be reconstructed}\wen{require to be reconstructed} by the proposed algorithm, resulting in a sampling rate (i.e., data completeness) of 56.5\% in the data.

%\begin{figure*}[ht!]
%	\centering
%	\includegraphics[width=\textwidth]{Fig/station_earthquake}
%	\caption{The distribution of USArray stations in this study. The lateral dimension of the reconstructed data volume is highlighted by the rectangle. A large portion of the data is missing due to relatively spare station coverage in the southwest.   The inset shows the location of the earthquake (red star) relative to the recording array (blue triangles).}
%	\label{fig:station_earthquake}
%\end{figure*}

\plot{station_earthquake}{width=\textwidth}{The distribution of USArray stations in this study. The lateral dimension of the reconstructed data volume is highlighted by the rectangle. A large portion of the data is missing due to relatively spare station coverage in the southwest.   The inset shows the location of the earthquake (red star) relative to the recording array (blue triangles).}

%\begin{figure*}[ht!]
%	\centering
%	\subfigure[]{\includegraphics[width=0.4\textwidth]{Fig/test0}
%    \label{fig:test0}}
%    \subfigure[]{\includegraphics[width=0.4\textwidth]{Fig/test1}
%    \label{fig:test1}}\\
%    \subfigure[]{\includegraphics[width=0.4\textwidth]{Fig/test2}
%    \label{fig:test2}}
%	\caption{A 3D view of the earthquake data recorded \dlo{from the}\wen{by} USArray analyzed in our study. (a) Observed data on a regular grid. The circled area shows the region with\dlo{ a} poor spatial sampling.  The red arrows indicate the weak-amplitude P-wave arrivals contaminated by the noise. (b) Reconstructed data using \wen{the} global rank-reduction method. (c) Reconstructed data using \wen{the} localized rank-reduction method.   }
%	\label{fig:comp}
%\end{figure*}

%\begin{figure*}[ht!]
%	\centering
%	\includegraphics[width=0.8\textwidth]{Fig/Figure9}
%	\caption{A comparison \new{of reconstruction results} between different time slices. \old{(a) The time slice corresponding to $t=1200$ s of observed (left) and reconstructed (right) USArray data.  (b) The same as (a) but for time slice at $2100$ s.  The clear phase arrivals are reconstructed in the SW corner of the seismic array.}\new{(a) The time slice corresponding to $t=1200$ s of observed USArray data. (b) The time slice corresponding to $t=1200$ s of reconstructed USArray data. (c)-(d) The same as (a)-(b) but for time slice at $2100$ s.  The clear phase arrivals are reconstructed in the SW corner of the seismic array.  }}
%	\label{fig:comp}
%\end{figure*}

\multiplot{3}{test0,test1,test2}{width=0.4\textwidth}{A 3D view of the earthquake data recorded \dlo{from the}\wen{by} USArray analyzed in our study. (a) Observed data on a regular grid. The circled area shows the region with\dlo{ a} poor spatial sampling.  The red arrows indicate the weak-amplitude P-wave arrivals contaminated by the noise. (b) Reconstructed data using \wen{the} global rank-reduction method. (c) Reconstructed data using \wen{the} localized rank-reduction method.}

\plot{comp}{width=0.8\textwidth}{A comparison \new{of reconstruction results} between different time slices. \old{(a) The time slice corresponding to $t=1200$ s of observed (left) and reconstructed (right) USArray data.  (b) The same as (a) but for time slice at $2100$ s.  The clear phase arrivals are reconstructed in the SW corner of the seismic array.}\new{(a) The time slice corresponding to $t=1200$ s of observed USArray data. (b) The time slice corresponding to $t=1200$ s of reconstructed USArray data. (c)-(d) The same as (a)-(b) but for time slice at $2100$ s.  The clear phase arrivals are reconstructed in the SW corner of the seismic array. }}

%\begin{figure*}[ht!]
%	\centering
%	\subfigure[]{\includegraphics[width=0.39\textwidth]{Fig/Figure10a}
%    \label{fig:us_lon1}}
%    \subfigure[]{\includegraphics[width=0.39\textwidth]{Fig/Figure10b}
%    \label{fig:us_lon2}}\\
%	\subfigure[]{\includegraphics[width=0.39\textwidth]{Fig/us_lon1_z}
%    \label{fig:us_lon1_z}}
%    \subfigure[]{\includegraphics[width=0.39\textwidth]{Fig/us_lon22_z}
%    \label{fig:us_lon2_z}}\\
%    \subfigure[]{\includegraphics[width=0.39\textwidth]{Fig/us_uncertainty}
%    \label{fig:us_uncert}}
%	\caption{A detailed comparison of reconstruction performance along with a longitudinal slice (longitude = 107.6$^o$ W). \old{comparison of waveforms (a) before and (b) after the reconstructions .}\new{(a) Raw waveforms before reconstruction. (b) Reconstructed waveforms.} The main phase arrivals are marked by the red lines and labeled. The missing traces have been reconstructed and the signal-to-noise ratio of the main phases are significantly improved in (b). \new{(c)-(d) Detailed comparison of the weak amplitude phases (P and PP) that are highlighted by the green rectangles in (a)-(b).} \old{The green rectangles highlight the weak amplitude phases (P and PP) that are examined in detail in (c) and (d).  }(e)The reconstruction uncertainty for the longitudinal slice.}
%	\label{fig:lons}
%\end{figure*}

\multiplot{5}{us_lon1,us_lon2,us_lon1_z,us_lon2_z,us_uncert}{width=0.39\textwidth}{A detailed comparison of reconstruction performance along with a longitudinal slice (longitude = 107.6$^o$ W). \old{comparison of waveforms (a) before and (b) after the reconstructions .}\new{(a) Raw waveforms before reconstruction. (b) Reconstructed waveforms.} The main phase arrivals are marked by the red lines and labeled. The missing traces have been reconstructed and the signal-to-noise ratio of the main phases are significantly improved in (b). \new{(c)-(d) Detailed comparison of the weak amplitude phases (P and PP) that are highlighted by the green rectangles in (a)-(b).} \old{The green rectangles highlight the weak amplitude phases (P and PP) that are examined in detail in (c) and (d).  }(e)The reconstruction uncertainty for the longitudinal slice.}

During the earthquake, TA was deployed in western US covering the Basin and Range Province and the Great Plains, which marks a transition region from the active western US to the relatively stable eastern part.  This diverse tectonic environment provides an ideal \dlo{natural laboratory}\wen{dataset} to test the robustness and accuracy of our reconstruction algorithm.  We aim to create a complete data volume using the vertical component seismograms acquired at 625 stations. The same method can be applied to reconstruct the other two horizontal components. As a first step, the original traces are subject to a sequence of preprocessing including instrument response removal, integration to displacement, and binning onto a regular grid \wen{(Supplementary Note 1)}. The processed data forms a 3D cube with a dimension of $5400\times 16\times 28$ along time, longitude and latitude axes \wen{(Figure \ref{fig:test0})}.  The quality of this dataset is mainly limited by 1) the missing traces that account for a significant portion of the data volume and 2) strong noises that interfere with \dlo{the} phase arrivals.  The former constraining factor leads to \dlo{the} reduced resolution in regions with incomplete data sampling (e.g., the circled area on Figure \ref{fig:test0}) and the presence of noise \dlo{could }\wen{can} mask relatively low\wen{-}amplitude arrivals such as the P waves (see Figure \ref{fig:test0}).

We apply the two rank-reduction methods to the preprocessed data.  Figure \ref{fig:test1} shows the reconstructed data using the global rank-reduction method. In global reconstruction, we treat the whole 3D data cube as the input and set the  rank to eight, which is determined carefully by our tests. The reconstruction results show an improved data coherency compared to the input, as demonstrated by a more detailed wavefield variation in the \dlo{same }time slice at 2600 sec (Figures \ref{fig:test0} and \ref{fig:test1}). However, a major issue with the global method is that it tends to smooth small-scale arrivals (e.g., \dlo{see }P waves indicated by red arrows in Figure \ref{fig:test1}).  In this example, because of the \dlo{weak amplitude}\wen{relatively weak energy} of the first arrivals, they cannot be robustly distinguished from the noise using the global rank-reduction algorithm.  This issue is largely resolved \dlo{using}\wen{by} the localized rank-reduction method, where both time \dlo{slide}\wen{slices} and the first arrivals are well recovered\wen{ (Figure \ref{fig:test2})}.

%In this test, because the seismic events are relatively planar, and the data structure is not very complicated (as compared with the previously discussed synthetic example), we use a relatively larger local window of size $1000\times 16\times 28$, which means we do not segment the data in both longitude and latitude dimensions.\\ REMOVE SINCE IT WEAKENS OUR ARGUMENT
We \dlo{then }compare two time slices that contain weak phase arrivals between the original and the reconstructed data.  The first time slice shows the energy related to \dlo{P-wave coda}\wen{PP phase} \new{(Figures \ref{fig:comp}(a) and \ref{fig:comp}(b))}, the free surface multiple of P wave. This weak phase is severely contaminated by the \dlo{scattering}\wen{scattered} energy associated with the P-wave codas.  As a result, the wavefield pattern of PP is largely incoherent across the recording array, even in the center and northeastern portions where station coverage is high. The second time slice focuses on the wavefield around the excepted arrival time of SS phase, which is the shear wave reflected off the surface at the midpoint of source-station \wen{path}, showing much coherent \dlo{energies}\wen{energy} compared to the scattered wavefield \new{(Figures \ref{fig:comp}(c) and \ref{fig:comp}(d))}. The reconstructed time slice successfully fills the data gap and captures the detailed variation in wavefield energy. We demonstrate the reconstruction performance on full seismogram in Figure \ref{fig:lons}, where nine traces are missing in this longitude slice. The quality of various phase arrivals \dlo{are}\wen{is} severely degraded by noise.  After reconstruction, these phases are clearly identifiable from both pre-existing and reconstructed traces. \wen{A more detailed examination of weak amplitude phases shows that 1) the waveform characteristics (e.g., phase and amplitude) of the existing traces are well preserved by the reconstruction algorithm without excessive smoothing and 2) the reconstructed traces well capture the coherent energy of the data, showing similar waveform quality to the nearby (observed) traces (Figures \ref{fig:us_lon1_z} and \ref{fig:us_lon2_z}).}

We conduct a bootstrapping test\cite{bootstrap1991} to estimate the effect of spatial sampling of wavefield on reconstruction. We randomly select 40\% of the observed seismograms to reconstruct the 3D data cube and repeat this step 20 times. We calculate the standard deviation of the 20 reconstructed datasets and use the normalized deviation as an estimate of uncertainty. The reconstruction uncertainty is low for body-wave phases (e.g., P and S) even in \wen{the} presence of intermediate (~200 km) data gap  (Figure \ref{fig:us_uncert}), whereas the uncertainty is slightly higher in time ranges with weak arrivals (e.g., body wave codas), especially in regions with poor \dlo{spatial distribution of stations}\wen{station coverage} (e.g., big recording gaps).  \dlo{On the other hand, a relatively large uncertainty is observed in surface waves (see Figure \ref{fig:us_uncert}).  This increased uncertainty is mainly caused by the waveform complexity of surface wave, which is characterized by a dispersive wave train rather than a distinct (linear) phase arrival (e.g., body waves).}\wen{Compared to the well-recovered body wave phases, the surface wave portion shows relatively large uncertainties in amplitude recovery (see Figure 10(e)). The degraded reconstruction performance is mainly challenged by the waveform complexity of surface wave, which is characterized by a dispersive wave train rather than a distinct (linear) phase arrival (e.g., body waves). To alleviate these effects, a frequency-dependent, instead of a linear, time window may be required to better isolate the surface wave energy. For example, one may consider a Gaussian window with varying center frequencies as widely adopted in dispersion analysis \cite{dziewonski1969technique}. As importantly, a more careful examination (and selection) of surface wave related rank values is also essential to better capture the surface wave energy. Both aspects are critical to an improved reconstruction performance of surface waves and are worth future investigations.}  The lateral distribution of uncertainty is relatively constant across the study area except at the southwest corner (Supplementary Figure \color{blue}{12}\color{black}{}), where uncertainty is about 3 times higher due to highly insufficient data sampling. \dlo{Overall, the comparisons suggest the effectiveness of}\wen{Through waveform comparisons and uncertainty analysis, we are confident to suggest that} the proposed localized rank-reduction method \dlo{in reconstructing}\wen{enables a robust reconstruction of} the incomplete earthquake recordings\wen{, in particular, body wave phases}, which provides useful data constraints to the regions where no seismometers were placed.\\

\section*{Discussions}
The synthetic and real data examples demonstrate the ability of localized rank-reduction method in reconstructing the missing traces. The complete dataset, with improved quality and spatial sampling, is critical for improving array-based seismic imaging methods \cite{rost2002array, gu2010arrays}.  In this section, we demonstrate the accuracy of our method and its  application in seismic imaging using the cross-correlation travel time measurement, a widely used technique in travel time tomography.

Seismic tomography is one of the most commonly applied seismic imaging techniques that greatly \dlo{improves}\wen{improve} the understanding of the internal structure of Earth. Seismic tomography can be broadly classified based on the types of data (travel time or waveform) and the approximation of wave propagation theory (ray or finite frequency) \cite{liu2012seismic}. One classical method of \wen{the} tomographic family is regional travel time tomography \cite{aki1977determination} that utilizes the travel time difference between nearby stations to resolve the subsurface velocity structure. The density of the station and \wen{the} accuracy of travel time measurements are critical factors for high-resolution imaging. We provide an example of travel time measurements to demonstrate the \dlo{accuracy}\wen{capability} of the proposed reconstruction \dlo{method}\wen{method in improving P wavefield}.

The relative travel times between stations in a recording array are measured using multi-channel cross-correlation \cite{vandecar1990determination}.  For a pair of stations, the\dlo{ir} optimal relative travel time is determined by the time delay that leads to the maximum correlation coefficient between the two traces containing the phase of interest (e.g., P wave). To ensure the consistency of travel time measurements among all recording stations, the relative travel time between each station pair is optimized through a least-squares inversion. This optimization process also imposes a zero average constraint to the travel times.  \dlo{As a final step}\wen{Finally}, the demeaned theoretical arrival times (based on a reference Earth model) are subtracted from the optimized values to obtain the relative travel time residuals that can be inverted for velocity perturbations underlying the recording array.

The travel time measurement is first performed on the original data. We filter the seismic traces between 0.03 and 0.125 Hz to enhance the useful signal and utilize a 100 sec \dlo{time}\wen{cross-correlation} window starting 50 sec prior to the \dlo{predicated}\wen{predicted} P-wave arrival time based on AK135 model \cite{kennett1995constraints}. The resulting travel time pattern is similar to the predictions (i.e., theoretical arrival times from AK135) because the time perturbations induced by structural variation is much smaller than the move-out (Supplementary Figure \color{blue}{13}\color{black}{}). After correcting for the move-out effect, the remaining values (i.e., relative travel time residuals) are considered to be mainly caused by \dlo{velocity anomalies near the stations}\wen{the receiver-side velocity anomalies}. The measured residuals from the original data generally \dlo{shows}\wen{show} a dichotomy of \dlo{travel time pattern}\wen{travel times}: delay in the SW and advance in the NE (Figure \ref{fig:ttres_vel}\color{blue}{(a)}\color{black}{}), suggesting distinctive mantle structures in these two regions.  Some \dlo{local scale}\wen{local-scale} variations are also observable in the travel \dlo{times}\wen{times (e.g., time delay related to Yellowstone hotspot)}. We then conduct travel time measurements on the reconstructed data using identical parameters (\dlo{e.g.}\wen{i.e.,} frequency and window length).   The resulting travel time variation is more coherent compared to that from the original data (Figure \ref{fig:ttres_vel}\color{blue}{(b)}\color{black}{}). A major difference is \dlo{the}\wen{a} significant time advance in the \dlo{center}\wen{central} part of the array, which \dlo{transition}\wen{transitions} sharply to the regime of time delay in the SW.   In comparison, the travel time advance in the original data appears to be more scattered and the transition\dlo{ to time delay} is much smoother.

Seismic travel time is sensitive to velocity anomalies within the Fresnel zone around the ray path \cite{dahlen2000frechet}, thus the consistency of the travel time pattern with the velocity structures can be used as an effective metric to evaluate the robustness of the travel time measurements. For a plane wave from a teleseismic source, it illuminates the upper mantle portion of the Earth structure beneath the recording array from the direction of back-azimuth  at a steep incidence angle. The presence of negative (i.e., slow\dlo{er}) and positive (i.e., fast\dlo{er}) velocity anomalies respectively causes the delay and advance of the P-wave arrivals. The availability of high-resolution seismic velocity models in \wen{the} western US enables a detailed examination of the travel time accuracy. We utilize a recent \wen{high-resolution} tomographic model of the upper mantle of continental US \cite{schmandt2014p}, which is constructed using 516,668 P-wave travel time residuals measured within multi-frequency bands in combination with a finite-frequency kernel \cite{dahlen2000frechet}. \dlo{Besides}\wen{In addition to} the high model resolution, the choice of this model is prompted by the same travel time type (i.e., relative residuals) that permits a direct comparison with our measurements. Since travel time residual reflects an integrated effect of velocity anomalies in the upper mantle, in particular the heterogeneous mantle lithosphere, we \dlo{compute velocity anomalies}\wen{consider velocity structures} between 50-250 km and compute the average amplitude (i.e., perturbation) of the seismic velocity anomaly (Figure \ref{fig:ttres_vel}\color{blue}{(c)}\color{black}{}). The resulting velocity perturbation agrees well with the reconstructed travel time pattern, whereas its correlation with the travel times from original data is less apparent. In particular, the high-velocity zone beneath the southern Wyoming craton is in excellent agreement with the coherent travel time advance in the reconstructed data, while the original data shows \dlo{much a}\wen{a much} scattered travel time pattern. \wen{Furthermore}, the sharp velocity transition to the \wen{low-velocity} Cordillera is clearly delineated by the travel time variation from the reconstructed data, while this travel time contrast is largely smeared in the original data. In addition, some small-scale structure variations (e.g., the SE corner of the array \wen{and the Yellowstone anomaly}) are captured by the travel times from the reconstructed data.  More importantly, in the regions with large data gaps, the accuracy of the reconstructed travel times are supported by the \dlo{velocity}\wen{velocities}.  For example, in the western part of the array between 36-43$^o$  N, the travel time shows an overall delay pattern that corresponds to \dlo{the }below than average seismic \wen{velocities}, and the smaller data gap at the NE corner also exhibits a reasonable agreement between \wen{the} two variables.

We further evaluate the uncertainty of travel time measurements from both datasets. For each station, we compute its travel time errors with respect to other stations defined as the difference between the least-squares optimized and cross-correlation determined travel times. The standard deviation of all measurement errors is then used as an estimate of the measurement uncertainty at this station. The respective average uncertainties of the original (Figure \ref{fig:raw_ssa_tt}\color{blue}{(a)}\color{black}{}) and the reconstructed data (Figure \ref{fig:raw_ssa_tt}\color{blue}{(b)}\color{black}{}) are 0.50 sec and 0.41 sec, respectively. We notice that the uncertainty of the reconstructed data is in fact dominated by a few large outliers at \dlo{relatively }poorly constrained nodes (see Figure \ref{fig:raw_ssa_tt}\color{blue}{(b)}\color{black}{}), where the absolute value of travel time residual is on average greater than 2.0 sec. Most of these nodes are located in the regions with the largest data gap or near the edges of the data volume (e.g., SW corner). These anomalously large measurements are typically caused by cycle-skipping or poor data quality\dlo{ hence}\wen{, and thus} are removed from the inversion process in regional tomographic study \cite{chen2017finite}. After removing the outliers, which accounts for 4.5\% of the total measurements, the \dlo{overall}\wen{average} uncertainty decreases to 0.35 sec and is significantly smaller than that \dlo{from}\wen{of} the original data, suggesting \dlo{the improvement in}\wen{an improved} \dlo{phase}\wen{P-wave} consistency in the reconstructed data.

The travel time example demonstrates the improved resolving power of the complete dataset to small-scale structure variations.  Thanks to the rapid development of dense seismic \wen{arrays} around the \dlo{global}\wen{globe}, new seismic imaging techniques have been focusing on simultaneous processing of recordings from nearby sensors on a uniform/semi-uniform grid. One of the rapidly advancing fields is seismic surface tomography that utilizes either the travel time \cite{lin2009eikonal, jin2015surface} or the shape of the wavefield \cite{lin2011helmholtz, langston2007wave} recorded at \dlo{the }dense arrays to infer the elastic properties of the subsurface. These methods typically require the calculation of spatial derivatives with \dlo{respective}\wen{respect} to a certain parameter such as \dlo{traveltime}\wen{the travel time} (e.g., Eikonal tomography \cite{lin2009eikonal}) or amplitude of \wen{the} surface wave (e.g., Helmholtz tomography \cite{lin2011helmholtz} and gradiometry \cite{langston2007wave}), which is best performed on a regular grid to ensure the numerical stability and accuracy.  The compressive-sensing based reconstruction approach proposed by Zhan et al. (2018) \cite{zhan2018application} has demonstrated the improvement in \dlo{velocity estimates}\wen{resolving velocities} using the reconstructed wavefields.  Similarly, we \dlo{except}\wen{expect} an improved imaging performance of these gradient-based tomographic approaches when applied to the reconstructed data.  The validation of this argument is beyond the scope of this paper and will be investigated in future studies. Finally, the improvement in sensor technology as exemplified in several large N array experiments \cite{lin2013high,schmandt2013analysis,hansen2015automated,ward2018high} has permitted a higher-density sampling that is close to \wen{an} exploration-scale survey. The development of imaging technology, such as the \wen{one} proposed in our study, should work hand-in-hand with the improvement in data acquisition to achieve the ultimate goal of having a better understanding of the Earth's structure.

%Seismic array data can suffer from high noise level and incomplete spatial sampling despite the best efforts in improving the acquisition design. To alleviate these data related issues, we develop an effective iterative localized rank-reduction algorithm to simultaneously suppress the noise and reconstruct the missing traces. The proposed method, when compared with the traditional global rank-reduction based method, shows superior performance in preserving small-scale features such as the curved wavefront and weak-amplitude arrivals. The application of our method to both synthetic data and real earthquake recordings demonstrate greatly improved quality and coherency of the reconstructed data.  Finally, we compare the relative travel time residuals, the input for travel time tomography, measured from original and reconstructed data.   The travel times from the latter dataset shows 1) a better match with the velocity structures revealed from recent tomographic model and 2) a reduced uncertainty in the cross-correlation measurements. Overall, our study provides a useful tool for improving the quality of array data and compensating the deployment limitation of seismic arrays. Since our method is fully compatible with the higher-density seismic survey that start building momentum in global seismology community, we can expect its great potential in improving the existing and motivating new array-based seismic imaging techniques.

%\begin{figure*}[ht!]
%	\centering
%%	\includegraphics[width=0.7\textwidth]{Fig/ttres_vel}
%	\includegraphics[width=0.7\textwidth]{Fig/Figure11}
%	\caption{\old{P-wave relative travel time residuals across the recording array measured from (a) the original and (b) the reconstructed data.}\new{A comparison of P-wave travel time measurements between the original and reconstructed data. (a) Relative travel time residuals across the recording array measured from the original data. (b) Relative travel time residuals measured from the reconstructed data.} Measurements with uncertainties larger than one standard deviation of the cross-correlation error are \dlo{shaded in gray}\wen{represented by gray circles} in (b). The brown lines indicate the boundaries of major tectonic domains in \wen{the} western US. (c) Average P-wave velocity perturbations between 50-250 km depths from \wen{Schmandt and Lin (2014)} \cite{schmandt2014p}.}
%	\label{fig:ttres_vel}
%\end{figure*}

%\begin{figure*}[ht!]
%	\centering
%	\includegraphics[width=0.7\textwidth]{Fig/raw_ssa_tt}
%	\caption{ \new{A comparison of travel time measurement uncertainties.}\old{Travel time measurement uncertainties of (a) the original and (b) the reconstructed data.}\new{ (a) Travel time plot of the original data. (b) Travel time plot of the reconstructed data.} Both measured and predicted travel times are demeaned to emphasize the perturbations. The blue data points in (b) represent measurement outliers differing by more than 2 sec from the predictions, which are excluded from tomographic inversion in real practice.}
%	\label{fig:raw_ssa_tt}
%\end{figure*}
%

\plot{ttres_vel}{width=0.7\textwidth}{\old{P-wave relative travel time residuals across the recording array measured from (a) the original and (b) the reconstructed data.}\new{A comparison of P-wave travel time measurements between the original and reconstructed data. (a) Relative travel time residuals across the recording array measured from the original data. (b) Relative travel time residuals measured from the reconstructed data.} Measurements with uncertainties larger than one standard deviation of the cross-correlation error are \dlo{shaded in gray}\wen{represented by gray circles} in (b). The brown lines indicate the boundaries of major tectonic domains in \wen{the} western US. (c) Average P-wave velocity perturbations between 50-250 km depths from \wen{Schmandt and Lin (2014)} \cite{schmandt2014p}.}

\plot{raw_ssa_tt}{width=0.7\textwidth}{ \new{A comparison of travel time measurement uncertainties.}\old{Travel time measurement uncertainties of (a) the original and (b) the reconstructed data.}\new{ (a) Travel time plot of the original data. (b) Travel time plot of the reconstructed data.} Both measured and predicted travel times are demeaned to emphasize the perturbations. The blue data points in (b) represent measurement outliers differing by more than 2 sec from the predictions, which are excluded from tomographic inversion in real practice.}

%\section*{Conclusions}
%Seismic array data can suffer from high noise level and incomplete spatial sampling despite the best efforts in improving the acquisition design. To alleviate these data related issues, we develop an effective iterative localized rank-reduction algorithm to simultaneously suppress the noise and reconstruct the missing traces. The proposed method, when compared with the traditional global rank-reduction based method, shows superior performance in preserving small-scale features such as the curved wavefront and weak-amplitude arrivals. The application of our method to both synthetic data and real earthquake recordings demonstrate greatly improved quality and coherency of the reconstructed data.  Finally, we compare the relative travel time residuals, the input for travel time tomography, measured from original and reconstructed data.   The travel times from the latter dataset shows 1) a better match with the velocity structures revealed from recent tomographic model and 2) a reduced uncertainty in the cross-correlation measurements. Overall, our study provides a useful tool for improving the quality of array data and compensating the deployment limitation of seismic arrays. Since our method is fully compatible with the higher-density seismic survey that start building momentum in global seismology community, we can expect its great potential in improving the existing and motivating new array-based seismic imaging techniques.

\section*{Methods}
\subsection*{Iterative rank-reduction method} The incomplete earthquake data on \wen{a} regular grid\dlo{s} can be expressed simply as
\begin{equation}
\label{eq:dsamp}
\mathbf{u}=\mathbf{S}\mathbf{v},
\end{equation}
where $\mathbf{v}$ denotes the complete earthquake data, $\mathbf{u}$ denotes the observed incomplete data, and $\mathbf{S}$ is the sampling operator. \wen{Both $\mathbf{u}$ and $\mathbf{v}$ denote vectors of size $N_tN_xN_y\times 1$. $N_t,N_x,N_y$ denote the lengths of the $t,x,y$ axes, respectively.} The sampling \dlo{matrix}\wen{operator} is a diagonal \dlo{operator}\wen{matrix} \wen{of size $N_tN_xN_y\times N_tN_xN_y$.}\dlo{, where the diagonal entries correspond to each entry in the sampling matrix, which is of the same size of the data matrix. Here, both $\mathbf{u}$ and $\mathbf{v}$ denote vectorized data.} In the sampling operator, each ``zero'' diagonal entry corresponds to a missing sample and ``one'' diagonal entry denotes a sampling point. The sampling matrix will be presented when analyzing the results of data \dlo{restoration}\wen{reconstruction}.

Given a reconstruction filter $\mathbf{P}$, we follow the weighted projection-onto-convex sets (POCS)-like scheme to iterative\wen{ly} reconstruct the missing earthquake data and suppress the strong random noise that downgrades the quality of the data. The weighted POCS-like method is expressed as
\begin{equation}
\label{eq:wpocs}
\mathbf{v}_n  = \alpha_n\mathbf{u} + (1-\alpha_n\mathbf{S}) \mathbf{P} \mathbf{v}_{n-1},
\end{equation}
where $\alpha_n$ is an iteration-dependent relaxation factor to control the suppression of the random ambient noise. Here, we follow the linear-decreasing strategy used in \wen{Chen et al. (2016)} \cite{yangkang2016irr5d} for iteratively suppressing the noise while restoring the noisy data with newly interpolated data.

In the rank-reduction method \cite{mssa}, the filtering is conducted in the frequency-space domain of the multi-channel earthquake data. When rewriting $\mathbf{v}$ in a \dlo{matrix}\wen{tensor} form $V(x,y,t)$, the rank-reduction method first transforms the data from $t-x-y$ domain to $f-x-y$ domain, i.e., $V(x,y,f)$. The frequency domain data \dlo{matrix }is then rearranged into a multiple of \wen{block} Hankel matrices for each frequency slice. The Hankel matrix $\mathbf{R}_i$ for row $i$ of the matrix $V(x,y,f)$ constructed from the frequency slice of $f$ is
\begin{equation}
\label{eq:mssa3d}
\mathcal{R}_i(f)=\left(\begin{array}{cccc}
V(i,1,f) & V(i,2,f) & \cdots &V(i,M_x,f) \\
V(i,2,f) & V(i,3,f)  &\cdots &V(i,M_x+1,f) \\
\vdots & \vdots &\ddots &\vdots \\
V(i,L_x,f)&V(i,L_x+1,f) &\cdots&V(i,N_x,f)
\end{array}
\right).
\end{equation}
By omitting $f$, equation \ref{eq:mssa3d} is then inserted into a block Hankel matrix by
\begin{equation}
\label{eq:mssa3d2}
\mathcal{H}=\left(\begin{array}{cccc}
\mathcal{R}_1 & \mathcal{R}_2 & \cdots &\mathcal{R}_{M_y}\\
\mathcal{R}_2 & \mathcal{R}_3  &\cdots &\mathcal{R}_{M_y}\\
\vdots & \vdots &\ddots &\vdots \\
\mathcal{R}_{L_y} &\mathcal{R}_{L_y+1} &\cdots&\mathcal{R}_{N_y}
\end{array}
\right),
\end{equation}
where the Hankel matrix $\mathcal{H}$ is assumed to be of low rank. $N_x$ \wen{and $N_y$} denote the number of channels in \wen{the $x$ and $y$ dimension of }the data. $L_x=\lfloor N_x/2 \rfloor+1$ and $M_x=N_x-L_x+1$, where $\lfloor \cdot \rfloor$ is the operator to calculate the integer part. \wen{Similarly, $L_y=\lfloor N_y/2 \rfloor+1$ and $M_y=N_y-L_y+1$.} The low-rank extraction of the key information from the Hankel matrix is equivalent to the principal component analysis of the Hankel matrix. To optimally extract the principal components, i.e., the signals, from the Hankel matrix of an updated data, we aim at solving the following optimization problem
\begin{equation}
\label{eq:E}
\begin{split}
\min &\parallel \mathcal{E} \parallel_F^2 \\
\text{s.t.} \quad \text{rank}(\mathcal{S}) & =K, \text{and}, \mathcal{E}=\mathcal{H}-\mathcal{S},
\end{split}
\end{equation}
\wen{where $\mathcal{S}$ denotes a low-rank matrix and $\mathcal{E}$ denotes small random perturbations. }
Problem \ref{eq:E} can be conveniently solved via the singular value decomposition (SVD) algorithm. \dlo{$[\mathcal{P},\Sigma,\mathcal{Q}]=\text{SVD}(\mathcal{H})$,}

\dlo{The decomposed value matrices are used to reconstruct a rank-reduced matrix by selecting only the first $K$ singular vectors and singular values $\hat{\mathcal{H}} = [\mathcal{P}(1:K,:),\Sigma(1:K,1:K),\mathcal{Q}(:,1:K)]$.}
\wen{
The SVD of $\mathcal{H}$ can be expressed as 
\begin{equation}
\label{eq:svd}
\mathcal{H} = \mathcal{P}\Sigma\mathcal{Q}^T,
\end{equation}
where $[\cdot]^T$ denotes transpose, and 
\begin{equation}
\begin{split}
\mathcal{P} &= [\mathbf{p}_1,\mathbf{p}_2,\cdots,\mathbf{p}_N], \\
\Sigma &= [\sigma_1,\sigma_2,\cdots,\sigma_N],\\
\mathcal{Q} &= [\mathbf{q}_1,\mathbf{q}_2,\cdots,\mathbf{q}_N].
\end{split}
\end{equation}
$\mathbf{p}_i$ and $\mathbf{q}_i$ ($1\le i \le N$) are $i$th left and right singular \wen{vectors} of SVD. $\sigma_i$ denotes the $i$th singular value. $N$ denotes the number of columns in matrix $\mathcal{H}$. The decomposed value matrices are used to reconstruct a rank-reduced matrix by selecting only the first $K$ singular vectors and singular values
\begin{equation}
\label{eq:svd}
\hat{\mathcal{H}} = \sum_{i=1}^{K}\sigma_i\mathbf{p}_i\mathbf{q}_i^T.
\end{equation}
}
The rank-reduced Hankel matrix is then remapped back to a 1D vector by averaging along the anti-diagonals. The mapping from each frequency slice to the Hankel matrix is referred to as the Hankelization step and the averaging along anti-diagonals is called the inverse Hankelization process. The overall process including the Hankelization, principal component extraction, and inverse Hankelization can be denoted by the restoration filtering operator $\mathbf{P}$ expressed previously in equation \ref{eq:wpocs}. \wen{Note that similar strategies are commonly used in the subspace separation methods, e.g., defining the log-likelihood of each eigenvalue to be related to signal subspace to estimate the signal component.}

\subsection*{Automatic rank selection} In the rank-reduction filtering introduced above, the predefined rank parameter $K$ plays a significant role in \dlo{the }obtaining satisfactory performance. It has been documented that an appropriate selection of $K$ can be the number of seismic events that have distinct slownesses \cite{mssa}. However, the real earthquake data is never a simple composition of several wave types with clear arrivals. Instead, the earthquake data can be much more complicated, e.g., the seismic arrivals are buried  in the strong noise or the weak phases are hidden in the more dominant strong codas. Besides, the events in the earthquake record can be curving when the range of epicentral distance is large.

Thus, \dlo{to select}\wen{the selection} the optimal rank is a non-trivial task. Generally speaking, if the rank is chosen too large, the rank-reduction filter tends to preserve all subtle features in the data, including the random noise and missing seismograms, thus the \dlo{resulted}\wen{resulting} data will contain strong residual noise and not be able to reconstruct the true-amplitude of the missing data. If the rank is chosen too small, the rank-reduction filter can remove most useful signal components and only leave the most dominant energy in the seismic record, e.g., the coda waves or the PP phases with strong amplitude. The rank parameter is highly correlated with the structural complexity of the data, and traditionally the optimal rank requires a lot of human \dlo{effort}\wen{efforts} and \dlo{priori}\wen{prior} knowledge.

Thus, we introduce an adaptive method to optimally select the rank parameter for the rank-reduction filtering. We utilize the difference of the singular values between signals and noise in the singular spectrum to define the rank. We first define a singular value ratio sequence
\begin{equation}
\label{eq:ratio}
r_i = \frac{\sigma_i}{\sigma_{i+1}}, i=1,2,3,\cdots,N-1,
\end{equation}
where $\sigma_i$ is the $i$th singular value of the Hankel matrix $\mathcal{H}$ and $\{r_i\}$ denotes the singular value ratio sequence. $N$ denotes the size of the singular spectrum. The optimal rank $K$ is obtained when the sequence $r_i$ reaches the maximum
\begin{equation}
\label{eq:r}
\hat{K} = \arg \max_{i} r_i.
\end{equation} 
The principles of the adaptive rank selection method introduced in equations \ref{eq:ratio} and \ref{eq:r} are based on the\dlo{ detecting}\wen{ detection of} the cut-off rank in the singular value spectrum which indicates the separation between signal and noise energy.

\subsection*{Data availability}
All broadband seismic waveforms are retrieved from IRIS-DMC (Incorporated Research Institutions for Seismology, Data Management Center) (http://ds.iris.edu/ds/nodes/dmc/). Results obtained in this study are available upon requested from the corresponding author.

\new{\subsection*{Code availability}
The codes of 3D seismic reconstruction are available from the corresponding author upon reasonable request.}

\bibliography{us}
%\bibliographystyle{naturemag-doi}
\bibliographystyle{seg}

%\noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu. Use the cite command for an inline citation, e.g.  \cite{Figueredo:2009dg}.

\section*{Acknowledgements}
The earthquake data used in this study is requested from Incorporated Research Institutions for Seismology (IRIS). The authors are grateful to \wen{Jinwei Fang,} Wei Chen, Shaohuan Zu, Mi Zhang, Yatong Zhou, and Sergey Fomel for insightful discussions. The research is partially supported by the “Thousand Youth Talents Plan”, and the Starting Funds from Zhejiang University.

\section*{Author contributions}
Y.C. designed the project.
Y.C. and M.B. processed the field data. Y.C. and Y.C. analyzed the results.
Y.C., M.B., and Y.C. wrote the manuscript. All authors reviewed the manuscript.

\section*{\old{Additional information}\new{Competing Interests Statement}}
The authors declare no competing \old{financial }interests.

%\end{document}

### 2020-12-17 usarray/matfun/Syn.m

@@ -67,10 +67,9 @@ r1=0.5;r2=0.5;r3=0.5;
 d1=win3d_mask(@localfxymssa_recon, dm, param, d0, n1win, n2win, n3win, r1, r2, r3);
 
 %% global RR
-flow=0;fhigh=100;dt=0.004;N=9;Niter=10;mode=1;verb=1;
+flow=0;fhigh=100;dt=0.004;N=9;mode=1;verb=1;
 a=(Niter-(1:Niter))/(Niter-1); %linearly decreasing
 d2=fxymssa_recon(d0,dm,flow,fhigh,dt,N,Niter,eps,verb,mode,a);
-
 yc_snr(d,d1,2)	%21.0808
 yc_snr(d,d2,2)	%17.1526
 

### 2020-12-17 usarray/matfun/Syn_ratios.m

@@ -42,6 +42,7 @@ snrs0=zeros(nr,1);
 snrs1=zeros(nr,1);
 snrs2=zeros(nr,1);
 
+[nt,nx,ny]=size(d);
 for ir=1:nr;
 ratio=ratios(ir);
 mask=yc_genmask(reshape(d,nt,nx*ny),ratio,'c',2014151617);
@@ -70,12 +71,8 @@ n1win=50;n2win=50;n3win=50;
 r1=0.5;r2=0.5;r3=0.5;
 %% Main program goes here !
 D1_win=win3d_mask(@localfxymssa_recon, mask, param, d0, n1win, n2win, n3win, r1, r2, r3);
-% D1_win=win3d_mask(@localfxydmssa_recon, mask, param, dn, n1win, n2win, n3win, r1, r2, r3);
-figure;imagesc([d(:,:,9),d0(:,:,9),D1_win(:,:,9),d(:,:,9)-D1_win(:,:,9)]);
 yc_snr(d,D1_win,2)
 
-snrs0(ir)=yc_snr(d(40:100,:,:),d0(40:100,:,:),2);
-snrs1(ir)=yc_snr(d(40:100,:,:),D1_win(40:100,:,:),2);
 
 % 
 %% global processing
@@ -83,69 +80,14 @@ flow=0;fhigh=12.5;dt=0.04;N=30;Niter=10;mode=1;verb=0;
 N=10;
 a=(Niter-(1:Niter))/(Niter-1); %linearly decreasing
 D1=fxymssa_recon(d0,mask,flow,fhigh,dt,N,Niter,eps,verb,mode,a);
-figure;imagesc([d(:,:,9),d0(:,:,9),D1(:,:,9),d(:,:,9)-D1(:,:,9)]);
 yc_snr(d,D1,2)
 
+%% think about why?
+snrs0(ir)=yc_snr(d(40:100,:,:),d0(40:100,:,:),2);
+snrs1(ir)=yc_snr(d(40:100,:,:),D1_win(40:100,:,:),2);
 snrs2(ir)=yc_snr(d(40:100,:,:),D1(40:100,:,:),2);
 
 fprintf('Ratio=%g is done, snr0=%g,snr1=%g,snr2=%g\n',ratios(ir),snrs0(ir),snrs1(ir),snrs2(ir));
-
-% 
-% NN=3;
[…]

### 2020-12-17 usarray/paper.tex
2020年12月16日 星期三 18时50分14秒 CST

@@
 One excellent example is USAarry, the seismology component of the national Earth science program EarthScope, that \dlo{had been migrating}\wen{migrated} continuously across the North American continent (year 2004-2013\wen{; now deployed in Alaska and northwestern Canada}), providing a dense sampling of the seismic wavefield beneath its footprint.
-The availability of a large amount \wen{of} high-quality \dlo{array }data offers unique opportunities for \dlo{conducting }high-resolution seismic imaging, which leads to \wen{a} \dlo{much improved}\wen{much-improved} understanding of \wen{the} Earth's structure at various scales \cite{van2005surface,moschetti2007surface,yang2008structure,lin2009eikonal,yuan2010lithospheric,sigloch2011mantle,porritt2014seismic,schaeffer2014imaging,schmandt2014p,bao2016imaging,burdick2017model}.
-The relatively even-spaced sensors, with an average spacing of $ \sim $70 km, form an ideal network configuration for \dlo{applying the} \wen{the application of} array-based \dlo{method}\wen{methods} \cite{rost2002array,gu2010arrays}.
+The availability of a large amount \wen{of} high-quality \dlo{array }data offers unique opportunities for \dlo{conducting }high-resolution seismic imaging, which leads to \wen{a} \dlo{much improved}\wen{much-improved} understanding of \wen{the} Earth's structure at various scales \cite[]{van2005surface,moschetti2007surface,yang2008structure,lin2009eikonal,yuan2010lithospheric,sigloch2011mantle,porritt2014seismic,schaeffer2014imaging,schmandt2014p,bao2016imaging,burdick2017model}.
+The relatively even-spaced sensors, with an average spacing of $ \sim $70 km, form an ideal network configuration for \dlo{applying the} \wen{the application of} array-based \dlo{method}\wen{methods} \cite[]{rost2002array,gu2010arrays}.
 While the quantity of array data is continuously growing, \dlo{its quality is still limited}\wen{the improvement of data quality is hampered} by the presence of noise and a biased spatial sampling \dlo{resulting}\wen{that results} from \dlo{the }unevenly distributed earthquake sources and stations.
@@
 Most \dlo{resolution}\wen{data} improvement efforts have been focusing on increasing the data volume whereas generally less attention was paid to improve the quality of \dlo{the }existing \dlo{data}\wen{recordings}.
-The high-quality data with a regular spatial sampling can greatly benefit data analysis, processing and visualization, and also improve the numerical stability and accuracy for grid-based seismic imaging techniques (e.g., Eikonal \cite{lin2009eikonal} and Helmholtz tomography \cite{lin2011helmholtz}).
-As a result, \dlo{the }regularization approach\wen{es} that suppress\dlo{es} the noise and interpolate\dlo{s} the missing traces of array data \dlo{is}\wen{are} highly demanded \cite{mostafa2016geo,mostafa2016bssa,schneider2017improvement}.
+The high-quality data with a regular spatial sampling can greatly benefit data analysis, processing and visualization, and also improve the numerical stability and accuracy for grid-based seismic imaging techniques (e.g., Eikonal \cite[]{lin2009eikonal} and Helmholtz tomography \cite[]{lin2011helmholtz}).
+As a result, \dlo{the }regularization approach\wen{es} that suppress\dlo{es} the noise and interpolate\dlo{s} the missing traces of array data \dlo{is}\wen{are} highly demanded \cite[]{mostafa2016geo,mostafa2016bssa,schneider2017improvement}.
 
 \dlo{There are some}\wen{Some} effective methods for seismic data reconstruction \dlo{from}\wen{have been proposed in} the exploration seismology community.
-One type of the most widely used methods is based on \wen{a} sparse transform that maps the seismic signals to certain domains (e.g., Fourier \cite{abma2006}, curvelet \cite{yu2017mapping}, \wen{slant stacklet \cite{ventosa2015extraction}, }and seislet domains \cite{fomel2010seislet}), where the useful information can be sparsely represented and separated from the missing data and random noise.
-Another type of mainstream \wen{methods} is based on the Cadzow filtering or the Singular Spectrum Analysis (SSA) \cite{ssa}, which is a rank-reduction based method that transforms the data to frequency-wavenumber or frequency-space domains to extract the spatial coherency of the entire data set for reconstructing the missing information.
-Oropeza and Sacchi (2011) \cite{mssa} extended the SSA method to multi-channel version to tackle the 3-D seismic data reconstruction challenge and later on Kreimer et al.
-(2013) \cite{kreimer2013} formulated the high-dimensional reconstruction as a nuclear-norm constrained tensor completion problem in the frequency-space domain.
+One type of the most widely used methods is based on \wen{a} sparse transform that maps the seismic signals to certain domains (e.g., Fourier \cite[]{abma2006}, curvelet \cite[]{yu2017mapping}, \wen{slant stacklet \cite[]{ventosa2015extraction}, }and seislet domains \cite[]{fomel2010seislet}), where the useful information can be sparsely represented and separated from the missing data and random noise.
+Another type of mainstream \wen{methods} is based on the Cadzow filtering or the Singular Spectrum Analysis (SSA) \cite[]{ssa}, which is a rank-reduction based method that transforms the data to frequency-wavenumber or frequency-space domains to extract the spatial coherency of the entire data set for reconstructing the missing information.
+Oropeza and Sacchi (2011) \cite[]{mssa} extended the SSA method to multi-channel version to tackle the 3-D seismic data reconstruction challenge and later on Kreimer et al.
+(2013) \cite[]{kreimer2013} formulated the high-dimensional reconstruction as a nuclear-norm constrained tensor completion problem in the frequency-space domain.
 More recently, Chen et al.
-(2016) \cite{yangkang2016irr5d} improved the traditional truncated singular value decomposition (TSVD) method by deriving a new rank-reduction formula\dlo{, which}\wen{ that} better decomposes the data space into signal and noise subspaces.
+(2016) \cite[]{yangkang2016irr5d} improved the traditional truncated singular value decomposition (TSVD) method by deriving a new rank-reduction formula\dlo{, which}\wen{ that} better decomposes the data space into signal and noise subspaces.
 All aforementioned reconstruction methods are commonly applied to seismic data from exploration-scale surveys, while their applications to earthquake data, especially the multidimensional data recorded by large-scale seismic \dlo{array}\wen{arrays}, have been seldom reported.
@@
 In global seismology community, several methods have been proposed to interpolate the irregularly sampled seismic data.
-Most earlier studies have been concentrating on interpolating the receiver functions \cite{langston1977effect} that consist of P to S converted waves based on a certain form of spatial smoothing \dlo{such as}\wen{, including, for example,} weighted stacking with either linear \cite{chengping2015}, gaussian \cite{neal1999imaging, song2017moho} or cubic spline functions \cite{sheldrake2002regional, zhang2014receiver}.
-Also implemented are methods based on high-resolution Radon transform \cite{wilson2007teleseismic}, \dlo{sigular}\wen{singular} spectrum analysis \cite{gu2015sharp, dokht2016singular} and, more recently, non-linear waveform stretching-and-squeezing \cite{hu2018wavefield}.
+Most earlier studies have been concentrating on interpolating the receiver functions \cite[]{langston1977effect} that consist of P to S converted waves based on a certain form of spatial smoothing \dlo{such as}\wen{, including, for example,} weighted stacking with either linear \cite[]{chengping2015}, gaussian \cite[]{neal1999imaging, song2017moho} or cubic spline functions \cite[]{sheldrake2002regional, zhang2014receiver}.
+Also implemented are methods based on high-resolution Radon transform \cite[]{wilson2007teleseismic}, \dlo{sigular}\wen{singular} spectrum analysis \cite[]{gu2015sharp, dokht2016singular} and, more recently, non-linear waveform stretching-and-squeezing \cite[]{hu2018wavefield}.
 Aside from interpolating the receiver functions, Schneider et al.
-(2017) \cite{schneider2017improvement} reconstruct\wen{ed} the weak-amplitude under-side reflections from the mantle transition zone (i.e., PP precursors) while utilizing a compressive sensing based approach that seeks the sparsity of dominating \dlo{energies}\wen{energy} in the frequency-wavenumber domain.
-A recent study also \dlo{applies}\wen{applied} the idea of compressive sensing to reconstruct the synthetic surface wavefields via a sparse representation using a plane wave basis \cite{zhan2018application}.
+(2017) \cite[]{schneider2017improvement} reconstruct\wen{ed} the weak-amplitude under-side reflections from the mantle transition zone (i.e., PP precursors) while utilizing a compressive sensing based approach that seeks the sparsity of dominating \dlo{energies}\wen{energy} in the frequency-wavenumber domain.
+A recent study also \dlo{applies}\wen{applied} the idea of compressive sensing to reconstruct the synthetic surface wavefields via a sparse representation using a plane wave basis \cite[]{zhan2018application}.
 These earlier studies represent \dlo{continuous}\wen{continuing} efforts of the global seismology community in improving the earthquake data towards a regularly sampled wavefield\dlo{, yet}\wen{.
@@
 We first conduct a synthetic test to demonstrate the performance of the proposed methodology.
-The model is designed to honor  the complex Moho structure in central US \cite{schmandt2015distinct} that is characterized by \dlo{a large depth variation}\wen{large depth variations} by as much as 20 km (Figure \ref{fig:syn}).
-The elastic properties (velocity and density) of the crust and upper mantle are obtained from the average values of AK135 continental model\cite{kennett1995constraints} (Figures 1a-1c).
+The model is designed to honor  the complex Moho structure in central US \cite[]{schmandt2015distinct} that is characterized by \dlo{a large depth variation}\wen{large depth variations} by as much as 20 km (Figure \ref{fig:syn-us-vp,syn-us-vs,syn-us-rho,obs}).
+The elastic properties (velocity and density) of the crust and upper mantle are obtained from the average values of AK135 continental model\cite[]{kennett1995constraints} (Figures 1a-1c).
 We synthesize the recorded wavefield by solving the 3D elastic wave equation based on a finite-difference method\dlo{ with a GPU implementation}\old{ (see Supplementary material for mathematical detail)}.
@@
 
-The 3D seismic data consists of 200 time samples with a sampling rate of 0.5 sec and 100 equally spaced spatial samples in both longitudinal \new{(X) and  latitudinal (Y)} directions (Figure \ref{fig:syn-clean}).
-The simulated wavefield shows clear P and Moho converted phases (Ps) (Figure \ref{fig:syn-clean}).
-To mimic the realistic signal-to-noise ratio (SNR), we add real noise that \dlo{proceeds}\wen{precedes} the first arrivals (i.e., P waves) from the USArray data to the synthetics (Figure \ref{fig:syn-noisy}).
-The missing traces are generated by applying the sampling matrix (Figure \ref{fig:syn-mask}) to the noisy data.
-The final simulated data contains 30\% missing traces (Figure \ref{fig:syn-obs}).
+The 3D seismic data consists of 200 time samples with a sampling rate of 0.5 sec and 100 equally spaced spatial samples in both longitudinal \new{(X) and  latitudinal (Y)} directions (Figure \ref{fig:syn-us-clean}).
+The simulated wavefield shows clear P and Moho converted phases (Ps) (Figure \ref{fig:syn-us-clean}).
+To mimic the realistic signal-to-noise ratio (SNR), we add real noise that \dlo{proceeds}\wen{precedes} the first arrivals (i.e., P waves) from the USArray data to the synthetics (Figure \ref{fig:syn-us-noisy}).
+The missing traces are generated by applying the sampling matrix (Figure \ref{fig:syn-us-mask}) to the noisy data.
+The final simulated data contains 30\% missing traces (Figure \ref{fig:syn-us-obs}).
 To quantitatively evaluate the data quality, we use a SNR criterion defined as follows: $\text{SNR}=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2^2}{\Arrowvert \mathbf{s} -\hat{\mathbf{s}}\Arrowvert_2^2}$, where $\mathbf{s}$ denotes the exact solution (i.e., the clean data), and $\hat{\mathbf{s}}$ is the noise contaminated or incomplete data.
@@
 It is also clear that the amplitude of the second event decreases from about 1.5 at the four corners to about 0.6 in the center.
-Figures \ref{fig:syn-rr} and \ref{fig:syn-rr-e} show the reconstructed data and its corresponding reconstruction error using the global rank-reduction method.
-Figures \ref{fig:syn-lrr} and \ref{fig:syn-lrr-e} plot the reconstructed data using the localized rank-reduction method and its corresponding reconstruction error.
-The global rank-reduction method assumes that the seismic data are composed of several plane waves, \dlo{while}\wen{however,} this assumption is often violated due to the presence of  non-planar wavefield\wen{s} in realistic models (see Figure \ref{fig:syn}).
+Figures \ref{fig:syn-us-rr} and \ref{fig:syn-us-rr-e} show the reconstructed data and its corresponding reconstruction error using the global rank-reduction method.
+Figures \ref{fig:syn-us-lrr} and \ref{fig:syn-us-lrr-e} plot the reconstructed data using the localized rank-reduction method and its corresponding reconstruction error.
+The global rank-reduction method assumes that the seismic data are composed of several plane waves, \dlo{while}\wen{however,} this assumption is often violated due to the presence of  non-planar wavefield\wen{s} in realistic models (see Figure \ref{fig:syn-us-vp,syn-us-vs,syn-us-rho,obs}).
 Thus, we improve the global rank-reduction \dlo{based MSSA}\wen{method} using a localized scheme.
 This method divides the data cube into several smaller volumes to minimize the curvature of seismic waves, which essentially imposes a local plane-wave constraint to alleviate the non-planar effect\wen{s}.
-More sophisticated methods based on non-plane-wave assumption\wen{s} (e.g.,  non-stationary principal component analysis \cite{zhao2016principal}) may offer better solutions to the curved wavefronts.
+More sophisticated methods based on non-plane-wave assumption\wen{s} (e.g.,  non-stationary principal component analysis \cite[]{zhao2016principal}) may offer better solutions to the curved wavefronts.
 To implement the localized rank-reduction method, we apply a 3D moving window with \wen{a} size of $50\times 50\times 50$ to the data volume.
 We \dlo{also }\dlo{allows}\wen{allow} \dlo{an}\wen{a} 25-points \wen{(i.e., 50\%)} overlap in each direction between successive windows to suppress the edge effects.
-For each subset of the data volume within the moving window, we use a \wen{reference} rank of three to \dlo{synthesize}\wen{compute} the trajectory matrix \wen{(see Methods)}, \dlo{whereas the rank used in the global rank-reduction method is nine.}\wen{whereas a reference value of nine is adopted in global rank-reduction method.}  In the global case, the two plane waves are well reconstructed (Figure \ref{fig:syn-rr}), but the curved wavefront exhibits significant reconstruction errors, particularly in \dlo{the }areas with large curvatures (Figure \ref{fig:syn-rr-e}).
-\dlo{On the other hand}\wen{In comparison}, the localized rank-reduction method does not cause obvious damages to the signal (Figure \ref{fig:syn-lrr}) and the reconstruction error is almost zero everywhere (Figure \ref{fig:syn-lrr-e}).
+For each subset of the data volume within the moving window, we use a \wen{reference} rank of three to \dlo{synthesize}\wen{compute} the trajectory matrix \wen{(see Methods)}, \dlo{whereas the rank used in the global rank-reduction method is nine.}\wen{whereas a reference value of nine is adopted in global rank-reduction method.}  In the global case, the two plane waves are well reconstructed (Figure \ref{fig:syn-us-rr}), but the curved wavefront exhibits significant reconstruction errors, particularly in \dlo{the }areas with large curvatures (Figure \ref{fig:syn-us-rr-e}).
+\dlo{On the other hand}\wen{In comparison}, the localized rank-reduction method does not cause obvious damages to the signal (Figure \ref{fig:syn-us-lrr}) and the reconstruction error is almost zero everywhere (Figure \ref{fig:syn-us-lrr-e}).
 Based on SNR metric, the respective quality \dlo{factors}\wen{metrics} for the global and localized reconstructions are \dlo{7.51 dB and 14.38 dB}\wen{17.34 dB and 21.53 dB}, suggesting a better performance of \dlo{localized reconstruction than the global algorithm}\wen{the latter approach}.
-We extract a single trace at \dlo{the}\wen{a} location where large curvature exists (Figure \ref{fig:syn-trace}).
-\dlo{It is clear that the}\wen{The} reconstructed trace using localized rank-reduction method (green) almost fully recovers the input (black; Figure \ref{fig:syn-ss-z}), whereas an obvious time shift is present in the trace obtained from the global method (blue; see Figure \ref{fig:syn-ss-z}).
+We extract a single trace at \dlo{the}\wen{a} location where large curvature exists (Figure \ref{fig:syn-us-ss-0,syn-us-ss-z}).
+\dlo{It is clear that the}\wen{The} reconstructed trace using localized rank-reduction method (green) almost fully recovers the input (black; Figure \ref{fig:syn-us-ss-z}), whereas an obvious time shift is present in the trace obtained from the global method (blue; see Figure \ref{fig:syn-us-ss-z}).
 
-We also use local similarity \cite{fomel2007localattr}, which measures the similarity between two signals in a local sense, to evaluate the reconstruction performance.
+We also use local similarity \cite[]{fomel2007localattr}, which measures the similarity between two signals in a local sense, to evaluate the reconstruction performance.
 A mathematical introduction of the local similarity metric is provided in the Supplementary \old{material}\new{Note 2}.
 In our case, we intend to obtain a reconstruction result that is as close to the clean data as possible.
-The local similarity between the clean and the reconstructed data using the global rank-reduction method shows obvious low values along the curved wavefront (Figure \ref{fig:syn-rr-simi}).
-\dlo{The}\wen{In comparison, the} local similarity of localized reconstruction is high throughout the data volume regardless of the shape of the wavefront (Figure \ref{fig:syn-lrr-simi}).
+The local similarity between the clean and the reconstructed data using the global rank-reduction method shows obvious low values along the curved wavefront (Figure \ref{fig:syn-us-rr-simi}).
+\dlo{The}\wen{In comparison, the} local similarity of localized reconstruction is high throughout the data volume regardless of the shape of the wavefront (Figure \ref{fig:syn-us-lrr-simi}).
 We \dlo{also}\wen{further} investigate the effects of sampling ratios (i.e., the percentage of missing data) on the reconstruction.
@@
 
-%\begin{figure*}[ht!]
-%	\centering
-%	\subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-vp}
-%    \label{fig:syn-jw-vp}}
-%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-vs}
-%    \label{fig:syn-jw-vs}}
-%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-rho}
-%    \label{fig:syn-jw-rho}}\\
-%    \subfigure[]{\includegraphics[width=0.6\textwidth]{Fig/observation}
-%    \label{fig:obs}}
-%	\caption{Wavefield simulation of plane-wave incidence beneath a regional array.
-The synthetic model is constructed using real Moho constraints\cite{schmandt2015distinct} and\dlo{ and} elastic parameters of (a) P-wave velocities, (b) S-wave velocities and (c) densities from a 1D reference model\cite{kennett1995constraints}.
+\multiplot{4}{syn-us-vp,syn-us-vs,syn-us-rho,obs}{width=0.4\textwidth}{Wavefield simulation of plane-wave incidence beneath a regional array.
+The synthetic model is constructed using real Moho constraints and\dlo{ and} elastic parameters of (a) P-wave velocities, (b) S-wave velocities and (c) densities from a 1D reference model.
 The blue lines mark the location of horizontal and vertical slices, where the values of model parameters are demonstrated and projected onto the corresponding sides of the model cube.
@@
 }
-%	\label{fig:syn}
+
+\inputdir{syn}
+\multiplot{4}{syn-us-clean,syn-us-noisy,syn-us-mask,syn-us-obs}{width=0.4\textwidth}{The \dlo{input synthetic}\wen{synthesized} data.
+(a) The clean data \dlo{containing two main seismic phases.
+The colors at zero time slice indicate the relative time perturbations of the second phase arrivals.
+The cross-hair marks the location of the sample trace shown in Figure 6.}\wen{obtained from elastic wave simulation.} (b) The noisy data with \old{SNR=}\new{signal-to-noise ratio equals to} 10.12 dB.
+(c) The sampling matrix with a sampling ratio of \dlo{80}\wen{70}\% (d) The final data after applying the sampling matrix to noisy data in (b).
+The SNR of the \wen{input} data is \dlo{4.64}\wen{4.35} dB.}
+
+\multiplot{4}{syn-us-rr,syn-us-lrr,syn-us-rr-e,syn-us-lrr-e}{width=0.4\textwidth}{Synthetic test results.
+(a) Reconstructed data using the global rank-reduction method.
+The \old{SNR}\new{signal-to-noise ratio} of the reconstructed data is 17.34 dB.
+(b) Reconstructed data using the localized rank-reduction method (\old{SNR=}\new{signal-to-noise ratio is }21.53 dB).
+(c) and (d) Reconstruction errors corresponding to (a) and (b).}
+
+\multiplot{2}{syn-us-ss-0,syn-us-ss-z}{width=0.4\textwidth}{Comparison of the single trace amplitude (X=225,Y=225) in \new{different scales.}\old{ (a) original and (b) zoomed-in scales .} \new{(a) Comparison in the original scale.
+(b) Comparison in the zoomed-in scale.} The black and pink lines represent \dlo{the }clean and noisy data, respectively.
+The trace processed using global and localized rank-reduction methods are shown by the blue and green lines, respectively.
+The black line (localized reconstruction) is almost completely overlapped with the green line (true solution), indicating that the error of reconstruction is \dlo{very small}\wen{minimal} for the proposed approach.}
+
+\multiplot{2}{syn-us-rr-simi,syn-us-lrr-simi}{width=0.4\textwidth}{\old{Reconstruction performance comparison between (a) global and (b) localized rank-reduction methods using local similarity matrix.}\new{A comparison of reconstruction performance in terms of local similarity metric.
+(a) Local similarity using the global rank-reduction method.
+(b) Local similarity using the localized rank-reduction method.} Note that local similarity around curved wavefronts is noticeably lower in the global reconstruction results.}
+
+\plot{snr-n}{width=\textwidth}{Reconstruction results at different sampling ratios.
+The reconstruction performance (SNR) improves with the increasing sampling ratio.
+The localized rank-reduction method always outperforms the global algorithm.}
+\inputdir{./}
+
+%\begin{figure*}[ht!]
+%	\centering
+%	\subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-vp}
+%    \label{fig:syn-us-vp}}
+%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-vs}
+%    \label{fig:syn-us-vs}}
+%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-rho}
+%    \label{fig:syn-us-rho}}\\
+%    \subfigure[]{\includegraphics[width=0.6\textwidth]{Fig/obs}
+%    \label{fig:obs}}
+%	\caption{Wavefield simulation of plane-wave incidence beneath a regional array.
+The synthetic model is constructed using real Moho constraints\cite[]{schmandt2015distinct} and\dlo{ and} elastic parameters of (a) P-wave velocities, (b) S-wave velocities and (c) densities from a 1D reference model\cite[]{kennett1995constraints}.
+The blue lines mark the location of horizontal and vertical slices, where the values of model parameters are demonstrated and projected onto the corresponding sides of the model cube.
+(d) Observation system demonstrating the positions of planar source and receivers.
+The stars at the surface denote the evenly distributed receivers and symbols on the dipping plane denote the injected source positions.
+}
+%	\label{fig:syn-us-vp,syn-us-vs,syn-us-rho,obs}
 %\end{figure*}
@@
 %	\centering
-%	\subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-clean}
-%    \label{fig:syn-clean}}
-%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-noisy}
-%    \label{fig:syn-noisy}}
-%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-mask}
-%    \label{fig:syn-mask}}
-%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-obs}
-%    \label{fig:syn-obs}}
+%	\subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-clean}
+%    \label{fig:syn-us-clean}}
+%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-noisy}
+%    \label{fig:syn-us-noisy}}
+%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-mask}
+%    \label{fig:syn-us-mask}}
+%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-obs}
+%    \label{fig:syn-us-obs}}
 %	\caption{The \dlo{input synthetic}\wen{synthesized} data.
@@
 The SNR of the \wen{input} data is \dlo{4.64}\wen{4.35} dB.}
-%	\label{fig:syns}
+%	\label{fig:syn-clean,syn-noisy,syn-mask,syn-obs}
 %\end{figure*}
@@
 %	\centering
-%	\subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-rr}
-%    \label{fig:syn-rr}}
-%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-lrr}
-%    \label{fig:syn-lrr}}
-%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-rr-e}
-%    \label{fig:syn-rr-e}}
-%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-lrr-e}
-%    \label{fig:syn-lrr-e}}
+%	\subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-rr}
+%    \label{fig:syn-us-rr}}
+%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-lrr}
+%    \label{fig:syn-us-lrr}}
+%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-rr-e}
+%    \label{fig:syn-us-rr-e}}
+%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-lrr-e}
+%    \label{fig:syn-us-lrr-e}}
 %	\caption{Synthetic test results.
@@
 }
-%	\label{fig:syns-rn}
+%	\label{fig:syn-rr,syn-lrr,syn-rr-e,syn-lrr-e}
 %\end{figure*}
@@
 %	\centering
-%	\subfigure[]{\includegraphics[width=0.4\textwidth]{Fig/syn-jw-ss-0}
-%    \label{fig:syn-ss-0}}
-%    \subfigure[]{\includegraphics[width=0.4\textwidth]{Fig/syn-jw-ss-z}
-%    \label{fig:syn-ss-z}}
+%	\subfigure[]{\includegraphics[width=0.4\textwidth]{Fig/syn-us-ss-0}
+%    \label{fig:syn-us-ss-0}}
+%    \subfigure[]{\includegraphics[width=0.4\textwidth]{Fig/syn-us-ss-z}
+%    \label{fig:syn-us-ss-z}}
 %	\caption{Comparison of the single trace amplitude (X=225,Y=225) in \new{different scales.}\old{ (a) original and (b) zoomed-in scales .} \new{(a) Comparison in the original scale.
@@
 The black line (localized reconstruction) is almost completely overlapped with the green line (true solution), indicating that the error of reconstruction is \dlo{very small}\wen{minimal} for the proposed approach.}
-%	\label{fig:syn-trace}
+%	\label{fig:syn-us-ss-0,syn-us-ss-z}
 %\end{figure*}
@@
 %	\centering
-%	\subfigure[]{\includegraphics[width=0.25\textwidth]{Fig/syn-jw-rr-simi}
-%    \label{fig:syn-rr-simi}}
-%    \subfigure[]{\includegraphics[width=0.25\textwidth]{Fig/syn-jw-lrr-simi}
-%    \label{fig:syn-lrr-simi}}
+%	\subfigure[]{\includegraphics[width=0.25\textwidth]{Fig/syn-us-rr-simi}
+%    \label{fig:syn-us-rr-simi}}
+%    \subfigure[]{\includegraphics[width=0.25\textwidth]{Fig/syn-us-lrr-simi}
+%    \label{fig:syn-us-lrr-simi}}
 %	\caption{\old{Reconstruction performance comparison between (a) global and (b) localized rank-reduction methods using local similarity matrix.}\new{A comparison of reconstruction performance in terms of local similarity metric.
@@
 %	\centering
-%	\includegraphics[width=0.4\textwidth]{Fig/snr-jw-n}
+%	\includegraphics[width=0.4\textwidth]{Fig/snr-n}
 %	\caption{Reconstruction results at different sampling ratios.
@@
 Despite the best effort in acquisition design, earthquake data is rarely recorded on a perfectly even-spaced seismic array.
-Similar to earlier  interpolation methods \cite{neal1999imaging,dokht2016singular,schneider2017improvement}, the first step of our reconstruction algorithm is to bin the data onto a regular grid.
+Similar to earlier  interpolation methods \cite[]{neal1999imaging,dokht2016singular,schneider2017improvement}, the first step of our reconstruction algorithm is to bin the data onto a regular grid.
 To this end, we use a weighted interpolation method for the binning process.
@@
 }(e)The reconstruction uncertainty for the longitudinal slice.}
-%	\label{fig:lons}
+%	\label{fig:us_lon1,us_lon2,us_lon1_z,us_lon2_z,us_uncert}
 %\end{figure*}
@@
 The reconstructed time slice successfully fills the data gap and captures the detailed variation in wavefield energy.
-We demonstrate the reconstruction performance on full seismogram in Figure \ref{fig:lons}, where nine traces are missing in this longitude slice.
+We demonstrate the reconstruction performance on full seismogram in Figure \ref{fig:us_lon1,us_lon2,us_lon1_z,us_lon2_z,us_uncert}, where nine traces are missing in this longitude slice.
 The quality of various phase arrivals \dlo{are}\wen{is} severely degraded by noise.
@@
 
-We conduct a bootstrapping test\cite{bootstrap1991} to estimate the effect of spatial sampling of wavefield on reconstruction.
+We conduct a bootstrapping test\cite[]{bootstrap1991} to estimate the effect of spatial sampling of wavefield on reconstruction.
 We randomly select 40\% of the observed seismograms to reconstruct the 3D data cube and repeat this step 20 times.
@@
 To alleviate these effects, a frequency-dependent, instead of a linear, time window may be required to better isolate the surface wave energy.
-For example, one may consider a Gaussian window with varying center frequencies as widely adopted in dispersion analysis \cite{dziewonski1969technique}.
+For example, one may consider a Gaussian window with varying center frequencies as widely adopted in dispersion analysis \cite[]{dziewonski1969technique}.
 As importantly, a more careful examination (and selection) of surface wave related rank values is also essential to better capture the surface wave energy.
@@
 The synthetic and real data examples demonstrate the ability of localized rank-reduction method in reconstructing the missing traces.
-The complete dataset, with improved quality and spatial sampling, is critical for improving array-based seismic imaging methods \cite{rost2002array, gu2010arrays}.
+The complete dataset, with improved quality and spatial sampling, is critical for improving array-based seismic imaging methods \cite[]{rost2002array, gu2010arrays}.
 In this section, we demonstrate the accuracy of our method and its  application in seismic imaging using the cross-correlation travel time measurement, a widely used technique in travel time tomography.
@@
 Seismic tomography is one of the most commonly applied seismic imaging techniques that greatly \dlo{improves}\wen{improve} the understanding of the internal structure of Earth.
-Seismic tomography can be broadly classified based on the types of data (travel time or waveform) and the approximation of wave propagation theory (ray or finite frequency) \cite{liu2012seismic}.
-One classical method of \wen{the} tomographic family is regional travel time tomography \cite{aki1977determination} that utilizes the travel time difference between nearby stations to resolve the subsurface velocity structure.
+Seismic tomography can be broadly classified based on the types of data (travel time or waveform) and the approximation of wave propagation theory (ray or finite frequency) \cite[]{liu2012seismic}.
+One classical method of \wen{the} tomographic family is regional travel time tomography \cite[]{aki1977determination} that utilizes the travel time difference between nearby stations to resolve the subsurface velocity structure.
 The density of the station and \wen{the} accuracy of travel time measurements are critical factors for high-resolution imaging.
@@
 
-The relative travel times between stations in a recording array are measured using multi-channel cross-correlation \cite{vandecar1990determination}.
+The relative travel times between stations in a recording array are measured using multi-channel cross-correlation \cite[]{vandecar1990determination}.
 For a pair of stations, the\dlo{ir} optimal relative travel time is determined by the time delay that leads to the maximum correlation coefficient between the two traces containing the phase of interest (e.g., P wave).
@@
 The travel time measurement is first performed on the original data.
-We filter the seismic traces between 0.03 and 0.125 Hz to enhance the useful signal and utilize a 100 sec \dlo{time}\wen{cross-correlation} window starting 50 sec prior to the \dlo{predicated}\wen{predicted} P-wave arrival time based on AK135 model \cite{kennett1995constraints}.
+We filter the seismic traces between 0.03 and 0.125 Hz to enhance the useful signal and utilize a 100 sec \dlo{time}\wen{cross-correlation} window starting 50 sec prior to the \dlo{predicated}\wen{predicted} P-wave arrival time based on AK135 model \cite[]{kennett1995constraints}.
 The resulting travel time pattern is similar to the predictions (i.e., theoretical arrival times from AK135) because the time perturbations induced by structural variation is much smaller than the move-out (Supplementary Figure \color{blue}{13}\color{black}{}).
@@
 
-Seismic travel time is sensitive to velocity anomalies within the Fresnel zone around the ray path \cite{dahlen2000frechet}, thus the consistency of the travel time pattern with the velocity structures can be used as an effective metric to evaluate the robustness of the travel time measurements.
+Seismic travel time is sensitive to velocity anomalies within the Fresnel zone around the ray path \cite[]{dahlen2000frechet}, thus the consistency of the travel time pattern with the velocity structures can be used as an effective metric to evaluate the robustness of the travel time measurements.
 For a plane wave from a teleseismic source, it illuminates the upper mantle portion of the Earth structure beneath the recording array from the direction of back-azimuth  at a steep incidence angle.
@@
 The availability of high-resolution seismic velocity models in \wen{the} western US enables a detailed examination of the travel time accuracy.
-We utilize a recent \wen{high-resolution} tomographic model of the upper mantle of continental US \cite{schmandt2014p}, which is constructed using 516,668 P-wave travel time residuals measured within multi-frequency bands in combination with a finite-frequency kernel \cite{dahlen2000frechet}.
+We utilize a recent \wen{high-resolution} tomographic model of the upper mantle of continental US \cite[]{schmandt2014p}, which is constructed using 516,668 P-wave travel time residuals measured within multi-frequency bands in combination with a finite-frequency kernel \cite[]{dahlen2000frechet}.
 \dlo{Besides}\wen{In addition to} the high model resolution, the choice of this model is prompted by the same travel time type (i.e., relative residuals) that permits a direct comparison with our measurements.
@@
 Most of these nodes are located in the regions with the largest data gap or near the edges of the data volume (e.g., SW corner).
-These anomalously large measurements are typically caused by cycle-skipping or poor data quality\dlo{ hence}\wen{, and thus} are removed from the inversion process in regional tomographic study \cite{chen2017finite}.
+These anomalously large measurements are typically caused by cycle-skipping or poor data quality\dlo{ hence}\wen{, and thus} are removed from the inversion process in regional tomographic study \cite[]{chen2017finite}.
 After removing the outliers, which accounts for 4.5\% of the total measurements, the \dlo{overall}\wen{average} uncertainty decreases to 0.35 sec and is significantly smaller than that \dlo{from}\wen{of} the original data, suggesting \dlo{the improvement in}\wen{an improved} \dlo{phase}\wen{P-wave} consistency in the reconstructed data.
@@
 Thanks to the rapid development of dense seismic \wen{arrays} around the \dlo{global}\wen{globe}, new seismic imaging techniques have been focusing on simultaneous processing of recordings from nearby sensors on a uniform/semi-uniform grid.
-One of the rapidly advancing fields is seismic surface tomography that utilizes either the travel time \cite{lin2009eikonal, jin2015surface} or the shape of the wavefield \cite{lin2011helmholtz, langston2007wave} recorded at \dlo{the }dense arrays to infer the elastic properties of the subsurface.
-These methods typically require the calculation of spatial derivatives with \dlo{respective}\wen{respect} to a certain parameter such as \dlo{traveltime}\wen{the travel time} (e.g., Eikonal tomography \cite{lin2009eikonal}) or amplitude of \wen{the} surface wave (e.g., Helmholtz tomography \cite{lin2011helmholtz} and gradiometry \cite{langston2007wave}), which is best performed on a regular grid to ensure the numerical stability and accuracy.
+One of the rapidly advancing fields is seismic surface tomography that utilizes either the travel time \cite[]{lin2009eikonal, jin2015surface} or the shape of the wavefield \cite[]{lin2011helmholtz, langston2007wave} recorded at \dlo{the }dense arrays to infer the elastic properties of the subsurface.
+These methods typically require the calculation of spatial derivatives with \dlo{respective}\wen{respect} to a certain parameter such as \dlo{traveltime}\wen{the travel time} (e.g., Eikonal tomography \cite[]{lin2009eikonal}) or amplitude of \wen{the} surface wave (e.g., Helmholtz tomography \cite[]{lin2011helmholtz} and gradiometry \cite[]{langston2007wave}), which is best performed on a regular grid to ensure the numerical stability and accuracy.
 The compressive-sensing based reconstruction approach proposed by Zhan et al.
-(2018) \cite{zhan2018application} has demonstrated the improvement in \dlo{velocity estimates}\wen{resolving velocities} using the reconstructed wavefields.
+(2018) \cite[]{zhan2018application} has demonstrated the improvement in \dlo{velocity estimates}\wen{resolving velocities} using the reconstructed wavefields.
 Similarly, we \dlo{except}\wen{expect} an improved imaging performance of these gradient-based tomographic approaches when applied to the reconstructed data.
 The validation of this argument is beyond the scope of this paper and will be investigated in future studies.
-Finally, the improvement in sensor technology as exemplified in several large N array experiments \cite{lin2013high,schmandt2013analysis,hansen2015automated,ward2018high} has permitted a higher-density sampling that is close to \wen{an} exploration-scale survey.
+Finally, the improvement in sensor technology as exemplified in several large N array experiments \cite[]{lin2013high,schmandt2013analysis,hansen2015automated,ward2018high} has permitted a higher-density sampling that is close to \wen{an} exploration-scale survey.
 The development of imaging technology, such as the \wen{one} proposed in our study, should work hand-in-hand with the improvement in data acquisition to achieve the ultimate goal of having a better understanding of the Earth's structure.
@@
 The brown lines indicate the boundaries of major tectonic domains in \wen{the} western US.
-(c) Average P-wave velocity perturbations between 50-250 km depths from \wen{Schmandt and Lin (2014)} \cite{schmandt2014p}.}
+(c) Average P-wave velocity perturbations between 50-250 km depths from \wen{Schmandt and Lin (2014)} \cite[]{schmandt2014p}.}
 %	\label{fig:ttres_vel}
@@
 
-\plot{ttres_vel}{width=0.7\textwidth}{\old{P-wave relative travel time residuals across the recording array measured from (a) the original and (b) the reconstructed data.}\new{A comparison of P-wave travel time measurements between the original and reconstructed data.
+\plot{ttres_vel}{width=\textwidth}{\new{A comparison of P-wave travel time measurements between the original and reconstructed data.
 (a) Relative travel time residuals across the recording array measured from the original data.
@@
 The brown lines indicate the boundaries of major tectonic domains in \wen{the} western US.
-(c) Average P-wave velocity perturbations between 50-250 km depths from \wen{Schmandt and Lin (2014)} \cite{schmandt2014p}.}
+(c) Average P-wave velocity perturbations between 50-250 km depths from \wen{Schmandt and Lin (2014)}.}
 
-\plot{raw_ssa_tt}{width=0.7\textwidth}{ \new{A comparison of travel time measurement uncertainties.}\old{Travel time measurement uncertainties of (a) the original and (b) the reconstructed data.}\new{ (a) Travel time plot of the original data.
+\plot{raw_ssa_tt}{width=\textwidth}{ \new{A comparison of travel time measurement uncertainties.}\old{Travel time measurement uncertainties of (a) the original and (b) the reconstructed data.}\new{ (a) Travel time plot of the original data.
 (b) Travel time plot of the reconstructed data.} Both measured and predicted travel times are demeaned to emphasize the perturbations.
@@
 Here, we follow the linear-decreasing strategy used in \wen{Chen et al.
-(2016)} \cite{yangkang2016irr5d} for iteratively suppressing the noise while restoring the noisy data with newly interpolated data.
+(2016)} \cite[]{yangkang2016irr5d} for iteratively suppressing the noise while restoring the noisy data with newly interpolated data.
 
-In the rank-reduction method \cite{mssa}, the filtering is conducted in the frequency-space domain of the multi-channel earthquake data.
+In the rank-reduction method \cite[]{mssa}, the filtering is conducted in the frequency-space domain of the multi-channel earthquake data.
 When rewriting $\mathbf{v}$ in a \dlo{matrix}\wen{tensor} form $V(x,y,t)$, the rank-reduction method first transforms the data from $t-x-y$ domain to $f-x-y$ domain, i.e., $V(x,y,f)$.
@@
 \subsection*{Automatic rank selection} In the rank-reduction filtering introduced above, the predefined rank parameter $K$ plays a significant role in \dlo{the }obtaining satisfactory performance.
-It has been documented that an appropriate selection of $K$ can be the number of seismic events that have distinct slownesses \cite{mssa}.
+It has been documented that an appropriate selection of $K$ can be the number of seismic events that have distinct slownesses \cite[]{mssa}.
 However, the real earthquake data is never a simple composition of several wave types with clear arrivals.
@@
 Use the cite command for an inline citation, e.g.
-\cite{Figueredo:2009dg}.
+\cite[]{Figueredo:2009dg}.
 

### 2020-12-18 ddsisft/paper.tex
2020年12月18日 星期五 10时39分09秒 CST

\published{IEEE Geoscience and Remote Sensing Letters, 13, 197-201, (2016)}

\title{Simultaneous source separation using iterative seislet-frame thresholding}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Shuwei Gan\footnotemark[1], Shoudong Wang\footnotemark[2], Yangkang Chen\footnotemark[3], and Xiaohong Chen\footnotemark[2]}
\address{
\footnotemark[1] State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
\footnotemark[2]Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
Email: ykchen@utexas.edu \\
}

\lefthead{GRSL - Gan et al.}
\righthead{Simultaneous source separation}

\maketitle

\begin{abstract}
The distance-separated simultaneous sourcing technique can make the smallest interference between different sources. In a distance-separated simultaneous-source acquisition with two sources, we propose the use of a novel iterative seislet-frame thresholding approach to separate the blended data. Because the separation is implemented in common shot gathers (CSGs), there is no need for the random scheduling that is used in conventional simultaneous-source acquisition, where random scheduling is applied to ensure the incoherent property of blending noise in common midpoint, common receiver, or common offset gathers. Thus, distance-separated simultaneous sourcing becomes more flexible. The separation is based on the assumption that the local dips of the data from different sources are different. We can use plane-wave destruction (PWD) algorithm to simultaneously estimate the conflicting dips and then use seislet frames with two corresponding local dips to sparsify each signal component. Then the different signal components can be easily separated. Compared with the FK-based approach, the proposed seislet frames based approach has the potential to obtain better separated components with less artifacts because the seislet frames are local transforms while the Fourier transform is a global transform. Both simulated synthetic and field data examples show very successful performance of the proposed approach.
\end{abstract}

\section{keywords}
Deblending, distance-separated simultaneous-source data, seislet transform, seislet frame, iterative inversion

\section{Introduction}
The principal purpose of simultaneous source acquisition is to speed up the acquisition of seismic data with a denser spatial sampling, which saves huge on acquisition cost and increases data quality. The benefits are compromised by the intense interference between different shots \cite{berkhout2008}. One way of solving the problem caused by interference is first by separating and second by processing strategy \cite{mahdad2011,yangkang20142,yangkang2014svmf,yangkang2015pnmo}, which is also called deblending. Another way is by direct imaging and inversion of the blended data by attenuating the interference during inversion \cite{verschuur2011,zhiguang2014,yangkang2015image,shuwei2015vel}. Currently, deblending is still the dominant way of dealing with simultaneous-source data.

%There are generally two types of deblending approaches that have been reported in the literature: (1) treating deblending as a noise attenuation approach \cite{mediandeblend,yangkang2014svmf,yangkang2015ortho}, (2) treating deblending as an inversion problem \cite{sep,abma2010,yangkang20142}.  For the filtering based approaches, most of the approaches are based on median filter. \cite{yangkang2014nmo} proposed to use common midpoint domain for deblending, because of the better coherency of useful signals and also because the near-offset useful events follow the hyperbolic assumption and thus can be flattened using normal moveout (NMO) correction. A simple median filtering (MF) can be applied to the NMO corrected common-midpoint (CMP) gathers to attenuate blending noise. \cite{yangkang2014svmf} proposed a type of MF with spatially varying window length. The space-varying median filter (SVMF) does not require the events to be flattened and is also better applied in midpoint domain. \cite{mediandeblend} used a multidirectional vector median filter  after resorting the data into common midpoint gathers. For inversion based approaches, because of the ill-posed property of the inversion problem, there should be some constraint to regularize the inversion problem. \cite{akerberg2008} used sparsity constraint in the Radon domain to regularize the inversion. A sparsity constraint was also used by \cite{abma2010} to minimize the energy of incoherent events present in blended data. \cite{lin2009} connected a curvelet-based sparse inversion algorithm with the emerging field of compressive sensing. \cite{bagaini2012} compared two separation techniques for the dithered slip-sweep (DSS) data using the sparse inversion method \cite{moore2010} and f-x predictive filtering \cite{canales1984}, and pointed out the advantage of the inversion methods over the filtering based approaches. In order to deal with the aliasing problem, \cite{proj} proposed the alternating projection method (APM), which chooses corrective projections to exploit data characteristics and is claimed to be less sensitive to aliasing than alternative approaches. \cite{mahdad2010} proposed a coherence-based inversion approach to deblend the simultaneous-source data. The convergence properties and the algorithmic aspects of the method were discussed by \cite{panagiotis20122} and \cite{araz2012}, respectively.

Most simultaneous-source surveys utilize a random scheduling strategy, which aims at making each shot in a source array shot with a random schedule to create the incoherent property of interference in common midpoint gathers (CMGs), common receiver gathers (CRGs), and common offset gathers (COGs), and the separation quality heavily depends on the source scheduling \cite{abma2014,yangkang2015dbortho}. When source scheduling is not optimally operated, those assumptions for applying different constraints when solving the under-determined deblending problem cannot be satisfied.

There are other limitations for the random firing acquisition. For example, when the poor source sampling causes spatial aliasing, deblending fails to give satisfying results, in which case no coherency filter can distinguish the direction of wave propagation to successfully remove the interference. This further limits the acquisition design with respect to the source spacing. A new blended acquisition design that uses shot repetition was proposed in \cite{sixuethesis}; and this avoids
the dense source-sampling restriction. The design of this acquisition is aimed at separating blended shots in the shot domain so that there are no restrictions on the source-sampling interval. A novel configuration of simultaneous-source acquisition called \emph{distance-separated simultaneous sourcing} (DSSS) was also proposed \cite{bouska2009}; and this does not enforce a random scheduling and thus can be more flexible. The basic principle of DSSS is by using simultaneous sources with a large separated distance to minimize the interference between different sources. Because of a large ratio of clean energy to overlapped energy, the interference can be directly muted without separation. This new simultaneous sourcing approach offers more flexibility and motivation to push the development of simultaneous source technique.

In this paper, we propose a novel iterative separation approach designed specifically for the DSSS acquisition. The clean region can be directly preserved before separation and the overlapped data are selected for iterative separation. Our approach is based on the assumption that the interference in a DSSS acquisition has conflicting dips. Thus, when the two sources are not far from each other, indicating a more complicated slope overlap, the separation performance will be significantly affected. We use seislet frames \cite{seislet,shuwei20153} as the basis for sparsifying each dip component. The two local slopes of the two dip components can be obtained using the plane-wave destruction (PWD) algorithm \cite{fomel2002pwd}. The proposed iterative approach is called \emph{iterative seislet frame thresholding}. We demonstrate superior performance using the proposed approach over the commonly used FK-based approach in obtaining artifacts-free separated components. We use both simulated synthetic and field data examples to demonstrate the successful performance of the proposed approach. The proposed approach can also be used in any simultaneous-source configuration that will cause dip-conflicting seismic events.

\section{Theory}
\subsection{Numerical blending and iterative deblending using seislet frames in the shot domain}
Suppose the distance-separated simultaneous-source data can be acquired by directly summing up two independent common shot gathers:
\begin{equation}
\label{eq:sum}
\tilde{\mathbf{d}}=\sum_{i=1}^{2}\mathbf{d}_i,
\end{equation}
where $\tilde{\mathbf{d}}$ is the blended data, and $\mathbf{d}_1$ and $\mathbf{d}_2$ denote the first and second independent sources, respectively.

In the case of least-squares misfit, we need to solve the following minimization problem:
\begin{equation}
\label{eq:mini1}
\min_{\mathbf{d}_1,\mathbf{d}_2}  \parallel\tilde{\mathbf{d}} - \sum_{i=1}^{2}\mathbf{d}_i \parallel_2^2.
\end{equation}

To solve the problem as shown in equation \ref{eq:mini1}, a regularization term should be added such that
\begin{equation}
\label{eq:mini2}
\{\mathbf{d}_1,\mathbf{d}_2\} = \arg \min_{\mathbf{d}_1,\mathbf{d}_2} \parallel\tilde{\mathbf{d}} - \sum_{i=1}^{2}\mathbf{d}_i \parallel_2^2 + \lambda\mathbf{R}(\mathbf{d}_1,\mathbf{d}_2).
\end{equation}
Here, $\lambda$ is a controlling parameter, and $\mathbf{R}$ is the regularization operator.

An appropriate regularization is needed to ensure the least summation of $L_1$ norm of the sparse transform domain coefficients:
\begin{equation}
\label{eq:mini2}
\{\mathbf{d}_1,\mathbf{d}_2\} = \arg \min_{\mathbf{d}_1,\mathbf{d}_2} \parallel\tilde{\mathbf{d}} - \sum_{i=1}^{2}\mathbf{d}_i \parallel_2^2 + \lambda\sum_{i=1}^{2} \parallel \mathbf{A}_i^{-1}\mathbf{d}_i\parallel_1,
\end{equation}
where $\mathbf{A}_i$ denotes the seislet frame for the $i$th source.

%\subsection{Iterative deblending using seislet frames in the shot domain}
We propose the following iterative approach for solving equation \ref{eq:mini2}:
\begin{equation}
\label{eq:iter}
\mathbf{d}_{i}^{n+1} = \mathbf{S}_i [\mathbf{d}_{i}^{n} + \mathbf{B}[\tilde{\mathbf{d}} - \sum_{i=1}^{2}\mathbf{d}_i^n ] ],
\end{equation}
where $\mathbf{S}_i$ is the shaping operator, which iteratively shapes the model into its more admissible model space, and $\mathbf{B}$ is a backward operator, which gives an approximate inverse mapping from data to model space. In this paper, we propose the use of a transformed domain soft-thresholding operator as the shaping operator:
\begin{equation}
\label{eq:shape}
 \mathbf{S}_i = \mathbf{A}_i \mathbf{T}_{\alpha} \mathbf{A}_i^{-1},
\end{equation}
and $\mathbf{B}$ as a scaled identity operator: $\mathbf{B}=\gamma\mathbf{I}$. The sparsity-promoting transforms for two sources are selected as a pair of seislet frames. To make the algorithm more robust, we only apply the algorithm to the overlapped part to preserve the clean energy.

The traditional iterative seislet thresholding based deblending approach \cite{yangkang20142} used a similar framework as equation \ref{eq:iter} to separate the simultaneous sources. However, there are two significant differences between the traditional seislet thresholding approach and the proposed approach. First, the traditional seislet thresholding approach is applied in domains other than the shot domain and is based on the random shot scheduling assumption, while the proposed approach is applied in the shot domain and does not require the shot schedules to be random. Secondly, the traditional seislet thresholding requires only one slope map to compress the coherent seismic events while the proposed approach requires several slope maps that have smoothly variable local slope to compress different coherent events. The traditional seislet thresholding can be considered as a special case of the proposed approach where only one seislet frame is used.

\subsection{Two-slope estimation and a review of the plane-wave destruction algorithm}
The key factor affecting the sparsity of the seislet frame $\mathbf{A}_i$ shown in equation \ref{eq:mini2} is the local slope. The local slope, $\sigma$, of the seismic profile can be related to the plane wave using the following differential equation:
\begin{equation}
\label{eq:plane}
\frac{\partial P}{\partial x} + \sigma \frac{\partial P}{\partial t} = 0,
\end{equation}
for local plane wave propagation in the $x$ direction.

The wavefield propagation along the space direction can also be expressed as:
\begin{equation}
\label{eq:shift}
P(x,t)=P(x+\Delta x,t+\sigma\Delta t).
\end{equation}

In the Z transform formulation, equation \ref{eq:shift} corresponds to the following equation:
\begin{equation}
\label{eq:zt}
(1-Z_xZ_t^p)P(Z_x,Z_t)=0,
\end{equation}
where $P(Z_x,Z_t)$ denotes the Z transform of $P$. $Z_t$ is the unit time-shift operator, and $Z_x$ is the unit space-shift operator.
The term $1-Z_xZ_t^p$ is referred to as the plane-wave destructor operator and can be approximated by
\begin{equation}
\label{eq:pwd}
1-Z_xZ_t^p = 1- Z_x \frac{B(Z_t)}{B(1/Z_t)},
\end{equation}
where $\frac{B(Z_t)}{B(1/Z_t)}$ is an all-pass filter to approximate $Z_t^{\sigma}=e^{iw\sigma}$.
Thus, the plane wave can be predicted using the 2-D prediction filter:
\begin{equation}
\label{eq:pred}
A(Z_t,Z_x) = 1- Z_x\frac{B(Z_t)}{B(1/Z_t)}.
\end{equation}
To avoid polynomial division, multiplying both sides of equation \ref{eq:pred} by $B(1/Z_t)$, then we obtain a more stable 2D prediction filter:
\begin{equation}
\label{eq:pred2}
C(Z_t,Z_x) = B(1/Z_t)- Z_xB(Z_t).
\end{equation}
The formulation of $B(Z)$ can be determined using an implicit finite difference scheme \cite{fomel2002pwd}.

If we apply $C$ onto the seismic data, given the known local slope $\sigma$, we can destruct the local plane waves and obtain a zero section.
To estimate the local slope, we can turn to solving the following equation:
\begin{equation}
\label{eq:zero}
C(\sigma)P(Z_x,Z_t) \approx 0.
\end{equation}
Because of the non-linear relation between $C$ and $\sigma$, we use Gauss-Newton's method to solve it by first linearizing equation \ref{eq:zero}:
\begin{equation}
\label{eq:linear}
C'(\sigma)P(Z_x,Z_t)\Delta \sigma  + C(\sigma)P(Z_x,Z_t) \approx 0.
\end{equation}
where $C'$ is the derivative of $C$ at $\sigma$.

When there is more than one slope in the data, we can still use equation \ref{eq:linear} to solve them, just by substituting the $C(\sigma)$ with $C(\sigma_1)C(\sigma_2)$,
and correspondingly equation \ref{eq:linear} becomes
\begin{equation}
\label{eq:double}
\begin{split}
C'(\sigma_1)C(\sigma_2)\Delta\sigma_1P(Z_x,Z_t)  &+C(\sigma_1)C'(\sigma_2)\Delta\sigma_2P(Z_x,Z_t)  + \\
&C(\sigma_1)C(\sigma_2)P(Z_x,Z_t) \approx 0.
\end{split}
\end{equation}
We start from an initial pair of $\sigma_1$ and $\sigma_2$, and by iteratively solving equation \ref{eq:double} we can obtain the converged $\sigma_1$ and $\sigma_2$.
%When transformed equation \ref{eq:plane} into frequency domain assuming $\sigma$ does not change with $t$,
%\begin{equation}
%\label{eq:freq}
%\frac{d \hat{P}}{d x} + iw\sigma \hat{P}= 0.
%\end{equation}
%It is obvious that equation \ref{eq:freq} has the following solution:
%\begin{equation}
%\label{eq:general}
%\hat{P}(x) = \hat{P}(0)e^{iw\sigma}.
%\end{equation}
%It's obviously that

\subsection{Deblending workflow for the DSSS blended data}
The overlapped data in the DSSS acquisition is relatively small compared with the whole data size. Conventionally, we simply mute the overlapped part or simply overlook it, and the final migration result will not differ too much compared with the single-shot shooting case. Based on the previous sections, we have designed a specific deblending approach for removing the overlapped part from the blended data by iterative inversion with a sparsity constraint in the seislet frame transformed domain. To fully utilize the clean signals, and not affect their energy, we suggest applying the proposed approach only to the overlapped part. Both slope estimation and iterative inversion are applied to the overlapped part. The proposed workflow is shown in Fig. \ref{fig:flowchart}.  Note that the proposed approach can only be used to separate simultaneous source data that contain distinct slope conflicts. The proposed approach also highly depends on the estimation accuracy of the local slope. The PWD algorithm is robust and can generally obtain accurate slope estimation. As long as the two sources are shot with a significantly large distance in field deployment, the basic assumption of dip conflicts can be easily met.

\inputdir{./}
\plot{flowchart}{width=\columnwidth}{Flowchart for deblending the DSSS data using the proposed approach.}

\section{Simulated data example}
We used a pair of two common shot gathers (CSG) to simulate the distance-separated blended data. Fig. \ref{fig:demo1,demo2,demo3} shows a demonstration of the simulated acquisition geometry. Figs. \ref{fig:demo1} and \ref{fig:demo2} show conventional acquisitions with a single source. We needed to cover the target regions showed by first shooting the regions in Fig \ref{fig:demo1} (red dots) and secondly, by shooting the regions in Fig \ref{fig:demo2} (green dots), continuously. However,  the conventional acquisition had low efficiency. Figs. \ref{fig:demo3} shows
the DSSS acquisition system. Two sources (denoted by the red and green dots) shoot simultaneously with a large distance between them. It is obvious that the acquisition efficiency has increased twice and because of the overlap between the seismic rays of two sources, there is interference in the recorded data.

\multiplot{3}{demo1,demo2,demo3}{width=0.45\columnwidth}{DSSS geometry demonstration. (a) Single source on the left side (red dots). (b) Single source on the right side (green dots). (c) Double sources with long separated distance.}

The first example is based on simulated synthetic example. The two clean synthetic data for simulation are shown in Figs. \ref{fig:hyper-shot1} and \ref{fig:hyper-shot2}. The distance-separated blended data are shown in Fig \ref{fig:hypers}. By fully utilizing the clean data, we muted the data such that the overlapped and the clean data are separated, as shown in Figs. \ref{fig:hyper-lap} and \ref{fig:hypers-clean}. After muting, we applied the proposed iterative seislet frame thresholding to the overlapped data, as shown in Fig \ref{fig:hyper-lap-zoom}. By applying the PWD algorithm as introduced in \cite{fomel2002pwd} and reviewed in the previous section, we obtained two dominant slopes, as shown in Figs. \ref{fig:hyper-lap-dip1} and \ref{fig:hyper-lap-dip2}. The two seislet frames that utilize the two dominant slopes can help to sparsify each dip component and treat the other slope component as unpredictable noise. After iterative separation using equation \ref{eq:iter}, we obtained two well-separated dip components, as shown in Figs. \ref{fig:hyper-lap-rec1-t} and \ref{fig:hyper-lap-rec2-t}. The normalized misfit during the iterative inversion (difference between the simulated data and observed blended data) is shown in Fig \ref{fig:hyper-lap-misfit-norm}. We also compared the performance using the proposed approach with that using the FK-based approach. The FK-based approach refers to the simple dip filter that uses 2D FFT transform \cite{sanyi2015} to separate the positive and negative wavenumber components . The two separated components using the FK-based approach are shown in Figs. \ref{fig:hyper-lap-fk1} and \ref{fig:hyper-lap-fk2}, respectively. It is obvious that the FK-based approach causes some artifacts in the separated components while the proposed approach might obtain nearly perfect artifacts-free components. The superior performance using the proposed approach results from the fact that the seislet frames are local transforms while the Fourier transform is a global transform, which will sometimes result in local artifacts in the filtered images. Note that if some random noise in the data exists, some pre-processing steps should be used to remove the random noise without harming the coherent events \cite{yangkang2015ortho} to ensure a good separation performance of the proposed approach. Putting the separated component to the original clean data results in the separated profiles. The separated components in the original scale and the clean components are shown in Figs. \ref{fig:hyper-lap-rec1}, \ref{fig:hyper-shot1-clean}, \ref{fig:hyper-lap-rec2} and \ref{fig:hyper-shot2-clean}.  Figs. \ref{fig:hyper-shot1-sep} and \ref{fig:hyper-shot2-sep} show the two deblended CSG. They are nearly the same as the unblended data, as shown in Figs. \ref{fig:hyper-shot1} and \ref{fig:hyper-shot2}.

\inputdir{hyper}
\multiplot{3}{hyper-shot1,hyper-shot2,hypers}{width=0.45\columnwidth}{Synthetic example. (a) Unblended source 1. (b) Unblended source 2. (c) Blended data using DSSS.}

\multiplot{2}{hyper-lap,hypers-clean}{width=0.45\columnwidth}{Synthetic example. Separated interference (a) and clean data (b).}

\multiplot{3}{hyper-lap-zoom,hyper-lap-dip1,hyper-lap-dip2}{width=0.45\columnwidth}{Synthetic example. (a) Zoomed interference. (b) Dip estimation for the first component. (c) Dip estimation for the second component. }

\multiplot{5}{hyper-lap-zoom,hyper-lap-rec1-t,hyper-lap-rec2-t,hyper-lap-fk1,hyper-lap-fk2}{width=0.3\columnwidth}{Synthetic example. (a) Zoomed interference. (b) Separated first component using the proposed approach. (c) Separated second component using the proposed approach. (d) Separated first component using the FK-based approach. (e) Separated second component using the FK-based approach. }

\multiplot{6}{hyper-lap-rec1,hyper-shot1-clean,hyper-shot1-sep,hyper-lap-rec2,hyper-shot2-clean,hyper-shot2-sep}{width=0.3\columnwidth}{Synthetic example. (a) Separated first component.  (b) Separated clean data for the first source.   (c) Separated first source (combining (a) and (b)).  (d) Separated second component. (e) Separated clean data for the second source.   (f) Separated second source (combining (d) and (e)).}

\plot{hyper-lap-misfit-norm}{width=0.8\columnwidth}{Convergence diagram (misfit function) for the synthetic example.}

\inputdir{field}
\multiplot{3}{field-shot1-0,field-shot2,fields-0}{width=0.45\columnwidth}{Field data example. (a) Unblended source 1. (b) Unblended source 2. (c) Blended data using DSSS.}

\multiplot{2}{field-lap,fields-clean}{width=0.45\columnwidth}{Field data example. Separated interference (a) and clean data (b).}

\multiplot{3}{field-lap-zoom,field-lap-dip1,field-lap-dip2}{width=0.45\columnwidth}{Field data example. (a) Zoomed interference. (b) Dip estimation for the first component. (c) Dip estimation for the second component.}

\multiplot{3}{field-lap-zoom,field-lap-rec1-t,field-lap-rec2-t}{width=0.45\columnwidth}{Field data example. (a) Zoomed interference. (b) Separated first component. (c) Separated second component.}

\multiplot{6}{field-lap-rec1,field-shot1-clean,field-shot1-sep-0,field-lap-rec2,field-shot2-clean,field-shot2-sep}{width=0.3\columnwidth}{Field data example. (a) Separated first component.  (b) Separated clean data for the first source.   (c) Separated first source (combining (a) and (b)).  (d) Separated second component. (e) Separated clean data for the second source.   (f) Separated second source (combining (d) and (e)).}

\plot{field-trace-comp}{width=\columnwidth}{Comparison of the amplitude between 1s and 2s of the 75th trace in the simulated field data example. The black solid line denotes the unblended trace (true trace). The green dashed line corresponds to blended data. The red dot-dashed line corresponds to deblended data. Note the removal of interference as indicated by the amplitude difference between the green dashed line and red dot-dashed line.}

The second example is based on a simulated field data example. The two clean field data for simulation are shown in Figs. \ref{fig:field-shot1-0} and \ref{fig:field-shot2}. The distance-separated blended data are shown in Fig \ref{fig:fields-0}. We followed the same procedures as the first example, and first muted the data such that the overlapped and the clean data are separated, as shown in Figs. \ref{fig:field-lap} and \ref{fig:fields-clean}. After muting, we applied the proposed iterative seislet frame thresholding to the overlapped data, as shown in Fig \ref{fig:field-lap-zoom}. The two dominant slopes calculated using PWD algorithms are shown in Figs. \ref{fig:field-lap-dip1} and \ref{fig:field-lap-dip2}.  After iterative separation using equation \ref{eq:iter}, we obtained two well-separated dip components, as shown in Figs. \ref{fig:field-lap-rec1-t} and \ref{fig:field-lap-rec2-t}. The separated components in the original scale and the clean components are shown in Figs. \ref{fig:field-lap-rec1}, \ref{fig:field-shot1-clean}, \ref{fig:field-lap-rec2} and \ref{fig:field-shot2-clean}.  Figs. \ref{fig:field-shot1-sep-0} and \ref{fig:field-shot2-sep} show the two deblended CSG. We also compared the amplitude between 1s and 2s of the 75th trace in the simulated field data example, shown in Fig \ref{fig:field-trace-comp}. The selected trace is highlighted by the dashed lines in Figs. \ref{fig:field-shot1-0}, \ref{fig:fields-0}, and \ref{fig:field-shot1-sep-0}. The black solid line denotes the unblended trace (true trace). The green dashed line corresponds to blended data. We can see the big difference between green dashed line and the other two lines. The red dot-dashed line corresponds to the deblended data. Note the removal of blending interference as indicated by the amplitude difference between the green dashed line and red dot-dashed line. Although the deblended trace is not exactly the same as the blended trace, they are close to each other, which indicates a successful deblending performance.

\section{Conclusions}
We proposed an iterative seislet frame thresholding approach for deblending of the distance-separated simultaneous-source data. Instead of directly muting the overlapped area, we iteratively separate the dip-conflicting overlapped data. The whole processing steps include: muting the whole CSG into clean part and overlapped part, conflicting dips estimation using PWD, iterative seislet frame thresholding on the overlapped data, and combining the clean and separated data to form the final deblended data. The DSSS acquisition does not require random scheduling, and can be pre-processed in the common shot domain. The presented simulated synthetic and field data examples both show nearly perfect deblending performances. Compared with the FK-based approach, the proposed approach can obtain artifacts-free and more accurate separated components since the FK-based approach uses a global 2D FFT transform while the proposed approach uses a local seislet frame transform. Our ongoing project is to compare the migrated results of the DSSS data using the traditional approach (simply muting the interference) and the proposed iterative inversion approach.

\section{Acknowledgements}
We would like to thank Shan Qu, Shaohuan Zu, Zhaoyu Jin, Jiang Yuan, and five anonymous reviewers for discussions and suggestions that improved the manuscript greatly. This research is supported by the National Natural Science Foundation of China (Grant No.41274137), the National Science and Technology of Major Projects of China (Grant No. 2011ZX05019-006), and the National Engineering Laboratory of Offshore Oil Exploration.

\bibliographystyle{seg}
\bibliography{ddsisft}

### 2020-12-19 somf/paper.tex
2020年12月18日 星期五 19时16分49秒 CST

%\title{Deblending using a structural-oriented median filter in the flattened domain }
\title{Separation of simultaneous sources using a structural-oriented median filter in the flattened dimension}
\author{Shuwei Gan\footnotemark[1] , Shoudong Wang\footnotemark[1], Yangkang Chen\footnotemark[2], Xiaohong Chen\footnotemark[1], and Kui Xiang\footnotemark[1]}

\address{
\footnotemark[1]State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
gsw19900128@126.com \& wangshoudong@163.com \& chenxh@cup.edu.cn \& xiangkui15@126.com \\
\footnotemark[2]Bureau of Economic Geology, \\
Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
USA \\
%+1-5125478899 \\
%ykchen@utexas.edu \\
}

\lefthead{Gan et al.}
\righthead{Structural-oriented median filter}

\maketitle

\begin{abstract}
Simultaneous-source shooting can help tremendously shorten the acquisition period and improve the quality of seismic data for better subsalt seismic imaging, but at the expense of introducing strong interference (blending noise) to the acquired seismic data. We propose to use a structural-oriented median filter to attenuate the blending noise along the structural direction of seismic profiles. The principle of the proposed approach is to first flatten the seismic record in local spatial windows and then to apply a traditional median filter (MF) to the third flattened dimension. The key component of the proposed approach is the estimation of the local slope, which can be calculated by first scanning the NMO velocity and then transferring the velocity to the local slope. Both synthetic and field data examples show that the proposed approach can successfully separate the simultaneous-source data into individual sources. We provide an open-source toy example to \new{better} demonstrate \old{better} the proposed methodology. 
\end{abstract}

\section{Keywords}
Simultaneous sources, structural-oriented median filter, plane-wave destruction, velocity slope transformation

\section{Introduction}
\new{Wide-azimuth acquisition geometry can improve the illumination of subsalt structures, which helps improve the quality of seismic imaging. However, wide-azimuth acquisition suffers from the low-efficiency problem, resulting from the large temporal shooting interval between two consecutive shots. The large temporal shooting interval is needed to ensure that no interference exists between adjacent shots. } The principal purpose of simultaneous source acquisition is to faster the acquisition of a larger-density seismic dataset \new{that allows the temporal or spatial overlap between different shots}, which saves numerous acquisition cost and increases data quality. The improved seismic data with denser spatial sampling can \new{also} help improve the seismic imaging quality of the subsalt structure. The benefits of the new technique are compromised by the intense interference between different shots \cite[]{berkhout2008}. One way for solving the problem caused by interference is by first-separating and second-processing strategy \cite[]{yangkang20142}, which is also called deblending \cite[]{akerberg2008,abma2010,mediandeblend,sep,blac2012,proj,panagiotis20122,araz2012,bagaini2012,chengbo2013,yangkang2014,yangkang2014nmo,berkhout2014seg,yangkang2014svmf,qushan2015,yangkang2015dbortho,shaohuan2015}. Another way is by direct imaging and inversion of the blended data by attenuating the interference during inversion process \cite[]{verschuur2011,daiwei2011,zhiguang2014,yangkang2015image,shuwei2015vel}. Currently, deblending is still the dominant way for dealing with simultaneous-source data.

There are generally two types of deblending approaches that have been reported in the literature: (1) treating deblending as a noise attenuation approach \cite[]{mediandeblend,yangkang2014,yangkang2014nmo,yangkang2014svmf,yangkang2014simi,yangkang2015ortho}, (2) treating deblending as an inversion problem \cite[]{sep,abma2010,yangkang20142,shuwei2015seg}.  For the filtering based approaches, most of the approaches are based on median filter. \cite{yangkang2014nmo} proposed to use common midpoint domain for deblending, because of the better coherency of useful signals and also because the near-offset useful events follow the hyperbolic assumption and thus can be flattened using normal moveout (NMO) correction. A simple median filtering (MF) can be applied to the NMO corrected common-midpoint (CMP) gathers to attenuate blending noise. \cite{yangkang2014svmf} proposed a type of MF with spatially varying window length. The space-varying median filter (SVMF) does not require the events to be flattened and is also better applied in midpoint domain. \cite{mediandeblend} used a multidirectional vector median filter  after resorting the data into common midpoint gathers. For inversion based approaches, because of the ill-posed property of the inversion problem, there should be some constraint to regularize the inversion problem. \cite{akerberg2008} used sparsity constraint in the Radon domain to regularize the inversion. A sparsity constraint was also used by \cite{abma2010} to minimize the energy of incoherent events present in blended data. \cite{lin2009} connected a curvelet-based sparse inversion algorithm with the emerging field of compressive sensing. \cite{bagaini2012} compared two separation techniques for the dithered slip-sweep (DSS) data using the sparse inversion method  and f-x predictive filtering \cite[]{canales1984}, and pointed out the advantage of the inversion methods over the filtering based approaches. In order to deal with the aliasing problem, \cite{proj} proposed the alternating projection method (APM), which chooses corrective projections to exploit data characteristics and is claimed to be less sensitive to aliasing than alternative approaches. \cite{mahdad2010} proposed a coherence-based inversion approach to deblend\new{ing of} the simultaneous-source data. The convergence properties and the algorithmic aspects of the method were discussed by \cite{panagiotis20122} and \cite{araz2012}, respectively. \new{Although the inversion-based approaches have been demonstrated to obtain better deblending performance \cite[]{bagaini2012}, it usually takes many iterations to process the data. Currently, the most efficient way for deblending is using some types of median filtering.  However, most of the median filtering approaches are directly borrowed from the signal-processing field and do not utilize the structure information of seismic data. }

In this paper, we propose a novel type of MF \new{that makes use of the structural features of seismic data} by means of first flattening the seismic record in local spatial windows and then applying MF along the flattened dimension. The flattening operator is constructed by predicting the neighbor traces following the local slope. One concern for such flattening processing is the estimation of an accurate-enough local slope map, which can be solved by first scanning the NMO velocity and then transferring the velocity to the local slope in the common midpoint domain. We first review the principle of separating simultaneous sources (deblending) and then introduce the theory of both traditional MF and the proposed structural-oriented median filter (SOMF). Next, we introduce the method of transferring the NMO velocity to local slope in the common midpoint domain. Finally, we use two synthetic examples and one simulated field data example to demonstrate the separating performance of the proposed approach.

\section{Method}
\subsection{Deblending of simultaneous-source data}
In a simultaneous-source acquisition, more than one source are blended onto one constant receiver record:
\begin{equation}
\label{eq:blend}
\mathbf{d}=\Gamma\mathbf{m},
\end{equation}
where $\mathbf{d}$ is the blended data, $\mathbf{m}$ is the unblended data, and $\Gamma$ denotes the blending operator \cite[]{sep,yangkang20142,yangkang2015pnmo}. The \old{principle}\new{principal} issue in simultaneous-source acquisition is to separate the blended sources into individual sources as if they were acquired independently, which also corresponds to solving the equation \ref{eq:blend} for $\mathbf{m}$.

The simplest way to approximate $\mathbf{m}$ is called the pseudo-deblending:
\begin{equation}
\label{eq:pseudo}
\hat{\mathbf{m}} = \Gamma^*\mathbf{d}.
\end{equation}
Equation \ref{eq:pseudo} corresponds to arranging the seismic records according to the shot schedules of each source in a common receiver gather, which honors the coherency between different shots in each source and makes the interference from other sources randomly spread\old{ing} the receiver domain. The inversion problem \new{as shown in equation} \ref{eq:blend} is then transformed to be a noise attenuation problem that separate\new{s} the spatially coherent signals from the random interference.

A more accurate but also time-consuming approach for solving equation \ref{eq:blend} is to use iterative solver to invert $\mathbf{m}$ with some constraints. One of the currently popular and effective way\new{s} is to use a POCS like solver with a transformed domain sparse constraint \cite[]{abma2010,yangkang20142}:
\begin{equation}
\label{eq:pocs}
\mathbf{m}_{n+1}=\mathbf{A}^{-1}\mathbf{T}\mathbf{A}[\mathbf{m}_n+\lambda\Gamma^*(\mathbf{d}-\Gamma\mathbf{m}_n)],
\end{equation}
where $\mathbf{m}_{n}$ is the inverted solution after $n$th iterations, $\mathbf{A}$ and $\mathbf{A}^{-1}$ denotes the forward and inverse sparse transforms, $\mathbf{T}$ denotes a thresholding operator, and $\lambda$ denotes the step size of the model update. The Fourier transform, the curvelet transform, the Radon transform, and the seislet transform are the currently popular sparse transforms for deblending.

The performance of deblending heavily depends on the sparsity of the selected sparse transform. However, most sparse transforms are model dependent, which means that the transforms are based on some assumptions about the data structure. As we know, the seismic data is highly non-stationary and the commonly used sparse transforms can not obtain acceptable level of sparsity, which will result in non-optimal inversion performance. What is even worse is that the inversion may not be stable when blending interference is too strong or the sparse transform domain is not sparse enough. Even though we can use inversion based deblending approach to obtain satisfactory results, the deblending process will take a large number of iterations. Considering the modern seismic acquisition is becoming amazingly larger and larger, the iterative inversion is very time consuming. In the next sections, we will propose a non-iterative deblending approach based on median filtering, which is of exceptional convenience for removing the blending interference.

\subsection{Median filtering}
The MF is commonly used to remove spiky noise in signal-processing field. For the purpose of removing spiky noise in seismic data, the MF is applied point by point. For each point in the seismic data, we choose a local window that centers at the current point and then pick the median of the local window to be the final value of the current point. The basics of finding the median of a local window is to solve the following minimization problem:
\begin{equation}
\label{eq:mf1}
\hat{u}_{i,j}=\arg\min_{u_m\in U_{i,j}}\sum_{l=1}^{L}\Arrowvert u_m-u_l \Arrowvert_p,
\end{equation}
where $\hat{u}_{i,j}$ is the output value for location $x_{i,j}$, $U_{i,j}=\{u_1,u_2,\cdots,u_L\}$, $i,j$ are the position indices in a 2-D profile, and $l$ and $m$ are both indices in the filtering window. $L$ is the length of the filtering window, and $p$ denotes $L_p$ norm. Commonly $p=1$ corresponds to standard MF.

Because the blending noise caused from the simultaneous shooting is spike-like along the spatial direction, we can use the MF to effectively remove \old{them}\new{it}. However, the traditional MF is only applicable to those seismic data that \old{is main}\new{mainly} composed of horizontal reflections, otherwise much useful reflection energy will be damaged. Thus, we need to either find a way to flatten the seismic data or apply the MF along the structural direction.

\subsection{Structural-oriented median filtering}
We propose a type of median filter that is applied along the local structure to remove the blending interference. The principle of the approach is to first flatten the seismic data in a local spatial window:
\begin{equation}
\label{eq:flatten}
 \mathbf{P}_j \mathbf{D}_j^R= \overline{\mathbf{D}}_j^R.
\end{equation}
where $\mathbf{P}_j$ is the $j$th flattening operator, \new{and} $j$ corresponds to the $j$th trace. And then, we apply a traditional median filter along the flatten\new{ed} direction. Here, the flattening operator is chosen as a plane-wave prediction operator related with the local slope. $\mathbf{D}_j^R$ denotes the $j$th spatial window (corresponding to $j$th trace) with a radius of $R$, $\overline{\mathbf{D}}_j^R$ denotes the flattened local spatial window.
Equation \ref{eq:flatten} has the following detailed form \cite[]{shuwei2015}:
\begin{equation}
\label{eq:detail}
\begin{split}
& \left[
\begin{array}{cccccc}
\mathbf{P}_{(1,j)\rightarrow(1+R,j)}(\sigma_{1,j}) &  & & \\
 &  & \ddots & \\
 &  & & \mathbf{P}_{(1+2R,j)\rightarrow(1+R,j)}(\sigma_{1+2R,j})\\
\end{array}
\right]\\
&[\mathbf{d}_{1,j},\cdots,\mathbf{d}_{1+R,j}, \cdots, \mathbf{d}_{1+2R,j}]\\
&=[\overline{\mathbf{d}}_{1,j},\cdots,\overline{\mathbf{d}}_{1+R,j}, \cdots, \overline{\mathbf{d}}_{1+2R,j}]. 
\end{split}
\end{equation}
Here, $\mathbf{P}_{(i,j)\rightarrow(k,j)}(\sigma_{i,j})$ denotes the prediction operator from trace $i$ to trace $k$ in $j$th spatial window, which is connected with the local slope of $i$th trace \new{$\sigma_{i,j}$}. \new{ $\mathbf{d}_{i,j}$ denotes the $i$th trace in the $j$th spatial window. $\overline{\mathbf{d}}_{i,j}$ denotes the $i$th trace in the $j$th spatial window after flattening.} Prediction of a trace consists of shifting the original trace along dominant event slopes \cite[]{fomel2010painting}.  
Prediction of a trace from a distant neighbor can be accomplished by simple recursion \cite[]{liuyang2010}, i.e., predicting trace $k$ from trace $1$ is simply
\begin{equation}
\label{eq:recur}
\begin{split}
\mathbf{P}_{(1,j)\rightarrow(k,j)} (\sigma_{1,j})&= \mathbf{P}_{(k-1,j)\rightarrow(k,j)}(\sigma_{k-1,j})\cdots\\
&\mathbf{P}_{(2,j)\rightarrow(3,j)}(\sigma_{2,j})\mathbf{P}_{(1,j)\rightarrow(2,j)}(\sigma_{1,j}).
\end{split}
\end{equation}

\old{The prediction operator is a numerical solution of the local plane differential equation 
$\frac{\partial P}{\partial x} + \sigma \frac{\partial P}{\partial t} = 0,$
for local plane wave propagation in the $x$ direction. }

The dominant slopes are estimated by solving the following least-square minimization problem using regularized least-squares optimization:
\begin{equation}
\label{eq:mini}
\hat{\mathbf{\sigma}} = \arg\min_{\sigma} \parallel \mathbf{W}(\sigma)\mathbf{D} \parallel_2^2,
\end{equation}
where $\mathbf{W}$ is the destruction operator defined as

\begin{displaymath} 
\mathbf{W} = \left[
\begin{array}{ccccc} 
\mathbf{I} & 0 & 0 & \cdots & 0\\
-\mathcal{\mathbf{P}}_{1\rightarrow 2} &\mathbf{I} & 0 &\cdots &0\\
0 &-\mathcal{\mathbf{P}}_{2\rightarrow 3} & \mathbf{I} & \cdots & 0 \\
\cdots & \cdots & \cdots & \cdots & \cdots \\
0& 0 & \cdots & - \mathcal{\mathbf{P}}_{N-1\rightarrow N} & \mathbf{I}
\end{array}\right]\;, 
\end{displaymath}
where $\mathbf{I}$ stands for the identity operator, and $\mathcal{\mathbf{P}}_{i\rightarrow k}$ describes prediction of trace $k$ from trace $i$ (same as the previous version $\mathbf{P}_{(i,j)\rightarrow(k,j)}(\sigma_{i,j})$ except for not in a specific spatial window). The optimization approach as shown in equation \ref{eq:mini} for obtaining local slope estimation is called plane wave destruction (PWD) \cite[]{fomel2002pwd}.

For each trace, we apply the aforementioned flattening, and then we can obtain a 3D cube of the flattened domain. The final filtered result is obtained by selecting the middle slice in the added third dimension after applying median filtering.

\subsection{Estimating local slope from velocity analysis}
The local slope estimation in highly noisy blended data is challenging. Instead of directly estimating the local slope using the PWD algorithm, we can alternatively first calculate the NMO velocity using simple NMO-correction based velocity analysis and transform\old{s} the NMO velocity to local slope \cite[]{liuyang2013} by using
\begin{equation}
\label{eq:vtop}
p(t,x)=\frac{x}{t(x)v_n^2(t_0,x)},
\end{equation}
where $t_0$ is the zero-offset traveltime, $t(x)$ is the traveltime recorded at offset $x$, $v_n(t_0,x)$ is the NMO velocity, and $p(t,x)=dt/dx$ is the local slope. The detailed introduction of the velocity to slope transformation was introduced in \cite{liuyang2013}.

\section{Examples}
The first example is a simulated synthetic example. The data has been sorted into common midpoint domain. Figures \ref{fig:hyper} and \ref{fig:hypers} shows the unblended and blended data, respectively. By using the direct slope estimation using PWD algorithm and the velocity-slope transformation, we can obtain two dramatically different local slope estimations, as shown in Figure \ref{fig:hyper-pdip,hyper-vdip}. It is obvious that the velocity-slope transformation can obtain much better slope estimation. Figures \ref{fig:hypers-vcube} and \ref{fig:hypers-vcube-mf} show the 3D cubes of the flattened domain for blended and deblended data, respectively\new{, using the local slope map from the velocity-slope transformation}. \new{Figure \ref{fig:hypers-pcube} shows the flattened blended data that uses the slope map from PWD algorithm. Figures \ref{fig:hypers-pcube} and \ref{fig:hypers-vcube} are very similar, which demonstrate the fact that the flattening process is not very sensitive to the estimated slope.} A traditional MF is applied along the third dimension of the 3D cube as shown in Figure \ref{fig:hypers-vcube}. Figures \ref{fig:hyper-pmf} and \ref{fig:hyper-vmf} show the final deblended data using the two slopes from PWD and velocity-slope estimation, respectively. Both deblended results are very successful because all the blending noise has been removed and there is no obvious damage in the useful energy. We can further confirm the performance by comparing the blending noise sections (Figure \ref{fig:hyper-pmf-dif,hyper-vmf-dif}) and the deblending error sections (Figure \ref{fig:hyper-pmf-err,hyper-vmf-err}). We also amplified the error sections (Figure \ref{fig:hyper-pmf-err-5,hyper-vmf-err-5}) in order to better compare the difference. From Figures \ref{fig:hyper-pmf-err,hyper-vmf-err} and \ref{fig:hyper-pmf-err-5,hyper-vmf-err-5}, we can conclude that both deblended results are very similar to the unblended data and the deblended data using the slope from velocity-slope transformation has smaller deblending error. We provide a Python script that can regenerate all the figures (from Figure \ref{fig:hyper,hypers} to Figure \ref{fig:hyper-pmf-err-5,hyper-vmf-err-5}) of the first example. \new{From this example, we can see that the two slope estimation approaches will generate similar flattened events and will generate similar deblended results. Thus, the proposed structural-oriented median filter might obtain robust deblending performance even when the slope estimation is not very accurate. } \new{It should also be mentioned that though the proposed algorithm is relatively robust, it still depend on an acceptable estimation of the local slope. In the case of extremely strong blending noise, even with the slope-slope transformation we cannot obtain good slope estimation, preliminary processing steps are required to obtain an acceptable slope estimation.} The Python script (SConstruct) should be run in the Madagascar open-source environment \cite[]{mada2013}, which can be downloaded at $www.ahay.org$.

The second example is a simulated pre-stack example. The unblended 3D data cube is shown in Figure \ref{fig:data-csg}. There are 1501 time samples in this synthetic example and the temporal sampling is 4 ms. The peak frequency is 10 Hz. There are 251 shots and 51 receivers in this example. The shot and receiver intervals are both 50 m. We simulate the blending geometry by using two sources shooting at the two sides of a towed-streamer. Both of the two sources shoot\old{ing} arbitrarily \old{and} with a small random dithering. The simulated blended shooting causes strong interference to the data as shown in Figure \ref{fig:datas-csg}. It is apparent that the blending noise appears coherent in common shot gathers and appears random in common offset gathers. By sorting the shot domain (Figure \ref{fig:datas-csg}) to midpoint domain (Figure \ref{fig:data-b}), we can observe that the blending noise appears random in both common offset gathers and common midpoint gathers. The deblending procedures using the proposed approach are applied to Figure \ref{fig:data-b}. The detailed deblending comparison is provided in Figure \ref{fig:data-cmg,data-db,data-db-dif,data-db-err}. Figure \ref{fig:data-db-csg} shows the final deblended result that is sorted back to the shot domain. We can conclude a successful separation considering the high similarity between Figures \ref{fig:data-csg} and \ref{fig:data-db-csg}. In Figure \ref{fig:data-cmg,data-db,data-db-dif,data-db-err}, we compare the unblended and deblended data in the midpoint domain in Figures \ref{fig:data-cmg} and \ref{fig:data-db}, and show the removed the blending noise cube and deblending error cube in Figures \ref{fig:data-db-dif} and \ref{fig:data-db-err}, respectively. From the very clean deblended data, incoherent blending noise, and small deblending error, we can further confirm that the proposed approach obtain a successful separation between the signals and interference.

The third example is a simulated field data example. Figure \ref{fig:fieldsr} shows the unblended data from a constant-receiver 2D marine survey. Figure \ref{fig:fieldsrs} shows the blended data. As we can see, the blending interference appears incoherent in common receiver gathers and coherent in common shot gathers. Figure \ref{fig:fieldsrs-db} shows the deblended result using the proposed approach and Figure \ref{fig:fieldsrs-db-dif} shows the blending noise cube. It is obvious that the blending noise in each common receiver gather\old{s} do\new{es} not contain coherent reflections and the blending noise appears as coherent source when observed along the third dimension. As we can see, we can use the proposed approach to obtain a nearly perfect separation of simultaneous sources.

\section{Conclusion}
We have proposed a novel deblending approach using a structural oriented median filter. The proposed median filter is applied in a pre-flattened third dimension of the original data. We use prediction operator following the local slope to flatten the seismic record in local spatial windows. The key aspect in the flattening process is the estimation of the local slope from the highly noisy blended data. Instead of directly estimating the local slope using PWD algorithm, we can use the velocity-slope transformation to alternatively estimate the slope. \new{While the slope estimation from the PWD algorithm can help obtain acceptable deblending performance, the slope from velocity-slope transformation can help obtain even better performance. } Both synthetic and field data examples show successful deblending performance using the proposed approach.

\section{Acknowledgements}
We would like to thank Shan Qu, Shaohuan Zu, Zhaoyu Jin, and Jiang Yuan for helpful discussions on the topics of deblending. \new{We also thank the chief editor Jef Caers and four anonymous reviewers for suggestions that improve the manuscript greatly.}  This research is supported by the National Natural Science Foundation of China (Grant No.41274137), the National Science and Technology of Major Projects of China (Grant No. 2011ZX05019-006), and National Engineering Laboratory of Offshore Oil Exploration.

\inputdir{hypermf}
\multiplot{2}{hyper,hypers}{width=0.46\textwidth}{Synthetic example in common midpoint domain. (a) Unblended data. (b) Blended data.}

\multiplot{2}{hyper-pdip,hyper-vdip}{width=0.46\textwidth}{Local slope maps using (a) PWD, (b) velocity-slope transformation.}

%\plot{hypers-vcube}{width=\textwidth}{Flattened domain of the blended data. The MF is to be applied along the third dimension of the cube. \new{(a) From the slope map using PWD. (b) From the slope map using velocity-slope transformation.}}
\multiplot{2}{hypers-pcube,hypers-vcube}{width=0.6\textwidth}{Flattened domain of the blended data. The MF is to be applied along the third dimension of the cube. \new{(a) From the slope map using PWD. (b) From the slope map using velocity-slope transformation.}}

\plot{hypers-vcube-mf}{width=\textwidth}{Flattened domain of the blended data after MF. }

\multiplot{2}{hyper-pmf,hyper-vmf}{width=0.46\textwidth}{Deblended results using using slopes from (a) PWD, (b) velocity-slope transformation.}

\multiplot{2}{hyper-pmf-dif,hyper-vmf-dif}{width=0.46\textwidth}{Blending noise  sections using slopes from (a) PWD, (b) velocity-slope transformation.}

\multiplot{2}{hyper-pmf-err,hyper-vmf-err}{width=0.46\textwidth}{Deblending error sections using slopes from (a) PWD, (b) velocity-slope transformation.}

\multiplot{2}{hyper-pmf-err-5,hyper-vmf-err-5}{width=0.46\textwidth}{Amplified deblending error sections ($\times5$) using slopes from (a) PWD, (b) velocity-slope transformation.}

%\inputdir{field1}
%\multiplot{2}{field1,fields}{width=0.46\textwidth}{Single receiver gather example. (a) Unblended common receiver gather. (b) Blended common receiver gather.}

%\plot{fields-cube}{width=\textwidth}{Flattened domain of the blended data. The MF is to be applied along the third dimension of the cube.}
%\plot{fields-cube-mf}{width=\textwidth}{Flattened domain of the blended data after MF. }

%\multiplot{2}{field-fx,field-mf}{width=0.46\textwidth}{Deblended result using (a) FX decon, (b) SOMF.}
%\multiplot{2}{field-fx-dif,field-mf-dif}{width=0.46\textwidth}{Blending noise sections using (a) FX decon, (b) SOMF.}

\inputdir{presynth}
\multiplot{4}{data-csg,datas-csg,data-b,data-db-csg}{width=0.45\textwidth}{Pre-stack synthetic example. (a) Unblended data in shot domain. (b) Blended data in shot domain. (c) Blended data in midpoint domain. (d) Deblended data in shot domain.}

\multiplot{4}{data-cmg,data-db,data-db-dif,data-db-err}{width=0.45\textwidth}{Pre-stack synthetic example. (a) Unblended data in midpoint domain. (b) Deblended data in midpoint domain. (c) Blending noise in midpoint domain. (d) Deblending error in midpoint domain.}

\inputdir{fieldsr}
\multiplot{4}{fieldsr,fieldsrs,fieldsrs-db,fieldsrs-db-dif}{width=0.45\textwidth}{Field data example. (a) Unblended data. (b) Blended data. (c) Deblended data. (d) Blending noise.}

\bibliographystyle{seg}
\bibliography{dblendstr}

### 2020-12-19 usarray/matfun/Syn.m

@@ -72,8 +72,8 @@ d1=win3d_mask(@localfxymssa_recon, dm, param, d0, n1win, n2win, n3win, r1, r2, r
 flow=0;fhigh=100;dt=0.004;N=9;mode=1;verb=1;
 a=(Niter-(1:Niter))/(Niter-1); %linearly decreasing
 d2=fxymssa_recon(d0,dm,flow,fhigh,dt,N,Niter,eps,verb,mode,a);
-yc_snr(d,d1,2)	%21.0808
-yc_snr(d,d2,2)	%17.1526
+yc_snr(d,d1,2)	
+yc_snr(d,d2,2)	
 
 
 %% from Matlab to Madagascar

### 2020-12-19 usarray/matfun/Syn_ratios.m

@@ -94,14 +94,6 @@ end
 %fid=fopen('syn_us_ratios_snrs.bin','w');
 %fwrite(fid,[snrs0,snrs1,snrs2],'float');
 
-%ratio=0.1: 4.7284;4.2651
-%ratio=0.2: 9.8721;8.6852;
-%ratio=0.3: 14.5532;11.7224
-%ratio=0.4: 18.4519,15.1889
-%ratio=0.5: 20.5601,17.4001
-%ratio=0.6: 20.9589,17.7631
-%ratio=0.7: 21.0329,17.9402
-
 snrs=[snrs0,snrs1,snrs2];
 
 %% from Matlab to Madagascar

### 2020-12-19 usarray/matfun/win3d_mask.m

@@ -1,8 +1,6 @@
 function [ dout ] =win3d_mask(oper, mask, param, din, n1win, n2win, n3win, r1, r2, r3)
 % Processing in 3D windows (can also deal with 2D processing)
-% 2D version similar to process_win
-% coding strategy follows exactly usr/cm/Mfxmssa_win.c
-%
+% 
 % din:          input data
 % oper:         operator
 % mask:         sampling/masking operator for data reconstruction

### 2020-12-22 lr5d/paper.tex
2020年12月22日 星期二 17时43分16秒 CST

\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2020.DOI}

\title{Fast and robust low-rank approximation for high-dimensional seismic data reconstruction}
%\author{\uppercase{Juan Wu}\authorrefmark{1},
%\uppercase{Second B. Author\authorrefmark{2}, and Y. Chen}.\authorrefmark{3},
%\IEEEmembership{Member, IEEE}}
%\address[1]{National Institute of Standards and 
%Technology, Boulder, CO 80305 USA (e-mail: author@boulder.nist.gov)}
%\address[2]{Department of Physics, Colorado State University, Fort Collins, 
%CO 80523 USA (e-mail: author@lamar.colostate.edu)}
%\address[3]{Electrical Engineering Department, University of Colorado, Boulder, CO 
%80309 USA}

%\markboth
%{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
%{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}

\author{Juan Wu\footnotemark[1], Min Bai\footnotemark[1], Dong Zhang\footnotemark[2], Hang Wang\footnotemark[3], Guangtan Huang \footnotemark[3], and Yangkang Chen\footnotemark[3] }

%\author{*}
\address{
\footnotemark[1]Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
Yangtze University\\
Wuhan 430100, China\\
%yangkang.chen@zju.edu.cn \\
\footnotemark[2] Faculty of Applied Sciences \\
Delft University of Technology \\
Lorentzweg 1, Delft, Netherlands, 2628CJ  \\
%d.zhang-3@tudelft.nl \\ 
\footnotemark[3] School of Earth Sciences \\
Zhejiang University \\
Hangzhou, Zhejiang, 310027 \\
}

\corresp{Corresponding author: M. Bai (e-mail: baimin2016@126.com).}
\tfootnote{This research is sponsored by the National Natural Science Foundation of China (Nos. \new{41904110,}41704121), \new{the China Postdoctoral Science Foundation (No. 2019M662567), and the Postdoctoral Science Foundation of Hubei Province.}}

\def\thevol{8}
\def\myyear{2020}

\begin{abstract}
Five-dimensional (5D) seismic data reconstruction becomes more appealing in recent years because it takes advantage of five physical dimensions of the seismic data \old{for reconstruction }and can reconstruct data with large gap. The low-rank approximation approach is one of the most effective methods for reconstructing 5D dataset. However, the main disadvantage of the low-rank approximation method is its low computational efficiency because of many singular value decompositions (SVD) of the block Hankel\new{/Toeplitz} matrix in the frequency domain. In this paper, we develop an SVD-free low-rank approximation method for efficient and effective reconstruction and denoising of the seismic data that \old{contains}\new{contain} four spatial dimensions. Our SVD-free rank constraint model is based on an alternating minimization strategy, which updates one variable each time while fixes the other two. For each update, we only need to solve a linear least-squares problem with much less expensive QR factorization. The SVD-based and SVD-free low-rank approximation \new{methods} in the singular spectrum analysis (SSA) framework are compared in detail, regarding the reconstruction performance and computational cost. The comparison shows that the SVD-free low-rank approximation method can obtain similar reconstruction performance as the SVD-based method but with a large computational speed up.
\end{abstract}

\begin{keywords}
Multidimensional seismic data, \old{lowrank}\new{low-rank} approximation, seismic data processing, \new{seismic reconstruction, matrix completion}
\end{keywords}

\titlepgskip=-15pt

\maketitle

\section{Introduction}
\label{sec:introduction}

Data reconstruction is extremely important during the entire seismic processing chain due to the fact that our acquired data are never complete and regular in spatial dimensions. More specifically, abundant physical and economic restrictions happen throughout the acquisition phase resulting in data incompletion, e.g., feathering, near-offset gap, cross-line under-sampling in towed marine streamer acquisition and obstacles, terrain restrictions in land acquisition \cite{ronen,spitz1991,canning1996,fomel2002pwd,fomel2003,abmapocs,herrmann2008non,mostafa2010,mostafa2013,wang2011recovery,shuwei2016cs,shaohuan2016gap,yangkang2016irr5d,amir2017ieee}. Incompletely and irregularly recorded seismic data always have severely negative effects on the subsequent data processing work flow, such as surface related multiple elimination, velocity analysis, full waveform inversion, wave equation migration, time-frequency analysis, amplitude versus offset inversion and seismic interpretation \cite{verschuure1991,shuwei20153,shuwei2016vscan,liuwei2016dealiase}.

Seismic data reconstruction, therefore, has drawn a large amount of attention from both academia and industry in the past several decades. It can be divided into two very basic categories: model-driven methods and data-driven methods. Although model driven methods are powerful and could be highly accurate, \old{a prior}\new{a-priori} knowledge about the model needs to be provided, while it is not simple at all to build an accurate model. In addition to \old{a prior}\new{a-priori} knowledge about the model, computational cost is another big issue for model-driven reconstruction methods. On the contrary, data-driven reconstruction methods are significantly popular among seismic exploration community because of their higher efficiency and less dependency on model. Usually, simple mathematical assumptions are utilized in data-driven methods for interpolating seismic data, which turns out to be more solid and effective. Since the last decade, a majority of researchers have made lots of efforts to investigate all different types of data-driven reconstruction methods. In recent years, dictionary learning and machine learning are applied to the reconstruction of 5D simple data \cite{YuSiwei2015, YuSiwei2016, Jia2017, amir2017sp,amir2017geo, Jia2018}. Data driven tight frame (DDTF) is a kind of dictionary-learning method, which can simultaneously denoise and interpolate 5D seismic data \cite{YuSiwei2015}. In DDTF, a sparsity-promoting algorithm is used to build the dictionary which can represent the observed data and estimate the complete data. \cite{Jia2017} combined the DDTF with a classic machine learning method named support vector regression (SVR) to optimize the learning, which obtained better performance than the Gauss SVR method. With the continuous improvement of intelligent methods, learning-based 5D data reconstruction will be a hot research topic in the future.

In the seismic data processing literature, it is also noticed that the challenge of random noise always comes along with data reconstruction. In general, random noise suppression is of significant importance for both increasing the signal-to-noise ratio ($SNR$) \cite{yangkang2015ortho} and improving seismic data reconstruction performance. Random noise are capable of severely affecting the final performances of reconstruction methods, and thus, much attention has been drawn to random noise attenuation algorithms \cite{guochang2012,fxnaghizadeh,beckouche,yangkang2015ortho}. While most random noise attenuation approaches utilize the signal predictability, the irregularity of seismic data can directly influence this predictability and result in unsatisfactory denoising performance. Because of these mutual influences mentioned above between random noise suppression and data reconstruction, simultaneous reconstruction and denoising approaches are widely studied in \cite{oropezamssa}, \cite{gaomssa}, \cite{Gaogp}, \cite{gholami}, \cite{benfengpocs} and \cite{pmf}. Among all these approaches, low-rank approximation methods are most commonly studied.

Meanwhile in recent years, simultaneous 5D seismic data reconstruction and denoising have become very popular due to the fact that it is capable of taking all physical dimensions of seismic data into consideration \cite{Liubin2004, Trad2007, Trad2009}, and thus, can take advantage of more data constraints and correlations to improve the reconstruction performance even at an extremely high data missing ratio. Especially when compared with 2D and 3D data cases, 5D data interpolation and denoising can always provide much better results. There exist two different categories for 5D interpolation: Fourier based approaches and low-rank approximation based approaches. Nowadays, 5D Fourier based interpolation methods have already become a standard for industry due to its stability and efficiency. Nevertheless, it is reported that the reconstruction performance of 5D Fourier based methods is less accurate than the low-rank approximation based approaches especially when dealing with curved events. On the other hand, low-rank approximation methods for simultaneous 5D seismic data reconstruction and denoising are widely studied during the last decade.

low-rank approximation approaches still have two subcategories: tensor based methods and block Hankel\new{/Toeplitz} matrix based methods. The first category regards multi-dimensional data as multi-linear arrays and applies dimensionality reduction on multi-linear arrays, in which some folding and unfolding operations are utilized. These methods are usually referred to as tensor completion. The other category transforms seismic data into multi-level block Hankel\new{/Toeplitz} matrix and a rank reduction algorithm can be used to recover the data, which can also be named multichannel singular spectrum analysis (MSSA) or Cadzow filtering. Although simultaneous 5D seismic data reconstruction and denoising via low-rank approximation becomes more attractive recently, there are still many challenges within this framework. \new{Major issues in low-rank approximation approaches for 5D data interpolation are \cite{Xie2017}: (1) high computational cost during SVD process, (2) the inevitable residual noise \cite{yangkang2016irr5d} and (3) the rank inconsistency problem \cite{yangkang2020odrr}}.

Firstly, high computational cost during SVD process is the biggest problem we encounter to overcome especially for 5D dataset \cite{lu2015fast,jinkun2016}. Since our target multi-level block Hankel\new{/Toeplitz} matrix or tensor array tends to be extremely large, the truncated SVD process consumes huge amounts of time. Many researchers have made lots of efforts to solve this problem. \cite{oropezamssa} proposed to replace truncated SVD with randomized SVD to accelerate the MSSA based rank reduction method. \cite{gaomssa} introduced a fast rank reduction approach along four spacial dimensions based on Lanczos bidiagonalization. Instead of accelerated low-rank approximation for multi-level Hankel\new{/Toeplitz} matrix, \cite{pmf} presented a tensor completion based fast algorithm via parallel matrix factorization to speed up the 5D interpolation process. \new{Recently, \cite{jianjun2017five} developed a parallel square matrix factorization method for efficient 5D data reconstruction without SVD calculation, which however could be difficult in the implementation.}

Secondly, the recently discovered inevitable residual noise is another big issue preventing low-rank approximation approaches from having even better performance \cite{gavish2014optimal,trickett2015preserving,aharchaou2017singular,yatong2018gji}. Usually, conventional low-rank approximation methods can obtain reasonably good results while there are still amount of visible residual noise left, which is more severe for land seismic data. The reason behind is simply due to the incomplete decomposition between signals and noise. \cite{weilin2016} first noticed the inevitable residual noise during the truncated SVD process in MSSA for random noise attenuation and it is proved that the residual noise come from the signal-plus-noise subspace, which is decomposed by the truncated SVD. Therefore, damped MSSA is proposed to mitigate this noise leakage problem by introducing a damping factor to better decompose the signal and noise \cite{weilin2016}. Note that the later proposed double least-squares projection has more or less the similar concept with damped MSSA \cite{weilingieeedls}. \cite{dong} proposed a multi-step damped MSSA algorithm to further improve the SNR during reconstruction. \new{Straightforwardly, \cite{yangkang2016irr5d} extended damped MSSA to simultaneous 5D seismic data reconstruction and denoising in the condition with extremely noisy land seismic data. A much cleaner and more robust 5D interpolation result can be obtained by imposing more accurate signal and noise space decomposition.} In addition, \cite{dong2017} presented a novel hybrid rank sparsity constraint on seismic data to improve the interpolation performance with less residual noise. This hybrid constraint can take advantage of both constraints to upgrade the final results. \wen{A similar strategy hybrid model was proposed in \cite{yufeng2017} based on a different framework called the three-operator proximal splitting scheme.}

Thirdly, an easily neglected but highly important issue is the rank inconsistency problem during low-rank approximation \cite{yangkangelra,shaohuan2017gji,baimin2018cg}. Seismic events are usually complicated, therefore, it is difficult to select a single appropriate rank value for the whole dataset. If the rank is chosen too large, little noise will be removed and if the rank is too small, even useful signals are lost. An effective strategy to mitigate this issue is to process the data within local windows, which better satisfies the basic linear assumption of low-rank approximation methods. However, it still fails due to highly nonstationary property of seismic data in both time and space, for example, when dealing with crossing events where the rank should be higher than other local windows. \cite{yangkangelra} proposed empirical low-rank approximation, in which the multi-dip data are decomposed to multiple single-dip data so that the optimal rank one can be applied to each local window. \new{More recently, \cite{yangkang2020odrr} developed an adaptive rank thresholding method to make the damped rank-reduction method suitable for local processing.}

In this paper, we address the first issue, i.e., the problem of low computational efficiency, of the low-rank approximation methods. We discuss an SVD-free low-rank approximation method for efficient and effective reconstruction and denoising of 5D seismic data that contains four spatial dimensions. Our SVD-free rank constraint model is based on an alternating minimization strategy, which updates one variable each time while fixing the other two. For each update, we only need to solve a linear least-squares problem with much more efficient QR factorization. We compare the performance of the traditional SVD-based and the proposed SVD-free low-rank approximation methods in detail. Extensive results show that the proposed SVD-free low-rank approximation method can obtain similar performance as the traditional SVD-based method, but with a much higher computing speed. The computational efficiency becomes more noticeable when the data size becomes larger.

\section{low-rank approximation framework for 5D seismic data}
\wen{\subsection{The inverse problem}
The 5D reconstruction problem aims to solve the following inverse problem \cite{oropezamssa,stanton2013processing,gaomssa}:
\begin{equation}
\label{eq:5d}
\mathbf{D}^{obs}=\mathcal{S}\circ \mathbf{D}^{ideal},
\end{equation}
where $\mathbf{D}^{obs}$ denotes the observed data, $\mathbf{D}^{ideal}$ denotes the complete data, and $\mathcal{S}$ denotes the sampling operator,  which can be more specifically displayed as follows:
\begin{equation}
\mathcal{S}(i,j)=\left\{
\begin{array}{lr}
1, & for \ (i,j) \in \Omega\\             
0, & for \ (i,j) \notin \Omega
\end{array}
\right..
\end{equation}
$\Omega$ represents the subset of observed indices. $\mathcal{S}$ equals 1 at the observation point while 0 at the missing traces. $\circ$ denotes element-wise product. Both $\mathbf{D}^{obs}$ and $\mathbf{D}^{ideal}$ are considered in the frequency domain.}

The inverse problem can be solved via the rank-reduction method, based on a weighted iterative algorithm \cite{oropezamssa,gaomssa}:
\begin{equation}
\label{eq:mssapocs}
\begin{split}
&\mathbf{D}_n=a_n \mathbf{D}_{obs} + (1-a_n) \mathcal{S}\circ \mathcal{M} \mathbf{D}_{n-1} + (1-\mathcal{S}) \circ\mathcal{M}\mathbf{D}_{n-1},\\
&\qquad n=1,2,3,\cdots,n_{max},
\end{split}
\end{equation}
where $\mathbf{D}_0=\mathbf{D}_{obs}$. The operator $\mathcal{M}$ represents the low-rank approximation operator that is based on \new{truncated singular value decomposition (TSVD)}\old{TSVD} for rank reduction.  $a_n$ is an iteration-dependent scalar that linearly decreases from $a_1=1$ to $a_{n_{max}}=0$.  The algorithm stops when either a maximum number of iterations $n_{max}$ has been reached or $\Arrowvert \mathbf{D}_n - \mathbf{D}_{n-1}\Arrowvert_F^2 \leq tol$. $tol$ denotes a very small tolerance value. In fact, equation \ref{eq:mssapocs} represents the general low-rank approximation for simultaneous seismic data reconstruction and denoising. Next, we will introduce the rank constraint model that is connected with the rank-reduction operator.

\subsection{The rank constraint model}
Presuming the original data matrix $\mathbf{X}$ is of low-rank structure, due to the theory of matrix completion, the randomly missing data can be reconstructed by a rank-minimizing model:
\begin{equation}
\label{eq:rank1}
\begin{split}
\min_{\mathbf{X}} & \quad \text{rank}(\mathbf{H} \mathbf{X}) \qquad s.t. \ \mathbf{X}_{i,j,k,l}=\mathbf{Y}_{i,j,k,l}\\
 & \text{for} \  (i,j,k,l) \in \Omega,
 \end{split}
\end{equation}
where $rank(\mathbf{H} \mathbf{X})$ is the number of non-zero singular values of $\mathbf{H} \mathbf{X}$. $\mathbf{H}$ denotes some mapping operations, for instance, the block Hankelization\new{/Toeplitization} operator in equation \ref{eq:hankelopt}. $\mathbf{Y}$ is the observed seismic data. \dlo{$\Omega$ represents the subset of observed indices.}

The constrained minimization problem in equation \ref{eq:rank1} can be converted to the unconstrained minimization problem in equation \ref{eq:rank2} by introducing the balancing parameter:
\begin{equation}
\label{eq:rank2}
\min_{\mathbf{X}} rank(\mathbf{H} \mathbf{X}) + \frac{1}{2} \mu \Arrowvert \mathbf{S}_{\Omega}(\mathbf{X}) -\mathbf{Y}\Arrowvert_F^2,
\end{equation}
where $\Arrowvert\cdot\Arrowvert_F$ denotes the Frobenius norm. $\mathbf{S}_{\Omega}$ denotes trace sampling. $\mu$ denotes balancing coefficient, which can balance the weight between rank constraint and data misfit. In practice, this balancing parameter is explicitly connected to the estimated rank value in the rank constraint.

\dlo{Inspired by ? and ?, the conventional rank constraint model for 5D seismic data can be solved as follows: Take a block of 5D seismic data $\mathbf{D}_{time}(t,hx,hy,x,y)$ of $N_t$ by $N_{hx}$ by $N_{hy}$ by $N_x$ by $N_y$ samples $(t=1\cdots N_t, hx=1\cdots N_{hx}, hy=1\cdots N_{hy}, x=1\cdots N_x,y=1\cdots N_y)$ into consideration. The low-rank approximation works on seismic data as follows: first, the low-rank approximation directly transforms $\mathbf{D}_{time}(t,hx,hy,x,y)$ into $\mathbf{D}_{freq}(\omega,hx,hy,x,y), (\omega=1\cdots N_\omega)$ of complex values in the frequency domain. Each frequency slice in the data, at a specific frequency $\omega_0$, can be described by $\mathbf{D}(\omega_0)$. For simplicity, we drop the argument $\omega_0$ to avoid notational clutter. So now the 5D seismic data can be regarded as a number of 4D frequency data slices or matrices. }
The transformation of the 4D data matrix into a level-four block Hankel\new{/Toeplitz} matrix can be represented in operator notation as follows:
\begin{equation}
\label{eq:hankelopt}
\mathbf{M}=\mathcal{H}\mathbf{D},
\end{equation}
where $\mathcal{H}$ denotes the level-four block Hankelization\new{/Toeplitization} operator. \dlo{The detailed construction process of level-four Hankelization operator is elaborated in the Appendix A.}

Both missing traces and additive noise increase the rank of the matrix $\mathbf{M}$, which originally possesses low-rank structure. We assume that $\mathbf{M}$ has full rank, $rank(\mathbf{M})=J$ and the desired low-rank matrix $\mathbf{M}_K$ has deficient rank, $rank(\mathbf{M}_K)=K<J$. Therefore, the desired low-rank approximation can be obtained by a rank reduction method using truncated singular value decomposition (TSVD):
\begin{equation}
\label{eq:reductionopt}
\mathbf{M}_K=\mathbf{U}_K\mathbf{U}_K^H\mathbf{M}=\mathcal{R}_K\mathbf{M},
\end{equation} 
where we use $\mathcal{R}_K$ as the rank reduction operator via TSVD. $\mathbf{U}_K$ resulting from TSVD denotes the first $K$ singular vectors of matrix $\mathbf{M}$. The symbol $[\cdot]^H$ represents the conjugate transpose of a matrix. \new{Due to the TSVD step, the low-rank approximation method discussed in this paper can also be understood as a PCA method \cite{weilingieeedls}.}

After rank reduction, the filtered data can be recovered with random noise attenuated and missing traces reconstructed via properly averaging along the anti-diagonals of the target low-rank approximation matrix $\mathbf{M}_K$: 
\begin{equation}
\label{eq:mssaopt}
\hat{\mathbf{D}}=\mathcal{A}\mathbf{M}_{K}=\mathcal{A}\mathcal{R}_K\mathbf{M}=
\mathcal{A}\mathcal{R}_K\mathcal{H}\mathbf{D}=\mathcal{M}\mathbf{D},
\end{equation}
where $\mathcal{A}$ denotes the averaging operator. \dlo{The operator $\mathcal{M}$ represents the low-rank approximation operator that is based on TSVD for rank reduction.}

Here is a complete and detailed description of low-rank approximation framework for 5D seismic data. We adopt the following algorithm for reconstructing 5D noisy seismic data with missing traces:
\begin{algorithm}{LR}{\mathcal{S},\mathcal{F}_d,\mathbf{D}_{obs}(t,hx,hy,x,y),a_n,tol,N,F}
	\mathbf{D}_{obs}(w,hx,hy,x,y) \= \mathbf{D}_{obs}(t,hx,hy,x,y)\\
	 \text{by 1D forward FFT} \\
	\mathbf{D}_0 \= \mathbf{D}_{obs} \\
	\begin{FOR}{f \= 1, 2, \ldots, F} \\	
		\begin{FOR}{n \= 1, 2, \ldots, N} \\
			\mathbf{D}_n^f \= a_n \mathbf{D}_{obs}^f + (1-a_n) \mathcal{S} \circ \mathcal{F}_d \mathbf{D}_{n-1}^f\\
			 + (1-\mathcal{S}) \circ \mathcal{F}_d \mathbf{D}_{n-1}^f\\
			\begin{IF}{\Arrowvert \mathbf{D}_n^f - \mathbf{D}_{n-1}^f \Arrowvert_F^2 \leq tol} 
				\RETURN \mathbf{D}_n^f
			\end{IF}     
		\end{FOR} \\
		\RETURN \mathbf{D}_N^f
	\end{FOR}\\ 
	\RETURN \mathbf{D}_{recoverd}\\
	\mathbf{D}_{recoverd}(t,hx,hy,x,y) \= \mathbf{D}_{recoverd}(w,hx,hy,x,y) \\
	\text{by 1D inverse FFT}
\end{algorithm}
The iteration terminates after all $F$ frequencies are finished. For each frequency slice, the iteration terminates after $N$ iterations or upon reaching convergence to the specified tolerance $tol$.

\section{Fast and robust low-rank approximation approach}
Both conventional rank constraint and its solution are valid and robust, however, the computational cost is a major issue due to SVD in the low-rank approximation framework. SVD consumes most computational time during the whole process and it is especially severe for large scale problem, such as 5D seismic data reconstruction. In order to avoid SVD-related computations, we introduce a new SVD-free rank constraint model \wen{following \cite{lmafit}}.

\subsection{SVD-free rank constraint model}
Still presuming the original data matrix $\mathbf{X}$ is of low-rank structure, our target level-four block Hankel\new{/Toeplitz} matrix after mapping $\mathbf{H}\mathbf{X}$  possess the same property. It is common sense that $m$ by $n$ matrix $\mathbf{H}\mathbf{X}$ with rank up to $K$ can be represented by a matrix product $\mathbf{H}\mathbf{X}=\mathbf{P}\mathbf{Q}$ where the size of $\mathbf{P}$ is $m$ by $K$ and the size of $\mathbf{Q}$ is $K$ by $n$. A new SVD-free rank constraint model can be expressed as:
\begin{equation}
\label{eq:rank11}
\min_{\mathbf{P},\mathbf{Q},\mathbf{R}} \Arrowvert \mathbf{P}\mathbf{Q} -\mathbf{R}\Arrowvert_F^2, \qquad s.t. \ \mathbf{R}_{i,j}=(\mathbf{H}\mathbf{Y})_{i,j}, \qquad for \  (i,j) \in \Omega,
\end{equation}
where $\mathbf{R}$ is introduced mainly for a computational reason. \new{$\mathbf{P}$ and $\mathbf{Q}$ are the two low-rank decomposition matrices using the SVD-free algorithm, such that the product of the estimated $\mathbf{P}$ and $\mathbf{Q}$ is the low-rank approximated result. } The advantage of this new SVD-free rank constraint model is the higher computational efficiency without costly SVD-related process. More specifically speaking, normal QR factorization instead of full or partial SVD is the principle components for computation.

Similar to other algorithms, the solution to our SVD-free rank constraint model should be naturally based on an alternating minimization strategy. That is to say, updating one variable each time while fixing the other two. For each update, we only need to solve a linear least-squares problem with much less expensive QR factorization. In addition, a more complex nonlinear successive over-relaxation scheme with dynamically adjusted relaxation weight is utilized \cite{lmafit}. The detailed updates in each iteration are displayed as follows:

\begin{equation}
\label{eq:lmafit1}
\mathbf{P}_{\ast}=\omega\mathbf{R}\mathbf{Q}^T(\mathbf{Q}\mathbf{Q}^T)^{\dagger} + (1-\omega)\mathbf{P},
\end{equation}
\begin{equation}
\label{eq:lmafit2}
\mathbf{Q}_{\ast}=\omega(\mathbf{P}_{\ast}^T\mathbf{P}_{\ast})^{\dagger}(\mathbf{P}_{\ast}^T\mathbf{R}) + (1-\omega)\mathbf{Q},
\end{equation}
\begin{equation}
\label{eq:lmafit3}
\mathbf{R}_{\ast}=\mathbf{P}_{\ast}\mathbf{Q}_{\ast} + \mathbf{S}_{\Omega}^{H}(\mathbf{H}\mathbf{Y}-\mathbf{P}_{\ast}\mathbf{Q}_{\ast}),
\end{equation}
where $(.)^{\dagger}$ denotes the Moore-Penrose pseudo-inverse of a target matrix, which is implemented by a normal QR algorithm. $\omega$ is the relaxation weight parameter and $\mathbf{S}_{\Omega}^{H}$ represents sampling on the Hankel\new{/Toeplitz} matrix instead of the original data matrix. $\mathbf{P}_{\ast}$, $\mathbf{Q}_{\ast}$ and $\mathbf{R}_{\ast}$ are the updated version of $\mathbf{P}$, $\mathbf{Q}$ and $\mathbf{R}$.

To improve the efficiency of the introduced algorithm, an update on the relaxation weight parameter is used based on the calculation of residual ratio $\gamma$ \wen{\cite{lmafit}}:
\begin{equation}
\label{eq:iter_cri1}
\gamma=\dfrac{\Arrowvert \mathbf{W}_{\ast}\Arrowvert_F}{\Arrowvert \mathbf{W}\Arrowvert_F},
\end{equation}
where
\begin{equation}
\label{eq:iter_cri2}
\mathbf{W}=\mathbf{S}_{\Omega}^{H}(\mathbf{H}\mathbf{Y}-\mathbf{P}\mathbf{Q}),
\end{equation}
\begin{equation}
\label{eq:iter_cri3}
\mathbf{W}_{\ast}=\mathbf{S}_{\Omega}^{H}(\mathbf{H}\mathbf{Y}-\mathbf{P}_{\ast}\mathbf{Q}_{\ast}),
\end{equation}
if $\gamma>1$, we simply reset $\omega$ to 1 and if $\gamma<1$, we should keep it unchanged. However, if $\gamma<1$ but is close to $1$, we need to increase $\omega$ to $min(\omega+\tau, \omega_{max})$. Here, $\tau$ is a tiny increment and $\omega_{max}$ is the maximum value that $\omega$ can be.

\new{\subsection{Fast 5D reconstruction}}
Therefore, according to equations \ref{eq:lmafit1}, \ref{eq:lmafit2} and \ref{eq:lmafit3}, the new SVD-free rank constraint model can be effectively solved. \wen{Note that a proof of the convergence of SVD-free low-rank approximation algorithm can be found in \cite{lmafit}.} Due to the absence of SVD-related calculation, the new model is generally able to have a large speedup compared to the conventional model. Besides, it is extremely easy to apply the new model to the low-rank approximation framework. The whole solution to new model can be regarded as a low-rank approximation operator, and then equation \ref{eq:mssaopt} can be revised to:
\begin{equation}
\label{eq:lmafitopt}
\hat{\mathbf{D}}=\mathcal{A}\mathbf{M}_{L}=\mathcal{A}\mathcal{R}_L\mathbf{M}=
\mathcal{A}\mathcal{R}_L\mathcal{H}\mathbf{D}=\mathcal{L}\mathbf{D},
\end{equation}
where $\mathcal{R}_L$ denotes the rank reduction operator based on the SVD-free rank constraint model and $\mathcal{L}$ is its corresponding low-rank approximation operator. The final fast and robust low-rank approximation framework for 5D seismic data is introduced as follows:
\begin{equation}
\label{eq:lmafitpocs}
\begin{split}
\mathbf{D}_n&=a_n \mathbf{D}_{obs} + (1-a_n) \mathcal{S}\circ \mathcal{L} \mathbf{D}_{n-1} + (1-\mathcal{S})\circ \mathcal{L}\mathbf{D}_{n-1},\\
& n=1,2,3,\cdots,n_{max}.
\end{split}
\end{equation} 
 it is clear that the only difference between equations \ref{eq:mssapocs} and \ref{eq:lmafitpocs} is the SVD-free rank constraint based low-rank approximation operator.

\new{It is the first time that the fast SVD-free low-rank decomposition method \cite{lmafit} is used in the 5D seismic reconstruction problem. It is known that the matrix completion is a common mathematical model. The method developed in \cite{lmafit} is a general solution to accelerate a matrix completion problem. It was developed to accelerate a variety of real-world applications, like the one in this paper. Here, we leverage this fast algorithm to accelerate the state-of-the-art 5D seismic reconstruction framework.}
%\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt){linear_time/Fig/synth-ss}
%{Magnetization as a function of applied field.
%It is good practice to explain the significance of the figure in the caption.\label{fig1}}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-clean-3d}
   \label{fig:syn5d-clean-3d}}
 \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-noisy-3d}
   \label{fig:syn5d-noisy-3d}}
 \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-decimated-3d}
   \label{fig:syn5d-decimated-3d}}        
  \caption{Common offset gathers for the 5D synthetic example with linear events. (a) Clean data. (b) Noisy data. (c) The observed data with 80\% traces randomly removed.}
  \label{fig:syn5d-clean-3d,syn5d-noisy-3d,syn5d-decimated-3d}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-svd-3d}
    \label{fig:syn5d-svd-3d}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-n-svd-3d}
    \label{fig:syn5d-n-svd-3d}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-r-svd-3d}
    \label{fig:syn5d-r-svd-3d}} 
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-lmafit-3d}
    \label{fig:syn5d-lmafit-3d}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-n-lmafit-3d}
    \label{fig:syn5d-n-lmafit-3d}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-r-lmafit-3d}
    \label{fig:syn5d-r-lmafit-3d}}       
   \caption{Comparison of reconstruction performance in common offset gathers for the 5D synthetic example with linear events. (a) Reconstructed data using the SVD-based low-rank approximation method. (b) The removed noise from the noisy data corresponding to (a). (c) The reconstruction error corresponding to (a). (d) Reconstructed data using the SVD-free low-rank approximation method. (e) The removed noise from the noisy data corresponding to (d). (f) The reconstruction error corresponding to (d).}
\label{fig:syn5d-svd-3d,syn5d-n-svd-3d,syn5d-r-svd-3d,syn5d-lmafit-3d,syn5d-n-lmafit-3d,syn5d-r-lmafit-3d}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-clean-3d-1}
    \label{fig:syn5d-clean-3d-1}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-noisy-3d-1}
    \label{fig:syn5d-noisy-3d-1}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-decimated-3d-1}
    \label{fig:syn5d-decimated-3d-1}}        
   \caption{Common midpoint gathers for the 5D synthetic example with linear events. (a) Clean data. (b) Noisy data. (c) The observed data with 80\% traces randomly removed.}
   \label{fig:syn5d-clean-3d-1,syn5d-noisy-3d-1,syn5d-decimated-3d-1}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-svd-3d-1}
    \label{fig:syn5d-svd-3d-1}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-n-svd-3d-1}
    \label{fig:syn5d-n-svd-3d-1}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-r-svd-3d-1}
    \label{fig:syn5d-r-svd-3d-1}} 
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-lmafit-3d-1}
    \label{fig:syn5d-lmafit-3d-1}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-n-lmafit-3d-1}
    \label{fig:syn5d-n-lmafit-3d-1}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-r-lmafit-3d-1}
    \label{fig:syn5d-r-lmafit-3d-1}}       
   \caption{Comparison of reconstruction performance in common midpoint gathers for the 5D synthetic example with linear events. (a) Reconstructed data using the SVD-based low-rank approximation method. (b) The removed noise from the noisy data corresponding to (a). (c) The reconstruction error corresponding to (a). (d) Reconstructed data using the SVD-free low-rank approximation method. (e) The removed noise from the noisy data corresponding to (d). (f) The reconstruction error corresponding to (d).}
\label{fig:syn5d-svd-3d-1,syn5d-n-svd-3d-1,syn5d-r-svd-3d-1,syn5d-lmafit-3d-1,syn5d-n-lmafit-3d-1,syn5d-r-lmafit-3d-1}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-clean-2d}
    \label{fig:syn5d-clean-2d}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-noisy-2d}
    \label{fig:syn5d-noisy-2d}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-decimated-2d}
    \label{fig:syn5d-decimated-2d}} 
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-svd-2d}
    \label{fig:syn5d-svd-2d}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-lmafit-2d}
    \label{fig:syn5d-lmafit-2d}}    
   \caption{Comparison of reconstruction performance in a 2D section. (a) Clean data. (b) Noisy data. (c) The observed data. (d) Reconstructed data using the SVD-based low-rank approximation method. (e) Reconstructed data using the SVD-free low-rank approximation method.}
\label{fig:syn5d-clean-2d,syn5d-noisy-2d,syn5d-decimated-2d,syn5d-svd-2d,syn5d-lmafit-2d}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=0.45\textwidth]{linear_time/Fig/synth-ss}
   \caption{Comparison of the middle trace amplitude of each cubes in different datasets. The black line denotes the trace from the clean data.  The red line denotes the noisy data. The observed trace cannot be seen from this FIGURE because it is a blank trace in the selection position. The SVD-based and SVD-free methods are denoted as blue and green lines, respectively.}
   \label{fig:synth-ss}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/simi-syn5d-noisy-2d}
    \label{fig:simi-syn5d-noisy-2d}}
  \subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/simi-syn5d-decimated-2d}
    \label{fig:simi-syn5d-decimated-2d}} \\
  \subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/simi-syn5d-svd-2d}
    \label{fig:simi-syn5d-svd-2d}} 
  \subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/simi-syn5d-lmafit-2d}
    \label{fig:simi-syn5d-lmafit-2d}}  
   \caption{Comparison of reconstruction performance in terms of local similarity. (a) Local similarity of the noisy data. (b) Local similarity of the observed data. (c) Local similarity of the reconstructed data using SVD-based low-rank approximation method. (d) Local similarity of the reconstructed data using SVD-free low-rank approximation method.}
\label{fig:simi-syn5d-noisy-2d,simi-syn5d-decimated-2d,simi-syn5d-svd-2d,simi-syn5d-lmafit-2d}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-clean-3d-1}
    \label{fig:curve5d-clean-3d-1}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-noisy-3d-1}
    \label{fig:curve5d-noisy-3d-1}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-decimated-3d-1}
    \label{fig:curve5d-decimated-3d-1}}        
   \caption{Common midpoint gathers for the 5D synthetic example with hyperbolic events. (a) Clean data. (b) Noisy data. (c) The observed data with 80\% traces randomly removed.}
   \label{fig:curve5d-clean-3d-1,curve5d-noisy-3d-1,curve5d-decimated-3d-1}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-svd-3d-1}
    \label{fig:curve5d-svd-3d-1}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-n-svd-3d-1}
    \label{fig:curve5d-n-svd-3d-1}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-r-svd-3d-1}
    \label{fig:curve5d-r-svd-3d-1}} 
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-lmafit-3d-1}
    \label{fig:curve5d-lmafit-3d-1}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-n-lmafit-3d-1}
    \label{fig:curve5d-n-lmafit-3d-1}}
  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-r-lmafit-3d-1}
    \label{fig:curve5d-r-lmafit-3d-1}}       
   \caption{Comparison of reconstruction performance in common midpoint gathers for the 5D synthetic example with hyperbolic events. (a) Reconstructed data using the SVD-based low-rank approximation method. (b) The removed noise from the noisy data corresponding to (a). (c) The reconstruction error corresponding to (a). (d) Reconstructed data using the SVD-free low-rank approximation method. (e) The removed noise from the noisy data corresponding to (d). (f) The reconstruction error corresponding to (d).}
\label{fig:curve5d-svd-3d-1,curve5d-n-svd-3d-1,curve5d-r-svd-3d-1,curve5d-lmafit-3d-1,curve5d-n-lmafit-3d-1,curve5d-r-lmafit-3d-1}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[]{\includegraphics[width=0.45\columnwidth]{curve/Fig/simi-curve5d-noisy-3d-1}
    \label{fig:simi-curve5d-noisy-3d-1}}
 \subfigure[]{\includegraphics[width=0.45\columnwidth]{curve/Fig/simi-curve5d-decimated-3d-1}
    \label{fig:simi-curve5d-decimated-3d-1}} \\
  \subfigure[]{\includegraphics[width=0.45\columnwidth]{curve/Fig/simi-curve5d-svd-3d-1}
    \label{fig:simi-curve5d-svd-3d-1}}
  \subfigure[]{\includegraphics[width=0.45\columnwidth]{curve/Fig/simi-curve5d-lmafit-3d-1}
    \label{fig:simi-curve5d-lmafit-3d-1} }
   \caption{Comparison of reconstruction performance in terms of local similarity. (a) Local similarity of the noisy data. (b) Local similarity of the observed data. (c) Local similarity of the reconstructed data using SVD-based low-rank approximation method. (d) Local similarity of the reconstructed data using SVD-free low-rank approximation method.}
\label{fig:simi-curve5d-noisy-3d-1,simi-curve5d-decimated-3d-1,simi-curve5d-svd-3d-1,simi-curve5d-lmafit-3d-1}
\end{figure}

\begin{figure*}[htb!]
  \centering
  \subfigure[]{\includegraphics[width=\textwidth]{field/Fig/field5d-decimated2d-0}
    \label{fig:field5d-decimated2d-0}}
 \subfigure[]{\includegraphics[width=\textwidth]{field/Fig/field5d-svd2d-0}
    \label{fig:field5d-svd2d-0}}
  \subfigure[]{\includegraphics[width=\textwidth]{field/Fig/field5d-lmafit2d-0}
    \label{fig:field5d-lmafit2d-0}}
   \caption{Comparison of reconstruction performance in common offset gathers for the 5D field data example. (a) Observed data with roughly 80\% traces missing. (b) Reconstructed data using the SVD-based low-rank approximation method. (c) Reconstructed data using the SVD-free low-rank approximation method. The frame box areas are zoomed and highlighted in FIGURE \ref{fig:z-decimated,z-svd,z-lmafit}.}
\label{fig:field5d-decimated2d-0,field5d-svd2d-0,field5d-lmafit2d-0}
\end{figure*}

\begin{figure}[htb!]
  \centering
  \subfigure[]{\includegraphics[width=0.9\columnwidth]{field/Fig/z-decimated}
    \label{fig:z-decimated}}
 \subfigure[]{\includegraphics[width=0.9\columnwidth]{field/Fig/z-svd}
    \label{fig:z-svd}}
  \subfigure[]{\includegraphics[width=0.9\columnwidth]{field/Fig/z-lmafit}
    \label{fig:z-lmafit}}
   \caption{Zoomed comparison of reconstruction performance in common offset gathers for the 5D field data example. (a) Observed data with roughly 80\% traces missing. (b) Reconstructed data using the SVD-based low-rank approximation method. (c) Reconstructed data using the SVD-free low-rank approximation method.}
\label{fig:z-decimated,z-svd,z-lmafit}
\end{figure}

%
%\inputdir{linear} % figure directory
%\multiplot{3}{syn5d-clean-3d,syn5d-noisy-3d,syn5d-decimated-3d}{width=0.28\textwidth}{Common offset gathers for the 5D synthetic example with linear events. (a) Clean data. (b) Noisy data. (c) The observed data with 80\% traces randomly removed. }
%
%\multiplot{6}{syn5d-svd-3d,syn5d-n-svd-3d,syn5d-r-svd-3d,syn5d-lmafit-3d,syn5d-n-lmafit-3d,syn5d-r-lmafit-3d}{width=0.28\textwidth}{Comparison of reconstruction performance in common offset gathers for the 5D synthetic example with linear events. (a) Reconstructed data using the SVD-based low-rank approximation method. (b) The removed noise from the noisy data corresponding to (a). (c) The reconstruction error corresponding to (a). (d) Reconstructed data using the SVD-free low-rank approximation method. (e) The removed noise from the noisy data corresponding to (d). (f) The reconstruction error corresponding to (d).}
%
%\multiplot{3}{syn5d-clean-3d-1,syn5d-noisy-3d-1,syn5d-decimated-3d-1}{width=0.28\textwidth}{Common midpoint gathers for the 5D synthetic example with linear events. (a) Clean data. (b) Noisy data. (c) The observed data with 80\% traces randomly removed.}
%
%\multiplot{6}{syn5d-svd-3d-1,syn5d-n-svd-3d-1,syn5d-r-svd-3d-1,syn5d-lmafit-3d-1,syn5d-n-lmafit-3d-1,syn5d-r-lmafit-3d-1}{width=0.28\textwidth}{Comparison of reconstruction performance in common midpoint gathers for the 5D synthetic example with linear events. (a) Reconstructed data using the SVD-based low-rank approximation method. (b) The removed noise from the noisy data corresponding to (a). (c) The reconstruction error corresponding to (a). (d) Reconstructed data using the SVD-free low-rank approximation method. (e) The removed noise from the noisy data corresponding to (d). (f) The reconstruction error corresponding to (d).}
%
%\multiplot{5}{syn5d-clean-2d,syn5d-noisy-2d,syn5d-decimated-2d,syn5d-svd-2d,syn5d-lmafit-2d}{width=0.28\textwidth}{Comparison of reconstruction performance in a 2D section. (a) Clean data. (b) Noisy data. (c) The observed data. (d) Reconstructed data using the SVD-based low-rank approximation method. (e) Reconstructed data using the SVD-free low-rank approximation method.}
%
%\inputdir{linear_time} 
%\plot{synth-ss}{width=0.9\columnwidth}{Comparison of the middle trace amplitude of each cubes in different datasets. The black line denotes the trace from the clean data.  The red line denotes the noisy data. The observed trace cannot be seen from this figure because it is a blank trace in the selection position. The SVD-based and SVD-free methods are denoted as blue and green lines, respectively. }%The yellow long-dashed line corresponds to $fl=10$ Hz. 
%%	The blue line corresponds to the traditional rank-reduction method. The green line corresponds to the proposed method. Note that the black and green lines are very close to each other, thus the reconstruction error using the proposed approach is much less than the traditional method for most parts.}
%
%\inputdir{linear} 
%\multiplot{4}{simi-syn5d-noisy-2d,simi-syn5d-decimated-2d,simi-syn5d-svd-2d,simi-syn5d-lmafit-2d}{width=0.34\textwidth}{Comparison of reconstruction performance in terms of local similarity. (a) Local similarity of the noisy data. (b) Local similarity of the observed data. (c) Local similarity of the reconstructed data using SVD-based low-rank approximation method. (d) Local similarity of the reconstructed data using SVD-free low-rank approximation method.}
%
%\inputdir{curve} % figure directory
%\multiplot{3}{curve5d-clean-3d-1,curve5d-noisy-3d-1,curve5d-decimated-3d-1}{width=0.28\textwidth}{Common midpoint gathers for the 5D synthetic example with hyperbolic events. (a) Clean data. (b) Noisy data. (c) The observed data with 80\% traces randomly removed. }
%
%\multiplot{6}{curve5d-svd-3d-1,curve5d-n-svd-3d-1,curve5d-r-svd-3d-1,curve5d-lmafit-3d-1,curve5d-n-lmafit-3d-1,curve5d-r-lmafit-3d-1}{width=0.28\textwidth}{Comparison of reconstruction performance in common midpoint gathers for the 5D synthetic example with hyperbolic events. (a) Reconstructed data using the SVD-based low-rank approximation method. (b) The removed noise from the noisy data corresponding to (a). (c) The reconstruction error corresponding to (a). (d) Reconstructed data using the SVD-free low-rank approximation method. (e) The removed noise from the noisy data corresponding to (d). (f) The reconstruction error corresponding to (d).}
%
%
%\multiplot{4}{simi-curve5d-noisy-3d-1,simi-curve5d-decimated-3d-1,simi-curve5d-svd-3d-1,simi-curve5d-lmafit-3d-1}{width=0.34\textwidth}{Comparison of reconstruction performance in terms of local similarity. (a) Local similarity of the noisy data. (b) Local similarity of the observed data. (c) Local similarity of the reconstructed data using SVD-based low-rank approximation method. (d) Local similarity of the reconstructed data using SVD-free low-rank approximation method.}

%\inputdir{./}
%\multiplot{2}{sr0,sr}{width=\textwidth}{\wen{(a) Source-receiver geometry for the SEG/EAGE salt synthetic data. (b) Source-receiver geometry for the decimated data. Red stars denote the shot positions. Blue inverted triangles denote the receiver positions.} }
%
%\multiplot{2}{sr00,sr11}{width=\textwidth}{\wen{(a) Source-receiver geometry for five representative shots without missing traces. (b) Source-receiver geometry for five representative shots with missing traces. Red stars denote the shot positions. Blue inverted triangles denote the receiver positions.} }

%\plot{bin}{width=0.8\textwidth}{\wen{Schematic plot demonstrating the data binning process (in a 2D surface view). The circles denote the binned regular grid points with (red) and without (green) waveform data. The black triangles denote the irregularly distributed receivers. Those within one grid distance to the nearby nodes contribute to the waveform stacking. The grid points without nearby stations are empty and need to be reconstructed.}}

%\inputdir{segeage}
%\multiplot{3}{seg0-3d-sxy,seg-svd-3d-sxy-rr,seg-svd-3d-sxy-lmafit}{width=0.45\textwidth}{\wen{Result of the SEG/EAGE salt example in common offset domain. (a) Incomplete data. (b) Reconstructed data using the SVD-based low-rank approximation method. (c) Reconstructed data using the SVD-free low-rank approximation method.} }
%
%\multiplot{3}{seg0-3d-hxy,seg-svd-3d-hxy-rr,seg-svd-3d-hxy-lmafit}{width=0.38\textwidth}{\wen{Result of the SEG/EAGE salt example in common shot-point domain. (a) Incomplete data. (b) Reconstructed data using the SVD-based low-rank approximation method. (c) Reconstructed data using the SVD-free low-rank approximation method.} }
%
%\multiplot{4}{seg0-2d-sxy-1,seg0-2d-sxy-2,seg1-2d-sxy-1,seg1-2d-sxy-2}{width=0.45\textwidth}{\wen{Comparison of 2D slices in common offset domain. (a) Incomplete data with SX=4340 m. (b) Reconstructed data with SX=4340 m using the proposed method. (c) Incomplete data with SX=5460 m. (d) Reconstructed data with SX=5460 m using the proposed method.} }
%
%\multiplot{4}{seg0-2d-sxy-3,seg0-2d-sxy-4,seg1-2d-sxy-3,seg1-2d-sxy-4}{width=0.38\textwidth}{\wen{Comparison of 2D slices in common offset domain. (a) Incomplete data with SY=3433 m. (b) Reconstructed data with SY=5845 m using the proposed method. (c) Incomplete data with SY=3433 m. (d) Reconstructed data with SX=5845 m using the proposed method.} }
%
%
%\multiplot{4}{seg0-2d-hxy-1,seg0-2d-hxy-2,seg1-2d-hxy-1,seg1-2d-hxy-2}{width=0.38\textwidth}{\wen{Comparison of 2D slices in common shot-point domain. (a) Incomplete data with HX=-100 m. (b) Reconstructed data with HX=20 m using the proposed method. (c) Incomplete data with HX=-100 m. (d) Reconstructed data with HX=20 m using the proposed method.} }
%
%\multiplot{4}{seg0-2d-hxy-3,seg0-2d-hxy-4,seg1-2d-hxy-3,seg1-2d-hxy-4}{width=0.45\textwidth}{\wen{Comparison of 2D slices in common shot-point domain. (a) Incomplete data with T=1.6 s (T denotes time). (b) Reconstructed data with T=2.4 s using the proposed method. (c) Incomplete data with T=1.6 s. (d) Reconstructed data with T=2.4 s using the proposed method.} }
%

%\renewcommand{\figdir}{field} % figure directory
%\inputdir{field}
%\multiplot{3}{field5d-decimated2d-0,field5d-svd2d-0,field5d-lmafit2d-0}{width=0.7\textwidth}{Comparison of reconstruction performance in common offset gathers for the 5D field data example. (a) Observed data with roughly 80\% traces missing. (b) Reconstructed data using the SVD-based low-rank approximation method. (c) Reconstructed data using the SVD-free low-rank approximation method. The frame box areas are zoomed and highlighted in Figure \ref{fig:z-decimated,z-svd,z-lmafit}.}
%
%\multiplot{3}{z-decimated,z-svd,z-lmafit}{width=0.45\textwidth}{Zoomed comparison of reconstruction performance in common offset gathers for the 5D field data example. (a) Observed data with roughly 80\% traces missing. (b) Reconstructed data using the SVD-based low-rank approximation method. (c) Reconstructed data using the SVD-free low-rank approximation method.}

\begin{table*}[h]
\caption{Comparison of computational cost of both the SVD-based and SVD-free low-rank approximation for different data sizes \wen{based on an Intel Core i7 CPU}.}
    \begin{center}
     \begin{tabular}{|c|c|c|c|} 
	  \hline Data size & $100\times10^4$  &  $100\times20^2\times10^2$  &   $300\times20^2\times10^2$ \\ 
	  \hline SVD-based (s) & 603 & 14320 & 92318 \\
      	  \hline SVD-free (s) & 153 & 2753 & 15302	       		 \\ 
          \hline
    \end{tabular} 
   \end{center}
\label{tbl:time}
\end{table*}

% 100*10*10*10*10: 	603,153
% 101*32*32*5*5: 	7226,1543
% 301*10*10*20*20: 	92340,15378
%

\new{\section{Synthetic examples}}
In this section, we use several\new{synthetic}  examples to demonstrate that the proposed SVD-free low-rank approximation method can significantly accelerate the reconstruction of 5D seismic data without loss of accuracy. \new{Although Hankel and Toeplitz matrices \cite{top1,top2} seem to be similar as the low-rank matrix, but in some cases one can lead us to better results in comparison to the other one. According to our experience, the Toeplitz matrix results in a slightly better reconstruction performance. So, here, we prefer to use the Toeplitz matrix as the low-rank matrix.} The first example is a synthetic example with linear events. We first construct a clean synthetic data, then we add some random noise to the data and also randomly remove some traces from the noisy data to simulate the incomplete seismic data. The size of this synthetic data is $100\times10\times10\times10\times10$. A comparison of the clean data, noisy data, and the incomplete data is presented in Figure \ref{fig:syn5d-clean-3d,syn5d-noisy-3d,syn5d-decimated-3d}, from which we can see that the added random noise is so strong that most useful seismic signals are not visible. Since 80\% of the total traces are removed from the original noisy data, the observed data is considered to be highly incomplete. We compare the reconstruction performance between the SVD-based low-rank approximation method and the SVD-free  low-rank approximation method in Figure \ref{fig:syn5d-svd-3d,syn5d-n-svd-3d,syn5d-r-svd-3d,syn5d-lmafit-3d,syn5d-n-lmafit-3d,syn5d-r-lmafit-3d}. The top row in Figure \ref{fig:syn5d-svd-3d,syn5d-n-svd-3d,syn5d-r-svd-3d,syn5d-lmafit-3d,syn5d-n-lmafit-3d,syn5d-r-lmafit-3d} corresponds to the results from the SVD-based low-rank approximation method and the bottom row in Figure \ref{fig:syn5d-svd-3d,syn5d-n-svd-3d,syn5d-r-svd-3d,syn5d-lmafit-3d,syn5d-n-lmafit-3d,syn5d-r-lmafit-3d} corresponds to the results from the SVD-free low-rank approximation method. In  Figure \ref{fig:syn5d-svd-3d,syn5d-n-svd-3d,syn5d-r-svd-3d,syn5d-lmafit-3d,syn5d-n-lmafit-3d,syn5d-r-lmafit-3d}, we show the reconstructed data in common offset gathers in the left column, the removed noise from the noisy data in the middle column, and the reconstruction error in the right column. The results show that the SVD-based and SVD-free low-rank approximation methods both obtain very successful reconstructions. The gaps in the observed incomplete data have been filled with seismic signals for both methods. The removed noise cubes of both methods do not contain obvious signal patterns, indicating that there are no significant damages to the useful signals during the reconstruction. The reconstruction error cubes also demonstrate that the error is negligible for both methods. However, for this example, the proposed SVD-free method is much faster than the SVD-based method. As tested on a Mac Pro Laptop equipped with an Intel Core i7 CPU clocked at 2.5 GHz and 16 GB of RAM, the SVD-based method takes 603 s to finish the calculation while the proposed only takes 153 s. The computational speedup is almost four times. A comparison of the computational efficiency of different methods for different data sizes is shown in Table \ref{tbl:time}.

The denoising performance in the common midpoint gathers is presented in Figures \ref{fig:syn5d-clean-3d-1,syn5d-noisy-3d-1,syn5d-decimated-3d-1} and \ref{fig:syn5d-svd-3d-1,syn5d-n-svd-3d-1,syn5d-r-svd-3d-1,syn5d-lmafit-3d-1,syn5d-n-lmafit-3d-1,syn5d-r-lmafit-3d-1}. Figure \ref{fig:syn5d-clean-3d-1,syn5d-noisy-3d-1,syn5d-decimated-3d-1} plots the clean synthetic data, noisy data, and decimated data with 80\% traces randomly removed. Figure \ref{fig:syn5d-svd-3d-1,syn5d-n-svd-3d-1,syn5d-r-svd-3d-1,syn5d-lmafit-3d-1,syn5d-n-lmafit-3d-1,syn5d-r-lmafit-3d-1} shows the reconstructed data, removed noise, and reconstruction error cubes using the SVD-based and SVD-free low-rank approximation methods. A single-slice comparison in the common offset gather is presented in Figure \ref{fig:syn5d-clean-2d,syn5d-noisy-2d,syn5d-decimated-2d,syn5d-svd-2d,syn5d-lmafit-2d}. From the single-slice comparison, we can see that both methods obtain very similar results (Figures \ref{fig:syn5d-svd-2d} and \ref{fig:syn5d-lmafit-2d}), which are very close to the clean data (Figure \ref{fig:syn5d-clean-2d}). To numerically compare the reconstruction performance, we use the signal-to-noise ratio (SNR) defined as follows \cite{weilin2016,weilin2017gji}:
\begin{equation}
\label{eq:dsnr}
SNR=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2^2}{\Arrowvert \mathbf{s} -\hat{\mathbf{s}}\Arrowvert_2^2}.
\end{equation}
where $\mathbf{s}$ denotes the vectorized clean data and $\hat{\mathbf{s}}$ denotes the vectorized reconstructed data.

To further compare the amplitude difference among different datasets, we extract a single trace from each data cubes of the clean, noisy, observed, and reconstructed data using two methods. The trace to be compared is the middle trace in each dataset. The single-trace comparison is plotted in Figure \ref{fig:synth-ss}. The clean data is plotted as the black line. The noisy data is plotted as the red line. The observed data is not plotted because in this position it is a blank trace. The blue line plots the trace using the SVD-based low-rank approximation method. The green line plots the trace using the SVD-free method. It is apparent that both SVD-based and SVD-free methods obtain very successful recovery of the exact solution, i.e., the clean trace. Although there are tiny differences between the blue and the green lines, they are overall very similar.

The calculated SNR of the incomplete data is -8.08 dB. The SNRs of the SVD-based and SVD-free low-rank approximation methods are \old{9.49 dB and 9.64 dB}\new{9.53 dB and 9.79 dB}, respectively. We find that the proposed SVD-free low-rank approximation can even obtain a slight improvement in terms of SNR. Besides, we also use the local similarity metric \cite{yangkang2015ortho} to compare the reconstruction performance of different methods. Figure \ref{fig:simi-syn5d-noisy-2d,simi-syn5d-decimated-2d,simi-syn5d-svd-2d,simi-syn5d-lmafit-2d} shows the comparison of local similarity maps of different datasets. Figure \ref{fig:simi-syn5d-noisy-2d} plots the local similarity between clean data and the noisy data, where we can see that the high local similarity is consistent with the distribution of the useful signals. Although, it is difficult to observe signals from the very noisy data, it is possible to use local similarity to highlight the distribution of the useful signals in the presence of extremely strong random noise. Figure \ref{fig:simi-syn5d-decimated-2d} shows the local similarity map between the observed incomplete data and the clean data. The right side of the section has distinctly zero local similarity value, due to the missing traces. Figures \ref{fig:simi-syn5d-svd-2d} and \ref{fig:simi-syn5d-lmafit-2d} show the local similarity maps corresponding to the SVD-based and SVD-free low-rank approximation methods. The very close local similarity maps of two methods indicate that the reconstruction performance is nearly the same.

Next, we use a synthetic example with hyperbolic events to test the performance of the proposed method in the case of curved events. The clean data, noisy data, and incomplete data with 80\% missing traces are shown in Figure \ref{fig:curve5d-clean-3d-1,curve5d-noisy-3d-1,curve5d-decimated-3d-1}. The size of this synthetic data is $101\times32\times32\times5\times5$.  The comparison of reconstruction results using the SVD-based and SVD-free methods is presented in Figure \ref{fig:curve5d-svd-3d-1,curve5d-n-svd-3d-1,curve5d-r-svd-3d-1,curve5d-lmafit-3d-1,curve5d-n-lmafit-3d-1,curve5d-r-lmafit-3d-1}. The left column in Figure \ref{fig:curve5d-svd-3d-1,curve5d-n-svd-3d-1,curve5d-r-svd-3d-1,curve5d-lmafit-3d-1,curve5d-n-lmafit-3d-1,curve5d-r-lmafit-3d-1} plots the reconstructed data. The middle column in Figure \ref{fig:curve5d-svd-3d-1,curve5d-n-svd-3d-1,curve5d-r-svd-3d-1,curve5d-lmafit-3d-1,curve5d-n-lmafit-3d-1,curve5d-r-lmafit-3d-1} plots the removed noise. The right column in Figure \ref{fig:curve5d-svd-3d-1,curve5d-n-svd-3d-1,curve5d-r-svd-3d-1,curve5d-lmafit-3d-1,curve5d-n-lmafit-3d-1,curve5d-r-lmafit-3d-1} plots the reconstruction error. From Figure \ref{fig:curve5d-svd-3d-1,curve5d-n-svd-3d-1,curve5d-r-svd-3d-1,curve5d-lmafit-3d-1,curve5d-n-lmafit-3d-1,curve5d-r-lmafit-3d-1}, it is clear that both methods obtain very similar performance. However, the computational costs for the SVD-based and SVD-free methods are 7226 s, and 1543s, respectively. Figure \ref{fig:simi-curve5d-noisy-3d-1,simi-curve5d-decimated-3d-1,simi-curve5d-svd-3d-1,simi-curve5d-lmafit-3d-1}
shows the comparison of local similarity cubes. Figure \ref{fig:simi-curve5d-noisy-3d-1} plots the local similarity between the noisy data and the clean data. Figure \ref{fig:simi-curve5d-decimated-3d-1} plots the local similarity between the observed incomplete data and the clean data. Figure \ref{fig:simi-curve5d-svd-3d-1} plots the local similarity between the reconstructed data and the clean data using the SVD-based low-rank approximation method. Figure \ref{fig:simi-curve5d-lmafit-3d-1} plots the local similarity between the reconstructed data and the clean data using the SVD-free low-rank approximation method. From the similarity cubes, we see that the reconstructions from both methods help recover most of the useful signals and obtain high local similarity measures. The performance of the SVD-free method is further confirmed to be close to the SVD-based method in terms of local similarity measure. The SNRs of the reconstructed data using the SVD-based method and the SVD-free method are \old{1.72 dB and 1.89 dB}\new{1.75 dB and 1.92 dB}, respectively. Note that the SNR of the incomplete data of this example is extremely low, i.e., -13.73 dB. This example also demonstrates the effectiveness of the SVD-free low-rank approximation method in the case of ultra-low SNR.

\new{\section{Real data example}}
Finally, we apply the proposed SVD-free low-rank approximation method to a 5D field data. The data have been binned onto a regular grid and a common offset gather of the field data is shown in Figure \ref{fig:field5d-decimated2d-0,field5d-svd2d-0,field5d-lmafit2d-0}. In Figure \ref{fig:field5d-decimated2d-0,field5d-svd2d-0,field5d-lmafit2d-0}, the \old{coloured}\new{colored} stripes are the recorded seismic traces. The white blanks denote the missing traces, which means that we do not observe seismic data in these positions. The size of this field data is $301\times10\times10\times20\times20$. Because of the difficulty in displaying a 5D data set, we only show a common mid-point gather here. The 3D common midpoint gather is re-arranged into a 2D matrix for a better view. The transparent \old{coloured}\new{colored} windows denote zooming areas for an amplified comparison. In this example, roughly 80 percent traces are missing from the regular grids. Because of the high ratio of missing traces, the observed seismic traces do not show any spatial coherency. It is difficult to see the waveforms from the raw data. The results from the two aforementioned methods, i.e., SVD-based and SVD-free methods, are shown in Figures \ref{fig:field5d-svd2d-0} and \ref{fig:field5d-lmafit2d-0}. After 5D reconstruction, the white blanks in the raw data have been filled with seismic traces. The waveforms become well aligned along the spatial direction. Compared with the raw data, all methods seem to obtain a dramatic improvement on the data quality. It is salient that both low-rank approximation methods obtain much smoother and cleaner results.  When zooming the data in the transparent red rectangles in both Figures \ref{fig:field5d-svd2d-0} and \ref{fig:field5d-lmafit2d-0}, the comparison among different datasets becomes much clearer. From Figure \ref{fig:z-decimated,z-svd,z-lmafit}, we observe that both low-rank approximation methods obtain very similar results. In this example, the SVD-free method takes 15378 s while the SVD-based method takes 92340 s. The speedup using the proposed SVD-free low-rank approximation is nearly six times.

\section{Conclusion}
The traditional singular value decomposition (SVD) based low-rank approximation method suffers from the bottleneck of computational cost due to many SVD calculations. In order to relieve the computation overburden, we develop an SVD-free low-rank approximation method in this paper. The SVD-free matrix decomposition is based on an alternating minimization strategy. During the iterative update, we only need a much faster QR factorization for solving a linear least-squares problem. The SVD-free low-rank approximation can be easily inserted into the singular spectrum analysis (SSA) framework. We test the effectiveness of the SVD-free method on synthetic examples with linear and curving events,  and a real 5D seismic data. The results show that the proposed SVD-free method do not degrade the reconstruction performance compared with the traditional method. However, the proposed SVD-free method can greatly improve the computational efficiency.

\begin{thebibliography}{00}
\bibitem{ronen}
J.~Ronen, ``Wave-equation trace interpolation,'' \emph{Geophysics}, vol.~52,
  pp. 973--984, 1987.

\bibitem{spitz1991}
S.~Spitz, ``Seismic trace interpolation in the f-x domain,'' \emph{Geophysics},
  vol.~56, pp. 785--794, 1991.

\bibitem{chen1995}
J.~Chen and J.~Cihlar, ``Quantifying the effect of canopy architecture on
  optical measurements of leaf area index using two gap size analysis
  methods,'' \emph{IEEE Transactions on Geoscience and Remote Sensing},
  vol.~33, pp. 777--787, 1995.

\bibitem{canning1996}
A.~Canning and G.~H.~F. Gardner, ``Reducing 3{D} acquisition footprint for 3{D}
  dmo and 3{D} prestack migration,'' \emph{Geophysics}, vol.~63, pp.
  1177--1183, 1996.

\bibitem{fomel2002pwd}
S.~Fomel, ``Application of plane-wave destruction filters,'' \emph{Geophysics},
  vol.~67, pp. 1946--1960, 2002.

\bibitem{fomel2003}
------, ``Seismic reflection data interpolation with differential offset and
  shot continuation,'' \emph{Geophysics}, vol.~68, pp. 733--744, 2003.

\bibitem{abmapocs}
R.~Abma and N.~Kabir, ``\protect{3D} interpolation of irregular data with a
  \protect{POCS} algorithm,'' \emph{Geophysics}, vol.~71, pp. E91--E97, 2006.

\bibitem{herrmann2008non}
F.~J. Herrmann and G.~Hennenfent, ``Non-parametric seismic data recovery with
  curvelet frames,'' \emph{Geophysical Journal International}, vol. 173, no.~1,
  pp. 233--248, 2008.

\bibitem{protter2009}
M.~Protter and M.~Elad, ``Image sequence denoising via sparse and redundant
  representations,'' \emph{IEEE Trans Image Process}, vol.~18, no.~1, pp.
  27--35, 2009.

\bibitem{mostafa2010}
M.~Naghizadeh and M.~D. Sacchi, ``Beyond alias hierarchical scale curvelet
  interpolation of regularly and irregularly sampled seismic data,''
  \emph{Geophysics}, vol.~75, p. WB189–WB202, 2010.

\bibitem{mostafa2013}
------, ``Multidimensional de-aliased cadzow reconstruction of seismic
  records,'' \emph{Geophysics}, vol.~78, no.~1, pp. A1--A5, 2010.

\bibitem{wang2011recovery}
Y.~Wang, J.~Cao, and C.~Yang, ``Recovery of seismic wavefields based on
  compressive sensing by an l 1-norm constrained trust region method and the
  piecewise random subsampling,'' \emph{Geophysical Journal International},
  vol. 187, no.~1, pp. 199--213, 2011.

\bibitem{yanan2014}
Y.~Tian, Y.~Li, and B.~Yang, ``Variable-eccentricity hyperbolic-trace {TFPF}
  for seismic random noise attenuation,'' \emph{IEEE Transactions on Geoscience
  and Remote Sensing}, vol.~52, pp. 6449--6458, 2014.

\bibitem{yanhui2016}
Y.~Zhou, J.~Gao, W.~Chen, and P.~Frossard, ``Seismic simultaneous source
  separation via patchwise sparse representation,'' \emph{IEEE Transactions on
  Geoscience and Remote Sensing}, vol.~54, pp. 5271--5284, 2016.

\bibitem{kazemi2016}
N.~Kazemi, E.~Bongajum, and M.~D. Sacchi, ``Surface-consistent sparse
  multichannel blind deconvolution of seismic signals,'' \emph{IEEE
  Transactions on Geoscience and Remote Sensing}, vol.~54, pp. 3200--3207,
  2016.
\bibitem{shuwei2016cs}
S.~Gan, S.~Wang, Y.~Chen, X.~Chen, W.~Huang, and H.~Chen, ``Compressive sensing
  for seismic data reconstruction via fast projection onto convex sets based on
  seislet transform,'' \emph{Journal of Applied Geophysics}, vol. 130, pp.
  194--208, 2016.

\bibitem{lorenzi2016}
L.~Lorenzi, F.~Melgani, and G.~Mercier, ``Missing-area reconstruction in
  multispectral images under a compressive sensing perspective,'' \emph{IEEE
  Transactions on Geoscience and Remote Sensing}, vol.~51, pp. 3998--4008,
  2016.

\bibitem{shaohuan2016gap}
S.~Zu, H.~Zhou, Y.~Chen, X.~Pan, S.~Gan, and D.~Zhang, ``Interpolating big gaps
  using inversion with slope constraint,'' \emph{IEEE Geoscience and Remote
  Sensing Letters}, vol.~13, pp. 1369--1373, 2016.

\bibitem{yangkang2016irr5d}
Y.~Chen, D.~Zhang, Z.~Jin, X.~Chen, S.~Zu, W.~Huang, and S.~Gan, ``Simultaneous
  denoising and reconstruction of 5{D} seismic data via damped rank-reduction
  method,'' \emph{Geophysical Journal International}, vol. 206, pp. 1695--1717,
  2016.

\bibitem{amir2017ieee}
R.~Anvari, M.~A.~N. Siahsar, S.~Gholtashi, A.~R. Kahoo, and M.~Mohammadi,
  ``Seismic random noise attenuation using synchrosqueezed wavelet transform
  and low-rank signal matrix approximation,'' \emph{IEEE Transactions on
  Geoscience and Remote Sensing}, vol.~55, no.~11, pp. 6574--6581, 2017.

\bibitem{verschuure1991}
D.~J. Verschuur, ``Surface-related multiple elimination: An inversion
  approach,'' \emph{PhD thesis, Delft University of Technology}, 1991.

\bibitem{jingjie2011review}
J.~Cao, Y.~Wang, J.~Zhao, and C.~Yang, ``A review on restoration of seismic
  wavefields based on regularization and compressive sensing,'' \emph{Inverse
  Problems in Science and Engineering}, vol.~19, no.~5, pp. 679--704, 2011.

\bibitem{yangkang20142}
Y.~Chen, S.~Fomel, and J.~Hu, ``Iterative deblending of simultaneous-source
  seismic data using seislet-domain shaping regularization,''
  \emph{Geophysics}, vol.~79, pp. V179--V189, 2014.

\bibitem{shuwei20153}
S.~Gan, S.~Wang, Y.~Chen, Y.~Zhang, and Z.~Jin, ``Dealiased seismic data
  interpolation using seislet transform with low-frequency constraint,''
  \emph{IEEE Geoscience and Remote Sensing Letters}, vol.~12, pp. 2150--2154,
  2015.

\bibitem{shuwei2016vscan}
S.~Gan, S.~Wang, Y.~Chen, S.~Qu, and S.~Zu, ``Velocity analysis of
  simultaneous-source data using high-resolution semblance-coping with the
  strong noise,'' \emph{Geophysical Journal International}, vol. 204, pp.
  768--779, 2016.

\bibitem{liuwei2016dealiase}
W.~Liu, S.~Cao, S.~Gan, Y.~Chen, S.~Zu, and Z.~Jin, ``One-step slope estimation
  for dealiased seismic data reconstruction via iterative seislet
  thresholding,'' \emph{IEEE Geoscience and Remote Sensing Letters}, vol.~13,
  pp. 1462--1466, 2016.

\bibitem{shaohuan2017gji}
S.~Zu, H.~Zhou, W.~Mao, D.~Zhang, C.~Li, X.~Pan, and Y.~Chen, ``Iterative
  deblending of simultaneous-source data using a coherency-pass shaping
  operator,'' \emph{Geophysical Journal International}, vol. 211, no.~1, pp.
  541--557, 2017.

\bibitem{YuSiwei2015}
S.~Yu, J.~Ma, X.~Zhang, and M.~D. Sacchi, ``Interpolation and denoising of
  high-dimensional seismic data by learning a tight frame,'' \emph{Geophysics},
  vol.~80, no.~5, pp. V119--V132, 2015. [Online]. Available:
  \url{https://doi.org/10.1190/geo2014-0396.1}

\bibitem{YuSiwei2016}
S.~Yu, J.~Ma, and S.~Osher, ``Monte carlo data-driven tight frame for seismic
  data recovery,'' \emph{Geophysics}, vol.~81, no.~4, pp. V327--V340, 2016.
  [Online]. Available: \url{https://doi.org/10.1190/geo2015-0343.1}

\bibitem{Jia2017}
Y.~Jia and J.~Ma, ``What can machine learning do for seismic data processing?
  an interpolation application,'' \emph{Geophysics}, vol.~82, no.~3, pp.
  V163--V177, 2017. [Online]. Available:
  \url{https://doi.org/10.1190/geo2016-0300.1}

\bibitem{amir2017sp}
M.~A.~N. Siahsar, V.~Abolghasemi, and Y.~Chen, ``Simultaneous denoising and
  interpolation of 2{D} seismic data using data-driven non-negative dictionary
  learning,'' \emph{Signal Processing}, vol. 141, pp. 309--321, 2017.

\bibitem{amir2017geo}
M.~A.~N. Siahsar, S.~Gholtashi, A.~R. Kahoo, W.~Chen, and Y.~Chen,
  ``Data-driven multi-task sparse dictionary learning for noise attenuation of
  3{D} seismic data,'' \emph{Geophysics}, vol.~82, no.~6, p. V385–V396, 2017.

\bibitem{Jia2018}
Y.~Jia, S.~Yu, and J.~Ma, ``Intelligent interpolation by monte carlo machine
  learning,'' \emph{Geophysics}, vol.~83, no.~2, pp. V83--V97, 2018. [Online].
  Available: \url{https://doi.org/10.1190/geo2017-0294.1}

\bibitem{zhangmi2019}
M.~Zhang, Y.~Liu, M.~Bai, and Y.~Chen, ``Seismic noise attenuation using
  unsupervised sparse feature learning,'' \emph{IEEE Transactions on Geoscience
  and Remote Sensing}, p. doi: 10.1109/TGRS.2019.2928715, 2019.

\bibitem{yangkang2015ortho}
Y.~Chen and S.~Fomel, ``Random noise attenuation using local signal-and-noise
  orthogonalization,'' \emph{Geophysics}, vol.~80, pp. WD1--WD9, 2015.

\bibitem{guochang2012}
G.~Liu, X.~Chen, J.~Du, and K.~Wu, ``Random noise attenuation using \emph{f-x}
  regularized nonstationary autoregression,'' \emph{Geophysics}, vol.~77, pp.
  V61--V69, 2012.

\bibitem{fxnaghizadeh}
M.~Naghizadeh and M.~Sacchi, ``Multicomponent f-x seismic random noise
  attenuation via vector autoregressive operators,'' \emph{Geophysics},
  vol.~77, pp. V91--V99, 2012.

\bibitem{beckouche}
S.~Beckouche and J.~Ma, ``Simultaneous dictionary learning and denoising for
  seismic data,'' \emph{Geophysics}, vol.~79, pp. A27--A31, 2014.

\bibitem{mostafa2016bssa}
S.~M. Mousavi and C.~A. Langston, ``Hybrid seismic denoising using higher-order
  statistics and improved wavelet block thresholding,'' \emph{Bulletin of the
  Seismological Society of America}, vol. 106, no.~4, pp. 1380--1393, 2016.

\bibitem{mostafa2017geo}
------, ``Automatic noise-removal/signal-removal based on general
  cross-validation thresholding in synchrosqueezed domain and its application
  on earthquake data,'' \emph{Geophysics}, vol.~82, no.~4, pp. V211--V227,
  2017.

\bibitem{zhaoqiang2018}
Q.~Zhao, Q.~Du, X.~Gong, and Y.~Chen, ``Signal-preserving erratic noise
  attenuation via iterative robust sparsity-promoting filter,'' \emph{IEEE
  Transactions on Geoscience and Remote Sensing}, vol.~56, no.~6, pp.
  1558--0644, 2018.

\bibitem{oropezamssa}
V.~Oropeza and M.~Sacchi, ``Simultaneous seismic data denoising and
  reconstruction via multichannel singular spectrum analysis,''
  \emph{Geophysics}, vol.~76, pp. V25--V32, 2011.

\bibitem{gaomssa}
J.~Gao, M.~Sacchi, and X.~Chen, ``A fast reduced-rank interpolation method for
  prestack seismic volumes that depend on four spatial dimensions,''
  \emph{Geophysics}, vol.~78, pp. V21--V30, 2013.

\bibitem{Gaogp}
J.~Gao, A.~Stanton, M.~Naghizadeh, M.~D. Sacchi, and X.~Chen, ``Convergence
  improvement and noise attenuation considerations for beyond alias projection
  onto convex sets reconstruction,'' \emph{Geophysical Prospecting}, vol.~61,
  pp. 138--151, 2013.

\bibitem{gholami}
A.~Gholami, ``Non-convex compressed sensing with frequency mask for seismic
  data reconstruction and denoising,'' \emph{Geophysical Prospecting}, vol.~62,
  pp. 1389--1405, 2015.

\bibitem{benfengpocs}
B.~Wang, R.~Wu, X.~Chen, and J.~Li, ``Simultaneous seismic data interpolation
  and denoising with a new adaptive method based on dreamlet transform,''
  \emph{Geophysical Journal International}, vol. 201, pp. 1180--1192, 2015.

\bibitem{pmf}
J.~Gao, A.~Stanton, and M.~D. Sacchi, ``Parallel matrix factorization algorithm
  and its application to 5{D} seismic reconstruction and denoising,''
  \emph{Geophysics}, vol.~80, pp. V173--V187, 2015.

\bibitem{wangchong2018}
C.~Wang, Z.~Zhu, H.~Gu, X.~Wu, and S.~Liu, ``Hankel low-rank approximation for
  seismic noise attenuation,'' \emph{IEEE Transactions on Geoscience and Remote
  Sensing}, no.~99, pp. 1--13, 2018.

\bibitem{Liubin2004}
B.~Liu and M.~D. Sacchi, ``Minimum weighted norm interpolation of seismic
  records,'' \emph{Geophysics}, vol.~69, no.~6, pp. 1560--1568, 2004. [Online].
  Available: \url{https://doi.org/10.1190/1.1836829}

\bibitem{Trad2007}
D.~Trad, ``A strategy for wide azimuth land interpolation,'' \emph{SEG
  Technical Program Expanded Abstracts}, pp. 946--950, 2007. [Online].
  Available: \url{https://library.seg.org/doi/abs/10.1190/1.2792562}

\bibitem{Trad2009}
------, ``Five-dimensional interpolation: Recovering from acquisition
  constraints,'' \emph{Geophysics}, vol.~74, pp. V123--V132, 2009.

\bibitem{GaoJianjun2017}
J.~Gao, J.~Cheng, and M.~D. Sacchi, ``Five-dimensional seismic reconstruction
  using parallel square matrix factorization,'' \emph{IEEE Transactions on
  Geoscience and Remote Sensing}, vol.~55, no.~4, pp. 2124--2135, April 2017.

\bibitem{Xie2017}
Y.~Xie and D.~Gajewski, ``5-{D} interpolation with wavefront attributes,''
  \emph{Geophysical Journal International}, vol. 211, pp. 897--919, 08 2017.

\bibitem{lu2015fast}
L.~Lu, W.~Xu, and S.~Qiao, ``A fast {SVD} for multilevel block hankel matrices
  with minimal memory storage,'' \emph{Numerical Algorithms}, vol.~69, no.~4,
  pp. 875--891, 2015.

\bibitem{jinkun2016}
J.~Cheng and M.~Sacchi, ``Fast dual-domain reduced-rank algorithm for 3{D}
  deblending via randomized qr decomposition,'' \emph{Geophysics}, vol.~81, pp.
  V89--V101, 2014.

\bibitem{jianjun2017five}
J.~Gao, J.~Cheng, and M.~D. Sacchi, ``Five-dimensional seismic reconstruction
  using parallel square matrix factorization,'' \emph{IEEE Transactions on
  Geoscience and Remote Sensing}, vol.~55, no.~4, pp. 2124--2135, 2017.

\bibitem{gavish2014optimal}
M.~Gavish and D.~L. Donoho, ``The optimal hard threshold for singular values is
  4/sqrt(3),'' \emph{IEEE Transactions on Information Theory}, vol.~60, no.~8,
  pp. 5040--5053, 2014.

\bibitem{trickett2015preserving}
S.~Trickett, ``Preserving signal: Automatic rank determination for noise
  suppression,'' in \emph{SEG Technical Program Expanded Abstracts 2015}.\hskip
  1em plus 0.5em minus 0.4em\relax Society of Exploration Geophysicists, 2015,
  pp. 4703--4707.

\bibitem{aharchaou2017singular}
M.~Aharchaou, J.~Anderson, S.~Hughes, and J.~Bingham, ``Singular-spectrum
  analysis via optimal shrinkage of singular values,'' in \emph{SEG Technical
  Program Expanded Abstracts 2017}.\hskip 1em plus 0.5em minus 0.4em\relax
  Society of Exploration Geophysicists, 2017, pp. 4950--4954.

\bibitem{yatong2018gji}
Y.~Zhou, S.~Li, D.~Zhang, and Y.~Chen, ``Seismic noise attenuation using an
  online subspace tracking algorithm,'' \emph{Geophysical Journal
  International}, vol. 212, no.~2, p. 1072–1097, 2018.

\bibitem{wujuan2018jge3}
J.~Wu and M.~Bai, ``Adaptive rank-reduction method for seismic data
  reconstruction,'' \emph{Journal of Geophysics and Engineering}, vol.~15, p.
  1688, 2018.

\bibitem{weilin2016}
W.~Huang, R.~Wang, Y.~Chen, H.~Li, and S.~Gan, ``Damped multichannel singular
  spectrum analysis for 3{D} random noise attenuation,'' \emph{Geophysics},
  vol.~81, no.~4, pp. V261--V270, 2016.

\bibitem{weilingieeedls}
W.~Huang, R.~Wang, X.~Chen, and Y.~Chen, ``Double least-squares projections
  method for signal estimation,'' \emph{IEEE Transactions on Geoscience and
  Remote Sensing}, vol.~55, pp. 4111--4129, 2017.

\bibitem{dong}
D.~Zhang, Y.~Chen, W.~Huang, and S.~Gan, ``Multi-step damped multichannel
  singular spectrum analysis for simultaneous reconstruction and denoising of
  3{D} seismic data,'' \emph{Journal of Geophysics and Engineering}, vol.~13,
  pp. 704--720, 2016.

\bibitem{dong2017}
D.~Zhang, Y.~Zhou, H.~Chen, W.~Chen, S.~Zu, and Y.~Chen, ``Hybrid rank-sparsity
  constraint model for simultaneous reconstruction and denoising of 3{D}
  seismic data,'' \emph{Geophysics}, vol.~82, pp. V351--V367, 2017.

\bibitem{yufeng2017}
Y.~Wang, H.~Zhou, S.~Zu, W.~Mao, and Y.~Chen, ``Three-operator proximal
  splitting scheme for 3{D} seismic data reconstruction,'' \emph{IEEE
  Geoscience and Remote Sensing Letters}, vol.~14, no.~10, pp. 1830--1834,
  2017.

\bibitem{yangkangelra}
Y.~Chen, Y.~Zhou, W.~Chen, S.~Zu, W.~Huang, and D.~Zhang, ``Empirical low-rank
  approximation for seismic noise attenuation,'' \emph{IEEE Transactions on
  Geoscience and Remote Sensing}, vol.~55, pp. 4696--4711, 2017.

\bibitem{baimin2018cg}
M.~Bai, J.~Wu, S.~Zu, and W.~Chen, ``A structural rank reduction operator for
  removing artifacts in least-squares reverse time migration,'' \emph{Computers
  and Geosciences}, vol. 117, pp. 9--20, 2018.

\bibitem{stanton2013processing}
A.~Stanton, N.~Kazemi, and M.~D. Sacchi, ``Processing seismic data in the
  presence of residual statics,'' in \emph{SEG Technical Program Expanded
  Abstracts 2013}.\hskip 1em plus 0.5em minus 0.4em\relax Society of
  Exploration Geophysicists, 2013, pp. 1838--1842.

\bibitem{lmafit}
Z.~Wen, W.~Yin, and Y.~Zhang, ``Solving a low-rank factorization model for
  matrix completion by a nonlinear successive over-relaxation algorithm,''
  \emph{Mathematical Programming Computation}, vol.~4, pp. 333--361, 2012.

\bibitem{weilin2017gji}
W.~Huang, R.~Wang, S.~Zu, and Y.~Chen, ``Low-frequency noise attenuation in
  seismic and microseismic data using mathematical morphological filtering,''
  \emph{Geophysical Journal International}, vol. 211, p. 1318–1340, 2017.

\bibitem{yangkang2020odrr}
Y.~Chen, M.~Bai, Z.~Guan, Q. Zhang, M. Zhang, and H.~Wang, ``Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method,''
  \emph{Geophysical Journal International}, vol. 222, p. 1824-1845, 2020.

\bibitem{top1}
A.~Bottcher, S.M.~Grudsky, and T.~Kunz, ``Toeplitz Matrices, Asymptotic Linear Algebra, and Functional Analysis,''
  \emph{ISBN: 978-3-7643-6290-4,A Birkhäuser book}, 2000.

\bibitem{top2}
R.M.~Gray, ``Toeplitz and Circulant Matrices: A review,''
  \emph{Foundations and Trends in Communications and Information Theory}, vol. 2, pp. 155-239, 2006.

\end{thebibliography}

%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a1.png}}]{First A. Author} (M'76--SM'81--F'87) and all authors may include 
%biographies. Biographies are often not included in conference-related
%papers. This author became a Member (M) of IEEE in 1976, a Senior
%Member (SM) in 1981, and a Fellow (F) in 1987. The first paragraph may
%contain a place and/or date of birth (list place, then date). Next,
%the author's educational background is listed. The degrees should be
%listed with type of degree in what field, which institution, city,
%state, and country, and year the degree was earned. The author's major
%field of study should be lower-cased. 
%
%The second paragraph uses the pronoun of the person (he or she) and not the 
%author's last name. It lists military and work experience, including summer 
%and fellowship jobs. Job titles are capitalized. The current job must have a 
%location; previous positions may be listed 
%without one. Information concerning previous publications may be included. 
%Try not to list more than three books or published articles. The format for 
%listing publishers of a book within the biography is: title of book 
%(publisher name, year) similar to a reference. Current and previous research 
%interests end the paragraph. The third paragraph begins with the author's 
%title and last name (e.g., Dr.\ Smith, Prof.\ Jones, Mr.\ Kajor, Ms.\ Hunter). 
%List any memberships in professional societies other than the IEEE. Finally, 
%list any awards and work for IEEE committees and publications. If a 
%photograph is provided, it should be of good quality, and 
%professional-looking. Following are two examples of an author's biography.
%\end{IEEEbiography}
%
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a2.png}}]{Second B. Author} was born in Greenwich Village, New York, NY, USA in 
%1977. He received the B.S. and M.S. degrees in aerospace engineering from 
%the University of Virginia, Charlottesville, in 2001 and the Ph.D. degree in 
%mechanical engineering from Drexel University, Philadelphia, PA, in 2008.
%
%From 2001 to 2004, he was a Research Assistant with the Princeton Plasma 
%Physics Laboratory. Since 2009, he has been an Assistant Professor with the 
%Mechanical Engineering Department, Texas A{\&}M University, College Station. 
%He is the author of three books, more than 150 articles, and more than 70 
%inventions. His research interests include high-pressure and high-density 
%nonthermal plasma discharge processes and applications, microscale plasma 
%discharges, discharges in liquids, spectroscopic diagnostics, plasma 
%propulsion, and innovation plasma applications. He is an Associate Editor of 
%the journal \emph{Earth, Moon, Planets}, and holds two patents. 
%
%Dr. Author was a recipient of the International Association of Geomagnetism 
%and Aeronomy Young Scientist Award for Excellence in 2008, and the IEEE 
%Electromagnetic Compatibility Society Best Symposium Paper Award in 2011. 
%\end{IEEEbiography}
%
\clearpage
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{juan}}]{Juan Wu} received the Ph.D. degree in geophysics from the China University of Petroleum, Beijing, China, in 2016, under the supervision of Prof. Xiaohong Chen.
She is currently a Post-Doctoral Researcher with Yangtze University, Jingzhou, China. She has authored or coauthored more than 30 journal articles. Her research interests include seismic signal analysis and seismic imaging.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{min}}]{Min Bai}
 received the Ph.D. degree in geophysics from the China University of Petroleum, Beijing, China, in 2016, under the supervision of Prof. Xiaohong Chen.
He is currently a Post-Doctoral Researcher with the School of Earth Sciences, Zhejiang University, Hangzhou, China, and a Lecturer with Yangtze University, Jingzhou, China. He has authored or coauthored more than 30 journal articles. His research interests include seismic imaging and inversion and seismic signal analysis.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{dong}}]{Dong Zhang} received the B.S. degree in applied geophysics from Jilin University, Changchun, China, in 2014.  He is currently pursuing a PhD degree in Geophysics at Delft university of technology. His current research interests include seismic signal analysis, seismic imaging and simultaneous-source data deblending and imaging.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{hang}}]{Hang Wang} received a master degree in geological resources and geological engineering from China University of Petroleum (Beijing), and he is a Ph.D. candidate in geophysics at Zhejiang University. His research interests include seismic signal processing, machine learning and FWI.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{guangtan}}]{Guangtan Huang} received the B.S., M.S., and Ph.D. degrees in exploration geophysics from the China University of Petroleum (East China), Beijing, Beijing, China, in 2012, 2015, and 2019, respec- tively. He holds a post-doctoral position in geophyiscs at Zhejiang University, Hangzhou, China. His research interests include seismic forward modeling and high-resolution seismic inversion.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{yangkang}}]{Yangkang Chen} received the B.S. degree in explo- ration geophysics from the China University of Petroleum, Beijing, Beijing, China, in 2012, and the Ph.D. degree in geophysics from the University of Texas at Austin, Austin, TX, USA, in 2015, under the supervision of Prof. S. Fomel.
He was a Distinguished Post-Doctoral Research Associate with Oak Ridge National Laboratory, Oak Ridge, TN, USA, where he conducted research on global adjoint tomography. He is an Assistant Pro- fessor with Zhejiang University, Hangzhou, China. He has authored or coauthored more than 100 internationally renowned journal articles and more than 80 international conference papers. His research interests include seismic signal analysis, seismic modeling and inversion, simultaneous-source data deblending and imaging, global adjoint tomography, machine learning, and high-performance computing.
\end{IEEEbiography}

\EOD

### 2020-12-25 lr5d/paper.tex
2020年12月25日 星期五 03时25分50秒 CST

@@
-\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
-\doi{10.1109/ACCESS.2020.DOI}
+%\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
+%\doi{10.1109/ACCESS.2020.DOI}
+
+\DeclareRobustCommand{\dlo}[1]{}
+\DeclareRobustCommand{\wen}[1]{#1}
+
+\published{IEEE Access, 8, 175501-175512, (2020)}
 
@@
 
-\corresp{Corresponding author: M. Bai (e-mail: baimin2016@126.com).}
-\tfootnote{This research is sponsored by the National Natural Science Foundation of China (Nos.
+%\corresp{Corresponding author: M. Bai (e-mail: baimin2016@126.com).}
+%\tfootnote{This research is sponsored by the National Natural Science Foundation of China (Nos.
 \new{41904110,}41704121), \new{the China Postdoctoral Science Foundation (No.
 2019M662567), and the Postdoctoral Science Foundation of Hubei Province.}}
+%
 
-\def\thevol{8}
-\def\myyear{2020}
+%\def\thevol{8}
+%\def\myyear{2020}
 
@@
 
-\begin{keywords}
-Multidimensional seismic data, \old{lowrank}\new{low-rank} approximation, seismic data processing, \new{seismic reconstruction, matrix completion}
-\end{keywords}
+%\begin{keywords}
+%Multidimensional seismic data, \old{lowrank}\new{low-rank} approximation, seismic data processing, \new{seismic reconstruction, matrix completion}
+%\end{keywords}
 
-\titlepgskip=-15pt
+%\titlepgskip=-15pt
 
@@
 
-\begin{figure}[htb!]
- \centering
- \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-clean-3d}
-   \label{fig:syn5d-clean-3d}}
- \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-noisy-3d}
-   \label{fig:syn5d-noisy-3d}}
- \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-decimated-3d}
-   \label{fig:syn5d-decimated-3d}}        
-  \caption{Common offset gathers for the 5D synthetic example with linear events. (a) Clean data. (b) Noisy data. (c) The observed data with 80\% traces randomly removed.}
-  \label{fig:syn5d-clean-3d,syn5d-noisy-3d,syn5d-decimated-3d}
-\end{figure}
+\inputdir{linear}
+\multiplot{3}{syn5d-clean-3d,syn5d-noisy-3d,syn5d-decimated-3d}{width=0.3\columnwidth}{Common offset gathers for the 5D synthetic example with linear events.
+(a) Clean data.
+(b) Noisy data.
+(c) The observed data with 80\% traces randomly removed.}
 
-\begin{figure}[htb!]
-  \centering
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-svd-3d}
-    \label{fig:syn5d-svd-3d}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-n-svd-3d}
-    \label{fig:syn5d-n-svd-3d}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-r-svd-3d}
-    \label{fig:syn5d-r-svd-3d}} 
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-lmafit-3d}
-    \label{fig:syn5d-lmafit-3d}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-n-lmafit-3d}
-    \label{fig:syn5d-n-lmafit-3d}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-r-lmafit-3d}
-    \label{fig:syn5d-r-lmafit-3d}}       
-   \caption{Comparison of reconstruction performance in common offset gathers for the 5D synthetic example with linear events.
+\multiplot{6}{syn5d-svd-3d,syn5d-n-svd-3d,syn5d-r-svd-3d,syn5d-lmafit-3d,syn5d-n-lmafit-3d,syn5d-r-lmafit-3d}{width=0.3\columnwidth}{Comparison of reconstruction performance in common offset gathers for the 5D synthetic example with linear events.
 (a) Reconstructed data using the SVD-based low-rank approximation method.
@@
 (f) The reconstruction error corresponding to (d).}
-\label{fig:syn5d-svd-3d,syn5d-n-svd-3d,syn5d-r-svd-3d,syn5d-lmafit-3d,syn5d-n-lmafit-3d,syn5d-r-lmafit-3d}
-\end{figure}
 
-\begin{figure}[htb!]
-  \centering
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-clean-3d-1}
-    \label{fig:syn5d-clean-3d-1}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-noisy-3d-1}
-    \label{fig:syn5d-noisy-3d-1}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-decimated-3d-1}
-    \label{fig:syn5d-decimated-3d-1}}        
-   \caption{Common midpoint gathers for the 5D synthetic example with linear events. (a) Clean data. (b) Noisy data. (c) The observed data with 80\% traces randomly removed.}
-   \label{fig:syn5d-clean-3d-1,syn5d-noisy-3d-1,syn5d-decimated-3d-1}
-\end{figure}
+\multiplot{3}{syn5d-clean-3d-1,syn5d-noisy-3d-1,syn5d-decimated-3d-1}{width=0.3\columnwidth}{Common midpoint gathers for the 5D synthetic example with linear events.
+(a) Clean data.
+(b) Noisy data.
+(c) The observed data with 80\% traces randomly removed.}
 
-\begin{figure}[htb!]
-  \centering
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-svd-3d-1}
-    \label{fig:syn5d-svd-3d-1}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-n-svd-3d-1}
-    \label{fig:syn5d-n-svd-3d-1}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-r-svd-3d-1}
-    \label{fig:syn5d-r-svd-3d-1}} 
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-lmafit-3d-1}
-    \label{fig:syn5d-lmafit-3d-1}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-n-lmafit-3d-1}
-    \label{fig:syn5d-n-lmafit-3d-1}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-r-lmafit-3d-1}
-    \label{fig:syn5d-r-lmafit-3d-1}}       
-   \caption{Comparison of reconstruction performance in common midpoint gathers for the 5D synthetic example with linear events.
+\multiplot{6}{syn5d-svd-3d-1,syn5d-n-svd-3d-1,syn5d-r-svd-3d-1,syn5d-lmafit-3d-1,syn5d-n-lmafit-3d-1,syn5d-r-lmafit-3d-1}{width=0.3\columnwidth}{Comparison of reconstruction performance in common midpoint gathers for the 5D synthetic example with linear events.
 (a) Reconstructed data using the SVD-based low-rank approximation method.
@@
 (f) The reconstruction error corresponding to (d).}
-\label{fig:syn5d-svd-3d-1,syn5d-n-svd-3d-1,syn5d-r-svd-3d-1,syn5d-lmafit-3d-1,syn5d-n-lmafit-3d-1,syn5d-r-lmafit-3d-1}
-\end{figure}
 
-\begin{figure}[htb!]
-  \centering
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-clean-2d}
-    \label{fig:syn5d-clean-2d}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-noisy-2d}
-    \label{fig:syn5d-noisy-2d}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-decimated-2d}
-    \label{fig:syn5d-decimated-2d}} 
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-svd-2d}
-    \label{fig:syn5d-svd-2d}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{linear/Fig/syn5d-lmafit-2d}
-    \label{fig:syn5d-lmafit-2d}}    
-   \caption{Comparison of reconstruction performance in a 2D section.
+\multiplot{5}{syn5d-clean-2d,syn5d-noisy-2d,syn5d-decimated-2d,syn5d-svd-2d,syn5d-lmafit-2d}{width=0.3\columnwidth}{Comparison of reconstruction performance in a 2D section.
 (a) Clean data.
@@
 (e) Reconstructed data using the SVD-free low-rank approximation method.}
-\label{fig:syn5d-clean-2d,syn5d-noisy-2d,syn5d-decimated-2d,syn5d-svd-2d,syn5d-lmafit-2d}
-\end{figure}
 
-\begin{figure}[htb!]
-  \centering
-  \includegraphics[width=0.45\textwidth]{linear_time/Fig/synth-ss}
-   \caption{Comparison of the middle trace amplitude of each cubes in different datasets.
+\plot{synth-ss}{width=0.3\columnwidth}{Comparison of the middle trace amplitude of each cubes in different datasets.
 The black line denotes the trace from the clean data.
@@
 The SVD-based and SVD-free methods are denoted as blue and green lines, respectively.}
-   \label{fig:synth-ss}
-\end{figure}
 
-\begin{figure}[htb!]
-  \centering
-  \subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/simi-syn5d-noisy-2d}
-    \label{fig:simi-syn5d-noisy-2d}}
-  \subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/simi-syn5d-decimated-2d}
-    \label{fig:simi-syn5d-decimated-2d}} \\
-  \subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/simi-syn5d-svd-2d}
-    \label{fig:simi-syn5d-svd-2d}} 
-  \subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/simi-syn5d-lmafit-2d}
-    \label{fig:simi-syn5d-lmafit-2d}}  
-   \caption{Comparison of reconstruction performance in terms of local similarity.
+\multiplot{4}{simi-syn5d-noisy-2d,simi-syn5d-decimated-2d,simi-syn5d-svd-2d,simi-syn5d-lmafit-2d}{width=0.45\columnwidth}{Comparison of reconstruction performance in terms of local similarity.
 (a) Local similarity of the noisy data.
@@
 (d) Local similarity of the reconstructed data using SVD-free low-rank approximation method.}
-\label{fig:simi-syn5d-noisy-2d,simi-syn5d-decimated-2d,simi-syn5d-svd-2d,simi-syn5d-lmafit-2d}
-\end{figure}
 
-\begin{figure}[htb!]
-  \centering
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-clean-3d-1}
-    \label{fig:curve5d-clean-3d-1}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-noisy-3d-1}
-    \label{fig:curve5d-noisy-3d-1}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-decimated-3d-1}
-    \label{fig:curve5d-decimated-3d-1}}        
-   \caption{Common midpoint gathers for the 5D synthetic example with hyperbolic events. (a) Clean data. (b) Noisy data. (c) The observed data with 80\% traces randomly removed.}
-   \label{fig:curve5d-clean-3d-1,curve5d-noisy-3d-1,curve5d-decimated-3d-1}
-\end{figure}
+\inputdir{curve}
+\multiplot{3}{curve5d-clean-3d-1,curve5d-noisy-3d-1,curve5d-decimated-3d-1}{width=0.3\columnwidth}{Common midpoint gathers for the 5D synthetic example with hyperbolic events.
+(a) Clean data.
+(b) Noisy data.
+(c) The observed data with 80\% traces randomly removed.}
 
-\begin{figure}[htb!]
-  \centering
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-svd-3d-1}
-    \label{fig:curve5d-svd-3d-1}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-n-svd-3d-1}
-    \label{fig:curve5d-n-svd-3d-1}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-r-svd-3d-1}
-    \label{fig:curve5d-r-svd-3d-1}} 
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-lmafit-3d-1}
-    \label{fig:curve5d-lmafit-3d-1}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-n-lmafit-3d-1}
-    \label{fig:curve5d-n-lmafit-3d-1}}
-  \subfigure[]{\includegraphics[width=0.3\columnwidth]{curve/Fig/curve5d-r-lmafit-3d-1}
-    \label{fig:curve5d-r-lmafit-3d-1}}       
-   \caption{Comparison of reconstruction performance in common midpoint gathers for the 5D synthetic example with hyperbolic events.
+\multiplot{6}{curve5d-svd-3d-1,curve5d-n-svd-3d-1,curve5d-r-svd-3d-1,curve5d-lmafit-3d-1,curve5d-n-lmafit-3d-1,curve5d-r-lmafit-3d-1}{width=0.3\columnwidth}{Comparison of reconstruction performance in common midpoint gathers for the 5D synthetic example with hyperbolic events.
 (a) Reconstructed data using the SVD-based low-rank approximation method.
@@
 (f) The reconstruction error corresponding to (d).}
-\label{fig:curve5d-svd-3d-1,curve5d-n-svd-3d-1,curve5d-r-svd-3d-1,curve5d-lmafit-3d-1,curve5d-n-lmafit-3d-1,curve5d-r-lmafit-3d-1}
-\end{figure}
 
-\begin{figure}[htb!]
-  \centering
-  \subfigure[]{\includegraphics[width=0.45\columnwidth]{curve/Fig/simi-curve5d-noisy-3d-1}
-    \label{fig:simi-curve5d-noisy-3d-1}}
- \subfigure[]{\includegraphics[width=0.45\columnwidth]{curve/Fig/simi-curve5d-decimated-3d-1}
-    \label{fig:simi-curve5d-decimated-3d-1}} \\
-  \subfigure[]{\includegraphics[width=0.45\columnwidth]{curve/Fig/simi-curve5d-svd-3d-1}
-    \label{fig:simi-curve5d-svd-3d-1}}
-  \subfigure[]{\includegraphics[width=0.45\columnwidth]{curve/Fig/simi-curve5d-lmafit-3d-1}
-    \label{fig:simi-curve5d-lmafit-3d-1} }
-   \caption{Comparison of reconstruction performance in terms of local similarity.
+\multiplot{4}{simi-curve5d-noisy-3d-1,simi-curve5d-decimated-3d-1,simi-curve5d-svd-3d-1,simi-curve5d-lmafit-3d-1}{width=0.45\columnwidth}{Comparison of reconstruction performance in terms of local similarity.
 (a) Local similarity of the noisy data.
@@
 (d) Local similarity of the reconstructed data using SVD-free low-rank approximation method.}
-\label{fig:simi-curve5d-noisy-3d-1,simi-curve5d-decimated-3d-1,simi-curve5d-svd-3d-1,simi-curve5d-lmafit-3d-1}
-\end{figure}
 
-\begin{figure*}[htb!]
-  \centering
-  \subfigure[]{\includegraphics[width=\textwidth]{field/Fig/field5d-decimated2d-0}
-    \label{fig:field5d-decimated2d-0}}
- \subfigure[]{\includegraphics[width=\textwidth]{field/Fig/field5d-svd2d-0}
-    \label{fig:field5d-svd2d-0}}
-  \subfigure[]{\includegraphics[width=\textwidth]{field/Fig/field5d-lmafit2d-0}
-    \label{fig:field5d-lmafit2d-0}}
-   \caption{Comparison of reconstruction performance in common offset gathers for the 5D field data example.
+\inputdir{./}
+\multiplot{3}{field5d-decimated2d-0,field5d-svd2d-0,field5d-lmafit2d-0}{width=0.8\columnwidth}{Comparison of reconstruction performance in common offset gathers for the 5D field data example.
 (a) Observed data with roughly 80\% traces missing.
@@
 The frame box areas are zoomed and highlighted in FIGURE \ref{fig:z-decimated,z-svd,z-lmafit}.}
-\label{fig:field5d-decimated2d-0,field5d-svd2d-0,field5d-lmafit2d-0}
-\end{figure*}
 
-\begin{figure}[htb!]
-  \centering
-  \subfigure[]{\includegraphics[width=0.9\columnwidth]{field/Fig/z-decimated}
-    \label{fig:z-decimated}}
- \subfigure[]{\includegraphics[width=0.9\columnwidth]{field/Fig/z-svd}
-    \label{fig:z-svd}}
-  \subfigure[]{\includegraphics[width=0.9\columnwidth]{field/Fig/z-lmafit}
-    \label{fig:z-lmafit}}
-   \caption{Zoomed comparison of reconstruction performance in common offset gathers for the 5D field data example.
+\multiplot{3}{z-decimated,z-svd,z-lmafit}{width=0.45\columnwidth}{Zoomed comparison of reconstruction performance in common offset gathers for the 5D field data example.
 (a) Observed data with roughly 80\% traces missing.
@@
 (c) Reconstructed data using the SVD-free low-rank approximation method.}
-\label{fig:z-decimated,z-svd,z-lmafit}
-\end{figure}
 
@@
 In this section, we use several\new{synthetic}  examples to demonstrate that the proposed SVD-free low-rank approximation method can significantly accelerate the reconstruction of 5D seismic data without loss of accuracy.
-\new{Although Hankel and Toeplitz matrices \cite{top1,top2} seem to be similar as the low-rank matrix, but in some cases one can lead us to better results in comparison to the other one.
+\new{Although Hankel and Toeplitz matrices seem to be similar as the low-rank matrix, but in some cases one can lead us to better results in comparison to the other one.
 According to our experience, the Toeplitz matrix results in a slightly better reconstruction performance.
@@
 
-\begin{thebibliography}{00}
-\bibitem{ronen}
-J.~Ronen, ``Wave-equation trace interpolation,'' \emph{Geophysics}, vol.~52,
-  pp. 973--984, 1987.
-
-\bibitem{spitz1991}
-S.~Spitz, ``Seismic trace interpolation in the f-x domain,'' \emph{Geophysics},
-  vol.~56, pp. 785--794, 1991.
-
-\bibitem{chen1995}
-J.~Chen and J.~Cihlar, ``Quantifying the effect of canopy architecture on
-  optical measurements of leaf area index using two gap size analysis
-  methods,'' \emph{IEEE Transactions on Geoscience and Remote Sensing},
-  vol.~33, pp. 777--787, 1995.
-
-\bibitem{canning1996}
-A.~Canning and G.~H.~F. Gardner, ``Reducing 3{D} acquisition footprint for 3{D}
-  dmo and 3{D} prestack migration,'' \emph{Geophysics}, vol.~63, pp.
-  1177--1183, 1996.
-
-\bibitem{fomel2002pwd}
-S.~Fomel, ``Application of plane-wave destruction filters,'' \emph{Geophysics},
-  vol.~67, pp. 1946--1960, 2002.
-
-\bibitem{fomel2003}
-------, ``Seismic reflection data interpolation with differential offset and
-  shot continuation,'' \emph{Geophysics}, vol.~68, pp. 733--744, 2003.
-
-\bibitem{abmapocs}
-R.~Abma and N.~Kabir, ``\protect{3D} interpolation of irregular data with a
-  \protect{POCS} algorithm,'' \emph{Geophysics}, vol.~71, pp. E91--E97, 2006.
-
-\bibitem{herrmann2008non}
-F.~J. Herrmann and G.~Hennenfent, ``Non-parametric seismic data recovery with
-  curvelet frames,'' \emph{Geophysical Journal International}, vol. 173, no.~1,
-  pp. 233--248, 2008.
-
-\bibitem{protter2009}
-M.~Protter and M.~Elad, ``Image sequence denoising via sparse and redundant
-  representations,'' \emph{IEEE Trans Image Process}, vol.~18, no.~1, pp.
-  27--35, 2009.
-
-\bibitem{mostafa2010}
-M.~Naghizadeh and M.~D. Sacchi, ``Beyond alias hierarchical scale curvelet
-  interpolation of regularly and irregularly sampled seismic data,''
-  \emph{Geophysics}, vol.~75, p. WB189–WB202, 2010.
-
-\bibitem{mostafa2013}
-------, ``Multidimensional de-aliased cadzow reconstruction of seismic
-  records,'' \emph{Geophysics}, vol.~78, no.~1, pp. A1--A5, 2010.
-
-\bibitem{wang2011recovery}
-Y.~Wang, J.~Cao, and C.~Yang, ``Recovery of seismic wavefields based on
-  compressive sensing by an l 1-norm constrained trust region method and the
-  piecewise random subsampling,'' \emph{Geophysical Journal International},
-  vol. 187, no.~1, pp. 199--213, 2011.
-
-\bibitem{yanan2014}
-Y.~Tian, Y.~Li, and B.~Yang, ``Variable-eccentricity hyperbolic-trace {TFPF}
-  for seismic random noise attenuation,'' \emph{IEEE Transactions on Geoscience
-  and Remote Sensing}, vol.~52, pp. 6449--6458, 2014.
-
-\bibitem{yanhui2016}
-Y.~Zhou, J.~Gao, W.~Chen, and P.~Frossard, ``Seismic simultaneous source
-  separation via patchwise sparse representation,'' \emph{IEEE Transactions on
-  Geoscience and Remote Sensing}, vol.~54, pp. 5271--5284, 2016.
-
-\bibitem{kazemi2016}
-N.~Kazemi, E.~Bongajum, and M.~D. Sacchi, ``Surface-consistent sparse
-  multichannel blind deconvolution of seismic signals,'' \emph{IEEE
-  Transactions on Geoscience and Remote Sensing}, vol.~54, pp. 3200--3207,
-  2016.
-\bibitem{shuwei2016cs}
-S.~Gan, S.~Wang, Y.~Chen, X.~Chen, W.~Huang, and H.~Chen, ``Compressive sensing
-  for seismic data reconstruction via fast projection onto convex sets based on
-  seislet transform,'' \emph{Journal of Applied Geophysics}, vol. 130, pp.
-  194--208, 2016.
-
-\bibitem{lorenzi2016}
-L.~Lorenzi, F.~Melgani, and G.~Mercier, ``Missing-area reconstruction in
-  multispectral images under a compressive sensing perspective,'' \emph{IEEE
-  Transactions on Geoscience and Remote Sensing}, vol.~51, pp. 3998--4008,
-  2016.
-
-\bibitem{shaohuan2016gap}
-S.~Zu, H.~Zhou, Y.~Chen, X.~Pan, S.~Gan, and D.~Zhang, ``Interpolating big gaps
-  using inversion with slope constraint,'' \emph{IEEE Geoscience and Remote
-  Sensing Letters}, vol.~13, pp. 1369--1373, 2016.
-
-\bibitem{yangkang2016irr5d}
-Y.~Chen, D.~Zhang, Z.~Jin, X.~Chen, S.~Zu, W.~Huang, and S.~Gan, ``Simultaneous
-  denoising and reconstruction of 5{D} seismic data via damped rank-reduction
-  method,'' \emph{Geophysical Journal International}, vol. 206, pp. 1695--1717,
-  2016.
-
-\bibitem{amir2017ieee}
-R.~Anvari, M.~A.~N. Siahsar, S.~Gholtashi, A.~R. Kahoo, and M.~Mohammadi,
-  ``Seismic random noise attenuation using synchrosqueezed wavelet transform
-  and low-rank signal matrix approximation,'' \emph{IEEE Transactions on
-  Geoscience and Remote Sensing}, vol.~55, no.~11, pp. 6574--6581, 2017.
-
-\bibitem{verschuure1991}
-D.~J. Verschuur, ``Surface-related multiple elimination: An inversion
-  approach,'' \emph{PhD thesis, Delft University of Technology}, 1991.
-
-\bibitem{jingjie2011review}
-J.~Cao, Y.~Wang, J.~Zhao, and C.~Yang, ``A review on restoration of seismic
-  wavefields based on regularization and compressive sensing,'' \emph{Inverse
-  Problems in Science and Engineering}, vol.~19, no.~5, pp. 679--704, 2011.
-
-\bibitem{yangkang20142}
-Y.~Chen, S.~Fomel, and J.~Hu, ``Iterative deblending of simultaneous-source
-  seismic data using seislet-domain shaping regularization,''
-  \emph{Geophysics}, vol.~79, pp. V179--V189, 2014.
-
-\bibitem{shuwei20153}
-S.~Gan, S.~Wang, Y.~Chen, Y.~Zhang, and Z.~Jin, ``Dealiased seismic data
-  interpolation using seislet transform with low-frequency constraint,''
-  \emph{IEEE Geoscience and Remote Sensing Letters}, vol.~12, pp. 2150--2154,
-  2015.
-
-\bibitem{shuwei2016vscan}
-S.~Gan, S.~Wang, Y.~Chen, S.~Qu, and S.~Zu, ``Velocity analysis of
-  simultaneous-source data using high-resolution semblance-coping with the
-  strong noise,'' \emph{Geophysical Journal International}, vol. 204, pp.
-  768--779, 2016.
-
-\bibitem{liuwei2016dealiase}
-W.~Liu, S.~Cao, S.~Gan, Y.~Chen, S.~Zu, and Z.~Jin, ``One-step slope estimation
-  for dealiased seismic data reconstruction via iterative seislet
-  thresholding,'' \emph{IEEE Geoscience and Remote Sensing Letters}, vol.~13,
-  pp. 1462--1466, 2016.
-
-\bibitem{shaohuan2017gji}
-S.~Zu, H.~Zhou, W.~Mao, D.~Zhang, C.~Li, X.~Pan, and Y.~Chen, ``Iterative
-  deblending of simultaneous-source data using a coherency-pass shaping
-  operator,'' \emph{Geophysical Journal International}, vol. 211, no.~1, pp.
-  541--557, 2017.
-
-\bibitem{YuSiwei2015}
-S.~Yu, J.~Ma, X.~Zhang, and M.~D. Sacchi, ``Interpolation and denoising of
-  high-dimensional seismic data by learning a tight frame,'' \emph{Geophysics},
-  vol.~80, no.~5, pp. V119--V132, 2015. [Online]. Available:
-  \url{https://doi.org/10.1190/geo2014-0396.1}
-
-\bibitem{YuSiwei2016}
-S.~Yu, J.~Ma, and S.~Osher, ``Monte carlo data-driven tight frame for seismic
-  data recovery,'' \emph{Geophysics}, vol.~81, no.~4, pp. V327--V340, 2016.
-  [Online]. Available: \url{https://doi.org/10.1190/geo2015-0343.1}
-
-\bibitem{Jia2017}
-Y.~Jia and J.~Ma, ``What can machine learning do for seismic data processing?
-  an interpolation application,'' \emph{Geophysics}, vol.~82, no.~3, pp.
-  V163--V177, 2017. [Online]. Available:
-  \url{https://doi.org/10.1190/geo2016-0300.1}
-
-\bibitem{amir2017sp}
-M.~A.~N. Siahsar, V.~Abolghasemi, and Y.~Chen, ``Simultaneous denoising and
-  interpolation of 2{D} seismic data using data-driven non-negative dictionary
-  learning,'' \emph{Signal Processing}, vol. 141, pp. 309--321, 2017.
-
-\bibitem{amir2017geo}
-M.~A.~N. Siahsar, S.~Gholtashi, A.~R. Kahoo, W.~Chen, and Y.~Chen,
-  ``Data-driven multi-task sparse dictionary learning for noise attenuation of
-  3{D} seismic data,'' \emph{Geophysics}, vol.~82, no.~6, p. V385–V396, 2017.
-
-\bibitem{Jia2018}
-Y.~Jia, S.~Yu, and J.~Ma, ``Intelligent interpolation by monte carlo machine
-  learning,'' \emph{Geophysics}, vol.~83, no.~2, pp. V83--V97, 2018. [Online].
-  Available: \url{https://doi.org/10.1190/geo2017-0294.1}
-
-\bibitem{zhangmi2019}
-M.~Zhang, Y.~Liu, M.~Bai, and Y.~Chen, ``Seismic noise attenuation using
-  unsupervised sparse feature learning,'' \emph{IEEE Transactions on Geoscience
-  and Remote Sensing}, p. doi: 10.1109/TGRS.2019.2928715, 2019.
-
-\bibitem{yangkang2015ortho}
-Y.~Chen and S.~Fomel, ``Random noise attenuation using local signal-and-noise
-  orthogonalization,'' \emph{Geophysics}, vol.~80, pp. WD1--WD9, 2015.
-
-\bibitem{guochang2012}
-G.~Liu, X.~Chen, J.~Du, and K.~Wu, ``Random noise attenuation using \emph{f-x}
-  regularized nonstationary autoregression,'' \emph{Geophysics}, vol.~77, pp.
-  V61--V69, 2012.
-
-\bibitem{fxnaghizadeh}
-M.~Naghizadeh and M.~Sacchi, ``Multicomponent f-x seismic random noise
-  attenuation via vector autoregressive operators,'' \emph{Geophysics},
-  vol.~77, pp. V91--V99, 2012.
-
-\bibitem{beckouche}
-S.~Beckouche and J.~Ma, ``Simultaneous dictionary learning and denoising for
-  seismic data,'' \emph{Geophysics}, vol.~79, pp. A27--A31, 2014.
-
-\bibitem{mostafa2016bssa}
-S.~M. Mousavi and C.~A. Langston, ``Hybrid seismic denoising using higher-order
-  statistics and improved wavelet block thresholding,'' \emph{Bulletin of the
-  Seismological Society of America}, vol. 106, no.~4, pp. 1380--1393, 2016.
-
-\bibitem{mostafa2017geo}
-------, ``Automatic noise-removal/signal-removal based on general
-  cross-validation thresholding in synchrosqueezed domain and its application
-  on earthquake data,'' \emph{Geophysics}, vol.~82, no.~4, pp. V211--V227,
-  2017.
-
-\bibitem{zhaoqiang2018}
-Q.~Zhao, Q.~Du, X.~Gong, and Y.~Chen, ``Signal-preserving erratic noise
-  attenuation via iterative robust sparsity-promoting filter,'' \emph{IEEE
-  Transactions on Geoscience and Remote Sensing}, vol.~56, no.~6, pp.
-  1558--0644, 2018.
-
-\bibitem{oropezamssa}
-V.~Oropeza and M.~Sacchi, ``Simultaneous seismic data denoising and
-  reconstruction via multichannel singular spectrum analysis,''
-  \emph{Geophysics}, vol.~76, pp. V25--V32, 2011.
-
-\bibitem{gaomssa}
-J.~Gao, M.~Sacchi, and X.~Chen, ``A fast reduced-rank interpolation method for
-  prestack seismic volumes that depend on four spatial dimensions,''
-  \emph{Geophysics}, vol.~78, pp. V21--V30, 2013.
-
-\bibitem{Gaogp}
-J.~Gao, A.~Stanton, M.~Naghizadeh, M.~D. Sacchi, and X.~Chen, ``Convergence
-  improvement and noise attenuation considerations for beyond alias projection
-  onto convex sets reconstruction,'' \emph{Geophysical Prospecting}, vol.~61,
-  pp. 138--151, 2013.
-
-\bibitem{gholami}
-A.~Gholami, ``Non-convex compressed sensing with frequency mask for seismic
-  data reconstruction and denoising,'' \emph{Geophysical Prospecting}, vol.~62,
-  pp. 1389--1405, 2015.
-
-\bibitem{benfengpocs}
-B.~Wang, R.~Wu, X.~Chen, and J.~Li, ``Simultaneous seismic data interpolation
-  and denoising with a new adaptive method based on dreamlet transform,''
-  \emph{Geophysical Journal International}, vol. 201, pp. 1180--1192, 2015.
-
-\bibitem{pmf}
-J.~Gao, A.~Stanton, and M.~D. Sacchi, ``Parallel matrix factorization algorithm
-  and its application to 5{D} seismic reconstruction and denoising,''
-  \emph{Geophysics}, vol.~80, pp. V173--V187, 2015.
-
-\bibitem{wangchong2018}
-C.~Wang, Z.~Zhu, H.~Gu, X.~Wu, and S.~Liu, ``Hankel low-rank approximation for
-  seismic noise attenuation,'' \emph{IEEE Transactions on Geoscience and Remote
-  Sensing}, no.~99, pp. 1--13, 2018.
-
-\bibitem{Liubin2004}
-B.~Liu and M.~D. Sacchi, ``Minimum weighted norm interpolation of seismic
-  records,'' \emph{Geophysics}, vol.~69, no.~6, pp. 1560--1568, 2004. [Online].
-  Available: \url{https://doi.org/10.1190/1.1836829}
-
-\bibitem{Trad2007}
-D.~Trad, ``A strategy for wide azimuth land interpolation,'' \emph{SEG
-  Technical Program Expanded Abstracts}, pp. 946--950, 2007. [Online].
-  Available: \url{https://library.seg.org/doi/abs/10.1190/1.2792562}
-
-\bibitem{Trad2009}
-------, ``Five-dimensional interpolation: Recovering from acquisition
-  constraints,'' \emph{Geophysics}, vol.~74, pp. V123--V132, 2009.
-
-\bibitem{GaoJianjun2017}
-J.~Gao, J.~Cheng, and M.~D. Sacchi, ``Five-dimensional seismic reconstruction
-  using parallel square matrix factorization,'' \emph{IEEE Transactions on
-  Geoscience and Remote Sensing}, vol.~55, no.~4, pp. 2124--2135, April 2017.
-
-\bibitem{Xie2017}
-Y.~Xie and D.~Gajewski, ``5-{D} interpolation with wavefront attributes,''
-  \emph{Geophysical Journal International}, vol. 211, pp. 897--919, 08 2017.
-
-\bibitem{lu2015fast}
-L.~Lu, W.~Xu, and S.~Qiao, ``A fast {SVD} for multilevel block hankel matrices
-  with minimal memory storage,'' \emph{Numerical Algorithms}, vol.~69, no.~4,
-  pp. 875--891, 2015.
-
-\bibitem{jinkun2016}
-J.~Cheng and M.~Sacchi, ``Fast dual-domain reduced-rank algorithm for 3{D}
-  deblending via randomized qr decomposition,'' \emph{Geophysics}, vol.~81, pp.
-  V89--V101, 2014.
-
-\bibitem{jianjun2017five}
-J.~Gao, J.~Cheng, and M.~D. Sacchi, ``Five-dimensional seismic reconstruction
-  using parallel square matrix factorization,'' \emph{IEEE Transactions on
-  Geoscience and Remote Sensing}, vol.~55, no.~4, pp. 2124--2135, 2017.
-
-\bibitem{gavish2014optimal}
-M.~Gavish and D.~L. Donoho, ``The optimal hard threshold for singular values is
-  4/sqrt(3),'' \emph{IEEE Transactions on Information Theory}, vol.~60, no.~8,
-  pp. 5040--5053, 2014.
-
-\bibitem{trickett2015preserving}
-S.~Trickett, ``Preserving signal: Automatic rank determination for noise
-  suppression,'' in \emph{SEG Technical Program Expanded Abstracts 2015}.\hskip
-  1em plus 0.5em minus 0.4em\relax Society of Exploration Geophysicists, 2015,
-  pp. 4703--4707.
-
-\bibitem{aharchaou2017singular}
-M.~Aharchaou, J.~Anderson, S.~Hughes, and J.~Bingham, ``Singular-spectrum
-  analysis via optimal shrinkage of singular values,'' in \emph{SEG Technical
-  Program Expanded Abstracts 2017}.\hskip 1em plus 0.5em minus 0.4em\relax
-  Society of Exploration Geophysicists, 2017, pp. 4950--4954.
-
-\bibitem{yatong2018gji}
-Y.~Zhou, S.~Li, D.~Zhang, and Y.~Chen, ``Seismic noise attenuation using an
-  online subspace tracking algorithm,'' \emph{Geophysical Journal
-  International}, vol. 212, no.~2, p. 1072–1097, 2018.
-
-\bibitem{wujuan2018jge3}
-J.~Wu and M.~Bai, ``Adaptive rank-reduction method for seismic data
-  reconstruction,'' \emph{Journal of Geophysics and Engineering}, vol.~15, p.
-  1688, 2018.
-
-\bibitem{weilin2016}
-W.~Huang, R.~Wang, Y.~Chen, H.~Li, and S.~Gan, ``Damped multichannel singular
-  spectrum analysis for 3{D} random noise attenuation,'' \emph{Geophysics},
-  vol.~81, no.~4, pp. V261--V270, 2016.
-
-\bibitem{weilingieeedls}
-W.~Huang, R.~Wang, X.~Chen, and Y.~Chen, ``Double least-squares projections
-  method for signal estimation,'' \emph{IEEE Transactions on Geoscience and
-  Remote Sensing}, vol.~55, pp. 4111--4129, 2017.
-
-\bibitem{dong}
-D.~Zhang, Y.~Chen, W.~Huang, and S.~Gan, ``Multi-step damped multichannel
-  singular spectrum analysis for simultaneous reconstruction and denoising of
-  3{D} seismic data,'' \emph{Journal of Geophysics and Engineering}, vol.~13,
-  pp. 704--720, 2016.
-
-\bibitem{dong2017}
-D.~Zhang, Y.~Zhou, H.~Chen, W.~Chen, S.~Zu, and Y.~Chen, ``Hybrid rank-sparsity
-  constraint model for simultaneous reconstruction and denoising of 3{D}
-  seismic data,'' \emph{Geophysics}, vol.~82, pp. V351--V367, 2017.
-
-\bibitem{yufeng2017}
-Y.~Wang, H.~Zhou, S.~Zu, W.~Mao, and Y.~Chen, ``Three-operator proximal
-  splitting scheme for 3{D} seismic data reconstruction,'' \emph{IEEE
-  Geoscience and Remote Sensing Letters}, vol.~14, no.~10, pp. 1830--1834,
-  2017.
-
-\bibitem{yangkangelra}
-Y.~Chen, Y.~Zhou, W.~Chen, S.~Zu, W.~Huang, and D.~Zhang, ``Empirical low-rank
-  approximation for seismic noise attenuation,'' \emph{IEEE Transactions on
-  Geoscience and Remote Sensing}, vol.~55, pp. 4696--4711, 2017.
-
-\bibitem{baimin2018cg}
-M.~Bai, J.~Wu, S.~Zu, and W.~Chen, ``A structural rank reduction operator for
-  removing artifacts in least-squares reverse time migration,'' \emph{Computers
-  and Geosciences}, vol. 117, pp. 9--20, 2018.
-
-\bibitem{stanton2013processing}
-A.~Stanton, N.~Kazemi, and M.~D. Sacchi, ``Processing seismic data in the
-  presence of residual statics,'' in \emph{SEG Technical Program Expanded
-  Abstracts 2013}.\hskip 1em plus 0.5em minus 0.4em\relax Society of
-  Exploration Geophysicists, 2013, pp. 1838--1842.
-
-\bibitem{lmafit}
-Z.~Wen, W.~Yin, and Y.~Zhang, ``Solving a low-rank factorization model for
-  matrix completion by a nonlinear successive over-relaxation algorithm,''
-  \emph{Mathematical Programming Computation}, vol.~4, pp. 333--361, 2012.
-
-\bibitem{weilin2017gji}
-W.~Huang, R.~Wang, S.~Zu, and Y.~Chen, ``Low-frequency noise attenuation in
-  seismic and microseismic data using mathematical morphological filtering,''
-  \emph{Geophysical Journal International}, vol. 211, p. 1318–1340, 2017.
-
-\bibitem{yangkang2020odrr}
-Y.~Chen, M.~Bai, Z.~Guan, Q. Zhang, M. Zhang, and H.~Wang, ``Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method,''
-  \emph{Geophysical Journal International}, vol. 222, p. 1824-1845, 2020.
-
-\bibitem{top1}
-A.~Bottcher, S.M.~Grudsky, and T.~Kunz, ``Toeplitz Matrices, Asymptotic Linear Algebra, and Functional Analysis,''
-  \emph{ISBN: 978-3-7643-6290-4,A Birkhäuser book}, 2000.
-
-\bibitem{top2}
-R.M.~Gray, ``Toeplitz and Circulant Matrices: A review,''
-  \emph{Foundations and Trends in Communications and Information Theory}, vol. 2, pp. 155-239, 2006.
-
-\end{thebibliography}
+\bibliographystyle{seg}
+\bibliography{5d}
 
@@
 %
-\clearpage
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{juan}}]{Juan Wu} received the Ph.D.
-degree in geophysics from the China University of Petroleum, Beijing, China, in 2016, under the supervision of Prof.
-Xiaohong Chen.
-She is currently a Post-Doctoral Researcher with Yangtze University, Jingzhou, China.
-She has authored or coauthored more than 30 journal articles.
-Her research interests include seismic signal analysis and seismic imaging.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{min}}]{Min Bai}
- received the Ph.D. degree in geophysics from the China University of Petroleum, Beijing, China, in 2016, under the supervision of Prof. Xiaohong Chen.
-He is currently a Post-Doctoral Researcher with the School of Earth Sciences, Zhejiang University, Hangzhou, China, and a Lecturer with Yangtze University, Jingzhou, China.
-He has authored or coauthored more than 30 journal articles.
-His research interests include seismic imaging and inversion and seismic signal analysis.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{dong}}]{Dong Zhang} received the B.S.
-degree in applied geophysics from Jilin University, Changchun, China, in 2014.
-He is currently pursuing a PhD degree in Geophysics at Delft university of technology.
-His current research interests include seismic signal analysis, seismic imaging and simultaneous-source data deblending and imaging.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{hang}}]{Hang Wang} received a master degree in geological resources and geological engineering from China University of Petroleum (Beijing), and he is a Ph.D.
-candidate in geophysics at Zhejiang University.
-His research interests include seismic signal processing, machine learning and FWI.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{guangtan}}]{Guangtan Huang} received the B.S., M.S., and Ph.D.
-degrees in exploration geophysics from the China University of Petroleum (East China), Beijing, Beijing, China, in 2012, 2015, and 2019, respec- tively.
-He holds a post-doctoral position in geophyiscs at Zhejiang University, Hangzhou, China.
-His research interests include seismic forward modeling and high-resolution seismic inversion.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{yangkang}}]{Yangkang Chen} received the B.S.
-degree in explo- ration geophysics from the China University of Petroleum, Beijing, Beijing, China, in 2012, and the Ph.D.
-degree in geophysics from the University of Texas at Austin, Austin, TX, USA, in 2015, under the supervision of Prof.
-S.
-Fomel.
-He was a Distinguished Post-Doctoral Research Associate with Oak Ridge National Laboratory, Oak Ridge, TN, USA, where he conducted research on global adjoint tomography.
-He is an Assistant Pro- fessor with Zhejiang University, Hangzhou, China.
-He has authored or coauthored more than 100 internationally renowned journal articles and more than 80 international conference papers.
-His research interests include seismic signal analysis, seismic modeling and inversion, simultaneous-source data deblending and imaging, global adjoint tomography, machine learning, and high-performance computing.
-\end{IEEEbiography}
-
-\EOD

### 2020-12-25 lr5d/matfun/P_HH.m

@@ -1,0 +1,88 @@
+function [dout]=P_HH(din,lx,ly,lxx,lhx,lhy,lhxx,lhyy)
+
+H2=P_H2(din,lhx,lhy,lhxx,lhyy);
+dout=P_H4(H2,lx,ly,lxx,lhx,lhy,lhxx,lhyy);
+
+return
+end
+
+function [dout]=P_H4(din,lx,ly,lxx,lhx,lhy,lhxx,lhyy)
+% forming block Hankel matrix
+[~,nhy,~,~]=size(din);
+
+for j=1:nhy
+    h2=squeeze(din(:,j,:,:));
+    r=P_H3(h2,lhx,lhy,lhxx,lhyy);
+    if j<ly
+        for id=1:j
+            dout(1+(j-1)*lx*lhx*lhy-(id-1)*lx*lhx*lhy:j*lx*lhx*lhy-(id-1)*lx*lhx*lhy,1+(id-1)*lxx*lhxx*lhyy:lxx*lhxx*lhyy+(id-1)*lxx*lhxx*lhyy) = r;
+        end
+    else
+        for id=1:(nhy-j+1)
+            dout((ly-1)*lx*lhx*lhy+1-(id-1)*lx*lhx*lhy:ly*lx*lhx*lhy-(id-1)*lx*lhx*lhy,(j-ly)*lxx*lhxx*lhyy+1+(id-1)*lxx*lhxx*lhyy:(j-ly+1)*lxx*lhxx*lhyy+(id-1)*lxx*lhxx*lhyy)=r;
+        end
+    end
+end
+return
+end
+
+function [dout]=P_H3(din,lhx,lhy,lhxx,lhyy)
+% forming 3rd order block Hankel matrix
+
+[nhx,~,~]=size(din);
+lx=floor(nhx/2)+1;
+
+for j=1:nhx
+    if j<lx
+        for id=1:j
+            dout(1+(j-1)*lhx*lhy-(id-1)*lhx*lhy:j*lhx*lhy-(id-1)*lhx*lhy,1+...
+                (id-1)*lhxx*lhyy:lhxx*lhyy+(id-1)*lhxx*lhyy) = din(j,:,:);
+        end
+    else
+        for id=1:(nhx-j+1)
+            dout((lx-1)*lhx*lhy+1-(id-1)*lhx*lhy:lx*lhx*lhy-(id-1)*lhx*lhy,...
[…]

### 2020-12-25 lr5d/matfun/P_Lmafit.m

@@ -1,0 +1,34 @@
+function [dout]=P_Lmafit(din,N)
+% Rank reduction on the block Hankel matrix
+    [m,n]=size(din);
+    [data,position]=PreServ(din);    
+    opts=[];
+    [X,Y,~] = lmafit_mc_adp(m,n,N,position,data,opts);
+    dout=X*Y;
+return
+end
+
+function [data, position]=PreServ(input)
+[m n]=size(input);
+% count=1;
+% 
+% for i=1:n
+%     
+%     for j=1:m
+%         
+%         if input(j,i)~=0
+%             
+%             data(count)=input(j,i);            
+%             position(count)=(i-1)*m+j;
+%             count=count+1;
+%             
+%         end
+%         
+%     end
+% 
+% end
+
+position=1:m*n;
+data=reshape(input,1,m*n);
+
+end

### 2020-12-25 lr5d/matfun/lmafit/lmafit_mc_adp.m

@@ -1,0 +1,262 @@
+function [X,Y,Out] = lmafit_mc_adp(m,n,k,Known,data,opts)
+%
+% Solver for matrix completion:
+%
+%        U_ij ~= A_ij,  for i,j in Known
+%
+% where U =  X*Y and A_ij's are given in an known index set.
+%
+% Output:
+%           X --- m x k matrix
+%           Y --- k x n matrix
+%         Out --- output information
+% Input:
+%        m, n --- matrix sizes
+%           k --- rank estimate
+%        data --- values of known elements in a 1D row vector
+%       Known --- positions of known elements in a 1D row vector
+%                 assuming matrices are arranged column-wise
+%             or  Known is a structure with two fields [Ik, Jk]
+%        opts --- option structure with fields as follows:
+%
+%        ******************************************************************
+%        Fields in opts:
+%        tol      -    tolerance, default: 1.25e-4
+%        maxit    -    max. number of iterations, default:  500
+%        print    = {0, 1, 2}; level of output information
+%        DoQR     = 1; use QR to solve the least square subproblem
+%                 = 0; use "linsolve" ....
+%        Zfull    = 0; use a dense matrix to store Z
+%                   1; use the factor and sparse form Z = XY + S
+%        est_rank = 0; rank is fixed
+%                 = 1; the decreasing rank strategy, 
+%                      related fields: rank_min, rk_jump
+%                 = 2; the increasing rank strategy
+%                      related fields: rank_max, rk_inc
+%        rank_min -    the minimal rank allowed if est_rank = 1
+%                      default: 1
+%        rank_max -    the maximal rank allowed if est_rank = 2
+%                      default: max(floor(0.1*min(m,n)),2*k)
+%        rk_jump  -    tolerance to decrease the rank if est_rank = 1
+%                      default: 10
+%        rk_inc   -    the increase of the rank if est_rank = 2
+%                      default: 1; 
[…]

### 2020-12-25 lr5d/matfun/lmafit/partXY.c

@@ -1,0 +1,60 @@
+/* -------------------------------------------------------------------------- */
+/* partXY_mex mexFunction */
+/* -------------------------------------------------------------------------- */
+
+#include "mex.h"
+#include "blas.h"
+
+/* compute a part of X*Y */
+void mexFunction
+(
+    int nargout,
+    mxArray *pargout [ ],
+    int nargin,
+    const mxArray *pargin  [ ]
+)
+{
+    double *Xt, *Y, *Z, *I, *J, *v, LL;
+    ptrdiff_t m, n, r, L, p, ir, jr, k;
+    ptrdiff_t inc = 1;
+
+    if (nargin != 5 || nargout > 1)
+        mexErrMsgTxt ("Usage: v = partXY (Xt, Y, I, J, L)") ;
+
+    /* ---------------------------------------------------------------- */
+    /* inputs */
+    /* ---------------------------------------------------------------- */
+    
+    Xt = mxGetPr( pargin [0] );
+    Y  = mxGetPr( pargin [1] );
+    I  = mxGetPr( pargin [2] );
+    J  = mxGetPr( pargin [3] );
+    LL = mxGetScalar( pargin [4] ); L = (ptrdiff_t) LL;
+    m  = mxGetN( pargin [0] );
+    n  = mxGetN( pargin [1] );
+    r  = mxGetM( pargin [0] ); 
+    if ( r != mxGetM( pargin [1] ))
+        mexErrMsgTxt ("rows of Xt must be equal to rows of Y") ;
+    if ( r > m || r > n )
+        mexErrMsgTxt ("rank must be r <= min(m,n)") ;
+    
+    /* ---------------------------------------------------------------- */
+    /* output */
+    /* ---------------------------------------------------------------- */
+
+    pargout [0] = mxCreateDoubleMatrix(1, L, mxREAL);
+    v = mxGetPr( pargout [0] );
+    
+    /* C array indices start from 0 */
+    for (p = 0; p < L; p++) {
+        ir = ( I[p] - 1 ) * r;
+        jr = ( J[p] - 1 ) * r;
+        v[p] = 0.0;
+        for (k = 0; k < r; k++)
+            v[p] += Xt[ ir + k ] * Y[ jr + k ];
+        /* v[p] = ddot(&r, Xt+ir, &inc, Y+jr, &inc);*/
+    }
+    
+    return;
+}
+

### 2020-12-25 lr5d/matfun/lmafit/updateSval.c

@@ -1,0 +1,40 @@
+/* -------------------------------------------------------------------------- */
+/* SetSpv mexFunction */
+/* -------------------------------------------------------------------------- */
+
+#include "mex.h"
+#include "blas.h"
+/*#include "matrix.h"*/
+
+/* set values to sparse matrix S */
+void mexFunction
+(
+    int nargout,
+    mxArray *pargout [ ],
+    int nargin,
+    const mxArray *pargin  [ ]
+)
+{
+    double *Sval, *v, LL;
+    unsigned long int L, k;
+    ptrdiff_t inc = 1;
+
+    if (nargin != 3 || nargout > 0)
+        mexErrMsgTxt ("Usage:  SetSpv ( S, v, L )") ;
+
+    /* ---------------------------------------------------------------- */
+    /* inputs */
+    /* ---------------------------------------------------------------- */
+    
+    Sval = mxGetPr( pargin [0] );
+    v   = mxGetPr( pargin [1] );
+    LL = mxGetScalar( pargin [2] );  L = (unsigned long int) LL;
+    
+    /* ---------------------------------------------------------------- */
+    /* output */
+    /* ---------------------------------------------------------------- */
+
+    for (k = 0; k < L; k++) Sval[k] = v[k];
+    /* dcopy(&L,v, &inc, Sval, &inc); */
+    return;
+}

### 2020-12-25 lr5d/matfun/lr5d_lmafit.m

@@ -1,0 +1,71 @@
+function [d_recon] = mssa5d_lmafit(dn0,nt,nf,nhx,nhy,nx,ny,dt,flow,fhigh,N,K,eps,Niter,a,mask)
+%% data processing - MSSA
+
+% Transform into F-X domain
+DATA_FX=fft(dn0,nf,1);
+DATA_FX0=zeros(nf,nhx,nhy,nx,ny);
+
+MASK=squeeze(mask(1,:,:,:,:));
+
+% First and last nts of the DFT.
+ilow  = floor(flow*dt*nf)+1;
+
+if ilow<1
+    ilow=1;
+end;
+
+ihigh = floor(fhigh*dt*nf)+1;
+
+if ihigh > floor(nf/2)+1
+    ihigh=floor(nf/2)+1;
+end
+
+lhx=floor(nx/2)+1;
+lhxx=nx-lhx+1;
+lhy=floor(ny/2)+1;
+lhyy=ny-lhy+1;
+
+lx=floor(nhx/2)+1;
+lxx=nhx-lx+1;
+ly=floor(nhy/2)+1;
+lyy=nhy-ly+1;
+
+% main loop on frequency
+for k=ilow:ihigh
+
+    S_obs=squeeze(DATA_FX(k,:,:,:,:)); 
+    Sn_1=S_obs;
+    
+    for iter=1:Niter
+        
+        M4=P_HH(Sn_1,lx,ly,lxx,lhx,lhy,lhxx,lhyy);
+        M4=P_Lmafit(M4,N);
+        Sn=P_AA(M4,nf,nhx,nhy,nx,ny,lx,ly,lxx,lhx,lhy,lhxx,lhyy);
+        
+        Sn=a(iter)*S_obs+(1-a(iter))*MASK.*Sn+(1-MASK).*Sn;
+        
+        if norm(reshape(Sn,nhx*nhy,nx*ny)-reshape(Sn_1,nhx*nhy,nx*ny),'fro')<eps
+            break;
+        end
+        
+        Sn_1=Sn;
+        
+    end
+    
+    DATA_FX0(k,:,:,:,:)=reshape(Sn,1,nhx,nhy,nx,ny);
+   
+    if(mod(k,5)==0)
+        fprintf( 'F %d is done!\n\n',k);
+    end
+    
+end
+
+% Back to TX (the output)
+for k=nf/2+2:nf
[…]

### 2020-12-25 lr5d/matfun/lr5d_rsvd.m

@@ -1,0 +1,72 @@
+function [d_recon] = mssa5d_rsvd(dn0,nt,nf,nhx,nhy,nx,ny,dt,flow,fhigh,N,K,P,eps,Niter,a,mask)
+%% data processing - MSSA
+
+% Transform into F-X domain
+DATA_FX=fft(dn0,nf,1);
+DATA_FX0=zeros(nf,nhx,nhy,nx,ny);
+
+MASK=squeeze(mask(1,:,:,:,:));
+
+% First and last nts of the DFT.
+ilow  = floor(flow*dt*nf)+1;
+
+if ilow<1
+    ilow=1;
+end;
+
+ihigh = floor(fhigh*dt*nf)+1;
+
+if ihigh > floor(nf/2)+1
+    ihigh=floor(nf/2)+1;
+end
+
+lhx=floor(nx/2)+1;
+lhxx=nx-lhx+1;
+lhy=floor(ny/2)+1;
+lhyy=ny-lhy+1;
+
+lx=floor(nhx/2)+1;
+lxx=nhx-lx+1;
+ly=floor(nhy/2)+1;
+lyy=nhy-ly+1;
+
+% main loop on frequency
+for k=ilow:ihigh
+
+    S_obs=squeeze(DATA_FX(k,:,:,:,:)); 
+    Sn_1=S_obs;
+    
+    for iter=1:Niter
+        
+        M4=P_HH(Sn_1,lx,ly,lxx,lhx,lhy,lhxx,lhyy);
+        %M4=rsvd(M4,N);
+        M4=rSVDbasic(M4,N,P,K);
+        Sn=P_AA(M4,nf,nhx,nhy,nx,ny,lx,ly,lxx,lhx,lhy,lhxx,lhyy);
+        
+        Sn=a(iter)*S_obs+(1-a(iter))*MASK.*Sn+(1-MASK).*Sn;
+        
+        if norm(reshape(Sn,nhx*nhy,nx*ny)-reshape(Sn_1,nhx*nhy,nx*ny),'fro')<eps
+            break;
+        end
+        
+        Sn_1=Sn;
+        
+    end
+    
+    DATA_FX0(k,:,:,:,:)=reshape(Sn,1,nhx,nhy,nx,ny);
+   
+    if(mod(k,5)==0)
+        fprintf( 'F %d is done!\n\n',k);
+    end
+    
+end
+
+% Back to TX (the output)
[…]

### 2020-12-29 grouse/paper.tex
2020年12月29日 星期二 15时17分46秒 CST

\title{Seismic noise attenuation using an online subspace tracking algorithm}
\author{Yatong Zhou\footnotemark[1] and Shuhua Li\footnotemark[1] and Dong Zhang\footnotemark[2] and Yangkang Chen\footnotemark[3]}

\address{
\footnotemark[1] School of Electronic and Information Engineering \\
Hebei University of Technology \\
Xiping Road No. 5340, Beichen District\\
Tianjin, China, 300401 \\
zyt\_htu@126.com \\ 
\footnotemark[2] Departments of Imaging Physics \\
Delft university of technology \\
D.Zhang-3@tudelft.nl \\
%331334826@qq.com
%liutingjiy@126.com \\
%+86-18810415565 
%\footnotemark[2] Department of Physics\\
%University of Alberta\\
%Edmonton, AB T6G 2R3, Canada \\
%xjyshl@sina.com \\
\footnotemark[3] Previously: Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
Currently: National Center for Computational Sciences \\
Oak Ridge National Laboratory \\
One Bethel Valley Road, \\
Oak Ridge, TN 37831-6008 \\
Email: chenyk2016@gmail.com\\
%University Station, Box X\\
%Austin, TX 78713-8924, USA \\
%Email: ykchen@utexas.edu
}
\DeclareRobustCommand{\dlo}[1]{\ifthenelse{\boolean{@revd}}{}{}}
\DeclareRobustCommand{\wen}[1]{%
  \ifthenelse{\boolean{@revd}}{\textcolor{black}{#1}}{#1}}

\lefthead{Zhou et al.}
\righthead{Online subspace tracking algorithm}

\begin{abstract}
We propose a new low-rank based noise attenuation method using an efficient  algorithm for tracking subspaces from highly corrupted seismic observations. The subspace tracking algorithm requires only basic linear algebraic manipulations. %Each subspace update can be performed in linear time in the dimension of the subspace. 
The algorithm is derived by analyzing incremental gradient descent on the Grassmannian manifold of subspaces. When the multi-dimensional seismic data is mapped to a low-rank space, the subspace tracking algorithm can be directly applied to the input low-rank matrix to estimate the useful signals. Since the subspace tracking algorithm is an online algorithm, it is more robust to random noise than traditional \wen{truncated} singular value decomposition (TSVD) based subspace tracking algorithm. Compared with the state-of-the-art algorithms, the proposed denoising method can obtain better performance. More specifically, the proposed method outperforms the \wen{TSVD-based} singular spectrum analysis (SSA) method in causing less residual noise and also in saving half of the computational cost. Several synthetic and field data examples with different levels of complexities demonstrate the effectiveness and robustness of the presented algorithm in rejecting different types of noise including random noise, spiky noise, blending noise, and coherent noise. 
\end{abstract}

\maketitle

\section{Introduction}
Seismic data is inevitably corrupted by different types of noise. The existence of noise in the prestack seismic data masks useful signals, affects the amplitude information, and thus causes unreliable inversion results. Even in post-stack seismic data, the existence of noise will affect interpretation result which directly links the seismic images with subsurface oil \& gas reservoirs \cite[]{yanfei2011,yangkangthesis,pstmjse2016,jsewe2016,yangkang2016emd,shuwei2016vscan}. A successful separation between useful reflection signals and unwanted noise is a long standing problem in the area of seismic data processing and greatly affects the fidelity of subsequent seismic imaging and geophysical inversion, like amplitude-variation-with-offset (AVO) inversion, full waveform inversion, attenuation estimation, and geological interpretation \cite[]{jsehessian2015,jserugekutta2016,jsepssp2016,jsedecon2016,fangyu2016,qianping2016,mostafa2016geo,mostafa2016jag,mostafa2016bssa,zhaoyu2016,qushan2016seg,jingnan2017,qushan2017,saleh2017,mostafa2017geo}. Effectively rejecting the cross-talke interference caused in the simultaneous-source seismic acquisition also plays a significant role in tremendously saving the data recording cost \cite[]{berkhout2008,qushan2014,abma2015,qushan2015,shaohuan2015,yangkang2015pnmo,yangkang2015image,yangkang2015dbortho,qushan2016,yangkang2017lsrtm,shaohuan2017,shaohuan2017jag,shaohuan2017gji,yatong2017}.

Over the past few decades, a large number of denoising methods for random noise have been developed and widely applied in practice. The simplest denoising method is by stacking the seismic data along the offset direction \cite[]{Mayne62,guochang2009,wencheng2015stack}. By stacking the useful signals from multiple traces and multiple directions (e.g., offset and midpoint), the signal is enhanced while influence of noise is mitigated. Prediction based methods utilize the predictable property of useful signals to construct prediction \dlo{filterers}\wen{filters} and then enhance signals and reject noise, for example, t-x predictive filtering \cite[]{abma1995}, f-x deconvolution \cite[]{canales1984,mostafa2012}, the forward-backward prediction approach \cite[]{yanghua1999}, the polynomial fitting based approach \cite[]{guochang20112}, and non-stationary predictive filtering \cite[]{guochang2012,guochang2013}.

Sparse transform based approaches first transform seismic data to a sparse domain \cite[]{sacchi1995,benfengpocs,yangkang2017sgk,weilin2017seg1}, then apply soft thresholding to the coefficients, finally transform the sparse coefficients back to the time-space domain. Widely used sparse transforms are Fourier transform \cite[]{pratt1998,mostafa2011,benfeng2015,jsevscan2016,jsefwi2016,zhongwei2016}, curvelet transform \cite[]{candes20061,hermann2007,neelamani2008,shaohuan2016,liuwei20162}, seislet transform \cite[]{fomel2010seislet,liuyang2010,liuyang2014,yangkang20142,yangkang2015emdseis,shuwei20153,shuwei2015seg2,shuwei2016cs,liuwei2016dealiase}, seislet frame transform \cite[]{fomel2010seislet,shuwei2015seg1,shuwei20163}, shearlet transform \cite[]{jsedecon2016,jseshearlet2016}, Radon transform \cite[]{sacchi1995,yaru2014,jsedemul2016,yaru2016,yaru20172}, and different types of wavelet transforms (e.g., physical, synchrosqueezing, empirical wavelet transforms, etc) \cite[]{donoho1994,zhangr2003,jinghuai2006,xieqian2015eage,liuwei2016sswt,liuwei2016}, and dictionary learning based sparse transform \cite[]{elad2006,mairal2008,siwei2015,yangkang2016dsd,amir2017,amir2017geo}.

Decomposition based approaches decompose the noisy seismic data into different components and then select the principal components to represent the useful signals. Empirical mode decomposition and its variations \cite[]{yangkang20141,yangkang2015enhemd,shuwei2016ag,chenwei2016,chenwei2016seg2,chenwei2017,chenwei2017emd,chenwei2017iceemd}, variational mode decomposition \cite[]{liuwei2016eage,liuwei2016vmd,liuwei2017}, singular value decomposition based approaches \cite[]{bekara2007,weilin2016seg2,yufeng2017}, morphological decomposition \cite[]{huijian2016,huijian20162,weilin2017morph,weilin2017ieee2,weilin2017gji}, empirical wavelet transform \cite[]{gilles2013,kumar2015}, and regularized non-stationary decomposition based approaches \cite[]{fomel20132,guoning2017} are frequently used to extract the useful components of multi-dimensional seismic data in the literature.

Rank-reduction based approaches assume the seismic data to be low-rank after some data rearrangement steps. Such methods include the Cadzow filtering \cite[]{trickett2008}, singular spectrum analysis \cite[]{vautard1992singular,mssa,jianjun2013,jinkun2015}, damped  singular spectrum analysis \cite[]{weilin2015,weilin2016,yangkang2016irr5d,yangkang2016irr3d,amir2017grsl}, multi-step singular spectrum analysis \cite[]{zhangdong2016cseg,zhangdong2016}, sparsity-regularized singular spectrum analysis \cite[]{zhangdong2016eage,zhangdong2016seg,amir2016,amir2017ieee,zhangdong2017}, randomized-order singular spectrum analysis \cite[]{weilin2017}, structural low-rank approximation \cite[]{yatong2017ieee}, empirical low-rank approximation \cite[]{yangkang2017ieee}. Mean (or stacking) and median filters utilize the statistical difference between signal and noise to reject the Gaussian white noise or impulsive noise \cite[]{liuyang2009tvmf,yike2013,xieqian2015eage2,wencheng2015stack,shuwei2016,jianyong2017,chenwei2017mf}.  Instead of developing a standalone denoising strategy, \cite{yangkang2015ortho} proposed a two-step denoising approach that tries to solve a long-existing problem in almost all denoising approaches: the signal leakage problem. By initiating a new concept called local orthogonalization, \cite{yangkang2015ortho} successfully retrieved the coherent signals from the removed noise section to guarantee no signal leakage in any denoising algorithms. \cite{weilin2017sr} used a similar algorithm to extract useful signals from the highly noise-corrupted microseismic data using an orthogonalized morphological decomposition method. In addition to these classic noise attenuation methods, some advanced denoising methods have been proposed in recent years. Time-frequency peak filtering \cite[]{kahoo2009,lin2013} based approaches utilize the high-resolution property of time-frequency transform to distinguish between useful signals and random noise. \cite{yaru2016dblend} used the rank-increasing property of noise when iteratively estimating the useful signals from simultaneous-source data.

In this paper, we follow the general set-up of the rank-reduction based methods and propose a new algorithm based on completely different low-rank decomposition engine. We substitute the singular value decomposition (SVD) used in traditional rank-reduction method with an efficient online subspace tracking method. The subspace tracking algorithm requires only basic linear algebraic manipulations. Each subspace update can be performed in linear time in the dimension of the subspace. The algorithm is derived by analyzing incremental gradient descent on the Grassmannian manifold of subspaces \cite[]{laura2010}. The subspace tracking method was initially proposed for matrix completion. Here, we carefully studied the application of the subspace tracking method in seismic noise attenuation following the rank reduction framework. After the seismic data is mapped to a low-rank space, the subspace tracking algorithm can be applied directly for low-rank decomposition. Due to the online nature of the subspace tracking algorithm, it reconstructs less random noise than the traditional SVD based subspace tracking algorithm during low-rank approximation. \wen{Here, the "online" simply means that each column of a low-rank matrix is inserted one-by-one into the algorithm for low-rank approximation.} The traditional singular spectrum analysis (SSA) can be \dlo{straightforwardly substituted}\wen{replaced} by the proposed algorithm for obtaining significantly better performance and higher computational efficiency.

The paper is organized as follows: we first introduce the low-rank approximation theory that is widely used in data processing applications, like matrix completion, seismic noise attenuation, and data restoration. We then introduce the online subspace tracking algorithm, where we provide detailed mathematical implications since it is relatively new in the seismic community. We also introduce the application of the subspace tracking method in seismic noise attenuation as a low-rank decomposition engine.  Next, we use \dlo{a bunch of }synthetic and field data examples to test and confirm the effectiveness of the proposed algorithm. \dlo{What is special here is that we}\wen{We} investigate the proposed algorithm from the perspective of removing different types of noise in the seismic data, which includes random noise, spiky noise, blending noise, and coherent noise. We draw some key conclusions at the end of the paper.

\section{Theory}
\subsection{Low-rank approximation}
Given a low-rank matrix $\mathbf{D}$, it can be approximated by tracking the $K$-dimensional subspace $S$ such that 
the following objective function is minimized 
\begin{equation}
\label{eq:obj}
\min_{S} J(S) = \min_{\mathbf{U},\mathbf{V}} \parallel \mathbf{U}\mathbf{V} - \mathbf{D} \parallel_F^2.
\end{equation}
where $\mathbf{U}$ is a matrix whose columns span $S$.  $\mathbf{V}$ is the corresponding weighting matrix. $J=\parallel \mathbf{U}\mathbf{V} - \mathbf{D} \parallel_F^2$ is the objective function. $\parallel \cdot \parallel_F$ denotes the Frobenius norm of an input matrix. Note that $\mathbf{U}\in \mathbb{R}^{M\times K}$, $\mathbf{V}\in \mathbb{R}^{K\times N}$, and $\mathbf{D}\in \mathbb{R}^{M\times N}$.

%\subsection{Subspace tracking}
%Matrix completion problem can be expressed as
%\begin{equation}
%\label{eq:mc}
%\begin{split}
%\overline{F}(S)&=\sum_{t=1}^{T} \min \parallel \mathbf{U}_{\Omega_n}a-v_{\Omega_n} \parallel^2 \\
%&=\min_{A\in \mathbb{R}^{d\times T}} \sum_{(i,j)\in\Omega} (UA-V)^2_{i,j}
%\end{split}
%\end{equation}
%$S$ denotes $d$-dimensional subspace of $\mathbb{R}^n$ that evolves over time. $U\in\mathbb{R}^{n\times d}$. $V\in\mathbb{R}^{n\times T}$.

%Equation \ref{eq:mc} is the starting point for the algorithms and analyses in \cite{keshavan2010} and \cite{dai2010}. 
There have been a lot of different algorithms to solve equation \ref{eq:obj}. \cite{keshavan2010} used a gradient descent algorithm to jointly  minimize both $\mathbf{U}$ and $\mathbf{V}$ while \cite{dai2010} minimized this cost function by first solving for $\mathbf{V}$ 
and then taking a gradient step with respect to $\mathbf{U}$. Most algorithms are based on the batch subspace tracking strategy \cite[]{laura2010}, where the full information in $\mathbf{D}$ is treated as a whole to solve for $\mathbf{U}$ and $\mathbf{V}$. These methods often require eigenvalue decomposition, or singular value decomposition (SVD) \wen{\cite[]{golub1996,Sarwar02inc,svmc}}. Some accelerated decomposition algorithms like Lanczos \cite[]{jianjun2013}, QR decomposition \cite[]{jinkun2016}, randomized SVD methods \cite[]{mssa} can also be used to solve equation \ref{eq:obj} with higher efficiency.

We will first introduce the most widely used SVD method for solving equation \ref{eq:obj} \wen{\cite[]{golub1996,jianfeng2010}}. SVD is a matrix factorization technique commonly used for producing low-rank approximations. 
The SVD of the data matrix $\mathbf{D}$ can be expressed as:
\begin{equation}
\label{eq:svd0}
\mathbf{D}=\mathbf{U\Sigma V}^T.
\end{equation}
Here, $\mathbf{U}$ is composed of the eigenvectors of $\mathbf{DD}^T$. $\mathbf{V}$ is composed of the eigenvectors of $\mathbf{D}^T\mathbf{D}$. $\mathbf{\Sigma}$ is a diagonal matrix composed of the decreasing singular values. \dlo{Let us denote $\mathbf{U}$, $\mathbf{\Sigma}$, and $\mathbf{D}$ in the following form:}
\dlo{$\begin{array}{l}
\mathbf{U}=[\mathbf{u}_1,\mathbf{u}_2,\cdots,\mathbf{u}_n],\\
\mathbf{\Sigma}=diag(\sigma_1,\sigma_2,\cdots,\sigma_n),\\
\mathbf{D}=[\mathbf{d}_1,\mathbf{d}_2,\cdots,\mathbf{d}_n].
\end{array}$}
\dlo{The vectors $\mathbf{u}_i$ and $\mathbf{d}_i$ are also called the propagation vectors and the eigen-wavelets, respectively. The singular values $\sigma_i$ are sorted such that $\sigma_1\ge\sigma_2\ge\cdots\ge\sigma_n$. They can be obtained by calculating the positive square roots of the eigenvalues of the data covariance matrix $\mathbf{D}\mathbf{D}^T$. Equation \ref{eq:svd0} can be expressed as:}\dlo{$\mathbf{D} = \sum_{i=1}^{n}\sigma_i\mathbf{u}_i\mathbf{d}^T_{i}$.}

\dlo{where $\mathbf{u}_i\mathbf{d}_i^T$ is the rank-one matrix called the $i$th eigenimage of $\mathbf{D}$. Thus, from equation \ref{eq:svd2}, the seismic image can be decomposed into $n$ eigenimages, %Matrix $\mathbf{D}$ can be decomposed into $r$ parts, 
the energy of which corresponds to the value of each element in matrix $\mathbf{\Sigma}$. }
\dlo{We can neglect the small singular values and approximate the data using the first several eigenimages:}
\dlo{$\hat{D}_{svd} = \sum_{k=1}^{K} \sigma_k\mathbf{u}_k\mathbf{d}_k^T$.}

The SVD method is a bach subspace tracking method or an offline subspace tracking algorithm \cite[]{laura2010}. The $K$-dimensional subspace $S$ is tracked provided that the whole matrix $\mathbf{D}$ is given. An opposite of the offline subspace tracking algorithm is the online subspace tracking algorithm, where the low-rank approximation is done step by step, with consecutively inserted columns from $\mathbf{D}$ for updating matrix $\mathbf{U}$. There are two main obvious advantages of the online subspace tracking strategy. 
\begin{enumerate}
\item It will be highly time and memory efficient when the number of columns in $\mathbf{D}$ is extremely large.
\item \dlo{It will only track the subspace which stands for the most principal components in the data.}\wen{It will better decompose the data into signal subspace with less residual noise.} 
\end{enumerate}  
\dlo{It would be straightforward to undertand the first advantage. For the second advantage, since each column is inserted to the algorithm step-by-step, the less principal information can be neglected during the tracking process. It is especially beneficial when rejecting random noise. Random noise might not be optimally random in the full-dimensional subspace and thus may be approximated using those offline algorithms. However, by using an online algorithm, it can be easily overlooked since noise is inserted step-by-step and appears less principal than the useful signals. Later in the paper we will use numerical examples to demonstrate this phenomenon.}\wen{Later in the paper we will use numerical examples to demonstrate better subspace tracking performance of the online method. A theoretical proof of the mixed signal-and-noise subspace decomposed from the traditional TSVD-based SSA method is given in the Appendix B.}  In the next subsection, we will introduce in detail an online subspace tracking algorithm, which is called grassmannian rank-one update subspace estimation (GROUSE) and was initially proposed by \cite{laura2010}.

\subsection{Grassmannian rank-one update subspace estimation (GROUSE)}
\cite{laura2010} considered optimizing the objective function shown in equation \ref{eq:obj} one column at a time. They showed that by using the online algorithm, where each measurement $\mathbf{d}_n$ corresponds to a random column of the matrix $\mathbf{D}$, it is possible to obtain a good approximation of the given matrix $\mathbf{D}$. %state-of-the-art performance on matrix completion problems.

The set of all subspaces of $\mathbb{R}^M$ of dimension $K$ is denoted as $\mathcal{G}(M,K)$ and is called the \emph{Grassmannian}. The Grassmannian is a compact Riemannian manifold, and its geodesics can be explicitly computed according to \cite{edelman1988}. An element $S\in\mathcal{G}^{n\times d}$ can be represented by any $M\times K$ matrix $\mathbf{U}$ whose columns form an orthonormal basis for $S$. GROUSE algorithm derives from an application  of incremental gradient descent on the Grassmannian manifold.

We can first compute a gradient of the cost function $J$, and then follow this gradient along a short geodesic curve in the Grassmannian. To compute the gradient of $J$ on the Grassmannian manifold, we first need to compute the partial derivatives of $J$ with respect to the components of $\mathbf{U}$. For a generic subspace, the matrix  $\mathbf{U}^T\mathbf{U}$ has full rank. 
We can rewrite the objective function as
\begin{equation}
J(S,n)=\parallel \mathbf{U}\mathbf{v}-\mathbf{d}_n \parallel_2^2.
\end{equation}
Here, $n$ also denotes the $n$th column in $\mathbf{D}$. $\mathbf{v}$ denotes a column vector in $\mathbf{V}$. It follows that the derivative of $J$ with respect to the elements of $\mathbf{U}$ is
\begin{equation}
\label{eq:der}
\begin{split}
\frac{\partial J}{\partial U} &=2(\mathbf{Uv}-\mathbf{d}_n)\mathbf{v}^T\\
&=-2(\mathbf{d}_n-\mathbf{Uv})\mathbf{v}^T\\
\end{split}
\end{equation}

\dlo{Let $\mathbf{v}$ be fixed to be $\mathbf{w}$, e.g., as the least-squares solution of }\wen{$\mathbf{v}$ is chosen as the least-squares solution ($\mathbf{w}$) of equation \ref{eq:ls}:}
\begin{equation}
\label{eq:ls}
\min_{\mathbf{v}} \parallel \mathbf{Uv}-\mathbf{d}_n \parallel_2^2,
\end{equation}
that is 
\begin{equation}
w=(\mathbf{U}^T\mathbf{U})^{-1}\mathbf{U}\mathbf{d}_n,
\end{equation}
and $\mathbf{r}=(\mathbf{d}_n-\mathbf{Uv})$, which denotes the zero padded residual vector,
equation \ref{eq:der} can be formulated as
\begin{equation}
\label{eq:der2}
\frac{\partial J}{\partial \mathbf{U}} = -2\mathbf{r}\mathbf{w}^T.
\end{equation}

%According to equation (2.70) in \cite{edelman1988}, we can calculate the gradient on the Grassmannian from this partial derivative
It can be further derived that \cite[]{edelman1988}
\begin{equation}
\label{eq:grad}
\begin{split}
\nabla J &= (\mathbf{I}-\mathbf{UU}^T)\frac{\partial J}{\partial \mathbf{U}} \\
&=-2(\mathbf{I}-\mathbf{UU}^T)\mathbf{rw}^T\\
&=-2\mathbf{rw}^T
\end{split}
\end{equation}

%The final equality follows because the residual vector $\mathbf{r}$ is orthogonal to all of the columns of $\mathbf{U}$. This can be verified from the definitions of $\mathbf{r}$ and $\mathbf{w}$. 
A gradient step along the geodesic with tangent vector $-\nabla J$ is given %by equation (2.65) in \cite{edelman1988}
in  \cite{edelman1988}, and is a function of the 
singular values and vectors of $\nabla J$. It is trivial to compute the singular value decomposition of $\nabla J$, as it is rank one.

The sole non-zero singular value is $\sigma=2\parallel \mathbf{r} \parallel\parallel \mathbf{w} \parallel$ and the corresponding left and right singular vectors are $\frac{\mathbf{r}}{\parallel \mathbf{r} \parallel}$ and $\frac{\mathbf{w}}{\parallel \mathbf{w} \parallel}$, respectively. Let $\mathbf{x}_2,\cdots,\mathbf{x}_K$ be an orthonormal set orthogonal to $\mathbf{r}$ and $\mathbf{y}_2,\cdots,\mathbf{y}_K$ be an orthonormal set orthogonal to $\mathbf{w}$. Then

\begin{equation}
\label{eq:svd}
-2\mathbf{rw}^T = \left[\begin{array}{cccc}
-\frac{\mathbf{r}}{\parallel \mathbf{r} \parallel} & \mathbf{x}_2 & \cdots & \mathbf{x}_K 
\end{array} \right] \times \text{diag}(\sigma,0,\cdots,0)\times
\left[\begin{array}{cccc}
\frac{\mathbf{w}}{\parallel \mathbf{w} \parallel} & \mathbf{y}_2 & \cdots & \mathbf{y}_K 
\end{array} \right]
\end{equation}
forms an SVD for the gradient. It can be derived that for $\eta>0$, a step of length $\eta$ in the direction $\nabla J$ is given by
\begin{equation}
\label{eq:upsize}
\begin{split}
\mathbf{U}(\eta) & =\mathbf{U}+\frac{(\cos(\sigma\eta)-1)}{\parallel \mathbf{w} \parallel^2} \mathbf{Uww}^T+\sin(\sigma\eta) \frac{\mathbf{r}}{\parallel \mathbf{r} \parallel} \frac{\mathbf{w}^T}{\parallel \mathbf{w} \parallel} \\
&=\mathbf{U}+\left( \sin(\sigma\eta)\frac{\mathbf{r}}{\parallel \mathbf{r} \parallel} + (\cos(\sigma\eta)-1)\frac{\mathbf{p}}{\parallel \mathbf{p} \parallel} \right) \frac{\mathbf{w}^T}{\parallel \mathbf{w} \parallel}
\end{split}
\end{equation}
where $\mathbf{p}=\mathbf{Uw}$, the predicted value of the projection of the vector $\mathbf{d}$ onto $S$. Appendix A provides a detailed derivation of the step size $\Delta \mathbf{U}=\mathbf{U}_{n+1}-\mathbf{U}_{n}$. The whole GROUSE algorithm is detailed in Algorithm \ref{alg:alg1} \cite[]{laura2010}.

  \begin{algorithm}
   \caption{Grassmannian Rank-One Update Subspace Estimation}
   \textbf{Require:} An $M\times K$ orthogonal matrix $\mathbf{U}_0$. A sequence of vectors $\mathbf{d}_n$. A set of step sizes $\eta_n$. \wen{Number of columns $N$ in the input matrix $\mathbf{D}$.}
    \begin{algorithmic}[1]
        \For{$n$ = $1,\cdots,N$}
     \State \textbf{Estimate weights}: $\mathbf{w}=\arg\min_{\mathbf{v}} \parallel \mathbf{Uv}-\mathbf{d}_n \parallel^2$
     \State \textbf{Predicted full vector}: $\mathbf{p}=\mathbf{U}_n \mathbf{w}$
     \State \textbf{Compute residual}: $\mathbf{r}=\mathbf{d}_n-\mathbf{p}$
     \State \textbf{Update subspace}: $\mathbf{U}_{n+1}=\mathbf{U}_n+\left( \sin(\sigma\eta)\frac{\mathbf{r}}{\parallel \mathbf{r} \parallel} + (\cos(\sigma\eta)-1)\frac{\mathbf{p}}{\parallel \mathbf{p} \parallel} \right) \frac{\mathbf{w}^T}{\parallel \mathbf{w} \parallel}$, where $\sigma=\parallel \mathbf{r} \parallel\parallel \mathbf{p} \parallel$
        \EndFor
\end{algorithmic}
\label{alg:alg1}
\end{algorithm}

\subsection{Low-rank matrix construction and algorithms}
We follow \cite{mssa} to construct the low-rank matrix. A Hankel matrix for each frequency slice in $f-x$ domain can be constructed to represent the useful signal components in a low-rank manner. The Hankel matrix for each frequency slice $D(x,w)$ is constructed as:
\begin{equation}
\label{eq:mssa}
\mathbf{H}=\left(\begin{array}{cccc}
D(1,w) & D(2,w) & \cdots &D(p,w) \\
D(2,w) & D(3,w)  &\cdots &D(p+1,w) \\
\vdots & \vdots &\ddots &\vdots \\
D(L,w)&D(L+1,w) &\cdots&D(N_x,w)
\end{array}
\right),
\end{equation}
where $L=\lfloor\frac{N_x}{2}\rfloor+1$ and $p=N_x-L+1$, $\lfloor \cdot \rfloor$ denotes the integer part of its argument, $w$ denotes frequency. As a bridge connecting the state-of-the-art singular spectrum analysis (SSA) method to the proposed method, we first introduce the implementation of the \dlo{SSA}\wen{TSVD-based SSA} method.

In the \dlo{SSA}\wen{TSVD-based SSA} method, after constructing the Hankel matrix, we apply truncated singular value decomposition (TSVD), \dlo{which corresponds to equation \ref{eq:svddenoise}, }to the matrix $\mathbf{H}$:
\begin{equation}
\label{eq:tsvd}
\hat{\mathbf{H}}=\text{TSVD}\left(\mathbf{H}\right).
\end{equation}
 Then an averaging operator is applied along the antidiagonals of the low-rank approximated matrix $\hat{\mathbf{D}}$. The whole algorithm can be shown in Algorithm \ref{alg:alg2}, where $\hat{\mathcal{H}}$ denotes the Hankelization operator and $\mathcal{A}$ denotes the averaging operator.

  \begin{algorithm}
   \caption{Denoising seismic data via \dlo{SSA}\wen{TSVD-based SSA} algorithm. }
   \textbf{Require:} An input matrix denoting the seismic data and the predefined rank $K$.
    \begin{algorithmic}[1]
    \State \textbf{1D forward FFT}: $D(x,w)=\text{FFT}\left(D(x,t)\right)$
        \For{$w$ = $1,\cdots,W$}
     \State \textbf{Hankelization}: $\mathbf{H}=\mathcal{H}(D(:,w))$
     \State \textbf{Low-rank decomposition}: $[\mathbf{U},\boldsymbol{\Sigma},\mathbf{V}]=\text{SVD}(\mathbf{H},K)$
     \State \textbf{Low-rank approximation}: $\hat{\mathbf{H}}=\mathbf{U}\boldsymbol{\Sigma}\mathbf{V}^T$
     \State \textbf{Averaging along anti-diagonals}: $\hat{D}(:,w)=\mathcal{A}(\hat{\mathbf{H}})$
        \EndFor 
         \State \textbf{1D inverse FFT}: $\hat{D}(x,t)=\text{IFFT}\left(\hat{D}(x,w)\right)$
\end{algorithmic}
\label{alg:alg2}
\end{algorithm}

The proposed method simply substitutes the low-rank decomposition operator using SVD with the \new{GROUSE-based} low-rank decomposition operator. It is also worth mentioning that GROUSE method is just one choice of the online subspace tracking (OSST) algorithm. Other \dlo{OSST}\wen{subspace tracking} algorithms such as incremental SVD \cite[]{Sarwar02inc} can also be used for the purpose of low-rank decomposition. We will use \dlo{OSST}\wen{GROUSE-based SSA} to briefly refer to the proposed algorithm through out the paper. The detailed \dlo{OSST}\wen{GROUSE-based SSA} algorithm in a similar way as Algorithm \ref{alg:alg2} is shown in Algorithm \ref{alg:alg3}. \wen{For a better understanding of the algorithm, Figure \ref{fig:flowchart} shows the main steps of the algorithm. The low-rank approximation step is chosen as GROUSE method in the proposed GROUSE-based method.}

\begin{algorithm}
   \caption{Denoising seismic data via \dlo{OSST}\wen{GROUSE-based SSA} algorithm. }
   \textbf{Require:} An input matrix denoting the seismic data and the predefined rank $K$.
    \begin{algorithmic}[1]
    \State \textbf{1D forward FFT}: $D(x,w)=\text{FFT}\left(D(x,t)\right)$
        \For{$w$ = $1,\cdots,W$}
     \State \textbf{Hankelization}: $\mathbf{H}=\mathcal{H}(D(:,w))$
     \State \textbf{Low-rank decomposition}: $[\mathbf{U},\mathbf{V}]=\text{GROUSE}(\mathbf{H},K)$
     \State \textbf{Low-rank approximation}: $\hat{\mathbf{H}}=\mathbf{U}\mathbf{V}$
     \State \textbf{Averaging along anti-diagonals}: $\hat{D}(:,w)=\mathcal{A}(\hat{\mathbf{H}})$
        \EndFor 
         \State \textbf{1D inverse FFT}: $\hat{D}(x,t)=\text{IFFT}\left(\hat{D}(x,w)\right)$
\end{algorithmic}
\label{alg:alg3}
\end{algorithm}

\section{Examples}

\subsection{Evaluation of denoising performance}
For synthetic examples, since we have the clean data, we can use the following signal-to-noise ratio (SNR) measurement to evaluate denoising performance \cite[]{guochang2009}:
\begin{equation}
\label{eq:snr}
SNR=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2^2}{\Arrowvert \mathbf{s} -\hat{\mathbf{s}}\Arrowvert_2^2}.
\end{equation}
where $\mathbf{s}$ and $\hat{\mathbf{s}}$ are clean signal and estimated signal, respectively.

For field data examples, we do not know the correct signal. In order to numerically measure the denoising performance, we utilize the local similarity measurement \cite[]{yangkang2015ortho}. \dlo{Appendix D gives a brief review of local similarity between two signals or two matrices.} Measuring denoising performance using local similarity is based on the criterion that denoised signal and noise should be orthogonal to each other. Thus, a high local similarity between denoised signal and noise indicates a mixture between signal and noise subspace, or there are some useful signals in the removed noise section. For a successful denoising performance, the local similarity map should be zero everywhere. \wen{It is worth mentioning that local similarity is effective in detecting the damage degree of denoising methods but is less effective in evaluating the noise removal ability of a denoising method.}

\wen{To effectively apply the SSA filter, the denoised data are constrained to be low-rank in Hankel matrices extracted from small temporal-spatial windows (or patches). The local-window strategy is important because the SSA method is a valid denoising and reconstruction technique for a superposition of plane waves. In a small window, the data can be approximated via a limited number of dips plus incoherent noise. The size of local windows depends on the complexity of input seismic data. For relatively more complex seismic data, e.g., pre-stack data with large curvature in some areas, the window size should be small enough so that in each window the events are roughly linear events. For structurally simpler data, e.g., most post-stack data, the selection of window size can be more flexible since both small window and large window can obtain similar results. For most data presented in this paper, the local curvature of the geological structures is not very large, so we will choose relatively smaller window sizes. Neighbor windows will have 50\% overlap and a cosine taper is applied in both time and space. The window size is a relatively term. "Large" or "small" should be evaluated based on the ratio between window size and complete data size. We will specify the window sizes for each example when discussing the denoising performance.}

\subsection{Synthetic examples}
The first example is a 2D example. This example is relatively simple, containing only three linear events, as shown in Figure \ref{fig:syn1}. Figure \ref{fig:syn1-c} shows the clean data or the ground truth for this example. We test the performance of the proposed algorithm in rejecting three types of noise, namely, random noise, spiky noise, and blending noise which arises from the simultaneous source acquisition \cite[]{shaohuan2016}. We also compare the online subspace tracking (OSST) based method with the traditional singular spectrum analysis (SSA) based method. The noisy data containing \wen{band-limited} random noise is shown in Figure \ref{fig:syn1}. \dlo{The added random noise is initially Gaussian white noise. We applied a bandpass filter to the random noise with a low cut-off frequency around 5 Hz and a high cut-off frequency around 40 Hz. The random noise is then considered as band-limited and is used to mimic the real random noise in the field. }

Figure \ref{fig:syn1-dn} shows the denoising performance for both \dlo{SSA}\wen{TSVD-based SSA} and \dlo{OSST}\wen{GROUSE-based SSA} methods. Figure \ref{fig:syn1-ssa} shows the denoised data using \dlo{SSA}\wen{TSVD-based SSA} method while Figure \ref{fig:syn1-sst} shows the denoised data using \dlo{the proposed method}\wen{OSST}. Comparing Figures \ref{fig:syn1-ssa} and \ref{fig:syn1-sst}, \dlo{it is quite obvious that }the denoised data using the proposed method is cleaner than the traditional \dlo{SSA}\wen{TSVD-based SSA} method. In addition to comparing the noise rejection ability, we are also interested in comparing the signal preservation ability. The best way to see if any useful energy is damaged is to check the removed noise section. The removed noise section is the difference between the noisy data and denoised data. If there is obvious coherent energy in the noise section, it indicates damages to the useful signals. Figures \ref{fig:syn1-ssa-n} and \ref{fig:syn1-sst-n} show the removed noise sections using the \dlo{SSA}\wen{TSVD-based SSA} method and the proposed method, respectively. Both removed noise sections do not show obvious coherent events and demonstrate that both \dlo{SSA}\wen{TSVD-based SSA} and \dlo{OSST}\wen{GROUSE-based SSA} methods do not cause significant damages to useful signals. To quantitatively compare the performance of two methods, we calculate the SNRs of different data based on equation \ref{eq:snr}. The SNR of noisy data is -5.12 dB. The SNRs of the \dlo{SSA}\wen{TSVD-based SSA} and \dlo{OSST}\wen{GROUSE-based SSA} methods are 5.35 dB and 6.72 dB, respectively. In this example, both methods use the same predefined rank: $K=3$.

In order to compare the performance of two methods in different noise level. We increase the variance of noise  from 0.1 to 1, and calculate the SNRs of denoised data of both methods and show them in Table \ref{tbl:snrs}. To see the varied SNRs more vividly, we plot the data from Table \ref{tbl:snrs} in Figure \ref{fig:snr-n}. The black line shows the SNRs varying with input noise variances. The red line shows the SNRs corresponding to the \dlo{SSA}\wen{TSVD-based SSA} method. The green line shows the SNRs of the proposed method. It is obvious that both methods obtain large SNR improvement for all noise levels and the SNRs of the proposed method are always higher than the \dlo{SSA}\wen{TSVD-based SSA} method. We can also observe clearly that the difference between the \dlo{SSA}\wen{TSVD-based SSA} and \dlo{OSST}\wen{GROUSE-based SSA} methods decreases first and reaches a minimum when noise variance $\sigma^2=0.3$, then the difference increases as noise variance becomes larger, which indicates that the proposed method outperforms the \dlo{SSA}\wen{TSVD-based SSA} method more when the seismic data becomes noisier.

\begin{table}[h]
\caption{Comparison of SNRs for different input noise level. The diagrams corresponding to this table is shown in Figure \ref{fig:snr-n}.}
\begin{center}
     \begin{tabular}{|c|c|c|c|} 
	  \hline Noise variance & Input SNR & SNR of \dlo{SSA}\wen{TSVD-based SSA} & SNR of \dlo{OSST}\wen{GROUSE-based SSA} \\ 
	  \hline 0.1 & 4.42 & 15.16 & 19.78\\
	  \hline 0.2 & -1.59 & 8.94 & 10.96\\
	  \hline 0.3 & -5.12 & 5.34 & 6.72 \\
	  \hline 0.4 & -7.62 & 2.83 & 4.18 \\
	  \hline 0.5 & -9.553 & 0.82 & 2.46 \\
	  \hline 0.6 & -11.14 & -0.81 & 1.35 \\
	  \hline 0.7 & -12.47 & -2.25 & 0.61 \\
	  \hline 0.8 & -13.64 & -3.50 & 0.17 \\
	  \hline 0.9 & -14.66 & -4.61 & -0.13\\
	  \hline 1.0 & -15.57 & -5.57 & -0.39 \\
          \hline
    \end{tabular} 
\end{center}
\label{tbl:snrs}
\end{table}

In order to test the robustness of the proposed algorithm to different types of noise, we then apply it to reject spiky noise and blending noise \cite[]{yangkang20142}. The noisy data containing spiky noise is shown in Figure \ref{fig:syn1-sp}. Figures \ref{fig:syn1-sp-ssa} and \ref{fig:syn1-sp-sst} show denoised data using the \dlo{SSA}\wen{TSVD-based SSA} and \dlo{OSST}\wen{GROUSE-based SSA} methods, respectively. The performance shows that both methods can be used to effectively reject spiky noise and the proposed \dlo{OSST}\wen{GROUSE-based SSA} method can obtain a slightly smoother result with less residual noise. Figures \ref{fig:syn1-sp-ssa-n} and \ref{fig:syn1-sp-sst-n} show their corresponding noise sections. The noise sections confirm the effective signal preservation abilities of the two methods. The SNRs of the noisy data, denoised data using \dlo{SSA}\wen{TSVD-based SSA} method, and denoised data using \dlo{OSST}\wen{GROUSE-based SSA} methods are 2.24 dB, 16.73 dB, and 18.97 dB, respectively, which quantitatively verifies the superior performance of the proposed \dlo{OSST}\wen{GROUSE-based SSA} method. Next, we apply the proposed method to remove blending noise caused from the marine simultaneous source acquisition \cite[]{berkhout2008}. Rejecting the blending noise is significant in boosting a huge economic saving in modern marine acquisition. The noisy data that contains blending noise is shown in Figure \ref{fig:syn1-bd}. Figures \ref{fig:syn1-bd-ssa} and \ref{fig:syn1-bd-sst} show the denoised data using the \dlo{SSA}\wen{TSVD-based SSA} and \dlo{OSST}\wen{GROUSE-based SSA} methods, respectively. Figures \ref{fig:syn1-bd-ssa-n} and \ref{fig:syn1-bd-sst-n} show their corresponding noise sections. Although both methods cause some residual crosstalk noise in the data, the denoised data are both much cleaner than the noisy data. Considering the strong amplitude of the blending noise, it is usually rejected using an iterative way. Figure \ref{fig:syn1-bd-dn} just shows the performance of one-step filtering. The subsequent filtering will compensate for the imperfect performance of both methods. However, we do see that the proposed method can obtain a slightly cleaner performance than the traditional \dlo{SSA}\wen{TSVD-based SSA} method. \wen{Since this example contains only linear events, we do not apply local windows to process the data.}

We further investigate the reason why the traditional \dlo{SSA}\wen{TSVD-based SSA} method causes more residual noise than the \dlo{OSST}\wen{GROUSE-based SSA} method. The strategy we use is to test the noise influence in the low-rank approximation of both \dlo{SSA}\wen{TSVD-based SSA} and \dlo{OSST}\wen{GROUSE-based SSA} method. We apply \dlo{SSA}\wen{TSVD-based SSA} and \dlo{OSST}\wen{GROUSE-based SSA} with different predefined ranks to pure random noise (which is band-limited here to simulate the real random noise in seismic data), and quantitatively measure how different low-rank approximation methods try to approximate the noise. Ideally, a low-rank approximation algorithm should approximate none (or very small amount) of the noise, since there is no significant spatially coherent signals in the pure noise. The pure noise is shown in Figure \ref{fig:syn1-noise}. 
Figures \ref{fig:syn1-ssak1} and \ref{fig:syn1-sstk1} show the results with predefined rank $K=1$ from \dlo{SSA}\wen{TSVD-based SSA} and \dlo{OSST}\wen{GROUSE-based SSA} methods. Figures \ref{fig:syn1-ssak3} and \ref{fig:syn1-sstk3} show the results with predefined rank $K=3$ from \dlo{SSA}\wen{TSVD-based SSA} and \dlo{OSST}\wen{GROUSE-based SSA} methods, respectively. It is very salient from Figure \ref{fig:syn1-nssat} that either $K=1$ or $K=3$, the \dlo{SSA}\wen{TSVD-based SSA} method causes a much stronger noise reconstruction performance than the \dlo{OSST}\wen{GROUSE-based SSA} method, which indicates that for the same predefined rank, the \dlo{SSA}\wen{TSVD-based SSA} method will approximate more noise than the \dlo{OSST}\wen{GROUSE-based SSA} method. In other wolds, the proposed method is less sensitive to noise when approximating the low-rank components using the online subspace tracking algorithm than the \dlo{SSA}\wen{TSVD-based SSA} method which uses an offline algorithm. Figure \ref{fig:e-n} shows the diagrams of reconstructed noise energy varying with different ranks. The noise energy here is defined as
\begin{equation}
\label{eq:ne}
E_n = \parallel \mathbf{n} \parallel_2^2,
\end{equation} 
where $E_n$ denotes the energy of reconstructed noise and $\mathbf{n}$ denotes the vectorized noise vector. $\parallel \cdot \parallel_2$ denotes the $L_2$ norm. In Figure \ref{fig:e-n}, the black line denotes the constant input noise energy. The red line denotes the reconstructed noise energy using the \dlo{SSA}\wen{TSVD-based SSA} method varying with different ranks. The green line denotes the reconstructed noise energy using the proposed method varying with different ranks. It is quite reasonable that as the rank increases, both methods reconstruct more and more noise. It is obvious that the \dlo{OSST}\wen{GROUSE-based SSA} method is always reconstructing less noise than the \dlo{SSA}\wen{TSVD-based SSA} method for the same predefined rank. As the rank increases, the difference in noise energy between two methods also increases, which indicates that the superiority of the proposed method over the \dlo{SSA}\wen{TSVD-based SSA} method will become more obvious when the predefined ranks is larger. This observation is very useful in practice since in processing field data, the rank is usually chosen relatively large, where the proposed method will be more appropriate to substitute the traditional \dlo{SSA}\wen{TSVD-based SSA} method.

This noise influence test supports the advantage of online subspace tracking algorithm\wen{s} over those offline subspace tracking algorithm\wen{s}\wen{i.e., the traditional TSVD-based SSA method}. \dlo{In online algorithms, each column of the low-rank matrix is inserted to the algorithm step-by-step, thus it is easier to avoid the influence of less principal information (e.g., the noise) during the subspace tracking process. When viewed in the full-dimensional subspace, the random noise may be approximated as "fake" principal components in those offline algorithms. In the opposite, by using an online algorithm, noise can be easily overlooked since it is inserted step-by-step and appears less principal than the useful signals.} \wen{In fact, the TSVD-based SSA method can only decompose the input noisy data into into a mixed signal-and-noise subspace. The mixed signal-and-noise subspace explains why there is a large amount of residual noise left in the denoised data, even for input pure-noise data as shown in Figure \ref{fig:syn1-noise}. Appendix B gives a detailed proof on mixed signal-and-noise subspace decomposed from traditional TSVD method.} \new{Another insightful explanation on why the TSVD-based SSA method still causes residual noise is provided in \cite{aharchaou2017singular}, where the authors explained that thresholding alone (given a value for the rank) in the singular spectrum is not enough for rejecting all noise, shrinking (to counteract the effect of noise) of those (inflated) singular values is also necessary.}

\new{In addition, in the GROUSE-based method, a spatial randomization operator is applied to the Hankel matrix before the online subspace tracking. The randomization operator helps the low-dimensional subspace better represent the full-dimensional measurement. Besides, the randomization operator helps make the locally coherent random noise incoherent by a global column rearrangment, which also accounts for the reason why the GROUSE-based method is less sensitive to noise and can achieve better denoising performance than the TSVD-based method. Figure \ref{fig:test_random} provides a demonstration for such randomization. It can be seen from Figure \ref{fig:test_random}(a) that in a low-rank signal matrix, some noise may appear to be locally coherent although globally random. By applying a spatial randomization operator, the noise becomes highly random both locally and globally. This procedure makes the GROUSE method only extract the useful signals during subspace tracking. }

\new{We highly recommend the readers to think in depth the noise influence test we conducted in this paper (Figures \ref{fig:syn1-nssat} and \ref{fig:e-n}). It is very important to understand the difference between two methods in being sensitive to noise. Before initializing the project related with the paper, we were keeping asking ourselves if a new method can really substitute the TSVD-based SSA method and why it can. We are keeping it in mind when testing the GROUSE-based method. We clearly see that the TSVD-based SSA method tends to extract a lot more of components in the noise than the GROUSE-based SSA method. To explain the reason, we theoretically analyse the TSVD-based method. We show that the TSVD-based SSA method decomposes the data into a mixed signal-and-noise subspace, which explains why the denoised data using TSVD-based method contains a lot more residual noise and theoretically supports the noise influence test. Since the GROUSE-based method has a different algorithm setup as the the TSVD-based method, we cannot formulate the two algorithms in the same system, e.g., in the linear-algebra setup shown in the Appendix B. It is really difficult for us to derive a similar formula as the TSVD-based method from the GROUSE-based method so that we can intuitively understand why one is superior than the other. However, what we really can do is to investigate which method is more sensitive to noise. The more sensitive, the more residual noise we will obtain in the final result. From this aspect, we found that the GROUSE-based method is less sensitive.}

Nowadays, it becomes even more important to remove various forms of coherent noise than to remove pure random noise. The proposed algorithm can also be straightforwardly applied in some coherent noise attenuation problems. Following \cite{weilin2017}, when the trajectory of a coherent noise component is successfully tracked \wen{(or the trajectory of useful signal component is obtained)}, the coherent noise can be randomized to facilitate the application of a common random noise attenuation algorithm in attenuating the randomized coherent noise. \wen{For better understanding the randomization process, we gives a brief introduction of the randomization here. The randomization process is implemented to eliminate the correlation of coherent noise while preserving the useful signals. The trajectory of the useful signal is regarded as the shape of the window for the randomization operator. Then, the order of the data in this window can be randomly rearranged. After energy balancing, the useful signals with the same shape in the window have approximately equal amplitude at each point, whereas the coherent noise and the random noise do not. After the rearrangement, the useful signals are almost unchanged assuming waveforms on consecutive traces are the same, whereas the energies of the coherent and random noise are dispersed randomly. In other words, the correlation of the coherent noise is eliminated. This process transforms coherent noise into random noise to some extent.} Figure \ref{fig:coh} provides an example for attenuating coherent noise, where we treat the first hyperbolic event with the steepest dip as the coherent noise. Figure \ref{fig:hyper-coh} shows the noisy data, where the noise is pointed by the labeled arrow. After randomizing the data along the structural direction of the useful reflections, the shuffled data is shown in Figure \ref{fig:hyper-sn}. Figure \ref{fig:hyper-s-dn} shows the denoised data with both coherent and random noise successfully removed using the proposed method. Figure \ref{fig:hyper-s-dn2} shows the denoised result using the \dlo{SSA}\wen{TSVD-based SSA} method.  Both methods successfully remove random and coherent noise but the proposed method is cleaner than the \dlo{SSA}\wen{TSVD-based SSA} method. The \dlo{SSA}\wen{TSVD-based SSA} method causes significant residual noise due to the strong reconstructed noise during low-rank approximation. It is consistent with the above detailed analysis on noise influence. Figures \ref{fig:hyper-s-dnn} and \ref{fig:hyper-s-dnn2} show the removed noise sections using two methods, which do not contain any useful energy. \wen{The data size of this example is $501\times 150$. The window size we use is $50\times50$. \wen{$50\times50$ means 50 time samples by 50 space traces.}}

The next synthetic example is a model that contains flat events, flat events with amplitude-versus-offset (AVO) phenomenon, curved events, and discontinuities. Although containing only several events as shown in Figure \ref{fig:syn-c}, the reflectors stand for very typical geological structures such as sedimentary layers, salt domes, pinch-outs, and faults. Figure \ref{fig:syn} shows the noisy data by adding some band-limited random noise. Since the structure of this example is more complicated, we apply both \dlo{SSA}\wen{TSVD-based SSA} and \dlo{OSST}\wen{GROUSE-based SSA} methods in local windows. The data size of this example is $512\times 50$. The window size we use is $50\times20$. In each local window, we use a predefined rank $K=2$. Figures \ref{fig:syn-ssa} and \ref{fig:syn-sst} show denoised data using the \dlo{SSA}\wen{TSVD-based SSA} and \dlo{OSST}\wen{GROUSE-based SSA} methods, respectively, where the \dlo{OSST}\wen{GROUSE-based SSA} method is slightly cleaner than the \dlo{SSA}\wen{TSVD-based SSA} method. Figures \ref{fig:syn-ssa-dif} and \ref{fig:syn-sst-dif}  show the corresponding noise sections, where no observable signals are existing. For this example, to get a better comparison between two methods, we calculate the FK spectra of different data. Figure \ref{fig:syn-dnfk} shows a comparison of different FK spectra from the clean data (Figure \ref{fig:syn-c-fk}), noisy data (Figure \ref{fig:syn-fk}), denoised data using \dlo{SSA}\wen{TSVD-based SSA} method (Figure \ref{fig:syn-ssa-fk}), and denoised data using \dlo{OSST}\wen{GROUSE-based SSA} method (Figure \ref{fig:syn-sst-fk}). From Figure \ref{fig:syn-dnfk}, it is more obvious that the FK spectrum of \dlo{OSST}\wen{GROUSE-based SSA} result is cleaner than that of \dlo{SSA}\wen{TSVD-based SSA} result, and is much more similar to that of the clean data. In this example, the SNRs of the noisy data and denoised results from \dlo{SSA}\wen{TSVD-based SSA} and \dlo{OSST}\wen{GROUSE-based SSA} methods are 0.73 dB, 5.10 dB, and 7.22 dB, respectively. This example confirms the effectiveness of the proposed method in dealing with curved and more complex events.

We then use a 3D synthetic example to further compare the performance of different methods. The clean data is shown in Figure \ref{fig:syn3d-c}, which contains three plane-wave components. Figure \ref{fig:syn3d-n} shows the noisy data with band-limited random noise. For 3D data, it is slightly different to construct the low-rank matrix. Appendix C provides how to construct the low-rank matrix in the case of 3D seismic data. In this example, in addition to the \dlo{SSA}\wen{TSVD-based SSA} method, we also compare the proposed method with the FK thresholding method and accelerated \dlo{SSA}\wen{TSVD-based SSA} method with randomized singular value decomposition (RSVD). The results from four aforementioned methods are shown in Figure \ref{fig:syn3d-n-fk,syn3d-n-mssa,syn3d-n-rsvd,syn3d-n-mc}. It is obvious that the FK method causes most residual noise, which is followed by the \dlo{SSA}\wen{TSVD-based SSA} method. Although the accelerated \dlo{SSA}\wen{TSVD-based SSA} method is much cleaner than FK and \dlo{SSA}\wen{TSVD-based SSA} methods, the amplitude of the useful events is damaged a lot, which can be verified from its removed noise cube as shown in Figure \ref{fig:syn3d-n-rsvd}. Figure \ref{fig:syn3d-n-fk,syn3d-n-mssa,syn3d-n-rsvd,syn3d-n-mc} shows the removed noise cubes corresponding to the four mentioned methods. All Figures except for Figure \ref{fig:syn3d-n-rsvd} do not contain observable spatially coherent energy. In Figure \ref{fig:syn3d-n-rsvd}, there is significant useful energy which indicates the worse signal preservation ability of the RSVD based \dlo{SSA}\wen{TSVD-based SSA} method. The proposed method obtains the cleanest result without damaging useful energy. Figure \ref{fig:syn3d-c-s,syn3d-fk-s,syn3d-ssa-s,syn3d-n-s,syn3d-rsvd-s,syn3d-mc-s} shows a comparison of 2D sections extracted from the 3D data cubes, from which we can get a clearer conclusion mentioned above. The SNR of the noisy data in this example is -8.39 dB. The SNRs of FK method, \dlo{SSA}\wen{TSVD-based SSA} method, RSVD method, and the proposed method are 4.30 dB, 4.60 dB, 3.94 dB, and 6.81 dB, respectively. For this example, we also measure the computational time for different methods. The data size for this example is $300\times 20\times 20$. The time cost for FK method, \dlo{SSA}\wen{TSVD-based SSA} method, RSVD method, and the proposed method is 0.05s, 11.63s, 1.7s, and 5.96s, respectively. We conclude from this example that while the RSVD algorithm accelerates \dlo{SSA}\wen{TSVD-based SSA} a lot (by a factor of seven), it sacrifices the denoising performance to some extent. The proposed method obtains the best denoising performance and it is also faster than the traditional \dlo{SSA}\wen{TSVD-based SSA} method (by a factor of two). \wen{Since this example only contains planar events, we do not use local windows to process the data.}

\subsection{Real data examples}
The first \dlo{real}\wen{field} data example is a 2D time-migrated seismic profile, as shown in Figure \ref{fig:real}. This is a very noisy data set, where strong random noise masks the shallow reflection signals seriously and some useful signals are hardly seen. Figure \ref{fig:real-dn} shows a comparison between the \dlo{SSA}\wen{TSVD-based SSA} method and the proposed method, which both significantly improve the seismic image. The shallow part seismic reflection signals are much clearer than the raw data. It is not easy to judge the performance solely from the denoised data. The removed noise sections shown in Figure \ref{fig:real-n} offer more clues in judging the denoising performance of the two methods. It is very clear from Figure \ref{fig:real-n} that there are significant damages to useful reflection signals caused by the \dlo{SSA}\wen{TSVD-based SSA} method, as indicated by the arrows in Figure \ref{fig:r-ssa-n}. The removed noise from the proposed method contains almost no useful signals, which indicates a successful preservation of those useful signals. \wen{An enlarged comparison between the two removed noise sections are shown in Figure \ref{fig:real-n-z}, where we can see even more clearly that the TSVD-based \dlo{SSA}\wen{TSVD-based SSA} method cause some damages to useful signals.} As introduced in the beginning of this section, we use local similarity to quantitatively compare the denoising performance for real data. Figure \ref{fig:real-simi} shows a comparison of local similarity between denoised data and removed noise for two methods. It is seen that the local similarity successfully detects those areas where we lost significant useful energy. The abnormal values in Figure \ref{fig:r-ssa-simi} (highlighted by the arrows) point out the areas of signal damages, which is consistent with the observed spatially coherent signals in Figure \ref{fig:r-ssa-n}. \wen{The data size of this example is $1001\times 201$. The window size we use is $200\times50$. }

The second \dlo{real}\wen{field} data example is a 3D stacked seismic profile. The raw data is shown in Figure \ref{fig:field}. Figures \ref{fig:field-ssa} and \ref{fig:field-sst} show the denoised data using the \dlo{SSA}\wen{TSVD-based SSA} method and the proposed method, respectively. Both denoising methods obtain much cleaner data. Figures \ref{fig:field-n-ssa} and \ref{fig:field-n-sst} show their corresponding noise sections. Figure \ref{fig:fsimi} shows a comparison of local similarity between denoised data and removed noise for two methods. The two local similarity cubes do not contain any abnormal values, which indicates that both methods preserve useful signals well. We extract one Xline section\dlo{s} from each figure in Figures \ref{fig:field} and \ref{fig:field-3d} and compare them in Figure \ref{fig:field-2d}. As highlighted by the green frameboxes, both methods successfully remove a huge amount of random noise and the proposed method obtains more spatially coherent reflection signals. The frameboxes are then zoomed in Figure \ref{fig:field-z}, where the comparison between two methods is much clearer. The \dlo{SSA}\wen{TSVD-based SSA} method causes a small amount of residual noise while the proposed method makes the seismic events very smooth and spatially coherent. \wen{The data size of this example is $751\times 100\times 10$. The window size we use is $100\times50\times10$. }

The last \dlo{real}\wen{field} data example is an earthquake data stack profile. Figure \ref{fig:reftran} shows Professor Peter Shearer's stacks over many earthquakes
at constant epicentral distance (offset angle) \cite[]{shearer2,shearer1}. Figure \ref{fig:reftran} has been improved a lot from the raw data by stacking different earthquake data. Different seismic phases can be seen from the Figure \ref{fig:reftran}, as highlighted by the labelled arrows. However, we can see that there are still significant random and erratic noise existing in the stack profile. By applying the proposed method to denoise the raw stack data, we obtain a much improved result, which is shown in Figure \ref{fig:ref-sst}. Different phases have been shown much clearer in the denoised data. To check whether we have removed any useful signals, we plot the difference section in Figure \ref{fig:ref-sst-n}, where we see no obvious spatially coherent signals. The noise section confirms that we only remove unwanted components while leaving the spatially coherent signals clearer. \wen{The data size of this example is $1200\times 360$. The window size we use is $200\times 90$. }

\section{Conclusions}
We have introduced a new online subspace tracking (OSST) based low-rank approximation algorithm to attenuate different types of noise existing in multi-dimensional seismic data. Each subspace update can be performed in linear time in the dimension of the subspace and thus is efficient. The algorithm is derived by analyzing incremental gradient descent on the Grassmannian manifold of subspaces. We comprehensively investigate the application in different noise attenuation problems through a bunch of synthetic and real data examples, which demonstrates the robustness of the algorithm to different types of noise including random noise, spiky noise, blending noise, and even coherent noise. We specifically compare the proposed method with the traditional singular spectrum analysis (SSA) based method, which is currently widely used in many fields. The numerical examples show that the proposed method can obtain significantly better performance in causing less residual noise in the denoised data. The superiority of the propose method over the \dlo{SSA}\wen{TSVD-based SSA} method is even more obvious in dealing with extremely noisy data. The numerical example also shows that the \dlo{SSA}\wen{TSVD-based SSA} method approximates more noise than the \dlo{OSST}\wen{GROUSE-based SSA} method when used with denoising for the same predefined rank, which explains the question why \dlo{SSA}\wen{TSVD-based SSA} method causes more residual noise. The propose method is also faster than the typical \dlo{SSA}\wen{TSVD-based SSA} method which uses standard singular value decomposition (SVD) by a factor of two.

\section{Acknowledgements}
This work was supported by the China Postdoctoral Science Foundation (No.2014M561053), Humanity and Social Science Foundation of Ministry of Education of China (No.15YJA630108), and Hebei Province Natural Science Foundation (No. E2016202341). \wen{We are appreciated to editor Jean Virieux, reviewer Mehdi Aharchaou and two anonymous reviewers for constructive suggestions that greatly improved the manuscript.} %\wen{We would like to thank Chaojun Shi and Chunying Han for checking the grammar of the manuscript.}

\append{Derivation of the stepsize}
A gradient step along the geodesic with tangent vector with tangent vector $-\nabla J$ can be expressed as \cite[]{edelman1988}:
\begin{equation}
\label{eq:geod}
\begin{split}
\mathbf{U}_{n+1} &= \left[\begin{array}{cc}
\mathbf{U}_{n}\mathcal{V} & \mathcal{U}
\end{array}\right] \left[\begin{array}{c}
\cos(\Sigma\eta) \\
\sin(\Sigma\eta)
 \end{array}\right]\mathcal{V}^T  \\
 &=\mathbf{U}_{n}\mathcal{V}\cos(\Sigma\eta)\mathcal{V}^T + \mathcal{U}\sin(\Sigma\eta)\mathcal{V}^T
 \end{split}
\end{equation}
where $\eta$ is the step size, $\mathcal{U}\Sigma\mathcal{V}^T$ is the compact singular value decomposition (SVD) of $-\nabla J$.

Equation \ref{eq:geod} can be further derived as
\begin{equation}
\label{eq:up}
\begin{split}
\Delta U &= \mathbf{U}_{n+1} - \mathbf{U}_{n}  \\
&=\mathbf{U}_{n}\mathcal{V}\cos(\Sigma\eta)\mathcal{V}^T-\mathbf{U}_{n} + \mathcal{U}\sin(\Sigma\eta)\mathcal{V}^T 
\end{split}
\end{equation}
Since $\mathcal{V}\mathcal{V}^T=I$, 
\begin{equation}
\label{eq:up2}
\begin{split}
\Delta U &= \mathbf{U}_{n+1} - \mathbf{U}_{n}  \\
&=\mathbf{U}_{n}\mathcal{V}\cos(\Sigma\eta)\mathcal{V}^T-\mathbf{U}_{n} + \mathcal{U}\sin(\Sigma\eta)\mathcal{V}^T \\
&=\mathbf{U}_{n}\left(\mathcal{V}\cos(\Sigma\eta)\mathcal{V}^T -\mathcal{V}\mathcal{V}^T\right) +\mathcal{U}\sin(\Sigma\eta)\mathcal{V}^T \\
&=\mathbf{U}_{n}\mathcal{V}\left(\cos(\Sigma\eta)-I\right)\mathcal{V}^T +\mathcal{U}\sin(\Sigma\eta)\mathcal{V}^T.
\end{split}
\end{equation}

%Since $\nabla J = -2rw^T$, 
Let 
\begin{equation}
\label{eq:svda}
-\nabla J = 2rw^T = \mathcal{U}\Sigma\mathcal{V}^T,
\end{equation}
where
\begin{equation}
\label{eq:u}
\mathcal{U}=\left[\begin{array}{cccc}
\frac{\mathbf{r}}{\parallel \mathbf{r} \parallel} & \mathbf{x}_2 & \cdots & \mathbf{x}_K 
\end{array} \right],
\end{equation}

\begin{equation}
\label{eq:s}
\Sigma=\text{diag}(\sigma,0,\cdots,0),
\end{equation}

\begin{equation}
\label{eq:v}
\mathcal{V}=\left[\begin{array}{cccc}
\frac{\mathbf{w}}{\parallel \mathbf{w} \parallel} & \mathbf{y}_2 & \cdots & \mathbf{y}_K 
\end{array} \right].
\end{equation}

In equations \ref{eq:u}-\ref{eq:v},
$\sigma=2\parallel \mathbf{r} \parallel \parallel \mathbf{w} \parallel$.
$[\mathbf{x}_2,\cdots,\mathbf{x}_K]$ is an orthonormal set orthogonal to $\mathbf{r}$ and 
$[\mathbf{y}_2,\cdots,\mathbf{y}_K]$ is an orthonormal set orthogonal to $\mathbf{w}$.

Inserting equations \ref{eq:u}-\ref{eq:v} to equation \ref{eq:svda}, the updating step can be obtained as
\begin{equation}
\label{eq:up3}
\begin{split}
\Delta U &=\mathbf{U}_{n}\mathcal{V}\left(\cos(\Sigma\eta)-I\right)\mathcal{V}^T +\mathcal{U}\sin(\Sigma\eta)\mathcal{V}^T \\
&=\mathbf{U}_{n} \frac{\mathbf{w}}{\parallel \mathbf{w} \parallel}(\cos(\sigma\eta)-1)\frac{\mathbf{w}^T}{\parallel \mathbf{w} \parallel} + \frac{\mathbf{r}}{\parallel r \parallel}\sin(\sigma\eta) \frac{\mathbf{w}}{\parallel \mathbf{w} \parallel}\\
&=\mathbf{U}_{n}(\cos(\sigma\eta)-1)\frac{\mathbf{w}\mathbf{w}^T}{\parallel \mathbf{w} \parallel^2}+\sin(\sigma\eta)\frac{\mathbf{r}}{\parallel \mathbf{r} \parallel}\frac{\mathbf{w}}{\parallel \mathbf{w} \parallel}
\end{split}
\end{equation}
Let $\mathbf{p}=\mathbf{U}_n\mathbf{w}$, 
\begin{equation}
\label{eq:up4}
\Delta \mathbf{U} = \left((\cos(\sigma\eta)-1)\frac{\mathbf{p}}{\parallel \mathbf{p} \parallel} + \sin(\sigma\eta)\frac{\mathbf{r}}{\parallel \mathbf{r} \parallel}\right) \frac{\mathbf{w}^T}{\parallel \mathbf{w} \parallel}
\end{equation}

\wen{
\append{Mixed Signal and noise subspace using TSVD-based SSA}
Let us reformulate the Hankel matrix $\mathbf{H}$ expressed in equation \ref{eq:mssa} as follows:
\begin{equation}
\label{eq:M_a}
\mathbf{H}=\mathbf{S}+\mathbf{N},
\end{equation}
\old{where $\mathbf{S}$ and $\mathbf{N}$ denote signal component and the random noise component in $\mathbf{H}$, respectively}\new{where $\mathbf{S}$ denotes the signal component in $\mathbf{H}$ and $\mathbf{N}$ denotes the pre-arranged noise in the Hankel matrix}. The SVD of $\mathbf{S}$ can be represented as:
\begin{equation}
\label{eq:svds_a}
\mathbf{S} = [\mathcal{U}_1^{S}\quad \mathcal{U}_2^{S}]\left[\begin{array}{cc}
\Sigma_1^{S} & \mathbf{0}\\
\mathbf{0} & \Sigma_2^{S}
\end{array}
\right]\left[\begin{array}{c}
(\mathcal{V}_1^{S})^T\\
(\mathcal{V}_2^{S})^T
\end{array}
\right].
\end{equation}
Because of the deficient rank, the matrix $\mathbf{S}$ can be written as
\begin{equation}
\label{eq:S_a}
\mathbf{S}=\mathcal{U}_1^S\Sigma_1^S(\mathcal{V}_1^S)^T.
\end{equation}
Because equation \ref{eq:svds_a} is a SVD of the signal matrix $\mathbf{S}$, the left matrix in equation \ref{eq:svds_a} is a unitary matrix:
\begin{equation}
\label{eq:unit}
\mathbf{I}=\mathcal{U}^S(\mathcal{U}^S)^T=[\mathcal{U}_1^S\quad \mathcal{U}_2^S]\left[\begin{array}{c} 
(\mathcal{U}_1^S)^T \\
(\mathcal{U}_2^S)^T 
\end{array}
\right].
\end{equation}
Combining equations \ref{eq:M_a}, \ref{eq:S_a}, and \ref{eq:unit}, we can derive:
\begin{equation}
\label{eq:factorapp}
\begin{split}
\mathbf{H}&=\mathbf{S}+\mathbf{N}\\
&=\mathbf{S}+\mathbf{IN}\\
&=[\mathcal{U}_1^S\quad \mathcal{U}_2^S]\left[\begin{array}{c} 
(\mathcal{U}_1^S)^T \\
(\mathcal{U}_2^S)^T
\end{array}
\right]\mathbf{N} \\
&=\mathcal{U}_1^S\Sigma_1^S(\mathcal{V}_1^S)^T + \left( 
\mathcal{U}_1^S(\mathcal{U}_1^S)^T+\mathcal{U}_2^S(\mathcal{U}_2^S)^T
\right)\mathbf{N}\\
&=\mathcal{U}_1^S \left(
(\mathcal{U}_1^S)^T\mathbf{N}+\Sigma_1^S(\mathcal{V}_1^S)^T
\right)+\mathcal{U}_2^S(\mathcal{U}_2^S)^T\mathbf{N}\\
&=\mathcal{U}_1^S\left(
\mathbf{N}^T\mathcal{U}_1^S+\mathcal{V}_1^S\Sigma_1^S
\right)^T + \mathcal{U}_2^S(\mathbf{N}^T\mathcal{U}_2^S)^T\\
&= [\mathcal{U}_1^S \quad \mathcal{U}_2^S]\left[\begin{array}{cc} 
\mathbf{I} & \mathbf{0}\\
\mathbf{0} & \mathbf{I}
\end{array}
\right]\left[\begin{array}{c} 
(\mathbf{N}^T\mathcal{U}_1^S+\mathcal{V}_1^S\Sigma_1^S)^T\\
(\mathbf{N}^T\mathcal{U}_2^S)^T
\end{array}
\right],
\end{split}
\end{equation}
%where $\Sigma_1$ and $\Sigma_2$ are introduced  matrices and are diagonal and positive definite.
we can further derive equation \ref{eq:factorapp} and factorize $\mathbf{H}$ as follows:
\begin{equation}
\label{eq:factorm}
\mathbf{H} = [\mathcal{U}_1^S \quad \mathcal{U}_2^S]\left[\begin{array}{cc} 
\Sigma_{1} & \mathbf{0}\\
\mathbf{0} & \Sigma_{2}
\end{array}
\right]\left[\begin{array}{c} 
(\Sigma_{1})^{-1}(\mathbf{N}^T\mathcal{U}_1^S+\mathcal{V}_1^S\Sigma_1^S)^T\\
(\Sigma_{2})^{-1}(\mathbf{N}^T\mathcal{U}_2^S)^T
\end{array}
\right],
\end{equation} 
where $\Sigma_1$ and $\Sigma_2$ denote diagonal and positive definite matrices. Note that $\mathbf{H}$ is constructed such that it is close to a square matrix \cite[]{mssa}, and thus the $\Sigma_1$ and $\Sigma_2$ are assumed to be square matrices for derivation convenience.  We observe that the left matrix has orthonormal columns and the middle matrix is diagonal. It can be shown that the right matrix also has orthonormal columns.  Thus, equation \ref{eq:factorm} is an SVD of $\mathbf{H}$. According to the TSVD method, we let $\Sigma_2$ be $\mathbf{0}$ and then the following equation holds:
\begin{equation}
\label{eq:tsvd2}
\begin{split}
\tilde{\mathbf{H}} &= \mathcal{U}_1^S(\mathcal{U}_1^S)^T\mathbf{N} + \mathcal{U}_1^S\Sigma_1^S(\mathcal{V}_1^S)^T \\
 &=\mathbf{S} + \mathcal{U}_1^S(\mathcal{U}_1^S)^T\mathbf{N}.
\end{split}
\end{equation}
From equation \ref{eq:tsvd2}, it is straightforward to understand that TSVD result $\tilde{\mathbf{H}}$ still contains significant random noise $\mathcal{U}_1^S(\mathcal{U}_1^S)^T\mathbf{N}$, or in other words, the traditional TSVD can only decompose the data space into a mixture of signal and noise subspace \cite[]{weilin2017ieee}. 
}

\append{Derivation of the 3D low-rank matrix construction}
Instead of constructing a Hankel matrix from a 1D spatial trace, in 3D case, we construct a block Hankel matrix from a 2D spatial matrix ($X$ and $Y$) in the frequency domain \cite[]{mssa}.

Consider a block of 3D data $\mathbf{D}_{time}(x,y,t)$ of $N_x$ by $N_y$ by $N_t$ samples. First, we transforms $\mathbf{D}_{time}(x,y,t)$ into $\mathbf{D}_{freq}(x,y,w)(w=1\cdots N_w)$ with complex values in the frequency domain. Each frequency slice of the data, at a given frequency $w_0$, can be represented by the following matrix:
\begin{equation}
\label{eq:mssa3d}
\mathbf{D}(w_0)=\left(\begin{array}{cccc}
D(1,1) & D(1,2) & \cdots &D(1,N_x) \\
D(2,1) & D(2,2)  &\cdots &D(2,N_x) \\
\vdots & \vdots &\ddots &\vdots \\
D(N_y,1)&D(N_y,2) &\cdots&D(N_y,N_x)
\end{array}
\right).
\end{equation}

In the following context, $w_0$ is omitted for notational convenience. Then, we construct a Hankel matrix for each row of $\mathbf{D}$. The Hankel matrix $\mathbf{R}_i$ for row $i$ of $\mathbf{D}$ is as follows:
\begin{equation}
\label{eq:data}
\mathbf{R}_i=\left(\begin{array}{cccc}
D(i,1) & D(i,2) & \cdots &D(i,p) \\
D(i,2) & D(i,3)  &\cdots &D(i,p+1) \\
\vdots & \vdots &\ddots &\vdots \\
D(i,N_x-p+1)&D(i,N_x-p+2) &\cdots&D(i,N_x)
\end{array}
\right),
\end{equation}
which is exactly the same as equation \ref{eq:mssa}. The block matrix is constructed by treating all Hankel matrix $\mathbf{R}_i$ as an element and arranging them into a block matrix:
\begin{equation}
\label{eq:hankel2}
\mathbf{H}=\left(\begin{array}{cccc}
\mathbf{R}_1 &\mathbf{R}_2 & \cdots &\mathbf{R}_q \\
\mathbf{R}_2 &\mathbf{R}_3 &\cdots &\mathbf{R}_{q+1} \\
\vdots & \vdots &\ddots &\vdots \\
\mathbf{R}_{N_y-q+1}&\mathbf{R}_{N_y-q+2} &\cdots&\mathbf{R}_{N_y}
\end{array}
\right).
\end{equation}
The size of $\mathbf{H}$ is $I\times J$, $I=(N_x-p+1)(N_y-q+1)$, $J=pq$. $p$ and $q$ are predefined integers chosen such that the Hankel matrix $\mathbf{R}_i$ and the block Hankel matrix $\mathbf{M}$  are close to square matrices, for example, $p=N_x-\lfloor\frac{N_x}{2}\rfloor$ and $q=N_y-\lfloor\frac{N_y}{2}\rfloor$, where $\lfloor\cdot\rfloor$ denotes the integer part of the argument. The following steps for low-rank decomposition is exactly the same as those in 2D case, as introduced in detail in the main context, which includes either SVD or GROUSE decomposition.

 \dlo{Local similarity between vectors $\mathbf{v}$ and $\mathbf{b}$ is defined as:}\dlo{$\mathbf{c}=\sqrt{\mathbf{c}_1\circ\mathbf{c}_2}$}\dlo{where $\circ$ denotes dot product, $\mathbf{c}_1$ and $\mathbf{c}_2$ can be obtained by solving the following two least-squares minimization problems:}\dlo{$\mathbf{c}_1 =\arg\min_{\mathbf{c}_1}\Arrowvert \mathbf{a}-\mathbf{B} \mathbf{c}_1 \Arrowvert_2^2$$\mathbf{c}_2 =\arg\min_{\mathbf{c}_2}\Arrowvert \mathbf{b}-\mathbf{A} \mathbf{c}_2 \Arrowvert_2^2$}
\dlo{where $\mathbf{A}$ is a diagonal operator composed of the elements of $\mathbf{a}$, $\mathbf{B}$ is a diagonal operator composed of the elements of $\mathbf{b}$. Note that in equations \ref{eq:local}-\ref{eq:local2}, $\mathbf{a}$, $\mathbf{b}$, and $\mathbf{c}$  denote vectorized 2D matrices. Equations \ref{eq:local1} and \ref{eq:local2} can be solved using the shaping regularization algorithm with a local triangle smoothing operator:}
\dlo{where $\mathbf{T}$ is the smoothing operator and $\lambda_1$ and $\lambda_2$ are two parameters controlling the physical dimensionality and enabling fast convergence when inversion is implemented iteratively. These two parameters can be chosen as $\lambda_1  = \Arrowvert\mathbf{B}^T\mathbf{B}\Arrowvert_2$ and $\lambda_2  = \Arrowvert\mathbf{A}^T\mathbf{A}\Arrowvert_2$.}

\bibliographystyle{seg}
\bibliography{mc}

\newpage

\begin{figure}[htb!]
  \centering
  \includegraphics[width=0.6\columnwidth]{Fig/flowchart}          
   \caption{Flowchart of the algorithm.}
   \label{fig:flowchart}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{syn1/Fig/syn1-c}
    \label{fig:syn1-c}}
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{syn1/Fig/syn1}
    \label{fig:syn1}}            
   \caption{2D synthetic example. (a) Clean data. (b) Noisy data.}
   \label{fig:syn1}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{syn1/Fig/syn1-ssa}
    \label{fig:syn1-ssa}}
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{syn1/Fig/syn1-sst}
    \label{fig:syn1-sst}} \\
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{syn1/Fig/syn1-ssa-n}
    \label{fig:syn1-ssa-n}}
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{syn1/Fig/syn1-sst-n}
    \label{fig:syn1-sst-n}}             
   \caption{Denoising comparison. (a) Denoised data using SSA. (b) Denoised data using OSST. (c) Removed noise using SSA. (d) Removed noise using OSST.}
   \label{fig:syn1-dn}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=\columnwidth]{syn1/Fig/snr-n}        
   \caption{Output SNRs varying with different input noise level. The noise level is measured by noise variance.}
   \label{fig:snr-n}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn1/Fig/syn1-sp}
    \label{fig:syn1-sp}}
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn1/Fig/syn1-sp-ssa}
    \label{fig:syn1-sp-ssa}}
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn1/Fig/syn1-sp-sst}
    \label{fig:syn1-sp-sst}} \\
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn1/Fig/syn1-sp-ssa-n}
    \label{fig:syn1-sp-ssa-n}}
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn1/Fig/syn1-sp-sst-n}
    \label{fig:syn1-sp-sst-n}}             
   \caption{Spiky noise test. (a) Denoised data using SSA. (b) Denoised data using OSST. (c) Removed noise using SSA. (d) Removed noise using OSST. SNRs of (a),(b),(c) are 2.24 dB, 16.73 dB, and 18.97 dB, respectively.}
   \label{fig:syn1-sp-dn}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn1/Fig/syn1-bd}
    \label{fig:syn1-bd}}
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn1/Fig/syn1-bd-ssa}
    \label{fig:syn1-bd-ssa}}
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn1/Fig/syn1-bd-sst}
    \label{fig:syn1-bd-sst}} \\
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn1/Fig/syn1-bd-ssa-n}
    \label{fig:syn1-bd-ssa-n}}
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn1/Fig/syn1-bd-sst-n}
    \label{fig:syn1-bd-sst-n}}             
   \caption{Blending noise test. (a) Denoised data using SSA. (b) Denoised data using OSST. (c) Removed noise using SSA. (d) Removed noise using OSST. SNRs of (a),(b),(c) are 0.85 dB, 12.23 dB, 15.15 dB, respectively.}
   \label{fig:syn1-bd-dn}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn1/Fig/syn1-noise}
    \label{fig:syn1-noise}}
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn1/Fig/syn1-ssak1}
    \label{fig:syn1-ssak1}}
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn1/Fig/syn1-sstk1}
    \label{fig:syn1-sstk1}} \\
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn1/Fig/syn1-ssak3}
    \label{fig:syn1-ssak3}}
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn1/Fig/syn1-sstk3}
    \label{fig:syn1-sstk3}}             
   \caption{Test of applying \dlo{SSA}\wen{TSVD-based SSA} and \dlo{OSST}\wen{GROUSE-based SSA} methods to pure random noise. (a) Pure random noise. (b) Result from \dlo{SSA}\wen{TSVD-based SSA} with $K=1$. (c) Result from \dlo{OSST}\wen{GROUSE-based SSA} with $K=1$. (d) Result from \dlo{SSA}\wen{TSVD-based SSA} with $K=3$. (e) Result from \dlo{OSST}\wen{GROUSE-based SSA} with $K=3$. Note that the \dlo{SSA}\wen{TSVD-based SSA} method approximates stronger noise than \dlo{OSST}\wen{GROUSE-based SSA} method for the same predefined rank $K$}
   \label{fig:syn1-nssat}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=\columnwidth]{syn1/Fig/e-n}        
   \caption{Noise approximation test. Note that the \dlo{SSA}\wen{TSVD-based SSA} method approximates stronger noise than \dlo{OSST}\wen{GROUSE-based SSA} method for the same predefined rank $K$. }
   \label{fig:e-n}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=\columnwidth]{Fig/demo_random}        
   \caption{\new{Demonstration for the influence of the randomization operator to the random property of unwanted-noise.}}
   \label{fig:test_random}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{hyper/Fig/hyper-coh}
    \label{fig:hyper-coh}}
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{hyper/Fig/hyper-s-dn}
    \label{fig:hyper-s-dn}}
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{hyper/Fig/hyper-s-dn2}
    \label{fig:hyper-s-dn2}}    \\
      \subfloat[]{\includegraphics[width=0.3\columnwidth]{hyper/Fig/hyper-sn}
    \label{fig:hyper-sn}} 
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{hyper/Fig/hyper-s-dnn}
    \label{fig:hyper-s-dnn}}           
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{hyper/Fig/hyper-s-dnn2}
    \label{fig:hyper-s-dnn2}}     
   \caption{Coherent noise test. (a) Noisy data containing coherent noise. (b) Denoised data using the \dlo{SSA}\wen{TSVD-based SSA} method. (b) Denoised data using the proposed method. (d) Randomized data using the method proposed in \cite{weilin2017}.  (e) Removed noise including both random and coherent noise using the \dlo{SSA}\wen{TSVD-based SSA} method. (f) Removed noise including both random and coherent noise  using the proposed method.}
   \label{fig:coh}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.45\columnwidth]{liuwei1/Fig/syn-c}
    \label{fig:syn-c}}
  \subfloat[]{\includegraphics[width=0.45\columnwidth]{liuwei1/Fig/syn}
    \label{fig:syn}}            
   \caption{2D synthetic example. (a) Clean data. (b) Noisy data. SNR of (b) is 0.73 dB.}
   \label{fig:syn-c,syn}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.45\columnwidth]{liuwei1/Fig/syn-ssa}
    \label{fig:syn-ssa}}
  \subfloat[]{\includegraphics[width=0.45\columnwidth]{liuwei1/Fig/syn-sst}
    \label{fig:syn-sst}} \\
  \subfloat[]{\includegraphics[width=0.45\columnwidth]{liuwei1/Fig/syn-ssa-dif}
    \label{fig:syn-ssa-dif}}
  \subfloat[]{\includegraphics[width=0.45\columnwidth]{liuwei1/Fig/syn-sst-dif}
    \label{fig:syn-sst-dif}}             
   \caption{Denoising comparison. (a) Denoised data using SSA. (b) Denoised data using OSST. (c) Removed noise corresponding to (a). (d) Removed noise corresponding to (b). SNRs of (a) and (b) are 5.10 dB and 7.22 dB, respectively.}
   \label{fig:syn-dn}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.45\columnwidth]{liuwei1/Fig/syn-c-fk}
    \label{fig:syn-c-fk}}
  \subfloat[]{\includegraphics[width=0.45\columnwidth]{liuwei1/Fig/syn-fk}
    \label{fig:syn-fk}} \\
  \subfloat[]{\includegraphics[width=0.45\columnwidth]{liuwei1/Fig/syn-ssa-fk}
    \label{fig:syn-ssa-fk}}
  \subfloat[]{\includegraphics[width=0.45\columnwidth]{liuwei1/Fig/syn-sst-fk}
    \label{fig:syn-sst-fk}}             
   \caption{FK spectrum comparison. (a) FK spectrum of clean data. (b) FK spectrum of noisy data. (c) FK spectrum of \dlo{SSA}\wen{TSVD-based SSA} processed data. (d) FK spectrum of \dlo{OSST}\wen{GROUSE-based SSA} processed data.}
   \label{fig:syn-dnfk}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{syn3d/Fig/syn3d-c}
    \label{fig:syn3d-c}}
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{syn3d/Fig/syn3d-n}
    \label{fig:syn3d-n}}           
   \caption{3D synthetic example. (a) Clean data. (b) Noisy data.}
   \label{fig:syn3d-c,syn3d-n}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{syn3d/Fig/syn3d-fk}
    \label{fig:syn3d-fk}}
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{syn3d/Fig/syn3d-ssa}
    \label{fig:syn3d-mssa}}  \\ 
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{syn3d/Fig/syn3d-rsvd}
    \label{fig:syn3d-rsvd}}
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{syn3d/Fig/syn3d-mc}
    \label{fig:syn3d-mc}}        
   \caption{Denoising comparison.  (a) Denoised data using FK method. (b) Denoised data using \dlo{SSA}\wen{TSVD-based SSA} method with SVD for low-rank decomposition. (c) Denoised data using \dlo{SSA}\wen{TSVD-based SSA} method with RSVD for low-rank decomposition. (d) Denoised data using \dlo{OSST}\wen{GROUSE-based SSA} method via GROUSE for low-rank decomposition.}
   \label{fig:syn3d-fk,syn3d-mssa,syn3d-rsvd,syn3d-mc}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{syn3d/Fig/syn3d-n-fk}
    \label{fig:syn3d-n-fk}}
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{syn3d/Fig/syn3d-n-ssa}
    \label{fig:syn3d-n-mssa}}  \\ 
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{syn3d/Fig/syn3d-n-rsvd}
    \label{fig:syn3d-n-rsvd}}
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{syn3d/Fig/syn3d-n-mc}
    \label{fig:syn3d-n-mc}}        
   \caption{Noise comparison. (a) Removed noise using FK method. (b) Removed noise using \dlo{SSA}\wen{TSVD-based SSA} method with SVD for low-rank decomposition. (c) Removed noise using \dlo{SSA}\wen{TSVD-based SSA} method with RSVD for low-rank decomposition. (d) Removed noise using \dlo{OSST}\wen{GROUSE-based SSA} method via GROUSE for low-rank decomposition.}
   \label{fig:syn3d-n-fk,syn3d-n-mssa,syn3d-n-rsvd,syn3d-n-mc}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn3d/Fig/syn3d-c-s}
    \label{fig:syn3d-c-s}}
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn3d/Fig/syn3d-fk-s}
    \label{fig:syn3d-fk-s}}
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn3d/Fig/syn3d-ssa-s}
    \label{fig:syn3d-ssa-s}}  \\ 
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn3d/Fig/syn3d-n-s}
    \label{fig:syn3d-n-s}}
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn3d/Fig/syn3d-rsvd-s}
    \label{fig:syn3d-rsvd-s}}
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{syn3d/Fig/syn3d-mc-s}
    \label{fig:syn3d-mc-s}}        
   \caption{2D section comparison (5th Xline section). (a) Clean data. (b) Denoised data using FK. (c) Denoised data using SSA. (d) Noisy data. (e) Denoised data using RSVD. (f) Denoised data using OSST.}
   \label{fig:syn3d-c-s,syn3d-fk-s,syn3d-ssa-s,syn3d-n-s,syn3d-rsvd-s,syn3d-mc-s}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=0.7\columnwidth]{guochang/Fig/real}          
   \caption{2D field data example.}
   \label{fig:real}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.7\columnwidth]{guochang/Fig/r-ssa}
    \label{fig:r-ssa}}\\
  \subfloat[]{\includegraphics[width=0.7\columnwidth]{guochang/Fig/r-sst}
    \label{fig:r-sst}}            
   \caption{Denoising comparison. (a) Denoised data using SSA. (b) Denoised data using OSST. }
   \label{fig:real-dn}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.7\columnwidth]{guochang/Fig/r-ssa-n-0}
    \label{fig:r-ssa-n}}\\
  \subfloat[]{\includegraphics[width=0.7\columnwidth]{guochang/Fig/r-sst-n-0}
    \label{fig:r-sst-n}}            
   \caption{Denoising comparison. (a) Removed noise using SSA. (d) Removed noise using OSST. \wen{The zoomed sections of the frameboxes are shown in Figure \ref{fig:real-n-z}.}}
   \label{fig:real-n}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.7\columnwidth]{guochang/Fig/r-ssa-n-z}
    \label{fig:r-ssa-n-z}}\\
  \subfloat[]{\includegraphics[width=0.7\columnwidth]{guochang/Fig/r-sst-n-z}
    \label{fig:r-sst-n-z}}            
   \caption{\wen{Zoomed denoising comparison}\dlo{Denoising comparison}. (a) Removed noise using SSA. (d) Removed noise using OSST.}
   \label{fig:real-n-z}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.7\columnwidth]{guochang/Fig/r-ssa-simi-0}
    \label{fig:r-ssa-simi}}\\
  \subfloat[]{\includegraphics[width=0.7\columnwidth]{guochang/Fig/r-sst-simi-0}
    \label{fig:r-sst-simi}}            
   \caption{Denoising comparison in terms of local similarity between denoised data and removed noise. (a) Local similarity using SSA. (d) Local similarity using OSST.}
   \label{fig:real-simi}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=0.7\columnwidth]{field/Fig/field}          
   \caption{3D field data example.}
   \label{fig:field}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{field/Fig/field-ssa}
    \label{fig:field-ssa}}
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{field/Fig/field-sst}
    \label{fig:field-sst}} \\
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{field/Fig/field-n-ssa}
    \label{fig:field-n-ssa}}
  \subfloat[]{\includegraphics[width=0.4\columnwidth]{field/Fig/field-n-sst}
    \label{fig:field-n-sst}}            
   \caption{Denoising comparison in 3D volume. (a) Denoised data using SSA. (b) Denoised data using OSST. (c) Removed noise corresponding (a). (d) Removed noise corresponding to (b).}
   \label{fig:field-3d}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.48\columnwidth]{field/Fig/f-ssa-simi}
    \label{fig:f-ssa-simi}}
  \subfloat[]{\includegraphics[width=0.48\columnwidth]{field/Fig/f-sst-simi}
    \label{fig:f-sst-simi}}          
   \caption{Denoising comparison in terms of local similarity between denoised data and removed noise. (a) Local similarity using \dlo{SSA}\wen{TSVD-based SSA} method. (b) Local similarity using \dlo{OSST}\wen{GROUSE-based SSA} method.}
   \label{fig:fsimi}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.32\columnwidth]{field/Fig/field-s-0}
    \label{fig:field-s}}
  \subfloat[]{\includegraphics[width=0.32\columnwidth]{field/Fig/field-s-ssa-0}
    \label{fig:field-s-ssa}}
  \subfloat[]{\includegraphics[width=0.32\columnwidth]{field/Fig/field-s-sst-0}
    \label{fig:field-s-sst}} \\
  \subfloat[]{\includegraphics[width=0.32\columnwidth]{field/Fig/field-sn-ssa}
    \label{fig:field-sn-ssa}}
  \subfloat[]{\includegraphics[width=0.32\columnwidth]{field/Fig/field-sn-sst}
    \label{fig:field-sn-sst}}            
   \caption{Denoising comparison in 2D section. (a) Raw seismic data. (b) Denoised data using SSA. (c) Denoised data using OSST. (d) Removed noise corresponding (a). (e) Removed noise corresponding to (b).}
   \label{fig:field-2d}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=0.45\columnwidth]{field/Fig/z-field}
    \label{fig:z-field}}\\
  \subfloat[]{\includegraphics[width=0.45\columnwidth]{field/Fig/z-ssa}
    \label{fig:z-ssa}}
  \subfloat[]{\includegraphics[width=0.45\columnwidth]{field/Fig/z-sst}
    \label{fig:z-sst}}          
   \caption{Zoomed comparison. (a) Raw seismic data. (b) Denoised data using SSA. (c) Denoised data using OSST.}
   \label{fig:field-z}
\end{figure}

%\begin{figure}[htb!]
%  \centering
%  \subfloat[]{\includegraphics[width=0.48\columnwidth]{earthquake/Fig/reftran}
%    \label{fig:reftran}}\\
%  \subfloat[]{\includegraphics[width=0.48\columnwidth]{earthquake/Fig/ref-sst}
%    \label{fig:ref-sst}}
%  \subfloat[]{\includegraphics[width=0.48\columnwidth]{earthquake/Fig/ref-sst-n}
%    \label{fig:ref-sst-n}}          
%   \caption{(a) Raw stack data. (b) Denoised stack. (c) Removed noise.}
%   \label{fig:earth}
%\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=0.95\columnwidth]{earthquake/Fig/reftran}     
   \caption{Raw earthquake stack data. }
   \label{fig:reftran}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=0.95\columnwidth]{earthquake/Fig/ref-sst}

   \caption{Denoised stack data. }
    \label{fig:ref-sst} 
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=0.95\columnwidth]{earthquake/Fig/ref-sst-n}

   \caption{Removed noise from the raw earthquake stack data.}
    \label{fig:ref-sst-n}  
\end{figure}

### 2021-01-12 rtseis/paper.tex
up

\title{Relative-time seislet transform}
\author{Zhicheng Geng~\footnotemark[1], 
        Xinming Wu~\footnotemark[1],  
        Sergey Fomel~\footnotemark[1] and
        Yangkang Chen~\footnotemark[2]}

\address{
    \footnotemark[1]Bureau of Economic Geology \\
    John A. and Katherine G. Jackson School of Geosciences \\
    The University of Texas at Austin \\
    University Station, Box X \\
    Austin, Texas, USA \\
    \footnotemark[2]Zhejiang University\\
    School of Earth Sciences\\
    Hangzhou, Zhejiang, China
}

\righthead{RT-seislet transform}
\lefthead{Geng et al. (2019)}

\maketitle

\begin{abstract}
    The seislet transform utilizes the wavelet-lifting scheme and local slopes 
    to analyze the seismic data. 
    In its definition, the designing of prediction operators specifically for 
    seismic images and data is an important issue. 
    We propose a new formulation of the seislet transform based on the relative time (RT) attribute. 
    This method uses RT volume to construct multiscale prediction 
    operators. With the new prediction operators, the seislet transform gets accelerated 
    since distant traces get predicted directly. 
    We apply the proposed method to synthetic and real data to demonstrate that 
    the new approach reduces computational cost and obtains excellent sparse
    representation on test datasets. %\par
\end{abstract}

%-----------------------------------------------------------------
\section{Introduction}
    Sparse transforms aim to represent the most important information of an 
    image with few coefficients in the transform domain while obtaining a good 
    quality approximation of the original image. 
    Over the past several decades, different types of wavelet-like transforms 
    have been proposed and successfully applied in image compression and 
    denoising~\cite[]{Hennen2006, Li2013}, including 
    curvelets~\cite[]{Starck2002, Ma2010}, contourlets~\cite[]{Do2005}, 
    shearlets~\cite[]{Demetrio2005}, directionlets~\cite[]{Velisavljevic2006}, 
    bandelets~\cite[]{LePennec2005}. 
    The strong anisotropic selectivity of these wavelet-like transforms helps 
    achieve excellent data compression and accurate reconstruction for seismic 
    images.

    \cite{Fomel2010a} introduced the seislet transform, which is a digital 
    wavelet-like transform designed specifically for seismic data. 
    Based on the lifting scheme used in digital wavelet transform (DWT) 
    construction~\cite[]{Sweldens1995}, the seislet transform follows dominant 
    local slopes obtained by plane-wave destruction (PWD)~\cite[]{Claerbout1992,
    Fomel2002} to predict seismic events. 
    Instead of using PWD, \cite{Liu2010} used offset continuation (OC) to 
    construct updating and prediction operators. 
    The OC-seislet transform has better performance than the PWD-seislet 
    transform in characterizing and compressing structurally complex prestack 
    reflection data. 
    To reduce sensitivity to strong noise interference, \cite{Liu2015} proposed 
    a velocity-dependent (VD) seislet transform. 
    In this method, the normal moveout equation was introduced to serve as a 
    connection between local slope and scanned velocities. 
    \cite{Chen2018} utilized empirical mode decomposition (EMD) to obtain 
    smoothly non-stationary data, and then applied the 1D non-stationary seislet 
    transform to the data. This new approach was called the EMD-seislet 
    transform and has shown excellent performance in attenuating random noise. 
    Recently, several studies show the superiority of the seislet transform
    on sparse representation of seismic data over the Fourier transform, the 
    wavelet transform and the curvelet transform \cite[]{Fomel2010a, Gan2015, 
    Chen2018}.

    With the ability to compress and reconstruct seismic images, the 
    seislet transform has been successfully applied in seismic data processing 
    such as noise attenuation \cite[]{Chen2016a, Chen2016b}, deblending 
    \cite[]{Chen2014, Gan2016} and data interpolation \cite[]{Cai2013, shuwei2016cs}, 
    However, the original implementation of PWD-seislet transform requires
    recursively computation when predicting distant traces, which increases its 
    computation cost, especially when the dataset is very large.
    Additionally, the smooth slopes from PWD in the original seislet transform 
    can fail to correctly follow reflections across discontinuities including 
    faults and unconformities. 
    Therefore, geologically meaningful discontinuities may not be optimally 
    compressed.

    The \old{Relative Time}\new{relative time} (RT) \old{Volume}\new{volume}, $\tau(x,y,t)$, has different meanings in
    different domains. 
    In seismic image domain, the \old{Relative Time}\new{RT} is the same as the 
    \old{Relative Geologic Time}\new{relative geologic time}~\cite[]{Stark2003, Stark2004} and each RT contour 
    corresponds to a geologic horizon.
    However, RT volumes of seismic gathers \old{don't}\new{do not} necessarily have geologic 
    meaning, since in this case, constant RT contours align with seismic events.
    There are several ways to generate an RT volume. 
    One can always pick out as many horizons or events as possible to obtain it, 
    which is simple but laborious. 
    The RT volume can also be generated by unwrapping seismic instantaneous 
    phase~\cite[]{Stark2003, Wu2012}.
    \cite{Fomel2010b} used local slopes of seismic events estimated by 
    PWD~\cite[]{Fomel2002} to generate the RT volume, which has superior 
    computational performance. 
    The RT volume already has \old{successful applications}\new{been successfully applied} in missing well-log 
    data prediction \cite[]{Bader2018}\new{ and} seismic horizons construction 
    \cite[]{Wu2015}\old{ and sedimentological interpretation}.

    In this paper, we propose a new implementation of the seislet transform, 
    called RT-seislet transform, by using the \old{Relative Time}\new{RT} 
    obtained from the predictive painting ~\cite[]{Fomel2010b} to construct 
    prediction operators for the seislet transform. 
    In this way, prediction of one trace from distant traces is computed 
    directly and accurately, which saves a lot of computation and has better 
    performance with faults and unconformities.
    By applying the new formulation of the seislet transform to synthetic and 
    real data, we demonstrate that the proposed method is efficient and able to 
    preserve discontinuities, while achieving excellent sparse representation of 
    seismic data.

    This paper is organized as follows: we first review the seislet 
    transform and the estimation of \new{a} RT volume. 
    Then, we incorporate RT attribute to construct new formulation of prediction 
    and update operators for the seislet transform.
    Finally, we test the proposed RT-seislet transform on both synthetic and 
    real datasets and compare its performance with the PWD-seislet transform.

%-----------------------------------------------------------------
\section{Theory}
\subsection{Reviews of 2D Seislet Transform}
    As proposed by \cite{Fomel2010a}, the seislet transform can be constructed 
    using the lifting scheme \cite[]{Sweldens1995}. 
    The procedure of the lifting scheme is as follows:
    \begin{enumerate}
        \item Arrange the input data as a sequence of records. 
            In the seislet transform, the input data \old{is}\new{are} common shot gather or 
            seismic image.
        \item Divide the arranged records into even and odd components 
            $\mathbf{e}$ and $\mathbf{o}$. For the 2D seislet transform, each 
            trace is a component and the seismic data \old{is}\new{are} split into two parts 
            according to trace indices.
        \item Find the residual $\mathbf{r}$ between the odd component and 
            its prediction from the even component
            \begin{equation}
                \mathbf{r} = \mathbf{o} - \mathbf{P[e]},
                \label{eq:a}
            \end{equation}
            where $\mathbf{P}$ is a \emph{prediction} operator.
        \item Using the difference from the previous step to get a coarse 
            approximation $\mathbf{c}$ of the data by updating the even 
            component
            \begin{equation}
                \mathbf{c} = \mathbf{e} + \mathbf{U[r]},
                \label{eq:b}
            \end{equation}
            where $\mathbf{U}$ is an \emph{update} operator.
        \item The coarse approximation $\mathbf{c}$ obtained from last step 
            becomes the new data, and previous steps are applied to the new data 
            at the next scale level.
    \end{enumerate}

    The coarse approximation $\mathbf{c}$ from the final scale and residual
    difference $\mathbf{r}$ from all scales form the result of the seislet 
    transform.

    The prediction and update operators are defined, for example, by modifying 
    operators in the construction of CDF 5/3 biorthogonal 
    wavelets~\cite[]{Cohen1992} as follows:
    \begin{equation}
        \label{P}
        \mathbf{P[e]}_k = \left(\mathbf{S}_k^{(+)}[\mathbf{e}_{k-1}]+
        \mathbf{S}_k^{(-)}[\mathbf{e}_{k}] \right) / 2
    \end{equation}
    and
    \begin{equation}
        \label{U}
        \mathbf{U[r]}_k = \left(\mathbf{S}_k^{(+)}[\mathbf{r}_{k-1}]+
        \mathbf{S}_k^{(-)}[\mathbf{r}_{k}] \right) / 4,
    \end{equation}
    where $\mathbf{S}_k^{(+)}$ and $\mathbf{S}_k^{(-)}$ can accomplish the 
    prediction of a trace from its left and right neighbors, respectively. 
    The predictions need to be applied at different scales. 
    For 2D seislet transform, different scales mean different distances 
    between traces. 
    More accurate higher-order formulations are possible. 
    Following the inverse lifting scheme from coarse \old{scale }to fine scale, 
    the inverse seislet transform can be constructed.

\subsection{Relative Time volume estimation}
    In the proposed method, \old{the }predictive painting~\cite[]{Fomel2010b}, \old{which
    is }based on the prediction operator arising from PWD~\cite[]{Fomel2002}, is 
    utilized to generate the \old{Relative Time}\new{RT} volume\old{,}\new{.} 
    In the predictive painting, after local slopes are estimated, an RT 
    volume is computed by spreading time values of reference traces along 
    dominant event slopes throughout the whole seismic volume.

    Using linear operator notation, PWD operation is defined as
    \begin{equation}
        \mathbf{d} = \mathbf{D}{}\mathbf{s},
    \end{equation}
    where $\mathbf{s} =[\mathbf{s}_1 \,\mathbf{s}_2 \,\cdots\, \mathbf{s}_N]^T$ 
    is a collection of seismic traces and $\mathbf{d}$ denotes the residual from 
    destruction. $\mathbf{D}$ is the destruction operator defined as 
    \begin{equation}
        \label{pred}
        \mathbf{D}=
        \begin{bmatrix}
            \mathbf{I} & 0 & 0 & \cdots & 0 \\
            -\mathbf{P}_{1,2} & \mathbf{I} & 0 & \cdots & 0 \\
            0 & -\mathbf{P}_{2,3} & \mathbf{I} & \cdots & 0 \\
            \vdots & \ddots & \ddots & \ddots & \vdots \\
            0 & \cdots & 0 & -\mathbf{P}_{N-1,N} & \mathbf{I}
        \end{bmatrix},
    \end{equation}
    where $\mathbf{I}$ denotes the identity matrix and $\mathbf{P}_{i,i+1}$ is 
    an operator that predicts the $(i+1)$-th trace from the $i$-th trace 
    according to the local slope of seismic event or seismic horizon.

    By a simple recursion, a trace can be predicted utilizing a distant trace. 
    For example, $\mathbf{P}_{r,k}$, predicting the $k$-th trace from the $r$-th 
    trace, is \old{simply }defined as
    \begin{equation}
        \label{predict}
        \mathbf{P}_{r,k}=\mathbf{P}_{k-1,k}\mathbf{P}_{k-2,k-1}\cdots
        \mathbf{P}_{r+1,r+2}\mathbf{P}_{r,r+1}.
    \end{equation}
    Then, the prediction of trace $\mathbf{s}_r$, given a reference trace
    $\mathbf{s}_r$ is accomplished by
    \begin{equation}
        \label{pp}
        \mathbf{s}_k^{\text{pre}}=\mathbf{P}_{r,k}\mathbf{s}_r.
    \end{equation}
    After determining the prediction operators in 
    \old{E}\new{e}quation~\ref{pred} by PWD, 
    the predictive painting algorithm recursively spreads information from a 
    reference trace to the whole seismic data volume by following local slopes
    using \new{e}\old{E}quation \ref{pp}. 
    If the information spread by the predictive painting \old{is}\new{are} the time \old{value}\new{coordinates}, an 
    RT volume is easily computed.

    Figure~\ref{fig:sigmoid} shows a synthetic image with several complex 
    geologic structures. 
    Local slopes corresponding to Figure~\ref{fig:sigmoid} are shown in 
    Figure~\ref{fig:dip-pad}, which \old{is}\new{are} estimated by PWD. 
    Figure~\ref{fig:pick-1} is the \old{Relative Time}\new{RT} volume calculated 
    by the predictive painting using local slopes in Figure~\ref{fig:dip-pad}. 
    The reference trace of this RT volume is in the center of the image, which 
    is marked as a vertical line in Figure~\ref{fig:pick-1}. 
    This single reference RT volume is used to flatten the input seismic 
    image (Figure \ref{fig:sigmoid}) by unshifting each traces using the 
    information it contains, since \old{Relative Time}\new{RT} indicates how 
    much a given trace is shifted with respect to the reference trace.
    The flattened image is shown in Figure~\ref{fig:flat-1}.
    Another RT volume with multiple references, shown in 
    Figure~\ref{fig:pick-5}, is generated by selecting five reference traces and 
    calculating the average of all estimated \old{Relative Time}\new{RT} 
    volumes.
    Figure~\ref{fig:flat-5} shows the corresponding flattened image.
    The comparison between two flattened seismic images (Figure~\ref{fig:flat-1} 
    and \ref{fig:flat-5}) indicates that the RT volume with only one reference 
    trace \old{doesn't}\new{does not} necessarily have information about all seismic events since 
    there are discontinuities such as faults and unconformities, while the RT 
    volume computed with more reference traces contains more information.

    \inputdir{rt}
    \plot{sigmoid}{width=0.8\columnwidth}{Synthetic seismic image from 
        \cite{Claerbout2000}.}
    \plot{dip-pad}{width=0.8\columnwidth}{Local slopes estimated from 
        Figure~\ref{fig:sigmoid}.}
    \multiplot{2}{pick-1,pick-5}{width=0.6\columnwidth}{\old{Relative time}
        \new{RT} estimated by predictive painting from Figure~\ref{fig:sigmoid} 
        using (a) a single reference trace and (b) multiple reference traces.}
    \multiplot{2}{flat-1,flat-5}{width=0.6\columnwidth}{Flattened images using
        RT volumes from (a) Figure \ref{fig:pick-1} and (b) 
        Figure~\ref{fig:pick-5}.}

\subsection{RT formulation of prediction and update operators}
    \old{Relative time}\new{RT} contains the relationship between traces. 
    From RT volume, it is straightforward to obtain the shift of one trace with 
    respect to the reference. 
    Therefore, the trace prediction using RT volumes is formulated as follows:
    \begin{equation}
        \mathbf{s}_k^{\text{pre}}(t)=\mathbf{s}_r(\mathbf{\tau}_{k,r}(t))
        \label{new_form}
    \end{equation}
    where $\mathbf{s}_k$ and $\mathbf{s}_r$ denote the $k$-th and the $r$-th 
    trace, respectively. 
    $\tau_{k,r}(t)$ is the RT value of the $k$-th trace with the $r$-th trace as 
    the reference trace, indicating the shift of the $k$-th trace with
    respect to the $r$-th trace. 
    According to \new{e}\old{E}quation \ref{new_form}, the prediction of the 
    $k$-th trace from the $r$-th trace is easily accomplished by simply applying 
    forward interpolation to the $r$-th trace using corresponding RT values.
    In the proposed method, we use \new{e}\old{E}quation \ref{new_form} to 
    define operators $\mathbf{S}$ in \new{e}\old{E}quations \ref{P} and 
    \ref{U} to construct corresponding prediction and update operators. 
    In this way, a trace is predicted from a distant trace directly by the 
    \old{Relative Time}\new{RT} attribute instead of the recursive computation 
    used in the PWD-seislet transform. 
    Also, because an accurate RT volume stores information about all horizons 
    and structural discontinuities including faults and unconformities, 
    predictions of traces around discontinuities using \new{e}\old{E}quation 
    \ref{new_form} are accurate. 
    Therefore, a better \old{approximation}\new{delineation} of faults and unconformities can be 
    achieved.

    In computing an RT volume, we need to first choose one or multiple reference 
    traces. 
    After computing the RT volume, the \old{Relative Time}\new{RT} attribute 
    between any two traces is easily obtained from one RT volume using\old{ the 
    following formulation}:
    \begin{equation}
        \label{rt}
        \mathbf{\tau}_{k,r}(t)=\mathbf{\tau}^{-1}_{r,l}(\mathbf{\tau}_{k,l}(t)),
    \end{equation}
    where $\mathbf{\tau}_{j,i}(t)$ represents the RT value of the $j$-th trace 
    with the $i$-th trace as the reference trace, and 
    $\mathbf{\tau}^{-1}_{r,l}(t)$ is the time warping \cite[]{Burnett2009} of 
    $\tau_{r,l}(t)$. 
    According to \new{e}\old{E}quation \ref{rt}, given the shift information 
    $\tau_{r,l}(t)$ and $\tau_{k,l}(t)$, the shift relationship between the 
    $k$-th trace and the $r$-th trace can be obtained by applying an inverse 
    interpolation to $\tau_{r,l}(t)$ using $\tau_{k,l}(t)$. 
    Then, \new{e}\old{E}quation \ref{new_form} is applied to implement the 
    prediction of the $k$-th trace from the $r$-th trace.
    Therefore, only one RT volume is needed for the proposed implementation of 
    the seislet transform.

    Figure~\ref{fig:pick-150,invint,pick-50,pick-50-true} shows an example of
    \old{how to utilize}\new{implementing} \new{e}\old{E}quation~\ref{rt} to compute an RT volume from 
    another \old{RT volume}\new{one} with different reference traces. 
    The RT volume in Figure~\ref{fig:pick-150} is obtained by the predictive 
    painting with the 150th trace as the reference trace. 
    This RT volume can be represented by $\mathbf{\tau}_{k,150}(t), 
    k=1,2,\ldots,n$. 
    Figure~\ref{fig:invint} is the time warping of this RT volume. 
    We extract the 50th trace from Figure~\ref{fig:invint}, which is denoted by 
    $\mathbf{\tau}^{-1}_{50,150}(t)$. 
    Then, by implementing \new{e}\old{E}quation~\ref{rt}, i.e., inverse 
    interpolating $\mathbf{\tau}^{-1}_{50,150}(t)$ using the whole RT volume 
    ($\mathbf{\tau}_{k,150}(t), k=1,2,\ldots,n$), we can get a new 
    RT volume, \new{as }shown in Figure~\ref{fig:pick-50} ($\mathbf{\tau}_{k,50}(t), 
    k=1,2,\ldots,n$). Here, we use the 50th trace as the reference trace. 
    To evaluate the effectiveness of \new{e}\old{E}quation \ref{rt}, RT 
    volumes from Figure \ref{fig:pick-50} and \ref{fig:pick-50-true} are used to 
    flatten Figure \ref{fig:sigmoid}. 
    Flattened images are shown in Figure \ref{fig:flat1,flat2}. Small 
    differences between Figure \ref{fig:flat1} and \ref{fig:flat2} indicate that 
    these two RT volumes (Figure \ref{fig:pick-50} and \ref{fig:pick-50-true}) 
    contain similar information, which \old{proves}\new{demonstrate} that 
    \new{e}\old{E}quation~\ref{rt} can be used to get the relationship between 
    any two traces from one single RT volume.

    \multiplot{4}{pick-150,invint,pick-50,pick-50-true}{width=0.4\columnwidth}{
        (a) The RT volume obtained by the predictive painting and the reference 
        trace is the 150th trace. (b) Time warping of (a). (c) RT 
        volume obtained by \new{e}\old{E}quation~\ref{rt}. (d) The RT volume 
        obtained by the predictive painting and the reference trace is the 50th 
        trace.}
    \multiplot{3}{flat1,flat2}{width=0.7\columnwidth}{Flattened images using RT 
        volumes from (a) Figure \ref{fig:pick-50} and (b) 
        Figure \ref{fig:pick-50-true}.}

\subsection{Workflow}
    The workflow of the proposed method is shown in Figure~\ref{fig:workflow}. 
    As we can see, the proposed approach is convenient to implement since only 
    one RT volume is needed before applying the new formulation of the seislet 
    transform. 
    In the proposed approach, we need first use PWD to compute the local slopes 
    of the input seismic data such that the \old{Relative Time}\new{RT} volume 
    can be computed by the predictive painting from the estimated slopes, as 
    discussed in the previous section. 
    \old{Then with}\new{With} the help of the generated RT volume, the RT-seislet transform is 
    \new{then} applied to the input data to get coefficients in the RT-seislet transform 
    domain. 
    With the transformed data, signal processing tasks, including data 
    reconstruction and noise attenuation, can be easily applied.

    \inputdir{.}
    \plot{workflow}{width=0.8\columnwidth}{Workflow of the proposed RT-seislet
    transform.}

%-----------------------------------------------------------------
\section{Synthetic Data Example}
    We use the same data example from Figure~\ref{fig:sigmoid} to demonstrate 
    the performance of the proposed method in ef{}ficient data reconstruction. 
    Figure~\ref{fig:rt} shows the \old{Relative Time}\new{RT} calculated from 
    the image using the predictive painting with multiple reference traces. 
    We applied both the original PWD-seislet transform and the RT-seislet 
    transform to this image. 
    Then, we threshold coefficients and keep only the largest ones from both the 
    transforms to reconstruct the same original data. 
    By using the same percent (1\%) of large coefficients, the reconstruction 
    from the new formulation (Figure \ref{fig:rtseisrec1}) recovers more 
    accurate amplitude values and better preserves structural discontinuities 
    near faults and unconformities than the one from PWD-seislet transform 
    (Figure \ref{fig:pwdseisrec1}).

    \inputdir{sigmoid}
    \plot{rt}{width=0.8\columnwidth}{\old{Relative time}\new{RT} volume 
        estimated by the predictive painting using multiple reference traces.}
    \multiplot{2}{pwdseisrec1,rtseisrec1}{width=0.6\columnwidth}{Synthetic 
        seismic image reconstruction by thresholding coefficients and keeping 
        only 1\% of significant coefficients using (a) inverse PWD-seislet 
        transform and (b) inverse RT-seislet transform.}
    \plot{coef}{width=0.8\columnwidth}{Normalized coefficients from the 
        PWD-seislet transform (red \new{dashed} line) and the RT-seislet 
        transform (blue \new{solid} line) sorted from large to small on a 
        decibel scale.}

    The comparison between coefficients from the PWD-seislet transform and 
    the RT-seislet transform is shown in Figure \ref{fig:coef}. 
    The minor difference of their decay rate indicates that the PWD-seislet 
    transform and the proposed transform obtain the same sparsity for the input 
    data.
    Figure \ref{fig:tim} shows the plot of CPU time against the number of 
    traces. The proposed formulation of the seislet transform shows promising 
    computation efficiency since the prediction of a trace using distant 
    traces is accomplished directly instead of recursively as in the original 
    PWD-seislet transform.

    \inputdir{time}
    \plot{tim}{width=0.80\columnwidth}{CPU time of the PWD-seislet transform 
        (red \new{dashed} line) and the RT-seislet transform (blue \new{solid}
        line) \old{vs.}\new{versus} the number of traces.}

    For the purpose of testing the sensitivity of the RT-seislet transform to 
    noise, we add random noise to the synthetic model and utilize 
    signal-to-noise ratio (SNR) as measurement: 
    \begin{equation}
        \label{snr}
        SNR=10\log_{10}\frac{\|\mathbf{s}_{true}\|^2_2}
        {\|\mathbf{s}_{true}-\mathbf{s}\|^2_2}\,,
    \end{equation}
    where $\mathbf{s}_{true}$ is the original data, and $\mathbf{s}$ denotes
    the reconstructed data (e.g., Figure~\ref{fig:rtseisrec1}) or noisy data.
    We plot SNRs of reconstructed data using the inverse PWD-seislet transform 
    and the inverse RT-seislet transform with respect to the noise variance in 
    Figure~\ref{fig:snr}. 
    Apparently, as the noise level increases, the performance of the RT-seislet 
    gets worse, which shows that the proposed method is sensitive to noise. 
    But, compared with the original PWD-seislet transform, the new method has 
    superior performance \old{with less sensitivity}\new{that is less sensitive} to noise.
    Figure~\ref{fig:sigmoid-noise0,rtseisrec-noise0} shows one example of the
    noisy data and the reconstructed data. The SNR of 
    Figure~\ref{fig:rtseisrec-noise0} is 17.19 dB.

    \inputdir{noise}
    \plot{snr}{width=0.80\columnwidth}{SNR diagram of the PWD-seislet transform 
        (red \new{dashed} line) and the RT-seislet transform (blue \new{solid}
        line) with respect to the noise level (variance value).}
    \multiplot{2}{sigmoid-noise0,rtseisrec-noise0}{width=0.6\columnwidth}{(a)
        Noisy data. (b) Reconstructed data using 10\% coefficients (SNR=17.19).}

    Figure~\ref{fig:para,para-rtseisrec1,para-diff} presents another synthetic example. 
    Figure~\ref{fig:para} and \ref{fig:para-rtseisrec1} shows the synthetic shot gather with three hyperbolic 
    events and Figure~\ref{fig:para-rtseisrec1} is the data reconstruction by the 
    RT-seislet transform using only 1\% of the most significant coefficients, respectively. 
    We use \old{only the middle trace}\new{the first, the middle and the last 
    traces} as the reference trace\new{s} to compute the 
    \old{Relative Time}\new{RT} volume.
    \new{The residual between the synthetic shot gather and the reconstruction
    result is shown in Figure~\ref{fig:para-diff}.}
    For this simple synthetic shot gather, the proposed method achieves an 
    excellent data reconstruction result.

    \inputdir{synth}
    \multiplot{3}{para,para-rtseisrec1,para-diff}{width=0.45\columnwidth}{
        (a) Synthetic shot gather. (b) Data reconstruction by the inverse 
        RT-seislet transform using only 1\% of the most significant 
        coefficients. (c) Difference between (a) and (b).}

\section{2-D Field Data Example}
    To further test the proposed method, we use a common-midpoint gather from the 
    North Sea dataset (Figure~\ref{fig:gath}). Figure~\ref{fig:seis} shows the 
    data in the seislet transform domain. We observe that significant 
    coefficients are apparent in only a narrow area on the left, which 
    indicates the excellent compression ability of the proposed RT formulation 
    of the seislet transform. The field data reconstruction using only 1\% of 
    the most significant RT-seislet coefficients is shown in 
    Figure~\ref{fig:seisrec1}. The reconstructed image \old{contains}\new{retains} the most 
    important seismic events in the original seismic data.

    If we mute the RT-seislet coefficients at fine scales while keeping the 
    significant coefficients at coarse scales (Figure~\ref{fig:seisdeno}), the 
    inverse RT-seislet transform enables effective denoising, removing 
    incoherent noise from the gather. 
    The result of denoising are shown in Figure~\ref{fig:seis16}. 
    Figure~\ref{fig:diff} shows the removed noise section using the proposed implementation of the seislet transform.

    The RT-seislet is also able to perform interpolation. 
    We add two more scales with small random noise to Figure~\ref{fig:seis} and 
    interpolate the \old{Relative Time}\new{RT} volume by a factor of four. 
    Then the interpolated shot gather is obtained and the number of traces is 
    increased by four. 
    The extended data in the seislet transform domain is shown in Figure~\ref{fig:seisrand2}. 
    Figure~\ref{fig:gath4} is the interpolated shot gather. 
    Figure \ref{fig:fft,fft2} shows the F-K spectrum of the zero-padded 
    field data and the interpolated gather. 
    The zero-padded shot gather is generated by manually padding zero traces 
    between two traces.
    In this example, the seislet transform domain is extended with random noise 
    because there is unpredictable noise in the real case.

    \inputdir{gath}
    \plot{gath}{width=0.80\columnwidth}{Common-midpoint gather.}
    \multiplot{2}{seis,seisrec1}{width=0.60\columnwidth}{(a) The field data in 
        the RT-seislet transform domain and (b) \old{the field data }reconstruction using only 1\% of significant coefficients by the inverse 
        RT-seislet transform.}
    \multiplot{4}{gath,seisdeno,seis16,diff}{width=0.45\columnwidth}{\new{(a) Original gather. }(b) \old{Denoising}\new{Denoised} 
        result by muting RT-seislet coefficients at fine scales (a) and (c) 
        the removed noise section using the RT-seislet transform.}
    \multiplot{2}{seisrand2,gath4}{width=0.6\columnwidth}{(a) Extended seislet 
        transform domain. (b) Interpolated shot gather by the inverse RT-seislet 
        transform.}
    \multiplot{2}{fft,fft2}{width=0.6\columnwidth}{F-K \old{spectrum}\new{spectra} of (a) 
        zero-padded \old{field data} and (b) the interpolated field data.}

\section{3-D Field Data Example}
    We also test the proposed method on a 3D dataset. 
    Figure~\ref{fig:cuber} is the Teapot Dome seismic dataset. 
    After inline and crossline slopes (Figure~\ref{fig:dip1,dip2}) are 
    estimated, the \old{Relative Time}\new{RT} volume (Figure~\ref{fig:pick}) is 
    easily obtained from the predictive painting with multiple reference traces. 
    With the RT volume, the 3D seislet transform can be constructed by 
    cascading the 2D seislet transform along inline and crossline directions. 
    To be specific, we first apply the 2D RT-seislet transform along inline 
    direction, and then another 2D transform along crossline is applied on the 
    coefficients from the previous step to obtain the coefficients in the 3D 
    transform domain.
    The coefficients of the 2D seislet transform along inline direction and the 
    3D seislet transform are shown in Figure \ref{fig:rtseis-inline} and 
    \ref{fig:rtseis}.
    In the seislet domain, most of the coefficients concentrate in the coarse 
    scales, which shows the excellent compression ability of the RT-seislet 
    transform. 
    Figure~\ref{fig:teapot-rtseisrec5} is the data reconstruction result using 
    only 5\% of the most significant coefficients. 
    The difference between Figure \ref{fig:cuber} and the reconstructed data, 
    contains mainly noise, is shown in Figure \ref{fig:teapot-diff}.
    The proposed method has \old{excellent}\new{good} performance for reconstruction and 
    preserving the structures of the dataset.

    \inputdir{teapot}
    \multiplot{2}{cuber,pick}{width=0.6\columnwidth}{(a) Teapot dome dataset. 
        (b) \old{Relative time}\new{RT} volume estimated by the predictive 
        painting.}
    \multiplot{2}{dip1,dip2}{width=0.6\columnwidth}{Inline (a) and Crossline (b)
        Dip.}
    \multiplot{4}{rtseis-inline,rtseis,teapot-rtseisrec5,teapot-diff}
    {width=0.4\columnwidth}{(a) The coefficients in 2D seislet domain along 
        inline only. (b) The coefficients in 3D seislet domain. 
        (c) Data reconstruction using only 5\% of significant coefficients by 
        the inverse RT-seislet transform.
        (d) Difference between (c) and the original seismic volume 
        (Figure \ref{fig:cuber}).}

%-----------------------------------------------------------------
\section{Discussion}
    The proposed formulation of the seislet transform attempts to construct 
    multiscale prediction operators, to enhance the performance of the 
    seislet transform. 
    The prediction operators in the original seislet transform are defined by 
    PWD, so the prediction of distant traces needs recursive computation, which 
    is very time-consuming when it comes to large size dataset. 
    In the proposed RT-seislet transform, an RT volume is used to define a 
    multiscale prediction operator. 
    As shown in the previous sections, the relationship between any two traces 
    can be obtained from the \old{Relative Time}\new{RT} volume, which helps 
    avoid the recursive computation for the prediction of distant traces. 
    As a result, the RT-seislet transform is much more efficient than the 
    original seislet transform.

    Besides, in the implementation of the proposed method, the choice of 
    reference traces plays an important role in the generation of the RT volume. 
    More reference traces usually mean a better \old{Relative Time}\new{RT} 
    volume. 
    The location of reference traces also needs to be considered carefully. 
    In practice, evenly distributed reference traces are recommended.
    Besides, complex geologic structures need to be treated differently.
    For example, it is better to put reference traces at each side of faults. 
    Another important issue is about the smoothing radius when estimating local 
    slopes by PWD. 
    For noise-free data, small smoothing radius is enough. 
    The smoothing radius is three for the estimation of Figure~\ref{fig:dip-pad}. 
    And with the increasing of the noise level, larger smoothing radius is 
    needed.

    The proposed RT-seislet transform highly depends on the RT volume. 
    In our method, local slopes by PWD, which are easily 
    affected by noise, are utilized to generate the RT volume, so the new 
    formulation is sensitive to the noise. 
    However, this problem certainly can be solved by improving the PWD or using 
    other methods, which are not sensitive to noise, to generate the RT volume.

%-----------------------------------------------------------------
\section{Conclusions}
    We have proposed a new formulation of the seislet transform, a novel 
    approach to sparse seismic data. 
    In our approach, we use an RT volume to construct multiscale prediction and 
    update operators for the seislet transform. 
    This proposed approach is computationally more efficient and better 
    preserves geologically meaningful discontinuities than the original 
    formulation of the seislet transform in reconstructing the \old{original 
    seismic dataset}\new{raw seismic data}. 
    It also has excellent performance in obtaining the sparse representation of
    seismic data.
    Synthetic \old{data }and field data examples show that the proposed new 
    formulation is efficient and effective in data reconstruction and noise 
    attenuation.

%-----------------------------------------------------------------
\section{Acknowledgements}
    The research is partially supported by Texas Consortium for Computation (TCCS), the “Thousand Youth Talents Plan”, and the Starting Funds from Zhejiang University. The computational examples reported in this paper are reproducible using the \emph{Madagascar} open-source software package \cite[]{Fomel2013}.

\section{DATA AND MATERIALS AVAILABILITY}
Data associated with this research are available and can be obtained by contacting the corresponding author.

\bibliographystyle{seg}
\bibliography{rtseis}

### 2021-01-12 rtseis/time/Tflow.py

@@ -1,0 +1,47 @@
+'extra flows'
+
+import string, re, sys, os
+from rsf.proj import *
+
+
+def Tflow(target, source, command, prefix='sf',):
+
+    if sys.platform == 'darwin':
+        time_nm='gtime'
+    else:
+        time_nm='time'
+
+    timer=WhereIs(time_nm)
+    if timer==None:
+        sys.stderr.write('Tflow need %s.'%time_nm)
+        sys.exit(1)
+
+    if isinstance(target, list):
+        tfiles = target
+    else:
+        tfiles = target.split(' ')
+#	tfiles.insert(0, tfiles[0]+'_runtime')
+    pars=command.split()
+    p0=pars.pop(0)
+
+    p1=WhereIs(p0) # sfdip
+    if p1==None :
+        p1=WhereIs(prefix+p0) # dip
+    if re.match(r'[^/]+\.exe$',p0) :
+        p1=os.path.join('.',p0) # Mdip.exe
+
+    pars.insert(0,p1)
+    cmd=' '.join(pars)
+    Flow(tfiles, source,
+            '''
+            ( %s -f "%%S %%U" %s <${SOURCES[0]} >/dev/null )
+                        >& time.out &&
+            (tail -1 time.out;
+            echo in=time0.rsf n1=2 data_format=ascii_float)
+                    > time0.rsf &&
+            dd form=native < time0.rsf | stack axis=1 norm=n
+            > time1.rsf &&
+            cmplx ${SOURCES[2]} time1.rsf > ${TARGETS[0]} &&
+            %s -f time.out time0.rsf && rm time1.rsf
+            '''%(timer, cmd, WhereIs('rm')),
+            stdin=None, stdout=None)

### 2021-01-12 rtseis/paper.tex
Update paper.tex

@@
 \section{Acknowledgements}
-    The research is partially supported by Texas Consortium for Computation (TCCS), the “Thousand Youth Talents Plan”, and the Starting Funds from Zhejiang University.
+    The research is partially supported by Texas Consortium for Computation (TCCS) and the Starting Funds from Zhejiang University.
 The computational examples reported in this paper are reproducible using the \emph{Madagascar} open-source software package \cite[]{Fomel2013}.

### 2021-01-29 fxy/fxy.tex
2021年 1月29日 星期五 00时15分44秒 CST

\title{Non-stationary predictive filtering for seismic random noise suppression - A tutorial}
%\author{Hang Wang\footnotemark[1], Wei Chen\footnotemark[2], Weilin Huang\footnotemark[3], Shaohuan Zu\footnotemark[4], Xingye Liu\footnotemark[1], Liuqing Yang\footnotemark[2] and Yangkang Chen\footnotemark[1]}
\author{Authors}
% new functions: 
% 1. 2D + 3D + 4D
% 2. smoothing along frequency 
% 3. frequency-dependent smoothing along space (increase with frequency to better cope with noise)
% 4. User-defined smoothing (radius) along frequency, space (X/Y)
% 5. windowing strategy

% can be separated into two papers (1: with smoothing along frequency and frequency-dependent smoothing, public; 2: all functions, private)

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\ms{GEO-2020} %\ms{GJI-2019}

%\address{
%\footnotemark[1]
%School of Earth Sciences\\
%Zhejiang University\\
%Hangzhou, Zhejiang Province, China, 310027\\
%yangkang.chen@zju.edu.cn \\
%\footnotemark[2] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
%Yangtze University\\
%Daxue Road No.111\\
%Caidian District\\
%Wuhan, China, 430100\\
%\footnotemark[3] State Key Laboratory of Petroleum Resources and Prospecting \\
%China University of Petroleum \\
%Fuxue Road 18th\\
%Beijing, China, 102200\\
%cup\_hwl@126.com \\
%\footnotemark[4] College of Geophysics\\
%Chengdu University of Technology \\
%Dongsanlu, Erxianqiao, Chengdu 610059, Sichuan, China
%%
%%\footnotemark[3] Hubei Cooperative Innovation Center of Unconventional Oil and Gas\\
%%Daxue Road No.111\\
%%Caidian District\\
%}

%\lefthead{Wang et al.}
\righthead{Non-stationary predictive filtering}

\begin{abstract}
Predictive filtering in the frequency domain is one of the most widely used denoising algorithms in the seismic data processing workflow. Predictive filtering is based on the assumption of linear/planar events in the time-space domain. In traditional predictive filtering method, the predictive filter is fixed across the spatial dimension, which cannot deal with the spatial variation of seismic data well. To handle the curving events, the predictive filter is either applied in local windows or extended to a non-stationary version. The regularized non-stationary autoregression (RNAR) method can be treated as a non-stationary extension of the traditional predictive filtering, where the predictive filter coefficients are variable in different space locations. The highly under-determined inverse problem is solved by shaping regularization with a smoothness constraint in space. We further extend the RNAR method to a more general case, where we can apply more constraints to the filter coefficients according to the features of seismic data. First, apart from the smoothness in space, we also apply a smoothing constraint in frequency, considering the coherency of the coefficients in the frequency dimension. Secondly, we apply a frequency dependent smoothing radius along the space dimension to better take advantage of the non-stationarity of seismic data in the frequency axis, and to better deal with noise. The proposed method is validated via several synthetic and field data examples.
\end{abstract}

%\section{Keywords}
%key1,key2,key3

\section{Introduction}
Removing spatially incoherent noise from seismic data is one important task in reflection seismology. The noise suppression is either applied in pre-stack seismic data for improving the velocity analysis and seismic migration to obtain a better seismic image, or applied in post-stack seismic images or attribute maps to facilitate a more reliable seismic interpretation. Therefore, the noise suppression performance highly affects most steps in the seismic processing, imaging, and interpretation chain \cite[]{mostafa2011,mostafa2012,yangkang2018eseis,chenwei2018,chenwei2020}. However, due to the complexity of seismic data, a simple assumption that is required in most denoising algorithms is not always valid. For such reason, many denoising algorithms based on different assumptions are developed during the past decades.

Those widely used denoising approaches are the prediction-based methods \cite[]{canales1984,siwei2015}, either in $t-x/y$ domain \cite[]{abma1995} or $f-x/y$ domain \cite[]{guochang2012,guochang2013}, which assume that seismic data are spatially predictable and thus a prediction filter can be designed to predict the useful signals. Sparsity based methods first transform the seismic data to a sparsity-promoting domain, where the useful signals and noise can be easily separated because of the amplitude difference. The performance of the transform methods highly depends on the sparsity that is close related with the amplitude difference between signal and noise in the transform domain \cite[]{amir2017,amir2017geo}. Thus, researchers were competing to find the sparest transform for seismic data among curvelet transform \cite[]{neelamani2008}, shearlet transform \cite[]{zhang2018multicomponent}, wavelet transform \cite[]{mostafa2016geo}, Radon transform \cite[]{wenkai2013}, and seislet transform \cite[]{fomel2010seislet,liuyang2010oc,shuwei20163}, etc. The rank-reduction methods emerged in the past decade because of its decent performance in dealing with complex seismic data \cite[]{mssa,weilin2016dmssa,yangkang2016irr5d,wang2020low}. Seismic data are first transformed to a low-rank space and then the principal components are extracted to stand for the useful seismic signals. However, these methods suffer from the intense computation required by the singular value decomposition (SVD) operations. Decomposition based methods divide the seismic data into several components, where the useful signals can be obtained by recombine these components by either frequency or morphological difference \cite[]{weilin2017gji}. Because of the extreme complexity of seismic data, one or more methods are sometimes combined to output a better performance than an individual method \cite[]{yangkang20141}.

While many denoising algorithms have been developed by researchers , the most widely accepted method in the industry is still the prediction filter based method. Because of the high efficiency and the stable performance (although may not be optimal), processing seismologists prefer to improve the traditional prediction filter by simple and efficient strategies, with the purpose of maintaining the high-efficiency advantage and improving the existing performance, rather than utilizing more complicated and time-consuming denoising methods. The most classic prediction filter originated by \cite{canales1984} with a design of frequency-domain wiener filter, which was referred to as the $f-x$ predictive filtering method. The predictive filter was then introduced separately by \cite{gulunay1986fxdecon} and was referred to as the famous FXDECON algorithm. Since then, a variety of variants have been proposed to improve the classic implementation of the predictive filter. \cite{fxydecon} proposed the non-causal prediction filter to better utilize the constraints from both forward and backward prediction, and applied it to 3D random noise suppression. \cite{naghizadeh2009f} developed an adaptive predictive filter to handle the multi-dip problem in complex seismic data without the need of local windowing and applied it to the seismic interpolation problem.  \cite{guochang2012} developed a regularized non-stationary autoregression (RNAR) method to deal with the spatial curvature and the non-stationarity of seismic data. The RNAR method formulates the predictive filter as the form of auto-regression and extends the autoregression to each non-stationary version. \cite{guochang2013} further applied the RNAR method to 3D problems.  \cite{fx2017} discussed the signal leakage issues in various implementations of the $f-x$ deconvolution algorithms based on the open-source Teapot domain dataset. Recently, \cite{fuchao2020} developed a structure-guided predictive filter to handle the non-stationarity of seismic data by squeezing and shrink the length of prediction filter according to the structural complexity.

In this paper, we further extend the RNAR approach to a more integrated framework, where we deal with the spatial non-stationarity of seismic data by extending the stationary autoregression to non-stationary autoregression and take advantage of the temporal coherency, i.e., narrow-band and smooth spectrum, by smoothing the autoregression coefficients in frequency and applying frequency-dependent smoothing to the coefficients in space.  To distinguish from the RNAR method, we name the proposed new method as the non-stationary predictive filtering (NPF) method. Compared with the stationary predictive filtering (PF) \cite[]{canales1984}, there are two meanings of the non-stationarity we refer to here. First, we synthesize the non-stationary data by regularized non-stationary autoregression. Secondly, we deal with the non-stationary model (the frequency-dependent non-stationary autoregression coefficients) by applying non-stationary model constraint, e.g., frequency-dependent spatial smoothing. We organize the paper as follows. We first introduce the fundamentals of the stationary predictive filtering (SPF) and NPF, with the focus on the new constraints we have applied compared with the RNAR method. Then we use several 2D/3D synthetic and real data examples to demonstrate the better denoising performance of the proposed NPF method. Finally, we sumarize some conclusions according to the numerical experiments.

\section{Theory}
\subsection{Stationary predictive filtering}
The stationary predictive filtering (SPF) is based on the plane-wave assumption. Let us first consider the plane-wave equation as follows \cite[]{fomel2002pwd}:
\begin{equation}
\label{eq:plane}
p \frac{\partial u}{\partial t} + \frac{\partial u}{\partial x} = 0,
\end{equation}
where $p$ denotes the slope, $u(t,x)$ denotes the wavefield at time $t$ and space $x$. The plane-wave equation has the following analytical solution:
\begin{equation}
\label{eq:pre}
u(t,x)=g(t-px),
\end{equation}
where $g(t)$ denotes the wavelet.  When taken into the frequency domain:
\begin{equation}
\label{eq:pref}
U(f,x)=G(f)e^{i2\pi fpx},
\end{equation}
where $U(f,x)$ and $G(f)$ denote the frequency-domain spectrum of wavefield and wavelet. From equation \ref{eq:pref}, it can be derived that:
\begin{equation}
\label{eq:pref2}
U(f,x+1)=e^{i2\pi fp}U(f,x).
\end{equation}
When several planes exist, 
\begin{equation}
\label{eq:pref22}
U(f,x+1)=e^{i2\pi fp_1}U(f,x)+e^{i2\pi fp_2}U(f,x-1)+e^{i2\pi fp_3}U(f,x-2)+\cdots+e^{i2\pi fp_{L}}U(f,x-L+1),
\end{equation}
which can be considered as an auto-regression (AR) model or order $L$ \cite[]{tufts1980,canales1984,yangkang20141}. The AR model expressed in equation \ref{eq:pref22} is known as the $f-x$ predictive filtering based on the forward prediction. The AR model can also be formulated as a causal prediction filter:
\begin{equation}
\label{eq:pref22causal}
U(f,x)=\sum_{i=-L,i\ne 0}^{L}a_i(f)U(f,x+i),
\end{equation}
where $a_i(f)=e^{i2\pi fp_i}$. Here, $L$ denotes the order of the causal prediction filter.

\subsection{Non-stationary predictive filtering}
Since the SPF is based on the plane-wave assumption, it is normally combined with a local windowing strategy to best denoise a complicated seismic data. However, there will be many drawbacks using the local windowing strategy, e.g., one needs to consider the window size, the tapering strategy around edges, the parameter inconsistency issue \cite[]{shaohuan2017gji}. The more appropriate way to deal with complicated seismic data is to modify the SPF expression in equation \ref{eq:pref22} in a non-stationary form:
\begin{equation}
\label{eq:ncausal}
U(f,x)=\sum_{i=-L,i\ne 0}^{L}a_i(f,x)U(f,x+i),
\end{equation}
where the auto-regression coefficients $a_i(f,x)$ vary across the $f-x$ domain. The auto-regression formula expressed in equation \ref{eq:ncausal} bypass the need of local windowing since it expresses the auto-regression coefficients, which is related with the slope, in an non-stationary version. However, equation \ref{eq:ncausal} requires solving a highly under-determined inverse problem. Traditionally, the stationary \cite[]{canales1984} or non-stationary auto-regression coefficients \cite[]{guochang2012}, $a_i(f)$ or $a_i(f,x)$, are solved frequency-by-frequency. For example, for the non-stationary auto-regression in equation \ref{eq:ncausal}, $a_i(f,x)$ is obtained by solving the following equation system:
\begin{equation}
\label{eq:sys}
\begin{split}
\hat{a_i}(f_1,x) &= \arg \min_{a_i(f_1,x)} \parallel U(f_1,x)-\sum_{i=-L,i\ne 0}^{L}a_i(f_1,x)U(f_1,x+i) \parallel  \\
\hat{a_i}(f_2,x) &= \arg \min_{a_i(f_2,x)} \parallel U(f_2,x)-\sum_{i=-L,i\ne 0}^{L}a_i(f_2,x)U(f_2,x+i) \parallel  \\
&\vdots\\
\hat{a_i}(f_{N_f},x) &= \arg \min_{a_i(f_{N_f},x)} \parallel U(f_{N_f},x)-\sum_{i=-L,i\ne 0}^{L}a_i(f_{N_f},x)U(f_{N_f},x+i) \parallel.
\end{split}
\end{equation}
Solving equation \ref{eq:sys} is referred to as the regularized non-stationary autoregression \cite[]{guochang2012}. The benefit of solving the non-stationary auto-regression coefficients $a_i(f,x)$ frequency by frequency via equation \ref{eq:sys} is that the computation is easy to parallelized, as introduced in \cite{guochang2012}. However, solving $a_i(f,x)$ frequency by frequency could lose the inherent model constraint along the frequency axis.

Here, we propose to formulate the inverse problem \ref{eq:ncausal} in a more integrated form, where we can understand the nature of this inverse problem more intuitively, thereby applying more physically plausible constraints to the model, i.e., $a_i(f,x)$. To solve equation \ref{eq:ncausal} using the classic inversion theory, we first transform it into a matrix-vector form as follows:
\begin{align}
\label{eq:mv}
\mathbf{u} = \left[\begin{array}{cccc}
\mathbf{u}_{-L} &\mathbf{u}_{-L+1}&\cdots&\mathbf{u}_{L}
\end{array}\right]\left[\begin{array}{c}
\mathbf{a}_{-L}\\
\mathbf{a}_{-L+1}\\
\vdots\\
\mathbf{a}_L
\end{array}\right],
\end{align}
where $\mathbf{u}$ is the vector form of $U(f,x)$, $\mathbf{u}_i$ is the vector form of $U(f,x+i)$, and $\mathbf{a}_i$ is the vector form of $a_i(f,x)$. All $\mathbf{u}$, $\mathbf{u}_i$, and $\mathbf{a}_i$ are vectors of size $N_f\times N_x$. $N_f$ and $N_x$ denote the size in frequency and space dimensions. Equation \ref{eq:mv} can be expressed more briefly as
\begin{equation}
\label{eq:fx}
\mathbf{Fa}=\mathbf{u},
\end{equation}
where
\begin{equation}
\label{eq:fx2}
\mathbf{F}=\left[\begin{array}{cccc}
\mathbf{u}_{-L} &\mathbf{u}_{-L+1}&\cdots&\mathbf{u}_{L}
\end{array}\right] \quad \text{and}\quad \mathbf{a}=\left[\begin{array}{c}
\mathbf{a}_{-L}\\
\mathbf{a}_{-L+1}\\
\vdots\\
\mathbf{a}_L
\end{array}\right].
\end{equation}
In the form of an optimization problem, equation \ref{eq:fx} can be solved via:
\begin{equation}
\label{eq:fx3}
\hat{\mathbf{a}} = \arg\min_{\mathbf{a}} \parallel \mathbf{u}-\mathbf{Fa} \parallel_2^2 + \mathbf{R}(\mathbf{a}),
\end{equation}
where $\mathbf{R}$ denotes a regularization operator.  Equation \ref{eq:fx3} can be solved using standard regularized inversion methods, e.g., Tikhonov regularization \cite[]{tikhonov1963} or shaping regularization \cite[]{fomel2007shape}. Here, we use the shaping regularization method to solve the optimization problem \ref{eq:fx3} via an iterative procedure:
 \begin{equation}
\label{eq:iter}
\mathbf{a}_{m+1} = \mathbf{S}[\mathbf{a}_m + \mathbf{B}^T(\mathbf{u}-\mathbf{Fa}_m)] ,
\end{equation}
where $\mathbf{a}_{m}$ denotes the model after $m$th iteration. $\mathbf{S}$ and $\mathbf{B}$ are called shaping and backward operators, $\mathbf{S}$ is used to apply a priori constraint to the model while  $\mathbf{B}$ provides an approximate inverse of the forward operator $\mathbf{F}$. In the conjugate gradient algorithm (CG) \cite[]{fomel2007shape}, the model update $\mathbf{B}^T(\mathbf{u}-\mathbf{Fa}_m)$ is calculated following the general CG definition. The shaping operator $\mathbf{S}$ is chosen as a multi-dimensional triangle smoothing operator, i.e., smoothing along the space direction (like in \cite{guochang2012}) as well as the frequency direction to ensure the frequency smoothness. The iterative formula \ref{eq:iter} converges to the following solution:
\begin{equation}
\label{eq:fx33}
\hat{\mathbf{a}} = [\lambda^2\mathbf{I} + \mathbf{S}(\mathbf{F}^T\mathbf{F}-\lambda^2\mathbf{I}) ]^{-1}\mathbf{S}\mathbf{F}^T\mathbf{a},
\end{equation}
where $\lambda$ is fixed to be $\parallel\mathbf{F}^T\mathbf{F}\parallel_2$ \cite[]{fomel2007shape}. Because of the convenience offerred by the shaping regularization, it is flexible to apply any physical meaningful constraint to the model, e.g., a frequency-dependent smoothing along the space direction. From equation \ref{eq:fx}, we are aware that the model in the inverse problem corresponds to the non-stationary auto-regression coefficients spreading across the frequency-space domain. It is intuitive that the frequency-space coefficients should be smooth in both frequency and space dimensions, thus we apply the smoothing in both directions. It is also intuitive that the auto-regression coefficients could be more and more oscillating and even unstable when frequency increases, since high-frequency spectrum more corresponds to the noise. To facilitate a stronger anti-noise ability and to ensure the stability when solving high-frequency non-stationary auto-regression coefficients, we propose to apply the frequency-dependent smoothing. For example, we can increase the smoothing radius from a low value around the dominant frequency (e.g., 10 Hz) to a larger value around the Nyquist frequency following a fraction power function:
\begin{align}
\label{eq:fs}
R(f) = \left\{\begin{array}{ll}
R_d, & 0<=f<=f_d \\
R_d+\left(\left(\frac{f-f_d}{f_n-f_d}\right)^{\alpha}R_d-R_n\right),& f_d<f<=f_n
\end{array} \right.
\end{align}
where $R_d$ and $R_n$ are the smoothing radii for dominant ($f_d$) and Nyquist ($f_n$) frequencies, and $\alpha$ is called the fraction parameter ($\alpha=0.5$ in default). To distinguish between the regularized non-stationary auto-regression (RNAR) method and the proposed method (although both are intended to solve the non-stationary auto-regression coefficients), we name the proposed method the non-stationary predictive filtering (NPF) method. We admit that RNAR and NPF are closely related with each other, but with differences in the implementation and model constraint. These differences, however, could result in significant differences in final denoised result, which will be illustrated in the section of EXAMPLES.

\subsection{3D extension of the non-stationary predictive filtering}
The non-stationary AR model can be extended to 3D or even higher dimensions straightforwardly. Considering a 3D seismic data $u(t,x,y)$, first we transform the 3D data volume from $t-x-y$ domain to $f-x-y$ domain, $U(f,x,y)$, then we can express the non-stationary AR model as:
\begin{equation}
\label{eq:ncausal3}
U(f,x,y)=\sum_{iy=-L_y,iy\ne 0}^{L_y}\sum_{ix=-L_x,ix\ne 0}^{L_x}a_{ix,iy}(f,x,y)U(f,x+ix,y+iy),
\end{equation}
where $L_x$ and $L_y$ denote the AR orders in $x$ and $y$ directions, respectively. 
Equation \ref{eq:ncausal3} can be expressed briefly in the form of equation \ref{eq:fx} but with $\mathbf{F}$ and $\mathbf{a}$ denoting slightly different formulas:
\begin{equation}
\label{eq:fx3d}
\mathbf{F}=\left[\begin{array}{cccc}
\tilde{\mathbf{u}}_{-Ly} &\tilde{\mathbf{u}}_{-Ly+1}&\cdots&\tilde{\mathbf{u}}_{Ly}
\end{array}\right] \quad \text{and}\quad \mathbf{a}=\left[\begin{array}{c}
\tilde{\mathbf{a}}_{-L_y}\\
\tilde{\mathbf{a}}_{-L_y+1}\\
\vdots\\
\tilde{\mathbf{a}}_{L_y}
\end{array}\right],
\end{equation}
where
\begin{equation}
\label{eq:fx3d}
\tilde{\mathbf{u}}=\left[\begin{array}{cccc}
\mathbf{u}_{-{L_x}} &\mathbf{u}_{-L_x+1}&\cdots&\mathbf{u}_{L_x}
\end{array}\right] \quad \text{and}\quad \tilde{\mathbf{a}}=\left[\begin{array}{c}
\mathbf{a}_{-L_x}\\
\mathbf{a}_{-L_x+1}\\
\vdots\\
\mathbf{a}_{L_x}
\end{array}\right].
\end{equation}
In 3D case, the size of vector $\mathbf{a}$ is $(L_xL_y-1)N_fN_xN_y$, where $N_x$ and $N_y$ denote the size in the x and y dimensions. Solving the non-stationary AR problem in 3D is the same as the 2D case based on the shaping regularization method expressed in equation \ref{eq:iter}. However, in the 3D case, the multi-dimensional triangle smoothing operator means smoothing in frequency, space X and space Y directions.  The smoothing radius formula expressed in equation \ref{eq:fs} holds for the smoothing radii in both X and Y directions.

\section{Examples}
We use one synthetic and two field data examples to demonstrate the performance of the NPF method, and compare it with the SPF and RNAR methods. For the synthetic example, we use the signal-to-noise ratio (SNR) as the metric to evaluate the denoising performance. The definition of SNR is given as:
\begin{equation}
\label{eq:diff}
SNR=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2^2}{\Arrowvert \hat{\mathbf{s}} -\mathbf{s}\Arrowvert_2^2},
\end{equation}
where $\mathbf{s}$ is the clean signal and $\hat{\mathbf{s}}$ is the noisy/denoised data. In addition, we use local similarity \cite[]{fomel2007localattr,yangkang2015ortho} to evaluate the signal leakage of different denoising methods. For the real data examples, we only use the local similarity to evaluate the signal leakage. The local similarity between the denoised data and removed noise is calculated to indicate which part of the noise section is significantly similar to the same part of the denoised data, i.e., signal leakage.

To ensure all the competing methods to obtain acceptable results, we use the local similarity as a reference to tune the parameters so that each method can obtain the same level of signal preservation (i.e., low signal leakage). Based on the same level of signal leakage, we focus on the comparison of denoised data. The cleaner and smoother seismic data indicate better performance. For those methods that will inevitably cause high signal leakage, we tune the parameters to minimize the leakages as revealed from the local similarity metric.

The synthetic example is plotted in Figure \ref{fig:cmp0,cmp}, with left figure showing the clean data and right showing the noisy data. The SNR of the noisy data is -9.23 dB. Figure \ref{fig:test2,test1,test0,test00} shows the denoised data using different methods. Figure \ref{fig:test2} shows the denoised data using the SPF method. The SPF method uses a causal autoregression filter with two points prediction length for forward and backward prediction. The prediction length for X and Y directions are the same. Figure \ref{fig:test1} shows the result from the RNAR method. Figure \ref{fig:test0} shows the result from the NPF method (with only frequency-direction smoothing but without frequency-dependent smoothing). Figure \ref{fig:test00} plots the result from the NPF method with both frequency-direction smoothing and frequency-dependent space-direction smoothing (NPFFS). For both RNAR and NPF, we use a causal filter with two-points forward and backward prediction in each space direction (X and Y). We use a smoothing radius of three points in frequency for NPF (Figures \ref{fig:test0} and \ref{fig:test00}).  For frequency-dependent smoothing, we increase the smoothing radius from four points around the dominant frequency (e.g., 10 Hz for this example) to 20 points of the Nyquist frequency following a fraction power function (with the power fraction to be 0.5). This frequency smoothing strategy is the default form of the NPF method. Figure \ref{fig:test2dif,test1dif,test0dif,test00dif} shows the removed noise corresponding to the four approaches shown in Figure \ref{fig:test2,test1,test0,test00}.  It is clear that only the SPF method causes obvious signal damages, while all other methods do not leave significant signal energy in the noise. The SNRs of the four methods, namely SPF, RNAR, NPF, NPFFS, are 
2.34 dB, 2.56 dB, 2.93 dB, and 4.80 dB, respectively, indicating a gradually improved performance from the SPF to RNAR and to NPF methods. The frequency-space domain spectra comparison is plotted in Figure \ref{fig:hyper-f,hypern-f,test2-f,test1-f,test0-f,test00-f}. It is clear that the noise level is very high from the noise spectra in Figure \ref{fig:hypern-f}. The SPF method significantly damages the signal spectra, as shown in Figure \ref{fig:test2-f}. The RNAR method obtains a good recovery of the signal spectra. Both NPF methods obtain cleaner spectra than the RNAR method. The NPF with frequency smoothing obtains the cleanest signal spectra.
It is convenient to compare the signal leakage by the local similarity maps, as plotted in Figure \ref{fig:simi2,simi1,simi0,simi00}. The signal leakage of the SPF method is clearly revealed in Figure \ref{fig:simi2} as the high similarity values depict the distribution of the seismic events correctly. Both RNAR and NPFFS methods cause negligible signal leakage, while the NPF (without frequency-dependent smoothing) causes a little stronger signal leakages. However, the large similarity values are mostly spreading those areas lacking signals, indicating that the pure frequency-direction smoothing could cause potential hidden weak artifacts (which is not visible from the data) and further cause the weak artifacts in the noise section. Such hidden artifacts could result in an abnormal local similarity value. However, note that since the overall similarity values of all the methods are very low, e.g., below 0.1, the aforementioned signal leakages for these methods are not significant. A single-trace comparison (20th X-direction trace and 20th Y-direction trace) of this dataset is plotted in Figure \ref{fig:hyper-ss-0,hyper-ss-z}. The top panel shows the comparison in the original scale and the bottom row plots the comparison in the zoomed scale. The zooming area is indicated by the frame box in the top panel. In Figure \ref{fig:hyper-ss-0,hyper-ss-z}, the black line corresponds to the clean data. The green line corresponds to the noisy data. The black line corresponds to the clean data. The pink line corresponds to the SPF method. The red line corresponds to the RNAR method.  The cyan and blue lines correspond to the denoised data using the NPF methods without and with  frequency-dependent smoothing, respectively. It is clear that the SPF deviates from the clean trace most. The RNAR method contains the largest residual noise. Both NPF methods are close to the clean trace but the NPF method with frequency-dependent smoothing is closest to the clean trace.

The first field data example is a 2D seismic section, which has been previously used in \cite{guochang2012}. It is a very complicated seismic profile after time-migration, but is still very noisy, as shown in Figure \ref{fig:real2d-0}. Figure \ref{fig:r2test2-0,r2test1-0,r2test0-0,r2test00-0} plots the comparison of the four methods, i.e., SPF, RNAR, NPF, NPFFS. Comparing all four results with the raw data, it is clear that all these methods obtain significant improvement. The removed noise sections are plotted in Figure \ref{fig:r2test2-n-0,r2test1-n-0,r2test0-n-0,r2test00-n-0}, where the SPF method causes some visible damages in the removed noise and other three methods cause negligible damages. The local similarity comparison is plotted in Figure \ref{fig:r2simi2,r2simi1,r2simi0,r2simi00}, where all the methods cause low local similarity maps. Among them, the SPF, RNAR, and NPF methods have slightly higher local similarity. NPFFS method shows obviously lower similarity values, indicates a better signal preservation because of the frequency-dependent smoothing. For a better comparison of the denoised results, we zoom in an area from each plot in Figures \ref{fig:real2d-0} and \ref{fig:r2test2-0,r2test1-0,r2test0-0,r2test00-0}, and show them in Figure \ref{fig:real2d-z,r2test2-z,r2test1-z,r2test0-z,r2test00-z,r2test00dif-z}. From the zoomed sections, we confirm that the SPF method loses some details, the RNAR method contains more residual noise, the NPF method obtains quite successful denoising performance, while the NPFFS method obtains an even better result than NPF by mitigating more high-frequency noise. The difference between Figures \ref{fig:r2test0-z} and \ref{fig:r2test00-z} is plotted in Figure \ref{fig:r2test00dif-z}, where it shows some removed high-frequency noise due to the frequency-dependent smoothing. We further zoom in a part from the removed noise sections (Figure \ref{fig:r2test2-n-0,r2test1-n-0,r2test0-n-0,r2test00-n-0}) and show them in Figure \ref{fig:r2test2-n-z,r2test1-n-z0,r2test0-n-z,r2test00-n-z}, where we can see more clearly that both SPF and RNAR methods cause some leaked signals and the NPF method does not cause visible signal leakage.

The third example is a 3D field dataset, as plotted in Figure \ref{fig:real}. The denoised data using different methods are plotted in Figure \ref{fig:rtest2,rtest1,rtest0,rtest00}. The SPF and NPF methods seem to obtain smoother results than the RNAR method. The removed noise cubes are plotted in Figure \ref{fig:rtest2-n,rtest1-n,rtest0-n,rtest00-n}. The local similarity cubes are plotted in Figure \ref{fig:rsimi2,rsimi1,rsimi0,rsimi00}, showing the a similar level of signal leakage for all the methods. It is also clear that the RNAR method seems to cause a little more signal leakages than the other methods. Figure \ref{fig:real-z,rtest2-z,rtest1-z,rtest0-z,rtest00-z,rtest00dif-z} shows a zoomed comparison between the raw data and denoised data using different methods. From the zoomed comparison, we conclude that the result from the SPF method is smooth, but contains a little weaker energy. The RNAR method removes less noise. The two NPF approaches obtain smooth results and preserves the details well. The frequency-dependent smoothing can make the denoised result a little smoother by removing more high-frequency noise.

\inputdir{hyper3d}
\multiplot{2}{cmp0,cmp}{width=0.45\textwidth}{Synthetic example. (a) Clean data. (b) Noisy data (SNR=-9.23 dB).}

\multiplot{4}{test2,test1,test0,test00}{width=0.45\textwidth}{Denoised data using (a) stationary predictive filtering (SNR=2.34 dB), (b) regularized non-stationary auto-regression (SNR=2.56 dB), (c) non-stationary predictive filtering without frequency-dependent smoothing (SNR=2.93 dB), and (d) non-stationary predictive filtering with frequency-dependent smoothing (SNR=4.80 dB).}
\multiplot{4}{test2dif,test1dif,test0dif,test00dif}{width=0.45\textwidth}{Removed noise using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering without frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-dependent smoothing.}

\multiplot{6}{hyper-f,hypern-f,test2-f,test1-f,test0-f,test00-f}{width=0.3\textwidth}{FX spectra of (a) clean data, (b) noisy data, (c) denoised data using stationary predictive filtering, (d) denoised data using regularized non-stationary auto-regression, (e) non-stationary predictive filtering without frequency-dependent smoothing, and (f) non-stationary predictive filtering with frequency-dependent smoothing.}

\multiplot{4}{simi2,simi1,simi0,simi00}{width=0.45\textwidth}{Local similarity (between denoised data and removed noise) using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering without frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-dependent smoothing.}

\multiplot{2}{hyper-ss-0,hyper-ss-z}{width=0.8\textwidth}{Single-trace comparison (20th X-direction trace and 20th Y-direction trace). (a) Comparison in the original scale. (b) Comparison in the zoomed scale. The zooming area is highlighted by the black frame box in (a). The green line corresponds to the noisy data. The black line corresponds to the clean data. The pink line corresponds to the SPF method. The red line corresponds to the RNAR method.  The cyan and blue lines correspond to the denoised data using the NPF methods without and with  frequency-dependent smoothing, respectively. }

\inputdir{real2d_win}
\plot{real2d-0}{width=0.8\textwidth}{Real 2D seismic profile.}

\multiplot{4}{r2test2-0,r2test1-0,r2test0-0,r2test00-0}{width=0.4\textwidth}{Denoised data using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering without frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-dependent smoothing.}
\multiplot{4}{r2test2-n-0,r2test1-n-0,r2test0-n-0,r2test00-n-0}{width=0.4\textwidth}{Removed noise using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering without frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-dependent smoothing.}

\multiplot{4}{r2simi2,r2simi1,r2simi0,r2simi00}{width=0.4\textwidth}{Local similarity (between denoised data and removed noise) using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering without frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-dependent smoothing.}

\multiplot{6}{real2d-z,r2test2-z,r2test1-z,r2test0-z,r2test00-z,r2test00dif-z}{width=0.4\textwidth}{Zoomed comparison of denoised data using (a) raw data, (b) stationary predictive filtering, (c) regularized non-stationary auto-regression, (d) non-stationary predictive filtering without frequency-dependent smoothing, and (e) non-stationary predictive filtering with frequency-dependent smoothing. (f) Difference between (d) and (e). Note that the frequency-dependent smoothing (e) has removed more high-frequency noise compared with (d).}

\multiplot{4}{r2test2-n-z,r2test1-n-z0,r2test0-n-z,r2test00-n-z}{width=0.4\textwidth}{Zoomed comparison of removed noise using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering without frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-dependent smoothing. Note the obvious signal leakages in (a) and (b). }

\inputdir{real}
\plot{real}{width=0.8\textwidth}{3D field data example. }

\multiplot{4}{rtest2,rtest1,rtest0,rtest00}{width=0.4\textwidth}{Denoised data using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering without frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-dependent smoothing.}
\multiplot{4}{rtest2-n,rtest1-n,rtest0-n,rtest00-n}{width=0.4\textwidth}{Removed noise using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering without frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-dependent smoothing.}

\multiplot{4}{rsimi2,rsimi1,rsimi0,rsimi00}{width=0.4\textwidth}{Local similarity (between denoised data and removed noise) using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering without frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-dependent smoothing.}

\multiplot{6}{real-z,rtest2-z,rtest1-z,rtest0-z,rtest00-z,rtest00dif-z}{width=0.4\textwidth}{Zoomed comparison of denoised data using (a) raw data, (b) stationary predictive filtering, (c) regularized non-stationary auto-regression, (d) non-stationary predictive filtering without frequency-dependent smoothing, and (e) non-stationary predictive filtering with frequency-dependent smoothing. (f) Difference between (d) and (e). Note that the frequency-dependent smoothing (e) has removed more high-frequency noise compared with (d).}

%\section{Discussions}
\section{Conclusions}
The traditional predictive filter is not able to characterize the non-stationarity of seismic data along the space dimension. 
The RNAR method calculates the space-variable predictive filter coefficients by solving an inverse problem with spatial smoothness constrained shaping regularization. By formulating the non-stationary filter coefficients in all frequency bands into the same inverse problem, we can solve 
a non-stationary predictive filter that is constrained in both space and frequency dimensions. The new non-stationary predictive filtering method is more competent in denoising very noisy seismic data with more robust performance. In addition, the frequency-dependent smoothing method helps the non-stationary predictive filtering method to attenuate more random noise in moderate to high-frequency bands. The proposed method is easily applied to 2D/3D/4D applications with effective performance. Several synthetic and field data examples demonstrate the appealing performance.

\section{DATA AND MATERIALS AVAILABILITY}
All datasets and source codes associated with this research will be made available online (www.ahay.org) in the format of reproducible research \cite[]{mada2013}.

%\section{Acknowledgements}

%\inputdir{test}
%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
%\multiplot{2}{test1,test2}{width=0.45\textwidth}{(a) Caption a. (b) Caption b.}

\bibliographystyle{seg}
\bibliography{fxy}

%\AtEndDocument{}

%\newpage
%\listoffigures

%\begin{figure}[htb!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
%	\caption{Caption.}
%	\label{fig:fig}
%\end{figure}

%\begin{figure}[htb!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
%    \label{fig:fig1}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
%    \label{fig:fig2}}\\
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure}

%\begin{figure*}[ht!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
%    \label{fig:fig1}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
%    \label{fig:fig2}}\\
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure*}

%\begin{table}[h]
%\caption{Table caption}
%\begin{center}
%     \begin{tabular}{|c|c|c|c|c|c|} 
%	  \hline Column1 (unit)  & Column2 (unit) & Column3 (unit) \\ 
%	  \hline 1 & 2  & 3 \\
%       \hline
%    \end{tabular} 
%\end{center}
%\label{tbl:table1}
%\end{table}

### 2021-01-29 fxy/paper.tex
2021年 1月29日 星期五 00时15分44秒 CST

\title{Non-stationary predictive filtering for seismic random noise suppression - A tutorial}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Hang Wang\footnotemark[1], Wei Chen\footnotemark[2], Weilin Huang\footnotemark[3], Shaohuan Zu\footnotemark[4], Xingye Liu\footnotemark[5], Liuqing Yang\footnotemark[3] and Yangkang Chen\footnotemark[1]}
\ms{GEO-2021} %\ms{GJI-2019}

\address{
\footnotemark[1]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
18328504171@163.com \& chenyk2016@gmail.com \\
\footnotemark[2] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
Yangtze University\\
Daxue Road No.111\\
Caidian District\\
Wuhan, China, 430100\\
chenwei2014@yangtzeu.edu.cn\& yangliuqingqin@163.com\\
\footnotemark[3] State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200\\
cup\_hwl@126.com \\
\footnotemark[4] College of Geophysics\\
Chengdu University of Technology \\
Dongsanlu, Erxianqiao, Chengdu 610059, Sichuan, China \\
zushaohuan@qq.com\\
\footnotemark[5] College of Geology and Environment\\
Xi’an University of Science and Technology\\
Xi’an, Shaanxi Province, China, 710054 \\
lwxwyh506673@126.com\\
Corresponding author: Yangkang Chen, chenyk2016@gmail.com
}

\righthead{Non-stationary predictive filtering}

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}

\begin{abstract}
Predictive filtering in the frequency domain is one of the most widely used denoising algorithms in  seismic data processing. Predictive filtering is based on the assumption of linear or planar events in the time-space domain. In traditional predictive filtering methods, a predictive filter is fixed across the spatial dimension, which cannot deal with spatial variations in seismic data well. To handle the curved events, the predictive filter is either applied in local windows or extended into a non-stationary version. The regularized non-stationary autoregression (RNAR) method can be treated as a non-stationary extension of the traditional predictive filtering, where the predictive filter coefficients are variable between different spatial locations. This highly under-determined inverse problem is solved by shaping regularization with a smoothness constraint in space. We further extend the RNAR method to the more general case, where we can apply more constraints to the filter coefficients according to the features of seismic data. First, apart from the smoothness in space, we also apply a smoothing constraint in frequency, considering the coherency of the coefficients in the frequency dimension. 
Second, we apply a frequency-dependent smoothing radius in the spatial dimension to better take advantage of the non-stationarity of seismic data in the frequency axis and to better deal with noise. \new{Effectiveness of the}\old{The} proposed method is validated via several synthetic and field data examples.
\end{abstract}

\maketitle

\section{Introduction}
Removing spatially incoherent noise from seismic data is an important task in reflection seismology. \old{The noise}\new{Noise} suppression is either applied in pre-stack seismic data for improving the velocity analysis and seismic migration to obtain a better seismic image or applied in post-stack seismic images or attribute maps to facilitate a more reliable seismic interpretation. Therefore, the noise suppression performance affects most steps in the seismic processing, imaging, and interpretation chain \cite[]{yangkang20142,chenwei2018,liu2019seismic,shucai2020,chenwei2020,omar2020geo1}. Due to the complexity of seismic data, \old{however,}\new{though} simple assumptions that are required in most denoising algorithms are not always valid. For these reasons, many denoising algorithms based on different assumptions \dlo{are}\wen{have been} developed during the past decades.

\dlo{Those}\wen{Two} widely used denoising approaches are the prediction-based methods \cite[]{canales1984}, either in $t-x-y$ domain \cite[]{abma1995} or $f-x-y$ domain \cite[]{guochang2012,guochang2013}, which assume that seismic data are spatially predictable, and thus a prediction filter can be designed to predict the useful signals. Sparsity based methods first transform the seismic data to a sparsity-promoting domain, where the useful signals and noise can be separated. The performance of the transform methods depends on the sparsity that is closely related to the amplitude\wen{/location} difference between signal and noise in the transform domain \cite[]{amir2017,amir2017geo}. Thus, researchers \old{were seeking}\new{seek} the \dlo{sparest}\wen{sparsest} transform for seismic data, among these being the curvelet \old{transform }\cite[]{neelamani2008}, the wavelet \old{transform }\cite[]{mostafa2016geo,liuwei2016ewt}, and the seislet \old{transform }\cite[]{fomel2010seislet,shuwei20163} \new{transforms}. The rank-reduction methods emerged in the past decade because of their \dlo{decent}\wen{good} performance in dealing with complex seismic data \cite[]{mssa,weilin2016dmssa,yangkang2016irr5d,yangkang2019nc,wang2020low}. Seismic data are first transformed to a low-rank space, and then the principal components are extracted to obtain the useful seismic signals. However, these methods suffer from the intense computation required by the singular value decomposition (SVD) operations. Decomposition-based methods divide the seismic data into several components, where the useful signals can be obtained by \dlo{recombine}\wen{recombining} these components either by frequency or morphological differences \cite[]{huijian20161,weilin2020gji}. Because of the complexity of seismic data, one or more methods are sometimes combined to output a better performance than an individual method \cite[]{yangkang20141}.

While many denoising algorithms have been developed by researchers, the most widely accepted methods in the industry are still the prediction filter-based methods. Because of the efficiency and the stable performance (although these may not be optimal), processing seismologists prefer to improve the traditional prediction filtering by simple and efficient strategies, with the purpose of maintaining the efficiency advantages while improving the existing performance, rather than \old{utilizing}\new{using} more complicated and time-consuming denoising methods. \cite{canales1984} presents the classic prediction filter that uses a frequency-domain Wiener filter, referred to as the f-x predictive filtering method. The predictive filter was then introduced by \cite{gulunay1986fxdecon} and was referred to as the famous \dlo{FXDECON}\wen{f-x decon} algorithm. Since then, a variety of variants have been proposed to improve the classic implementation of the predictive filter. \cite{fxydecon} proposes the non-causal prediction filter to better utilize the constraints from both forward and backward prediction and applied it to 3D random noise suppression. \cite{naghizadeh2009f} develop an adaptive predictive filter to handle the multi-dip problem in complex seismic data without the need \dlo{of}\wen{for} local windowing and applied it to the seismic interpolation problem.  \cite{guochang2012} develop a regularized non-stationary autoregression (RNAR) method to \old{deal with}\new{handle} the spatial curvature and the non-stationarity of seismic data. The RNAR method formulates the predictive filter as an auto-regression problem and extends the autoregression to each non-stationary version. \cite{guochang2013} \old{further applied}\new{apply} the RNAR method to 3D problems.  \cite{fx2017} discusses the signal leakage issues in various implementations of the f-x deconvolution algorithms based on the open-source Teapot domain dataset. \old{Recently,} \cite{fuchao2020} develop a structurally guided predictive filter to handle the non-stationarity of seismic data by squeezing and \dlo{shrink}\wen{shrinking} the length of prediction filter according to the structural complexity.

In this paper, we further extend the RNAR approach to a more integrated framework, where we deal with the spatial non-stationarity of seismic data by extending the stationary autoregression to non-stationary autoregression, taking advantage of the temporal coherency, i.e., the narrow-band and smooth spectrum, by smoothing the autoregression coefficients in frequency and applying frequency-dependent smoothing to the coefficients in space.  To distinguish our approach from the RNAR method, we refer to the proposed method as the non-stationary predictive filtering (NPF) method. Compared with the stationary predictive filtering (PF) \cite[]{canales1984}, there are two \dlo{meanings of}\wen{steps to handling} the non-stationarity we refer to here. First, we synthesize the non-stationary data by the regularized non-stationary autoregression. Second, we deal with the non-stationary model (the frequency-dependent non-stationary autoregression coefficients) by applying a non-stationary model constraint, e.g., frequency-dependent spatial smoothing. We organize the paper as follows: we first introduce the fundamentals of the stationary predictive filtering (SPF) and NPF, with the focus on the new constraints we have applied compared with the RNAR method. Then, we use several 2D/3D synthetic and real data examples to demonstrate the better denoising performance of the proposed NPF method. 
\section{Theory}
\subsection{Stationary predictive filtering}
The stationary predictive filtering (SPF) is based on a plane-wave assumption. Let us first consider the plane-wave equation as follows \cite[]{fomel2002pwd}:
\begin{equation}
\label{eq:plane}
p \frac{\partial u}{\partial t} + \frac{\partial u}{\partial x} = 0,
\end{equation}
where $p$ denotes the slope, and $u(t,x)$ denotes the wavefield at time $t$ and space $x$. The plane-wave equation has the following analytical solution:
\begin{equation}
\label{eq:pre}
u(t,x)=g(t-px),
\end{equation}
where $g(t)$ denotes the wavelet.  When taken into the frequency domain one obtains
\begin{equation}
\label{eq:pref}
U(f,x)=G(f)e^{i2\pi fpx},
\end{equation}
where $U(f,x)$ and $G(f)$ denote the frequency-domain spectra of wavefield and wavelet. From equation \ref{eq:pref}, it can be shown that
\begin{equation}
\label{eq:pref2}
U(f,x+1)=e^{i2\pi fp}U(f,x).
\end{equation}
When several plane waves exist, 
\begin{equation}
\label{eq:pref22}
U(f,x+1)=e^{i2\pi fp_1}U(f,x)+e^{i2\pi fp_2}U(f,x-1)+e^{i2\pi fp_3}U(f,x-2)+\cdots+e^{i2\pi fp_{L}}U(f,x-L+1),
\end{equation}
which can be considered as an auto-regression (AR) model of order $L$ \cite[]{tufts1980,canales1984,yangkang20141}. The AR model expressed in equation \ref{eq:pref22} is known as the f-x predictive filtering based on the forward prediction. The AR model can also be formulated as a \dlo{causal}\wen{non-causal} prediction filter
\begin{equation}
\label{eq:pref22causal}
U(f,x)=\sum_{i=-L,i\ne 0}^{L}a_i(f)U(f,x+i),
\end{equation}
where $a_i(f)=e^{i2\pi fp_i}$ and $L$ denotes the order of the \dlo{causal}\wen{non-causal} prediction filter.

\subsection{Non-stationary predictive filtering}
Since the SPF is based on the plane-wave assumption, it is normally combined with a local windowing strategy to best denoise complicated seismic data. However, there are many drawbacks to using the local windowing strategy, e.g., one needs to consider the window size, the tapering strategy around edges, and the parameter inconsistency issue \cite[]{shaohuan2017gji}. A more appropriate way to deal with complicated seismic data is to modify the SPF expression in equation \ref{eq:pref22} in a non-stationary form:
\begin{equation}
\label{eq:ncausal}
U(f,x)=\sum_{i=-L,i\ne 0}^{L}a_i(f,x)U(f,x+i),
\end{equation}
where the auto-regression coefficients $a_i(f,x)$ vary across the f-x domain. The auto-regression formula expressed in equation \ref{eq:ncausal} \dlo{bypass}\wen{bypasses} the need \dlo{of}\wen{for} local windowing since it expresses the auto-regression coefficients, which \dlo{is}\wen{are} related with the slope, in a non-stationary version. However, equation \ref{eq:ncausal} requires solving a highly under-determined inverse problem. Traditionally, the stationary \cite[]{canales1984} or non-stationary auto-regression coefficients \cite[]{guochang2012}, $a_i(f)$ or $a_i(f,x)$, are solved frequency-by-frequency. For example, for the non-stationary auto-regression in equation \ref{eq:ncausal}, $a_i(f,x)$ is obtained by solving the following system of equations:
\begin{equation}
\label{eq:sys}
\begin{split}
\hat{a_i}(f_1,x) &= \arg \min_{a_i(f_1,x)} \parallel U(f_1,x)-\sum_{i=-L,i\ne 0}^{L}a_i(f_1,x)U(f_1,x+i) \parallel  \\
\hat{a_i}(f_2,x) &= \arg \min_{a_i(f_2,x)} \parallel U(f_2,x)-\sum_{i=-L,i\ne 0}^{L}a_i(f_2,x)U(f_2,x+i) \parallel  \\
&\vdots\\
\hat{a_i}(f_{N_f},x) &= \arg \min_{a_i(f_{N_f},x)} \parallel U(f_{N_f},x)-\sum_{i=-L,i\ne 0}^{L}a_i(f_{N_f},x)U(f_{N_f},x+i) \parallel.
\end{split}
\end{equation}
Solving equation \ref{eq:sys} is referred to as the regularized non-stationary autoregression \cite[]{guochang2012}. The benefit of solving the non-stationary auto-regression coefficients $a_i(f,x)$ 
frequency-by-frequency via equation \ref{eq:sys} is that the computation is easy to \wen{be} parallelized, as introduced in \cite{guochang2012}. However, solving $a_i(f,x)$ frequency-by-frequency could lose the inherent model constraint along the frequency axis.

Here, we propose formulating the inverse problem \wen{described by equation} \ref{eq:ncausal} in a more integrated form where we can understand the nature of this inverse problem more intuitively, thereby applying more physically plausible constraints to the model, i.e., $a_i(f,x)$. To solve equation \ref{eq:ncausal} using the classic inversion theory, we first transform it into a matrix-vector form as follows:
\begin{align}
\label{eq:mv}
\mathbf{u} = \left[\begin{array}{cccc}
\mathbf{U}_{-L} &\mathbf{U}_{-L+1}&\cdots&\mathbf{U}_{L}
\end{array}\right]\left[\begin{array}{c}
\mathbf{a}_{-L}\\
\mathbf{a}_{-L+1}\\
\vdots\\
\mathbf{a}_L
\end{array}\right],
\end{align}
where $\mathbf{u}$ is the vector form of $U(f,x)$, $\mathbf{U}_i$ is the diagonal matrix constructed from the vector $\mathbf{u}_i$ that corresponds to $U(f,x+i)$, and $\mathbf{a}_i$ is the vector form of $a_i(f,x)$. \wen{$\mathbf{u}_i$ is a spatially shifted version of $\mathbf{u}$ with a shifting size of $i$.} All $\mathbf{u}$, $\mathbf{u}_i$, and $\mathbf{a}_i$ are vectors of size $N_f\times N_x$. $N_f$ and $N_x$ denote the size in frequency and space dimensions. Equation \ref{eq:mv} can be expressed more compactly as:
\begin{equation}
\label{eq:fx}
\mathbf{Fa}=\mathbf{u},
\end{equation}
where
\begin{equation}
\label{eq:fx2}
\mathbf{F}=\left[\begin{array}{cccc}
\mathbf{U}_{-L} &\mathbf{U}_{-L+1}&\cdots&\mathbf{U}_{L}
\end{array}\right] \quad \text{and}\quad \mathbf{a}=\left[\begin{array}{c}
\mathbf{a}_{-L}\\
\mathbf{a}_{-L+1}\\
\vdots\\
\mathbf{a}_L
\end{array}\right].
\end{equation}
As an optimization problem, equation \ref{eq:fx} can be solved via:
\begin{equation}
\label{eq:fx3}
\hat{\mathbf{a}} = \arg\min_{\mathbf{a}} \parallel \mathbf{u}-\mathbf{Fa} \parallel_2^2 + \mathbf{R}(\mathbf{a}),
\end{equation}
where $\mathbf{R}$ denotes a regularization operator. Equation \ref{eq:fx3} can be solved using standard regularized inversion methods, e.g., \cite{tikhonov1963} or shaping \cite[]{fomel2007shape} regularization. Here, we use the shaping regularization method to solve the optimization problem in equation \ref{eq:fx3} via an iterative procedure:
 \begin{equation}
\label{eq:iter}
\mathbf{a}_{m+1} = \mathbf{S}[\mathbf{a}_m + \mathbf{B}^T(\mathbf{u}-\mathbf{Fa}_m)] ,
\end{equation}
where $\mathbf{a}_{m}$ denotes the model after $m$th iteration. $\mathbf{S}$ and $\mathbf{B}$ are called shaping and backward operators, $\mathbf{S}$ is used to apply a priori constraint to the model while  $\mathbf{B}$ provides an approximate inverse of the forward operator $\mathbf{F}$. In the conjugate gradient algorithm (CG) \cite[]{fomel2007shape}, model update $\mathbf{B}^T(\mathbf{u}-\mathbf{Fa}_m)$ is calculated following the general CG definition. The shaping operator $\mathbf{S}$ is chosen as a multi-dimensional triangle smoothing operator, i.e., smoothing along the space direction (as in \cite{guochang2012}) as well as the frequency direction to ensure the frequency smoothness. The iterative formula \wen{described by equation} \ref{eq:iter} converges to the following solution:
\begin{equation}
\label{eq:fx33}
\hat{\mathbf{a}} = [\lambda^2\mathbf{I} + \mathbf{S}(\mathbf{F}^T\mathbf{F}-\lambda^2\mathbf{I}) ]^{-1}\mathbf{S}\mathbf{F}^T\mathbf{a},
\end{equation}
where $\lambda$ is fixed to be $\parallel\mathbf{F}^T\mathbf{F}\parallel_2$ \cite[]{fomel2007shape}. Because of the convenience offered by the shaping regularization, it is useful to apply physically meaningful constraints to the model, e.g., a frequency-dependent smoothing along the space direction. From equation \ref{eq:fx}, we are aware that the model in the inverse problem corresponds to the non-stationary auto-regression coefficients spread across the frequency-space domain. It is intuitive that the frequency-space coefficients should be smooth in both \wen{the} frequency and space dimensions; thus, we apply the smoothing in both directions. It is also intuitive that the auto-regression coefficients could show even more oscillation and even become unstable when the frequency increases, since high-frequency spectrum corresponds more to the noise. To facilitate a stronger anti-noise ability and to ensure the stability when solving high-frequency non-stationary auto-regression coefficients, we propose applying a frequency-dependent smoothing. For example, we can increase the smoothing radius from a low value around the dominant frequency (e.g., 10 Hz) to a larger value around the Nyquist frequency following a fraction power function:
\begin{align}
\label{eq:fs}
R(f) = \left\{\begin{array}{ll}
R_d, & 0<=f<=f_d \\
R_d+\left(\frac{f-f_d}{f_n-f_d}\right)^{\alpha}\left(R_n-R_d\right),& f_d<f<=f_n
\end{array} \right.
\end{align}
where $R_d$ and $R_n$ are the smoothing radii for dominant ($f_d$) and Nyquist ($f_n$) frequencies, and $\alpha$ is called the fraction parameter ($\alpha=0.5$ in default). \new{We normally choose an $\alpha<1$ because we want the increase of the smoothing radius be fast in the beginning and slow in the end. It corresponds to the fact that the useful signals become less dominant for the high-frequency band.} To distinguish between the regularized non-stationary auto-regression (RNAR) method and the proposed method (although both are intended to solve the non-stationary auto-regression coefficients), we refer to the proposed method as the non-stationary predictive filtering (NPF) method. We admit that RNAR and NPF are closely related with each other, but they have differences in the implementation and model constraint. These differences, however, could result in significant differences in the final denoised results, as will be illustrated in the \dlo{section of EXAMPLES}\wen{Examples section}.

\subsection{3D extension of the non-stationary predictive filtering}
The non-stationary AR model can be extended to 3D or even higher dimensions in a straightforward manner. Considering a 3D seismic dataset $u(t,x,y)$, we first transform the 3D data volume from the $t-x-y$ domain to the $f-x-y$ domain, $U(f,x,y)$, where we can then express the non-stationary AR model as:
\begin{equation}
\label{eq:ncausal3}
U(f,x,y)=\sum_{iy=-L_y,iy\ne 0}^{L_y}\sum_{ix=-L_x,ix\ne 0}^{L_x}a_{ix,iy}(f,x,y)U(f,x+ix,y+iy),
\end{equation}
where $L_x$ and $L_y$ denote the AR orders in the $x$ and $y$ directions, respectively. 
Equation \ref{eq:ncausal3} can be expressed compactly in the form of equation \ref{eq:fx}, but with $\mathbf{F}$ and $\mathbf{a}$ denoting slightly different formulas:
\begin{equation}
\label{eq:fx3d}
\mathbf{F}=\left[\begin{array}{cccc}
\tilde{\mathbf{U}}_{-Ly} &\tilde{\mathbf{U}}_{-Ly+1}&\cdots&\tilde{\mathbf{U}}_{Ly}
\end{array}\right] \quad \text{and}\quad \mathbf{a}=\left[\begin{array}{c}
\tilde{\mathbf{a}}_{-L_y}\\
\tilde{\mathbf{a}}_{-L_y+1}\\
\vdots\\
\tilde{\mathbf{a}}_{L_y}
\end{array}\right],
\end{equation}
where
\begin{equation}
\label{eq:fx3d2}
\tilde{\mathbf{U}}_{iy}=\left[\begin{array}{cccc}
\mathbf{U}_{-{L_x},iy} &\mathbf{U}_{-L_x+1,iy}&\cdots&\mathbf{U}_{L_x,iy}
\end{array}\right] \quad \text{and}\quad \tilde{\mathbf{a}}_{iy}=\left[\begin{array}{c}
\mathbf{a}_{-L_x,iy}\\
\mathbf{a}_{-L_x+1,iy}\\
\vdots\\
\mathbf{a}_{L_x,iy}
\end{array}\right].
\end{equation}
In equation \ref{eq:fx3d2}, $\mathbf{U}_{ix,iy}$ denotes the diagonal matrix constructed from $U(f,x+ix,y+iy)$. $\mathbf{a}_{ix,iy}$ denotes the vector constructed from $a_{ix,iy}(f,x,y)$. In the 3D case, the size of vector $\mathbf{a}_{ix,iy}$ is $N_fN_xN_y$, where $N_x$ and $N_y$ denote the size in the x and y dimensions. Solving the non-stationary AR problem in 3D is the same as the 2D case based on the shaping regularization method expressed in equation \ref{eq:iter}. However, in the 3D case the multi-dimensional triangle smoothing operator means smoothing in frequency, and \old{space x and space y}\new{the spatial x and y} directions.  The smoothing radius formula expressed in equation \ref{eq:fs} holds for the smoothing radii in both x and y directions. \wen{Based on the same framework, the NPF method is also extendable to 4D and 5D datasets, e.g., seismic data that depends on the temporal dimension and three or four spatial dimensions.} \wen{As indicated by equations \ref{eq:pref22causal} and \ref{eq:ncausal}, both the SPF and NPF methods require a selection of $L$, the filter length. In addition, the NPF method requires a selection of the smoothing radii in both the space ($R_x$ and $R_y$) and frequency ($R_f$) directions. When the frequency-dependent smoothing is applied, the two smoothing radii $R_d$ and $R_n$ (shown in equation \ref{eq:fs}) need to be defined. The computational complexity of SPF and RNAR are both $O(LN_xN_yN_fN_{iter})$. The extra computational cost of NPF is simply caused by the multi-dimensional smoothing, i.e., $O(N_fN_xN_y)$.  }

\section{Examples}
We use one synthetic and two field data examples to demonstrate the performance of the NPF method and compare it to the SPF and RNAR methods. For the synthetic example, we use the signal-to-noise ratio (SNR) as the metric \old{to evaluate}\new{for evaluating} the denoising performance. The definition of SNR is given as
\begin{equation}
\label{eq:diff}
SNR=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2^2}{\Arrowvert \hat{\mathbf{s}} -\mathbf{s}\Arrowvert_2^2},
\end{equation}
where $\mathbf{s}$ is the clean signal and $\hat{\mathbf{s}}$ is the denoised data with residual noise. In addition, we use local similarity \cite[]{fomel2007localattr,yangkang2015ortho} to evaluate the signal leakage of different denoising methods. For the real data examples, we only use the local similarity to evaluate the signal leakage. The local similarity between the denoised data and noise removed is calculated to indicate which part of the noise section is significantly similar to the same part of the denoised data, i.e., signal leakage.

To ensure that all the competing methods obtain acceptable results, we use the local similarity as a reference to tune the parameters so that each method can obtain the same level of signal preservation (i.e., low signal leakage). Based on the same level of signal leakage, we focus on the comparisons of denoised data. Cleaner and smoother seismic data indicate better performance. For those methods that will inevitably cause high signal leakage, we tune the parameters to minimize the leakage as revealed from the local similarity metric. \new{Although the proposed method does not require the windowing strategy to make the results to be acceptable, it usually achieves better performance when applied windows. Thus, all the field data examples (both 2D and 3D) in this paper are all based on the windowed implementation. }

Figures \ref{fig:cmp0} and \ref{fig:cmp} show the clean and noisy data from the synthetic model. The SNR of the noisy data is -9.23 dB. Figure \ref{fig:test2,test1,test0,test00} shows the denoised data using varioius methods. Figure \ref{fig:test2} shows the denoised data using the SPF method. The SPF method uses a \dlo{causal}\wen{non-causal} autoregression filter with a two point prediction length for the forward and backward prediction. The prediction length for the x and y directions are the same. Figure \ref{fig:test1} shows the result from the RNAR method. Figure \ref{fig:test0} shows the result from the NPF method (with only frequency-direction smoothing, but without frequency-dependent spatial smoothing). Figure \ref{fig:test00} plots the result from the NPF method with both frequency-direction smoothing and frequency-dependent space-direction smoothing (NPFFS). For both RNAR and NPF, we use a \dlo{causal}\wen{non-causal} filter with two-point forward and backward predictions in each spatial direction (x and y). We use a smoothing radius of three points in frequency for the NPF method (Figures \ref{fig:test0} and \ref{fig:test00}).  For frequency-dependent smoothing, we increase the smoothing radius from four points around the dominant frequency (e.g., 10 Hz for this example) to 20 points at the Nyquist frequency, following the fraction power function (with a power fraction of 0.5). This frequency-smoothing strategy is the default form for the NPF method. Figure \ref{fig:test2dif,test1dif,test0dif,test00dif} shows the removed noise corresponding to the four approaches shown in Figure \ref{fig:test2,test1,test0,test00}.  It is clear that only the SPF method causes obvious signal damage, while all the other methods do not leave significant signal energy in the noise. The SNRs of the four methods, namely SPF, RNAR, NPF, NPFFS, are 
2.34 dB, 2.56 dB, 2.93 dB, and 4.80 dB, respectively, indicating a gradually improved performance from the SPF to RNAR and to NPF methods. \new{The root-mean-squares (RMS) of the clean data, noisy data, denoised data using the SPF, RNAR, NPF, and NPFFS methods is 0.023, 0.071, 0.016, 0.027, 0.026, 0.023, respectively.} The frequency-space domain spectra comparison is plotted in Figure \ref{fig:hyper-f,hypern-f,test2-f,test1-f,test0-f,test00-f}. It is clear that the noise level is \dlo{very }high for the noise spectra in Figure \ref{fig:hypern-f}. The SPF method significantly damages the signal spectra, as shown in Figure \ref{fig:test2-f}. The RNAR method obtains a good recovery of the signal spectra. Both NPF methods obtain cleaner spectra than the RNAR method. The NPF method with frequency smoothing obtains the cleanest signal spectra.

It is convenient to compare the signal leakage by the local similarity maps, as plotted in Figure \ref{fig:simi2,simi1,simi0,simi00}. The signal leakage of the SPF method is clearly revealed in Figure \ref{fig:simi2}, where the high similarity values depict the distribution of the seismic events correctly. The RNAR and NPFFS methods cause negligible signal leakage, while the NPF (without frequency-dependent smoothing) allows a little stronger signal leakages. 
\dlo{However, the large similarity values are mostly spreading those areas lacking signals, indicating that the pure frequency-direction smoothing could cause potential hidden weak artifacts (which is not visible from the data) and further cause the weak artifacts in the noise section.}
\wen{The large similarity values indicate that applying the frequency-direction smoothing only could cause potential weak artifacts (which are not visible from the data) and further cause the weak artifacts in the noise section.} Such \dlo{hidden}\wen{weak} artifacts could result in an abnormal local similarity value. However, because the overall similarity values of all the methods are very low, e.g., below 0.1, the aforementioned signal leakage for these methods is not significant.

A single-trace comparison (the 20th x-direction trace and the 20th y-direction trace) of this dataset is plotted in Figure \ref{fig:hyper-ss-0,hyper-ss-z-0}. Figures \ref{fig:hyper-ss-0} and \ref{fig:hyper-ss-z-0} show the single-trace comparison and a zoomed version, respectively. The zoomed area is indicated by the box in Figure \ref{fig:hyper-ss-0}. In Figure \ref{fig:hyper-ss-0,hyper-ss-z-0}, the black line corresponds to the clean data. The green line corresponds to the noisy data. The pink line corresponds to the SPF method. The red line corresponds to the RNAR method.  The cyan and blue lines correspond to the denoised data using the NPF methods without and with  the frequency-dependent smoothing, respectively. It is clear that the SPF result deviates from the signal in the clean trace the most. The RNAR method contains the largest residual noise. Both NPF methods are close to the clean trace but the NPF method with frequency-dependent smoothing is closest to the clean trace.
%
%
%\textbf{You might consider plotting only the zoomed results in the squares in Figures 7, 8, 9, and 10.  Seeing differences is very difficult at the present scale, and these plots seem unnecessary.}

The first field data example is a 2D seismic section. It is a complicated seismic profile with time-migration applied, but it is still very noisy (see Figure \ref{fig:real2d-0}). To better compare the denoised results, Figure \ref{fig:real2d-z0,r2test2-z0,r2test1-z0,r2test0-z0,r2test00-z0,r2test00dif-z0} presents a zoomed area from each plot in Figure \ref{fig:real2d-0} and \wen{all denoised data}. From the zoomed sections, we confirm that the SPF method loses some details, the RNAR method contains more residual noise, the NPF method obtains quite successful denoising performance, while the NPFFS method obtains an even better result than NPF by mitigating more high-frequency noise. The difference between Figures \ref{fig:r2test0-z0} and \ref{fig:r2test00-z0} is plotted in Figure \ref{fig:r2test00dif-z0}, illustrates some of the removed high-frequency noise due to the frequency-dependent smoothing. We also zoom into a part of the sections showing the noise removed and show them in Figure \ref{fig:r2test2-n-z,r2test1-n-z0,r2test0-n-z,r2test00-n-z}, where we can more clearly see that both SPF and RNAR methods cause some leaked signals and the NPF method causes minimal visible signal leakage.

The third example is a 3D field dataset, as plotted in Figure \ref{fig:real}. The denoised data using the various methods are plotted in Figure \ref{fig:rtest2,rtest1,rtest0,rtest00}. The SPF and NPF methods seem to obtain smoother results than the RNAR method. The cubes showing the noise removed are plotted in Figure \ref{fig:rtest2-n,rtest1-n,rtest0-n,rtest00-n}. The local similarity cubes are plotted in Figure \ref{fig:rsimi2,rsimi1,rsimi0,rsimi00}, showing 
 a similar level of signal leakage for all the methods. It is also clear that the RNAR method seems to cause a little more signal leakage than the other methods. Figure \ref{fig:real-z,rtest2-z,rtest1-z,rtest0-z,rtest00-z,rtest00dif-z} shows a zoomed comparison between the raw data and denoised data using the different methods. From the zoomed comparison, we conclude that the result from the SPF method is smooth, but contains a little weaker energy. The RNAR method removes less noise. The two NPF approaches obtain smooth results and preserve the details well. The frequency-dependent smoothing can make the denoised result a little smoother by removing more high-frequency noise.

\inputdir{hyper3d}
\multiplot{2}{cmp0,cmp}{width=0.45\textwidth}{Synthetic example. (a) Clean data. (b) Noisy data (SNR=-9.23 dB).}

\multiplot{4}{test2,test1,test0,test00}{width=0.45\textwidth}{Denoised data using (a) stationary predictive filtering (SPF) (SNR=2.34 dB), (b) regularized non-stationary auto-regression (RNAR) (SNR=2.56 dB), (c) non-stationary predictive filtering without frequency-dependent smoothing (NPF) (SNR=2.93 dB), and (d) non-stationary predictive filtering with frequency-dependent smoothing (NPFFS) (SNR=4.80 dB).}
\multiplot{4}{test2dif,test1dif,test0dif,test00dif}{width=0.45\textwidth}{Removed noise using (a) stationary predictive filtering (SPF), (b) regularized non-stationary auto-regression (RNAR), (c) non-stationary predictive filtering without frequency-dependent smoothing (NPF), and (d) non-stationary predictive filtering with frequency-dependent smoothing (NPFFS).}

\multiplot{6}{hyper-f,hypern-f,test2-f,test1-f,test0-f,test00-f}{width=0.3\textwidth}{FX spectra of (a) clean data, (b) noisy data, (c) denoised data using stationary predictive filtering (SPF), (d) denoised data using regularized non-stationary auto-regression (RNAR), (e) non-stationary predictive filtering without frequency-dependent smoothing (NPF), and (f) non-stationary predictive filtering with frequency-dependent smoothing (NPFFS).}

\multiplot{4}{simi2,simi1,simi0,simi00}{width=0.45\textwidth}{Local similarity (between denoised data and removed noise) using (a) stationary predictive filtering (SPF), (b) regularized non-stationary auto-regression (RNAR), (c) non-stationary predictive filtering without frequency-dependent smoothing (NPF), and (d) non-stationary predictive filtering with frequency-dependent smoothing (NPFFS).}

\multiplot{2}{hyper-ss-0,hyper-ss-z-0}{width=0.8\textwidth}{Single-trace comparison (20th x-direction trace and 20th y-direction trace). (a) Comparison in the original scale. (b) Comparison in the zoomed scale. The zooming area is highlighted by the black frame box in (a). The green line corresponds to the noisy data. The black line corresponds to the clean data. The pink line corresponds to the SPF method. The red line corresponds to the RNAR method.  The cyan and blue lines correspond to the denoised data using the NPF methods without and with  frequency-dependent smoothing, respectively. }

\inputdir{real2d}
\plot{real2d-0}{width=0.8\textwidth}{Real 2D seismic profile.}

%\multiplot{4}{r2test2-0,r2test1-0,r2test0-0,r2test00-0}{width=0.4\textwidth}{Denoised data using (a) stationary predictive filtering (SPF), (b) regularized non-stationary auto-regression (RNAR), (c) non-stationary predictive filtering without frequency-dependent smoothing (NPF), and (d) non-stationary predictive filtering with frequency-dependent smoothing (NPF(SF)).}
%\multiplot{4}{r2test2-n-0,r2test1-n-0,r2test0-n-0,r2test00-n-0}{width=0.4\textwidth}{Removed noise using (a) stationary predictive filtering (SPF), (b) regularized non-stationary auto-regression (RNAR), (c) non-stationary predictive filtering without frequency-dependent smoothing (NPF), and (d) non-stationary predictive filtering with frequency-dependent smoothing (NPFFS).}
%
%\multiplot{4}{r2simi2,r2simi1,r2simi0,r2simi00}{width=0.4\textwidth}{Local similarity (between denoised data and removed noise) using (a) stationary predictive filtering (SPF), (b) regularized non-stationary auto-regression (NSAR), (c) non-stationary predictive filtering without frequency-dependent smoothing (NPF), and (d) non-stationary predictive filtering with frequency-dependent smoothing (NPFFS).}

\multiplot{6}{real2d-z0,r2test2-z0,r2test1-z0,r2test0-z0,r2test00-z0,r2test00dif-z0}{width=0.35\textwidth}{Zoomed comparison \new{(pink solid frame in Figure \ref{fig:real2d-0})} of denoised data using (a) raw data, (b) stationary predictive filtering (SPF), (c) regularized non-stationary auto-regression (RNAR), (d) non-stationary predictive filtering without frequency-dependent smoothing NPF), and (e) non-stationary predictive filtering with frequency-dependent smoothing (NPFFS). (f) Difference between (d) and (e). Note that the frequency-dependent smoothing (e) has removed more high-frequency noise compared with (d). \wen{Note the obvious differences highlighted by the arrows.}}

\multiplot{4}{r2test2-n-z,r2test1-n-z0,r2test0-n-z,r2test00-n-z}{width=0.4\textwidth}{Zoomed comparison \new{(green dashed frame in Figure \ref{fig:real2d-0})} of removed noise using (a) stationary predictive filtering (SPF), (b) regularized non-stationary auto-regression (RNAR), (c) non-stationary predictive filtering without frequency-dependent smoothing (NPF), and (d) non-stationary predictive filtering with frequency-dependent smoothing (NPFFS). Note the obvious signal leakages in (a) and (b). }

\inputdir{real}
\plot{real}{width=0.8\textwidth}{3D field data example. }

\multiplot{4}{rtest2,rtest1,rtest0,rtest00}{width=0.4\textwidth}{Denoised data using (a) stationary predictive filtering (SPF), (b) regularized non-stationary auto-regression (RNAR), (c) non-stationary predictive filtering without frequency-dependent smoothing (NPF), and (d) non-stationary predictive filtering with frequency-dependent smoothing (NPFFS).}
\multiplot{4}{rtest2-n,rtest1-n,rtest0-n,rtest00-n}{width=0.4\textwidth}{Removed noise using (a) stationary predictive filtering (SPF), (b) regularized non-stationary auto-regressionv(RNAR), (c) non-stationary predictive filtering without frequency-dependent smoothing (NPF), and (d) non-stationary predictive filtering with frequency-dependent smoothing (NPFFS).}

\multiplot{4}{rsimi2,rsimi1,rsimi0,rsimi00}{width=0.4\textwidth}{Local similarity (between denoised data and removed noise) using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering without frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-dependent smoothing.}

\multiplot{6}{real-z,rtest2-z,rtest1-z,rtest0-z,rtest00-z,rtest00dif-z}{width=0.4\textwidth}{Zoomed comparison of denoised data using (a) raw data, (b) stationary predictive filtering (SPF), (c) regularized non-stationary auto-regression (RNAR), (d) non-stationary predictive filtering without frequency-dependent smoothing (NPF), and (e) non-stationary predictive filtering with frequency-dependent smoothing (NPFFS). (f) Difference between (d) and (e). Note that the frequency-dependent smoothing (e) has removed more high-frequency noise compared with (d).}

\section{Conclusions}
The traditional predictive filter is unable to accurately characterize the non-stationarity of seismic data in the spatial dimensions. 
The RNAR method calculates the spatially variable predictive filter coefficients by solving an inverse problem with a spatial smoothness-constrained shaping regularization. By formulating the non-stationary filter coefficients in all the frequency bands into the same inverse problem, we can solve a non-stationary predictive filter that is constrained in both spatial and frequency dimensions. The new non-stationary predictive filtering method is better at denoising \dlo{very }noisy seismic data with more robust performance than the alternatives. In addition, the frequency-dependent smoothing method helps the non-stationary predictive filtering method to attenuate more random noise in the mid-frequency to high-frequency bands. The proposed method is easily applied to 2D, 3D, or 4D applications with effective performance. Several synthetic and field data examples demonstrate the \dlo{appealing}\dlo{excellent}\wen{attractive} performance of the proposed method.

\section{DATA AND MATERIALS AVAILABILITY}
Data associated with this research are available and can be obtained by contacting the corresponding author.

\section{Acknowledgements}
We would like to thank Ray Abma and two anonymous reviewers for constructive suggestions.

\bibliographystyle{seg}
\bibliography{fxy}

### 2021-01-29 fxyn/ieee.tex
2021年 1月29日 星期五 02时12分17秒 CST

%\title{Non-stationary predictive filtering with frequency-space dependent smoothness constraint}
\title{Frequency-space-dependent smoothing regularized \\
non-stationary predictive filtering}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Guangtan Huang, Min Bai, Hang Wang, Xingye Liu, and Yangkang Chen
%\author{*
%\thanks{G. Huang, H. Wang, and Y. Chen is with School of Earth Sciences, Zhejiang University, Hangzhou, Zhejiang Province, China, 310027, yangkang.chen@zju.edu.cn}
%\thanks{X. Liu is with the College of Geology and Environment, Shaanxi Provincial Key Laboratory of Geological Support for Coal Green Exploitation, Xi’an University of Science and Technology, Xi’an, China, 710054, e-mail: lwxwyh506673@126.com}
%\thanks{M. Bai is is with the Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education, Yangtze University, Wuhan, China, 430100, bmwj103@163.com}

\thanks{G. Huang, H. Wang, and Y. Chen is with Zhejiang University}
\thanks{X. Liu is with Xi’an University of Science and Technology}
\thanks{M. Bai is is with Yangtze University}
\thanks{This work was supported in part by the starting fund from Zhejiang University, and in part by the National Natural Science Foundation of China under Grant 41704121}}
\maketitle

\begin{abstract}
Predictive filtering is one of the most widely used denoising algorithms in the seismic data processing community because of its high efficiency and stability in different situations. The traditional predictive filtering, however, is not able to deal with structurally complex dataset unless applied in local windows. We develop a novel non-causal predictive filtering method that is free of the windowing step but is able to denoise complicated dataset. We extend the stationary predictive filtering method to its non-stationary version, where the predictive filter coefficients vary across the frequency-space domain. The non-stationary predictive filtering model requires solving a highly underdetermined inverse problem using an iterative shaping regularization method. The traditional shaping regularization method solves an inverse problem by applying a constant smoothing operator and thus does not consider the heterogeneity of the filter coefficients in the frequency-space domain. We propose to apply a non-stationary smoothing operator to constrain the model in the shaping regularization framework. The smoothing radius in the non-stationary smoothing operator is chosen based on a priori information of the model, e.g., the non-stationarity of the data in the frequency-space domain. The proposed non-stationary predictive filtering method offers the flexibility in controlling the smoothness and sharpness of the calculated filter coefficients in both frequency and space dimensions. Several synthetic datasets and complicated real data examples are used to demonstrate the advantages of the new method.
\end{abstract}

\begin{keywords}
Signal processing, predictive filtering, seismic data
\end{keywords}

\section{Introduction}
Due to the severe recording environment, seismic data are usually contaminated with strong random noise \cite{wangchong2019hankel,zhaoqiang2019tgrs,baimin2019tgrs,zhangmi2019}. The strong random noise may deteriorate the performance of many seismic tasks, e.g., surface-related multiple attenuation, velocity analysis, seismic migration, amplitude-variation-with-offset (AVO) inversion, full waveform inversion, and even post-stack seismic interpretation. Thus, the removal of the seismic random noise is beneficial for the whole seismic processing, imaging, and interpretation workflow \cite{hongbo2014,yanan2014,yu2017complex,li2018seismic,liu2019seismic,liuwei2019ewt}.

Among the hundreds of algorithms, the predictive filtering, rank-reduction, and sparse transform methods are the most widely used for denoising. The predictive filtering method assumes the seismic events are locally plane waves, which can be well characterized by the plane-wave equation. Based on the plane-wave equation, a predictive filter can be designed to reject noise while preserving signals in either the time or the frequency domain \cite{abma1995}.  Since predictive filtering aims to solve an inverse problem, several implementations in solving the inverse problem are used in different predictive filtering methods in the literature \cite{canales1984,gulunay1986fxdecon}. However, it is difficult to process curving and even more complicated datasets. To tackle this problem, the predictive filtering is normally applied in local windows, which introduces extra issues inevitably due to the windowing strategy\new{, like the parameter inconsistency problem \cite{shaohuan2017gji}}. Liu et al. (2012) \cite{guochang2012} developed a window-free predictive filtering method by extending the standard auto-regression model to the non-stationary auto-regression. The non-stationary auto-regression model was then extended to 2D version for the application in 3D random noise attenuation problems \cite{guochang2013}.

Rank-reduction methods assume the seismic data to be lowrank when the data is mapped to another domain. The classic rank-reduction method is the singular spectrum analysis (SSA) method, which arises from the general signal processing field \cite{ssa}. The SSA method was applied to denoise seismic data by \new{Oropeza} \cite{mssa}, where the SSA operator is applied to each frequency slice of seismic data. \old{When dealing with 3D seismic data, the Hankel matrix required by the SSA operator is extended to a block Hankel matrix.}\new{When dealing with 3D seismic data, the SSA method requires a block Hankel matrix.} The block Hankel-matrix-based method is referred to as the multi-channel singular spectrum analysis (MSSA) method. Huang et al. (2016) \cite{weilin2016dmssa} derived a theoretically optimal rank-reduction operator to better separate signal and noise by introducing a damping operator. Considering the rank inconsistency problem \cite{shaohuan2017gji,wang2020low} when the rank-reduction method is applied locally, Chen et al. (2017) \cite{yangkang2017ieee} proposed an empirical rank-reduction method, where the seismic data in each local window are first decomposed into an ensemble of lowrank components, each with a constant rank. Chen et al. (2019) \cite{yangkang2019nc} applied the rank-reduction method to denoise earthquake data that are recorded by USArray, a pioneering seismic network across the North American continent.

Sparse-transform methods assume the seismic data to be sparse in a transform domain, where the signal and noise can be easily separated by applying a thresholding operation. \old{The performance of sparse-transform methods depends on the sparsity of seismic data in the transform domain.}\new{The performance of sparse-transform methods depends on the sparsity in the transform domain.} To achieve a good sparsity, a variety of sparse transforms have been proposed and applied for seismic data. Fourier transform is the most traditional sparse transform widely applied in seismic data \cite{abma2009}. The wavelet transform is also a frequently used sparse transform due to its flexibility in choosing the appropriate mother wavelets \cite{mostafa2016geo}. The curvelet transform has been applied by many researchers to achieve decent performance in various seismic denoising and inverse problems \cite{neelamani2008,candes2009}. The seislet transform is the special transform tailored for seismic data compression and analysis based on the second-generation wavelet transform \cite{fomel2010seislet,yangkang20142}. The shearlet transform is a recently emerging sparse transform, which has been successfully applied to deal with complicated datasets, e.g., microseismic dataset \cite{zhang2018multicomponent}. 
%

\new{In addition, Deep learning has recently gained a lot of attention on denoising seismic data \cite{omar2020geo1,omar2020gp1,chenwei2020,song2020seismic}.} All the aforementioned denoising methods have their pros and cons. On the one hand, all denoising methods need to compromise between noise removal and signal preservation, which is controlled by the input parameters. In this sense, those denoising methods differ by the convenience in choosing the appropriate parameters. On the other hand, most denoising methods need to compromise between performance and efficiency. Even though some advanced denoising methods are more effective in separating signal and noise, they may result in a significantly larger computational cost. Thus, despite of a huge number of denoising algorithms developed so far, the prediction-based methods still play a central role in industrial applications because they are both stable and fast. In this paper, we deal with the main drawback of the prediction-based methods, i.e., less convenient to denoise complicated datasets, and propose a general non-stationary predictive filtering method. The proposed non-stationary predictive filtering method can process complex seismic data with large dips and curvatures by taking advantage of the spatial heterogeneity to design the optimal constraints during inversion. We first introduce the fundamentals of the stationary and non-stationary predictive filtering, and then use several representative 2D/3D synthetic and field seismic datasets to demonstrate the decent performance.

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.32\textwidth]{hyper3d2/Fig/cmp0}
\label{fig:cmp0}}
\subfigure[]{\includegraphics[width=0.32\textwidth]{hyper3d2/Fig/cmp}
\label{fig:cmp}}
\caption{Synthetic example. (a) Clean data. (b) Noisy data (SNR=-8.13 dB).}
\label{fig:cmp0,cmp}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\textwidth]{hyper3d2/Fig/test2-0}
\label{fig:test2-0}}
\subfigure[]{\includegraphics[width=0.31\textwidth]{hyper3d2/Fig/test1-0}
\label{fig:test1-0}}\\
\subfigure[]{\includegraphics[width=0.31\textwidth]{hyper3d2/Fig/test00-0}
\label{fig:test00-0}}
\subfigure[]{\includegraphics[width=0.31\textwidth]{hyper3d2/Fig/test3-0}
\label{fig:test3-0}}
\caption{Denoised data using (a) stationary predictive filtering (SNR=2.87 dB), (b) regularized non-stationary auto-regression (SNR=2.90 dB), (c) non-stationary predictive filtering with frequency-dependent smoothing (SNR=5.49 dB), and (d) non-stationary predictive filtering with frequency-space-dependent smoothing (SNR=7.12 dB).}
\label{fig:test2-0,test1-0,test00-0,test3-0}
\end{figure}

\begin{figure}[htb!]
\centering
\includegraphics[width=0.5\textwidth]{hyper3d2/Fig/rect1}
\caption{Smoothing radius distribution in the $f-x-y$ domain. The smoothing radius distribution is used in all three directions, i.e., frequency, space X, and space Y. Note that the maximum smoothing radius is chosen as 20 points for high-frequency band and the minimum smoothing radius is chosen as 4 points for low-frequency band. }
\label{fig:rect1}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\textwidth]{hyper3d2/Fig/test2dif-0}
\label{fig:test2dif-0}}
\subfigure[]{\includegraphics[width=0.31\textwidth]{hyper3d2/Fig/test1dif-0}
\label{fig:test1dif-0}}\\
\subfigure[]{\includegraphics[width=0.31\textwidth]{hyper3d2/Fig/test00dif-0}
\label{fig:test0dif-0}}
\subfigure[]{\includegraphics[width=0.31\textwidth]{hyper3d2/Fig/test3dif-0}
\label{fig:test00dif-0}}
\caption{Removed noise using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering with frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-space-dependent smoothing.}
\label{fig:test2dif-0,test1dif-0,test0dif-0,test00dif-0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.30\textwidth]{hyper3d2/Fig/simi2}
\label{fig:simi2}}
\subfigure[]{\includegraphics[width=0.30\textwidth]{hyper3d2/Fig/simi1}
\label{fig:simi1}}\\
\subfigure[]{\includegraphics[width=0.30\textwidth]{hyper3d2/Fig/simi00}
\label{fig:simi0}}
\subfigure[]{\includegraphics[width=0.30\textwidth]{hyper3d2/Fig/simi3}
\label{fig:simi00}}
\caption{Local similarity (between denoised data and removed noise) using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering with frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-space-dependent smoothing.}
\label{fig:simi2,simi1,simi0,simi00}
\end{figure}

\begin{figure*}[ht!]
\centering
\subfigure[]{\includegraphics[width=0.30\textwidth]{hyper3d2/Fig/hyper-f}
\label{fig:hyper-f}}
\subfigure[]{\includegraphics[width=0.30\textwidth]{hyper3d2/Fig/hypern-f}
\label{fig:hypern-f}}
\subfigure[]{\includegraphics[width=0.30\textwidth]{hyper3d2/Fig/test2-f}
\label{fig:test2-f}}\\
\subfigure[]{\includegraphics[width=0.30\textwidth]{hyper3d2/Fig/test1-f}
\label{fig:test1-f}}
\subfigure[]{\includegraphics[width=0.30\textwidth]{hyper3d2/Fig/test00-f}
\label{fig:test00-f}}
\subfigure[]{\includegraphics[width=0.30\textwidth]{hyper3d2/Fig/test3-f}
\label{fig:test3-f}}
\caption{Frequency-space spectrum comparison of (a) clean data, (b) noisy data, (c) stationary predictive filtering, (d) regularized non-stationary auto-regression, (e) non-stationary predictive filtering with frequency-dependent smoothing, and (f) non-stationary predictive filtering with frequency-space-dependent smoothing.}
\label{fig:hyper-f,hypern-f,test2-f,test1-f,test00-f,test3-f}
\end{figure*}

\section{THEORY}
\subsection{Stationary and non-stationary auto-regression}
The stationary predictive filtering aims to solve an auto-regression problem in the frequency domain. A stationary auto-regression model can be expressed as \cite{sdrnar}:
\begin{equation}
\label{eq:ar}
b(x) = \sum_{n=1}^{N}a_nb(x-n),
\end{equation}
where $b(x)$ denotes a signal. $a_n$ denotes the $n$th auto-regression coefficient. $N$ denotes the order of the auto-regression model. %Since the auto-regression coefficient is fixed at all space locations $x$, equation \ref{eq:ar} is referred to as the stationary auto-regression. 
As shown in the equation \ref{eq:ar}, the auto-regression coefficient of the stationary auto-regression model is fixed at all space locations.

For non-stationary signals, the stationary auto-regression cannot sufficiently model the variation. Instead, the non-stationary auto-regression can be used to characterize a non-stationary signal:
\begin{equation}
\label{eq:nar}
b(x) = \sum_{n=1}^{N}a_n(x)b(x-n),
\end{equation}
where the auto-regression coefficient $a_n(x)$ varies with the space coordinate $x$. Equation \ref{eq:nar} is referred to as the non-stationary auto-regression model \cite{fomel20132}. However, since more unknowns need to be solved based on the same signal $b(x)$, solving equation \ref{eq:nar} is more challenging than solving equation \ref{eq:ar}.

Solving equations \ref{eq:ar} and \ref{eq:nar} requires inverting the following optimization problems, respectively, i.e.,
\begin{equation}
\label{eq:arinv}
\hat{a}_n = \arg \min_{a_n} \sum_{x=1}^{L_x}| b(x)-\sum_{n=1}^{N}a_nb(x-n) |^2,
\end{equation}
and 
\begin{equation}
\label{eq:narinv}
\hat{a}_n(x) = \arg \min_{a_n(x)} \sum_{x=1}^{L_x}| b(x)-\sum_{n=1}^{N}a_n(x)b(x-n) |^2,
\end{equation}
where $L_x$ denotes the number of samples of $b(x)$ in the $x$ axis.

\subsection{Stationary and non-stationary predictive filtering}
Stationary predictive filtering is based on the assumption that a linear event can be predicted by the following relation in the time-space domain \cite{yangkang20141,wanghang2021geo}:
\begin{equation}
\label{eq:pre}
d(t,x+1)=d(t-x\sigma,1),
\end{equation}
which is basically the general solution to the plane-wave equation \cite{fomel2002pwd}, considering that $d(t-x\sigma,1)$ denotes the source wavelet. \old{$\sigma\frac{\partial d}{\partial t} + \frac{\partial d}{\partial x} =0$}
Transforming equation \ref{eq:pre} into frequency domain, we obtain
\begin{equation}
\label{eq:fpre}
D(f,x+1)=D(f,1)e^{-i2\pi\sigma x},
\end{equation}
which can be expressed as the prediction formula in terms of a two-point prediction filter $[1,-e^{-i2\pi\sigma x}]$. Assuming $N$ plane-wave components, the prediction formula can be expressed as
\begin{equation}
\label{eq:fpre2}
\begin{split}
D(f,x+1)&=w_1(f)D(f,x)+ w_2(f)D(f,x-1) + \cdots \\
&+ w_N(f)D(f,x-N+1),
\end{split}
\end{equation}
where $w_n(f)$ denotes the prediction filter. Substituting  $D(f,x+1)$ by $b(x)$ and $w_n(f)$ by $a_n$, equation \ref{eq:fpre2} can be expressed as the same formula as equation \ref{eq:ar}, which is a stationary AR model of order $N$. Thus, the prediction formula of equation \ref{eq:fpre2} can be referred to as the stationary predictive filter. In a similar way, the non-stationary predictive filtering formula can be expressed as
\begin{equation}
\label{eq:fpre22}
D(f,x+1)=\sum_{n=1}^{N}w_n(f,x)D(f,x-n+1),
\end{equation}
where $w_n(f,x)$ is the coefficient of the non-stationary predictive filter. Equation \ref{eq:fpre2} can be solved via the regularized shaping regularization method:
\begin{equation}
\label{eq:fpre2inv}
\begin{split}
&\hat{w}_n(f,x) \\
&=\arg \min_{w_n(f,x)} \sum_{x=1}^{L_x}| D(f,x+1)-\sum_{n=1}^{N}w_n(f,x)D(f,x-n+1)|^2 \\
&+ \mathcal{R}(w_n(f,x)),
\end{split}
\end{equation}
where $\mathcal{R}(\cdot)$ denotes a regularization term applied onto the non-stationary predictive filter coefficients. \new{The computational cost of the non-stationary predictive filtering method is $O(N_aN_fN_xN_yN_{iter}$, where $N_a$ denotes the filter size. $N_f$, $N_x$, and $N_y$ denote the dimension of frequency, X and Y directions, respectively. $N_{iter}$ is the number of iterations.} In \cite{guochang2012}, $\mathcal{R}$ is chosen as a triangle smoothing operator with a fixed smoothing radius along the space direction in each frequency slice.

Considering the non-stationary feature of a seismic data, the predictive filter coefficient $w_n(f,x)$ should vary across the whole frequency-space domain, which has been characterized by the non-stationary auto-regression model in equation \ref{eq:fpre2inv}. However, to ensure the stability of the model $w_n(f,x)$, the constraint applied onto the model, i.e., the smoothing, should also be non-stationary, or frequency-and-space dependent. The non-stationary model constraint/smoothing considers the model non-stationarity and makes the estimated model more physically appropriate. In this paper, following the philosophy of two-fold non-stationarity of both data and model, we propose a non-stationary model constraint to solve equation \ref{eq:fpre2inv}. More specifically, we propose to apply a triangle smoothing operator with frequency-space-dependent smoothing radius across the whole model domain, taking all physical dimensions (frequency and space) into consideration, to constrain the predictive filter coefficients. \old{In order to distinguish the new method from the one proposed in ?, we}\new{We} refer the new algorithm as the non-stationary predictive filtering method. \new{The traditional f–x–y regularized nonstationary auto-regression (RNAR) method proposed in Liu et al. \cite{guochang2012} does not use a spatially varying smoothing filter to regularize the regression coefficients. In other words, in the traditional RNAR method, the smoothing is fixed. In the new method, the smoothing is spatially varying.} The non-stationary smoothing radius can be designed based on any a priori information\new{, e.g., the result from an initial denoising}. Some feasible strategies will be introduced during the illustration of examples.

\begin{figure}[htb!]
\centering
\includegraphics[width=0.45\textwidth]{real2d2/Fig/real2d-0}
\caption{Real 2D seismic profile. }
\label{fig:real2d-0}
\end{figure}

\begin{figure*}[ht!]
\centering
\subfigure[]{\includegraphics[width=0.350\textwidth]{real2d2/Fig/r2test2-0}
\label{fig:r2test2-0}}
\subfigure[]{\includegraphics[width=0.350\textwidth]{real2d2/Fig/r2test1-0}
\label{fig:r2test1-0}}\\
\subfigure[]{\includegraphics[width=0.350\textwidth]{real2d2/Fig/r2test00-0}
\label{fig:r2test00-0}}
\subfigure[]{\includegraphics[width=0.350\textwidth]{real2d2/Fig/r2test3-0}
\label{fig:r2test3-0}}
\caption{Denoised data using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering with frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-space-dependent smoothing. \new{The rectangles are zoomed for detailed comparison in Fig. \ref{fig:real2d-z,r2test2-z,r2test1-z,r2test00-z,r2test3-z}.}}
\label{fig:r2test2-0,r2test1-0,r2test00-0,r2test3-0}
\end{figure*}

\begin{figure*}[ht!]
\centering
\subfigure[]{\includegraphics[width=0.350\textwidth]{real2d2/Fig/r2test2-n}
\label{fig:r2test2-n}}
\subfigure[]{\includegraphics[width=0.350\textwidth]{real2d2/Fig/r2test1-n}
\label{fig:r2test1-n}}\\
\subfigure[]{\includegraphics[width=0.350\textwidth]{real2d2/Fig/r2test00-n}
\label{fig:r2test00-n}}
\subfigure[]{\includegraphics[width=0.350\textwidth]{real2d2/Fig/r2test3-n}
\label{fig:r2test3-n}}
\caption{Removed noise using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering with frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-space-dependent smoothing.}
\label{fig:r2test2-n,r2test1-n,r2test00-n,r2test3-n}
\end{figure*}

\begin{figure*}[ht!]
\centering
\subfigure[]{\includegraphics[width=0.350\textwidth]{real2d2/Fig/r2simi2}
\label{fig:r2simi2}}
\subfigure[]{\includegraphics[width=0.350\textwidth]{real2d2/Fig/r2simi1}
\label{fig:r2simi1}}\\
\subfigure[]{\includegraphics[width=0.350\textwidth]{real2d2/Fig/r2simi00}
\label{fig:r2simi00}}
\subfigure[]{\includegraphics[width=0.350\textwidth]{real2d2/Fig/r2simi3}
\label{fig:r2simi3}}
\caption{Local similarity (between denoised data and removed noise) using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering with frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-space-dependent smoothing.}
\label{fig:r2simi2,r2simi1,r2simi00,r2simi3}
\end{figure*}

\begin{figure*}[ht!]
\centering
\subfigure[]{\includegraphics[width=0.30\textwidth]{real2d2/Fig/real2d-z}
\label{fig:real2d-z}}
\subfigure[]{\includegraphics[width=0.30\textwidth]{real2d2/Fig/r2test2-z}
\label{fig:r2test2-z}}
\subfigure[]{\includegraphics[width=0.30\textwidth]{real2d2/Fig/r2test1-z}
\label{fig:r2test1-z}}\\
\subfigure[]{\includegraphics[width=0.30\textwidth]{real2d2/Fig/r2test00-z}
\label{fig:r2test00-z}}
\subfigure[]{\includegraphics[width=0.30\textwidth]{real2d2/Fig/r2test3-z}
\label{fig:r2test3-z}}
\caption{Zoomed comparison of denoised data using (a) raw data, (b) stationary predictive filtering, (c) regularized non-stationary auto-regression, (d) non-stationary predictive filtering with frequency-dependent smoothing, and (e) non-stationary predictive filtering with frequency-space-dependent smoothing. \old{(f) Difference between (d) and (e). Note that the frequency-space-dependent smoothing (e) has removed more high-frequency noise compared with (d).}}
\label{fig:real2d-z,r2test2-z,r2test1-z,r2test00-z,r2test3-z}
\end{figure*}

\subsection{Non-stationary smoothing}
To apply the non-stationary model constraint with frequency-space smoothing radius, we propose to use an efficient recursion-based smoothing method. Considering the triangle smoothing operator in the Z transform domain:
\begin{equation}
\label{eq:tri}
T(Z)=B^2(Z),
\end{equation}
where $B(Z)$ denotes the rectangle smoothing operator in the Z transform domain. A rectangle smoothing operator means a simple average of all neighbor samples. Correspondingly, in Z transform domain, it can be expressed as
\begin{equation}
\label{eq:box}
B(Z) = 1 + Z + Z^2 +\cdots + Z^{R-1},
\end{equation}
where $R$ denotes the size of the rectangle smoothing operator or the radius of the triangle smoothing operator.  Equation \ref{eq:box} can be further computed analytically as
\begin{equation}
\label{eq:box2}
B(Z) = \frac{1-Z^R}{1-Z}.
\end{equation}
Equation \ref{eq:box2} becomes very beneficial for the fast implementation of a rectangle smoothing operator since both the numerator and the denominator can be calculated in the way of recursion. For example, equation \ref{eq:box2} can be expressed as cascaded two filters:
\begin{equation}
\label{eq:box3}
B(Z) = H_1(Z)H_2(Z),
\end{equation}
where
\begin{equation}
\label{eq:box31}
\begin{split}
H_1(Z)&=1-Z^R,\\
H_2(Z)&=1/(1-Z).
\end{split}
\end{equation}
The filter $H_1(Z)$ is equivalent to the following filter in the space domain
\begin{equation}
\label{eq:h1}
y(n)=x(n)-x(n+R).
\end{equation}
The filter $H_2(Z)$ is equivalent to a causal integration 
\begin{equation}
\label{eq:h2}
y(n)=y(n-1)+x(n).
\end{equation}
The recursion-based smoothing is efficient since the causal integration is implemented only once for all the samples and the $H_1$ filter only requires one floating operation between two samples. Besides, a great benefit of this implementation is that the filter $H_1$ is a function of the smoothing radius. The non-stationary smoothing thus can be implemented conveniently without the need of windowing operation, as required by many other types of smoothing operators.

The $f-x$ non-stationary predictive filter, expressed in equation \ref{eq:fpre2inv}, can be easily extended to 3D version by simple modifications:
\begin{equation}
\label{eq:fpre2inv2}
\begin{split}
&\hat{w}_{n_x,n_y}(f,x,y)=\arg \min_{w_{n_x,n_y}(f,x,y)} \sum_{x=1}^{L_x}\sum_{y=1}^{L_y} \\
&|D(f,x+1,y+1)-\sum_{n_x=1}^{N_x}\sum_{n_y=1}^{N_y}w_{n_x,n_y}(f,x,y)\\
&D(f,x-n_x+1,y-n_y+1)|^2 + \mathcal{R}(w_{n_x,n_y}(f,x,y)),
\end{split}
\end{equation}
%\begin{figure*}
%\begin{equation}
%\label{eq:fpre2inv2}
%\hat{w}_{n_x,n_y}(f,x,y)=\arg \min_{w_{n_x,n_y}(f,x,y)} \sum_{x=1}^{L_x}\sum_{y=1}^{L_y} 
%|D(f,x+1,y+1)-\sum_{n_x=1}^{N_x}\sum_{n_y=1}^{N_y}w_{n_x,n_y}(f,x,y)
%D(f,x-n_x+1,y-n_y+1)|^2 + \mathcal{R}(w_{n_x,n_y}(f,x,y)),
%\end{equation}
%\end{figure*}
where $L_y$ denotes the number of samples in the $y$ axis, $N_x$ and $N_y$ denotes the prediction length of the non-stationary filter in $x$ and $y$ directions, respectively. Correspondingly, the non-stationary smoothing operator is applied along the frequency, $x$, and $y$ directions, respectively. \new{The proposed method can be straightforwardly extended to high-dimension (e.g., 4D/5D) versions, where the triangle smoothing operator is variable in the 3D/4D spatial dimensions. }

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.355\textwidth]{real3d2/Fig/real}}
\caption{3D real data example.}
\label{fig:real}
\end{figure}

\begin{figure*}[ht!]
\centering
\subfigure[]{\includegraphics[width=0.38\textwidth]{real3d2/Fig/rtest2}
\label{fig:rtest2}}
\subfigure[]{\includegraphics[width=0.38\textwidth]{real3d2/Fig/rtest1}
\label{fig:rtest1}}\\
\subfigure[]{\includegraphics[width=0.38\textwidth]{real3d2/Fig/rtest00}
\label{fig:rtest00}}
\subfigure[]{\includegraphics[width=0.38\textwidth]{real3d2/Fig/rtest3}
\label{fig:rtest3}}
\caption{Denoised data using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering with frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-space-dependent smoothing.}
\label{fig:rtest2,rtest1,rtest00,rtest3}
\end{figure*}

\begin{figure*}[ht!]
\centering
\subfigure[]{\includegraphics[width=0.38\textwidth]{real3d2/Fig/rtest2-n}
\label{fig:rtest2-n}}
\subfigure[]{\includegraphics[width=0.38\textwidth]{real3d2/Fig/rtest1-n}
\label{fig:rtest1-n}}\\
\subfigure[]{\includegraphics[width=0.38\textwidth]{real3d2/Fig/rtest00-n}
\label{fig:rtest00-n}}
\subfigure[]{\includegraphics[width=0.38\textwidth]{real3d2/Fig/rtest3-n}
\label{fig:rtest3-n}}
\caption{Removed noise using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering with frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-space-dependent smoothing.}
\label{fig:rtest2-n,rtest1-n,rtest00-n,rtest3-n}
\end{figure*}

\begin{figure*}[ht!]
\centering
\subfigure[]{\includegraphics[width=0.38\textwidth]{real3d2/Fig/rsimi2}
\label{fig:rsimi2}}
\subfigure[]{\includegraphics[width=0.38\textwidth]{real3d2/Fig/rsimi1}
\label{fig:rsimi1}}\\
\subfigure[]{\includegraphics[width=0.38\textwidth]{real3d2/Fig/rsimi00}
\label{fig:rsimi00}}
\subfigure[]{\includegraphics[width=0.38\textwidth]{real3d2/Fig/rsimi3}
\label{fig:rsimi3}}
\caption{Local similarity (between denoised data and removed noise) using (a) stationary predictive filtering, (b) regularized non-stationary auto-regression, (c) non-stationary predictive filtering with frequency-dependent smoothing, and (d) non-stationary predictive filtering with frequency-space-dependent smoothing.}
\label{fig:rsimi2,rsimi1,rsimi00,rsimi3}
\end{figure*}

\begin{figure*}[ht!]
\centering
\subfigure[]{\includegraphics[width=0.38\textwidth]{real3d2/Fig/real-z}
\label{fig:real-z}}
\subfigure[]{\includegraphics[width=0.38\textwidth]{real3d2/Fig/rtest2-z}
\label{fig:rtest2-z}}\\
\subfigure[]{\includegraphics[width=0.38\textwidth]{real3d2/Fig/rtest1-z}
\label{fig:rtest1-z}}
\subfigure[]{\includegraphics[width=0.38\textwidth]{real3d2/Fig/rtest00-z}
\label{fig:rtest00-z}}\\
\subfigure[]{\includegraphics[width=0.38\textwidth]{real3d2/Fig/rtest3-z}
\label{fig:rtest3-z}}
\caption{Zoomed comparison of denoised data using (a) raw data, (b) stationary predictive filtering, (c) regularized non-stationary auto-regression, (d) non-stationary predictive filtering with frequency-dependent smoothing, and (e) non-stationary predictive filtering with frequency-space-dependent smoothing. \old{(f) Difference between (d) and (e). Note that the frequency-space-dependent smoothing (e) has removed more high-frequency noise compared with (d).}}
\label{fig:real-z,rtest2-z,rtest1-z,rtest00-z,rtest3-z}
\end{figure*}

\section{Examples}
In this section, we apply the proposed non-stationary predictive filtering method to three examples, i.e., 3D synthetic dataset, 2D field dataset, and 3D field dataset. For benchmark comparison, we compare the non-stationary predictive filtering method (NPF) with the stationary predictive filtering (SPF) method and the \old{regularized non-stationary auto-regression method (RNAR)}\new{regularized non-stationary auto-regression method (RNAR)}. We also compare two non-stationary predictive filtering methods by designing different model smoothing strategies, i.e., frequency dependent smoothing (NPFFS) \cite{wanghang2021geo} and frequency-space-dependent smoothing (NPFFXS). To evaluate the denoising performance, we use two metrics, i.e., the commonly used signal-to-noise ratio (SNR) \cite{guochang2009,weilin2018} and the local similarity metric \cite{fomel2007localattr,yangkang2015ortho}. The SNR is defined as 
\begin{equation}
\label{eq:diff}
\text{SNR}=10\log_{10}\frac{\Arrowvert \mathbf{d} \Arrowvert_2^2}{\Arrowvert \hat{\mathbf{d}} -\mathbf{d}\Arrowvert_2^2},
\end{equation}
where $\mathbf{d}$ is the ground-truth signal and $\hat{\mathbf{d}}$ is the noisy or estimated signal. The local similarity metric measures the correlation between denoised data and removed noise. It is intuitive that if the local similarity shows abnormal values, it indicates strong signal leakage. Besides, it is convenient to locate the signal leakage from the local similarity map. The local similarity metric is especially useful in evaluating field data example, where no ground-truth signal is available and thus the SNR metic cannot be computed. In addition, we use the local similarity metric as a reference to tune the parameters of different methods to ensure that each method obtains its best performance and avoids significant signal leakage.

The first example is shown in Fig. \ref{fig:cmp0,cmp}, with the left showing the clean data and the right showing the noisy data. The SNR of the noisy data is \old{-8.13}\new{-6.92} dB. Note that a SNR value below zero is considered very noisy for a common denoising test. The noise level in the noisy data is very high as we can barely see the useful signals in some areas. In the dataset, there are \old{four}\new{many} hyperbolic events\old{, with two of them crossing each other}. Each hyperbolic event has an apex point, where the curvature is very large. This synthetic dataset is representative because it contains both large dips and curvatures, which make it challenging for a common denoising algorithm. Fig. \ref{fig:test2-0,test1-0,test00-0,test3-0} shows the comparison of different denoising methods. The top two results correspond to the traditional stationary predictive filtering method \cite{canales1984} and the regularized non-stationary auto-regression method \cite{guochang2012}. From these two results, it is clear that the stationary predictive filtering method tends to damage the signal amplitude in large offsets. The regularized non-stationary auto-regression method, successfully removes significant noise, but causes some residual noise. \old{The bottom two figures}\new{Figs. \ref{fig:test00-0} and \ref{fig:test3-0}} correspond to the non-stationary predictive filtering methods with different model smoothing strategies. \old{The bottom left Fig.}\new{Fig. \ref{fig:test00-0}} shows the result using a frequency-dependent smoothing strategy. In the frequency-dependent smoothing scheme, we use a constant smoothing radius of 4 points along the frequency axis and use a frequency-dependent varying smoothing radius for the space axis. The reference shortest smoothing radius along the space directions (both X and Y) is 4 points below the dominant frequency of the data (10 Hz), and then gradually increases to 20 points around the Nyquist frequency, following a fraction power function (with the fraction as 0.5). The 
frequency-space-dependent smoothing scheme uses a smoothing map that varies across the whole $f-x-y$ domain. Here, we use a simple way to obtain the non-stationary smoothing map by taking the a priori information offered from the initial estimate using the regularized non-stationary auto-regression method. We calculate the $f-x-y$ spectra of the initial estimate (Fig. \ref{fig:test1-0}), compute the energy, and set a hard threshold, below which the radius is set as the 4 points and above which the radius is set as 20 points, to obtain the non-stationary smoothing radius estimation. The non-stationary smoothing radius map we use to obtain the result shown in Fig. \ref{fig:test3-0} is plotted in Fig. \ref{fig:rect1}. 
Note that both smoothing strategies are possible only in the proposed non-stationary predictive filtering framework. Other smoothing options and radius estimation options (that takes better a priori information) are also applicable. Using the two smoothing operations, we obtain very successful denoising for this dataset. \new{The SNRs of the top two results in Fig. \ref{fig:test2-0,test1-0,test00-0,test3-0} are 1.47 dB and 2.01 dB, respectively.} The SNRs of the bottom two results in Fig. \ref{fig:test2-0,test1-0,test00-0,test3-0} are \old{5.49 dB and 7.12 dB}\new{4.14 dB and 5.14 dB}, respectively, which are far larger than those obtained from the stationary predictive filtering method and the regularized non-stationary auto-regression method. We conclude from this test that applying both non-stationary smoothing strategies helps improve the results significantly and the smoothing radius that varies across the whole $f-x-y$ domain obtains the best result.

The removed noise sections are shown in Fig. \ref{fig:test2dif-0,test1dif-0,test0dif-0,test00dif-0}. Except for \old{the top left result}\new{Fig. \ref{fig:test2-0}} \old{(stationary predictive filtering method)}\new{(SPF method)} \new{and Fig. \ref{fig:test1-0} (RNAR method)}, \old{all other}\new{the other two} methods seem to cause negligible signal leakage\new{, as indicated by the arrows}. To confirm the observation of signal leakage, we compare the local similarity (between denoised data and removed noise) maps in Fig. \ref{fig:simi2,simi1,simi0,simi00}. As shown in Fig. \ref{fig:simi2,simi1,simi0,simi00}, we can see that stationary predictive filtering shows clear similarity anomalies around the seismic events, indicating significantly higher signal leakage. The result from the frequency-dependent non-stationary predictive filtering shows low similarity around the seismic events, but show relatively higher anomalies in non-event areas, which indicate that the frequency-dependent smoothing could result in some invisible artifacts that cause relatively higher similarity values. The similarity maps corresponding to the regularized non-stationary auto-regression method and the frequency-space-dependent non-stationary predictive filtering method show very low values across the similarity cubes, confirming the negligible signal leakage of these two methods. Fig. \ref{fig:hyper-f,hypern-f,test2-f,test1-f,test00-f,test3-f} shows a spectrum comparison of different data. The spectrum comparison further demonstrates the effectiveness of the proposed non-stationary predictive filtering method. It is clear that the stationary predictive filtering causes damages to frequency components above 20Hz. The regularization non-stationary auto-regression method causes obvious residual noise. The non-stationary predictive filtering method with frequency-dependent smoothing obtains very good performance. The non-stationary predictive filtering method with frequency-space-dependent smoothing obtains a even better result.

The second example is shown in Fig. \ref{fig:real2d-0}. \old{This example was previously studied by ? and ?. This field data is very complicated because it contains various non-stationary features, e.g., large dips, large curvatures, pinch-outs, amplitude variations, and weak events.} The denoised results are plotted in Fig. \ref{fig:r2test2-0,r2test1-0,r2test00-0,r2test3-0}. The top two figures show the results using the stationary predictive filtering method and the regularized non-stationary auto-regression method. The bottom two results correspond to the non-stationary predictive filtering method with different non-stationary smoothing operations, i.e., frequency-dependent and frequency-space-dependent smoothing. The removed noise corresponding to different denoising methods are plotted in Fig. \ref{fig:r2test2-n,r2test1-n,r2test00-n,r2test3-n}. Except for the stationary predictive filtering method, all the other three methods cause negligible signal leakages. The local similarity comparison corresponding to different methods are plotted in Fig. \ref{fig:r2simi2,r2simi1,r2simi00,r2simi3}, where the similarity values for all these methods are low. There are some anomalies in the top two figures. The non-stationary predictive filtering methods with different model smoothing options show obviously low similarity values. For a better comparison, we zoom a part of the raw data and each denoised data, and show the zoomed sections in Fig. \ref{fig:real2d-z,r2test2-z,r2test1-z,r2test00-z,r2test3-z}. The zoomed raw data is plotted in Fig. \ref{fig:real2d-z}. The results from the aforementioned methods are plotted in Figs. \ref{fig:r2test2-z}-\ref{fig:r2test3-z}, respectively. From the zoomed comparison, it is clear that the amplitude of Fig. \ref{fig:r2test2-z} (stationary predictive filtering method) is a little weaker than the other methods. The result from the regularized non-stationary auto-regression method is a little noisier than other methods. The two non-stationary predictive filtering results preserve better the details and remove relatively more noise, with the frequency-dependent smoothing causing a little more residual noise than the frequency-space-dependent smoothing. \old{The difference between Figs. \ref{fig:r2test00-z} and \ref{fig:r2test3-z} is plotted in Fig. \ref{fig:r2test3dif-z}, which corresponds to mostly the high-frequency noise. The difference plotted in Fig. \ref{fig:r2test3dif-z} indicates that the frequency-space-dependent smoothing helps remove more high-frequency noise than the frequency-dependent smoothing.} %We also zoom a part from each noise sections and show the comparison in Fig. \ref{fig:real2d-z,r2test2-z,r2test1-z,r2test00-z,r2test3-z}. From the zoomed comparison of noise sections, it is clear all methods except for the stationary predictive filtering method cause no visible damages to useful signals.

The third example is plotted in Fig. \ref{fig:real}. The denoised data using the four aforementioned methods are plotted in Fig. \ref{fig:rtest2,rtest1,rtest00,rtest3}. It is clear that both non-stationary predictive filtering results are obviously cleaner than the other two results. The regularized non-stationary auto-regression method causes slightly more residual noise in the denoised data. Fig. \ref{fig:rtest2-n,rtest1-n,rtest00-n,rtest3-n} shows the comparison of \old{noise}\new{removed noise sections}, Fig. \ref{fig:rsimi2,rsimi1,rsimi00,rsimi3} shows the comparison of local similarity cubes, where the regularized non-stationary auto-regression result causes obviously larger similarity anomalies, indicating a slightly larger signal damage. The non-stationary predictive filtering with frequency-space-dependent smoothing causes much lower similarity values in most areas except for the area in the middle of the cube. \old{Note that all similarity cubes show relatively small values (mostly below 0.05), indicating that all methods obtain acceptable results by tuning.} A zoomed comparison of different datasets are plotted in Fig. \ref{fig:real-z,rtest2-z,rtest1-z,rtest00-z,rtest3-z}, where we can clearly see the improvement from top to bottom. The results corresponding to the frequency-dependent (Fig. \ref{fig:rtest00-z}) and frequency-space-dependent (Fig. \ref{fig:rtest3-z}) non-stationary predictive filtering methods \old{show a quite similar effect, with the latter one removing more high-frequency noise (Fig. \ref{fig:rtest3dif-z}) and thus making the events a little more coherent.}\new{both show successful performance, but the latter makes the events more coherent, as indicated by the arrows.}

\section{Discussions}
We particularly want to emphasize the point that the main purpose of the similarity comparison in this paper is to show that all competing methods are doing a reasonable job as they all remove significant noise without damaging the useful signals (since the best way to detect the signal leakage is by local similarity, which is used herein). We do not intend to make the traditional methods completely wrong and show how successful our proposed method is, since that is not fair. A lot of factors could make an actually good method not perform well. Here, we have tuned each method and made their performance best for each method. The full paper is completely reproducible based on the Madagascar platform (www.ahay.org) \cite{mada2013}, and all source codes and datasets will be put online after its publication (http://www.ahay.org/wiki/Reproducible\_Documents). Thus, it is easy to find that the traditional method is not working in its best way if we use improper parameters, and the conclusion from this paper is not convincing and not solid. Based on the fact that all these competing methods are performing reasonably well, we use the local similarity to judge which is slightly better in the sense of preserving the signals. However, to judge which method is significantly better, we need to check the denoised data. The best denoising method corresponds to the cleaner image and better amplitude-preserving performance.

\section{Conclusions}
Seismic data is highly non-stationary in either time-space or frequency-space domain, thus the traditional predictive filter is not able to denoise the complicated seismic data successfully without using local windows. The non-stationary predictive filtering method estimates a filter with frequency-space dependent coefficients to predict the useful signals in an optimal way. The non-stationary predictive filter can be inverted based on either a stationary smoothness constraint, assuming the homogeneous distribution of coefficients energy, or a non-stationary smoothness constraint, where the coefficient heterogeneity is also taken into consideration.  The non-stationary predictive filter estimated with a non-stationary smoothness constraint is better at removing more random noise and preserving the signal energy. Designing the frequency-space dependent smoothing radius takes advantages of the a priori information of the filter coefficients, which correlates with the non-stationarity of the data in the frequency-space domain. Utilizing the a priori information of the filter coefficients and designing  better non-stationary model constraint is an open research topic and is worth more attention in the future. The results shown in this paper demonstrate the obviously better performance of the new method compared with the traditional methods.

\section{Acknowledgements}
All datasets and source codes associated with this research will be made available online (www.ahay.org) in the format of reproducible research \cite{mada2013}.

\bibliographystyle{IEEEtran}
\bibliography{fxy}

%\begin{figure}[htb!]
%	\centering
%	\subfigure[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
%	\caption{Caption.}
%	\label{fig:fig}
%\end{figure}

%\begin{figure}[htb!]
%	\centering
%	\subfigure[]{\includegraphics[width=0.355\textwidth]{Fig/fig1}}\\
%    \subfigure[]{\includegraphics[width=0.355\textwidth]{Fig/fig2}}
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure}

%\begin{table}[h]
%\caption{Table caption}
%\begin{center}
%     \begin{tabular}{|c|c|c|c|c|c|} 
%	  \hline Column1 (unit)  & Column2 (unit) & Column3 (unit) \\ 
%	  \hline 1 & 2  & 3 \\
%       \hline
%    \end{tabular} 
%\end{center}
%\label{tbl:table1}
%\end{table}

### 2021-01-30 nonMada/erratic_sosvmf/test_field.m
2021年 1月30日 星期六 00时09分43秒 CST

@@ -1,0 +1,317 @@
+clc;clear;close all;
+
+is_real=1;           % Type of the transform(0: complex-valued curvelets,1: real-valued curvelets)
+finest=2;            % Chooses one of two possibilities for the coefficients at the finest level(1: curvelets,2: wavelets)
+alpha=1.0;           % 噪音标准差的alpha倍阈值（1.2左右较为理想）
+
+niter=10;
+
+infile='~/chenyk.data2/various/cyksmall/zq_real_input.su';
+[ori]=glreadsu(infile,'su');
+dn=scalecyk(ori,2);
+[n1,n2]=size(dn);
+figure;imagesc([dn]);colormap(seis);caxis([-0.5,0.5]);
+
+
+F=ones(n1,n2);                                  % ones(n)返回n*n的1矩阵，频率域
+X=fftshift(ifft2(F))*sqrt(prod(size(F)));       % prod返回size(F)的乘积,X是一个见脉冲，标准差为1
+C=fdct_wrapping(X,0,finest);                    % 进行曲波变换用的是复曲波,最外层为小波变换
+% Compute norm of curvelets (exact)
+E=cell(size(C));
+for s=1:length(C)
+    E{s}=cell(size(C{s}));
+    for w=1:length(C{s})
+        A=C{s}{w};
+        E{s}{w}=sqrt(sum(sum(A.*conj(A)))/prod(size(A)));    %计算A的模，计算标准差，复数域单点相乘
+    end
+end
+
+Cdn=fdct_wrapping(dn,is_real,finest);     %进行曲波变换用的是实曲波,最外层为小波变换
+Smax=length(Cdn);
+Sigma0=alpha*median(median(abs(Cdn{Smax}{1})))/0.58;     %求取噪音标准差，选取最大尺度
+Sigma=Sigma0;
+% sigma=[Sigma,5*Sigma,2*Sigma, Sigma, 0.6*Sigma,Sigma/5];
+% sigma=[Sigma,5*Sigma,2*Sigma, Sigma, 0.6*Sigma,Sigma*0.1];
+sigma=[Sigma,linspace(2.5*Sigma,0.5*Sigma,niter)];
+Sigma=sigma(1);
+
+Ct=Cdn;
+for s=2:length(Cdn)
+    thresh=Sigma+Sigma*s;    %最外层设置为4*sigma
+    for w=1:length(Cdn{s})
[…]

### 2021-01-30 nonMada/erratic_sosvmf/test_linear.m

@@ -1,0 +1,594 @@
+clc;clear;close all;
+
+is_real=1;           % Type of the transform(0: complex-valued curvelets,1: real-valued curvelets)
+finest=2;            % Chooses one of two possibilities for the coefficients at the finest level(1: curvelets,2: wavelets)
+alpha=1.2;           % 噪音标准差的alpha倍阈值（1.2左右较为理想）
+alpha=1.2;
+niter=10;
+
+dc=levents(200);dc=yc_scale(dc);
+
+[n1,n2]=size(dc);
+
+mask=rand(1,n2);
+mask(logical(mask<0.9))=0;
+mask(logical(mask>=0.9))=1;
+
+err_n=zeros(size(dc));
+for i=1:n1
+    randn('state',123456+i);
+    err_n(i,:)=0.2*randn(1,n2).*mask;
+end
+
+randn('state',201920);
+ran_n=0.1*randn(n1,n2);
+
+dn=dc+err_n+ran_n;
+
+dt=0.004;
+t=[0:n1-1]*dt;x=[1:n2];
+
+figure;imagesc([dc,dn]);caxis([-0.5,0.5]);colormap(seis);
+
+
+F=ones(n1,n2);                                  % ones(n)返回n*n的1矩阵，频率域
+X=fftshift(ifft2(F))*sqrt(prod(size(F)));       % prod返回size(F)的乘积,X是一个见脉冲，标准差为1
+C=fdct_wrapping(X,0,finest);                    % 进行曲波变换用的是复曲波,最外层为小波变换
+% Compute norm of curvelets (exact)
+E=cell(size(C));
+for s=1:length(C)
+    E{s}=cell(size(C{s}));
+    for w=1:length(C{s})
+        A=C{s}{w};
+        E{s}{w}=sqrt(sum(sum(A.*conj(A)))/prod(size(A)));    %计算A的模，计算标准差，复数域单点相乘
+    end
+end
+
+Cdn=fdct_wrapping(dn,is_real,finest);     %进行曲波变换用的是实曲波,最外层为小波变换
+Smax=length(Cdn);
+Sigma0=alpha*median(median(abs(Cdn{Smax}{1})))/0.58;     %求取噪音标准差，选取最大尺度
+Sigma=Sigma0;
[…]

### 2021-01-30 nonMada/erratic_sosvmf/test_linear_noiselevels.m

@@ -1,0 +1,485 @@
+clc;clear;close all;
+
+is_real=1;           % Type of the transform(0: complex-valued curvelets,1: real-valued curvelets)
+finest=2;            % Chooses one of two possibilities for the coefficients at the finest level(1: curvelets,2: wavelets)
+alpha=1.2;           % 噪音标准差的alpha倍阈值（1.2左右较为理想）
+alpha=1.2;
+niter=10;
+
+dc=levents(200);dc=yc_scale(dc);
+
+[n1,n2]=size(dc);
+
+Ntest=4;
+Dn=zeros(n1,n2,Ntest);
+D3=zeros(n1,n2,Ntest);
+D4=zeros(n1,n2,Ntest);
+sigmas=[0.03,0.06,0.10,0.16];
+% thrs=[0.9,0.8,0.7,0.6];
+% thrs=[0.9,0.8,0.7,0.6];
+thrs=[0.9,0.9,0.9,0.9];
+thrs=[0.8,0.8,0.8,0.8];
+for itest=1:Ntest
+rand('state',201819);
+mask=rand(1,n2);
+mask(logical(mask<thrs(itest)))=0;
+mask(logical(mask>=thrs(itest)))=1;
+
+err_n=zeros(size(dc));
+for i=1:n1
+    randn('state',123456+i);
+    err_n(i,:)=0.2*randn(1,n2).*mask;
+end
+
+randn('state',201920);
+ran_n=sigmas(itest)*randn(n1,n2);
+
+dn=dc+err_n+ran_n;
+
+dt=0.004;
+t=[0:n1-1]*dt;x=[1:n2];
+
+figure;imagesc([dc,dn]);caxis([-0.5,0.5]);colormap(seis);
+
+
+F=ones(n1,n2);                                  % ones(n)返回n*n的1矩阵，频率域
+X=fftshift(ifft2(F))*sqrt(prod(size(F)));       % prod返回size(F)的乘积,X是一个见脉冲，标准差为1
+C=fdct_wrapping(X,0,finest);                    % 进行曲波变换用的是复曲波,最外层为小波变换
+% Compute norm of curvelets (exact)
+E=cell(size(C));
+for s=1:length(C)
+    E{s}=cell(size(C{s}));
+    for w=1:length(C{s})
+        A=C{s}{w};
+        E{s}{w}=sqrt(sum(sum(A.*conj(A)))/prod(size(A)));    %计算A的模，计算标准差，复数域单点相乘
[…]

### 2021-02-03 rdrr5d/paper.tex
2021年 2月 3日 星期三 11时40分39秒 CST

%\documentclass[manuscript]{geophysics}
%\usepackage{amsmath}
\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}
%\usepackage{amsmath}
%\usepackage{cite}
%\usepackage{inputenc}
\newcommand{\n}[1]{{\color{black}{#1}}}
%\usepackage{ifthen}
%\usepackage{seg}
%\usepackage{color}
%\usepackage{graphicx}
%\usepackage{graphicx} % needed for \includegraphics
%\usepackage{wrapfig} 
%%\usepackage{indentfirst}
%\usepackage{subfig}
%\usepackage[linesnumbered,ruled,vlined]{algorithm2e}

%\begin{document}

\title{Robust damped rank-reduction method for simultaneous denoising and reconstruction of 5D seismic data}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Yapo Abol{\'e} Serge Innocent Obou{\'e}\footnotemark[1], Wei Chen\footnotemark[2], Hang Wang\footnotemark[1] and Yangkang Chen\footnotemark[1]}

\ms{GEO-2020} %\ms{GJI-2019}

\address{\footnotemark[1]\quad Zhejiang University\\
	School of Earth Sciences\\
	Hangzhou, Zhejiang, China\\
	obouesonofgod1@gmail.com \& 18328504171@163.com \& chenyk2016@gmail.com\\
	\footnotemark[2]\quad Yangtze University\\
	Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
	Wuhan, Hubei, China\\
	chenwei2014@yangtzeu.edu.cn

Corresponding Author: Yangkang Chen (chenyk2016@gmail.com)
}

\lefthead{Obou{\'e} et al.}
\righthead{RDRR}

\maketitle

%\begin{center}
%	\huge{\textbf{Robust damped rank-reduction method for simultaneous denoising and reconstruction of 5-D seismic data}} 
%\end{center}

%\renewcommand{\thefootnote}{\fnsymbol{footnote}}

%\author{Yapo Abol{\'e} Serge Innocent Obou{\'e} \footnotemark[1], Wei Chen\footnotemark[2], Hang Wang\footnotemark[1] and Yangkang Chen\footnotemark[1]}

%\ms{GEO-2020} %\ms{GJI-2019}

%\address{\footnotemark[1]\quad Zhejiang University\\
%	School of Earth Sciences\\
%	Hangzhou, Zhejiang, China\\
%	obouesonofgod1@gmail.com \& 18328504171@163.com \& chenyk2016@gmail.com\\
%	\footnotemark[2]\quad Yangtze University\\
%	Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
%	Wuhan, Hubei, China\\
%	chenwei2014@yangtzeu.edu.cn

%Corresponding Author: Yangkang Chen (chenyk2016@gmail.com)
%}

%\lefthead{Obou{\'e} et al.}
%\righthead{RDRR}

\begin{abstract}

We have developed a new method for simultaneous denoising and reconstruction of 5D seismic data corrupted by random noise and missing traces. Several algorithms have been developed for seismic data restoration based on rank-reduction (RR) methods. More recently, a damping operator has been introduced into the conventional truncated singular-value decomposition (TSVD) formula to further remove residual noise, the presence of which disturbs the quality of the seismic results. Despite the success of the damped RR (DRR) method when the observed data have an extremely low signal-to-noise ratio (S/N), random noise is still a limiting factor for obtaining a perfect quality of the result. Therefore, how to accurately solve the simultaneous denoising and reconstruction problem with high fidelity is still challenging. We assume that introducing only the damping operator into the TSVD formula is not enough to remove the random noise and restore the useful signal well. By combining the soft thresholding (ST) operator and the moving-average (MA) filter, we have developed a new operator, which we call the STMA operator. Then, by introducing the STMA operator into the DRR framework, we have developed a new algorithm known as the robust DRR method, which aims at mixing the advantages of the STMA operator and the damping operator. The STMA operator is applied to the Hankel matrix after
damped TSVD to better remove residual noise. Examples of our approach on synthetic and field 5D seismic data demonstrate the better performance in terms of the visual examination and numerical test compared with the DRR approach. Our method aims at producing an effective low-rank filter and, thus, can perfectly enhance the S/N of the simultaneously denoised and reconstructed results with higher accuracy.
\end{abstract}

\section{Introduction}

   \dlo{In seismology exploration}\wen{In exploration seismology}, one of the main concerns is \dlo{to obtain}\wen{obtaining} a sufficient amount of data to draw meaningful conclusions. To achieve this, the data acquisition process must obey the Nyquist/Shannon sampling theorem to accurately restore the seismic data and, thus, provide an accurate image of the subsurface \citep{cao2011review,wang2013data}. However, because of physical and/or economic difficulties, seismic data are generally sub-sampled either sparsely or irregularly in one or more spatial directions. Such \dlo{reasons negatively influence}\wen{acquisition choices adversely affect} the Nyquist/Shannon sampling theorem \citep{chiu2014multidimensional}. Noisy and incomplete data are the direct consequences of the limitations in the acquisition process. Therefore, it is imperative that such data lacking much useful information is restored suitably. Otherwise, it may \wen{negatively} affect \dlo{seriously}fundamental processing steps\dlo{fundamental processing steps seriously}, \dlo{for instance}\wen{e.g.,} multiple attenuation, amplitude versus offset analysis, migration imaging filtering \citep{adamo20143d,lopez2015closed}. Restoration of noisy and missing traces becomes therefore unavoidable in the seismic data processing chain \citep{shuwei2016cs,yangkang2019nc}.

To overcome data acquisition issues, several approaches have been proposed over the years. Among these approaches, we discern a wide and popular group of methods in geophysics, which uses the prediction\wen{-}based approach. They are able to handle aliased events using nonaliased low-frequency components of data to restore the missing traces. This category is highly competitive for the interpolation of aliased data \citep{spitz1991seismic,crawley1999interpolation,porsani1999seismic}.
\dlo{On another hand}\wen{On the other hand}, we note the group of approaches known as wave equation method\wen{s} \citep{ronen1987wave}. \dlo{These approaches focused}\wen{Those approaches relying} on the main information provided by the subsurface parameters such as the velocity distribution, are more often computationally expensive \citep{canning1998reducing,fomel2003seismic}. \dlo{Besides}\wen{In addition to} these methods, there is a group of sparsity-promoting transforms that can be understood \dlo{first}as an analytical transform. It has a fixed basis that uses the well-known techniques: for instance, Fourier and Radon transforms \citep{kabir1995restoration,abma20063d}, curvelet\dlo{and sparse wavelet} transforms \citep{candes20061}, \wen{and} seislet \dlo{and shearlet}transform \citep{fomel2010seislet}. Then, as a well-known approach, learning-based \citep{cai2014data,amir2017geo} methods are also widely used.

Seismic data are generally considered as low-rank structures. Unfortunately, missing values, unrecorded data and/or noise\dlo{s} may extend the rank of seismic matrix or tensor \citep{chen2016simultaneous}. This basic assumption has favored the implementation of methods based on low-rank \wen{approximation} for the past years. Using truncated singular value decomposition (TSVD), which constitutes an essential tool of low-rank approaches, we can overcome the negative effects that augment the rank of seismic data. This wide category of the method can be referred to as multichannel singular spectrum analysis (MSSA)\wen{,} which \dlo{are}\wen{is} also known as Cadzow filtering. MSSA usually starts by including all the seismic data components into a matrix called Hankel or Toeplitz, and then, a rank\wen{-}reduction (RR) algorithm is used to restore the \dlo{mains}\wen{main} features of the data \citep{chen2016open,chen2016simultaneous,huang2016damped,huang2017double,zhang2017hybrid}. However, we have techniques based on multi-linear arrays decomposition. In this sub-group, seismic data \old{is}\wen{are} regarded as a tensor \citep{kreimer2012tensor,gao2015parallel}. The method operates directly on the seismic tensor rather than embedding the components into a multilevel Hankel or Toeplitz matrix.

For a long time, the low-rank method has been broadly applied for noise removal \citep{freire1988application,Trickett2008Cadzow,sacchi2009fx,trickett2009prestack}. More recently, it was successfully used for seismic data interpolation  \citep{oropeza2011simultaneous,chiu2014multidimensional,gan2015dealiased,huang2016damped,chen2016open,chen2016simultaneous,zhang2017hybrid,yangkang2020odrr}. Given the fact that low-rank matrix completion (MC) is based on \dlo{rank-reduction approach}\wen{low-rank} assumption, we can, therefore, bring it closer to some methods like compressed sensing (CS) \citep{candes2009exact}. \dlo{Focused}\wen{Focusing} on this idea, \citet{recht2010guaranteed} established a connection between MC and CS. Based on low-frequency elements to recover seismic data on regular grids, \citet{naghizadeh2012multidimensional} \dlo{suggested}\wen{suggest} using the theory developed by \citet{spitz1991seismic}. Indeed, \dlo{approaches like MSSA-based}\wen{MSSA-based approaches} are not effective to interpolate regularly sampled data. 
%By constructing a so-called "texture-patch mapping", \citet{yang2012seismic} rearranged first the seismic data into a texture-patch matrix that is of low-rank and then, used MC algorithms to solve the nuclear-norm minimization. Compared with the Hankel matrix-based methods, the direct MC algorithm is much faster and can deal well with the higher-scale problem \citep{yang2012seismic}.
\citet{kumar2012fast} \dlo{used}\wen{use} a matrix factorization with max-norm (MFMN) \citep{lee2010practical} to solve the MC optimization problem. Singular-value decomposition (SVD)-based algorithms suffer enough from running time. Using the MFMN, one can efficiently reduce the computation cost.
%which is the same as the method used in \citet{yang2012seismic}
Because seismic reconstruction issues are usually high-dimensional \citep{liu2004minimum,xu2010antileakage}, it is necessary to set problems where the irregularity of the sampling is in the two midpoint and offset coordinates. In this context, 5D seismic denoising and/or reconstruction appears and focuses on all spatial components of data. This particularity makes it more usual in recent years. Compared to 2D and 3D reconstruction\wen{s}, such data restoration is a helpful tool to enhance reconstruction performance \citep{gao2015parallel}.
Research area such as simultaneous denoising and reconstruction of seismic data \citep{oropeza2011simultaneous,chen2016simultaneous,zhang2017hybrid} has arisen to overcome high-dimensional seismic data interpolation problem, which usually suffers from random noise. In this perspective, \citet{oropeza2011simultaneous} introduce the MSSA approach based on a low-rank assumption into seismic data restoration. 
The \dlo{solution} method first introduces the physical elements of seismic data into the block Hankel matrix and then uses a rapid strategy like randomized SVD (RSVD) to efficiently recover the signal. Although the affinities between a key parameter called alpha and signal-to-noise ratio (S/N) are not well understood from this approach, it accomplished its task with great success. In the same context, \citet{kreimer2012tensor} \old{considered}\wen{consider} the 5D seismic volume as a tensor and then used the high-order SVD (HOSVD) to reduce the rank of the tensor to restore the seismic data. Computation time is still a basic concern for most approaches based on low-rank assumption even though there are some rapid strategies, for instance, RSVD used in \cite{rokhlin2009randomized}, \cite{oropeza2011simultaneous} and \cite{chen2016simultaneous}, Lanczos bidiagonalization \citep{gao2013fast}, and the SVD-free methods proposed by \cite{gao2015parallel}. As shown in most seismic processing literature, both groups of methods\dlo{: sparsity-promoting transforms and low-rank approaches} \wen{(sparsity-promoting transforms and low-rank approaches)} can be distinguished by their strength\wen{s} and weakness\wen{es} when recovering seismic data. This idea motivated \cite{sternfels2015multidimensional} to develop an efficient optimization method that constructs a model between sparse inversion technique and low-rank method. Following the same idea, \citet{zhang2017hybrid} \dlo{resolved}\wen{resolves} 3D seismic data simultaneous denoising and interpolation problems, first by designing a rank constraint and sparsity transforms model, and then, by proposing a detailed framework to solve it. This approach successfully removed random noise and reduced computation time.

\old{In more recent years}\wen{Recently}, \citet{huang2016damped} \dlo{inserted}\wen{insert} a helpful tool called damping operator into the TSVD formula to suppress the remnant noise by RR algorithm. Based on this meaningful theory, 
%\citet{zhang2016multi} first applied the damped rank-reduction (DRR) method to simultaneous denoising and reconstruction, and then, proposed the multistep DRR approach to further enhance its performances.
\citet{chen2016simultaneous} \dlo{extended}\wen{extend} the DRR method \citep{huang2016damped} to 5D seismic data simultaneous denoising and reconstruction. This method shows a superior reconstruction quality even though land seismic data have very low S/Ns. However, this approach has its limits when the \dlo{level}\wen{degree} of missing traces and residual noise increases, which can be explained by the fact that the DRR process certainly reflects the contribution of noise in the approximation signal. That is to say, only using the damping operator as a constraint is not sufficient \dlo{enough}for noise removal. Thus, it is needed to introduce a new improved operator into the DRR framework to effectively remove the random noise and hence, enhance the \dlo{SRN}\wen{S/N}.

Following \citet{chen2016simultaneous}, we first develop an operator called soft thresholding (ST) moving-average (MA)(STMA) by combining the broadly used \dlo{iterative}ST operator \citep{donoho1995noising,daubechies2004iterative,candes2006robust} and the MA filter \citep{schafer1989discrete}. Then, \wen{by applying the STMA operator to the Hankel matrix after the damped truncated singular value decomposition (DTSVD)}, we construct a connection between STMA \wen{operator} and DRR formula to model a robust damped RR (RDRR) method formula. The proposed approach \dlo{that}aims at straightforwardly applying \dlo{many}\wen{several} operators to restore the useful signal, \dlo{mixes}\wen{mixing} the advantages of the damping\dlo{operator, which is applied after TSVD}\wen{, TSVD,} and STMA operators. \dlo{These useful tools are mixed into the same algorithm.}Thus, the RDRR method offers a higher degree of filter for simultaneous denoising and reconstruction of \dlo{five-dimensional}\wen{5D} seismic data. Using synthetic and field \dlo{five-dimensional}\wen{5D} seismic data sets, we compared the RDRR method with the DRR method. The RDRR method is demonstrated to be better than the DRR method.

\dlo{To better follow this work, w}\wen{W}e subdivide the paper as follows\wen{.}\dlo{:} First, we briefly \dlo{remind}\wen{review} the construction of the well-known level-4 block Hankel matrix and the DRR formulation. Then, we elaborate on our proposed algorithm framework. \dlo{Inspection visual}\wen{Visual inspection} and numerical experiments are given to demonstrate the accuracy of our proposed \dlo{solution}approach for simultaneous denoising and reconstruction of \dlo{five-dimensional}\wen{5D} seismic data. Finally, a
discussion and our conclusions are presented.

\section{\dlo{Theory}\wen{The DRR method}}
\subsection{Constructing a level-4 block Hankel matrix}

A volume of \dlo{five-dimensions}\wen{5-D} seismic data $\mathbf{D}(t, n_1, n_2, p_1, p_2)$ that depends on the source-receiver positions \dlo{pays our attention}\wen{is the main object} in this paper. The terms $n_1$ and $n_2$ correspond to the receiver coordinates, $p_1$ and $p_2$ are the source positions, and t is the time. \dlo{Such tensor that}\wen{This tensor, which} depends on four spatial \dlo{indices}\wen{dimensions} can be formed by transforming the data to \dlo{a nominal}\wen{the} midpoint-offset domain as \dlo{$\mathbf{D}(t, Nx_1, Nx_2, x_1, x_2)$, where $Nx_1$, $Nx_2$ represent common midpoint positions and $x_1$ and $x_2$ stand for offset coordinates}\wen{$\mathbf{D}(t, hx, hy, x, y)$. The components $hx$, $hy$, $ x $ and $ y $, represent $ x $ and $ y $ offsets and $x$ and $y$ midpoints coordinates}. \dlo{RDRR method for such seismic data recovering can be executed by forming the level-4 block Hankel matrix.}To reach the desired matrix, we first convert the \dlo{five-dimensions}\new{5D} seismic data defined in time-space domain \dlo{$\mathbf{D}(t, Nx_1, Nx_2, x_1, x_2)$ into $\mathbf{D}(\omega, Nx_1, Nx_2, x_1, x_2)$}\wen{$\mathbf{D}(t, hx, hy, x, y)$ into $\mathbf{D}(\omega, hx, hy, x, y)$} of complex values in the frequency-space domain, where ${t}$ and $\omega$ denote time and frequency components, respectively. Thus, in this process, one can model each observed noisy and incomplete data at a known frequency portion by a four-dimensional spatial multilevel cube $\mathbf{D}_{e_1,e_2,e_3,e_4}$ with $e_i = 1 \cdot\cdot\cdot T_i$, {$i = 1,2,3,4$}, when the spatial variables are regularly sampled. Each frequency portion behaves in the same way. \dlo{RDRR method for such seismic data recovering can be executed by forming the level-4 block Hankel matrix} \dlo{The desired matrix must be closer to a square matrix as clearly outlined in}For simplification, \wen{we use $\textbf{G}$ as our level-4 block Hankel matrix.} 
%\cite{gao2015parallel}. 
\dlo{To succeed, we define parameters $Z_i$ as $\lfloor\frac{T_i}{2}\rfloor+1, i = 1, 2, 3, 4$. The symbol $\lfloor\cdot\rfloor$ corresponds to the integer part of its argument. At a known frequency $\omega_0$, all elements that characterize the seismic data set in the first level of the tensor $\mathbf{D}_{e_1,e_2,e_3,e_4}$ are used to introduce the seismic data first, in a level-1 block Hankel matrix. This operation is done gradually until we reach the size of the desired matrix. This procedure allows constructing the following level-1 block Hankel matrix, which is defined by its size $Z_{1}\times(T_{1}-Z_{1} + 1)$,}
%\begin{equation}
%\textbf{B}^{(l_1)}_{e_2,e_3,e_4}=\begin{bmatrix}
%\textbf{D}_{1,e_2,e_3,e_4} & \textbf{D}_{2,e_2,e_3,e_4} & ... & \textbf{D}_{T_{1}-Z_{1}+1,e_2,e_3,e_4}\\ 
%\textbf{D}_{2,e_2,e_3,e_4} & \textbf{D}_{3,e_2,e_3,e_4} & ... & \textbf{D}_{T_{1}-Z_{1}+2,e_2,e_3,e_4}\\ 
%\vdots & \vdots & \ddots & \vdots\\
%\textbf{D}_{{Z_{1}}{e_2,e_3,e_4}} & \textbf{D}_{{Z_{1}+1},{e_2,e_3,e_4}}  & ... & \textbf{D}_{T_{1},e_2,e_3,e_4}
%\end{bmatrix}.
%\end{equation}
%
%Then, we inserted these matrices shown in eq.(1) in a level-2 block Hankel matrix of size $(Z_{1}Z_{2})\times(T_{1}-Z_{1} + 1)(T_{2}-Z_{2}+1)$.
%
%\begin{equation}
%\textbf{B}^{(l_2)}_{e_3,e_4}=\begin{bmatrix}
%\textbf{B}^{(l_1)}_{1,e_3,e_4} & \textbf{B}^{(l_1)}_{2,e_3,e_4} & ... & \textbf{B}^{(l_1)}_{T_{2}-Z_{2}+1,e_3,e_4}\\ 
%\textbf{B}^{(l_1)}_{2,e_3,e_4} & \textbf{B}^{(1)}_{3,e_3,e_4} & ... & \textbf{B}^{(1)}_{T_{2}-Z_{2}+2,e_3,e_4}\\
%\vdots & \vdots & \ddots & \vdots\\
%\textbf{B}^{(l_1)}_{Z_{3},{e_4}} & \textbf{B}^{(l_1)}_{Z_{2}{+1,e_3,e_4}} & ... & \textbf{B}^{(l_1)}_{T_{2},e_3,e_4}\\ 
%\end{bmatrix}.
%\end{equation}
%
%Eq.(2) corresponds to the level-2 of the desired matrix.\\
%Afterward, the previous matrices are included in a level-3 block Hankel matrix:
%
%\begin{equation}
%\textbf{B}^{(l_3)}_{e_4}=\begin{bmatrix}
%\textbf{B}^{(l_2)}_{1,e_4} & \textbf{B}^{(l_2)}_{2,e_4} & ... & \textbf{B}^{(l_2)}_{T_{3}-Z_{3}+1,e_4}\\ 
%\textbf{B}^{(l_2)}_{2,e_4} & \textbf{B}^{(l_2)}_{3,e_4} & ... & \textbf{B}^{(l_2)}_{T_{3}-Z_{3}+2,e_4}\\ 	
%\vdots & \vdots & \ddots & \vdots\\
%\textbf{B}^{(l_2)}_{Z_{3},e_4} & \textbf{B}^{(l_2)}_{Z_{3},1+e_4} & ... & \textbf{B}^{(l_2)}_{T_{3},e_4}
%\end{bmatrix}.
%\end{equation}
%
%$(Z_{1}Z_{2}Z_{3})\times(T_{1}-Z_{1} + 1)(T_{2}-Z_{2}+1)(T_{3}-Z_{3}+1)$ denotes the size of the matrices in eq.(3).
%
%Finally, we construct the desired matrix by embedding the level-3 block Hankel matrices shown in eq.(3) in a level-4 block Hankel matrix:
%
%\begin{equation}
%\textbf{B}^{(l_4)}=\begin{bmatrix}
%\textbf{B}^{(l_3)}_1 & \textbf{B}^{(l_3)}_2 & ... & \textbf{B}^{(l_3)}_{T_4-Z_4+1}\\ 
%\textbf{B}^{(l_3)}_2 & \textbf{B}^{(l_3)}_3 & ... & \textbf{B}^{(l_3)}_{T_4-Z_4+2}\\ 
%\vdots & \vdots & \ddots & \vdots\\
%\textbf{B}^{(l_3)}_{Z_{4}} & \textbf{B}^{(l_3)}_{Z_{4} +1} & ... & \textbf{B}^{(l_3)}_{T_{4}}
%\end{bmatrix}.
%\end{equation}
%
%Eq.(4) corresponds to the desired matrix. 
%$ \textbf{B} $ and $l_n$ denote respectively the block Hankel matrix and its corresponding level. The size of $\textbf{B}^{(l_4)}$,
%which corresponds to 
%${(Z_1Z_2Z_3Z_4)\times(T_1 - Z_1 + 1)(T_2 - Z_2 + 1)(T_3 - Z_3 + 1)(T_4 - Z_4 + 1)}$ 
%can be written as $(Z_1Z_2Z_3Z_4)\times(Z_1Z_2Z_3Z_4)$ if $T_i$ is an odd integer. 
%For simplification, \wen{we use $\textbf{G}$ as our level-4 block Hankel matrix.}
%\begin{equation}
%\textbf{B}^{(l_4)}= \textbf{G},
%\end{equation}

%where $\textbf{G}$ corresponds henceforward to our level-4 block Hankel matrix.

\subsection{\dlo{DRR method for simultaneous denoising and reconstruction of 5-D seismic data}\wen{Damped TSVD}}

In this section, first we briefly \dlo{remind}\wen{review} the expression of the true model of $\textbf{G}$, and then the basic elements of \wen{the} DRR formula are given.

To simplify notation, it is better to disregard the argument {$e_1, e_2, e_3, e_4$} of {$\mathbf{D}_{e_1,e_2,e_3,e_4}$}. The Hankelization operator \citep{chen2016open,chen2016simultaneous,zhang2017hybrid} converts the \dlo{four-dimensional}\wen{4D} data at a single frequency into the matrix $\textbf{G}$ as follows:
\begin{equation}
\mathbf{G}=h\mathbf{D},                    
\end{equation}
where ${h}$ is the well-known Hankelization operator.

The matrix {$\mathbf{G}$} can be modeled in a general form as:
\begin{equation}
\mathbf{G} = \mathbf{A}+\mathbf{N},                       
\end{equation}
where $\mathbf{A}$ and $\mathbf{N}$ correspond, respectively, to the signal and random noise accumulated during the acquisition process. \dlo{In order t}\wen{T}o formulate the singular value decomposition of $ \mathbf{G} $, we suppose that the rank of {$ \mathbf{G} $} and $\mathbf{N}$ is complete. The size of the matrix {$\mathbf{G}$} can be written as {$I \times J$} with {$J < I$}. {$rank(\mathbf{G})=rank(\mathbf{N}) = J$, $I= Z_1Z_2Z_3Z_4, J= (T_1 -  Z_1 + 1)(T_2 - Z_2 + 1)(T_3 -  Z_3 + 1)(T_4 - Z_4 + 1)$}. The signal {$\mathbf{A}$} has incomplete rank, with {$rank(\mathbf{A})= K < J$}. In these conditions, we write the approximation of {$\mathbf{G}$} as follows:
\begin{equation}
\mathbf{G}=\begin{bmatrix}
U^{\mathbf{G}}_1 & U^{\mathbf{G}}_2\\
\end{bmatrix}
\begin{bmatrix}
\Sigma^{\mathbf{G}}_1 & 0\\
0 & \Sigma^{\mathbf{G}}_2\\
\end{bmatrix}
\begin{bmatrix}
(V^{\mathbf{G}}_1)^{\mathbf{t}}\\
(V^{\mathbf{G}}_2)^{\mathbf{t}}
\end{bmatrix},
\end{equation}
where the first diagonal matrix {$\Sigma^{\mathbf{G}}_1(K\times K)$} is characterized by its larger singular values and the second {$\Sigma^{\mathbf{G}}_2(I -  K) \times(J -  K)$} by its smaller singular values. The conjoint matrices with singular vectors are denoted by {$U^{\mathbf{G}}_1(I \times K)$}, {$U^{\mathbf{G}}_2(I\times(I -  K))$}, {$(V^{\mathbf{G}}_1)^{\mathbf{t}}(J \times K)$} and \dlo{$(V^{\mathbf{G}}_2)^{\mathbf{h}}(J \times(J -  K))$} \wen{$(V^{\mathbf{G}}_2)^{\mathbf{t}}(J \times(J -  K))$}. The conjugate transpose of the matrix is represented by the symbol {$\left(\cdot\right)^{\mathbf{t}}$}. In order to simultaneously denoise and reconstruct the useful signal during the first iteration, we substitute {$\Sigma^{\mathbf{G}}_2$} with {$0$}. This substitution leads to the following \dlo{eq.}\wen{equation} 4, which corresponds to the truncated singular value decomposition (TSVD) formula:
\begin{equation}
\mathbf{\tilde{G}}=U^{\mathbf{G}}_1{\Sigma^{\mathbf{G}}_1}{(V^{\mathbf{G}}_1)^{\mathbf{t}}}.
\end{equation}
\citet{huang2016damped} explain clearly why $\mathbf{\tilde{G}}$ still suffers from residual noise. According to their approach, we express the approximation of {$\mathbf{A}$} as follows:
\begin{equation}
\mathbf{A}=\begin{bmatrix}
U^\mathbf{A}_1 & U^\mathbf{A}_2\\
\end{bmatrix}
\begin{bmatrix}
\Sigma^\mathbf{A}_1 & 0\\
0 & \Sigma^\mathbf{A}_2\\
\end{bmatrix}
\begin{bmatrix}
(V^\mathbf{A}_1)^{\mathbf{t}}\\
(V^\mathbf{A}_2)^{\mathbf{t}}\\
\end{bmatrix}.
\end{equation}
Contrary to {$\mathbf{\tilde{G}}$}, the rank of $\mathbf{A}$ has to be incomplete and {$\Sigma^\mathbf{A}_2$} should be set as zero diagonal matrix\new{,} which allows to express $ \mathbf{A} $ in its short model:
\begin{equation}
\mathbf{A}=U^{\mathbf{A}}_1{\Sigma^{\mathbf{A}}_1}(V^{\mathbf{A}}_1)^{\mathbf{t}}.
\end{equation}
The true model of \wen{$\mathbf{\tilde{G}}$} \dlo{$\mathbf{G}$} (see \dlo{eq.(7)}\wen{equation 7}) can be obtained via the combination of \dlo{eqs (2), (5) and (6)}\new{equations 2, 5 and 6,}\dlo{.}   
\begin{align}
\mathbf{\tilde{G}}= \mathbf{A}+ U^{\mathbf{A}}_1(U^{\mathbf{A}}_1)^{\mathbf{t}}\mathbf{N}.
\end{align}
\dlo{Eq.(7)}\wen{This equation} clearly shows that {$\mathbf{\tilde{G}}$} still suffers from random noise ${U^\mathbf{A}_1(U^\mathbf{A}_1)^{\mathbf{t}}\mathbf{N}}$. Therefore, \citet{chen2016simultaneous} \dlo{extended}\new{extend} \wen{the} DRR algorithm \citep{huang2016damped} to \dlo{five-dimensions}\wen{5-D} seismic data restoration. The approximation of {$\mathbf{A}$} using the DRR \wen{operator} is given as follows:
\begin{align}
\mathbf{A}=U^{\mathbf{G}}_1{\Sigma^{\mathbf{G}}_1}\Lambda\left( V^{\mathbf{G}}_1\right)^{\mathbf{t}},
\end{align}
\begin{align}
\Lambda= I - (\Sigma^{\mathbf{G}}_1 )^{-d}{{\gamma}^d},
\end{align} 
where \wen{${\gamma}$}\dlo{${\gamma}^d$} represents the maximum element of {$\Sigma^{\mathbf{G}}_2$}\wen{.}\dlo{and} $d$ corresponds to the damping factor. \dlo{$\Lambda$ loses its abilities when $d$ increases gradually and eq.(8) tends towards eq.(4)}\wen{DRR reverts to the traditional method} when {$d\rightarrow+\infty$}. \dlo{Eq.(8) indicates the formula of the DRR method.}

\section{\dlo{The RDRR method for simultaneous denoising and reconstruction of 5-D seismic data}\wen{The RDRR method}}

Following \cite{chen2016simultaneous}, we focus on the approximation of $\mathbf{A}$ to restore the \dlo{serviceable}\wen{useful} events from $\mathbf{G}$. As shown in \old{eq.(8)}\new{equation 8}, the estimated signal $\mathbf{A}$ is influenced by the introduced damping operator $(\Lambda)$. This mathematical relationship between $\Lambda$ (see \dlo{eq.(9)}\new{equation 9}) and the TSVD formula (see \dlo{eq.(4)}\wen{equation 4}) corresponds to the DRR formula. 
\wen{Based on \dlo{eqs (8) and (9)}\wen{equations 8 and 9}, the original signal can be regarded as a damped version of the TSVD result $\mathbf{\tilde{G}}$ in \dlo{eq.(4)}\new{equation 4} \citep{chen2016simultaneous}. By considering the formula of the DRR method, the approximation signal should be very close to the original signal. However, that is not verified when the data to be restored \dlo{is}\wen{are} corrupted by a high noise level and percentage of missing traces. In this paper, we assign the term coefficients to the values of the observed data that can be transformed by the DTSVD to obtain the useful signal. In the DRR approach, the observation matrix $\mathbf{G}$ is transformed by the DTSVD process to compute the signal matrix $\mathbf{A}$. The resulting \dlo{four-dimensional}\wen{4D} signal matrix $\mathbf{A}\in R^{J \times I}$ consists of the transformed coefficients. In this work,} we assume that the small \dlo{transform}\wen{transformed} coefficients, which correspond to the unwanted values in $\mathbf{A}$ \wen{obtained after} \dlo{during the DRR process certainly reflect the contributions from noise}\wen{the DTSVD process\wen{,} essentially correspond to noise}. This assumption can explain the residual noise that still \dlo{contains}\wen{remains in} the results of the DRR method. Thus, it is \dlo{needed}\wen{demanded} to handle the \dlo{transform}\wen{transformed coefficients of the approximation matrix $\mathbf{A}$ (\dlo{eq.(8)}\wen{equation 8}), which is obtained after DTSVD} by introducing an improved operator into the framework of the DRR algorithm, which aims at effectively attenuating the random noise while reconstructing the useful signal.

\subsection*{\dlo{Regularized iterative}ST}

Broadly utilized to promote sparsity \citep{donoho1995noising,figueiredo2003algorithm,daubechies2004iterative}, the ST operator can be applied to a signal $\mathbf{X}$ \dlo{in order} to minimize the contribution of noise. Based on this advantage, we first impose sparsity in the Hankel matrix $\mathbf{G}$ by applying \dlo{iterative} \wen{the} ST operator on the representation signal $\textbf{X}$, which is calculated with respect to the DRR framework. \dlo{This technique, known as iterative regularization}\wen{The ST function} \citep{donoho1995noising,candes2010matrix,yeganli2017noise} is given by:  
\begin{equation}
Is_\tau\left(\mathbf{X}\right)=sgn(\mathbf{X})\cdot max(0,{\mid \mathbf{X} \mid - \mid \tau \mid}),
\end{equation}
where \textbf{X} denotes the signal to be approximated, $Is_\tau\left(\mathbf{X}\right)$ corresponds to the transformed signal after applying \dlo{the regularized iterative}the soft thresholding operator $IS_\tau$, and $sgn( \textbf{X})$ is the signum function. The ST operator shrinks each coefficient of the signal by the amount of $\tau$ called ST parameter.

In this paper, we propose to set $\tau$ as follows:
\begin{equation}
\tau=\frac{\beta \cdot \lambda}{\alpha},
\end{equation}
where $\lambda$ denotes the regularization operator $\alpha$ is the scaling parameter used to manage $\tau$, and $\beta$ is the \dlo{decrease}\wen{decreasing} factor for cooling \dlo{lambda}\wen{$\lambda$}. Note that $\beta$ is a given value $\in$ R used to regulate $\tau$. This parameter provides us much freedom to control the simultaneous denoising and reconstruction operation.

We estimate $\lambda$ and $\alpha$ through the \dlo{following}linear forward model \wen{for the following} recovery problem defined in \cite{hennenfent2008sampling}:
\begin{equation}
\mathbf{Y}=L\mathbf{M},
\end{equation}
where $\mathbf{Y}$ represents the sampled entries and ${L}$ denotes the restriction operator that put together the acquired samples from the model in \dlo{eq.(12)}\wen{equation 12}. The term ${L}$ is applied to the vectorized $\textbf{M}$ of the signal $\mathbf{X}$. In forward mode, ${L}$ selects certain entries from $\mathbf{X}$ and returns a corresponding shortened vector.

Considering the model in \old{eq.(12)}\new{equation 12}, we set $\lambda$ and $\alpha$ as follows:
\begin{equation}
\lambda=\beta \cdot \left\| max\left(\mid \mathbf{Y} \mid \right) \right\|_0, 
\end{equation}
\begin{equation}
\alpha=\sigma \cdot \left(\left\| max\left(\mid \mathbf{Y} \mid \right) \right\|_0 + \sqrt{length(\mathbf{Y})} \right),
\end{equation}
where $\left\|\cdot\right\|_0$ corresponds to the $l_0$ norm and $\sigma$ stands for the noise standard deviation in $\mathbf{Y}$.\\

From \dlo{eq.(10)}\wen{equation 10}, it is obvious that $IS_\tau$ can be directly applied to the approximation signal \wen{$\mathbf{A}$} using the DRR method \wen{to nullify the coefficients below a fixed threshold}. Thus, \wen{by} using $IS_\tau$, we transform \dlo{eq.(8)}\new{equation 8} as follows:
\begin{align}
\nonumber
Is_\tau\left(\mathbf{A}\right)&=sgn(\mathbf{A})\cdot max(0,{\mid \mathbf{A} \mid - \mid \tau \mid})\\
\nonumber
&=sgn({U^{\mathbf{G}}_1{\Sigma^{\mathbf{G}}_1}\Lambda\left( V^{\mathbf{G}}_1\right)^{\mathbf{t}}})\cdot max(0,{\mid {U^{\mathbf{G}}_1{\Sigma^{\mathbf{G}}_1}\Lambda\left( V^{\mathbf{G}}_1\right)^{\mathbf{t}}} \mid - \mid \tau \mid}),\\
Is_\tau\left(\mathbf{A}\right)&\approx \mathbf{A}_\tau,
\end{align}
where $\mathbf{A}_\tau$ denotes the approximation \wen{signal} using both the damping and \dlo{iterative}ST operators.

\subsection*{MA filter}

The MA filter is broadly used for smoothing an array of the sampled signal. A significant gain of MA is its random noise attenuation capability while preserving the \dlo{serviceable}\wen{useful} signal response. The following difference equation explains a \dlo{MAF}\wen{MA} of the signal $\mathbf{X}$:
\begin{equation}
\mathbf{X}[i] =\frac{1}{T}\sum_{J=0}^{T-1}\mathbf{X}\left[i-j\right],   
\end{equation}                                               
where $T$ denotes the number of filter coefficients (also known as filter length) and $T -1$ corresponds to the filter order.

\old{Eq.(16)}\new{Equation 16} operates on an input signal $\mathbf{X}$ using the following rational transfer function:

\begin{equation}
{M(y)=\frac{q(1)+q(2)y^{-1}+...+q(t_q + 1)y^{-t_q}}{1+r(2)y^{-1} +...+ r(t_r+1)y^{-t_r}}}{N(y)}\dlo{,}\wen{.}
\end{equation}

\dlo{Eq.(17)}\wen{Equation 17} shows the relationship between the rational transfer function $M(y)$ of a discrete-time filter's output \dlo{$m(i)$}\wen{$M(i)$} and rational transfer function $N(y)$ of the input $N(i)$. The terms ${q_i}$ and ${r_i}$ are the filter coefficients, $t_r$ designates the feedback filter order, and $t_q$ corresponds to the feed-forward filter order. Due to normalization, we assume $r(1) = 1$ \citep{schafer1989discrete}.

The MA filter transforms $\mathbf{A}$ in \dlo{eq.(12)}\wen{\dlo{eq.(8)}\wen{equation 8}} \dlo{as follows}\wen{as follows}:
\begin{align}
\nonumber
\mathbf{A}[i]  &=\frac{1}{T}\sum_{J=0}^{T-1}\mathbf{A}\left[i-j\right]\\\nonumber
&=\frac{1}{T}\sum_{J=0}^{T-1}{\left( U^{\mathbf{G}}_1{\Sigma^{\mathbf{G}}_1}\Lambda\left( V^{\mathbf{G}}_1\right)^{\mathbf{t}}\right) }\left[i-j\right],\\
\mathbf{A}[i] &\approx \mathbf{A}_m, 
\end{align}
where $\mathbf{A}_m$ denotes the approximation \wen{signal} using the damping \wen{operator} and the MA filter.\\

Our experience with both operators above shows that each of them has a significant advantage in \dlo{reconstructing the signal}\wen{attenuating the contribution of residual noise in the approximation signal $\mathbf{A}$}. Therefore, \wen{by} combining the two operators, we can simultaneously take advantages of them for high accuracy.

\subsection*{\dlo{Connection between}\wen{Combining} ST and MA: STMA operator}

As shown, the \dlo{regularized iterative}ST and the MA \wen{operators} can be applied directly to the \wen{approximation} signal $\mathbf{A}$ \wen{after DTSVD}. Thus, a connection can be established to develop a novel improved operator called STMA operator, which can be applied directly to the \wen{approximation} signal \wen{$\mathbf{A}$ after DTSVD}. Combining \dlo{eq\wen{s}.(10) and (16)}\wen{equations 10 and 16}, we design the mathematical relationship between the ST and the MA filter as follows:
\begin{equation}
\mathbf{X}[i]  =\frac{1}{T}\sum_{J=0}^{T-1}{ Is_{\tau}\left(\mathbf{X}\right)} \left[i-j\right].   
\end{equation}   
\dlo{Eq.(19)}\wen{Equation 19} denotes the STMA operator, which results from the combination of the \dlo{iterative}ST \wen{operator \citep{donoho1995noising}} and the MA filter \wen{\citep{schafer1989discrete}}.

\wen{The proposed operator that we call STMA is used to nullify the unwanted value (also known as small transformed coefficients) in $\mathbf{A}$ after DTSVD. This operation \dlo{leads to compensate}\wen{compensates} for the DRR method operator, which has been introduced to attenuate the random noise after the conventional TSVD process. The STMA operator aids at \dlo{enhance}\wen{enhancing} the quality of the signal provided by the DRR method. This operator can be seen as an improved proximity function used to minimize the contribution of random noise at a lower level. We connect this function to the DRR framework after DTSVD to further \dlo{afford}\wen{provide} an accurate approximation signal matrix $\mathbf{A}$}.

\subsection*{\dlo{Connection between}\wen{Combining} STMA and DRR formula: RDRR}

In this section, we establish a connection between STMA and DRR formula to construct the proposed \dlo{program}\wen{algorithm}. This novel algorithm \dlo{aspires}\wen{aims} at mixing the benefits of both operators: damping and STMA operators \wen{to improve the quality of $ \mathbf{A}$ defined in \dlo{eq.(8)}\wen{equation 8}}. The resulting filter obtained via this combination can be regarded as applying \wen{an enhanced filter} \dlo{multiple operators} for simultaneous denoising and reconstruction of 5D seismic data.\\
The operation of STMA transforms the DRR method for 5D interpolation into an \dlo{improve}\wen{improved} method called RDRR method. The approximation of the signal $\mathbf{A}$ using the RDRR method can be formulated as follows:
\begin{align}
\nonumber
\mathbf{A}[i] & =\frac{1}{T}\sum_{J=0}^{T-1}Is_{\tau}\left(U^{\mathbf{G}}_1\Sigma^{\mathbf{G}}_{1}\Lambda(V^{\mathbf{G}}_1)^{{t}}\right)\left[i-j\right],\\
\mathbf{A}[i]&\approx \mathbf{\tilde{A}},
\end{align}   
where $\mathbf{\tilde{A}}$ denotes the approximation signal using the proposed \dlo{program}\wen{algorithm}.\\
\wen{The} RDRR method requires five \dlo{keys}\wen{key} parameters: the rank constraint ($K$) used in the conventional RR method; the damping factor ($d$) used in DRR method, the ST parameter ($\tau$), the rational transfer \wen{function} coefficient ($e$), (here e serves as a scaling factor
of the moving average filter, i.e., in equation 17, $r(1) = e$, $t_r = 0$), and the window size ($T$) used in STMA operator. Note that, $\tau$ is adjusted and controlled by a given value {$\beta$} {$\in R$} called \wen{the} cooling factor.

We model the relationship between $\mathbf{\tilde{A}}$, $\mathbf{{G}}$ and the improved DRR algorithm operator as follows:
\begin{equation}
\mathbf{\tilde{A}}={R}_{d\tau_m}{\mathbf{{G}}}, 
\end{equation}
where ${R}_{d\tau_m}$ is the RDRR operator whereas ${R}_d$ is used for the DRR.

Afterward, we apply the averaging function \citep{chen2016open} along the anti-diagonals of $\mathbf{\tilde{A}}$ in the following way:
%\old{
\begin{equation}
\mathbf{\hat{D}}={L}\mathbf{\tilde{A}}={L}{R}_{d\tau_m}\mathbf{G}={{L}}{{R}}_{d\tau_m}{{{h}}\mathbf{D}}={F}_{d\tau_m}\mathbf{D}.
\end{equation}
%}
${L} $ is the averaging operator. ${F}_{d\tau_m}$ and ${R}_{d\tau_m}$ are respectively the robust damped rank-reduction filter and operator, and ${R}_d$ and ${F}_d$ are used for damped rank-reduction operator and filter, respectively.

The following \dlo{eq.(23)}\new{equation 23} designates the weighted iterative algorithm based on DRR method:
\begin{equation}
\mathbf{D}_i= a_{i}\mathbf{D}_{ob} + (1 - a_{i}{T})\circ {F}_{d}\mathbf{D}_{i - 1}, \quad i = 1, 2, 3, . . . , i_{max}, 
\end{equation}
where ${F}_d$ denotes the DRR filter.

Using the RDRR filter $({F}_{d\tau_m})$, we \dlo{review the DRR program and}formulate our proposed algorithm for simultaneous denoising and reconstruction of 5-D seismic data as follows:
\begin{equation}
\mathbf{D}_i= a_{i}\mathbf{D}_{ob} + (1 - a_{i}{T})\circ {F}_{d\tau_m}\mathbf{D}_{i - 1}, \quad i = 1, 2, 3, . . . , i_{max}, 
\end{equation}
where $\mathbf{D}_0 = \mathbf{D}_{ob}$ corresponds to the observed noisy and incomplete data. The coefficient $a_{i}$ is an iteration scalar, which strictly diminish from $a_1=1$ to $a_{i_{max}}=0$. The term ${T}$ denotes the sampling operator. Furthermore, the elements of ${T}$ are equal to 1 when $ \mathbf{D}_{ob} $ is not empty, otherwise $0$ at the missing values. The symbol $\circ$ corresponds to the Hadamard product of two entities with the same size.\\

\dlo{Below is outlined t}\wen{T}he DRR algorithm \dlo{adopted}for simultaneous denoising and reconstruction of 5D seismic data \wen{is outlined as follows:}

\begin{center}
	\begin{algorithm}[H]
		\DontPrintSemicolon
		\dlo{$\mathbf{D}_{ob}(f, Nx_1, Nx_2, x_1, x_2)\leftarrow \mathbf{D}_{ob}(t, Nx_1, Nx_2, x_1, x_2)$}\wen{$\mathbf{D}_{ob}(f,hx, hy, x, y)\leftarrow \mathbf{D}_{ob}(t,hx, hy, x, y)$} via 1D forward FFT\;    
		$\mathbf{D}_0\leftarrow\mathbf{D}_{ob}$\;
		\For{$f\leftarrow 1,2,\dots,{F}$}{
			\For{$i\leftarrow 1,2,\dots,i_{max}$}{
				$\mathbf{D}^f_i \leftarrow a_i\mathbf{D}^f_{ob} + (1 - a_i){TF}_{d}\mathbf{D}^f_{i-1} + (1 - {T}){F}_{d}\mathbf{D}^f_{i-1}$\;
				\If{$\left\|\mathbf{D}^f_i - \mathbf{D}^f_{i-1}\right\|_F^2\leq\epsilon$}{
					\textbf{return} $\mathbf{D}^f_i$\;
				}
				\textbf{return} $\mathbf{D}^f_{i_{max}}$\;
			}
			\textbf{return} $\mathbf{D}_{recovered}$\;
		}
		\dlo{$\mathbf{D}_{recovered}(t,Nx_1, Nx_2, x_1, x_2)\leftarrow \mathbf{D}_{recovered}(f,Nx_1, Nx_2, x_1, x_2)$}\wen{$\mathbf{D}_{recovered}(t,hx, hy, x, y)\leftarrow \mathbf{D}_{recovered}(f,hx, hy, x, y)$} via 1D inverse FFT\;

		\caption{Damped rank-reduction ({${T}$}, {${F}_{d}$}, {$\mathbf{D}_{ob}$}, {$a_{i}$}, \dlo{${Tol}$}\wen{$\epsilon$}, {$i_{max}$}, {${F}$})}

	\end{algorithm}
\end{center}

The following workflow presents our proposed robust damped rank-reduction algorithm for simultaneous denoising and reconstruction of 5D seismic data:

\begin{center}
	\begin{algorithm}[H]
		\DontPrintSemicolon
		\dlo{$\mathbf{D}_{ob}(f,Nx_1, Nx_2, x_1, x_2)\leftarrow \mathbf{D}_{obs}(t,Nx_1, Nx_2, x_1, x_2)$}\wen{$\mathbf{D}_{ob}(f,hx, hy, x, y)\leftarrow \mathbf{D}_{obs}(t,hx, hy, x, y)$} via 1D forward FFT\;    
		$\mathbf{D}_0\leftarrow\mathbf{D}_{ob}$\;
		\For{$f\leftarrow 1,2,\dots,{F}$}{
			\For{$n\leftarrow 1,2,\dots,i_{max}$}{
				$\mathbf{D}^f_i \leftarrow a_i\mathbf{D}^f_{ob} + (1 - a_i){TF}_{d\tau_m}\mathbf{D}^f_{i-1} + (1 - {T}){F}_{d\tau_m}\mathbf{D}^f_{i-1}$\;
				\If{$\left\|\mathbf{D}^f_i - \mathbf{D}^f_{i-1}\right\|_F^2\leq\epsilon$}{
					\textbf{return} $\mathbf{D}^f_i$\;
				}
				\textbf{return} $\mathbf{D}^f_{i_{max}}$\;
			}
			\textbf{return} $\mathbf{D}_{recovered}$\;
		}
		\dlo{$\mathbf{D}_{recovered}(t,Nx_1, Nx_2, x_1, x_2)\leftarrow \mathbf{D}_{recovered}(f,Nx_1, Nx_2, x_1, x_2)$}\wen{$\mathbf{D}_{recovered}(t,hx, hy, x, y)\leftarrow \mathbf{D}_{recovered}(f,hx, hy, x, y)$} by 1D inverse FFT\;		
		\caption{Robust damped rank-reduction ($T$, {${F}_{d\tau_m}$}, $\mathbf{D}_{ob}$, $a_{i}$, \dlo{${Tol}$}\wen{$\epsilon$}, $i_{max}$, $F$)}
	\end{algorithm}
\end{center}

In both algorithms, when the frequencies denoted by ${F}$ are completed, the process of iteration stops immediately. Besides, the algorithms stop running according to two independent \dlo{principles :}\wen{principles:} (1) when {$i_{max}$} that corresponds to the maximum number of iterations is \dlo{achieved}\wen{reached} and (2) when {$\left\|\mathbf{D}^f_i - \mathbf{D}^f_{i-1}\right\|_F^2\leq \epsilon$} for each ${F}$ portion. The term $\epsilon$ is a given small tolerance and the symbol {$\left\|\cdot\right\|_F$} corresponds to the Frobenuis norm. The main difference between DRR framework and the proposed RDRR algorithm is the filter {${F}_{d\tau_m}$}. Here is a short \dlo{detail}\wen{description} of the proposed algorithm. First, we convert the observed 5D seismic data from time domain \dlo{$\mathbf{D}_{ob}(t,Nx_1, Nx_2, x_1, x_2)$}\wen{$\mathbf{D}_{ob}(t,hx, hy, x, y)$} into the frequency domain \dlo{$\mathbf{D}_{ob}(f,Nx_1, Nx_2, x_1, x_2)$}\wen{$\mathbf{D}_{ob}(f,hx, hy, x, y)$}. Then, for each outward loop, we remove noise and reconstruct the entire incomplete data {$\mathbf{D}_{ob}$} for all ${F}$ components. Inside the loop, we use the improved filter {${F}_{d\tau_m}$} included in the weighted POCS-like algorithm. Finally, the recovered data \dlo{$\mathbf{D}_{recovered}(f,Nx_1, Nx_2, x_1, x_2)$}\wen{$\mathbf{D}_{recovered}(f,hx, hy, x, y)$} obtained in the frequency domain are converted back into the time domain \dlo{$\mathbf{D}_{recovered}(t,Nx_1, Nx_2, x_1, x_2)$}\wen{$\mathbf{D}_{recovered}(t,hx, hy, x, y)$}.

\section{Examples}

Using \dlo{one}\wen{two} synthetic 5D data, \dlo{first,}we conduct many tests with different iteration numbers, noise levels, and percentage of missing data. Then, we use three 5D synthetic data of different sizes to estimate the computation time. At last, \dlo{one}field 5D seismic data is used to verify the performance of the proposed algorithm.

\dlo{In order t}\wen{T}o quantitatively compare the recovering quality of both approaches, we first use the widely used S/N \citep{chen2016simultaneous,zhang2017hybrid} formulated as follows:
\begin{equation}
S/N =10\log_{10}\frac{\Vert \mathbf{X^{c}} \Vert^2_2}{\Vert \mathbf{X^{c}}-\mathbf{X^{r}}\Vert^2_2},
\end{equation}
where $\mathbf{X^{c}}$ corresponds to the vectorized clean data and $\mathbf{X^{r}}$ indicates the vectorized restored data.

Then, we use the commonly used root-square-mean error (rms error) defined as follows to measure the accuracy of each approach:
\begin{equation}
rms\quad error={\sqrt{\frac{1}{N}\sum_{\mathbf{i}=1}^{N}(\mathbf{X^{c}_i-\mathbf{X^{r}})^2}}}\times100,
\end{equation}
where $\mathbf{X^{c}_i}$ denotes the original data and $\mathbf{X^{r}}$ is the simultaneously denoised and reconstructed data.

%\old{Finally, we use the percentage of similarity defined below to further quantify the performance of the robust damped rank-reduction method:	
%\begin{equation}
%\mathbf{S}=\frac{mean(\mathbf{X^{c}}-\mathbf{X^{r}})^2\times100}{mean\left(\mathbf{X^{c}}\right)^2},
%\end{equation}
%}
%\old{
%where $\mathbf{S}$ denotes the percentage of similarity, $\mathbf{X^{c}}$ and $\mathbf{X^{r}}$ are the vectorized original data and the vectorized restored data, respectively. The range of $\mathbf{S}$ is from 0 to 100\%. The lower percentage of similarity will denote better restoration performance.}

\subsection{Synthetic data examples}

To demonstrate the performance of the proposed algorithm, we apply both methods \wen{first, on 5D synthetic seismic data set that is composed of linear events and then curved events. \dlo{The four spatial dimensions of both 5D data are $hx$, $hy$, $x$ and $y$}}

\wen{For the first case,} we generate a 5D data model with the size of $100 \times 12 \times 12 \times 12 \times 12$, \wen{where}\dlo{which is composed of linear events.} $12 \times 12 \times 12 \times 12$ denotes the spatial size of the model. \wen{We conduct many experiments with this data}. In the first experiment, we randomly decimate $70\%$ of the traces and add a noise \dlo{variance of 0.3}\wen{of 0.3 variance} to examine the simultaneous denoising and reconstruction quality of both algorithms. The 3D figures in one common-midpoint gather \dlo{($Nx_1$ = 6, $Nx_2$ = 6)}\wen{($x$ = 6, $y$ = 6)} and one common offset gather \dlo{($x_1$ = 6, $x_2$ = 6)}\wen{($hx$ = 6, $hy$ = 6)} of the true, noisy, and decimated data are presented in Figures \ref{synth-clean-hxhy}\dlo{(a)}-\ref{synth-obs-hxhy}\dlo{(c)} and \ref{synth-clean-hxhy}\dlo{(a)}-\ref{synth-obs-hxhy}\dlo{(c)}, respectively.

The S/N\wen{s} of the noisy and observed data are extremely low with values of {$-$5.38 dB} and {$-$2.40 dB}, respectively. It is difficult to detect any coherent \dlo{valid}events in the observed noisy and incomplete data. To restore the useful signal, we use a rank {$K$ = 6} and a damped factor {$d$ = 2} for the DRR approach. Figures \ref{synth-drr-hxhy}\dlo{(d)} and \ref{synth-drr-xy}\dlo{(d)} show the results obtained using the DRR method. The simultaneously denoised and reconstructed data are satisfactory. Indeed, almost all signals are restored and the random noise has been perfectly reduced. However, the visual examination reveals some residual noise in the results. Using the proposed algorithm, with the same parameters used for DRR approach, we use a valid combination of cooling factor ${\beta = 3.3}$, rational transfer function coefficient ${e = 0.972}$, and window size ${T = 1}$. We run both methods using \dlo{ten}\wen{10} weighted POCS-like iterations. Figures \ref{synth-rdrr-hxhy}\dlo{(e)} and \ref{synth-rdrr-xy}\dlo{(e)} show the results obtained via the proposed RR approach. Compared with the DRR results, our method greatly removes the residual noise and recovers the useful signal. The output S/Ns for the DRR and the proposed approaches are {$15.55$} and {$21.89$ dB}, respectively. From the visual examination and the S/Ns comparison, we deduce that the restoration of the useful signal by the proposed approach is better than the DRR method.

\AtEndDocument{
	\begin{center}
		\begin{table}[h]
			\caption{Comparison of running time of the DRR and the proposed approach for different data sizes after \dlo{10}\wen{ten} iterations and a frequency band of $0-100$ Hz based on an Intel Core i7 7th Gen.}
			\begin{tabular}{c c c c c c} 
				\hline Test &$100\times8\times8\times8\times8$
				& $100\times10\times10\times10\times10$  & $100\times12\times12\times12\times12$ & \\ 
				\hline \dlo{DMSSA} \wen{DRR} (s) & 57.83 & 495.14 & 4419.36\\
				Proposed (s) & 48.64 & 469.69 & 4359.02 \\
				\hline
			\end{tabular} 
			\label{tbl:table1}
		\end{table}
	\end{center}
}
\wen{
	\AtEndDocument{
		\begin{center}
			\begin{table}[htb!]
				\caption{Comparison of S/N values among the ST, MA, STMA, RR, RR + ST, RR + MA, RR + damping factor (DRR), DRR + ST, RR + STMA, DRR + MA, and DRR + STMA (RDRR) for $0.3$ as noise variance and $70\%$ missing traces after \dlo{ten}\wen{10} iterations.}
				\begin{tabular}{c c c c c c} 
					\hline Approaches & S/N (dB) after 10 weighted {POCS-like} iterations & \\ 
					\hline ST& -1.77 & \\
					MA & 9.20 & \\
					STMA & 9.97 &\\
					RR & 11.83 &\\
					RR + ST & 11.83 &\\
					RR + MA &12.51&\\
					RR + damping factor (DRR) &15.55&\\
					RR + damping factor + ST & 15.55 &\\
					RR + STMA & 17.01 &\\
					RR + damping fator + MA & 21.17 &\\
					RR + damping factor + STMA (RDRR) & 21.89 &\\
					\hline
				\end{tabular} 
				\label{tbl:table2}
			\end{table}
		\end{center}
}}
\AtEndDocument{
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_originalfinal}
%			\label{cmp_originalfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_noisyfinal}
%			\label{cmp_noisyfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_observedfinal}
%			\label{cmp_observedfinal}}\\	
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_drrokfinal}
%			\label{cmp_drrokfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_proposedfinal}
%			\label{cmp_proposedfinal}}	
%		\caption{Common midpoint 3-D figures comparison ($x$ = 6, $y$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{10}\wen{ten} iterations. (a) Clean data. (b) Noisy data with $ 0.3 $ as noise level. (c) Observed noisy and incomplete data with $70\%$ of missing traces. (d and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed method, respectively.}
%		\label{cmp_originalfinal,cmp_noisyfinal,cmp_observedfinal,cmp_drrokfinal,cmp_proposedfinal}
%	\end{figure}%fig.1
\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-clean-hxhy}\label{synth-clean-hxhy}}
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-noisy-hxhy}\label{synth-noisy-hxhy}}
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-obs-hxhy}\label{synth-obs-hxhy}}\\
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-drr-hxhy}\label{synth-drr-hxhy}}
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-rdrr-hxhy}\label{synth-rdrr-hxhy}}
	\caption{Common-midpoint 3D figures comparison ($x$ = 6, $y$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{ten}\wen{10} iterations. (a) Clean data. (b) Noisy data with $0.3$ as noise level. (c) Observed noisy and incomplete data with $70\%$ of missing traces. (d and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed method, respectively.}
	\label{synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-drr-hxhy,synth-rdrr-hxhy}
\end{figure}%fig.1
%\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_originalfinal}
%			\label{offset_originalfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_noisyfinal}
%			\label{offset_noisyfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_observedfinal}
%			\label{offset_observedfinal}}

%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_drrokfinal}
%			\label{offset_drrokfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_proposedfinal}
%			\label{offset_proposedfinal}}
%		\caption{Common offset gather 3-D figures comparison ($hx$ = 6, $hy$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{10}\wen{ten} iterations. (a) True data. (b) Noisy data with $ 0.3 $ as noise level. (c) Observed noisy and incomplete data with $ 70\% $ of %missing traces. (d and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed approach, respectively.}
%		\label{offset_originalfinal,offset_noisyfinal,offset_observedfinal,offset_drrokfinal,offset_proposedfinal}
%	\end{figure}%fig.2
\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-clean-xy}\label{synth-clean-xy}}
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-noisy-xy}\label{synth-noisy-xy}}
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-obs-xy}\label{synth-obs-xy}}\\
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-drr-xy}\label{synth-drr-xy}}
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-rdrr-xy}\label{synth-rdrr-xy}}
	\caption{Common-offset gather 3D figures comparison ($hx$ = 6, $hy$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{ten}\wen{10} iterations. (a) True data. (b) Noisy data with $0.3$ as noise level. (c) Observed noisy and incomplete data with $70\%$ of missing traces. (d and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed approach, respectively.}
	\label{synth-clean-xy,synth-noisy-xy,synth-obs-xy,synth-drr-xy,synth-rdrr-xy}
\end{figure}%fig.2
}
%\dlo{To make a good comparison based on visual examination, we plot the 2-D figures of each synthetic 5-D data aforementioned. The results in one common midpoint gather and one common offset gather are displayed in Figures \ref{3} and \ref{5}, respectively. Figures \ref{3}\dlo{(a)}\wen{a} and \ref{5}\dlo{(a)}\wen{a} denote the original data. Figures \ref{3}\dlo{(b)}\wen{b} and \ref{5}\dlo{(b)}\wen{b} show the noisy data. Figures \ref{3}\dlo{(c)}\wen{c} and \ref{5}\dlo{(c)}\wen{c} show the decimated data. Figures \ref{3}\dlo{(d)}\wen{d} and \ref{5}\dlo{(d)}\wen{d} display the simultaneously denoised and reconstructed data using the DRR algorithm. From this comparison, it is clear that the results obtained by our algorithm displayed in Figures \ref{3}\dlo{(e)}\wen{e} and \ref{5}\dlo{(e)}\wen{e} are still preferable than those of the DRR method.}
%\AtEndDocument{
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2Dcmpclean7003}
%			\label{a}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DcmpNoisy7003}
%			\label{b}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DcmpObserved7003}
%			\label{Fiigure:c}}\\
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DcmpDRR7003}
%			\label{Fiigure:d}}
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DcmpProposed7003}
%			\label{Fiigure:e}}
%		\caption{Common midpoint 2-D figures comparison ($Nx_1$ = 6, $Nx_2$ = 6) after 10 iterations between both algorithms. (a) Clean data. (b) Noisy data with 0.3 as noise level. (c) Observed noisy and incomplete data with 70\% of missing traces. (d-e) Simultaneously denoised and reconstructed  data using the DRR method and the proposed approach, respectively.}
%		\label{3}
%	\end{figure}
%}
To see the difference more clearly, we display the rms error results obtained by subtracting the recovered data from the original data in \wen{Figure \ref{synth-drr-hxhy-e,synth-rdrr-hxhy-e,synth-drr-xy-e,synth-rdrr-xy-e}. Figures \ref{synth-drr-hxhy-e}\dlo{(a)} and \ref{synth-drr-xy-e}\dlo{(c)} correspond to the DRR approach with rms error values of $2.22\%$ and $2.64\%$ respectively in one common-midpoint and common-offset gather. Figure \ref{synth-rdrr-hxhy-e}\dlo{(b)} and \ref{synth-rdrr-xy}\dlo{(d)} is from the proposed algorithm with rms error values of $1.53\% $ and $1.48\% $ respectively in one common-midpoint and common-offset gathers.} From this comparison, it is \dlo{further} apparent that our approach performs better with fewer denoising and reconstruction errors and thus can provide a better simultaneously denoised and reconstructed improvement than the DRR algorithm. This comparison confirms the superiority of our approach in terms of accuracy. 
\AtEndDocument{
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.34\textwidth]{Figures/cmp_drrokerrfinal}
%			\label{cmp_drrokerrfinal}}
%		\subfloat[]{\includegraphics[width=0.34\textwidth]{Figures/cmp_proposederrfinal}
%			\label{cmp_proposederrfinal}}\\
%		\subfloat[]{\includegraphics[width=0.34\textwidth]{Figures/diff_offset_drrokfinal}
%			\label{diff_offset_drrokfinal}}
%		\subfloat[]{\includegraphics[width=0.34\textwidth]{Figures/diff_offset_proposedfinal}
%			\label{diff_offset_proposedfinal}}
%		\caption{Simultaneous denoising and reconstruction error \wen{3-D figures} comparison between \dlo{both}\wen{two} algorithms after \dlo{10}\wen{ten} iterations. (a and c) show the DRR approach with RMSE values of $ 2.22\% $ and $ 2.64\% $ in one common midpoint and one common offset gathers, respectively. (b and d) correspond to the proposed approach with RMSE values of $ 1.53\% $ and $ 1.48\% $ in one common midpoint and one common offset gathers, respectively.}
%		\label{cmp_drrokerrfinal,cmp_proposederrfinal,diff_offset_drrokfinal,diff_offset_proposedfinal}
%	\end{figure}%fig.3
\begin{figure}[htb!]
		\centering
	        \subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-drr-hxhy-e}\label{synth-drr-hxhy-e}}
	        \subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-rdrr-hxhy-e}\label{synth-rdrr-hxhy-e}}\\
	        \subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-drr-xy-e}\label{synth-drr-xy-e}}
	        \subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-rdrr-xy-e}\label{synth-rdrr-xy-e}}
		\caption{Simultaneous denoising and reconstruction error \wen{3D figures} comparison between \dlo{both}\wen{two} algorithms after \dlo{10}\wen{ten} iterations. (a and c) show the DRR approach with rms error values of $2.22\%$ and $2.64\%$ in one common-midpoint and one common-offset gather, respectively. (b and d) correspond to the proposed approach with rms error values of $1.53\%$ and $1.48\%$ in one common-midpoint and one common-offset gather, respectively.}
		\label{synth-drr-hxhy-e,synth-rdrr-hxhy-e,synth-drr-xy-e,synth-rdrr-xy-e}
	\end{figure}%fig.3
}
%\begin{figure}[htb!] 
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2Doffsetclean7003}
%			\label{a}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DoffsetNoisy7003}
%			\label{b}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DoffsetObserved7003}
%			\label{Fiigure:c}}\\
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DoffsetDRR7003}
%			\label{Fiigure:d}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DoffsetProposed7003}
%			\label{Fiigure:e}}	
%		\caption{Common offset 2-D figures comparison ($x_1$ = 6, $x_2$ = 6) after 10 iterations between both algorithms. (a) Clean data. (b) Noisy data with 0.3 as noise variance. (c) Observed noisy and incomplete data with 70\% of missing traces. (d-e) Simultaneously denoised and reconstructed data using both methods, respectively.}
%		\label{5}
%	\end{figure}
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DRMSEoffsetDRR7003}
%			\label{a}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DRMSEoffsetProposed7003}
%			\label{b}}
%		\caption{Simultaneous reconstruction and denoising errors comparison in common offset ($x_1$ = 6, $x_2$ = 6) after 10 iterations between both algorithms. (a) shows the DRR approach with an RMSE of 2.64\%. (b) shows the proposed approach with an RMSE of 1.48\%.}
%		\label{6}
%	\end{figure}
%}

\wen{Moreover,} we conduct a comparison between the amplitude of each corresponding \dlo{5-D}data \wen{plotted in Figure \ref{synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-drr-hxhy,synth-rdrr-hxhy}} to highlight more distinctly the differences. Figure \dlo{\ref{7}}\wen{\ref{synth-ss}} displays a comparison between each amplitude. The green, yellow and black lines are, respectively, from the original, noisy, and observed data. The amplitude of the observed data cannot be detected in this figure due to the influence \dlo{of the percentage}of missing traces. The blue and red lines correspond to the DRR approach and proposed approach, respectively. Clearly shown in Figure \dlo{\ref{7}}\wen{\ref{synth-ss}}, the blue and red lines are very regular in most areas. However, we find that the green and red lines are \dlo{too much close} \wen{much closer} to each other. This comparison further demonstrates the high accuracy of the proposed algorithm.

%\AtEndDocument{
%	\old{\begin{figure}
%			\centering
%			\includegraphics[width=1\%textwidth]{Figures/Amplit%ude_with_Time}
%			\caption{Comparison of the amplitude of each corresponding 5-D synthetic data after 10 iterations between both algorithms. The green line is from the clean data. The yellow line denotes the noisy data. The amplitude of the observed data, in this case, is zero and thus cannot be seen from the figure. The blue line corresponds to the damped rank-reduction method. The red line corresponds to the proposed method. The proposed method can provide a good amplitude very close to the clean data than the DRR method.}
%			\label{7}
%	\end{figure}
%}
%}
%\section{acknowledgments}
%
%The authors would like to thank Hang Wang for constructive
%comments and suggestions, which have helped to improve this manuscript. The authors also thank Min Bai, Dong Zhang, Mi Zhang, Weilin Huang, and Yatong Zhou for fruitful discussions on the rank-reduction method.
\AtEndDocument{
	\wen{\begin{figure}
			\centering
                        {\includegraphics[width=0.9\textwidth]{synth_Linear_NV03_MT70/Fig/synth-ss}}
			\caption{Comparison of a single trace amplitude of each \dlo{5-D synthetic} data \wen{shown in Figure \ref{synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-drr-hxhy,synth-rdrr-hxhy}}. The green line is from the clean data. The yellow line denotes the noisy data. The amplitude of the observed data denoted by the black line is zero and thus cannot be seen from the figure. The blue line corresponds to the DRR method. The red line corresponds to the proposed method. The proposed method can provide a good amplitude very close to the clean compared to the DRR method.}
			\label{synth-ss}
	\end{figure}}
}%fig.4
\dlo{We further compare the performance of the DRR method and our approach from another aspect using the amplitude \dlo{and frequency-space (f-x)} spectra. According to the amplitude spectrum comparison displayed in Figure \dlo{\ref{8}}\wen{\ref{5}}, we deduce that both approaches can recover the signal. However, there is a remarkable difference in the amplitude in favor of our algorithm. It can be explained by the fact that DRR approach suppresses the residual noise at the entire frequency band to a relatively weak degree whereas our approach removes the residual noise sufficiently. That is why the amplitude spectrum of the proposed approach shown in Figure \dlo{\ref{8}(e)} \ref{5}(e) is perfect and very similar to that of the true data shown in Figure \dlo{\ref{8}(a)} \wen{\ref{5}(a)}. This analysis demonstrates one more time the better performance of the proposed algorithm compared to the DRR method. \wen{Therefore, we deduce that the proposed method can obtain successful results even though the observed noisy and incomplete data have very low amplitudes as shown in Figures \ref{5}(c)} \dlo{\ref{8}(c)}.}

%\AtEndDocument{
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/AmplitudeSpectrumClean}
%			\label{a}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/AmplitudeSpectrumNoisy}
%			\label{b}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/AmplitudeSpectrumObserved}
%			\label{Fiigure:c}}\\
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/AmplitudeSpectrumdrr}
%			\label{Fiigure:d}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/AmplitudeSpectrumPropoposed}
%			\label{Fiigure:e}}
%		\caption{Amplitude spectra comparison of each \old{5-D data after 10 iterations between both algorithms} data \new{displayed in Figure \ref{2}}. (a) is from the clean data. (b) represents the noisy data. (c) shows the observed data. (d) is from the DRR approach. (e) is from the proposed method. The amplitude spectrum of the true data and that of the proposed method are very close to each other.}
%		\label{5}
%	\end{figure}
%}
%\dlo{According to the f-x spectra of each corresponding 5-D data, we specify that Figures \ref{6} and \ref{7} denote the f-x spectra in one common midpoint and offset gathers, respectively. From these figures, we find that the f-x spectra of our method displayed in Figures \ref{6}(e) and \ref{7}(e) are much smoother and clearer than those of the DRR algorithm shown in Figures \ref{6}(d) and \ref{7}(d). The f-x spectra comparison corroborates the better restoration performance of our approach in the frequency domain. Therefore, we deduce that the proposed method can obtain successful results even though the observed noisy and incomplete data have very low frequencies as shown in Figures \ref{5}(c), \ref{6}(c) and \ref{7}(c).}

%\AtEndDocument{
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencycmpclean}
%			\label{a}}
%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencycmpnoisy}
%			\label{b}}
%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencycmpobserved}
%			\label{Fiigure:c}}\\
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencycmpdrr}
%			\label{Fiigure:d}}
%%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencycmpproposed}
%			\label{Fiigure:e}}
%		\caption{Common midpoint f-x spectrum comparison of each 5-D synthetic data ($Nx_1$ = 6, $Nx_2$ = 6) after 10 iterations between both algorithms. (a-c) show the f-x spectra of clean, noisy, observed data, respectively. (d and e) show f-x spectra after using the DRR approach and the proposed approach, respectively.}
%		\label{9}
%	\end{figure}
%	\begin{figure}[htb!]

%		\centering
%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencyOffsetclean}
%			\label{a}}
%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencyOffsetnoisy}
%			\label{b}}
%%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencyOffsetobserved}
%			\label{Fiigure:c}}\\
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencyOffsetdrr}
%			\label{Fiigure:d}}
%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencyOffsetproposed}
%			\label{Fiigure:e}}
%		\caption{Common offset f-x spectrum comparison of each 5-D synthetic data ($x_1$ = 6, $x_2$ = 6) after 10 iterations between both algorithms. (a-c) display the f-x spectra of clean, noisy, observed data, respectively. (d and e) display the f-x spectra after using the DRR approach and the proposed approach, respectively.}
%		\label{10}
%	\end{figure}
%}
Moreover, we conduct several numerical tests to compare the performances of both algorithms. The key idea of these experiments is to provide a practical guideline by quantifying the performance of both methods. They are implemented in terms of iterations number, \dlo{the} percentage of missing data, and \dlo{the}noise levels. Using the same observed noisy and incomplete 5D synthetic data corrupted by a noise level of $0.3$ and $70\%$ of missing traces, we \dlo{first} highlight the behavior of each method in terms of S/N \dlo{and RMSE}to the iteration numbers. \dlo{Figures \ref{11}(a) and \ref{11}(b) show the S/N and rms error diagrams respectively, for}\wen{Figure \ref{SNR_with_iterations} shows} the S/N \wen{values} for the iteration numbers \dlo{ranged}\wen{ranging} from $5$ to $30$. The blue and red lines indicate the S/N diagrams of the DRR method and the proposed approach, respectively. As shown on the figure\dlo{these figures}, it is visible that the proposed method surpasses the DRR method in terms of S/N\dlo{and RMSE}. \dlo{In both cases,}\wen{From this comparison, we find that} when the iteration number becomes large (approximately $25$), the S/N \wen{values} tends to decrease slightly.\dlo{Thus, the RMSE increases slowly.} We can therefore deduce from this analysis that both approaches behave the same way even though the proposed method is still better than the DRR method. From this comparison, which greatly highlights the accuracy of both methods concerning the iteration numbers, we can intuitively know the performance of each framework in terms of S/N \dlo{and RMSE}as the iteration number increase\wen{s}. 
\wen{From this figure, the best result from the proposed approach is at 15 iterations, whereas the best result from DRR is at 20 iterations. We find that the proposed method could save \old{$\frac{1}{4}$}\wen{25\%} of the computation\dlo{s} time, and \dlo{ten}\wen{10} \dlo{weight}\wen{weighted} POCS-like iterations can be used for the proposed method. Therefore, all examples in this paper are conducted with \dlo{ten}\wen{10} iterations.}

\AtEndDocument{
	\begin{figure}[htb!]
		\centering
		\includegraphics[width=0.5\textwidth]{Fig/SNR_with_iterations}
		\caption{Comparison of S/N diagrams regarding the iteration numbers. The blue and red lines correspond to the DRR and the proposed approaches, respectively. The performance of the proposed method is better than that of the DRR method as the iteration number increases. We decimated $70\%$ of traces and added a noise level of $0.3$ for this test.}
		\label{SNR_with_iterations}
	\end{figure}
}%fig.5
%\AtEndDocument{
%	\begin{figure}[htb!]
%		\centering
%		\includegraphics[width=0.5\textwidth]{Figures/SNRwithiterations}
%	\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSEwithiterations}
%			\label{b}}
%		\caption{Comparison of SNR diagrams with respect to the iteration number. The blue and red lines correspond to the DRR method and the proposed approach, respectively. The accuracy of the proposed method is better than the DRR method as the iteration number increases. We decimated $70\%$ of traces and added a noise level of $ 0.3 $.}
%		\label{11}
%	\end{figure}
%}
Then, we use $0.3$ as noise variance and we realize nine experiments with different decimated 5D synthetic data ranging from $10\% $ to $90\% $. Figure \dlo{\ref{12}(a)}\wen{\ref{SNR_with_MissingTraces}\dlo{(a)}} \dlo{and (b) show respectively the SNR and RMSE}\wen{shows the S/N} diagrams with respect to the percentage of decimated data. At last, we randomly decimate $90\%$ of the 5D synthetic data and we conduct six tests using different noise levels 0.05, 0.2, 0.4, 0.6, 0.8 and 1. 
Figure \dlo{\ref{13}(a)}\wen{\ref{SNR_with_noise_levels}\dlo{(b)} denotes}\dlo{present respectively,} the S/N \dlo{and RMSE}diagrams regarding noise levels. In both cases, the blue and red lines denote the diagrams of the restored data using the DRR approach and our method, respectively. As can be observed from the figures, our method performs better than the DRR method. When the percentage of decimated data becomes large, the distance between the DRR method and the RDRR method also becomes \dlo{imposing}\wen{more apparent}. Manifestly, when the noise variances increase, the \dlo{distance}\wen{difference} between both methods also decreases. However, the \dlo{distance}\wen{difference} between both diagrams is \dlo{still imposing}\wen{always evident.} From the diagrams presented, we deduce that our algorithm provides better results than the DRR method in terms of S/N\dlo{and RMSE}. Thus, the proposed RDRR method can be used to denoise 5D seismic data while reconstructing the missing values even in the conditions of a high degree of missing traces and strong random noise.

\AtEndDocument{
	\begin{figure}[htb!]
		\centering
		\subfloat[]{\includegraphics[width=0.5\textwidth]{Fig/SNR_with_MissingTraces}
			\label{SNR_with_MissingTraces}}
		\subfloat[]{\includegraphics[width=0.5\textwidth]{Fig/SNR_with_noise_levels}
			\label{SNR_with_noise_levels}}
		\caption{Comparison of S/N\dlo{(a) and RMSE (b)} diagrams after \dlo{ten}\wen{10} iterations between \dlo{both}\wen{two} algorithms. (a) S/N diagrams for the percentage of missing data. (b) S/N diagrams concerning the noise levels. In both cases, the blue and red lines correspond to the DRR and the proposed approaches, respectively. The red line still presents \dlo{the least RMSE} higher \wen{S/N values}. We used a noise variance of $0.3$, and then we decimated the traces from $10$ to $90\%$ for this demonstration.}
		\label{SNR_with_MissingTraces,SNR_with_noise_levels}
	\end{figure}
}%fig.6

%\AtEndDocument{
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[%width=0.5\textwidth]{Figures/%SNRwithMissingTraces}
%			\label{a}}
%%		\subfloat[]{\includegraphics[%width=0.5\textwidth]{Figures/%SNRwithnoiselevels}
%			\label{b}}
%	\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSEwithmissingTraces}
%			\label{b}}
%		\caption{Comparison of SNR \old{(a) and RMSE (b)} diagrams for the percentage of missing data (a) and noise levels (b)  after 10 iterations between both algorithms. The blue and red line corresponds to the DRR method and the proposed approach, respectively. The red line still presents \old{the least RMSE} higher \new{SNRs values}. We used a noise variance of $ 0.3 $, and then, decimated the %traces from $ 10 $ to $ 90\% %$.}
%		\label{12}
%	\end{figure}
%}
%\dlo{At last, we randomly decimate $ 90\% $ of the 5-D synthetic data and we conduct six tests using different noise levels 0.05, 0.2, 0.4, 0.6, 0.8 and 1. Figures \ref{13}(a-b) present respectively, the SNR and RMSE diagrams with respect to noise levels. After analysis of the plotted results, it is evident that the SNR diagrams using the proposed method presented in red line is always superior to that of the DRR in blue line. The relative errors values of the proposed approach (red line) are still fewer than that of the DRR approach (blue line). It is well visible that the proposed method yields smaller denoising and reconstruction errors than the DRR method. Manifestly, when the noise variances increase, the distance between both low-rank methods also decreases. However, the distance between both diagrams is still imposing. From the diagrams presented, we deduce that our algorithm provides better results than the DRR method in terms of SNR and RMSE. Thus, the proposed RDRR method can be used to denoise 5-D seismic data while reconstructing the missing values even in the conditions of a high degree of missing traces and strong random noise.}

%\AtEndDocument{
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/SNRwithnoiselevels}
%			\label{a}}
%		\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSEwithnoiselevels}
%			\label{b}}
%		\caption{Comparison of SNR (a) and RMSE (b) diagrams with respect to noise variance after 10 iterations between both algorithms. The proposed method in the red line outperforms the DRR approach denoted in blue line when the noise level increase. Here, we used 90\% as a percentage of missing traces and then we added the noise variance as shown in the figure.}
%		\label{13}
%	\end{figure}
%}

%\dlo{To corroborate the numerical tests, we display the results for only a single shot gather of each simultaneously denoised and reconstructed signal. The data are from an observed data contaminated by a noise level of $ 0.3 $ and $ 80\% $ of missing data. Here, the following parameters are chosen to examine the performance of both algorithms : rank {$K$ = 6} and a damped factor {$d$ = 2} for the DRR approach. In addition to these values, we used a cooling factor ${\beta = 3.3}$, a rational transfer function coefficient ${e = 0.95}$ and a window size ${T = 1}$ for the proposed algorithm. We run both methods using 10 weighted POCS-like iterations. Figure \ref{14}(a) displays the true data. Figures \ref{14}(b) and (c) denote the noisy data with SNR of -5.38 dB and observed noisy and incomplete data with SNR of $ -1.74 $ dB, respectively. Figures \ref{14}(d) and \ref{14}(e) display the results using the DRR method and the proposed method, respectively. The SNRs are 10.40 dB and 19.18 dB for the DRR approach and the proposed approach, respectively. Figures \ref{15}(a) corresponds to the RMSE result of the DRR method and  Figures \ref{15}(b) is from the proposed method. The useful signal is recovered with an RMSE of $4.89\%$ and $1.56\%$ respectively for the DRR approach and our algorithm. We then compare the corresponding frequency-wavenumber spectra of the clean, noisy, observed, simultaneously denoised and reconstructed data form the former algorithm and the proposed approach. They are respectively displayed in Figures \ref{16}(a-e) to see the performance in other domain. Here, our algorithm provides smoother and clear results than the DRR method. Indeed, the frequency-wavenumber spectrum obtained with the proposed approach is even clearer than that of the DRR method.} 
\wen{To corroborate the numerical tests, we display the results for only a single shot gather of each simultaneously denoised and reconstructed signal. The results are from an observed data contaminated by a noise level of $0.3$ and $80\%$ of missing data. Here, we select the following parameters to examine the performance of both algorithms: rank {$K$ = 6} and a \dlo{damped}\wen{damping} factor {$d$ = 2} for the DRR approach. In addition to these values, we use a cooling factor ${\beta = 3.3}$, a rational transfer function coefficient ${e = 0.95}$ and a window size ${T = 1}$ for the proposed algorithm. We run both methods using \dlo{ten}\wen{$10$} weighted POCS-like iterations. Figure \ref{synth-clean-hxhy-s}\dlo{(a)} displays the true data. Figures \ref{synth-noisy-hxhy-s}\dlo{(b)} and \ref{synth-obs-hxhy-s}\dlo{(c)} denote the noisy data with S/N of $-5.38$ dB and observed noisy and incomplete data with S/N of $-1.74$ dB, respectively. Figures \ref{synth-drr-hxhy-s}\dlo{(d)} and \ref{synth-rdrr-hxhy-s}\dlo{(e)} display the results using the DRR method and the proposed method, respectively. The SNRs are $10.40$ and $19.18$ dB for the DRR approach and the proposed approach, respectively. Figures \ref{synth-drr-hxhy-s-e}\dlo{(a)} and \ref{synth-rdrr-hxhy-s-e}\dlo{(b)} are the rms error \dlo{results}\wen{figures} of the DRR method and the proposed method, respectively. The useful signal is recovered with an rms error of $4.89\%$ and $1.56\%$ respectively for the DRR approach and our approach.}

\AtEndDocument{
\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_linear_NV03_MT80/Fig/synth-clean-hxhy-s}\label{synth-clean-hxhy-s}}
	\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_linear_NV03_MT80/Fig/synth-noisy-hxhy-s}\label{synth-noisy-hxhy-s}}
	\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_linear_NV03_MT80/Fig/synth-obs-hxhy-s}\label{synth-obs-hxhy-s}}\\
	\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_linear_NV03_MT80/Fig/synth-drr-hxhy-s}\label{synth-drr-hxhy-s}}
	\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_linear_NV03_MT80/Fig/synth-rdrr-hxhy-s}\label{synth-rdrr-hxhy-s}}
	\caption{Simultaneous reconstruction and denoising \wen{2D figures} comparison in only a single shot gather. (a) Clean data. (b) Noisy data with a variance of $0.3$. (c) Observed noisy with $80\%$ of missing traces. (d and e) Simultaneously denoised and reconstructed data using the DRR method the proposed approach, respectively.}
	\label{synth-clean-hxhy-s,synth-noisy-hxhy-s,synth-obs-hxhy-s,synth-drr-hxhy-s,synth-rdrr-hxhy-s}
\end{figure}%fig.7
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/single_shot_Clean_0380}
%			\label{single_shot_Clean_0380}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/single_shot_Noisy_0380}
%			\label{single_shot_Noisy_0380}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/single_shot_Observed_0380}
%			\label{single_shot_Observed_0380}}\\
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/single_shot_DRR_0380}
%			\label{single_shot_DRR_0380}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/single_shot_Proposed_0380}
%			\label{single_shot_Proposed_0380}}
%		\caption{Simultaneous reconstruction and denoising \wen{2-D figures} comparison in only a single shot gather. (a) Clean data. (b) Noisy data with a variance of $0.3$. (c) Observed noisy with $80\%$ of missing traces. (d and e) Simultaneously denoised and reconstructed data using the DRR method the proposed approach, respectively.}
%		\label{single_shot_Clean_0380,single_shot_Noisy_0380,single_shot_Observed_0380,single_shot_DRR_0380,single_shot_Proposed_0380}%fig.7
%	\end{figure}
	\begin{figure}[htb!]
		\centering
		\subfloat[]{\includegraphics[width=0.5\textwidth]{synth_linear_NV03_MT80/Fig/synth-drr-hxhy-s-e}\label{synth-drr-hxhy-s-e}}
		\subfloat[]{\includegraphics[width=0.5\textwidth]{synth_linear_NV03_MT80/Fig/synth-rdrr-hxhy-s-e}\label{synth-rdrr-hxhy-s-e}}	
		\caption{Simultaneous reconstruction and denoising error \wen{2D figures} comparison of only one shot gather extracted from the 5D data matrix. (a) DRR approach with an rms error of $4.89\%$. (b) Proposed approach with an rms error of $1.56\%$.}
		\label{synth-drr-hxhy-s-e,synth-rdrr-hxhy-s-e}
	\end{figure}
}%fig.8
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/WaveNumberclean}
%			\label{a}}
%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/WaveNumbernoisy}
%			\label{b}}
%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/WaveNumberObserved}
%			\label{Fiigure:c}}\\
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/WaveNumberdrr}
%			\label{Fiigure:d}}
%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/WaveNumberproposed}
%			\label{Fiigure:e}}
%		\caption{Frequency-wavenumber spectra comparison of a group of only one shot gathers (15) extracted from the 5-D data matrix. (a-c) correspond to the clean data, noisy data with a variance of 0.3 and observed data with $ 80\% $ of missing data, respectively. (c and d) denote the DRR approach and the proposed framework, respectively.}
%		\label{12}
%	\end{figure}
%}
Figure \dlo{\ref{17} and \ref{19}}\wen{\ref{synth-drr-hxhy-s0290,synth-rdrr-hxhy-s0290,synth-drr-xy-s0290,synth-rdrr-xy-s0290}} illustrates the numerical analysis\dlo{, respectively} in one common midpoint \dlo{($Nx_1$ = 6, $Nx_2$ = 6)}\wen{($x$ = 6, $y$ = 6)} and offset \dlo{($x_1$ = 6, $x_2$ = 6)}\wen{($hx$ = 6, $hy$ = 6)} gathers of each simultaneously denoised and reconstructed signal from \dlo{the}\wen{an} observed data corrupted by a noise variance of $0.2$ and $90\%$ of missing data. \wen{The S/N of this observed data $-0.23$ dB.} In these conditions, we use a rank {$K$ = 6} and a \dlo{damped}\wen{damping} factor {$d$ = 2} for the DRR approach. \dlo{In addition to}\wen{Based on} these parameters, we use a cooling factor ${\beta = 2.5}$, a rational transfer function coefficient ${e = 0.891}$ and a window size ${T= 1}$ for the proposed approach. We run both methods using \dlo{ten}\wen{$10$} weighted POCS-like iterations. Figures \ref{synth-drr-hxhy-s0290}\dlo{(a)} and \ref{synth-drr-hxhy-s0290}\dlo{(c)} display the results of the simultaneous denoising and reconstruction data via the DRR method. The S/N is approximately $5.20$ dB. Figures \wen{\ref{synth-rdrr-hxhy-s0290}\dlo{(b)} and \ref{synth-rdrr-hxhy-s0290}\dlo{(d)}} display the results using the proposed method. The S/N is about $17.84$ dB. \wen{The recovery error using each approach is displayed in Figure \ref{synth-drr-hxhy-s-e0290,synth-rdrr-hxhy-s-e0290,synth-drr-xy-s-e0290,synth-rdrr-xy-s-e0290}. Figures \ref{synth-drr-hxhy-s-e0290}\dlo{(a)} and \ref{synth-drr-xy-s-e0290}\dlo{(c)} show the DRR approach with \wen{an} an rms error of $8.37\%$ and $8.82\%$ in one common-midpoint and one common-offset gather, respectively. Figures \ref{synth-drr-hxhy-s-e0290}\dlo{(b)} and \ref{synth-rdrr-xy-s-e0290}\dlo{(d)} are from the proposed approach with \wen{an} rms error of $2.63\%$ and $2.34\%$ in one common-midpoint and one common-offset gather, respectively. This comparison shows the superiority of the proposed algorithm when the observed data is severely decimated.}
%\dlo{Figures \ref{17}(a) and \ref{19}(a) denote the original data. Figures \ref{17}(b) and \ref{19}(b) are from the noisy data. The SNR of the noisy data is of {$-1.86$ dB}. Figures \ref{17}(c) and \ref{19}(c) show the observed noisy data with $ 90 \% $ missing. The SNR is extremely low with a value of $ -0.23 $ dB. Figures \ref{17}(d) and \ref{19}(d) display the results of the simultaneous denoising and reconstruction data from the DRR method. The SNR is about $ 5.20 $ dB. Figures \ref{17}(e) and \ref{19}(e) display the results from the proposed method. The SNR is about $ 17.84 $ dB. The proposed approach results are much better than those of the DRR method. Figures \ref{18} and \ref{20} show the RMSE from each method in one common midpoint gather and one common offset gather, respectively. Figures \ref{18}(a) and \ref{20}(a) are from the DRR method with RMSE values of $ 8.37 \% $ and $ 8.82 \% $, respectively. Figures \ref{18}(b) and \ref{20}(b) correspond to the proposed method with  RMSE values of $ 2.63 \%$ and $ 2.34 \%$, respectively. This comparison shows the superiority of the proposed algorithm when the observed data is severely decimated.}

\AtEndDocument{
	\begin{figure}[htb!]
		\centering
		\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_linear_NV02_MT90/Fig/synth-drr-hxhy-s0290} 
			\label{synth-drr-hxhy-s0290}}
		\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_linear_NV02_MT90/Fig/synth-rdrr-hxhy-s0290}
			\label{synth-rdrr-hxhy-s0290}}\\
		\centering
		\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_linear_NV02_MT90/Fig/synth-drr-xy-s0290}
			\label{synth-drr-xy-s0290}}
		\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_linear_NV02_MT90/Fig/synth-rdrr-xy-s0290}
			\label{synth-rdrr-xy-s0290}}
		\caption{Simultaneous denoising and reconstruction \wen{2D figures} comparison between \dlo{both}\wen{two} approaches after \dlo{ten}\wen{10} iterations. (a and c) display the DRR approach in one common-midpoint and one common-offset gather, respectively. (b and d) display the proposed approach in one common-midpoint and one common-offset gather, respectively. We used an observed data corrupted by a noise variance of $0.2$ and $90\%$ of missing data for this example.}
		\label{synth-drr-hxhy-s0290,synth-rdrr-hxhy-s0290,synth-drr-xy-s0290,synth-rdrr-xy-s0290}
	\end{figure}
}%fig.9
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSEcmpDRR9002}
%			\label{a}}
%		\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSEcmpProposed9002}
%			\label{b}}
%		\caption{Simultaneous denoising and reconstruction errors comparison of common midpoint 2-D figure ($Nx_1$ = 6, $Nx_2$ = 6) after 10 iterations between both algorithms. (a) shows the DRR approach with an RMSE of $ 8.37\% $. (b) shows the proposed approach with an RMSE of $ 2.63\% $.}
%		\label{14}
%	\end{figure}

%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSEoffsetDRR9002}
%			\label{a}}
%		\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSEoffsetProposed9002}
%			\label{b}}

%		\caption{Simultaneous denoising and reconstruction errors comparison in common offset ($x_1$ = 6, $x_2$= 6) after 10 iterations between both algorithms. (a) displays the DRR approach with an RMSE of $ 8.82\% $. (b) shows the proposed approach with an RMSE of $ 2.34\% $.}
%		\label{16}
%	\end{figure}
%}
\AtEndDocument{
	\begin{figure}[htb!]
		\centering
		\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_linear_NV02_MT90/Fig/synth-drr-hxhy-s-e0290}
			\label{synth-drr-hxhy-s-e0290}}
		\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_linear_NV02_MT90/Fig/synth-rdrr-hxhy-s-e0290}
			\label{synth-rdrr-hxhy-s-e0290}}\\
		\centering
		\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_linear_NV02_MT90/Fig/synth-drr-xy-s-e0290}
			\label{synth-drr-xy-s-e0290}}
		\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_linear_NV02_MT90/Fig/synth-rdrr-xy-s-e0290}
			\label{synth-rdrr-xy-s-e0290}}
		\caption{Simultaneous denoising and reconstruction error \wen{2D figures} comparison between both approaches after \dlo{ten}\wen{10} iterations. (a and c) display the DRR approach with an rms error of $8.37\%$ and $8.82\%$ in one common-midpoint and one common-offset gather, respectively. (b and d) display the proposed approach with an rms error of $2.63\%$ and $2.34\%$ in one common-midpoint and one common-offset gather, respectively.}
		\label{synth-drr-hxhy-s-e0290,synth-rdrr-hxhy-s-e0290,synth-drr-xy-s-e0290,synth-rdrr-xy-s-e0290}
	\end{figure}
}%fig.10
To further examine the performance of both approaches on a higher level of missing traces ($90\%$), we conduct a comparison using the periodogram power spectral density (PSD) of each corresponding 5D synthetic data mentioned in this last test. After a comparison of the different PSD diagrams shown in Figure \dlo{\ref{21}}\wen{\ref{Periodogrampsdcomparison9002}}, we find that the PSD of the restored data from our approach denoted in the red line and that of the true data shown in the green line are much closer to each other than the PSD of the DRR method indicated in \wen{the} the blue line. This comparison vividly \dlo{proves}\wen{demonstrates} that the proposed approach can yield the closest results to the original data\wen{,} even though we are in the conditions of a high level of missing traces.\\
Qualitative and quantitative analysis of these two illustrations conducted by using different noise variances and percentages of missing data further confirm the performance of the proposed approach in terms of accuracy. Note that, as the percentage of missing data increases, the proposed method becomes more accurate than the former approach.

\AtEndDocument{
	\begin{figure}
		\centering
		\includegraphics[width=0.7\textwidth]{Fig/Periodogrampsdcomparison9002}
		\caption{Comparison of the periodogram power spectral density (PSD) of each 5D data set after \dlo{ten}\wen{10} iterations between both algorithms. The green line is from the clean data. The yellow line denotes the noisy data. The observed data is represented by the black line. The blue line corresponds to the DRR method. The red line is from the proposed method. The red and green lines are very close to each other in most areas.}
		\label{Periodogrampsdcomparison9002}
	\end{figure}
}%fig.11
%\dlo{Figure \ref{22} compares the diagrams of percentage of similarity between the original data (green line) and both approaches results. They are first to the iteration number as shown in Figure \ref{22}(a), then ratio of missing data as displayed in Figure \ref{22}(b) and finally noise level as illustrated in Figure \ref{22}(c). Each sub-figure demonstrates that the percentage of similarity between the results obtained via the DRR method (blue line) is much bigger than that of the proposed results (red line). We, therefore, deduce that our approach can reduce the percentage of similarity to a very low level contrary to the DRR method. The diagram of the proposed method is closer to that of the original data as shown by the different sub-figures. The percentage of similarity demonstrates that the proposed approach can produce results closest to the original data.}

%\AtEndDocument{
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/Swithiterations}
%			\label{ a}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/SwithmissingTraces}
%			\label{ b}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/Swithnoiselevels}
%			\label{Fiigure: c}}

%		\caption{Comparison of the percentage of similarity diagrams with respect to (a) iteration number, (b) ratio of decimated data (\%), (c) noise level. In each case, the green, blue and red line denotes the percentage of similarity diagram of the true, DRR, and proposed data, respectively. The green and red lines are closer to each other.}
%		\label{ 22}
%	\end{figure}
%}
\wen{We then conduct another example to demonstrate the effectiveness of the proposed method on 5D synthetic data containing curved events. We compare the performances of the proposed approach to that of the DRR approach. We display the one common-midpoint gather comparison in Figure \ref{hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}. The clean data is displayed in Figure \ref{hyper-clean2d-0}\dlo{(a)}. Figure \ref{hyper-obs2d-0}\dlo{(b)} denotes the observed data with $80\%$ missing values and $0.2$ as noise variance. The significant events are difficult to see due to the percentage of missing traces and strong noise. By using a rank {$K = 12$} and a \dlo{damped}\wen{damping} factor {$d = 3$}, we denoise and reconstruct the observed data with the DRR approach. Based on these same values of $K$ and $d$, we apply our algorithm by using a ${\beta = 5}$, ${e = 0.954}$ and ${T = 1}$. We run both algorithms with \dlo{ten}\wen{$10$} POCS-like iterations. Figures \ref{hyper-drr2d-0}\dlo{(c)} and \ref{hyper-rdrr2d-0}\dlo{(d)} show the recovered data obtained using the DRR and the proposed approaches, respectively.} \wen{Compared to the DRR approach, our method performs much better results. As \dlo{reveals}\wen{revealed by} the comparison, the DRR result seems \wen{to} contain artifacts due to the presence of significant noise, which affects the quality of the useful signal. To see the difference in detail, we magnify a section of each corresponding data displayed in Figure \ref{hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}. The red\dlo{s} frame boxes indicate the magnified section plotted in Figure \ref{hyper-z-clean,hyper-z-obs,hyper-z-drr,hyper-z-rdrr}. The Figures \ref{hyper-z-clean}\dlo{(a)}-\ref{hyper-z-rdrr}\dlo{(d)} correspond to the clean data, observed data, \dlo{recovered data}\wen{and data recovered} using the DRR and the proposed approaches, respectively.} 
\wen{\AtEndDocument{
		\begin{figure}[htb!]
			\centering
			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-clean2d-0}
				\label{hyper-clean2d-0}}\\
			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-obs2d-0}
				\label{hyper-obs2d-0}}\\
			\centering
			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-drr2d-0}
				\label{hyper-drr2d-0}}\\
			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-rdrr2d-0}
				\label{hyper-rdrr2d-0}}		
			\caption{\dlo{2-D figures c}\wen{C}omparison in one common-midpoint gather after \dlo{ten}\wen{10} iterations between \dlo{both}\wen{two} algorithms. (a) Clean data. (b) Observed noisy with $80\%$ of missing traces and $0.2$ as noise variance. (c and d) Simultaneously denoised and reconstructed data using the DRR method the proposed method, respectively.}
			\label{hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}
\end{figure}}} %fig.12

\wen{\AtEndDocument{
		\begin{figure}[htb!]
			\centering
			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-z-clean}
				\label{hyper-z-clean}}\\
			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-z-obs}
				\label{hyper-z-obs}}\\
			\centering
			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-z-drr}
				\label{hyper-z-drr}}\\
			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-z-rdrr}
				\label{hyper-z-rdrr}}	
			\caption{\dlo{{2-D figures c}}\wen{C}omparison of the magnified data displayed in Figure \ref{hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0} (the red frame box). (a) Clean data. (b) Observed noisy with $80 \%$ of missing trace and $0.2$ as noise variance. (c and d) Simultaneously denoised and reconstructed data using the DRR and the proposed approaches, respectively.}
			\label{hyper-z-clean,hyper-z-obs,hyper-z-drr,hyper-z-rdrr}
	\end{figure}}
}%fig.13
%\new{
%To see the difference in detail, we display a single shot gather of each data shown in Figure \ref{16}. The clean data is presented in Figure \ref{16}(a). The sub-figures \ref{16}(b)-\ref{16}(d) correspond to the observed data, the DRR data, and our algorithm data.}

%\new{\AtEndDocument{
%		\begin{figure}[htb!]
%			\centering
%			\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/single_shot_Clean_0280_curvedEvents}
%				\label{a}}
%			\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/single_shot_Observed_0280_curvedEvents}
%				\label{Fiigure:c}}\\
%			\centering
%			\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/single_shot_DRR_0280_curvedEvents}
%				\label{Fiigure:d}}
%			\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/single_shot_Proposed_0280_curvedEvents}
%				\label{Fiigure:e}}	%		
%			\caption{Simultaneous denoising and reconstruction \new{2-D figures} comparison of a single shot gather after 10 iterations between both algorithms. (a) Clean data. (b) Observed data with $ 80\% $ of missing trace and $ 0.2 $ as noise variance. (c and d) Simultaneously denoised and reconstructed data using the DRR method the proposed approach, respectively.}
%			\label{16}
%		\end{figure}}
%}
\wen{
	\dlo{Figures \ref{17} and \ref{18}}\wen{Figure \ref{hyper-drr2d-e,hyper-rdrr2d-e} corresponds} to the error figure of each restored data displayed in Figure \ref{hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}. \dlo{and Figures \ref{16}, respectively}\dlo{Figures \ref{17}(a) and \ref{18}(a) are}\wen{Figure \ref{hyper-drr2d-e}\dlo{(a)} is from the DRR approach}. \dlo{Figures \ref{17}(b) and \ref{18}(b)}\wen{Figure \ref{hyper-rdrr2d-e}\dlo{(b)} denotes the error figure} of the proposed algorithm. From Figures \ref{hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}\dlo{to Figure} \wen{to} \ref{hyper-drr2d-e,hyper-rdrr2d-e}, we find that although the DRR algorithm removes noise and reconstructs the missing traces well, our approach still performs better results. From the magnified data comparison, which vividly \dlo{demonstrate}\wen{demonstrates} the superiority of our approach, we find that the restored data obtained using our approach is much similar to the clean data than those of the DRR result. The visual examination of each subfigure shows that the proposed method offers better simultaneously denoised and reconstructed data. From the fewer errors that \dlo{provides}the proposed algorithm \wen{provides}, we deduce that the recovered data has the smallest amount of artifacts. In this example, the S/N values of the observed data, the recovered data using the DRR method, and the proposed method are {$0.58$}, {$10.94$}, and {$18.43$ dB}, respectively. The DRR approach and the proposed approach achieve the simultaneous denoising and reconstruction process with rms error values $9.07\%$ and $3.08\%$, respectively. Based on the numerical analysis, it is evident that the proposed algorithm can produce higher S/N values, consequently\wen{,} lower rms error values, and thus, the recovered data can be much \dlo{similar}\dlo{related}\wen{closer} to the clean data. We deduce that our algorithm can introduce fewer artifacts. The visual examination and the numerical test comparison demonstrate the recovery improvement of our algorithm on curved events.}
\wen{
	\AtEndDocument{
		\begin{figure}[htb!]
			\centering
			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-drr2d-e}
				\label{hyper-drr2d-e}}\\
			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-rdrr2d-e}
				\label{hyper-rdrr2d-e}}			
			\caption{Simultaneous denoising and reconstruction error comparison in common-midpoint gather. \dlo{(a) Simultaneously denoised and reconstructed errors using the DRR method with an rms error of $9.07\%$. (a) Simultaneously denoised and reconstructed errors using the proposed method with an rms error of $3.08\%$.}\wen{(a) \dlo{shows the 2-D figures of t}\wen{T}he error using the DRR method with an rms error of $9.07\%$. (b) \dlo{displays the 2D figures of t}\wen{T}he error using the proposed method with an rms error of $3.08\%$.}}
			\label{hyper-drr2d-e,hyper-rdrr2d-e}
	\end{figure}}
}%fig.14
%\new{
%	\AtEndDocument{
%		\begin{figure}[htb!]
%			\centering
%			\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSE_single_shot_DRR_0280_curvedEvents}
%				\label{a}}
%			\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSE_single_shot_Proposed_0280_curvedEvents}
%				\label{b}}
%			\caption{Simultaneous denoising and reconstruction error \new{2-D figures} comparison in a single shot gather. (a and b) Simultaneously denoised and reconstructed error using the DRR approach the proposed approach, respectively.}
%			\label{18}
%		\end{figure}}}

\wen{
	To demonstrate the performance of the proposed approach in other perspective\wen{s}, we display in Figure \dlo{\ref{19}}\wen{\ref{fx_clean_curved,fx_Observed_curved,fx_DRR_curved,fx_Proposed_curved}}, the corresponding f-x spectra of each data shown in Figure \dlo{\ref{16}}\wen{\ref{hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}}. The \dlo{sub-figures \dlo{\ref{19}(a)-\ref{19}(d)}\wen{\ref{15}(a)-\ref{15}(d)}}Figures \wen{\ref{fx_clean_curved}-\ref{fx_Proposed_curved}} correspond to the f-x spectra of the clean data, the observed data, the restored data using the DRR and the proposed approaches, respectively. From the comparison of each subfigure, we find that both approaches can successfully denoise and reconstruct the missing values in the whole frequency band (from $0$ \new{Hz} to $125$ Hz). However, a detailed comparison highlights the greatest difference between both approaches. Indeed, based on the lower frequencies (from $0$ \wen{Hz} to approximately $40$ Hz), we can affirm that our algorithm further \dlo{remove}\wen{removes} the noise energy to a weaker degree and improves the signal quality compared with the DRR algorithm, which shows the better quality of the recovered results using our algorithm. From this analysis, we can intuitively deduce that our approach can successfully remove the random noise while reconstructing the useful signal more adequately than the DRR approach.}		
\wen{	
	\AtEndDocument{
		\begin{figure}[htb!]
			\centering
			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/fx_clean_curved}
				\label{fx_clean_curved}}
			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/fx_Observed_curved}
				\label{Fiigure:fx_Observed_curved}}\\
			\centering
			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/fx_DRR_curved}
				\label{fx_DRR_curved}}
			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/fx_Proposed_curved}
				\label{fx_Proposed_curved}}		
			\caption{\dlo{One single shot gathers}Frequency-space (f-x) spectra comparison after \dlo{ten}\wen{10} iterations between \dlo{both}\wen{two} algorithms. (a and b) The clean data and observed data, respectively. (c and d) The DRR approach and the proposed framework, respectively.}
			\label{fx_clean_curved,fx_Observed_curved,fx_DRR_curved,fx_Proposed_curved}
	\end{figure}}
}%fig.15

%\dlo{\wen{To further demonstrate the performance of the proposed method on curved events, we compare the amplitude spectrum of each data shown in Figure \ref{14}. Figure \dlo{\ref{20}} \wen{\ref{18}} displays the comparison. The sub-figures \dlo{\ref{20,}(a)-\ref{20}(d)} \wen{\ref{18}(a)-\ref{18}(d)} correspond to the amplitudes spectra of the clean data, observed data, recovered data using the DRR approach and the proposed approach, respectively. The amplitude spectrum using our approach is very similar to the clean data than that of DRR approach. From this comparison, we find that the proposed approach can greatly restore the amplitude of the useful signal in the whole frequency band even though the data to be recovered has very low SNR that can seriously affect its amplitude. From the amplitude spectra comparison, it is evident that the proposed algorithm can conserve the significant feature of the recovered data than the DRR approach.}}   
%\wen{
%\AtEndDocument{
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/Amplite_spectrum_comparison_curved_data_clean}
%			\label{a}}
%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/Amplite_spectrum_comparison_curved_data_observed}
%			\label{Fiigure:c}}\\
%		\centering
%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/Amplite_spectrum_comparison_curved_data_DRR}
%			\label{Fiigure:d}}
%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/Amplite_spectrum_comparison_curved_data_Proposed}
%			\label{Fiigure:e}}		
%		\caption{Amplitude spectra comparison after 10 iterations between both algorithms. (a and b) correspond to the clean data and the observed data, respectively. (c and d) denote the DRR approach, and the proposed framework, respectively.}
%		\label{18}
%	\end{figure}}
%}

\wen{In the presence of random noise and missing traces, we evaluate the quality of the simultaneously denoised and reconstructed data using both approaches after \dlo{ten}\wen{$10$} iterations. We fix the noise variance at $0.2$ while varying the missing traces from $10\%$ to $90\%$, and we measure the S/N values. Figure \dlo{\ref{21}}\wen{\ref{snr_missing_traces_curvedD}} shows the S/N values as functions of missing traces. From this figure \dlo{above mentioned}\wen{mentioned above}, it is undeniable that as the percentage of missing trace becomes large, the proposed method (the red line) consistently provides higher values of S/N than the DRR approach (the blue line). For both approaches, the simultaneous denoising and reconstruction quality decreases as the percentage of missing traces \dlo{increase}\wen{increases}. However, our algorithm can provide \wen{a} satisfactory result\wen{,} even though the observed data is corrupted with a significant ratio of missing traces and noise levels. These numerical and visual \dlo{analyses}\wen{analyses} further confirm the adaptability of our approach \dlo{on}\wen{to} data containing curved events. 
}
\wen{
	\AtEndDocument{
		\begin{figure}[htb!]
			\centering
			\includegraphics[width=0.5\textwidth]{Fig/snr_missing_traces_curvedD}	
			\caption{Comparison of S/N diagrams for the percentage of missing data after \dlo{ten}\wen{10} iterations between \dlo{both}\wen{two} algorithms on data containing curved events. The blue and red lines correspond to the DRR method and the proposed approach, respectively. The red line still presents higher S/N values. We used a noise variance of $0.2$ and then decimated the traces from $10$ to $90\% $ for this comparison.}
			\label{snr_missing_traces_curvedD}
	\end{figure}}
}%fig.16

In order to evaluate the computing time, we test the efficiency of each approach on different 5D synthetic data sizes after \dlo{ten}\wen{10} iterations and a frequency band \wen{of} $0$-$100$ Hz. The comparison of the running time is shown in Table \ref{tbl:table1}. \dlo{Let us mention that b}\wen{B}oth algorithms have been performed on an Intel Core i7 7th generation running MATLAB codes (R2017a). From this comparison, we can note a \dlo{small}\wen{little} bit of difference between both approaches in favor of our method. Because of this relatively less difference, we deduce that the computation time of these methods is almost the same. However, we find that as the size of the matrix increases, the computation time also increases for both approaches. The same is true for the number of iterations and the frequency.

\subsection{Field data examples}
To verify the performance of our approach in practice, we apply both algorithms on a 5D field seismic data. Here, we have considered a visual examination of the results obtained via both methods to demonstrate the performances of our algorithm.
%\dlo{Figures \ref{23}, \ref{24} and \ref{25} display the comparison in one common midpoint gather, one common offset gather and 500 traces, respectively. Figures \ref{23}(a), \ref{24}(a) and \ref{25}(a) show the observed noisy and incomplete data. In this example, about 75\% of traces are missing. To preserve the significant features of the useful signal, we select rank {$K= 6$} and damping factor {$d = 2$} for the DRR approach. Figures \ref{23}(b), \ref{24}(b) and \ref{25}(b) present the results of this approach. The DRR method obtains successful results. Indeed, the recovery of the missing data is perfect. However, coherent events cannot be seen clearly due to the presence of residual noise in the results. In addition to the same parameters used for the DRR method, we use a cooling factor $\beta= 3$, a rational transfer function coefficient ${e= 0.9}$ and a window size ${T= 1}$ for the proposed method. We run both programs using 10 weighted {POCS-like} iterations. As can be seen in Figures \ref{23}(c), \ref{24}(c) and \ref{25}(c), which display the results obtained by the proposed approach, all useful signal\wen{s} \dlo{is}\wen{are} perfectly recovered. All significant events are highlighted and can be perceived without much effort on each sub-figures mentioned. To better compare them in detail, we zoom a portion from each sub-figure in Figure \ref{25} and display the comparison in Figure \ref{26}. The red frame boxes are shown in Figure \ref{25} to highlight the zoomed data. After a comparison of the Figures \ref{26}(a-c), it is obvious that our method provides better results than those of the DRR approach. The zoomed data comparison further demonstrates the accuracy of our algorithm.}
\wen{Figures \dlo{\ref{22} and \ref{23}}\wen{\ref{cmp_field_obseerved,cmp_field_DRR,cmp_field_proposed} and \ref{offset_field_obseerved,offset_field_DRR,offset_field_Proposed}} display the comparison in one common-midpoint and one common-offset gather, respectively. Figures \dlo{\ref{22}}\wen{\ref{cmp_field_obseerved}}\dlo{(a)} and \dlo{\ref{23}}\wen{\ref{offset_field_obseerved}}\dlo{(a)} show the observed noisy and incomplete data. In this example, approximately $75\%$ of traces are missing. To preserve the significant features of the useful signal, we select rank {$K= 6$} and damping factor {$d = 2$} for the DRR approach. Figures \dlo{\ref{22}}\wen{\ref{cmp_field_DRR}}\dlo{(b)} and \dlo{\ref{23}}\wen{\ref{offset_field_DRR}}\dlo{(b)} show the results\dlo{of this approach}. The DRR method obtains successful results. Indeed, the recovery of the missing data is \old{perfect}\wen{better}. However, coherent events cannot be seen clearly \dlo{due to the presence of}because of residual noise in the results. In addition to the same parameters used for the DRR method, we use a cooling factor $\beta= 3$, a rational transfer function coefficient ${e= 0.9}$, and a window size ${T= 1}$ for the proposed method.} We run both \dlo{programs}\wen{algorithms} using \dlo{ten}\wen{10} weighted {POCS-like} iterations. As can be seen in Figures \dlo{\ref{22}}\wen{\ref{cmp_field_proposed}}\dlo{(c)} and \dlo{\ref{23}}\wen{\ref{offset_field_Proposed}}\dlo{(c)}, which display the results obtained by the proposed approach, all useful signal\wen{s} \dlo{is}\wen{are} perfectly recovered. \dlo{All}\wen{The} significant events are highlighted and can be perceived without much effort on each subfigure\dlo{mentioned}. \wen{For further comparison, we display in Figures \dlo{\ref{24}(a)-\ref{24}(c)}\wen{\ref{Zoomed_offset_field_obseerved}\dlo{(a)}-\ref{Zoomed_offset_field_Proposed}\dlo{(c)}}, the magnified section of each subfigure \dlo{\ref{23}(a)-\ref{23}(c)}\wen{\ref{offset_field_obseerved}\dlo{(a)}-\ref{offset_field_Proposed}\dlo{(c)}}, which are highlighted by the green frame boxes, respectively. The magnified data reveals \dlo{the presence of}\wen{some} curved events in one common offset gather. We can therefore deduce that although the field data \dlo{is}\wen{are} mainly composed of linear events, it is also \dlo{consist}\wen{consisted} of curved events in some sections. From\dlo{,} the magnified data comparison, it is obvious that the proposed method provides better results than \dlo{those of}the DRR method. The magnified data comparison further demonstrates the accuracy of our algorithm.} 
%\old{
%\AtEndDocument{
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\te%xtwidth]{Figures/cmpObservedfielddata}
%			\label{ a}}
%		\subfloat[]{\includegraphics[width=0.3\te%xtwidth]{Figures/cmpDRRfielddata}
%			\label{ b}}
%		\subfloat[]{\includegraphics[width=0.3\te%xtwidth]{Figures/cmpProposedfielddata}
%			\label{Fiigure: c}}

%		\caption{Common midpoint gather comparison. (a) Observed noisy and incomplete data. (b-c) denote the simultaneously denoised and reconstructed data using the DRR method %and the proposed approach, respectively.}
%		\label{23}
%	\end{figure}
%	
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\te%xtwidth]{Figures/offsetObservedfielddata}
%			\label{ a}}
%		\subfloat[]{\includegraphics[width=0.3\te%xtwidth]{Figures/offsetDRRfielddata}
%			\label{ b}}
%		\subfloat[]{\includegraphics[width=0.3\te%xtwidth]{Figures/offsetProposedfielddata}
%			\label{Fiigure: c}}

%		\caption{Common offset gather comparison. (a) Observed data. (b-c) display the simultaneously denoised and reconstructed data using the DRR method and the proposed approach, respectively.}
%		\label{ 24}
%	\end{figure}

%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.9\te%xtwidth]{Figures/Tx500tracesObservedfield%data}
%			\label{ a}}\\
%		\subfloat[]{\includegraphics[width=0.9\te%xtwidth]{Figures/Tx500tracesDRRfielddata}
%			\label{ b}}\\
%		\subfloat[]{\includegraphics[width=0.9\te%xtwidth]{Figures/Tx500tracesProposedfielddata}
%			\label{Fiigure: c}}
%		
%		\caption{Comparison of 500 traces extracted from the 5-D field data matrix. (a) shows the observed data. (b-c) denote the simultaneously denoised and reconstructed data using the DRR method and the proposed approach, respectively.}
%		\label{ 25}
%	\end{figure}

%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.5\te%xtwidth]{Figures/ZoomedTx500tracesObserve%dfielddata}
%			\label{ a}}\\
%		\subfloat[]{\includegraphics[width=0.5\te%xtwidth]{Figures/ZoomedTx500tracesDRRfielddata}
%			\label{ b}}
%		\subfloat[]{\includegraphics[width=0.5\te%xtwidth]{Figures/ZoomedTx500tracesPropose%dfielddata}
%			\label{Fiigure: c}}

%		\caption{Comparison of the zoomed sections from Figure \ref{ 25}. (a) shows the observed data. (b-c) denote the simultaneously denoised and reconstructed data using the DRR method and the proposed approach, respectively.}
%		\label{ 26}
%	\end{figure}
%}
%}
\dlo{On the other hand, we compare both methods using the corresponding f-x spectrum and normalized PSD of the 500 traces of aforementioned data. Figures \ref{27} and \ref{28} display the f-x spectrum and normalized PSD, respectively. In Figure \ref{27}, (a) denotes the f-x spectrum of the observed noisy and incomplete data. (b) is from the DRR approach and (c) corresponds to the f-x spectrum of the proposed approach. The yellow, blue and red lines shown in Figure \ref{28} are the normalized PSD of the decimated data, the restored data from the DRR algorithm and our approach, respectively.}
%\old{
%\AtEndDocument{
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.7\te%xtwidth]{Figures/fx500tracesobservedfielddata}
%			\label{ a}}\\
%		\subfloat[]{\includegraphics[width=0.7\te%xtwidth]{Figures/fx500tracesdrrfielddata}
%			\label{ b}}\\
%		\subfloat[]{\includegraphics[width=0.7\te%xtwidth]{Figures/fx500tracesproposedfielddata}
%			\label{Fiigure: c}}

%		\caption{Frequency-space (f-x) spectra comparison of the corresponding 500 traces of each 5-D seismic field data. (a) shows the f-x spectrum of the decimated data, (c and d) correspond to the f-x spectra obtained after using the DRR method and the proposed framework, %respectively.}
%		\label{ 27}
%	\end{figure}

%	\begin{figure}
%		\centering
%		\includegraphics[width=0.8\textwidth]{Figures/NormalizedPSDfielddata}
%		\caption{Comparison of the normalized power spectral density (PSD) of the corresponding 500 traces of each 5-D seismic field data. The yellow line shows the PSD of the observed data. The blue and red lines denote the PSD of the simultaneously denoised and reconstructed data using the DRR approach and the proposed approach, respectively.}
%		\label{ 28}
%	\end{figure}
%}
%}
%\dlo{Simultaneous analysis of the f-x spectrum and normalized PSD better prove that random noise contained in the decimated data cannot be completely attenuated by only using the damping operator. From the comparison, we find that our method can yield perfect results than the DRR approach. It is visible that the red line is smoother than the blue line (see Figure \ref{28}) due to the less noise in the restored data. Thus, the simultaneous denoising and reconstruction errors of the proposed approach are very smaller than that of the DRR method. The f-x spectrum and PSD further verify the better recovering quality of our algorithm. From Figures \ref{27}, \ref{28}, we deduce that the proposed approach can provide a higher resolution than the DRR method.}

\AtEndDocument{
	\begin{figure}[htb!]
		\centering
		\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/cmp_field_obseerved}
			\label{cmp_field_obseerved}}
		\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/cmp_field_DRR}
			\label{cmp_field_DRR}}
		\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/cmp_field_proposed}
			\label{cmp_field_proposed}}
		\caption{Common midpoint gather \wen{2D figures} comparison. (a) Observed noisy and incomplete data with about $75\%$ of missing traces. (b and c) denote the simultaneously denoised and reconstructed data using the DRR approach and the proposed approach, respectively.}
		\label{cmp_field_obseerved,cmp_field_DRR,cmp_field_proposed}
\end{figure}}%fig.17
\wen{
	\AtEndDocument{
		\begin{figure}[htb!]
			\centering
			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/offset_field_obseerved}
				\label{offset_field_obseerved}}
			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/offset_field_DRR}
				\label{offset_field_DRR}}
			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/offset_field_Proposed}
				\label{offset_field_Proposed}}			
			\caption{Common-offset gather \wen{2D figures} comparison. (a) Observed noisy and incomplete data with approximately $75\%$ of missing traces. (b and c) The simultaneously denoised and reconstructed data using the DRR approach and the proposed approach, respectively.}
			\label{offset_field_obseerved,offset_field_DRR,offset_field_Proposed}
	\end{figure}}
}%fig.18
\wen{
	\AtEndDocument{
		\begin{figure}[htb!]
			\centering
			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/Zoomed_offset_field_obseerved}
				\label{Zoomed_offset_field_obseerved}}
			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/Zoomed_offset_field_DRR}
				\label{Zoomed_offset_field_DRR}}
			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/Zoomed_offset_field_Proposed}
				\label{Zoomed_offset_field_Proposed}}
			\caption{Magnified section from Figure \ref{offset_field_obseerved,offset_field_DRR,offset_field_Proposed} (the green frame boxes) comparison. (a) Observed noisy and incomplete data with approximately $75\% $ of missing traces. (b and c) The simultaneously denoised and reconstructed data using the DRR method and the proposed approach, respectively.}
			\label{Zoomed_offset_field_obseerved,Zoomed_offset_field_DRR,Zoomed_offset_field_Proposed}
	\end{figure}}
}%fig.19		 
\wen{
	Moreover, we compare both methods using the corresponding f-x spectrum of each data displayed in Figure \dlo{\ref{23}}\wen{\ref{offset_field_obseerved,offset_field_DRR,offset_field_Proposed}}. \dlo{In Figure \dlo{\ref{25}, \ref{25}(a)}\wen{\ref{20}},}\wen{Figure \ref{fx_offset_obs_field}-\ref{fx_offset_Proposed_field}}\dlo{\ref{20}} denotes the f-x \dlo{spectrum}\wen{spectra} of the observed noisy and incomplete data\dlo{. \dlo{\ref{25}}\dlo{\ref{20}}(b) is from}\wen{,} the DRR approach, and \dlo{\dlo{\ref{25}}\dlo{\ref{20}}(c) corresponds to the f-x spectrum of}the proposed approach, \wen{respectively}. Analysis of the f-x spectra \dlo{better proves}\wen{further shows} that random noise included in the decimated data cannot be completely attenuated by only using the damping operator. From the comparison, we find that our method can yield \dlo{perfect}\wen{better} results than the DRR approach. It is visible that the proposed approach can improve the quality of the useful signal \dlo{due to}\wen{because of} the energy of the events. We can deduce that the simultaneous denoising and reconstruction errors of the proposed approach are \dlo{very}\wen{much} smaller than that of the DRR method. The f-x spectra comparison further verifies the better reconstruction quality of our algorithm. From Figure \dlo{\ref{25}}\wen{\ref{fx_offset_obs_field,fx_offset_DRR_field,fx_offset_Proposed_field}}, we deduce that the proposed approach can provide a higher resolution than the DRR method.}
\wen{	
	\AtEndDocument{
		\begin{figure}[htb!]
			\centering
			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/fx_offset_obs_field}
				\label{fx_offset_obs_field}}
			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/fx_offset_DRR_field}
				\label{fx_offset_DRR_field}}
			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/fx_offset_Proposed_field}
				\label{fx_offset_Proposed_field}}		
			\caption{Frequency-space (f-x) spectra comparison of each data displayed in Figure \dlo{\ref{23}}\wen{\ref{offset_field_obseerved,offset_field_DRR,offset_field_Proposed}}. (a) The f-x spectra of the decimated data. (b and c) The f-x spectra obtained after using the DRR and the proposed approaches, respectively.}
			\label{fx_offset_obs_field,fx_offset_DRR_field,fx_offset_Proposed_field}
		\end{figure}
}}%fig.20
\section{discussion}

This paper investigates the feasibility of the RDRR method \dlo{developed herein}for simultaneous denoising and reconstruction of 5D seismic data. The damping operator, which is one of the key\dlo{s} parameters of the DRR framework, has been introduced into the conventional TSVD formula to further suppress random noise. However, we find that \dlo{using only}\wen{only using} this operator is not enough to recover the useful signal when the percentage of missing traces \wen{and the noise level} \dlo{become}\wen{becomes} large. Hence, how to accurately restore the useful signal \dlo{pays our attention}\wen{becomes our focus}. \dlo{One of the contributions}\wen{The contribution} of this work is the development of the STMA into the existing DRR framework. The proposed algorithm \dlo{that}aims at designing an ideal combination of STMA operator and DRR formula to further enhance the recovery of the useful signal\wen{s}. \dlo{, can \dlo{benefit from} the individual advantage of each operator.}Acceleration of computation time usually \dlo{pays}\wen{attracts} attention \dlo{of}\dlo{to}\wen{from} most researchers when using the low-rank method for seismic data simultaneous denoising and reconstruction. Here, by introducing the STMA operator into the DRR formula, we focus not only on enhancing the computation cost but also \wen{on} random noise removal.

The tight connection established between the STMA operator and the DRR formula compensates for the DRR method. Thus, the RDRR formula can be regarded as an improved DRR formula, which further removes the residual noise and recovers the useful signal.

\wen{Our RDRR framework}\dlo{We understand these clarifications as the physical definition of our robust damped rank-reduction framework, which} uses five keys parameters: rank $K$, damping factor $d$, cooling factor $\beta$ that is used to control the effects of the thresholding parameter $\tau$, the rational transfer function coefficient $e$ and window size $T$. These parameters used in our proposed framework are essential to achieve the \dlo{ultimate}goal of this work. The empirical selection of these five useful parameters usually leads to satisfactory results.

\wen{The proposed RDRR method was implemented by varying $K$, $d$, $\beta$, $e$ and $T$, and the resulting \dlo{SNRs}\wen{S/N} and rms error values were selected as the quantitative measures to \dlo{analysis}\wen{analyze} their influence on the simultaneous denoising and reconstruction performance. In this section, we use the first \dlo{example of synthetic data}\wen{synthetic example} to show the influence of each parameter on the proposed algorithm performance. The parameters $K$, $d$, $\beta$, $e$ and $T$ were set at $6$, $2$, $3.3$, $0.972$ and $1$, respectively to simultaneous denoise and reconstruct observed data corrupted by $0.3$ as noise variance and $70\%$ of missing traces. Figure \wen{\ref{snr_with_K}}\dlo{(a)} shows the influence of $K$ for different values.\dlo{We vary the values of $K$ from $1$ to $10$ while fixing the other parameters to see its influence.} As seen from this subfigure, a $K$ value of $6$ produces a better result in terms of S/N. Thus, we adopted this value of rank to restore the useful signal. Besides, as \dlo{can be seen}observed in Figure \wen{\ref{snr_with_d}}\dlo{(b)}, it is \dlo{explicit}\wen{clear} that \dlo{the damping factor}$d=2$ can positively affect the result. \dlo{we range the damping factor from $1$ to $3$, and plot the results in Figure \ref{26}. From this figure, it is explicit that $d=2$ can positively affect the result.}From Figure \ref{snr_with_beta}\dlo{(c)}, \dlo{it is clear that}$\beta$ of $3$ can produce the best S/N value. Therefore, by adjusting this parameter properly, we adopted \dlo{$\beta$ of $3.3$}\wen{$\beta = 3.3$} to recover the useful signal in this example. \dlo{Then, we change the cooling factor from $1$ to $10$ to see its influence on this result. Figure \ref{26}\dlo{(c)}\wen{c} shows the results. From this figure, $\beta$ of $3$ can produce the best S/N value. Therefore, by adjusting this parameter properly, we adopted $\beta$ of $3.3$ to recover the useful signal in this example. In the same way, we analyze the effect of $e$ by ranging its values from 0.95, 0.96,..., to $1$. As shown in Figure \ref{26}}As shown in Figure \wen{\ref{snr_with_e}}\dlo{(d)}, the best quality of the signal can be provided by fixing $e$ around $0.97$. So, by regulating the parameter accurately, we used $e=0.972$ to recover the useful signal.\dlo{Finally, as displayed in the sub-figure \ref{26} we range the parameter $T$ from $ 1 $ to $ 5 $ to analyze its behavior. The analysis of this diagram demonstrates}\dlo{.} Finally, as displayed in the \dlo{sub-figure}\wen{Figure} \wen{\ref{snr_with_T}}\dlo{(e)}, all values of $T$ set above $1$ produce lower S/N values. Thus, we selected $T$ of $1$ to restore the useful signal. From this analysis, we can \dlo{appreciate}\wen{understand} the contribution of each parameter to the quality of our results.} \wen{The parameter $e$ is \dlo{a} helpful \dlo{tool} to enhance the energy of the useful signal when the best trade-off with the parameter $T$ is reached.}
\wen{\AtEndDocument{
		\begin{figure}[htb!]
			\centering
			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/snr_with_K}
				\label{snr_with_K}}
			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/snr_with_d}
				\label{snr_with_d}}
			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/snr_with_beta}
				\label{snr_with_beta}}\\
			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/snr_with_e}
				\label{snr_with_e}}
			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/snr_with_T}
				\label{snr_with_T}}
			\caption{Influence of the five key parameters under a noise variance of $0.3$ and $70\%$ as missing traces after $10$ iterations. (a) The influence of the rank constraint. (b) The influence of the damping factor. (c) The influence of the cooling factor. (d) The influence of the rational transfer function coefficient. (e) The effect of the window size.
				\label{snr_with_K,snr_with_d,snr_with_beta,snr_with_e,snr_with_T}}
\end{figure}}}%fig.21

\wen{The proposed approach uses \dlo{many}\wen{several} operators to recover the useful signal from the noisy observation. It is therefore necessary to show their influence on the quality of our results. By using the same observed data \dlo{above mentioned}\wen{mentioned above}, we first show the performance of the ST operator, the MA operator, the STMA operator, and the RR operator on the level-4 block Hankel matrix. The S/N of the observed data is $-2.40$ dB. In Figure \dlo{\ref{27}}\wen{\ref{influence_operator_block_HMatrice}}, we plot the S/N\dlo{s} values as a function of iteration numbers ranging from $5$ to $30$.}
\wen{The black, gray, gray dashed, and blue lines correspond to the RR, STMA, MA, and ST operators, respectively. From this figure, we find that the ST operator fails to simultaneously denoise and reconstruct the missing traces whatever the value of the cooling factor used to adjust the threshold parameter. The influence of ST on the level-4 block Hankel is almost insignificant because it provides very low S/N. In contrast, the MA operator can recover the useful signal from the level-4 block Hankel matrix because the S/N\dlo{s} values (Figure \dlo{\ref{27}}\wen{\ref{influence_operator_block_HMatrice}}) are quite acceptable. Note that, when we set $T$ at $2$, and we use the smaller values of $e$ ($e= 0.1,...,0.7$), we cannot obtain acceptable results. The results become acceptable at approximately $e=0.9$. All values of $e$ selected above $1$ damage the features of the useful signal. \dlo{The the amplitude of the signal can be degraded.}}\wen{Besides, when we fix $e$ at $0.99$ while using a small value of window size (e.g., $T=2$), the MA operator cannot \dlo{adequately simultaneous}\wen{effectively} denoise and reconstruct the missing values when it is directly applied to the level-4 block Hankel matrix. The approximation signal contains an important quantity of noise, whereas large values can recover the useful signal from its noisy observation. However, the recovered data lose an important amount of \dlo{data}\wen{signals} in one common midpoint gather. The results in \dlo{one}\wen{the} common-offset gather are \dlo{generally quite}acceptable.}
\wen{As shown in Figure \dlo{\ref{27}}\wen{\ref{influence_operator_block_HMatrice}}, the S/N \dlo{diagram}\wen{values} using the STMA operator \dlo{outperforms}\wen{are higher than} both the ST and MA \wen{S/N} values. We deduce that by combining the ST and the MA operators (STMA), we can \dlo{profit to}\wen{benefit from} their individual performance and thus further influence the level-4 block Hankel matrix. In Figure \dlo{\ref{28}}\wen{\ref{synth-hxhy-s-stma1,synth-hxhy-s-stma2,synth-xy-s-stma1,synth-xy-s-stma2}}, we plot the STMA results first, for $\mathbf{\beta}=80$, $e=0.999$, $T=2$, and then, $\mathbf{\beta}=15$, $e=0.999$, $T=17$. Figures \dlo{\ref{28}(a) and \ref{28}(c) and Figures \ref{28}\dlo{(b)}\new{b} and \ref{28}\dlo{(d)}\wen{d}} \wen{\ref{synth-hxhy-s-stma1}\dlo{(a)} and \ref{synth-xy-s-stma1}\old{(c)} and Figures \ref{synth-hxhy-s-stma2}\dlo{(b)} and \ref{synth-xy-s-stma2}\old{(d)}} show the results using both cases, respectively. The first case yields \wen{S/N =$4.07$} dB \dlo{as SNR}while the second situation \dlo{performs with $10.46$ dB}\wen{S/N = $8.00$} dB after $15$ iterations. From this comparison, we find that when applying the STMA operator directly on the level-4 block Hankel matrix, the larger values of $T$ can provide higher values in terms of S/N. However, the smoothing \dlo{degree} damages the useful signal in one common-midpoint gather (Figure \dlo{\ref{28}}\wen{\ref{synth-hxhy-s-stma2}}\dlo{(b)}). \dlo{Whereas}\wen{However}, the \dlo{one} common-offset gather result (Figure \dlo{\ref{28}}\wen{\ref{synth-xy-s-stma2}}\dlo{(d)}) is satisfactory. From this test, we find that the influence of the ST operator can be seen when it is combined with the MA operator.} \wen{From Figure \dlo{\ref{27}}\ref{influence_operator_block_HMatrice}, the RR operator demonstrates its superiority over the ST, MA, and STMA operators with \wen{a} rank \wen{of} six. From the different tests, we find that for $T=1$, the STMA operator provides the same result as the ST operator whatever the combination of the parameters when it is directly applied to the level-4 block Hankel matrix to recover the useful signal. STMA can simultaneous\new{ly} denoise and reconstruct the level-4 block Hankel matrix when $T>1$. However, all values of $T$ selected above $1$ induce some loss of data in one common-midpoint gather. From our experience, we find that STMA is not adequate to preserve all features of the useful signal when it is directly applied to the block Hankel matrix\wen{.}\dlo{ to denoise and reconstruct the missing traces.} STMA can be introduced in an existing algorithm of denoising and/or reconstruction to improve its performance.}

\wen{\AtEndDocument{
		\begin{figure}[htb!]
			\centering
			\includegraphics[width=0.4\textwidth]{Fig/influence_operator_block_HMatrice}
			\caption{Influence of the operators (ST, MA, STMA, and RR) on the level-4 block Hankel matrix under a noise variance of $0.3$ and $70\%$ as missing traces after \dlo{ten}\wen{$10$} iterations. The blue line corresponds to the ST operator. The dashed and solid gray lines are from the MA and STMA operators, respectively. The black line denotes the RR operator.
				\label{influence_operator_block_HMatrice}}
\end{figure}}
}%fig.22
\AtEndDocument{
	\begin{figure}[htb!]
		\centering
		\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_stma_block_Hankel_matrix/Fig/synth-hxhy-s-stma1}
			\label{synth-hxhy-s-stma1}}
		\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_stma_block_Hankel_matrix/Fig/synth-hxhy-s-stma2}
			\label{synth-hxhy-s-stma2}}\\
		\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_stma_block_Hankel_matrix/Fig/synth-xy-s-stma1}
			\label{synth-xy-s-stma1}}
		\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_stma_block_Hankel_matrix/Fig/synth-xy-s-stma2}
			\label{synth-xy-s-stma2}}
		\caption{Influence of the STMA operator on the level-4 block Hankel matrix. (a and c) The one common-midpoint and and common-offset gather\dlo{2-D figures}, respectively, for \wen{$\mathbf{\beta}=80$, $e=0.999$, $T=2$}. (b and d) The one common-midpoint and common-offset gather, respectively, for \wen{$\mathbf{\beta}=15$, $e=0.999$, \wen{and} $T=17$.}}
		\label{synth-hxhy-s-stma1,synth-hxhy-s-stma2,synth-xy-s-stma1,synth-xy-s-stma2}
	\end{figure}
}%fig.23
\wen{To verify the adaptability of the STMA operator with some iterative denoising and reconstruction methods, we introduce the proposed STMA operator in the damped data-driven optimal singular value shrinkage algorithm \citep{siahsar2017simultaneous} framework for simultaneous denoising and interpolation of 3D seismic. Here, STMA is first applied to the block Hankel matrix before SVD, and then, to the singular values just after the SVD. For this test, we add a noise variance of $0.2$ to the 3D synthetic data and we decimate $50\%$. The S/N of the noisy data and the observed data is approximately $-8.40$ dB and $-5.98$ dB, respectively. Figures \dlo{\ref{29} and \ref{30}}\wen{\ref{syn3d-c-s,syn3d-n-s,syn3d-obs-s,syn3d-opshrinkdamped-s,syn3d-opshrinkdampedstma-s}}\dlo{and \ref{25}} show the 2D slice comparison in the 5th crossline\dlo{ and inline sections, respectively}. Figures \dlo{\ref{29}(a)-\ref{29}(c)}\wen{\ref{syn3d-c-s}\dlo{(a)}-\ref{syn3d-obs-s}\dlo{(c)}} correspond to the clean data, noisy data, and observed data, respectively. Figures \dlo{\ref{30}(d) and \ref{30}(e)}\wen{\ref{syn3d-opshrinkdamped-s}\dlo{(d)} and \ref{syn3d-opshrinkdampedstma-s}\dlo{(e)}} display the recovered data using the damped data-driven optimal singular value shrinkage (damped optshrink) algorithm\wen{,} and the modified damped data-driven optimal singular value shrinkage algorithm, respectively. From the comparison of each sub-figure mentioned, the modified algorithm can obtain better recovery performance.\dlo{(Figures \ref{29}(e) and \ref{30})} The result of the modified algorithm is obtained with  $K=3$, $d=2$, $\mathbf{\beta}=2.10$, $e=0.991$, and $T=1$. The S/Ns are $7.77$ dB and $8.22$ dB for the damped data-driven optimal singular value shrinkage algorithm\wen{,} and the modified algorithm, respectively. We also analyze the contribution of the STMA operator by conducting two \dlo{significant}\wen{meaningful} numerical tests. First, by considering the S/N values as a function of iteration numbers. For this experiment, we range the iteration numbers from $5$ to $30$, and we plot the results in Figure \dlo{\ref{31}}\wen{\ref{snr_IterationN_DampedOpshrinkSTMA}}\dlo{(a)}. Then, we fix the noise level at $0.2$ and we vary the missing traces from $10\%$ to $90\%$. We \dlo{displays}\wen{display} the performance of each approach for the percentage of missing data in Figure \dlo{\ref{31}}\wen{\ref{snr_missing_trace_DampedOpshrink_stma}}\dlo{(b)}. From both subfigures, we find that the STMA operator can effectively improve the damped data-driven optimal singular value shrinkage algorithm.} 
\wen{
	\AtEndDocument{
		\begin{figure}[htb!]
			\centering
			\subfloat[]{\includegraphics[width=0.3\textwidth]{optshrink_damped_stma/Fig/syn3d-c-s}
				\label{syn3d-c-s}}
			\subfloat[]{\includegraphics[width=0.3\textwidth]{optshrink_damped_stma/Fig/syn3d-n-s}
				\label{syn3d-n-s}}
			\subfloat[]{\includegraphics[width=0.3\textwidth]{optshrink_damped_stma/Fig/syn3d-obs-s}
				\label{syn3d-obs-s}}\\
			\centering
			\subfloat[]{\includegraphics[width=0.3\textwidth]{optshrink_damped_stma/Fig/syn3d-opshrinkdamped-s}
				\label{syn3d-opshrinkdamped-s}}
			\subfloat[]{\includegraphics[width=0.3\textwidth]{optshrink_damped_stma/Fig/syn3d-opshrinkdampedstma-s}
				\label{syn3d-opshrinkdampedstma-s}}
			\caption{\dlo{Single slice comparison (5th crossline slice). (a-c) Clean, noisy, and observed data, respectively. (d and e) Recovered.} \wen{Single slice 2D figures comparison (fifth crossline slice). (a) Clean data. (b) Noisy data. (c) Observed data. (d and e) The recovered data obtained using the damped data-driven optimal singular value shrinkage algorithm and the modified algorithm, respectively.}}
			\label{syn3d-c-s,syn3d-n-s,syn3d-obs-s,syn3d-opshrinkdamped-s,syn3d-opshrinkdampedstma-s}
		\end{figure}
}}%fig.24
%\wen{
%	\AtEndDocument{
%		\begin{figure}[htb!]
%			\centering
%			\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/Inline_Clean}
%				\label{a}}
%			\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/Inline_Noise}
%				\label{b}}
%			\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/Inline_Observed}
%				\label{c}}\\
%			\centering
%			\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/Inline_Dampedopshrink}
%				\label{d}}
%			\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/Inline_DampedOpshrinkSTMA}
%				\label{e}}
%			\caption{\old{Single slice comparison (5th inline slice). (a-c) Clean, noisy, and observed data, respectively.(d and e) Recovered.} \new{Single slice 2-D figures comparison (5th inline slice). (a) Clean data. (b) Noisy data. (c) Observed data. (d and e) show the recovered} data obtained using the damped data-driven optimal singular value shrinkage algorithm and the modified algorithm, respectively.}
%			\label{25}
%\end{figure}}}
\wen{
	\AtEndDocument{
		\begin{figure}[htb!]
			\centering
			\subfloat[]{\includegraphics[width=0.3\textwidth]{Fig/snr_IterationN_DampedOpshrinkSTMA}
				\label{snr_IterationN_DampedOpshrinkSTMA}}
			\subfloat[]{\includegraphics[width=0.3\textwidth]{Fig/snr_missing_trace_DampedOpshrink_stma}
				\label{snr_missing_trace_DampedOpshrink_stma}}		
			\caption{S/N diagrams comparison between two approaches.\dlo{a noise level $0.2$ and $50\%$ as missing traces} (a) S/N\dlo{s} values for iteration numbers. (b) S/N\dlo{s} values as a function of missing traces after $15$ iterations. In both cases, the gray and black lines are from the damped data-driven optimal singular value shrinkage algorithm, and the modified algorithm, respectively.} 				  
			\label{snr_IterationN_DampedOpshrinkSTMA,snr_missing_trace_DampedOpshrink_stma}
\end{figure}}}
%fig.25

\wen{Then, to show the \wen{individual} contribution of each operator that uses our approach, we conducted the following combination: the RR and ST operators (RR + ST), the RR and MA operators (RR + MA), the RR operator and the damping factor (DRR method), the RR and STMA operators (RR + ST + MA), the DRR and ST operators (RR + damping + ST), the DRR and MA operators (RR + damping + MA), and the DRR and STMA operators (RR + damping + ST + MA, which corresponds to the proposed approach)\wen{.}\dlo{combine first, the RR and ST operators (RR + ST) in the same framework to see the effect of ST. Then, we mix the RR and MA operators (RR + MA) to see the performance of MA. Afterward; we introduce the damping factor into the conventional RR framework (RR + damping factor, which corresponds to the DRR method), to show the influence of the damping factor. In the same way, we remove the damping factor, and; we connect the STMA operator, to see the contribution of STMA. Besides, we remove the MA function from the proposed approach (RDRR), to analyze the result using the DRR with ST (DRR + ST). Similarly, we drop the ST and keep the DRR associated with the MA function (DRR + MA), to analyze the effect. Finally, the DRR and STMA operators (RR + damping factor + ST + MA, which corresponds to the proposed approach) are connected into the same framework to simultaneous denoise and reconstruct the missing trace.} Based on these experiments, the proposed approach can be regarded as a combination of the RR, damping, ST, and MA operators. We apply these mixed operators on the synthetic data of our first example (5D synthetic data having linear events corrupted by $ 0.3 $ as noise variance and $70 \% $ of missing traces). Because of the best quality of the result, we adopted rank 6 for the RR approach. We select $K=6$ and $\mathbf{\beta}=0$, for RR + ST, and $K=6$, ${d}=2$, $\mathbf{\beta}=0$, for RR + damping + ST. In both cases, we have adopted $\mathbf{\beta}=0$ because all values of $\mathbf{\beta}$ selected below or above $0$ influence negatively the S/N and hence affect the quality of the result. To restore the useful signal via RR + MA, we selected $K=6$, $e=0.982$, and $T=1$. For RR + ST + MA, we set $K$, $\mathbf{\beta}$, $T$, $e$ and  at $6$, $30$, $1$, and $0.964$, respectively. The parameters used by RR + damping + MA were set at $K=6$, $d=2$, $e=0.975$ and $T=1$. For the proposed approach (RR + damping + ST + MA), we selected $K=6$, $d=2$, $\mathbf{\beta}=3.3$, $e=0.972$ and $T=1$. We run all approaches with \dlo{ten}\wen{10} iterations. As can be seen, when STMA is \dlo{joined to}\wen{combined with} the RR or DRR approaches, we need to select the cooling factor $\mathbf{\beta} > 0$ to adjust the threshold parameter $\tau$. We deduce that the three parameters ($e$, $T$, and $\mathbf{\beta}$) that STMA uses are not negligible to achieve the goal of the proposed method. Table \ref{tbl:table2} displays the S/N values obtained by each operator and mixed operators after \old{ten}\wen{10} iterations. From the comparison of S/N\dlo{s} values, we find that only the ST operator is not able to improve the RR and DRR algorithm. Indeed, the results are almost the same. However, it is clear that only using the MA operator can improve the RR and the DRR algorithm. When we remove the damping factor from the proposed algorithm (RDRR), it corresponds to the RR + ST + MA approach. From Figures \dlo{\ref{29}(b) and \ref{32}(b)}\wen{\ref{synth-rrstma-s}\dlo{(b)} and \ref{synth-rrstma-xy-e-s}\old{(b)}}, we find that the introduced STMA function into the RR method framework after the TSVD process can \dlo{greatly}\wen{successfully} improve the result of the simultaneous denoising and reconstruction of 5D data. Compared to the damping operator (Figure \dlo{\ref{31}(a) and \ref{32}(a)}\wen{\ref{synth-rrdamping-s}\old{(a)} and \ref{synth-rrdamping-xy-e-s}\dlo{(a)}}), we find that RR + ST + MA operators can better reconstruct the missing traces than RR + damping operators. However, based on the visual comparison, the RR + damping operators can perfectly remove the residual noise from the noisy observation than the RR + ST + MA operators. Therefore, by introducing the damping and the STMA operators in the RR framework, we can greatly denoise while reconstructing the noisy and missing data from the noisy level-4 block Hankel matrix. Figures \dlo{\ref{31}(e) and \ref{32}(e)}\wen{\ref{synth-rrdampingstma-s}\dlo{(e)} and \ref{synth-rrdampingstma-xy-e-s}\dlo{(e)}} show the results obtained by combining the RR, damping and STMA operators.

We also analyze the influence of each approach by evaluating the S/N\dlo{s} values for iterations numbers (varying from $ 5 $ to $ 30 $). Figure \dlo{\ref{30}}\wen{\ref{Contribution_of_each_operator}} shows the S/N\dlo{s} diagrams obtained using the RR operator (the yellow line), RR + MA operator (the green line), RR + STMA operators (the gray line), RR + damping operators (DRR)(the blue line), DRR + MA operators (the black line) and DRR + STMA operators (RDRR)(the red line). From the S/N diagrams, we deduce that the proposed STMA operator can be used to greatly improve the conventional RR and the DRR methods. The comparison of each S/N diagram highlights the contribution of the proposed STMA operator in the RR and DRR methods.}

%\new{
%\AtEndDocument{
%%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/offset_rr_0370ok}
%			\label{a}}
%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/offset_RR_ST1}
%			\label{b}}
%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/offset_MA_RR}
%			\label{c}}\\
%		\centering
%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/2D_offset_RR_damping_70_03}
%			\label{d}}
%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/offset_RR_STMA}
%			\label{Fiigure:e}}
%		\caption{Comparison in one common offset after 10 iterations. (a-e) denote the RR, RR+ST, RR+MA, RR+ damping (correspond to the DRR method) and RR+STMA (corresponds to the RDRR without the damping factor), respectively. We test these approaches on 5-D synthetic data corrupted by 0.3 as noise level and $ 70\% $ of missing traces.}
%		\label{44}
%	\end{figure}
%}
%}
%\new{
%\AtEndDocument{
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/RMSE_RR_offset_rr03_70}
%			\label{a}}
%		\subfloat[]{\includegraphics[width=0.35\te%xtwidth]{Figures/RMSE_offset_RR_ST1}
%			\label{b}}
%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/RMSE_offset_RR_MA}
%	                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               		\label{c}}\\		
%		\subfloat[]{\includegraphics[width=0.35\te%xtwidth]{Figures/2D_RMSE_offset_RR_damping%_70_03}
%			\label{d}}
%		\subfloat[]{\includegraphics[width=0.35\te%xtwidth]{Figures/RMSE_offset_rr_stma}
%			\label{Fiigure:e}}
%		\caption{RMSE figures comparison in one common offset after 10 iterations. (a-e) denote RR, RR + ST RR + MA, RR + damping (correspond to the DRR method), RR + STMA (RDRR without the damping factor), %respectively.}
%		\label{45}
%	\end{figure}
%}
%}
\wen{
	\AtEndDocument{
		\begin{figure}[htb!]
			\centering
			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrdamping-s} 
				\label{synth-rrdamping-s}}
			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrstma-s} 
				\label{synth-rrstma-s}}
			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrdampingst-s}
				\label{synth-rrdampingst-s}}\\
			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrdampingma-s}
				\label{synth-rrdampingma-s}}
			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrdampingstma-s}
				\label{synth-rrdampingstma-s}}		
			\caption{\wen{Common-offset 2D figures comparison after \wen{ten}\dlo{10} iterations.} (a) The RR + damping operators (DRR method). (b) The RR + ST + MA operators. (c) The result of RR + damping + ST operators. (d) The result provided by the RR + damping + MA operators. (e) The result of the proposed approach (RR + damping + ST+ MA). We have tested these approaches on 5D synthetic data corrupted by 0.3 as the noise level and $70\%$ of missing traces}.
			\label{synth-rrdamping-s,synth-rrstma-s,synth-rrdampingst-s,synth-rrdampingma-s,synth-rrdampingstma-s}
		\end{figure}}
}%fig.26
\wen{
	\AtEndDocument{
		\begin{figure}[htb!]
			\centering
			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrdamping-xy-e-s} 
				\label{synth-rrdamping-xy-e-s}}
			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrstma-xy-e-s} 
				\label{synth-rrstma-xy-e-s}}
			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrdampingst-xy-e-s}
				\label{synth-rrdampingst-xy-e-s}}\\
			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrdampingma-xy-e-s}
				\label{synth-rrdampingma-xy-e-s}}
			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrdampingstma-xy-e-s}
				\label{synth-rrdampingstma-xy-e-s}}		
			\caption{\wen{\dlo{2D figures c}\wen{C}omparison of the simultaneous denoising and reconstruction error in one common-offset gather after 10 iterations.} (a) RR + damping operators (the DRR method). (b) The error using the RR + ST + MA operators. (c) The error using the RR + damping + ST operators. (d) The RR + damping + MA operators. (e) The proposed approach (RR + damping + ST + MA).}
			\label{synth-rrdamping-xy-e-s,synth-rrstma-xy-e-s,synth-rrdampingst-xy-e-s,synth-rrdampingma-xy-e-s,synth-rrdampingstma-xy-e-s}
		\end{figure}
	}
}%fig.27
\wen{
	\AtEndDocument{
		\begin{figure}[htb!]
			\centering
			\includegraphics[width=0.4\textwidth]{Fig/Contribution_of_each_operator}
			\caption{Comparison of S/N\dlo{s} values as a function of ratio of missing traces between the RR (the yellow line), RR + MA (the green line), RR + STMA (the gray line), DRR (the blue line), DRR + MA (the black line), and DRR + STMA (the red line) under a noise variance of $0.3$ and $70\%$ as missing traces.  
				\label{Contribution_of_each_operator}}
		\end{figure}%fig.28
}}\wen{The five key parameters \dlo{that use}\wen{in} the proposed approach are selected using the following strategy.} According to the Cadzow filtering method based on the linear event assumption, $K$ is defined as the number of different dip elements. \wen{In the condition of curved and complex events, $K$ should be approximately higher than the number of different dip components for producing more reliable results. The selection of $K$ generally influences substantially the performance of the RR-based methods. Indeed, the smaller values of $K$ will damage the signal, whereas higher values of $K$ will generate considerable noise in the result.} \dlo{Based on this assumption, we have conducted several tests to figure out the best results. The selection of $K$ influences substantially the performance of the proposed method. Indeed, the smaller value of $K$ will damage the signal whereas higher values of $K$ will generate considerable noise in the result. Because of the best quality of the signals obtained after applying the proposed method, it is better to choose rank $K$ = 6, for synthetic and field seismic data sets}\dlo{.}\wen{The damping factor can be selected in the interval \wen{of} $d\in[1,3]$}.\dlo{Concerning the damping factor,} \wen{In the case of data generally including linear events or no complex structures, $d = 1$ damages the useful signal. When $d = 3$, it produces some residual noise in the result. However, when we use $d = 2$, the results are perfect. Indeed, random noise can be greatly suppressed and the useful signal can be recovered for synthetic and field seismic data sets. However, when the data to be restored contains curved events or complex structures, $d = 3$ can be selected.} \dlo{When we use $d$ = 1, the proposed approach damages the useful signal. When $d$ = 3, it produces some residual noise in the result. However, when we use $d$ = 2, the results are \old{perfect}\new{better}. Indeed, random noise can be greatly suppressed and the useful signal can be recovered for synthetic and field seismic data sets}\dlo{.}\wen{Besides, the parameter $T$ should be a positive integer ($T>0$). It is important to know that when $T$ is too \dlo{long}\wen{larger}, it \dlo{creates}\wen{causes} some loss of useful signals (Figure \dlo{\ref{28}}\wen{\ref{synth-hxhy-s-stma2}\dlo{(b)}) even though the S/N can be improved. As a consequence, the amplitude of the signal can be seriously degraded. Moreover, if $T$ is \dlo{much short}\wen{too small} (Figure \ref{synth-hxhy-s-stma1}), it cannot attenuate residual noise well.\dlo{(Figures \dlo{\ref{30}(a and c)}\wen{\ref{31}(a) and \ref{31}(c)}).} However, the useful signal can be preserved. Therefore, in the proposed approach we should select a smaller value of $T$ to preserve the quality of the useful signal. To avoid \dlo{the signal damage}\wen{damaging signal}, we always select $T=1$ whatever the condition of noise and missing data and also the type (complex, linear or curved events) of the data to be reconstructed.
The parameters $e$ and $\beta$ should be selected considering \dlo{some information about}the noise level, the percentage of missing traces, and the iteration numbers used to run the proposed algorithm. In general, $e$ should be \old{greater than $0$ but less or equal to $1$}$ 0 < e \leq 1$. \wen{The larger value of $e$}\dlo{If the value of $e$ is much large, it} may produce redundant data and cause new noise\dlo{.}\wen{, and t}he energy of the signal may be seriously affected. In addition, if $e$ is extremely small, it may yield \dlo{over-smoothing results}\wen{an overly smooth result} and signal distortion. After conducting many numerical tests on different synthetic data, we realize that it is better to always set $e$ around $1$ ($e \leq 1$). From these tests, we can deduce significant conclusions about this useful parameter. When the percentage of missing data decreases, $e$ must be selected very close to $1$ ($ e \leq 1 $). In other words, we have to select $e$ by decreasing $1$ very slightly until achieving the best result. For instance, when the 5D synthetic data \old{is}\new{are} corrupted by a noise level of $0.3$ with $20\%$ of missing data, we choose $e = 0.997$. However, for the $90\%$ decimation, we need to select $e$ by gradually moving away from $1$. For example, using a noise level of $0.2$ with $90\%$ of missing traces, we choose $e = 0.891$. This meaningful indication about $e$ can also be applied in the case of field data. For instance, we used $e = 0.9$ when recovering the real field data of this paper, which missed approximately $75\%$ of traces. Under the same condition of noise and missing traces, we should increase gradually the value of $e$ when the iteration numbers increase. For example, $e$ can be set from $0.95, 0.97,..,$ to $1$ for iteration varying from $5, 10,.., $ to $40$ based on the same noise level and missing data. This is verified for any type of data to be recovered}}. 
To greatly impose sparsity into the level-4 block Hankel matrix \wen{after DTSVD}, we set the thresholding parameter $\tau$ as \dlo{the value}defined in the “The RDRR Method” section. From this approach, we use the cooling factor $\beta$ to adjust $\tau$. This useful tool helps to control the smoothing degree. According to our experience, it is better to select a small $\beta$ \wen{for data having linear events. All $\beta$ used for the synthetic data examples containing linear \wen{events} have been selected between values from \dlo{$2$}\wen{$2.0$} to $3.5$. In contrast, a relatively greater value of $\beta$ should be set for data that are composed of curved events. The values of $\beta$ have been selected from $5$ to $17$ for the different tests on curved data of this paper. As a general rule, when the percentage of missing traces, noise levels and iteration numbers decrease, a relatively larger value of $\beta$ should be selected.} Note that, \wen{if}\dlo{even though only} one parameter is not appropriately set, it may affect the simultaneous denoising and reconstruction performance. Thus, to reach the best trade-off between random noise \dlo{attenuating}\wen{attenuation} and useful signal preservation, we should choose the parameters properly.

\dlo{According to our experience, it is better to select a small $\beta$ around 3 in general for synthetic data. All $\beta$ used for the synthetic data examples have been selected between values from 2 to 3.5. A relatively small $\beta$ is also generally more adequate and suitable for field data. For the field data examples, we use $\beta$ = 3. Note that, when $\beta$ is very large, the smoothing damages the useful signal amplitude. Besides, when $T$ is too long, it creates some loss of useful signals. However, if $T$ is much short, it cannot attenuate residual noise well. Therefore, we always select $T$ = 1 for synthetic and field data to avoid the signal damage. On the other hand, \dlo{if the rational transfer coefficient $e$ is much large, it}\wen{larger values of $e$} may produce redundant data and cause new noise. Also, if $e$ is extremely small, it may yield over-smoothing results and signal distortion. After conducting many numerical tests on different synthetic data, we realize that it is better to set $e$ always to around 1. From these tests, we can deduce significant conclusions about this last parameter. When the percentage of missing data decreases, $e$ must be selected very close to 1. In other words, we have to select $e$ by decreasing 1 very slightly until achieving the best result. For instance, when the 5D synthetic data \dlo{is}\wen{are} corrupted by a noise level of $0.3$ with $20\%$ of missing data, we choose $e$ = 0.997. On the other hand, for the $90\%$ decimation, we need to select $e$ by gradually moving away from 1. For example, using a noise level of $0.2$ with $90\%$ of missing traces, we choose $e$ = 0.891. This meaningful indication about $e$ can also be applied in the case of field data. For instance, we use $e$ = 0.9 when recovering the real field data of this paper.}

Here, we focus our attention on the comparison of the visual examination and numerical tests. Compared with the DRR framework, the proposed method can successfully outperform in each \dlo{case aforementioned}\wen{aforementioned case}. \dlo{Indeed, t}\wen{T}he simultaneously denoised and reconstructed data from our approach are always better than those of the DRR method. As the noise level, the percentage of missing traces, and the number of iterations increase, the difference between both algorithms is still \dlo{impressive}\wen{evident}. Based on the lower rms error values of our method, we deduce that the proposed algorithm can yield better accuracy results than the DRR approach. The analysis of the numerical tests provides \dlo{a}useful and practical instruction that the RDRR method can be successfully used in the situation \dlo{. It may even contain}\wen{of} \dlo{stiff}\wen{strong} random noise and a high level of missing observation, which is often the characteristic of most seismic data acquired on land. According to the frequency analysis, our method can be used to enhance the resolution of seismic data because of its better ability to provide \dlo{high frequency}\wen{high-frequency components} compared to the DRR approach.

\section{conclusions}
We have demonstrated the feasibility of a novel method for simultaneous denoising and reconstruction of 5D seismic data. Using the advantages of the damping operator and the proposed STMA operator, we have constructed a novel improved method based on a new RDRR formula. We introduce the proposed framework to accurately restore the useful signal and suppress the random noise left after the DRR method process. The proposed approach benefiting from multiple operators yields better results compared to the DRR method. We use different 5D synthetic and one 5D field seismic data sets corrupted by random noise to examine the accuracy of our algorithm. The results for simultaneous denoising and reconstruction are shown in terms of the visual examination and numerical tests. As demonstrated from the detailed analysis, our proposed framework behaves very well even in the situation of very high noise levels and high ratios of missing traces.

\section{acknowledgments}
We would like to thank three anonymous reviewers for constructive suggestions. The research is supported by the National Natural Science Foundation of China (grant no. 41804140) and the starting fund from Zhejiang University.

\section{Data and materials availability}
Data associated with this research are available and can be obtained by contacting the corresponding author.

\bibliographystyle{apalike}
\bibliography{rdrr}

\newpage
\listoftables

\newpage
\listoffigures

%\end{document}

%\AtEndDocument{}

%\newpage
%\listoffigures

%\begin{figure}[htb!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
%	\caption{Caption.}
%	\label{fig:fig}
%\end{figure}

%\begin{figure}[htb!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
%    \label{fig:fig1}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
%    \label{fig:fig2}}\\
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure}

%\begin{figure*}[ht!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
%    \label{fig:fig1}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
%    \label{fig:fig2}}\\
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure*}

%\begin{table}[h]
%\caption{Table caption}
%\begin{center}
%     \begin{tabular}{|c|c|c|c|c|c|} 
%	  \hline Column1 (unit)  & Column2 (unit) & Column3 (unit) \\ 
%	  \hline 1 & 2  & 3 \\
%       \hline
%    \end{tabular} 
%\end{center}
%\label{tbl:table1}
%\end{table}

### 2021-02-03 rdrr5d/matfun/drr5d_lb_recon.m

@@ -1,0 +1,298 @@
+function [ D1 ] = drr5d_lb_recon(D,MASK,flow,fhigh,dt,N,NN,Niter,eps,verb,mode,iflb,a)
+%  MSSA5D: multichannel singular spectrum analysis (MSSA) for 5D
+%          simultaneous denoising and reconstruction
+%          with Lanczos bidiagonalization
+%
+%  IN   D:   	intput 5D data
+%       MASK:   sampling mask (consistent with the POCS based approaches)
+%       flow:   processing frequency range (lower)
+%       fhigh:  processing frequency range (higher)
+%       dt:     temporal sampling interval
+%       N:      number of singular value to be preserved
+%       NN:     damping factor
+%       Niter:  number of maximum iteration
+%       eps:    tolerence (||S(n)-S(n-1)||_F<eps*S(n))
+%       verb:   verbosity flag (default: 0)
+%       mode:   mode=1: denoising and reconstruction
+%               mode=0: reconstruction only
+%       iflb:   default 0;
+%               1: with LB, MGS orthogonalized
+%               0: traditional
+%       a:      scalar
+%
+%  OUT  D1:  	output data
+%
+%  Copyright (C) 2015 The University of Texas at Austin
+%  Copyright (C) 2015 Yangkang Chen
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
[…]

### 2021-02-03 rdrr5d/matfun/drr_st5d_lb_recon.m

@@ -1,0 +1,303 @@
+function [ D1 ] = drr_st5d_lb_recon(D,MASK,flow,fhigh,dt,N,NN,Niter,eps,verb,mode,iflb,a,K)
+%  RR + damping + ST: Damped rank-reduction (DRR) method + soft thresholding (ST) operator for simultaneous denoising and 
+%        reconstruction of 5D seismic data with Lanczos bidiagonalization
+%
+%  IN   D:   	intput 5D data
+%       MASK:   sampling mask (consistent with the POCS based approaches)
+%       flow:   processing frequency range (lower)
+%       fhigh:  processing frequency range (higher)
+%       dt:     temporal sampling interval
+%       N:      number of singular value to be preserved
+%       NN:     damping factor
+%       Niter:  number of maximum iteration
+%       eps:    tolerence (||S(n)-S(n-1)||_F<eps*S(n))
+%       verb:   verbosity flag (default: 0)
+%       mode:   mode=1: denoising and reconstruction
+%               mode=0: reconstruction only
+%       iflb:   default 0;
+%               1: with LB, MGS orthogonalized
+%               0: traditional
+%       a:      scalar
+%       K:      decrease factor for cooling lambda
+%  OUT  D1:  	output data
+%
+%  Copyright (C) 2020 Zhejiang University
+%  Copyright (C) Oboue et al. 2020
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
[…]

### 2021-02-03 rdrr5d/matfun/fxydmssa_recon_optshrink.m

@@ -1,0 +1,223 @@
+function [ D1 ] = fxydmssa_recon_optshrink(D,MASK,flow,fhigh,dt,N,NN,Niter,eps,verb,mode,a)
+%  FXY_MSSA: F-XY domain multichannel singular spectrum analysis (MSSA) for
+%  simultaneous denoising and reconstruction
+%
+%  IN   D:   	intput 3D data
+%       MASK:   sampling mask (consistent with the POCS based approaches)
+%       flow:   processing frequency range (lower)
+%       fhigh:  processing frequency range (higher)
+%       dt:     temporal sampling interval
+%       N:      number of singular value to be preserved
+%       NN:     damping factor
+%       Niter:  number of maximum iteration
+%       eps:    tolerence (||S(n)-S(n-1)||_F<eps*S(n))
+%       verb:   verbosity flag (default: 0)
+%       mode:   mode=1: denoising and reconstruction
+%               mode=0: reconstruction only
+%       a:      scalar
+%
+%  OUT  D1:  	output data
+%
+%  Copyright (C) 2015 The University of Texas at Austin
+%  Copyright (C) 2015 Yangkang Chen
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details: http://www.gnu.org/licenses/
+%
+%  Reference:   Simultaneous seismic data denoising and reconstruction via multichannel
+%               singular spectrum analysis, Geophysics, 2011, 76, V25-V32
+%
[…]

### 2021-02-03 rdrr5d/matfun/rdrr5d_lb_recon.m

@@ -1,0 +1,304 @@
+function [ D1 ] = denoising_recon_rdrr(D,MASK,flow,fhigh,dt,N,NN,Niter,eps,verb,mode,iflb,a,K,e,ws)
+%  RDRR: Robust damped rank-reduction (RDRR) method for simultaneous denoising and 
+%        reconstruction of 5D seismic data
+%        with Lanczos bidiagonalization
+%
+%  IN   D:   	intput 5D data
+%       MASK:   sampling mask (consistent with the POCS based approaches)
+%       flow:   processing frequency range (lower)
+%       fhigh:  processing frequency range (higher)
+%       dt:     temporal sampling interval
+%       N:      number of singular value to be preserved
+%       NN:     damping factor
+%       Niter:  number of maximum iteration
+%       eps:    tolerence (||S(n)-S(n-1)||_F<eps*S(n))
+%       verb:   verbosity flag (default: 0)
+%       mode:   mode=1: denoising and reconstruction
+%               mode=0: reconstruction only
+%       iflb:   default 0;
+%               1: with LB, MGS orthogonalized
+%               0: traditional
+%       a:      scalar
+%       K:      decrease factor for cooling lambda
+%       e:      rational tranfer function coefficient 
+%       ws:     windows size 
+%  OUT  D1:  	output data
+%
+%  Copyright (C) 2020 Zhejiang University
+%  Copyright (C) Oboue et al. 2020
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
[…]

### 2021-02-03 rdrr5d/matfun/rperm.m

@@ -1,0 +1,23 @@
+function p = rperm(n,seed)
+%RPERM: Random permutation with seeds.
+%   
+%   See also RANDPERM
+%   RANDPERM(n) is a random permutation of the integers from 1 to n.
+%   For example, RANDPERM(6) might be [2 4 5 6 1 3].
+%
+%  Copyright (C) 2014 The University of Texas at Austin
+%  Copyright (C) 2014 Yangkang Chen
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details:
+%  http://www.gnu.org/licenses/
+
+rand('state',seed);
+[~,p] = sort(rand(1,n));

### 2021-02-03 rdrr5d/matfun/rr5d_lb_st_ma_recon.m

@@ -1,0 +1,301 @@
+function [ D1 ] =rr_st_ma5d_lb_recon(D,Data5Dmask,flow,fhigh,dt,N,Niter,eps,verb,mode,a,K,e,ws)
+%  RR + ST + MA: Rank-reduction (RR) + soft thresholding (ST) + moving average (MA) operators for simultaneous denoising and 
+%           reconstruction of 5D seismic data  
+% 
+%  IN   D:   	intput 5D data
+%       MASK:   sampling mask (consistent with the POCS based approaches)
+%       flow:   processing frequency range (lower)
+%       fhigh:  processing frequency range (higher)
+%       dt:     temporal sampling interval
+%       N:      number of singular value to be preserved
+%       NN:     damping factor
+%       Niter:  number of maximum iteration
+%       eps:    tolerence (||S(n)-S(n-1)||_F<eps*S(n))
+%       verb:   verbosity flag (default: 0)
+%       mode:   mode=1: denoising and reconstruction
+%               mode=0: reconstruction only
+%       iflb:   default 0;
+%               1: with LB, MGS orthogonalized
+%               0: traditional
+%       a:      scalar
+%
+%       K:      decrease factor for cooling lambda
+%       e:      rational tranfer function coefficient 
+%       ws:     windows size 
+
+%  OUT  D1:  	output data
+%
+%  Copyright (C) 2020 Zhejiang University
+%  Copyright (C) Oboue et al. 2020
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
[…]

### 2021-02-03 rdrr5d/matfun/synth_linear_NV02_MT90.m

@@ -1,0 +1,145 @@
+function synth_linear_NV02_MT90(clean,noisy,obs,drr,rdrr)
+% Author      : Oboue et al. 2020
+%               Zhejiang University
+% 
+% Date        : January, 2021
+% Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
+%    
+%  Copyright (C) 2020 Zhejiang University
+%  Copyright (C) Oboue et al. 2020
+%  This program is free software; you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published by
+%  the Free Software Foundation; either version 2 of the License, or
+%  (at your option) any later version.
+%  
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%  
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, write to the Free Software
+%  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  
+
+%% load data
+load ob_synth5d.mat
+d=synth5d;d=d/max(max(max(max(max(d)))));
+[nt,nhx,nhy,nx,ny]=size(d);
+
+%% simultaneous denoising and reconstruction
+randn('state',201314);
+var=0.2;
+dn=d+var*randn(size(d));
+
+%% decimate
+[nt,nhx,nhy,nx,ny]=size(d);
+ratio=0.1;
+mask=genmask(reshape(d,nt,nhx*nhy*nx*ny),ratio,'c',201415);
+mask=reshape(mask,nt,nhx,nhy,nx,ny);
+d0=dn.*mask;
+
+% DRR
+flow=0;fhigh=100;dt=0.004;N=6;NN=2;Niter=10;mode=1;verb=1;iflb=0; 
+a=(Niter-(1:Niter))/(Niter-1);
[…]

### 2021-02-03 rdrr5d/matfun/synth_stma.m

@@ -1,0 +1,91 @@
+function synth_stma(stma1,stma2)
+% Author      : Oboue et al. 2020
+%               Zhejiang University
+% 
+% Date        : January, 2021
+% Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
+%    
+%  Copyright (C) 2020 Zhejiang University
+%  Copyright (C) Oboue et al. 2020
+%  
+%  This program is free software; you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published by
+%  the Free Software Foundation; either version 2 of the License, or
+%  (at your option) any later version.
+%  
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%  
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, write to the Free Software
+%  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  
+% 
+
+
+%% load data
+load ob_synth5d.mat
+d=synth5d;d=d/max(max(max(max(max(d)))));
+[nt,nhx,nhy,nx,ny]=size(d);
+%
+%% simultaneous denoising and reconstruction
+randn('state',201314);
+var=0.3;
+dn=d+var*randn(size(d));
+
+%% decimate
+%[nt,nhx,nhy,nx,ny]=size(d);
+ratio=0.3;
+mask=genmask(reshape(d,nt,nhx*nhy*nx*ny),ratio,'c',201415);
+mask=reshape(mask,nt,nhx,nhy,nx,ny);
+d0=dn.*mask;
+
+%% stma 1st case 
+K1=80; e1=0.999; T1=2; 
+flow=0;fhigh=90;dt=0.004;Niter=15;mode=1;verb=1;iflb=0; 
+a=(Niter-(1:Niter))/(Niter-1);
+d1=denoising_reconstruction_stma5d(d0,mask,flow,fhigh,dt,Niter,eps,verb,mode,a,K1,e1,T1);
+
+%% stma 2nd case 
+K2=15; e2=0.999; T2=17; 
[…]

### 2021-02-03 rdrr5d/matfun/yc_lb.m

@@ -1,0 +1,159 @@
+function [U,B_k,V] = yc_lb(A,p,k,reorth)
+%yc_lb: Lanczos bidiagonalization
+%
+% B_k = yc_lb(A,p,k,reorth)
+% [U,B_k,V] = yc_lb(A,p,k,reorth)
+% p: Starting vector must be nonzero (zeros(size(A,1),1))
+% 
+% Performs k steps of the Lanczos bidiagonalization process with
+% starting vector p, producing a lower bidiagonal matrix
+%           [b_11               ]
+%           [b_21 b_22          ]
+%     B_k = [     b_32 .        ]
+%           [          . b_kk   ]
+%           [            b_k+1,k]
+% such that
+%    A=U*B_k*V' or A*V = U*B_k ,
+% where U and V consist of the left and right Lanczos vectors.
+%
+% Reorthogonalization is controlled by means of reorth:
+%    reorth = 0 : no reorthogonalization,
+%    reorth = 1 : reorthogonalization by means of MGS (Modified Gram-Schmidt), 
+%    reorth = 2 : Householder-reorthogonalization.
+%    MGS by means of projection, Householder by means of reflection
+%
+% No reorthogonalization is assumed if reorth is not specified.
+%
+%  Copyright (C) 2015 The University of Texas at Austin
+%  Copyright (C) 2015 Yangkang Chen
+%
+%  Per Christian Hansen, IMM, April 8, 2001.
+% 
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details: http://www.gnu.org/licenses/
+%
+% Reference:    G. H. Golub & C. F. Van Loan, "Matrix Computations", 3. Ed., 
[…]

### 2021-02-03 rdrr5d/matfun/yc_optshrink_damp.m

@@ -1,0 +1,109 @@
+function [Shat,relmse_hat,mse_hat] = yc_optshrink_damp(Xtil,r, K)
+% Damped optshrink by Yangkang Chen, Oct, 2017
+% 
+% K: damping factor
+% 
+% Input: Xtil = Signal-plus-noise matrix
+%        r    = Estimate of (effective) rank of signal matrix
+% Note: r can be estimated from eyeballing the "knee" of the singular value plot
+%       or from your favorite random matrix theory based test
+%
+% Output: Shat = Rank r denoised estimate of signal matrix
+%         relmse_hat = Estimate of normalized MSE
+%         mse_hat    = Estimate of MSE 
+%
+% Idea: Shat has same singular vectors as Xtil but "shrunk" singular values
+%       The shrinkage is computed in an optimal manner from the "noise portion" of the
+%       singular value spectrum
+%       
+% ValueOfInformation type Metric: relmse_hat quantifies 'noisiness'; if  close to 1 then 
+%                                 Shat is likely very unreliable
+%
+% Reference: Algorithm 1 in http://arxiv.org/abs/1306.6042
+% Author: Raj Rao Nadakuditi (rajnrao@umich.edu)
+% Date: July 22, 2013
+%
+% Nested sub-functions: estimateDz and estimateDpz
+% 
+% Example:
+%
+% n = 100; m = 150; theta= 2;
+% u = sign(randn(n,1))/sqrt(n); v = sign(randn(m,1))/sqrt(m);
+% S = theta*u*v'; 
+% Xtil = S + randn(n,m)/sqrt(m);
+% [Shat,relmse_hat,mse_hat] = optshrink(Xtil,1);
+% [Util,Stil,Vtil] = svds(Xtil,1);
+% Stsvd = Stil*Util*Vtil';
+% disp('New algorithm error vs Truncated SVD error')
+% [norm(S-Shat,'fro')^2 norm(S-Stsvd,'fro')^2]
+% Improvement = (1-ans(1)/ans(2))*100;
+% ['Improvement = ' num2str(Improvement) ' %']
+
+
[…]

### 2021-02-04 rdrr5d/paper.tex
2021年 2月 4日 星期四 10时31分49秒 CST

@@
 
-The following workflow presents our proposed robust damped rank-reduction algorithm for simultaneous denoising and reconstruction of 5D seismic data:
+The following workflow presents our proposed RDRR algorithm for simultaneous denoising and reconstruction of 5D seismic data:
 
@@
 In the first experiment, we randomly decimate $70\%$ of the traces and add a noise \dlo{variance of 0.3}\wen{of 0.3 variance} to examine the simultaneous denoising and reconstruction quality of both algorithms.
-The 3D figures in one common-midpoint gather \dlo{($Nx_1$ = 6, $Nx_2$ = 6)}\wen{($x$ = 6, $y$ = 6)} and one common offset gather \dlo{($x_1$ = 6, $x_2$ = 6)}\wen{($hx$ = 6, $hy$ = 6)} of the true, noisy, and decimated data are presented in Figures \ref{synth-clean-hxhy}\dlo{(a)}-\ref{synth-obs-hxhy}\dlo{(c)} and \ref{synth-clean-hxhy}\dlo{(a)}-\ref{synth-obs-hxhy}\dlo{(c)}, respectively.
+The 3D figures in one common-midpoint gather \dlo{($Nx_1$ = 6, $Nx_2$ = 6)}\wen{($x$ = 6, $y$ = 6)} and one common-offset gather \dlo{($x_1$ = 6, $x_2$ = 6)}\wen{($hx$ = 6, $hy$ = 6)} of the true, noisy, and decimated data are presented in Figures \ref{fig:synth-clean-hxhy}\dlo{(a)}-\ref{fig:synth-obs-hxhy}\dlo{(c)} and \ref{fig:synth-clean-hxhy}\dlo{(a)}-\ref{fig:synth-obs-hxhy}\dlo{(c)}, respectively.
 
@@
 To restore the useful signal, we use a rank {$K$ = 6} and a damped factor {$d$ = 2} for the DRR approach.
-Figures \ref{synth-drr-hxhy}\dlo{(d)} and \ref{synth-drr-xy}\dlo{(d)} show the results obtained using the DRR method.
+Figures \ref{fig:synth-drr-hxhy}\dlo{(d)} and \ref{fig:synth-drr-xy}\dlo{(d)} show the results obtained using the DRR method.
 The simultaneously denoised and reconstructed data are satisfactory.
@@
 We run both methods using \dlo{ten}\wen{10} weighted POCS-like iterations.
-Figures \ref{synth-rdrr-hxhy}\dlo{(e)} and \ref{synth-rdrr-xy}\dlo{(e)} show the results obtained via the proposed RR approach.
+Figures \ref{fig:synth-rdrr-hxhy}\dlo{(e)} and \ref{fig:synth-rdrr-xy}\dlo{(e)} show the results obtained via the proposed RR approach.
 Compared with the DRR results, our method greatly removes the residual noise and recovers the useful signal.
@@
 }}
-\AtEndDocument{
+%\AtEndDocument{
 %	\begin{figure}[htb!]
@@
 %		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_originalfinal}
-%			\label{cmp_originalfinal}}
+%			\label{Figure:cmp_originalfinal}}
 %		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_noisyfinal}
-%			\label{cmp_noisyfinal}}
+%			\label{Figure:cmp_noisyfinal}}
 %		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_observedfinal}
-%			\label{cmp_observedfinal}}\\	
+%			\label{Figure:cmp_observedfinal}}\\	
 %		\centering
 %		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_drrokfinal}
-%			\label{cmp_drrokfinal}}
+%			\label{Figure:cmp_drrokfinal}}
 %		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_proposedfinal}
-%			\label{cmp_proposedfinal}}	
+%			\label{Figure:cmp_proposedfinal}}	
 %		\caption{Common midpoint 3-D figures comparison ($x$ = 6, $y$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{10}\wen{ten} iterations.
@@
 (d and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed method, respectively.}
-%		\label{cmp_originalfinal,cmp_noisyfinal,cmp_observedfinal,cmp_drrokfinal,cmp_proposedfinal}
+%		\label{Figure:cmp_originalfinal,cmp_noisyfinal,cmp_observedfinal,cmp_drrokfinal,cmp_proposedfinal}
 %	\end{figure}%fig.1
-\begin{figure}[htb!]
-	\centering
-	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-clean-hxhy}\label{synth-clean-hxhy}}
-	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-noisy-hxhy}\label{synth-noisy-hxhy}}
-	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-obs-hxhy}\label{synth-obs-hxhy}}\\
-	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-drr-hxhy}\label{synth-drr-hxhy}}
-	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-rdrr-hxhy}\label{synth-rdrr-hxhy}}
-	\caption{Common-midpoint 3D figures comparison ($x$ = 6, $y$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{ten}\wen{10} iterations.
+
+\inputdir{synth_Linear_NV03_MT70}
+\multiplot{5}{synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-drr-hxhy,synth-rdrr-hxhy}{width=0.3\textwidth}{Common-midpoint 3D figures comparison ($x$ = 6, $y$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{ten}\wen{10} iterations.
 (a) Clean data.
@@
 (d and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed method, respectively.}
-	\label{synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-drr-hxhy,synth-rdrr-hxhy}
-\end{figure}%fig.1
+
+%\begin{figure}[htb!]
+%	\centering
+%	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-clean-hxhy}\label{Figure:synth-clean-hxhy}}
+%	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-noisy-hxhy}\label{Figure:synth-noisy-hxhy}}
+%	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-obs-hxhy}\label{Figure:synth-obs-hxhy}}\\
+%	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-drr-hxhy}\label{Figure:synth-drr-hxhy}}
+%	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-rdrr-hxhy}\label{Figure:synth-rdrr-hxhy}}
+%	\caption{Common-midpoint 3D figures comparison ($x$ = 6, $y$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{ten}\wen{10} iterations.
+(a) Clean data.
+(b) Noisy data with $0.3$ as noise level.
+(c) Observed noisy and incomplete data with $70\%$ of missing traces.
+(d %and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed method, respectively.}
+%	\label{Figure:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-drr-hxhy,synth-rdrr-hxhy}
+%\end{figure}%fig.1
 %\begin{figure}[htb!]
@@
 %		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_originalfinal}
-%			\label{offset_originalfinal}}
+%			\label{Figure:offset_originalfinal}}
 %		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_noisyfinal}
-%			\label{offset_noisyfinal}}
+%			\label{Figure:offset_noisyfinal}}
 %		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_observedfinal}
-%			\label{offset_observedfinal}}
+%			\label{Figure:offset_observedfinal}}
 
@@
 %		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_drrokfinal}
-%			\label{offset_drrokfinal}}
+%			\label{Figure:offset_drrokfinal}}
 %		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_proposedfinal}
-%			\label{offset_proposedfinal}}
+%			\label{Figure:offset_proposedfinal}}
 %		\caption{Common offset gather 3-D figures comparison ($hx$ = 6, $hy$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{10}\wen{ten} iterations.
@@
 (d and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed approach, respectively.}
-%		\label{offset_originalfinal,offset_noisyfinal,offset_observedfinal,offset_drrokfinal,offset_proposedfinal}
+%		\label{Figure:offset_originalfinal,offset_noisyfinal,offset_observedfinal,offset_drrokfinal,offset_proposedfinal}
 %	\end{figure}%fig.2
-\begin{figure}[htb!]
-	\centering
-	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-clean-xy}\label{synth-clean-xy}}
-	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-noisy-xy}\label{synth-noisy-xy}}
-	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-obs-xy}\label{synth-obs-xy}}\\
-	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-drr-xy}\label{synth-drr-xy}}
-	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-rdrr-xy}\label{synth-rdrr-xy}}
-	\caption{Common-offset gather 3D figures comparison ($hx$ = 6, $hy$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{ten}\wen{10} iterations.
+
+\inputdir{synth_Linear_NV03_MT70}
+\multiplot{5}{synth-clean-xy,synth-noisy-xy,synth-obs-xy,synth-drr-xy,synth-rdrr-xy}{width=0.3\textwidth}{Common-offset gather 3D figures comparison ($hx$ = 6, $hy$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{ten}\wen{10} iterations.
 (a) True data.
@@
 (d and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed approach, respectively.}
-	\label{synth-clean-xy,synth-noisy-xy,synth-obs-xy,synth-drr-xy,synth-rdrr-xy}
-\end{figure}%fig.2
-}
-%\dlo{To make a good comparison based on visual examination, we plot the 2-D figures of each synthetic 5-D data aforementioned.
-The results in one common midpoint gather and one common offset gather are displayed in Figures \ref{3} and \ref{5}, respectively.
-Figures \ref{3}\dlo{(a)}\wen{a} and \ref{5}\dlo{(a)}\wen{a} denote the original data.
-Figures \ref{3}\dlo{(b)}\wen{b} and \ref{5}\dlo{(b)}\wen{b} show the noisy data.
-Figures \ref{3}\dlo{(c)}\wen{c} and \ref{5}\dlo{(c)}\wen{c} show the decimated data.
-Figures \ref{3}\dlo{(d)}\wen{d} and \ref{5}\dlo{(d)}\wen{d} display the simultaneously denoised and reconstructed data using the DRR algorithm.
-From this comparison, it is clear that the results obtained by our algorithm displayed in Figures \ref{3}\dlo{(e)}\wen{e} and \ref{5}\dlo{(e)}\wen{e} are still preferable than those of the DRR method.}
-%\AtEndDocument{
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2Dcmpclean7003}
-%			\label{a}}
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DcmpNoisy7003}
-%			\label{b}}
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DcmpObserved7003}
-%			\label{Fiigure:c}}\\
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DcmpDRR7003}
-%			\label{Fiigure:d}}
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DcmpProposed7003}
-%			\label{Fiigure:e}}
-%		\caption{Common midpoint 2-D figures comparison ($Nx_1$ = 6, $Nx_2$ = 6) after 10 iterations between both algorithms.
-(a) Clean data.
-(b) Noisy data with 0.3 as noise level.
-(c) Observed noisy and incomplete data with 70\% of missing traces.
-(d-e) Simultaneously denoised and reconstructed  data using the DRR method and the proposed approach, respectively.}
-%		\label{3}
-%	\end{figure}
-%}
-To see the difference more clearly, we display the rms error results obtained by subtracting the recovered data from the original data in \wen{Figure \ref{synth-drr-hxhy-e,synth-rdrr-hxhy-e,synth-drr-xy-e,synth-rdrr-xy-e}.
-Figures \ref{synth-drr-hxhy-e}\dlo{(a)} and \ref{synth-drr-xy-e}\dlo{(c)} correspond to the DRR approach with rms error values of $2.22\%$ and $2.64\%$ respectively in one common-midpoint and common-offset gather.
-Figure \ref{synth-rdrr-hxhy-e}\dlo{(b)} and \ref{synth-rdrr-xy}\dlo{(d)} is from the proposed algorithm with rms error values of $1.53\% $ and $1.48\% $ respectively in one common-midpoint and common-offset gathers.} From this comparison, it is \dlo{further} apparent that our approach performs better with fewer denoising and reconstruction errors and thus can provide a better simultaneously denoised and reconstructed improvement than the DRR algorithm.
+
+To see the difference more clearly, we display the rms error results obtained by subtracting the recovered data from the original data in \wen{Figure \ref{fig:synth-drr-hxhy-e,synth-rdrr-hxhy-e,synth-drr-xy-e,synth-rdrr-xy-e}.
+Figures \ref{fig:synth-drr-hxhy-e}\dlo{(a)} and \ref{fig:synth-drr-xy-e}\dlo{(c)} correspond to the DRR approach with rms error values of $2.22\%$ and $2.64\%$ respectively in one common-midpoint and common-offset gather.
+Figure \ref{fig:synth-rdrr-hxhy-e}\dlo{(b)} and \ref{fig:synth-rdrr-xy}\dlo{(d)} is from the proposed algorithm with rms error values of $1.53\% $ and $1.48\% $ respectively in one common-midpoint and common-offset gathers.} From this comparison, it is \dlo{further} apparent that our approach performs better with fewer denoising and reconstruction errors and thus can provide a better simultaneously denoised and reconstructed improvement than the DRR algorithm.
 This comparison confirms the superiority of our approach in terms of accuracy.
-\AtEndDocument{
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.34\textwidth]{Figures/cmp_drrokerrfinal}
-%			\label{cmp_drrokerrfinal}}
-%		\subfloat[]{\includegraphics[width=0.34\textwidth]{Figures/cmp_proposederrfinal}
-%			\label{cmp_proposederrfinal}}\\
-%		\subfloat[]{\includegraphics[width=0.34\textwidth]{Figures/diff_offset_drrokfinal}
-%			\label{diff_offset_drrokfinal}}
-%		\subfloat[]{\includegraphics[width=0.34\textwidth]{Figures/diff_offset_proposedfinal}
-%			\label{diff_offset_proposedfinal}}
-%		\caption{Simultaneous denoising and reconstruction error \wen{3-D figures} comparison between \dlo{both}\wen{two} algorithms after \dlo{10}\wen{ten} iterations.
-(a and c) show the DRR approach with RMSE values of $ 2.22\% $ and $ 2.64\% $ in one common midpoint and one common offset gathers, respectively.
-(b and d) correspond to the proposed approach with RMSE values of $ 1.53\% $ and $ 1.48\% $ in one common midpoint and one common offset gathers, respectively.}
-%		\label{cmp_drrokerrfinal,cmp_proposederrfinal,diff_offset_drrokfinal,diff_offset_proposedfinal}
-%	\end{figure}%fig.3
-\begin{figure}[htb!]
-		\centering
-	        \subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-drr-hxhy-e}\label{synth-drr-hxhy-e}}
-	        \subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-rdrr-hxhy-e}\label{synth-rdrr-hxhy-e}}\\
-	        \subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-drr-xy-e}\label{synth-drr-xy-e}}
-	        \subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-rdrr-xy-e}\label{synth-rdrr-xy-e}}
-		\caption{Simultaneous denoising and reconstruction error \wen{3D figures} comparison between \dlo{both}\wen{two} algorithms after \dlo{10}\wen{ten} iterations.
+
+\inputdir{synth_Linear_NV03_MT70}
+\multiplot{4}{synth-drr-hxhy-e,synth-rdrr-hxhy-e,synth-drr-xy-e,synth-rdrr-xy-e}{width=0.35\textwidth}{Simultaneous denoising and reconstruction error \wen{3D figures} comparison between \dlo{both}\wen{two} algorithms after \dlo{wen}\wen{10} iterations.
 (a and c) show the DRR approach with rms error values of $2.22\%$ and $2.64\%$ in one common-midpoint and one common-offset gather, respectively.
 (b and d) correspond to the proposed approach with rms error values of $1.53\%$ and $1.48\%$ in one common-midpoint and one common-offset gather, respectively.}
-		\label{synth-drr-hxhy-e,synth-rdrr-hxhy-e,synth-drr-xy-e,synth-rdrr-xy-e}
-	\end{figure}%fig.3
-}
-%\begin{figure}[htb!] 
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2Doffsetclean7003}
-%			\label{a}}
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DoffsetNoisy7003}
-%			\label{b}}
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DoffsetObserved7003}
-%			\label{Fiigure:c}}\\
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DoffsetDRR7003}
-%			\label{Fiigure:d}}
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DoffsetProposed7003}
-%			\label{Fiigure:e}}	
-%		\caption{Common offset 2-D figures comparison ($x_1$ = 6, $x_2$ = 6) after 10 iterations between both algorithms.
-(a) Clean data.
-(b) Noisy data with 0.3 as noise variance.
-(c) Observed noisy and incomplete data with 70\% of missing traces.
-(d-e) Simultaneously denoised and reconstructed data using both methods, respectively.}
-%		\label{5}
-%	\end{figure}
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DRMSEoffsetDRR7003}
-%			\label{a}}
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DRMSEoffsetProposed7003}
-%			\label{b}}
-%		\caption{Simultaneous reconstruction and denoising errors comparison in common offset ($x_1$ = 6, $x_2$ = 6) after 10 iterations between both algorithms.
-(a) shows the DRR approach with an RMSE of 2.64\%.
-(b) shows the proposed approach with an RMSE of 1.48\%.}
-%		\label{6}
-%	\end{figure}
-%}
-
-\wen{Moreover,} we conduct a comparison between the amplitude of each corresponding \dlo{5-D}data \wen{plotted in Figure \ref{synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-drr-hxhy,synth-rdrr-hxhy}} to highlight more distinctly the differences.
-Figure \dlo{\ref{7}}\wen{\ref{synth-ss}} displays a comparison between each amplitude.
+
+\wen{Moreover,} we conduct a comparison between the amplitude of each corresponding \dlo{5-D}data \wen{plotted in Figure \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-drr-hxhy,synth-rdrr-hxhy}} to highlight more distinctly the differences.
+Figure \dlo{\ref{fig:7}}\wen{\ref{fig:synth-ss}} displays a comparison between each amplitude.
 The green, yellow and black lines are, respectively, from the original, noisy, and observed data.
@@
 The blue and red lines correspond to the DRR approach and proposed approach, respectively.
-Clearly shown in Figure \dlo{\ref{7}}\wen{\ref{synth-ss}}, the blue and red lines are very regular in most areas.
+Clearly shown in Figure \dlo{\ref{fig:7}}\wen{\ref{fig:synth-ss}}, the blue and red lines are very regular in most areas.
 However, we find that the green and red lines are \dlo{too much close} \wen{much closer} to each other.
@@
 
-%\AtEndDocument{
-%	\old{\begin{figure}
-%			\centering
-%			\includegraphics[width=1\%textwidth]{Figures/Amplit%ude_with_Time}
-%			\caption{Comparison of the amplitude of each corresponding 5-D synthetic data after 10 iterations between both algorithms.
-The green line is from the clean data.
-The yellow line denotes the noisy data.
-The amplitude of the observed data, in this case, is zero and thus cannot be seen from the figure.
-The blue line corresponds to the damped rank-reduction method.
-The red line corresponds to the proposed method.
-The proposed method can provide a good amplitude very close to the clean data than the DRR method.}
-%			\label{7}
-%	\end{figure}
-%}
-%}
-%\section{acknowledgments}
-%
-%The authors would like to thank Hang Wang for constructive
-%comments and suggestions, which have helped to improve this manuscript.
-The authors also thank Min Bai, Dong Zhang, Mi Zhang, Weilin Huang, and Yatong Zhou for fruitful discussions on the rank-reduction method.
-\AtEndDocument{
-	\wen{\begin{figure}
-			\centering
-                        {\includegraphics[width=0.9\textwidth]{synth_Linear_NV03_MT70/Fig/synth-ss}}
-			\caption{Comparison of a single trace amplitude of each \dlo{5-D synthetic} data \wen{shown in Figure \ref{synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-drr-hxhy,synth-rdrr-hxhy}}.
+\inputdir{synth_Linear_NV03_MT70}
+\plot{synth-ss}{width=0.8\columnwidth}{Comparison of a single trace amplitude of each \dlo{5-D synthetic} data \wen{shown in Figure \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-drr-hxhy,synth-rdrr-hxhy}}.
 The green line is from the clean data.
@@
 The proposed method can provide a good amplitude very close to the clean compared to the DRR method.}
-			\label{synth-ss}
-	\end{figure}}
-}%fig.4
+
 \dlo{We further compare the performance of the DRR method and our approach from another aspect using the amplitude \dlo{and frequency-space (f-x)} spectra.
-According to the amplitude spectrum comparison displayed in Figure \dlo{\ref{8}}\wen{\ref{5}}, we deduce that both approaches can recover the signal.
+According to the amplitude spectrum comparison displayed in Figure \dlo{\ref{fig:8}}\wen{\ref{fig:5}}, we deduce that both approaches can recover the signal.
 However, there is a remarkable difference in the amplitude in favor of our algorithm.
 It can be explained by the fact that DRR approach suppresses the residual noise at the entire frequency band to a relatively weak degree whereas our approach removes the residual noise sufficiently.
-That is why the amplitude spectrum of the proposed approach shown in Figure \dlo{\ref{8}(e)} \ref{5}(e) is perfect and very similar to that of the true data shown in Figure \dlo{\ref{8}(a)} \wen{\ref{5}(a)}.
+That is why the amplitude spectrum of the proposed approach shown in Figure \dlo{\ref{Figure:8}(e)} \ref{Figure:5}(e) is perfect and very similar to that of the true data shown in Figure \dlo{\ref{Figure:8}(a)} \wen{\ref{Figure:5}(a)}.
 This analysis demonstrates one more time the better performance of the proposed algorithm compared to the DRR method.
-\wen{Therefore, we deduce that the proposed method can obtain successful results even though the observed noisy and incomplete data have very low amplitudes as shown in Figures \ref{5}(c)} \dlo{\ref{8}(c)}.}
-
-%\AtEndDocument{
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/AmplitudeSpectrumClean}
-%			\label{a}}
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/AmplitudeSpectrumNoisy}
-%			\label{b}}
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/AmplitudeSpectrumObserved}
-%			\label{Fiigure:c}}\\
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/AmplitudeSpectrumdrr}
-%			\label{Fiigure:d}}
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/AmplitudeSpectrumPropoposed}
-%			\label{Fiigure:e}}
-%		\caption{Amplitude spectra comparison of each \old{5-D data after 10 iterations between both algorithms} data \new{displayed in Figure \ref{2}}.
-(a) is from the clean data.
-(b) represents the noisy data.
-(c) shows the observed data.
-(d) is from the DRR approach.
-(e) is from the proposed method.
-The amplitude spectrum of the true data and that of the proposed method are very close to each other.}
-%		\label{5}
-%	\end{figure}
-%}
-%\dlo{According to the f-x spectra of each corresponding 5-D data, we specify that Figures \ref{6} and \ref{7} denote the f-x spectra in one common midpoint and offset gathers, respectively.
-From these figures, we find that the f-x spectra of our method displayed in Figures \ref{6}(e) and \ref{7}(e) are much smoother and clearer than those of the DRR algorithm shown in Figures \ref{6}(d) and \ref{7}(d).
-The f-x spectra comparison corroborates the better restoration performance of our approach in the frequency domain.
-Therefore, we deduce that the proposed method can obtain successful results even though the observed noisy and incomplete data have very low frequencies as shown in Figures \ref{5}(c), \ref{6}(c) and \ref{7}(c).}
-
-%\AtEndDocument{
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencycmpclean}
-%			\label{a}}
-%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencycmpnoisy}
-%			\label{b}}
-%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencycmpobserved}
-%			\label{Fiigure:c}}\\
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencycmpdrr}
-%			\label{Fiigure:d}}
-%%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencycmpproposed}
-%			\label{Fiigure:e}}
-%		\caption{Common midpoint f-x spectrum comparison of each 5-D synthetic data ($Nx_1$ = 6, $Nx_2$ = 6) after 10 iterations between both algorithms.
-(a-c) show the f-x spectra of clean, noisy, observed data, respectively.
-(d and e) show f-x spectra after using the DRR approach and the proposed approach, respectively.}
-%		\label{9}
-%	\end{figure}
-%	\begin{figure}[htb!]
-
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencyOffsetclean}
-%			\label{a}}
-%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencyOffsetnoisy}
-%			\label{b}}
-%%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencyOffsetobserved}
-%			\label{Fiigure:c}}\\
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencyOffsetdrr}
-%			\label{Fiigure:d}}
-%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/frequencyOffsetproposed}
-%			\label{Fiigure:e}}
-%		\caption{Common offset f-x spectrum comparison of each 5-D synthetic data ($x_1$ = 6, $x_2$ = 6) after 10 iterations between both algorithms.
-(a-c) display the f-x spectra of clean, noisy, observed data, respectively.
-(d and e) display the f-x spectra after using the DRR approach and the proposed approach, respectively.}
-%		\label{10}
-%	\end{figure}
-%}
+\wen{Therefore, we deduce that the proposed method can obtain successful results even though the observed noisy and incomplete data have very low amplitudes as shown in Figures \ref{Figure:5}(c)} \dlo{\ref{Figure:8}(c)}.}
+
 Moreover, we conduct several numerical tests to compare the performances of both algorithms.
@@
 Using the same observed noisy and incomplete 5D synthetic data corrupted by a noise level of $0.3$ and $70\%$ of missing traces, we \dlo{first} highlight the behavior of each method in terms of S/N \dlo{and RMSE}to the iteration numbers.
-\dlo{Figures \ref{11}(a) and \ref{11}(b) show the S/N and rms error diagrams respectively, for}\wen{Figure \ref{SNR_with_iterations} shows} the S/N \wen{values} for the iteration numbers \dlo{ranged}\wen{ranging} from $5$ to $30$.
+\dlo{Figures \ref{Figure:11}(a) and \ref{fig:11}(b) show the S/N and rms error diagrams respectively, for}\wen{Figure \ref{fig:SNR_with_iterations} shows} the S/N \wen{values} for the iteration numbers \dlo{ranged}\wen{ranging} from $5$ to $30$.
 The blue and red lines indicate the S/N diagrams of the DRR method and the proposed approach, respectively.
@@
 
-\AtEndDocument{
-	\begin{figure}[htb!]
-		\centering
-		\includegraphics[width=0.5\textwidth]{Fig/SNR_with_iterations}
-		\caption{Comparison of S/N diagrams regarding the iteration numbers.
+\inputdir{./}
+\plot{SNR_with_iterations}{width=0.5\columnwidth}{Comparison of S/N diagrams regarding the iteration numbers.
 The blue and red lines correspond to the DRR and the proposed approaches, respectively.
@@
 We decimated $70\%$ of traces and added a noise level of $0.3$ for this test.}
-		\label{SNR_with_iterations}
-	\end{figure}
-}%fig.5
-%\AtEndDocument{
-%	\begin{figure}[htb!]
-%		\centering
-%		\includegraphics[width=0.5\textwidth]{Figures/SNRwithiterations}
-%	\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSEwithiterations}
-%			\label{b}}
-%		\caption{Comparison of SNR diagrams with respect to the iteration number.
-The blue and red lines correspond to the DRR method and the proposed approach, respectively.
-The accuracy of the proposed method is better than the DRR method as the iteration number increases.
-We decimated $70\%$ of traces and added a noise level of $ 0.3 $.}
-%		\label{11}
-%	\end{figure}
-%}
+
 Then, we use $0.3$ as noise variance and we realize nine experiments with different decimated 5D synthetic data ranging from $10\% $ to $90\% $.
-Figure \dlo{\ref{12}(a)}\wen{\ref{SNR_with_MissingTraces}\dlo{(a)}} \dlo{and (b) show respectively the SNR and RMSE}\wen{shows the S/N} diagrams with respect to the percentage of decimated data.
+Figure \dlo{\ref{Figure:12}(a)}\wen{\ref{fig:SNR_with_MissingTraces}\dlo{(a)}} \dlo{and (b) show respectively the SNR and RMSE}\wen{shows the S/N} diagrams with respect to the percentage of decimated data.
 At last, we randomly decimate $90\%$ of the 5D synthetic data and we conduct six tests using different noise levels 0.05, 0.2, 0.4, 0.6, 0.8 and 1.
-Figure \dlo{\ref{13}(a)}\wen{\ref{SNR_with_noise_levels}\dlo{(b)} denotes}\dlo{present respectively,} the S/N \dlo{and RMSE}diagrams regarding noise levels.
+Figure \dlo{\ref{Figure:13}(a)}\wen{\ref{fig:SNR_with_noise_levels}\dlo{(b)} denotes}\dlo{present respectively,} the S/N \dlo{and RMSE}diagrams regarding noise levels.
 In both cases, the blue and red lines denote the diagrams of the restored data using the DRR approach and our method, respectively.
@@
 
-\AtEndDocument{
-	\begin{figure}[htb!]
-		\centering
-		\subfloat[]{\includegraphics[width=0.5\textwidth]{Fig/SNR_with_MissingTraces}
-			\label{SNR_with_MissingTraces}}
-		\subfloat[]{\includegraphics[width=0.5\textwidth]{Fig/SNR_with_noise_levels}
-			\label{SNR_with_noise_levels}}
-		\caption{Comparison of S/N\dlo{(a) and RMSE (b)} diagrams after \dlo{ten}\wen{10} iterations between \dlo{both}\wen{two} algorithms.
+\inputdir{./}
+\multiplot{2}{SNR_with_MissingTraces,SNR_with_noise_levels}{width=0.45\textwidth}{Comparison of S/N\dlo{(a) and RMSE (b)} diagrams after \dlo{ten}\wen{10} iterations between \dlo{both}\wen{two} algorithms.
 (a) S/N diagrams for the percentage of missing data.
@@
 We used a noise variance of $0.3$, and then we decimated the traces from $10$ to $90\%$ for this demonstration.}
-		\label{SNR_with_MissingTraces,SNR_with_noise_levels}
-	\end{figure}
-}%fig.6
-
-%\AtEndDocument{
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[%width=0.5\textwidth]{Figures/%SNRwithMissingTraces}
-%			\label{a}}
-%%		\subfloat[]{\includegraphics[%width=0.5\textwidth]{Figures/%SNRwithnoiselevels}
-%			\label{b}}
-%	\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSEwithmissingTraces}
-%			\label{b}}
-%		\caption{Comparison of SNR \old{(a) and RMSE (b)} diagrams for the percentage of missing data (a) and noise levels (b)  after 10 iterations between both algorithms.
-The blue and red line corresponds to the DRR method and the proposed approach, respectively.
-The red line still presents \old{the least RMSE} higher \new{SNRs values}.
-We used a noise variance of $ 0.3 $, and then, decimated the %traces from $ 10 $ to $ 90\% %$.}
-%		\label{12}
-%	\end{figure}
-%}
-%\dlo{At last, we randomly decimate $ 90\% $ of the 5-D synthetic data and we conduct six tests using different noise levels 0.05, 0.2, 0.4, 0.6, 0.8 and 1.
-Figures \ref{13}(a-b) present respectively, the SNR and RMSE diagrams with respect to noise levels.
-After analysis of the plotted results, it is evident that the SNR diagrams using the proposed method presented in red line is always superior to that of the DRR in blue line.
-The relative errors values of the proposed approach (red line) are still fewer than that of the DRR approach (blue line).
-It is well visible that the proposed method yields smaller denoising and reconstruction errors than the DRR method.
-Manifestly, when the noise variances increase, the distance between both low-rank methods also decreases.
-However, the distance between both diagrams is still imposing.
-From the diagrams presented, we deduce that our algorithm provides better results than the DRR method in terms of SNR and RMSE.
-Thus, the proposed RDRR method can be used to denoise 5-D seismic data while reconstructing the missing values even in the conditions of a high degree of missing traces and strong random noise.}
-
-%\AtEndDocument{
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/SNRwithnoiselevels}
-%			\label{a}}
-%		\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSEwithnoiselevels}
-%			\label{b}}
-%		\caption{Comparison of SNR (a) and RMSE (b) diagrams with respect to noise variance after 10 iterations between both algorithms.
-The proposed method in the red line outperforms the DRR approach denoted in blue line when the noise level increase.
-Here, we used 90\% as a percentage of missing traces and then we added the noise variance as shown in the figure.}
-%		\label{13}
-%	\end{figure}
-%}
-
-%\dlo{To corroborate the numerical tests, we display the results for only a single shot gather of each simultaneously denoised and reconstructed signal.
-The data are from an observed data contaminated by a noise level of $ 0.3 $ and $ 80\% $ of missing data.
-Here, the following parameters are chosen to examine the performance of both algorithms : rank {$K$ = 6} and a damped factor {$d$ = 2} for the DRR approach.
-In addition to these values, we used a cooling factor ${\beta = 3.3}$, a rational transfer function coefficient ${e = 0.95}$ and a window size ${T = 1}$ for the proposed algorithm.
-We run both methods using 10 weighted POCS-like iterations.
-Figure \ref{14}(a) displays the true data.
-Figures \ref{14}(b) and (c) denote the noisy data with SNR of -5.38 dB and observed noisy and incomplete data with SNR of $ -1.74 $ dB, respectively.
-Figures \ref{14}(d) and \ref{14}(e) display the results using the DRR method and the proposed method, respectively.
-The SNRs are 10.40 dB and 19.18 dB for the DRR approach and the proposed approach, respectively.
-Figures \ref{15}(a) corresponds to the RMSE result of the DRR method and  Figures \ref{15}(b) is from the proposed method.
-The useful signal is recovered with an RMSE of $4.89\%$ and $1.56\%$ respectively for the DRR approach and our algorithm.
-We then compare the corresponding frequency-wavenumber spectra of the clean, noisy, observed, simultaneously denoised and reconstructed data form the former algorithm and the proposed approach.
-They are respectively displayed in Figures \ref{16}(a-e) to see the performance in other domain.
-Here, our algorithm provides smoother and clear results than the DRR method.
-Indeed, the frequency-wavenumber spectrum obtained with the proposed approach is even clearer than that of the DRR method.}
+
 \wen{To corroborate the numerical tests, we display the results for only a single shot gather of each simultaneously denoised and reconstructed signal.
@@
 We run both methods using \dlo{ten}\wen{$10$} weighted POCS-like iterations.
-Figure \ref{synth-clean-hxhy-s}\dlo{(a)} displays the true data.
-Figures \ref{synth-noisy-hxhy-s}\dlo{(b)} and \ref{synth-obs-hxhy-s}\dlo{(c)} denote the noisy data with S/N of $-5.38$ dB and observed noisy and incomplete data with S/N of $-1.74$ dB, respectively.
-Figures \ref{synth-drr-hxhy-s}\dlo{(d)} and \ref{synth-rdrr-hxhy-s}\dlo{(e)} display the results using the DRR method and the proposed method, respectively.
-The SNRs are $10.40$ and $19.18$ dB for the DRR approach and the proposed approach, respectively.
-Figures \ref{synth-drr-hxhy-s-e}\dlo{(a)} and \ref{synth-rdrr-hxhy-s-e}\dlo{(b)} are the rms error \dlo{results}\wen{figures} of the DRR method and the proposed method, respectively.
+Figure \ref{fig:synth-clean-hxhy-s}\dlo{(a)} displays the true data.
+Figures \ref{fig:synth-noisy-hxhy-s}\dlo{(b)} and \ref{fig:synth-obs-hxhy-s}\dlo{(c)} denote the noisy data with S/N of $-5.38$ dB and observed noisy and incomplete data with S/N of $-1.74$ dB, respectively.
+Figures \ref{fig:synth-drr-hxhy-s}\dlo{(d)} and \ref{fig:synth-rdrr-hxhy-s}\dlo{(e)} display the results using the DRR method and the proposed method, respectively.
+The S/Ns are $10.40$ and $19.18$ dB for the DRR approach and the proposed approach, respectively.
+Figures \ref{fig:synth-drr-hxhy-s-e}\dlo{(a)} and \ref{fig:synth-rdrr-hxhy-s-e}\dlo{(b)} are the rms error \dlo{results}\wen{figures} of the DRR method and the proposed method, respectively.
 The useful signal is recovered with an rms error of $4.89\%$ and $1.56\%$ respectively for the DRR approach and our approach.}
 
-\AtEndDocument{
-\begin{figure}[htb!]
-	\centering
-	\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_linear_NV03_MT80/Fig/synth-clean-hxhy-s}\label{synth-clean-hxhy-s}}
-	\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_linear_NV03_MT80/Fig/synth-noisy-hxhy-s}\label{synth-noisy-hxhy-s}}
-	\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_linear_NV03_MT80/Fig/synth-obs-hxhy-s}\label{synth-obs-hxhy-s}}\\
-	\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_linear_NV03_MT80/Fig/synth-drr-hxhy-s}\label{synth-drr-hxhy-s}}
-	\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_linear_NV03_MT80/Fig/synth-rdrr-hxhy-s}\label{synth-rdrr-hxhy-s}}
-	\caption{Simultaneous reconstruction and denoising \wen{2D figures} comparison in only a single shot gather.
+\inputdir{synth_linear_NV03_MT80}
+\multiplot{5}{synth-clean-hxhy-s,synth-noisy-hxhy-s,synth-obs-hxhy-s,synth-drr-hxhy-s,synth-rdrr-hxhy-s}{width=0.30\textwidth}{Simultaneous reconstruction and denoising \wen{2D figures} comparison in only a single shot gather.
 (a) Clean data.
@@
 (d and e) Simultaneously denoised and reconstructed data using the DRR method the proposed approach, respectively.}
-	\label{synth-clean-hxhy-s,synth-noisy-hxhy-s,synth-obs-hxhy-s,synth-drr-hxhy-s,synth-rdrr-hxhy-s}
-\end{figure}%fig.7
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/single_shot_Clean_0380}
-%			\label{single_shot_Clean_0380}}
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/single_shot_Noisy_0380}
-%			\label{single_shot_Noisy_0380}}
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/single_shot_Observed_0380}
-%			\label{single_shot_Observed_0380}}\\
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/single_shot_DRR_0380}
-%			\label{single_shot_DRR_0380}}
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/single_shot_Proposed_0380}
-%			\label{single_shot_Proposed_0380}}
-%		\caption{Simultaneous reconstruction and denoising \wen{2-D figures} comparison in only a single shot gather.
-(a) Clean data.
-(b) Noisy data with a variance of $0.3$.
-(c) Observed noisy with $80\%$ of missing traces.
-(d and e) Simultaneously denoised and reconstructed data using the DRR method the proposed approach, respectively.}
-%		\label{single_shot_Clean_0380,single_shot_Noisy_0380,single_shot_Observed_0380,single_shot_DRR_0380,single_shot_Proposed_0380}%fig.7
-%	\end{figure}
-	\begin{figure}[htb!]
-		\centering
-		\subfloat[]{\includegraphics[width=0.5\textwidth]{synth_linear_NV03_MT80/Fig/synth-drr-hxhy-s-e}\label{synth-drr-hxhy-s-e}}
-		\subfloat[]{\includegraphics[width=0.5\textwidth]{synth_linear_NV03_MT80/Fig/synth-rdrr-hxhy-s-e}\label{synth-rdrr-hxhy-s-e}}	
-		\caption{Simultaneous reconstruction and denoising error \wen{2D figures} comparison of only one shot gather extracted from the 5D data matrix.
+
+\inputdir{synth_linear_NV03_MT80}
+\multiplot{2}{synth-drr-hxhy-s-e,synth-rdrr-hxhy-s-e}{width=0.35\textwidth}{Simultaneous reconstruction and denoising error \wen{2D figures} comparison of only one shot gather extracted from the 5D data matrix.
 (a) DRR approach with an rms error of $4.89\%$.
 (b) Proposed approach with an rms error of $1.56\%$.}
-		\label{synth-drr-hxhy-s-e,synth-rdrr-hxhy-s-e}
-	\end{figure}
-}%fig.8
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/WaveNumberclean}
-%			\label{a}}
-%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/WaveNumbernoisy}
-%			\label{b}}
-%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/WaveNumberObserved}
-%			\label{Fiigure:c}}\\
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/WaveNumberdrr}
-%			\label{Fiigure:d}}
-%		\subfloat[]{\includegraphics[width=0.3\tex%twidth]{Figures/WaveNumberproposed}
-%			\label{Fiigure:e}}
-%		\caption{Frequency-wavenumber spectra comparison of a group of only one shot gathers (15) extracted from the 5-D data matrix.
-(a-c) correspond to the clean data, noisy data with a variance of 0.3 and observed data with $ 80\% $ of missing data, respectively.
-(c and d) denote the DRR approach and the proposed framework, respectively.}
-%		\label{12}
-%	\end{figure}
-%}
-Figure \dlo{\ref{17} and \ref{19}}\wen{\ref{synth-drr-hxhy-s0290,synth-rdrr-hxhy-s0290,synth-drr-xy-s0290,synth-rdrr-xy-s0290}} illustrates the numerical analysis\dlo{, respectively} in one common midpoint \dlo{($Nx_1$ = 6, $Nx_2$ = 6)}\wen{($x$ = 6, $y$ = 6)} and offset \dlo{($x_1$ = 6, $x_2$ = 6)}\wen{($hx$ = 6, $hy$ = 6)} gathers of each simultaneously denoised and reconstructed signal from \dlo{the}\wen{an} observed data corrupted by a noise variance of $0.2$ and $90\%$ of missing data.
+
+Figure \dlo{\ref{fig:17} and \ref{fig:19}}\wen{\ref{fig:synth-drr-hxhy-s0290,synth-rdrr-hxhy-s0290,synth-drr-xy-s0290,synth-rdrr-xy-s0290}} illustrates the numerical analysis\dlo{, respectively} in one common midpoint \dlo{($Nx_1$ = 6, $Nx_2$ = 6)}\wen{($x$ = 6, $y$ = 6)} and offset \dlo{($x_1$ = 6, $x_2$ = 6)}\wen{($hx$ = 6, $hy$ = 6)} gathers of each simultaneously denoised and reconstructed signal from \dlo{the}\wen{an} observed data corrupted by a noise variance of $0.2$ and $90\%$ of missing data.
 \wen{The S/N of this observed data $-0.23$ dB.} In these conditions, we use a rank {$K$ = 6} and a \dlo{damped}\wen{damping} factor {$d$ = 2} for the DRR approach.
@@
 We run both methods using \dlo{ten}\wen{$10$} weighted POCS-like iterations.
-Figures \ref{synth-drr-hxhy-s0290}\dlo{(a)} and \ref{synth-drr-hxhy-s0290}\dlo{(c)} display the results of the simultaneous denoising and reconstruction data via the DRR method.
+Figures \ref{fig:synth-drr-hxhy-s0290}\dlo{(a)} and \ref{fig:synth-drr-hxhy-s0290}\dlo{(c)} display the results of the simultaneous denoising and reconstruction data via the DRR method.
 The S/N is approximately $5.20$ dB.
-Figures \wen{\ref{synth-rdrr-hxhy-s0290}\dlo{(b)} and \ref{synth-rdrr-hxhy-s0290}\dlo{(d)}} display the results using the proposed method.
+Figures \wen{\ref{fig:synth-rdrr-hxhy-s0290}\dlo{(b)} and \ref{fig:synth-rdrr-hxhy-s0290}\dlo{(d)}} display the results using the proposed method.
 The S/N is about $17.84$ dB.
-\wen{The recovery error using each approach is displayed in Figure \ref{synth-drr-hxhy-s-e0290,synth-rdrr-hxhy-s-e0290,synth-drr-xy-s-e0290,synth-rdrr-xy-s-e0290}.
-Figures \ref{synth-drr-hxhy-s-e0290}\dlo{(a)} and \ref{synth-drr-xy-s-e0290}\dlo{(c)} show the DRR approach with \wen{an} an rms error of $8.37\%$ and $8.82\%$ in one common-midpoint and one common-offset gather, respectively.
-Figures \ref{synth-drr-hxhy-s-e0290}\dlo{(b)} and \ref{synth-rdrr-xy-s-e0290}\dlo{(d)} are from the proposed approach with \wen{an} rms error of $2.63\%$ and $2.34\%$ in one common-midpoint and one common-offset gather, respectively.
+\wen{The recovery error using each approach is displayed in Figure \ref{fig:synth-drr-hxhy-s-e0290,synth-rdrr-hxhy-s-e0290,synth-drr-xy-s-e0290,synth-rdrr-xy-s-e0290}.
+Figures \ref{fig:synth-drr-hxhy-s-e0290}\dlo{(a)} and \ref{fig:synth-drr-xy-s-e0290}\dlo{(c)} show the DRR approach with \wen{an} an rms error of $8.37\%$ and $8.82\%$ in one common-midpoint and one common-offset gather, respectively.
+Figures \ref{fig:synth-drr-hxhy-s-e0290}\dlo{(b)} and \ref{fig:synth-rdrr-xy-s-e0290}\dlo{(d)} are from the proposed approach with \wen{an} rms error of $2.63\%$ and $2.34\%$ in one common-midpoint and one common-offset gather, respectively.
 This comparison shows the superiority of the proposed algorithm when the observed data is severely decimated.}
-%\dlo{Figures \ref{17}(a) and \ref{19}(a) denote the original data.
-Figures \ref{17}(b) and \ref{19}(b) are from the noisy data.
-The SNR of the noisy data is of {$-1.86$ dB}.
-Figures \ref{17}(c) and \ref{19}(c) show the observed noisy data with $ 90 \% $ missing.
-The SNR is extremely low with a value of $ -0.23 $ dB.
-Figures \ref{17}(d) and \ref{19}(d) display the results of the simultaneous denoising and reconstruction data from the DRR method.
-The SNR is about $ 5.20 $ dB.
-Figures \ref{17}(e) and \ref{19}(e) display the results from the proposed method.
-The SNR is about $ 17.84 $ dB.
-The proposed approach results are much better than those of the DRR method.
-Figures \ref{18} and \ref{20} show the RMSE from each method in one common midpoint gather and one common offset gather, respectively.
-Figures \ref{18}(a) and \ref{20}(a) are from the DRR method with RMSE values of $ 8.37 \% $ and $ 8.82 \% $, respectively.
-Figures \ref{18}(b) and \ref{20}(b) correspond to the proposed method with  RMSE values of $ 2.63 \%$ and $ 2.34 \%$, respectively.
-This comparison shows the superiority of the proposed algorithm when the observed data is severely decimated.}
-
-\AtEndDocument{
-	\begin{figure}[htb!]
-		\centering
-		\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_linear_NV02_MT90/Fig/synth-drr-hxhy-s0290} 
-			\label{synth-drr-hxhy-s0290}}
-		\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_linear_NV02_MT90/Fig/synth-rdrr-hxhy-s0290}
-			\label{synth-rdrr-hxhy-s0290}}\\
-		\centering
-		\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_linear_NV02_MT90/Fig/synth-drr-xy-s0290}
-			\label{synth-drr-xy-s0290}}
-		\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_linear_NV02_MT90/Fig/synth-rdrr-xy-s0290}
-			\label{synth-rdrr-xy-s0290}}
-		\caption{Simultaneous denoising and reconstruction \wen{2D figures} comparison between \dlo{both}\wen{two} approaches after \dlo{ten}\wen{10} iterations.
+
+\inputdir{synth_linear_NV02_MT90}
+\multiplot{4}{synth-drr-hxhy-s0290,synth-rdrr-hxhy-s0290,synth-drr-xy-s0290,synth-rdrr-xy-s0290}{width=0.35\textwidth}{Simultaneous denoising and reconstruction \wen{2D figures} comparison between \dlo{both}\wen{two} approaches after \dlo{ten}\wen{10} iterations.
 (a and c) display the DRR approach in one common-midpoint and one common-offset gather, respectively.
@@
 We used an observed data corrupted by a noise variance of $0.2$ and $90\%$ of missing data for this example.}
-		\label{synth-drr-hxhy-s0290,synth-rdrr-hxhy-s0290,synth-drr-xy-s0290,synth-rdrr-xy-s0290}
-	\end{figure}
-}%fig.9
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSEcmpDRR9002}
-%			\label{a}}
-%		\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSEcmpProposed9002}
-%			\label{b}}
-%		\caption{Simultaneous denoising and reconstruction errors comparison of common midpoint 2-D figure ($Nx_1$ = 6, $Nx_2$ = 6) after 10 iterations between both algorithms.
-(a) shows the DRR approach with an RMSE of $ 8.37\% $.
-(b) shows the proposed approach with an RMSE of $ 2.63\% $.}
-%		\label{14}
-%	\end{figure}
-
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSEoffsetDRR9002}
-%			\label{a}}
-%		\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSEoffsetProposed9002}
-%			\label{b}}
-
-%		\caption{Simultaneous denoising and reconstruction errors comparison in common offset ($x_1$ = 6, $x_2$= 6) after 10 iterations between both algorithms.
-(a) displays the DRR approach with an RMSE of $ 8.82\% $.
-(b) shows the proposed approach with an RMSE of $ 2.34\% $.}
-%		\label{16}
-%	\end{figure}
-%}
-\AtEndDocument{
-	\begin{figure}[htb!]
-		\centering
-		\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_linear_NV02_MT90/Fig/synth-drr-hxhy-s-e0290}
-			\label{synth-drr-hxhy-s-e0290}}
-		\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_linear_NV02_MT90/Fig/synth-rdrr-hxhy-s-e0290}
-			\label{synth-rdrr-hxhy-s-e0290}}\\
-		\centering
-		\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_linear_NV02_MT90/Fig/synth-drr-xy-s-e0290}
-			\label{synth-drr-xy-s-e0290}}
-		\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_linear_NV02_MT90/Fig/synth-rdrr-xy-s-e0290}
-			\label{synth-rdrr-xy-s-e0290}}
-		\caption{Simultaneous denoising and reconstruction error \wen{2D figures} comparison between both approaches after \dlo{ten}\wen{10} iterations.
+
+\inputdir{synth_linear_NV02_MT90}
+\multiplot{4}{synth-drr-hxhy-s-e0290,synth-rdrr-hxhy-s-e0290,synth-drr-xy-s-e0290,synth-rdrr-xy-s-e0290}{width=0.35\textwidth}{Simultaneous denoising and reconstruction error \wen{2D figures} comparison between both approaches after \dlo{ten}\wen{10} iterations.
 (a and c) display the DRR approach with an rms error of $8.37\%$ and $8.82\%$ in one common-midpoint and one common-offset gather, respectively.
 (b and d) display the proposed approach with an rms error of $2.63\%$ and $2.34\%$ in one common-midpoint and one common-offset gather, respectively.}
-		\label{synth-drr-hxhy-s-e0290,synth-rdrr-hxhy-s-e0290,synth-drr-xy-s-e0290,synth-rdrr-xy-s-e0290}
-	\end{figure}
-}%fig.10
+
 To further examine the performance of both approaches on a higher level of missing traces ($90\%$), we conduct a comparison using the periodogram power spectral density (PSD) of each corresponding 5D synthetic data mentioned in this last test.
-After a comparison of the different PSD diagrams shown in Figure \dlo{\ref{21}}\wen{\ref{Periodogrampsdcomparison9002}}, we find that the PSD of the restored data from our approach denoted in the red line and that of the true data shown in the green line are much closer to each other than the PSD of the DRR method indicated in \wen{the} the blue line.
+After a comparison of the different PSD diagrams shown in Figure \dlo{\ref{fig:21}}\wen{\ref{fig:Periodogrampsdcomparison9002}}, we find that the PSD of the restored data from our approach denoted in the red line and that of the true data shown in the green line are much closer to each other than the PSD of the DRR method indicated in \wen{the} the blue line.
 This comparison vividly \dlo{proves}\wen{demonstrates} that the proposed approach can yield the closest results to the original data\wen{,} even though we are in the conditions of a high level of missing traces.\\
@@
 
-\AtEndDocument{
-	\begin{figure}
-		\centering
-		\includegraphics[width=0.7\textwidth]{Fig/Periodogrampsdcomparison9002}
-		\caption{Comparison of the periodogram power spectral density (PSD) of each 5D data set after \dlo{ten}\wen{10} iterations between both algorithms.
+\inputdir{./}
+\plot{Periodogrampsdcomparison9002}{width=0.5\columnwidth}{Comparison of the periodogram power spectral density (PSD) of each 5D data set after \dlo{ten}\wen{10} iterations between both algorithms.
 The green line is from the clean data.
@@
 The red and green lines are very close to each other in most areas.}
-		\label{Periodogrampsdcomparison9002}
-	\end{figure}
-}%fig.11
-%\dlo{Figure \ref{22} compares the diagrams of percentage of similarity between the original data (green line) and both approaches results.
-They are first to the iteration number as shown in Figure \ref{22}(a), then ratio of missing data as displayed in Figure \ref{22}(b) and finally noise level as illustrated in Figure \ref{22}(c).
-Each sub-figure demonstrates that the percentage of similarity between the results obtained via the DRR method (blue line) is much bigger than that of the proposed results (red line).
-We, therefore, deduce that our approach can reduce the percentage of similarity to a very low level contrary to the DRR method.
-The diagram of the proposed method is closer to that of the original data as shown by the different sub-figures.
-The percentage of similarity demonstrates that the proposed approach can produce results closest to the original data.}
-
-%\AtEndDocument{
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/Swithiterations}
-%			\label{ a}}
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/SwithmissingTraces}
-%			\label{ b}}
-%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/Swithnoiselevels}
-%			\label{Fiigure: c}}
-
-%		\caption{Comparison of the percentage of similarity diagrams with respect to (a) iteration number, (b) ratio of decimated data (\%), (c) noise level.
-In each case, the green, blue and red line denotes the percentage of similarity diagram of the true, DRR, and proposed data, respectively.
-The green and red lines are closer to each other.}
-%		\label{ 22}
-%	\end{figure}
-%}
+
 \wen{We then conduct another example to demonstrate the effectiveness of the proposed method on 5D synthetic data containing curved events.
 We compare the performances of the proposed approach to that of the DRR approach.
-We display the one common-midpoint gather comparison in Figure \ref{hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}.
-The clean data is displayed in Figure \ref{hyper-clean2d-0}\dlo{(a)}.
-Figure \ref{hyper-obs2d-0}\dlo{(b)} denotes the observed data with $80\%$ missing values and $0.2$ as noise variance.
+We display the one common-midpoint gather comparison in Figure \ref{fig:hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}.
+The clean data is displayed in Figure \ref{fig:hyper-clean2d-0}\dlo{(a)}.
+Figure \ref{fig:hyper-obs2d-0}\dlo{(b)} denotes the observed data with $80\%$ missing values and $0.2$ as noise variance.
 The significant events are difficult to see due to the percentage of missing traces and strong noise.
@@
 We run both algorithms with \dlo{ten}\wen{$10$} POCS-like iterations.
-Figures \ref{hyper-drr2d-0}\dlo{(c)} and \ref{hyper-rdrr2d-0}\dlo{(d)} show the recovered data obtained using the DRR and the proposed approaches, respectively.} \wen{Compared to the DRR approach, our method performs much better results.
+Figures \ref{fig:hyper-drr2d-0}\dlo{(c)} and \ref{fig:hyper-rdrr2d-0}\dlo{(d)} show the recovered data obtained using the DRR and the proposed approaches, respectively.} \wen{Compared to the DRR approach, our method performs much better results.
 As \dlo{reveals}\wen{revealed by} the comparison, the DRR result seems \wen{to} contain artifacts due to the presence of significant noise, which affects the quality of the useful signal.
-To see the difference in detail, we magnify a section of each corresponding data displayed in Figure \ref{hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}.
-The red\dlo{s} frame boxes indicate the magnified section plotted in Figure \ref{hyper-z-clean,hyper-z-obs,hyper-z-drr,hyper-z-rdrr}.
-The Figures \ref{hyper-z-clean}\dlo{(a)}-\ref{hyper-z-rdrr}\dlo{(d)} correspond to the clean data, observed data, \dlo{recovered data}\wen{and data recovered} using the DRR and the proposed approaches, respectively.}
-\wen{\AtEndDocument{
-		\begin{figure}[htb!]
-			\centering
-			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-clean2d-0}
-				\label{hyper-clean2d-0}}\\
-			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-obs2d-0}
-				\label{hyper-obs2d-0}}\\
-			\centering
-			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-drr2d-0}
-				\label{hyper-drr2d-0}}\\
-			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-rdrr2d-0}
-				\label{hyper-rdrr2d-0}}		
-			\caption{\dlo{2-D figures c}\wen{C}omparison in one common-midpoint gather after \dlo{ten}\wen{10} iterations between \dlo{both}\wen{two} algorithms.
+To see the difference in detail, we magnify a section of each corresponding data displayed in Figure \ref{fig:hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}.
+The red\dlo{s} frame boxes indicate the magnified section plotted in Figure \ref{fig:hyper-z-clean,hyper-z-obs,hyper-z-drr,hyper-z-rdrr}.
+The Figures \ref{fig:hyper-z-clean}\dlo{(a)}-\ref{fig:hyper-z-rdrr}\dlo{(d)} correspond to the clean data, observed data, \dlo{recovered data}\wen{and data recovered} using the DRR and the proposed approaches, respectively.}
+
+\inputdir{synth_hyper}
+\multiplot{4}{hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}{width=1\textwidth}{\dlo{2-D figures c}\wen{C}omparison in one common-midpoint gather after \dlo{ten}\wen{10} iterations between \dlo{both}\wen{two} algorithms.
 (a) Clean data.
@@
 (c and d) Simultaneously denoised and reconstructed data using the DRR method the proposed method, respectively.}
-			\label{hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}
-\end{figure}}} %fig.12
-
-\wen{\AtEndDocument{
-		\begin{figure}[htb!]
-			\centering
-			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-z-clean}
-				\label{hyper-z-clean}}\\
-			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-z-obs}
-				\label{hyper-z-obs}}\\
-			\centering
-			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-z-drr}
-				\label{hyper-z-drr}}\\
-			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-z-rdrr}
-				\label{hyper-z-rdrr}}	
-			\caption{\dlo{{2-D figures c}}\wen{C}omparison of the magnified data displayed in Figure \ref{hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0} (the red frame box).
+
+\inputdir{synth_hyper}
+\multiplot{4}{hyper-z-clean,hyper-z-obs,hyper-z-drr,hyper-z-rdrr}{width=1\textwidth}{\dlo{{2-D figures c}}\wen{C}omparison of the magnified data displayed in Figure \ref{fig:hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0} (the red frame box).
 (a) Clean data.
@@
 (c and d) Simultaneously denoised and reconstructed data using the DRR and the proposed approaches, respectively.}
-			\label{hyper-z-clean,hyper-z-obs,hyper-z-drr,hyper-z-rdrr}
-	\end{figure}}
-}%fig.13
-%\new{
-%To see the difference in detail, we display a single shot gather of each data shown in Figure \ref{16}.
-The clean data is presented in Figure \ref{16}(a).
-The sub-figures \ref{16}(b)-\ref{16}(d) correspond to the observed data, the DRR data, and our algorithm data.}
-
-%\new{\AtEndDocument{
-%		\begin{figure}[htb!]
-%			\centering
-%			\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/single_shot_Clean_0280_curvedEvents}
-%				\label{a}}
-%			\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/single_shot_Observed_0280_curvedEvents}
-%				\label{Fiigure:c}}\\
-%			\centering
-%			\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/single_shot_DRR_0280_curvedEvents}
-%				\label{Fiigure:d}}
-%			\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/single_shot_Proposed_0280_curvedEvents}
-%				\label{Fiigure:e}}	%		
-%			\caption{Simultaneous denoising and reconstruction \new{2-D figures} comparison of a single shot gather after 10 iterations between both algorithms.
-(a) Clean data.
-(b) Observed data with $ 80\% $ of missing trace and $ 0.2 $ as noise variance.
-(c and d) Simultaneously denoised and reconstructed data using the DRR method the proposed approach, respectively.}
-%			\label{16}
-%		\end{figure}}
-%}
+
 \wen{
-	\dlo{Figures \ref{17} and \ref{18}}\wen{Figure \ref{hyper-drr2d-e,hyper-rdrr2d-e} corresponds} to the error figure of each restored data displayed in Figure \ref{hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}.
-\dlo{and Figures \ref{16}, respectively}\dlo{Figures \ref{17}(a) and \ref{18}(a) are}\wen{Figure \ref{hyper-drr2d-e}\dlo{(a)} is from the DRR approach}.
-\dlo{Figures \ref{17}(b) and \ref{18}(b)}\wen{Figure \ref{hyper-rdrr2d-e}\dlo{(b)} denotes the error figure} of the proposed algorithm.
-From Figures \ref{hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}\dlo{to Figure} \wen{to} \ref{hyper-drr2d-e,hyper-rdrr2d-e}, we find that although the DRR algorithm removes noise and reconstructs the missing traces well, our approach still performs better results.
+	\dlo{Figures \ref{fig:17} and \ref{fig:18}}\wen{Figure \ref{fig:hyper-drr2d-e,hyper-rdrr2d-e} corresponds} to the error figure of each restored data displayed in Figure \ref{fig:hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}.
+\dlo{and Figures \ref{fig:16}, respectively}\dlo{Figures \ref{fig:17}(a) and \ref{fig:18}(a) are}\wen{Figure \ref{fig:hyper-drr2d-e}\dlo{(a)} is from the DRR approach}.
+\dlo{Figures \ref{fig:17}(b) and \ref{fig:18}(b)}\wen{Figure \ref{fig:hyper-rdrr2d-e}\dlo{(b)} denotes the error figure} of the proposed algorithm.
+From Figures \ref{fig:hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}\dlo{to Figure} \wen{to} \ref{fig:hyper-drr2d-e,hyper-rdrr2d-e}, we find that although the DRR algorithm removes noise and reconstructs the missing traces well, our approach still performs better results.
 From the magnified data comparison, which vividly \dlo{demonstrate}\wen{demonstrates} the superiority of our approach, we find that the restored data obtained using our approach is much similar to the clean data than those of the DRR result.
@@
 The visual examination and the numerical test comparison demonstrate the recovery improvement of our algorithm on curved events.}
-\wen{
-	\AtEndDocument{
-		\begin{figure}[htb!]
-			\centering
-			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-drr2d-e}
-				\label{hyper-drr2d-e}}\\
-			\subfloat[]{\includegraphics[width=0.9\textwidth]{synth_hyper/Fig/hyper-rdrr2d-e}
-				\label{hyper-rdrr2d-e}}			
-			\caption{Simultaneous denoising and reconstruction error comparison in common-midpoint gather.
+
+\inputdir{synth_hyper}
+\multiplot{4}{hyper-drr2d-e,hyper-rdrr2d-e}{width=1\textwidth}{Simultaneous denoising and reconstruction error comparison in common-midpoint gather.
 \dlo{(a) Simultaneously denoised and reconstructed errors using the DRR method with an rms error of $9.07\%$.
@@
 (b) \dlo{displays the 2D figures of t}\wen{T}he error using the proposed method with an rms error of $3.08\%$.}}
-			\label{hyper-drr2d-e,hyper-rdrr2d-e}
-	\end{figure}}
-}%fig.14
-%\new{
-%	\AtEndDocument{
-%		\begin{figure}[htb!]
-%			\centering
-%			\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSE_single_shot_DRR_0280_curvedEvents}
-%				\label{a}}
-%			\subfloat[]{\includegraphics[width=0.5\textwidth]{Figures/RMSE_single_shot_Proposed_0280_curvedEvents}
-%				\label{b}}
-%			\caption{Simultaneous denoising and reconstruction error \new{2-D figures} comparison in a single shot gather.
-(a and b) Simultaneously denoised and reconstructed error using the DRR approach the proposed approach, respectively.}
-%			\label{18}
-%		\end{figure}}}
 
 \wen{
-	To demonstrate the performance of the proposed approach in other perspective\wen{s}, we display in Figure \dlo{\ref{19}}\wen{\ref{fx_clean_curved,fx_Observed_curved,fx_DRR_curved,fx_Proposed_curved}}, the corresponding f-x spectra of each data shown in Figure \dlo{\ref{16}}\wen{\ref{hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}}.
-The \dlo{sub-figures \dlo{\ref{19}(a)-\ref{19}(d)}\wen{\ref{15}(a)-\ref{15}(d)}}Figures \wen{\ref{fx_clean_curved}-\ref{fx_Proposed_curved}} correspond to the f-x spectra of the clean data, the observed data, the restored data using the DRR and the proposed approaches, respectively.
+	To demonstrate the performance of the proposed approach in other perspective\wen{s}, we display in Figure \dlo{\ref{Figure:19}}\wen{\ref{fig:fx_clean_curved,fx_Observed_curved,fx_DRR_curved,fx_Proposed_curved}}, the corresponding f-x spectra of each data shown in Figure \dlo{\ref{fig:16}}\wen{\ref{fig:hyper-clean2d-0,hyper-obs2d-0,hyper-drr2d-0,hyper-rdrr2d-0}}.
+The \dlo{sub-figures \dlo{\ref{fig:19}(a)-\ref{fig:19}(d)}\wen{\ref{fig:15}(a)-\ref{fig:15}(d)}}Figures \wen{\ref{fig:fx_clean_curved}-\ref{fig:fx_Proposed_curved}} correspond to the f-x spectra of the clean data, the observed data, the restored data using the DRR and the proposed approaches, respectively.
 From the comparison of each subfigure, we find that both approaches can successfully denoise and reconstruct the missing values in the whole frequency band (from $0$ \new{Hz} to $125$ Hz).
@@
 From this analysis, we can intuitively deduce that our approach can successfully remove the random noise while reconstructing the useful signal more adequately than the DRR approach.}
-\wen{	
-	\AtEndDocument{
-		\begin{figure}[htb!]
-			\centering
-			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/fx_clean_curved}
-				\label{fx_clean_curved}}
-			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/fx_Observed_curved}
-				\label{Fiigure:fx_Observed_curved}}\\
-			\centering
-			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/fx_DRR_curved}
-				\label{fx_DRR_curved}}
-			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/fx_Proposed_curved}
-				\label{fx_Proposed_curved}}		
-			\caption{\dlo{One single shot gathers}Frequency-space (f-x) spectra comparison after \dlo{ten}\wen{10} iterations between \dlo{both}\wen{two} algorithms.
+
+\inputdir{./}
+\multiplot{4}{fx_clean_curved,fx_Observed_curved,fx_DRR_curved,fx_Proposed_curved}{width=0.35\textwidth}{\dlo{One single shot gathers}Frequency-space (f-x) spectra comparison after \dlo{ten}\wen{10} iterations between \dlo{both}\wen{two} algorithms.
 (a and b) The clean data and observed data, respectively.
 (c and d) The DRR approach and the proposed framework, respectively.}
-			\label{fx_clean_curved,fx_Observed_curved,fx_DRR_curved,fx_Proposed_curved}
-	\end{figure}}
-}%fig.15
-
-%\dlo{\wen{To further demonstrate the performance of the proposed method on curved events, we compare the amplitude spectrum of each data shown in Figure \ref{14}.
-Figure \dlo{\ref{20}} \wen{\ref{18}} displays the comparison.
-The sub-figures \dlo{\ref{20,}(a)-\ref{20}(d)} \wen{\ref{18}(a)-\ref{18}(d)} correspond to the amplitudes spectra of the clean data, observed data, recovered data using the DRR approach and the proposed approach, respectively.
-The amplitude spectrum using our approach is very similar to the clean data than that of DRR approach.
-From this comparison, we find that the proposed approach can greatly restore the amplitude of the useful signal in the whole frequency band even though the data to be recovered has very low SNR that can seriously affect its amplitude.
-From the amplitude spectra comparison, it is evident that the proposed algorithm can conserve the significant feature of the recovered data than the DRR approach.}}
-%\wen{
-%\AtEndDocument{
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/Amplite_spectrum_comparison_curved_data_clean}
-%			\label{a}}
-%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/Amplite_spectrum_comparison_curved_data_observed}
-%			\label{Fiigure:c}}\\
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/Amplite_spectrum_comparison_curved_data_DRR}
-%			\label{Fiigure:d}}
-%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/Amplite_spectrum_comparison_curved_data_Proposed}
-%			\label{Fiigure:e}}		
-%		\caption{Amplitude spectra comparison after 10 iterations between both algorithms.
-(a and b) correspond to the clean data and the observed data, respectively.
-(c and d) denote the DRR approach, and the proposed framework, respectively.}
-%		\label{18}
-%	\end{figure}}
-%}
 
@@
 We fix the noise variance at $0.2$ while varying the missing traces from $10\%$ to $90\%$, and we measure the S/N values.
-Figure \dlo{\ref{21}}\wen{\ref{snr_missing_traces_curvedD}} shows the S/N values as functions of missing traces.
+Figure \dlo{\ref{Figure:21}}\wen{\ref{fig:snr_missing_traces_curvedD}} shows the S/N values as functions of missing traces.
 From this figure \dlo{above mentioned}\wen{mentioned above}, it is undeniable that as the percentage of missing trace becomes large, the proposed method (the red line) consistently provides higher values of S/N than the DRR approach (the blue line).
@@
 }
-\wen{
-	\AtEndDocument{
-		\begin{figure}[htb!]
-			\centering
-			\includegraphics[width=0.5\textwidth]{Fig/snr_missing_traces_curvedD}	
-			\caption{Comparison of S/N diagrams for the percentage of missing data after \dlo{ten}\wen{10} iterations between \dlo{both}\wen{two} algorithms on data containing curved events.
+
+\inputdir{./}
+\plot{snr_missing_traces_curvedD}{width=0.5\columnwidth}{Comparison of S/N diagrams for the percentage of missing data after \dlo{ten}\wen{10} iterations between \dlo{both}\wen{two} algorithms on data containing curved events.
 The blue and red lines correspond to the DRR method and the proposed approach, respectively.
 The red line still presents higher S/N values.
-We used a noise variance of $0.2$ and then decimated the traces from $10$ to $90\% $ for this comparison.}
-			\label{snr_missing_traces_curvedD}
-	\end{figure}}
-}%fig.16
+We used a noise variance of $0.2$ and then decimated the traces from $10$ to $90\%$ for this comparison.}
 
@@
 Here, we have considered a visual examination of the results obtained via both methods to demonstrate the performances of our algorithm.
-%\dlo{Figures \ref{23}, \ref{24} and \ref{25} display the comparison in one common midpoint gather, one common offset gather and 500 traces, respectively.
-Figures \ref{23}(a), \ref{24}(a) and \ref{25}(a) show the observed noisy and incomplete data.
+%\dlo{Figures \ref{Figure:23}, \ref{Figure:24} and \ref{Figure:25} display the comparison in one common midpoint gather, one common offset gather and 500 traces, respectively.
+Figures \ref{Figure:23}(a), \ref{Figure:24}(a) and \ref{Figure:25}(a) show the observed noisy and incomplete data.
 In this example, about 75\% of traces are missing.
 To preserve the significant features of the useful signal, we select rank {$K= 6$} and damping factor {$d = 2$} for the DRR approach.
-Figures \ref{23}(b), \ref{24}(b) and \ref{25}(b) present the results of this approach.
+Figures \ref{Figure:23}(b), \ref{Figure:24}(b) and \ref{Figure:25}(b) present the results of this approach.
 The DRR method obtains successful results.
@@
 We run both programs using 10 weighted {POCS-like} iterations.
-As can be seen in Figures \ref{23}(c), \ref{24}(c) and \ref{25}(c), which display the results obtained by the proposed approach, all useful signal\wen{s} \dlo{is}\wen{are} perfectly recovered.
+As can be seen in Figures \ref{Figure:23}(c), \ref{Figure:24}(c) and \ref{Figure:25}(c), which display the results obtained by the proposed approach, all useful signal\wen{s} \dlo{is}\wen{are} perfectly recovered.
 All significant events are highlighted and can be perceived without much effort on each sub-figures mentioned.
-To better compare them in detail, we zoom a portion from each sub-figure in Figure \ref{25} and display the comparison in Figure \ref{26}.
-The red frame boxes are shown in Figure \ref{25} to highlight the zoomed data.
-After a comparison of the Figures \ref{26}(a-c), it is obvious that our method provides better results than those of the DRR approach.
+To better compare them in detail, we zoom a portion from each sub-figure in Figure \ref{Figure:25} and display the comparison in Figure \ref{Figure:26}.
+The red frame boxes are shown in Figure \ref{Figure:25} to highlight the zoomed data.
+After a comparison of the Figures \ref{Figure:26}(a-c), it is obvious that our method provides better results than those of the DRR approach.
 The zoomed data comparison further demonstrates the accuracy of our algorithm.}
-\wen{Figures \dlo{\ref{22} and \ref{23}}\wen{\ref{cmp_field_obseerved,cmp_field_DRR,cmp_field_proposed} and \ref{offset_field_obseerved,offset_field_DRR,offset_field_Proposed}} display the comparison in one common-midpoint and one common-offset gather, respectively.
-Figures \dlo{\ref{22}}\wen{\ref{cmp_field_obseerved}}\dlo{(a)} and \dlo{\ref{23}}\wen{\ref{offset_field_obseerved}}\dlo{(a)} show the observed noisy and incomplete data.
+\wen{Figures \dlo{\ref{fig:22} and \ref{fig:23}}\wen{\ref{fig:cmp_field_obseerved,cmp_field_DRR,cmp_field_proposed} and \ref{fig:offset_field_obseerved,offset_field_DRR,offset_field_Proposed}} display the comparison in one common-midpoint and one common-offset gather, respectively.
+Figures \dlo{\ref{fig:22}}\wen{\ref{fig:cmp_field_obseerved}}\dlo{(a)} and \dlo{\ref{fig:23}}\wen{\ref{fig:offset_field_obseerved}}\dlo{(a)} show the observed noisy and incomplete data.
 In this example, approximately $75\%$ of traces are missing.
 To preserve the significant features of the useful signal, we select rank {$K= 6$} and damping factor {$d = 2$} for the DRR approach.
-Figures \dlo{\ref{22}}\wen{\ref{cmp_field_DRR}}\dlo{(b)} and \dlo{\ref{23}}\wen{\ref{offset_field_DRR}}\dlo{(b)} show the results\dlo{of this approach}.
+Figures \dlo{\ref{fig:22}}\wen{\ref{fig:cmp_field_DRR}}\dlo{(b)} and \dlo{\ref{fig:23}}\wen{\ref{fig:offset_field_DRR}}\dlo{(b)} show the results\dlo{of this approach}.
 The DRR method obtains successful results.
@@
 In addition to the same parameters used for the DRR method, we use a cooling factor $\beta= 3$, a rational transfer function coefficient ${e= 0.9}$, and a window size ${T= 1}$ for the proposed method.} We run both \dlo{programs}\wen{algorithms} using \dlo{ten}\wen{10} weighted {POCS-like} iterations.
-As can be seen in Figures \dlo{\ref{22}}\wen{\ref{cmp_field_proposed}}\dlo{(c)} and \dlo{\ref{23}}\wen{\ref{offset_field_Proposed}}\dlo{(c)}, which display the results obtained by the proposed approach, all useful signal\wen{s} \dlo{is}\wen{are} perfectly recovered.
+As can be seen in Figures \dlo{\ref{fig:22}}\wen{\ref{fig:cmp_field_proposed}}\dlo{(c)} and \dlo{\ref{fig:23}}\wen{\ref{fig:offset_field_Proposed}}\dlo{(c)}, which display the results obtained by the proposed approach, all useful signal\wen{s} \dlo{is}\wen{are} perfectly recovered.
 \dlo{All}\wen{The} significant events are highlighted and can be perceived without much effort on each subfigure\dlo{mentioned}.
-\wen{For further comparison, we display in Figures \dlo{\ref{24}(a)-\ref{24}(c)}\wen{\ref{Zoomed_offset_field_obseerved}\dlo{(a)}-\ref{Zoomed_offset_field_Proposed}\dlo{(c)}}, the magnified section of each subfigure \dlo{\ref{23}(a)-\ref{23}(c)}\wen{\ref{offset_field_obseerved}\dlo{(a)}-\ref{offset_field_Proposed}\dlo{(c)}}, which are highlighted by the green frame boxes, respectively.
+\wen{For further comparison, we display in Figures \dlo{\ref{fig:24}(a)-\ref{fig:24}(c)}\wen{\ref{fig:Zoomed_offset_field_obseerved}\dlo{(a)}-\ref{fig:Zoomed_offset_field_Proposed}\dlo{(c)}}, the magnified section of each subfigure \dlo{\ref{fig:23}(a)-\ref{fig:23}(c)}\wen{\ref{fig:offset_field_obseerved}\dlo{(a)}-\ref{fig:offset_field_Proposed}\dlo{(c)}}, which are highlighted by the green frame boxes, respectively.
 The magnified data reveals \dlo{the presence of}\wen{some} curved events in one common offset gather.
@@
 The magnified data comparison further demonstrates the accuracy of our algorithm.}
-%\old{
-%\AtEndDocument{
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\te%xtwidth]{Figures/cmpObservedfielddata}
-%			\label{ a}}
-%		\subfloat[]{\includegraphics[width=0.3\te%xtwidth]{Figures/cmpDRRfielddata}
-%			\label{ b}}
-%		\subfloat[]{\includegraphics[width=0.3\te%xtwidth]{Figures/cmpProposedfielddata}
-%			\label{Fiigure: c}}
-
-%		\caption{Common midpoint gather comparison.
-(a) Observed noisy and incomplete data.
-(b-c) denote the simultaneously denoised and reconstructed data using the DRR method %and the proposed approach, respectively.}
-%		\label{23}
-%	\end{figure}
-%	
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.3\te%xtwidth]{Figures/offsetObservedfielddata}
-%			\label{ a}}
-%		\subfloat[]{\includegraphics[width=0.3\te%xtwidth]{Figures/offsetDRRfielddata}
-%			\label{ b}}
-%		\subfloat[]{\includegraphics[width=0.3\te%xtwidth]{Figures/offsetProposedfielddata}
-%			\label{Fiigure: c}}
-
-%		\caption{Common offset gather comparison. (a) Observed data. (b-c) display the simultaneously denoised and reconstructed data using the DRR method and the proposed approach, respectively.}
-%		\label{ 24}
-%	\end{figure}
-
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.9\te%xtwidth]{Figures/Tx500tracesObservedfield%data}
-%			\label{ a}}\\
-%		\subfloat[]{\includegraphics[width=0.9\te%xtwidth]{Figures/Tx500tracesDRRfielddata}
-%			\label{ b}}\\
-%		\subfloat[]{\includegraphics[width=0.9\te%xtwidth]{Figures/Tx500tracesProposedfielddata}
-%			\label{Fiigure: c}}
-%		
-%		\caption{Comparison of 500 traces extracted from the 5-D field data matrix.
-(a) shows the observed data.
-(b-c) denote the simultaneously denoised and reconstructed data using the DRR method and the proposed approach, respectively.}
-%		\label{ 25}
-%	\end{figure}
-
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.5\te%xtwidth]{Figures/ZoomedTx500tracesObserve%dfielddata}
-%			\label{ a}}\\
-%		\subfloat[]{\includegraphics[width=0.5\te%xtwidth]{Figures/ZoomedTx500tracesDRRfielddata}
-%			\label{ b}}
-%		\subfloat[]{\includegraphics[width=0.5\te%xtwidth]{Figures/ZoomedTx500tracesPropose%dfielddata}
-%			\label{Fiigure: c}}
-
-%		\caption{Comparison of the zoomed sections from Figure \ref{ 25}.
-(a) shows the observed data.
-(b-c) denote the simultaneously denoised and reconstructed data using the DRR method and the proposed approach, respectively.}
-%		\label{ 26}
-%	\end{figure}
-%}
-%}
+
 \dlo{On the other hand, we compare both methods using the corresponding f-x spectrum and normalized PSD of the 500 traces of aforementioned data.
-Figures \ref{27} and \ref{28} display the f-x spectrum and normalized PSD, respectively.
-In Figure \ref{27}, (a) denotes the f-x spectrum of the observed noisy and incomplete data.
+Figures \ref{Figure:27} and \ref{Figure:28} display the f-x spectrum and normalized PSD, respectively.
+In Figure \ref{Figure:27}, (a) denotes the f-x spectrum of the observed noisy and incomplete data.
 (b) is from the DRR approach and (c) corresponds to the f-x spectrum of the proposed approach.
-The yellow, blue and red lines shown in Figure \ref{28} are the normalized PSD of the decimated data, the restored data from the DRR algorithm and our approach, respectively.}
-%\old{
-%\AtEndDocument{
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.7\te%xtwidth]{Figures/fx500tracesobservedfielddata}
-%			\label{ a}}\\
-%		\subfloat[]{\includegraphics[width=0.7\te%xtwidth]{Figures/fx500tracesdrrfielddata}
-%			\label{ b}}\\
-%		\subfloat[]{\includegraphics[width=0.7\te%xtwidth]{Figures/fx500tracesproposedfielddata}
-%			\label{Fiigure: c}}
-
-%		\caption{Frequency-space (f-x) spectra comparison of the corresponding 500 traces of each 5-D seismic field data.
-(a) shows the f-x spectrum of the decimated data, (c and d) correspond to the f-x spectra obtained after using the DRR method and the proposed framework, %respectively.}
-%		\label{ 27}
-%	\end{figure}
-
-%	\begin{figure}
-%		\centering
-%		\includegraphics[width=0.8\textwidth]{Figures/NormalizedPSDfielddata}
-%		\caption{Comparison of the normalized power spectral density (PSD) of the corresponding 500 traces of each 5-D seismic field data.
-The yellow line shows the PSD of the observed data.
-The blue and red lines denote the PSD of the simultaneously denoised and reconstructed data using the DRR approach and the proposed approach, respectively.}
-%		\label{ 28}
-%	\end{figure}
-%}
-%}
-%\dlo{Simultaneous analysis of the f-x spectrum and normalized PSD better prove that random noise contained in the decimated data cannot be completely attenuated by only using the damping operator.
-From the comparison, we find that our method can yield perfect results than the DRR approach.
-It is visible that the red line is smoother than the blue line (see Figure \ref{28}) due to the less noise in the restored data.
-Thus, the simultaneous denoising and reconstruction errors of the proposed approach are very smaller than that of the DRR method.
-The f-x spectrum and PSD further verify the better recovering quality of our algorithm.
-From Figures \ref{27}, \ref{28}, we deduce that the proposed approach can provide a higher resolution than the DRR method.}
-
-\AtEndDocument{
-	\begin{figure}[htb!]
-		\centering
-		\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/cmp_field_obseerved}
-			\label{cmp_field_obseerved}}
-		\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/cmp_field_DRR}
-			\label{cmp_field_DRR}}
-		\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/cmp_field_proposed}
-			\label{cmp_field_proposed}}
-		\caption{Common midpoint gather \wen{2D figures} comparison.
+The yellow, blue and red lines shown in Figure \ref{Figure:28} are the normalized PSD of the decimated data, the restored data from the DRR algorithm and our approach, respectively.}
+
+\inputdir{./}
+\multiplot{3}{cmp_field_obseerved,cmp_field_DRR,cmp_field_proposed}{width=0.30\textwidth}{Common midpoint gather \wen{2D figures} comparison.
 (a) Observed noisy and incomplete data with about $75\%$ of missing traces.
 (b and c) denote the simultaneously denoised and reconstructed data using the DRR approach and the proposed approach, respectively.}
-		\label{cmp_field_obseerved,cmp_field_DRR,cmp_field_proposed}
-\end{figure}}%fig.17
-\wen{
-	\AtEndDocument{
-		\begin{figure}[htb!]
-			\centering
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/offset_field_obseerved}
-				\label{offset_field_obseerved}}
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/offset_field_DRR}
-				\label{offset_field_DRR}}
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/offset_field_Proposed}
-				\label{offset_field_Proposed}}			
-			\caption{Common-offset gather \wen{2D figures} comparison.
+
+\inputdir{./}
+\multiplot{3}{offset_field_obseerved,offset_field_DRR,offset_field_Proposed}{width=0.29\textwidth}{Common-offset gather \wen{2D figures} comparison.
 (a) Observed noisy and incomplete data with approximately $75\%$ of missing traces.
 (b and c) The simultaneously denoised and reconstructed data using the DRR approach and the proposed approach, respectively.}
-			\label{offset_field_obseerved,offset_field_DRR,offset_field_Proposed}
-	\end{figure}}
-}%fig.18
-\wen{
-	\AtEndDocument{
-		\begin{figure}[htb!]
-			\centering
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/Zoomed_offset_field_obseerved}
-				\label{Zoomed_offset_field_obseerved}}
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/Zoomed_offset_field_DRR}
-				\label{Zoomed_offset_field_DRR}}
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/Zoomed_offset_field_Proposed}
-				\label{Zoomed_offset_field_Proposed}}
-			\caption{Magnified section from Figure \ref{offset_field_obseerved,offset_field_DRR,offset_field_Proposed} (the green frame boxes) comparison.
+
+\inputdir{./}
+\multiplot{4}{Zoomed_offset_field_obseerved,Zoomed_offset_field_DRR,Zoomed_offset_field_Proposed}{width=0.29\textwidth}{Magnified section from Figure \ref{fig:offset_field_obseerved,offset_field_DRR,offset_field_Proposed} (the green frame boxes) comparison.
 (a) Observed noisy and incomplete data with approximately $75\% $ of missing traces.
 (b and c) The simultaneously denoised and reconstructed data using the DRR method and the proposed approach, respectively.}
-			\label{Zoomed_offset_field_obseerved,Zoomed_offset_field_DRR,Zoomed_offset_field_Proposed}
-	\end{figure}}
-}%fig.19		 
+
 \wen{
-	Moreover, we compare both methods using the corresponding f-x spectrum of each data displayed in Figure \dlo{\ref{23}}\wen{\ref{offset_field_obseerved,offset_field_DRR,offset_field_Proposed}}.
-\dlo{In Figure \dlo{\ref{25}, \ref{25}(a)}\wen{\ref{20}},}\wen{Figure \ref{fx_offset_obs_field}-\ref{fx_offset_Proposed_field}}\dlo{\ref{20}} denotes the f-x \dlo{spectrum}\wen{spectra} of the observed noisy and incomplete data\dlo{.
-\dlo{\ref{25}}\dlo{\ref{20}}(b) is from}\wen{,} the DRR approach, and \dlo{\dlo{\ref{25}}\dlo{\ref{20}}(c) corresponds to the f-x spectrum of}the proposed approach, \wen{respectively}.
+	Moreover, we compare both methods using the corresponding f-x spectrum of each data displayed in Figure \dlo{\ref{fig:23}}\wen{\ref{fig:offset_field_obseerved,offset_field_DRR,offset_field_Proposed}}.
+\dlo{In Figure \dlo{\ref{fig:25}, \ref{fig:25}(a)}\wen{\ref{fig:20}},}\wen{Figure \ref{fig:fx_offset_obs_field}-\ref{fig:fx_offset_Proposed_field}}\dlo{\ref{fig:20}} denotes the f-x \dlo{spectrum}\wen{spectra} of the observed noisy and incomplete data\dlo{.
+\dlo{\ref{fig:25}}\dlo{\ref{fig:20}}(b) is from}\wen{,} the DRR approach, and \dlo{\dlo{\ref{fig:25}}\dlo{\ref{fig:20}}(c) corresponds to the f-x spectrum of}the proposed approach, \wen{respectively}.
 Analysis of the f-x spectra \dlo{better proves}\wen{further shows} that random noise included in the decimated data cannot be completely attenuated by only using the damping operator.
@@
 The f-x spectra comparison further verifies the better reconstruction quality of our algorithm.
-From Figure \dlo{\ref{25}}\wen{\ref{fx_offset_obs_field,fx_offset_DRR_field,fx_offset_Proposed_field}}, we deduce that the proposed approach can provide a higher resolution than the DRR method.}
-\wen{	
-	\AtEndDocument{
-		\begin{figure}[htb!]
-			\centering
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/fx_offset_obs_field}
-				\label{fx_offset_obs_field}}
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/fx_offset_DRR_field}
-				\label{fx_offset_DRR_field}}
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/fx_offset_Proposed_field}
-				\label{fx_offset_Proposed_field}}		
-			\caption{Frequency-space (f-x) spectra comparison of each data displayed in Figure \dlo{\ref{23}}\wen{\ref{offset_field_obseerved,offset_field_DRR,offset_field_Proposed}}.
+From Figure \dlo{\ref{fig:25}}\wen{\ref{fig:fx_offset_obs_field,fx_offset_DRR_field,fx_offset_Proposed_field}}, we deduce that the proposed approach can provide a higher resolution than the DRR method.}
+
+\inputdir{./}
+\multiplot{3}{fx_offset_obs_field,fx_offset_DRR_field,fx_offset_Proposed_field}{width=0.30\textwidth}{Frequency-space (f-x) spectra comparison of each data displayed in Figure \dlo{\ref{fig:23}}\wen{\ref{fig:offset_field_obseerved,offset_field_DRR,offset_field_Proposed}}.
 (a) The f-x spectra of the decimated data.
 (b and c) The f-x spectra obtained after using the DRR and the proposed approaches, respectively.}
-			\label{fx_offset_obs_field,fx_offset_DRR_field,fx_offset_Proposed_field}
-		\end{figure}
-}}%fig.20
+
 \section{discussion}
@@
 The parameters $K$, $d$, $\beta$, $e$ and $T$ were set at $6$, $2$, $3.3$, $0.972$ and $1$, respectively to simultaneous denoise and reconstruct observed data corrupted by $0.3$ as noise variance and $70\%$ of missing traces.
-Figure \wen{\ref{snr_with_K}}\dlo{(a)} shows the influence of $K$ for different values.\dlo{We vary the values of $K$ from $1$ to $10$ while fixing the other parameters to see its influence.} As seen from this subfigure, a $K$ value of $6$ produces a better result in terms of S/N.
+Figure \wen{\ref{fig:snr_with_K}}\dlo{(a)} shows the influence of $K$ for different values.\dlo{We vary the values of $K$ from $1$ to $10$ while fixing the other parameters to see its influence.} As seen from this subfigure, a $K$ value of $6$ produces a better result in terms of S/N.
 Thus, we adopted this value of rank to restore the useful signal.
-Besides, as \dlo{can be seen}observed in Figure \wen{\ref{snr_with_d}}\dlo{(b)}, it is \dlo{explicit}\wen{clear} that \dlo{the damping factor}$d=2$ can positively affect the result.
-\dlo{we range the damping factor from $1$ to $3$, and plot the results in Figure \ref{26}.
-From this figure, it is explicit that $d=2$ can positively affect the result.}From Figure \ref{snr_with_beta}\dlo{(c)}, \dlo{it is clear that}$\beta$ of $3$ can produce the best S/N value.
+Besides, as \dlo{can be seen}observed in Figure \wen{\ref{fig:snr_with_d}}\dlo{(b)}, it is \dlo{explicit}\wen{clear} that \dlo{the damping factor}$d=2$ can positively affect the result.
+\dlo{we range the damping factor from $1$ to $3$, and plot the results in Figure \ref{fig:26}.
+From this figure, it is explicit that $d=2$ can positively affect the result.}From Figure \ref{fig:snr_with_beta}\dlo{(c)}, \dlo{it is clear that}$\beta$ of $3$ can produce the best S/N value.
 Therefore, by adjusting this parameter properly, we adopted \dlo{$\beta$ of $3.3$}\wen{$\beta = 3.3$} to recover the useful signal in this example.
 \dlo{Then, we change the cooling factor from $1$ to $10$ to see its influence on this result.
-Figure \ref{26}\dlo{(c)}\wen{c} shows the results.
+Figure \ref{fig:26}\dlo{(c)}\wen{c} shows the results.
 From this figure, $\beta$ of $3$ can produce the best S/N value.
@@
 In the same way, we analyze the effect of $e$ by ranging its values from 0.95, 0.96,..., to $1$.
-As shown in Figure \ref{26}}As shown in Figure \wen{\ref{snr_with_e}}\dlo{(d)}, the best quality of the signal can be provided by fixing $e$ around $0.97$.
-So, by regulating the parameter accurately, we used $e=0.972$ to recover the useful signal.\dlo{Finally, as displayed in the sub-figure \ref{26} we range the parameter $T$ from $ 1 $ to $ 5 $ to analyze its behavior.
-The analysis of this diagram demonstrates}\dlo{.} Finally, as displayed in the \dlo{sub-figure}\wen{Figure} \wen{\ref{snr_with_T}}\dlo{(e)}, all values of $T$ set above $1$ produce lower S/N values.
+As shown in Figure \ref{fig:26}}As shown in Figure \wen{\ref{fig:snr_with_e}}\dlo{(d)}, the best quality of the signal can be provided by fixing $e$ to approximately $0.97$.
+So, by regulating the parameter accurately, we used $e=0.972$ to recover the useful signal.\dlo{Finally, as displayed in the sub-figure \ref{fig:26} we range the parameter $T$ from $ 1 $ to $ 5 $ to analyze its behavior.
+The analysis of this diagram demonstrates}\dlo{.} Finally, as displayed in the \dlo{sub-figure}\wen{Figure} \wen{\ref{fig:snr_with_T}}\dlo{(e)}, all values of $T$ set above $1$ produce lower S/N values.
 Thus, we selected $T$ of $1$ to restore the useful signal.
 From this analysis, we can \dlo{appreciate}\wen{understand} the contribution of each parameter to the quality of our results.} \wen{The parameter $e$ is \dlo{a} helpful \dlo{tool} to enhance the energy of the useful signal when the best trade-off with the parameter $T$ is reached.}
-\wen{\AtEndDocument{
-		\begin{figure}[htb!]
-			\centering
-			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/snr_with_K}
-				\label{snr_with_K}}
-			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/snr_with_d}
-				\label{snr_with_d}}
-			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/snr_with_beta}
-				\label{snr_with_beta}}\\
-			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/snr_with_e}
-				\label{snr_with_e}}
-			\subfloat[]{\includegraphics[width=0.35\textwidth]{Fig/snr_with_T}
-				\label{snr_with_T}}
-			\caption{Influence of the five key parameters under a noise variance of $0.3$ and $70\%$ as missing traces after $10$ iterations.
+
+\inputdir{./}
+\multiplot{5}{snr_with_K,snr_with_d,snr_with_beta,snr_with_e,snr_with_T}{width=0.3\textwidth}{Influence of the five key parameters under a noise variance of $0.3$ and $70\%$ as missing traces after $10$ iterations.
 (a) The influence of the rank constraint.
@@
 (d) The influence of the rational transfer function coefficient.
-(e) The effect of the window size.
-				\label{snr_with_K,snr_with_d,snr_with_beta,snr_with_e,snr_with_T}}
-\end{figure}}}%fig.21
+(e) The effect of the window size.}
 
@@
 The S/N of the observed data is $-2.40$ dB.
-In Figure \dlo{\ref{27}}\wen{\ref{influence_operator_block_HMatrice}}, we plot the S/N\dlo{s} values as a function of iteration numbers ranging from $5$ to $30$.}
+In Figure \dlo{\ref{fig:27}}\wen{\ref{fig:influence_operator_block_HMatrice}}, we plot the S/N\dlo{s} values as a function of iteration numbers ranging from $5$ to $30$.}
 \wen{The black, gray, gray dashed, and blue lines correspond to the RR, STMA, MA, and ST operators, respectively.
@@
 The influence of ST on the level-4 block Hankel is almost insignificant because it provides very low S/N.
-In contrast, the MA operator can recover the useful signal from the level-4 block Hankel matrix because the S/N\dlo{s} values (Figure \dlo{\ref{27}}\wen{\ref{influence_operator_block_HMatrice}}) are quite acceptable.
+In contrast, the MA operator can recover the useful signal from the level-4 block Hankel matrix because the S/N\dlo{s} values (Figure \dlo{\ref{fig:27}}\wen{\ref{fig:influence_operator_block_HMatrice}}) are quite acceptable.
 Note that, when we set $T$ at $2$, and we use the smaller values of $e$ ($e= 0.1,...,0.7$), we cannot obtain acceptable results.
@@
 The results in \dlo{one}\wen{the} common-offset gather are \dlo{generally quite}acceptable.}
-\wen{As shown in Figure \dlo{\ref{27}}\wen{\ref{influence_operator_block_HMatrice}}, the S/N \dlo{diagram}\wen{values} using the STMA operator \dlo{outperforms}\wen{are higher than} both the ST and MA \wen{S/N} values.
+\wen{As shown in Figure \dlo{\ref{fig:27}}\wen{\ref{fig:influence_operator_block_HMatrice}}, the S/N \dlo{diagram}\wen{values} using the STMA operator \dlo{outperforms}\wen{are higher than} both the ST and MA \wen{S/N} values.
 We deduce that by combining the ST and the MA operators (STMA), we can \dlo{profit to}\wen{benefit from} their individual performance and thus further influence the level-4 block Hankel matrix.
-In Figure \dlo{\ref{28}}\wen{\ref{synth-hxhy-s-stma1,synth-hxhy-s-stma2,synth-xy-s-stma1,synth-xy-s-stma2}}, we plot the STMA results first, for $\mathbf{\beta}=80$, $e=0.999$, $T=2$, and then, $\mathbf{\beta}=15$, $e=0.999$, $T=17$.
-Figures \dlo{\ref{28}(a) and \ref{28}(c) and Figures \ref{28}\dlo{(b)}\new{b} and \ref{28}\dlo{(d)}\wen{d}} \wen{\ref{synth-hxhy-s-stma1}\dlo{(a)} and \ref{synth-xy-s-stma1}\old{(c)} and Figures \ref{synth-hxhy-s-stma2}\dlo{(b)} and \ref{synth-xy-s-stma2}\old{(d)}} show the results using both cases, respectively.
+In Figure \dlo{\ref{Figure:28}}\wen{\ref{fig:synth-hxhy-s-stma1,synth-hxhy-s-stma2,synth-xy-s-stma1,synth-xy-s-stma2}}, we plot the STMA results first, for $\mathbf{\beta}=80$, $e=0.999$, $T=2$, and then, $\mathbf{\beta}=15$, $e=0.999$, $T=17$.
+Figures \dlo{\ref{fig:28}(a) and \ref{fig:28}(c) and Figures \ref{fig:28}\dlo{(b)}\new{b} and \ref{fig:28}\dlo{(d)}\wen{d}} \wen{\ref{fig:synth-hxhy-s-stma1}\dlo{(a)} and \ref{fig:synth-xy-s-stma1}\old{(c)} and Figures \ref{fig:synth-hxhy-s-stma2}\dlo{(b)} and \ref{fig:synth-xy-s-stma2}\old{(d)}} show the results using both cases, respectively.
 The first case yields \wen{S/N =$4.07$} dB \dlo{as SNR}while the second situation \dlo{performs with $10.46$ dB}\wen{S/N = $8.00$} dB after $15$ iterations.
 From this comparison, we find that when applying the STMA operator directly on the level-4 block Hankel matrix, the larger values of $T$ can provide higher values in terms of S/N.
-However, the smoothing \dlo{degree} damages the useful signal in one common-midpoint gather (Figure \dlo{\ref{28}}\wen{\ref{synth-hxhy-s-stma2}}\dlo{(b)}).
-\dlo{Whereas}\wen{However}, the \dlo{one} common-offset gather result (Figure \dlo{\ref{28}}\wen{\ref{synth-xy-s-stma2}}\dlo{(d)}) is satisfactory.
-From this test, we find that the influence of the ST operator can be seen when it is combined with the MA operator.} \wen{From Figure \dlo{\ref{27}}\ref{influence_operator_block_HMatrice}, the RR operator demonstrates its superiority over the ST, MA, and STMA operators with \wen{a} rank \wen{of} six.
+However, the smoothing \dlo{degree} damages the useful signal in one common-midpoint gather (Figure \dlo{\ref{fig:28}}\wen{\ref{fig:synth-hxhy-s-stma2}}\dlo{(b)}).
+\dlo{Whereas}\wen{However}, the \dlo{one} common-offset gather result (Figure \dlo{\ref{fig:28}}\wen{\ref{fig:synth-xy-s-stma2}}\dlo{(d)}) is satisfactory.
+From this test, we find that the influence of the ST operator can be seen when it is combined with the MA operator.} \wen{From Figure \dlo{\ref{fig:27}}\ref{fig:influence_operator_block_HMatrice}, the RR operator demonstrates its superiority over the ST, MA, and STMA operators with \wen{a} rank \wen{of} six.
 From the different tests, we find that for $T=1$, the STMA operator provides the same result as the ST operator whatever the combination of the parameters when it is directly applied to the level-4 block Hankel matrix to recover the useful signal.
@@
 
-\wen{\AtEndDocument{
-		\begin{figure}[htb!]
-			\centering
-			\includegraphics[width=0.4\textwidth]{Fig/influence_operator_block_HMatrice}
-			\caption{Influence of the operators (ST, MA, STMA, and RR) on the level-4 block Hankel matrix under a noise variance of $0.3$ and $70\%$ as missing traces after \dlo{ten}\wen{$10$} iterations.
+\inputdir{./}
+\plot{influence_operator_block_HMatrice}{width=0.5\columnwidth}{Influence of the operators (ST, MA, STMA, and RR) on the level-4 block Hankel matrix under a noise variance of $0.3$ and $70\%$ as missing traces after \dlo{ten}\wen{$10$} iterations.
 The blue line corresponds to the ST operator.
 The dashed and solid gray lines are from the MA and STMA operators, respectively.
-The black line denotes the RR operator.
-				\label{influence_operator_block_HMatrice}}
-\end{figure}}
-}%fig.22
-\AtEndDocument{
-	\begin{figure}[htb!]
-		\centering
-		\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_stma_block_Hankel_matrix/Fig/synth-hxhy-s-stma1}
-			\label{synth-hxhy-s-stma1}}
-		\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_stma_block_Hankel_matrix/Fig/synth-hxhy-s-stma2}
-			\label{synth-hxhy-s-stma2}}\\
-		\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_stma_block_Hankel_matrix/Fig/synth-xy-s-stma1}
-			\label{synth-xy-s-stma1}}
-		\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_stma_block_Hankel_matrix/Fig/synth-xy-s-stma2}
-			\label{synth-xy-s-stma2}}
-		\caption{Influence of the STMA operator on the level-4 block Hankel matrix.
+The black line denotes the RR operator.}
+
+\inputdir{synth_stma_block_Hankel_matrix}
+\multiplot{4}{synth-hxhy-s-stma1,synth-hxhy-s-stma2,synth-xy-s-stma1,synth-xy-s-stma2}{width=0.35\textwidth}{Influence of the STMA operator on the level-4 block Hankel matrix.
 (a and c) The one common-midpoint and and common-offset gather\dlo{2-D figures}, respectively, for \wen{$\mathbf{\beta}=80$, $e=0.999$, $T=2$}.
 (b and d) The one common-midpoint and common-offset gather, respectively, for \wen{$\mathbf{\beta}=15$, $e=0.999$, \wen{and} $T=17$.}}
-		\label{synth-hxhy-s-stma1,synth-hxhy-s-stma2,synth-xy-s-stma1,synth-xy-s-stma2}
-	\end{figure}
-}%fig.23
+
 \wen{To verify the adaptability of the STMA operator with some iterative denoising and reconstruction methods, we introduce the proposed STMA operator in the damped data-driven optimal singular value shrinkage algorithm \citep{siahsar2017simultaneous} framework for simultaneous denoising and interpolation of 3D seismic.
@@
 The S/N of the noisy data and the observed data is approximately $-8.40$ dB and $-5.98$ dB, respectively.
-Figures \dlo{\ref{29} and \ref{30}}\wen{\ref{syn3d-c-s,syn3d-n-s,syn3d-obs-s,syn3d-opshrinkdamped-s,syn3d-opshrinkdampedstma-s}}\dlo{and \ref{25}} show the 2D slice comparison in the 5th crossline\dlo{ and inline sections, respectively}.
-Figures \dlo{\ref{29}(a)-\ref{29}(c)}\wen{\ref{syn3d-c-s}\dlo{(a)}-\ref{syn3d-obs-s}\dlo{(c)}} correspond to the clean data, noisy data, and observed data, respectively.
-Figures \dlo{\ref{30}(d) and \ref{30}(e)}\wen{\ref{syn3d-opshrinkdamped-s}\dlo{(d)} and \ref{syn3d-opshrinkdampedstma-s}\dlo{(e)}} display the recovered data using the damped data-driven optimal singular value shrinkage (damped optshrink) algorithm\wen{,} and the modified damped data-driven optimal singular value shrinkage algorithm, respectively.
-From the comparison of each sub-figure mentioned, the modified algorithm can obtain better recovery performance.\dlo{(Figures \ref{29}(e) and \ref{30})} The result of the modified algorithm is obtained with  $K=3$, $d=2$, $\mathbf{\beta}=2.10$, $e=0.991$, and $T=1$.
+Figures \dlo{\ref{Figure:29} and \ref{fig:30}}\wen{\ref{fig:syn3d-c-s,syn3d-n-s,syn3d-obs-s,syn3d-opshrinkdamped-s,syn3d-opshrinkdampedstma-s}}\dlo{and \ref{fig:25}} show the 2D slice comparison in the 5th crossline\dlo{ and inline sections, respectively}.
+Figures \dlo{\ref{fig:29}(a)-\ref{fig:29}(c)}\wen{\ref{fig:syn3d-c-s}\dlo{(a)}-\ref{fig:syn3d-obs-s}\dlo{(c)}} correspond to the clean data, noisy data, and observed data, respectively.
+Figures \dlo{\ref{fig:30}(d) and \ref{fig:30}(e)}\wen{\ref{fig:syn3d-opshrinkdamped-s}\dlo{(d)} and \ref{fig:syn3d-opshrinkdampedstma-s}\dlo{(e)}} display the recovered data using the damped data-driven optimal singular value shrinkage (damped optshrink) algorithm\wen{,} and the modified damped data-driven optimal singular value shrinkage algorithm, respectively.
+From the comparison of each sub-figure mentioned, the modified algorithm can obtain better recovery performance.\dlo{(Figures \ref{fig:29}(e) and \ref{fig:30})} The result of the modified algorithm is obtained with  $K=3$, $d=2$, $\mathbf{\beta}=2.10$, $e=0.991$, and $T=1$.
 The S/Ns are $7.77$ dB and $8.22$ dB for the damped data-driven optimal singular value shrinkage algorithm\wen{,} and the modified algorithm, respectively.
@@
 First, by considering the S/N values as a function of iteration numbers.
-For this experiment, we range the iteration numbers from $5$ to $30$, and we plot the results in Figure \dlo{\ref{31}}\wen{\ref{snr_IterationN_DampedOpshrinkSTMA}}\dlo{(a)}.
+For this experiment, we range the iteration numbers from $5$ to $30$, and we plot the results in Figure \dlo{\ref{fig:31}}\wen{\ref{fig:snr_IterationN_DampedOpshrinkSTMA}}\dlo{(a)}.
 Then, we fix the noise level at $0.2$ and we vary the missing traces from $10\%$ to $90\%$.
-We \dlo{displays}\wen{display} the performance of each approach for the percentage of missing data in Figure \dlo{\ref{31}}\wen{\ref{snr_missing_trace_DampedOpshrink_stma}}\dlo{(b)}.
+We \dlo{displays}\wen{display} the performance of each approach for the percentage of missing data in Figure \dlo{\ref{Figure:31}}\wen{\ref{fig:snr_missing_trace_DampedOpshrink_stma}}\dlo{(b)}.
 From both subfigures, we find that the STMA operator can effectively improve the damped data-driven optimal singular value shrinkage algorithm.}
-\wen{
-	\AtEndDocument{
-		\begin{figure}[htb!]
-			\centering
-			\subfloat[]{\includegraphics[width=0.3\textwidth]{optshrink_damped_stma/Fig/syn3d-c-s}
-				\label{syn3d-c-s}}
-			\subfloat[]{\includegraphics[width=0.3\textwidth]{optshrink_damped_stma/Fig/syn3d-n-s}
-				\label{syn3d-n-s}}
-			\subfloat[]{\includegraphics[width=0.3\textwidth]{optshrink_damped_stma/Fig/syn3d-obs-s}
-				\label{syn3d-obs-s}}\\
-			\centering
-			\subfloat[]{\includegraphics[width=0.3\textwidth]{optshrink_damped_stma/Fig/syn3d-opshrinkdamped-s}
-				\label{syn3d-opshrinkdamped-s}}
-			\subfloat[]{\includegraphics[width=0.3\textwidth]{optshrink_damped_stma/Fig/syn3d-opshrinkdampedstma-s}
-				\label{syn3d-opshrinkdampedstma-s}}
-			\caption{\dlo{Single slice comparison (5th crossline slice).
+
+\inputdir{optshrink_damped_stma}
+\multiplot{5}{syn3d-c-s,syn3d-n-s,syn3d-obs-s,syn3d-opshrinkdamped-s,syn3d-opshrinkdampedstma-s}{width=0.3\textwidth}{\dlo{Single slice comparison (5th crossline slice).
 (a-c) Clean, noisy, and observed data, respectively.
@@
 (d and e) The recovered data obtained using the damped data-driven optimal singular value shrinkage algorithm and the modified algorithm, respectively.}}
-			\label{syn3d-c-s,syn3d-n-s,syn3d-obs-s,syn3d-opshrinkdamped-s,syn3d-opshrinkdampedstma-s}
-		\end{figure}
-}}%fig.24
-%\wen{
-%	\AtEndDocument{
-%		\begin{figure}[htb!]
-%			\centering
-%			\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/Inline_Clean}
-%				\label{a}}
-%			\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/Inline_Noise}
-%				\label{b}}
-%			\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/Inline_Observed}
-%				\label{c}}\\
-%			\centering
-%			\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/Inline_Dampedopshrink}
-%				\label{d}}
-%			\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/Inline_DampedOpshrinkSTMA}
-%				\label{e}}
-%			\caption{\old{Single slice comparison (5th inline slice).
-(a-c) Clean, noisy, and observed data, respectively.(d and e) Recovered.} \new{Single slice 2-D figures comparison (5th inline slice).
-(a) Clean data.
-(b) Noisy data.
-(c) Observed data.
-(d and e) show the recovered} data obtained using the damped data-driven optimal singular value shrinkage algorithm and the modified algorithm, respectively.}
-%			\label{25}
-%\end{figure}}}
-\wen{
-	\AtEndDocument{
-		\begin{figure}[htb!]
-			\centering
-			\subfloat[]{\includegraphics[width=0.3\textwidth]{Fig/snr_IterationN_DampedOpshrinkSTMA}
-				\label{snr_IterationN_DampedOpshrinkSTMA}}
-			\subfloat[]{\includegraphics[width=0.3\textwidth]{Fig/snr_missing_trace_DampedOpshrink_stma}
-				\label{snr_missing_trace_DampedOpshrink_stma}}		
-			\caption{S/N diagrams comparison between two approaches.\dlo{a noise level $0.2$ and $50\%$ as missing traces} (a) S/N\dlo{s} values for iteration numbers.
+
+\inputdir{./}
+\multiplot{2}{snr_IterationN_DampedOpshrinkSTMA,snr_missing_trace_DampedOpshrink_stma}{width=0.35\textwidth}{S/N diagrams comparison between two approaches.\dlo{a noise level $0.2$ and $50\%$ as missing traces} (a) S/N\dlo{s} values for iteration numbers.
 (b) S/N\dlo{s} values as a function of missing traces after $15$ iterations.
 In both cases, the gray and black lines are from the damped data-driven optimal singular value shrinkage algorithm, and the modified algorithm, respectively.}
-			\label{snr_IterationN_DampedOpshrinkSTMA,snr_missing_trace_DampedOpshrink_stma}
-\end{figure}}}
-%fig.25
 
@@
 When we remove the damping factor from the proposed algorithm (RDRR), it corresponds to the RR + ST + MA approach.
-From Figures \dlo{\ref{29}(b) and \ref{32}(b)}\wen{\ref{synth-rrstma-s}\dlo{(b)} and \ref{synth-rrstma-xy-e-s}\old{(b)}}, we find that the introduced STMA function into the RR method framework after the TSVD process can \dlo{greatly}\wen{successfully} improve the result of the simultaneous denoising and reconstruction of 5D data.
-Compared to the damping operator (Figure \dlo{\ref{31}(a) and \ref{32}(a)}\wen{\ref{synth-rrdamping-s}\old{(a)} and \ref{synth-rrdamping-xy-e-s}\dlo{(a)}}), we find that RR + ST + MA operators can better reconstruct the missing traces than RR + damping operators.
+From Figures \dlo{\ref{fig:29}(b) and \ref{fig:32}(b)}\wen{\ref{fig:synth-rrstma-s}\dlo{(b)} and \ref{fig:synth-rrstma-xy-e-s}\old{(b)}}, we find that the introduced STMA function into the RR method framework after the TSVD process can \dlo{greatly}\wen{successfully} improve the result of the simultaneous denoising and reconstruction of 5D data.
+Compared to the damping operator (Figure \dlo{\ref{fig:31}(a) and \ref{fig:32}(a)}\wen{\ref{fig:synth-rrdamping-s}\old{(a)} and \ref{fig:synth-rrdamping-xy-e-s}\dlo{(a)}}), we find that RR + ST + MA operators can better reconstruct the missing traces than RR + damping operators.
 However, based on the visual comparison, the RR + damping operators can perfectly remove the residual noise from the noisy observation than the RR + ST + MA operators.
 Therefore, by introducing the damping and the STMA operators in the RR framework, we can greatly denoise while reconstructing the noisy and missing data from the noisy level-4 block Hankel matrix.
-Figures \dlo{\ref{31}(e) and \ref{32}(e)}\wen{\ref{synth-rrdampingstma-s}\dlo{(e)} and \ref{synth-rrdampingstma-xy-e-s}\dlo{(e)}} show the results obtained by combining the RR, damping and STMA operators.
+Figures \dlo{\ref{fig:31}(e) and \ref{fig:32}(e)}\wen{\ref{fig:synth-rrdampingstma-s}\dlo{(e)} and \ref{fig:synth-rrdampingstma-xy-e-s}\dlo{(e)}} show the results obtained by combining the RR, damping and STMA operators.
 
 We also analyze the influence of each approach by evaluating the S/N\dlo{s} values for iterations numbers (varying from $ 5 $ to $ 30 $).
-Figure \dlo{\ref{30}}\wen{\ref{Contribution_of_each_operator}} shows the S/N\dlo{s} diagrams obtained using the RR operator (the yellow line), RR + MA operator (the green line), RR + STMA operators (the gray line), RR + damping operators (DRR)(the blue line), DRR + MA operators (the black line) and DRR + STMA operators (RDRR)(the red line).
+Figure \dlo{\ref{fig:30}}\wen{\ref{fig:Contribution_of_each_operator}} shows the S/N\dlo{s} diagrams obtained using the RR operator (the yellow line), RR + MA operator (the green line), RR + STMA operators (the gray line), RR + damping operators (DRR)(the blue line), DRR + MA operators (the black line) and DRR + STMA operators (RDRR)(the red line).
 From the S/N diagrams, we deduce that the proposed STMA operator can be used to greatly improve the conventional RR and the DRR methods.
@@
 
-%\new{
-%\AtEndDocument{
-%%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/offset_rr_0370ok}
-%			\label{a}}
-%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/offset_RR_ST1}
-%			\label{b}}
-%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/offset_MA_RR}
-%			\label{c}}\\
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/2D_offset_RR_damping_70_03}
-%			\label{d}}
-%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/offset_RR_STMA}
-%			\label{Fiigure:e}}
-%		\caption{Comparison in one common offset after 10 iterations.
-(a-e) denote the RR, RR+ST, RR+MA, RR+ damping (correspond to the DRR method) and RR+STMA (corresponds to the RDRR without the damping factor), respectively.
-We test these approaches on 5-D synthetic data corrupted by 0.3 as noise level and $ 70\% $ of missing traces.}
-%		\label{44}
-%	\end{figure}
-%}
-%}
-%\new{
-%\AtEndDocument{
-%	\begin{figure}[htb!]
-%		\centering
-%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/RMSE_RR_offset_rr03_70}
-%			\label{a}}
-%		\subfloat[]{\includegraphics[width=0.35\te%xtwidth]{Figures/RMSE_offset_RR_ST1}
-%			\label{b}}
-%		\subfloat[]{\includegraphics[width=0.35\textwidth]{Figures/RMSE_offset_RR_MA}
-%	                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               		\label{c}}\\
-%		\subfloat[]{\includegraphics[width=0.35\te%xtwidth]{Figures/2D_RMSE_offset_RR_damping%_70_03}
-%			\label{d}}
-%		\subfloat[]{\includegraphics[width=0.35\te%xtwidth]{Figures/RMSE_offset_rr_stma}
-%			\label{Fiigure:e}}
-%		\caption{RMSE figures comparison in one common offset after 10 iterations.
-(a-e) denote RR, RR + ST RR + MA, RR + damping (correspond to the DRR method), RR + STMA (RDRR without the damping factor), %respectively.}
-%		\label{45}
-%	\end{figure}
-%}
-%}
-\wen{
-	\AtEndDocument{
-		\begin{figure}[htb!]
-			\centering
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrdamping-s} 
-				\label{synth-rrdamping-s}}
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrstma-s} 
-				\label{synth-rrstma-s}}
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrdampingst-s}
-				\label{synth-rrdampingst-s}}\\
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrdampingma-s}
-				\label{synth-rrdampingma-s}}
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrdampingstma-s}
-				\label{synth-rrdampingstma-s}}		
-			\caption{\wen{Common-offset 2D figures comparison after \wen{ten}\dlo{10} iterations.} (a) The RR + damping operators (DRR method).
+\inputdir{synth_operators}
+\multiplot{5}{synth-rrdamping-s,synth-rrstma-s,synth-rrdampingst-s,synth-rrdampingma-s,synth-rrdampingstma-s}{width=0.29\textwidth}{Common-offset 2D figures comparison after \wen{10}\dlo{wen} iterations.
+(a) The RR + damping operators (DRR method).
 (b) The RR + ST + MA operators.
@@
 (e) The result of the proposed approach (RR + damping + ST+ MA).
-We have tested these approaches on 5D synthetic data corrupted by 0.3 as the noise level and $70\%$ of missing traces}.
-			\label{synth-rrdamping-s,synth-rrstma-s,synth-rrdampingst-s,synth-rrdampingma-s,synth-rrdampingstma-s}
-		\end{figure}}
-}%fig.26
-\wen{
-	\AtEndDocument{
-		\begin{figure}[htb!]
-			\centering
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrdamping-xy-e-s} 
-				\label{synth-rrdamping-xy-e-s}}
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrstma-xy-e-s} 
-				\label{synth-rrstma-xy-e-s}}
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrdampingst-xy-e-s}
-				\label{synth-rrdampingst-xy-e-s}}\\
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrdampingma-xy-e-s}
-				\label{synth-rrdampingma-xy-e-s}}
-			\subfloat[]{\includegraphics[width=0.33\textwidth]{synth_operators/Fig/synth-rrdampingstma-xy-e-s}
-				\label{synth-rrdampingstma-xy-e-s}}		
-			\caption{\wen{\dlo{2D figures c}\wen{C}omparison of the simultaneous denoising and reconstruction error in one common-offset gather after 10 iterations.} (a) RR + damping operators (the DRR method).
-(b) The error using the RR + ST + MA operators.
-(c) The error using the RR + damping + ST operators.
-(d) The RR + damping + MA operators.
-(e) The proposed approach (RR + damping + ST + MA).}
-			\label{synth-rrdamping-xy-e-s,synth-rrstma-xy-e-s,synth-rrdampingst-xy-e-s,synth-rrdampingma-xy-e-s,synth-rrdampingstma-xy-e-s}
-		\end{figure}
-	}
-}%fig.27
-\wen{
-	\AtEndDocument{
-		\begin{figure}[htb!]
-			\centering
-			\includegraphics[width=0.4\textwidth]{Fig/Contribution_of_each_operator}
-			\caption{Comparison of S/N\dlo{s} values as a function of ratio of missing traces between the RR (the yellow line), RR + MA (the green line), RR + STMA (the gray line), DRR (the blue line), DRR + MA (the black line), and DRR + STMA (the red line) under a noise variance of $0.3$ and $70\%$ as missing traces.
-				\label{Contribution_of_each_operator}}
-		\end{figure}%fig.28
-}}\wen{The five key parameters \dlo{that use}\wen{in} the proposed approach are selected using the following strategy.} According to the Cadzow filtering method based on the linear event assumption, $K$ is defined as the number of different dip elements.
+We have tested these approaches on 5D synthetic data corrupted by 0.3 as the noise level and $70\%$ of missing traces.}
+
+\inputdir{synth_operators}
+\multiplot{5}{synth-rrdamping-xy-e-s,synth-rrstma-xy-e-s,synth-rrdampingst-xy-e-s,synth-rrdampingma-xy-e-s,synth-rrdampingstma-xy-e-s}{width=0.3\textwidth}{Common-offset 2D figures comparison after \wen{ten}\dlo{10} iterations.
+(a) The RR + damping operators (DRR method).
+(b) The RR + ST + MA operators.
+(c) The result of RR + damping + ST operators.
+(d) The result provided by the RR + damping + MA operators.
+(e) The result of the proposed approach (RR + damping + ST+ MA).
+We have tested these approaches on 5D synthetic data corrupted by 0.3 as the noise level and $70\%$ of missing traces.}
+
+\inputdir{./}
+\plot{Contribution_of_each_operator}{width=0.5\columnwidth}{Comparison of S/N\dlo{s} values as a function of ratio of missing traces between the RR (the yellow line), RR + MA (the green line), RR + STMA (the gray line), DRR (the blue line), DRR + MA (the black line), and DRR + STMA (the red line) under a noise variance of $0.3$ and $70\%$ as missing traces.}
+
+\wen{The five key parameters \dlo{that use}\wen{in} the proposed approach are selected using the following strategy.} According to the Cadzow filtering method based on the linear event assumption, $K$ is defined as the number of different dip elements.
 \wen{In the condition of curved and complex events, $K$ should be approximately higher than the number of different dip components for producing more reliable results.
@@
 Indeed, random noise can be greatly suppressed and the useful signal can be recovered for synthetic and field seismic data sets}\dlo{.}\wen{Besides, the parameter $T$ should be a positive integer ($T>0$).
-It is important to know that when $T$ is too \dlo{long}\wen{larger}, it \dlo{creates}\wen{causes} some loss of useful signals (Figure \dlo{\ref{28}}\wen{\ref{synth-hxhy-s-stma2}\dlo{(b)}) even though the S/N can be improved.
+It is important to know that when $T$ is too \dlo{long}\wen{larger}, it \dlo{creates}\wen{causes} some loss of useful signals (Figure \dlo{\ref{fig:28}}\wen{\ref{fig:synth-hxhy-s-stma2}\dlo{(b)}) even though the S/N can be improved.
 As a consequence, the amplitude of the signal can be seriously degraded.
-Moreover, if $T$ is \dlo{much short}\wen{too small} (Figure \ref{synth-hxhy-s-stma1}), it cannot attenuate residual noise well.\dlo{(Figures \dlo{\ref{30}(a and c)}\wen{\ref{31}(a) and \ref{31}(c)}).} However, the useful signal can be preserved.
+Moreover, if $T$ is \dlo{much short}\wen{too small} (Figure \ref{fig:synth-hxhy-s-stma1}), it cannot attenuate residual noise well.\dlo{(Figures \dlo{\ref{fig:30}(a and c)}\wen{\ref{fig:31}(a) and \ref{fig:31}(c)}).} However, the useful signal can be preserved.
 Therefore, in the proposed approach we should select a smaller value of $T$ to preserve the quality of the useful signal.
@@
 \bibliography{rdrr}
-
-\newpage
-\listoftables
-
-\newpage
-\listoffigures
-
-%\end{document}
-
-%\AtEndDocument{}
-
-%\newpage
-%\listoffigures
-
-%\begin{figure}[htb!]
-%	\centering
-%	\subfloat[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
-%	\caption{Caption.}
-%	\label{fig:fig}
-%\end{figure}
-
-%\begin{figure}[htb!]
-%	\centering
-%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
-%    \label{fig:fig1}}\\
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
-%    \label{fig:fig2}}\\
-%	\caption{(a) Caption a. (b) Caption b.}
-%	\label{fig:fig1,fig2}
-%\end{figure}
-
-%\begin{figure*}[ht!]
-%	\centering
-%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
-%    \label{fig:fig1}}\\
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
-%    \label{fig:fig2}}\\
-%	\caption{(a) Caption a. (b) Caption b.}
-%	\label{fig:fig1,fig2}
-%\end{figure*}
-
-%\begin{table}[h]
-%\caption{Table caption}
-%\begin{center}
-%     \begin{tabular}{|c|c|c|c|c|c|} 
-%	  \hline Column1 (unit)  & Column2 (unit) & Column3 (unit) \\ 
-%	  \hline 1 & 2  & 3 \\
-%       \hline
-%    \end{tabular} 
-%\end{center}
-%\label{tbl:table1}
-%\end{table}

### 2021-02-24 orthon/paper.tex
up

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}

\title{Non-stationary local signal-and-noise orthogonalization}
\author{Yangkang Chen\footnotemark[1] and Sergey Fomel\footnotemark[2]}
%\author{Authors}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\ms{GEO-2021} %\ms{GJI-2018}

\address{
\footnotemark[1]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
chenyk2016@gmail.com \\
\footnotemark[2]Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
sergey.fomel@beg.utexas.edu
}

\lefthead{Chen and Fomel, 2021}
\righthead{Non-stationary orthogonalization}

\begin{abstract}
The local signal-and-noise orthogonalization method has been widely used in the seismic processing and imaging community. This method uses a fixed triangle smoother for regularizing the local orthogonalization weight, which is based on the assumption that the energy is homogeneously distributed across the whole seismic profile. The fixed triangle smoother limits the performance of the local orthogonalization method in processing complicated seismic datasets. Here, we propose a new local orthogonalization method that uses a variable triangle smoother. The non-stationary smoothing radius is obtained by solving an optimization problem, where the low-pass filtered seismic data are matched by the smoothed data in terms of the local frequency attribute. The new local orthogonalization method with non-stationary model smoothness constraint is called the non-stationary local orthogonalization method. We use several synthetic and field data examples to demonstrate the successful performance of the new method.
\end{abstract}

\maketitle

\section{Introduction}
\old{Signal and noise are two relative terms}\new{The definitions of signal and noise depend on the specific application}. Those components one treats as noise could be signals to others. For example, the multiple reflection waves that were long treated as noise in \old{conventional}\new{the traditional} seismic imaging workflow are signals in full wavefield seismic imaging \cite[]{verschuur2011}. \old{The spatially less discontinuous diffracted waves as compared with reflected waves}\new{Diffracted waves, which are often neglected or removed as spatially discontinuous noise,} are signals when it comes to diffraction imaging \cite[]{fomel2007}. The interfering ambient noise is treated as the signal when \old{it }is taken for passive seismic imaging \cite[]{de2011ambient}.  Here, we generalize the meaning of signal to refer to those desired components in the observed data, while using noise to refer to the \dlo{rest}\wen{remaining} unwanted components. Local signal-and-noise orthogonalization\dlo{, initially proposed in } \cite[]{yangkang2015ortho} is \old{a secondary processing step}\new{an effective method} to optimize the signal-and-noise separation after the initial \old{processing}\new{denoising} step, \old{in the sense that}\new{making} the resulted signal and noise \old{are }locally orthogonal to each other.

\cite{yangkang2015ortho} \old{introduced}\new{introduce} the concept of local signal-and-noise orthogonalization to deal with one commonly existing issue in all denoising methods, i.e., the signal leakage problem. \old{In a nutshell}\new{Simply speaking}, almost all denoising algorithms could cause more or less signal leakage because of either incorrect parameter selection or \old{inadequacy of}\new{inappropriate} denoising assumptions \cite[]{yangkang2015ortho}. The local signal-and-noise orthogonalization method can \old{supplement}\new{complement} a traditional denoising algorithm by applying an element-wise weighting operator to the noise to retrieve the lost signal energy. The element-wise weighting operator can be calculated by solving an inverse problem, where the model is constrained by a smoothing operator. For simplicity, we will omit the ``signal-and-noise'' when referring to the local orthogonalization method throughout the paper. \cite{yangkang2015ortho} \old{demonstrated}\new{demonstrate} the performance via a simple but representative seismic application, i.e., random noise attenuation. \old{Since then}\new{Then}, the local orthogonalization algorithm has been applied widely in the whole seismic data processing and imaging community. \cite{yangkang2015orthogroll} \old{applied}\new{apply} the local orthogonalization method to suppress the ground roll noise by first applying a simple low-pass filtering method to suppress all ground roll components and secondly applying the local orthogonalization method to retrieve all lost reflection \old{components}\new{energy} back to the low-pass filtered data. \cite{yangkang2015dbortho} \old{incorporated}\new{incorporates} the local orthogonalization method into the iterative simultaneous-source separation framework \cite[]{shaohuan2019} to better separate the useful signals and interfering blending noise in each step and thus improves the deblending performance and \old{accelerated}\new{accelerates} the convergence rate. \cite{weilin2018} \old{applied}\new{apply} the local orthogonalization method to decompose a microseismic trace (via the mathematical morphology algorithm) into quasi-orthogonal components for weak microseismic signal detection. \cite{sripanich2017elastic} \old{applied}\new{apply} the local orthogonalization method to separate the elastic wave modes in heterogeneous anisotropic media by compensating for the amplitude loss in each separated wave component.  \cite{jeong2019enhanced} \old{applied}\new{apply} the local orthogonalization method to separate the P and S wave \new{modes} in elastic modeling and multi-parameter full waveform inversion\old{ more robustly}. They \old{showed}\new{show} that the residual energy or crosstalk caused by divergence and curl operators in the P- and S-wave separation can be significantly decreased using the local orthogonalization method, and the resulted elastic multi-parametric inversion converges faster and is less likely to fall into the local minima. More recently, \cite{zhangdong2019ortho} \old{applied}\new{apply} the local orthogonalization method to retrieve the leaked multiples energy in the initially demultipled data based on the surface-related multiple elimination (SRME) framework and \old{obtained}\new{obtain} a successful separation between primaries and multiples even in the case of imperfect circumstances or built-in assumptions. \new{\cite{qu2020robust} apply the local orthogonalization method to mitigate the amplitude-variation-with-offset (AVO) effect in the one-way wave-equation based joint migration inversion framework. \cite{zhangdong2021geo} further apply the local orthogonalization method to leaked internal multiple crosstalk estimation and attenuation on full-wavefield migrated images. }

Despite \new{of many}\old{ the} reported successes in the literature, the traditional local orthogonalization method still suffers from \old{one}\new{a} problem. The smoothing radius of the triangle smoother that regularizes the inverse problem and greatly affects the signal-and-noise separation performance \dlo{(as demonstrated in ?) }is fixed across the whole seismic dataset in the conventional framework. The fixed smoothing radius makes the local orthogonalization method when handling structurally complex seismic profiles. A larger smoothing radius tends to over-smooth the local orthogonalization weight and causes a failure in retrieving the \old{lost signals}\new{signal leakage} in complex areas. A smaller smoothing radius tends to \old{bring more noise back to}\new{cause more residual noise in} the denoised data and may also cause instability issues. Thus, one needs to adjust the \new{globally} constant smoothing radius carefully to obtain the best compromise.

In this paper, we introduce a non-stationary local signal-and-noise orthogonalization method that uses a spatially variable smoothing radius to deal with the structurally complex seismic data. The non-stationary local orthogonalization \old{requires applying}\new{applies} a non-stationary triangle smoother to regularize the ill-posed inverse problem for solving the local orthogonalization weight. While the spatially variable smoothing radius \old{could}\new{can} be obtained by incorporating \old{the}\new{some} a priori information, e.g., \dlo{longer}\wen{shorter} radius for more structurally complex areas and \dlo{shorter}\wen{longer} radius for simpler areas, we provide an elegant way to estimate the \old{optimal spatially variable smoothing radius}\new{optimal distribution of smoothing radius} by optimization. The \old{goal}\new{principle} is to match a low-pass filtered seismic data and a smoothed seismic data via the non-stationary smoothing operator in terms of minimal \old{local-frequency}\new{local frequency} difference. The optimization problem is solved by an iterative line-search method with a fast convergence.

We organize the paper as follows. We first introduce the basics of the local signal-and-noise orthogonalization method. Then, we introduce in detail the formulation of the non-stationary triangle smoother and the iterative optimization method to adaptively obtain the smoothing radius map. We use a set of representative examples to demonstrate the performance of the non-stationary local orthogonalization method. \old{Finally, we draw some key conclusions.}

\section{Theory}
\subsection{Stationary local orthogonalization}
Given an initial estimation of the signal $\mathbf{s}$ and noise $\mathbf{n}$, the locally orthogonalized signal and noise can be expressed as\new{:}
\begin{align}
\label{eq:sn1}
\hat{\mathbf{s}} = \mathbf{s} + \mathbf{w} \circ \mathbf{s}, \\
\label{eq:sn2}
\hat{\mathbf{n}} = \mathbf{n} - \mathbf{w} \circ \mathbf{s}, 
\end{align}
where $\hat{\mathbf{s}}$ and $\hat{\mathbf{n}}$ are the orthogonalized signal and noise, respectively; $\mathbf{w}$ denotes the local orthogonalization weight \cite[]{yangkang2015ortho}; and $\circ$ denotes the Hadamard product.

When the local orthogonalization weight is a constant $w$, equations \ref{eq:sn1} and \ref{eq:sn2} become the global orthogonalization formulas: 
\begin{align}
\label{eq:sn11}
\hat{\mathbf{s}} = \mathbf{s} + w \mathbf{s}, \\
\label{eq:sn22}
\hat{\mathbf{n}} = \mathbf{n} - w \mathbf{s}. 
\end{align}
Following the Gram-Schmidt orthogonalization \cite[]{gram}, to make $\hat{\mathbf{s}}$ and $\hat{\mathbf{n}}$ orthogonal, 
\begin{equation}
\label{eq:gow}
w=\frac{\mathbf{n}^T\mathbf{s}}{\mathbf{s}^T\mathbf{s}}.
\end{equation} 
$w$ in equation \ref{eq:gow} is called the global orthogonalization weight, and
can be understood as the least-squares solution to the following optimization problem
\begin{equation}
\label{eq:gowo}
\arg \min_{w} \parallel w \mathbf{s} - \mathbf{n} \parallel_2^2.
\end{equation} 
To draw an analogy, the local orthogonalization weight can be understood as the least-squares solution to the following problem
\begin{equation}
\label{eq:lowo}
\arg \min_{\mathbf{w}} \parallel  \mathbf{w}\circ\mathbf{s} - \mathbf{n} \parallel_2^2.
\end{equation}

To solve $\mathbf{w}$\old{ stably}, a regularization term is \dlo{required}\wen{added} to the objective function as follows:
\begin{equation}
\label{eq:lowr}
\arg \min_{\mathbf{w}} \parallel  \mathbf{S}\mathbf{w} - \mathbf{n} \parallel_2^2 + \mathbf{R}(\mathbf{w}),
\end{equation} 
where $\mathbf{S}\mathbf{w}$ is used to substitute $\mathbf{w}\circ\mathbf{s}$.

Based on the shaping regularization method \cite[]{fomel2007shape}, the solution can be obtained as\new{:}
\begin{equation}
\label{eq:lowr2}
\hat{\mathbf{w}}_S = [\lambda^2 \mathbf{I} + \mathbf{T}_S (\mathbf{S}^T\mathbf{S} -\lambda^2 \mathbf{I})]^{-1}\mathbf{T}_S\mathbf{S}^T\mathbf{n}, 
\end{equation} 
where $\mathbf{T}_S$ denotes a stationary triangle smoothing operator; and $\mathbf{I}$ is an identity matrix. $\lambda=\parallel \mathbf{s} \parallel_2^2$.  The stationary local orthogonalization \old{is completed}\new{can be implemented} by substituting the inverted $\hat{\mathbf{w}}_S$ into equation \ref{eq:sn1}.

\subsection{Non-stationary smoothing and local orthogonalization}
The triangle smoothing operator is equivalent to applying a rectangle (box) smoothing operator twice. 
The rectangle smoothing operator can be expressed in the Z-transform form as follows:
\begin{equation}
\label{eq:box}
B(Z) = \frac{1}{N} ( 1+ Z + Z^2 +\cdots+Z^{N-1}) = \frac{1-Z^N}{N(1-Z)},
\end{equation}
where $N$ is the length for the rectangle smoothing operator, or the radius for the triangle smoothing operator. Correspondingly, the triangle smoothing operator in the Z-transform form is expressed as follows:
\begin{equation}
\label{eq:tri}
T(Z) = B(Z)B(Z) = \frac{(1-Z^N)^2}{N^2(1-Z)(1-Z)} =\frac{2Z^N-Z^{2N}-1}{N^2(1-Z)(Z-1)}.
\end{equation}
In equation \ref{eq:tri}, the division by $1-Z$ corresponds to the following recursion
\begin{equation}
\label{eq:rec0}
y_n=y_{n-1}+x_n,
\end{equation}
denoting a causal integration operation.
Correspondingly, division by $Z-1$ denotes the reverse causal integration operation:
\begin{equation}
\label{eq:rec1}
y_{n-1}=y_{n}+x_n.
\end{equation}
The numerator in equation \ref{eq:tri} denotes the following recursion:
\wen{\begin{equation}
\label{eq:rec2}
y_{n}=2x_{n-N}-x_{n-2N}-x_{n}.
\end{equation}}
Thus, the triangle smoothing operator consists of the following steps: 
1) Causal integration following equation \ref{eq:rec0}; 2) Reverse causal integration following equation \ref{eq:rec1}; 3) Recursion following equation \ref{eq:rec2}; 4) Division by $N^2$.

\new{Note that the reverse causal integration denoted by $1/(Z-1)$ and $y_{n-1}=y_{n}+x_n$ is a little different from the anticausal integration denoted by $1/(1-1/Z)$ and $y_{n-1}=y_{n}+x_{n-1}$. The anticausal integration is the exact adjoint of the causal integration. To apply consecutive causal and anticausal integrations, one needs to reformulate equation \ref{eq:tri} as $\frac{2Z^{N-1}-Z^{2N-1}-Z^{-1}}{N^2(1-Z)(1-Z^{-1})}$, and revise the recursion expressed in equation \ref{eq:rec2} correspondingly. }

Because operator multiplication in the Z-transform domain is sequence independent (like the operator multiplication in the Fourier domain), there is no need for a given order for the above four steps. Note that for equation \ref{eq:rec2}, the recursion for each point depends on the smoothing radius $N$. When $N$ is fixed constantly, equation \ref{eq:rec2} corresponds to a stationary smoothing operator $\mathbf{T}_S$. When $N$ is spatially variable \old{controlled by}\new{with} the smoothing radius map $\mathbf{r}$, equation \ref{eq:rec2} corresponds to a non-stationary smoothing operator $\mathbf{T}_N$. Substituting $\mathbf{T}_S$ by $\mathbf{T}_N$ in equation \ref{eq:lowr}, we can obtain the non-stationary local orthogonalization weight: 
\begin{equation}
\label{eq:lowrn}
\hat{\mathbf{w}}_N = [\lambda^2 \mathbf{I} + \mathbf{T}_N (\mathbf{S}^T\mathbf{S} -\lambda^2 \mathbf{I})]^{-1}\mathbf{T}_N\mathbf{S}^T\mathbf{n}, 
\end{equation} 
which is the base for the non-stationary \old{version of }local orthogonalization as defined by equations \ref{eq:sn1} and \ref{eq:sn2}.

\subsection{Iterative smoothing radius estimation}
We formulate the smoothing radius estimation as an optimization problem. Here, we use a global band-pass filtering method as a benchmark method to evaluate the smoothing effect \old{offered by}\new{from} the non-stationary smoothing operator. The basic assumption is that by using a local non-stationary smoothing operator, we obtain an equivalent smoothing effect as a global smoothing filter, e.g., the band-pass filter. To measure the match between two methods, we use the local frequency operator \cite[]{fomel2007localattr} as the metric. The objective function of the optimization problem is expressed as:
\begin{equation}
\label{eq:robj}
J=\parallel \mathbf{L}(\mathbf{T}_N(\mathbf{r}) \mathbf{d}) -\mathbf{L}(\mathbf{d}_F)  \parallel_2^2,
\end{equation}
where $\mathbf{L}$ denotes the local frequency operator, as detailed in \new{\cite{fomel2007localattr}}. \wen{Generally speaking, the local frequency operator transforms the direct division of calculating the instantaneous frequency as a regularized inverse problem and then \old{use}\new{uses} the shaping regularization method to solve it. } $\mathbf{T}_N(\mathbf{r})$ denotes the non-stationary smoothing operator with an input spatially varying radius map $\mathbf{r}$. The non-stationary smoothing operator is a serial multi-dimensional filter, meaning that a 1D smoothing filter defined by equation \ref{eq:tri} is applied to each direction of the seismic data (e.g., time, space, offset) in a serial form. 
 $\mathbf{d}$ is the observed noisy data. $\mathbf{d}_F$ denotes the low-pass filtered data with a cut-off high frequency of $F$, which is simply chosen as the dominant frequency of the seismic data.  Note that choosing a direct L2 metric could contain more local minima than choosing a local frequency operator. Thus, we \old{intend to choose}\new{choose a smoother}\old{ a smooth} function, which first highlights the frequency content of the data and secondly provides a sufficiently smooth evaluation of the distance between the two objects\old{ that ensures a fast convergence}, \new{to ensure a fast convergence}

To obtain the optimal spatially varying smoothing radius, two basic assumptions should be kept in mind. First, if the local frequency of a point after smoothing the input data is still higher than the low-pass filtered data, meaning that the smoothing is not strong enough, then we increase the smoothing radius. Second, if the local frequency of a point after smoothing the input data is lower than the low-pass filtered data, meaning that it is over-smoothing, we decrease the smoothing radius. Following \cite{greer2018matching}, we use a line-search method to solve the optimization in equation \ref{eq:robj}:
\begin{equation}
\label{eq:r}
\mathbf{r}_{n+1} = \mathbf{r}_{n} + \alpha_n \mathbf{s}_n,
\end{equation}
where $\mathbf{r}_{n}$ denotes the radius map after $n$ iterations, $\alpha_n$ is the step size, and $\mathbf{s}_n$ is the search direction. Here, we define the search direction as:
\begin{equation}
\label{eq:r}
\mathbf{s}_{n} = \mathbf{L}(\mathbf{T}_N(\mathbf{r}_n) \mathbf{d}) -\mathbf{L}(\mathbf{d}_F).
\end{equation}
To facilitate a fast convergence, we linearly decrease\old{ the} $\alpha_n$ from a high value, e.g., 0.7, to a small value, e.g., 0.05, gradually. In this paper, we use  $\alpha_1=0.7$, and decrease it by a half at each iteration, and reach $\alpha_5=0.05$ at the 5th iteration.

\section{Examples}
We apply the proposed non-stationary local orthogonalization method to one synthetic example and three field data examples. \old{We use two examples (first two field datasets) that were previously used in ? for  benchmark comparison.} We first test the performance of the proposed method on a synthetic dataset, for which we have the ground truth. The clean data are plotted in Figure \ref{fig:hyper}. We add some band-limited noise into the clean data and obtain the noisy data shown in Figure \ref{fig:hyper-n}. The cut-off high frequency for band-limitting the Gaussian white noise is 50 Hz. The dominant frequency for the signal is 15 Hz. We also use the signal-to-noise ratio (S/N) definition as defined in \cite{yangkang2015ortho} to measure the noise level and denoising performance. The S/N of the noisy data is 1.56 dB. We show the results in Figure \ref{fig:hyper-fx,hyper-ortho,hyper-orthon,hyper-fx-n,hyper-ortho-n,hyper-orthon-n,hyper-fx-s,hyper-ortho-s,hyper-orthon-s}. Here, we apply the FX method (first column), the traditional stationary orthogonalization method (second column), and the proposed method to denoise the data (third column). \old{Readers are referred to ? for more details about the FX method.} The first row in Figure \ref{fig:hyper-fx,hyper-ortho,hyper-orthon,hyper-fx-n,hyper-ortho-n,hyper-orthon-n,hyper-fx-s,hyper-ortho-s,hyper-orthon-s} plots a comparison of three denoised data. The second row in Figure \ref{fig:hyper-fx,hyper-ortho,hyper-orthon,hyper-fx-n,hyper-ortho-n,hyper-orthon-n,hyper-fx-s,hyper-ortho-s,hyper-orthon-s} plots a comparison of the removed noise using different methods. The artifacts in 1.5 s could be caused by the failure of the FX method to accurately estimate the prediction filter at the notch frequencies due to a superposition of several Ricker wavelets at different time positions. Because the orthogonalization method is a two-step technique. It \old{acts}\new{performs} on the result from the first-step denoising, \old{in this case,}\new{i.e.,} the FX method. Thus, two orthogonalization methods also \old{more or less }cause \new{more or less} such artifacts. The third row in Figure \ref{fig:hyper-fx,hyper-ortho,hyper-orthon,hyper-fx-n,hyper-ortho-n,hyper-orthon-n,hyper-fx-s,hyper-ortho-s,hyper-orthon-s} plots a comparison of the local similarity between denoised data and removed noise. Here, the local similarity is used as a complement metric for evaluating denoising performance, i.e., to evaluate the signal leakage \cite[]{yangkang2015ortho}. Larger \old{value}\new{values} in the local similarity map \old{indicates}\new{indicate} stronger signal leakage. It is clear that the stationary orthogonalization method improves the FX method by reducing the residual noise, also by significantly reducing the signal leakage. The non-stationary orthogonalization method further improves the stationary orthogonalization method by reducing more residual noise and signal leakage.  The leakage signal caused by the FX method is well highlighted by the high values in the local similarity map in Figure \ref{fig:hyper-fx-s}. The signal leakage caused by the stationary orthogonalization method is much less than the FX method, as indicated by the much smaller local similarity values. The proposed method obtains a negligible local similarity map, and demonstrates a strong signal-preserving capability. The calculated S/Ns of the FX, stationary orthogonalization, and non-stationary orthogonalization methods are 6.37 dB, 7.78 dB, and 9.41 dB, respectively. In this test, we use a prediction length of six points for the FX method, a constant smoothing radius of 30 samples for the stationary orthogonalization method, and an adaptively estimated smoothing radius map for the non-stationary orthogonalization method. A comparison of the FK spectra is shown in Figure \ref{fig:hyper-fs}. The FK spectra of the clean and noisy data are plotted on the top row. The bottom row plots the spectra of the denoised data using three aforementioned methods. It is clear that noise spectra becomes less from left to right in the bottom row. The low-frequency signal spectra are better recovered from left to right. The iteratively solved smoothing radius maps are plotted in Figure \ref{fig:hyper-rect10,hyper-rect20,hyper-rect30,hyper-rect40,hyper-rect50}. Figures \ref{fig:hyper-rect10}-\ref{fig:hyper-rect50} show the estimated smoothing radius maps after one to five iterations, respectively. From the smoothing radius maps, we can conclude two things. First, the smoothing radius map well captures the signal positions, where we should use a smaller radius, and the non-signal positions, where we should use a larger radius. Second, the iterative radius estimation method converges fast. After three iterations, the radius map is almost unchanged, as indicated by the color of the maps and range of the scalebars.

We then apply the proposed method to a field dataset that was previously studied in \cite{yangkang2015ortho}. For benchmark comparison, we use the exactly same parameters as those in \cite{yangkang2015ortho} for the FX and stationary orthogonalization methods. We add the result from the proposed non-stationary orthogonalization method to show the further improvement over the published ones. The field data are plotted in Figure \ref{fig:pp-0}. Figures \ref{fig:pp-z} and \ref{fig:pp-z1} plot the enlarged sections from the raw data, corresponding to the cyan and green frame boxes, respectively. The comparison of denoising performance is plotted in Figure \ref{fig:pp-fx-0,pp-ortho-0,pp-orthon-0,pp-fx-z,pp-ortho-z,pp-orthon-z,pp-fx-z1,pp-ortho-z1,pp-orthon-z1}. Same as the first test, we compare the proposed method (third column) with the FX method (first column) and the stationary orthogonalization method (second column). The second and third rows plot enlarged sections from the first row for the first frame box (cyan) and the second frame box (green), \old{correspondingly}\new{respectively}. From the second row in Figure \ref{fig:pp-fx-0,pp-ortho-0,pp-orthon-0,pp-fx-z,pp-ortho-z,pp-orthon-z,pp-fx-z1,pp-ortho-z1,pp-orthon-z1}, we observe that the orthogonalization method seems to be less continuous than the FX method because of a very small constant smoothing radius to reduce the signal leakage. The non-stationary orthogonalization method, however, is as continuous as the FX method. From the third row in Figure \ref{fig:pp-fx-0,pp-ortho-0,pp-orthon-0,pp-fx-z,pp-ortho-z,pp-orthon-z,pp-fx-z1,pp-ortho-z1,pp-orthon-z1}, we can observe that the energy of the FX method seems to be obviously weaker than the other two orthogonalization methods. Comparing the removed noise sections shown in Figure \ref{fig:pp-fx-n0,pp-ortho-n0,pp-orthon-n0}, we can see that the FX method tends to lose some small-scale signal components in the noise section, e.g., the dipping structure\dlo{ highlighted by the pink frame box}, and some observable low-frequency energy around 1.5 s between traces 200 and 350. \wen{The second and third rows in Figure \ref{fig:pp-fx-n0,pp-ortho-n0,pp-orthon-n0} show zoomed sections corresponding to the cyan and green frame boxes, respectively.} Both orthogonalization methods obtain a very good preservation of useful signals and cause negligible signal leakage. However, the energy of the removed noise using the stationary orthogonalization method seems to be weaker than the non-stationary orthogonalization method, indicating that the stationary method removes less noise than the proposed method. The iteratively estimated radius maps are plotted in Figure \ref{fig:pp-rect10,pp-rect20,pp-rect30,pp-rect40,pp-rect50}. It is clear that the smoothing radius map is updated dramatically from \new{the} first to \new{the} third iterations, and almost converges since the fourth iteration. The short and long radii in the finally estimated radius map correspond well to the structurally complex and simple areas in the raw seismic profile.

\dlo{We test another field example that was used in ?. We follow the example setup of ?, and only add a new result from the proposed non-stationary orthogonalization method for benchmark comparison. Figure \ref{fig:g-0,g-z,g-z1} shows the raw seismic data, two zoomed sections corresponding to frame boxes A and B, respectively. Figure \ref{fig:g-rna-0,g-ortho-0,g-orthon-0,g-rna-z-a,g-ortho-z-a0,g-orthon-z-a0,g-rna-z-b,g-ortho-z-b0,g-orthon-z-b0} plot a comparison of different methods. Here, following ?, we use a more advanced FX prediction method for dealing with the very complicated structures in this dataset, i.e., the FX regularization non-stationary autoregression (RNAR) method ?.  From the first to the third columns, the results correspond to the FX RNAR, stationary orthogonalization, and non-stationary orthogonalization methods, respectively. The second and third rows correspond to the zooming areas highlighted by the frame boxes A and B, respectively. From the second row of Figure \ref{fig:g-rna-0,g-ortho-0,g-orthon-0,g-rna-z-a,g-ortho-z-a0,g-orthon-z-a0,g-rna-z-b,g-ortho-z-b0,g-orthon-z-b0}, we can observe that both orthogonalization methods obtain a cleaner image with stronger energy compared with the FX RNAR method. However, if we observe carefully on the result from the stationary orthogonalization method, we can find some blank pixels, as highlighted by the labelled arrows in Figure \ref{fig:g-ortho-z-a0}. However, the non-stationary orthogonalization method has filled in these gaps, as highlighted by the labelled arrows in Figure \ref{fig:g-orthon-z-a0}. Here, the blank pixels are caused by the instability due to an over-small smoothing radius during the inversion for local orthogonalization weight. However, for the traditional orthogonalization method, if we use a larger fixed smoothing radius, the ability to retrieve the leaked signals is also weakened, as demonstrated by the aforementioned synthetic example. By using the non-stationary smoothing radius, we can overcome such a problem. \dlo{The same thing can also be observed}\wen{We also observe} from the third row in Figure \ref{fig:g-rna-0,g-ortho-0,g-orthon-0,g-rna-z-a,g-ortho-z-a0,g-orthon-z-a0,g-rna-z-b,g-ortho-z-b0,g-orthon-z-b0}\dlo{, where}\wen{ that} the stationary orthogonalization method causes some stability issues. A comparison of the removed noise is plotted in Figure \ref{fig:g-rna-n0,g-ortho-n0,g-orthon-n0,g-rna-n-z-a,g-ortho-n-z-a,g-orthon-n-z-a,g-rna-n-z-b,g-ortho-n-z-b,g-orthon-n-z-b}, where we can see that both orthogonalization methods successfully retrieve the leaked signals from the noise section initially obtained from the FX RNAR method. The iteratively solved smoothing radius maps for this dataset are plotted in Figure \ref{fig:g-rect10,g-rect20,g-rect30,g-rect40,g-rect50}.}
Next, we apply the proposed method to another field data example. Figure \ref{fig:f2-0,f2-z1} shows the raw seismic data and one zoomed section corresponding to frame box. Figure \ref{fig:f2-fx-0,f2-ortho-0,f2-orthon-0,f2-fx-n0,f2-ortho-n0,f2-orthon-n0} plots a comparison of different methods. The first to the third columns correspond to the FX method, stationary orthogonalization, and non-stationary orthogonalization method results, respectively. The top row shows the denoised results of different methods. The bottom row shows the removed noise of different methods. From the comparison of denoised results, it is obvious that the non-stationary orthogonalization method obtains a better amplitude recovery. From comparison of removed noise, it we observe that the FX method damages the most signal energy. The stationary orthogonalization method recovers a lot of the leaked signals but still causes some remaining \old{leakages}\new{leakage}. The non-stationary orthogonalization method, however, causes the least signal \old{leakages}\new{leakage}. The leaked signals in Figure \ref{fig:f2-orthon-n0} are almost negligible. We plot a zoomed comparison of each frame box \old{of Figure}\new{from Figure} \ref{fig:f2-fx-0,f2-ortho-0,f2-orthon-0,f2-fx-n0,f2-ortho-n0,f2-orthon-n0} \new{and show the comparison} in Figure \ref{fig:f2-fx-z1-0,f2-ortho-z1-0,f2-orthon-z1-0,f2-fx-n-z1,f2-ortho-n-z1,f2-orthon-n-z1} for a better view, where the arrows on the top row indicate those areas with significant amplitude and coherence difference.  The bottom row of Figure \ref{fig:f2-fx-z1-0,f2-ortho-z1-0,f2-orthon-z1-0,f2-fx-n-z1,f2-ortho-n-z1,f2-orthon-n-z1} further confirms that the non-stationary orthogonalization method obtains a better recovery of leaked signals than the stationary orthogonalization method because the leaked spatially coherent energy in the noise becomes weaker from left to right.

Finally, we apply the proposed method to a 3D Teapot Dome field data example, as shown in Figure \ref{fig:tea,t-fxy,t-ortho,t-orthon}. Figure \ref{fig:tea} plots the 
initially stacked 3D seismic image that contains very strong noise. Figures \ref{fig:t-fxy}-\ref{fig:t-orthon} plot the results from the FXY RNAR method \cite[]{guochang2013,wanghang2021geo}, the stationary and non-stationary orthogonalization methods. It is clear that all three methods \old{obtain}\new{achieve a} successful removal of the random noise. Figure \ref{fig:t-fxy-n0,t-ortho-n0,t-orthon-n0} plots a comparison of the removed noise. As highlighted by the arrows on the top slice, the FXY RNAR method causes some signal leakage in Figure \ref{fig:t-fxy-n0}, which is slightly improved by the traditional stationary orthogonalization method in Figure \ref{fig:t-ortho-n0}. However, we can still see signal in Figure \ref{fig:t-ortho-n0}.  The proposed non-stationary orthogonalization method successfully retrieves the leaked signals and causes a negligible amount of signal leakage.  A constant time slice (corresponding to 1 s) comparison of the removed noise cubes is plotted in Figure \ref{fig:slice-fxy-0,slice-ortho-0,slice-orthon-0,slice-fxy-z,slice-ortho-z,slice-orthon-z}. Figures \ref{fig:slice-fxy-0}-\ref{fig:slice-orthon-0} plot the time slices using the FXY RNAR method, stationary orthogonalization method, and non-stationary orthogonalization method. Figures \ref{fig:slice-fxy-z}-\ref{fig:slice-orthon-z} plot the zoomed comparison of Figures \ref{fig:slice-fxy-0}-\ref{fig:slice-orthon-0}, corresponding to the frame boxes. It is \old{more clear}\new{clearer} that the signal leakage is reduced from left to right.

\section{Discussion}
The non-stationary orthogonalization method is more \dlo{convenient to adjust the parameter}\wen{adaptive}, i.e., \new{in choosing the} smoothing radius, than the traditional local orthogonalization method. For highly non-stationary seismic data, the traditional orthogonalization method can retrieve all the leaked signals only if one uses a very small smoothing radius\old{ (constantly through the whole profile)}\new{, which is constant throughout the whole dataset}. However, the \old{constantly}\new{constant} small smoothing radius could cause more \old{retrieved}\new{residual} noise. If one uses a \old{constantly}\new{constant} large smoothing radius, then the denoised data will be much smoother, but it is not possible to retrieve all the leaked signals. Thus, the noise removal and signal retrieval are always a compromise.  The non-stationary local orthogonalization method \old{just solves this contradiction problem}\new{overcomes this contradiction}, i.e., varying the smoothing radius adaptively. \old{The benefit is that it only retrieves the leaked signals.}

The smoothing radius controls the stability of the inverse problem to calculate the local orthogonalization weight $\mathbf{w}$ in equations \ref{eq:lowr} and \ref{eq:lowr2}. Thus, when using a very small smoothing radius in the traditional local orthogonalization method, inversion of equation \ref{eq:lowr} could be unstable due to the singularities in $\mathbf{S}$. The unstable inversion could cause \old{the problem of missing samples}\new{the missing simples in the result}\old{ in the second field data example}. However, a larger smoothing radius could bring a less accurate inversion result. From this perspective, the non-stationary local orthogonalization method offers a more convenient way in compromising the stability and accuracy when solving the local orthogonalization weight. In the same time, a smaller smoothing radius indicates a higher resolution and a weaker anti-noise performance of the local orthogonalization weight, as illustrated by Figure 1 in \cite{yangkang2015ortho}. This effect makes the traditional local orthogonalization method obtain a noisier result than the FX method in the first field data example. From this perspective, the non-stationary local orthogonalization method offers a more convenient way in compromising the resolution and anti-noise ability when solving the local orthogonalization weight.

The non-stationary smoothing radius estimation approach introduced in this paper is only one option. This \old{method}\new{procedure} takes most of the computation time in the proposed non-stationary orthogonalization method. For example, for \old{the second field data example}\new{a 2D dataset of size $2501\times 1001$}, the FX RNAR method takes 49.3 s, the stationary orthogonalization method takes only 19.2 s, and the non-stationary orthogonalization method takes 283.9 s. But the smoothing radius calculation step takes 263.3 s and the non-stationary orthogonalization process only takes 20.6 s, which is comparable with the stationary one. The comparison is based on a Mac Pro Laptop with a 2.5 Ghz Intel Core i7 processor, and 16 GB LPDDR3 memory.  Other options that take the a priori information or structural complexity into consideration is also worth investigation\wen{, and is probably more computationally efficient}. For examples, there are some related strategies that have been published in the literature. \cite{liuyang2009tvmf} \old{used}\new{use} the signal energy criterion to design the spatially variable filter length for a median filtering operation. \cite{yangkang2015svmf} \old{use}\new{uses} the signal reliability criterion to design the non-stationary filter length according to the a priori information of the signal distribution. \cite{fuchao2020} \old{used}\new{use} the structural complexity criterion to design the non-stationary filter length in the FX method. All these strategies could also benefit the non-stationary local orthogonalization framework.

\section{Conclusions}
We introduced a novel non-stationary local signal-and-noise orthogonalization method to suppress random seismic noise without damaging useful signals. We show that the selection of smoothing radius in the traditional local orthogonalization method \new{greatly} affects the final denoising performance. A larger smoothing radius could fail in retrieving the \old{leakage signals back}\new{signal leakage} while a smaller smoothing radius tends to \old{bring back more}\new{cause more residual} random noise. The non-stationary smoothing radius \old{in the triangle smoothers}\new{for regularizing the local orthogonalization weight can be}\old{ is} obtained by solving an optimization problem that connects the smoothing radius with the smoothing performance, as benchmarked by a global low-pass filter. We demonstrate in detail that the optimally calculated smoothing radius \old{can have}\new{enjoys} a better compromise in reducing signal leakage and noise contamination simultaneously, and thus \new{helps} obtain a higher \old{signal-to-noise ratio}\new{S/N}. The non-stationary local orthogonalization method is not limited to application of seismic random noise attenuation and can be capable of better separating the desired ``signal" and unwanted ``noise" components when the signal leakage problem exists.

%\section{Acknowledgements}
%We thank Danilo Velis and three anonymous reviewers for constructive suggestions. The research is supported by the starting funds from Zhejiang University and Tecas Consortium for Computational Seismology.

%\inputdir{test}
%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
%\multiplot{2}{test1,test2}{width=0.45\textwidth}{(a) Caption a. (b) Caption b.}

\AtEndDocument{
\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.3\textwidth]{hyper/Fig/hyper}
   \label{fig:hyper}}
   \subfloat[]{\includegraphics[width=0.3\textwidth]{hyper/Fig/hyper-n}
   \label{fig:hyper-n}}\\
\caption{Synthetic example. (a) Clean data. (b) Noisy data with band-limited noise. }
\label{fig:hyper,hyper-n}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.25\textwidth]{hyper/Fig/hyper-fx0}
   \label{fig:hyper-fx}}
   \subfloat[]{\includegraphics[width=0.25\textwidth]{hyper/Fig/hyper-ortho0}
   \label{fig:hyper-ortho}}
   \subfloat[]{\includegraphics[width=0.25\textwidth]{hyper/Fig/hyper-orthon0}
   \label{fig:hyper-orthon}}\\
\subfloat[]{\includegraphics[width=0.25\textwidth]{hyper/Fig/hyper-fx-n0}
   \label{fig:hyper-fx-n}}
   \subfloat[]{\includegraphics[width=0.25\textwidth]{hyper/Fig/hyper-ortho-n0}
   \label{fig:hyper-ortho-n}}
   \subfloat[]{\includegraphics[width=0.25\textwidth]{hyper/Fig/hyper-orthon-n0}
   \label{fig:hyper-orthon-n}}\\  
\subfloat[]{\includegraphics[width=0.25\textwidth]{hyper/Fig/hyper-fx-s}
   \label{fig:hyper-fx-s}}
   \subfloat[]{\includegraphics[width=0.25\textwidth]{hyper/Fig/hyper-ortho-s}
   \label{fig:hyper-ortho-s}}
   \subfloat[]{\includegraphics[width=0.25\textwidth]{hyper/Fig/hyper-orthon-s}
   \label{fig:hyper-orthon-s}}\\ 
\caption{\wen{Synthetic example. Denoised data using (a) FX method, (b) stationary orthogonalization method, (c) non-stationary orthogonalization method. Removed noise using (d) FX method, (e) stationary orthogonalization method, (f) non-stationary orthogonalization method. Local similarity using (g) FX method, (h) stationary orthogonalization method, (i) non-stationary orthogonalization method.} }
\label{fig:hyper-fx,hyper-ortho,hyper-orthon,hyper-fx-n,hyper-ortho-n,hyper-orthon-n,hyper-fx-s,hyper-ortho-s,hyper-orthon-s}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.33\textwidth]{hyper/Fig/hyper-f0}
   \label{fig:hyper-f}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{hyper/Fig/hyper-nf}
   \label{fig:hyper-nf}}\\
\subfloat[]{\includegraphics[width=0.33\textwidth]{hyper/Fig/hyper-fxf0}
   \label{fig:hyper-fxf}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{hyper/Fig/hyper-orthof0}
   \label{fig:hyper-orthof}} 
   \subfloat[]{\includegraphics[width=0.33\textwidth]{hyper/Fig/hyper-orthonf0}
   \label{fig:hyper-orthonf}} 
\caption{\wen{Synthetic example. FK spectra of (a) clean data, (b) noisy data, (c) denoised data using FX method, (d) denoised data using stationary orthogonalization method, and (e) denoised data using the non-stationary orthogonalization method.}}
\label{fig:hyper-fs}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.33\textwidth]{hyper/Fig/hyper-rect10}
   \label{fig:hyper-rect10}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{hyper/Fig/hyper-rect20}
   \label{fig:hyper-rect20}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{hyper/Fig/hyper-rect30}
   \label{fig:hyper-rect30}}\\
\subfloat[]{\includegraphics[width=0.33\textwidth]{hyper/Fig/hyper-rect40}
   \label{fig:hyper-rect40}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{hyper/Fig/hyper-rect50}
   \label{fig:hyper-rect50}} 
\caption{Synthetic example. Iteratively estimated non-stationary smoothing radius after (a) one iteration, (b) two iterations, (c) three iterations, (d) four iterations, and (e) five iterations.}
\label{fig:hyper-rect10,hyper-rect20,hyper-rect30,hyper-rect40,hyper-rect50}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.45\textwidth]{vecta/Fig/pp-0}
   \label{fig:pp-0}}\\
   \subfloat[]{\includegraphics[width=0.45\textwidth]{vecta/Fig/pp-z}
   \label{fig:pp-z}}
   \subfloat[]{\includegraphics[width=0.45\textwidth]{vecta/Fig/pp-z1}
   \label{fig:pp-z1}}\\
\caption{\wen{Field data example. (a) Raw field data. (b) First zoomed section (cyan). (c) Second zoomed section (green).}  }
\label{fig:pp-0,pp-z,pp-z1}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-fx-0}
   \label{fig:pp-fx-0}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-ortho-0}
   \label{fig:pp-ortho-0}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-orthon-0}
   \label{fig:pp-orthon-0}}\\
\subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-fx-z0}
   \label{fig:pp-fx-z}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-ortho-z0}
   \label{fig:pp-ortho-z}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-orthon-z0}
   \label{fig:pp-orthon-z}}\\ 
\subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-fx-z10}
   \label{fig:pp-fx-z1}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-ortho-z10}
   \label{fig:pp-ortho-z1}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-orthon-z10}
   \label{fig:pp-orthon-z1}}\\  
\caption{\wen{Field data example. Denoised data using (a) FX method, (b) stationary orthogonalization method, (c) non-stationary orthogonalization method. Zoomed sections using (d) and (g) FX method, (e) and (h) stationary orthogonalization method, (f) and (i) non-stationary orthogonalization method. The second row corresponds to the cyan frame box and the third row corresponds to the green frame box.}}
\label{fig:pp-fx-0,pp-ortho-0,pp-orthon-0,pp-fx-z,pp-ortho-z,pp-orthon-z,pp-fx-z1,pp-ortho-z1,pp-orthon-z1}
\end{figure}

%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-fx-n0}
%   \label{fig:pp-fx-n0}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-ortho-n0}
%   \label{fig:pp-ortho-n0}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-orthon-n0}
%   \label{fig:pp-orthon-n0}}  
%\caption{\wen{Field data example. Removed noise using (a) FX method, (b) stationary orthogonalization method, (c) non-stationary orthogonalization method.} }
%\label{fig:pp-fx-n0,pp-ortho-n0,pp-orthon-n0}
%\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-fx-n0}
   \label{fig:pp-fx-n0}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-ortho-n0}
   \label{fig:pp-ortho-n0}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-orthon-n0}
   \label{fig:pp-orthon-n0}}  \\
   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-fx-n-z}
   \label{fig:pp-fx-n-z}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-ortho-n-z}
   \label{fig:pp-ortho-n-z}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-orthon-n-z}
   \label{fig:pp-orthon-n-z}}\\ 
\subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-fx-n-z1}
   \label{fig:pp-fx-n-z1}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-ortho-n-z1}
   \label{fig:pp-ortho-n-z1}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-orthon-n-z1}
   \label{fig:pp-orthon-n-z1}}\\  
\caption{Field data example. Removed noise using (a) FX method, (b) stationary orthogonalization method, (c) non-stationary orthogonalization method. \wen{Zoomed sections using (d) and (g) FX method, (e) and (h) stationary orthogonalization method, (f) and (i) non-stationary orthogonalization method. The second row corresponds to the cyan frame box and the third row corresponds to the green frame box. The smaller pink frame box indicates the dramatic change of signal leakage before and after using the local orthogonalization methods.}}
\label{fig:pp-fx-n0,pp-ortho-n0,pp-orthon-n0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-rect10}
   \label{fig:pp-rect10}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-rect20}
   \label{fig:pp-rect20}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-rect30}
   \label{fig:pp-rect30}}\\
\subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-rect40}
   \label{fig:pp-rect40}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{vecta/Fig/pp-rect50}
   \label{fig:pp-rect50}} 
\caption{Field data example. Iteratively estimated non-stationary smoothing radius after (a) one, (b) two, (c) three, (d) four, and (e) five iterations.}
\label{fig:pp-rect10,pp-rect20,pp-rect30,pp-rect40,pp-rect50}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.45\textwidth]{field/Fig/f2-0}
   \label{fig:f2-0}}\\
   \subfloat[]{\includegraphics[width=0.45\textwidth]{field/Fig/f2-z1}
   \label{fig:f2-z1}}
\caption{\wen{Field data example. (a) Raw field data. (b) Zoomed section. }  }
\label{fig:f2-0,f2-z1}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.33\textwidth]{field/Fig/f2-fx-0}
   \label{fig:f2-fx-0}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{field/Fig/f2-ortho-0}
   \label{fig:f2-ortho-0}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{field/Fig/f2-orthon-0}
   \label{fig:f2-orthon-0}}\\
\subfloat[]{\includegraphics[width=0.33\textwidth]{field/Fig/f2-fx-n0}
   \label{fig:f2-fx-n0}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{field/Fig/f2-ortho-n0}
   \label{fig:f2-ortho-n0}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{field/Fig/f2-orthon-n0}
   \label{fig:f2-orthon-n0}}\\  
\caption{\wen{Field data example. Denoised data using (a) FX method, (b) stationary orthogonalization method, (c) non-stationary orthogonalization method. (d)-(f) Removed noise corresponding to (a)-(c), respectively.}}
\label{fig:f2-fx-0,f2-ortho-0,f2-orthon-0,f2-fx-n0,f2-ortho-n0,f2-orthon-n0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.33\textwidth]{field/Fig/f2-fx-z1-0}
   \label{fig:f2-fx-z1-0}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{field/Fig/f2-ortho-z1-0}
   \label{fig:f2-ortho-z1-0}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{field/Fig/f2-orthon-z1-0}
   \label{fig:f2-orthon-z1-0}}\\
\subfloat[]{\includegraphics[width=0.33\textwidth]{field/Fig/f2-fx-n-z1}
   \label{fig:f2-fx-n-z1}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{field/Fig/f2-ortho-n-z1}
   \label{fig:f2-ortho-n-z1}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{field/Fig/f2-orthon-n-z1}
   \label{fig:f2-orthon-n-z1}}\\  
\caption{\wen{Field data example. (a)-(f) Zoomed sections corresponding to the frame boxes  in Figure \ref{fig:f2-fx-0,f2-ortho-0,f2-orthon-0,f2-fx-n0,f2-ortho-n0,f2-orthon-n0}.}}
\label{fig:f2-fx-z1-0,f2-ortho-z1-0,f2-orthon-z1-0,f2-fx-n-z1,f2-ortho-n-z1,f2-orthon-n-z1}
\end{figure}

%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.33\textwidth]{field/Fig/f2-rect10}
%   \label{fig:f2-rect10}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{field/Fig/f2-rect20}
%   \label{fig:f2-rect20}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{field/Fig/f2-rect30}
%   \label{fig:f2-rect30}}\\
%\subfloat[]{\includegraphics[width=0.33\textwidth]{field/Fig/f2-rect40}
%   \label{fig:f2-rect40}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{field/Fig/f2-rect50}
%   \label{fig:f2-rect50}} 
%\caption{Field data example. Iteratively estimated non-stationary smoothing radius after (a) one iteration, (b) two iterations, (c) three iterations, (d) four iterations, and (e) five iterations.}
%\label{fig:f2-rect10,f2-rect20,f2-rect30,f2-rect40,f2-rect50}
%\end{figure}

%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.45\textwidth]{rna2/Fig/g-0}
%   \label{fig:g-0}}\\
%   \subfloat[]{\includegraphics[width=0.45\textwidth]{rna2/Fig/g-z-a}
%   \label{fig:g-z}}
%   \subfloat[]{\includegraphics[width=0.45\textwidth]{rna2/Fig/g-z-b}
%   \label{fig:g-z1}}\\
%\caption{\wen{Field data example. (a) Raw field data. (b) First zoomed section (frame box A). (c) Second zoomed section (frame box B).}}
%\label{fig:g-0,g-z,g-z1}
%\end{figure}
%
%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-rna-0}
%   \label{fig:g-rna-0}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-ortho-0}
%   \label{fig:g-ortho-0}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-orthon-0}
%   \label{fig:g-orthon-0}}\\
%\subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-rna-z-a}
%   \label{fig:g-rna-z-a}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-ortho-z-a0}
%   \label{fig:g-ortho-z-a0}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-orthon-z-a0}
%   \label{fig:g-orthon-z-a0}}\\ 
%\subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-rna-z-b}
%   \label{fig:g-rna-z-b}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-ortho-z-b0}
%   \label{fig:g-ortho-z-b0}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-orthon-z-b0}
%   \label{fig:g-orthon-z-b0}}\\  
%\caption{\wen{Field data example. Denoised data using (a) FX RNAR method, (b) stationary orthogonalization method, (c) non-stationary orthogonalization method. Zoomed sections using (d)\&(g) FX  RNAR method, (e)\&(h) stationary orthogonalization method, (f)\&(i) non-stationary orthogonalization method. The second row corresponds to the frame box A and the third row corresponds to the frame box B.}}
%\label{fig:g-rna-0,g-ortho-0,g-orthon-0,g-rna-z-a,g-ortho-z-a0,g-orthon-z-a0,g-rna-z-b,g-ortho-z-b0,g-orthon-z-b0}
%\end{figure}
%
%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-rna-n0}
%   \label{fig:g-rna-n0}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-ortho-n0}
%   \label{fig:g-ortho-n0}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-orthon-n0}
%   \label{fig:g-orthon-n0}}\\
%\subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-rna-n-z-a}
%   \label{fig:g-rna-n-z-a}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-ortho-n-z-a}
%   \label{fig:g-ortho-n-z-a}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-orthon-n-z-a}
%   \label{fig:g-orthon-n-z-a}}\\ 
%\subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-rna-n-z-b}
%   \label{fig:g-rna-n-z-b}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-ortho-n-z-b}
%   \label{fig:g-ortho-n-z-b}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-orthon-n-z-b}
%   \label{fig:g-orthon-n-z-b}}\\  
%\caption{\wen{Field data example. Removed noise using (a) FX RNAR method, (b) stationary orthogonalization method, (c) non-stationary orthogonalization method. Zoomed sections using (d)\&(g) FX  RNAR method, (e)\&(h) stationary orthogonalization method, (f)\&(i) non-stationary orthogonalization method. The second row corresponds to the frame box A and the third row corresponds to the frame box B.}}
%\label{fig:g-rna-n0,g-ortho-n0,g-orthon-n0,g-rna-n-z-a,g-ortho-n-z-a,g-orthon-n-z-a,g-rna-n-z-b,g-ortho-n-z-b,g-orthon-n-z-b}
%\end{figure}
%
%
%
%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.45\textwidth]{rna2/Fig/g-ortho-z-aa}
%   \label{fig:g-ortho-z-aa}}
%   \subfloat[]{\includegraphics[width=0.45\textwidth]{rna2/Fig/g-orthon-z-aa}
%   \label{fig:g-orthon-z-aa}}\\
%   \subfloat[]{\includegraphics[width=0.45\textwidth]{rna2/Fig/g-ortho-z-bb}
%   \label{fig:g-ortho-z-bb}}
%\subfloat[]{\includegraphics[width=0.45\textwidth]{rna2/Fig/g-orthon-z-bb}
%   \label{fig:g-orthon-z-bb}}
%\caption{\wen{Demonstration of the stability issue. Left column: zoomed result using stationary orthogonalization method (from Figures \ref{fig:g-ortho-z-a0} and \ref{fig:g-orthon-z-a0}). Right column: zoomed result using non-stationary orthogonalization method (from Figures \ref{fig:g-ortho-z-b0} and \ref{fig:g-orthon-z-b0}). Note the blank pixels caused due to a small smoothing radius.} }
%\label{fig:g-ortho-z-aa,g-orthon-z-aa,g-ortho-z-bb,g-orthon-z-bb}
%\end{figure}
%
%
%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-rect10}
%   \label{fig:g-rect10}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-rect20}
%   \label{fig:g-rect20}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-rect30}
%   \label{fig:g-rect30}}\\
%\subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-rect40}
%   \label{fig:g-rect40}}
%   \subfloat[]{\includegraphics[width=0.33\textwidth]{rna2/Fig/g-rect50}
%   \label{fig:g-rect50}} 
%\caption{Field data example. Iteratively estimated non-stationary smoothing radius after (a) one iteration, (b) two iterations, (c) three iterations, (d) four iterations, and (e) five iterations.}
%\label{fig:g-rect10,g-rect20,g-rect30,g-rect40,g-rect50}
%\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.5\textwidth]{teapot/Fig/tea}
   \label{fig:tea}}
\subfloat[]{\includegraphics[width=0.5\textwidth]{teapot/Fig/t-fxy}
   \label{fig:t-fxy}}\\
   \subfloat[]{\includegraphics[width=0.5\textwidth]{teapot/Fig/t-ortho}
   \label{fig:t-ortho}}
   \subfloat[]{\includegraphics[width=0.5\textwidth]{teapot/Fig/t-orthon}
   \label{fig:t-orthon}}\\
\caption{3D field data example. (a) Teapot Dome dataset. Denoised data using (b) FXY RNAR method, (c) stationary orthogonalization method, and (d) non-stationary orthogonalization method.}
\label{fig:tea,t-fxy,t-ortho,t-orthon}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.5\textwidth]{teapot/Fig/t-fxy-n0}
   \label{fig:t-fxy-n0}}
   \subfloat[]{\includegraphics[width=0.5\textwidth]{teapot/Fig/t-ortho-n0}
   \label{fig:t-ortho-n0}}\\
   \subfloat[]{\includegraphics[width=0.5\textwidth]{teapot/Fig/t-orthon-n0}
   \label{fig:t-orthon-n0}}
\caption{3D Teapot Dome data example. Removed noise using (a) FXY RNAR method, (b) stationary orthogonalization method, and (c) non-stationary orthogonalization method.}
\label{fig:t-fxy-n0,t-ortho-n0,t-orthon-n0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.32\textwidth]{teapot/Fig/slice-fxy-0}
   \label{fig:slice-fxy-0}}
   \subfloat[]{\includegraphics[width=0.32\textwidth]{teapot/Fig/slice-ortho-0}
   \label{fig:slice-ortho-0}}
   \subfloat[]{\includegraphics[width=0.32\textwidth]{teapot/Fig/slice-orthon-0}
   \label{fig:slice-orthon-0}} \\
\subfloat[]{\includegraphics[width=0.32\textwidth]{teapot/Fig/slice-fxy-z}
   \label{fig:slice-fxy-z}}
   \subfloat[]{\includegraphics[width=0.32\textwidth]{teapot/Fig/slice-ortho-z}
   \label{fig:slice-ortho-z}}
   \subfloat[]{\includegraphics[width=0.32\textwidth]{teapot/Fig/slice-orthon-z}
   \label{fig:slice-orthon-z}}\\
\caption{3D Teapot Dome data example. Comparison of the constant time slice (1 s) using (a) FXY RNAR method, (b) stationary orthogonalization method, and (c) non-stationary orthogonalization method. \new{(d)-(f) Zoomed comparison (highlighted by the frame boxes) of the top row.}}
\label{fig:slice-fxy-0,slice-ortho-0,slice-orthon-0,slice-fxy-z,slice-ortho-z,slice-orthon-z}
\end{figure}
}

\bibliographystyle{seg}
\bibliography{ortho}

\newpage
\listoffigures

### 2021-02-25 regi/paper.tex
add regi

\published{Geophysics, 86, no. XX, XX-XX, (2021)}

\title{Time-lapse image registration by high-resolution \\ time-shift scan}

\author{Xingye Liu\footnotemark[1], Xiaohong Chen\footnotemark[2], Min Bai\footnotemark[3], and Yangkang Chen\footnotemark[4]}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
%
%\author{Authors}

\ms{GEO-2021} %\ms{GJI-2019}

\address{
\footnotemark[1]
College of Geology and Environment\\
Xi’an University of Science and Technology\\
Xi’an, Shaanxi Province, China, 710054 \\
lwxwyh506673@126.com\\
\footnotemark[2]State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
\footnotemark[3]
Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
Yangtze University\\
Wuhan, Hubei Province, China, 430100 \\
\footnotemark[4]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
%yangkang.chen@zju.edu.cn \\
%Corresponding Author: Min Bai, baimin2016@126.com
%chenxh@cup.edu.cn \\
}

%\lefthead{Liu et al.}
\righthead{High-resolution time-shift scan}

\begin{abstract}
Seismic image registration is crucial for the joint interpretation of multi-vintage seismic images in time-lapse reservoir monitoring. Time-shift analysis is a commonly used method to estimate the warping function by creating a time-shift map, where the energy of each time-shift point in the 3D map indicates the probability of a correct registration. We propose a new method to obtain a high-resolution time-shift analysis spectrum, which can help both manual and automatic picking. The time-shift scan map is obtained by trying different local shifts and calculating the local similarity attributes between the shifted and reference images. We propose a high-resolution calculation of the time-shift scan map by applying the non-stationary model constraint in solving the local similarity attributes. The non-stationary model constraint ensures the time-shift scan map to be smooth in all physical dimensions, e.g., time, local shift, and space. In addition, it permits variable smoothing strength across the whole volume, which enables the high resolution of the calculated time-shift scan map. We use an automatic picking algorithm to demonstrate the accuracy of the high-resolution time-shift scan map and its positive influence on the  time-lapse image registration. Both synthetic (2D) and real (3D) time-lapse seismic images are used for demonstrating the better registration performance of the proposed method.
\end{abstract}

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}

%\lefthead{Liu et al.}
%\section{Keywords}
%key1,key2,key3
\maketitle

\section{Introduction}
Time-lapse seismic refers to the process of monitoring oil and gas reservoir performance by different seismic \dlo{information}\wen{data} obtained from repeated seismic \dlo{observation}\wen{observations} in the same work area at different \dlo{times}\wen{stages} \wen{\cite[]{lumley2001time,zhang2013time,zhang2014time}}. 
Because this method is usually carried out in the form of 3D observation, \dlo{that is to say}\wen{i.e.}, the same seismic observation system and \dlo{observation }parameters are used for more than two repeated 3D observations in different \dlo{time}\wen{stages} for the same exploration area,  \dlo{which is}\wen{it is} also called 4D seismic  \cite[]{Tucker2000time}. 
With the exploitation of oil and gas resources, underground fluid field, pressure field, \new{coherent and random noise,} and reservoir physical properties will change\dlo{, then}\wen{. Then,} \old{the seismic data collected in different periods are different}\new{the seismic data acquired at different periods is thus different}, i.e., the change of properties of underground medium and reservoir will be reflected in the time-lapse seismic data  \cite[]{hicks2016time-lapse}.
Therefore, \wen{the} time-lapse seismic response can represent the change of reservoir properties, \wen{which }then can be used as \dlo{the} effective  reservoir monitoring information.  Time-lapse seismic techniques have been widely applied in reservoir characterization to monitor and guide the management and adjustment of oil and gas fields, so as to  improve the recovery and development efficiency of oil and gas fields  \cite[]{landro2001discrimination}.

Theoretically, the static properties (such as structural and lithological properties) of the reservoir are eliminated after the subtraction of time-lapse seismic data, i.e., the difference between the two seismic data is the image of the dynamic fluid properties (such as fluid saturation, pressure, temperature, etc.) of the reservoir  \cite[]{grana2015bayesian}.
However,  the inconsistency of surface conditions, environment noise, source type, firing position or shooting mode, and different types of acquisition instruments will lead to different instrument noise and different spectrum characteristics. 
Moreover, it is impossible for the new seismic \wen{survey} to adopt the same acquisition parameters as the original one  \cite[]{Tucker2000time}. 
At the same time, the difference of observation system\dlo{, etc.,} will also bring \dlo{difficulty}\wen{difficulties} \dlo{to}\wen{in} comparing the two data volumes. 
\old{Besides}\new{In addition}, the difference \dlo{of}\wen{in} processing tools and parameters will also cause the difference \dlo{of}\wen{between} the two seismic \dlo{data}\wen{datasets}.
Hence, in practice, time-lapse seismic data may be acquired and processed in different manners, and it is difficult to ensure that all factors are completely consistent in the two acquisition and processing \wen{stages}. \dlo{In other words, inconsistency caused by acquisition and processing is inevitable. }All \dlo{of above}\wen{these} factors impact the \old{traveltime and amplitude}\new{traveltimes and amplitudes} of time-lapse seismic data. Thus, the task is to separate changes caused by \wen{the} reservoir itself and by other factors, and \wen{to} minimize the inconsistency caused by various non-geological factors, i.e., \wen{to }register the time-lapse seismic data.

Geophysicists have developed a wide range of techniques to register the time-lapse seismic data, \dlo{of}\wen{in} which time shifts estimation is one of the \dlo{the }\dlo{essential works}\wen{important methods}  \cite[]{bertrand2008detectability}. \wen{The} two most common methods for seismic image registration are local crosscorrelation \cite[]{hale2006fast} and dynamic time warping \cite[]{hale2013dynamic}.
\cite{nguyen2015a} \old{reviewed}\new{review} the processing of time-lapse seismic data, and \old{emphasized}\new{emphasize} the \dlo{signification}\wen{significance} of time shifts estimation.
Cross-equalization is a commonly used method that can estimate the time shifts and remove the differences between different seismic surveys \cite[]{ross1997time-lapse}. 
However, \cite{rickett2001cross} \old{pointed}\new{point} out that cross-equalization \dlo{needed}\wen{requires} additional processes, and \old{introduced}\new{introduce} a residual migration operator to estimate the time shifts and register time-lapse images.
\cite{huang2001seismic} \old{studied}\new{study} the method to correct the time shifts of time-lapse seismic data.
\cite{Alismaili2002Non} \old{proposed}\new{propose} a non-linear cross-equalization method based on artificial neural networks to improve the accuracy of estimated time shifts, and matched the time-lapse seismic images. 
\cite{vasco2004seismic} \old{analyzed}\new{analyze} the \dlo{time-lapse seismic amplitude changes}\wen{changes of time-lapse seismic amplitude} and suggested \wen{that} it should be estimated to improve the accuracy of reservoir monitoring.
\cite{gallop2011midpoint} \old{developed}\new{develop} a midpoint match filter to match baseline and monitor data, and \old{reduced}\new{reduce} the effect of noise. \wen{Applying timeshifts in 4D seismic data dates back to \cite{barkved20034d} and \cite{hatchell2003whole}.} \cite{bertrand2008detectability} \old{used}\new{use} a 4D tuning method to remove the \old{change of traveltimes}\new{traveltime changes}. 
\cite{hale2009a} \old{estimated}\new{estimate} the time displacements in time-lapse seismic images. 
\cite{bergmann2014timelapse} \old{proposed}\new{propose} a prestack crosscorrelations to \old{correct the static}\new{remove the time-shift} differences between two time-lapse seismic images and applied the method to a \old{filed}\new{field} data. \old{It is a data-driven approach to remove the  time shifts of  individual time-lapse data. }\cite{hatchell2019matching} \old{compared}\new{compare} the spectrum balancing and \dlo{conventional}\wen{traditional} \dlo{least square}\wen{least-squares} filters for estimating time shifts and matching the time-lapse seismic data, and analyzed their advantages and disadvantages. There are many other modern image registration techniques used in industrial/\dlo{commerical}\wen{commercial} applications, including \cite{williamson2007new}, and \cite{phillips2016seismic}; as well as promising recent developments using machine learning, including \cite{dramsch2019deep}.

However, \wen{most of} these mentioned methods directly estimated time shifts and matched the time-lapse seismic image.   \cite{ayeni2009optimized} \old{pointed}\new{point} out that the performance of these methods \dlo{were}\wen{was} limited by the stationary parameters and \old{could not assure to preserve the true amplitude}\new{cannot guarantee preservation of the true amplitude of the signal}\old{ of time-lapse seismic signals}. 
\cite{fomel2005a} used a \dlo{muti-step}\wen{multi-step} method to register seismic images by rapidly scanning the data.  The most important step is scanning the map to estimate the time shifts. The method can analyze the time shifts,  register the multicomponent images in the time domain, and provide the velocity \dlo{radio}\wen{ratio}. However, it \dlo{demands}\wen{requires} an initial interpretation \dlo{about}\wen{of} the geologic features in the depth domain, thus is not completely automatic.
Subsequently, \cite{fomel20094} \old{developed}\new{develop} an automatic time-lapse seismic images registration approach based on the local-similarity \cite[]{fomel2007local, yangkang2015ortho}, which \old{had intrigued some successful applications of this technology}\new{has inspired the application of this technology} to other geophysical data registration problems, including seismic-well ties \cite[]{bader2019missing} and image merging \cite[]{greer2018matching}. 
One of the advantages is that the method can detect an optimal registration from the monitor image to \wen{the} base image by scanning and matching their local similarity.  After calculating and scanning the local similarity attributes of the whole seismic image, the strongest similarity trend is picked, then the corresponding time shift is applied to achieve time-lapse seismic \dlo{images}\wen{image} registration. 
Through time-shift scan, the accuracy  is improved, which is helpful for fine dynamic characterization of reservoirs.
Besides, the estimated local time shift is meaningful to evaluate reservoir compaction, and \wen{can intuitively reflect the reservoir change \cite[]{hatchell2005measuring, rickett20074d}}.
Resolution of the map scan results will \dlo{impact}\wen{affect} the accuracy of the matching results. High-resolution scan results can better match the seismic images collected in different periods. 
In addition, scanning results with high resolution can provide \wen{a} more accurate estimated velocity ratio that is important to excavate changes of reservoirs.
\cite{ayeni2009optimized} \old{illustrated}\new{illustrate} the significance and superiority of map scan and match for time shift estimation, \dlo{and }proposed a local matching method based on the least-squares formulation\wen{,} and used \wen{an} evolutionary optimization algorithm to select the local parameters.
\cite{zhang2014scan} \old{pointed}\new{point} out time-shift scan can detect small \dlo{delay}\wen{delays} and improve the resolution of image registration.
\cite{decastro2016rapid} \old{presented}\new{present} a dual-channel scan approach to further  boost the performance of \wen{the} time-shift scan method, and \old{obtained}\new{obtain} \dlo{a }high resolution registration results.
\dlo{Therefor}\wen{Therefore}, time-shift scan methods with high resolution are beneficial for time-lapse seismic data registration, then enhance the accuracy of reservoir monitor.

In this paper, we propose a high-resolution time-shift scan method to improve the time-lapse image registration based on the general framework of \cite{fomel20094}. The image registration method in \cite{fomel20094} requires the calculation of local similarity between the reference and warped image. The local similarity is calculated by solving two inverse problems, where the accuracy and resolution of the model highly \dlo{depends}\wen{depend} on the smoothness constraint applied during the iterative inversion. A strong smoothing could cause over-smoothing of the model, i.e., local similarity, which further results in a time-shift scan map of too low resolution. A weak smoothing, however, could cause \dlo{the }instability and a less anti-noise ability during the inversion. Considering the contradiction in choosing an appropriate smoothing in the traditional method \cite[]{fomel20094}, we propose to apply a non-stationary smoothing constraint to the model, which ensures both the stability and \dlo{the }high resolution when calculating \wen{the} time-shift scan map. The non-stationary smoothing is applied in an efficient way and can utilize the \old{apriori}\new{a priori} information of the model, e.g., the probability distribution of the time-shift scan map, \new{and} signal/noise distribution\dlo{, etc}. The high-resolution time-shift scan map \old{is beneficial}\new{helps} \dlo{in reducing}\wen{to reduce} the uncertainty when picking the stretch curves from the map using either a manual or automatic way, and further will make the time-lapse images better matched.

We organize the paper as follows. We first introduce the time-shift scan method \wen{that was proposed in \cite{fomel20094}}, based on which we \dlo{apply}\wen{implement} the registration. Secondly, we introduce in detail the non-stationary method in calculating the time-shift scan map \wen{(the contribution of this paper)}. We use one carefully designed synthetic example and a 3D seismic dataset from multi-\dlo{stage}\wen{vintage} time-lapse seismic monitoring to demonstrate the performance of the proposed method. \old{Finally, we draw some key conclusions.}

\section{Theory}
\subsection{Time-shift scan}
Let $u_1(t,x)$ denote the reference image, e.g., seismic image before reservoir development, \wen{and} $u_2(t,x)$ denote the image to be registered, e.g., seismic image after reservoir development. \old{Assume}\new{Assuming} that $u_1(t,x)$ and $u_2(t,x)$ can be registered via a warping function $w(t)$, then
the goal is to solve the following optimization problem:
\wen{\begin{equation}
\label{eq:pro}
\arg \max_{w} \text{S}(u_1(t,x),u_2(w(t,x),x)),
\end{equation}}
where $\text{S}$ denotes a metric measuring the similarity between the two images. To solve the optimization problem in equation \ref{eq:pro}, we use a time-shift analysis method \cite[]{fomel20094}. First, we define the ratio between the warped time axis and the reference time axis as the relative stretch:
\begin{equation}
\label{eq:str}
\gamma(t,x)=\frac{w(t,x)}{t}.
\end{equation}
When $\gamma(t,x)>1$, it means stretching the time axis, and when $\gamma(t,x)<1$, it means squeezing the time axis. The local point is unchanged when $\gamma(t,x)=1$.

Then, we use a set of $\gamma$ values (e.g., starting $\gamma$: $\gamma_0=0.98$, interval of $\gamma$: $d\gamma=0.0004$, number of $\gamma$: $N_\gamma=101$), to squeeze and stretch the image:
\wen{\begin{equation}
\label{eq:gm}
\overline{u}_2(t,x,\gamma)=u_2(t\gamma,x),
\end{equation}}
where the right term is calculated by a \old{simple }linear interpolation scheme (the stretched time $t\gamma$ is not on \old{the}\new{a} regular \old{grids}\new{grid}) from the regular-grid function $u_2(t\gamma,x)$.

Next, we calculate the local similarity between $u_1(t,x)$ and \wen{$\overline{u}_2(t,x,\gamma_i)$} to get a time-shift map, where we can pick the peaks in the map to find the optimal stretching values $\gamma(t,x)$, either using a manual way like in traditional NMO-based velocity analysis or using an automatic way \cite[]{fomel20091}. The time-shift analysis approach is not limited in 2D, but is applicable to problems of any dimensions. For example, in 3D problems, the scalar $x$ becomes a vector $\mathbf{x}$ denoting two lateral directions.

\subsection{Non-stationary time-shift map calculation}
The local similarity between the reference image $u_1(t,x)$ and the warped image $u_2(t,x)$ can be calculated by
\begin{equation}
\label{eq:simi}
s(t,x)=\sqrt{s_1(t,x)s_2(t,x)},
\end{equation}
where $s_1(t,x)$ and $s_2(t,x)$ are calculated by solving
\begin{equation}
\label{eq:s1}
\min \sum_{t,x}\left(u_1(t,x)-s_1(t,x)u_2(t\gamma,x)\right),
\end{equation}
and
\begin{equation}
\label{eq:s2}
\min \sum_{t,x}\left(u_2(t\gamma,x)-s_2(t,x)u_1(t,x)\right).
\end{equation}
In a matrix-vector form, the solutions of equations \ref{eq:s1} and \ref{eq:s2} can be expressed as:
\new{\begin{align}
\label{eq:s11}
\mathbf{s}_1 &= \left[\lambda_1^2\mathbf{I} +\mathbf{T}(\mathbf{U}_2^T\mathbf{U}_2-\lambda_1^2\mathbf{I}) \right]^{-1}\mathbf{T}\mathbf{U_2}^T\mathbf{u}_1, \\
\label{eq:s22}
\mathbf{s}_2 &= \left[\lambda_2^2\mathbf{I} +\mathbf{T}(\mathbf{U}_1^T\mathbf{U}_1-\lambda_2^2\mathbf{I}) \right]^{-1}\mathbf{T}\mathbf{U_1}^T\mathbf{u}_2,
\end{align}}
\old{Here,}\new{where} $\mathbf{s}_1$ and $\mathbf{s}_2$ denote the vectors composed of $s_1(t,x)$ and $s_2(t,x)$, respectively\old{.}\new{;} $\mathbf{u}_1$ and $\mathbf{u}_2$ denote the vectors composed of $u_1(t,x)$ and $u_2(t\gamma,x)$, respectively\old{.}\new{;} $\mathbf{U}_1$ and $\mathbf{U}_2$ denote the diagonal matrices composed of vectors $\mathbf{u}_1$ and $\mathbf{u}_2$, respectively\old{.}\new{; and} $\mathbf{T}$ denotes a triangle smoothing operator. The strength of $\mathbf{T}$ is controlled by the smoothing \old{radius. The smoothing radius}\new{radius, which} greatly affects the smoothness and resolution in the calculated time-shift scan map. A larger smoothing radius will cause a low resolution, which \old{further }causes a \old{large}\new{larger} uncertainty when picking the optimal stretch curves. A smaller smoothing radius will make the inversions in equations \ref{eq:s11} and \ref{eq:s22} less stable and also make the time-shift scan less anti-noising.  In this paper, we propose a flexible non-stationary smoothing scheme, where we can design a temporally and spatially variable smoothing radius to better control the resolution and the stability when calculating the time-shift scan map.

We use a recursion-based method to apply the non-stationary smoothing. First, we consider the triangle smoother as the product of two rectangle smoothers in the Z-transform domain:
\begin{equation}
\label{eq:tri}
T(Z)=R(Z)R(Z),
\end{equation}
where $T(Z)$ and $R(Z)$ denotes the Z-transform formulas of the triangle and rectangle smoothing operators. The rectangle smoothing operator can be explicitly formulated as:
\wen{\begin{equation}
\label{eq:ri}
R(Z)=1+Z+Z^2+\cdots+Z^{N-1}=\frac{1-Z^N}{1-Z},
\end{equation}}
where $N$ denotes the smoothing radius for a 1D triangle smoother. Equation \ref{eq:ri} can be \old{splited}\new{split} into two parts: 
\begin{enumerate}
\item $1-Z^N$ corresponds to the recursion 
\wen{\begin{equation}
\label{eq:recur1}
y_n=x_n-x_{n-N}
\end{equation}}
\item $\frac{1}{1-Z}$ corresponds to the recursion 
\begin{equation}
\label{eq:recur2}
y_n=y_{n-1}+x_n
\end{equation}
\end{enumerate}
From equations \ref{eq:recur1} and \ref{eq:recur2}, it is clear that the triangle smoothing operations can be applied efficiently based on \old{the simple recursions}\new{recursion}. Equations \ref{eq:tri}-\ref{eq:recur2} describe a 1D triangle smoother. A 2D or 3D triangle smoother is equivalent to applying a 1D triangle smoother consecutively along each dimension. When the smoothing radius varies \old{with time and space locations}\new{in time and space}, it can be expressed as $N_t(t,x)$ or $N_x(t,x)$, which denote the smoothing radius along the $t$ or $x$ axis at position $(t,x)$\wen{, respectively}.

In the proposed non-stationary calculation of local similarity, the aforementioned nonstationary  triangle smoothing operator is taken as the shaping operator $\mathbf{T}$ in equations \ref{eq:s11} and \ref{eq:s22}. The iterative inversion procedures to solve equations  \ref{eq:s11} and \ref{eq:s22} need to enable a multi-dimensional non-stationary smoothing operator following the recursion-based implementation to constrain the model in the shaping regularization framework \cite[]{fomel2007shape}. The success of the non-stationary time-shift map calculation relies on \old{a}\new{the} proper design of the smoothing radius based on the \old{apriori}\new{a priori} information, e.g., the probability distribution of the time-shift scan map, \new{and} signal/noise distribution\old{, etc}. For example, we can use the initially generated time-scan map as the reference to define a non-stationary map following the energy distribution of the initial result \cite[]{yangkang2015svmf}. It is also possible to estimate the non-stationary smoothing radius automatically, e.g., following the method developed in \cite{greer2018matching}. In the worst case, when the smoothing radius $N_{t/x}(t,x)$ is a constant, the proposed non-stationary method downgrades to the traditional method. If we can \dlo{extracts}\wen{extract} some \dlo{a priori}\old{apriori}\new{a priori} information of the model (time-shift scan map), e.g., using an initial estimation, we can design a radius map that better \dlo{compromise}\wen{compromises} the resolution and stability of the model to facilitate a higher resolution for picking.

\section{Examples}
\subsection{2D synthetic example}
\dlo{For better distinguishing between different methods}\wen{For comparing the different methods}, we use ``traditional'' \new{and ``proposed"} to refer to the method developed in \cite{fomel20094}, and \old{the ``proposed  method'' to refer to the new method}\new{herein, respectively}. The 2D synthetic example is plotted in Figure \ref{fig:time1,mdif-time2}\new{, which is similar to \cite{fomel20094}}. Figure \ref{fig:time1} \old{plots}\new{presents} the synthetic velocity model\old{. There are}\new{, which has} several horizontal layers and a narrow curving layer \old{in this model. The narrow curving layer corresponds to}\new{corresponding to} \old{an oil\&gas reservoir}\new{a petroleum reservoir}.  Figure  \ref{fig:mdif-time2} plots the velocity perturbation due to the reservoir development. \old{This synthetic model is close to the synthetic model demonstrated in } The synthetic seismic image is generated using a convolutional %reflectivity 
modeling method. The synthetic seismic image before reservoir development is plotted in Figure \ref{fig:c-seis-time1}. Figure \ref{fig:c-seis-time2} plots the synthetic seismic image after reservoir development, taking the velocity perturbation into consideration. Figure \ref{fig:c-dif-time2} \old{plots}\new{presents} the time-lapse difference image before registration by directly subtracting Figure \ref{fig:c-seis-time2} from Figure \ref{fig:c-seis-time1}. In Figure \ref{fig:c-dif-time2}, the two horizontal reflectors below the reservoir area are obviously the artifacts of the time-lapse difference.

By applying different stretches to the seismic image after reservoir development and \dlo{calculate}\wen{calculating} its local similarity with the reference image, we can obtain the time-shift scan map as shown in Figure \ref{fig:c-scan-time2-0}. Here, we use a constant smoothing radius of 25 samples to calculate the scan map. Then, we apply the proposed high-resolution method with non-stationary smoothing radius to calculate the scan map, which is plotted in Figure \ref{fig:c-scan-time2-n0}. The non-stationary smoothing radius is plotted in Figure \ref{fig:c-rect1}. It is \wen{obvious} that the proposed method obtains \dlo{an obviously}\wen{a} higher resolution along the stretch axis of the scan map, which facilitates a more accurate picking of the optimal stretch value. From the non-stationary smoothing radius distribution, we can see that the radius varies from the \dlo{minimum}\wen{minimal} 20 samples to the \dlo{maximum}\wen{maximal} 25 samples. Here, we use a simple example to show that even we use a simple binary non-stationary smoothing radius map, we can get a significantly better result. The threshold used to generate this binary smoothing radius map can be any small value (e.g., 0.05 in this example) that can reasonably separate the main energy clusters out in the initially generated time-scan map. However, \old{how to design a more appropriate }\new{designing an optimal} non-stationary smoothing radius map remains \dlo{as }an open question. The proposed method also offers us the freedom to choose a non-stationary smoothing radius map based on some \old{apriori}\new{a priori} information, e.g., according to the heterogeneity of the data. We use an automatic picking method introduced in \cite{fomel20091} to \old{pick}\new{determine} the optimal stretch value that corresponds to the highest value in the scan map. The picked stretch maps corresponding to the traditional and the high-resolution methods are plotted in Figure \ref{fig:c-pick-time2-0} and \ref{fig:c-pick-time2-n-0}, respectively. The closer to green, the \dlo{smallest}\wen{smaller} \new{the} stretch, \dlo{meaning}\wen{indicating} \old{less}\new{a poorer} registration. The closer to blue (squeezing) or red (stretching), the \old{larger level of registration}\new{more improved the registration}. From Figure \ref{fig:c-pick-time2-0,c-pick-time2-n-0}, it is clear that the traditional method causes more blue areas on the left and right parts of the maps. Note that the \old{more or less}\new{more-or-less} negative and positive polarities on the left and right sides in both Figure \ref{fig:c-pick-time2-0} and \ref{fig:c-pick-time2-n-0} are unavoidable using the automatic picking method introduced in \cite{fomel20091}. In addition, because we cannot explicitly express the time shift/stretch value in terms of the true velocity model or reflectivity model, we do not plot the ground-truth stretch map. But it is still straightforward to conclude that the stretch map obtained using the new method is more plausible than that using the traditional method.  However, from the ground truth plotted in Figure \ref{fig:c-seis-time1,c-seis-time2,c-dif-time2}, it is clear that the left and right parts of the images should have no registration stretch, which indicates that the traditional method may cause registration \dlo{erros}\wen{errors} on the left and right parts of the time-lapse difference image. The registration results, i.e., time-lapse difference images, of the two methods are plotted in Figure \ref{fig:c-long-dif,c-long-dif-n}. From the difference images, it is obvious that the traditional \dlo{methods}\wen{method} causes some errors (as highlighted by the \dlo{labelled}\wen{labeled} arrows) on the left, right, and below areas of the reservoir region. The proposed method, however, causes negligible registration \dlo{error}\wen{errors}.

To test the effect of noise \dlo{to}\wen{on} the time-shift analysis, we add some \new{additive random} noise into the synthetic seismic images of two time-lapse stages, as seen in Figure \ref{fig:seis-time1} and \ref{fig:seis-time2}. The \old{SNRs}\new{S/N}, as defined in \cite{yangkang2015ortho}, of Figure \ref{fig:seis-time1} and \ref{fig:seis-time2} are -3.25 dB and -2.91 dB, respectively. The difference image calculated by direct subtraction is plotted in Figure \ref{fig:dif-time2}. In this case, when calculating the time-shift scan map, to ensure \dlo{a }stable and anti-noise performance, we need to use a relatively larger smoothing radius, e.g., 30 samples along \wen{the} time axis, 8 samples along the $\gamma$ axis, 12 samples along the space axis. The resulted time-shift scan is shown in Figure \ref{fig:scan-time2}, which has a low resolution because of the over-smoothing. If we use a \dlo{relatively }smaller smoothing radius, the result could be highly unstable and seriously affected by noise. In  Figure \ref{fig:scan-time22}, we show a result using a smaller smoothing radius, e.g., \old{10}\new{ten} samples along the time axis, \old{2}\new{two} samples along the $\gamma$ axis, \old{4}\new{and four} samples along the space axis. It is clear that this result is heavily affected by the noise and is not acceptable for picking the optimal stretch map $\gamma(t,x)$. In Figure \ref{fig:scan-time2-n}, we show the high-resolution result using the proposed method, where \dlo{we can have a}\wen{we observe a} clean and high-resolution time-shift scan map. It is obvious that the result in Figure \ref{fig:scan-time2-n} is much more reliable for picking. The non-stationary smoothing radius we use to obtain the high-resolution result is plotted in Figure \ref{fig:rect1}. Note that here we only plot the non-stationary smoothing radius along the time axis. The proposed method also requires the smoothing radius along the $\gamma$ and space axes. In this example, we calculate the smoothing radius map by treating the result from the \dlo{conventional}\wen{traditional} method (with a relatively larger smoothing radius) as the \dlo{a priori}\old{apriori}\new{a priori} information, and set a smaller radius for smaller values in the initial scan map and a larger radius for larger values in the initial scan map. We select a relative stretch gather at the location of the 55th trace for comparing the detailed picking performance. \old{Figure \ref{fig:scan-time-test,scan-time-test-n} shows the comparison between the traditional (left) and the proposed (right) methods.}\new{Figure \ref{fig:scan-time-test} and \ref{fig:scan-time-test-n} show the comparison between the traditional and the proposed methods.} The \old{strings}\new{curves} on the scan map denote the automatically picked stretch \old{curve}\new{function}. Comparing with the ground truth in Figure \ref{fig:time1,mdif-time2}, we conclude that the \old{result in Figure \ref{fig:scan-time-test-n} is correct and the result in Figure \ref{fig:scan-time-test} is wrong.}\new{results in Figure \ref{fig:scan-time-test-n} and \ref{fig:scan-time-test} are correct and wrong, respectively.} The picked stretch maps corresponding to the traditional and the high-resolution methods are plotted in Figure \ref{fig:pick-time2} and \ref{fig:pick-time2-n}, respectively. In Figure \ref{fig:pick-time2}, it is clear that there is a vertical red anomaly around the 35th trace, which is obviously a wrong picked stretch (compared with the ground truth in Figure \ref{fig:time1,mdif-time2}). Using the picked stretch map based on the two methods, we can do the registration and obtain the results in Figure \ref{fig:long-dif,long-dif-n}. It is clear that the difference image obtained from the traditional method causes some artifacts below the reservoir layer and around the 35th traces where we observe the stretch anomaly in Figure \ref{fig:pick-time2,pick-time2-n}. \new{To quantitatively compare the difference between two methods, we calculate the S/N \cite[]{yangkang2015ortho} of the registered result using different methods. Here, the registered section is compared with the ground truth solution to evaluate the performance. For the clean data example, the S/N of the results using the traditional and proposed method are 19.02 dB and 25.25 dB, respectively. For the noisy data, the S/N of the results using the traditional and proposed method are -5.01 dB and -4.88 dB, respectively. It is clear that the proposed method obtains higher registration accuracy.}

\subsection{3D real data example}
Next, we apply the proposed method to a set of 3D seismic images that are recorded from steam-flood monitoring in the Duri field \cite[]{lumley19954,lumley1995seismic}. There are six images at different stages of the steam-flood monitoring project, i.e., before the monitoring, after \old{2}\new{two} months, \old{5}\new{five} months, \old{9}\new{nine} months, 13 months, and 19 months. The six seismic images (extracted 2D sections) are plotted in Figure \ref{fig:duri-slice}. Because of the steam-flood process, both shallow layers and reservoir properties are strongly affected. The time-shift scan maps (for registering the reference image and the image after a \old{2-month}\new{two-month} monitoring period) using the traditional and the proposed high-resolution methods are compared in Figure \ref{fig:scan1,scann1}. It is clear that the time-shift scan map of the proposed method (Figure \ref{fig:scann1}) is cleaner and has a higher resolution than that of the traditional method (Figure \ref{fig:scan1}). \new{Here, the higher resolution means that the energy clusters are more focused and appear to be sparser in the time-shift scan map. Although the 4D differencing noise can also appear as ``higher resolution", due to the smoothing applied when calculating the time-shift scan map, the noise can barely contribute to the energy clusters in the map.} The automatically picked stretch curves in different locations are plotted in Figure \ref{fig:pick1,pickn1}. \old{Compare the top and bottom panels in Figure \ref{fig:pick1,pickn1}}\new{Comparing the panels in Figure \ref{fig:pick1} and \ref{fig:pickn1}}, it is clear that the two methods are more similar in the shallow area, i.e., exhibiting a ``stretching'' pattern, but differ greatly in the deep area. The stretch map on the bottom seems to more consistent in the deep part, i.e., exhibiting a steadily ``squeezing'' pattern, while the stretch map on the top \dlo{are}\wen{is} much irregular in the deep part. The stretch map from the proposed method, however, is more consistent with \wen{the} physical process in the steam-flood monitoring, i.e., decreased velocity in the shallow area makes the seismic events ``collapse'' (stretching) and the increased velocity in the reservoir area makes the seismic events ``stand up'' (squeezing).  \old{Figure \ref{fig:duri-warp,duri-warp-n} compares the warped data using the traditional (top) and the proposed (bottom) methods.}\new{Figure \ref{fig:duri-warp} and \ref{fig:duri-warp-n} compare the warped data using the traditional and the proposed methods.} Although the registration using the proposed method makes the seismic events better aligned in different monitoring stages, the proposed method makes the events even better matched. For example, the labelled arrows in Figure \ref{fig:duri-warp,duri-warp-n} point out an area where the registration is significantly improved by the proposed method. \old{Figure \ref{fig:duri-dif,duri-dif-n} compares the time-lapse difference images in different stages using the  traditional (top) and the proposed (bottom) methods.}\new{Figure \ref{fig:duri-dif} and \ref{fig:duri-dif-n} compare the time-lapse difference images in different stages using the  traditional and the proposed methods.} It is clear that both methods obtain \old{very}\new{a} good registration in the shallow part, but the proposed method is \old{much }more successful in registering the deep part of these images, i.e., causing significantly \old{less}\new{fewer} difference artifacts below the reservoir layers.  The \old{much-}reduced difference artifacts using the proposed method are highlighted by the white arrows in Figure \ref{fig:duri-dif,duri-dif-n}. To quantitatively compare the difference between two methods, we calculate the root mean squares (RMS) of the difference images at the locations of the arrows. The RMS of the difference images using the traditional method after two months, five months, nine months, 13 months, and 19 months are 1.45, 1.88, 2.30, 1.80, 1.83, respectively, while the RMS of the difference images using the proposed method after two months, five months, nine months, 13 months, and 19 months are 1.42, 1.68, 2.09, 1.83, 1.80, respectively. The RMS of the difference images using the proposed method is generally smaller than using the traditional method, indicating a better registration.

%\section{Discussions}

\section{Conclusions}
The time-shift analysis is an effective way \dlo{in}\wen{of} estimating the local shift for optimal \dlo{time-lase}\wen{time-lapse} image registration. The high resolution of the time-shift scan map is crucial for \old{the accurate estimation of}\new{accurately estimating} the warping function, especially when the seismic images contain strong random noise. We have proposed a useful method for obtaining a high-resolution time-shift scan map by modifying the inversion-based local similarity calculation during the registration process. The local similarity attribute is calculated iteratively by applying a model-driven non-stationary smoothing operator, which ensures a high-resolution time-shift scan map that facilitates \old{an }accurate time-shift scan. The non-stationary smoothing operator not only ensures the model in the inverse problem \old{to}\new{will} be smooth across the whole physical domain, but also maintains the heterogeneity of the model that is related \dlo{with}\wen{to} the high resolution of the final scan map. Synthetic examples show that the proposed method can obtain a more accurate time-shift scan map when there is \dlo{strong}\wen{stronger} background noise. The high-resolution time-shift scan map can significantly \dlo{improves}\wen{improve} the registration performance, i.e., causing \dlo{less}\wen{fewer} artifacts in the difference image. The real 3D time-lapse image registration example further validates the practical potential of the proposed method.

\section{DATA AND MATERIALS AVAILABILITY}
Data associated with this research are available and can be obtained by contacting the corresponding author.

\section{Acknowledgements}
We would like to thank Mason Phillips and two anonymous reviewers for constructive suggestions.

%\inputdir{test}
%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
%\multiplot{2}{test1,test2}{width=0.45\textwidth}{(a) Caption a. (b) Caption b.}

\inputdir{long}
\multiplot{2}{time1,mdif-time2}{width=0.45\textwidth}{Synthetic test. (a) \old{Velocity}\new{P-wave velocity} model before registration. (b) \old{Velocity}\new{P-wave velocity} perturbation due to the reservoir development. }

\inputdir{longc}
\multiplot{3}{c-seis-time1,c-seis-time2,c-dif-time2}{width=0.45\textwidth}{\old{Clean data test. }(a) Seismic image before reservoir development. (b) Seismic image after reservoir development. (c) Difference image before registration.}

\multiplot{3}{c-scan-time2-0,c-scan-time2-n0,c-rect1}{width=0.45\textwidth}{\old{Clean data test. }Time-shift scan map using \old{(a) the}\new{the (a)} traditional \old{method }and (b) \old{the }high-resolution \old{method}\new{methods}. (c) Smoothing radius distribution used to obtain (b).  }

\multiplot{2}{c-pick-time2-0,c-pick-time2-n-0}{width=0.45\textwidth}{\old{Clean data test. }Picked time shifts using \old{(a) the}\new{the (a)} traditional method and (b) \wen{the} high-resolution method.}

\multiplot{2}{c-long-dif,c-long-dif-n}{width=0.45\textwidth}{\old{Clean data test. }Time-lapse difference images using \old{(a) the}\new{the (a)} traditional picking \old{method }and (b) \old{the }high-resolution picking \old{method}\new{methods}.}

\inputdir{long}

\multiplot{3}{seis-time1,seis-time2,dif-time2}{width=0.45\textwidth}{Noisy data test. (a) Seismic image before reservoir development. (b) Seismic image after reservoir development. (c) Difference image before registration.}

\multiplot{4}{scan-time2,scan-time22,scan-time2-n,rect1}{width=0.45\textwidth}{Time-shift scan maps using (a)  \wen{the} \dlo{conventional}\wen{traditional} method with a relatively larger smoothing radius, (b)  \wen{the} \dlo{conventional}\wen{traditional} method with a relatively smaller smoothing radius, and (c) high-resolution method. (d) Smoothing radius distribution used to obtain (c). Note that the time-shift scan map in (b) is not considered acceptable.}

\multiplot{2}{scan-time-test,scan-time-test-n}{width=0.45\textwidth}{Picking comparison for one relative stretch gather at the location of the 55th trace using (a)  the traditional \old{method }and (b)  the high-resolution \old{method}\new{methods}. The blue \old{strings}\new{curves} denote the automatically picked relative stretch curves. Comparing the picking results with the ground truth in Figure \ref{fig:time1,mdif-time2}, we confirm that (b) is accurate and (a) is wrong. }

\multiplot{2}{pick-time2,pick-time2-n}{width=0.45\textwidth}{Picked time shifts using (a) \wen{the}  \dlo{conventional}\wen{traditional} method and (b) \wen{the}  high-resolution method.}

\multiplot{2}{long-dif,long-dif-n}{width=0.45\textwidth}{Time-lapse difference images using (a) the traditional \old{picking method }and (b) \wen{the}  high-resolution picking \old{method}\new{methods}.}

\inputdir{duri}
\plot{duri-slice}{width=0.8\textwidth}{Stacked data in different time-lapse stages. }
\multiplot{2}{scan1,scann1}{width=0.6\textwidth}{Time-shift scan maps (after a \old{2}\new{two}-month period) using \old{(a) the}\new{the (a)} traditional \old{method }and (b) \old{the }high-resolution \old{method}\new{methods}.}

\multiplot{2}{pick1,pickn1}{width=0.7\textwidth}{Picked time shifts (after a \old{2}\new{two}-month period) using \old{(a) the}\new{the (a)} traditional \old{method }and (b) \old{the }high-resolution \old{method}\new{methods}.}

\multiplot{2}{duri-warp,duri-warp-n}{width=0.8\textwidth}{Warped data using \old{(a) the}\new{the (a)} traditional \old{method }and (b) \old{the }high-resolution \old{method}\new{methods}.}

\multiplot{2}{duri-dif,duri-dif-n}{width=0.8\textwidth}{Time-lapse difference images using \old{(a) the}\new{the (a)} traditional \old{method }and (b) \old{the }high-resolution \old{method}\new{methods}.}

\bibliographystyle{seg}
\bibliography{regi}

### 2021-02-25 tf/paper.tex
add tf

\published{Geophysics, 86, no. XX, XX-XX, (2021)}

\title{Non-stationary local time-frequency transform}
\author{Yangkang Chen}

\ms{GEO-2021} %\ms{GJI-2019}

\address{
Key Laboratory of Geoscience Big Data and Deep Resource of Zhejiang Province\\
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
chenyk2016@gmail.com
}

\righthead{Non-stationary LTFT}

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}

\begin{abstract}
Time-frequency analysis is a fundamental approach to many seismic problems. Time-frequency decomposition transforms input seismic data from the time domain to the time-frequency domain, offering a new dimension to probe the hidden information inside the data. Considering the non-stationary nature of seismic data, time-frequency spectra can be obtained by applying a local time-frequency transform (LTFT) method, which matches the input data by fitting the Fourier basis with non-stationary Fourier coefficients in the shaping regularization framework. The key part in the LTFT is the temporal smoother with a fixed smoothing radius that guarantees the stability of the non-stationary least-squares fitting.  We propose a new LTFT method to \old{deal with}\new{handle} the non-stationarity in all time, frequency, and space (X and Y) directions of the input seismic data by extending the fixed-radius temporal smoothing to non-stationary smoothing with variable radius in all physical dimensions. The resulting time-frequency transform is referred to as the non-stationary LTFT method, which could significantly increase the resolution and anti-noise ability of time-frequency \dlo{transform}\wen{transformation}. There are two meanings of the non-stationarity, i.e., coping with the non-stationarity in the data by the local time-frequency transform and dealing with the non-stationarity in the model by the non-stationary smoothing. We demonstrate the performance of the proposed non-stationary LTFT method in several standard seismic applications via both synthetic and field datasets, e.g., arrival picking, quality factor estimation, low-frequency shadow detection, channel detection, multi-component data registration, and benchmark the results with the traditional stationary LTFT method.
\end{abstract}

%\section{Keywords}
%key1,key2,key3

\maketitle
\section{Introduction}
\dlo{Time-frequency transform plays an important role in analyzing non-stationary variations of frequency contents in seismic data, which could reveal significant hidden information of the data beyond the observation ability in time domain}\wen{The time-frequency transform plays an important role in analyzing non-stationary variations of frequency content in seismic data, which could reveal significant hidden information,  beyond the observation ability within the time domain} \cite[]{tary2014spectral}. In the past decades, many classic time-frequency analysis methods have been developed for achieving different purposes. The short-time Fourier transform (STFT) method \cite[]{allen1977unified} applies a short-time window along the time series to be analyzed and conducts many Fourier transforms in the time windows to create a localized Fourier analysis for each data point, resulting in a 2D time-frequency map showing the variations of frequency content in both time and frequency. The continuous wavelet transform (CWT) \cite[]{rioul1992fast} is another widely used method to calculate \dlo{the}\wen{a} time-frequency map. Instead of the Fourier basis functions, CWT uses different mother wavelets as the basis functions to match the input data and creates a 2D scale-time spectral map, where the scale axis can be further transformed into a frequency axis. When the time window is chosen as a Gaussian window, the STFT method is developed into a Gabor transform. Considering the \old{contradiction}\new{ambiguity} between window scales and resolution, \dlo{i.e., a larger window could decrease the resolution for high-frequency contents but increase the ability in analyzing low-frequency contents. The}\wen{the} Stockwell transform (ST) \cite[]{stockwell1996localization,zixiang2017bgs} varies time window length for conducting Fourier analysis in different frequency bands. There are also many other classic algorithms which are not used as commonly as the aforementioned methods, e.g., Wigner-Ville distribution \cite[]{boashash1987efficient}, matching pursuit \cite[]{mallat1993matching}, basis pursuit \cite[]{chen2001atomic}, short-time autoregression \cite[]{burg1972relationship} methods.

One of the most important purposes of conducting the time-frequency transform is to locate or separate different components of the data in the time-frequency domain, i.e., obtaining \dlo{a }higher resolution \dlo{in the }spectra.  Analyzing the frequency contents based on a windowing strategy\dlo{, e.g., in those aforementioned classic methods,} has its inherent weakness \wen{\cite[]{tary2014spectral}}. Although the ST transform can relieve the contradiction between resolution and accuracy, all the window-based methods still suffer \wen{from} this problem. In other words, when a larger window is used, it tends to \dlo{decrease}\wen{increase} the frequency resolution \wen{but decreases the time resolution}\dlo{ or widen the main lobe of the dominant frequency}; when a smaller window is used, it better characterizes the non-stationarity in time but widens \wen{the} main lobe of the dominant frequency, leading to a decreased frequency resolution. To solve this problem, several relatively new methods have been developed based on the empirical mode decomposition (EMD) \cite[]{huangemd} and the synchrosqueezing technique \cite[]{daubechies2011}. In the EMD based method, the input data \old{is}\new{are} first decomposed into several modes, also known as intrinsic mode functions (IMF), each with a distinct oscillating frequency. The method is then combined with the Hilbert transform to extract the frequency contents and then to obtain a 2D time-frequency representation. The EMD method, however, suffers from the mode-mixing problem, meaning that different IMFs could share the same frequency \old{contents}\new{content}. \dlo{Then, a}\wen{A} number of variants of EMD are used to \dlo{conquer}\wen{mitigate} the mode-mixing problem, e.g., the ensemble empirical mode decomposition (EEMD) \cite[]{eemd}, the complete ensemble empirical mode decomposition (CEEMD) \wen{methods} \cite[]{torres2011complete}, and the improved CEEMD \cite[]{colominas2014improved}. Many EMD-like decomposition methods are also developed to substitute EMD to obtain better time-frequency spectra while maintaining the high-resolution merits of EMD, e.g., the empirical wavelet transform \cite[]{liuwei2016ewt,liuwei2019ewt}, variational mode decomposition (VMD) \cite[]{vmd2014,liuwei2016vmd,liuwei2018tgrs}, non-stationary autoregression decomposition \cite[]{fomel20132,guoning2018} \wen{methods}. While those EMD variants cannot be well controlled due to the lack of theoretical foundation, other EMD-like decompositions are mostly mathematically supported.  The synchrosqueezing wavelet transform (SSWT) \cite[]{daubechies2011,mostafa2016geo,mostafa2017geo} is another way to obtain a high resolution in the time-frequency map by narrowing the main lobe of the spectra in both time and frequency directions based on the continuous wavelet transform framework.

\dlo{In a different way to}\wen{To} avoid the windowing strategy, \cite{liuyang2012} developed an invertible local time-frequency transform (LTFT) which is based on matching the input data by the Fourier basis in an inverse problem framework. The Fourier coefficients are \dlo{enforced}\wen{forced} to be time-variant \old{in order }to obtain a local representation of the Fourier basis functions, thereby achieving a local time-frequency analysis\old{ of the} data. The windowing strategy to regularize the non-stationary Fourier coefficients is effectively replaced with smoothing during inversion based on the shaping regularization framework.  In \cite{liuyang2012}, the smoothing is applied in the time direction to stabilize the inversion, where the smoothing radius is fixed, assuming that the model (i.e., time-frequency spectra) behavior is stationary along the time direction. However, a high-resolution time-frequency representation should be non-stationary in all time, frequency, and space dimensions.

In this paper, we further develop a non-stationary LTFT method, where we can apply smoothness constraints in all physical dimensions. Considering the heterogeneous \old{feature}\new{nature} of the model domain, the smoothing is applied in a non-stationary way, \dlo{i.e.,}\wen{thereby} ensuring a model-dependent pointwise variable smoothing radius in the time-frequency maps (for 2D) and cubes (for 3D). The non-stationary smoothing constraint ensures a significantly higher resolution and anti-noise ability of the LTFT method. Besides, the design of a smoothing radius in different physical dimensions offers great flexibility in constraining the model behavior according to any \dlo{a priori}\wen{a-priori} information. In the proposed non-stationary LTFT method, \dlo{there are two-fold meanings of the non-stationarity}\wen{we consider both data and model non-stationarity}. The non-stationary Fourier coefficients\dlo{, also}\wen{ as also used} in the traditional LTFT method, offers a way to characterize the non-stationarity in the data domain \wen{by non-stationary regression}, while the non-stationary smoothing offers a scheme to constrain the non-stationarity of the model domain, \dlo{which is preferred in obtaining the high resolution to locate}\wen{to obtain a high resolution for separating} different components.

We organize the paper as \old{follows: we first}\new{follows. First, we} introduce the principle of the LTFT framework and then extend \dlo{the traditional LTFT method}\wen{it} to its non-stationary version. \dlo{We focus on the next part, i.e., using}\wen{Then, we introduce} a variety of examples to demonstrate the potential of the proposed non-stationary LTFT method in a number of seismic applications, including (but not limited to) seismic phase arrival picking, quality factor estimation, low-frequency shadow detection, channel detection, and multi-component data registration. Finally, we draw some conclusions according to the findings in the paper.

\section{Method}
\wen{\subsection{Local time-frequency transform (LTFT)}}
The LTFT uses the Fourier basis functions to represent the input data. An arbitrary continuous signal $d(t), t\in[0,T]$, can be represented using the Fourier series as follows:
\begin{equation}
\label{eq:fs}
d(t) = \frac{a_0}{2} + \sum_{n=1}^{N}\left(a_n\cos(2\pi nt/T) + b_n\sin(2\pi nt/T) \right),
\end{equation}
where $N$ denotes the number of frequency components. Theoretically, $N$ should be large enough to minimize the mismatch between $d(t)$ and the Fourier series\dlo{.}\wen{, and} $a_n$ and $b_n$ are two Fourier coefficients.

Equation \ref{eq:fs} can also be expressed \dlo{briefly }as:
\begin{equation}
\label{eq:fs2}
d(t) = \sum_{n=0}^{N} \mathbf{b}(t,n)\mathbf{a}(n),
\end{equation}
where
\wen{
\begin{equation}
\label{eq:Bn}
\mathbf{b}(t,n)=\left\{\begin{array}{ll}
\left[\begin{array}{cc}
\cos(2\pi nt/T) & \sin(2\pi nt/T)
\end{array}\right], & n\ge 1, \\
\left[\begin{array}{cc}
1/2 & 0
\end{array}\right], & n = 0,
\end{array} \right.
\end{equation}}
and
\begin{equation}
\label{eq:Mn}
\mathbf{a}(n)=\left[\begin{array}{c}
a_n \\
b_n
\end{array}\right].
\end{equation}
Equation \ref{eq:fs2} refers to a stationary regression with the regression coefficients being $\mathbf{a}(n)$. The fixed regression coefficients along the time axis $\mathbf{a}(n)$ mean that equation \ref{eq:fs2} seeks a global fitting of the Fourier basis functions, i.e., equal to a Fourier transform. To ensure a local characterization in terms of the Fourier basis functions, equation \ref{eq:fs2} can be expressed in a non-stationary autoregression \wen{form} as follows:
\begin{equation}
\label{eq:fs3}
d(t) = \sum_{n=0}^{N} \mathbf{b}(t,n)\mathbf{a}(t,n),
\end{equation}
where $\mathbf{a}(t,n)$ denotes the locally variable regression (or Fourier) coefficients. Solving equation \ref{eq:fs3} is much more challenging than \dlo{that in}\wen{solving} equation \ref{eq:fs2} since many more non-stationary coefficients need to be solved based on the following least-squares formula:
\wen{\begin{equation}
\label{eq:fs4}
\min_{\mathbf{a}(t,n)} \sum_{t} \left( d(t) - \sum_{n=0}^{N} \mathbf{b}(t,n)\mathbf{a}(t,n) \right)^2,
\end{equation}}
\wen{where $\mathbf{a}(t,n)=[a_n(t),b_n(t)]^T$.} Reformulating equation \ref{eq:fs4} as a matrix-vector formula, we can obtain
\begin{equation}
\label{eq:fs44}
\min_{\mathbf{m}} \parallel \mathbf{d} -  \mathbf{B}\mathbf{m} \parallel_2^2,
\end{equation}
where 
\begin{align}
\label{eq:dBm}
\mathbf{d} = \left[\begin{array}{c}
d(1) \\
d(2) \\
\vdots \\
d(N_t)
\end{array}
\right], \mathbf{B}=\left[\begin{array}{cccc}
\mathbf{B}_1 & \mathbf{B}_2 & \cdots & \mathbf{B}_N \\
\end{array}
\right], \text{and}\quad \mathbf{m}=\left[\begin{array}{c}
\mathbf{m}_1\\
\mathbf{m}_2\\
\vdots\\
\mathbf{m}_N\\
\end{array}\right].
\end{align}

$\mathbf{B}_n$ in equation \ref{eq:dBm} denotes the diagonal matrix composed of $\mathbf{b}(t,n)$, $t\in[1,2,\cdots,N_t]$, and $\mathbf{m}_n$ denotes the column vector composed of $\mathbf{a}(t,n)$, $t\in[1,2,\cdots,N_t]$. 
%\mathbf{B}=\left[\begin{array}{cccc}
%B(1,1) & B(1,2) & \cdots & B(1,N) \\
%B(2,1) & B(2,2) & \cdots & B(2,N) \\
%\vdots & \vdots & \vdots & \vdots \\
%B(N_t,1) & B(N_t,2) & \cdots & B(N_t,N) 
%\end{array}
%\right]
The shaping regularization method \cite[]{fomel2007shape} can be used to solve equation \ref{eq:fs3} with the following iterative formula:
\begin{equation}
\label{eq:shape}
\mathbf{m}_{k+1} = \mathbf{T}\left[\mathbf{m}_k + \alpha_k \mathbf{B}^T(\mathbf{d}-\mathbf{Bm}_k)\right],
\end{equation}
where $\mathbf{m}_{k}$ denotes the model after $k$ iterations, $\mathbf{T}$ is a smoothing operator, $\alpha_k$ denotes the step \old{length, which can be computed following}\new{length herein computed by} the conjugate gradient method, and $\mathbf{B}^T$ denotes the adjoint/\wen{complex} tranpose of the forward operator. The smoothing operator $\mathbf{T}$ is a serial multi-dimensional filter, meaning that a 1D smoothing filter \dlo{defined by equation \ref{eq:tri}} is applied to each \old{direction of the seismic data}\new{seismic dimension} (e.g., time and space) in a serial form. After solving the model, i.e., $\mathbf{a}(t,n)$, the complex spectra can be obtained by considering the first element in $\mathbf{a}(t,n)$ as the real value and the second element in $\mathbf{a}(t,n)$ as the imaginary value. \wen{Note that we can obtain a time-frequency map in the $t-n$ domain by solving equation \ref{eq:fs4}. To obtain the spectra in the $t-f$ domain, a}\dlo{A} final $n-f$ transformation should be done in order to obtain the normal time-frequency spectra map by considering $f=n\frac{1}{2Ndt}$.

\subsection{Non-stationary LTFT}
In the traditional LTFT method, \dlo{the smoothing operator }$\mathbf{T}$ is simply a triangle smoothing operator along the time axis to stabilize the inversion \dlo{of}\wen{in} equation \ref{eq:fs3}. \dlo{Besides}\wen{In addition}, assuming the \dlo{homogeneity of the time-frequency spectra along the time axis, the smoothing radius in the smoothing operator is fixed.}\wen{homogeneity of the time-frequency spectra along the time axis, the radius of the smoothing operator is fixed.}

Here, we propose to vary the time-only smoothing operator to a multi-dimensional \wen{triangular} smoothing operator $\mathbf{T}_N$, which can be used to smooth along all physical dimensions, e.g., frequency, time, and space\dlo{ (X and Y)}. \wen{The multi-dimensional smoothing operator ensures that the new method utilizes coherency along all dimensions, thus significantly improving the anti-noise ability of the LTFT method.}\dlo{Besides, because}\wen{ In addition, because} of the large heterogeneity in the model domain, \dlo{as required by a high-resolution time-frequency transform, the smoothing should not be stationary, i.e., using the same smoothing radius across the whole domain. We}\wen{we} propose to apply a non-stationary smoothing to all the physical domains. It means that we could vary the smoothing radius for each point of the multi-dimensional time-frequency map/cube according to the spectral energy distribution or other a-priori information. This non-stationary smoothing offers the flexibility of better locating those areas of the time-frequency domain having a higher resolution using a specifically designed smoothing radius map.

Due to the multidimensional smoothing applied onto the model, the non-stationary LTFT method \dlo{takes}\wen{considers} the whole input seismic data, e.g., a trace, a 2D section, or a 3D volume, as a single object. Unlike the traditional LTFT method expressed in equation \ref{eq:fs4} that can be solved trace-by-trace in parallel, the non-stationary LTFT method inverts for the time-frequency representations in all the dimensions, e.g., scale/frequency, time, space (X and Y), concurrently \wen{as follows},
\begin{equation}
\label{eq:fs5}
\min_{\mathbf{m}(t,x,y,n)} \sum_{t} \left( d(t,x,y) - \sum_{n=0}^{N} \mathbf{b}(t,x,y,n)\mathbf{a}(t,x,y,n) \right)^2,
\end{equation}
where $d(t,x,y)$ and $\mathbf{a}(t,x,y,n)$ denote the data and model in all physical dimensions.

\dlo{Due to the large model space, an efficient smoothing should be applied. We apply the following efficient implementation of a triangle smoother. The triangle smoother with a smoothing radius $N$}\wen{Due to the large model space, an efficient smoothing should be applied. We apply the following implementation of a triangular smoother \cite[]{lumley1994anti,claerbout2008gee}. The triangular filter with a smoothing radius $R$} can be obtained by cascading two rectangle smoothers, which can be expressed in the Z-transform form as:
\wen{
\begin{equation}
\label{eq:tri}
\mathbf{T}=\frac{1}{R^2}(1+Z+Z^2+\cdots+Z^{R-1})(1+Z+Z^2+\cdots+Z^{R-1}) = \frac{Z^{2R}-2Z^R+1}{(1-Z)^2R^2}.
\end{equation}}
\dlo{The numerator of equation}\wen{Equation} \ref{eq:tri} can be efficiently implemented in a recursion form:
\begin{equation}
\label{eq:first}
y_n = \frac{1}{R^2}(x_{n-2R} + x_n - 2x_{n-R}) +2y_{n-1}-y_{n-2},
\end{equation}
\new{where} $y_n$ and $x_n$ refer to the data samples in given directions. \wen{The recursion in equation \ref{eq:first} makes the smoothing efficient.} Equation \ref{eq:first} is directly related \dlo{with}\wen{to} the smoothing radius $R$, which makes the recursion method applicable to non-stationary smoothing.

Note that when the smoothing radii in the frequency direction and space direction are both constantly set to be one point, the non-stationary  LTFT method downgrades to the traditional LTFT method. When the smoothing radius in the time direction is further increased to \dlo{the} infinity, the non-stationary  LTFT method \dlo{further downgrades}\wen{reverts} to the Fourier transform.

\subsection{A synthetic benchmark comparison}
To demonstrate the merits of the non-stationary LTFT method in obtaining higher resolution and better anti-noise ability \wen{compared with state-of-the-art methods}, we conduct a benchmark comparison with the traditional LTFT method based on the same synthetic example in \cite{liuyang2012}. Figure \ref{fig:cchirpsc} shows the crossing-chirp signal \cite[]{liuyang2012} \dlo{(a)} and \wen{Figure \ref{fig:cchirps}} the noisy crossing-chirp signal \dlo{(b) }by adding some random noise. Figures \ref{fig:rect-n0} and \ref{fig:rect-n1} show the adaptively designed smoothing radius maps in the frequency and time directions, respectively. Here, we use the output from the traditional LTFT method as a reference and calculate the energy distribution of the LTFT spectra. Then, we set \dlo{as }a threshold of 5\% of the maximum energy, below which the smoothing radius is set as a smaller value and above which the smoothing radius is set a larger value. The ``larger and smaller'' values of the smoothing radius map depend on the level of smoothing one wants to apply. For example, \dlo{in}\wen{on} the time axis, we set the smoothing radius as either \old{7}\new{seven} points for a weaker smoothing of signal or 14 points for a stronger smoothing of noise. Here, ``signal'' means the target components in the spectrum and ``noise'' means the unwanted components. \old{In}\new{On} the frequency axis, since a \wen{smoothing} radius of \old{3}\new{three} points is strong\dlo{ for smoothing}, we only choose \old{1}\new{one} point for smoothing the signal and \old{3}\new{three} points for smoothing the noise.  This is only a simple example of designing the non-stationary smoothing radius\dlo{. Other}\wen{ and} better strategies can \dlo{also }be used. We compare the time-frequency spectra \old{in}\new{for} different scenarios in Figure \ref{fig:st,ltft_s,ltft_s3,ltft_s4,ltft_s2,ltft_n}. Figure \ref{fig:st} shows the result from the \wen{ST} transform. Figure \ref{fig:ltft_s} shows the result from the LTFT method with $R_t=7$ and $R_f=1$. Here, $R_t$ and $R_f$ denote the smoothing radii in time and frequency directions. Figure \ref{fig:ltft_s3} shows the result from the LTFT method with stationary smoothing radii $R_t=7$ and $R_f=2$. Figure \ref{fig:ltft_s4} shows the result from the LTFT method with stationary smoothing radii $R_t=7$ and $R_f=3$. Figure \ref{fig:ltft_s2} shows the result from the LTFT method with $R_t=14$ and $R_f=1$. Figure \ref{fig:ltft_n} shows the result from the LTFT method with the non-stationary smoothing radius maps shown in Figure \ref{fig:rect-n0,rect-n1}. In these time-frequency maps, the result from the ST method seems to be \old{very }affected by the noise and has a low resolution. The results corresponding to the traditional LTFT method \wen{with single smoothing in time}, i.e., Figures \ref{fig:ltft_s} and \ref{fig:ltft_s2}, improve the result a bit but \dlo{it is inconvenient to adjust the}\wen{is sensitive to the smoothing} parameter\dlo{: single smoothing in time}. The results from the \dlo{non-}stationary LTFT method (Figures \ref{fig:ltft_s3} and \ref{fig:ltft_s4}) with a stationary smoothing radius in frequency is dangerous in over-smoothing the spectra and causing a complete smearing along the frequency dimension. \dlo{The result from the non-stationary LTFT with non-stationary time and frequency smoothing radii obtains an excellent performance, i.e., high resolution and anti-noise ability, as shown in Figure \ref{fig:ltft_n}.}\wen{The proposed method with non-stationary time and frequency smoothing radii obtains a high-resolution and anti-noise performance, as shown in Figure \ref{fig:ltft_n}.}

\inputdir{cross}
\multiplot{2}{cchirpsc,cchirps}{width=\textwidth}{(a) Clean chirp signal. (b) Noisy chirp signal.}

\multiplot{2}{rect-n0,rect-n1}{width=\textwidth}{Non-stationary smoothing radius (a) along the frequency axis and (b) along the time axis (b).}

\multiplot{6}{st,ltft_s,ltft_s3,ltft_s4,ltft_s2,ltft_n}{width=0.45\textwidth}{Time-frequency spectra of the noisy chirp signal using (a) S transform, (b) stationary LTFT with $R_t=7$ and $R_f=1$, (c) stationary LTFT with $R_t=7$ and $R_f=2$, (d) stationary LTFT with $R_t=7$ and $R_f=3$, (e) stationary LTFT with $R_t=14$, and (f) \wen{non-}stationary LTFT with smoothing radius in time and frequency shown in Figure \ref{fig:rect-n0,rect-n1}.}

\inputdir{usarray}
\plot{earth_pick}{width=\textwidth}{Earthquake data recorded from \old{the}\new{a} station at longitude=107.6$^o$W and latitude=37.7$^o$ corresponding to the January 18, 2009, Kermadec Islands, New Zealand, Mw 6.4 earthquake. The vertical lines indicate the manually picked arrival times for P, PP, S, SS, Rayleigh waves\old{ (from left to right)}.}

\multiplot{2}{earth_rect-n0,earth_rect-n1}{width=\textwidth}{Non-stationary smoothing radius along the frequency axis (a) and along the time axis (b) for the earthquake data analysis example.}

\multiplot{3}{earth_st_pick,earth_ltfts_pick,earth_ltftn_pick}{width=\textwidth}{Time-frequency spectra overlapped with the manually picked arrival times. (a) Result from the S transform. (b) Result from the stationary LTFT method ($R_t=20$). (c) Result from the proposed non-stationary LTFT method with the smoothing radius in time and frequency shown in Figure \ref{fig:earth_rect-n0,earth_rect-n1}.}

\section{Applications}

The first application of the proposed non-stationary LTFT method is to analyze the time-frequency features of an earthquake seismogram of the January 18, 2009, Kermadec Islands, New Zealand, Mw 6.4 earthquake, \old{which was }recorded from the station \new{located} at longitude 107.6$^o$W and latitude 37.7$^o$. \new{Figure \ref{fig:earth_pick} plots} the raw seismogram\old{, which is very noisy, is} borrowed from \cite{yangkang2019nc}\old{ and is plotted in Figure \ref{fig:earth_pick}}. There are 5400 samples in this trace\old{. The sampling rate is 1 s}\new{ at a 1 s sampling rate}. The seismogram is extracted from the continuous record starting from -586 s ahead of the earthquake event. The vertical lines from left to right correspond to the manually picked P, PP, S, SS, Rayleigh phases arrival times. 
We design non-stationary smoothing radius maps in both frequency and time directions in the \wen{same} way as the aforementioned crossing-chirp signals. The \dlo{resulted}\wen{resulting} non-stationary smoothing radii are plotted in Figure \ref{fig:earth_rect-n0,earth_rect-n1}.  The maximum and minimum smoothing radii in the frequency direction are \old{3}\new{three} points and \old{1}\new{one} point, respectively. The maximum and minimum smoothing radii in the time direction are 40 points and 20 points \new{long}, respectively. We show a comparison of time-frequency spectra using different methods in Figure \ref{fig:earth_st_pick,earth_ltfts_pick,earth_ltftn_pick}. Figure \ref{fig:earth_st_pick} shows the time-frequency spectra using the ST method, where significant noise \dlo{spectra are}\wen{is} revealed around the frequency band 0.1-0.2 Hz. Figure \ref{fig:earth_ltfts_pick} \dlo{plots}\wen{displays} the time-frequency spectra using the traditional LTFT method, where the noise influence has been significantly mitigated due to the temporal smoothing and the resolution in the low-frequency band has also been enhanced compared with the ST method. Figure \ref{fig:earth_ltftn_pick} shows the time-frequency spectra using the proposed non-stationary LTFT method based on the non-stationary smoothing radius maps shown in Figure \ref{fig:earth_rect-n0,earth_rect-n1}. The result using the proposed method is surprisingly high-resolution and clean, showing a very good correlation between the \dlo{spectra}\wen{spectral} peaks and the manually picked phase arrivals. \dlo{Besides}\wen{In addition}, due to the \dlo{enabled }frequency smoothing, the proposed method shows an obviously higher resolution in time than the traditional LTFT method, which could be very helpful for phase arrival picking. Its application in arrival picking, either in a traditional scheme \cite[]{mostafa2016geo} or in a deep-learning based scenario \cite[]{chen2019ess,guoyin2020geo}, is\dlo{ worth investigating in the future}\wen{ a notable future area of investigation}.

\inputdir{section}
\multiplot{2}{tracesc,traces}{width=0.45\textwidth}{Multi-channel seismic data example. (a) Clean data. (b) Noisy data.}
\multiplot{4}{tracesc-ltft,traces-ltft,traces-ltftn-no,traces-ltftn}{width=0.45\textwidth}{Time-frequency spectra of (a) clean data using stationary LTFT, (b) noisy data using stationary LTFT, (c) noisy data using non-stationary LTFT with no spatial smoothing, (d) noisy data using non-stationary LTFT with spatial smoothing.}
\multiplot{4}{traces-ratio-S,traces-ratio-N,traces-lsfits-S2,traces-lsfits-N2}{width=0.45\textwidth}{\wen{(a) Spectral ratio (between $t=0.5$ s and $t=0.8$ s) using the traditional LTFT method. (b) Spectral ratio (between $t=0.5$ s and $t=0.8$ s) using the non-stationary LTFT method. (c) Spectral ratio \wen{(red)} and fitted \wen{(blue)} line for the 16th spatial trace using the traditional LTFT method. (d) Spectral ratio \wen{(red)} and fitted \wen{(blue)} line for the 16th spatial trace using the non-stationary LTFT method.}}
\plot{traces-comp0}{width=\textwidth}{Quality factor estimation comparison. }

The second application of the proposed non-stationary LTFT method is quality factor estimation. The application is based on a 2D seismic section \dlo{as }shown in Figure \ref{fig:tracesc,traces}. Figure \ref{fig:tracesc} \dlo{plots}\wen{shows} the clean seismic section and Figure \ref{fig:traces} \dlo{plots}\wen{displays} the noisy seismic section by adding random noise. The clean data \old{is}\new{are} used to calculate its time-frequency cube as plotted in Figure \ref{fig:tracesc-ltft} for benchmarking the time-frequency cubes of different methods. In this synthetic test, we simulate the attenuation between the seismic event at \dlo{time 0.5s and the seismic event at time 0.8s}\wen{t=0.5 s and seismic event at t=0.8 s} using a constant quality factor \dlo{$Q=60$}\wen{Q of 60}. Since we know \dlo{the exact quality factor of this example}\wen{Q}, we can estimate the quality factors using different methods based on the spectral ratio method (SRM)\old{ framework as} detailed in \cite{yangkang2019gjiQ}, and then compare them with the exact solution\dlo{ to evaluate the accuracy}. First, we calculate the time-frequency cubes corresponding to the noisy data using the traditional LTFT method and the proposed method. The result from the traditional LTFT method is shown in Figure \ref{fig:traces-ltft}, which contains many \dlo{artifacts}\wen{artefacts} due to the strong random noise. Figure \ref{fig:traces-ltftn-no} shows the result from the non-stationary LTFT method when setting a constant \old{3}\new{three}-point smoothing radius (same as the traditional LTFT method) in time, and a constant \old{1}\new{one}-point smoothing radius for both frequency and space directions. \dlo{It is clear that the two results in Figures \ref{fig:traces-ltft} and \ref{fig:traces-ltftn-no} are almost the same, confirming that the proposed non-stationary LTFT method downgrades to the traditional LTFT method when no smoothing in frequency and space is used, although the traditional LTFT method does the inversion (equation \ref{eq:fs4}) trace by trace and the proposed LTFT framework (equation \ref{eq:fs5}) does the inversion by utilizing all the traces at one time.}\wen{It is clear that the two results in Figures \ref{fig:traces-ltft} and \ref{fig:traces-ltftn-no} are almost the same, confirming that the proposed non-stationary LTFT method downgrades to the traditional LTFT method when no smoothing in frequency and space is used. Note that the traditional LTFT method does the inversion (equation \ref{eq:fs4}) trace by trace but the proposed LTFT framework (equation \ref{eq:fs5}) does the inversion by utilizing all the traces at one time.} Figure \ref{fig:traces-ltftn} shows the result from the proposed method by using a 30-point lateral smoothing radius and a \old{3}\new{three}-point temporal smoothing radius, which is very clean and accurate \dlo{as benchmarked}\wen{when compared} by the exact solution in Figure \ref{fig:tracesc-ltft}. We take the spectral ratio between the \dlo{0.5-sec slice and 0.8-sec}\wen{0.5 s slice and 0.8 s} slice based on the regularized inversion framework \cite[]{yangkang2019gjiQ} and show \dlo{the }comparisons between the traditional and proposed LTFT methods in Figure \ref{fig:traces-ratio-S,traces-ratio-N,traces-lsfits-S2,traces-lsfits-N2}. \old{The top row in Figure \ref{fig:traces-ratio-S,traces-ratio-N,traces-lsfits-S2,traces-lsfits-N2}}\new{Figures \ref{fig:traces-ratio-S} and \ref{fig:traces-ratio-N}} show the spectral division in the frequency-space domain using the traditional LTFT method \old{(left)}\new{(Figures \ref{fig:traces-ratio-S} and \ref{fig:traces-lsfits-S2})} and the proposed method \old{(right)}\new{(Figures \ref{fig:traces-ratio-N} and \ref{fig:traces-lsfits-N2})}. \old{The bottom row of Figure \ref{fig:traces-ratio-S,traces-ratio-N,traces-lsfits-S2,traces-lsfits-N2} shows}\new{Figures \ref{fig:traces-lsfits-S2} and \ref{fig:traces-lsfits-N2} show} the extracted one column from \old{each of the top row}\new{Figures \ref{fig:traces-ratio-S} and \ref{fig:traces-ratio-N}} and the least-squares fitted lines using the traditional \old{(left) }and the proposed \old{(right) }methods\new{, respectively}. The slope of the least-squares fitted line is used to calculate the quality factor. It is clear that the spectral ratio using the non-stationary LTFT method can be fitted well\dlo{, indicating a better physically explained spectral ratio}. \dlo{The}\wen{A} comparison of the estimated quality factors using the traditional\dlo{ and}\wen{,} proposed LTFT methods and \dlo{the }exact solution is shown in Figure \ref{fig:traces-comp0}. The pink horizontal line corresponds to the exact solution, i.e., $Q=60$. The blue line corresponds to the estimated Q from the proposed non-stationary LTFT method, which is very close to the pink line. The red line corresponds to the result using the traditional LTFT method, which is very oscillating and not stable.

The third application is low-frequency shadow detection. The low-frequency shadow refers to the phenomenon that the low-frequency slice shows evident anomalies in those reservoir-related areas while the high-frequency slice does not show these anomalies in the same areas due to high-frequency attenuation \cite[]{castagna2003instantaneous}. \old{We show}\new{Figure \ref{fig:old-1} shows} a field data example that is borrowed from \cite{guochang20113}\old{ in Figure \ref{fig:old-1}}. We extract three constant frequency slices, \old{i.e.,}\new{at} 15 Hz, 31 Hz, and 70 Hz, from the time-frequency cubes using the traditional and \old{the }proposed methods. \dlo{The}\wen{A} comparison is shown in Figure \ref{fig:lf-ltft1-0,lf-ltftn1-0,lf-ltft2-0,lf-ltftn2-0,lf-ltft3-0,lf-ltftn3-0}, with the \old{left}\new{left and right columns} showing the results from the traditional \old{LTFT method, and the right column showing the results from}\new{and} the non-stationary LTFT \old{method}\new{methods, respectively}. It is clear that the \old{non-stationary LTFT method}\new{latter} significantly increases the temporal and spatial resolution of the time-frequency spectra, making the low-frequency shadow more evident and better localized. The low-frequency shadow is highlighted by the frame boxes in Figure \ref{fig:lf-ltft1-0,lf-ltftn1-0,lf-ltft2-0,lf-ltftn2-0,lf-ltft3-0,lf-ltftn3-0}. In this example, we use the same way as the crossing-chirp signals to design the non-stationary smoothing radius. The maximum and minimum smoothing radii along the time direction are \old{10 samples and 8 samples}\new{ten and eight samples}, respectively. The maximum and minimum smoothing radii along the space direction are \old{5 samples and 3}\new{five and three} samples, respectively.

\inputdir{lowf}
\plot{old-1}{width=\textwidth}{2D field data for \new{a} low-frequency shadow detection test.}
\multiplot{6}{lf-ltft1-0,lf-ltftn1-0,lf-ltft2-0,lf-ltftn2-0,lf-ltft3-0,lf-ltftn3-0}{width=0.4\textwidth}{\wen{Frequency slices at 15 Hz (a), 31 Hz (c), 70 Hz (e)  using the traditional LTFT. Frequency slices at 15 Hz (b), 31 Hz (d), 70 Hz (f)  using the non-stationary LTFT.}}

The fourth application is channel detection. We apply the LTFT method to analyze a 3D seismic cube and then extract different constant-frequency horizontal slices, where the channels can be revealed. \new{Figure \ref{fig:flat} presents the}\old{The} 3D cube\old{ is} borrowed from \cite{guochang20113}\old{ and is plotted in Figure \ref{fig:flat}}. This field data \old{has}\new{have} been flattened using the predictive painting method \cite[]{fomel2010painting}. The flattening procedure can help reveal the stratigraphic features in the dataset. \old{More introduction about the}\new{The} preprocessing steps \old{is referred to}\new{are presented in} \cite{guochang20113}. Here, we simply use this dataset to show a benchmark comparison of the channel detection performance between the traditional and the proposed LTFT methods. In this example, \dlo{we use the same way as the last example to design the non-stationary radius maps in all directions. We}\wen{we} do not smooth along the frequency direction. The maximum and minimum smoothing radii along both time and space directions are \old{5 samples and 3 samples}\new{five and three samples}, respectively. Figure %\ref{fig:ltft-slice25-0,ltft-slice30-0,ltft-slice35-0,ltftn-slice25-0,ltftn-slice30-0,ltftn-slice35-0} 
\ref{fig:ltft-slice25-0,ltft-slice35-0,ltft-slice50-0,ltftn-slice25-0,ltftn-slice35-0,ltftn-slice50-0}
shows a comparison of \old{three constant-frequency slices corresponding to }\dlo{25 Hz, 30 Hz, and 35 Hz}\new{the 25Hz, 35 Hz, and 50 Hz frequency slices}.
The top row corresponds to the results from the traditional LTFT method and the bottom row shows the results from the proposed method. It is clear that due to the spatial coherency constraint, the \old{resulted}\new{estimated} spectra is \old{much }cleaner and maintains the key stratigraphic features, e.g., the channels. The detected channels are \old{pointed}\new{shown} by the arrows in Figure %\ref{fig:ltft-slice25-0,ltft-slice30-0,ltft-slice35-0,ltftn-slice25-0,ltftn-slice30-0,ltftn-slice35-0}. 
\ref{fig:ltft-slice25-0,ltft-slice35-0,ltft-slice50-0,ltftn-slice25-0,ltftn-slice35-0,ltftn-slice50-0}.
It is apparent that the channel delineation is \old{much }clearer using the non-stationary LTFT method. For example, the channels using the traditional method are only clear in the 25 Hz slice, while the channels in the \dlo{30Hz}\wen{35 Hz} slice become \old{very }vague, and it is almost invisible from the \dlo{30Hz}\wen{50 Hz} slice \old{because of}\new{due to} the strong interference of high-frequency noise. However, the channels are clear in all three constant-frequency slices using the non-stationary LTFT method. Even in the \dlo{35Hz}\wen{50 Hz} slice, the proposed method still unveils the channels due to its much stronger anti-noise \old{ability}\new{capability}.

\inputdir{chev}
\plot{flat}{width=\textwidth}{\wen{Flattened} 3D seismic volume. \new{The front face shows a constant time slice.}}
%\multiplot{6}{ltft-slice25-0,ltft-slice30-0,ltft-slice35-0,ltftn-slice25-0,ltftn-slice30-0,ltftn-slice35-0}{width=0.3\textwidth}{Horizontal slice comparison of the time-frequency spectra. Top row: horizontal slices of 25 Hz (left), 30 Hz (middle), 35 Hz (right), respectively, using the traditional LTFT method. Bottom row: horizontal slices of 25 Hz (left), 30 Hz (middle), 35 Hz (right), respectively, using the non-stationary LTFT method. \wen{The arrows highlight the differences of depicted channels between two methods.}}

\multiplot{6}{ltft-slice25-0,ltft-slice35-0,ltft-slice50-0,ltftn-slice25-0,ltftn-slice35-0,ltftn-slice50-0}{width=0.3\textwidth}{\wen{Horizontal slices comparison of the time-frequency spectra. Horizontal slices at 25 Hz (a), 35 Hz (b), 50 Hz (c), respectively, using the traditional LTFT method. Horizontal slices at 25 Hz (d), 35 Hz (e), 50 Hz (f), respectively, using the non-stationary LTFT method. The arrows highlight the differences of depicted channels between two methods.}}

The fifth application is \old{the}\new{a} multi-component data registration example. As demonstrated in \cite{fomel20052}, the time-frequency transform can be used to balance the frequency contents between the PP and warped PS images \old{in order to get a better}\new{to obtain improved} image registration\old{ performance}. \new{Here, warping means temporally shifting each sample in the PS image to match the PP image.} The principle of the spectral balancing is to match the spectra of PP and PS images to that of a Ricker wavelet, after which the balanced PP and PS images share a closer \old{spectra}\new{spectral} content. We directly use the result from \cite{liuyang2012} using the traditional LTFT method as a benchmark comparison with the proposed non-stationary LTFT method. In this test, we use a fixed constant smoothing radius of 20 samples in time as the same as the traditional LTFT method. We use a smoothing radius of \old{5}\new{five} samples in space to utilize the spatial coherency to constrain the resolution of the spectra. The PP and PS images before registration are shown in Figures \ref{fig:vpp} and \ref{fig:vss}, respectively. Figures \ref{fig:ppltft-new} and \ref{fig:ppltftn-new} show the time-frequency spectra cubes of the PP image before matching obtained using the traditional and the proposed LTFT methods, respectively. The comparison for the warped PS image are shown on the bottom row of Figure \ref{fig:ppltft-new,ppltftn-new,pswltft-new,pswltftn-new}. It is clear that the non-stationary LTFT method obtains a better result with \old{a }higher resolution. Figures \ref{fig:before,after,after1} shows the interleaved data comparison. The interleaved data \old{is}\new{are} a way to evaluate the performance of multi-component data registration. The \old{principle}\new{idea} is that by interleaving the PP and PS traces one by one, it is easier to \old{find}\new{spot} the differences between them (especially the alignment of events in the time axis)\old{ between different results}. \old{It is intuitive}\new{Note} that the more spatially coherent registration result is better in aligning the PP and PS events. From the \old{highlighting }frame boxes in Figure \ref{fig:before,after,after1}, the non-stationary LTFT method obtains an obviously better result. \wen{The frame boxes are also zoomed in Figure \ref{fig:before-z,after-z,after1-z} for a better view.}

\inputdir{vecta}
\multiplot{2}{vpp,vss}{width=0.45\textwidth}{Multi-component data registration example. (a) PP image. (b) PS image. }

\multiplot{4}{ppltft-new,ppltftn-new,pswltft-new,pswltftn-new}{width=0.45\textwidth}{Time-frequency spectra cubes using (a) traditional LTFT method and (b) non-stationary LTFT method for the PP image before matching, (c) traditional LTFT method and (d) non-stationary LTFT method for the warped PS image before matching.}

\multiplot{3}{before,after,after1}{width=0.48\textwidth}{Interleaved data comparisons. Interleaved data before registration (a), after registration using the traditional LTFT method (b), and after registration using the non-stationary LTFT method (c). \wen{The green boxes highlight an area that shows apparent registration difference in these results. The green boxes are also zoomed for a better view in Figure \ref{fig:before-z,after-z,after1-z}.}}

\multiplot{3}{before-z,after-z,after1-z}{width=0.5\textwidth}{\wen{Zoomed comparison of the green boxes in Figure \ref{fig:before,after,after1}. The coherency of the interleaved PP-PS image has been dramatically enhanced from top to bottom.}}

\section{Conclusions}
In an inversion-based time-frequency transform, seismic data \old{is}\new{are} highly non-stationary in both data and model (spectra) domains. While \old{the}\new{data} non-stationarity\old{ of the data} has been taken into account in the traditional LTFT method, \old{the}\new{model} non-stationarity\old{ of the model} has not been considered. We propose a non-stationary LTFT method to obtain the time-frequency spectra with a high resolution, where the data non-stationarity is characterized by non-stationary regression and the model non-stationarity is characterized by non-stationary smoothing. The non-stationary smoothing is applied to all the physical dimensions of the time-frequency spectra, i.e., frequency, time, and space. A synthetic test on the crossing-chirp signal shows that the proposed non-stationary LTFT method can significantly improve the resolution and anti-noise ability of the time-frequency analysis compared with the ST transform and the standard LTFT method. The non-stationary smoothing radius \old{maps/cubes}\new{maps and cubes} offer an effective way to apply \old{a-priori}\new{a priori} constraint to the time-frequency spectra so as to obtain a model domain that is more physically meaningful. The applications of the proposed non-stationary LTFT method to several field data examples with respect to different purposes demonstrate that the new method \old{is very}\new{has a lot of} potential in many practical problems.
%\section{Acknowledgements}
%The work is supported by the starting fund from Zhejiang University.

\section{DATA AND MATERIALS AVAILABILITY}
Data associated with this research are available and can be obtained by contacting the corresponding author.

\bibliographystyle{seg}
\bibliography{tf}

### 2021-02-25 tf/matfun/Gentrace.m

@@ -1,0 +1,56 @@
+ function Gentrace(t1,t2,dt,nt,f0,Q,trace)
+% Author      : Yangkang Chen
+%               Texas Consortium of Computational Seismology
+%               Jackson School of Geosciences
+%               The University of Texas at Austin
+%         
+% Date        : Oct, 2014
+
+% Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
+    
+%  Copyright (C) 2014 The University of Texas at Austin
+%  Copyright (C) 2014 Yangkang Chen
+%  
+%  This program is free software; you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published by
+%  the Free Software Foundation; either version 2 of the License, or
+%  (at your option) any later version.
+%  
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%  
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, write to the Free Software
+%  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  USA
+
+% create synthetic trace with attenuation
+addpath(genpath('~/chenyk/matlibcyk'));
+t=0:dt:(nt-1)*dt;
+nf=nt;
+df=1.0/dt/(nf-1);
+k1=t1/dt+1;
+k2=t2/dt+1;
+
+% f0 Hz Ricker wavelet
+w1=yc_ricker(f0,dt);
+nw1=size(w1,1);
+
+% apply attenuation to the spectrum of Ricker wavelet
+w2=ifft(fft([w1;zeros(nf-nw1,1)]).*exp(-[[0:fix(nf/2)]*df,[fix(nf/2)-1:-1:1]*df]'*pi*(t2-t1)/Q));
+w2=w2(1:nw1);
+
+% convolution
+r1=zeros(nt,1);r1(k1)=10;
+x1=conv(r1,w1,'same');
+
+r2=zeros(nt,1);r2(k2)=10;
+x2=conv(r2,w2,'same');
+
+% normalize the data
+x=x1+x2;x=x/max(x);
+
+% from Matlab to Madagascar
+rsf_create(trace,size(x)');
+rsf_write(x,trace);

### 2021-02-26 tf/paper.tex
2021年 2月26日 星期五 16时03分15秒 CST

@@
 
-\inputdir{vecta}
-\multiplot{2}{vpp,vss}{width=0.45\textwidth}{Multi-component data registration example. (a) PP image. (b) PS image. }
-
-\multiplot{4}{ppltft-new,ppltftn-new,pswltft-new,pswltftn-new}{width=0.45\textwidth}{Time-frequency spectra cubes using (a) traditional LTFT method and (b) non-stationary LTFT method for the PP image before matching, (c) traditional LTFT method and (d) non-stationary LTFT method for the warped PS image before matching.}
-
-\multiplot{3}{before,after,after1}{width=0.48\textwidth}{Interleaved data comparisons.
+%\inputdir{vecta}
+%\multiplot{2}{vpp,vss}{width=0.45\textwidth}{Multi-component data registration example. (a) PP image. (b) PS image. }
+%
+%\multiplot{4}{ppltft-new,ppltftn-new,pswltft-new,pswltftn-new}{width=0.45\textwidth}{Time-frequency spectra cubes using (a) traditional LTFT method and (b) non-stationary LTFT method for the PP image before matching, (c) traditional LTFT method and (d) non-stationary LTFT method for the warped PS image before matching.}
+%
+%\multiplot{3}{before,after,after1}{width=0.48\textwidth}{Interleaved data comparisons.
 Interleaved data before registration (a), after registration using the traditional LTFT method (b), and after registration using the non-stationary LTFT method (c).
@@
 The green boxes are also zoomed for a better view in Figure \ref{fig:before-z,after-z,after1-z}.}}
-
-\multiplot{3}{before-z,after-z,after1-z}{width=0.5\textwidth}{\wen{Zoomed comparison of the green boxes in Figure \ref{fig:before,after,after1}.
+%
+%\multiplot{3}{before-z,after-z,after1-z}{width=0.5\textwidth}{\wen{Zoomed comparison of the green boxes in Figure \ref{fig:before,after,after1}.
 The coherency of the interleaved PP-PS image has been dramatically enhanced from top to bottom.}}
+%
 

### 2021-03-01 tf/paper.tex
fix tf

--- 2021-02-25 tf/paper.tex
@@
 
-\multiplot{4}{ppltft-new,ppltftn-new,pswltft-new,pswltftn-new}{width=0.45\textwidth}{Time-frequency spectra cubes using (a) traditional LTFT method and (b) non-stationary LTFT method for the PP image before matching, (c) traditional LTFT method and (d) non-stationary LTFT method for the warped PS image before matching.}
+\multiplot{4}{ppltft,ppltftn,pswltft,pswltftn}{width=0.45\textwidth}{Time-frequency spectra cubes using (a) traditional LTFT method and (b) non-stationary LTFT method for the PP image before matching, (c) traditional LTFT method and (d) non-stationary LTFT method for the warped PS image before matching.}
 

### 2021-03-01 tf/vecta/newwarp.py

@@ -228,8 +228,8 @@ def nwarp2(name,       # name prefix
         gamma = n('gamma')
         Flow(gamma,wrp,warp2gamma(ss))
         Plot(gamma,vplot)
-
-        Result(psw,[pp,psw,dif,gamma],'TwoRows')
+# commented on 2021/02/26
+#         Result(psw,[pp,psw,dif,gamma],'TwoRows')
 
         psw1 = n('psw1')
         pp1 = n('pp1')
@@ -237,14 +237,15 @@ def nwarp2(name,       # name prefix
         Flow(psw1,psw,'window n2=1 f2=286')
 
         ppps = n('ppps')
-        Result(ppps,[psw1,pp1],
-               '''
-               add scale=1,-1 ${SOURCES[1]} |
-               cat ${SOURCES[0]} ${SOURCES[1]} axis=2 |
-               dots gaineach=n Xscreenwd=9.225 Xscreenht=5.2 Xyyscale=0.8
-               labels="Difference:PS warped:PP" label1=Time unit1=s
-               title="LTF transform balancing"
-               ''')
+# commented on 2021/02/26
+#         Result(ppps,[psw1,pp1],
+#                '''
+#                add scale=1,-1 ${SOURCES[1]} |
+#                cat ${SOURCES[0]} ${SOURCES[1]} axis=2 |
+#                dots gaineach=n Xscreenwd=9.225 Xscreenht=5.2 Xyyscale=0.8
+#                labels="Difference:PS warped:PP" label1=Time unit1=s
+#                title="LTF transform balancing"
+#                ''')
 
         ####################
         # SPECTRAL BALANCING
@@ -368,14 +369,15 @@ def nwarp2(name,       # name prefix
         Flow(sr1,sr,'window n2=1 f2=286')
 
         ltftppps = n('ltftppps')
-        Result(ltftppps,[sr1,pr1],
-               '''
-               add scale=1,-1 ${SOURCES[1]} |
-               cat ${SOURCES[0]} ${SOURCES[1]} axis=2 |
-               dots gaineach=0 Xscreenwd=9.225 Xscreenht=5.2 Xyyscale=0.8
-               labels="Difference:PS warped:PP" label1=Time unit1=s
-               title="LTF transform balancing"
-               ''')
+# commented on 2021/02/26
+#         Result(ltftppps,[sr1,pr1],
+#                '''
[…]

### 2021-03-07 npef/paper.tex
2021年 3月 7日 星期日 11时33分01秒 CST

\title{5D de-aliased seismic data interpolation using non-stationary prediction error filter}

\author{Yangkang Chen\footnotemark[1], Sergey Fomel\footnotemark[2], Hang Wang\footnotemark[1], and Shaohuan Zu\footnotemark[3]}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\ms{GEO-2021}

\address{
\footnotemark[1]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
chenyk2016@gmail.com \\
\footnotemark[2]Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
sergey.fomel@beg.utexas.edu\\
\footnotemark[3] College of Geophysics\\
Chengdu University of Technology \\
Dongsanlu, Erxianqiao, Chengdu 610059, Sichuan, China\\
Corresponding author: Yangkang Chen, chenyk2016@gmail.com
}

\lefthead{Chen et al., 2021}
\righthead{5D NPEF}

\maketitle

\begin{abstract}
The prediction error filter (PEF) assumes that the seismic data can be destructed to zero by applying a convolutional operation between the target data and prediction filter in either time-space or frequency-space domain. Here, we extend the commonly known PEF in 2D or 3D problems to its 5D version. To handle the non-stationary property of the seismic data, we formulate the PEF in a non-stationary way, which is called the non-stationary prediction error filter (NPEF). In the NPEF, the coefficients of a fixed-size PEF vary across the whole seismic data. In NPEF, we aim at solving a highly ill-posed inverse problem via the computationally efficient iterative shaping regularization. The NPEF can be used to denoise multi-dimensional seismic data, and more importantly, to restore the highly incomplete aliased 5D seismic data. We compare the proposed NPEF method with the state-of-the-art rank-reduction method for the 5D seismic data interpolation in cases of irregularly and regularly missing traces via several synthetic and real seismic data. Results show that although the proposed NPEF method is less effective than the rank-reduction method in interpolating irregularly missing traces especially in the case of low signal to noise ratio (S/N), it outperforms the rank-reduction method in interpolating aliased 5D dataset with regularly missing traces.
\end{abstract}

%\section{Keywords}
%key1,key2,key3

\section{Introduction}
\wen{The prediction}\dlo{Prediction} error filter (PEF) is a classic algorithm that has been widely used in many geophysical estimation problems \cite[]{peacock1969predictive,ott1972kalman,kumaresan1983zeros,wanghang2021geo}.  \cite{sacchi2009adaptive} apply the PEF to attenuate random noise in seismic data assuming that the local seismic data can be modeled by a superposition of several planar waves. \cite{haleseamless} proposes a local PEF to filter seismic images. PEF can be implemented in either time-space domain or frequency-space domain. The time-space PEF can better deal with the aliasing issue of the regularly missing seismic traces \cite[]{abma1995}. The frequency-space PEF can be understood \dlo{as }as solving a Z-transform polynomial equation, the roots of which correspond to different plane-wave components \cite[]{canales1984,yangkang20141}.

\dlo{PEF can be closely related with the well-known plane-wave destruction}\wen{The PEF is closely related to the plane-wave destruction} (PWD) filter \cite[]{fomel2002pwd}, which has been widely used to estimate the local slope of a seismic dataset. The PWD filter is normally estimated in the time-space domain, where the plane-wave differential equation is discretized by a finite-difference method. The discretization connects the local slope with the seismic data through a non-linear relation. Each finite-difference stencil is a non-linear function of the non-stationary local slope. The non-linear relation between local slope and seismic data is then linearized for estimating the local slope by linear inversion. Given a local slope map, the discretized PWD filter has the exact form as a PEF, where the coefficients of a PEF are directly related to the local slope. Thus, both time-space and frequency-space PEFs can be thought of predicting the plane waves.

\wen{Seismic data interpolation is an important application of PEFs.} \cite{spitz1991} develops the frequency-space PEF to interpolate aliased seismic data, where the coefficients of the PEF are estimated from the less-aliased low-frequency data and then applied to aliased high-frequency data for the interpolation. \cite{claerbout1992pvi} extends the Spitz's method to the time-space PEF to interpolate aliased seismic data. \cite{porsani1999seismic} developed the half-step PEF to interpolate seismic data with much greater computational efficiency. When the PEF is applied locally, the PEF can handle the non-stationary seismic data. The very early application of the non-stationary prediction error filter (NPEF) to seismic trace interpolation was introduced in \cite{crawley2000seismic}. Crawley's strategy for NPEF was based on\dlo{ the} local patches, where the seismic data are assumed to be locally stationary and thus can be interpolated using the classic PEF. To avoid the abrupt change on the edge of each patch after interpolation, the patches are smoothed around the edges. \cite{curry2006interpolating} applies the NPEF to interpolate diffracted multiples. Most NPEF applications are based on segmented local windows, which rely on carefully chosen parameters like window size, tapering width, and PEF parameters inside the local windows.

\cite{fomel2002pwd} designs a NPEF framework that does not depend on \dlo{the }local windows. Instead, the NPEF is estimated completely via least-squares inversion. In \cite{fomel2002pwd}, the local slope that is directly related with the NPEF coefficients is estimated by shaping regularization with local smoothness constraint.  The window-related parameters are substituted and controlled by the smoothing radius during the inversion.  Based on a similar strategy, \cite{liuyang2011rna} develop the NPEF method for interpolating 2D/3D seismic data, where the NPEF coefficients are estimated by solving a least-squares inverse problem. In addition to the NPEF in the time-space domain, its frequency-space domain counterpart was developed in \cite{guochang2012} and was called the regularized non-stationary autoregression. However, compared with the frequency-space domain NPEF, the time-space domain approach is usually less likely to cause artifacts \cite[]{abma1995,crawley2000seismic}.

In this paper, we extend the time-space domain NPEF from 2D/3D applications to 5D problems. \wen{5D interpolation has been proven to be useful for compensating the acquisition limits in the seismic exploration industry \cite[]{trad2009,kreimer2012,wujuan2020,wanghang2021tgrs3}.} More specifically, we apply the high-dimensional NPEF to interpolate aliased 5D seismic data. \wen{Due to the time-space domain implementation of the NPEF, the proposed method is more anti-aliasing than other frequency-space domain 5D interpolation methods, e.g., the rank-reduction method \cite[]{jianjun2013,yangkang2016irr5d}.} We will introduce in detail the mathematical formulation of the 5D NPEF and the way to cast it into the interpolation-related inverse problem. 
The two main contributions of this work are summarized as follows. First, this is the first work to extend the 2D/3D NPEF to 5D. We demonstrate this application via a 5D interpolation problem; Second, this is the first work to compare a NPEF method with a more dominant rank-reduction method \cite[]{kreimer2012,jianjun2013,yangkang2016irr5d,oboue2021geo1}. We show that the 5D NPEF method is better than the standard rank-reduction method in the presence of aliasing, but is worse when handling irregularly sampled data. Thus, a common framework  can be proposed in practice based on this observation, i.e., combining the rank-reduction method and NPEF method for obtaining densely sampled 5D data volumes.

We organize the paper as follows. First, we introduce the NPEF in low dimensions. Then, we introduce how to solve for the 5D NPEF from iterative inversion. Afterwards, we introduce another inverse problem for filling the missing traces. Next, we apply the proposed method to interpolate several 5D seismic datasets, and \dlo{more importantly }compare it with a more state-of-the-art rank-reduction method based on both regularly and irregularly sampled cases.

\section{Theory}
\subsection{Stationary prediction error filter in space}
The well-known plane-wave differential equation
\begin{equation}
\label{eq:pw}
\frac{\partial u}{\partial x} + \sigma \frac{\partial u}{\partial t} = 0,
\end{equation}
has \dlo{a}\wen{the} general solution as 
\begin{equation}
\label{eq:pwso}
u(t,x) = f(t-\sigma x),
\end{equation}
where $u(t,x)$ is the 2D wavefield, $\sigma$ is the local slope, \dlo{$f(t)$ denotes an arbitrary waveform, e.g., the source wavelet.}\wen{$f(t)$ is an arbitrary waveform such as the source wavelet.}

Taking equation \ref{eq:pwso} into the frequency domain, we have
\begin{equation}
\label{eq:pwso1}
U(w,x) = e^{iw\sigma x}F(w),
\end{equation}
\dlo{where $U(w,x)$ denotes the wavefield in the frequency domain. $e^{iw\sigma x}$ denotes a phase-shift operator. $F(w)$ denotes the spectrum of the wavelet.}\wen{where $U(w,x)$ is the wavefield in the frequency domain, $e^{iw\sigma x}$ is a phase shift operator, and $F(w)$ is the wavelet spectrum.} It is easy to derive a simple recursion from equation \ref{eq:pwso1} as:
\begin{equation}
\label{eq:pwso2}
U(w,x) = e^{iw\sigma} U(w,x-1).
\end{equation}
Equation \ref{eq:pwso2} shows that a plane wave can be predicted by a simple two-point prediction error filter (PEF) in the space direction:
\begin{equation}
\label{eq:pwso22}
a_0 U(w,x) + a_1 U(w,x-1) =0,
\end{equation}
where $a_0=1$ and $a_1=-e^{iw\sigma}$. We can \dlo{further }transform equation \ref{eq:pwso22} into a Z-transform notation as:
\begin{equation}
\label{eq:pwso2z}
(a_0+a_1Z_x) U(w,Z_x) =0,
\end{equation}
indicating a two-point PEF like
\begin{equation}
\label{eq:twop}
A(Z_x) = 1 + a_1Z_x.
\end{equation}
When several plane waves exist, the wavefield can be predicted by several cascaded two-point PEFs, i.e., in the Z-transform notation,
\begin{equation}
\label{eq:twop}
A(Z_x) = 1 + a_1Z_x + a_z Z_x^2 + \cdots +a_{N_x}Z_x^{N_x}.
\end{equation}
Thus, the space-domain PEF, in the Z-transform notation, takes the following form:
\begin{equation}
\label{eq:pefx}
A(Z_x) U(w,Z_x) = 0.
\end{equation}

\subsection{Stationary prediction error filter in time and space}
\wen{This section aims to establish the general form of the PEF.} Transforming equation \ref{eq:pwso2} into Z-transform notation by substituting $e^{-iw}$ with $Z_t$, we obtain
\begin{equation}
\label{eq:pwsozt}
U(w(Z_t),x) = Z_t^{-\sigma} U(w(Z_t),x-1),
\end{equation}
i.e.,
\begin{equation}
\label{eq:pwsozt}
U(Z_t,x) = Z_t^{-\sigma} U(Z_t,x-1).
\end{equation}
$Z_t^{-\sigma}$ denotes an all-pass filter, which can be approximated \cite[]{fomel2002pwd} by a third-order filter as:
\begin{equation}
\label{eq:three}
\begin{split}
Z_t^{-\sigma} &= \frac{P_3(Z_t)}{P_3(1/Z_t)},\\
P_3(Z_t) &= \frac{(1-\sigma)(2-\sigma)}{12} Z_t^{-1} + \frac{(2+\sigma)(2-\sigma)}{6} +  \frac{(1+\sigma)(2+\sigma)}{12} Z_t,
\end{split}
\end{equation}
or a fifth-order filter as:
\begin{equation}
\label{eq:five}
\begin{split}
Z_t^{-\sigma} &= \frac{P_5(Z_t)}{P_5(1/Z_t)},\\
P_5(Z_t) &= \frac{(1-\sigma)(2-\sigma)(3-\sigma)(4-\sigma)}{1680} Z_t^{-2} + \\
&\frac{(4-\sigma)(2-\sigma)(3-\sigma)(4+\sigma)}{420} Z_t^{-1}+ \\
&\frac{(4-\sigma)(3-\sigma)(3+\sigma)(4+\sigma)}{280} + \\
&\frac{(4-\sigma)(2+\sigma)(3+\sigma)(4+\sigma)}{420} Z_t + \\
&\frac{(1+\sigma)(2+\sigma)(3+\sigma)(4+\sigma)}{1680} Z_t^{2}.
\end{split}
\end{equation}
Equation \ref{eq:pwsozt} can be transformed into Z-transform notation with respect to space $x$ as 
\begin{equation}
\label{eq:pwsoztzx}
U(Z_t,Z_x) = Z_t^{-\sigma} Z_x U(Z_t,Z_x),
\end{equation}
or 
\begin{equation}
\label{eq:pwsoztzx1}
(1-Z_t^{-\sigma} Z_x) U(Z_t,Z_x) = 0.
\end{equation}

Substituting equation \ref{eq:three} or \ref{eq:five} into equation \ref{eq:pwsoztzx}, we obtain the form of 2D PEF as
\begin{equation}
\label{eq:pwsoztzx2}
A(Z_t,Z_x) U(Z_t,Z_x) = 0,
\end{equation}
where
\begin{equation}
\label{eq:pwsoztzx3}
A(Z_t,Z_x)= (1-Z_x\frac{P(Z_t)}{P(1/Z_t)}).
\end{equation}
Following \cite{fomel2002pwd}, we multiply each side of equation \ref{eq:pwsoztzx} by $P(1/Z_t)$ to obtain a simplified 2D PEF
\begin{equation}
\label{eq:pwsoztzx4}
C(Z_t,Z_x) = P(1/Z_t)-Z_xP(Z_t).
\end{equation}
In the case of a fifth-order all-pass filter approximation, and a two-trace spatial prediction, equation \ref{eq:pwsoztzx} corresponds to a 2D PEF with five-points prediction in time and two-points prediction in space. With higher-order all-pass filter approximation or a spatial prediction with more traces, e.g., $N_x$ in equation \ref{eq:twop}, we can design a larger 2D PEF. \wen{Figure \ref{fig:demo} demonstrates the prediction directions of the PEF for a 3D dataset.  The two red arrows denote the two-sided prediction in the time axis. Green and blue arrows denote the one-sided prediction along two space axes. All the spatial predictions are one-sided in the proposed method.}\new{ Note that one can also use the two-sided prediction along the two space axes, which is supposed to output better results than the one-sided method. It is worth enhancing the current software framework in the future research.}

\subsection{Non-stationary prediction error filter in 2D}
\dlo{The stationary PEF in Z-transform notation can also be written in discretized time-space domain formulation as:}\wen{The stationary PEF in Z-transform notation (equation \ref{eq:pwsoztzx4}) can also be written in the discretized time-space domain as:}
\begin{equation}
\label{eq:pef2d}
u(t,x) - \sum_{n_t=1}^{N_t}\sum_{n_x=1}^{N_x} C_{n_t,n_x}u_{n_t,n_x}(t,x) = 0 .
\end{equation}
$n_t$ and $n_x$ denote PEF coefficient indices. $u_{n_t,n_x}(t,x)$ denotes the time-shifted and space-shifted wavefield.  By solving equation \ref{eq:pef2d} for the coefficients of $C_{n_t,n_x}$, and then connecting them with the local slope $\sigma$ according to the aforementioned derivations, especially equations \ref{eq:three} and \ref{eq:five}, we can obtain the local slope estimation. \dlo{However, here,}\wen{Here, however,} we bypass the step of slope estimation, and directly estimate the PEF coefficients for reconstructing missing seismic traces. \dlo{In the least-squares criterion, equation}\wen{Equation \ref{eq:pef2d} can be solved using a least-squares criterion:}\dlo{ \ref{eq:pef2d} can be solved via:}
\begin{equation}
\label{eq:pef2d_inv}
\hat{C}_{n_t,n_x} = \arg_{C_{n_t,n_x}} \parallel u(t,x) - \sum_{n_t=1}^{N_t}\sum_{n_x=1}^{N_x} C_{n_t,n_x}u_{n_t,n_x}(t,x) \parallel_2^2,
\end{equation}
$\hat{C}_{n_t,n_x}$, $n_t=1,2,\cdots,N_t$ and $n_x=1,2,\cdots,N_x$, are the coefficients for the stationary PEF.

In a non-stationary PEF, each coefficient varies with time and space locations,
\begin{equation}
\label{eq:pef2d_inv}
\hat{C}_{n_t,n_x}(t,x) = \arg_{C_{n_t,n_x}(t,x)} \parallel u(t,x) - \sum_{n_t=1}^{N_t}\sum_{n_x=1}^{N_x} C_{n_t,n_x}(t,x)u_{n_t,n_x}(t,x) \parallel_2^2.
\end{equation}
In \dlo{a }matrix-vector form, equation \ref{eq:pef2d_inv} becomes
\begin{equation}
\label{eq:inv}
\hat{\mathbf{c}}_{n_t,n_x}(t,x) = \arg_{\mathbf{c}_{n_t,n_x}} \parallel \mathbf{u} - \sum_{n_t=1}^{N_t}\sum_{n_x=1}^{N_x} \mathbf{U}_{n_t,n_x} \mathbf{c}_{n_t,n_x} \parallel_2^2,
\end{equation}
where $\mathbf{U}_{n_t,n_x}$ is \dlo{the}\wen{a} diagonal matrix \dlo{composed of $\mathbf{u}_{n_t,n_x}$}\wen{whose diagonal elements are the values of $u_{n_t,n_x}(t,x)$}. \wen{$\mathbf{c}_{n_t,n_x}$} is the vector composed of $C_{n_t,n_x}(t,x)$. Equation \ref{eq:inv} is a highly under-determined optimization problem\dlo{, we need to add a regularization term so that}\wen{that can be regularized as follows:}
\begin{equation}
\label{eq:inv}
\hat{\mathbf{c}}_{n_t,n_x}(t,x) = \arg_{\mathbf{c}_{n_t,n_x}} \parallel \mathbf{u} - \sum_{n_t=1}^{N_t}\sum_{n_x=1}^{N_x} \mathbf{U}_{n_t,n_x}\mathbf{c}_{n_t,n_x} \parallel_2^2 + \mu \mathbf{R}(\mathbf{c}_{n_t,n_x}),
\end{equation}
\dlo{we use the shaping regularization method ? to solve equation \ref{eq:inv} for $\hat{\mathbf{c}}_{n_t,n_x}(t,x)$.} \wen{where $\mathbf{R}(\mathbf{c}_{n_t,n_x})$ is a shaping regularization term \cite[]{fomel2007shape}. }

\subsection{Non-stationary prediction error filter in 5D}
\dlo{In 5D problems, equation \ref{eq:inv} turns to}\wen{For 5D problems, equation \ref{eq:inv} becomes} 
\begin{equation}
\label{eq:inv2}
\begin{split}
\hat{\mathbf{c}}_{n_1,n_2,n_3,n_4,n_5} = &\arg_{\mathbf{c}_{n_1,n_2,n_3,n_4,n_5}} \parallel \mathbf{u} - \sum_{n_1=1}^{N_1}\sum_{n_2=1}^{N_2} \sum_{n_3=1}^{N_3}\sum_{n_4=1}^{N_4}\sum_{n_5=1}^{N_5}\mathbf{U}_{n_1,n_2,n_3,n_4,n_5}\mathbf{c}_{n_1,n_2,n_3,n_4,n_5} \parallel_2^2 \\
&+\mu \mathbf{R}(\mathbf{c}_{n_1,n_2,n_3,n_4,n_5}),
\end{split}
\end{equation}
where $n_i$, $i=1,2,3,4,5$, denote the indices in the 1st, 2nd, 3rd, 4th, and 5th dimensions. $N_i$, $i=1,2,3,4,5$, denote the filter sizes of the 1st, 2nd, 3rd, 4th, and 5th dimensions. Note that in equation \ref{eq:inv2}, $\mathbf{c}_{n_1,n_2,n_3,n_4,n_5}$ is short for $\mathbf{c}_{n_1,n_2,n_3,n_4,n_5}(x_1,x_2,x_3,x_4,x_5)$. $x_i$, $i=1,2,3,4,5$, denote the position indices of the  1st, 2nd, 3rd, 4th, and 5th dimensions. Given that the sizes of all the five dimensions are $X_1,X_2,X_3,X_4,X_5$, the total size of the NPEF coefficient vector $\mathbf{c}_{n_1,n_2,n_3,n_4,n_5}(x_1,x_2,x_3,x_4,x_5)$ is $N_1N_2N_3N_4N_5X_1X_2X_3X_4X_5$. $\mathbf{u}$ is the vectorized 5D seismic data. $\mathbf{U}_{n_1,n_2,n_3,n_4,n_5}$ denotes the diagonal matrix composed of $\mathbf{u}_{n_1,n_2,n_3,n_4,n_5}$. $\mathbf{u}_{n_1,n_2,n_3,n_4,n_5}$ denote the shifted data according to the shifting sizes in different dimensions $n_i$. Equation \ref{eq:inv2} can be formulated as a more familiar equation as
\begin{equation}
\label{eq:inv3}
\hat{\mathbf{c}} = \arg_{\mathbf{c}} \parallel \mathbf{u} - \mathbf{U}\mathbf{c} \parallel_2^2 +\mu \mathbf{R}(\mathbf{c}),
\end{equation}
where $\mathbf{c}$ is short for $\mathbf{c}_{n_1,n_2,n_3,n_4,n_5}(x_1,x_2,x_3,x_4,x_5)$, and $\mathbf{U}$ denotes a linear operator applied onto the vector $\mathbf{c}$ that represents the multi-dimensional non-stationary auto-regression \cite[]{fomel20132}: $\sum_{n_1=1}^{N_1}\sum_{n_2=1}^{N_2} \sum_{n_3=1}^{N_3}\sum_{n_4=1}^{N_4}\sum_{n_5=1}^{N_5}\mathbf{U}_{n_1,n_2,n_3,n_4,n_5}\mathbf{c}_{n_1,n_2,n_3,n_4,n_5}$ in short. Equation \ref{eq:inv3} can be solved conveniently using the shaping regularization method \cite[]{fomel2007shape} and the solution can be obtained as:
\begin{equation}
\label{eq:shape}
\hat{\mathbf{c}} = [\lambda^2 \mathbf{I} + \mathbf{T} (\mathbf{U}^T\mathbf{U} -\lambda^2 \mathbf{I})]^{-1}\mathbf{T}\mathbf{U}^T\mathbf{u}, 
\end{equation}
where $\lambda=\parallel  \mathbf{U}^T\mathbf{U} \parallel_2$, $\mathbf{T}$ is a multi-dimensional smoothing operator applied onto the model $\mathbf{c}$. \new{We use the shaping regularization method because it sometimes makes the iterative schemes converge faster.} \new{The shaping operator is a triangle smoothing operator that biases the solution (non-stationary prediction error filter coefficients) towards a smooth solution in space.} Considering that the filter size $N_i$ in each dimension is commonly chosen as a small integer, e.g., $N_1=4$ and $N_2=N_3=N_4=N_5=2$, the smoothing operator $\mathbf{T}$ is chosen as a five-dimensional triangle smoothing filter.

\subsection{De-aliased interpolation by least-squares inversion}
When the seismic data contains missing traces, we revise equation \ref{eq:inv3} as:
\begin{equation}
\label{eq:inv4}
\hat{\mathbf{c}} = \arg_{\mathbf{c}} \parallel \mathbf{S}(\mathbf{u} - \mathbf{U}\mathbf{c}) \parallel_2^2 +\mu \mathbf{R}(\mathbf{c}),
\end{equation} 
where $\mathbf{S}$ denotes the sampling operator, which is a diagonal matrix with \dlo{zero indicating sampling a trace and one indicating missing a trace}\wen{one indicating sampling a trace and zero indicating missing a trace} \cite[]{yangkang2019sg}. Equation \wen{\ref{eq:inv4}} can be solved in a similar way as equation \ref{eq:shape}, by substituting $\mathbf{u}$ with $\mathbf{Su}$ and $\mathbf{U}$ with $\mathbf{SU}$. In this way, the NPEF coefficients $\hat{\mathbf{c}}$ are first estimated and then used for estimating the missing data based on the following least-squares problem:
\begin{equation}
\label{eq:inv44}
\begin{split}
\hat{\mathbf{u}} = &\arg_{\mathbf{u}} \parallel \mathbf{u} - \sum_{n_1=1}^{N_1}\sum_{n_2=1}^{N_2} \sum_{n_3=1}^{N_3}\sum_{n_4=1}^{N_4}\sum_{n_5=1}^{N_5}\mathbf{C}_{n_1,n_2,n_3,n_4,n_5}\mathbf{u}_{n_1,n_2,n_3,n_4,n_5} \parallel_2^2,\\
&\text{s.t.}\quad \hat{\mathbf{u}}(\mathbf{x}_{obs})= \mathbf{u}(\mathbf{x}_{obs}),
\end{split}
\end{equation} 
where $\mathbf{x}_{obs}$ denotes the index vector for positions that record signals.
We solve equation \ref{eq:inv44} with the conjugate gradient algorithm \cite[]{hestenes1952,fomel2006pwc}. \new{The computational cost of the NPEF based interpolation algorithm is $O(N_{iter}N_1N_2N_3N_4N_5X_1X_2X_3X_4X_5)$, while the cost for the state-of-the-art rank-reduction method  is $O(N_{iter}X_1(X_2X_3X_4X_5)^3)$ using the full singular value decomposition (SVD) and truncation, $O(N_{iter}X_1K(X_2X_3X_4X_5)^2)$ using the partial SVD, where $K$ denotes the rank, $O(N_{iter}X_1K(X_2X_3X_4X_5)^2\log(X_2X_3X_4X_5))$ using the full SVD and truncation based on the fast Hankel-matrix multiplication, and $O(N_{iter}KX_1(X_2X_3X_4X_5)\log(X_2X_3X_4X_5))$ using the partial SVD based on the fast Hankel-matrix multiplication. The partial SVDs, although relatively faster, could show some deterioration in results. Generally, the NPEF method is much faster than the rank-reduction method.}
%https://www.mathworks.com/matlabcentral/answers/420057-what-is-the-complexity-of-matlab-s-implementation-of-svd

%
%The PWD filter can be expressed
%\begin{equation}
%\label{eq:P}
%\mathbf{P}(\sigma)\mathbf{d} = \mathbf{0}
%\end{equation}
%
%The non-stationary prediction error filter can be expressed
%\begin{equation}
%\label{eq:P}
%\mathbf{U}(\sigma)\mathbf{d} = \mathbf{0}
%\end{equation}
%
%Here, we want to use both PWD and non-stationary prediction error filters to constrain the inversion, i.e., 
%\begin{equation}
%\label{eq:P}
%\left[\begin{array}{c}
%\mathbf{P}\\
%\mathbf{U}
%\end{array}\right] \mathbf{d} = \mathbf{0}.
%\end{equation}

\section{Examples}
We apply the proposed 5D interpolation method based on NPEF to several synthetic and field data examples in this section. The two synthetic examples are borrowed from the first two examples in \cite{yangkang2016irr5d} for benchmark comparison. Note that since it is difficult to visualize a 5D dataset, we plot the results from the 5D datasets in either common midpoint gathers or common offset gathers.  In addition to the visual observation, we use the signal-to-noise ratio (S/N) to quantitatively measure the reconstruction performance when the ground-truth solution is available. The S/N \cite[]{guochang2012,weilin2016dmssa} is defined as
\begin{equation}
\label{eq:snr}
\text{S/N}=10\log_{10}\frac{\Arrowvert \mathbf{u} \Arrowvert_2^2}{\Arrowvert \mathbf{u} -\hat{\mathbf{u}}\Arrowvert_2^2},
\end{equation}
where $\mathbf{u}$ denotes the ground-truth solution and $\hat{\mathbf{u}}$ denote either the decimated or reconstructed data.

The state-of-the-art 5D reconstruction methods are based on different versions of rank reduction strategies \cite[]{kreimer2012,kreimer2013,jianjun2013,yangkang2020odrr,oboue2021geo2}. A detailed comparison of the standard rank-reduction and damped rank-reduction methods have been given in \cite{yangkang2016irr5d}, which demonstrates that the damped rank-reduction method outperforms the standard rank-reduction method when the seismic data are noisy and equals to standard rank-reduction method when the seismic data are clean, so we do not compare the NPEF method with other rank-based methods, and only with the damped rank-reduction method. The rank parameter in the damped rank-reduction method is chosen close to the number of distinct dipping components. The damping factor is conservatively chosen as 3 \cite[]{yangkang2016irr5d}.

The first synthetic example is a 5D dataset that contains linear/planar events, as shown in Figure \ref{fig:l_clean5d,l_obs5d,l_drr5d,l_npef5d}. It has a data size of $100\times 10\times 10\times 10\times 10$, with 100 temporal samples, 10 midpoint $X$ and midpoint $Y$ samples, and 10 offset $Hx$ and offset $Hy$ samples. We use it as a benchmark comparison between the damped rank-reduction method and the proposed NPEF method here. We test the performance of two competing methods, the damped rank-reduction method and the NPEF method in \dlo{three}\wen{two} different cases: (1) \dlo{noise-free }irregularly sampled data; \dlo{2) noisy irregularly sampled data; and 3)}(2)\dlo{ noise-free }regularly sampled data. \dlo{It is worth noting here that the}\dlo{The state-of-the-art 5D reconstruction methods are based on different versions of rank reduction strategies ?. A detailed comparison of the standard rank-reduction and damped rank-reduction methods have been given in ?, which demonstrates that the damped rank-reduction method outperforms the standard rank-reduction method when the seismic data is noisy and equals to standard rank-reduction method when the seismic data is clean, so we do not compare the NPEF method with other rank-based methods, and only show the comparison with the damped rank-reduction method.} Figures \ref{fig:l_clean5d,l_obs5d,l_drr5d,l_npef5d}-\ref{fig:l_clean5d2,l_obs5d2,l_drr5d2,l_npef5d2} demonstrate the comparison for \dlo{noise-free}\wen{irregularly sampled} data. \dlo{Figures \ref{fig:ln_noisy5d,ln_obs5d,ln_drr5d,ln_npef5d}-\ref{fig:ln_noisy5d2,ln_obs5d2,ln_drr5d2,ln_npef5d2} demonstrate the comparison for noisy data.} Figure \ref{fig:la_obs5d,la_drr5d,la_npef5d} demonstrates the comparison for regularly sampled data.

Figure \ref{fig:l_clean5d} shows the clean and complete data in a common midpoint gather ($X=1$ and $Y=1$). Figure \ref{fig:l_obs5d} plots the decimated data with 70\% randomly removed traces. Because of the large portion of the missing data, some big local gaps exist when viewed in the low dimensions (see Figure \ref{fig:l_obs5d}). Figures \ref{fig:l_drr5d} and \ref{fig:l_npef5d} plot the reconstructed data using the damped rank-reduction method and the NPEF method, respectively. It clear that both methods obtain very good performance in restoring the missing data. The reconstructed data of both methods are very close to the ground-truth solution. Based on the S/N criterion, the S/N of the damped rank-reduction method increases from -0.29 dB of the decimated data to 30.34 dB, while the NPEF method obtains a S/N of 15.69 dB. From the S/N comparison, it is clear the rank-reduction method outperforms the NPEF method. \dlo{In this paper}\wen{In all of our examples}, we use a temporal prediction size of four points and a spatial prediction size of two points. \wen{Figure \ref{fig:l_clean5d-fk,l_obs5d-fk,l_drr5d-fk,l_npef5d-fk} plots a comparison of the FK spectra of each data cube in Figure \ref{fig:l_clean5d,l_obs5d,l_drr5d,l_npef5d}. It is clear that the the reconstructed FK spectra of both damped rank-reduction method and proposed method are close to the spectrum of the complete data. } Figure \ref{fig:l_npef1,l_npef2,l_npef3,l_npef4} plots the coefficients cubes of the estimated NPEF ($X=1$ and $Y=1$). Figures \ref{fig:l_npef1}-\ref{fig:l_npef4} correspond to the first, second, third, and fourth temporal filter indices. We see that the filter coefficients show obvious large/small values in the signal-distributed areas. Figure \ref{fig:l_clean5d2,l_obs5d2,l_drr5d2,l_npef5d2} shows the same comparison as Figure \ref{fig:l_clean5d,l_obs5d,l_drr5d,l_npef5d} but in a common offset gather ($Hx=6$ and $Hy=6$), where we can confirm that the performance is also decent in common offset gathers.

\dlo{\dlo{Figure \ref{fig:ln_noisy5d} plots a noisy data by adding some random noise.}\wen{Figure\ref{fig:ln_noisy5d} shows noisy synthetic data generated by adding random noise to our previous example.} The S/N of the noisy data is -0.29 dB. Figure \ref{fig:ln_obs5d} shows the corresponding randomly decimated data, with the same sampling operator as the noise-free test. The S/N of the decimated data is 
-0.21 dB. Figures \ref{fig:ln_drr5d} and \ref{fig:ln_npef5d} plot the reconstructed data by the damped rank-reduction method and the proposed NPEF method. Although both methods reconstruct the missing data, the proposed NPEF method still contains a lot of residual noise, especially at those positions with recorded traces.  The S/Ns of the damped rank-reduction method and the NPEF method are 16.83 dB and 2.93 dB, respectively. The S/N comparison confirms that the rank-reduction method still obtains a satisfactory result while the NPEF method fails in obtaining acceptable results. Figure \ref{fig:ln_noisy5d2,ln_obs5d2,ln_drr5d2,ln_npef5d2} plot a comparison of different datasets in a common offset gather, which is consistent with the performance in a common midpoint gather.}

Figure \ref{fig:la_obs5d,la_drr5d,la_npef5d} demonstrates the test of different methods in reconstructing regularly sampled data. %Here, we only focus on the comparison of a common offset gather. 
We up-sample the clean synthetic data (e.g., data shown in Figure \ref{fig:l_clean5d}) by a factor of two in each spatial dimension and show a common offset gather in Figure \ref{fig:la_obs5d}. Here, the 3D common offset gather has been reshaped into a 2D matrix to see more signals in the data. The blank areas correspond to added zero traces between two neighbor traces in the clean data. The target of the de-aliased interpolation is to reconstruct the data in those blank areas. Figures \ref{fig:la_drr5d} and \ref{fig:la_npef5d} plot a comparison of reconstructed results from the rank-reduction and NPEF methods. It is obvious that the rank-reduction method fails completely in reconstructing this data, i.e., those blank traces are still not filled with signals. The proposed NPEF method, however, obtains a successful recovery of the missing traces, as indicated by the coherent and clean events in Figure \ref{fig:la_npef5d}. \wen{Figure \ref{fig:la_obs5dfk,la_drr5dfk,la_npef5dfk} plots a comparison of FK spectra of each data in Figure \ref{fig:la_obs5d,la_drr5d,la_npef5d}. It is clear that the because of the under-sampling, the incomplete data shows obvious aliasing in high-wavenumber components, e.g., left part of Figure \ref{fig:la_obs5dfk,la_drr5dfk,la_npef5dfk}. The damped rank-reduction method cannot relieve the aliasing issue but the proposed NPEF method successfully mitigate the aliasing issue by filling the missing traces.}

A synthetic example containing hyperbolic events are shown in Figure \ref{fig:ha_obs5d,ha_drr5d,ha_npef5d}. The data size  is $101\times 32\times 32\times 5\times 5$. \dlo{Figure \ref{fig:h_clean5d} shows the clean data in a common midpoint gather ($X=3$ and $Y=3$). Figure \ref{fig:h_obs5d} shows the decimated data with 70\% randomly missing traces. We also add some random noise into the existing traces. The resulted S/N of the decimated data is 0.59 dB. The reconstructed data using the rank-reduction method and the NPEF method are shown in Figures \ref{fig:h_drr5d} and \ref{fig:h_npef5d}, respectively. \dlo{In a similar way, the}\wen{The} rank-reduction method reconstructs the missing traces successfully, as well as suppressing the random noise. The NPEF method, though reconstructing most of the useful hyperbolic signals, fails in suppressing the noise. The performance from the NPEF method is obviously worse than that from the rank-reduction method. The calculated S/Ns of the two methods are 16.32 dB for the rank-reduction method, and 6.38 dB for the NPEF method. This test shows that both rank-reduction and NPEF methods are capable of reconstructing curving events, but the NPEF method is not able to suppress the noise.} Figure \ref{fig:ha_obs5d,ha_drr5d,ha_npef5d} demonstrates a reconstruction test for regularly missing traces. \wen{The up-sampled data has a size of $101\times 64\times 64\times 5\times 5$.} Figure \ref{fig:ha_obs5d} plots an up-sampled common midpoint gather, where a zero trace is put between two neighbor traces  in each spatial dimension. Figure \ref{fig:ha_drr5d} plots the reconstructed result using the rank-reduction method, where no missing traces are recovered well. The proposed NPEF method, however, obtains a very successful recovery of all the missing traces, as plotted in Figure \ref{fig:ha_npef5d}.

Next, we apply the NPEF method onto a \dlo{field}\wen{real} dataset from Eastern China. This field data are prepared by binning a pre-stack land dataset from a 3D seismic survey. There are 250 samples in time with a sampling rate of 4 ms, 10 samples in the midpoint X direction, 10 samples in the midpoint Y direction, 21 samples in the offset X direction, and 10 samples in the offset Y direction. Figure \ref{fig:r_obs5d} shows the raw data in a common offset gather, where only 5083 traces (24.2\%) of the total 21000 traces are recorded traces. Figure \ref{fig:r_drr5d} shows the result using the rank-reduction method, where all missing traces \dlo{have been filled with signals}\wen{have been interpolated}. The random noise in the recorded traces is also attenuated well. As a comparison, Figure \ref{fig:r_npef5d} plots the result using the NPEF method. Although the missing traces are \dlo{filled with signals}\wen{filled in}, there is still a significant amount of residual noise, making the seismic events \dlo{not continuous}\wen{discontinuous} along the space direction. In some areas, like in traces 40-50 of Figure \ref{fig:r_npef5d}, the recovered signals show \dlo{apparently }weak energy compared with the recorded data. We zoom \wen{in on} two areas, as highlighted by the frame boxes A and B, from each sub-figure in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}, and show the plots in Figure \ref{fig:r_obs5d1a,r_obs5d1b,r_drr5d1a,r_drr5d1b,r_npef5d1a,r_npef5d1b}. The left column in Figure \ref{fig:r_obs5d1a,r_obs5d1b,r_drr5d1a,r_drr5d1b,r_npef5d1a,r_npef5d1b} corresponds to the frame box A in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}. The right column in Figure \ref{fig:r_obs5d1a,r_obs5d1b,r_drr5d1a,r_drr5d1b,r_npef5d1a,r_npef5d1b} corresponds to the frame box B in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}. Figure \ref{fig:r_obs5d1a,r_obs5d1b,r_drr5d1a,r_drr5d1b,r_npef5d1a,r_npef5d1b} shows a much clearer comparison between the raw and reconstructed data using different methods, where we further confirm that the rank-reduction method obtains a significantly better result than the NPEF method in filling these irregularly distributed traces.  Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4} shows a comparison of the same data but in common midpoint gather. Here, \dlo{it is worth noting that }we apply a normal moveout correction to the raw data before binning the pre-stack data to 5D regular grids, so we can see that events in the common midpoint gather are generally flat. Figure \ref{fig:r_obs5d4} shows the raw incomplete data. Figures \ref{fig:r_drr5d4} and \ref{fig:r_npef5d4} show the reconstructed data using the rank-reduction and NPEF methods, respectively. It is clear that, in this case, the NPEF method is much worse than the rank-reduction method in reconstructing the missing signals and suppressing the existing noise. We also zoom \wen{in on} two areas from Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4} and show them in Figure \ref{fig:r_obs5d2a,r_obs5d2b,r_drr5d2a,r_drr5d2b,r_npef5d2a,r_npef5d2b}. The left and right columns of Figure \ref{fig:r_obs5d2a,r_obs5d2b,r_drr5d2a,r_drr5d2b,r_npef5d2a,r_npef5d2b} correspond to the frame boxes A and B, highlighted in Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4}. It is evident that the NPEF method causes more discontinuous events, as seen in Figures \ref{fig:r_npef5d2a} and \ref{fig:r_npef5d2b}.

Considering that the proposed NPEF method is less effective in reconstructing noisy and irregularly missing traces, but capable of reconstructing regularly missing traces, we handle the field data example by two steps. In the first step, we use the traditional rank-reduction method to reconstruct the irregularly missing traces and attenuate the noise. The resulting data are much smoother and complete, as shown in Figures \ref{fig:r_drr5d} and \ref{fig:r_drr5d4}. In the second step, we use the NPEF to up-sample the seismic data by reconstructing the regularly added zero traces. The up-sampled data with a regularly missing trace every other trace in all spatial dimensions is plotted in Figure \ref{fig:ra_obs5d}. The reconstructed data using the NPEF method is plotted in Figure \ref{fig:ra_npef5d}. \wen{Figure \ref{fig:ra_obs5d_new-3fk,ra_npef5d_new-3fk} plots a comparison of the FK spectra before and after the up-sampling interpolation. Before the interpolation, there is obvious aliasing on the high-wavenumber spectra, but after interpolation, the aliasing issue is greatly reduced. }For a better comparison and evaluation of the reconstruction performance, the areas highlighted by frame boxes A and B in Figure \ref{fig:ra_obs5d,ra_npef5d} are zoomed and plotted in the left and right columns in Figure \ref{fig:ra_obs5da,ra_npef5da,ra_obs5db,ra_npef5db}, respectively. From Figures \ref{fig:ra_obs5d,ra_npef5d} and  \ref{fig:ra_obs5da,ra_npef5da,ra_obs5db,ra_npef5db}, we conclude that the proposed NPEF method can successfully reconstruct regularly sampled field seismic data and help prepare a well-sampled seismic data with a denser spatial sampling, as a complement of the traditional rank-reduction method.

\new{To test whether directly mapping the raw data onto the densified regular grids can be better, which is referred to as a one-step interpolation strategy, we further conduct a test, where we compare the results between the aforementioned two-step interpolation strategy and the one-step strategy. The comparison is plotted in Figure \ref{fig:os_obs,os_recon,ts_recon}. Figure \ref{fig:os_obs} plots the observed data when binned onto the regular grids of two times denser (for each spatial dimension). Figure \ref{fig:os_recon} shows the reconstructed data by the one-step rank-reduction interpolation strategy. Figure \ref{fig:ts_recon} shows the reconstructed data by the two-step rank-reduction and NPEF interpolation strategy. It shows that directly mapping the data from irregular grids to regular grids will not be as successful as the two-step strategy. Actually, due to the very large ratio of missing traces when each spatial grid gets two times denser, the traditional rank-reduction method completely fails.}

Next, we apply the proposed NPEF method to the second field dataset. We densify each spatial dimension of the original datasets by two times to combat the aliasing issue. The raw data with filled zero traces for a common shot gather are plotted in Figure \ref{fig:zero2d}. It is clear that this dataset contains much more complicated data structure than the previous examples. We first apply the standard rank-reduction method to interpolate the regularly missing traces and obtain the result shown in Figure \ref{fig:recon2d2}. It seems that the rank-reduction method only fills in some low-frequency components into the blank traces but is far from being successful. The proposed NPEF method, however, obtains a very good recovery of the incomplete traces, which is shown in Figure \ref{fig:recon2d}. We compare the FK spectra of each dataset of this example in Figure \ref{fig:zerofk2d,reconfk2d2,reconfk2d}. It is clear that the raw data (Figure \ref{fig:zerofk2d}) seriously suffers from the aliasing issue, especially on the left and right edges. The rank-reduction method (Figure \ref{fig:reconfk2d2}) causes negligible difference compared with the raw data. The proposed NPEF method (Figure \ref{fig:reconfk2d}) clearly solves the aliasing issue.

\AtEndDocument{
\begin{figure}[htb!]
\centering
\includegraphics[width=0.8\textwidth]{Fig/demo}
\caption{\wen{PEF direction for a 3D dataset. The two red arrows denote the two-sided prediction in the time axis. Green and blue arrows denote the one-sided prediction along two space axes. All the spatial predictions are one-sided.}}
\label{fig:demo}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_clean5d}
    \label{fig:l_clean5d}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_obs5d}
    \label{fig:l_obs5d}}\\
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_rr5d}
    \label{fig:l_drr5d}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_recon5d}
    \label{fig:l_npef5d}}\\
	\caption{Interpolation results of the noise-free linear-events example for $X=1$ and $Y=1$. (a) Clean data. (b) Decimated data \dlo{by}\wen{with} irregularly missing 70\% traces (S/N=-0.29 dB). (c) Reconstructed data using the rank-reduction method (S/N=30.34 dB). (d) Reconstructed data using the NPEF method (S/N=15.69 dB). }
	\label{fig:l_clean5d,l_obs5d,l_drr5d,l_npef5d}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_clean5d-fk}
    \label{fig:l_clean5d-fk}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_obs5d-fk}
    \label{fig:l_obs5d-fk}}\\
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_rr5d-fk}
    \label{fig:l_drr5d-fk}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_recon5d-fk}
    \label{fig:l_npef5d-fk}}\\
	\caption{\wen{FK spectra of interpolation results of the noise-free linear-events example for $X=1$ and $Y=1$. (a) Clean data. (b) Decimated data. (c) Reconstructed data using the rank-reduction method. (d) Reconstructed data using the NPEF method.} }
	\label{fig:l_clean5d-fk,l_obs5d-fk,l_drr5d-fk,l_npef5d-fk}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5d_n/Fig/synth_apef5-s1}
    \label{fig:l_npef1}}
    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5d_n/Fig/synth_apef5-s2}
    \label{fig:l_npef}}\\
    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5d_n/Fig/synth_apef5-s3}
    \label{fig:l_npef3}}
    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5d_n/Fig/synth_apef5-s4}
    \label{fig:l_npef4}}\\
	\caption{Coefficients cubes of the estimated NPEF for $X=1$ and $Y=1$.  NPEF coefficients corresponding to the first (a), second (b), third (c), and fourth (d) temporal filter indices.   }
	\label{fig:l_npef1,l_npef2,l_npef3,l_npef4}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_clean5d-2}
    \label{fig:l_clean5d2}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_obs5d-2}
    \label{fig:l_obs5d2}}\\
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_rr5d-2}
    \label{fig:l_drr5d2}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_recon5d-2}
    \label{fig:l_npef5d2}}\\
	\caption{Interpolation results of the noise-free linear-events example for $Hx=6$ and $Hy=6$. Each common offset cube has been reshaped into a 2D matrix. (a) Clean data. (b) Decimated data \dlo{by}\wen{with} irregularly missing 70\% traces (S/N=-0.29 dB). (c) Reconstructed data using the rank-reduction method (S/N=30.34 dB). (d) Reconstructed data using the NPEF method (S/N=15.69 dB). }
	\label{fig:l_clean5d2,l_obs5d2,l_drr5d2,l_npef5d2}
\end{figure}

%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_noisy5d}
%    \label{fig:ln_noisy5d}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_obs5d}
%    \label{fig:ln_obs5d}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_rr5d}
%    \label{fig:ln_drr5d}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_recon5d}
%    \label{fig:ln_npef5d}}\\
%	\caption{Interpolation results of the noisy linear-events example for $X=1$ and $Y=1$. Each common midpoint cube has bee reshaped into a 2D matrix. (a) Noisy data (S/N=-0.66 dB). (b) Decimated data \dlo{by}\wen{with} irregularly missing 70\% traces (S/N=-0.21 dB). (c) Reconstructed data using the rank-reduction method (S/N=16.83 dB). (d) Reconstructed data using the NPEF method (S/N=2.93 dB). Note that the NPEF method fails in this case.}
%	\label{fig:ln_noisy5d,ln_obs5d,ln_drr5d,ln_npef5d}
%\end{figure}
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_noisy5d-2}
%    \label{fig:ln_noisy5d2}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_obs5d-2}
%    \label{fig:ln_obs5d2}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_rr5d-2}
%    \label{fig:ln_rr5d2}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_recon5d-2}
%    \label{fig:ln_npef5d2}}\\
%	\caption{Interpolation results of the noisy linear-events example for $Hx=6$ and $Hy=6$. Each common offset cube has bee reshaped into a 2D matrix. (a) Noisy data. (b) Decimated data \dlo{by}\wen{with} irregularly missing 70\% traces. (c) Reconstructed data using the rank-reduction method. (d) Reconstructed data using the NPEF method. Note that the NPEF method fails in this case.}
%	\label{fig:ln_noisy5d2,ln_obs5d2,ln_drr5d2,ln_npef5d2}
%\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_obs5d-3}
    \label{fig:la_obs5d}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_rr5d-3}
    \label{fig:la_drr5d}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_recon5d-3}
    \label{fig:la_npef5d}}\\
	\caption{De-aliased interpolation results of the linear-events example for $X=3$ and $Y=3$. Each common midpoint cube has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the standard rank-reduction method completely fails in this case.}
	\label{fig:la_obs5d,la_drr5d,la_npef5d}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_obs5d-3fk}
    \label{fig:la_obs5dfk}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_rr5d-3fk}
    \label{fig:la_drr5dfk}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_recon5d-3fk}
    \label{fig:la_npef5dfk}}\\
	\caption{\wen{FK spectra of de-aliased interpolation results of the linear-events example for $X=3$ and $Y=3$. Each common midpoint cube has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method.}}
	\label{fig:la_obs5dfk,la_drr5dfk,la_npef5dfk}
\end{figure}

%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{hyper5d/Fig/hyper_clean5d}
%    \label{fig:h_clean5d}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{hyper5d/Fig/hyper_obs5d}
%    \label{fig:h_obs5d}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{hyper5d/Fig/hyper_drr5d}
%    \label{fig:h_drr5d}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{hyper5d/Fig/hyper_recon5d}
%    \label{fig:h_npef5d}}\\
%	\caption{Interpolation results of the noisy hyperbolic-events example for $X=3$ and $Y=3$. (a) Clean data. (b) Irregularly missing data 70\% (S/N=0.59 dB). (c) Reconstructed data using the rank-reduction method (S/N=16.32 dB). (d) Reconstructed data using the NPEF method (S/N=6.38 dB). }
%	\label{fig:h_clean5d,h_obs5d,h_drr5d,h_npef5d}
%\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_obs5d-3}
    \label{fig:ha_obs5d}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_rr5d-3}
    \label{fig:ha_drr5d}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_recon5d-3}
    \label{fig:ha_npef5d}}\\
	\caption{De-aliased interpolation results of the hyperbolic-events example for $X=3$ and $Y=3$. Each common midpoint cube has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the standard rank-reduction method completely fails in this case.}
	\label{fig:ha_obs5d,ha_drr5d,ha_npef5d}
\end{figure}

%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_obs5d-3fk}
%    \label{fig:ha_obs5dfk}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_rr5d-3fk}
%    \label{fig:ha_drr5dfk}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_recon5d-3fk}
%    \label{fig:ha_npef5dfk}}\\
%	\caption{\wen{FK spectra of de-aliased interpolation results of the hyperbolic-events example for $X=3$ and $Y=3$. Each common midpoint cube has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method.}}
%	\label{fig:ha_obs5dfk,ha_drr5dfk,ha_npef5dfk}
%\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_obs5d-3-0}
    \label{fig:r_obs5d}}\\
    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_drr5d-3-0}
    \label{fig:r_drr5d}}\\
    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_npef5d-3-0}
    \label{fig:r_npef5d}}\\
	\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$. Each common offset cube has bee reshaped into a 2D matrix. (a) The raw data gridded onto regular grids. Those blank areas denote missing traces. (b) Reconstructed data using the damped rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the damped rank-reduction outperforms the NPEF method in the case of irregularly missing traces.}
	\label{fig:r_obs5d,r_drr5d,r_npef5d}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cog-zA}
    \label{fig:r_obs5d1a}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cog-zB}
    \label{fig:r_obs5d1b}}\\
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cog-zA}
    \label{fig:r_drr5d1a}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cog-zB}
    \label{fig:r_drr5d1b}}\\
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cog-zA}
    \label{fig:r_npef5d1a}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cog-zB}
    \label{fig:r_npef5d1b}}\\
	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}. Note the strong residual noise seen in (f) caused by the NPEF method. }
	\label{fig:r_obs5d1a,r_obs5d1b,r_drr5d1a,r_drr5d1b,r_npef5d1a,r_npef5d1b}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_obs5d-4-0}
    \label{fig:r_obs5d4}}\\
    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_drr5d-4-0}
    \label{fig:r_drr5d4}}\\
    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_npef5d-4-0}
    \label{fig:r_npef5d4}}\\
	\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$. Each common offset cube has bee reshaped into a 2D matrix. (a) The raw data gridded onto regular grids. Those blank areas denote missing traces. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the damped rank-reduction outperforms the NPEF method in the case of irregularly missing traces.}
	\label{fig:r_obs5d4,r_drr5d4,r_npef5d4}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cmg-zA}
    \label{fig:r_obs5d2a}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cmg-zB}
    \label{fig:r_obs5d2b}}\\
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cmg-zA}
    \label{fig:r_drr5d2a}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cmg-zB}
    \label{fig:r_drr5d2b}}\\
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cmg-zA}
    \label{fig:r_npef5d2a}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cmg-zB}
    \label{fig:r_npef5d2b}}\\
	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4}. Note the obviously more discontinuous events in (e) and (f) caused by the NPEF method.}
	\label{fig:r_obs5d2a,r_obs5d2b,r_drr5d2a,r_drr5d2b,r_npef5d2a,r_npef5d2b}
\end{figure}

\begin{figure}[htb!]
    \centering
   \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3-0}
%    \subfloat[]{\includegraphics[width=1.0\textwidth]{Fig/test2} %eps2pdf problem
    \label{fig:ra_obs5d}}\\
    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_npef5d_new-3-0}
    \label{fig:ra_npef5d}}\\
	\caption{De-aliased interpolation results of the real 5D seismic data example for $Hx=6$ and $Hy=6$. We treat the reconstructed data using the damped rank-reduction method as the starting data and further interpolate a trace every other traces in the $X$ and $Y$ directions. Each common offset cube has bee reshaped into a 2D matrix. (a) The regularly sampled data. Those blank areas denote missing traces. (b) Reconstructed data using the NPEF method. In this case of regularly missing traces, the rank-reduction method completely fails so we omit its result.}
	\label{fig:ra_obs5d,ra_npef5d}
\end{figure}

\begin{figure}[htb!]
    \centering
%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3-0}
    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3fk} %eps2pdf problem
    \label{fig:ra_obs5d_new-3fk}}\\
    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_npef5d_new-3fk}
    \label{fig:ra_npef5d_new-3fk}}\\
	\caption{\wen{FK spectra of de-aliased interpolation results of the real 5D seismic data example for $Hx=6$ and $Hy=6$. (a) The regularly sampled data before interpolation. (b) Reconstructed data using the NPEF method. }}
	\label{fig:ra_obs5d_new-3fk,ra_npef5d_new-3fk}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_obs5d_new-cog-zA}
    \label{fig:r_obs5da}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_obs5d_new-cog-zB}
    \label{fig:r_npef5db}}\\
    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_npef5d_new-cog-zA}
    \label{fig:r_obs5da}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_npef5d_new-cog-zB}
    \label{fig:r_npef5db}}\\
	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:ra_obs5d,ra_npef5d}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:ra_obs5d,ra_npef5d}.}
	\label{fig:ra_obs5da,ra_npef5da,ra_obs5db,ra_npef5db}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=\textwidth]{real5d_smaller_onestep/Fig/os_obs}
    \label{fig:os_obs}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{real5d_smaller_onestep/Fig/os_recon}
    \label{fig:os_recon}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{real5d_smaller_onestep/Fig/ts_recon}
    \label{fig:ts_recon}}
	\caption{\new{Comparison between the two-step and one-step interpolation strategies. (a) Observed data when binned onto the regular grids of two times denser. (b) Reconstructed data by the one-step rank-reduction interpolation strategy. (c) Reconstructed data by the two-step rank-reduction and NPEF interpolation strategy.}  }
	\label{fig:os_obs,os_recon,ts_recon}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/zero2d}
    \label{fig:zero2d}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/recon2d2}
    \label{fig:recon2d2}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/recon2d}
    \label{fig:recon2d}}\\
	\caption{\new{De-aliased interpolation results of the second field data example for a common shot gather. Each gather has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the rank-reduction method completely fails in this case.}}
	\label{fig:zero2d,recon2d2,recon2d}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/zerofk2d}
    \label{fig:zerofk2d}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/reconfk2d2}
    \label{fig:reconfk2d2}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/reconfk2d}
    \label{fig:reconfk2d}}\\
	\caption{\new{FK spectra of de-aliased interpolation results of the second field data example.  Each gather has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method.}}
	\label{fig:zerofk2d,reconfk2d2,reconfk2d}
\end{figure}
}

\section{Discussion}
The anti-aliasing ability of the proposed method could be attributed to the time-space domain implementation of the PEF. Since in time-space domain, multi-scale/frequency components are coupled together, thus it is easier to extract the coherency among the datasets. In the frequency domain, however, the seismic data are separated into different frequencies, causing the problem that low-frequency components are more anti-aliasing while the high-frequency components tend to be aliasing. Traditionally, the anti-aliasing effect of the frequency-space domain interpolation method is achieved by constraining the high-frequency solution via the non-aliased low-frequency solution \cite[]{herrmann2000aliased}. \cite{cary2011aliasing}, however, finds that the low-frequency constraint may not be strong enough to enable the anti-aliasing effect for high-frequency components, which results in a poorly reconstructed data volume that mixes the aliased and non-aliased data. \cite{chiu20135d} develop a 5D anti-aliasing minimum weighted norm interpolation (MWNI) method by a two-step strategy. In the first step, an approximate initial model is obtained. In the second step, the initial model is used to compute the spectral weights to constrain the least-squares solutions of MWNI. Although the method was found to be effective, it is less straightforward and the performance highly depends on initial model. The proposed method, due to its time-domain implementation, is more convenient to conquer the aliasing issue.

Although mathematically the proposed NPEF method is similar to the slope estimation method based on PWD, it does not suffer from the high-frequency limitation as the PWD method.  The reason why PWD method suffers from the high-frequency limit is that one needs to seek an explicit approximation of the phase-shift operator via a third-order and fifth-order filter (as a function of the local slope $\sigma$), e.g., in equations 12 or 13. Only if we have an explicit relation between the phase-shift operator and the local slope $\sigma$ can we use non-linear inversion methods to solve for the local slope. However, the accuracy of the approximation is greatly decreased for high frequencies, as illustrated by Figure 1 in \cite{fomel2002pwd}. However, in the NPEF method introduced here, the local slope is implicitly involved in the prediction filter coefficients $C_{n_t,n_x}(t,x)$. The large approximation error in high frequencies no longer exists.%In other words, in NPEF, we do not care the slope, only care the filter coefficients of PWD.}

We solve the NPEF coefficients due to the convenience and capabilities of the shaping regularization method. It is widely known that the standard L2 norm applied onto the solution is a type of smooth regularization, which, in this regard, is similar to the shaping regularization method. Compared with the shaping regularization, the L2 norm constraint is a global regularization (or global smoothing). The L2 norm regularized inverse problem is usually solved via a damped least-squares method. The damping has the effect of smoothing. Normally, the damping is globally consistent. But via shaping regularization, one can apply a smoothing filter to the solution, which is a local operation. Thus, the shaping regularization better preserves the local features (or resolution) of the solution.

Several synthetic and field datasets show that the NPEF method can be an effective method for interpolating both irregularly sampled data or the more challenging regularly sampled data. Although it is capable of interpolating the irregularly missing traces especially when the S/N is relatively high, it is recommended to be combined with a more advanced interpolation method for irregularly missing traces, e.g., the freely available rank-reduction method ($http://ahay.org/RSF/book/tccs/drr5d/paper\_html/$). The rank-reduction method, however, is less competent in densifying the spatial sampling. In the current interpolation framework, it does not work effectively for very noisy data due to the hard constraint in the interpolation model in equation \ref{eq:inv44}, which means that the existing noisy traces are directly used as the output traces. It is worth investigating an anti-noise strategy by modifying equation \ref{eq:inv44} in the NPEF interpolation framework in the future research.

\section{Conclusions}
We have extended the PEF from common 2D/3D applications to a 5D problem, i.e., 5D seismic data interpolation. The NPEF is the non-stationary version of the PEF filter, where the coefficients of a fixed-size PEF vary with the time and space locations. The NPEF is in a 10D space where the first five dimensions correspond to the filter coefficients for a specific point in the 5D data space. To solve the highly ill-posed inverse problem that involves the 10D NPEF, we use the \new{computationally efficient} shaping regularization method, where the solution is constrained to be smooth with \old{an efficient 5D}\new{a} triangle smoothing operator. To interpolate the missing traces, another inverse problem needs to be solved, where the solution is constrained by the 10D NPEF. The performance of the proposed NPEF method is tested by two synthetic and a real seismic dataset, in the cases of both irregularly sampled and regularly sampled traces, and benchmarked with the state-of-the-art rank-reduction method. Results show that the proposed method outperforms the rank-reduction method in interpolating regularly sampled seismic data although \dlo{being}\wen{is} less effective in reconstructing the irregularly missing traces \new{especially in the presence of strong random noise}.

\section{DATA AND MATERIALS AVAILABILITY}
Data associated with this research are available and can be obtained by contacting the corresponding author.

%\inputdir{test}
%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
%\multiplot{2}{test1,test2}{width=0.45\textwidth}{(a) Caption a. (b) Caption b.}

\bibliographystyle{seg}
\bibliography{npef}

\newpage
\listoffigures

%\begin{figure}[htb!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
%	\caption{Caption.}
%	\label{fig:fig}
%\end{figure}

%\begin{figure}[htb!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
%    \label{fig:fig1}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
%    \label{fig:fig2}}\\
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure}

%\begin{figure*}[ht!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
%    \label{fig:fig1}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
%    \label{fig:fig2}}\\
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure*}

%\begin{table}[h]
%\caption{Table caption}
%\begin{center}
%     \begin{tabular}{|c|c|c|c|c|c|} 
%	  \hline Column1 (unit)  & Column2 (unit) & Column3 (unit) \\ 
%	  \hline 1 & 2  & 3 \\
%       \hline
%    \end{tabular} 
%\end{center}
%\label{tbl:table1}
%\end{table}

### 2021-03-08 elrme5d/paper.tex
up

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}
%\usepackage{xspace}
% combine suggestions from @bdh_dtu and @egreg with xspace
\newcommand{\R}{\textup{\textrm{R}}\xspace}
\newtheorem{Assumption}{Assumption}

\title{Enhanced low-rank matrix estimation for simultaneous denoising and reconstruction of five-dimensional seismic data}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\author{Yapo Abol{\'e} Serge Innocent Obou{\'e} and Yangkang Chen}

\ms{GEO-2021}

\address{Zhejiang University\\
	School of Earth Sciences\\
	Hangzhou, Zhejiang, China\\
	obouesonofgod1@gmail.com \& chenyk2016@gmail.com\\
	Corresponding Author: Yangkang Chen (chenyk2016@gmail.com) 
}

\lefthead{Obou{\'e} and Chen}
\righthead{Enhanced low-rank matrix estimation}

\maketitle

\begin{abstract}			
  Noise and missing traces usually influence the quality of multidimensional seismic data. It is, therefore, necessary to estimate the useful signal from its noisy observation. The damped rank-reduction (DRR) method has emerged as an effective method to reconstruct the useful signal matrix from\dlo{its} noisy \wen{and incomplete  observations}\dlo{observation}. However, the higher the noise level and the \wen{larger} ratio of missing traces, the weaker the DRR operator becomes. Consequently, the estimated low-rank signal matrix includes a \dlo{meaningful}\dlo{unignorable}\wen{significant} amount of residual noise that influences the \dlo{next}\wen{following} processing steps. \dlo{In this paper, we focus}\dlo{This paper focuses}\wen{Therefore, we focus} on the problem of estimating a low-rank signal matrix from its noisy observation. To elaborate on the novel algorithm, we formulate an improved proximity function by mixing the moving-average filter and the arctangent penalty function. We first apply the proximity function to the level-4 block Hankel matrix before the singular value decomposition (SVD), and then, to singular values, during the damped truncated SVD process. The \dlo{relationship between}\wen{combination of} the novel proximity function and the DRR framework leads to an optimization problem, which results in better recovery performance. The proposed algorithm aims at producing an enhanced rank-reduction operator to estimate the useful signal matrix with a higher quality. Experiments are conducted on synthetic and real 5-D seismic data to compare the effectiveness of our approach to the DRR approach. The proposed approach \dlo{is shown to obtain}\wen{obtains} better performance since the estimated low-rank signal matrix is cleaner and contains \dlo{less amount of}\wen{fewer} artifacts compared to \dlo{the}\wen{that reconstructed by the} DRR algorithm.
\end{abstract}

\section{Introduction}

High\dlo{er} quality of seismic data is valuable for all processing steps in exploration seismology. However, physical limitations and \dlo{probably financial costs}\wen{economical considerations} in \dlo{a}multidimensional seismic data acquisition \dlo{process}often \dlo{induce}\wen{introduce} noisy and \dlo{sub-sampled}\wen{poorly sampled} data \citep{chiu2014multidimensional}. Therefore, the recovery \wen{of the useful signal} from noisy and incomplete data becomes one of the most significant tasks confronted by seismic data processing researchers. \dlo{Over the years, m}\wen{M}any useful algorithms have been introduced in seismic data processing literature to solve the multidimensional seismic data acquisition problems. Otherwise, the incompleteness of the raw data could seriously affect the processing and imaging steps \citep{chen2015random,lopez2015closed,ikelle2016up}.

In this context, approaches like wave-equation methods \citep{ronen1987wave,fomel2003seismic} that \dlo{need some basic knowledge of the subsurface}\wen{require subsurface knowledge} such as the velocity model have been proposed to restore the incomplete data. \dlo{Besides, several}\wen{Numerous} researchers \citep{spitz1991seismic,porsani1999seismic,crawley2000seismic,curry2003interpolation,liu2015adaptive,fomel2016streaming,wanghang2021geo} have introduced approaches based on the linear prediction-error filters (PEFs) to recover the useful signal. \cite{fomel2016streaming} introduce\dlo{d} the streaming PEFs and propose\dlo{d} a fast method for missing data restoration. \cite{li2017multidimensional} propose\dlo{d} a multidimensional adaptive PEF in the frequency domain for aliased seismic data interpolation. Based on the shaping regularization, this approach enhances the \dlo{computation}\wen{computational} performance. Generally, the rank of the seismic data tensor or matrix increases because of the \dlo{noise level and the ratio of sub-sampled traces}\wen{existence of noise and missing traces}. This assumption has motivated the \dlo{invention}\wen{development} of the low-rank methods for seismic data restoration. Low-rank \wen{(LR)} methods \dlo{can be seen as approaches based on}\wen{may be thought of as} decomposition techniques, for instance, higher-order singular value decomposition (HO-SVD) introduce\dlo{d} by \cite{de2000multilinear}. \dlo{Such a}\wen{This} method works directly on the seismic data tensor to restore the useful signal \citep{kreimer2012tensor,kreimer2013tensor,ely20155d,carozzi2019robust}. \dlo{We mention}\dlo{There is also a}\wen{A}nother subgroup of LR methods \dlo{Then, as approaches} \dlo{that include}\wen{includes} all the seismic data components into a matrix such as the Hankel or Toeplitz matrix \citep{gao2013fast,siahsar2017simultaneous,zhang2017hybrid,oboue2020robust}. Here, the algorithms restore the whole seismic data volume by the low-rank approximation strategy, and then apply the averaging function \citep{chen2016open} on the resulting approximation signal matrix. Finally, the weighted POCS-like algorithm based on the rank-reduction method is utilized to complete the missing values \wen{\citep{oropeza2011simultaneous}}. 
\dlo{Over time, the seismic data components have been inserted into a designed texture-patch matrix and the matrix completion (MC) algorithm has been applied to solve the optimization problem. This approach has shown its efficiency compared with the Hankel matrix-based approaches.}\dlo{Researchers like}\cite{oropeza2011simultaneous}, \cite{gan2015simultaneous}, \cite{gao2015parallel}, \cite{chen2016simultaneous} and \cite{oboue2020robust}\dlo{brought their contribution in}\wen{contributed to} the research area of simultaneous denoising and reconstruction to solve the multidimensional seismic data interpolation problem. Furthermore, five-dimensional \wen{(5-D)} seismic data restoration \citep{ely20155d,chen2016simultaneous}\dlo{appeared and, \dlo{become}\wen{became}}\wen{has become} more common since it considers all the physical coordinates of the seismic data to restore the useful signal matrix or tensor. Although almost all low-rank methods demonstrate\dlo{d} their \dlo{performance}\wen{ability} to perfectly denoise and/or reconstruct the seismic data, computation time remains a problem for most\dlo{ of them}. 
Therefore, some efficient approaches \dlo{: for instance,}\wen{like the randomized singular value decomposition (RSVD) \citep{oropeza2011simultaneous,halko2011finding}, the SVD-free techniques \citep{gao2015parallel} and the Lanczos bidiagonalization \citep{gao2013fast} are more often applied to \dlo{enhance}\wen{decrease} the computation cost}. Besides, mixed approaches based on the sparsity transforms and rank-reduction approaches \citep{zhang2017hybrid} have been proposed to restore the seismic signal while reducing the computation cost. On the other hand, some \dlo{meaningful}\wen{sparsity-promoting} transform\dlo{s} techniques such as Fourier transform \citep{zwartjes2007fourier}, \dlo{Random}\wen{Radon} transform \citep{xue2017amplitude}, curvelet transform \citep{liu2016effective}, seislet transform \citep{gan2015dealiased,gan2016compressive,liu2016one}, and sparse wavelet transform \citep{liu2015seismic,mostafa2016bssa,mostafa2016geo} have appeared to successfully recover the seismic data. \wen{\cite{wanghang2020tgrs3} introduce\dlo{d} the fast dictionary learning for high-dimensional seismic reconstruction.}

\wen{The damped rank-reduction (DRR) method \citep{chen2016simultaneous} has been proposed to further enhance the quality of the simultaneous denoising and reconstruction of seismic data. The DRR method successfully improve\wen{s}\dlo{d} the quality of the low-rank signal matrix even when the land seismic data are affected by strong noise and missing traces. As outlined in \cite{chen2016simultaneous}, the damped TSVD (DTSVD) process aims to produce the closest approximation to the useful signal matrix from its noisy observation. However, the DTSVD operator, which uses essentially the rank constraint and the damping factor, becomes \dlo{weak}\wen{less effective} when the noise level and the percentage of missing traces increase. As a result, the estimated signal matrix is still corrupted with a significant amount of residual noise after the DTSVD operation. Therefore, it is necessary to enhance the quality of the estimated signal matrix by implementing a new approach.}

\wen{The \dlo{${l}_{1}$}\wen{${l}_{1}$-}norm minimization technique that can be regarded as applying the proximity operator associated with the soft-threshold function \citep{donoho1995noising} has been used to promote sparsity, and thus, enhance\dlo{d} seismic data restoration. This proximity function can minimize the non-null signal values when it is applied to promote sparsity \citep{nadakuditi2014optshrink}. However, the non-convex regularization function such as the arctangent penalty function has been preferred to compute the non-null signal values carefully \citep{parekh2017improved} because of its abilities \dlo{Furthermore, it has been demonstrated that the non-convex penalty functions can}\wen{to further} induce sparsity of the singular values more effectively than the nuclear norm \citep{chartrand2012nonconvex,parekh2016enhanced,parekh2017improved}. Therefore, i}\dlo{I}n this work, we \dlo{favor}\wen{leverage} the proximity operator using the arctangent penalty function \citep{selesnick2014sparse,parekh2017improved} \wen{to restore the low-rank signal matrix more accurately}.

\wen{To achieve the goal of this work,} we formulate first, a proximity function using the moving-average filter \citep{schafer1989discrete} and the arctangent penalty function \citep{selesnick2014sparse,parekh2017improved}. Then, by introducing the proposed proximity function in the DRR algorithm workflow, we discuss the problem of computing a signal matrix from its noisy and incomplete observation. We introduce an optimization problem composed of a noisy and incomplete seismic signal, the DRR operator, and the \wen{proposed} proximity operator. We derive an algorithm called enhanced low-rank matrix estimation (ELRME) for 5-D seismic data recovery to solve the optimization problem. \dlo{Our}\wen{The proposed ELRME} approach will benefit from the use\wen{s} of the rank constraint and the damping factor \citep{chen2016simultaneous}, and the proposed proximity function to provide a more accurate low-rank signal matrix. \wen{In addition to the key parameters of the DRR method, the proposed ELRME method uses a valid combination of parameters of the proposed proximity function for the estimation of the useful signal matrix. The proposed ELRME method produces an improved low-rank operator to compute the useful signal matrix correctly compared to the DRR algorithm.}

The paper starts by briefly emphasizing the essential steps of the DRR algorithm. Afterward, we develop the proposed algorithm. Then, we conduct numerical experiments using synthetic and field 5-D seismic data to compare the effectiveness of the proposed approach to the DRR approach. \dlo{The results show a better performance of the proposed ELRME algorithm. Finally, discussion and conclusions are given.}

\section{Theory}

\subsection{Damped rank-redcution method (DRR)}

The DRR algorithm \dlo{computes}\wen{estimates} the signal matrix $\mathbf{B}\in R^{I \times J}$ from its noisy observation \dlo{$\mathbf{A}$}{\wen{$\mathbf{D}\in R^{I \times J}$}}. The matrix \dlo{$\mathbf{A}$}\wen{$\mathbf{D}$} \dlo{written as follows} is a blend of the matrix $\mathbf{B}$ and random noise $\mathbf{N}\in R^{I \times J}$ acquired \dlo{during}\wen{by} the acquisition process\wen{, which can be expressed as follows:}
\begin{equation}
\mathbf{D} = \mathbf{B}+\mathbf{N}.  
\label{eq:eq1}                  
\end{equation}
Consider an observed 5-D seismic data denoted by $\mathbf{D}(t, hx, hy, x, y)$. $t$ corresponds to the time \dlo{compoment}\wen{component}. $hx$, $hy$, $x$ and $y$ correspond to $x$ and $y$ offsets and $x$ and $y$ midpoints. To restore the useful signal matrix $\mathbf{B}$ from such noisy observation, the DRR algorithm converts first, the observed data defined in time domain into $\mathbf{D}(f, hx, hy, x, y)$, where $f$ denotes the frequency component\dlo{s}. In this process, each observed noisy and incomplete data for a known frequency band is modeled by a four-dimensional spatial multilevel cube $\mathbf{D}_{n_1,n_2,n_3,n_4}$ with $n_v = 1 \cdot\cdot\cdot T_v$, {$v = 1,2,3,4$}. As outlined in \cite{chen2016simultaneous}, the DRR algorithm for \dlo{the estimation of the}\wen{estimating} signal $\mathbf{B}$ is achieved by constructing the level-four block Hankel matrix. Let {$\textbf{A}$} be this target matrix. We summarize the Hankelization process via equation \ref{eq:eq2}:
\begin{equation}
\mathbf{A}={\mathcal{H}}\mathbf{D},     
\label{eq:eq2}               
\end{equation}
where ${\mathcal{H}}$ is the Hankelization operator \citep{oropeza2011simultaneous,chen2016simultaneous}. 
\wen{Equation \ref{eq:eq2} can be rewritten as follows:}
\begin{equation}
\mathbf{A} = \mathbf{B}+\mathbf{N}.  
\label{eq:eq3}                  
\end{equation}
The DRR approach assumes that $\mathbf{A}$ and $\mathbf{N}$ have complete rank unlike $\mathbf{B}$. Hence, we suppose that $rank(\mathbf{A})=rank(\mathbf{N}) = J$, and $rank(\mathbf{B})= K < J$. The estimated signal $\mathbf{X}$ using the damped rank-reduction algorithm \wen{\citep{chen2016simultaneous}} is given as follows:
\begin{align}
\mathbf{B}=\mathbf{U}^{\mathbf{A}}_1{\Sigma^{\mathbf{A}}_1}\ell\left(\mathbf{V}^{\mathbf{A}}_1\right)^{{r}},
\label{eq:eq4}
\end{align}
where ${\Sigma^{\mathbf{A}}_1}$ corresponds to the diagonal matrix which is composed of larger singular values. The \dlo{matrix}\wen{matrices} $\mathbf{U}^{\mathbf{A}}_1$ and $\left(\mathbf{V}^{\mathbf{A}}_1\right)$ have singular vectors. $\left(\cdot\right)^{{r}}$ corresponds to the conjugate transpose. Equation \ref{eq:eq4} is known as \dlo{the damped truncated singular values decomposition (}DTSVD\dlo{)} used in the DRR algorithm. \wen{The DTSVD process is based on the damping operator $\ell$ given by:}
\begin{align}
\ell= \mathbf{I} - (\Sigma^{\mathbf{A}}_1 )^{-{q}}{{\gamma}^{q}},
\label{eq:eq5}
\end{align} 
\wen{where} ${\gamma}$ represents the maximum element of the smaller singular values, \dlo{and}${q}$ corresponds to the damping factor\dlo{.}\wen{, and} \wen{$\mathbf{I}$ denotes an identity matrix.}

The process of obtaining the estimated signal matrix $\mathbf{B}$ from $\mathbf{A}$ using the DRR method formula (see equation \ref{eq:eq4}) is summarized by:
\begin{equation}
\mathbf{B}={R_\ell}{\mathbf{{A}}}, 
\label{eq:eq6}
\end{equation}
where ${R_\ell}$ is the DRR operator \wen{\citep{chen2016open,chen2016simultaneous}}.

\subsection{Enhanced low-rank matrix estimation for 5-D seismic data recovery}

\dlo{Our experience with the DRR algorithm shows that ${R_\ell}$ becomes weak when the noise level and the percentage of missing traces increase. This operator cannot estimate the low-rank matrix $\mathbf{B}$ well}\wen{The operator ${R_\ell}$ bases essentially on the rank constraint and the damping factor to further recover the useful signal matrix, which is still blended with the noisy matrix after the TSVD process. As explained in \cite{chen2016simultaneous}, the aim of the DTSVD process is to provide the closest approximation to the low-rank matrix $\mathbf{B}$ based on the noisy observation matrix $\mathbf{A}$. As shown in equation \dlo{\ref{eq:eq4}}\wen{\ref{eq:eq5}}, the damping factor is directly applied to the singular values of the noisy observation matrix $\mathbf{A}$ after TSVD to drop the noise components. \wen{However, our experience with the DTSVD process reveals that the ${R_\ell}$ operator becomes weak when the noise level and the percentage of missing traces increase.} \dlo{However, as the noise level and the percentage of missing traces increase, the diagonal matrix that includes the singular values becomes noisier and sparse. Hence,}\wen{Indeed,} the damping factor loses its power to ease the contribution of noise. As a result, the DRR algorithm cannot obtain an approximation signal $\mathbf{B}$ closest to the original signal matrix. In this work, we assume that the DRR algorithm becomes less effective because of the weakness of \wen{the performance of} its operator (${R_\ell}$) to further shrink the singular values in a condition of strong noise and a high level of missing traces.} This paper intends to estimate an improved low-rank matrix signal $\mathbf{B}$ based on a new strategy. \wen{We first formulate an improved proximity function by mixing the moving average filter and the arctangent penalty function. \dlo{The resulted proximity function aims to enhance the DTSVD process.} Next, we apply the new proximity function to the level-4 block Hankel matrix before SVD, and then, to the singular values, during the DTSVD process. This \dlo{novel}\wen{modified} strategy produces an enhanced RR operator to further shrink the singular values, even when the noise level and the ratio missing traces increase\dlo{s}.}

\wen{The moving average filter \wen{for the noisy observation matrix $\mathbf{A}$} is given by}: 
\begin{equation}
\mathbf{A}[i] =\frac{1}{\varphi}\sum_{j=0}^{\varphi-1}\mathbf{A}\left[i-j\right],
\label{eq:eq7}
\end{equation}
where $\varphi$ corresponds to the filter length and $\varphi-1$ denotes the filter order.

\wen{Equation \ref{eq:eq7}} uses the following rational transfer function to minimize the unwanted values in ${\mathbf{{A}}}$:
\begin{equation}
{P(h)=\frac{c(1)+c(2)h^{-1}+...+c(l_c + 1)h^{-l_c}}{1+d(2)h^{-1} +...+ d(l_d+1)h^{-l_d}}}{Q(h)}.
\label{eq:eq8}
\end{equation}
Equation \ref{eq:eq8} establishes a relationship between the rational transfer function $P(h)$ of a discrete-time filter's output $P(i)$ and rational transfer function $Q(h)$ of the input $Q(i)$. ${c_i}$ and ${d_i}$ are the filter coefficients. $l_d$ denotes the feedback filter order, and $l_c$ corresponds to the feed forward filter order. We set $d(1) = 1$ because of the normalization \citep{schafer1989discrete}. \wen{In this work, we set $d(1) = \beta$ and $l_d=0$. $\beta$ corresponds to a given filter coefficient of the moving average filter\wen{, which can be}\dlo{ It can be} regarded as a scaling factor.}

We simplify the moving-average function via the following notation: 
\begin{equation}
\mathbf{A}=\mathbf{{A}_{(\varphi,\beta)}},   
\label{eq:eq9} 
\end{equation}
where $\varphi$ and $\beta$ denote the filter length and the rational transfer function coefficient, respectively.

The proximity operator joined with the arctangent penalty function \citep{selesnick2014sparse,parekh2017improved}, is given by:
\begin{align}
\textrm{prox}_{\psi}(\mathbf{A};\lambda,{c}) = \textrm{arg}\min_{\mathbf{B} \in R}\left\lbrace \frac{1}{2}\left(\mathbf{A}-\mathbf{B} \right) ^2 +\lambda\psi\left(\mathbf{B},{c} \right)\right\rbrace,
\label{eq:eq10}
\end{align}	
where $\lambda$ denotes the threshold parameter. The term \dlo{$ \psi\left(\mathbf{X},{c} \right)$}\wen{$ \psi\left(\mathbf{B},{c} \right)$} correspond\dlo{s}\wen{ing} to the arctangent penalty function \citep{selesnick2014sparse} \wen{is} given by:
\begin{equation}
\psi\left(\mathbf{B},{c} \right)=\frac{2}{{c} \sqrt{3}}\left(\textrm{atan}\left( \dfrac{1+2{c} \left|\mathbf{B}\right|}{\sqrt{3}}\right) -\frac{\pi}{6}\right),
\label{eq:eq11}
\end{equation}	
where ${c}>0 $ denotes the penalty convexity parameter. The value of ${c}$ produces the level of the non-convexity of the penalty functions $ \left(\psi\right) $ \citep{parekh2017improved}.

Equation \ref{eq:eq11} satisfies \wen{the following} $\mathbf{Assumption}$ $\mathbf{1}$. $\psi\left(\mathbf{B},{c} \right)$ is asymptotically near the identity function \citep{selesnick2014sparse}. \dlo{Mention that, contrary}\wen{Unlike} the proximity operator using the \dlo{${l}_{1}$}\wen{${l}_{1}$-}norm known as the soft-threshold function \citep{donoho1995noising}, which minimizes non-zero values, the proximity operator expressed in equation \ref{eq:eq11} considers the non-zero values more correctly than the soft-threshold function \citep{parekh2017improved}.

\begin{Assumption}
$\psi$ : $R \rightarrow R $ obeys the following\\
	1. $\psi$ is continuous on R, twice differentiable on $R\backslash\left\lbrace 0\right\rbrace$ and symmetric, \dlo{e.i.,}\wen{i.e.,} $\psi\left(-B,c \right) = \psi\left(\mathbf{B},c \right)$\\
	2. $ \psi^{'}\left(\mathbf{B},c \right)>0, \mathbf{B}>0 $\\	
	3. $ \psi^{''}\left(\mathbf{B},c \right)\leq 0, \mathbf{B}>0 $\\	
	4. $ \psi^{'}\left(0^{+}\right) = 1 $\\
	5. $\inf_{\mathbf{B}\neq 0}\psi^{''}\left(\mathbf{B},c \right)= \psi^{''}\left( 0^{+};c \right)=-c$
\end{Assumption}

The performance of \dlo{both aforementioned operators}\wen{the moving average filter and the proximity operator joined with the arctangent penalty function} motivates us to combine the\wen{ir} advantages \dlo{of each}to better enhance the estimation of the matrix $\mathbf{B}$. From equation\wen{s} \ref{eq:eq8} and\dlo{equation} \ref{eq:eq9}, we can obtain a compromise between the moving-average filter and the arctangent penalty function. By combining these equations, we formulate an improved proximity operator defined as follows:
\begin{align}
\textrm{prox}_{\psi}(\mathbf{A};\varphi,\beta,\lambda,{b}) = \textrm{arg}\min_{\mathbf{B} \in R}\left\lbrace \frac{1}{2}\left(\mathbf{A}-\mathbf{B} \right)^2 +\omega\beta\lambda\psi\left( \mathbf{B},{b} \right)\right\rbrace\dlo{,}\new{.}
\label{eq:eq12}
\end{align}		
Equation \dlo{\ref{eq:eq11}}\wen{\ref{eq:eq12}} denotes the proposed proximity operator based on the moving-average filter and the arctangent penalty function. The following parameters characterize this function: the window size $\omega$, the rational transfer function coefficient $\beta$, the threshold parameter $\lambda$ and the penalty convexity parameter ${b}$. \wen{The proposed proximity function aims to enhance the DTSVD process.}

To estimate the signal matrix $\mathbf{B}$ from $\mathbf{A}$, we introduce the function defined in equation \ref{eq:eq11} into the DRR algorithm framework and \dlo{we}propose the following optimization problem:
\begin{align}
\textrm{arg}\min_{\mathbf{B} \in R}\left\lbrace F(\mathbf{B}):=\frac{1}{2}
\left\|\mathbf{A} - \mathbf{B}\right\|_F^2 + \varphi_0\beta_0\lambda_0
\sum_{i=1}^{k}\psi\left(\sigma_i\left( \mathbf{B}\right),{b_0} \right) + \varphi_1\beta_1\lambda_1\sum_{i=1}^{I}\sum_{j=1}^{J}\psi\left(\mathbf{B_{i,j}},{b_1} \right)\right\rbrace.
\label{eq:eq13}
\end{align}	
Equation \ref{eq:eq13} corresponds to the optimization problem based on the proposed proximity function and the damped rank-reduction operator. Hence, the rank constraint and the damping factor are some key parameters to solve it. The term $\sigma_i\left(\mathbf{B}\right)$ denotes the singular values of the matrix $\mathbf{B}^{I \times J} $. $\psi : R \rightarrow R$ denote\wen{s} a parameterized non-convex penalty function with $k = min \left( I, J\right) $. $\lambda_i \geq 0$ correspond to the regularization parameters. ${b_i} > 0$ are the penalty convexity parameters. The window size and the rational transfer function coefficients are denoted by $\varphi_i$ and $\beta_i$, respectively.

\wen{We solve \dlo{equation}the optimization problem in the following way: \dlo{first,}the proposed proximity function is directly applied to the input noisy and incomplete matrix $\mathbf{{A}}$ after the Hankelization operation (before SVD) and then, to the larger singular values of (${\Sigma^{\mathbf{A}}_1}$) during the ${R}_{\ell}$ process.}

To reach the goal of this work, we set the regularization parameters $\lambda_i$ as:   
\begin{equation}
\lambda_0 = \delta_0\times\sqrt{\textrm{length}(\sigma_i\left( \mathbf{B}\right))}\slash{\textrm{length}(\sigma_i\left(\mathbf{B}\right))},
\label{eq:eq14}
\end{equation}
\begin{equation}
\lambda_1=\frac{\delta_1\times \left\| \textrm{max}\left(\mid \mathbf{A} \mid \right) \right\|_0 .}{\sigma \times \left(\left\| \textrm{max}\left(\mid \mathbf{A} \mid \right) \right\|_0 + \sqrt{\textrm{length}(\mathbf{A})} \right)},
\label{eq:eq15}
\end{equation}
where $\left\|\cdot\right\|_0$ corresponds to the $l_0$ norm and $\sigma$ stands for the noise standard deviation in $\mathbf{A}$. $\delta_0$ and $\delta_1 \in R$ are the values used to regulate and control $\lambda_0$ and $\lambda_1$, respectively. \dlo{We solve equation \ref{eq:eq13} in the following way: first, the proposed proximity function is directly applied to the input noisy and incomplete matrix $\mathbf{{A}}$ after the Hankelization operation (before SVD) and then, to the larger singular values of (${\Sigma^{\mathbf{A}}_1}$) during the ${R}_{\ell}$ process.}

By solving equation \ref{eq:eq13}, we enhance the DRR operator to provide an improved estimated low-rank signal matrix: 	 
\begin{equation}
\mathbf{\tilde{B}}={R}_{e\ell}{\mathbf{{A}}}, 
\label{eq:eq16}
\end{equation}
where $\mathbf{\tilde{B}}$ denotes the estimated signal matrix using the proposed algorithm. ${R}_{e\ell}$ is the enhanced damped rank-reduction operator used to solve equation \ref{eq:eq13}.

The averaging function is then applied along the anti-diagonal of the estimated signal matrix $\mathbf{\tilde{B}}$:
\begin{equation}
\mathbf{\hat{D}}={M}\mathbf{\tilde{B}}={M}{R_{e\ell}}\mathbf{A}={M}{{R_{e\ell}}}\mathbf{{\mathcal{H}}\mathbf{D}}={F}_{e\ell}\mathbf{{D}},
\label{eq:eq17}
\end{equation}
where ${M}$ and ${F}_{e\ell}$ correspond to the averaging operator and the proposed\dlo{approach} filter, respectively.
\label{eq:eq18}
Then, the enhanced filter ${F}_{e\ell}$ is used to update the weighted iterative algorithm based on the DRR method as follows: 
\begin{equation}
\mathbf{D}_i= a_{i}\mathbf{D}_o + (1 - a_{i}{L})\circ{F}_{e\ell}\mathbf{D}_{i - 1},  i = 1, 2, 3, . . . , i_{max}, 
\end{equation}
where $\mathbf{D}_0=\mathbf{D}_o$ corresponds to the observation matrix. The iteration scalar denoted by $a_{i}$, diminishes gradually from $a_1=1$ to $a_{i_{max}}=0$. ${L}$ corresponds to the sampling operator. Moreover, the elements of ${L}$ correspond to \dlo{$ 1 $}\wen{one} when the observation is non-zero, otherwise \dlo{$0$}\wen{zero} when missing values. $\circ$ is the Hadamard product.\dlo{utilized to multiply two matrices having the same size.}

The solution for the proposed enhanced low-rank matrix estimation (ELRME) for \dlo{five-dimensional}\wen{5-D} seismic data interpolation can be outlined as follows:

\begin{center}
	\begin{algorithm}[H]
		\DontPrintSemicolon
		$\mathbf{D}_o(f, hx, hy, x, y)\leftarrow \mathbf{D}_o(t, hx, hy, x, y)$ via 1-D forward FFT\;    
		$\mathbf{D}_0\leftarrow\mathbf{D}_o$\;
		\For{$f\leftarrow 1,2,\dots,{F}$}{
			\For{$i\leftarrow 1,2,\dots,i_{max}$}{
				$\mathbf{D}^f_i \leftarrow a_i\mathbf{D}^f_{o} + (1 - a_i){LF}_{e\ell}\mathbf{D}^f_{i-1} + (1 - {L}){F}_{e\ell}\mathbf{D}^f_{i-1}$\;
				\If{$\left\|\mathbf{D}^f_i - \mathbf{D}^f_{i-1}\right\|_F^2\leq Tol$}{
					\textbf{return} $\mathbf{D}^f_i$\;
				}
				\textbf{return} $\mathbf{D}^f_{i_{max}}$\;
			}
			\textbf{return} $\mathbf{D}_{restored}$\;
		}
		$\mathbf{D}_{restored}(t,h_{x}, h_{y}, x, y)\leftarrow \mathbf{D}_{restored}(f,h_{x}, h_{y}, x, y)$ via 1-D inverse FFT\;

		\caption{Enhanced low-rank matrix estimation (ELRME) algorithm ({${L}$}, {${F}_{e\ell}$}, {$\mathbf{D}_{o}$}, {$a_{i}$}, {$Tol$}, {$i_{max}$}, {${F}$})}

	\end{algorithm}
\end{center}

After the completion of the given frequency band ${F}$, \dlo{the process of iteration ceases and,} the code stops running when the maximum number of iteration ({$i_{max}$}) is reached or when {$\left\|\mathbf{D}^f_i - \mathbf{D}^f_{i-1}\right\|_F^2\leq Tol$} for each ${F}$. The \wen{given} tolerance and the Frobenuis norm are denoted by $Tol$ and {$\left\|\cdot\right\|_F$}, respectively.

\section{Examples}

We use two \wen{highly decimated} 5-D synthetic data \wen{sets}\dlo{seriously decimated} ($80\%$ missing traces)\dlo{and} contaminated with random noise ($0.2$ as noise variance), and one 5-D field seismic data (about $75\%$ missing traces) to show the performance of our approach. The size\wen{s} of the three data matrices \dlo{is}\wen{are} given by $t\times h_{x}\times h_{y}\times x \times y$, where $ h_{x}\times h_{y}\times x \times y $ indicates the size of the four spatial dimensions of the model with $t$ time samples per trace. The first synthetic data \wen{set} includes linear events, and the second includes curved events.

\subsection{Synthetic data examples}

The \dlo{first 5-D synthetic data matrix model is $100\times 10\times10\times10\times10$}\wen{size of the first 5-D synthetic data matrix model is $100\times 10\times10\times10\times10$}. Figures \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-drr-hxhy,synth-elrme-hxhy} and \ref{fig:synth-clean-xy,synth-noisy-xy,synth-obs-xy,synth-drr-xy,synth-elrme-xy} illustrate the effectiveness in \old{one}common midpoint and \old{one}common offset gathers, respectively. The true data \old{is}\new{are} displayed in Figures \ref{fig:synth-clean-hxhy} and \ref{fig:synth-clean-xy}. We synthetically generate noisy data by adding \old{a}\new{the} noise \old{of}\new{with} 0.2 variance \dlo{of $0.2$}to the true data. We plot the noisy data in Figures \ref{fig:synth-noisy-hxhy} and \ref{fig:synth-noisy-xy}. Then, we randomly decimate $80\%$ of traces of the noisy data to produce the noisy observation data matrix displayed in Figures \ref{fig:synth-obs-hxhy} and \ref{fig:synth-obs-xy}. Using \old{$10$}\new{ten} weighted POCS-like iterations and a band of frequencies \old{varied}\new{varying} from $0$ to $125$ Hz, we apply both algorithms to estimate the useful signal. We apply the DRR algorithm with rank ${n}=3$ and damping factor ${q}=3$. Figures \ref{fig:synth-drr-hxhy} and \ref{fig:synth-drr-xy} \old{display the results. From these figures, we find that even}\new{show that} though the results are acceptable, the coherent events are not well restored, mainly because of residual noise. Therefore, the use of the proposed algorithm becomes more necessary to enhance the quality of the estimated signal. We select the following parameters: rank ${n}=3$, damping factor ${q}=3$, windows size ${\varphi_0=\varphi_1}=1$, rational transfer function coefficients ${\beta_0}=0.971$ and ${\beta_1}=0.977$, cooling factors $\delta_0 = 3.75$ and $\delta_1 = 3.25$, penalty convexity parameters ${b_0}=25$ and ${b_1}=23$. The results using our algorithm are plotted in Figures \ref{fig:synth-elrme-hxhy} and \ref{fig:synth-elrme-xy}. Compared to that of the DRR method, our results are much better. \dlo{The signal events are cleaner and well restored.}It is visible that the ELRME algorithm can better recover the detailed features of the signal matrix than the DRR algorithm.

\inputdir{synth_linear}
\multiplot{5}{synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-drr-hxhy,synth-elrme-hxhy}{width=0.3\textwidth}{Common midpoint 3-D figures comparison ($x$ = 5, $y$ = 5) between two algorithms after \old{10}\new{ten} iterations and frequency band from 0 to 125 Hz. (a) Original data. (b) Noisy data with $0.2$ as noise variance. (c) Observed noisy and incomplete data with $80\%$ of missing traces. (d) Simultaneously denoised and reconstructed data using the DRR approach. (e) Simultaneously denoised and reconstructed data using the proposed approach.}

\inputdir{synth_linear}
\multiplot{5}{synth-clean-xy,synth-noisy-xy,synth-obs-xy,synth-drr-xy,synth-elrme-xy}{width=0.3\textwidth}{Common offset 3-D figures comparison ($hx$ = 5, $hy$ = 5) between two algorithms after \old{10}\new{ten} iterations and frequency band from $0$ to $125$ Hz. (a) Original data. (b) Noisy data with $0.2$ as noise variance. (c) Observed noisy and incomplete data with $80\%$ of missing traces. (d) Simultaneously denoised and reconstructed data using the DRR approach. (e) Simultaneously denoised and reconstructed data using the proposed approach.}

We further highlight the performance of the proposed algorithm by deducting each recovered data from the original data. Such results that correspond to the recovery error of each approach in one common midpoint and\old{one} common offset gathers are displayed in Figure \ref{fig:synth-drr-hxhy-e,synth-elrme-hxhy-e,synth-drr-xy-e,synth-elrme-xy-e}. Figures \ref{fig:synth-drr-hxhy-e} and \ref{fig:synth-drr-xy-e} are \old{from}\new{obtained by} the DRR algorithm. The recovery error using the our algorithm is displayed in Figures \ref{fig:synth-elrme-hxhy-e} and \ref{fig:synth-elrme-xy-e}. \old{From this result, it is more obvious that the proposed algorithm works better with less denoising and reconstruction error.}

\inputdir{synth_linear}
\multiplot{4}{synth-drr-hxhy-e,synth-elrme-hxhy-e,synth-drr-xy-e,synth-elrme-xy-e}{width=0.35\textwidth}{Simultaneous denoising and reconstruction error comparison in one common midpoint ($x$ = 5, $y$ = 5) and one common offset ($hx$ = 5, $hy$ = 5) gathers after \old{10}\new{ten} iterations and frequency band from $0$ to $125$ Hz between two algorithms. (a and c) display the error using the DRR approach. (b and d) denote the error of the proposed approach.}

To make a quantitative comparison, we conduct the quality evaluation first in term of SNR measurement \citep{zhang2017hybrid} defined as\new{:}
\begin{equation}
SNR=10\log_{10}\frac{\Vert \mathbf{X^{o}} \Vert^2_2}{\Vert \mathbf{X^{o}}-\mathbf{X^{r}}\Vert^2_2}\old{,}\new{.}
\label{eq:eq22}
\end{equation}
Then, in term of normalized root square error (RSE) \citep{parekh2017improved} expressed as
\begin{equation}
RSE=\frac{\left\|\mathbf{X^r} - \mathbf{X^o}\right\|_\mathbf{F}}{\left\|\mathbf{X^o}\right\|_\mathbf{F}}\old{,}\new{.}
\label{eq:eq23}
\end{equation}
In both cases (equations \ref{eq:eq22} and \ref{eq:eq23}), $\mathbf{X^{o}}$ and $\mathbf{X^{r}}$ are the vectorized original data and the vectorized estimated signal, respectively. The range of RSE values is from $0$ to $1$. The smaller values will show better recovery quality.

\wen{Additionally, we display the simultaneous denoising and reconstruction performance of each approach by using the local similarity map \citep{chen2015random}. \old{The comparison using the local similarity}\new{This} allows us to measure the damage that each method can produce to the signal matrix. The \old{better signal}\new{improved signal estimate} is shown by the lower local similarity between the restored data and the suppressed noise.}

The SNR values of the noisy data, the observed data, the recovered data via the DRR approach, and the proposed approach are $-6.68$ dB, $-2.39$ dB, $9.10$ dB and $13.57$ dB, respectively. The DRR approach and the proposed approach obtain RSE values of $0.35$ and $0.21$, respectively. From the comparison of the SNR and RSE values, we can deduce that the quality of the estimated signal matrix using our approach is better than that of the DRR approach.

We further analyze the quality of both estimated signals from another viewpoint by comparing their frequency-wavenumber spectra. Figure \ref{fig:synth-clean-hxhy-fkk,synth-noisy-hxhy-fkk,synth-obs-hxhy-fkk,synth-drr-hxhy-fkk,synth-elrme-hxhy-fkk} displays the frequency-wavenumber representations in one common midpoint gather. The detailed comparison of each sub-figure reveals that the spectrum using our approach displayed in Figure \ref{fig:synth-elrme-hxhy-fkk} is better than that of the DRR algorithm shown in Figure \ref{fig:synth-drr-hxhy-fkk}. The proposed approach can attenuate the residual noise in the whole frequency band and preserve the useful signal better than the DRR approach. The frequency analysis further confirms the best quality of the estimated low-rank matrix signal of \dlo{our}\wen{the proposed} algorithm.

\inputdir{synth_linear}
\multiplot{5}{synth-clean-hxhy-fkk,synth-noisy-hxhy-fkk,synth-obs-hxhy-fkk,synth-drr-hxhy-fkk,synth-elrme-hxhy-fkk}{width=0.3\textwidth}{Common midpoint frequency-wavenumber spectrum comparison of each five-dimensional synthetic data ($x$ = 5, $y$ = 5) after \old{10}\new{ten} iterations in a frequency band from $ 0 $ to $ 125 $ Hz between two algorithms. (a) is from the true data. (b) is from the noisy data. (c) corresponds to the observed data. (d) plots the DRR approach result. (e) shows the spectrum of the proposed approach.}

\wen{To \old{additionally}\new{further} show the difference between the two methods, we display the removed noise and the corresponding local similarity map using each approach in one common offset gather. The removed noise and the local similarity map from the DRR method are displayed in Figure\old{s} \ref{fig:synth-n-drr-hxhy} and \ref{fig:synth-simi1}, respectively. Figure\old{s} \ref{fig:synth-n-elrme-hxhy} and \ref{fig:synth-simi2} are \dlo{from}\wen{corresponding to the proposed algorithm}\dlo{the proposed approach}. Based on the comparison of the local similarity map, we find that the proposed approach can preserve the main features of the signal matrix, while the DRR algorithm can cause signal leakage. The smaller local similarity shows the better performance of the proposed approach compared with the DRR approach.}

\inputdir{synth_linear}
\multiplot{4}{synth-n-drr-hxhy,synth-n-elrme-hxhy,synth-simi1,synth-simi2}{width=0.35\textwidth}{Comparison of simultaneous denoising and reconstruction performance. (a) Removed noise \dlo{from}\wen{corresponding to} the DRR method. (b) Removed noise \dlo{from}\wen{corresponding to} the proposed method. (c) plots the local similarity of the DRR approach. (d) is from the proposed approach.}

Next, we provide another example of 5-D synthetic data containing curved events. The four spatial sizes of this synthetic data (with 101 times samples per trace) are $32\times32\times5\times5$. We compare both approaches based on the same noise level and the ratio of missing traces like \new{those} in the previous experiment. To restore the useful events, we run the DRR and the proposed methods with \old{$10$}\new{ten} weighted POCS-like iterations. We use a portion of the frequency \old{varied}\new{varying} from $0$ to $125$ Hz. We apply the DRR algorithm with ${n} = 12$ and ${q} = 3$. By using the same values of ${n}$ and ${q}$, we perform the proposed algorithm with the following parameters: ${\varphi_0 = \varphi_1} = 1$, ${\beta_0} = 0.972$ and ${\beta_1} = 0.98$, ${\delta_0} = 8.20$ and ${\delta_1} = 7.40$, ${b_0} = 3.75$ and ${b_1} = 0.50$. Figure\dlo{s} \ref{fig:hyper-clean-hxhy,hyper-obs-hxhy,hyper-drr-hxhy,hyper-elrme-hxhy}\dlo{ and \ref{fig:hyper-True-hxhy,hyper-obs-hxhy,hyper-drr-hxhy,hyper-elrme-hxhy}} displays the performance in one common midpoint gather. 
\new{The true, the observed and the restored data using the DRR method are plotted in Figure\old{s} \ref{fig:hyper-clean-hxhy}, \ref{fig:hyper-obs-hxhy} and \ref{fig:hyper-drr-hxhy}, respectively.} 
\old{The true data is plotted in Figure\old{s} \ref{fig:hyper-clean-hxhy}\old{and \ref{fig:hyper-True2d}}. The observed data is displayed in Figure\old{s} \ref{fig:hyper-obs-hxhy}\old{and \ref{fig:hyper-obs2d}}. The restored data using the DRR is plotted in Figure\old{s} \ref{fig:hyper-drr-hxhy}\old{and \ref{fig:hyper-drr2d}}.} From the comparison of each sub-figure, the estimated signal matrix using the DRR approach is acceptable \new{since the useful signal is well restored}. However, there is still an \old{important}\new{obvious} amount of residual noise that can severely affect some significant properties, for instance, the amplitude of the estimated signal matrix. In contrast, as demonstrated in Figure\old{s} \ref{fig:hyper-elrme-hxhy}\old{and \ref{fig:hyper-elrme2d}}, the proposed approach produces much better results. The coherent events of the reconstructed data are cleaner. The SNR values of the observed data, the restored data using the DRR, and the proposed methods are $0.58$ dB, $10.94$ dB, and $18.72$ dB, respectively. The DRR approach and the proposed approach complete the simultaneous denoising and reconstruction process with normalized RSE values of $0.28$ and $0.11$, respectively. Based on the numerical and visual analysis, the estimated signal from the proposed algorithm contains the least artifacts compared to that of the DRR.

\inputdir{synth_hyper}
\multiplot{4}{hyper-clean-hxhy,hyper-obs-hxhy,hyper-drr-hxhy,hyper-elrme-hxhy}{width=0.35\textwidth}{Common midpoint 3-D figures comparison ($x$ = 16, $y$ = 16) between two algorithms after \old{10}\new{ten} iterations in a frequency band from $0$ to $125$ Hz. (a) True data. (b) Observed noisy and incomplete data with $0.2$ as noise variance and $80\%$ of missing traces. (c) Simultaneously denoised and reconstructed data using the DRR. (d) Simultaneously denoised and reconstructed data using the proposed approach.}

Figure \ref{fig:hyper-drr-e,hyper-elrme-e} shows the \dlo{recovery}\wen{reconstruction} error using each approach. Figure\old{s} \ref{fig:hyper-drr-e}\old{ and \ref{fig:hyper-drrErrorHyper2d}} show\new{s} the \dlo{recovery}\wen{reconstruction} error of the DRR algorithm. From the least \dlo{recovery}\wen{reconstruction} error that is displayed in Figure\old{s} \ref{fig:hyper-elrme-e}\old{ and \ref{fig:hyper-elrmeerrorhyp2d}}, we find that the proposed approach can enhance the quality of the useful signal \old{with high fidelity}even though the \old{observed seismic}\new{synthetic} data \old{having}\new{with} curved events is affected by a high level of missing traces and random noise.

\inputdir{synth_hyper}
\multiplot{2}{hyper-drr-e,hyper-elrme-e}{width=0.35\textwidth}{Simultaneous denoising and reconstruction errors comparison in common midpoint after \old{10}\new{ten} iterations and frequency band from 0 to 125 Hz between two algorithms. (a)\new{is}\old{and (c) are} from the DRR approach. (b)\new{is}\old{ and (d) are} from the proposed approach.}

We then analyze the quality of each estimated signal by comparing their corresponding frequency-wavenumber spectra. The comparison for frequency range of $0 - 60$ Hz is presented in Figure \ref{fig:hyper-True-fkk,hyper-obs-fkk,hyper-drr-fkk,hyper-elrme-fkk}. Figures \ref{fig:hyper-True-fkk} and \ref{fig:hyper-obs-fkk} display the spectra of the true and\old{the} observed data, respectively. The restored data of the DRR and the proposed methods are presented in Figures \ref{fig:hyper-drr-fkk} and \ref{fig:hyper-elrme-fkk}, respectively. A quick visual analysis of each sub-figure highlights the largest difference between both methods. The spectrum using \dlo{our}\wen{the proposed} algorithm is cleaner than that of the DRR algorithm. The spectrum using the DRR algorithm reveals significant residual noise. The analysis of this result reveals that the proposed approach can drop the noise energy to a weaker level and improve the signal energy compared to the DRR algorithm. This test further shows the excellent quality of the estimated signal using \dlo{our}\wen{the proposed} algorithm.

\inputdir{synth_hyper}
\multiplot{4}{hyper-True-fkk,hyper-obs-fkk,hyper-drr-fkk,hyper-elrme-fkk}{width=0.35\textwidth}{Common midpoint frequency-wavenumber spectrum comparison of each data displayed in Figure \ref{fig:hyper-clean-hxhy,hyper-obs-hxhy,hyper-drr-hxhy,hyper-elrme-hxhy}. (a) and (b) show the frequency-wavenumber spectra of the true and the observed data, respectively. (c) and (d) show the frequency-wavenumber spectra using the DRR approach and the proposed approach, respectively.}

\wen{Figures \ref{fig:hyper-n-drr-hxhy} \wen{and} \ref{fig:hyper-n-elrme-hxhy} plot the removed noise \dlo{from}\wen{corresponding to} each method. From the local similarity map displayed in Figure \ref{fig:hyper-n-drr-hxhy}, it \wen{is} clear that the DRR method can cause significant signal leakage compared to the proposed method (Figure \ref{fig:hyper-n-elrme-hxhy}). The proposed approach perfoms with lower local similarity values. This comparison shows the \old{better}\new{improved} denoising performance of the proposed approach on \new{the} data \new{with}\old{having} curved events.}

\inputdir{synth_hyper}
\multiplot{4}{hyper-n-drr-hxhy,hyper-n-elrme-hxhy,hyper-simi1,hyper-simi2}{width=0.35\textwidth}{Comparison of simultaneous denoising and reconstruction performance. (a) Removed noise \old{from}\wen{corresponding to} the DRR method. (b) Removed noise \old{from}\wen{corresponding to} the proposed method. (c) plots the local similarity of the DRR approach. (d) is from the proposed approach.}

We further conduct two types of tests to assess the recovery performance of our approach: first, SNR as a function of percentage (\%) of missing data then, SNR as a function of noise variances. For the first test, we fix the noise level at $0.2$ while ranging the missing traces from $10\%$ to $90\%$. For the second experiment, we randomly remove $80\%$ of traces, and we \old{handle}\new{implement} ten tests with noise variances ranging: 0.1, 0.2, ..., 1. Figures \ref{fig:snr_missing_traceslinear_eventsokok,snr_missing_tracesCurved_eventsokok} and \ref{fig:snr_noise_varianceslinearEventsokok,snr_noise_variancesCurvedEventsokok} show the results for the first and the second tests, respectively. Figures \ref{fig:snr_missing_traceslinear_eventsokok} and \ref{fig:snr_noise_varianceslinearEventsokok} are from the 5-D \old{data having linear events}\new{linear event data}. The SNR values of the 5-D \old{data containing curved events}\new{curved-event data} are displayed in Figures \ref{fig:snr_missing_tracesCurved_eventsokok} and \ref{fig:snr_noise_variancesCurvedEventsokok}. In each figure, the magenta and green lines denote the SNR diagrams of the DRR approach and the proposed approach, respectively. The comparison shows the superiority of the proposed \wen{approach} in different \new{noise} levels and ratios of missing traces.

\inputdir{./}
\multiplot{2}{snr_missing_traceslinear_eventsokok,snr_missing_tracesCurved_eventsokok}{width=0.45\textwidth}{Comparison of SNRs as a function of missing traces after \old{10}\new{ten} iterations between two algorithms. (a) Data containing linear events. (b) Data having curved events. In both cases, the green and magenta lines correspond to the proposed and DRR algorithms, respectively. We used a noise variance of $0.2$, and then, we varied the missing traces from $10\%$to $90\%$.}

\inputdir{./}
\multiplot{2}{snr_noise_varianceslinearEventsokok,snr_noise_variancesCurvedEventsokok}{width=0.45\textwidth}{Comparison of SNRs as a function of noise level after \old{10}\new{ten} iterations between two algorithms. (a) Data containing linear events. (b) Data having curved events. In both cases, the magenta and green lines correspond to the proposed and DRR approaches, respectively. We decimated $80\%$ of traces, and then\new{,} we varied the noise levels from 0.1, 0.2, ..., 1 to evaluate the performance of each approach.}

Moreover, by ranging the iteration numbers from $5$ to $40$, we examine the performance and the efficiency of both approaches. For this experiment, we use the observed noisy and incomplete data of the first example (5-D synthetic data \old{having}\new{with} linear events corrupted by a noise variance of $0.2$ and $80\%$ of traces missing). Here, we run both algorithms for frequenc\new{y}\old{ies} band $0 - 100$ Hz. For each iteration number ($ 5 $, $ 10 $, ..., and $ 40 $), we \old{perform}\new{run} $6$ times each algorithm and, we record the computing time that corresponds to the highest SNR value. Figure \ref{fig:snr_iteration_lenearEventsokok} shows the performance of each approach. As \old{demonstrated in this test, the more the number of iterations increases, the higher are the SNR values using the proposed approach than those of the DRR approach}\new{the number of iterations increases, the SNR values using the proposed approach outperform those of the DRR approach}. Furthermore, as the number of iterations increases, the proposed approach produces relatively identical SNR values. We can, therefore, deduce that the proposed algorithm perform well with a wide range of iteration numbers.

\inputdir{./}
\plot{snr_iteration_lenearEventsokok}{width=0.5\columnwidth}{SNR as a function of iteration numbers between both algorithms for frequency band 0-100 Hz. The \old{black and grey}\new{green and magenta} lines correspond to the proposed and DRR algorithms, respectively. We use a noise variance of $ 0.2 $, and decimated $ 80\% $ of traces.}

The average \old{running time}\new{runtime} that corresponds to the most suitable combination of the parameters using each approach is displayed in Table \ref{tbl:table1}. All methods were executed in MATLAB R2017a on a Windows $10$ computer having an Intel Core i7 7th generation, and $8$ GB RAM. From the results presented in Table \ref{tbl:table1}, we find that as the iteration number increases, the computation time of both approaches becomes expensive and almost similar.
\AtEndDocument{
	\begin{center}
		\begin{table}[htb!]
			\caption{Computing time \old{(second (s))}comparison between two approaches for frequency band $0-100$ Hz. We used a noise variance of $0.2$, and decimated $80\%$ of traces.}
			\begin{tabular}{c c c c c c} 
				\hline Iteration numbers  & DRR (s) & & ELRME (s)&\\ 
				\hline 5 &246.5 & &298.78&\\
				10 &493.9 & &583.20&\\
				15 &740.37& &797.99&\\
				20 &1009.94& &1055.89&\\
				25 &1219.67& &1297.78&\\
				30 &1467.98& &1497.98&\\
				35 &1620.16& &1695.97&\\
				40 &1798.78& &1809.67&\\
				\hline
			\end{tabular} 
			\label{tbl:table1}
		\end{table}
	\end{center}
}\wen{We also analyse the efficiency of both methods regarding different data sizes\old{. We analyse the running time} after \old{10}\new{ten} iterations and a frequency band of $0-125$ Hz. As displayed in Table \ref{tbl:table2}, the computation time of both methods increases when the data size increases. \old{But,}\new{However} from the comparison of the running time, we find that the DRR approach is less expensive compared to the proposed approach.}
\AtEndDocument{
	\begin{center}
		\begin{table}[h]
			\caption{Comparison of computation time \old{(second (s))}of the DRR and the proposed ELRME approaches regarding different data sizes after \old{10}\new{ten} iterations and a frequency band of $0-125$ Hz based on an Intel Core i7 7th Gen.}
			\begin{tabular}{c c c c c c} 
				\hline Test &$100\times8\times8\times8\times8$
				& $100\times9\times9\times9\times9$  & $100\times10\times10\times10\times10$ & \\ 
				\hline \wen{DRR} (s) & 101.55 & 395.7 & 755.98\\
				ELRME (s) & 125.97 & 456.98 & 797.78 \\
				\hline
			\end{tabular} 
			\label{tbl:table2}
		\end{table}
	\end{center}
}

\subsection{Field data examples}

The proposed ELRME algorithm is tested on a field 5-D seismic data to show its performance. The effectiveness is shown through qualitative analysis. To restore the signal matrix from the observed data missing $75\%$ of traces, we select {${n} = 6$}, {${q} = 2$}, ${\varphi_0 = \varphi_1} = 1$, ${\beta_0} = 0.90$, ${\beta_1} = 0.995$, ${\delta_0} = 12.5$, ${\delta_1} = 12$, ${b_0} = 20$ and ${b_1} = 19$ for the proposed approach, and we adopt the same value\new{s} of rank and damping factor for the DRR. We run both algorithms for frequencies from $ 0 $ to $ 125 $ Hz and $10$ weighted POCS-like iterations. Figures \ref{fig:fieldObserved-hxhy,fielddrr-hxhy,fieldelrme-hxhy} and \ref{fig:fieldObserved-xy,fielddrr-xy,fieldelrme-xy} correspond to the results in one common midpoint and offset gathers. We display the observed data in Figures \ref{fig:fieldObserved-hxhy} and \ref{fig:fieldObserved-xy}. The estimated signal using the DRR algorithm is displayed in Figures \ref{fig:fielddrr-hxhy} and \ref{fig:fielddrr-xy}. The result\new{s} obtained through the proposed method is plotted in Figures \ref{fig:fieldelrme-hxhy} and \ref{fig:fieldelrme-xy}. \old{From the comparison of each sub-figure, we find that the useful signal estimated by \dlo{our}\wen{the proposed} approach is better than that of the DRR method.} As seen in the 3-D cubes of the proposed method, all signal events are well recovered and can be identified easily. \dlo{For more details, we conduct a 2-D section comparison of each data plotted in Figure \ref{fig:12}. \dlo{Figure \ref{fig:14} shows the comparison.} Figure \ref{fig:Field-Observed-s} corresponds to the observed data. Figures \ref{fig:Field-drr-s} and \ref{fig:Field-elrme-s} are from the DRR and the proposed approaches, respectively. 
This example further shows the better performance of our algorithm. We can, therefore, deduce that the proposed method provides better results than the DRR method.}

\inputdir{./}
\multiplot{3}{fieldObserved-hxhy,fielddrr-hxhy,fieldelrme-hxhy}{width=0.30\textwidth}{Common midpoint gather 3-D figures comparison after \old{10}\new{ten} iterations in a frequency band from 0 to 125 Hz between two algorithms. (a) show the observed data. (b and c) show the data using the DRR approach and the proposed approach, respectively.}

\inputdir{./}
\multiplot{3}{fieldObserved-xy,fielddrr-xy,fieldelrme-xy}{width=0.30\textwidth}{Common offset gather 3-D figures comparison after \old{10}\new{ten} iterations in a frequency band from 0 to 125 Hz between two algorithms. (a) \old{show the o}\new{O}bserved data. (b and c) \old{show the d}\new{D}ata using the DRR approach and the proposed approach, respectively.}

\old{To explore the performance of the proposed approach, we display the 2-D figures in one common offset gather. \dlo{From Figure \ref{fig:offset_field_data_Obs} to Figure \ref{fig:Proposed_offset_field} to have}\wen{Figure\old{s} \ref{fig:offset_field_data_Obs}-\ref{fig:Proposed_offset_field} show} the observed data, the estimated signal using the DRR and the proposed methods, respectively. The comparison of each figure reveals all significant events restored by the proposed method. For more details, we plot in Figure \ref{fig:17} the zoomed section of each data shown by the green frame boxes in Figure \ref{fig:16}. Figure \ref{fig:Zoomed_offset_field_data_Obs} is from the observed noisy and incomplete data. Figures \ref{fig:Zoomed_DRR_offset_field} and \ref{fig:Zoomed_Proposed_offset_field} are from the DRR and the proposed approaches, respectively. This example further shows the better performance of the proposed algorithm even when the field data includes curved events in some sections. We can, therefore, deduce that the proposed method provides better results than the DRR method.}

Then, we conduct another analysis using the frequency-wavenumber spectrum of each result displayed in Figure \ref{fig:field-Observed-fkk,field-drr-fkk,field-elrme-fkk}. Figure \ref{fig:field-Observed-fkk} is from the observed data. Figure \ref{fig:field-drr-fkk} is from the DRR algorithm. Figure \ref{fig:field-elrme-fkk} displays the estimated signal using the proposed approach. According to these spectra comparisons, both approaches can remove the residual noise. When we consider the low-frequency band (frequency $< 70$ Hz), we \old{see}\new{can find} that the ELRME algorithm enhances the signal energy better than the DRR method. This illustration shows the high quality of the estimated low-rank signal matrix using the proposed method.

\inputdir{./}
\multiplot{3}{field-Observed-fkk,field-drr-fkk,field-elrme-fkk}{width=0.30\textwidth}{Common midpoint frequency-wavenumber spectrum comparison of each data plotted in Figure \ref{fig:fieldObserved-hxhy,fielddrr-hxhy,fieldelrme-hxhy} \old{data} after \old{$10$}\new{ten} iterations in a frequency band from $0$ to $125$ Hz between two algorithms. (a) \old{shows the f}\new{F}requency-wavenumber spectrum of the observed data. (b and c) \old{display the f}\new{F}requency-wavenumber spectra using the DRR approach and the proposed approach, respectively.}

\wen{The following example shows the local similarity between different restored data sets, and the observed data. Here, we conduct this quantitative analysis regarding the observed data because we do not have the noisy field data. \old{We plot the result in Figure \ref{fig:19}.}Figure \ref{fig:field-simi1} displays the local similarity between the result from the DRR method and the observed data. Figure \ref{fig:field-simi2} displays the local similarity between the result from the proposed method, and the observed data. The local similarity shows that both approaches can \dlo{take care of the useful signal}\wen{preserve the useful signal}.}

\inputdir{./}
\multiplot{2}{field-simi1,field-simi2}{width=0.4\textwidth}{Common midpoint local similarity comparison of each restored data displayed in Figure \ref{fig:fieldObserved-xy,fielddrr-xy,fieldelrme-xy}. (a) \old{plots the l}\new{L}ocal similarity of the DRR approach. (b) \old{is from the p}\new{P}roposed ELRME approach.}

\section{discussion}

The quality of the estimated signal matrix provided by the DRR method depends on the DRR operator (${R}_{\ell}$). Our experience with the DRR method reveals that \new{when the noise level and the ratio of missing traces increase, the operator ${R}_{\ell}$ becomes inadequate}\old{the higher is the noise level and the ratio of missing traces, the more inadequate the operator ${R}_{\ell}$ is}, and the estimated signal matrix contains meaningful noise\old{s}. The amplitude of the useful signal could also be severely affected. To overcome this problem, we introduce a novel proximity function in the DRR approach framework to enhance the estimation of the signal matrix. The goal of \dlo{our}\wen{the proposed} approach is to restore and preserve the features of the useful signal matrix, even though the ratio of missing data and noise level increases.

From the various tests conducted on synthetic and field 5-D seismic data sets, we can obtain significant conclusions about how to set the parameters of the proposed method. The ELRME algorithm needs the specification of the rank constraint ${n}$, the damping factor ${q}$, two windows size (${\varphi_0}$ and ${\varphi_1}$), two rational transfer function coefficient (${\beta_0}$ and ${\beta_1}$), two cooling factors (${\delta_0}$ and ${\delta_1}$) to control the regularization parameters (${\lambda_0}$ and ${\lambda_1}$), and two penalties parameters (${b_0}$ and ${b_1}$).

We focus first on the parameters that the proposed proximity operator requires. The parameter $\varphi_i$ \wen{should be}\dlo{is} a positive integer $(\varphi_i>0)$. \wen{To see its influence \old{in}\new{on} the proposed algorithm, we set ${n}=3$, ${q}=3$, ${\beta_0}=0.971$ and ${\beta_1}=0.977$, $\delta_0 = 3.75$ and $\delta_1 = 3.25$, ${b_0}=25$ and ${b_1}=23$\old{ by trial}, and we vary the value of $\varphi_i$ from $1$ to $5$ when estimating the low-rank signal matrix of the first synthetic data example. Figure \ref{fig:WindowsSizeφi} shows the SNRs diagram with different values of ${\varphi_i}$. We find that all values of ${\varphi_i}$ selected above $1$ weaken the \new{performance of the }proposed operator}\dlo{This parameter}\old{$\varphi_i$ produces some signal damages of data when it is greater than $1$}. To achieve the best quality of the result, we propose to set \old{$\varphi_0$ and $\varphi_1$ equal to $1$}\new{${\varphi_0}={\varphi_1}=1$} for any noisy and incomplete data to be estimated. \wen{In the same perspective, we keep the values of parameters mentioned including ${\varphi_0}={\varphi_1}=1$, and we show the strength of both ${\beta_0}$ and ${\beta_1}$ in Figure \ref{fig:RationalTransfertFunctionCoefficientbeta0and1}. From $0.900$ to $0.970$, ${\beta_0}$ helps to produce better results compared with ${\beta_1}$. In contrast, ${\beta_1}$ becomes better than ${\beta_0}$ from $0.980$ to $1$. Both parameters yield the same values of SNR around ${\beta_i = 0.974}$. But this value is not the best trade-off to achieve the performance of the proposed approach. Therefore, we need to adjust ${\beta_0}$ and ${\beta_1}$ around $0.970$ and $0.980$, respectively. After some trials we adopted ${\beta_0 = 0.971}$ and ${\beta_1 = 0.977}$ to estimate the signal matrix.} Usually, when $\beta_i$ is large, the smoothing level degrades the significant feature of the useful signal. If $\beta_i$ is too small, it generates extra noise in the data. Therefore, we usually choose $\beta_i \in \left[0, 1\right]$. As a general rule, $\beta_0$ should always be less than or equal to $\beta_1$ ($\beta_0 \leq \beta_1$) whatever the data to be restored is. \wen{Also}, as the iteration numbers and the noise levels increase, we should set $\beta_i$ by increasing gradually the values towards $1$. However, when the percentage of missing traces becomes high (from $10\% $ to $90\%$), we should select $\beta_i$ progressively from $1$ to $0$. The couples of parameters ($\varphi_0$, $\beta_0$) and ($\varphi_1$, $\beta_1$) are used to filter out the unwanted values that the singular values contain and the elements of the matrix to be estimated, respectively. \wen{This guideline is also verified for data \old{including}\new{with} curved events and/or complex structures like almost all field seismic data}. Then, we set the regularization parameters $\lambda_i$ as we proposed in the theory section. We use the regulating parameters called cooling factor $\delta_i$ to adjust $\lambda_i$. When the ratio of missing traces increases, the values of $\delta_i$ should decrease gradually. In contrast, when the noise level increases (from $0.1$ to $1$), the values of $\delta_i$ should increase gradually. The cooling factors $\delta_i$ provide us some flexibility to control the estimation of the low-rank matrix. The proposed regularization parameters $\lambda_i$ allow\old{s} exploiting sparsity along all dimensions of multidimensional seismic data. \wen{Figure \ref{fig:CoolingfactorsSigma0and1} shows the contribution of $\delta_0$ and $\delta_1$ in obtaining the result of the proposed strategy. As shown, from $0$ to $4$, the parameter $\delta_0$ (magenta line) aids at producing almost the same SNRs value. Its SNRs diagram seems to be invariable compared to that of $\delta_1$ (green line), which becomes stable from $20$ to $25$. Here,} to achieve a best trade-off with other parameters, we propose to set $\delta_0 \geq \delta_1$. \wen{Therefore, we have selected $\delta_0 = 3.75$ and $\delta_1 = 3.25$ when estimating the low-rank signal matrix having linear events. Relatively small values of $\delta_i$ can be selected for data, including curved events or complex structures.} Besides, the penalty convexity parameters $b_i$ should be greater than zero (${b_i} > 0 $). \wen{For this parameter, we analyze the simultaneous denoising and reconstruction quality of the ELRME algorithm by keeping all other parameters, while varying ${b_0}$ and ${b_1}$ from $1, 2, 3,..,$ to $25$. From Figure \ref{fig:PenaltyConvexityParametersb0b1}, the best values of both parameters can be selected around $23$. But we suggest setting ${b_0}\geq {b_1}$ for obtaining the best trad-off with the other parameters. Here, we selected ${b_0}=25$ and ${b_1}=23$ to recover the signal matrix. This analysis reveals that larger values of ${b_i}$ can be adopted for the restoration of data, including linear events. In contrast, in case of data including curved events, smaller values are demanded}. Note that, if ${b_i}$ is too small (${b_i} < 1e^{-10}$), there is no advantage in applying the arctangent penalty function, and the result is almost the same as applying the soft-thresholding function. It is important to know that when $\delta_i$ and ${b_i}$ are very large, it may degrade the amplitude of the estimated signal. ${b_0}$ and ${b_1}$ affect the sparsity of the singular values, and the elements of the noisy matrix, respectively. The rank ${n}$ needs to be set according to the number of different dip components, \old{with}\new{for} data \old{having}\new{with} linear events. For data containing curved events, ${n}$ needs to be relatively higher than the number of different dip components \citep{oropeza2010randomized}. \wen{Figure \ref{fig:rankn} highlights the effects of ${n}$ in our results for different input values. We adopted ${n}=3$ because of the best quality of the results. The 5D synthetic data used in this paper includes $3$ linear events. Thus, ${n} = 3$ confirms the linear events assumption. We display the influence of the damping factor for different values in Figure \ref{fig:dampingFactorq}. From this figure, we find that the damping operator of the proposed approach loses its ability when the parameter ${q}$ is very large. \old{The damping operator used in the DRR algorithm and that of the new algorithm behave, therefore, in the same way.} Based on this remark, ${q}$ should be chosen in the interval of ${q} \in \left[2, 3\right]$ for 5-D synthetic data and field data sets having linear or curved events as suggested in \cite{chen2016open} and \cite{chen2016simultaneous}}.

\new{How to select the parameters is generally true for all types (linear, curved, and complex events) of data as explained above. We have illustrated the selection of the parameters by using the examples conducted in the paper}. An adequate combination of the parameters described above leads to the construction of the novel improved rank-reduction operator (${R}_{e\ell}$) that aims to estimate the signal matrix properly. The new operator can deal with the residual noise and preserve the features of the useful signal in a large frequency band effectively. The proposed proximity function can successfully address the shortcomings of the DRR operator (${R}_{\ell}$).

\wen{The ELRME method mixes the DRR method and the new proximity function for the restoration of the useful signal. It is, therefore, SVD-based because of the DRR operator (${R}_{\ell}$). Thus, we can understand that the main running time of the proposed approach is the singular values decomposition of the level-4 block Hankel matrix. As shown in Table \ref{tbl:table1}, the computation time of the proposed approach is slightly higher than that of the DRR approach for different value\old{s} of iteration numbers. The difference in terms of computation cost can be justified because the ELRME operator (${R}_{e\ell}$) applies the proximity function first, to the level-4 block Hankel matrix, and then to the singular values just after SVD. We find that such a process can be a little more expensive compared with the damped RR process.}

\inputdir{./}
\multiplot{6}{rankn,dampingFactorq,WindowsSizeφi,RationalTransfertFunctionCoefficientbeta0and1,CoolingfactorsSigma0and1,PenaltyConvexityParametersb0b1}{width=0.3\textwidth}{Weight of each parameter. (a) rank constraint (n). (b) Damping factor (q). (c) Windows size ($\varphi_i$). (d) Rational transfert function coefficient ($\beta_i$). (e) Cooling factor ($\delta_i$). (f) Penalty convexity parameters ${b_i}$.}

\section{conclusions}

By introducing the proximity operator into the DRR framework, we develop a new simultaneous 5-D denoising and reconstruction method, which is called enhanced low-rank matrix estimation (ELRME) method. We focus on the problem of computing a signal matrix from its noisy and incomplete observation. The ELRME algorithm uses an improved rank-reduction operator to further eliminate the random noise and reconstruct the missing traces. We use many examples of synthetic and real 5-D seismic data to demonstrate the performance of the new method. As demonstrated \old{from}\new{by} the detailed examples, the proposed algorithm performs better than the DRR approach. The ELRME algorithm can solve the multidimensional seismic data recovery problem even in the situation of very high noise levels and large ratios of missing traces.

%\section{DATA AVAILABILITY STATEMENT}
%All datasets and source codes associated with this research will be made available online (www.ahay.org) as a reproducible article.

%\section{acknowledgments}

%	The authors would like to thank Hang Wang for constructive
%	comments and suggestions, which have helped to improve this manuscript. The authors also thank Min Bai, Dong Zhang, Mi Zhang, Weilin Huang, and Yatong Zhou for fruitful discussions on the rank-reduction method.

\bibliographystyle{seg}
\bibliography{elrme}

\newpage
\listoftables

\newpage
\listoffigures

### 2021-03-08 elrme5d/matfun/drr5d_denoising_recon_synth.m

@@ -1,0 +1,322 @@
+function [ D1 ] = drr5d_denoising_recon_synth(D,MASK,flow,fhigh,dt,N,NN,Niter,eps,verb,mode,a)
+%  MSSA5D: multichannel singular spectrum analysis (MSSA) for 5D
+%          simultaneous denoising and reconstruction
+%
+%  IN   D:   	intput 5D data
+%       MASK:   sampling mask (consistent with the POCS based approaches)
+%       flow:   processing frequency range (lower)
+%       fhigh:  processing frequency range (higher)
+%       dt:     temporal sampling interval
+%       N:      number of singular value to be preserved
+%       NN:     damping factor
+%       Niter:  number of maximum iteration
+%       eps:    tolerence (||S(n)-S(n-1)||_F<eps*S(n))
+%       verb:   verbosity flag (default: 0)
+%       mode:   mode=1: denoising and reconstruction
+%               mode=0: reconstruction only
+%       a:      scalar
+%
+%  OUT  D1:  	output data
+%
+%  Copyright (C) 2015 The University of Texas at Austin
+%  Copyright (C) 2015 Yangkang Chen
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details: http://www.gnu.org/licenses/
+%
+%  KEY REFERENCE
+
[…]

### 2021-03-08 elrme5d/matfun/elrme5d_denoising_recon_synth.m

@@ -1,0 +1,288 @@
+function [ D1 ] = elrme5d_denoising_recon_synth(D,MASK,flow,fhigh,dt,N,NN,Niter,eps,verb,mode,a,ws,e1,o1,b1,e0,o0,b0)
+%  ELRME: Enhanced low-rank matrix estimation (ELRME) for simultaneous denoising and reconstruction of five-dimensional seismic data
+%
+%  IN   D:   	intput 5D data
+%       MASK:   sampling mask (consistent with the POCS based approaches)
+%       flow:   processing frequency range (lower)
+%       fhigh:  processing frequency range (higher)
+%       dt:     temporal sampling interval
+%       N:      number of singular value to be preserved
+%       NN:     damping factor
+%       Niter:  number of maximum iteration
+%       eps:    tolerence (||S(n)-S(n-1)||_F<eps*S(n))
+%       verb:   verbosity flag (default: 0)
+%       mode:   mode=1: denoising and reconstruction
+%               mode=0: reconstruction only
+%       a:      scalar
+%       ws:     windows size 
+%       e0:     rational tranfer function coefficient
+%       e1:     rational tranfer function coefficient
+%       o0:     decrease factor for cooling lambda
+%       o1:     decrease factor for cooling lambda
+%       b0:     penalty convexity parameter 
+%       b1:     penalty convexity parameter 
+%
+%  OUT  D1:  	output data
+%
+%  Copyright (C) 2020 Zhejiang University
+%  Copyright (C) Oboue et al. 2020
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
[…]

### 2021-04-24 foot/paper.tex
2021年 4月23日 星期五 23时37分21秒 CDT

%
%\documentclass[10pt]{IEEEtran}
%\usepackage{amsmath}
%\usepackage{cite}
%\usepackage{ifthen}
%\usepackage{seg}
%\usepackage{color}
%\usepackage{graphicx}
%\usepackage{subfloat}
%\usepackage{algorithm}
%\usepackage{algpseudocode}
%
%\DeclareRobustCommand{\dlo}[1]{}
%\DeclareRobustCommand{\wen}[1]{#1}
%\DeclareRobustCommand{\old}[1]{}
%\DeclareRobustCommand{\new}[1]{#1}
%
%\begin{document}
\DeclareRobustCommand{\old}[1]{}
\DeclareRobustCommand{\new}[1]{#1}
\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}

\published{IEEE Transactions on Geoscience and Remote Sensing, xxx, xxx, (2021)}

\title{Statistics-guided residual dictionary learning for 
footprint noise removal}
\author{Wei Chen\footnotemark[1]\footnotemark[2], Omar M. Saad\footnotemark[1], Hang Wang\footnotemark[4], and Yangkang Chen\footnotemark[1]}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\ms{TGRS-2021}

\address{
\footnotemark[1]
Key Laboratory of Exploration Technology for Oil and Gas Resources\\
Ministry of Education\\
Yangtze University\\
\footnotemark[2]
Hubei Cooperative Innovation Center of Unconventional Oil and Gas\\
Yangtze University \\
\footnotemark[3]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
\footnotemark[4]
ENSN Laboratory\\
Seismology Department\\
National Research Institute of Astronomy and Geophysics (NRIAG), Egypt
}

\lefthead{Chen et al., 2021}
\righthead{Footprint noise removal}
%\thanks{This work was supported in part by the National Natural Science Foundation of China (NSFC) under Grant 41804140, and in part by the Open Fund of Cooperative Innovation Center of Unconventional Oil and Gas (Ministry of Education and Hubei Province), Yangtze University, under Grant UOG2020-01. (Corresponding author: Wei Chen.)}}

\maketitle

\begin{abstract}
The footprint noise is a type of coherent noise that arises from the acquisition geometry. The footprint noise is commonly seen in 3D seismic volumes and greatly affects the amplitude-based processing and interpretation steps in the seismic exploration workflow. Thus, removal of the footprint noise is necessary for warranting a reliable interpretation output of seismic data processing. However, because footprint noise is usually weak and also spatially coherent, it is inevitable to cause damages to useful signals during its removal steps. Here, we propose a dictionary learning based method to effectively remove the footprint noise. We design an algorithm framework to effectively learn the dictionary atoms of the signal waveforms and separate the features of the footprint noise from the learned atoms. Considering the special features of the footprint noise in the dictionary atoms, we propose a statistics guided way to separate the dictionary atoms into footprint-affected and footprint-free atoms. Then, the footprint-affected atoms are processed via a 2D median filtering step. The combination between the untouched footprint-free atoms and filtered footprint-affected atoms result in a better dictionary of the signal waveforms and the footprint atoms. We use residual dictionary learning to encode the input data by a linear combination of signal atoms and footprint atoms. Removal of footprint atoms and their corresponding sparse coefficients leads to a successful footprint removal. We use both 3D synthetic and field data examples to demonstrate the effectiveness of the proposed method.
\end{abstract}

%\begin{keywords}
%Seismic signal processing, dictionary learning, seismic amplitude, footprint
%\end{keywords}

\section{Introduction}
Enhancing the signal-to-noise ratio of seismic data is a very common topic that will never be out-of-date in the community of exploration geophysics. Noise that exists inevitably in the seismic data can be roughly divided into two categories, i.e., incoherent and coherent noise. Both of them may cause the degradation of the final imaging of geology structures if not handled properly. Thus, many denoising algorithms based on different mathematical fundamentals have been proposed to eliminate those noise, such as the sparse transforms \cite{Yaru2014Radon,Benfeng2014POCS,mostafa2017geo,Min2019Gaussian}, rank-reduction methods \cite{Yangkang2016drr,Yangkang2019orr}, prediction based methods \cite{Spitz1991fx,Chao2018Adap,Guochang2019Multi}, dictionary-learning based methods \cite{yangkang2016double,amir2017geo,amir2017,yangkang2019sparse}, and so on. Among many kinds of coherent noise, footprint is a very special one \cite{Marfurt1998ft}. It is mainly caused by the inherent drawbacks of the acquisition geometry, such as the irregular source-receiver position, insufficient spatial sampling rate and nonuniform fold number, which further lead to the regular but unwanted amplitude variation in the seismic profile (or 3D volume). This abnormal variation that is not caused by the subsurface structures will have some negative impacts on the subsequent geological interpretation since the footprint coherency may get mixed with that of signal and thus, is mistaken for the geological structure. Therefore, removing this kind of coherent noise is of great importance.

In the past decades, many researchers have observed the footprint noise in different types of seismic data, and analyzed features and causes of it \cite{Stephen1999plot,John2001ft,Jingye2008tow}. Marfurt et al. (1998) \cite{Marfurt1998ft} defined the footprint as the noise related to the acquisition geometry. The existence of this kind of noise may cause many troubles in calculating the seismic coherency, which further leads to the inaccurate identifications of the geological bodies, such as faults and channels. This phenomenon can be commonly seen in the sparse 3D land explorations with low fold numbers. They also showed that the proper use of 3D dip filtering could be very effective for alleviating the adverse impact of the footprint on the attribute calculation. Schuster and Liu (2001) \cite{Schuster2001ft} illustrated the relation between the footprint noise and the migration operator. Utilizing the array theorem borrowed from another subject, one can calculate the footprint noise accurately and rapidly for different array types. This allows the engineer to quickly check and design a proper acquisition system. Cooper et al. (2008) \cite{Joanna2008num} tried to use a synthetic test to simulate the formation of the footprint noise. A completed data set with very dense acquisition grids is first created as the reference, and a sparse data set is also given by extracting some traces from the former one. By comparing their imaging results, it can be concluded that the processing related artifacts appear in both the completed and decimated data. However, the amplitude variation, related to the geometry feature, is only observed in the later one. Brown (2010) \cite{Brown2010obc} analyzed the footprint noise appearing in a four-component data that are acquired in the ocean-bottom-cable (OBC) survey. He found that the appearance of the footprint is closely related to the leading receivers in the towing end of the cable. Some processing procedures for mitigating this interference are also proposed, such as surface-consistent deconvolution\old{, etc}.

The aforementioned algorithms can also effectively help attenuate the footprint noise \cite{Bannagi2005svd,Milos2007wt,Oswaldo2012ft,Abdulmohsen2016cwt}. Al-Bannagi et al. (2005) \cite{Muhammad2005tsvd} proposed to use the truncated singular value decomposition to simultaneously suppress the random and footprint noise. Falconer and Marfurt (2008) \cite{Scott2008ft} proposed an attribute based method that \old{utilizes}\new{utilized} the geometric features of the footprint noise\old{ to characterize it}. The formed noise is then adaptively subtracted from the original noisy data. Based on the new noise-free data, the attribute can be calculated more accurately. Zhang et al. (2009) \cite{Rui2009bpd} developed a Basis Pursuit (BP) algorithm to suppress the footprint noise in 3D seismic data. Instead of directly using 3D version of BP, he applied the 2D BP operator in time and spatial directions separately. This method can sufficiently eliminate footprint noise while preserving the signal details. Chen et al. (2012) \cite{Xuehua2012swt} developed a denoising algorithm based on the stationary wavelet transform to suppress the footprint noise in the 3D marine seismic volume. The key of this method is to adjust the thresholding parameters according to the data features in different time slices. This can help suppress sufficient noise while keeping the details of the signals, which further contributes to the accurate calculations of the attribute map. Considering the negative impact of footprint noise caused by the under-sampled raw data, Chopra and Marfurt (2013) \cite{Satinder2013interp} used \new{a} 5D interpolation algorithm to reconstruct the missing data, which can effectively alleviate the footprint artifact and help obtain the more accurate attribute calculation. Gorszczyk et al. (2015) \cite{Gorszczyk2015curvelet} used the 2D discrete curvelet transform to deal with the noisy seismic data acquired in the hardrock environment. By adopting a novel thresholding strategy in the transform domain, this algorithm can effectively attenuate not only the random noise but also the coherent footprint noise. Compared with the F-XY prediction based method, the new method can obtain a more satisfactory denoising result with less signal leakage. Gomez et al. (2019) \cite{Gomez2019emd} developed a novel method based on the empirical mode decomposition (EMD) to simultaneously suppress the random and footprint noise. This new decomposition filter is applied along the spatial plane, i.e., the time slice, instead of the time direction. The filter length is non-stationary in every slice and adapted according to the signal distribution. By discarding the high-frequency component, the corresponding noise can be attenuated. Three field data examples, including one 2D and two 3D cases, all indicate that the proposed empirical-mode filtering (EMF) algorithm can remove the noise sufficiently with causing negligible signal damages. Compared with the other F-X or EMD based methods, it can achieve even better results. %Gomez and Velis (2020) proposed dictionary learning frame for suppressing the footprint noise. They used the coherence-constrained dictionary learning (CDL) method to train an initial dictionary, and then used the domain transform to filter each atom, which further produces the filtered atom and its corresponding residual. %\cite{Gomez2020dl} proposed a residual dictionary denoising (RDD) framework to suppress the footprint noise in the 3D seismic data. This algorithm is based on the dictionary learning frame. First, it uses the coherence-constrained dictionary learning (CDL) method to train an initial dictionary. Then, the domain transform is used to filter each atom, which further produces the filtered atom and its corresponding residual. These two parts make up the augmented dictionary used to suppress the footprint noise. The 3D synthetic and field examples all show that it can not only separate the footprint noise accurately but also preserve the signal details well. Additionally, the algorithm needs only few training data to form the effective dictionary which can be further applied in the other data sets. This can significantly reduce the computational costs.

Sometimes, the suppression of footprint noise appears as an important step in the inversion, migration or interpretation framework \cite{Lee2005mig}. Canning and Gardner (1988) \cite{Canning1998ft} mentioned the detrimental effects of the footprint on the 3D dip moveout and prestack migration. They proposed to change the migration procedures to better mitigate the footprint interference. Gesbert (2001) \cite{Gesbert2001ft} illustrated the reason for the appearance of footprint noise and its negative impacts on the migration imaging. By dividing the big data set into small ones and changing the quadrature way, it can output an improved migration result with the good signal fidelity. Feng et al. (2018) \cite{Feng2018deblurring} proposed to use a multiparameter deblurring filter to help the multiparameter seismic inversion. Different tests show that, by adopting this filter,  the footprint noise is effectively suppressed and the signal true amplitudes are recovered well. The overall imaging quality can get a significant improvement. Qi et al. (2018) \cite{Qi2018fault} designed an effective workflow to better identify the faults in the seismic data. One of the main steps in the proposed workflow is to attenuate the footprint noise, which creates the optimized input data for the subsequent fault detection.

In this paper, we propose a new footprint removal method based on dictionary learning. We first learn the features of the useful signals and the footprint noise, respectively, based on a statistics-guided classification scheme. Then, the learned signal and noise atoms are concatenated as an augmented dictionary, and are used to separate the signal and noise via a residual dictionary learning step. We demonstrate the performance of the proposed method via both synthetic and real data examples.

\section{Theory}
\subsection{Dictionary learning}

Let $\mathbf{d}$ be the input seismic data. First, we apply a patching method to segment the input data into a group of patches:
\begin{equation}
\label{eq:patch}
\mathbf{Y}=p(\mathbf{d}).
\end{equation}
Supposing the patch size is $l_1\times l_2$, then each column in $\mathbf{Y}$ is of size $l_1l_2\times 1$.  $p(\cdot)$ denotes the patching process.

The goal of dictionary learning is to iteratively update a dictionary and a sparse coefficient matrix so that
\begin{equation}
\label{eq:eq2}
\mathbf{Y} \approx \mathbf{D}\mathbf{M}, \quad\text{s.t.}  \quad \forall_i ||\mathbf{m}_{i}||_{0}\le Q,
\end{equation}
where $\mathbf{D}$ is the learned dictionary and $\mathbf{M}$ is the sparse coefficient matrix\old{.}\new{,} $Q$ denotes the sparsity constraint, meaning that the number of non-zero entries of each column of $\mathbf{M}$ will be equal to Q.

To solve equation  \ref{eq:eq2}, one needs to iteratively solve the following two problems, i.e., dictionary updating and sparse coding, respectively. 
\begin{equation}
\label{eq:dic}
\hat{\mathbf{D}}^n = \arg\min_{\mathbf{D}^n} \parallel \mathbf{Y} - \mathbf{D}^n\mathbf{M}^n \parallel_F^2, 
\end{equation}
and 
\new{\begin{equation}
\label{eq:code}
\hat{\mathbf{M}}^n = \arg\min_{\mathbf{M}^n} \parallel \mathbf{Y} - \mathbf{D}^n\mathbf{M}^n \parallel_F^2, \quad\text{s.t.}  \quad \forall_i ||\mathbf{m}_{i}||_{0}\le Q,
\end{equation}}
\new{where $n$ denotes the iteration number.}

\subsection{K-SVD-based dictionary update}
The K-SVD algorithm is one of the most widely used methods to update the dictionary. 
In the K-SVD algorithm, 
\begin{equation}
\begin{split}
\mathbf{D}^{n+1}&=\arg\min||\mathbf{Y}-\mathbf{D}\mathbf{M}^{n}||^{2}_{F}\\
&=\arg\min||\mathbf{Y}-\sum_{j=1}^{L}\mathbf{d}_{j}\mathbf{m}^{T}_{j}||^{2}_{F}\\
\end{split}\quad,
\end{equation}
where $\mathbf{d}_{j}$ and $\mathbf{m}^T_{j}$ are the $j$th column of dictionary matrix $\mathbf{D}$ and $j$th row of the sparse coefficient $\mathbf{M}$.

One should fix the sparse coefficient $\mathbf{M}$ and update the dictionary $\mathbf{D}$ column by column, which can be expressed as follows:
\begin{equation}
\begin{split}
	\mathbf{D}		&=\arg\min||\mathbf{Y}-\sum_{j\neq k}^{L}\mathbf{d}_{j}\mathbf{m}^{T}_{j}-\mathbf{d}_{k}\mathbf{m}^{T}_{k}||^{2}_{F}\\
	&=\arg\min||\mathbf{R}_{k}-\mathbf{d}_{k}\mathbf{m}^{T}_{k}||^{2}_F\\
\end{split}
\quad ,
\end{equation}
where $\mathbf{R}_{k}$ denotes the residual between the input data $\mathbf{Y}$ and sparsely represented matrix excluding the $k$th column. Thus, the problem becomes to solve the rank-1 approximation of $\mathbf{R}_{k}$, which can be achieved by singular value decomposition (SVD). However, directly using SVD will destruct the sparse structure of the coefficient vector $\mathbf{m}^T_{k}$. To avoid that, one needs to apply a sub-sample operator to discard the columns in $\mathbf{R}_{k}$ where the corresponding entries in $\mathbf{m}_{k}$ are zero. The new error matrix and new coefficient vector thus become $\mathbf{R}^{new}_{k}$ and  $\mathbf{m}_{k}^{^Tnew}$, respectively. Then, the SVD is directly used for the rank-1 approximation. 
\begin{equation}
\text{J}=||\mathbf{R}_{k}-\mathbf{d}_{k}\mathbf{m}^T_k||_F^{2}=||\mathbf{R}_{k}^{new}-\mathbf{d}_{k}\mathbf{m}^{Tnew}_k||^{2}.
\end{equation}
After $\mathbf{D}$ is updated, the coefficient matrix is then updated via the orthonormal matching pursuit (OMP) method.

\begin{figure}[htb!]
\centering
\includegraphics[width=\columnwidth]{Fig/sta_atoms2}
\caption{Learned atoms and the manual picking results. The black circle indicates that we manually define this atom as a footprint noise related atom. }
\label{fig:sta_atoms2}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.8\columnwidth]{Fig/sta_curves}
   \label{fig:sta_curves}} \\
   \subfloat[]{\includegraphics[width=0.7\columnwidth]{Fig/sta_result}
   \label{fig:sta_result}} \\
   \subfloat[]{\includegraphics[width=0.7\columnwidth]{Fig/sta_err}
   \label{fig:sta_err}}
\caption{Statistic test. (a) Curves of different statistical measures. (b) Binary classification results. ``1" means noise atom and ``0" means signal atom. (c) Classification errors. Here, \new{the} error is either 1 or 0 for each atom. The summation of error $E$ of all atoms indicates the classification accuracy and is listed in the legends. }
\label{fig:sta_curves,sta_result,sta_err}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.32\columnwidth]{syn/Fig/syn-c}
   \label{fig:syn-c}}
\subfloat[]{\includegraphics[width=0.32\columnwidth]{syn/Fig/syn-nft}
   \label{fig:syn-nft}}\\
\subfloat[]{\includegraphics[width=0.32\columnwidth]{syn/Fig/syn-nrand}
   \label{fig:syn-nrand}}
   \subfloat[]{\includegraphics[width=0.32\columnwidth]{syn/Fig/syn-n}
   \label{fig:syn-n}}
\caption{Synthetic example. (a) Clean data. (b) Footprint noise. (c) Random noise. (d) Noisy data}
\label{fig:syn-c,syn-nft,syn-nrand,syn-n}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Fig/s_atom0}
   \label{fig:s_atom0}}\\
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Fig/s_atom1}
   \label{fig:s_atom1}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Fig/s_atom2}
   \label{fig:s_atom2}}
\caption{A comparison of the dictionary atoms of the synthetic data example. (a) Learned atoms directly from field data. (b) Learned signal atoms obtained by selecting noise-free atoms via the statistics-guided method and filtering the noise-contaminated atoms via the median filtering method. (c) Learned footprint noise atoms by subtracting (b) from (a). }
\label{fig:s_atom0,s_atom1,s_atom2}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.32\columnwidth]{syn/Fig/syn-drr}
   \label{fig:syn-drr}}
\subfloat[]{\includegraphics[width=0.32\columnwidth]{syn/Fig/syn-dl}
   \label{fig:syn-dl}}\\
\subfloat[]{\includegraphics[width=0.32\columnwidth]{syn/Fig/syn-mf-0}
   \label{fig:syn-mf-0}}
   \subfloat[]{\includegraphics[width=0.32\columnwidth]{syn/Fig/syn-sgrdl-0}
   \label{fig:syn-sgrdl-0}}
\caption{Denosing comparison of the synthetic example. Denoised data using (a) DRR method, (b) standard DL method, (c) median filtering method, and (d) the proposed SGRDL method. }
\label{fig:syn-drr,syn-dl,syn-mf-0,syn-sgrdl-0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.32\columnwidth]{syn/Fig/syn-drr-n}
   \label{fig:syn-drr-n}}
\subfloat[]{\includegraphics[width=0.32\columnwidth]{syn/Fig/syn-dl-n}
   \label{fig:syn-dl-n}}\\
\subfloat[]{\includegraphics[width=0.32\columnwidth]{syn/Fig/syn-mf-n-0}
   \label{fig:syn-mf-n-0}}
   \subfloat[]{\includegraphics[width=0.32\columnwidth]{syn/Fig/syn-sgrdl-n-0}
   \label{fig:syn-sgrdl-n-0}}
\caption{Denosing comparison of the synthetic example. Removed noise using (a) DRR method, (b) standard DL method, (c) median filtering method, and (d) the proposed SGRDL method. }
\label{fig:syn-drr-n,syn-dl-n,syn-mf-n-0,syn-sgrdl-n-0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.35\columnwidth]{syn/Fig/syn-drr-s}
   \label{fig:syn-drr-s}}
\subfloat[]{\includegraphics[width=0.35\columnwidth]{syn/Fig/syn-dl-s}
   \label{fig:syn-dl-s}}\\
\subfloat[]{\includegraphics[width=0.35\columnwidth]{syn/Fig/syn-mf-s}
   \label{fig:syn-mf-s}}
   \subfloat[]{\includegraphics[width=0.35\columnwidth]{syn/Fig/syn-sgrdl-s}
   \label{fig:syn-sgrdl-s}}
\caption{Denosing comparison of the synthetic example. Local similarity between the clean data and denoised data using (a) DRR method, (b) standard DL method, (c) median filtering method, and (d) the proposed SGRDL method. }
\label{fig:syn-drr-s,syn-dl-s,syn-mf-s,syn-sgrdl-s}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.3\columnwidth]{syn/Fig/syn-s-c}
   \label{fig:syn-s-c}}
\subfloat[]{\includegraphics[width=0.3\columnwidth]{syn/Fig/syn-s-n}
   \label{fig:syn-s-n}}
\subfloat[]{\includegraphics[width=0.3\columnwidth]{syn/Fig/syn-s-drr}
   \label{fig:syn-s-drr}}\\
\subfloat[]{\includegraphics[width=0.3\columnwidth]{syn/Fig/syn-s-dl}
   \label{fig:syn-s-dl}}
\subfloat[]{\includegraphics[width=0.3\columnwidth]{syn/Fig/syn-s-mf-0}
   \label{fig:syn-s-mf-0}}
\subfloat[]{\includegraphics[width=0.3\columnwidth]{syn/Fig/syn-s-sgrdl-0}
   \label{fig:syn-s-sgrdl-0}}
\caption{Single slice comparison of (a) clean data, (b) noisy data, and denoised data using (c) DRR method, (d) standard DL method, (e) median filtering method, and (f) the proposed SGRDL method. }
\label{fig:syn-s-c,syn-s-n,syn-s-drr,syn-s-dl,syn-s-mf-0,syn-s-sgrdl-0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.32\columnwidth]{syn/Fig/syn-s-drr-n}
   \label{fig:syn-s-drr-n}}
\subfloat[]{\includegraphics[width=0.32\columnwidth]{syn/Fig/syn-s-dl-n}
   \label{fig:syn-s-dl-n}}\\
\subfloat[]{\includegraphics[width=0.32\columnwidth]{syn/Fig/syn-s-mf-n-0}
   \label{fig:syn-s-mf-n-0}}
\subfloat[]{\includegraphics[width=0.32\columnwidth]{syn/Fig/syn-s-sgrdl-n}
   \label{fig:syn-s-sgrdl-n}}
\caption{Single slice comparison of removed noise using (a) DRR method, (b) standard DL method, (c) median filtering method, and (d) the proposed SGRDL method. }
\label{fig:syn-s-c,syn-s-n,syn-s-drr,syn-s-dl,syn-s-mf-0,syn-s-sgrdl}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.3\columnwidth]{syn/Fig/syn-c-t}
   \label{fig:syn-c-t}}
\subfloat[]{\includegraphics[width=0.3\columnwidth]{syn/Fig/syn-n-t}
   \label{fig:syn-n-t}}
\subfloat[]{\includegraphics[width=0.3\columnwidth]{syn/Fig/syn-drr-t}
   \label{fig:syn-drr-t}}\\
\subfloat[]{\includegraphics[width=0.3\columnwidth]{syn/Fig/syn-dl-t}
   \label{fig:syn-dl-t}}
\subfloat[]{\includegraphics[width=0.3\columnwidth]{syn/Fig/syn-mf-t}
   \label{fig:syn-mf-t}}
\subfloat[]{\includegraphics[width=0.3\columnwidth]{syn/Fig/syn-sgrdl-t}
   \label{fig:syn-sgrdl-t}}
\caption{Single slice comparison of (a) clean data, (b) noisy data, and denoised data using (c) DRR method, (d) standard DL method, (e) median filtering method, and (d) the proposed SGRDL method. }
\label{fig:syn-c-t,syn-n-t,syn-drr-t,syn-dl-t,syn-mf-t,syn-sgrdl-t}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=\columnwidth]{syn/Fig/syn-ss-0}
   \label{fig:syn-ss-0}}\\
\subfloat[]{\includegraphics[width=\columnwidth]{syn/Fig/syn-ss-z}
   \label{fig:syn-ss-z}}
\caption{Single trace comparison. The black line corresponds to the clean data. The green line corresponds to the noisy data. The red line corresponds to the proposed SGRDL method. The magenta line corresponds to the MF method. The blue line corresponds to the standard DL method. The cyan line corresponds to the DRR method. (a) Comparison in the original scale. (b) Comparison in the zoomed scale. It is clear from (b) that the red line is the closest to the ground-truth solution (the black line). }
\label{fig:syn-ss-0,syn-ss-z}
\end{figure}

\subsection{Statistics guided dictionary atom filtering}
When seismic data contain footprint noise, the learned dictionary atoms have special features. It is possible to manually pick those atoms that correspond to signals, e.g., in \cite{liu2020deep}. However, it is more convenient to develop an automatic way to classify the atoms into noise-contaminated and the noise-free atoms.  Here, we propose a statistics guided method for this task, like the one in \cite{yatong2021}. Since the footprint noise is a type of coherent noise, and appears as coherent stripes in the atoms, we propose to leverage several 2D statistical metrics to distinguish between disparate atoms.

Supposing each atom is of size ($l_1l_2\times 1$), for calculating the 2D statistical metrics, we first reshape each atom into a rectangle $A(i,j)$ of size $l_1\times l_2$. According to the shape of the footprint noise, e.g., horizontal or vertical, the statistical metrics are calculated along each column or row of the rectangle $A(i,j)$. Let us take the horizontal footprint noise as an example. The statistic metrics are calculated along the vertical direction of the rectangle $A(i,j)$:
\begin{equation}
\label{eq:me}
y=\sum_{j=1}^{l_2} f(\mathbf{a}_j),
\end{equation}
where $y$ is the output 2D statistic metric. $f(\cdot)$ denotes a 1D statistical metric, e.g., variance, skewness, and kurtosis, while $\mathbf{a}_j$ denotes the $j$th column in the rectangle $A(i,j)$. Here, we list three 1D statistical metrics as follows:
\begin{enumerate}
\item Variance
\begin{equation}
\label{eq:v}
v(\mathbf{a}) = \frac{1}{l_1} \sum_{i=1}^{l_1} [a(i) - \mu]^2,
\end{equation}
where $\mu= | \frac{1}{l_1} \sum_{i=1}^{l_1} a(i) |$ denotes the mean of the input vector $\mathbf{a}$. $a(i)$ denotes the $i$th entry in vector $\mathbf{a}$.

\item Skewness
\begin{equation}
\label{eq:s}
s(\mathbf{a})= \frac{ \displaystyle \frac{1}{l_1} \sum_{i=1}^{l_1} [a(i)-\mu]^3}{\displaystyle \left(\frac{1}{l_1}\left(\sum_{i=1}^{l_1} [a(i)-\mu]^2\right)\right)^{3/2} }.
\end{equation}

\item Kurtosis
\begin{equation}
\label{eq:k}
k(\mathbf{a}) = \frac{ \displaystyle \frac{1}{l_1} \sum_{i=1}^{l_1} [a(i)-\mu]^4}{\displaystyle \left(\frac{1}{l_1}\left(\sum_{i=1}^{l_1} [a(i)-\mu]^2\right)\right)^2 }.
\end{equation}
\end{enumerate}

To compare the effectiveness of different metrics in distinguishing between the noise-contaminated and noise-free atoms, we show some typical atoms extracted from a field dataset that are contaminated by footprint noise in Figure \ref{fig:sta_atoms2}. Each atom has a size of $8\times 8$. It is clear that among the 64 atoms, the morphological features can be roughly divided into two types, i.e., \old{wether}\new{whether} containing horizontal stripes or not. It is easy to pick those stripes-contaminated atoms manually from the 64 atoms, as indicated by the black circles in the middle of each atom. In this example, we manually choose 32 noise-contaminated atoms with the others being the noise-free atoms. The noise-contaminated atoms need to be filtered out in order to better represent the useful signal via the sparse coding process. To see which statistical metric best detects the morphological anomalies shown in the noise-contaminated atoms, we calculate the aforementioned statistical metrics for all these atoms. We show the values of different statistical metrics for all 64 atoms in Figure \ref{fig:sta_curves}. Red, blue, cyan correspond to kurtosis, skewness, and variance, respectively. We also plot the manually picked noise-contaminated atoms as the light blue windows overlapping the curves in Figure \ref{fig:sta_curves}. It is clear that the abnormally high values of the variance curve correlate with the existence of light windows well. However, the red kurtosis curve and blue skewness curve do not show clear correlation patterns.

We use these statistical metrics as the criterion for a binary classification, i.e., 1 for noise-contaminated atoms and 0 for noise-free atoms. We plot the classification results of different statistical metrics and the ground-truth solution (defined by the manual picks) in Figure \ref{fig:sta_result}. \new{It is clear that the curve using the variance metric is mostly overlapping the ground-truth solution, indicating a very accurate classification performance. The kurtosis (red) and skewness (blue) metrics, however, deviate greatly from the ground-truth solution.} Figure \ref{fig:sta_err} plots the errors using the three statistical metrics. It is clear that the error of the variance metric is mostly zero while the other two metrics cause significant classification error. Here, the error in the classification is defined as \cite{yangkang2018gji}:
\begin{equation}
\label{eq:err}
\text{E} = \sum_{i=1}^{K} |I(i) - \hat{I}(i) |,
\end{equation}
where $i$ denotes the atom index, $I$ denotes the classification result (1 or 0) for the ground-truth solution, $\hat{I}$ is the classification output using different methods. The error corresponding to the variance metric is only 2,  meaning that only two atoms are not classified correctly, while the errors of the kurtosis and skewness metrics are both 44, meaning that 44 atoms (in 64) are classified inaccurately.  Thus, we use the variance metric as the criterion to divide the learned atoms into noise-free and noise-contaminated atoms.

The noise-contaminated atoms, however, are not simply deserted. Since these atoms may still contain significant signal features that are hidden in the stripes-like noise, we propose to apply a median filter along the vertical direction to filter out stripes-like noise and recover the signal features. We obtain the signal atoms by combining the noise-free atoms picked by the statistic-guided method and the filtered noise-contaminated atoms via median filtering. In cases that the picked noise-free atoms still contain very weak stripes-like noise features, they will be processed by a weak median filters to further filter out the noise features. 
After the filtering, we obtain two dictionaries, i.e., signal and noise dictionaries. 
%% also add an algorithm

\subsection{Residual dictionary learning}
Supposing the filtered dictionary is $\tilde{\mathbf{D}}$,  in a traditional sparse coding method, the denoised seismic data can be obtained by \old{first }sparse coding:
\begin{equation}
\label{eq:sc0}
\forall_i \tilde{\mathbf{m}}_{i}=\arg\min_{\mathbf{M}}||\mathbf{Y}-\tilde{\mathbf{D}}\mathbf{M}||^{2}_{F}, \quad\text{s.t.}  \quad \forall_i ||\mathbf{m}_{i}||_{0}\le Q,
\end{equation}
\old{then, by linear combination of the learned dictionary atoms based on the sparse coefficients. We can obtain the denoised data using a standard dictionary learning scheme:}\new{then, by linear combination of the learned dictionary atoms based on the sparse coefficients, we can obtain the denoised data using a standard dictionary learning scheme:}
\begin{equation}
\label{eq:sc1}
\tilde{\mathbf{Y}} = \tilde{\mathbf{D}} \tilde{\mathbf{M}},
\end{equation}
where $\tilde{\mathbf{M}}$ is composed \old{by}\new{of} $\tilde{\mathbf{m}}_{i}$, and $\tilde{\mathbf{Y}}$ denotes the denoised patches.

In the proposed method, to make the denoised data $\tilde{\mathbf{D}}$ less contaminated by the footprint noise, we propose the following augmented sparse coding problem:
\begin{equation}
\label{eq:sc2}
\begin{split}
\forall_i [\tilde{\mathbf{m}}_{i},\tilde{\mathbf{g}}_{i}]&=\arg\min||\mathbf{Y}-\tilde{\mathbf{D}}\mathbf{M} - \tilde{\mathbf{B}}\mathbf{G} ||^{2}_{F}, \\
& \quad\text{s.t.}  \quad \forall_i ||\mathbf{m}_{i}||_{0}+||\mathbf{g}_{i}||_{0} \le Q,
\end{split}
\end{equation}
where $\tilde{\mathbf{B}}$ denotes the learned footprint feature atoms. It can be calculated simply by
\begin{equation}
\label{eq:ftf}
\tilde{\mathbf{B}}=\mathbf{D}-\tilde{\mathbf{D}}.
\end{equation}
Equation \ref{eq:sc2} is equivalent to learning the residual of the traditional dictionary learning $\mathbf{R}=\mathbf{Y}-\tilde{\mathbf{D}}\mathbf{M}$ via the learned footprint feature atoms $\tilde{\mathbf{B}}$. Thus, we call it residual dictionary learning.

%Let $\overline{\mathbf{D}} = [\tilde{\mathbf{D}},\tilde{\mathbf{B}}]$, and 
Equation \ref{eq:sc2} can be expressed as:
\begin{equation}
\label{eq:sc22}
\forall_i \tilde{\mathbf{p}}_{i}=\arg\min||\mathbf{Y}-\mathbf{F}\mathbf{P} ||^{2}_{F}, \quad\text{s.t.}  \quad \forall_i ||\mathbf{p}_{i}||_{0} \le Q,
\end{equation}
where 
\begin{equation}
\label{eq:scF}
\mathbf{F} = \left[\begin{array}{cc}
\tilde{\mathbf{D}} & \tilde{\mathbf{B}}
\end{array}
\right], \text{and}, 
\mathbf{P} = \left[\begin{array}{c}
\mathbf{M} \\
\mathbf{G}
\end{array}
\right].
\end{equation}
Equation \ref{eq:sc2} can be solved via the standard OMP algorithm. The solution of equation \ref{eq:sc2} ($\tilde{\mathbf{P}}$) can be expressed as:
\begin{equation}
\label{eq:scF}
\tilde{\mathbf{P}} = \left[\begin{array}{c}
\tilde{\mathbf{M}} \\
\tilde{\mathbf{G}}
\end{array}
\right],
\end{equation}
where $\tilde{\mathbf{M}}$ and $\tilde{\mathbf{G}}$ denote the sparse coefficients corresponding to the signal atoms $\tilde{\mathbf{D}}$ and noise atoms $\tilde{\mathbf{B}}$. The denoised data $\tilde{\mathbf{S}}$ and estimated footprint noise $\tilde{\mathbf{N}}$ can be represented by:
\new{\begin{equation}
\label{eq:sc1}
\tilde{\mathbf{S}} = \tilde{\mathbf{D}} \tilde{\mathbf{M}}\quad \text{and} \quad
\tilde{\mathbf{N}} = \tilde{\mathbf{B}} \tilde{\mathbf{G}}.
\end{equation}}

The complete algorithm of the proposed statistics-guided residual dictionary learning method (SGRDL) is detailed in Algorithm \ref{alg:alg1}.

\begin{algorithm}[htb!]
   \caption{Statistics-guided residual dictionary learning algorithm}
   \textbf{Input:} Noisy data $\mathbf{d}$, number of learning iterations $N_{iter}$, sparsity parameter $Q$.
    \begin{algorithmic}[1]
    \State Segment the data using a patching scheme
        \For{$i$ = $1,\cdots,N_{iter}$}
     \State \textbf{Solve}: $\hat{\mathbf{D}}^n = \arg\min_{\mathbf{D}^n} \parallel \mathbf{Y} - \mathbf{D}^n\mathbf{M}^n \parallel_F^2$
     \State \textbf{Solve}: $\hat{\mathbf{M}}^n = \arg\min_{\mathbf{M}^n} \parallel \mathbf{Y} - \mathbf{D}^n\mathbf{M}^n \parallel_F^2, \quad\text{s.t.}  \quad \forall_i ||\mathbf{m}_{i}||_{0}\le Q$
        \EndFor 
        \State Atom classification based on the statistics-guided scheme
        \State Apply median filtering to noise-contaminated atoms
        \State Augment the dictionary by $\mathbf{F} = [\tilde{\mathbf{D}}, \tilde{\mathbf{B}}]$
        \State Sparse coding by solving: $\forall_i [\tilde{\mathbf{p}}_{i}]=\arg\min_{\mathbf{P}}||\mathbf{Y}-\mathbf{F}\mathbf{P} ||^{2}_{F}, \quad\text{s.t.}  \quad \forall_i ||\mathbf{p}_{i}||_{0} \le Q$
        \State Obtain the denoised patches $\tilde{\mathbf{S}} = \tilde{\mathbf{D}} \tilde{\mathbf{M}}$
        \State Reconstruct the data via an unpatching scheme
%         \State \textbf{1D inverse FFT}: $\hat{D}(x,t)=\text{IFFT}\left(\hat{D}(x,w)\right)$
\end{algorithmic}
   \textbf{Output:} Denoised data $\hat{\mathbf{d}}$
\label{alg:alg1}
\end{algorithm}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.8\columnwidth]{peno/Fig/p}}
\caption{3D field data (the Penobscot dataset). }
\label{fig:p}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Fig/p_atom0}
   \label{fig:p_atom0}}\\
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Fig/p_atom1}
   \label{fig:p_atom1}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Fig/p_atom2}
   \label{fig:p_atom2}}
\caption{A comparison of the dictionary atoms of the field data example. (a) Learned atoms directly from field data. (b) Learned signal atoms obtained by selecting noise-free atoms via the statistics-guided method and filtering the noise-contaminated atoms via the median filtering method. (c) Learned footprint noise atoms by subtracting (b) from (a). The green atoms indicate those selected noise-free atoms. }
\label{fig:p_atom0,p_atom1,p_atom2}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.45\columnwidth]{peno/Fig/p-drr}
   \label{fig:p-drr}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{peno/Fig/p-dl-0}
   \label{fig:p-dl-0}}\\
\subfloat[]{\includegraphics[width=0.45\columnwidth]{peno/Fig/p-mf}
   \label{fig:p-mf}}
   \subfloat[]{\includegraphics[width=0.45\columnwidth]{peno/Fig/p-sgrdl}
   \label{fig:p-sgrdl}}
\caption{Denosing comparison of the field data example. Denoised data using (a) DRR method, (b) standard DL method, (c) median filtering method, and (d) the proposed SGRDL method. }
\label{fig:p-drr,p-dl-0,p-mf,p-sgrdl}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.45\columnwidth]{peno/Fig/p-drr-n-0}
   \label{fig:p-drr-n-0}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{peno/Fig/p-dl-n}
   \label{fig:p-dl-n}}\\
\subfloat[]{\includegraphics[width=0.45\columnwidth]{peno/Fig/p-mf-n-0}
   \label{fig:p-mf-n-0}}
   \subfloat[]{\includegraphics[width=0.45\columnwidth]{peno/Fig/p-sgrdl-n}
   \label{fig:p-sgrdl-n}}
\caption{Denosing comparison of the field data example. Removed noise using (a) DRR method, (b) standard DL method, (c) median filtering method, and (d) the proposed SGRDL method. }
\label{fig:p-drr-n-0,p-dl-n,p-mf-n-0,p-sgrdl-n}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.45\columnwidth]{peno/Fig/p-t}
   \label{fig:p-t}}\\
\subfloat[]{\includegraphics[width=0.45\columnwidth]{peno/Fig/p-drr-t}
   \label{fig:p-drr-t}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{peno/Fig/p-dl-t}
   \label{fig:p-dl-t}}\\
\subfloat[]{\includegraphics[width=0.45\columnwidth]{peno/Fig/p-mf-t}
   \label{fig:p-mf-t}}
   \subfloat[]{\includegraphics[width=0.45\columnwidth]{peno/Fig/p-sgrdl-t}
   \label{fig:p-sgrdl-t}}
\caption{Constant time slice comparison of the field data example. Denoised data using (a) DRR method, (b) standard DL method, (c) median filtering method, and (d) the proposed SGRDL method. }
\label{fig:p-drr-t,p-dl-t,p-mf-t,p-sgrdl-t}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.45\columnwidth]{peno/Fig/p-drr-n-t}
   \label{fig:p-drr-n-t}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{peno/Fig/p-dl-n-t}
   \label{fig:p-dl-n-t}}\\
\subfloat[]{\includegraphics[width=0.45\columnwidth]{peno/Fig/p-mf-n-t}
   \label{fig:p-mf-n-t}}
   \subfloat[]{\includegraphics[width=0.45\columnwidth]{peno/Fig/p-sgrdl-n-t}
   \label{fig:p-sgrdl-n-t}}
\caption{Constant time slice comparison of the field data example. Removed noise using (a) DRR method, (b) standard DL method, (c) median filtering method, and (d) the proposed SGRDL method. }
\label{fig:p-drr-n-t,p-dl-n-t,p-mf-n-t,p-sgrdl-n-t}
\end{figure}

\section{Examples}
First, we create a synthetic test to verify the ability of the proposed method in suppressing footprint noise. Because we have the ground-truth solution of the useful signals as well as the noise, we can evaluate the denoising performance of different methods quantitatively. We use the signal-to-noise ratio (SNR) metric defined as:
\begin{equation}
\label{eq:snr}
\text{SNR}=10\log_{10}\frac{\Arrowvert \mathbf{d} \Arrowvert_2^2}{\Arrowvert \mathbf{d} -\hat{\mathbf{d}}\Arrowvert_2^2},
\end{equation}
to compare different methods. In equation \ref{eq:snr}, $\mathbf{d}$ denotes the clean data. $\hat{\mathbf{d}}$ denotes the noisy data or estimated signals.

The synthetic data example is plotted in Figure \ref{fig:syn-c,syn-nft,syn-nrand,syn-n}. Figure \ref{fig:syn-c} shows the clean synthetic data. The data size is $300\times 40\times 40$. Figure \ref{fig:syn-nft} shows the simulated footprint noise. Figure \ref{fig:syn-nrand} shows the band-limited random noise. Figure \ref{fig:syn-n} shows the noisy data with both random noise and footprint noise. Figure \ref{fig:s_atom0,s_atom1,s_atom2} shows a comparison of different dictionaries. Figure \ref{fig:s_atom0} plots the learned dictionary from the 100th time slice using the K-SVD algorithm. There are 64 atoms in the dictionary. It is clear that some atoms are seriously contaminated with stripes-like noise. Figure \ref{fig:s_atom1} shows the filtered atoms using the proposed statistics-guided atom selection strategy. In this example, we choose the atoms of the 15\% largest variation metric as the noise-free atoms. For other atoms, we treat them as noise-contaminated atoms and apply median filtering on the atoms to filter out the stripes-like noise. The median filtering is applied four times consecutively with a filtering length of 4 samples.  To further make the selected noise-free atoms cleaner, we apply a mild median filtering with a filter length of 2 samples once. Figure \ref{fig:s_atom2} shows the learned footprint noise atoms by subtracting the signal atoms in Figure \ref{fig:s_atom1} from the initially learned atoms in Figure \ref{fig:s_atom0}. It is clear that the atoms in Figure \ref{fig:s_atom2} mostly represent the footprint noise. In this example, we learn the dictionary atoms from the 100th time slice and apply the atoms in sparse coding of all the other time slices.

Figure \ref{fig:syn-drr,syn-dl,syn-mf-0,syn-sgrdl-0} shows a denoising comparison. We compare the performance of the proposed SGRDL method with several state-of-the-art methods, e.g., the damped rank-reduction method (DRR), traditional dictionary learning (DL) method, and the median filtering (MF) method. We choose the DRR method for comparison because it is one of the most effective denoising methods for random noise. We choose the DL method for comparison because the new method is developed based on the DL method. We choose the MF method for comparison because it is an effective method for removing the footprint noise. From Figure \ref{fig:syn-drr,syn-dl,syn-mf-0,syn-sgrdl-0}, it is clear that both DRR and DL methods successfully remove the random noise, but completely fail in removing the footprint noise. The MF method removes most footprint noise but causes significant damages to the useful signals. The proposed method, however, obtains the best performance. Although there is some residual footprint noise, considering the difference before and after the denoising, the little residual footprint noise is insignificant. To better visualize the denoising performance, we show the removed noise cubes in Figure \ref{fig:syn-drr-n,syn-dl-n,syn-mf-n-0,syn-sgrdl-n-0}. It becomes clearer that both DRR and DL methods remove a lot of random noise but suppress negligible footprint noise. The MF method removes the footprint noise effectively, but causes significant coherent signal energy in the noise. The proposed method removes a lot of footprint noise while causing negligible damages to the useful signals. We use local similarity comparison to further verify the fidelity of the signal recovery from the noisy observations. The local similarity is an effective way to measure the accuracy of the recovered signals in a local way \cite{yangkang2015ortho}. The higher the local similarity map between the ground-truth solution and the recovered signals, the higher accuracy.  Figure \ref{fig:syn-drr-s,syn-dl-s,syn-mf-s,syn-sgrdl-s} shows the comparison of local similarity. It is clear that the proposed method obtains significantly higher local similarity values around the signal samples.

We show a single-slice comparison of the synthetic data in Figure \ref{fig:syn-s-c,syn-s-n,syn-s-drr,syn-s-dl,syn-s-mf-0,syn-s-sgrdl-0}. A single-slice noise comparison is shown in Figure \ref{fig:syn-s-c,syn-s-n,syn-s-drr,syn-s-dl,syn-s-mf-0,syn-s-sgrdl}. Figures \ref{fig:syn-s-c,syn-s-n,syn-s-drr,syn-s-dl,syn-s-mf-0,syn-s-sgrdl-0} and \ref{fig:syn-s-c,syn-s-n,syn-s-drr,syn-s-dl,syn-s-mf-0,syn-s-sgrdl} further confirm the better denoising performance of the proposed method.  A constant slice comparison (of time 0.8 s) of different datasets is plotted in Figure \ref{fig:syn-c-t,syn-n-t,syn-drr-t,syn-dl-t,syn-mf-t,syn-sgrdl-t}, where it is easier to find that the proposed method causes the least residual noise. To compare the amplitude-preservation performance of different methods in detail, we plot a single-trace comparison in Figure \ref{fig:syn-ss-0,syn-ss-z}. Figure \ref{fig:syn-ss-0} shows the comparison between the clean data, noisy data, denoised data using different methods in the original scale. Figure \ref{fig:syn-ss-z} plots a zoomed comparison, corresponding to the yellow frame box appearing in Figure \ref{fig:syn-ss-0}. The black line corresponds to the clean data. The green line corresponds to the noisy data. The red line corresponds to the proposed SGRDL method. The magenta line corresponds to the MF method. The blue line corresponds to the standard DL method. The cyan line corresponds to the DRR method. From Figure \ref{fig:syn-ss-z}, it is clear that the proposed method (red) is the closest to the clean data (black).

Then, we use a 3D field data example to demonstrate the performance of the proposed method. The 3D field data set is plotted in Figure \ref{fig:p}.  There is significant footprint noise in each time slice of this dataset, as shown in the top square panel of Figure \ref{fig:p}. The learned atoms from the 27th time slice are plotted in Figure \ref{fig:p_atom0}. Most of the atoms are contaminated with clear stripes-like footprint noise. We apply the statistics-guided atom selection and filtering strategy to obtain a filtered dictionary, as plotted in Figure \ref{fig:p_atom1}. In this case, we preserve 10\% of the atoms that have the largest variation values. We apply median filtering with a filter length of four samples by four consecutive times to filter out all the footprint noise patterns. The filtered atoms are much smoother and better represent the signal features. The estimated footprint noise atoms are plotted in Figure \ref{fig:p_atom2} by subtracting the filtered atoms (Figure \ref{fig:p_atom1}) from the raw atoms (Figure \ref{fig:p_atom0}). The subtracted atoms mostly contain the features of the footprint noise. The green atoms indicate those selected noise-free atoms, which are not applied the median filtering. In this example, we learn the dictionaries from the 27th time slice and apply the dictionaries to all the other time slices. The comparison of denoised data is plotted in Figure \ref{fig:p-drr,p-dl-0,p-mf,p-sgrdl}. It is clear that the DRR method over-smoothes the field data, removing a lot of details from the image. The traditional DL method fails in removing the footprint noise. The MF method effectively removes the footprint noise, but making the seismic data less continuous. The proposed method, however, removes all the footprint noise without causing artifacts.  Figure \ref{fig:p-drr-n-0,p-dl-n,p-mf-n-0,p-sgrdl-n} plots a comparison of the removed noise cubes. It is more obvious that the DRR method removes a lot of details from the data, as shown in the top panel of Figure \ref{fig:p-drr-n-0}. The DL method mostly removes the random noise. The MF method removes some footprint noise but causes clear discontinuity in the noise, indicating a significant amount of remaining footprint noise. The proposed method removes all the footprint noise without causing significant signal damages or residual noise. We show a comparison of constant time slice in Figure \ref{fig:p-drr-t,p-dl-t,p-mf-t,p-sgrdl-t}. The corresponding noise slices are plotted in Figure \ref{fig:p-drr-n-t,p-dl-n-t,p-mf-n-t,p-sgrdl-n-t}. It is clearer from these time slices that the DRR method causes significant signal damages, and the DL method fails in suppressing sufficient footprint noise. The median filter method causes significant discontinuities. The proposed SGRDL method, however, obtains an obviously better result.

\section{Discussions}
The proposed method adds no extra computational cost to the traditional DL method in the dictionary updating process. However, in the sparse coding process, due to the augmented dictionary concatenating both the filtered atoms and the footprint noise feature atoms, the coding cost will be roughly doubled. The statistics-guided atom selection process and the median filtering step are very efficient, and their computational costs compared with the dictionary updating and sparse coding processes are negligible. Considering the number of atoms $K$, calculating the variation metric for each atom has a computational complexity of $O(K)$. For selecting those noise-free atoms, one needs to sort the variances and select the atoms with the lowest values. This sorting process takes $O(K\log(K))$. The median filtering step applied onto each atom roughly takes $O(K)$. Considering that $K$ is usually a small value, e.g., 64, in all examples of this paper, the complexity of the atom selection and filtering step is very small. In both traditional DL method and the proposed method, the K-SVD step takes a significant portion of the total cost. More efficient dictionary updating schemes and their applications in the presented denoising framework are worth investigating. It is worth noting that we have tried the sequential generalized K -means (SGK) method developed in \cite{yangkang2020sgk}, but it does not work effectively for learning the  features of the useful signals and the footprint noise. It maybe caused by the fact that the summation of patches in the SGK method could smooth the footprint noise pattern and then weaken the ability of the framework to distinguish between the signal and noise in terms of learned atoms.

\new{The biggest contribution of this paper is the nearly automated framework for separating the footprint noise patterns from the learned signal atoms.} To do this, the variance based statistical metric is used for classifying the initially learned atoms. Statistical metrics other than the variance metric are worth testing for a specific problem. The kurtosis and skewness metrics that work reasonably well in some previous work \cite{yatong2021} might also work for specific datasets or applications. However, the overall framework is simple and easy to use. Changing a different statistical metric is straightforwardly applicable. The percentage used to preserve the noise-free atoms needs some try-and-error tuning processes, but is easy to adjust. Another parameter that might require some attention is the patch size to segment the 2D time slices. The patch size is a compromise between the resolution and smoothness in the learned atoms. A larger patch will result in the failure in capturing the detailed signal patterns, due to a lower resolution. A smaller patch has a higher resolution but tends to mix the signal and noise, which makes the statistical metric difficult to distinguish between the noise-free and noise-contaminated atoms. According to some previous studies, e.g., in \cite{guoyin2018,yangkang2019srl}, the patch size should better be chosen as half of the wavelength of useful signals.

%computational cost, why SGK does not work
%parameter, percentage
%
%

\section{Conclusions}
Because the footprint noise could significantly affect the fidelity of many seismic processing and interpretation tasks, we have proposed a statistics-guided residual dictionary learning (SGRDL) method to remove it from 3D seismic data volumes. The footprint noise will leave special feature patterns on the learned dictionary atoms using a standard K-SVD method. However, the initially learned dictionary patterns are not all affected by the footprint noise. To preserve the footprint-free atoms, we propose a statistics-guided strategy, where the atoms \old{corresponding the low values}\new{corresponding to the low values} of the chosen statistic (e.g., the variance) that represents a smaller energy oscillation are preserved. A median filter is applied to the other footprint-affected atoms to separate out the footprint patterns and output a footprint dictionary. The signal and footprint dictionaries are both used to encode the input seismic data to obtain both the optimal representation of the signal waveforms and the optimally learned footprint noise, which is referred to as a residual dictionary learning process. Both synthetic and field data examples demonstrate that the proposed method is effective and outperforms some state-of-the-art denoising methods.

%\section{Acknowledgements}
%\section{Discussions}
%\section{Conclusions}
%\section{Acknowledgements}

\bibliographystyle{seg}
\bibliography{ft}

%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{wei.jpg}}]{Wei Chen} received the B.E. and Ph.D. degrees in geophysics from the China University of Petroleum, Beijing, China, in 2008 and 2016, respectively.
%He is an Associate Professor with Yangtze University, Wuhan, China. His research interests include seismic signal analysis, time–frequency analysis, and seismic data processing.
%\end{IEEEbiography}
%
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{omar.jpg}}]{Omar M. Saad} received the B.S. and M.S. in Electrical Engineering, Arab Academy for Science Technology \& Maritime Transport (AASTMT), Alexandria, Egypt, in 2012 and 2015, respectively. Then he received a Ph.D. in Electrical Engineering from Egypt Japan University of Science and Technology - EJUST, Alexandria, Egypt, in 2019. Currently, he is a researcher at the National Research Institute of Astronomy and Geophysics (NRIAG), Egypt, and he is a Postdoc in School of Earth Sciences, Zhejiang University, China. He is mainly engaged in machine learning in the field of seismology, earthquake early warning systems, and signal processing techniques.
%\end{IEEEbiography}
%
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{hang}}]{Hang Wang} received a master degree in geological resources and geological engineering from China University of Petroleum (Beijing), and he is a Ph.D. candidate in geophysics at Zhejiang University. His research interests include seismic signal processing, machine learning and FWI.
%\end{IEEEbiography}
%
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{yangkang}}]{Yangkang Chen} (M'20) received the B.S. degree in exploration geophysics from the China University of Petroleum, Beijing, China, in 2012, and the Ph.D. degree in geophysics from the University of Texas at Austin, Austin, TX, USA, under the supervision of Prof. S. Fomel, in 2015. From 2016 to 2018, he was a Distinguished Post-Doctoral Research Associate with the Oak Ridge National Laboratory, Oak Ridge, Tennessee, USA. He is now an assistant professor at Zhejiang University, China. He has authored more than 100 internationally renowned journal articles and more than 80 international conference papers. His current research interests include seismic signal analysis, seismic modeling and inversion, simultaneous-source data deblending and imaging, global adjoint tomography, and high-performance computing.
%\end{IEEEbiography}

%\begin{figure}[htb!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.8\columnwidth]{Fig/fig}}
%	\caption{Caption.}
%	\label{fig:fig}
%\end{figure}

%\begin{figure}[htb!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.45\columnwidth]{Fig/fig1}}\\
%    \subfloat[]{\includegraphics[width=0.45\columnwidth]{Fig/fig2}}
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure}

%\begin{table}[h]
%\caption{Table caption}
%\begin{center}
%     \begin{tabular}{|c|c|c|c|c|c|} 
%	  \hline Column1 (unit)  & Column2 (unit) & Column3 (unit) \\ 
%	  \hline 1 & 2  & 3 \\
%       \hline
%    \end{tabular} 
%\end{center}
%\label{tbl:table1}
%\end{table}

### 2021-04-24 foot/matfun/Peno.m

@@ -1,0 +1,267 @@
+function Peno(noisy,d_sgrdl,d_mf,d_dl,d_drr)
+% Author      : Wei Chen and Yangkang Chen
+%               Yangtze University and Zhejiang University
+%         
+% Date        : Feb, 2021
+%
+% Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
+%
+%  Copyright (C) 2021 Yangtze University and Zhejiang University
+%  Copyright (C) 2021 Wei Chen and Yangkang Chen
+%  
+%  This program is free software; you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published by
+%  the Free Software Foundation; either version 2 of the License, or
+%  (at your option) any later version.
+%  
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%  
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, write to the Free Software
+%  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  
+%  
+%  Reference:
+%  Chen et al., 2021, Statistics-guided residual dictionary learning for footprint noise removal, IEEE TGRS, doi: 10.1109/TGRS.2021.3070903.
+%  Zhou et al., 2021, Statistics-guided dictionary learning for automatic coherent noise suppression, IEEE TGRS, doi: 10.1109/TGRS.2020.3039738.
+%  Wang et al., 2020, Fast dictionary learning for high-dimensional seismic reconstruction, IEEE TGRS, doi: 10.1109/TGRS.2020.3030740.
[…]

### 2021-04-24 foot/matfun/Synth.m

@@ -1,0 +1,379 @@
+function Synth(clean,nft,noisy,d_sgrdl,d_mf,d_dl,d_drr)
+% Author      : Wei Chen and Yangkang Chen
+%               Yangtze University and Zhejiang University
+%         
+% Date        : Feb, 2021
+%
+% Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
+%
+%  Copyright (C) 2021 Yangtze University and Zhejiang University
+%  Copyright (C) 2021 Wei Chen and Yangkang Chen
+%  
+%  This program is free software; you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published by
+%  the Free Software Foundation; either version 2 of the License, or
+%  (at your option) any later version.
+%  
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%  
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, write to the Free Software
+%  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  
+%  
+%  Reference:
+%  Chen et al., 2021, Statistics-guided residual dictionary learning for footprint noise removal, IEEE TGRS, doi: 10.1109/TGRS.2021.3070903.
+%  Zhou et al., 2021, Statistics-guided dictionary learning for automatic coherent noise suppression, IEEE TGRS, doi: 10.1109/TGRS.2020.3039738.
[…]

### 2021-04-24 foot/matfun/yc_kurtosis2.m

@@ -1,0 +1,39 @@
+function k = yc_kurtosis2(D,N1,N2,axis,flag)
+% yc_kurtosis2: kurtosis calculation for a 2D Dictionary 
+% By Wei Chen and Yangkang Chen
+% Jan, 2021
+% INPUT
+% x:     input
+% flag:  bias (1) or unbias (0)   
+% OUTPUT
+% k: Kurtosis
+%
+% DEMO
+% 1. a=randn(10,1);norm(yc_kurtosis(a)-kurtosis(a))
+% 2. a=randn(10,1);norm(yc_kurtosis(a,0)-kurtosis(a,0))
+% 
+% assuming x is a vector
+if nargin==3
+   axis=1;
+   flag=1;
+end
+
+[n1,n2]=size(D);
+if n1~=N1*N2
+   error('dimension mismatch'); 
+end
+
+k=zeros(1,n2);
+for i2=1:n2
+ 
+    dtmp=reshape(D(:,i2),N1,N2);
+    if axis==1
+       k(i2)=sum(yc_kurtosis(dtmp).^2); 
+    else
+       k(i2)=sum(yc_kurtosis(dtmp').^2);  
+    end
+end
+
+
+return
+

### 2021-05-12 passive/paper.tex
up

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}

\title{A compact program for 3D passive seismic \\
source-location imaging}

\author{Yangkang Chen\footnotemark[1], Omar M. Saad\footnotemark[1]\footnotemark[2], Min Bai\footnotemark[3],  Xingye Liu\footnotemark[4], Sergey Fomel\footnotemark[5] }
%\author{Authors}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

%\author{Authors}

\ms{SRL-2021} %\ms{GJI-2019}

\address{
%\footnotemark[1]
%School of Earth Sciences\\
%Zhejiang University\\
%Hangzhou, Zhejiang Province, China, 310027\\
%chenyk2016@gmail.com\\
%%yangkang.chen@zju.edu.cn \\
%\footnotemark[2]
%ENSN Lab \\
%Seismology Department \\
%National Research Institute of Astronomy and Geophysics (NRIAG)\\
%Helwan 11731, Egypt\\
%engomar91@ gmail.com\\
%\footnotemark[3] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
%Yangtze University\\
%Daxue Road No.111\\
%Caidian District\\
%Wuhan, China, 430100 \\
%\footnotemark[4]
%College of Geology and Environment\\
%Xi’an University of Science and Technology\\
%Xi’an, Shaanxi Province, China, 710054 \\
%lwxwyh506673@126.com\\
%\footnotemark[5]Bureau of Economic Geology \\
%John A. and Katherine G. Jackson School of Geosciences \\
%The University of Texas at Austin \\
%University Station, Box X \\
%Austin, TX 78713-8924 \\
%sergey.fomel@beg.utexas.edu\\
Corresponding Author: Yangkang Chen (chenyk2016@gmail.com) 
}

%\lefthead{Liu et al.}
\righthead{3D passive imaging\\
Declaration of Competing Interests: The authors acknowledge there are no conflicts of interest recorded.}

\begin{abstract}
Microseismic source-location imaging is important for inferring the dynamic status of reservoirs during hydraulic fracturing. The accuracy and resolution of the located microseismic sources are closely related to the imaging technique. We present an open-source program for high-fidelity and high-resolution 3D microseismic source-location imaging. The presented code is compact in the sense that all required subroutines are included in one single C program, based on which the seismic wavefields can be propagated either forward during a synthetic test, or backward during a real time-reversal imaging process. The compact C program is accompanied by a python script known as the SConstruct file in the Madagascar open-source platform to compile and run the C program. The velocity model and recorded microseismic data can be input using the python script. \wen{This compact program is useful for educational purposes and for future algorithm development.} We introduce the basics of the imaging method used in the presented package and present one representative synthetic example and a field data example. The results show that the presented program can be reliably used to locate source locations using a passive seismic dataset.
\end{abstract}

%\section{Keywords}
%key1,key2,key3

\section{Introduction}
The microseismic technology\dlo{, as an advanced technology,} has been applied in water reservoirs monitoring, mining engineering, CO$_2$ injection monitoring, and petroleum and gas exploration field \new{\cite[]{Phillips2002, Parotidis2004Back, 2005Characterization, Rongmao2010Microseismic, Xia2013Twin, 2016Discrimination, 2016Adaptive, 2016Hybrid}}. It focuses on the characteristics of microseismic sources, i.e., newly created or activated micro-cracks and fractures that may be caused by fracturing or mining processes, etc. The occurrence of microseismic events is always accompanied by propagating \dlo{the }seismic waves. For example, due to fluid injection of shale gas development, high injection pressure that exceeds \dlo{a certain level}\wen{the minimum tensile strength of the rock} will interact with fluid pressure in the existing fractures, open or create new fractures, then induce microseismic events.  When the dynamic information of the source carried by seismic waves is received by geophones, \old{one}\new{engineers} can localize the microseismic event and infer the spatial extent of induced fractures. As a result, microseismic imaging is significant to accurately reflect the location and spatial range of fractures with high resolution, then to optimize the production plan and avoid related hazards \cite[]{Nidhal2015}.

Microseismic event tracking or imaging is a typical passive seismic source-location imaging problem. 
A wide range of methods have been developed for passive seismic source-location imaging \wen{\cite[]{Husen2003, Nidhal2015, Steve2015, Anton2015, 2015Microseismic, Chuntao2016Joint}}. In general, localizing a passive source (e.g., earthquake hypocenter, microseismic event) can be regarded as an \old{inversion}\new{inverse} problem and \old{can be }solved by various inversion approaches. 
\cite{Waldhauser2000A} propose a double-difference technique and \old{localized}\new{localize} the passive sources by minimizing the least-squares error between computed and observed traveltime.
Then, \cite{2003Double} estimate the microseismic event locations and the corresponding velocity model by using the double-difference technique. 
These arrival \old{times}\new{time} based inversion algorithms aim to obtain the solution that makes the misfit function between the observed and calculated traveltimes reach the minimum. 
However, it heavily depends on accurate arrival \old{times}\new{time} picking, which is used to analyze the mechanism of microseismic events.  The short-term-average-to-long-term-average ratio method \cite[]{1978Automatic}, autoregression based method \cite[]{1999Multi}, Akaike information criterion method \cite[]{SLEEMAN1999265}, etc., have been developed for arrival times picking. 
However, the process is highly nonlinear, and \dlo{local optimization models}\wen{models that represent local minima of the objective function}, which are not the actual location of the hypocenter, are unavoidably considered as the solution \cite[]{Husen2003, Poliannikov2013A, Gesret2014Propagation, Nidhal2015}. Besides, the microseismic data are always accompanied by noise, which makes arrival times picking very challenging, and many approaches are sensitive to the noise \cite[]{Chen2018fast}. Therefore, it is necessary to suppress the noise as much as possible before applying the arrival times  based methods \cite[]{2015Microseismic, Juli2016A, 2016Hybrid}. The stacking location methods perform relatively better than the traditional arrival times picking  based approaches \cite[]{2005Reverse, 2007Localization, 2013Locating}. Nevertheless, the uncertainty is too strong when the records contain polarity reversal, and addressing this issue usually requires huge calculation resources \cite[]{2014Joint, Chuntao2016Joint}.

For passive source-location estimation, other commonly used methods are based on the \dlo{wave equation}\wen{waveform modeling}, which attracts more and more attention due to the improvements in computing power. \dlo{These methods assume that the wave modes remain identical during seismic wave propagation.} The time-reversal extrapolation can be conducted by solving the wave equation when the velocity model is \dlo{obtained}\wen{available} \cite[]{2005Reverse}. \cite{2008Time} track the earthquake location and the focal mechanism by using time-reversal imaging methods.  \cite{2010Source} point out that the problem of passive source-location imaging can be solved by the auto-correlation imaging condition because it could be regarded as a migration problem. They borrowed the imaging condition from the active-source seismic imaging to passive seismic source-location imaging. For microseismic imaging, \wen{\cite{2015Focusing}} improve the resolution in the horizontal and vertical directions with a deconvolution operator by using an accurate velocity model. 
\cite{Nori2015} use the geometric mean as the imaging condition in microseismic imaging based on the reverse time migration algorithm. This practice was similar to that of active-source seismic imaging. Geometric mean based reverse time migration methods are promising in retrieving velocity information, which is achieved by analyzing space and time lags of cross-correlation. 
\cite{LIN201688} develop a microseismic reverse time migration method on scattering waves for microseismic imaging and demonstrated the effectiveness by using some synthetic experiments. For continuous data, \cite{Norimitsu2016} repeatedly \dlo{utilized}\wen{use} the Green's function to extrapolate the observed data, reducing the calculation time. Then, they used multi-dimensional cross-correlation as an imaging condition and output an accurate source-location image.
However, some unwanted components (e.g., noise) are also received by geophone arrays, causing uncertainties of the passive sources by waveform based methods. 
For Woodford and Bakken shale reservoirs, \cite{Grechka2017High} \dlo{utilized}\wen{use} Kirchhoff migration to image hydraulic fractures. 
 \cite{Chen2018fast} \old{develop}\new{develops} a method based on machine learning to detect the signal waveforms automatically, then \old{eliminated}\new{eliminates} the influence of unwanted components contained in microseismic data. 
\cite{Jianlong2020} analyze several imaging conditions based on synthetic examples and \old{pointed}\new{point} out that the auto-correlation imaging condition is more proper to assure  resolution and noise resistance. \new{Another group of source-location imaging methods are based on full-waveform inversion (FWI). FWI can invert for the source image and velocity simultaneously, and has been intensively studied in the field of passive seismic imaging \cite[]{kaderli2015microseismic,sun2016full,wang2018microseismic,song2019microseismic2}. }
In addition, machine learning \old{technologies}\new{techniques} have  shown their potential in passive seismic source-location imaging recently, e.g.,  \cite{Jubran2017, qushan2020gji, Hanchen2020, Omar2020, Yatong2020}, etc.

Traditional methods either depend on accurate arrival times picking, or tend to be impacted by strong noise based on the waveforms and time-reversal imaging.  Inspired by both active and passive \old{sources}\new{source} seismic imaging, \cite{Junzhe2015} investigate the possibility of microseismic source-location imaging for data collected by distributed sensor networks. They concluded that borrowing the cross-correlation imaging condition from active \old{sources}\new{source} seismic imaging to passive seismic source-location imaging \old{does not need the information of arrival times}\new{does not require to pick the first arrival times}, and could simultaneously locate multiple microseismic events with a relatively high resolution. %\old{\cite{zhu2019hybrid} further apply this method to a real test of the Marcellus shale microseismic data.}

\wen{We extend the 2D passive seismic imaging method previously developed by \cite{Junzhe2015}, to a 3D version and provide a compact open-source program. Not only the forward propagated seismic wavefields (e.g., for synthetic tests), but also the backward propagation (required by time-reversal imaging) can be simulated by using the program. Even if the signal-to-noise ratio (S/N) is low, it is able to produce a microseismic imaging result with high fidelity and a high resolution while not requiring to pick the arrival times.} In the following section, we briefly review the new method and introduce the construction of the compact C program and the python script compiling and running it. Then, we demonstrate its effectiveness by a 3D synthetic experiment and a field data example. Next, we discuss various aspects that could affect the imaging performance and its wide applications. Finally, we summarize the method and the program\old{ in the end}.

\section{Method}
\subsection{Forward modeling method}
The second-order acoustic wave equation with constant density can be expressed as:
\begin{equation}
\label{eq:we}
\frac{1}{v^2}\frac{\partial^2 p}{\partial t^2} = \frac{\partial^2 p}{\partial z^2} + \frac{\partial^2 p}{\partial x^2} + \frac{\partial^2 p}{\partial y^2},
\end{equation}
where $v(z,x,y)$ denotes the heterogeneous velocity distribution, $p(z,x,y,t)$ denotes the acoustic wavefield.

A second-order temporal finite difference scheme to solve the acoustic wave equation can be expressed as:
\begin{equation}
\label{eq:we2}
p^{n+1}=2p^{n}-p^{n-1}+v^2\Delta t^2\left(\frac{\partial^2 p}{\partial z^2} + \frac{\partial^2 p}{\partial x^2} + \frac{\partial^2 p}{\partial y^2}\right),
\end{equation}
where $p^{n}$ denotes the wavefield at the $n$th time step. The spatial derivatives on the right side of equation \ref{eq:we2} can be calculated either by the Fourier method, i.e., the pseudo-spectral method, or by the finite difference method. In the presented program, we use the pseudo-spectral method to solve the acoustic wave equation: 
\begin{equation}
\label{eq:we22}
p^{n+1}=2p^{n}-p^{n-1}+v^2\Delta t^2\left(\mathcal{F}^{-1}[(-k_z^2-k_x^2-k_y^2)\mathcal{F}(p^n)]\right),
\end{equation}
where $\mathcal{F}$ and $\mathcal{F}^{-1}$ denote the forward and inverse 3D Fourier transform. $k_i$ denotes the wavenumber in the $i=z,x,y$ dimension.

\subsection{Absorbing boundary condition}
We use a simple sponge (or Gaussian decaying) absorbing boundary condition (ABC) for the wavefield simulation \cite[]{cerjan1985nonreflecting}. The sponge ABC takes the following form:
\begin{equation}
\label{eq:abc}
w(x)=e^{-\alpha(x-x_n)},
\end{equation}
where $w(x)$ denotes a 1D weighting or decaying vector applied onto the wavefield in the boundary region. $\alpha$ is the decaying parameter controlling the strength of the decay. $x_n$ denotes the location of the nearest boundary of the non-absorbing region.

\subsection{Imaging condition}
The imaging condition of traditional time-reversal imaging is similar to that of an exploding reflector, which is commonly used in the active-source imaging  \cite[]{2005Reverse}. 
Assuming there are $N$ receivers, the conventional time-reversal imaging condition $I_1(z,x,y)$ can be expressed by adding all backward propagated seismic wavefields at the same time: 
\begin{equation}\label{eq:ic1}
I_1(z,x,y)=\sum_{t}\sum_{n=0}^{N-1} p_{n}(z,x,y,t),
\end{equation}
where $p_n(z,x,y,t)$ represents the backward propagated seismic wavefield corresponding to $n$th recorded trace. $(z, x, y)$ denotes the spatial location and $t$ denotes the time. It is necessary to pick the arrival times for localizations of multiple passive sources. However, it is challenging when the energy of the noise is strong. Note that, the whole dataset received by all the receivers is added at once, causing only one calculation of the backward propagation process. Nevertheless, the resolution is limited \wen{for a surface acquisition geometry}, especially when the wavefield is complicated for \old{a complex problem}\new{a complicated velocity model}.

Inspired by the active-source imaging, the new method utilizes the cross-correlation imaging condition that is commonly used in prestack migration. It assumes that the backward propagated seismic wavefields from different receivers do not interact with each other, i.e., being independent \cite[]{Junzhe2015}.  When the recorded wavefield coincides with the source wavefield in both the time and space dimensions, the microseismic hypocenters are detected \cite[]{Nori2015}.
The \new{time-domain} cross-correlation imaging condition $I_2(z,x,y)$ can be expressed by multiplying instead of adding the backward propagated seismic wavefields of receivers: 
\begin{equation}\label{eq:ic2}
I_2(z,x,y)=\sum_{t}\prod_{n=0}^{N-1} p_{n}(z,x,y,t).
\end{equation}
If the velocity model is accurate, $I_2(z,x,y)$ will be zero except for the locations of microseismic events. The influence of noise can be \old{thresholded}\new{minimized} because the noise is usually random and the corresponding energy in the images is weaker than that of the effective signals. The resolution of the imaging condition expressed in equation \ref{eq:ic2} depends on the dominant frequency of the coherent signals. Although the resolution is relatively high when it is compared with the traditional time-reversal imaging condition, its computational cost is high, because the backward propagated seismic wavefield of each receiver is individually calculated \cite[]{Junzhe2015}.

Therefore, we can combine the two aforementioned image conditions, then obtain a compromise by forming a hybrid imaging condition as follows: 
\begin{equation}\label{eq:ic3}
I_3(z,x,y)=\sum_{t}\prod_{n_2=0}^{N_g-1}\sum_{n_1=0}^{(N/N_g)-1} p_{n_2*(N/N_g)+n_1}(z,x,y,t),
\end{equation}
where $N_g$ denotes the group number, i.e., dividing all the receivers into $N_g$ groups. \new{The idea of using receiver groups is proposed in \cite{sun2016full}.} The number of traces within each group is $N/N_g$. Equation \ref{eq:ic3} is referred to as the grouped cross-correlation imaging condition.  Then, the advantages of summation-based and cross-correlation-based imaging conditions are integrated into the hybrid imaging method. As a result, it can produce localization results of microseismic events or earthquake hypocenters with a high resolution and high fidelity in moderate calculation time. Besides, the hybrid imaging condition saves more human effort because it does not require the picking of arrival times.

\section{Code description}
\subsection{C program}
The C program is designed to be run in the Madagascar open-source platform. The C program implements the pseudo-spectral method introduced above for modeling acoustic wavefield that is required by the grouped cross-correlation-based passive seismic source-location imaging. For the purposes of education and methodological developments, the C program is designed as a compact and standard-alone program (except for several simple Madagascar library functions for I/O) for both forward acoustic wave simulation and time-reversal imaging using the surface-recorded passive seismic data. The C program can be divided into five parts. All parts are clearly documented in the program.  Note that all these components are necessary for any wave-equation based imaging and inversion applications. 
\begin{itemize}
\item Part I: 	Ricker wavelet \\
This part is responsible for generating the well-known Ricker wavelet.
\item Part II: 	 Absorbing boundary condition\\
This part implements the ABC method introduced above.
\item Part III: Fourier transform\\
This part implements the 3D Fourier transform as required by the pseudo-spectral method.
\item Part IV: Pseudo-spectral wave extrapolation \\
This part details the implementation of the pseudo-spectral method for acoustic wave propagation, as well as designing a new struct type for storing the parameters required by the pseudo-spectral method.
\item Part V: Main program \\
This part handles the I/O and calls the subroutines of the pseudo-spectral method for either forward wave propagation in \old{synthetic tests}\new{simulation} or backward  wave propagation in time-reversal imaging.
\end{itemize}

\subsection{Python script (SConstruct)}
The python script provides a template for compiling the C program and making it runnable for realistic passive seismic source-location imaging applications. The template python script included in the code package is composed of seven parts. All parts are clearly documented in the python script.
\begin{itemize}
\item Part I: 	Specifying parameters\\
There are two types of parameters, i.e., parameters for field data applications and parameters for synthetic tests. 
\item Part II: 	Compiling the C program\\
We use the ``Program'' command in the Madagascar environment to compile the C program: exe=Program(`mod3d.c').
\item Part III: Creating/Inputing the velocity model\\
For synthetic tests, we can generate any velocity models we like, or segment a part from any open-source benchmark velocity models, like the SEG/EAGE salt/overthrust models, and the SEAM model. In the same time, we also specify the predefined source locations here. The velocity model and source locations can be plotted in a 3D format in this part. For field data applications, this part can be omitted, and the available velocity model can be input directly for time-reversal imaging. 
\item Part IV: 	Generating/Inputing the recorded passive seismic data \\
For synthetic tests, we use the compiled C program to generate the recorded passive seismic data on the surface based on a pseudo-spectral method. For field data applications, this part can be omitted, and the recorded real passive seismic data are directly input into the imaging module. 
\item Part V: 	Backward propagating of the grouped receiver wavefield \\
In this part, the recorded passive seismic data are divided into several groups for individual backward propagation. The backward propagations of grouped receiver wavefields are also known as the hybrid summation-based and cross-correlation-based time-reversal imaging. 
\item Part VI: 	Applying the cross-correlation imaging condition\\
The backward propagated grouped receiver wavefields are cross-correlated with each other to output the final source-location image.
\item Part VII: Plotting the source locations\\
The obtained source location image is plotted in a 3D format in this part.
\end{itemize}

\section{Examples}
We use one synthetic example, which is included in the code package as the python script, and one field data example to demonstrate the applicability of the presented program. 
\subsection{Synthetic example}
The synthetic example is illustrated in Figures \ref{fig:data}-\ref{fig:vel1,location-tr1,location1,vel2,location-tr2,location2,vel3,location-tr3,location3}. Figure \ref{fig:data} plots the recorded synthetic passive seismic data. We create a synthetic velocity model with vertically increasing velocity to simulate the recorded seismic data. \new{The velocity range is [1500-4860] m/s.} We use three seismic sources, which are located at $(1000,1000,1000)$m, $(1400,1200,1200)$m, $(1800,1400,1400)$m, respectively, in the velocity \old{models}\new{model}. \new{The peak frequency of the Ricker wavelet is 10 Hz. The ignition times of the three sources are 0.2 s, 0.35 s, and 0.5 s, respectively. We add some Gaussian white noise (which can be easily substituted by band-limited random noise in the Python script) to the simulated passive dataset. During wavefield backward propagation, the data are simultaneously propagated, without a first deblending step.} \old{To}\new{We} compare the proposed method with the state-of-the-art method, i.e., the time-reversal imaging method based on picking the focused location and time \cite[]{2005Reverse}. For simplicity, we refer to the method in \cite{2005Reverse} as the traditional method. Since we use \old{four times of time-reversal modeling}\new{four receiver groups}, the computational cost of the proposed method is about four times that of the traditional method. The three source locations are highlighted by the red dots in Figures \ref{fig:vel1}, \ref{fig:vel2}, and \ref{fig:vel3}, respectively. \wen{The middle column shows the three imaged source locations using the traditional time-reversal imaging method.} The right column shows the three imaged source locations using the presented program. Although the imaging results using the traditional method are generally correct, they have an obviously lower resolution, tend to cause imaging artifacts, and are more \old{more }sensitive to random noise. The consistency of each location between the left and right \dlo{figures}\wen{columns} confirm the validity of the presented passive seismic imaging program. Figure \ref{fig:data_mask0,data_mask1,data_mask2,data_mask3} shows the four grouped passive seismic records, which are backward propagated to generate the grouped receiver wavefields. The backward propagated grouped receiver wavefields are then cross-correlated with each other to obtain the source-location images shown on the right column of Figure \ref{fig:vel1,location-tr1,location1,vel2,location-tr2,location2,vel3,location-tr3,location3}.

\subsection{Field data example}
We also apply the presented imaging program to a microseismic dataset recorded during the hydraulic fracturing of the Marcellus gas shale in Washington Country, Pennsylvania, USA. The Marcellus gas shale (with a roughly 30m thickness) is approximately 1.9 km below the surface \cite[]{tan2016further,huang2019passive}. The microseismic data have been binned onto regular grids and are plotted in Figure \ref{fig:rsf_real}. The surface monitoring system has 10 `arms', as revealed from the top slice in Figure \ref{fig:rsf_real}. There are a total of 1082 single-component geophones. We test the imaging performance for only one event. According to the published material \cite[]{tan2016further,huang2019passive}, we construct a 3D velocity model as shown in Figure \ref{fig:sov}. \new{We construct the velocity model based on some published models in the literature (e.g., the one in \cite{anikiev2014joint}). We extract the minimum and maximum velocities from the published models of the same dataset and construct a model that has a linearly increasing velocity with a constant velocity gradient. However, inputing a more accurate velocity model is straightforward, and hopefully will generate a more accurate source-location image.} \new{The 3D source-location images using the traditional and the proposed methods are plotted in Figures \ref{fig:f-location-tr} and \ref{fig:f-location1}, respectively.} It is clear that the \new{traditional method obtains a lower resolution and causes significantly more artifacts than the proposed method. } \new{The image from the proposed method} focuses well in around $(1824,2712,2256)$m, which is consistent with many published results \cite[]{anikiev2014joint,tan2016further,huang2019passive}. \new{One special thing of this example is that we do not apply any preprocessing to the field dataset. We just input the raw data (after binning onto the regular grids) into the imaging framework and output the result.}

\section{Discussion}
\subsection{Effect of group number}
The presented program can be used to study various factors that could affect the imaging performance via synthetic tests. For example, we first conduct several numerical tests to investigate the effect of the group number on the source-location images. We vary the number of groups $N_g$ and compare the corresponding images. Note that parameter $N_g$ can be easily set in the python script within the code package. The tests are based on the aforementioned synthetic example, where $N_g=4$ is used to generate the results shown in Figure \ref{fig:vel1,location-tr1,location1,vel2,location-tr2,location2,vel3,location-tr3,location3}. For simplicity, we only compare the imaging result of the first source location. We choose $N_g=2,6,8,10$ and show the first group in Figure \ref{fig:data_mask0_ng2,data_mask0_ng6,data_mask0_ng8,data_mask0_ng10}. Figure \ref{fig:location1-ng2,location1-ng6,location1-ng8,location1-ng10} shows the images corresponding to different $N_g$. The comparison shows that the number of group number has a small effect on the imaging result. Observing carefully, one can find that the imaging result corresponding to $N_g=10$ has a slightly higher resolution than that corresponding to $N_g=2$. However, when using a larger group number, the disk storage required for the imaging will be much higher due to a larger number of wavefields needed to be stored. \new{In practise, we normally choose $N_g=4$ or $N_g=6$. A larger number of $N_g$ will significantly increase the computational and storage cost but will not get obviously higher resolution. In practical situations, where the receiver distribution is highly irregular, how the receivers are grouped, however, plays an important role. For relatively dense receivers, a simple even grouping strategy is sufficient to obtain a good result, e.g., as shown in the field data example.  For relatively sparse receiver distribution, each group should contain a comparable number of nearby receivers, so that the wavefields in each group can be enhanced (and more anti-noising) by stacking the backward wavefields from each receiver. For very noisy data (e.g., in Figure \ref{fig:data-8}), a large group number (e.g., $N_g=10$) could result in instability issue due to the insufficient number of receivers in each group to mitigate the influence of strong noise.}

\subsection{Effect of noise}
Next, we study the effect of noise to the imaging performance. We increase noise variance $\sigma^2$ from 0.01 to 50 to deteriorate the data quality and then compare the imaging performance. We show four recorded data cubes corresponding to $\sigma^2=0.01,0.5,10,50$ in Figure \ref{fig:data-2,data-4,data-6,data-8}. The S/N of the data shown Figures \ref{fig:data-2}-\ref{fig:data-8} are -4.97 dB, -21.96 dB, -34.97 dB, and -41.96 dB, respectively. We calculate the S/N based on the following equation \cite[]{yangkang2015ortho}: 
\begin{equation}
\label{eq:diff}
\text{S/N}=10\log_{10}\frac{\Arrowvert \mathbf{s}_{clean} \Arrowvert_2^2}{\Arrowvert \mathbf{s}_{clean} -\mathbf{s}_{noisy}\Arrowvert_2^2},
\end{equation}
where $\mathbf{s}_{clean}$ and $\mathbf{s}_{noisy}$ are vectorized clean and noise data. Figure \ref{fig:location1-noise2,location1-noise4,location1-noise6,location1-noise8} shows the imaged first source location corresponding to the noisy data plotted in Figure \ref{fig:data-2,data-4,data-6,data-8}.  It is clear from Figures \ref{fig:data-2,data-4,data-6,data-8} and \ref{fig:location1-noise2,location1-noise4,location1-noise6,location1-noise8} that when the microseismic signal is observable, the source location is imaged accurately. Even when the signal is barely observable, the source location can still be imaged accurately, as shown in Figures \ref{fig:data-6} and \ref{fig:location1-noise6}. Only when the noise is extremely strong, e.g., $\sigma^2=50$, the presented program does not work properly, i.e., creating some spurious locations in the image (Figure \ref{fig:location1-noise8}). Note that the anti-noise ability is related with the distribution of the receivers on the surface. Here, we use a very dense receiver geometry ($81\times 81$ evenly distributed receivers), so the anti-noise performance is ultrahigh. A more realistic numerical tests should follow the geometry of a pratical application.

\subsection{Effect of receiver density}
Then, we investigate the effect of receiver density, i.e., number of traces in a given working area, on the imaging performance. We vary the number of recorded traces and compare their corresponding imaging results. Figure \ref{fig:data-d6,data-d8,data-d9,data-d10} shows four datasets with different number of recorded traces, i.e.,  121, 81, 16, and 8 recorded traces for (a)-(d), respectively. Figure \ref{fig:location1-density6,location1-density8,location1-density9,location1-density10} shows the imaging results corresponding to the data in Figure \ref{fig:data-d6,data-d8,data-d9,data-d10}. It is clear that the presented program is robust when there are only 16 recorded traces. When the number of recorded traces becomes fewer, the imaging result \old{becomes unable}\new{fails} to reveal the true source location. Note that the effect of receiver density is also related with the working area. The velocity model, grid size, receiver distribution could all affect the minimum number of receivers that warrants an accurate imaging of the source location. In any practical situation, the presented program can be helpful on designing the optimal receiver geometry via synthetic tests.

\subsection{Other applications}
Although the presented code is based on acoustic wave propagation, it could have some other applications in addition to microseismic imaging if organized properly. For example, the same grouped cross-correlation imaging method can also be applied to diffraction imaging \cite[]{yin2017diffraction}. When the diffraction energy is separated from pre-stack gathers, it can also be viewed as the passive seismic energy that is emitted from the subsurface diffractors. Thus, the same methodology and imaging framework also work for the purpose of migrating the diffraction energy to depict the underground discontinuities. Besides, the presented program could also be used to image the subsurface fracture network \cite[]{huang2019passive}. The principle is that the P wave and converted S wave should coincide with each other when they are both backward propagated onto the factures. Thus, by propagating the separated P and converted S waves using the presented acoustic propagator, and applying the cross-correlation imaging condition, it is possible to image the fractures or other discontinuous interfaces.  \new{More complicated P-to-S scattering pattern is possible to be considered because the simulation code is a two-way propagator. The effect of scattering pattern, however, highly depends on the resolution of the given velocity model.} \new{It is also possible to extend the present code to invert velocity models from passive seismic data.  A similar work about the source imaging and velocity inversion using a source-focusing objective function has been introduced in \cite{song2019microseismic}.} Further applications of the presented program are worth investigating, but are beyond the scope of this manuscript.

%\subsection{Motivation of the program}
%\wen{There are very few open-source packages that are easy and standalone to use for 3D passive seismic imaging in the
%seismology community. There are no resources (i.e., in the form of a reproducible article) in the Madagascar
%platform. We try our best to simplify the package of this work to include only one Python script and one C program. This ``simple" and compact program is useful for educational purposes and for future algorithm improvement. One can substitute those subroutines in the C program with his own versions. Except for these necessary components for forward wave propagation, there are several other important components for a 3D passive imaging goal, i.e., the geometry, imaging condition, I/O, visualization, concatenation, which are the focus of this manuscript.}

\section{Conclusions}
We have presented a compact program for locating passive (e.g., including but not limited \new{to} microseismic experiments arising from fluid injections) seismic sources in 3D subsurface media. The C program can be compiled and run using a python script, where the input velocity model and recorded passive seismic data can be specified. The imaging program uses a grouped cross-correlation method to locate the seismic sources, which has a robust, high-resolution, and high-fidelity performance. The imaging program can be used not only to migrate available passive seismic data, but also to forward model the data for synthetic tests. Both synthetic and real data examples demonstrate the successful applications of the presented program to realistic problems. Due to the compact and relatively simple format of the presented imaging program, it has the potential to be beneficial to a broad range of passive seismic studies.

\section{Data and Resources}
All datasets and source codes associated with this research are hosted via the Madagascar platform (www.ahay.org) in the form of reproducible research \cite[]{mada2013}.

%All datasets and source codes associated with this research are hosted via the Madagascar platform www.ahay.org in the format of reproducible research \cite[]{mada2013}.
\section{Acknowledgements}
The research is supported by the starting funds from Zhejiang University. We thank Microseismic, Inc. and Newfield Exploration Company for releasing the data set. We thank J. Sun from Texas Consortium for Computational Seismology (TCCS) for constructive discussions. %The presented passive seismic imaging program is based on the initial work by J. Sun \cite[]{Junzhe2015}. % and Y. Shi and S. Fomel from Texas Consortium for Computational Seismology (TCCS) for sharing the microseismic dataset of one event.

\inputdir{mod3d_geo}
\plot{data}{width=0.6\textwidth}{Recorded passive seismic data in the synthetic example.}
\multiplot{9}{vel1,location-tr1,location1,vel2,location-tr2,location2,vel3,location-tr3,location3}{width=0.3\textwidth}{\wen{Velocity model and the highlighted first source location (a), its time-reversal imaging result using the traditional (b) and proposed (c) methods. Velocity model and the highlighted second source location (d), its time-reversal imaging result using the traditional (e) and proposed (f) methods. Velocity model and the highlighted third source location (g), its time-reversal imaging result using the traditional (h) and proposed (i) methods.}}
\multiplot{4}{data_mask0,data_mask1,data_mask2,data_mask3}{width=0.45\textwidth}{Four grouped recorded passive seismic data. }

\inputdir{field3d_geo}
%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
\multiplot{4}{rsf_real,sov,f-location-tr,f-location1}{width=0.45\textwidth}{Field data example. (a) Recorded microseismic data. (b) Constructed velocity model. \dlo{(c) 3D source location image.}\wen{(c) 3D source location image using the traditional method. (d) 3D source location image using the proposed method.}}

\inputdir{mod3d_geo_ng}
\multiplot{4}{data_mask0_ng2,data_mask0_ng6,data_mask0_ng8,data_mask0_ng10}{width=0.45\textwidth}{The first group of recorded data when $N_g=2,6,8,10$, respectively. }

\multiplot{4}{location1-ng2,location1-ng6,location1-ng8,location1-ng10}{width=0.45\textwidth}{The images of the first source location when $N_g=2,6,8,10$, respectively. }

\inputdir{mod3d_geo_noise}
\multiplot{4}{data-2,data-4,data-6,data-8}{width=0.45\textwidth}{Recorded data when noise variation $\sigma^2=0.01,0.5,10,50$, respectively. The corresponding S/Ns of (a)-(d) are -4.97 dB, -21.96 dB, -34.97 dB, and -41.96 dB, respectively. }

\multiplot{4}{location1-noise2,location1-noise4,location1-noise6,location1-noise8}{width=0.45\textwidth}{The images of the first source location when noise variation $\sigma^2=0.01,0.5,10,50$, respectively. }

%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr1.rsf 
%   0:        -1.957
%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr2.rsf 
%   0:        -4.967
%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr3.rsf 
%   0:        -14.98
%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr4.rsf 
%   0:        -21.96
%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr5.rsf 
%   0:        -31.96
%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr6.rsf 
%   0:        -34.97
%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr7.rsf 
%   0:        -37.98
%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr8.rsf 
%   0:        -41.96
%

\inputdir{mod3d_geo_density}
\multiplot{4}{data-d6,data-d8,data-d9,data-d10}{width=0.45\textwidth}{The observed data with 121, 81, 16, and 8 recorded traces, respectively.  }

\multiplot{4}{location1-density6,location1-density8,location1-density9,location1-density10}{width=0.45\textwidth}{The images of the first source location when there are 121, 81, 16, and 8 recorded traces, respectively. }

\bibliographystyle{seg}
\bibliography{micro}

\clearpage
Yangkang Chen\footnotemark[1], Omar M. Saad\footnotemark[1]\footnotemark[2], Min Bai\footnotemark[3],  Xingye Liu\footnotemark[4], Sergey Fomel\footnotemark[5]  \\
\footnotemark[1]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
chenyk2016@gmail.com\\
%yangkang.chen@zju.edu.cn \\
\footnotemark[2]
ENSN Lab \\
Seismology Department \\
National Research Institute of Astronomy and Geophysics (NRIAG)\\
Helwan 11731, Egypt\\
engomar91@ gmail.com\\
\footnotemark[3] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
Yangtze University\\
Daxue Road No.111\\
Caidian District\\
Wuhan, China, 430100 \\
\footnotemark[4]
College of Geology and Environment\\
Xi’an University of Science and Technology\\
Xi’an, Shaanxi Province, China, 710054 \\
lwxwyh506673@126.com\\
\footnotemark[5]Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
sergey.fomel@beg.utexas.edu\\

%\AtEndDocument{}

%\newpage
%\listoffigures

%\begin{figure}[htb!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
%	\caption{Caption.}
%	\label{fig:fig}
%\end{figure}

%\begin{figure}[htb!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
%    \label{fig:fig1}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
%    \label{fig:fig2}}\\
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure}

%\begin{figure*}[ht!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
%    \label{fig:fig1}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
%    \label{fig:fig2}}\\
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure*}

%\begin{table}[h]
%\caption{Table caption}
%\begin{center}
%     \begin{tabular}{|c|c|c|c|c|c|} 
%	  \hline Column1 (unit)  & Column2 (unit) & Column3 (unit) \\ 
%	  \hline 1 & 2  & 3 \\
%       \hline
%    \end{tabular} 
%\end{center}
%\label{tbl:table1}
%\end{table}

### 2021-05-12 passive/paper.tex
add passive

@@
 \address{
-%\footnotemark[1]
-%School of Earth Sciences\\
-%Zhejiang University\\
-%Hangzhou, Zhejiang Province, China, 310027\\
-%chenyk2016@gmail.com\\
-%%yangkang.chen@zju.edu.cn \\
-%\footnotemark[2]
-%ENSN Lab \\
-%Seismology Department \\
-%National Research Institute of Astronomy and Geophysics (NRIAG)\\
-%Helwan 11731, Egypt\\
-%engomar91@ gmail.com\\
-%\footnotemark[3] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
-%Yangtze University\\
-%Daxue Road No.111\\
-%Caidian District\\
-%Wuhan, China, 430100 \\
-%\footnotemark[4]
-%College of Geology and Environment\\
-%Xi’an University of Science and Technology\\
-%Xi’an, Shaanxi Province, China, 710054 \\
-%lwxwyh506673@126.com\\
-%\footnotemark[5]Bureau of Economic Geology \\
-%John A. and Katherine G. Jackson School of Geosciences \\
-%The University of Texas at Austin \\
-%University Station, Box X \\
-%Austin, TX 78713-8924 \\
-%sergey.fomel@beg.utexas.edu\\
+\footnotemark[1]
+School of Earth Sciences\\
+Zhejiang University\\
+Hangzhou, Zhejiang Province, China, 310027\\
+chenyk2016@gmail.com\\
+%yangkang.chen@zju.edu.cn \\
+\footnotemark[2]
+ENSN Lab \\
+Seismology Department \\
+National Research Institute of Astronomy and Geophysics (NRIAG)\\
+Helwan 11731, Egypt\\
+engomar91@ gmail.com\\
+\footnotemark[3] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
+Yangtze University\\
+Daxue Road No.111\\
+Caidian District\\
+Wuhan, China, 430100 \\
+\footnotemark[4]
+College of Geology and Environment\\
+Xi’an University of Science and Technology\\
+Xi’an, Shaanxi Province, China, 710054 \\
+lwxwyh506673@126.com\\
+\footnotemark[5]Bureau of Economic Geology \\
+John A. and Katherine G. Jackson School of Geosciences \\
+The University of Texas at Austin \\
+University Station, Box X \\
+Austin, TX 78713-8924 \\
+sergey.fomel@beg.utexas.edu\\
 Corresponding Author: Yangkang Chen (chenyk2016@gmail.com) 
@@
 %\lefthead{Liu et al.}
-\righthead{3D passive imaging\\
-Declaration of Competing Interests: The authors acknowledge there are no conflicts of interest recorded.}
+%\righthead{3D passive imaging\\
+%Declaration of Competing Interests: The authors acknowledge there are no conflicts of interest recorded.}
 
@@
 
-\clearpage
-Yangkang Chen\footnotemark[1], Omar M. Saad\footnotemark[1]\footnotemark[2], Min Bai\footnotemark[3],  Xingye Liu\footnotemark[4], Sergey Fomel\footnotemark[5]  \\
-\footnotemark[1]
-School of Earth Sciences\\
-Zhejiang University\\
-Hangzhou, Zhejiang Province, China, 310027\\
-chenyk2016@gmail.com\\
-%yangkang.chen@zju.edu.cn \\
-\footnotemark[2]
-ENSN Lab \\
-Seismology Department \\
-National Research Institute of Astronomy and Geophysics (NRIAG)\\
-Helwan 11731, Egypt\\
-engomar91@ gmail.com\\
-\footnotemark[3] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
-Yangtze University\\
-Daxue Road No.111\\
-Caidian District\\
-Wuhan, China, 430100 \\
-\footnotemark[4]
-College of Geology and Environment\\
-Xi’an University of Science and Technology\\
-Xi’an, Shaanxi Province, China, 710054 \\
-lwxwyh506673@126.com\\
-\footnotemark[5]Bureau of Economic Geology \\
-John A. and Katherine G. Jackson School of Geosciences \\
-The University of Texas at Austin \\
-University Station, Box X \\
-Austin, TX 78713-8924 \\
-sergey.fomel@beg.utexas.edu\\
+%\clearpage
+%Yangkang Chen\footnotemark[1], Omar M. Saad\footnotemark[1]\footnotemark[2], Min Bai\footnotemark[3],  Xingye Liu\footnotemark[4], Sergey Fomel\footnotemark[5]  \\
+%\footnotemark[1]
+%School of Earth Sciences\\
+%Zhejiang University\\
+%Hangzhou, Zhejiang Province, China, 310027\\
+%chenyk2016@gmail.com\\
+%%yangkang.chen@zju.edu.cn \\
+%\footnotemark[2]
+%ENSN Lab \\
+%Seismology Department \\
+%National Research Institute of Astronomy and Geophysics (NRIAG)\\
+%Helwan 11731, Egypt\\
+%engomar91@ gmail.com\\
+%\footnotemark[3] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
+%Yangtze University\\
+%Daxue Road No.111\\
+%Caidian District\\
+%Wuhan, China, 430100 \\
+%\footnotemark[4]
+%College of Geology and Environment\\
+%Xi’an University of Science and Technology\\
+%Xi’an, Shaanxi Province, China, 710054 \\
+%lwxwyh506673@126.com\\
+%\footnotemark[5]Bureau of Economic Geology \\
+%John A. and Katherine G. Jackson School of Geosciences \\
+%The University of Texas at Austin \\
+%University Station, Box X \\
+%Austin, TX 78713-8924 \\
+%sergey.fomel@beg.utexas.edu\\
+%
 

### 2021-05-22 mrc5d/paper.tex
add mrc5d

\DeclareRobustCommand{\old}[1]{}
\DeclareRobustCommand{\new}[1]{#1}
\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}
\makeatletter
\newcommand\fs@norules{\def\@fs@cfont{\bfseries}\let\@fs@capt\floatc@ruled
	\def\@fs@pre{}%
	\def\@fs@post{}%
	\def\@fs@mid{\kern3pt}%
	\let\@fs@iftopcapt\iftrue}
\makeatother
\floatstyle{norules}
\restylefloat{algorithm}
\title{Mixed rank-constrained model for simultaneous denoising and reconstruction of 5-D seismic data}

\author{Yapo Abol{\'e} Serge Innocent Obou{\'e} and Yangkang Chen}

\address{Y.A.S.I. Obou{\'e} and Y. Chen are with School of Earth Sciences, Key Laboratory of Geoscience Big Data and Deep Resource of Zhejiang Province, Zhejiang University, Hangzhou, Zhejiang Province, China, 310027, obouesonofgod1@gmail.com\&chenyk2016@gmail.com.}

\thanks{This research is supported by the Starting Funds from Zhejiang University. (Corresponding author: Y. Chen.)}

\lefthead{TGRS - Obou{\'e} and Chen}
\righthead{Mixed rank-constrained model}

\maketitle

\begin{abstract}
Recently, researches on multidimensional seismic data interpolation through rank-constrained matrix or tensor completion have led to many effective methods, with satisfactory results. Despite the success of the rank-constrained matrix completion methods, e.g., damped rank-reduction (DRR), and the rank-constrained tensor completion methods, e.g., higher-order orthogonal iteration (HOOI), strong noise and highly decimated traces could still make the reconstruction results not acceptable. In this paper, we find that implementing only one rank constraint to solve the multidimensional seismic data recovery problem is not sufficient. Therefore, we consider a hybrid method to reconstruct the noisy and incomplete traces based on a new mixed rank-constrained (MRC) algorithm. The proposed MRC algorithm aims to take advantages of the merits of both the rank-constrained matrix and tensor completion models to restore the missing data. We first apply the unfolding and folding operator to the four-dimensional spatial hypercube data. Then, for each iteration, we connect the DRR and the HOOI approaches in the same framework to solve the proposed MRC model. The proposed MRC model aims to provide an enhanced level of rank constraint to improve the signal-to-noise ratio (SNR) of the recovered data. Synthetic and field 5-D seismic data are used to compare the performance of the new method with the HOOI and DRR methods. The comparison via visual inspection and numerical analysis reveal the better performance of the proposed MRC algorithm.
\end{abstract}

\section{Introduction}
Multidimensional recovery of seismic data is a significant processing stage in the seismological exploration in order to provide complete data for the subsequent procedures, e.g., multiple removal, time-lapse investigations, high-resolution processing \citep{chiu2014multidimensional}.

Recovery of seismic data is performed by several approaches like linear prediction-error filters (PEFs) \citep{porsani1999seismic,curry2003interpolation,gulunay2003seismic,liu2015adaptive,fomel2016streaming,li2017multidimensional}. In the group of PEFs approaches, first, the low-frequency non-aliased elements of the decimated seismic data volume are selected to form the anti-aliasing PEF. Then, the high-frequency aliased data elements are replaced by using the filters. Seismic data interpolation can also be achieved via approaches based on the wave-equation theory \citep{fomel2003seismic}. These methods require a fairly reliable subsurface velocity model. Over the years, several researchers applied sparsity-promoting transforms methods to restore the missing data from noisy and incomplete seismic observations. These methods are based on sparse transforms like Fourier, Random, curvelet, seislet, shearlet, sparse wavelet  \citep{gan2015seismic,gan2015dealiased,liu2015seismic,zhong2015irregularly,gan2016compressive,kong2016seismic,li2016unconventional,liu2016effective,liu2016one,liu2016seismic,sun2016constraints,zu2016periodically,xue2017amplitude}, and the learning-based approaches \citep{yangkang2020sgk,wanghang2020tgrs3}. Based on $L_1$-norm minimization techniques, approaches that promote sparsity have successfully overcome seismic interpolation problems with the aid of shearlet transform and curvelet transform \citep{shahidi2013application}. To achieve the goal of missing traces interpolation, the coefficients in the transform domain are constrained by the broadly used $L_0$ or $L_1$ norm. However, this standard strategy cannot achieve good results for seismic data interpolation problem, because of the difficulties of NP-hard when using the $L_0$-norm, and the non-sparsest solution of $L_1$-norm. Accordingly, \cite{zhong2015irregularly} proposed a new $L_1/_2$ norm strategy to reconstruct incomplete seismic traces. The high-order Radon transform approach \citep{xue2017amplitude} has been introduced to attenuate random noise accurately. Low-rank methods for seismic data interpolation have emerged and become more relevant for which two sub-groups can be distinguished. The first that includes methods like the conventional rank-reduction (RR), and the damped rank-reduction (DRR), incorporates all the seismic data components in a matrix called Hankel or Toeplitz matrix, and then uses the iterative low-rank algorithm to interpolate the missing traces \citep{oropeza2011simultaneous,chen2016simultaneous,huang2017double,siahsar2017simultaneous,zhang2017hybrid,huang2018damped,chen2019five,oboue2020geo1}.
Besides, some researchers \citep{yang2012seismic,kumar2015efficient} have introduced matrix completion (MC) approaches to further reduce the rank of the incomplete data matrices. To solve the MC optimization problem efficiently, \cite{kumar2012fast} introduced the matrix factorization via max-norm\dlo{known as MFMN}. The DRR algorithm \citep{chen2016simultaneous} has been proposed to increase the quality of the useful signal even though the seismic data are influenced by strong noise and missing traces. More recently, \cite{yangkang2020odrr} introduced an optimally DRR strategy to reconstruct 5-D seismic data. In the second sub-group of low-rank methods, tensor decomposition techniques like higher-order singular value decomposition (HO-SVD) proposed by \cite{de2000multilinear}, and parallel matrix factorization (PMF) introduced by \cite{gao2015parallel} are usually applied to the multidimensional array to reduce the rank of the noisy observation \citep{ely20135d,kreimer2013tensor,ely20155d,gao2015parallel,carozzi2019robust}. \cite{kreimer2012tensor} applied HO-SVD for 5-D seismic tensor completion. In this approach, the rank-reduced tensor is achieved iteratively via the high-order orthogonal iteration (HOOI) algorithm \citep{sheehan2007higher}, and then, the iterative weighted POCS-like algorithm based on low-rank methods is utilized to fill in the tensor. \cite{carozzi2019robust} proposed a novel PMF tensor completion approach to solve erratic noise problems. Both sub-groups of low-rank methods are focused on the seismic low-rank structure theory. Low-rank methods have promoted the improvement of approaches, which simultaneously remove noise and reconstruct the missing traces from the noisy observation \citep{elad2005simultaneous,kreimer2013tensor,benfeng2015pocs,chen2016simultaneous,zhang2017hybrid}. The groups of the methods mentioned above have their merits and shortcomings, which motivated some researchers to develop hybrid approaches by coupling sparsity-promoting transforms and low-rank approaches \citep{sternfels2015multidimensional,zhang2017hybrid}. Hybrid methods take benefit from the proper performance of each method to remove random noise and minimize the running time.

Although approaches based on matrix rank constraint, such as the DRR, and methods based on tensor rank constraint like HOOI have achieved some results, residual noise restricts their performance\dlo{s} and consequently their effectiveness when the observed 5-D seismic data is severely decimated and contains \dlo{notable}\wen{significant} random noise. In other words, when the observed data is extremely noisy and highly decimated, both rank-constrained models \dlo{become weak to provide}\wen{will not provide} acceptable recovery quality. Hence, we assume that implementing only one rank constraint to reach the goal of multidimensional seismic data interpolation is not sufficient. Therefore, in this paper, both sub-groups of low-rank methods are of interest to us. We consider double rank-reduction operators for multidimensional seismic data interpolation via a new mixed rank-constrained (MRC) method, which intends to mix the interests of both matrix and tensor rank constraints. We elaborate on the proposed MRC algorithm first, by applying the unfolding and folding operator to the four-dimensional spatial hypercube. Then, inside the loop for each iteration, we combine the DRR and the HOOI operators in the same framework to obtain an excellent recovery of the missing data. \dlo{At last}\wen{Finally}, we apply the iterative weighted POCS-like algorithm based on the low-rank methods to complete the tensor. The proposed MRC model aims at providing an enhanced level of rank constraint and increasing the SNR of the recovered data.

In the theory section, first, we present the damped rank-constrained matrix completion model and a brief review of the DRR approach for solving it. Then\dlo{,} \wen{the} rank-constrained tensor completion model and the approach based on HOOI to solve it are briefly introduced. Next, we construct the mixed rank-constrained model, and we propose the MRC algorithm to solve it. Tests are conducted on two synthetics and a field 5-D seismic data\wen{set} to compare the performance of the proposed method to both the HOOI and DRR methods. The comparison is done qualitatively via visual inspection and quantitatively in terms of SNR. The results demonstrate the better performance of the proposed MRC approach.

\section{Theory}

We use boldface capital letters, for instance, $\mathbf{D}$, and calligraphy letters such as $\mathcal{D}$, to symbolize matrices and tensors, respectively. Boldface lowercase letters ($\mathbf{a}$) and lowercase letters (${a}$)\dlo{,} will indicate vectors and scalars, respectively.

\subsection{Model 1: Rank-constrained matrix completion}

Consider a clean data matrix denoted by $\mathbf{C}$. The \dlo{observed}\wen{missing} data can be recovered using the matrix completion theory based on a rank-minimizing strategy:
\begin{equation}
\min_{\mathbf{C}}rank_d(M\mathbf{C}),\quad s.t.\quad  {Q}_\Phi(\mathbf{C}-\mathbf{D})=0, 
\end{equation}
where the number of non-zero singular values of $M\mathbf{C}$ obtained by applying the damped rank-constrained function ($rank_d(\cdot)$) corresponds to $rank_d(M\mathbf{C})$ for $(j_1,j_2,j_3,j_4)\in\Phi$. $M$ indicates the Hankelization operator (see eq.(10)). $\mathbf{D}$ and $\Phi$ correspond to the observed data and the subset of observed indices, respectively. \wen{$ Q_\Phi$ indicates the linear operator}.

The DRR algorithm proposed by \cite{chen2016simultaneous} is succinctly outlined as follows:

\begin{enumerate}
	\item Apply the 1-D forward FFT to transform the 5-D seismic data $\mathbf{D}_{time}(t, hx, hy, x, y)$ defined in time domain into $\mathbf{D}_{freq}(f, hx, hy, x, y)$ in the frequency-space domain. The components $ hx, hy, x, y $ indicate $ hx $ and $ hy $ offsets and $ x $ and $ y $ midpoints.
	\item Apply the Hankelization operator to embed the 4-D spatial hypercube in a level-4 block Hankel matrix \wen{at a given frequency $f_0$}.
	\item Apply the damped rank constraint to the level-4 block Hankel matrix to minimize the rank of the observed data. 
	\item Apply the averaging operator to the approximation signal to recover the filtered data.
	\item Apply the weighted POCS-like algorithm to interpolate the noisy decimated traces.
	\item Apply the 1-D inverse FFT to convert the result into the time domain.
\end{enumerate}

A full description of the DRR method is given by Algorithm \ref{alg:alg1}.

\begin{algorithm}[H] \caption{Damped rank-reduction algorithm (DRR) ({${H}$}, {${f}_{d}$}, $\mathbf{D}_{obsd}$, $a_{u}$, $tol$, $u_{max}$, ${F}$)}
	\label{alg:alg1}
	\begin{algorithmic}[1] 
\Require An input 5-D seismic data.\\

$\mathbf{D}_{obsd}(f, hx, hy, x, y)\leftarrow \mathbf{D}_{obsd}(t, hx, hy, x, y)$ via 1-D forward FFT\\		    
$\mathbf{D}_0\leftarrow\mathbf{D}_{obsd}$\;

\For{$f\leftarrow 1,2,\dots,{F}$}{ 
	\For{$u\leftarrow 1,2,\dots,u_{max}$}\\
	    {\wen{$\tilde{\mathbf{D}}\leftarrow{M}(\mathring{\mathbf{D}})$\\
${{\mathbf{X}}}\leftarrow rank_{d}(\tilde{\mathbf{D}})$\\
${\mathbf{D}^f_{u-1}}\leftarrow {W}{\mathbf{X}}$}\\
$\mathbf{D}^f_u \leftarrow a_u\mathbf{D}^f_{obsd} + (1 - a_u){Hf}_{d}\mathbf{D}^f_{u-1} + (1 - {H}){f}_{d}\mathbf{D}^f_{u-1}$\;
		\If{$\left\|\mathbf{D}^f_u - \mathbf{D}^f_{u-1}\right\|_F^2\leq tol$}\\
		{\textbf{return} $\mathbf{D}^f_u$\;
		}
	   \EndIf\\
		\textbf{return} $\mathbf{D}^f_{u_{max}}$\;
	}\EndFor\\
	\textbf{return} $\mathbf{D}_{recovered}$\;
}
\EndFor\\
$\mathbf{D}_{recovered}(t,hx, hy, x, y)\leftarrow \mathbf{D}_{recovered}(f,hx, hy, x, y)$ via 1-D inverse FFT\;
	\end{algorithmic}
\end{algorithm}

\wen{In Algorithm \ref{alg:alg1}}, ${H}$, ${f}_{d}$ and $a_{u}$ correspond to the sampling operator, the damped rank-reduction filter, and an iteration scalar, respectively. \wen{$\mathring{\mathbf{D}}$, $\tilde{\mathbf{D}}$ and ${\mathbf{X}}$ denote the 4-D spatial hypercube, the level-4 block Hankel matrix and the approximation low-rank matrix, respectively. ${W}$ denotes the averaging operator used to recover the filtered data after the $rank_d(\cdot)$ process.}

\subsection{Model 2: Rank-constrained tensor completion}

Incomplete seismic tensor $\mathcal{C} \in R^{I_1 \times I_2,...,\times I_N}$ is filled in via tensor completion model given by:
\begin{equation}
\min_{\mathcal{C}}rank_t(\mathcal{C}),\quad s.t.\quad Q_\Phi(\mathcal{C}-\mathcal{D}) = 0,  
\end{equation}
where $\Phi$ corresponds to the observed entries. Precisely, if $\mathcal{D}_{j_1,j_2,j_3,j_4}$ is an observed data, then $ (j_1,j_2,j_3,j_4) \in \Phi $. $ Q_\Phi $ denotes the linear operator. The term $rank_t\left(\cdot\right)$  is the tensor rank-constrained function.

\cite{kreimer2012tensor} proposed to solve model 2 via an iterative tensor completion outlined as follows:

\begin{enumerate}
	\item Convert the 5-D seismic data $\mathcal{D}_{time}(t, hx, hy, x, y)$ defined in time domain into $\mathcal{D}_{freq}(f, hx, hy, x, y)$ of complex values in the frequency-space domain via the 1-D forward FFT.
	\item \wen{Apply the tensor operator $T$ to the 4-D spatial data hypercube at a given frequency $f_0$ to model the level-four tensor.} 
	\item Apply the tensor rank constraint known as HOOI to the \dlo{4D spatial data hypercube}\wen{seismic tensor}. 
	\item Apply the double operator to recover the target filtered approximation tensor.
	\item Apply the iterative weighted POCS-like algorithm to complete the low-rank tensor.
	\item Transform the restored data into the time domain by using the 1-D forward FFT.
\end{enumerate}

The tensor completion approach using the HOOI operator to solve the model 2 is detailed in Algorithm \ref{alg:alg2}.

\begin{algorithm}[H] \caption{Tensor completion via Higher Order Orthogonal Iteration (HOOI)(${H}$, ${f_t}$, $\mathcal{D}_{obsd}$, {$a_{u}$}, $tol$, $u_{max}$, ${F}$)}
	\label{alg:alg2}
	\begin{algorithmic}[1] 
\Require An input 5-D seismic data.\\

$\mathcal{D}_{obsd}(f, hx, hy, x, y)\leftarrow \mathcal{D}_{obsd}(t, hx, hy, x, y)$ via 1-D forward FFT\\
$\mathcal{D}_0\leftarrow\mathcal{D}_{obsd}$\;
		\For{$f\leftarrow 1,2,\dots,{F}$}{
			\For{$u\leftarrow 1,2,\dots,u_{max}$}\\
\wen{$\tilde{\mathcal{D}}\leftarrow{T}(\mathring{\mathcal{D}})$\\
${\hat{\mathcal{D}}}\leftarrow rank_{t}(\tilde{\mathcal{D}})$\\
${\mathcal{D}^f_{u-1}}\leftarrow {d_l}(\hat{\mathcal{D}})$}\\
			{$\mathcal{D}^f_u \leftarrow a_u\mathcal{D}^f_{obsd} + (1 - a_u){Hf}_{t}\mathcal{D}^f_{u-1} + (1 - {H}){f}_{t}\mathcal{D}^f_{u-1}$\;
				\If{$\left\|\mathcal{D}^f_u - \mathcal{D}^f_{u-1}\right\|_F^2\leq tol$}\\
				{\textbf{return} $\mathcal{D}^f_u$\;
				}
				\EndIf\\
				\textbf{return} $\mathcal{D}^f_{u_{max}}$\;
			}\EndFor\\			
			\textbf{return} $\mathcal{D}_{recovered}$\;
		}
		\EndFor\\
		$\mathcal{D}_{recovered}(t,hx, hy, x, y)\leftarrow\mathcal{D}_{recovered}(f,hx, hy, x, y)$ via 1-D inverse FFT\;
	\end{algorithmic}
\end{algorithm}

\wen{In Algorithm \ref{alg:alg2}}, ${H}$ and ${f}_{t}$ correspond to the sampling operator and the tensor rank-reduction filter, respectively. The tensor operator \wen{${T}$ is applied to the 4-D spatial data hypercube $\mathring{\mathcal{D}}$. $\tilde{\mathcal{D}}$ is the resulting 4-D tensor. $\hat{\mathcal{D}}$ denotes the approximation of low-rank tensor. The notation ${d_l(\cdot)}$ denotes the double operator used to recover the filtered data after the $rank_t(\cdot)$ process.}

\subsection{Model 3: Mixed rank-constrained model}

Based on models 1 and 2, \dlo{we introduce a novel model that intends to combine}\wen{we introduce a model that combines} the damped and tensor rank-constrained models. The proposed model applies double rank constraints to solve the seismic data recovery problem. The noisy and incomplete data can be reconstructed by implementing the proposed mixed rank-constrained model: 
\begin{equation}
\min_{\mathbf{C},\mathcal{C}}rank_{dt}(M\mathbf{C},\mathcal{C}),\; s.t.\; \left( \mathbf{C},\mathcal{C}\right)_{j_1,j_2,j_3,j_4} =\left(\mathbf{D},\mathcal{D}\right)_{j_1,j_2,j_3,j_4}, 
\end{equation}
where $rank_{dt}\left(\cdot,\cdot\right)$ corresponds to the mixed rank-constrained function for $ (j_1,j_2,j_3,j_4) \in\Phi $.

By applying the unfolding operator, an Nth-order tensor $\mathcal{D}_{j_1,j_2,j_3,...,j_N}$ where $j_n$ = 1···$J_n$, $n = 1,...,N $ along each mode can be molded into $ N $ matrices. Also, the folding operator can be applied to convert a matrix into a tensor \cite{kolda2009tensor}. Therefore, we propose to solve the new model 3 by applying first the unfolding and folding operators to factorize the four-dimensional spatial hypercube $\mathcal{D}_{J_1, J_2,J_3,J_4}$ defined in frequency-space domain outside the loop for each iteration numbers. For simplification, we drop the components {$J_1,J_2,J_3,J_4$} of $\mathcal{D}_{J_1,J_2,J_3,J_4}$ where $J_n$ = 1···$J_n$ with $n = 1,2,3,4$. So, $\mathcal{D}_{J_1,J_2,J_3,J_4}$ can be seen as $\mathcal{D}$. The operation of unfolding and folding for a mode $ k $ is given by:   
\begin{equation}
\textbf{D}_{(k)}= unfold_{k}[\mathcal{D}],\quad k=1,...,N,
\label{eq:eq4}
\end{equation}
\begin{equation}
\mathcal{D}  = \sum_{k=1}^{N} fold_{k}\left[\textbf{D}_{(k)}\right], 
\label{eq:eq5}
\end{equation}
where $\mathcal{D}$ denotes our target folded 4-D spatial hypercube.

Such operation for a third-order tensor ($N = 3$) is summarized in \dlo{Fig. 1}\wen{Figs. \ref{fig:UNFOLDING_FOLDING-a}-\ref{fig:UNFOLDING_FOLDING-c}}
\inputdir{./}
\multiplot{3}{UNFOLDING_FOLDING-a,UNFOLDING_FOLDING-b,UNFOLDING_FOLDING-c}{width=0.2\textwidth}{Schematic representation of the unfolding and folding for a third-order tensor $(I_1\times I_2\times I_3)-$tensor $\mathcal{D}$. \wen{(a) Unfolding and folding mode-1. (b) Unfolding and folding mode-2. (c) Unfolding and folding mode-3.}}

Then, all components of the folded 4-D spatial hypercube data $\mathcal{D}$ are inserted into a level-one block Hankel matrix:
\begin{equation}
\textbf{G}^{(h_1)}=\begin{pmatrix}
\mathcal{D}_{1} & \mathcal{D}_{2} & ... & \mathcal{D}_{Y_{1}-U_{1}+1}\\ 
\mathcal{D}_{2} & \mathcal{D}_{3} & ... & \mathcal{D}_{Y_{1}-U_{1}+2}\\ 
\vdots & \vdots & \ddots & \vdots\\
\mathcal{D}_{{U_{1}}{}} & \mathcal{D}_{{U_{1}+1},}  & ... & \mathcal{D}_{Y_{1}}
\end{pmatrix}.
\end{equation}
The matrices in eq.(6) are then included in a second-level block Hankel matrix:
\begin{equation}
\textbf{G}^{(h_2)}=\begin{pmatrix}
\textbf{G}^{(h_1)}_{1} & \textbf{G}^{(h_1)}_{2} & ... & \textbf{G}^{(h_1)}_{Y_{2}-U_{2}+1}\\ 
\textbf{G}^{(h_1)}_{2} & \textbf{G}^{(h_1)}_{3} & ... & \textbf{G}^{(h_1)}_{Y_{2}-U_{2}+2}\\
\vdots & \vdots & \ddots & \vdots\\
\textbf{G}^{(h_1)}_{U_{3}} & \textbf{G}^{(h_1)}_{U_{2}{+1}} & ... & \textbf{G}^{(h_1)}_{Y_{2}}\\ 
\end{pmatrix}.
\end{equation}
The Hankelization operator follows the same process to construct the third level of the target block Hankel matrix:
\begin{equation}
\textbf{G}^{(h_3)}=\begin{pmatrix}
\textbf{G}^{(h_2)}_{1} & \textbf{G}^{(h_2)}_{2} & ... & \textbf{G}^{(h_2)}_{Y_{3}-U_{3}+1}\\ 
\textbf{G}^{(h_2)}_{2} & \textbf{G}^{(h_2)}_{3} & ... & \textbf{G}^{(h_2)}_{Y_{3}-U_{3}+2}\\ 	
\vdots & \vdots & \ddots & \vdots\\
\textbf{G}^{(h_2)}_{U_{3}} & \textbf{G}^{(h_2)}_{U_{3}+1} & ... & \textbf{G}^{(h_2)}_{Y_{3}}
\end{pmatrix}.
\end{equation}
At last, all level-three matrices are inserted to construct the expected level-four block Hankel matrix:
\begin{equation}
\textbf{G}^{(h_4)}=\begin{pmatrix}
\textbf{G}^{(h_3)}_1 & \textbf{G}^{(h_3)}_2 & ... & \textbf{G}^{(h_3)}_{Y_4-U_4+1}\\ 
\textbf{G}^{(h_3)}_2 & \textbf{G}^{(h_3)}_3 & ... & \textbf{G}^{(h_3)}_{Y_4-U_4+2}\\ 
\vdots & \vdots & \ddots & \vdots\\
\textbf{G}^{(h_3)}_{U_{4}} & \textbf{G}^{(h_3)}_{U_{4} +1} & ... & \textbf{G}^{(h_3)}_{Y_{4}}
\end{pmatrix},
\end{equation}
where $\textbf{G}$ is the desired block Hankel matrix containing the folded four-dimensional spatial hypercube data. $h_i$ corresponds to the reached level.
If $Y_n$ is an odd integer, the size of 
$\textbf{G}^{(h_4)}$ can be written as $(U_1U_2U_3U_4)\times(U_1U_2U_3U_4)$.

If we ignore the argument $h_4$ of the target matrix, the Hankelization operation can be expressed by: 
\begin{equation}
\mathbf{G}={M}\mathcal{D},              
\end{equation}
where ${M}$ is the Hankelization operator.

\cite{chen2016simultaneous} concluded the DRR formula for the low-rank signal matrix approximation as follows:
\begin{align}
\mathbf{X}=\mathbf{U}^{\mathbf{G}}_1{\Sigma^{\mathbf{G}}_1}\eta\left(\mathbf{V}^{\mathbf{G}}_1\right)^{{T}},
\end{align}
where $\mathbf{X}$ and ${\Sigma^{\mathbf{G}}_1}$ correspond to the approximation signal and the diagonal matrix that contains larger singular values. The matrices having singular vectors are denoted by $\mathbf{U}^{\mathbf{G}}_1$ and $\mathbf{V}^{\mathbf{G}}_1$. $\left(\cdot\right) ^{T}$ indicates the conjugate transpose. The symbol $\eta$, which is formulated as follows is the damping operator:
\begin{align}
\eta= I - (\Sigma^{\mathbf{G}}_1 )^{-{z}}{{\ell}^{z}},
\end{align} 
where ${\ell}$ represents the maximum element of the smaller singular values, and $z$ corresponds to the damping factor.

The process of obtaining the approximation signal matrix $\mathbf{X}$ is given as follows:
\begin{equation}
\mathbf{X}=R_\eta{\mathbf{{G}}}, 
\end{equation}
where $R_\eta$ denotes the DRR operator (eq.(1)).

The process of the averaging function, which is applied along the anti-diagonals of $\mathbf{X}$ can be expressed as
\begin{equation}
\mathbf{P}={W}\mathbf{X},
\end{equation}
where ${W}$ denotes the averaging operator.

Then, the 4-D data matrix $\mathbf{P}$ is transformed into a tensor $\mathcal{D}$ to estimate its best rank via the HOOI \citep{sheehan2007higher} decomposition technique. At this step, a connection between the damped and the tensor rank constraints is created.

Consider the Nth-order tensor $\mathcal{D}\in R^{I_1 \times I_2,...,\times I_N}$ and its corresponding low-rank tensor $\mathcal{\hat D} \in R^{I_1 \times I_2,...,\times I_N}$, which is constrained by 
$rank_{t1}(\mathcal{\hat D})= R_1$, $rank_{t2}(\mathcal{\hat D})= R_2,...,rank_{tN}(\mathcal{\hat D})=R_N$. The following least-squares problem
\begin{equation}
f(\mathcal{\hat D})=\left\|\mathcal{D}-\mathcal{\hat D}\right\|^2, 
\end{equation}
estimates $ \mathcal{\hat D} $ by computing a tensor $\mathcal{A}$ that optimizes the least-squares cost function $f(\mathcal{\cdot})$ in eq.(15). The tensor $\mathcal{A}$ is given by:
\begin{equation}
\mathcal{A}=\mathcal{D}\times_1\mathbf{S}^{(1)^{T}}\times_2\mathbf{S}^{(2)^{T}}...\times_N\mathbf{S}^{(N)^{T}}.
\end{equation}
The alternating least-squares (ALS) approach used to solve the $ Rank_t-({R_1,R_2,...,R_N}) $ problem in this paper is the HOOI. By using the MATLAB Tensor Toolbox proposed by \cite{bader2010matlab}, HOOI operator successively solves the restricted optimization problems \citep{sheehan2007higher}:
\begin{equation}
\min_{\mathbf{S}^P}\left\|\mathcal{D} - \mathcal{A} \times_1\mathbf{S}^{(1)}\times_2\mathbf{S}^{(2)}...\times_N\mathbf{S}^{(N)} \right\|_F^2.
\end{equation}
Optimization is achieved over the matrix $\mathbf{S}^P$ with the latest available values of other $\mathbf{S}^i$.

Based on the N-rank requirements, $\mathcal{\hat D}$ is decomposed in the following ways:
\begin{equation}
\mathcal{\hat{D}}=\mathcal{A}\times_1\mathbf{S}^{(1)}\times_2\mathbf{S}^{(2)}...\times_N\mathbf{S}^{(N)},
\end{equation}
in which $ \mathbf{S}^{(1)} \in R^{I_1 \times R_1} $, $ \mathbf{S}^{(1)} \in R^{I_2 \times R_2}$,..., $ \mathbf{S}^{(N)} \in R^{I_N \times R_N}$, and have orthonormal columns.  $ \mathcal{A} \in R^{R_1\times R_2 \times...\times R_N}$.

The tensor rank-reduction operator is given as follows:
\begin{equation}
\mathcal{\hat D} = {R_t}{\mathcal{D}}, 
\end{equation}
where ${R_t}$ denotes the HOOI operator.

Afterward, the filtered data is recovered by applying the double function to the target low-rank tensor $\mathcal{\hat D}$. 
From this operation, we can formulate an improved rank-reduction filter based on the mixed rank-constrained model:
\begin{equation}
\mathcal{\breve{D}}= d_l\left(\mathcal{\hat D}\right)=d_l\left( {R_t}{\mathcal{D}}\right)=d_l\left({R_t}T{W}{R_\eta}{M}\mathcal{D}\right)=f_{dt}\mathcal{D},
\end{equation}
\dlo{where $d_l\left(\cdot\right)$ and $T$ correspond to the double and tensor functions, respectively.}\wen{where} $f_{dt}$ denotes the mixed rank-constrained filter.

At last, we apply the following iterative algorithm to complete the low-rank tensor adequately:
\begin{equation}
\mathcal{D}_u = a_u\mathcal{D}_{obsd} + (1 - a_u){H}f_{dt}\mathcal{D}_{u-1} + (1 - {H})f_{dt}\mathcal{D}_{u-1},
\end{equation}  
where $\mathcal{D}_0=\mathcal{D}_{obsd}$ indicates the observed data. $u=1,2,3,...,u_{max}$ is an iteration number. $a_{u}$ corresponds to a given iteration dependent scalar, which diminish from $a_1=1$ to $a_{u_{max}}=0$. ${H}$ is the sampling operator. The elements of ${H}$ correspond to $ 1 $ when the observation is non-zero, otherwise $0$ for the incomplete values.

A comprehensive description of the MRC method to solve model 3 is given by Algorithm \ref{alg:alg3}.

\begin{algorithm}[H] \caption{Mixed rank constraints algorithm (MRC)(${H}$, ${f_{dt}}$, $\mathcal{D}_{obsd}$, $ r_1,_{\cdot\cdot\cdot},r_N $, {$a_{u}$}, $tol$, $u_{max}$, ${F}$)}
	\label{alg:alg3}
	\begin{algorithmic}[1] 
\Require An input 5-D seismic data.\\
$\mathcal{D}_{obsd}(f, hx, hy, x, y)\leftarrow \mathcal{D}_{obsd}(t, hx, hy, x, y)$ via 1-D forward FFT\\		    
$\mathcal{D}_0\leftarrow\mathcal{D}_{obsd}$\;
		\For{$f\leftarrow 1,2,\dots,{F}$}{
			\For{$k=1,\dots,N$}\\{$\mathcal{D}=\sum_{k=1}^{N} fold_{k}\left[{D}_{(k)}\right]$}
			\EndFor
			\For{$u\leftarrow 1,2,\dots,u_{max}$}\\
\wen{${\mathbf{G}}\leftarrow{M}({\mathcal{D}})$\\
${{\mathbf{X}}}\leftarrow rank_{d}({\mathbf{G}})$\\
${{\mathbf{P}}}\leftarrow {W}{\mathbf{X}}$\\
${\mathcal{\check{D}}}\leftarrow{T}({\mathbf{P}})$\\
${\hat{\mathcal{D}}}\leftarrow rank_{t}({\mathcal{\check{D}}})$\\
${\mathcal{D}^f_{u-1}}\leftarrow {d_l}(\hat{\mathcal{D}})$}\\
			{$\mathcal{D}^f_u \leftarrow a_u\mathcal{D}^f_{obsd} + (1 - a_u){Hf}_{d}\mathcal{D}^f_{u-1} + (1 - {H}){f}_{d}\mathcal{D}^f_{u-1}$\;
				\If{$\left\|\mathcal{D}^f_u - \mathcal{D}^f_{u-1}\right\|_F^2\leq tol$}\\
				{\textbf{return} $\mathcal{D}^f_u$\;
				}
				\EndIf\\
				\textbf{return} $\mathcal{D}^f_{u_{max}}$\;
			}\EndFor\\			
			\textbf{return} $\mathcal{D}_{recovered}$\;
		}
		\EndFor\\		
		$\mathcal{D}_{recovered}(t,hx, hy, x, y)\leftarrow \mathcal{D}_{recovered}(f,hx, hy, x, y)$ via 1-D inverse FFT\;
	\end{algorithmic}
\end{algorithm}

\wen{Noisy and severely decimated 4-D spatial hypercube data that the level-4 block Hankel matrix contains weakens the performances of the $rank_{d}(\cdot)$ process. To tackle this difficulty, \wen{we apply low-rank matrix factorization \citep{gao2015parallel} to each mode unfolding (eq. (\ref{eq:eq4})) of the 4-D spatial hypercube data to enforce low rank and update the matrix factors alternatively in eq. (\ref{eq:eq5}).}\dlo{we impose a low-rankness to the observed data by applying the unfolding and folding operator to the 4-D spatial hypercube.} This operation minimizes the contribution of noise in the resulting folded 4-D spatial hypercube $\mathcal{D}$. By including the components of $\mathcal{D}$ (\wen{eq. (\ref{eq:eq5})}) into $\mathbf{G}$, we improve the $rank_{d}(\cdot)$ process. Indeed, contrary to the DRR method, our target block Hankel matrix ${\mathbf{G}}$ is composed of the improved 4-D spatial hypercube data $\mathcal{D}$.}

\wen{The mixed rank-constrained function is a combination of the damped rank-constrained function ($rank_{d}(\cdot)$) and the tensor rank-constrained function ($rank_{t}(\cdot)$). After applying the function $rank_{d}(\cdot)$ to $\mathbf{G}$, the averaging operator ${W}$ is applied to transform the approximation signal ${\mathbf{X}}$ into the filtered data ${\mathbf{P}}$ having the physical components $hx, hy, x$ and $y$ as spatial size. Then, the tensor function is applied to convert ${\mathbf{P}}$ into the tensor ${\mathcal{\check{D}}}$ having the same spatial size. To perform this step, the tensor operator should match the physical components of ${\mathbf{P}}$. Next, the function $rank_{t}(\cdot)$ is applied to the resulting 4-D tensor ${\mathcal{\check{D}}}$ to further reduce the rank. Afterward, the filtered low-rank tensor ${\mathcal{\hat{D}}}$ got after applying the double function is filled in via the weighted POCS-like algorithm.}

\wen{By applying the mixed rank-constrained, we can further improve the quality of the useful signal even when the observed data is highly decimated. The proposed MRC method is relatively cheaper than the DRR approach in terms of computation time because of the low-rankness of the level-4 block Hankel matrix $\mathbf{G}$.}

In the three algorithms, the process of iteration ceases \dlo{when the frequencies ${F}$ are achieved}\wen{when all the frequencies ${F}$ are processed}. Two independent conditions induce the algorithm to stop running: first, when {$u_{max}$} that corresponds to the maximum number of iteration is finished. Then, if {$\left\|\mathcal{D}^f_u- \mathcal{D}^f_{u-1}\right\|_F^2\leq tol$} for each ${F}$ band\dlo{$tol$ and {$\left\|\cdot\right\|_F$} are the given small tolerance and the Frobenuis norm, respectively}. \wen{$tol$ is a given small tolerance. {$\left\|\cdot\right\|_F$} denotes the Frobenuis norm.}

\section{Examples}

\subsection{Synthetic data examples}

We show the simultaneous denoising and reconstruction performance of the proposed approach on 5-D synthetic data. The first and second synthetic data used in this paper contain linear and curved events, respectively. For each test, the effectiveness of the proposed \wen{MRC} approach is compared with the HOOI and the DRR approaches. The recovery quality is assessed through the SNR of the final results in decibels \citep{chen2016simultaneous}: 
\begin{equation}
SNR=10\log_{10}\frac{\Vert X^{o} \Vert^2_2}{\Vert X^{o}-X^{r}\Vert^2_2},
\end{equation}
where $X^{o}$ and $X^{r}$ are the vectorized original data (ground truth) and the vectorized recovered signal, respectively. The higher values of SNR will denote the more reliable recovery quality.

For the case of synthetic data containing linear events, we generate noisy data by adding a noise variance of $0.1$ to the original data. We create the observed data by removing $80\%$ of traces from the noisy data. The SNRs of the noisy and observed data are $ -0.66 $ dB and $ -0.14 $ dB, respectively. To recover the useful signal, we apply the HOOI algorithm with rank \dlo{$r_{k}=3$}\wen{$r_{k}=(3,3,3,3)$}. We run the DRR algorithm with rank $r=3$ and damping factor $z=3$. For the proposed \wen{MRC} algorithm, we select $r=3$, $z=3$, and \dlo{$r_{k}=10$}\wen{$r_{k}=(10,10,10,10)$}. We perform the three algorithms using a band of frequencies $5-100$ Hz and $15$ weighted POCS-like iterations. \dlo{Figs. \ref{fig:synth-original-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-hooi-hxhy,synth-drr-hxhy,synth-mrc-hxhy} and \ref{fig:synth-original-xy,synth-noisy-xy,synth-obs-xy,synth-hooi-xy,synth-drr-xy,synth-mrc-xy} display the comparison in one common midpoint and offset gathers, respectively}\wen{Fig. \ref{fig:synth-original-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-hooi-hxhy,synth-drr-hxhy,synth-mrc-hxhy} displays the comparison in one common midpoint gather. The comparison in one common offset gather is plotted in Fig.  \ref{fig:synth-original-xy,synth-noisy-xy,synth-obs-xy,synth-hooi-xy,synth-drr-xy,synth-mrc-xy}.} Figs. \ref{fig:synth-original-hxhy} and \ref{fig:synth-original-xy} show the original data. The noisy data is plotted in Figs. \ref{fig:synth-noisy-hxhy} and \ref{fig:synth-noisy-xy}. Figs. \ref{fig:synth-obs-hxhy} and \ref{fig:synth-obs-xy} display the observed data. Figs. \ref{fig:synth-hooi-hxhy} and \ref{fig:synth-hooi-xy} represent the recovered data using the HOOI algorithm. Figs. \ref{fig:synth-drr-hxhy} and \ref{fig:synth-drr-xy} correspond to the DRR approach. The recovered data using the proposed \wen{MRC} approach is displayed in Figs. \ref{fig:synth-mrc-hxhy} and \ref{fig:synth-mrc-xy}. From the comparison of each sub-figure, we find that our algorithm provides much better results than the other two algorithms since the useful signal is accurately restored and contains the least residual noise. This comparison also shows that the DRR approach can achieve a more satisfactory result than the HOOI approach.

\inputdir{synth}
\multiplot{6}{synth-original-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-hooi-hxhy,synth-drr-hxhy,synth-mrc-hxhy}{width=0.3\textwidth}{Common midpoint 3-D figures comparison ($x$ = 5, $y$ = 5) of synthetic data, including linear events. (a) shows the original data. (b) displays the noisy data. (c) is from the observed data. (d) corresponds to the recovered data using the HOOI approach. (e) denotes the recovered data using the DRR approach. (f) plots the recovered data using the proposed MRC approach.}

\inputdir{synth}
\multiplot{6}{synth-original-xy,synth-noisy-xy,synth-obs-xy,synth-hooi-xy,synth-drr-xy,synth-mrc-xy}{width=0.3\textwidth}{Common offset 3-D figures comparison ($hx$ = 5, $hy$ = 5) of synthetic data, including linear events. (a) displays the original data. (b) shows the noisy data. (c) is from the observed data. (d) denotes the recovered data using the HOOI approach. (e) designates the recovered data using the DRR approach. (f) corresponds to the recovered data using the proposed MRC approach.}

We illustrate the recovery error of each approach in Figs. \ref{fig:synth-hooi-hxhy-e,synth-drr-hxhy-e,synth-mrc-hxhy-e,synth-hooi-xy-e,synth-drr-xy-e,synth-mrc-xy-e}. Figs. \ref{fig:synth-hooi-hxhy-e}-\ref{fig:synth-mrc-hxhy-e} denote the error of the HOOI, the DRR and the proposed \wen{MRC} methods in one common midpoint gather, respectively. Figs. \ref{fig:synth-hooi-xy-e}-\ref{fig:synth-mrc-xy-e} display, respectively, the error of the HOOI, the DRR, and the proposed \wen{MRC} methods in one common offset gather. Because of \dlo{the less reconstruction error}\wen{a small reconstruction error}, we deduce that the proposed \wen{MRC} algorithm restores the useful events better than the DRR and the HOOI approaches. The reconstruction error comparison highlights the superiority of the proposed \wen{MRC} approach.

\inputdir{synth}
\multiplot{6}{synth-hooi-hxhy-e,synth-drr-hxhy-e,synth-mrc-hxhy-e,synth-hooi-xy-e,synth-drr-xy-e,synth-mrc-xy-e}{width=0.3\textwidth}{Simultaneous denoising and reconstruction error comparison. (a)-(c) correspond to the errors obtained by the HOOI, the DRR, and the proposed approaches in one common midpoint gather ($x$ = 5, $y$ = 5), respectively. (d)-(f) denote the errors obtained via the HOOI, the DRR, and the proposed MRC approaches in one common offset gather ($hx$ = 5, $hy$ = 5), respectively.}

The SNRs for this example are $8.12$ dB, $13.78$ dB, and $17.73$ dB for the HOOI, the DRR, and the proposed approaches, respectively. The quantitative analysis confirms the better recovery quality of our MRC approach.

To investigate the effectiveness of the proposed \wen{MRC} method in another representation, we compare the frequency-space (f-x) spectra of each data plotted in Fig. \ref{fig:synth-original-xy,synth-noisy-xy,synth-obs-xy,synth-hooi-xy,synth-drr-xy,synth-mrc-xy}. Figs. \ref{fig:fx_original_linear}-\ref{fig:fx_observed_linear} display the f-x spectra of the original, noisy, and observed data, respectively. Figs. \ref{fig:fx_HOOI_linear}-\ref{fig:fx_proposed_linear}, are, respectively, from the HOOI, the DRR, and the proposed approaches. The analysis of each result reveals that the DRR and the proposed \wen{MRC} approaches can remove the more residual noise in a large frequency band than the HOOI algorithm. However, when we focus on the small temporal frequencies band (from $10$ to $60$ Hz), we find that the proposed \wen{MRC} approach recovers the significant features of the signal better than the DRR method. The f-x representation distinctly proves that our algorithm provides similar recovered data to the original data.

\inputdir{./}
\multiplot{6}{fx_original_linear,fx_Noisy_linear,fx_observed_linear,fx_HOOI_linear,fx_DRR_linear,fx_proposed_linear}{width=0.3\textwidth}{Frequency-space (f-x) spectra comparison of each data shown in Fig. \ref{fig:synth-original-xy,synth-noisy-xy,synth-obs-xy,synth-hooi-xy,synth-drr-xy,synth-mrc-xy}. (a)-(c) correspond to the original, noisy, and observed synthetic data, respectively. (d)-(f) denote the HOOI, the DRR, and the proposed MRC approaches, respectively.}

We also compare the single trace amplitude of each data from Fig. \ref{fig:synth-original-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-hooi-hxhy,synth-drr-hxhy,synth-mrc-hxhy} in Fig. \ref{fig:synth-ss}. The red, black, and magenta lines are, respectively, from the original, the noisy, and the observed data. \dlo{The yellow and blue lines are, respectively, from the HOOI, and the DRR approaches}\wen{The yellow line is from HOOI method. The blue line corresponds to the single trace amplitude of the DRR method}. The green line is from the proposed \wen{MRC} method. As seen, because of the large percentage of incomplete traces, the amplitude of the observed data is degraded. A detailed comparison reveals that the red and the green lines are almost the same. We can, therefore, affirm that the proposed MRC algorithm can better restore the significant features of the useful signal than the HOOI and the DRR approaches.

\inputdir{synth}
\plot{synth-ss}{width=1\columnwidth}{Comparison of a single trace amplitude of each corresponding data shown in Fig. \ref{fig:synth-original-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-hooi-hxhy,synth-drr-hxhy,synth-mrc-hxhy}. The red line is from the original synthetic data. The black line denotes the noisy synthetic data. The magenta line is from the observed data. The yellow and blue lines are from the HOOI and the DRR methods, respectively. The amplitude provided by the proposed MRC method is denoted by the green line.}

We then conduct another experiment to show the effectiveness of the proposed MRC approach on synthetic data that is constituted of curved events. We compare the performance of the proposed \wen{MRC} algorithm with that of the HOOI and the DRR algorithms. By adding a noise level of $0.1$ to the original data and removing $80\%$ of traces, we generate the observed data with an SNR of about $0.86$ dB. For this experiment, we adopt rank \dlo{$r_{k}=1$}\wen{$r_{k}=(1,1,1,1)$} for the HOOI method, rank $r=12$, and damping factor $z=3$ for the DRR method. We select $r=14$, $z=3$ and \dlo{$r_{k}=2$}\wen{$r_{k}=(2,2,2,2)$}, for the proposed \wen{MRC} method. We implement the three algorithms in temporal frequencies band $5-100$ Hz with $15$ weight POCS-like iterations. We conduct the one common midpoint gather comparison in Fig. \ref{fig:hyper-clean2d-0,hyper-obs2d-0,hyper-hooi2d-0,hyper-drr2d-0,hyper-mrc2d-0}. The original data and the observed data are, respectively, displayed in Figs. \ref{fig:hyper-clean2d-0} and \ref{fig:hyper-obs2d-0}. \dlo{Figs. \ref{fig:hyper-hooi2d-0}, \ref{fig:hyper-drr2d-0}, and \ref{fig:hyper-mrc2d-0} show the results obtained by using the HOOI, the DRR, and the proposed \wen{MRC} algorithms, respectively.}\wen{Fig. \ref{fig:hyper-hooi2d-0} shows the result obtained by using the HOOI method. Fig. \ref{fig:hyper-drr2d-0} is from the DRR method. The restored data from the proposed MRC method is plotted in Fig. \ref{fig:hyper-mrc2d-0}}. From the visual inspection of each sub-figure, different methods can successfully reconstruct the noisy and missing traces. However, the results of the HOOI and the DRR approaches seem to contain serious artifacts because of the remaining noise.

\inputdir{hyper}
\multiplot{6}{hyper-clean2d-0,hyper-obs2d-0,hyper-hooi2d-0,hyper-drr2d-0,hyper-mrc2d-0}{width=0.9\textwidth}{Common midpoint 2-D figures comparison of synthetic data having curved events. (a) Original data. (b) Observed data. (c) Recovered data using the HOOI approach. (d) Recovered data using the DRR approach. (e) Recovered data using the proposed MRC approach.}

To precisely see the difference, we display in Fig. \ref{fig:hyper-z-clean,hyper-z-obs,hyper-z-hooi,hyper-z-drr,hyper-z-mrc} the zoomed data highlighted by each blue frame boxes in Fig. \ref{fig:hyper-clean2d-0,hyper-obs2d-0,hyper-hooi2d-0,hyper-drr2d-0,hyper-mrc2d-0}. \dlo{Figs. \ref{fig:hyper-z-clean} and \ref{fig:hyper-z-obs} are from the original and the observed data, respectively}\wen{Fig. \ref{fig:hyper-z-clean} corresponds to the original data. The noisy data is displayed in Fig. \ref{fig:hyper-z-obs}.} Figs. \ref{fig:hyper-z-hooi}-\ref{fig:hyper-z-mrc} correspond, respectively, to the HOOI, the DRR, and the proposed approaches. Compared to the HOOI, and the DRR approaches, the zoomed data using our approach contains the least residual noise.

\inputdir{hyper}
\multiplot{6}{hyper-z-clean,hyper-z-obs,hyper-z-hooi,hyper-z-drr,hyper-z-mrc}{width=0.3\textwidth}{Comparison of the zoomed sections from Figs. \ref{fig:hyper-clean2d-0,hyper-obs2d-0,hyper-hooi2d-0,hyper-drr2d-0,hyper-mrc2d-0} (the blue frame boxes). (a) displays the original data. (b) shows the observed data. (b), (c) and (d) denote the simultaneously denoised and reconstructed data using the HOOI, the DRR, and the proposed approaches, respectively.}

To make a valid comparison based on visual analysis, we display in Fig. \ref{fig:hyper-hooi2d-e,hyper-drr2d-e,hyper-mrc2d-e} the recovery error that uses each approach for the zoomed data\dlo{Fig. \ref{fig:hyper-hooi2d-e}, \ref{fig:hyper-drr2d-e} and \ref{fig:hyper-mrc2d-e} show the errors of the HOOI, the DRR, and the proposed methods, respectively}. \wen{Fig. \ref{fig:hyper-hooi2d-e} is from the HOOI method. Fig. \ref{fig:hyper-drr2d-e} plots the reconstruction error obtained using the DRR method. That of the proposed MRC method is displayed in Fig. \ref{fig:hyper-mrc2d-e}.} The comparison of the recovery error confirms that the proposed \wen{MRC} algorithm performs better with the least error. However, the error of the other two algorithms is significant because of the level of the residual noise.

\inputdir{hyper}
\multiplot{6}{hyper-hooi2d-e,hyper-drr2d-e,hyper-mrc2d-e}{width=0.3\textwidth}{Simultaneous denoising and reconstruction error comparison of the zoomed section. (a) shows the error using the HOOI approach. (b) displays the error using the DRR approach. (c) presents the error using the proposed MRC approach.}

Another perspective that requires a comprehensive examination to further demonstrate the performance of our \wen{MRC} algorithm is the frequency-space (f-x) domain representation of each curved data. Fig.  \ref{fig:fx_original_curved,fx_Observed_curved,fx_HOOI_curved,fx_DRR_curved,fx_proposed_curved} displays the comparison between each data for a band of frequency of $0 - 60$ Hz. \dlo{Figs. \ref{fig:fx_original_curved} and \ref{fig:fx_Observed_curved} are from the original and the observed data, respectively}\wen{Fig. \ref{fig:fx_original_curved} shows the corresponding spectrum of the original data. Fig. \ref{fig:fx_Observed_curved} is from the observed data.} \dlo{The f-x spectra using the HOOI, the DRR, and the proposed \wen{MRC} methods are displayed in Figs. \ref{fig:fx_HOOI_curved}, \ref{fig:fx_DRR_curved}, and \ref{fig:fx_proposed_curved}, respectively.} \wen{The f-x spectrum using the HOOI method is displayed in Fig. \ref{fig:fx_HOOI_curved}. Fig. \ref{fig:fx_DRR_curved} is from the DRR method. We display the f-x spectrum of the proposed MRC method in Fig. \ref{fig:fx_proposed_curved}}. The comparison of each spectrum still shows the better performance of our \wen{MRC} approach. The proposed \wen{MRC} approach can provide good results that are very close to the original data. All significant features of the useful signal using our \wen{MRC} approach are restored with the least residual noise in the whole frequency band.

\inputdir{./}
\multiplot{6}{fx_original_curved,fx_Observed_curved,fx_HOOI_curved,fx_DRR_curved,fx_proposed_curved}{width=0.3\textwidth}{Frequency-space (f-x) spectra comparison of each data displayed in Fig. \ref{fig:hyper-clean2d-0,hyper-obs2d-0,hyper-hooi2d-0,hyper-drr2d-0,hyper-mrc2d-0}. (a) displays the f-x spectrum of the original data. (b) shows the f-x spectrum of the decimated data. (c), (d) and (e) correspond to the f-x spectra obtained after using the HOOI, the DRR, and the proposed MRC methods, respectively.}

The SNRs in this example are $14.83$ dB, $15.04$ dB, and $23.73$ dB for the HOOI, the DRR, and the proposed MRC approaches, respectively. This numerical analysis confirms the superiority of our approach and its adaptability to data, including curved events.

To estimate the computation time, we add a noise variance of $0.1$ to the original data including linear events, and we randomly remove $20\%$, $40\%$, $60\%$, and $80\%$ traces from the noisy data. We fix the number of iterations at $15$, and the temporal frequencies band $5 - 100$ Hz. For each decimated data, we run the codes $7$ times for each method and record the running time. The average computation time corresponding to each method is displayed in Table \ref{tbl:table1}, which shows the best performance in terms of the computational cost of the HOOI algorithm compared to the DRR and the proposed \wen{MRC} algorithms. The proposed \wen{MRC} approach is relatively faster than the DRR method because of our target block Hankel matrix containing the folded four-dimensional spatial hypercube data that improves the computation time of SVD. This comparison shows that the proposed \wen{MRC} method decreases the computational cost compared to the DRR approach.

%\AtEndDocument{
\begin{table}[h]
	\caption{Comparison of computation time \wen{in seconds (s)} of the HOOI, the DRR and the proposed MRC approaches for different decimated data after 15 iterations and temporal frequencies band $5 - 100$ Hz based on an Intel Core i7 7th Gen.}
	\begin{center}
		\begin{tabular}{c c c c c c} 
			\hline observed data &$20\%$& $40\%$&$60\%$&$80\%$&\\ 
			\hline HOOI (s) & 35.85 & 36.70 & 38.57 & 38.76\\
			DRR (s) & 823.34 & 800.75 & 780.69 & 775.96\\
			Proposed (s) & 748 & 753.05 & 757.09& 759.09\\
			\hline
		\end{tabular} 
	\end{center}
	\label{tbl:table1}
\end{table}
%}

%\AtEndDocument{

\subsection{Field data examples}

In this section, a real field of seismic data is considered to show the effectiveness of our \wen{MRC} method. About $75\%$ of the traces are missing in the observed data. Only visual examination is considered for comparison since there are no original field data to conduct quantitative analysis like the SNR measurement. Here, we apply the HOOI approach with \dlo{$r_{k}=1$}\wen{$r_{k}=(1,1,1,1)$} \wen{because of the best representation of the restored data compared with the results obtained using larger values than ${k}=1$. For $k > 1$, the signal leaks even more than when $k = 1$, and contains significant residual noise.}. For the DRR approach, we use rank $r=6$ and damping factor $z=2$. To reconstruct the noisy and incomplete traces, we apply our \wen{MRC} algorithm with the following parameters: $r=6$, $z=2$, and \dlo{$r_{k}=3$}\wen{$r_{k}=(3,3,3,3)$}. We perform the three algorithms for frequencies band $5 - 100$ Hz and $15$ iterations. Fig. \ref{fig:Field-Observed-hxhy,Field-hooi-hxhy,Field-drr-hxhy,Field-mrc-hxhy} shows the comparison in one common midpoint gather. Fig. \ref{fig:Field-Observed-xy,Field-hooi-xy,Field-drr-xy,Field-mrc-xy} displays the results in one common offset gather. The observed data is displayed in Figs. \ref{fig:Field-Observed-hxhy} and \ref{fig:Field-Observed-xy}. The result obtained with the HOOI approach is shown in Figs. \ref{fig:Field-hooi-hxhy} and \ref{fig:Field-hooi-xy}. Figs. \ref{fig:Field-drr-hxhy} and \ref{fig:Field-drr-xy} present the recovered data using the DRR approach. Compared to the HOOI approach, the DRR can obtain better simultaneous denoising and reconstruction performance. However, the data recovered via the DRR approach contains significant residual noise as highlighted by the upper face of the 3-D cube (Figs. \ref{fig:Field-drr-hxhy} and \ref{fig:Field-drr-xy}). As presented in Figs. \ref{fig:Field-mrc-hxhy} and \ref{fig:Field-mrc-xy}, the proposed \wen{MRC} algorithm provides more coherent and cleaner events than the other two approaches. Compared to the DRR approach, the upper faces of the 3-D cubes of our \wen{MRC} approach are smoother and more regular.

\inputdir{./}
\multiplot{4}{Field-Observed-hxhy,Field-hooi-hxhy,Field-drr-hxhy,Field-mrc-hxhy}{width=0.4\textwidth}{Common midpoint 3-D figures comparison of the field data. (a) Observed data. (b)-(d) Simultaneously denoised and reconstructed data using the HOOI approach, the DRR approach, and the proposed MRC approach, respectively.}

\multiplot{4}{Field-Observed-xy,Field-hooi-xy,Field-drr-xy,Field-mrc-xy}{width=0.4\textwidth}{Common offset 3-D figures comparison of the field data. (a) Observed data. (b)-(d) Simultaneously denoised and reconstructed data using the HOOI approach, the DRR approach and the proposed approach, respectively.}

We also demonstrate the success of the proposed MRC algorithm by conducting a single shot gather comparison. We display in Fig. \ref{fig:Zoomed_Field_2D_ONE_SHOT_Observed,Zoomed_Field_2D_ONE_SHOT_HOOI,Zoomed_Field_2D_ONE_SHOT_DRR,Zoomed_Field_2D_ONE_SHOT_Proposed}, the zoomed section of each data shown through the red side boxes in Fig. \ref{fig:Field_2D_ONE_SHOT_observed,Field_2D_ONE_SHOT_HOOI,Field_2D_ONE_SHOT_DRR,Field_2D_ONE_SHOT_Proposed}. The observed data is shown in Fig. \ref{fig:Zoomed_Field_2D_ONE_SHOT_Observed}. From Fig. \ref{fig:Zoomed_Field_2D_ONE_SHOT_HOOI} to \ref{fig:Zoomed_Field_2D_ONE_SHOT_Proposed}, we show the results of the HOOI, the DRR, and the proposed MRC algorithms. The zoomed data comparison shows that the proposed MRC approach can provide better simultaneous denoising and reconstruction performance with less residual noise than the HOOI and the DRR approaches.

\inputdir{./}
\multiplot{4}{Field_2D_ONE_SHOT_observed,Field_2D_ONE_SHOT_HOOI,Field_2D_ONE_SHOT_DRR,Field_2D_ONE_SHOT_Proposed}{width=0.4\textwidth}{Single shot gather comparison of the field data. (a) Observed data. (b)-(d) Simultaneously denoised and reconstructed data using the HOOI approach, the DRR approach and the proposed MRC approach, respectively.}

\inputdir{./}
\multiplot{4}{Zoomed_Field_2D_ONE_SHOT_Observed,Zoomed_Field_2D_ONE_SHOT_HOOI,Zoomed_Field_2D_ONE_SHOT_DRR,Zoomed_Field_2D_ONE_SHOT_Proposed}{width=0.4\textwidth}{Zoomed section from Fig. \ref{fig:Field_2D_ONE_SHOT_observed,Field_2D_ONE_SHOT_HOOI,Field_2D_ONE_SHOT_DRR,Field_2D_ONE_SHOT_Proposed}. (a) Observed data. (b)-(d) Simultaneously denoised and reconstructed data using the HOOI approach, the DRR approach and the proposed MRC approach, respectively.}

\section{Discussion}

Despite the achievement of both the DRR and HOOI approaches, the properties of the reconstructed data are still influenced by \dlo{important}\wen{significant} residual noise, mainly when the input data is seriously decimated or contaminated by significant random noise. In this paper, we assume that only applying the damped rank constraint or the tensor rank constraint is not sufficient to suppress noise while reconstructing the missing traces. This work proposes a new mixed rank constraint model by combining matrix and tensor rank constraints to solve the seismic data interpolation problem adequately. The proposed \wen{MRC} algorithm, which starts by applying the unfolding and folding operation and then connects the DRR and the HOOI operators inside the loop of each iteration number, can be regarded as applying multiple operators to further reduce the rank of the observed data.

In this section, first, the ability of each rank constraint pays our attention. By using the synthetic data containing linear events, we considered the SNRs first, as a function of iteration numbers, then as a function of the percentage of missing values. As seen in Fig. \ref{fig:SNR_with_IterationNumbersok2}, we carried out the simultaneous denoising and reconstruction performance by evaluating the SNRs for the iteration numbers. We applied each rank constraint on an observed data corrupted by a noise level of $0.1$ missing $80\%$ of traces. Also, under the same noise variance, we compare the SNR diagram obtained after $15$ iterations for the sampling ratio percentage, as shown in Fig. \ref{fig:SNR_with_missingTracesok}. In both cases, we run the codes within a band of the frequency of $5-100$ Hz.

\wen{To conduct these tests, we first adopted \dlo{$r_{k}=3$}\wen{$r_{k}=(3,3,3,3)$} when recovering the useful signal via the HOOI method for missing traces percentage and iteration numbers. From 10\% to 70\% of missing traces, we have applied the DRR method with $r = 3$ and ${z}=2$ to restore the seismic events. For data seriously decimated (80\% and 90\% of missing traces), we selected $r = 3$ and ${z}=3$ to further enhance the SNR. We have adopted the same values of rank and damping factor ($r = 3$ and ${z}=3$) to restore the useful signal from the observed data missing 80\% of traces for each iteration number.} From the comparison of the SNR diagram using the DRR approach (blue line) and the HOOI approach (black line), we find that the DRR operator generates higher SNRs than the HOOI operator. When we remove the DRR operator from the proposed \wen{MRC} approach, the method can be regarded as applying the unfolding and folding operator, and the HOOI operator. \wen{Here, we have applied the resulting method (unfolding and folding + HOOI operators) with \dlo{$r_{k}=3$}\wen{$r_{k}=(3,3,3,3)$} for each missing trace percentage and iteration number}. The gray line corresponds to this approach. Similarly, the proposed MRC algorithm without the HOOI operator corresponds to apply the unfolding and folding operator and the DRR operator. \wen{For this case we have adopted \dlo{$r_{k}=3$}\wen{$r_{k}=(3,3,3,3)$}, $r = 3$ and $z = 2$ for the restoration of data missing 10\% to 70\% of traces. For each iteration number, we set $z = 2$ to reconstruct the useful signal from the observed data missing over 70\% of traces}. The SNR diagram for such a method is denoted by the magenta line. The comparison of both last cases shows the contribution of the unfolding and folding operation. Then, \dlo{to know the performance of the proposed MRC algorithm without the unfolding and folding operator,}we analyzed the recovery performance by connecting both the DRR and the HOOI operators. \wen{For this test, we have applied both the DRR and the HOOI (DRR + HOOI) operators to restore the signal matrix from 10\% to 70\% of decimated data with \dlo{$r_{k}=3$}\wen{$r_{k}=(3,3,3,3)$}, $r = 3$ and ${z}=2$. From 80\% to 90\% of missing traces, we have chosen \dlo{$r_{k}=3$}\wen{$r_{k}=(3,3,3,3)$}, $r = 3$ and ${z}=3$ to restore the seismic events for all iteration numbers.} The SNR diagram for this case is displayed in the dashed red line. This experiment shows that the connection of both rank-reduction methods can be helpful for iteration numbers higher than $20$. \wen{For the proposed MRC approach, we have adopted \dlo{$r_{k}=3$}\wen{$r_{k}=(3,3,3,3)$}, $r = 3$ and ${z}=2$ for the reconstruction of the seismic signal from the observed data missing 10\% to 60\% of traces. We selected the same value of rank and damping factor with $r_k = (4,4,4,4)$ for 70\% of missing traces. Above 70\% (80\% and 90\%) of missing traces, we have chosen \dlo{$r_{k}=10$}\wen{$r_{k}=(10,10,10,10)$}, $r = 3$ and ${z}=3$ to restore the useful signal for each iteration numbers}. The green line corresponds to the proposed \wen{MRC} approach, which applies first, unfolding and folding operator, and then connects the DRR and HOOI operators to recover the useful signal. From these figures, we find that as the number of iteration increases, the SNR diagram of the proposed \wen{MRC} approach still outperforms those of each approach mentioned. Even though the SNRs using our \wen{MRC} approach are still superior, let mention that for each method, the quality of the result becomes less reliable when the ratio of sampling data increases. 
\wen{From the different tests, we find that for all aforementioned DRR based methods; we need to select a damping factor ${z}=2$ to recover an observed data missing less than 80\% of traces. However, from 80\% to 90\%, a valid combination of parameters including ${z}=3$ can be defined. In this condition of a high percentage of missing traces, the rank $r_k$ should be large to get a better recovery performance when applying the proposed MRC approach on data containing linear events.}

\wen{The operation of unfolding and folding operator, and DRR operators (proposed without HOOI) denoted by the magenta line can improve the quality of the level-4 block Hankel matrix containing the 4-D spatial hypercube data specially for small iteration numbers (Fig. \ref{fig:SNR_with_IterationNumbersok2}) and when the noisy data is highly decimated (Fig. \ref{fig:SNR_with_missingTracesok}). From our experience, we find that this first step of the proposed approach can further help to reduce the rank of the noisy and incomplete seismic in case of highly decimated traces.}

\inputdir{./}
\plot{SNR_with_IterationNumbersok2}{width=0.35\textwidth}{Comparison of SNR values as a function of iteration. The black, blue, gray, magenta, dashed red and green lines correspond to the HOOI, the DRR, the proposed MRC approach without the DRR operator, the proposed MRC approach without the HOOI operator, the DRR operator with the HOOI operator, and the proposed MRC approaches, respectively. The green line always presents higher SNRs.}

\inputdir{./}
\plot{SNR_with_missingTracesok}{width=0.35\textwidth}{Comparison of SNR diagram for the percentage of missing data after 15 iterations. The black, blue, gray, magenta, dashed red and green lines correspond to the HOOI, the DRR, the proposed MRC approach without the DRR operator, the proposed MRC approach without the HOOI operator, the DRR operator with the HOOI operator, and the proposed MRC approaches, respectively. The green line always presents higher SNRs.}

In implementing the proposed MRC algorithm, we applied two main rank constraints: the damped rank constraint $(rank_{d})$ used by the DRR approach, and tensor rank constraint $(rank_{t})$ used for the unfolding and folding operation, and the HOOI approach. Based on the MRC model denoted by $rank_{dt}$, the proposed \wen{MRC} approach requires three keys parameters: the rank ${r}$, the damping factor ${z}$, and the rank $r_{k}$ to recover the useful signal more accurately. 
To show the effectiveness of the proposed MRC algorithm, we conducted examples of synthetic and field data. It is, therefore, necessary to understand the contribution of each parameter in the results of the proposed \wen{MRC} approach. By using an observed data missing $80\%$ of traces and corrupted with a noise level of $0.1$, we analyze the weight of each parameter. For the case of linear events, we selected ${z}=3$ and $r_k=(10,10,10,10)$, respectively, and we analyze the recovery quality for different values of the parameter $r$. Fig. \ref{fig:snr_rank_r_linear} displays the SNRs for rank $r$. From this figure, based on the lower SNRs, we find that the smaller value of ${r}$, for instance, $1$ and $2$ cannot restore the useful signal well. The result contains a large amount of noise. However, for $r =3$ the proposed \wen{MRC} approach performs better. As shown, all values of $r$ greater than $3$ can create extra noise in the result. Based on the Cadzow filtering method, $r$ can be set according to the number of dip elements for reaching perfect results. In Fig. \ref{fig:snr_dampingFactor_linear}, we show the effect of the parameter $z$ for ${r}=3$ and $r_k=(10,10,10,10)$. The SNRs reveal that $z=1$ is not appropriate\dlo{d} to produce a satisfactory result. The proposed \wen{MRC} approach can be implemented with $z=2$ and $z=3$. For $z$ selected above $3$, the quality of the restored data can be degraded. From Fig. \ref{fig:snr_rank_r_k_linear}, which displays the effect of $r_k$, we find that $r_k=(1,1,1,1)$ and $r_k=(2,2,2,2)$ are not adequate to provide acceptable simultaneous denoising and reconstruction performance. The best quality of the recovered data can be produced with $k$ values ranging from $3$ to $10$. From the analysis of Figs. \ref{fig:snr_rank_r_linear}, \ref{fig:snr_dampingFactor_linear} and \ref{fig:snr_rank_r_k_linear}, we have adopted the valid combination of $r=3$, $z=3$ and $r_k=(10,10,10,10)$ for the recovery of this observed data sample.

\inputdir{./}
\multiplot{4}{snr_rank_r_linear,snr_dampingFactor_linear,snr_rank_r_k_linear}{width=0.3\textwidth}{Influence of each parameter used in the proposed MRC method for 5-D synthetic data having linear events. (a) corresponds to the rank constraint ($r$). (b) corresponds to the damping factor ($z$). (c) corresponds to the rank constraint ($r_k$).}

Fig. \ref{fig:snr_rank_r_curved,snr_dampingFactor_curved,snr_rank_r_k_curved} displays the influence of each parameter with curved data. Fig. \ref{fig:snr_rank_r_curved} corresponds to the SNRs as a function of rank ($r$) when we set the parameters $z$ and $r_k$, respectively, at $2$ and $3$. From this result, it is evident that smaller values of $r$ cannot provide satisfactory results. The simultaneous denoising and reconstruction performance can be improved for relatively larger values of $r$. With data containing curved events or complex structures, $r$ needs to be approximately greater than the number of dip components.  
From Fig. \ref{fig:snr_dampingFactor_curved}, which displays the reconstruction quality for the values of ${z}$, we find that ${z}=3$ corresponds to the best value for this synthetic data sample \wen{(synthetic data containing linear events and missing 80\% of traces) as we have mentioned above}. The weight of the rank ($r_k$) is shown in Fig. \ref{fig:snr_rank_r_k_curved}. As can be seen, for $r_k \in [1,5]$, the proposed \wen{MRC} approach can obtain satisfactory results. However, we adopted $r_k=(2,2,2,2)$ for this example because of the best quality of the result. Based on the results plotted in Figs. \ref{fig:snr_rank_r_curved}, \ref{fig:snr_dampingFactor_curved} and \ref{fig:snr_rank_r_k_curved}, we have chosen $r=14$, $z=3$ and \dlo{$r_k=2$}\wen{$r_k=(2,2,2,2)$} for the restoration of the useful signal containing curved events. 
These analyses conducted on synthetics data are also verified for real data. \wen{We have restored the useful seismic signal from synthetic data containing curved events and the 5D field seismic data of this paper via the HOOI method with \dlo{$r_k = 1$}\wen{$r_k =(2,2,2,2)$} because of the best quality of the results. We can understand that the tensor rank constraint $rank_{t}$ requires a too small value of $r_k$ when the data to be reconstructed include curved events and/or complex structures. Thus, the lower value of rank ($r_k=(2,2,2,2)$) can be justified by the tensor rank constraint ($rank_{t}$) that our MRC method uses. The relatively smaller values of $r_k$ should also be selected when applying the MRC method for real seismic with complex structures. In contrast, larger values of $r_k$ need to be selected when the data include linear events.} In all cases, the parameter $r_k$ must be a positive integer and $\in [1,10]$.

\inputdir{./}
\multiplot{4}{snr_rank_r_curved,snr_dampingFactor_curved,snr_rank_r_k_curved}{width=0.3\textwidth}{Influence of each parameter used in the proposed MRC method for 5-D synthetic data having curved events. (a) corresponds to the rank constraint (r). (b) denotes the damping factor (z). (c) designates the rank constraint ($ r_k $).}

To solve the mixed rank-constrained model based on the proposed MRC algorithm, we need to select the rank constraints accurately. The valid combination of parameters aids in obtaining better recovery performance. \wen{In the current framework, the parameterization of the proposed MRC approach is empirical.}

\section{Conclusions}
By taking the advantages of the matrix and tensor rank constraints, we introduce a novel mixed rank-constrained (MRC) model for simultaneous denoising and reconstruction of 5-D seismic data. The MRC framework is proposed for solving the novel rank-constrained model effectively. As shown from the detailed analysis, the proposed MRC algorithm solves the multidimensional seismic data interpolation problem with better performance. The recovered data obtained by the proposed MRC method are smoother and more reliable. Compared with the HOOI and the DRR methods, the improvement through the proposed MRC algorithm is confirmed to be highly competitive with 5-D synthetic and real field seismic data.

\bibliographystyle{seg}
\bibliography{mrc}

### 2021-05-22 mrc5d/matfun/hyper.m

@@ -1,0 +1,94 @@
+function hyper(original,noisy,obs,HOOI,drr,mrc)
+% Author      : Oboue and Chen 2021
+%               Zhejiang University
+% 
+% Date        : May, 2021
+% Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
+%    
+%  Copyright (C) 2021 Zhejiang University
+%  Copyright (C) Oboue et Chen 2021
+%  This program is free software; you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published by
+%  the Free Software Foundation; either version 2 of the License, or
+%  (at your option) any later version.
+%  
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%  
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, write to the Free Software
+%  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  
+
+%% load data
+load yc_hyper5d.mat
+d=hyper5d;d=d/max(max(max(max(max(d)))));
+[nt,nhx,nhy,nx,ny]=size(d);
+dt=0.004;
+
+%% simultaneous denoising and reconstruction
+randn('state',201314);
+var=0.1;
+dn=d+var*randn(size(d));
+%save d0.mat d0
+
+%% decimate
+[nt,nhx,nhy,nx,ny]=size(d);
+ratio=0.2;
+mask=yc_genmask(reshape(d,nt,nhx*nhy*nx*ny),ratio,'c',201415);
+mask=reshape(mask,nt,nhx,nhy,nx,ny);
+d0=dn.*mask;
+%save d0.mat d0
+
+%% HOOI 
+flow=5;fhigh=100;dt=0.004;Niter=15;mode=1;verb=1;iflb=1;
+a=(Niter-(1:Niter))/(Niter-1); %linearly decreasing
+rk=[1,1,1,1];
+
[…]

### 2021-05-22 mrc5d/matfun/mrc5d_lb_recon_synth.m

@@ -1,0 +1,373 @@
+function [ D1 ] = mrc5d_lb_recon_synth(D,MASK,flow,fhigh,dt,K,NN,N,Niter,eps,verb,mode,iflb,a)
+%  MRC5D: Mixed rank-constrained model (MRC) for simultaneous denoising and reconstruction of 5-D seismic data
+%          with Lanczos bidiagonalization
+%
+%  IN   D:   	intput 5D data
+%       MASK:   sampling mask (consistent with the POCS based approaches)
+%       flow:   processing frequency range (lower)
+%       fhigh:  processing frequency range (higher)
+%       dt:     temporal sampling interval
+%       K:      number of singular value to be preserved in the matrix
+%       NN:     damping factor
+%       N:      number of singular value to be preserved in the tensor
+%       Niter:  number of maximum iteration
+%       eps:    tolerence (||S(n)-S(n-1)||_F<eps*S(n))
+%       verb:   verbosity flag (default: 0)
+%       mode:   mode=1: denoising and reconstruction
+%               mode=0: reconstruction only
+%       iflb:   default 0;
+%               1: with LB, MGS orthogonalized
+%               0: traditional
+%       a:      scalar
+%
+%  OUT  D1:  	output data
+%
+%  Copyright (C) 2015 The University of Texas at Austin
+%  Copyright (C) 2015 Yangkang Chen
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
[…]

### 2021-06-30 passive/paper.tex
2021年 5月13日 星期四 10时32分58秒 CDT
Wed Jun 30 14:45:32 CDT 2021

@@
 
-\title{A compact program for 3D passive seismic \\
-source-location imaging}
+\title{A compact program for 3D passive seismic source-location imaging}
 
-\author{Yangkang Chen\footnotemark[1], Omar M. Saad\footnotemark[1]\footnotemark[2], Min Bai\footnotemark[3],  Xingye Liu\footnotemark[4], Sergey Fomel\footnotemark[5] }
+\author{Yangkang Chen\footnotemark[1], Omar M. Saad\footnotemark[2]\footnotemark[3], Min Bai\footnotemark[4],  Xingye Liu\footnotemark[5], Sergey Fomel\footnotemark[1] }
 %\author{Authors}
@@
 \address{
-\footnotemark[1]
-School of Earth Sciences\\
-Zhejiang University\\
-Hangzhou, Zhejiang Province, China, 310027\\
-chenyk2016@gmail.com\\
+\footnotemark[1]Bureau of Economic Geology \\
+John A. and Katherine G. Jackson School of Geosciences \\
+The University of Texas at Austin \\
+University Station, Box X \\
+Austin, TX 78713-8924 \\
+sergey.fomel@beg.utexas.edu\\
+Corresponding Author: Yangkang Chen (chenyk2016@gmail.com) 
 %yangkang.chen@zju.edu.cn \\
@@
 engomar91@ gmail.com\\
-\footnotemark[3] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
+\footnotemark[3]
+School of Earth Sciences\\
+Zhejiang University\\
+Hangzhou, Zhejiang Province, China, 310027\\
+chenyk2016@gmail.com\\
+\footnotemark[4] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
 Yangtze University\\
@@
 Wuhan, China, 430100 \\
-\footnotemark[4]
+\footnotemark[5]
 College of Geology and Environment\\
@@
 lwxwyh506673@126.com\\
-\footnotemark[5]Bureau of Economic Geology \\
-John A. and Katherine G. Jackson School of Geosciences \\
-The University of Texas at Austin \\
-University Station, Box X \\
-Austin, TX 78713-8924 \\
-sergey.fomel@beg.utexas.edu\\
-Corresponding Author: Yangkang Chen (chenyk2016@gmail.com) 
 }
@@
 All datasets and source codes associated with this research are hosted via the Madagascar platform (www.ahay.org) in the form of reproducible research \cite[]{mada2013}.
+The compact passive imaging package can be found at \\
+$https://github.com/chenyk1990/passive\_imaging$.
 
@@
 
-\inputdir{mod3d_geo}
+\inputdir{mod3d}
 \plot{data}{width=0.6\textwidth}{Recorded passive seismic data in the synthetic example.}
@@
 
-\inputdir{field3d_geo}
-%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
-\multiplot{4}{rsf_real,sov,f-location-tr,f-location1}{width=0.45\textwidth}{Field data example.
+%\inputdir{field3d_geo}
+%%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
+%\multiplot{4}{rsf_real,sov,f-location-tr,f-location1}{width=0.45\textwidth}{Field data example.
 (a) Recorded microseismic data.
@@
 (d) 3D source location image using the proposed method.}}
-
-\inputdir{mod3d_geo_ng}
-\multiplot{4}{data_mask0_ng2,data_mask0_ng6,data_mask0_ng8,data_mask0_ng10}{width=0.45\textwidth}{The first group of recorded data when $N_g=2,6,8,10$, respectively. }
-
-\multiplot{4}{location1-ng2,location1-ng6,location1-ng8,location1-ng10}{width=0.45\textwidth}{The images of the first source location when $N_g=2,6,8,10$, respectively. }
-
-\inputdir{mod3d_geo_noise}
-\multiplot{4}{data-2,data-4,data-6,data-8}{width=0.45\textwidth}{Recorded data when noise variation $\sigma^2=0.01,0.5,10,50$, respectively.
+%
+%\inputdir{mod3d_geo_ng}
+%\multiplot{4}{data_mask0_ng2,data_mask0_ng6,data_mask0_ng8,data_mask0_ng10}{width=0.45\textwidth}{The first group of recorded data when $N_g=2,6,8,10$, respectively. }
+%
+%\multiplot{4}{location1-ng2,location1-ng6,location1-ng8,location1-ng10}{width=0.45\textwidth}{The images of the first source location when $N_g=2,6,8,10$, respectively. }
+%
+%\inputdir{mod3d_geo_noise}
+%\multiplot{4}{data-2,data-4,data-6,data-8}{width=0.45\textwidth}{Recorded data when noise variation $\sigma^2=0.01,0.5,10,50$, respectively.
 The corresponding S/Ns of (a)-(d) are -4.97 dB, -21.96 dB, -34.97 dB, and -41.96 dB, respectively.
 }
-
-\multiplot{4}{location1-noise2,location1-noise4,location1-noise6,location1-noise8}{width=0.45\textwidth}{The images of the first source location when noise variation $\sigma^2=0.01,0.5,10,50$, respectively.
+%
+%\multiplot{4}{location1-noise2,location1-noise4,location1-noise6,location1-noise8}{width=0.45\textwidth}{The images of the first source location when noise variation $\sigma^2=0.01,0.5,10,50$, respectively.
 }
-
-%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr1.rsf 
-%   0:        -1.957
-%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr2.rsf 
-%   0:        -4.967
-%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr3.rsf 
-%   0:        -14.98
-%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr4.rsf 
-%   0:        -21.96
-%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr5.rsf 
-%   0:        -31.96
-%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr6.rsf 
-%   0:        -34.97
-%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr7.rsf 
-%   0:        -37.98
-%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr8.rsf 
-%   0:        -41.96
 %
-
-\inputdir{mod3d_geo_density}
-\multiplot{4}{data-d6,data-d8,data-d9,data-d10}{width=0.45\textwidth}{The observed data with 121, 81, 16, and 8 recorded traces, respectively.  }
-
-\multiplot{4}{location1-density6,location1-density8,location1-density9,location1-density10}{width=0.45\textwidth}{The images of the first source location when there are 121, 81, 16, and 8 recorded traces, respectively.
+%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr1.rsf 
+%%   0:        -1.957
+%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr2.rsf 
+%%   0:        -4.967
+%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr3.rsf 
+%%   0:        -14.98
+%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr4.rsf 
+%%   0:        -21.96
+%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr5.rsf 
+%%   0:        -31.96
+%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr6.rsf 
+%%   0:        -34.97
+%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr7.rsf 
+%%   0:        -37.98
+%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr8.rsf 
+%%   0:        -41.96
+%%  
+%
+%\inputdir{mod3d_geo_density}
+%\multiplot{4}{data-d6,data-d8,data-d9,data-d10}{width=0.45\textwidth}{The observed data with 121, 81, 16, and 8 recorded traces, respectively.  }
+%
+%\multiplot{4}{location1-density6,location1-density8,location1-density9,location1-density10}{width=0.45\textwidth}{The images of the first source location when there are 121, 81, 16, and 8 recorded traces, respectively.
 }
-
+% 
 \bibliographystyle{seg}
 \bibliography{micro}
-
-%\clearpage
-%Yangkang Chen\footnotemark[1], Omar M. Saad\footnotemark[1]\footnotemark[2], Min Bai\footnotemark[3],  Xingye Liu\footnotemark[4], Sergey Fomel\footnotemark[5]  \\
-%\footnotemark[1]
-%School of Earth Sciences\\
-%Zhejiang University\\
-%Hangzhou, Zhejiang Province, China, 310027\\
-%chenyk2016@gmail.com\\
-%%yangkang.chen@zju.edu.cn \\
-%\footnotemark[2]
-%ENSN Lab \\
-%Seismology Department \\
-%National Research Institute of Astronomy and Geophysics (NRIAG)\\
-%Helwan 11731, Egypt\\
-%engomar91@ gmail.com\\
-%\footnotemark[3] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
-%Yangtze University\\
-%Daxue Road No.111\\
-%Caidian District\\
-%Wuhan, China, 430100 \\
-%\footnotemark[4]
-%College of Geology and Environment\\
-%Xi’an University of Science and Technology\\
-%Xi’an, Shaanxi Province, China, 710054 \\
-%lwxwyh506673@126.com\\
-%\footnotemark[5]Bureau of Economic Geology \\
-%John A. and Katherine G. Jackson School of Geosciences \\
-%The University of Texas at Austin \\
-%University Station, Box X \\
-%Austin, TX 78713-8924 \\
-%sergey.fomel@beg.utexas.edu\\
-%
-
-%\AtEndDocument{}
-
-%\newpage
-%\listoffigures
-
-%\begin{figure}[htb!]
-%	\centering
-%	\subfloat[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
-%	\caption{Caption.}
-%	\label{fig:fig}
-%\end{figure}
-
-%\begin{figure}[htb!]
-%	\centering
-%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
-%    \label{fig:fig1}}\\
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
-%    \label{fig:fig2}}\\
-%	\caption{(a) Caption a. (b) Caption b.}
-%	\label{fig:fig1,fig2}
-%\end{figure}
-
-%\begin{figure*}[ht!]
-%	\centering
-%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
-%    \label{fig:fig1}}\\
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
-%    \label{fig:fig2}}\\
-%	\caption{(a) Caption a. (b) Caption b.}
-%	\label{fig:fig1,fig2}
-%\end{figure*}
-
-%\begin{table}[h]
-%\caption{Table caption}
-%\begin{center}
-%     \begin{tabular}{|c|c|c|c|c|c|} 
-%	  \hline Column1 (unit)  & Column2 (unit) & Column3 (unit) \\ 
-%	  \hline 1 & 2  & 3 \\
-%       \hline
-%    \end{tabular} 
-%\end{center}
-%\label{tbl:table1}
-%\end{table}

### 2021-06-30 nonMada/dealise_rank/anti_Hankel_2.m

@@ -1,0 +1,33 @@
+function fa=anti_Hankel_2(M,Nx,Ny,Lx,Ly,n,m)
+a=Nx-Ny;
+b=Lx-Ly;
+M_new=zeros(Ny*Ly,Nx*Lx+(Ly-1)*Nx);
+temp=zeros(Ny,Nx,m);
+JS=ones(Ly,Lx);
+JS_new=zeros(Ly,Lx+Ly-1);
+for i=1:Ly
+    M_new(1+(i-1)*Ny:i*Ny,1+(i-1)*Nx:Nx*Lx+(i-1)*Nx)=M(1+(i-1)*Ny:i*Ny,:);
+    JS_new(i,i:Lx+i-1)=JS(i,:);
+end
+JS_1=sum(JS_new);
+for i=1:Lx+Ly-1
+    sump=zeros(Ny,Nx);
+    for j=1:Ly
+    sump=sump+M_new(1+(j-1)*Ny:j*Ny,1+(i-1)*Nx:i*Nx);
+    end
+    temp(:,:,i)=sump/JS_1(1,i);
+end
+
+N_new=zeros(Ny,Nx+Ny-1);
+JS=ones(Ny,Nx);
+JS_new=zeros(Ny,Nx+Ny-1);
+for i=1:m
+    w=temp(:,:,i);
+    for j=1:Ny
+      JS_new(j,j:Nx+j-1)=JS(j,:); 
+      N_new(j,j:Nx+j-1)=w(j,:);
+    end
+    fa(i,:)=sum(N_new)./sum(JS_new);
+end
+
+end

### 2021-06-30 nonMada/dealise_rank/h_hankel.m

@@ -1,0 +1,22 @@
+function A=h_hankel(fa,Nx,Lx)
+%Construct the hankel matrix
+%A=hankel(fa,50,40), A=hankel(fa,51,38)
+if nargin==2
+    Lx=1;
+end
+[n,m]=size(fa);
+Ny=m+1-Nx;
+Ly=n+1-Lx;
+for i=1:n
+    for j=1:Ny     
+        H(i,(j-1)*Nx+1:j*Nx)=fa(i,j:Nx+j-1);%Hankel matrix
+    end
+end
+for k=0:(Ly-1)
+    for i=1:Lx
+        for j=1:Ny
+            A((j+k*Ny),(i-1)*Nx+1:i*Nx)=H(i+k,(j-1)*Nx+1:j*Nx);
+        end
+    end
+end
+end

### 2021-06-30 passive/mod3d/mod3d.c

@@ -1,0 +1,1299 @@
+/* 3D acoustic wavefield modeling using the pseudo-spectral method  */
+/*
+  Copyright (C) 2020 XXX University
+  written by Authors (need to be updated because of blind review process)
+  
+  This program is free software; you can redistribute it and/or modify
+  it under the terms of the GNU General Public License as published by
+  the Free Software Foundation; either version 2 of the License, or
+  (at your option) any later version.
+  
+  This program is distributed in the hope that it will be useful,
+  but WITHOUT ANY WARRANTY; without even the implied warranty of
+  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+  GNU General Public License for more details.
+  
+  You should have received a copy of the GNU General Public License
+  along with this program; if not, write to the Free Software
+  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  USA
+*/
+
+#include <rsf.h>
+
+/** Part I: Ricker wavelet ********/
+float Ricker(float t, float f0, float t0, float A) 
+/*< ricker wavelet:
+ * f0: peak frequency
+ * t0: time lag
+ * A: amplitude
+ * ************************>*/
+{
+        float x=pow(SF_PI*f0*(t-t0),2);
+        return -A*exp(-x)*(1-2*x);
+}
+
+static kiss_fft_cpx *shape;
+
+void ricker_init(int nfft   /* time samples */, 
+		 float freq /* frequency */,
+		 int order  /* derivative order */)
+/*< initialize >*/
+{
+    int iw, nw;
+    float dw, w;
+    kiss_fft_cpx cw;
+
+    /* determine frequency sampling (for real to complex FFT) */
+    nw = nfft/2+1;
[…]

### 2021-07-01 passive/field3d/BIN.m
Wed Jun 30 22:35:06 CDT 2021

@@ -1,0 +1,58 @@
+function BIN(datain,x0,y0,dataout,nt,ntraces)
+% Author      : Yangkang Chen
+% Date        : Mar 2021
+% 
+% Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
+%    
+%  Copyright (C) 2021 Yangkang Chen
+%  
+%  This program is free software; you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published by
+%  the Free Software Foundation; either version 2 of the License, or
+%  (at your option) any later version.
+%  
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%  
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, write to the Free Software
+%  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  
+% 
+%nt=1001
+%ntraces=918
+
+x00=zeros(ntraces,1);
+y00=zeros(ntraces,1);
+data=zeros(nt,ntraces);
+rsf_read(x00,x0);
+rsf_read(y00,y0);
+rsf_read(data,datain); 
+
+x0=x00*0.3048;
+y0=y00*0.3048;
+
+%% binning (put a 2D data into a 3D volume)
+% about 100 receivers per arm
+nx=201;
+ny=201;
+ox=0;
+oy=0;
+mx=ox+200*24;
+my=oy+200*24;
+dt=0.002;
+[ dout,xout,yout,mask ] = yc_bin3d(data,x0,y0,nx,ny,ox,oy,mx,my);
+
+
+%% from Matlab to Madagascar
+dout=reshape(dout,nt,nx*ny);
+rsf_create(dataout,size(dout)');
+rsf_write(dout,dataout);
+
+
+
+
+
+
+

### 2021-07-01 passive/paper.tex
Wed Jun 30 22:35:06 CDT 2021
Thu Jul  1 11:14:43 CDT 2021

@@
 
-%\inputdir{field3d_geo}
-%%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
-%\multiplot{4}{rsf_real,sov,f-location-tr,f-location1}{width=0.45\textwidth}{Field data example.
+\inputdir{field3d}
+%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
+\multiplot{4}{rsf_real,sov,f-location-tr,f-location1}{width=0.45\textwidth}{Field data example.
 (a) Recorded microseismic data.
@@
 (d) 3D source location image using the proposed method.}}
-%
-%\inputdir{mod3d_geo_ng}
-%\multiplot{4}{data_mask0_ng2,data_mask0_ng6,data_mask0_ng8,data_mask0_ng10}{width=0.45\textwidth}{The first group of recorded data when $N_g=2,6,8,10$, respectively. }
-%
-%\multiplot{4}{location1-ng2,location1-ng6,location1-ng8,location1-ng10}{width=0.45\textwidth}{The images of the first source location when $N_g=2,6,8,10$, respectively. }
-%
-%\inputdir{mod3d_geo_noise}
-%\multiplot{4}{data-2,data-4,data-6,data-8}{width=0.45\textwidth}{Recorded data when noise variation $\sigma^2=0.01,0.5,10,50$, respectively.
+
+\inputdir{mod3d_ng}
+\multiplot{4}{data_mask0_ng2,data_mask0_ng6,data_mask0_ng8,data_mask0_ng10}{width=0.45\textwidth}{The first group of recorded data when $N_g=2,6,8,10$, respectively. }
+
+\multiplot{4}{location1-ng2,location1-ng6,location1-ng8,location1-ng10}{width=0.45\textwidth}{The images of the first source location when $N_g=2,6,8,10$, respectively. }
+
+\inputdir{mod3d_noise}
+\multiplot{4}{data-2,data-4,data-6,data-8}{width=0.45\textwidth}{Recorded data when noise variation $\sigma^2=0.01,0.5,10,50$, respectively.
 The corresponding S/Ns of (a)-(d) are -4.97 dB, -21.96 dB, -34.97 dB, and -41.96 dB, respectively.
 }
-%
-%\multiplot{4}{location1-noise2,location1-noise4,location1-noise6,location1-noise8}{width=0.45\textwidth}{The images of the first source location when noise variation $\sigma^2=0.01,0.5,10,50$, respectively.
+
+\multiplot{4}{location1-noise2,location1-noise4,location1-noise6,location1-noise8}{width=0.45\textwidth}{The images of the first source location when noise variation $\sigma^2=0.01,0.5,10,50$, respectively.
 }
@@
 %
-%\inputdir{mod3d_geo_density}
-%\multiplot{4}{data-d6,data-d8,data-d9,data-d10}{width=0.45\textwidth}{The observed data with 121, 81, 16, and 8 recorded traces, respectively.  }
-%
-%\multiplot{4}{location1-density6,location1-density8,location1-density9,location1-density10}{width=0.45\textwidth}{The images of the first source location when there are 121, 81, 16, and 8 recorded traces, respectively.
+\inputdir{mod3d_density}
+\multiplot{4}{data-d6,data-d8,data-d9,data-d10}{width=0.45\textwidth}{The observed data with 121, 81, 16, and 8 recorded traces, respectively.  }
+
+\multiplot{4}{location1-density6,location1-density8,location1-density9,location1-density10}{width=0.45\textwidth}{The images of the first source location when there are 121, 81, 16, and 8 recorded traces, respectively.
 }

### 2021-08-09 elrme5d/paper.tex
Mon Aug  9 16:40:12 CDT 2021

@@
 \wen{To see its influence \old{in}\new{on} the proposed algorithm, we set ${n}=3$, ${q}=3$, ${\beta_0}=0.971$ and ${\beta_1}=0.977$, $\delta_0 = 3.75$ and $\delta_1 = 3.25$, ${b_0}=25$ and ${b_1}=23$\old{ by trial}, and we vary the value of $\varphi_i$ from $1$ to $5$ when estimating the low-rank signal matrix of the first synthetic data example.
-Figure \ref{fig:WindowsSizeφi} shows the SNRs diagram with different values of ${\varphi_i}$.
+Figure \ref{fig:WindowsSizephi} shows the SNRs diagram with different values of ${\varphi_i}$.
 We find that all values of ${\varphi_i}$ selected above $1$ weaken the \new{performance of the }proposed operator}\dlo{This parameter}\old{$\varphi_i$ produces some signal damages of data when it is greater than $1$}.
@@
 \inputdir{./}
-\multiplot{6}{rankn,dampingFactorq,WindowsSizeφi,RationalTransfertFunctionCoefficientbeta0and1,CoolingfactorsSigma0and1,PenaltyConvexityParametersb0b1}{width=0.3\textwidth}{Weight of each parameter.
+\multiplot{6}{rankn,dampingFactorq,WindowsSizephi,RationalTransfertFunctionCoefficientbeta0and1,CoolingfactorsSigma0and1,PenaltyConvexityParametersb0b1}{width=0.3\textwidth}{Weight of each parameter.
 (a) rank constraint (n).

### 2021-10-06 dlleak/paper.tex
Wed Oct  6 14:47:34 CDT 2021

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}

\title{Retrieving the leaked signals from noise using a fast dictionary learning method}
\author{Wei Chen\footnotemark[1]\footnotemark[2], Omar M. Saad\footnotemark[3], Yapo Abol{\'e} Serge Innocent Obou{\'e}\footnotemark[4], Liuqing Yang\footnotemark[5], and Yangkang Chen\footnotemark[6]}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\address{
\footnotemark[1] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
Yangtze University\\
Daxue Road No.111\\
Caidian District\\
Wuhan, China, 430100 \\
\footnotemark[2] Hubei Cooperative Innovation Center of Unconventional Oil and Gas\\
Daxue Road No.111\\
Caidian District\\
Wuhan, China, 430100 \\
\footnotemark[3]
Seismology Department\\
National Research Institute of Astronomy and Geophysics (NRIAG)\\
Helwan 11731, Egypt \\
\footnotemark[4]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
yangkang.chen@zju.edu.cn \\
\footnotemark[5]State Key Laboratory of Petroleum Resources and Prospecting \\
China University of Petroleum \\
Fuxue Road 18th\\
Beijing, China, 102200 \\
\footnotemark[6]Bureau of Economic Geology\\
The University of Texas at Austin\\
University Station, Box X\\
Austin, Texas 78713-8924\\
chenyk2016@gmail.com \\
}

\lefthead{Chen et al.}
\righthead{Retrieving leaked signals}

\begin{abstract}
Most traditional seismic denoising algorithms will cause damages to useful signals, which are visible from the removed noise profiles and are known as signal leakage. The local signal-and-noise orthogonalization method is an effective method for retrieving the leaked signals from the removed noise. Retrieving leaked signals while rejecting the noise is compromised by the smoothing radius parameter in the local orthogonalization method. It is not convenient to adjust the smoothing radius because it is a global parameter while the seismic data is highly variable locally. To retrieve the leaked signals adaptively, we propose a new dictionary learning method. Because of the patch-based nature of the dictionary learning method, it can adapt to the local feature of seismic data. We train a dictionary of atoms that represent the features of the useful signals from the initially denoised data. Based on the learned features, we retrieve the weak leaked signals from the noise via a sparse coding step. Considering the large computational cost when training a dictionary from high-dimensional seismic data, we leverage a fast dictionary updating algorithm, where the singular value decomposition (SVD) is replaced via the algebraic mean to update the dictionary atom. We test the performance of the proposed method on several synthetic and field data examples, and compare it with that from the state-of-the-art local orthogonalization method. 
\end{abstract}

\section{Introduction}
Noise suppression of seismic data plays an important role in seismic exploration \cite[]{abma1995lateral,liuwei2017jge,huang2018damped,omar2020geo1}. In the past decades, numerous methods have been proposed to improve the signal-to-noise ratio (S/N) of seismic data \cite[]{fomel2013seismic,forghani2013effective,han2015microseismic,gomez2016simple,chenwei2018,baimin2018cg,liuwei2019ewt,chenwei2020}.

The decomposition-based algorithm assumes that the main components of the decomposed seismic data denote the signal while the rest are the noise. Thus, it first decomposes the noisy seismic data into different components through a certain method. Then, the noise components are suppressed by \dlo{shrinkage threshold, truncation, or damping}\wen{shrinking threshold, truncating, or damping} after decomposition. Obviously, the key to decomposition-based methods is whether the decomposition method can effectively decompose the effective signal and noise in the seismic data. The most representative decomposition methods include empirical mode decomposition (EMD) \cite[]{huang1998empirical}, singular value decomposition (SVD) \cite[]{bekara2007local}, and regularized non-stationary decomposition \cite[]{fomel2013seismic,lv2019noise}. Amongst, the denoised method based on the SVD algorithm is also called the rank-reduction-based method. It assumes that the ideal noise-free seismic data is a low-rank matrix, and the random noise will increase the rank of the matrix. Therefore, the random noise attenuation can be regarded as an approximation problem of rank reduction. However, such an assumption is not always true, i.e., the effective signal may exist in the low-rank components, which will cause the damage of the effective signal.

Different from the traditional sparse transform method with analytic basis functions, \wen{dictionary learning (DL) methods adaptively learn the basis functions to best represent the signal features, but at the expense of taking significantly longer computing time \cite[]{aksvd2008,kaplan2009sparse,chen2016double,wujuan2018cg1}}. Instead, it can adaptively obtain a better sparse representation effect according to the characteristics of field seismic data. Therefore, such a method has attracted more and more attention. \cite{kaplan2009sparse} propose a data-driven sparse coding method to adaptively obtain the basis function of sparse representation of seismic data. \cite{beckouche2014simultaneous} divide the seismic data into several small patches, and then use the data in these small patches to train the dictionary, and successfully achieve the signal-and-noise separation of noise corrupted seismic data. By combining the advantages of DL and the traditional sparse transformation method, \cite{chen2016double} propose a double-sparsity dictionary method. It can better represent the signal with specific characteristics in seismic data, and achieve better and more accurate signal-and-noise separation of seismic data. The KSVD-based dictionary learning method obtains the good sparse representation and updated dictionary by iterating and alternately executing the sparse coding and dictionary updating parts \cite[]{abma1995lateral}. The KSVD method obtains successful performance in the sparse-representation-based algorithms, which can not only guarantee the sparse representation to the greatest extent, but also improve the fidelity of the denoising method for seismic data processing \cite[]{sahoo2013dictionary}. However, such a method involves too many SVD operations, which consumes a lot of computational costs. It is not suitable for practical applications in field data, let alone 3-D or even 5-D seismic data.

In order to improve the computation efficiency of the K-SVD algorithm, \cite{yangkang2020sgk} and \cite{wang2020fast} propose a sequential generalized K-means method (SGK). While maintaining the overall denoising performance, the SGK method greatly improves the computational efficiency. Instead of minimizing the objective function by using the SVD algorithm, SGK exploits the least-squares method to solve the objective function. In the SGK algorithm, the low-rank approximation of the kth dictionary atom by the SVD operation is replaced by a simple summation of training samples. Moreover, based on the special structure of coefficient vectors, \cite{yangkang2020sgk} introduces an accelerated algorithm in the sparse coding procedure of the SGK method. Instead of using orthogonal matching pursuit (OMP) to iteratively get the optimal representation of the target data sample, the sparse coding is implemented for only one time, which greatly enhances the calculation efficiency.

Most traditional methods suffer from the inevitable signal leakage when applied to complex seismic data. The signal leakage refers to those useful signals in the removed noise that appear as spatially coherent.  The signal leakage is caused by either inappropriate parameterization or inappropriate denoising assumptions \cite[]{yangkang2015ortho}. The existence of the signal leakage significantly decreases the quality of the \dlo{denoise}\wen{denoised} seismic data regarding the amplitude fidelity. \cite{yangkang2015ortho} propose an effective way known as the local signal-and-noise orthogonalization method to mitigate the signal leakage in an arbitrary denoising framework. The local orthogonalization method assumes the denoised signal and removed noise to be locally orthogonal to each other and thus compensate for the amplitude loss via solving an inverse problem that is related to the well-known Gram–Schmidt orthogonalization. The local orthogonalization method has been widely used in the seismic community for a variety of different applications, including random noise attenuation \cite[]{yangkang2015ortho}, ground roll noise suppression \cite[]{yangkang2015orthogroll}, multiples elimination \cite[]{zhangdong2020ortho}, elastic wave mode separation \cite[]{sripanich2017elastic}, elastic full-waveform inversion \cite[]{jeong2019enhanced}, etc. However, the local orthogonalization method requires the selection of the smoothing radius parameter, which balances the retrieval of leaked signals and the level of the remaining noise. In addition, due to the inversion nature of the local orthogonalization method, it is highly sensitive to abnormally high amplitude of the erratic noise existing in the data.

In this paper, we propose to substitute the local orthogonalization method with a new method based on dictionary learning. The new dictionary learning method can obtain equivalent signal retrieval performance but with an easier control on handling small-scale leaked signals due to the patch-based processing. First, we learn the dictionary atoms from the initially denoised data. Then, we code the initial noise section/cube via the learned atoms, where the sparse coefficients corresponding to the leaked signals are high. Next, we apply a percentile thresholding scheme to the sparse coefficients to select those coefficients with distinctly large amplitude. Finally, we reconstruct the extracted leaked signals via the dictionary atoms and the thresholded sparse coefficients. We show that the percentile thresholding plays an important role in distinguishing between noise and leaked signals. Considering the heavy computational cost of the traditional SVD operation, we substitute it with a more efficient SVD-free dictionary learning method. We use different synthetic, 2D, and 3D field data examples to demonstrate the effectiveness of the proposed method, and more importantly, its advantage and flexibility compared with the state-of-the-art local orthogonalization method.

\section{Theory}
\subsection{Retrieving the signal leakage}
Given an arbitrary denoising operator $\mathbf{P}$, the estimation of signal and noise can be expressed as
\begin{align}
\label{eq:sn1}
\mathbf{s} = \mathbf{P}(\mathbf{d}), \\
\label{eq:sn2}
\mathbf{n} = \mathbf{d} - \mathbf{P}(\mathbf{d}),
\end{align}
where $\mathbf{d}$ denotes the input noisy data. However, the estimated signal and noise are not equal to the true signal $\mathbf{s}_{true}$ and true noise $\mathbf{n}_{true}$:
\begin{align}
\label{eq:sn1}
\mathbf{s} \ne \mathbf{s}_{true}, \\
\label{eq:sn2}
\mathbf{n} \ne \mathbf{n}_{true}.
\end{align}
The inaccuracy of the estimated signal is reflected as the signal leakage (spatially coherent signals) in the estimated/removed noise $\mathbf{n}$ and the remaining noise in the estimated signal $\mathbf{s}$.

The local orthogonalization method can retrieve the leaked signals by
\begin{align}
\label{eq:sn1}
\hat{\mathbf{s}} = \mathbf{s} + \mathbf{w} \circ \mathbf{s}, \\
\label{eq:sn2}
\hat{\mathbf{n}} = \mathbf{n} - \mathbf{w} \circ \mathbf{s}, 
\end{align}
where $\hat{\mathbf{s}}$ and $\hat{\mathbf{n}}$ are the compensated signal and noise after local orthogonalization. $\mathbf{w} \circ \mathbf{s}$ indicates an element-wise product between the weight vector/matrix $\mathbf{w}$ and the initially estimated signal $\mathbf{s}$.

The local orthogonalization weight $\mathbf{w}$ is solved via iterative inversion and smoothness regularized shaping regularization \cite[]{yangkang2015ortho}. In this paper, we propose a completely different way to retrieve the leaked signals based on dictionary learning\dlo{.}\wen{:} 
\begin{align}
\label{eq:sn1}
\hat{\mathbf{s}} = \mathbf{s} + \mathbf{F}\tilde{\mathbf{M}}, \\
\label{eq:sn2}
\hat{\mathbf{n}} = \mathbf{n} - \mathbf{F}\tilde{\mathbf{M}}, 
\end{align}
where $\mathbf{F}$ denotes a sparse dictionary and $\tilde{\mathbf{M}}$ denotes the optimal representation of the leaked signals (in the form of sparse coefficients) based on the sparse dictionary $\mathbf{F}$.

The DL method generally achieves the sparse representation of the complex seismic data by alternatively implementing the sparse coding and dictionary update steps. Here, to retrieve the leaked signals, we need to implement the conventional dictionary learning in two steps: (1) first, we obtain the dictionary atoms in $\mathbf{F}$ that follows the structural patterns of the useful signals by learning from the initially denoised data $\mathbf{s}$; (2) second, we use the learned dictionary atoms as the basis functions to code the initially estimated/removed noise $\mathbf{n}$, where the leaked signals will be well represented by the structure-informed atoms as large coefficients. To alleviate the influence of the pure noise in the coefficient matrix, we need to apply a thresholding step.

\subsection{Sparse coding for retrieving leaked signals}
The initially estimated noise can be divided into $N$ patches $\textbf{n}_{i}$ with $M$ samples (M$\times$1) . Then we can represent the noise in matrix form $\textbf{D}_{n}$ (M$\times$N) with these patches, where \textbf{n}$_{i}$ denotes the data in the $i$th column. We assume the matrix $\textbf{D}_{n}$ can be represented by the multiplication of the dictionary matrix $\mathbf{F}$ and sparse coefficient $\textbf{M}$, which can expressed as:
\begin{equation}
\textbf{D}_{n}=\mathbf{F}\textbf{M}.
\end{equation}
Note that $\textbf{D}_{n}$ has the size of $M\times N$, $\mathbf{F}$ has the size of $M\times L$, and $\textbf{M}$ has the size of $L\times N$.

Thus, the target of sparse coding is to achieve the dictionary matrix $\mathbf{F}$ and its corresponding sparse coefficient matrix \textbf{M} by solving the following equation:
\wen{\begin{equation}
\label{eq:code}
\hat{\textbf{M}}=\arg\min_{\mathbf{M}}||\textbf{D}_n-\mathbf{F}\textbf{M}||^{2}_{p}, \quad\text{s.t.}  \quad \forall_j ||\textbf{m}_j||_{0}\le Q,
\end{equation}}
where \textbf{M} corresponds to the counterpart of the rearranged data \textbf{D} in the sparse domain, $\mathbf{m}_i$ denotes the $i$th column in \textbf{M}, $||\cdot||_p$ represent $\ell_{p}$ norm of the vector, and $Q$ denotes the sparsity requirement \wen{, e.g., the number of non-zero entries}. Thus, the constraint $\forall_i ||\textbf{m}_i||_{0}\le Q$ indicates that the total number of the non-zero coefficients in each column of \textbf{M} should not exceed Q. Solving inverse problem like equation \ref{eq:code} is an NP-hard problem, which cannot directly obtain the optimal result and is generally solved by the approximation pursuit method. The OMP algorithm is usually exploited to obtain a suitable solution. The pursuit-based method algorithm can be implemented as follows: (1) first, giving an atom and searching the corresponding sparse coefficient of the atoms; (2) then, calculating and decomposing the residual signal by the new given atom; (3) repeating procedure (2) until the requirement is satisfied.

\subsection{Dictionary learning via KSVD}
To obtain $\mathbf{F}$, a dictionary learning step needs to be implemented. Dictionary learning consists of two separate steps: dictionary update and sparse coding. The sparse coding process is the same as the subsection above, except for substituting the data patches $\textbf{D}_{n}$ created from the initial noise $\mathbf{n}$ with the data patches $\textbf{D}_{s}$ created from the initial signal $\mathbf{s}$. However, the pursuit-based method for sparse coding cannot achieve a satisfactory result at one time. The dictionary should be updated to obtain a good performance. The KSVD method is proposed to better approximate the data features. According to the KSVD algorithm, a matrix of rank K can be recognized as the summation of K matrics of rank 1 as follows:
\begin{equation}
\begin{split}
\mathbf{F}^{i+1}&=\arg\min||\textbf{D}_s-\mathbf{F}\textbf{M}^{i}||^{2}_{p}\\
&=\arg\min||\textbf{D}_{s}-\sum_{j=1}^{L}\textbf{f}_{j}\textbf{m}^{i}_{j}||^{2}_{p}\\
\end{split}\quad,
\end{equation}
where \textbf{f}$_{j}$ and \textbf{m}$_{j}$ are the $j$th column of dictionary matrix $\mathbf{F}$ and sparse coefficient \textbf{M}. \wen{Here, $i$ denotes $i$th iteration.}

One should fix the sparse coefficient \textbf{M} and update the dictionary $\mathbf{F}$ column by column, which can be expressed as follows:
\begin{equation}
\begin{split}
	\mathbf{F}^{i+1}		&=\arg\min||\textbf{D}_{s}-\sum_{j\neq k}^{L}\textbf{f}_{j}\textbf{m}^{i}_{j}-\textbf{f}_{j}\textbf{m}^{i}_{j}||^{2}_{p}\\
	&=\arg\min||\textbf{R}_{k}-\textbf{f}_{k}\textbf{m}^{i}_{k}||^{2}_{p}\\
\end{split}
\quad ,
\end{equation}
where \dlo{\textbf{Q}$_{k}$}\wen{\textbf{R}$_{k}$} denotes the residual between the real data $\textbf{D}_s$ and the sparse representation excluding the $k$th column. Thus, the problem is converted as solving a matrix of rank 1 to approximate \textbf{R}$_{k}$. However, the updated \textbf{m}$_{j}$ will not be sparse if \textbf{R}$_{k}=$\textbf{f}$_{k}$\textbf{m}$_{k}$ is solved directly. To avoid damaging the sparse structure of the coefficient vector \textbf{m}$_{k}$, one should discard the columns in $\textbf{R}_{k}$ where the corresponding element in \textbf{m}$_{k}$ is zero. Here we use $\textbf{R}^{new}_{k}$ and $\textbf{m}_{k}^{new}$ to represent the new residual and the new coefficient vector without non-zero element, and the objective function can be rewritten as:
\begin{equation}
J=||\textbf{R}_{k}-\textbf{f}_{k}\textbf{m}_k||^{2}=||\textbf{R}_{k}^{new}-\textbf{f}_{k}\textbf{m}^{new}_k||^{2}.
\end{equation}
After all the columns of $\mathbf{F}$ are updated, one turns to solve equation \ref{eq:code} for M. Thus, the sparse representation of data is realized when a certain number of iterations is reached. Obviously, there are many SVD operations in the dictionary update step, which is computationally expensive. To overcome such a problem, the SGK-based dictionary update algorithm is proposed.

\subsection{Dictionary learning via SGK}
The SGK method \cite[]{sahoo2013dictionary,yangkang2020sgk} is also composed of the sparse coding and dictionary update steps. 
 For the first step, there is a slight difference for the constraint compared with the conventional sparse coding. The objective function can be expressed as:
\begin{equation}
\label{eq:sgk1}
\mathbf{F}^{i+1}=\arg\min||\textbf{D}_s-\mathbf{F}\textbf{M}^{i}||^{2}_{p}, \quad\text{s.t.}  \quad \forall_{j}\textbf{m}_{j}=\textbf{e}_{\tau},
\end{equation}
where \wen{\textbf{e}$_{\tau}$ denotes an identity vector}, $\tau$ denotes the \textbf{m}$_{j}$ has all zeros except one in the $\tau$th position.

The second part, i.e., dictionary updating, is altered as well. Instead of exploiting the SVD, the SGK-based method applies the least-squares method to minimizing the objective function \ref{eq:sgk1}. According to the least-squares method, the gradient of the objective function with respect to the dictionary atoms can be expressed as follows:
\begin{equation}
\label{eq:sgk2}
\frac{\partial J}{\partial \textbf{f}_{k}}=-2(\textbf{R}_{k}^{new}-\textbf{f}_{k}\textbf{m$_{k}^{new}$})(\textbf{m$_{k}^{new}$})^T.
\end{equation}
Thus, the least square solution of the equation \ref{eq:sgk2} can be expressed as follows:
\begin{equation} 
\textbf{f}_{k}=\textbf{R}_{k}^{new}(\textbf{m$_{k}^{new}$})^T(\textbf{m$_{k}^{new}$}(\textbf{m$_{k}^{new}$})^T)^{-1}.
\end{equation}
Using the idea of KSVD-based method for reference, we can rewrite the $\textbf{R}_{k}^{new}$ as follows:
\begin{equation}
\textbf{R}_{k}^{new}=(\textbf{D}_s^{new}-\sum_{j\neq k}^{L}\textbf{f}_{j}\textbf{m$_{j}^{new}$}).
\end{equation}
Since \textbf{m$_{k}^{new}$} (with $N^{k}$ samples) contains ones for all the entries, any column vector multiplied by \textbf{m$_{k}^{new}$} is equal to the summation of all elements of the column vector such as:
\begin{equation}
\begin{split}
\textbf{m$_{k}^{new}$}(\textbf{m$_{k}^{new}$})^T= N^{k},\\
\textbf{D}_s^{new}(\textbf{m$_{k}^{new}$})^T=\sum_{j=1}^{N^{k}}\textbf{d}_{j}.
\end{split}
\end{equation}
Moreover, since $\forall_{j}\textbf{m}_{j}=\textbf{e}_{\tau}$, 
\begin{equation}
\forall_{j\neq k}\textbf{m$_{k}^{new}$}(\textbf{m$_{k}^{new}$})^T=0.
\end{equation}
Thus, we can obtain the updated dictionary atoms as follows:
\begin{equation} 
\textbf{f}_{k}=\frac{1}{N^{k}}\sum_{j=1}^{N^{k}}\textbf{d}_{j}.
\end{equation}
As shown in the derivation of SGK, we can find that the SGK algorithm avoids the time-consuming calculation process. The SVD operation has been replaced by a summation across the training samples.
\subsection{Percentile thresholding of coefficients}
After $\hat{\mathbf{M}}$ is obtained by solving equation \ref{eq:code}, one needs to apply a thresholding step to remove those trivial coefficients that are related to noise:
\begin{equation}
\label{eq:thr}
\tilde{\mathbf{M}} = \mathbf{T} (\hat{\mathbf{M}} ),
\end{equation}
where $\mathbf{T}$ denotes a percentile thresholding operator. The sparse coding model expressed in equation \ref{eq:code} constrains the coefficient matrix $\mathbf{M}$ to be sparse. The sparsity level $Q$ constrains the non-zero entries in each column vector of $\mathbf{M}$. However, due to the fact that not all atoms in the dictionary follow the signal patterns and there are still some atoms contaminated by the noise, a significant portion of the non-zero coefficients in $\mathbf{M}$ correspond to the noise. To suppress the noise, we apply the thresholding to only preserve the largest coefficients that correspond to leaked signals.  The percentile thresholding refers to preserving a certain percentage of largest coefficients rather than preserving the coefficients larger than a certain threshold value. The threshold value varies greatly for different data but the percentage is less dependent on the data, and thus is easier to choose. For example, considering the total number of samples in $\mathbf{M}$ is $L\times N$, the number of non-zero entries is $Q\times N$, then the percentage should be $p\le Q/L$. We will discuss the influence of the percentage later in the Discussion section.

\AtEndDocument{
\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.45\textwidth]{hyper/Fig/hyper}
   \label{fig:hyper}}
   \subfloat[]{\includegraphics[width=0.45\textwidth]{hyper/Fig/hyper-n}
   \label{fig:hyper-n}}
\caption{Synthetic example. (a) Clean data. (b) Noisy data (SNR=1.56 dB).}
\label{fig:hyper,hyper-n}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.3\textwidth]{hyper/Fig/hyper-fx}
   \label{fig:hyper-fx}}
   \subfloat[]{\includegraphics[width=0.3\textwidth]{hyper/Fig/hyper-ortho}
   \label{fig:hyper-ortho}}
   \subfloat[]{\includegraphics[width=0.3\textwidth]{hyper/Fig/hyper-dl}
   \label{fig:hyper-dl}} \\
\subfloat[]{\includegraphics[width=0.3\textwidth]{hyper/Fig/hyper-fx-n}
   \label{fig:hyper-fx-n}}
   \subfloat[]{\includegraphics[width=0.3\textwidth]{hyper/Fig/hyper-ortho-n}
   \label{fig:hyper-ortho-n}}
   \subfloat[]{\includegraphics[width=0.3\textwidth]{hyper/Fig/hyper-dl-n}
   \label{fig:hyper-dl-n}} 
\caption{Synthetic example. Denoised data using (a) FX method (SNR=6.37 dB), (b) local orthogonalization method (SNR=7.78 dB), and (c) proposed method (SNR=9.13 dB). (d)-(f) Removed noise corresponding to (a)-(c).}
\label{fig:hyper-fx,hyper-ortho,hyper-dl,hyper-fx-n,hyper-ortho-n,hyper-dl-n}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.3\textwidth]{hyper/Fig/hyper-fx-s}
   \label{fig:hyper-fx-s}}
   \subfloat[]{\includegraphics[width=0.3\textwidth]{hyper/Fig/hyper-ortho-s}
   \label{fig:hyper-ortho-s}}
   \subfloat[]{\includegraphics[width=0.3\textwidth]{hyper/Fig/hyper-dl-s}
   \label{fig:hyper-dl-s}} 
\caption{Synthetic example. Local similarity between denoised data and removed noise using (a) FX method, (b) local orthogonalization method, and (c) proposed method. }
\label{fig:hyper-fx-s,hyper-ortho-s,hyper-dl-s}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=\textwidth]{hyper/Fig/hyper-comp}}
\caption{Denoising comparison. From left to right: initial result, initial noise, recovered leaked signals, new result, new noise.}
\label{fig:hyper-comp}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.5\textwidth]{Fig/atoms1}
   \label{fig:atoms1}}\\
   \subfloat[]{\includegraphics[width=0.5\textwidth]{Fig/atoms2}
   \label{fig:atoms2}}
\caption{Comparison between the initial atoms (a) and learned atoms (b). The white circles in (b) show clear features of the seismic signals learned by the SGK method.}
\label{fig:atoms1,atoms2}
\end{figure}

\begin{figure}[htb!]
\centering
   \subfloat[]{\includegraphics[width=0.7\textwidth]{Fig/hyper_XXn_z}
   \label{fig:hyper_XXn_z}}\\
   \subfloat[]{\includegraphics[width=0.7\textwidth]{Fig/hyper_Xn_z}
   \label{fig:hyper_Xn_z}}
\caption{Comparison of different patches. \old{(a) Input patches created from the initial noise. (b) Zoomed patches from (a). (c) Output patches after dictionary learning and thresholding. (d) Zoomed patches from (b). The zooming areas are highlighted by the red frame boxes. Note the clear retrieved signal patches.}\new{(a) Input patches created from the initial noise. (b) Output patches after dictionary learning and thresholding.} }
\label{fig:hyper_XXn_z,hyper_Xn_z}
\end{figure}
}
\section{Examples}
We test the effectiveness of the proposed method using a synthetic dataset, and several 2D and 3D real seismic datasets. We benchmark the proposed method with the state-of-the-art local orthogonalization method, which is proposed specifically for retrieving the leaked signals. For the synthetic data, we quantitatively evaluate the denoising performance using the SNR method:
\begin{equation}
\label{eq:snr}
\text{SNR}=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2^2}{\Arrowvert \mathbf{s} -\hat{\mathbf{s}}\Arrowvert_2^2},
\end{equation}
where $\mathbf{s}$ is the clean data, and $\hat{\mathbf{s}}$ is the noisy or denoised data.

The first example is a synthetic dataset, as plotted in Figure \ref{fig:hyper,hyper-n}. There are four hyperbolic events in the data. Figures  \ref{fig:hyper} and \ref{fig:hyper-n} show the clean and noisy data, respectively. The noise is additive and bandlimited random noise. Based on the definition in equation \ref{eq:snr}, the SNR of the noisy data is 1.56 dB. Figure \ref{fig:hyper-fx,hyper-ortho,hyper-dl,hyper-fx-n,hyper-ortho-n,hyper-dl-n} plots a comparison of denoised data using three different methods and their corresponding noise sections. Figures \ref{fig:hyper-fx} and \ref{fig:hyper-fx-n} correspond to the FX method. It is clear that significant signal leakage is observable in the removed noise. Figures \ref{fig:hyper-ortho} and \ref{fig:hyper-ortho-n} correspond to the local orthogonalization method. It is obvious that the local orthogonalization method retrieves a significant amount of leaked signal energy but causes a small amount of leaked signals in the noise. Figures \ref{fig:hyper-dl} and \ref{fig:hyper-dl-n} correspond to the proposed method, where almost all the leaked signals have been retrieved and the denoised signals become stronger. \wen{The artifacts in 1.5 s are caused due to the deficiency of the FX method, e.g., the failure of the FX method to accurately estimate the prediction filter at the notch frequencies due to a superposition of several Ricker wavelets at different time positions.} The SNRs of the results from FX, local orthogonalization, and the proposed methods are 6.37 dB, 7.78 dB, and 9.13 dB, respectively. Another metric to evaluate the denoising performance is the local similarity between the denoised data and removed noise. A high local similarity means a higher probability that the signal is leaked. The local similarity metric can effectively detect those areas with strong signal leakage \cite[]{yangkang2015ortho}.  The local similarity comparison is shown in Figure \ref{fig:hyper-fx-s,hyper-ortho-s,hyper-dl-s}. It is clear that the local similarity corresponding to the proposed method is generally the smallest.

To compare the difference between different data and further demonstrate what the proposed method has retrieved, we plot different data side by side in Figure \ref{fig:hyper-comp}. In Figure \ref{fig:hyper-comp}, from left to right, it corresponds to the initial result, initial noise, recovered leaked signals, new result, new noise. It is clear that the dictionary learning process only retrieves the leaked signals without random noise. We show a comparison of the initial dictionary atoms in Figure \ref{fig:atoms1} and the learned dictionary atoms in Figure \ref{fig:atoms2}. From Figure \ref{fig:atoms2}, it is clear that the fast dictionary learning method can successfully extract some signal features from the initially denoised data. The white circles highlight those obvious signal features extracted from the data. We also show a comparison between the patches generated from the initial noise (Figure \ref{fig:hyper_XXn_z}) and the denoised patches (Figure \ref{fig:hyper_Xn_z}), which correspond to the retrieved leaked signals. \old{To visualize clearly the patches, we zoom in some patches and show them in the right column of Figure \ref{fig:hyper_XXn_z,hyper_Xn_z}.} It is clear that the dictionary learning method successfully retrieves those leaked signals from the noise patches. The zooming areas are highlighted by the red frame boxes in the left column of Figure \ref{fig:hyper_XXn_z,hyper_Xn_z}.
\AtEndDocument{
\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/pp-0}
   \label{fig:pp-0}}\\
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/pp-z}
   \label{fig:pp-z}}
\caption{Field data example. (a) Raw field data. (b) Zoomed section corresponding to the cyan frame box.  }
\label{fig:pp-0,pp-z}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.33\textwidth]{real2d/Fig/pp-fx-0}
   \label{fig:pp-fx-0}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{real2d/Fig/pp-ortho-0}
   \label{fig:pp-ortho-0}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{real2d/Fig/pp-dl2-0}
   \label{fig:pp-dl2-0}}\\
\subfloat[]{\includegraphics[width=0.33\textwidth]{real2d/Fig/pp-fx-z0}
   \label{fig:pp-fx-z0}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{real2d/Fig/pp-ortho-z0}
   \label{fig:pp-ortho-z0}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{real2d/Fig/pp-dl2-z0}
   \label{fig:pp-dl2-z0}}
\caption{Field data example. Denoised data using (a) FX method, (b) local orthogonalization method, (c) proposed method. Zoomed sections using (d) FX method, (e) local orthogonalization method, (f) proposed method. }
\label{fig:pp-fx-0,pp-ortho-0,pp-dl2-0,pp-fx-z0,pp-ortho-z0,pp-dl2-z0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.33\textwidth]{real2d/Fig/pp-fx-n0}
   \label{fig:pp-fx-n0}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{real2d/Fig/pp-ortho-n0}
   \label{fig:pp-ortho-n0}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{real2d/Fig/pp-dl2-n0}
   \label{fig:pp-dl2-n0}}  \\
   \subfloat[]{\includegraphics[width=0.33\textwidth]{real2d/Fig/pp-fx-n-z}
   \label{fig:pp-fx-n-z}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{real2d/Fig/pp-ortho-n-z}
   \label{fig:pp-ortho-n-z}}
   \subfloat[]{\includegraphics[width=0.33\textwidth]{real2d/Fig/pp-dl2-n-z}
   \label{fig:pp-dl2-n-z}} 
\caption{Field data example. Removed noise using (a) FX method, (b) local orthogonalization method, (c) proposed method. Zoomed sections using (d) FX method, (e) local orthogonalization method, (f) proposed method. The second row corresponds to the cyan frame box. The smaller pink frame box indicates the dramatic change of signal leakage before and after using the local orthogonalization \old{methods}\new{and the proposed methods}.}
\label{fig:pp-fx-n0,pp-ortho-n0,pp-dl2-n0,pp-fx-n-z,pp-ortho-n-z,pp-dl2-n-z}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=\textwidth]{real2d/Fig/pp-comp2}}
\caption{Denoising comparison. From left to right: initial result, initial noise, recovered leaked signals, new result, new noise.}
\label{fig:pp-comp2}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/pp-reo-0}
   \label{fig:pp-reo-0}}\\
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/pp-re2-0}
   \label{fig:pp-re2-0}}
\caption{Comparison of the retrieved signals using (a) local orthogonalization method and (b) proposed method. }
\label{fig:pp-reo-0,pp-re2-0}
\end{figure}
}
Next, we apply the proposed method to a 2D field data example \wen{($1024\times 471$, sampling rate is 2 ms, and dominant frequency is about 50 Hz)}, as plotted in Figure \ref{fig:pp-0,pp-z}. Figure \ref{fig:pp-0} plots the raw data and Figure \ref{fig:pp-z} plots a zoomed section from the raw data. The zooming area is highlighted by the cyan frame box. From the zoomed section, one can observe that this field data is very noisy. Figure \ref{fig:pp-fx-0,pp-ortho-0,pp-dl2-0,pp-fx-z0,pp-ortho-z0,pp-dl2-z0} plots a comparison of denoised data using the FX method, local orthogonalization method, and the proposed method. The first row corresponds to the denoised data in the original scale while the second row corresponds to the zoomed comparison (from the cyan frame boxes on the first row). The pink frame box highlights an area with a distinct amplitude difference. Comparing the denoised data using different methods, one can find that the FX method causes damages to structural complex areas (e.g., the pink framework). The local orthogonalization method can retrieve the leaked signals but at the cost of bringing more noise into the denoised data. Thus we find that the denoised data using the local orthogonalization method are obviously noisier, especially in the shallow areas. The proposed method, however, retrieves the leaked signals without compromising the SNR. A comparison of the removed noise using different methods is shown in Figure \ref{fig:pp-fx-n0,pp-ortho-n0,pp-dl2-n0,pp-fx-n-z,pp-ortho-n-z,pp-dl2-n-z}. It is clear that the local orthogonalization method removes a little weaker noise than the FX and the proposed methods. The small dipping structure in the pink frame box is clearly shown in the noise section of the FX method, indicating significant signal leakage. The proposed method does not cause obvious signal leakage as revealed in its noise section. For a better comparison of different datasets and seeing how the retrieved signals compared with other datasets in terms of energy, we show a side-by-side comparison of different datasets in Figure \ref{fig:pp-comp2}, where, from left to right, it corresponds to the initial result, initial noise, recovered leaked signals, new result, new noise. Figure \ref{fig:pp-reo-0,pp-re2-0} compares the retrieved signals using the local orthogonalization method and the proposed method in the same amplitude scale. It is clear that the local orthogonalization retrieves obviously more random noise apart from the small-scale dipping signal. The proposed method seems to only retrieve those leaked signals. Note that, we can adjust the thresholding percentage of sparse coefficients to retrieve more signals, but at the risk of bringing more noise. However, adjusting the thresholding percentage is more flexible than the smoothing radius as used in the local orthogonalization method. In this example, we can retrieve the leaked dipping signal only when we use the shortest smoothing radius (2 samples).

\AtEndDocument{
\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.5\textwidth]{teapot/Fig/tea}
   \label{fig:tea}}
\subfloat[]{\includegraphics[width=0.5\textwidth]{teapot/Fig/t-fxy}
   \label{fig:t-fxy}}\\
   \subfloat[]{\includegraphics[width=0.5\textwidth]{teapot/Fig/t-ortho}
   \label{fig:t-ortho}}
   \subfloat[]{\includegraphics[width=0.5\textwidth]{teapot/Fig/t-dl}
   \label{fig:t-dl}}\\
\caption{3D field data example. (a) Teapot Dome dataset. Denoised data using (b) FXY RNAR method, (c) local orthogonalization method, and (d) proposed method.}
\label{fig:tea,t-fxy,t-ortho,t-dl}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.5\textwidth]{teapot/Fig/t-fxy-n0}
   \label{fig:t-fxy-n0}}
   \subfloat[]{\includegraphics[width=0.5\textwidth]{teapot/Fig/t-ortho-n0}
   \label{fig:t-ortho-n0}}\\
   \subfloat[]{\includegraphics[width=0.5\textwidth]{teapot/Fig/t-dl-n0}
   \label{fig:t-dl-n0}}
\caption{3D Teapot Dome data example. Removed noise using (a) FXY RNAR method, (b) local orthogonalization method, and (c) proposed method.}
\label{fig:t-fxy-n0,t-ortho-n0,t-dl-n0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.32\textwidth]{teapot/Fig/slice-fxy-0}
   \label{fig:slice-fxy-0}}
   \subfloat[]{\includegraphics[width=0.32\textwidth]{teapot/Fig/slice-ortho-0}
   \label{fig:slice-ortho-0}}
   \subfloat[]{\includegraphics[width=0.32\textwidth]{teapot/Fig/slice-dl-0}
   \label{fig:slice-dl-0}} \\
\subfloat[]{\includegraphics[width=0.32\textwidth]{teapot/Fig/slice-fxy-z}
   \label{fig:slice-fxy-z}}
   \subfloat[]{\includegraphics[width=0.32\textwidth]{teapot/Fig/slice-ortho-z}
   \label{fig:slice-ortho-z}}
   \subfloat[]{\includegraphics[width=0.32\textwidth]{teapot/Fig/slice-dl-z}
   \label{fig:slice-dl-z}}\\
\caption{3D Teapot Dome data example. Comparison of the constant time slice (1 s) using (a) FXY RNAR method, (b) local orthogonalization method, and (c) proposed method. \wen{(d)-(f) Zoomed comparison (highlighted by the frame boxes) of the top row.}}
\label{fig:slice-fxy-0,slice-ortho-0,slice-dl-0,slice-fxy-z,slice-ortho-z,slice-dl-z}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=\textwidth]{teapot/Fig/t-comp}}
\caption{Denoising comparison. From left to right in the front panel defined by the time and xline axes: initial result, initial noise, recovered leaked signals, new result, new noise.}
\label{fig:t-comp}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.5\textwidth]{Fig/t-atoms1}
   \label{fig:t-atoms1}}\\
   \subfloat[]{\includegraphics[width=0.5\textwidth]{Fig/t-atoms2}
   \label{fig:t-atoms2}}
\caption{Comparison between the initial atoms (a) and learned atoms (b). }
\label{fig:t-atoms1,t-atoms2}
\end{figure}

\begin{figure}[htb!]
\centering

   \subfloat[]{\includegraphics[width=0.7\textwidth]{Fig/t_XXn_z}
   \label{fig:t_XXn_z}}\\
   \subfloat[]{\includegraphics[width=0.7\textwidth]{Fig/t_Xn_z}
   \label{fig:t_Xn_z}}%\\
%   \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/t_Xnn}
%   \label{fig:t_Xnn}}
%   \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/t_Xnn_z}
%   \label{fig:t_Xnn_z}}
\caption{Comparison of different patches. \old{(a) Input patches created from the initial noise. (b) Zoomed patches from (a). (c) Output patches after dictionary learning and thresholding. (d) Zoomed patches from (b). \dlo{(e) Difference of patches between (a) and (c). (f) Zoomed patches from (e).} The zooming areas are highlighted by the red frame boxes. Note the clear retrieved signal patches.} \new{(a) Input patches created from the initial noise. (b) Output patches after dictionary learning and thresholding.}}
\label{fig:t_XXn_z,t_Xn_z}
\end{figure}
}

Finally, we test the performance of the proposed method on the TeapotDome 3D dataset ($900\times 75\times 150$ \wen{and sampling rate is 2 ms, and dominant frequency is about 40 Hz}), which is plotted in Figure \ref{fig:tea}. Figures \ref{fig:t-fxy}-\ref{fig:t-dl} plot the denoised data using the $f-x-y$ non-stationary predictive filtering (FXY) method \cite[]{wanghang2021geo}, the local orthogonalization method, and the proposed method, respectively. From the denoised data, it seems that all three methods obtain successful denoising performance. However, when compared in the removed noise cubes, the differences between different methods become clear. The FXY method causes significant damages to the useful signals, as pointed by the labeled arrows in Figure \ref{fig:t-fxy-n0}. The local orthogonalization method helps retrieve some leaked signals, and the signal energy in the noise cube becomes weaker, as pointed out by the arrow in Figure \ref{fig:t-ortho-n0}. However, the coherent signal energy is still visible in the noise cube in Figure \ref{fig:t-ortho-n0}.  The proposed DL method mitigates the signal leakage to a great extent and the coherent signal energy in the noise cube is almost negligible, as indicated by the arrows in Figure \ref{fig:t-dl-n0}. To better visualize the differences, we extract a constant-time slice from each noise cube in Figure \ref{fig:t-fxy-n0,t-ortho-n0,t-dl-n0} and show them in Figure \ref{fig:slice-fxy-0,slice-ortho-0,slice-dl-0,slice-fxy-z,slice-ortho-z,slice-dl-z}. Figures \ref{fig:slice-fxy-0}-\ref{fig:slice-dl-0} show the time slices in the original scale and Figures \ref{fig:slice-fxy-z}-\ref{fig:slice-dl-z} show the zoomed time slices from the pink frame boxes. From Figure \ref{fig:slice-fxy-0,slice-ortho-0,slice-dl-0,slice-fxy-z,slice-ortho-z,slice-dl-z}, it is very clear that the signal leakage becomes weaker and weaker from left to right. Figure \ref{fig:t-comp} shows a concatenated dataset showing a detailed comparison among initial result, initial noise, recovered leaked signals, new result, new noise (from left to right in the front panel).  It is clear that the dictionary learning process effectively retrieves those leaked signals without bringing back the incoherent noise, thus making the denoised reflection signals stronger. Figure \ref{fig:t-atoms1,t-atoms2} shows a comparison of the initial (a) and learned (b) dictionaries by plotting each dictionary atom as a 3D cube ($8\times 8 \times8$). It is clear that the dictionary learning process effectively extracts significant signal features from the data, which are crucial in retrieving the leaked signals in the 3D noise cube of a traditional method. Figure \ref{fig:t_XXn_z,t_Xn_z} plots a comparison of the input and output patches after the learning and coding the sparse dictionary. Figures \ref{fig:t_XXn_z} and \ref{fig:t_Xn_z}\dlo{, and \ref{fig:t_Xnn}} correspond to the input and output\dlo{, and difference} patches. \old{Figures \ref{fig:t_XXn_z} and \wen{\ref{fig:t_Xn_z}}\dlo{, and \ref{fig:t_XXn_z}} correspond to zoomed patches from the red frame boxes.} We can see that the proposed method can successfully retrieve those useful signals from very noise patches. While most noise patches are untouched, a significant amount of signal energy can be effectively detected and extracted.

\section{Discussion}
In the local orthogonalization method, the main parameter is the smoothing radius. A larger smoothing radius can mitigate the retrieval of random noise but could fail in retrieving the small-scale leaked signals, while a smaller smoothing radius is able to retrieve the small-scale signal leakage but could retrieve more noise, causing significant residual noise in the denoised data. In the proposed DL method, the main controlling parameter is the percentage of largest coefficients to be preserved in the sparse coefficients matrix $\mathbf{M}$. Thus, the proposed method is nearly an automatic algorithm to retrieve the leaked signals. To investigate how the percentage affects the signal retrieving performance, we compare retrieved sections using different percentages in Figure \ref{fig:pp-re-p1-0,pp-re-p2-0,pp-re-p3-0,pp-re-p4-0}. Figures \ref{fig:pp-re-p1-0}-\ref{fig:pp-re-p4-0} correspond to $p=0.3\%$, $p=0.6\%$, $p=1\%$, and $p=2\%$, respectively. It is clear that while all percentage values help retrieve the key leaked signals, the retrieved noise becomes stronger when $p$ increases. In practical usage, the percentage should be a small value, e.g., $<2\%$, one may need to adjust several times to obtain the best performance depending on the user's preference. Note that the small-scale leaked signals may look quite similar to the noise, thus sometimes one may choose to retrieve more noise to ensure no leaked small-scale signals. Some other parameters, like the patch size, shifting size, and sparsity level $T$, may affect the performance but not significantly. For example, a larger patch size has a stronger anti-noise ability and tends to obtain smoother dictionary atoms due to better coherency of the signals in a larger window, but tends to lose the resolution to retrieve the small-scale signals. A smaller patch size is more capable of retrieving small-scale signals but tends to be more sensitive to noise. For all the examples in this paper, we use a square/cubic patch with the length of a single side as eight samples. Some studies have shown that the vertical patch size is optimally chosen as half of the dominant wavelength \cite[]{guoyin2018,wanghang2020}. Other parameters like the shifting size and sparsity level could also slightly affect the performance, but we all fix them to be the default values (e.g., the shift size is two samples, and the sparsity level $T=3$) for all the examples in this paper.

The computational cost of the DL method is higher than the local orthogonalization method, even with the proposed fast dictionary learning scheme. For example, for the first field data example $1024\times 471$, the local orthogonalization method takes 2.03 s, and the proposed method takes 110.32 s. For the 3D Teapot Dome dataset, the proposed method takes less than an hour while the local orthogonalization method takes less than one minute. \wen{The comparison of running time during dictionary learning is listed in Table \ref{tbl:time} and compared with the KSVD algorithm. } The computation is carried out on a Mac Pro laptop with 2.5 GHz Intel Core i7 and 16 GB Ram. Although more expensive than the local orthogonalization method, the proposed method is still affordable. The dictionary learning step has been significantly accelerated by the SGK method due to the special sparse coding step and the SVD-free implementation. According to our experience and some published results, the SGK method can be 6-12 times faster than the traditional KSVD method. Generally speaking, the proposed method is affordable in industrial-scale applications.

\begin{table}[h]
\caption{Running time comparison during dictionary learning.}
\begin{center}
    \begin{tabular}{|c|c|c|c|c|c|} 
  \hline    & Synthetic & 2D field  & 3D field \\ 
  \hline SGK (s) & \new{3.1}  & \new{30.1}  & \new{825.5}\\
  \hline KSVD(s) & \new{26.5} & \new{313.5} & \new{6403.3} \\
      \hline
   \end{tabular} 
\end{center}
\label{tbl:time}
\end{table}

\AtEndDocument{
\begin{figure}[htb!]
\centering
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/pp-re-p1-0}
   \label{fig:pp-re-p1-0}}
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/pp-re-p2-0}
   \label{fig:pp-re-p2-0}}\\
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/pp-re-p3-0}
   \label{fig:pp-re-p3-0}}
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/pp-re-p4-0}
   \label{fig:pp-re-p4-0}}\\
\caption{Effect of percentage values. (a) Retrieved section using $p=0.3\%$. (b) Retrieved section using $p=0.6\%$. (c) Retrieved section using $p=1\%$. (d) Retrieved section using $p=2\%$.  }
\label{fig:pp-re-p1-0,pp-re-p2-0,pp-re-p3-0,pp-re-p4-0}
\end{figure}
}

\section{Conclusions}
The local signal-and-noise orthogonalization method is effective in retrieving the leaked seismic signals from the removed noise profile. However, due to the strong non-stationarity of seismic data, the smoothing radius parameter of the local orthogonalization method is not easy to adjust, which makes it difficult to retrieve the useful signals without bringing back too much random noise. To retrieve the signals in a more adaptive way, we need to either apply a local orthogonalization method in a non-stationary way where the non-stationary input parameter is difficult to choose or apply a new patch-based method that is less dependent on the manually chosen parameter. The proposed dictionary learning method retrieves the leaked useful signals in a patch-based way. The learned dictionary from the initially denoised data can effectively capture the features of seismic signals. Because of a diverse range of dictionary atoms and the sparse coding process based on the orthogonal matching pursuit method, it is easy to retrieve the leaked signals adaptively. The synthetic and field data examples both show that the proposed method performs successfully in practical situations.

\section{DATA AND MATERIALS AVAILABILITY}
Data associated with this research are available and can be obtained by contacting the corresponding author.

\bibliographystyle{seg}
\bibliography{dl}

### 2021-10-06 dlleak/matfun/Real.m

@@ -1,0 +1,111 @@
+function Real(noisy,denoised1,denoised2,n1,n2,n3,T,niter,K,ll1,ll2,ll3,ss1,ss2,ss3,perc)
+% Author      : Hang Wang and Yangkang Chen
+%               Zhejiang University
+%         
+% Date        : April, 2020
+%
+% Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
+%
+%  Copyright (C) 2020 Zhejiang University
+%  Copyright (C) 2020 Hang Wang and Yangkang Chen
+%  
+%  This program is free software; you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published by
+%  the Free Software Foundation; either version 2 of the License, or
+%  (at your option) any later version.
+%  
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%  
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, write to the Free Software
+%  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  
+%  
+%  Reference:
+%  Wang et al., 2020, Fast dictionary learning for high-dimensional seismic reconstruction, IEEE TGRS, doi: 10.1109/TGRS.2020.3030740
+%  Chen, 2020, Fast dictionary learning for noise attenuation of multidimensional seismic data, GJI, 222, 1717-1727.
+
+dn=zeros(n1,n2*n3);
+d1=zeros(n1,n2*n3);
+
+rsf_read(dn,noisy);dn=reshape(dn,n1,n2,n3);
+rsf_read(d1,denoised1);d1=reshape(d1,n1,n2,n3);
+
+
+%% simultaneous denoising and reconstruction
+%% SGK
[…]

### 2021-10-06 dlleak/matfun/yc_ompN.m

@@ -1,0 +1,12 @@
+function [ G ] = yc_ompN( D, X, K )
+%multi-column sparse coding
+% BY Yangkang Chen
+% Jan, 2020
+[n1,n2]=size(X);
+[n1,n3]=size(D);
+G=zeros(n3,n2);
+for i2=1:n2
+    G(:,i2)=yc_omp0(D,X(:,i2),K);
+end
+
+return

### 2021-10-06 dlleak/matfun/yc_patch.m

@@ -1,0 +1,79 @@
+function [ X ] = yc_patch( A,mode,l1,l2,s1,s2 )
+%decompose the image into patches:
+%  
+% by Yangkang Chen
+% Oct, 2017
+%
+% Input: 
+%   D: input image
+%   mode: patching mode
+%   l1: first patch size
+%   l2: second patch size
+%   s1: first shifting size
+%   s2: second shifting size
+%   
+% Output:
+%   X: patches
+% 
+% Modified on Dec 12, 2018 (the edge issue, arbitrary size for the matrix)
+% 		      Dec 31, 2018 (tmp1=mod(n1,l1) -> tmp1=mod(n1-l1,s1))
+% 
+%
+% Key Reference:
+% Chen, Y., 2020, Fast dictionary learning for noise attenuation of multidimensional seismic data, Geophysical Journal International, 222, 1717-1727.
+%
+% Other related references (e.g., introducing the subroutines)
+% Siahsar, M. A. N., Gholtashi, S., Kahoo, A. R., W. Chen, and Y. Chen, 2017, Data-driven multi-task sparse dictionary learning for noise attenuation of 3D seismic data, Geophysics, 82, V385-V396.
+% Siahsar, M. A. N., V. Abolghasemi, and Y. Chen, 2017, Simultaneous denoising and interpolation of 2D seismic data using data-driven non-negative dictionary learning, Signal Processing, 141, 309-321.
+% Chen, Y., M. Zhang, M. Bai, and W. Chen, 2019, Improving the signal-to-noise ratio of seismological datasets by unsupervised machine learning, Seismological Research Letters, 90, 1552-1564.
+% Chen, Y., S. Zu, W. Chen, M. Zhang, and Z. Guan, 2020, Learning the blending spikes using sparse dictionaries, Geophysical Journal International, 222, 1846–1863. 
+% Wang, H., Q. Zhang, G. Zhang, J. Fang, and Y. Chen, 2020, Self-training and learning the waveform features of microseismic data using an adaptive dictionary, Geophysics, 85, KS51?KS61.
+% Chen, Y., S. Fomel, 2015, Random noise attenuation using local signal-and-noise orthogonalization, Geophysics, 80, WD1-WD9.
[…]

### 2021-10-06 dlleak/matfun/yc_sgk.m

@@ -1,0 +1,172 @@
+function [D,G]=yc_sgk(X,param)
+%yc_sgk: SGK algorithm
+% BY Yangkang Chen
+% Jan, 2020
+%
+% INPUT
+% X:     input training samples
+% param: parameter struct
+%   param.mode=1;   %1: sparsity; 0: error
+%   param.niter=10; %number of SGK iterations to perform; default: 10
+%   param.D=DCT;    %initial D
+%   param.T=3;      %sparsity level
+%
+% OUTPUT
+% D:    learned dictionary
+% G:    sparse coefficients
+%
+% Key Reference:
+% Chen, Y., 2020, Fast dictionary learning for noise attenuation of multidimensional seismic data, Geophysical Journal International, 222, 1717-1727.
+%
+% Other related references (e.g., introducing the subroutines)
+% Siahsar, M. A. N., Gholtashi, S., Kahoo, A. R., W. Chen, and Y. Chen, 2017, Data-driven multi-task sparse dictionary learning for noise attenuation of 3D seismic data, Geophysics, 82, V385-V396.
+% Siahsar, M. A. N., V. Abolghasemi, and Y. Chen, 2017, Simultaneous denoising and interpolation of 2D seismic data using data-driven non-negative dictionary learning, Signal Processing, 141, 309-321.
+% Chen, Y., M. Zhang, M. Bai, and W. Chen, 2019, Improving the signal-to-noise ratio of seismological datasets by unsupervised machine learning, Seismological Research Letters, 90, 1552-1564.
+% Chen, Y., S. Zu, W. Chen, M. Zhang, and Z. Guan, 2020, Learning the blending spikes using sparse dictionaries, Geophysical Journal International, 222, 1846–1863.  
+% Wang, H., Q. Zhang, G. Zhang, J. Fang, and Y. Chen, 2020, Self-training and learning the waveform features of microseismic data using an adaptive dictionary, Geophysics, 85, KS51?KS61.
+% Chen, Y., S. Fomel, 2015, Random noise attenuation using local signal-and-noise orthogonalization, Geophysics, 80, WD1-WD9.
[…]

### 2021-10-16 npef/matfun/Linear5dn.m
Fri Oct 15 21:50:06 CDT 2021

@@ -1,0 +1,118 @@
+function Linear5dn(clean,noisy,obs,nobs,mmask,rr,drr,rrn,drrn)
+% Author      : Yangkang Chen
+% Date        : Oct, 2021
+% 
+% Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
+%    
+%  Copyright (C) 2021 The University of Texas at Austin
+%  Copyright (C) 2021 Yangkang Chen
+%  
+%  This program is free software; you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published by
+%  the Free Software Foundation; either version 2 of the License, or
+%  (at your option) any later version.
+%  
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%  
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, write to the Free Software
+%  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  
+% 
+%  Reference:   Chen et al., GJI, 2016; Chen et al., GJI, 2020; Chen et
+%  al., GEO, 2021
+
+% clc;clear;close all;
+
+
+%% load data
+% addpath(genpath('~/chenyk.data/cyk_small_dataset/'));
+
+load yc_synth5d.mat
+d=data5d;d=d/max(max(max(max(max(d)))));
+[nt,nhx,nhy,nx,ny]=size(d);
+dt=0.004;
+%% exploring the data
+%1) ploting CMP gather
+%figure;imagesc(reshape(d(:,:,:,1,1),100,10*10));
+
+%2) ploting common offset gather
+%figure;imagesc(reshape(d(:,5,5,:,:),100,10*10));
+
+%% simultaneous denoising and reconstruction
[…]

### 2021-10-16 npef/paper.tex
Fri Oct 15 21:50:06 CDT 2021
Fri Oct 15 23:05:19 CDT 2021

@@
+\DeclareRobustCommand{\dlo}[1]{}
+\DeclareRobustCommand{\wen}[1]{#1}
+
+\published{Geophysics, 86, no. 5, V419–V429, (2021)}
+
 \title{5D de-aliased seismic data interpolation using non-stationary prediction error filter}
@@
     \centering
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_clean5d}
+    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_clean5d}
     \label{fig:l_clean5d}}
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_obs5d}
+    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_obs5d}
     \label{fig:l_obs5d}}\\
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_rr5d}
+    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_drr5d}
     \label{fig:l_drr5d}}
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_recon5d}
+    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_recon5d}
     \label{fig:l_npef5d}}\\
@@
     \centering
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_clean5d-fk}
+    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_clean5d-fk}
     \label{fig:l_clean5d-fk}}
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_obs5d-fk}
+    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_obs5d-fk}
     \label{fig:l_obs5d-fk}}\\
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_rr5d-fk}
+    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_drr5d-fk}
     \label{fig:l_drr5d-fk}}
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_recon5d-fk}
+    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_recon5d-fk}
     \label{fig:l_npef5d-fk}}\\
@@
     \centering
-    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5d_n/Fig/synth_apef5-s1}
+    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5dn/Fig/synth_apef5-s1}
     \label{fig:l_npef1}}
-    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5d_n/Fig/synth_apef5-s2}
+    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5dn/Fig/synth_apef5-s2}
     \label{fig:l_npef}}\\
-    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5d_n/Fig/synth_apef5-s3}
+    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5dn/Fig/synth_apef5-s3}
     \label{fig:l_npef3}}
-    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5d_n/Fig/synth_apef5-s4}
+    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5dn/Fig/synth_apef5-s4}
     \label{fig:l_npef4}}\\
@@
     \centering
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_clean5d-2}
+    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_clean5d-2}
     \label{fig:l_clean5d2}}
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_obs5d-2}
+    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_obs5d-2}
     \label{fig:l_obs5d2}}\\
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_rr5d-2}
+    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_drr5d-2}
     \label{fig:l_drr5d2}}
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_recon5d-2}
+    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_recon5d-2}
     \label{fig:l_npef5d2}}\\
@@
 
+%% The following was reviewed during revision but actually very informative
 %\begin{figure}[htb!]
 %   \centering
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_noisy5d}
+%   \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_noisy5d}
 %   \label{fig:ln_noisy5d}}
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_obs5d}
+%   \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/nsynth_obs5d}
 %   \label{fig:ln_obs5d}}\\
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_rr5d}
+%   \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/nsynth_drr5d}
 %   \label{fig:ln_drr5d}}
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_recon5d}
+%   \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/nsynth_recon5d}
 %   \label{fig:ln_npef5d}}\\
-%	\caption{Interpolation results of the noisy linear-events example for $X=1$ and $Y=1$.
+%\caption{Interpolation results of the noisy linear-events example for $X=1$ and $Y=1$.
 Each common midpoint cube has bee reshaped into a 2D matrix.
@@
 Note that the NPEF method fails in this case.}
-%	\label{fig:ln_noisy5d,ln_obs5d,ln_drr5d,ln_npef5d}
+%\label{fig:ln_noisy5d,ln_obs5d,ln_drr5d,ln_npef5d}
 %\end{figure}
@@
 %   \centering
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_noisy5d-2}
+%   \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_noisy5d-2}
 %   \label{fig:ln_noisy5d2}}
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_obs5d-2}
+%   \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/nsynth_obs5d-2}
 %   \label{fig:ln_obs5d2}}\\
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_rr5d-2}
+%   \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/nsynth_drr5d-2}
 %   \label{fig:ln_rr5d2}}
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_recon5d-2}
+%   \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/nsynth_recon5d-2}
 %   \label{fig:ln_npef5d2}}\\
-%	\caption{Interpolation results of the noisy linear-events example for $Hx=6$ and $Hy=6$.
+%\caption{Interpolation results of the noisy linear-events example for $Hx=6$ and $Hy=6$.
 Each common offset cube has bee reshaped into a 2D matrix.
@@
 Note that the NPEF method fails in this case.}
-%	\label{fig:ln_noisy5d2,ln_obs5d2,ln_drr5d2,ln_npef5d2}
+%\label{fig:ln_noisy5d2,ln_obs5d2,ln_drr5d2,ln_npef5d2}
 %\end{figure}
+%% The above was reviewed during revision but actually very informative
 
@@
    \centering
-    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_obs5d-3}
+   \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/la_obs5d-3}
    \label{fig:la_obs5d}}\\
-    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_rr5d-3}
+   \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/la_drr5d-3}
    \label{fig:la_drr5d}}\\
-    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_recon5d-3}
+   \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/la_recon5d-3}
    \label{fig:la_npef5d}}\\
@@
    \centering
-    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_obs5d-3fk}
+   \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/la_obs5d-3fk}
    \label{fig:la_obs5dfk}}\\
-    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_rr5d-3fk}
+   \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/la_drr5d-3fk}
    \label{fig:la_drr5dfk}}\\
-    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_recon5d-3fk}
+   \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/la_recon5d-3fk}
    \label{fig:la_npef5dfk}}\\
@@
 
-%\begin{figure}[htb!]
-%    \centering
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{hyper5d/Fig/hyper_clean5d}
-%    \label{fig:h_clean5d}}
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{hyper5d/Fig/hyper_obs5d}
-%    \label{fig:h_obs5d}}\\
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{hyper5d/Fig/hyper_drr5d}
-%    \label{fig:h_drr5d}}
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{hyper5d/Fig/hyper_recon5d}
-%    \label{fig:h_npef5d}}\\
-%	\caption{Interpolation results of the noisy hyperbolic-events example for $X=3$ and $Y=3$.
-(a) Clean data.
-(b) Irregularly missing data 70\% (S/N=0.59 dB).
-(c) Reconstructed data using the rank-reduction method (S/N=16.32 dB).
-(d) Reconstructed data using the NPEF method (S/N=6.38 dB).
-}
-%	\label{fig:h_clean5d,h_obs5d,h_drr5d,h_npef5d}
-%\end{figure}
-
 \begin{figure}[htb!]
    \centering
-    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_obs5d-3}
+   \subfloat[]{\includegraphics[width=\textwidth]{hyper5da/Fig/ha_obs5d-3}
    \label{fig:ha_obs5d}}\\
-    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_rr5d-3}
+   \subfloat[]{\includegraphics[width=\textwidth]{hyper5da/Fig/ha_rr5d-3}
    \label{fig:ha_drr5d}}\\
-    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_recon5d-3}
+   \subfloat[]{\includegraphics[width=\textwidth]{hyper5da/Fig/ha_recon5d-3}
    \label{fig:ha_npef5d}}\\
@@
 %    \centering
-%    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_obs5d-3fk}
-%    \label{fig:ha_obs5dfk}}\\
-%    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_rr5d-3fk}
-%    \label{fig:ha_drr5dfk}}\\
-%    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_recon5d-3fk}
-%    \label{fig:ha_npef5dfk}}\\
-%	\caption{\wen{FK spectra of de-aliased interpolation results of the hyperbolic-events example for $X=3$ and $Y=3$.
-Each common midpoint cube has bee reshaped into a 2D matrix.
-(a) Regularly missing data.
-(b) Reconstructed data using the rank-reduction method.
-(c) Reconstructed data using the NPEF method.}}
-%	\label{fig:ha_obs5dfk,ha_drr5dfk,ha_npef5dfk}
-%\end{figure}
-
-\begin{figure}[htb!]
-    \centering
-    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_obs5d-3-0}
-    \label{fig:r_obs5d}}\\
-    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_drr5d-3-0}
-    \label{fig:r_drr5d}}\\
-    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_npef5d-3-0}
-    \label{fig:r_npef5d}}\\
-	\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$.
+%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_obs5d-3-0}
+%    \label{fig:r_obs5d}}\\
+%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_drr5d-3-0}
+%    \label{fig:r_drr5d}}\\
+%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_npef5d-3-0}
+%    \label{fig:r_npef5d}}\\
+%	\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$.
 Each common offset cube has bee reshaped into a 2D matrix.
@@
 Note that the damped rank-reduction outperforms the NPEF method in the case of irregularly missing traces.}
-	\label{fig:r_obs5d,r_drr5d,r_npef5d}
-\end{figure}
-
-\begin{figure}[htb!]
-    \centering
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cog-zA}
-    \label{fig:r_obs5d1a}}
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cog-zB}
-    \label{fig:r_obs5d1b}}\\
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cog-zA}
-    \label{fig:r_drr5d1a}}
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cog-zB}
-    \label{fig:r_drr5d1b}}\\
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cog-zA}
-    \label{fig:r_npef5d1a}}
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cog-zB}
-    \label{fig:r_npef5d1b}}\\
-	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}.
+%	\label{fig:r_obs5d,r_drr5d,r_npef5d}
+%\end{figure}
+%
+%\begin{figure}[htb!]
+%    \centering
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cog-zA}
+%    \label{fig:r_obs5d1a}}
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cog-zB}
+%    \label{fig:r_obs5d1b}}\\
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cog-zA}
+%    \label{fig:r_drr5d1a}}
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cog-zB}
+%    \label{fig:r_drr5d1b}}\\
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cog-zA}
+%    \label{fig:r_npef5d1a}}
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cog-zB}
+%    \label{fig:r_npef5d1b}}\\
+%	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}.
 Right column: zoomed comparison of frame boxes B in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}.
@@
 }
-	\label{fig:r_obs5d1a,r_obs5d1b,r_drr5d1a,r_drr5d1b,r_npef5d1a,r_npef5d1b}
-\end{figure}
-
-\begin{figure}[htb!]
-    \centering
-    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_obs5d-4-0}
-    \label{fig:r_obs5d4}}\\
-    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_drr5d-4-0}
-    \label{fig:r_drr5d4}}\\
-    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_npef5d-4-0}
-    \label{fig:r_npef5d4}}\\
-	\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$.
+%	\label{fig:r_obs5d1a,r_obs5d1b,r_drr5d1a,r_drr5d1b,r_npef5d1a,r_npef5d1b}
+%\end{figure}
+%
+%
+%
+%
+%\begin{figure}[htb!]
+%    \centering
+%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_obs5d-4-0}
+%    \label{fig:r_obs5d4}}\\
+%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_drr5d-4-0}
+%    \label{fig:r_drr5d4}}\\
+%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_npef5d-4-0}
+%    \label{fig:r_npef5d4}}\\
+%	\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$.
 Each common offset cube has bee reshaped into a 2D matrix.
@@
 Note that the damped rank-reduction outperforms the NPEF method in the case of irregularly missing traces.}
-	\label{fig:r_obs5d4,r_drr5d4,r_npef5d4}
-\end{figure}
-
-\begin{figure}[htb!]
-    \centering
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cmg-zA}
-    \label{fig:r_obs5d2a}}
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cmg-zB}
-    \label{fig:r_obs5d2b}}\\
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cmg-zA}
-    \label{fig:r_drr5d2a}}
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cmg-zB}
-    \label{fig:r_drr5d2b}}\\
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cmg-zA}
-    \label{fig:r_npef5d2a}}
-    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cmg-zB}
-    \label{fig:r_npef5d2b}}\\
-	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4}.
+%	\label{fig:r_obs5d4,r_drr5d4,r_npef5d4}
+%\end{figure}
+%
+%
+%
+%\begin{figure}[htb!]
+%    \centering
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cmg-zA}
+%    \label{fig:r_obs5d2a}}
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cmg-zB}
+%    \label{fig:r_obs5d2b}}\\
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cmg-zA}
+%    \label{fig:r_drr5d2a}}
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cmg-zB}
+%    \label{fig:r_drr5d2b}}\\
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cmg-zA}
+%    \label{fig:r_npef5d2a}}
+%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cmg-zB}
+%    \label{fig:r_npef5d2b}}\\
+%	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4}.
 Right column: zoomed comparison of frame boxes B in Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4}.
 Note the obviously more discontinuous events in (e) and (f) caused by the NPEF method.}
-	\label{fig:r_obs5d2a,r_obs5d2b,r_drr5d2a,r_drr5d2b,r_npef5d2a,r_npef5d2b}
-\end{figure}
-
-\begin{figure}[htb!]
-    \centering
-   \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3-0}
-%    \subfloat[]{\includegraphics[width=1.0\textwidth]{Fig/test2} %eps2pdf problem
-    \label{fig:ra_obs5d}}\\
-    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_npef5d_new-3-0}
-    \label{fig:ra_npef5d}}\\
-	\caption{De-aliased interpolation results of the real 5D seismic data example for $Hx=6$ and $Hy=6$.
+%	\label{fig:r_obs5d2a,r_obs5d2b,r_drr5d2a,r_drr5d2b,r_npef5d2a,r_npef5d2b}
+%\end{figure}
+%
+%
+%\begin{figure}[htb!]
+%    \centering
+%   \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3-0}
+%%    \subfloat[]{\includegraphics[width=1.0\textwidth]{Fig/test2} %eps2pdf problem
+%    \label{fig:ra_obs5d}}\\
+%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_npef5d_new-3-0}
+%    \label{fig:ra_npef5d}}\\
+%	\caption{De-aliased interpolation results of the real 5D seismic data example for $Hx=6$ and $Hy=6$.
 We treat the reconstructed data using the damped rank-reduction method as the starting data and further interpolate a trace every other traces in the $X$ and $Y$ directions.
@@
 In this case of regularly missing traces, the rank-reduction method completely fails so we omit its result.}
-	\label{fig:ra_obs5d,ra_npef5d}
-\end{figure}
-
-\begin{figure}[htb!]
-    \centering
-%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3-0}
-    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3fk} %eps2pdf problem
-    \label{fig:ra_obs5d_new-3fk}}\\
-    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_npef5d_new-3fk}
-    \label{fig:ra_npef5d_new-3fk}}\\
-	\caption{\wen{FK spectra of de-aliased interpolation results of the real 5D seismic data example for $Hx=6$ and $Hy=6$.
+%	\label{fig:ra_obs5d,ra_npef5d}
+%\end{figure}
+%
+%\begin{figure}[htb!]
+%    \centering
+%%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3-0}
+%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3fk} %eps2pdf problem
+%    \label{fig:ra_obs5d_new-3fk}}\\
+%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_npef5d_new-3fk}
+%    \label{fig:ra_npef5d_new-3fk}}\\
+%	\caption{\wen{FK spectra of de-aliased interpolation results of the real 5D seismic data example for $Hx=6$ and $Hy=6$.
 (a) The regularly sampled data before interpolation.
@@
 }}
-	\label{fig:ra_obs5d_new-3fk,ra_npef5d_new-3fk}
-\end{figure}
-
-\begin{figure}[htb!]
-    \centering
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_obs5d_new-cog-zA}
-    \label{fig:r_obs5da}}
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_obs5d_new-cog-zB}
-    \label{fig:r_npef5db}}\\
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_npef5d_new-cog-zA}
-    \label{fig:r_obs5da}}
-    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_npef5d_new-cog-zB}
-    \label{fig:r_npef5db}}\\
-	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:ra_obs5d,ra_npef5d}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:ra_obs5d,ra_npef5d}.}
-	\label{fig:ra_obs5da,ra_npef5da,ra_obs5db,ra_npef5db}
-\end{figure}
-
-\begin{figure}[htb!]
-    \centering
-    \subfloat[]{\includegraphics[width=\textwidth]{real5d_smaller_onestep/Fig/os_obs}
-    \label{fig:os_obs}}\\
-    \subfloat[]{\includegraphics[width=\textwidth]{real5d_smaller_onestep/Fig/os_recon}
-    \label{fig:os_recon}}\\
-    \subfloat[]{\includegraphics[width=\textwidth]{real5d_smaller_onestep/Fig/ts_recon}
-    \label{fig:ts_recon}}
-	\caption{\new{Comparison between the two-step and one-step interpolation strategies.
+%	\label{fig:ra_obs5d_new-3fk,ra_npef5d_new-3fk}
+%\end{figure}
+%
+%\begin{figure}[htb!]
+%    \centering
+%    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_obs5d_new-cog-zA}
+%    \label{fig:r_obs5da}}
+%    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_obs5d_new-cog-zB}
+%    \label{fig:r_npef5db}}\\
+%    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_npef5d_new-cog-zA}
+%    \label{fig:r_obs5da}}
+%    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_npef5d_new-cog-zB}
+%    \label{fig:r_npef5db}}\\
+%	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:ra_obs5d,ra_npef5d}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:ra_obs5d,ra_npef5d}.}
+%	\label{fig:ra_obs5da,ra_npef5da,ra_obs5db,ra_npef5db}
+%\end{figure}
+%
+%\begin{figure}[htb!]
+%    \centering
+%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_smaller_onestep/Fig/os_obs}
+%    \label{fig:os_obs}}\\
+%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_smaller_onestep/Fig/os_recon}
+%    \label{fig:os_recon}}\\
+%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_smaller_onestep/Fig/ts_recon}
+%    \label{fig:ts_recon}}
+%	\caption{\new{Comparison between the two-step and one-step interpolation strategies.
 (a) Observed data when binned onto the regular grids of two times denser.
@@
 (c) Reconstructed data by the two-step rank-reduction and NPEF interpolation strategy.}  }
-	\label{fig:os_obs,os_recon,ts_recon}
-\end{figure}
-
-\begin{figure}[htb!]
-    \centering
-    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/zero2d}
-    \label{fig:zero2d}}\\
-    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/recon2d2}
-    \label{fig:recon2d2}}\\
-    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/recon2d}
-    \label{fig:recon2d}}\\
-	\caption{\new{De-aliased interpolation results of the second field data example for a common shot gather.
+%	\label{fig:os_obs,os_recon,ts_recon}
+%\end{figure}
+%
+%
+%\begin{figure}[htb!]
+%    \centering
+%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/zero2d}
+%    \label{fig:zero2d}}\\
+%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/recon2d2}
+%    \label{fig:recon2d2}}\\
+%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/recon2d}
+%    \label{fig:recon2d}}\\
+%	\caption{\new{De-aliased interpolation results of the second field data example for a common shot gather.
 Each gather has bee reshaped into a 2D matrix.
@@
 Note that the rank-reduction method completely fails in this case.}}
-	\label{fig:zero2d,recon2d2,recon2d}
-\end{figure}
-
-\begin{figure}[htb!]
-    \centering
-    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/zerofk2d}
-    \label{fig:zerofk2d}}\\
-    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/reconfk2d2}
-    \label{fig:reconfk2d2}}\\
-    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/reconfk2d}
-    \label{fig:reconfk2d}}\\
-	\caption{\new{FK spectra of de-aliased interpolation results of the second field data example.
+%	\label{fig:zero2d,recon2d2,recon2d}
+%\end{figure}
+%
+%\begin{figure}[htb!]
+%    \centering
+%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/zerofk2d}
+%    \label{fig:zerofk2d}}\\
+%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/reconfk2d2}
+%    \label{fig:reconfk2d2}}\\
+%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/reconfk2d}
+%    \label{fig:reconfk2d}}\\
+%	\caption{\new{FK spectra of de-aliased interpolation results of the second field data example.
 Each gather has bee reshaped into a 2D matrix.
@@
 (c) Reconstructed data using the NPEF method.}}
-	\label{fig:zerofk2d,reconfk2d2,reconfk2d}
-\end{figure}
+%	\label{fig:zerofk2d,reconfk2d2,reconfk2d}
+%\end{figure}
 }
@@
 
-%\inputdir{test}
-%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
-%\multiplot{2}{test1,test2}{width=0.45\textwidth}{(a) Caption a. (b) Caption b.}
-
 \bibliographystyle{seg}
@@
 \listoffigures
-
-%\begin{figure}[htb!]
-%	\centering
-%	\subfloat[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
-%	\caption{Caption.}
-%	\label{fig:fig}
-%\end{figure}
-
-%\begin{figure}[htb!]
-%	\centering
-%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
-%    \label{fig:fig1}}\\
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
-%    \label{fig:fig2}}\\
-%	\caption{(a) Caption a. (b) Caption b.}
-%	\label{fig:fig1,fig2}
-%\end{figure}
-
-%\begin{figure*}[ht!]
-%	\centering
-%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
-%    \label{fig:fig1}}\\
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
-%    \label{fig:fig2}}\\
-%	\caption{(a) Caption a. (b) Caption b.}
-%	\label{fig:fig1,fig2}
-%\end{figure*}
-
-%\begin{table}[h]
-%\caption{Table caption}
-%\begin{center}
-%     \begin{tabular}{|c|c|c|c|c|c|} 
-%	  \hline Column1 (unit)  & Column2 (unit) & Column3 (unit) \\ 
-%	  \hline 1 & 2  & 3 \\
-%       \hline
-%    \end{tabular} 
-%\end{center}
-%\label{tbl:table1}
-%\end{table}

### 2021-10-16 npef/matfun/Linear5dn.m

@@ -60,24 +60,23 @@ d0=dn.*mask;
 %% reconstruct
 flow=1;fhigh=100;dt=0.004;N=3;Niter=10;mode=0;verb=1;iflb=0;
 a=(Niter-(1:Niter))/(Niter-1); %linearly decreasing
-% d1=rr5d_lb_recon(d0c,mask,flow,fhigh,dt,N,Niter,eps,verb,mode,iflb,a);
-d1=d0c;
+d1=rr5d_lb_recon(d0c,mask,flow,fhigh,dt,N,Niter,eps,verb,mode,iflb,a);
+
 
 flow=1;fhigh=100;dt=0.004;N=3;NN=3;Niter=10;mode=0;verb=1;iflb=0;
 a=(Niter-(1:Niter))/(Niter-1); %linearly decreasing
-% d2=drr5d_lb_recon(d0c,mask,flow,fhigh,dt,N,NN,Niter,eps,verb,mode,iflb,a);
-d2=d1;
+d2=drr5d_lb_recon(d0c,mask,flow,fhigh,dt,N,NN,Niter,eps,verb,mode,iflb,a);
+
 
 %% recon and denoise
 flow=1;fhigh=100;dt=0.004;N=3;Niter=10;mode=1;verb=1;iflb=0;
 a=(Niter-(1:Niter))/(Niter-1); %linearly decreasing
-% d1n=rr5d_lb_recon(d0,mask,flow,fhigh,dt,N,Niter,eps,verb,mode,iflb,a);
-d1n=d0;
+d1n=rr5d_lb_recon(d0,mask,flow,fhigh,dt,N,Niter,eps,verb,mode,iflb,a);
+
 
 flow=1;fhigh=100;dt=0.004;N=3;NN=3;Niter=10;mode=1;verb=1;iflb=0;
 a=(Niter-(1:Niter))/(Niter-1); %linearly decreasing
-% d2n=drr5d_lb_recon(d0,mask,flow,fhigh,dt,N,NN,Niter,eps,verb,mode,iflb,a);
-d2n=d0;
+d2n=drr5d_lb_recon(d0,mask,flow,fhigh,dt,N,NN,Niter,eps,verb,mode,iflb,a);
 
 yc_snr(d(:),dn(:))
 yc_snr(d(:),d0c(:))

### 2021-10-16 npef/paper.tex
Sat Oct 16 08:09:38 CDT 2021

@@
    \label{fig:ha_obs5d}}\\
-   \subfloat[]{\includegraphics[width=\textwidth]{hyper5da/Fig/ha_rr5d-3}
+   \subfloat[]{\includegraphics[width=\textwidth]{hyper5da/Fig/ha_drr5d-3}
    \label{fig:ha_drr5d}}\\
@@
 
-%\begin{figure}[htb!]
-%    \centering
-%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_obs5d-3-0}
-%    \label{fig:r_obs5d}}\\
-%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_drr5d-3-0}
-%    \label{fig:r_drr5d}}\\
-%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_npef5d-3-0}
-%    \label{fig:r_npef5d}}\\
-%	\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$.
+\begin{figure}[htb!]
+   \centering
+   \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d/Fig/r_obs5d-3-0}
+   \label{fig:r_obs5d}}\\
+   \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d/Fig/r_drr5d-3-0}
+   \label{fig:r_drr5d}}\\
+   \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d/Fig/r_npef5d-3-0}
+   \label{fig:r_npef5d}}\\
+\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$.
 Each common offset cube has bee reshaped into a 2D matrix.
@@
 Note that the damped rank-reduction outperforms the NPEF method in the case of irregularly missing traces.}
-%	\label{fig:r_obs5d,r_drr5d,r_npef5d}
-%\end{figure}
-%
-%\begin{figure}[htb!]
-%    \centering
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cog-zA}
-%    \label{fig:r_obs5d1a}}
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cog-zB}
-%    \label{fig:r_obs5d1b}}\\
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cog-zA}
-%    \label{fig:r_drr5d1a}}
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cog-zB}
-%    \label{fig:r_drr5d1b}}\\
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cog-zA}
-%    \label{fig:r_npef5d1a}}
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cog-zB}
-%    \label{fig:r_npef5d1b}}\\
-%	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}.
+\label{fig:r_obs5d,r_drr5d,r_npef5d}
+\end{figure}
+
+\begin{figure}[htb!]
+   \centering
+   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_obs5d-cog-zA}
+   \label{fig:r_obs5d1a}}
+   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_obs5d-cog-zB}
+   \label{fig:r_obs5d1b}}\\
+   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_drr5d-cog-zA}
+   \label{fig:r_drr5d1a}}
+   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_drr5d-cog-zB}
+   \label{fig:r_drr5d1b}}\\
+   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_npef5d-cog-zA}
+   \label{fig:r_npef5d1a}}
+   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_npef5d-cog-zB}
+   \label{fig:r_npef5d1b}}\\
+\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}.
 Right column: zoomed comparison of frame boxes B in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}.
@@
 }
-%	\label{fig:r_obs5d1a,r_obs5d1b,r_drr5d1a,r_drr5d1b,r_npef5d1a,r_npef5d1b}
-%\end{figure}
-%
-%
-%
-%
-%\begin{figure}[htb!]
-%    \centering
-%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_obs5d-4-0}
-%    \label{fig:r_obs5d4}}\\
-%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_drr5d-4-0}
-%    \label{fig:r_drr5d4}}\\
-%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_npef5d-4-0}
-%    \label{fig:r_npef5d4}}\\
-%	\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$.
+\label{fig:r_obs5d1a,r_obs5d1b,r_drr5d1a,r_drr5d1b,r_npef5d1a,r_npef5d1b}
+\end{figure}
+
+\begin{figure}[htb!]
+   \centering
+   \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d/Fig/r_obs5d-4-0}
+   \label{fig:r_obs5d4}}\\
+   \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d/Fig/r_drr5d-4-0}
+   \label{fig:r_drr5d4}}\\
+   \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d/Fig/r_npef5d-4-0}
+   \label{fig:r_npef5d4}}\\
+\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$.
 Each common offset cube has bee reshaped into a 2D matrix.
@@
 Note that the damped rank-reduction outperforms the NPEF method in the case of irregularly missing traces.}
-%	\label{fig:r_obs5d4,r_drr5d4,r_npef5d4}
-%\end{figure}
-%
-%
-%
-%\begin{figure}[htb!]
-%    \centering
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cmg-zA}
-%    \label{fig:r_obs5d2a}}
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cmg-zB}
-%    \label{fig:r_obs5d2b}}\\
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cmg-zA}
-%    \label{fig:r_drr5d2a}}
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cmg-zB}
-%    \label{fig:r_drr5d2b}}\\
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cmg-zA}
-%    \label{fig:r_npef5d2a}}
-%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cmg-zB}
-%    \label{fig:r_npef5d2b}}\\
-%	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4}.
+\label{fig:r_obs5d4,r_drr5d4,r_npef5d4}
+\end{figure}
+
+\begin{figure}[htb!]
+   \centering
+   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_obs5d-cmg-zA}
+   \label{fig:r_obs5d2a}}
+   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_obs5d-cmg-zB}
+   \label{fig:r_obs5d2b}}\\
+   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_drr5d-cmg-zA}
+   \label{fig:r_drr5d2a}}
+   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_drr5d-cmg-zB}
+   \label{fig:r_drr5d2b}}\\
+   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_npef5d-cmg-zA}
+   \label{fig:r_npef5d2a}}
+   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_npef5d-cmg-zB}
+   \label{fig:r_npef5d2b}}\\
+\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4}.
 Right column: zoomed comparison of frame boxes B in Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4}.
 Note the obviously more discontinuous events in (e) and (f) caused by the NPEF method.}
-%	\label{fig:r_obs5d2a,r_obs5d2b,r_drr5d2a,r_drr5d2b,r_npef5d2a,r_npef5d2b}
-%\end{figure}
-%
-%
-%\begin{figure}[htb!]
-%    \centering
-%   \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3-0}
-%%    \subfloat[]{\includegraphics[width=1.0\textwidth]{Fig/test2} %eps2pdf problem
-%    \label{fig:ra_obs5d}}\\
-%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_npef5d_new-3-0}
-%    \label{fig:ra_npef5d}}\\
-%	\caption{De-aliased interpolation results of the real 5D seismic data example for $Hx=6$ and $Hy=6$.
+\label{fig:r_obs5d2a,r_obs5d2b,r_drr5d2a,r_drr5d2b,r_npef5d2a,r_npef5d2b}
+\end{figure}
+
+\begin{figure}[htb!]
+   \centering
+  \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d/Fig/r_obs5d_new-3-0}
+%    \subfloat[]{\includegraphics[width=1.0\textwidth]{Fig/test2} %eps2pdf problem
+   \label{fig:ra_obs5d}}\\
+   \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d/Fig/r_npef5d_new-3-0}
+   \label{fig:ra_npef5d}}\\
+\caption{De-aliased interpolation results of the real 5D seismic data example for $Hx=6$ and $Hy=6$.
 We treat the reconstructed data using the damped rank-reduction method as the starting data and further interpolate a trace every other traces in the $X$ and $Y$ directions.
@@
 In this case of regularly missing traces, the rank-reduction method completely fails so we omit its result.}
-%	\label{fig:ra_obs5d,ra_npef5d}
-%\end{figure}
+\label{fig:ra_obs5d,ra_npef5d}
+\end{figure}
+
+\begin{figure}[htb!]
+   \centering
+%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d/Fig/r_obs5d_new-3-0}
+   \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d/Fig/r_obs5d_new-3fk} %eps2pdf problem
+   \label{fig:ra_obs5d_new-3fk}}\\
+   \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d/Fig/r_npef5d_new-3fk}
+   \label{fig:ra_npef5d_new-3fk}}\\
+\caption{\wen{FK spectra of de-aliased interpolation results of the real 5D seismic data example for $Hx=6$ and $Hy=6$.
+(a) The regularly sampled data before interpolation.
+(b) Reconstructed data using the NPEF method.
+}}
+\label{fig:ra_obs5d_new-3fk,ra_npef5d_new-3fk}
+\end{figure}
+
+\begin{figure}[htb!]
+   \centering
+   \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d/Fig/r_obs5d_new-cog-zA}
+   \label{fig:r_obs5da}}
+   \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d/Fig/r_obs5d_new-cog-zB}
+   \label{fig:r_npef5db}}\\
+   \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d/Fig/r_npef5d_new-cog-zA}
+   \label{fig:r_obs5da}}
+   \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d/Fig/r_npef5d_new-cog-zB}
+   \label{fig:r_npef5db}}\\
+\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:ra_obs5d,ra_npef5d}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:ra_obs5d,ra_npef5d}.}
+\label{fig:ra_obs5da,ra_npef5da,ra_obs5db,ra_npef5db}
+\end{figure}
 %
@@
 %    \centering
-%%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3-0}
-%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3fk} %eps2pdf problem
-%    \label{fig:ra_obs5d_new-3fk}}\\
-%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_npef5d_new-3fk}
-%    \label{fig:ra_npef5d_new-3fk}}\\
-%	\caption{\wen{FK spectra of de-aliased interpolation results of the real 5D seismic data example for $Hx=6$ and $Hy=6$.
-(a) The regularly sampled data before interpolation.
-(b) Reconstructed data using the NPEF method.
-}}
-%	\label{fig:ra_obs5d_new-3fk,ra_npef5d_new-3fk}
-%\end{figure}
-%
-%\begin{figure}[htb!]
-%    \centering
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_obs5d_new-cog-zA}
-%    \label{fig:r_obs5da}}
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_obs5d_new-cog-zB}
-%    \label{fig:r_npef5db}}\\
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_npef5d_new-cog-zA}
-%    \label{fig:r_obs5da}}
-%    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_npef5d_new-cog-zB}
-%    \label{fig:r_npef5db}}\\
-%	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:ra_obs5d,ra_npef5d}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:ra_obs5d,ra_npef5d}.}
-%	\label{fig:ra_obs5da,ra_npef5da,ra_obs5db,ra_npef5db}
-%\end{figure}
-%
-%\begin{figure}[htb!]
-%    \centering
-%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_smaller_onestep/Fig/os_obs}
+%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_onestep/Fig/os_obs}
 %    \label{fig:os_obs}}\\
-%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_smaller_onestep/Fig/os_recon}
+%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_onestep/Fig/os_recon}
 %    \label{fig:os_recon}}\\
-%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_smaller_onestep/Fig/ts_recon}
+%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_onestep/Fig/ts_recon}
 %    \label{fig:ts_recon}}

### 2021-10-17 npef/paper.tex
Sun Oct 17 00:57:31 CDT 2021

@@
 \end{figure}
-%
+
 %\begin{figure}[htb!]
 %   \centering
-%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_onestep/Fig/os_obs}
+%   \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/os_obs}
 %   \label{fig:os_obs}}\\
-%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_onestep/Fig/os_recon}
+%   \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/os_recon}
 %   \label{fig:os_recon}}\\
-%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_onestep/Fig/ts_recon}
+%   \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/ts_recon}
 %   \label{fig:ts_recon}}
-%	\caption{\new{Comparison between the two-step and one-step interpolation strategies.
+%\caption{\new{Comparison between the two-step and one-step interpolation strategies.
 (a) Observed data when binned onto the regular grids of two times denser.
@@
 (c) Reconstructed data by the two-step rank-reduction and NPEF interpolation strategy.}  }
-%	\label{fig:os_obs,os_recon,ts_recon}
+%\label{fig:os_obs,os_recon,ts_recon}
 %\end{figure}
-%
-%
-%\begin{figure}[htb!]
-%    \centering
-%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/zero2d}
-%    \label{fig:zero2d}}\\
-%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/recon2d2}
-%    \label{fig:recon2d2}}\\
-%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/recon2d}
-%    \label{fig:recon2d}}\\
-%	\caption{\new{De-aliased interpolation results of the second field data example for a common shot gather.
+
+\begin{figure}[htb!]
+   \centering
+   \subfloat[]{\includegraphics[width=\textwidth]{real2/Fig/zero2d}
+   \label{fig:zero2d}}\\
+   \subfloat[]{\includegraphics[width=\textwidth]{real2/Fig/recon2d2}
+   \label{fig:recon2d2}}\\
+   \subfloat[]{\includegraphics[width=\textwidth]{real2/Fig/recon2d}
+   \label{fig:recon2d}}\\
+\caption{\new{De-aliased interpolation results of the second field data example for a common shot gather.
 Each gather has bee reshaped into a 2D matrix.
@@
 Note that the rank-reduction method completely fails in this case.}}
-%	\label{fig:zero2d,recon2d2,recon2d}
-%\end{figure}
-%
-%\begin{figure}[htb!]
-%    \centering
-%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/zerofk2d}
-%    \label{fig:zerofk2d}}\\
-%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/reconfk2d2}
-%    \label{fig:reconfk2d2}}\\
-%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/reconfk2d}
-%    \label{fig:reconfk2d}}\\
-%	\caption{\new{FK spectra of de-aliased interpolation results of the second field data example.
+\label{fig:zero2d,recon2d2,recon2d}
+\end{figure}
+
+\begin{figure}[htb!]
+   \centering
+   \subfloat[]{\includegraphics[width=\textwidth]{real2/Fig/zerofk2d}
+   \label{fig:zerofk2d}}\\
+   \subfloat[]{\includegraphics[width=\textwidth]{real2/Fig/reconfk2d2}
+   \label{fig:reconfk2d2}}\\
+   \subfloat[]{\includegraphics[width=\textwidth]{real2/Fig/reconfk2d}
+   \label{fig:reconfk2d}}\\
+\caption{\new{FK spectra of de-aliased interpolation results of the second field data example.
 Each gather has bee reshaped into a 2D matrix.
@@
 (c) Reconstructed data using the NPEF method.}}
-%	\label{fig:zerofk2d,reconfk2d2,reconfk2d}
-%\end{figure}
+\label{fig:zerofk2d,reconfk2d2,reconfk2d}
+\end{figure}
 }

### 2021-10-17 npef/matfun/Real5dos.m

@@ -1,0 +1,74 @@
+function LDRR(dobs,dmask,dout)
+% Author      : Yangkang Chen
+% Date        : Dec, 2020
+
+% Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
+
+%  Copyright (C) 2020 Zhejiang University
+%  Copyright (C) 2020 Yangkang Chen
+%
+%  This program is free software; you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published by
+%  the Free Software Foundation; either version 2 of the License, or
+%  (at your option) any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, write to the Free Software
+%  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307
+
+%%from Madagascar to Matlab
+% create memory
+addpath(genpath('~/chenyk/matlibcyk'));
+
+%fid=fopen('../real5d_smaller/real5d_250_10_10_21_10.bin','r');
+%fidm=fopen('../real5d_smaller/real5d_mask_250_10_10_21_10.bin','r');
+
+%d=fread(fid,[250,10*10*21*10],'float');
+%dm=fread(fidm,[250,10*10*21*10],'float');
+
+load yc_field.mat;
+load yc_field_mask.mat;
+
+[nt,n1,n2,n3,n4]=size(Data5D);
+d0=Data5D;d0=yc_scale(d0(:),1);
+d0=reshape(d0,nt,n1,n2,n3,n4);
+mask=Data5Dmask;
+
+d=d0;
+dm=mask;
+
+
+d=reshape(d,250,10,10,21,10);
+dm=reshape(dm,250,10,10,21,10);
+
+D=zeros(250,20,20,21,10);
+Dm=zeros(250,20,20,21,10);
+D(:,1:2:end,1:2:end,:,:)=d;
+Dm(:,1:2:end,1:2:end,:,:)=dm;
+% for i=1:20
[…]

### 2021-10-17 npef/paper.tex
Sun Oct 17 10:41:06 CDT 2021

@@
 
-%\begin{figure}[htb!]
-%   \centering
-%   \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/os_obs}
-%   \label{fig:os_obs}}\\
-%   \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/os_recon}
-%   \label{fig:os_recon}}\\
-%   \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/ts_recon}
-%   \label{fig:ts_recon}}
-%\caption{\new{Comparison between the two-step and one-step interpolation strategies.
+\begin{figure}[htb!]
+  \centering
+  \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/os_obs}
+  \label{fig:os_obs}}\\
+  \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/os_recon}
+  \label{fig:os_recon}}\\
+  \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/ts_recon}
+  \label{fig:ts_recon}}
+\caption{\new{Comparison between the two-step and one-step interpolation strategies.
 (a) Observed data when binned onto the regular grids of two times denser.
@@
 (c) Reconstructed data by the two-step rank-reduction and NPEF interpolation strategy.}  }
-%\label{fig:os_obs,os_recon,ts_recon}
-%\end{figure}
+\label{fig:os_obs,os_recon,ts_recon}
+\end{figure}
 

### 2021-12-13 ndip/paper.tex
Mon Dec 13 16:40:14 CST 2021

--- 2020-09-16 ndip/ieee.tex
@@
 \maketitle
+
+\published{IEEE TGRS, 86, no. 3, W21-W30, (2021)}
+\title{obust non-stationary local slope estimation}
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+\author{Hang Wang\footnotemark[1], Guangtan Huang\footnotemark[1], and Yangkang Chen\footnotemark[1]}
+
+\address{
+\footnotemark[1]
+School of Earth Sciences\\
+Zhejiang University\\
+Hangzhou, Zhejiang Province, China, 310027\\
+chenyk2016@gmail.com \\}
+
+\righthead{Non-stationary local slope estimation}
 
@@
 
-\begin{keywords}
-Seismic signal analysis, structural filtering, local slope
-\end{keywords}
+%\begin{keywords}
+%Seismic signal analysis, structural filtering, local slope
+%\end{keywords}
 
@@
 The local slope is a seismic attribute that can be extracted from the raw data.
-It has been successfully applied in several geophysical processing and inverse problems, e.g., wavefield separation \cite{harlan1984signal,fomel2002pwd}, predictive painting \cite{fomel2010predictive}, velocity-independent seismic imaging \cite{fomel2007velocity}, regularized geophysical inversion \cite{fomel2007shape}, etc.
+It has been successfully applied in several geophysical processing and inverse problems, e.g., wavefield separation \cite[]{harlan1984signal,fomel2002pwd}, predictive painting \cite[]{fomel2010predictive}, velocity-independent seismic imaging \cite[]{fomel2007velocity}, regularized geophysical inversion \cite[]{fomel2007shape}, etc.
 
@@
 Researchers have started the seismic dip estimation from last century.
-There are at least three-generations methods for calculating the seismic dip \cite{chopra2007volumetric}, e.g., (1) cross-correlation based methods \cite{browaeys2010local,aqrawi2012hybrid,aarre2013consistent}, (2) semblance-based discrete scanning methods \cite{marfurt19983,lou2019accurate}, (3) structure tensor-based methods \cite{hale2007local,wu2017directional,wang2018robust}.}
+There are at least three-generations methods for calculating the seismic dip \cite[]{chopra2007volumetric}, e.g., (1) cross-correlation based methods \cite[]{browaeys2010local,aqrawi2012hybrid,aarre2013consistent}, (2) semblance-based discrete scanning methods \cite[]{marfurt19983,lou2019accurate}, (3) structure tensor-based methods \cite[]{hale2007local,wu2017directional,wang2018robust}.}
 
@@
 The plane-wave destruction (PWD) method was originally proposed by \cite{claerbout1992pvi}.
-Fomel (2002) \cite{fomel2002pwd} proposed to use an implicit finite difference scheme to discretize the plane-wave equation, where an infinite impulse response (IIR) filter (also known as the all-pass filter) to approximate the phase-shift operator and transforms the plane-wave equation into a non-linear inverse problem.
+\cite{fomel2002pwd} proposed to use an implicit finite difference scheme to discretize the plane-wave equation, where an infinite impulse response (IIR) filter (also known as the all-pass filter) to approximate the phase-shift operator and transforms the plane-wave equation into a non-linear inverse problem.
 Hale (2007) \cite{hale2007local} proposed the structure-tensor, also known as the gradient tensor \cite{van1995estimators}, \old{based slope estimation method based}\new{where the slope estimation is based} on the assumption that eigenvector corresponding to the largest eigenvalue of the structure tensor \old{point}\new{points} to the structural direction.
-Liu et al.
-(2015) \cite{liuyang2015} took advantage of the relation between 2D Hilbert transform and the derivatives of the seismic data and derive a fast non-iterative dip estimation method, which turns to be more robust than the PWD based slope estimation method in the case of noisy data \cite{yangkang2018gji3}.
-Chen et al.
-(2013) \cite{zhonghuan2013accelerated} accelerated the PWD method by deriving an analytical solution to the non-linear inverse problem based on the three-point all-pass approximation filter, thus the PWD method no longer requires outer-loop non-linear iterations and thus is significantly accelerated.
-Chen et al.
-(2013) \cite{zhonghuan2013omnidirectional} further improved the conventional PWD algorithm by proposing a circle-interpolating model that makes the PWD method avoid the aliasing issues, thereby well handling both vertical and horizontal structures.
+\cite{liuyang2015} took advantage of the relation between 2D Hilbert transform and the derivatives of the seismic data and derive a fast non-iterative dip estimation method, which turns to be more robust than the PWD based slope estimation method in the case of noisy data \cite{yangkang2018gji3}.
+\cite{zhonghuan2013accelerated} accelerated the PWD method by deriving an analytical solution to the non-linear inverse problem based on the three-point all-pass approximation filter, thus the PWD method no longer requires outer-loop non-linear iterations and thus is significantly accelerated.
+\cite{zhonghuan2013omnidirectional} further improved the conventional PWD algorithm by proposing a circle-interpolating model that makes the PWD method avoid the aliasing issues, thereby well handling both vertical and horizontal structures.
 
 The local slope of a seismic data can be used to compress the seismic events along the slope direction, i.e., to obtain an optimally sparse representation of the seismic data.
-This sparsification process is referred to as the seislet transform \cite{fomel2010seislet}.
+This sparsification process is referred to as the seislet transform \cite[]{fomel2010seislet}.
 Since the seislet transform is based on the structure direction to compress the data, its sparsity in the transform domain highly depends on the accuracy of the estimated local slope.
-Chen (2016) \cite{yangkang2016emd} discussed the influence of the error of local slope estimation in the sparsity performance of the seislet transform, and developed a dip-separated processing strategy to deal with the limitation of the PWD algorithm in the estimation of conflicting dips.
+\cite{yangkang2016emd} discussed the influence of the error of local slope estimation in the sparsity performance of the seislet transform, and developed a dip-separated processing strategy to deal with the limitation of the PWD algorithm in the estimation of conflicting dips.
 
@@
 The basics of the structural filtering is to create a local window along the structural direction and then apply a mean/median filter within this local window.
-\new{Liu et al.
-(2010)} \cite{liuyang2010} proposed a trace-prediction way to create local windows along the structure direction by creating a third dimension with predicted traces following the slope.
-Gan et al.
-(2016) \cite{shuwei2016somf} developed a structure-oriented median filtering method to suppress the blending noise arise from the simultaneous-source acquisition, where the slope is estimated by transforming the NMO-picked velocities to the slope.
-Chen et al.
-(2019) \cite{sosvmf} developed a structure-oriented space-varying median filtering method to deal with the problem of unflattened events in the third  dimension when the slope of seismic data is not accurately estimated.
+\cite{liuyang2010} proposed a trace-prediction way to create local windows along the structure direction by creating a third dimension with predicted traces following the slope.
+\cite{shuwei2016somf} developed a structure-oriented median filtering method to suppress the blending noise arise from the simultaneous-source acquisition, where the slope is estimated by transforming the NMO-picked velocities to the slope.
+\cite{sosvmf} developed a structure-oriented space-varying median filtering method to deal with the problem of unflattened events in the third  dimension when the slope of seismic data is not accurately estimated.
 
 Another important application of slope is to regularize the inversion-based seismic imaging approaches, e.g., the least-squares reverse time migration (LSRTM) and full waveform inversion (FWI).
-Xue et al.
-(2016) \cite{zhiguang2016} developed a constrained LSRTM method to deal with the intense migration artifacts caused by the simultaneous-source shooting or insufficient spatial data sampling, where the smoothing operator along the structural direction is used as a shaping operator to constrain the smoothness of the geological structures.
-Qu et al.
-(2019) \cite{qushan2019geo} developed a directional total variation (DTV) method to constrain the velocity model during the FWI iteration so as to avoid being trapped into a local minimum.
+\cite{zhiguang2016} developed a constrained LSRTM method to deal with the intense migration artifacts caused by the simultaneous-source shooting or insufficient spatial data sampling, where the smoothing operator along the structural direction is used as a shaping operator to constrain the smoothness of the geological structures.
+\cite{qushan2019geo} developed a directional total variation (DTV) method to constrain the velocity model during the FWI iteration so as to avoid being trapped into a local minimum.
 The DTV constraint is equivalent to the rotated traditional total variation following the dip angle of the geological structure.
@@
 Generally speaking, the PWD method has been a well-known slope estimation method in the exploration seismic community.
-However, the low anti-noise ability of the PWD method still limits its wide application in challenging situations where the random noise is strong \cite{curveletieee2016,yanan2014,weilin2017dlsp,shaohuan2018ieee,zhaoqiang2019tgrs,wang2019hankel}.
+However, the low anti-noise ability of the PWD method still limits its wide application in challenging situations where the random noise is strong \cite[]{curveletieee2016,yanan2014,weilin2017dlsp,shaohuan2018ieee,zhaoqiang2019tgrs,wang2019hankel}.
 From the parameter setting perspective, it is usually required to choose a large smoothing radius when dealing with a low signal-to-noise ratio so that the resulted local slope is sufficiently smooth, i.e., avoiding the unstable solution.
@@
 $A(Z_t,Z_x)$ and $H(Z_t,Z_x)$ are two different forms of the plane-wave destruction filter in the Z-transform domain.
-$L(Z_t)/L(1/Z_t)$ is referred to as the Thiran all-pass filter \cite{thiran1971recursive,fomel2002pwd,zhonghuan2013accelerated}.
+$L(Z_t)/L(1/Z_t)$ is referred to as the Thiran all-pass filter \cite[]{thiran1971recursive,fomel2002pwd,zhonghuan2013accelerated}.
 
@@
 \centering
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hyper}
+\subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hyper}
    \label{fig:hyper}}
-   \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hyper-n}
+   \subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hyper-n}
    \label{fig:hyper-n}}
@@
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hyper-dip}
-  \label{fig:hyper-dip}}
-  \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-dip}
-  \label{fig:hypern-dip}}\\
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-dip2}
-  \label{fig:hypern-dip2}}
-  \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-dip3}
-  \label{fig:hypern-dip3}}
-\caption{Slope estimation results.
+%\begin{figure}[htb!]
+%\centering
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hyper-dip}
+%  \label{fig:hyper-dip}}
+%  \subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-dip}
+%  \label{fig:hypern-dip}}\\
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-dip2}
+%  \label{fig:hypern-dip2}}
+%  \subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-dip3}
+%  \label{fig:hypern-dip3}}
+%\caption{Slope estimation results.
 (a) Estimated slope from the clean data with a constant smoothing radius $R=5$.
@@
 }
-\label{fig:hyper-dip,hypern-dip,hypern-dip2,hypern-dip3}
-\end{figure}
+%\label{fig:hyper-dip,hypern-dip,hypern-dip2,hypern-dip3}
+%\end{figure}
 
-\begin{figure}[htb!]
- \centering
- \includegraphics[width=\columnwidth]{hyper/Fig/rectdip1}
-  \caption{Adaptively estimated smoothing radius for non-stationary dip estimation.}
-  \label{fig:rectdip1}
-\end{figure}
+%\begin{figure}[htb!]
+% \centering
+% \includegraphics[width=\columnwidth]{hyper/Fig/rectdip1}
+%  \caption{Adaptively estimated smoothing radius for non-stationary dip estimation.}
+%  \label{fig:rectdip1}
+%\end{figure}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm1}
-   \label{fig:hypern-sm1}}
-   \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm2}
-   \label{fig:hypern-sm2}}\\
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm3}
-   \label{fig:hypern-sm3}}
-   \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm4}
-   \label{fig:hypern-sm4}}\\
-\caption{Smoothing test.
+%\begin{figure}[htb!]
+%\centering
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm1}
+%   \label{fig:hypern-sm1}}
+%   \subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm2}
+%   \label{fig:hypern-sm2}}\\
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm3}
+%   \label{fig:hypern-sm3}}
+%   \subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm4}
+%   \label{fig:hypern-sm4}}\\
+%\caption{Smoothing test.
 (a) Structurally smoothed using the slope estimated from the clean data (SNR=13.73 dB).
@@
 (d) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius (SNR=13.11 dB).}
-\label{fig:hypern-sm1,hypern-sm2,hypern-sm3,hypern-sm4}
-\end{figure}
+%\label{fig:hypern-sm1,hypern-sm2,hypern-sm3,hypern-sm4}
+%\end{figure}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm1-n}
-   \label{fig:hypern-sm1-n}}
-   \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm2-n}
-   \label{fig:hypern-sm2-n}}\\
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm3-n}
-   \label{fig:hypern-sm3-n}}
-   \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm4-n}
-   \label{fig:hypern-sm4-n}}\\
-\caption{Smoothing test. (a)-(d) Removed noise corresponding to Figs. \ref{fig:hypern-sm1}-\ref{fig:hypern-sm4}.}
-\label{fig:hypern-sm1-n,hypern-sm2-n,hypern-sm3-n,hypern-sm4-n}
-\end{figure}
+%\begin{figure}[htb!]
+%\centering
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm1-n}
+%   \label{fig:hypern-sm1-n}}
+%   \subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm2-n}
+%   \label{fig:hypern-sm2-n}}\\
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm3-n}
+%   \label{fig:hypern-sm3-n}}
+%   \subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm4-n}
+%   \label{fig:hypern-sm4-n}}\\
+%\caption{Smoothing test. (a)-(d) Removed noise corresponding to Figs. \ref{fig:hypern-sm1}-\ref{fig:hypern-sm4}.}
+%\label{fig:hypern-sm1-n,hypern-sm2-n,hypern-sm3-n,hypern-sm4-n}
+%\end{figure}
+\inputdir{hyper}
+\multiplot{2}{hyper,hyper-n}{width=0.45\textwidth}{Synthetic test. (a) Clean data. (b) Noisy data (SNR=1.56 dB). }
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-0}
-   \label{fig:g-0}}
-   \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-z-a}
-   \label{fig:g-z-a}}
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-z-b}
-   \label{fig:g-z-b}}
-\caption{Field data example. (a) Raw field data. (b) Zoomed section A. (c) Zoomed section B.}
-\label{fig:g-0,g-z-a,g-z-b}
-\end{figure}
+\multiplot{4}{hyper-dip,hypern-dip,hypern-dip2,hypern-dip3}{width=0.45\textwidth}{Slope estimation results.
+(a) Estimated slope from the clean data with a constant smoothing radius $R=5$.
+(b) Estimated slope from the noisy data with a constant smoothing radius $R=8$.
+(c) Estimated slope from the noisy data with a constant smoothing radius $R=50$.
+(d) Estimated slope from the noisy data with the non-stationary smoothing radius map shown in Fig.
+\ref{fig:rectdip1}.
+Note that (b) and (c) use the smallest and largest smoothing radii of the non-stationary smoothing radius map.
+}
 
-\begin{figure}[htb!]
-\centering
-\includegraphics[width=0.45\textwidth]{real2d/Fig/g-rectdip1}
-\caption{Field data example. Non-stationary smoothing radius.}
-\label{fig:g-rectdip1}
-\end{figure}
+\plot{rectdip1}{width=0.45\textwidth}{Adaptively estimated smoothing radius for non-stationary dip estimation.}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-dip1}
-   \label{fig:g-dip1}}
-   \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-dip2}
-   \label{fig:g-dip2}}
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-dip3}
-   \label{fig:g-dip3}}
-\caption{Smoothing test of the field data example.
+\multiplot{4}{hypern-sm1,hypern-sm2,hypern-sm3,hypern-sm4}{width=0.45\textwidth}{Smoothing test.
+(a) Structurally smoothed using the slope estimated from the clean data (SNR=13.73 dB).
+(b) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius (SNR=11.80 dB).
+(c) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius (SNR=10.71 dB).
+(d) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius (SNR=13.11 dB).}
+
+\multiplot{4}{hypern-sm1-n,hypern-sm2-n,hypern-sm3-n,hypern-sm4-n}{width=0.45\textwidth}{Smoothing test. (a)-(d) Removed noise corresponding to Figs. \ref{fig:hypern-sm1}-\ref{fig:hypern-sm4}.}
+
+%\begin{figure}[htb!]
+%\centering
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-0}
+%   \label{fig:g-0}}
+%   \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-z-a}
+%   \label{fig:g-z-a}}
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-z-b}
+%   \label{fig:g-z-b}}
+%\caption{Field data example. (a) Raw field data. (b) Zoomed section A. (c) Zoomed section B.}
+%\label{fig:g-0,g-z-a,g-z-b}
+%\end{figure}
+
+%\begin{figure}[htb!]
+%\centering
+%\includegraphics[width=0.45\textwidth]{real2d/Fig/g-rectdip1}
+%\caption{Field data example. Non-stationary smoothing radius.}
+%\label{fig:g-rectdip1}
+%\end{figure}
+%
+
+%\begin{figure}[htb!]
+%\centering
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-dip1}
+%   \label{fig:g-dip1}}
+%   \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-dip2}
+%   \label{fig:g-dip2}}
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-dip3}
+%   \label{fig:g-dip3}}
+%\caption{Smoothing test of the field data example.
 (a) Slope estimated from the noisy data with a small constant smoothing radius $R=8$.
@@
 (c) Slope estimated from the noisy data with non-stationary smoothing radius.}
-\label{fig:g-dip1,g-dip2,g-dip3}
-\end{figure}
+%\label{fig:g-dip1,g-dip2,g-dip3}
+%\end{figure}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-0}
-  \label{fig:g-sm1-0}}
-  \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-0}
-  \label{fig:g-sm2-0}}
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-0}
-  \label{fig:g-sm3-0}}
-\caption{Smoothing test of the field data example.
+%\begin{figure}[htb!]
+%\centering
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-0}
+%  \label{fig:g-sm1-0}}
+%  \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-0}
+%  \label{fig:g-sm2-0}}
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-0}
+%  \label{fig:g-sm3-0}}
+%\caption{Smoothing test of the field data example.
 (a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius.
@@
 (c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius.}
-\label{fig:g-sm1-0,g-sm2-0,g-sm3-0}
-\end{figure}
+%\label{fig:g-sm1-0,g-sm2-0,g-sm3-0}
+%\end{figure}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-n}
-  \label{fig:g-sm1-n}}
-  \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-n}
-  \label{fig:g-sm2-n}}
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-n}
-  \label{fig:g-sm3-n}}
-\caption{Smoothing test of the field data example. (a)-(c) Removed noise corresponding to Figs. \ref{fig:g-sm1-0}-\ref{fig:g-sm3-0}.}
-\label{fig:g-sm1-n,g-sm2-n,g-sm3-n}
-\end{figure}
+%\begin{figure}[htb!]
+%\centering
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-n}
+%  \label{fig:g-sm1-n}}
+%  \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-n}
+%  \label{fig:g-sm2-n}}
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-n}
+%  \label{fig:g-sm3-n}}
+%\caption{Smoothing test of the field data example. (a)-(c) Removed noise corresponding to Figs. \ref{fig:g-sm1-0}-\ref{fig:g-sm3-0}.}
+%\label{fig:g-sm1-n,g-sm2-n,g-sm3-n}
+%\end{figure}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-z-a0}
- \label{fig:g-sm1-z-a0}}
- \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-z-a0}
- \label{fig:g-sm2-z-a0}}
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-z-a0}
- \label{fig:g-sm3-z-a0}}
-\caption{Zoomed comparison of the field data example (frame box A).
+%\begin{figure}[htb!]
+%\centering
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-z-a0}
+% \label{fig:g-sm1-z-a0}}
+% \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-z-a0}
+% \label{fig:g-sm2-z-a0}}
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-z-a0}
+% \label{fig:g-sm3-z-a0}}
+%\caption{Zoomed comparison of the field data example (frame box A).
 (a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius.
@@
 (c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius.}
-\label{fig:g-sm1-z-a0,g-sm2-z-a0,g-sm3-z-a0}
-\end{figure}
+%\label{fig:g-sm1-z-a0,g-sm2-z-a0,g-sm3-z-a0}
+%\end{figure}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-z-b0}
-  \label{fig:g-sm1-z-b0}}
-  \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-z-b0}
-  \label{fig:g-sm2-z-b0}}
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-z-b0}
-  \label{fig:g-sm3-z-b0}}
-\caption{Zoomed comparison of the field data example (frame box B).
+%\begin{figure}[htb!]
+%\centering
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-z-b0}
+%  \label{fig:g-sm1-z-b0}}
+%  \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-z-b0}
+%  \label{fig:g-sm2-z-b0}}
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-z-b0}
+%  \label{fig:g-sm3-z-b0}}
+%\caption{Zoomed comparison of the field data example (frame box B).
 (a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius.
@@
 (c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius.}
-\label{fig:g-sm1-z-b0,g-sm2-z-b0,g-sm3-z-b0}
-\end{figure}
+%\label{fig:g-sm1-z-b0,g-sm2-z-b0,g-sm3-z-b0}
+%\end{figure}
+
+\inputdir{real2d}
+\multiplot{3}{g-0,g-z-a,g-z-b}{width=0.45\textwidth}{Field data example. (a) Raw field data. (b) Zoomed section A. (c) Zoomed section B.}
+
+\plot{g-rectdip1}{width=0.45\textwidth}{Field data example. Non-stationary smoothing radius.}
+
+\multiplot{3}{g-dip1,g-dip2,g-dip3}{width=0.45\textwidth}{Smoothing test of the field data example.
+(a) Slope estimated from the noisy data with a small constant smoothing radius $R=8$.
+(b) Slope estimated from the noisy data with a large constant smoothing radius $R=100$.
+(c) Slope estimated from the noisy data with non-stationary smoothing radius.}
+
+\multiplot{3}{g-sm1-0,g-sm2-0,g-sm3-0}{width=0.45\textwidth}{Smoothing test of the field data example.
+(a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius.
+(b) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius.
+(c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius.}
+
+\multiplot{3}{g-sm1-n,g-sm2-n,g-sm3-n}{width=0.45\textwidth}{Smoothing test of the field data example. (a)-(c) Removed noise corresponding to Figs. \ref{fig:g-sm1-0}-\ref{fig:g-sm3-0}.}
+
+\multiplot{3}{g-sm1-z-a0,g-sm2-z-a0,g-sm3-z-a0}{width=0.45\textwidth}{Zoomed comparison of the field data example (frame box A).
+(a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius.
+(b) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius.
+(c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius.}
+
+\multiplot{3}{g-sm1-z-b0,g-sm2-z-b0,g-sm3-z-b0}{width=0.45\textwidth}{Zoomed comparison of the field data example (frame box B).
+(a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius.
+(b) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius.
+(c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius.}
 
@@
 \new{In equation \ref{eq:linear}, the shaping operator is chosen as $\mathbf{S}=\mathbf{T}\mathbf{T}^T$.
-$\lambda$ is a scaling parameter that controls the relative scaling of the forward operator $\mathbf{J}$ \cite{fomel2007shape}.
+$\lambda$ is a scaling parameter that controls the relative scaling of the forward operator $\mathbf{J}$ \cite[]{fomel2007shape}.
 } The triangle smoothing operator takes the following form in the Z transform domain:
@@
 \end{equation}}
-where $O$ denotes the objective function of the optimization problem \cite{greer2018matching}.
-$\mathcal{L}$ denotes a local attribute estimator, e.g., the local frequency attribute \cite{fomel2007localattr}, $\mathbf{T}(\mathbf{n})$ denotes the triangle smoothing operator that is a function of the non-stationary smoothing radius vector $\mathbf{n}$, $\mathbf{d}$ denotes the input data, and $\mathbf{d}_B$ denotes a lowpass filter\new{, where the cut-off frequency could be chosen as the dominant frequency of the seismic data}.
+where $O$ denotes the objective function of the optimization problem \cite[]{greer2018matching}.
+$\mathcal{L}$ denotes a local attribute estimator, e.g., the local frequency attribute \cite[]{fomel2007localattr}, $\mathbf{T}(\mathbf{n})$ denotes the triangle smoothing operator that is a function of the non-stationary smoothing radius vector $\mathbf{n}$, $\mathbf{d}$ denotes the input data, and $\mathbf{d}_B$ denotes a lowpass filter\new{, where the cut-off frequency could be chosen as the dominant frequency of the seismic data}.
 %The idea is similar to that was proposed in , where the low-frequency legacy seismic data is merged to the high-resolution data with a non-stationary smoothing.
@@
 \ref{fig:hyper,hyper-n} with the clean data on the left and the noisy data on the right.
-The signal-to-noise ratio (SNR) of the noisy data is 1.56 dB, based on the definition expressed below \cite{benfeng2019efficient}:
+The signal-to-noise ratio (SNR) of the noisy data is 1.56 dB, based on the definition expressed below \cite[]{benfeng2019efficient}:
 \begin{equation}
@@
 Then, to compare the accuracy of the estimated local slope maps, we conduct a structure-oriented smoothing test.
-In the structure-oriented smoothing method \cite{sosvmf}, we first flat the seismic data based on a trace prediction strategy, and then apply a common triangle smoothing operator to the flattened dimension.
+In the structure-oriented smoothing method \cite[]{sosvmf}, we first flat the seismic data based on a trace prediction strategy, and then apply a common triangle smoothing operator to the flattened dimension.
 The smoothed data using the four slope maps (Fig.
@@
 
-\begin{figure}[htb!]
-\centering
-\includegraphics[width=0.45\textwidth]{real3d/Fig/real}
-\caption{\new{3D field data example.} }
-\label{fig:real}
-\end{figure}
+%\begin{figure}[htb!]
+%\centering
+%\includegraphics[width=0.45\textwidth]{real3d/Fig/real}
+%\caption{\new{3D field data example.} }
+%\label{fig:real}
+%\end{figure}
+%
+%\begin{figure}[htb!]
+%\centering
+%\includegraphics[width=0.45\textwidth]{real3d/Fig/rect1}
+%\caption{\new{3D field data example. Non-stationary smoothing radius.}}
+%\label{fig:rect1}
+%\end{figure}
+%
 
-\begin{figure}[htb!]
-\centering
-\includegraphics[width=0.45\textwidth]{real3d/Fig/rect1}
-\caption{\new{3D field data example. Non-stationary smoothing radius.}}
-\label{fig:rect1}
-\end{figure}
-
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-s2dip1}
-   \label{fig:real-s2dip1}}
-   \subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-s1dip1}
-   \label{fig:real-s1dip1}}
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-ndip1}
-   \label{fig:real-ndip1}}
-\caption{\new{Slope comparison of the 3D field data example.
+%\begin{figure}[htb!]
+%\centering
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-s2dip1}
+%   \label{fig:real-s2dip1}}
+%   \subfloat[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-s1dip1}
+%   \label{fig:real-s1dip1}}
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-ndip1}
+%   \label{fig:real-ndip1}}
+%\caption{\new{Slope comparison of the 3D field data example.
 (a) Slope estimated from the noisy data with a small constant smoothing radius $R=2$.
@@
 (c) Slope estimated from the noisy data with non-stationary smoothing radius.}}
-\label{fig:real-s2dip1,real-s1dip1,real-ndip1}
-\end{figure}
+%\label{fig:real-s2dip1,real-s1dip1,real-ndip1}
+%\end{figure}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws2-0}
-  \label{fig:real-pws2-0}}
-  \subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws2-0}
-  \label{fig:real-pws2-0}}
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws3-0}
-  \label{fig:real-pws3-0}}
-\caption{\new{Smoothing test of the field data example.
+%\begin{figure}[htb!]
+%\centering
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws2-0}
+%  \label{fig:real-pws2-0}}
+%  \subfloat[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws2-0}
+%  \label{fig:real-pws2-0}}
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws3-0}
+%  \label{fig:real-pws3-0}}
+%\caption{\new{Smoothing test of the field data example.
 (a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius.
@@
 Note the difference highlighted by the arrows.}}
-\label{fig:real-pws2-0,real-pws1-0,real-pws3-0}
-\end{figure}
+%\label{fig:real-pws2-0,real-pws1-0,real-pws3-0}
+%\end{figure}
 
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws2-n-0}
-  \label{fig:real-pws2-n-0}}
-  \subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws1-n-0}
-  \label{fig:real-pws1-n-0}}
-\subfigure[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws3-n-0}
-  \label{fig:real-pws3-n-0}}
-\caption{\new{Smoothing test of the field data example. (a)-(c) Removed noise corresponding to Figs. \ref{fig:real-pws2-0}-\ref{fig:real-pws3-0}. Note the difference highlighted by the arrows.}}
-\label{fig:real-pws2-n-0,real-pws1-n-0,real-pws3-n-0}
-\end{figure}
+%\begin{figure}[htb!]
+%\centering
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws2-n-0}
+%  \label{fig:real-pws2-n-0}}
+%  \subfloat[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws1-n-0}
+%  \label{fig:real-pws1-n-0}}
+%\subfloat[]{\includegraphics[width=0.45\textwidth]{real3d/Fig/real-pws3-n-0}
+%  \label{fig:real-pws3-n-0}}
+%\caption{\new{Smoothing test of the field data example. (a)-(c) Removed noise corresponding to Figs. \ref{fig:real-pws2-0}-\ref{fig:real-pws3-0}. Note the difference highlighted by the arrows.}}
+%\label{fig:real-pws2-n-0,real-pws1-n-0,real-pws3-n-0}
+%\end{figure}
+
+\inputdir{real3d}
+
+\plot{real}{width=0.45\textwidth}{\new{3D field data example.} }
+
+\plot{rect1}{width=0.45\textwidth}{\new{3D field data example. Non-stationary smoothing radius.}}
+
+\multiplot{3}{real-s2dip1,real-s1dip1,real-ndip1}{width=0.45\textwidth}{\new{Slope comparison of the 3D field data example.
+(a) Slope estimated from the noisy data with a small constant smoothing radius $R=2$.
+(b) Slope estimated from the noisy data with a large constant smoothing radius $R=20$.
+(c) Slope estimated from the noisy data with non-stationary smoothing radius.}}
+
+\multiplot{4}{real-pws2-0,real-pws1-0,real-pws3-0}{width=0.45\textwidth}{\new{Smoothing test of the field data example.
+(a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius.
+(b) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius.
+(c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius.
+Note the difference highlighted by the arrows.}}
+
+\multiplot{4}{real-pws2-n-0,real-pws1-n-0,real-pws3-n-0}{width=0.45\textwidth}{\new{Smoothing test of the field data example.
+(a)-(c) Removed noise corresponding to Figs.
+\ref{fig:real-pws2-0}-\ref{fig:real-pws3-0}.
+Note the difference highlighted by the arrows.}}
 
@@
 
-\bibliographystyle{IEEEtran}
+\bibliographystyle{seg}
 \bibliography{dip}
@@
 %	\centering
-%	\subfigure[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
+%	\subfloat[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
 %	\caption{Caption.}
@@
 %	\centering
-%	\subfigure[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}}\\
-%    \subfigure[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}}
+%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}}\\
+%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}}
 %	\caption{(a) Caption a. (b) Caption b.}

### 2022-01-02 diffrlrra3d/paper.tex
Sat Jan  1 22:12:43 CST 2022

\documentclass[10pt]{IEEEtran}
\usepackage{amsmath}
\usepackage{cite}
\usepackage{ifthen}
\usepackage{seg}
\usepackage{color}
\usepackage{graphicx}
\usepackage{subfigure}

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}
\DeclareRobustCommand{\old}[1]{}
\DeclareRobustCommand{\new}[1]{#1}

\begin{document}

\title{3D seismic diffraction separation and imaging using the local rank-reduction method}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Wei Chen, Xingye Liu, Omar M. Saad, Yapo Abol{\'e} Serge Innocent Obou{\'e}, Liuqing Yang, Hang Wang, and Yangkang Chen
\thanks{W. Chen is with Cooperative Innovation Center of Unconventional Oil and Gas (Ministry of Education \& Hubei Province), Yangtze University, Wuhan, 430100, China, and Key Laboratory of Exploration Technologies for Oil and Gas Resources of Ministry of Education, Yangtze University, Wuhan, 430100, China}
\thanks{X. Liu is with Chengdu University of Technology, Dongsanlu, Erxianqiao, Chengdu, 610059, China.}
\thanks{O.M. Saad is with Seismology Department, National Research Institute of Astronomy and Geophysics (NRIAG), Helwan, 11731, Egypt.}
\thanks{Y.A.S.I. Oboue and H. Wang are with School of Earth Sciences, Zhejiang University, Hangzhou, 310027, China.}
\thanks{L. Yang is with State Key Laboratory of Petroleum Resource and Prospecting, China University of Petroleum (Beijing), Beijing, 102200, China.}
\thanks{Y. Chen is with Bureau of Economic Geology, Jackson School of Geosciences, The University of Texas at Austin, Austin, Texas, 78713-8924, USA.}
\thanks{The research is supported by the National Natural Science Foundation of China (Grant No. 41804140) and the Open Fund of Cooperative Innovation Center of Unconventional Oil and Gas, Yangtze University (Ministry of Education \& Hubei Province) (Grant No. UOG2021-01).}}

\maketitle

\begin{abstract}
Diffractions in the seismic data are associated with the small-scale subsurface structures, thus their separation and imaging are helpful in characterizing the underground discontinuities with a high resolution that cannot be reached by traditional reflection imaging methods. Traditional seismic slope-based diffraction separation methods are strongly affected by the accuracy and stability of the slope estimation methods, e.g., the plane-wave destruction (PWD) method. When the local seismic slope is not properly estimated, the separated seismic diffraction waves suffer from the mixture between the reflection and diffraction energy due to their coupling in the slope map. We propose an automatic local rank-reduction (LRR) method to separate 3D diffraction waves from zero-offset seismic data, based on which we conduct 3D migration to output the diffraction images. Due to the difficulty in choosing the rank in each local 3D window, we apply an adaptive strategy to obtain the optimal rank. The proposed LRR method with adaptively selected ranks (LRRA) is applied to several 3D synthetic and field data examples and demonstrated to perform better than the traditional PWD, the LRR, and the global rank-reduction (GRR) methods. 
\end{abstract}

\begin{keywords}
Seismic signal separation, seismic denoising, seismic imaging, seismic diffraction
\end{keywords}

\section{Introduction}
Seismic data contain various useful information that can reflect the geologic features of the subsurface \cite{shucai2020,guoyin2018}. In general, reflections are generated by large-scale geologic objects that are continuous and have smooth-reflecting boundaries, and their energy in the seismic records is relatively strong \cite{2010Imaging, Peng2018Accurate}. 
Reflections are preserved in conventional seismic exploration workflow, and are the most commonly used signals to detect large-scale geologic structures. 
However, it is difficult to recognize small-scale geologic structures  (faults, small-size scattering points, and reflector edges, etc.) by using reflections. 
These small-scale geologic bodies will scatter the energy that is expressed as diffractions in the seismic records, which are destroyed or removed by the traditional seismic processing techniques.
However, diffractions are helpful to find unconventional reservoirs of oil and gas because they are associated with small-scale discontinuous objects \cite{2016Diffraction, 2020Separation}.

Researchers use seismic diffraction to detect subsurface discontinuities, provided that the seismic diffraction is separated from the original data.  
Nevertheless, it is a challenge because the energy of diffractions is weaker compared with the strong energy of reflections, which can even reach several orders of magnitude, i.e., diffractions are usually masked by reflections and noise \cite{1994Theory, 2007Post,omar2020geo1}. 
One of the most widely used methods is the path-summation-based method that uses the kinematic differences to separate reflections and diffractions. Based on the coherent summation of diffracted events according to the traveltime, \cite{1987A} and \cite{1988Imaging} achieve diffraction separation and imaging in common-offset and common-midpoint domains, respectively. 
\cite{2004Diffraction} separate and mute the reflection in the pseudodepth domain  by using the difference in properties of waves.
The most known diffraction separation and imaging method is based on a common-reflection-surface method that has been extended by many geophysicists.
 One of the advantages is that this method using several common midpoints to stack based on ray theory \cite{2013Recovering}.
\cite{2009Diffraction} propose a multi-focusing algorithm to focus diffractions while scattering reflections.
Similarly, \cite{2011Common} use the common-reflection-surface approach to achieve diffraction imaging.
\cite{2012Separation} achieve diffraction imaging in the migrated dip-angle domain and pointed out that it was more advantageous to separate diffraction from seismic data. \cite{2013Diffraction} propose a method that can adaptively choose parameters to fit the diffraction trvaltime and accelerate the computation.
\cite{Coimbra2018Enhancement} improve the accuracy of diffraction separation by a finite-offset double-square equation, and extended a fast version without losing accuracy.
\cite{2018Fast} develop a robust and fast method to extract the parameters of common-reflection-surface by using the local slope attribute, and it could be used for the diffraction separation. 
\cite{2018Common} point out that wavefront attributes of pre-stack seismic data could improve the illumination and are more appropriate for diffraction separation.
\cite{20193D} construct a new traveltime difference gather to flatten the diffraction, then muted the upward reflection.
For post-stack seismic data, \cite{2019Coherent} uses many wavefront filters to separate reflections and diffractions, and demonstrated its superiority in extracting diffractions masked by strong reflections.

Another effective diffraction separation and imaging method is based on the plane-wave destruction (PWD) proposed by \cite{Sergey2002Applications} and  \cite{2007Post}. Traveltimes of diffractions are quasi-hyperbolic-shaped while those of reflections are laterally continuous in the constant plane-wave slope sections. Thus, reflections can be predicted from neighbor traces by using a prediction-error filter. Then, the predicted reflection is suppressed and the diffraction is extracted.  After that, diffractions are migrated by selecting an optimal velocity. That is to say, the PWD-based method can simultaneously achieve velocity estimation and diffraction imaging \cite{2011Azimuthally}. 
\cite{2013Coal} utilize the PWD-based diffraction imaging method to detect the fractures in coals.
\cite{Binzhong2018seismic} propose a local moving-average-error-filter to achieve diffraction separation and applied it to coal structures detection. 
\cite{2018l1} developed an improved PWD-based method via wavelet transform and L1-norm, and achieved accurate diffraction separation.
The PWD-based method depends on the local slopes, thus a wide range of approaches are developed to accurately estimate the local slopes, such as \cite{2008Separation, 2010Nonlinear, 2018Dip}.
\cite{2020Least} achieve the diffraction separation by establishing an inversion objection and combining the PWD algorithm with other advanced techniques, such as Kirchhoff modeling, and path-summation-based methods.

Most diffraction separation and imaging methods only take kinematic features of diffractions and reflections into consideration, and the dynamic differences between diffractions and reflections are ignored. However, the dynamic discrepancy is significant to diffraction imaging \cite{2015Diffraction, 20193D, 2020Diffraction}.
\cite{2014Diffraction} update migration velocities according to shapes of reflections and diffractions in the migrated gathers by picking the angles related to reflections in the shot and opening-angle gathers, improving the accuracy.
\cite{2015Diffraction} develop a least-squares fitting method by using double exponential functions to analyze the amplitude function of diffracted waves and improve the performance of diffraction separation.
\cite{2016Imaging} develop a three-step diffraction separation and imaging approach based on wave-equation. It is computationally fast and resistant to random noise.
Based on the fact that the dip direction of reflectors could not be observed in both left- and right-downgoing propagating waves, \cite{2019Efficient} develop an efficient wave-equation-based approach for diffraction separation.
In frequency-wavenumber domain, \cite{2020Inspiration} use a double square root equation to simulate diffractions, and separated diffractions by using dip frequency filters.
To improve the image quality of diffractions, \cite{2020Periodic} propose a periodic plane-wave least-squares reverse time migration method.
\cite{2021Diffraction} applies a diffraction-angle filtering method to the virtual source in the acoustic full-waveform inversion to separate energy of reflections and transmissions. Diffractions can be separated by designing many types of diffraction-angle filters.

Consequently, both kinematic and dynamic differences between reflections and diffractions are important for seismic diffraction separation and imaging. Jointly using kinematic and dynamic properties of wave fields is helpful for diffraction separation and imaging \cite{2010Separation}. 
\cite{2020Separation} propose a 2D diffraction separation method based on a local rank-reduction algorithm, in which the rank is optimized by an adaptive selection approach.  \cite{2020Diffraction} utilize the multichannel singular-spectrum  analysis (MSSA) for diffraction separation and imaging. Their implementation of the MSSA method does not consider the strong non-stationarity of seismic data and thus does not use local windows for the diffraction separation, which is referred to as a global rank-reduction (GRR) method. In the post-stack domain, these two methods make full use of kinematic and dynamic differences between reflections and diffractions. Besides, these methods were tested on 2D seismic data. For 3D data, the complexity would increase and a unique rank value is unsatisfactory for accurate diffraction separation and imaging. 
Therefore, we present a novel method based on the local rank-reduction (LRR) method for 3D seismic diffraction separation. Both kinematic and dynamic properties are considered. The rank-reduction filter is carried out in each local window to enhance the performance \cite{shaohuan2017gji,yangkang2017ieee,yangkang2019nc}. In this case, specifying an appropriate rank for different windows is necessary to make the result more promising. Due to the rank inconsistency,  we propose an automatic selection approach to locally optimize the rank at different locations, which is not essential in the global strategy.

First, we describe the principles of the LRR method for 3D seismic data. Secondly, we introduce the automatic scheme for selecting local ranks in each window. Then, some 3D seismic data examples are tested and analyzed in detail to illustrate the advantages of the proposed method. Finally, we discuss the new method from several important aspects and draw some key conclusions.

\begin{figure}[htb!]
\centering
\includegraphics[width=\columnwidth]{Fig/demosigma}
\caption{Singular value distribution. (a) 3D reflection data containing three plane waves. (b) 3D seismic data containing reflections, diffractions and random noise. (c) 2D section extracted from (a). (d) 2D section extracted from (b). (e) Singular values distribution of the Hankel matrix in the 20 Hz slice of the data shown in (a).  (f) Singular values distribution of the data shown in (b). }
\label{fig:demosigma}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/refl}
   \label{fig:refl}}
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/diffr}
   \label{fig:diffr}}   
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/syn}
   \label{fig:syn}}    
\caption{Benchmark dataset with groundtruth reflections and diffractions. (a) Reflection data. (b) Diffraction data. (c) Synthetic data. }
\label{fig:refl,diffr,syn}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-pwd-0}
   \label{fig:s-pwd-0}}
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-grr-0}
   \label{fig:s-grr-0}}   
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-lrra-0}
   \label{fig:s-lrra-0}}    
\caption{Separated reflections using (a) PWD method, (b) global rank-reduction method, and (c) proposed method.}
\label{fig:s-pwd-0,s-grr-0,s-lrra-0}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-pwd-n-0}
   \label{fig:s-pwd-n-0}}
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-grr-n-0}
   \label{fig:s-grr-n-0}}   
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-lrra-n-0}
   \label{fig:s-lrra-n-0}}    
\caption{Separated diffractions using (a) PWD method (SNR=6.52 dB), (b) global rank-reduction method (SNR=1.42 dB), and (c) proposed method (SNR=9.14 dB).}
\label{fig:s-pwd-n-0,s-grr-n-0,s-lrra-n-0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-pwd-e-0}
  \label{fig:s-pwd-e-0}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-grr-e-0}
  \label{fig:s-grr-e-0}}   
\subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-lrra-e-0}
  \label{fig:s-lrra-e-0}}    
\caption{\new{Error of separated diffractions using (a) PWD method, (b) global rank-reduction method, and (c) proposed method.} \color{black}{}}
\label{fig:s-pwd-e-0,s-grr-e-0,s-lrra-e-0}
\end{figure}

\section*{THEORY AND Methods}
Diffraction separation can be regarded as a problem of seismic data reconstruction, in which diffractions are treated as effective signals while reflections are treated as noise.  In the post-stack seismic data, reflections appear as locally linear events, while diffractions behave as hyperbolic events.  The rank-reduction method can utilize the kinematic differences between diffractions and reflections to separate different components. Besides, the energy of diffractions is much weaker than that of reflections, thereby corresponding to different singular values and singular vectors. The distributions of singular values for diffractions and reflections are assumed to be disparate in the singular-value spectrum. Therefore, the contribution of the last few singular values is the smallest, while the first few singular values contribute more to reconstructing the data. The rank-reduction method also considers the energy discrepancy, i.e., the dynamic differences, to separate weak diffractions and strong reflections \cite{2010Separation, 2016Diffraction}.

\subsection{Local rank-reduction method}
Let a 3D seismic data be denoted by $S(x, y, t)$, $x=1,\cdots, N_x$, $y=1,\cdots, N_y$, and $t=1,\cdots, N_t$, where $N_x$, $N_y$ and $N_t$ represent the numbers of samples in spatial and time axes, respectively. The rank-reduction method \cite{2011Simultaneous,weilin2016dmssa} is implemented in the frequency domain, thus the first step is to obtain the corresponding frequency-domain data $S(x, y,f )$  by forward Fourier transform $\mathcal{F}$. For a given frequency $f_0$, we construct the block Hankel matrix $\mathbf{{H}}$ by mapping the frequency-domain data into several Hankel matrices $\mathbf{\widetilde{H}}_i(f_0)$ through the Hankelization operator $\mathcal{H}$. Then, we can obtain,
\begin{align} \label{eq:B} 
\mathbf{{H}}=
\begin{bmatrix}
\mathbf{\widetilde{H}}_1(f_0)&\mathbf{\widetilde{H}}_2(f_0)&\cdots&\mathbf{\widetilde{H}}_{n_x}(f_0)\\
\mathbf{\widetilde{H}}_2(f_0)&\mathbf{\widetilde{H}}_3(f_0)&\cdots&\mathbf{\widetilde{H}}_{n_x+1}(f_0)\\
\vdots&\vdots&\ddots&\vdots\\
\mathbf{\widetilde{H}}_{m_x}(f_0)&\mathbf{\widetilde{H}}_{m_x+1}(f_0)&\cdots&\mathbf{\widetilde{H}}_{m_x}(f_0)
\end{bmatrix}
,
\end{align}
where, 
\begin{align} \label{eq:Hif} 
&\mathbf{\widetilde{H}}_i(f_0)=\\
&\begin{bmatrix}
S(i,1,f_0)&S(i,2,f_0)&\cdots&S(i,n_y,f_0)\\
S(i,2,f_0)&S(i,3,f_0)&\cdots&S(i,n_y+1,f_0)\\
\vdots&\vdots&\ddots&\vdots\\
S(i,m_y,f_0)&S(i,m_y+1,f_0)&\cdots&S(i,N_y,f_0)
\end{bmatrix}
,
\end{align}
$m_x=\text{INT}(N_x/2)+1$ and $n_x=N_x-m_x+1$ are the key parameters to make the block Hankel matrix close to a square matrix. Similarly, $m_y=\text{INT}(N_y/2)+1$ and $n_y=N_y-m_y+1$.  $\text{INT}(\cdot)$ represents the integer part of an argument.

\cite{Zheng2014A} point out that the component with strong energy corresponds to a large singular value, i.e., the strong signals correspond to large singular values. On the contrary, the smaller singular values represent the energy of diffractions and noise. 
It is straightforward to infer that the largest singular values of block Hankel matrix represent the reflections.  If we can obtain the reflection wave $\mathbf{R}$ by extracting the corresponding singular values and vectors, then the diffraction wave $\mathbf{D}$ can be obtained by subtracting $\mathbf{R}$ from the data $\mathbf{S}$,
\begin{equation}\label{eq:dsr}
\mathbf{D}=\mathbf{S}-\mathbf{R}.
\end{equation}

Thus, the problem of diffraction separation is transformed into estimating the reflection, which can be addressed by applying the singular-value decomposition (SVD) algorithm to the block Hankel matrix \cite{Chen2016An}. In particular, truncated singular-value decomposition (TSVD) is usually used to suppress the noise. The TSVD of block Hankel matrix is expressed as
\begin{equation} \label{eq:svd}
\mathbf{\hat{H}}=\mathbf{U}\mathbf{\Sigma}\mathbf{V}^T,
\end{equation}
where $\mathbf{\hat{H}}$ denotes the denoised block Hankel matrix, i.e., the noise can be suppressed by ignoring some smaller singular values \cite{2020Diffraction}.  $\mathbf{\Sigma}=[{\sigma}_1,{\sigma}_2,\cdots,{\sigma}_N]$ is the diagonal singular matrix, $\mathbf{U}=[\mathbf{u}_1,\mathbf{u}_2,\cdots,\mathbf{u}_N]$ and $\mathbf{V}=[\mathbf{v}_1,\mathbf{v}_2,\cdots,\mathbf{v}_N]$ are left and right singular matrices, respectively. They are made up of singular vectors $\mathbf{u}_j$ and $\mathbf{v}_j$. $\sigma_j$ denotes the $j$th singular value, and $N$ denotes the number of singular values.

Then, we can reconstruct the block Hankel matrix of reflections $\mathbf{H}_R$ by selecting an appropriate rank $R$, which will be introduced in detail in the following section. After that, the inverse Hankelization operator $\mathcal{H}^{-1}$ and inverse Fourier transform $\mathcal{F}^{-1}$ are implemented to obtain reflections in time-domain. 
The processes can be expressed as,
%\begin{equation}
%\begin{array}{c}
\begin{align}\label{eq:rtime}
\begin{split}
\mathbf{R}&= \mathcal{F}^{-1} \mathcal{H}^{-1}\mathbf{H}_R\\ 
&= \mathcal{F}^{-1} \mathcal{H}^{-1}\mathcal{T}\mathbf{\hat{H}}\\ 
&= \mathcal{F}^{-1} \mathcal{H}^{-1}\mathcal{T}\mathcal{H}\mathbf{S}_F\\ 
&=\mathcal{F}^{-1} \mathcal{H}^{-1} \mathcal{T}\mathcal{H}\mathcal{F}\mathbf{S}, 
\end{split}
\end{align}
%\end{array}
%,
%\end{equation}
where $\mathcal{T}$ represents the principal component extraction operator, $\mathbf{S}$ and $\mathbf{S}_F$ represent the data in time- and frequency-domain, respectively. The reconstructed block Hankel matrix of reflections $\mathbf{H}_R$ is given by,
\begin{equation}\label{eq:HR}
\mathbf{H}_R=\mathcal{T}\mathbf{\hat{H}}=\sum^R \limits_{r=1} {\sigma}_r\mathbf{u}_r\mathbf{v}_r^\text{T}.
\end{equation}

It can seen from equation \ref{eq:HR} that it is important to determine whether the  singular value corresponds to diffraction or reflection, i.e., selecting appropriate rank values for rank reduction, especially for the singular values near the intersection of reflections and diffractions. Since the assumption of plane waves is only satisfied locally, it is advisable to perform the rank reduction in local windows to boost the performance for the complexity of 3D seismic data, i.e., the LRR method. Let $\mathcal{W}$ and $\mathcal{W}^{-1}$ represent the windowing and reconstruction operators, then the reconstructed reflections by using LRR can be written in operator notation as,
\begin{equation} \label{eq:wr}
\mathbf{R}=\mathcal{W}^{-1}\mathcal{F}^{-1} \mathcal{H}^{-1} \mathcal{T}\mathcal{H}\mathcal{F}\mathcal{W}\mathbf{S}.
\end{equation}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.6\columnwidth]{plot/Fig/ovp}
   \label{fig:ovp}}
 \subfigure[]{\includegraphics[width=0.6\columnwidth]{plot/Fig/o}
   \label{fig:o}}     
\caption{(a) Velocity model of the first synthetic example. (b) Zero-offset data simulated from the velocity model.}
\label{fig:ovp,o}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-pwd}
   \label{fig:o-pwd}}
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrr}
   \label{fig:o-lrr}}   
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrra}
   \label{fig:o-lrra}} \\
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-pwd-n-0}
   \label{fig:o-pwd-n-0}}
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrr-n-0}
   \label{fig:o-lrr-n-0}}   
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrra-n-0}
   \label{fig:o-lrra-n-0}}    
\caption{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. Second row: separated diffractions using (d) the PWD method, (e) the LRR method, and (f) the LRRA method.}
\label{fig:o-pwd,o-lrr,o-lrra,o-pwd-n-0,o-lrr-n-0,o-lrra-n-0}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-pwd-imag-0}
   \label{fig:o-pwd-imag-0}}
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrr-imag-0}
   \label{fig:o-lrr-imag-0}}   
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrra-imag-0}
   \label{fig:o-lrra-imag-0}}    
\caption{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. The arrows indicate less reflection energy and higher resolution using the LRRA method.}
\label{fig:o-pwd-imag-0,o-lrr-imag-0,o-lrra-imag-0}
\end{figure}

\subsection{Rank estimation in local windows}
Selecting an appropriate rank for each window is crucial in reflection reconstruction and diffraction separation. 
It is the key to judge whether a singular value corresponds to the reflection energy or the diffraction energy.
As the 3D seismic data are divided into various sub-volumes, it is necessary to independently estimate the rank for each local volumes. 
The common practice is specifying a threshold, and comparing the singular values with the threshold. 
If the singular values are larger than the threshold, they are regarded to correspond to reflections, thereby being preserved.
On the contrary, the residual singular values correspond to diffractions.
A small rank means that the disregarded energy is relatively large, then the reflection may exists in the separated diffractions.
A large value of threshold will damage the diffraction energy because a part of the diffraction energy is mixed in the  reconstructed reflections.
Consequently,  the determination of rank values is challenging, and conventional strategies, such as  the difference curvature method \cite{Vicente2011Simultaneous}, may be artificial. 
Besides, it is difficult and time-consuming to manually specify a rank value in each local window.
Based on the complexity of the 3D seismic volumes, we propose an adaptive and automatic method to determine the rank values in different windows.
Let us consider the singular value ratio in a window, which is given by
\begin{equation} \label{eq:svr}
V_i=\dfrac{\sigma_i}{\sigma_{i+1}},i=1,2,\cdots,L-1,
\end{equation}
where $V_i$ denotes the singular value ratio sequence from large to small and $L$ is the length of the singular spectrum. Then, we can estimate the rank $\hat{R}$ of a local window by selecting the maximum of  the singular value ratio sequence, 
\begin{equation} \label{eq:svr}
\hat{R}=\text{arg} \max\limits_i\quad V_i.
\end{equation}
Taking $\hat{R}$ into equation \ref{eq:HR}, we can separate diffractions and reflections according to equations \ref{eq:wr} and \ref{eq:dsr}.

We summarize the procedures of the proposed new method for diffraction separation as the following steps,
\begin{enumerate}
\item dividing the 3D seismic data into several volumes by sliding the local window,
\item transforming the time-domain data into frequency domain by using Fourier transform,
\item mapping the frequency-domain data into a block Hankel matrix,
\item applying the TSVD algorithm to the block Hankel matrix,
\item estimating the rank by using the proposed automatic determination approach,
\item reconstructing the block Hankel matrix of reflections by inverse Hankelization operator,
\item applying the inverse Fourier transform and aggregating all reflection volumes in different windows,
\item subtracting the reflections from the 3D seismic data and obtaining the diffractions. 
\end{enumerate}
We called the proposed automated local method the LRR method with adaptively selected ranks (LRRA).

To demonstrate the feasibility of the singular value ratios as an effective rank selection strategy, we conduct a simple test, where we create a synthetic reflection dataset with three plane waves and add a diffraction wave to it to see how the singular values vary with and without the diffraction wave. We also add some weak random noise to mimic the real situation. The 3D datasets without and with diffractions are plotted in Figures \ref{fig:demosigma}(a) and \ref{fig:demosigma}(b), respectively. Here, we plot the 3D data as a 2D matrix to see the details inside the data. To clearly visualize the diffraction wave, we also plot the 2D sections from the 3D datasets in Figures  \ref{fig:demosigma}(c) (without the diffraction) and \ref{fig:demosigma}(d)  (with the diffraction), where one can see the bow-tie-like diffraction wave clearly. We plot the first 25 singular values of the block Hankel matrix of 20 Hz in Figures \ref{fig:demosigma}(e) (without the diffraction) and \ref{fig:demosigma}(f)  (with the diffraction). The blue dots correspond to the singular values and the red curves correspond to the singular value ratios. From Figure \ref{fig:demosigma}(e), it is clear that when there are no diffractions, there are only three non-zero singular values, and the maximum of singular value ratios correctly picks the correct rank of this data. From Figure \ref{fig:demosigma}(f), it is clear that when there is a diffraction wave, there are still three distinctively large singular values, with other singular values close to zeros. It is obvious that the energy of the diffraction wave and the random noise is mainly spreading in the singular values after the three largest values. The maximum of the singular value ratios correctly picks the correct rank again despite the existence of the diffraction wave and random noise. This test shows that the singular value ratio is an effective way to automatically distinguish between reflections and diffractions in the singular spectrum.

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.6\columnwidth]{plot/Fig/kvp}
   \label{fig:kvp}}
 \subfigure[]{\includegraphics[width=0.6\columnwidth]{plot/Fig/k}
   \label{fig:k}}     
\caption{(a) Velocity model of the second synthetic example. (b) Zero-offset data simulated from the velocity model.}
\label{fig:kvp,k}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-pwd}
   \label{fig:k-pwd}}
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrr}
   \label{fig:k-lrr}}   
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrra}
   \label{fig:k-lrra}} \\
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-pwd-n-0}
   \label{fig:k-pwd-n-0}}
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrr-n-0}
   \label{fig:k-lrr-n-0}}   
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrra-n-0}
   \label{fig:k-lrra-n-0}}    
\caption{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. Second row: separated diffractions using (d) the PWD method, (e) the LRR method, and (f) the LRRA method.}
\label{fig:k-pwd,k-lrr,k-lrra,k-pwd-n-0,k-lrr-n-0,k-lrra-n-0}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-pwd-imag-0}
   \label{fig:k-pwd-imag-0}}
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrr-imag-0}
   \label{fig:k-lrr-imag-0}}   
 \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrra-imag-0}
   \label{fig:k-lrra-imag-0}}    
\caption{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. The arrows indicate less reflection energy and higher resolution using the LRRA method.}
\label{fig:k-pwd-imag-0,k-lrr-imag-0,k-lrra-imag-0}
\end{figure}

\section{Examples}
In this part, we will first benchmark the proposed method with two state-of-the-art methods, i.e., the PWD method \cite{2007Post} and the global rank-reduction (GRR) method \cite{2020Diffraction}, based on a relatively simple but representative 3D dataset. Then, we will test the effects of the diffraction separation methods on diffraction imaging of two 3D synthetic models. Finally, we will test the proposed method on a 3D field data example.

\subsection{Benchmark comparison}
We create a 3D synthetic dataset for comparing the diffraction separation performance of different methods. In this comparison, since we have the ground truth diffractions and reflections, we can quantitatively compare different methods based on the signal-to-noise ratio (SNR) metric shown below.
\begin{equation}
\label{eq:snr}
\text{SNR}=10\log_{10}\frac{\Arrowvert \mathbf{d} \Arrowvert_2^2}{\Arrowvert \mathbf{d} -\mathbf{d}_s\Arrowvert_2^2},
\end{equation}
where $\mathbf{d}$ denotes the vectorized ground-truth diffraction and $\mathbf{d}_s$ corresponds to the separated diffraction.

The synthetic reflections and diffractions are plotted in Figures \ref{fig:refl} and \ref{fig:diffr}, respectively. Figure \ref{fig:syn} shows the synthetic data containing both reflections and diffractions, i.e., the summation between Figures \ref{fig:refl} and \ref{fig:diffr}. The data size of this example is $200\times 100\times 100$. We simulate the diffraction waves by putting 16 evenly distributed diffraction points and use the kirchhoff modeling method to simulate both reflection and diffraction waves. We compare the separated reflections and diffractions using three methods, i.e., PWD, GRR, and the proposed methods, in Figures \ref{fig:s-pwd-0,s-grr-0,s-lrra-0} and \ref{fig:s-pwd-n-0,s-grr-n-0,s-lrra-n-0}. 
In the separated reflections shown in Figure \ref{fig:s-pwd-0,s-grr-0,s-lrra-0}, it is clear that all three methods separate most diffractions, but the GRR method causes significant residual diffractions in the reflections, as indicated by the arrows in Figure \ref{fig:s-grr-0}. 
It is easier for comparing different methods in the separated diffraction cubes in Figure \ref{fig:s-pwd-n-0,s-grr-n-0,s-lrra-n-0}, where the damages to reflection waves and the energy difference of the separated diffractions can be seen clearly. In Figure \ref{fig:s-pwd-n-0}, there are obvious reflections in the diffractions, indicating the serious coupling between reflections and diffractions after separation. Figure \ref{fig:s-grr-n-0} shows obviously weaker diffractions, indicating the strong residual diffractions in the reflections. The proposed method, however, obtains a good separation between reflections and diffractions. In this benchmark test, the parameters of different methods have been tuned to output the highest SNRs. The GRR method uses a global rank of 60, and the proposed method uses a window size of 40 samples in both spatial directions. The SNRs of the results from PWD, GRR, and the proposed method are 6.52 dB, 3.14 dB, and 9.14 dB, respectively, as compared to -28.23 dB of the input data containing the whole reflection data. \new{The error cubes of estimated diffractions are plotted in Figure \ref{fig:s-pwd-e-0,s-grr-e-0,s-lrra-e-0}, where it is clear that the proposed method obtains the smallest error.}

%\inputdir{plot}
%\multiplot{3}{refl,diffr,syn}{width=0.45\columnwidth}{Benchmark dataset with groundtruth reflections and diffractions. (a) Reflection data. (b) Diffraction data. (c) Synthetic data. }
%\multiplot{3}{s-pwd-0,s-grr-0,s-lrra-0}{width=0.45\columnwidth}{Separated reflections using (a) PWD method, (b) global rank-reduction method, and (c) proposed method.}
%\multiplot{3}{s-pwd-n-0,s-grr-n-0,s-lrra-n-0}{width=0.45\columnwidth}{Separated reflections using (a) PWD method (SNR=6.52 dB), (b) global rank-reduction method (SNR=1.42 dB), and (c) proposed method (SNR=9.14 dB).}

\subsection{Synthetic diffraction imaging test}
The first diffraction imaging test is based on the Ordovician model \cite{decker2015carbonate,janson2010ultra,decker2015carbonate}. This model 
is built based on the Ordovician limestone strata located in Tarim Basin, China, to test the diffraction imaging methods in characterizing paleokarst features in very deeply buried strata. The velocity model follows the Ordovician unconformity surface (between the basal Ordovician layer and the overlying siliciclastic Silurian layer) that is mapped from active-source reflection seismic data.  The paleo-caves are collapsed due to the deposition of sediments, which are modeled by randomly distributing the low acoustic impedance anomalies in the 3D model. The paleo-caves have a general size of 18 m in vertical slices and 300 $\times$ 300 m in horizontal slices. We show the velocity model ($416\times200\times 200$) in Figure \ref{fig:ovp}. Figure \ref{fig:o} plots the simulated zero-offset seismic data ($1351\times200\times 128$). The bow-tie-like diffractions are very obvious in the data. Figure \ref{fig:o-pwd,o-lrr,o-lrra,o-pwd-n-0,o-lrr-n-0,o-lrra-n-0} shows the comparison of separated reflections and diffractions. Figures \ref{fig:o-pwd}-\ref{fig:o-lrra} plot the separated reflections using the PWD, LRR, and the proposed methods, respectively. In both LRR and LRRA methods, we use a window size of 50 samples in both inline and crossline directions. Figures \ref{fig:o-pwd-n-0}-\ref{fig:o-lrra-n-0} plot their corresponding diffractions. Comparing the separated diffractions, it is clear that the PWD method tends to remove reflections when separating the diffractions, as indicated by the arrows. The diffractions separated by the LRR method without a proper selection of the rank are obviously weaker.  The proposed LRRA method (see Figure \ref{fig:o-lrra}), however, obtains good results. The migrated images using the separated diffractions are compared in Figure \ref{fig:o-pwd-imag-0,o-lrr-imag-0,o-lrra-imag-0}. It is clear that the image using the PWD method contains some energy corresponding to the reflections (see the arrows). The LRR method (Figure \ref{fig:o-lrr-imag-0}) obtains a more vague image than the other two methods. The proposed LRRA method (Figure \ref{fig:o-lrra-imag-0}), however, obtains a clear image of the paleo-caves.

%\inputdir{plot}
%\multiplot{2}{ovp,o}{width=0.6\columnwidth}{(a) Velocity model of the first synthetic example. (b) Zero-offset data simulated from the velocity model.}
%
%\multiplot{6}{o-pwd,o-lrr,o-lrra,o-pwd-n-0,o-lrr-n-0,o-lrra-n-0}{width=0.3\columnwidth}{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. Second row: separated diffractions using (d) the PWD method, (e) the LRR method, and (f) the LRRA method.}
%
%\multiplot{3}{o-pwd-imag-0,o-lrr-imag-0,o-lrra-imag-0}{width=0.45\columnwidth}{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. The arrows indicate less reflection energy and higher resolution using the LRRA method.}

The second diffraction imaging test is based on the Khuff model \cite{decker2015carbonate,janson2013outcrop}, which corresponds to the Permian-Triassic Khuff reservoir that crops out in central Saudi Arabia near Buraydah. This model was originally built to study the influence of small-scale heterogeneities in carbonate reservoirs on the subsurface flow models \cite{janson2013outcrop}. The velocity ($380\times200\times 128$) is plotted in Figure \ref{fig:kvp}. Figure \ref{fig:k} plots the numerically modelled zero-offset data ($400\times200\times 128$), where the bow-tie-like diffractions are evident. Figures \ref{fig:k-pwd}-\ref{fig:k-lrra} compare the separated reflections using the PWD, LRR, and LRRA methods.  All three methods obtain smooth reflections with most diffractions separated. Figures \ref{fig:k-pwd-n-0}-\ref{fig:k-lrra-n-0} compare the separated diffractions. It is clear that Figure \ref{fig:k-pwd-n-0} contains significant spatially coherent reflection waves, indicating a strong coupling between diffractions and reflections using the PWD method. The clear reflection energy is highlighted by the arrows in Figure \ref{fig:k-pwd-n-0}. Figure \ref{fig:k-lrr-n-0} has much weaker diffraction energy, indicating the less competent ability of the LRR method in separating the diffractions without a properly chosen rank parameter. The LRRA method, as plotted in Figure \ref{fig:k-lrra-n-0}, obtains better performance compared with the other two methods. Figure \ref{fig:k-pwd-imag-0,k-lrr-imag-0,k-lrra-imag-0} compares  the diffraction imaging results using three different methods. In both LRR and LRRA methods, we use a window size of 50 samples in the inline direction and a window size of 64 samples in the crossline direction. It is obvious that the PWD method causes obvious reflection structures (see the arrows in Figure \ref{fig:k-pwd-imag-0}), while the LRR method fails in separating all the diffractions, thereby causing less clear depictions of the small-scale heterogeneities. The LRRA method obtains a clearly better result.

%\multiplot{2}{kvp,k}{width=0.6\columnwidth}{(a) Velocity model of the second synthetic example. (b) Zero-offset data simulated from the velocity model.}
%
%\multiplot{6}{k-pwd,k-lrr,k-lrra,k-pwd-n-0,k-lrr-n-0,k-lrra-n-0}{width=0.3\columnwidth}{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. Second row: separated diffractions using (d) the PWD method, (e) the LRR method, and (f) the LRRA method.}
%
%\multiplot{3}{k-pwd-imag-0,k-lrr-imag-0,k-lrra-imag-0}{width=0.45\columnwidth}{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }
%

\subsection{Field data example}
Next, we apply the proposed method to a 3D field dataset. \new{It is a land seismic dataset from the Cooper Basin in Western Australia, which was used to characterize the tight-gas sand reservoir. Some previous studies regarding this dataset have been published in \cite{merzlikin2017analytical} and \cite{tyiasning2016comparison}.} \new{Detailed geological description of the area as well as the comparison of diffraction imaging results to discontinuity-type attributes is given by \cite{tyiasning2016comparison}. \new{In particular, this dataset has fully azimuthal distribution of offsets and a far offset of 4000 m. The horizon maps shown below come from an interface between a pervasive sheet coal and fluvial Permian Patchawarra Sand at a depth of approximately 2500 m \cite{tyiasning2016comparison}.} The Patchawarra Sand is a tight-gas sand at this field.} The 3D post-stack dataset is plotted in Figure \ref{fig:b}. Figures \ref{fig:b-pwd}-\ref{fig:b-lrra} plot the separated reflection data using the PWD, LRR, and LRRA methods, respectively. In both LRR and LRRA methods, we use a window size of 50 samples in both inline and crossline directions.  Correspondingly, we show the separated diffractions in Figure \ref{fig:b-pwd-n-0,b-lrr-n-0,b-lrra-n-0}, where it is clear that the LRR method fails in separating sufficient amount of diffractions.  Although the PWD method succeeds in separating the diffractions, it also tends to remove the reflections, which are more spatially coherent than the diffractions, as indicated by the arrows. The labeled arrow indicates a noticeable area of the crossline-coherent reflections. The crossline-coherent reflection refers to the reflection energy that is coherent only in the crossline direction and is incoherent in the inline direction. To better visualize the difference of the separated diffractions in a horizontal slice, we extract a time slice (t=1.7 s) from the diffraction cubes and show the comparison in Figure \ref{fig:b-pwd-n-t-0,b-lrr-n-t-0,b-lrra-n-t-0}, where it is clearer to see the reflection energy using the PWD method. We migrate the separated diffractions using an analytical path-summation imaging method \cite{merzlikin2017analytical}, and show an extracted time slice in Figure \ref{fig:b-pwd-rimag-0,b-pwd-imag-0,b-lrr-imag-0,b-lrra-imag-0}. Apart from the diffraction images, we also show a conventional reflection image in Figure \ref{fig:b-pwd-rimag-0} for evaluating the advantage of the diffraction imaging in delineating small-scale heterogeneities. It is clear that the diffraction image using the PWD method is more consistent with the reflection image, e.g., the area pointed out by the labeled arrow. The highlighted area by the arrows shows a crossline-oriented paleo-channel, which can be captured by both reflection and diffraction images. However, this consistency does not demonstrate the advantage of the diffraction imaging, which, instead, indicates the deficiency of the PWD method in excluding the reflection waves that are coherent in one direction. The image using the LRRA method, however, does not show the clear paleo-channel that is more characterized by the reflection waves. From the general comparison in Figure \ref{fig:b-pwd-rimag-0,b-pwd-imag-0,b-lrr-imag-0,b-lrra-imag-0}, the image using the LRRA method has an obviously higher resolution in delineating the small-scale heterogeneities (viewed from all directions), such as the paleo-karsts.

\section{Discussion}
%PWD
%parameter
%GRR
The PWD-based diffraction separation framework has been widely studied and used. While it has a superb capability in separating diffractions out from the post-stack seismic data, very little researches have been done to explore the shortcomings of this method. We have done many numerical as well as field data tests and found that the PWD-based method could suffer from the coupling effect between reflection and diffraction wave components. It is known that the PWD method is based on the local slope calculation and the spatial coherency difference between the reflections and diffractions. On the one hand, the slope estimation based on the PWD method suffers from the noise sensitivity, as reported in many previous studies \cite{shaohuan2017,wanghang2020tgrs2,chenwei2021geo,chenwei2021tgrs2}. The inaccurate slope estimation will affect the separation performance between diffractions and reflections, causing the coupling effect. On the other hand, the spatial coherency between diffractions and reflections is not always disparate, which will result in the coupling of them on the local slope estimation. In other words, when the diffractions and reflections are similar in terms of spatial coherency, the PWD method will also estimate the slope of the diffractions, making the separation algorithm treat both diffractions and reflections as signals and thereby causing either separated diffractions and reflections coupling together or an insufficient amount of separated diffraction energy. As can be seen in the aforementioned examples, the PWD method tends to cause a significant amount of reflection energy in the diffraction volumes, which further lowers the resolution of the diffraction image.

The rank-reduction method is a completely data-driven method that does not require an intermediate step like the PWD method. The difference between the reflections and diffractions is reflected in the amplitude distribution of singular values. Traditional rank-reduction methods rely on a manual selection of the rank parameter, which may involve several try-and-error steps. The general assumption is that the rank is equivalent to the number of distinct dipping components. It is valid for simple synthetic data with several plane waves. However, it is not applicable in complicated datasets where the seismic events are highly non-stationary. Thus, the assumption of the rank-reduction method is not valid for processing a large 3D realistic seismic dataset without applying the windowing strategy. Previous 2D diffraction imaging method based on the GRR method has shown some promising results \cite{2020Diffraction}, but causes significant artifacts due to the complication in the singular value distribution. The local rank-reduction method can help obtain better results because of the much-simplified data structure that follows the separation assumption. However, another problem arises due to the windowing strategy, i.e., the rank incoherency issue \cite{shaohuan2017gji,yangkang2017ieee}. The adaptive rank selection method proposed in this paper well solves the rank incoherency problem by adapting the local structure with the automatically chosen rank parameter. The proposed method is free of manual rank selection and thus is convenient to use. The only parameter required to adjust in the proposed framework is the window size. The window size here only refers to the spatial window size. Since the coherency to distinguish between diffractions and reflections is mainly related to the spatial dimension, we do not apply temporal window in the proposed framework. \new{In order to investigate how the spatial window can affect the diffraction separation performance, we conduct several tests based on the first benchmark example shown in Figure \ref{fig:refl,diffr,syn}.  We use different spatial window sizes to separate the diffractions and use the SNR to quantitatively evaluate the performance, and plot the SNR diagrams in Figure \ref{fig:curve}. Here, because our synthetic data is symmetric in the two spatial directions, we can only vary the window size in one spatial direction, and use the same value for the other direction.
In Figure \ref{fig:curve}, the horizontal axis corresponds to the window size, and the vertical axis corresponds to the SNR. It is clear that the SNR reaches the highest when the window size is 40 samples. It is clear that the 40 samples coincide with the spatial width of the bow-tie-like diffraction wave. Thus, we conclude from this test that the optimal window size should be chosen roughly as the spatial width of the observable diffraction wave component. }

\new{Existence of noise could affect the performance of the proposed method. If the noise is random, it will be combined with the diffraction energy as the output of the local rank-reduction method. It is possible to further separate the random noise from the diffraction energy by leveraging their differences in the singular spectrum \cite{weilin2017dlsp,oboue2021geo1,oboue2021geo2}. If the noise is random but linear, it will likely be considered as the diffraction energy, and could be interfering the separated diffraction energy when input to the imaging framework. However, it indeed depends on the spatial coherency difference between the linear noise and the diffraction energy. If the linear noise is steeply dipping and is more spatially incoherent than diffraction energy \cite{weilin2017mmf}, then the proposed method could still be effective in distinguishing the two components. }

The computational cost of the LRR method is much lower than the GRR method. The state-of-the-art rank-reduction method with a full singular value decomposition (SVD) has a computational cost of $O(N_1(N_2N_3)^3)$, and with a truncated SVD operation has a cost of $O(N_1K(N_2N_3)^2)$, where $N_i$ denotes the size of the $i$th dimension. $K$ denotes the rank parameter.
Thus, using a local rank-reduction method can also help significantly reduce the computational overburden. For the 3D examples presented in this paper, only the first synthetic example ($200\times 100\times 100$) can afford the global method, thus we present its result. For this test, the local method with a spatial window size of 40 samples takes 263.3 s, while the global method takes 3266.3 s. It is a speedup of 12.4 times. The computation is done on a Mac Pro laptop PC with 2.5 GHz Intel Core i7. For the other three datasets, the global method is prohibitively expensive, thus we do not show the results. Note that to further increase the computational efficiency, a randomized SVD can also be used to obtain a large speedup but at the expense of degrading the performance \cite{li2014large}. The automatic rank selection strategy almost adds no extra computational cost to the rank-reduction method, so the overall computational efficiency of the proposed method is acceptable.

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b}
   \label{fig:b}}
 \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-pwd}
   \label{fig:b-pwd}}    \\
 \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrr}
   \label{fig:b-lrr}}    
 \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrra}
   \label{fig:b-lrra}} 
\caption{Field data example. (a) A 3D field dataset. Separated reflection data using (b) the PWD method, (c) the LRR method, and (d) the LRRA method. }
\label{fig:b,b-pwd,b-lrr,b-lrra}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-pwd-n-0}
   \label{fig:b-pwd-n-0}}
 \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrr-n-0}
   \label{fig:b-lrr-n-0}}   
 \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrra-n-0}
   \label{fig:b-lrra-n-0}}    
\caption{Separated diffraction data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.}
\label{fig:b-pwd-n-0,b-lrr-n-0,b-lrra-n-0}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-pwd-n-t-0}
   \label{fig:b-pwd-n-t-0}}
 \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrr-n-t-0}
   \label{fig:b-lrr-n-t-0}}   
 \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrra-n-t-0}
   \label{fig:b-lrra-n-t-0}}    
\caption{A comparison of time slices extracted from the separated diffraction data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }
\label{fig:b-pwd-n-t-0,b-lrr-n-t-0,b-lrra-n-t-0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-pwd-rimag-0}
  \label{fig:b-pwd-rimag-0}}
\subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-pwd-imag-0}
  \label{fig:b-pwd-imag-0}} \\
\subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrr-imag-0}
  \label{fig:b-lrr-imag-0}}   
\subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrra-imag-0}
  \label{fig:b-lrra-imag-0}}    
\caption{(a) Time slice of the reflection image. Time slices of the diffraction image using (b) the PWD method, (c) the LRR method, and (d) the LRRA method. The arrows indicate the higher resolution using the LRRA method and the lower resolution of the PWD method due to the consistency in depicting the crossline-oriented paleo-channel between the reflection and diffraction images.}
\label{fig:b-pwd-rimag-0,b-pwd-imag-0,b-lrr-imag-0,b-lrra-imag-0}
\end{figure}

%\plot{b}{width=0.6\columnwidth}{3D field dataset.}
%\multiplot{4}{b,b-pwd,b-lrr,b-lrra}{width=0.45\columnwidth}{Field data example. (a) A 3D field dataset. Separated reflection data using (b) the PWD method, (c) the LRR method, and (d) the LRRA method. }
%\multiplot{3}{b-pwd-n-0,b-lrr-n-0,b-lrra-n-0}{width=0.45\columnwidth}{Separated diffraction data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }

%\multiplot{3}{b-pwd-n-t-0,b-lrr-n-t-0,b-lrra-n-t-0}{width=0.45\columnwidth}{A comparison of time slices extracted from the separated diffraction data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }

%\multiplot{4}{b-pwd-rimag-0,b-pwd-imag-0,b-lrr-imag-0,b-lrra-imag-0}{width=0.45\columnwidth}{(a) Time slice of the reflection image. Time slices of the diffraction image using (b) the PWD method, (c) the LRR method, and (d) the LRRA method. The arrows indicate the higher resolution using the LRRA method and the lower resolution of the PWD method due to the consistency in depicting the crossline-oriented paleo-channel between the reflection and diffraction images.}
%

\section{Conclusions}
The PWD method has a limitation when estimating the local slope of complicated 3D seismic data, i.e., it suffers from the coupling between diffractions and reflections in the resulted slope map. The coupling effect is attributed to the fact that the PWD method is sensitive to noise and is not capable of distinguishing between reflections and diffractions that have similar spatial coherency. Because of the coupling issue, the traditional PWD diffraction separation methods result in significant residual reflection energy in the separated diffraction waves, which further decreases the resolution of the migrated diffraction image. The proposed 3D LRRA method can adaptively separate the diffractions from the zero-offset seismic data in a robust way and with less remaining reflection energy. The 3D synthetic and field data examples demonstrate the great potential of the proposed method in a practical 3D diffraction imaging framework.

%\inputdir{./}
%\plot{curve}{width=0.8\columnwidth}{SNR diagrams varying with different spatial window sizes.}

\begin{figure}[htb!]
\centering
\includegraphics[width=0.7\columnwidth]{Fig/curve}
\caption{SNR diagrams varying with different spatial window sizes.}
\label{fig:curve}
\end{figure}

%\section{Acknowledgements}
%\section{DATA AND MATERIALS AVAILABILITY}
%All datasets and source codes associated with this research will be made available online (www.ahay.org) as a reproducible article.

\bibliographystyle{IEEEtran}
\bibliography{diffr}

\end{document}

### 2022-01-02 diffrlrra3d/matfun/fxydmssa_win.m

@@ -1,0 +1,77 @@
+function [ D1 ] = fxydmssa_win(D,flow,fhigh,dt,N,NN,verb,n1win,n2win,n3win,r1,r2,r3)
+%  FXY_MSSA: F-XY domain multichannel singular spectrum analysis (MSSA)
+%
+%  IN   D:   	intput 3D data
+%       flow:   processing frequency range (lower)
+%       fhigh:  processing frequency range (higher)
+%       dt:     temporal sampling interval
+%       N:      number of singular value to be preserved
+%       verb:   verbosity flag (default: 0)
+%
+%  OUT  D1:  	output data
+%
+%  Copyright (C) 2013 The University of Texas at Austin
+%  Copyright (C) 2013 Yangkang Chen
+%  Modified 2015 by Yangkang Chen
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details: http://www.gnu.org/licenses/
+%
+%  REFERENCES
+%  Wang et al., 2020, Separation and imaging of seismic diffractions using a localized rank-reduction method with adaptively selected ranks, 85, V497–V506.
+%  Chen et al., 2019, Obtaining free USArray data by multi-dimensional seismic reconstruction, Nature Communications, 10:4434.
+%  Bai et al., 2020, Seismic signal enhancement based on the lowrank methods, Geophysical Prospecting, 68, 2783-2807.
+%  Chen et al., 2020, Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method, Geophysical Journal International, 222, 1824-1845.
+%  Chen, Y., W. Huang, D. Zhang, W. Chen, 2016, An open-source matlab code package for improved rank-reduction 3D seismic data denoising and reconstruction, Computers & Geosciences, 95, 59-66.
[…]

### 2022-01-02 diffrlrra3d/matfun/fxydmssa_win_auto.m

@@ -1,0 +1,82 @@
+function [ D1 ] = fxydmssa_win_auto(D,flow,fhigh,dt,N,NN,verb,n1win,n2win,n3win,r1,r2,r3,mode)
+%  FXY_DMSSA: F-XY domain localized damped multichannel singular spectrum analysis (MSSA)
+%  with automatic rank selection
+%
+%  IN   D:   	intput 3D data
+%       flow:   processing frequency range (lower)
+%       fhigh:  processing frequency range (higher)
+%       dt:     temporal sampling interval
+%       N:      number of singular value to be preserved
+%       NN:     damping factor
+%       verb:   verbosity flag (default: 0)
+%
+%  OUT  D1:  	output data
+%
+%  Copyright (C) 2013 The University of Texas at Austin
+%  Copyright (C) 2013 Yangkang Chen
+%  Modified 2015 by Yangkang Chen
+%  Modified 2020 by Yangkang Chen
+% 
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details: http://www.gnu.org/licenses/
+%
+%  REFERENCES
+%  Wang et al., 2020, Separation and imaging of seismic diffractions using a localized rank-reduction method with adaptively selected ranks, 85, V497–V506.
+%  Chen et al., 2019, Obtaining free USArray data by multi-dimensional seismic reconstruction, Nature Communications, 10:4434.
+%  Bai et al., 2020, Seismic signal enhancement based on the lowrank methods, Geophysical Prospecting, 68, 2783-2807.
+%  Chen et al., 2020, Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method, Geophysical Journal International, 222, 1824-1845.
[…]

### 2022-01-02 diffrlrra3d/matfun/fxymssa.m

@@ -1,0 +1,185 @@
+function [ D1 ] = fxymssa(D,flow,fhigh,dt,N,verb)
+%  FXYMSSA: Rank reduction method
+%
+%  IN   D:   	intput 3D data
+%       flow:   processing frequency range (lower)
+%       fhigh:  processing frequency range (higher)
+%       dt:     temporal sampling interval
+%       N:      number of singular value to be preserved
+%       verb:   verbosity flag (default: 0)
+%
+%  OUT  D1:  	output data
+%
+%  Copyright (C) 2013 The University of Texas at Austin
+%  Copyright (C) 2013 Yangkang Chen
+%  Modified 2015 by Yangkang Chen
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details: http://www.gnu.org/licenses/
+%
+%  REFERENCES
+%  Wang et al., 2020, Separation and imaging of seismic diffractions using a localized rank-reduction method with adaptively selected ranks, 85, V497–V506.
+%  Chen et al., 2019, Obtaining free USArray data by multi-dimensional seismic reconstruction, Nature Communications, 10:4434.
+%  Bai et al., 2020, Seismic signal enhancement based on the lowrank methods, Geophysical Prospecting, 68, 2783-2807.
+%  Chen et al., 2020, Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method, Geophysical Journal International, 222, 1824-1845.
[…]

### 2022-01-02 diffrlrra3d/matfun/fxymssa_auto2.m

@@ -1,0 +1,233 @@
+function [ D1,H ] = fxymssa_auto2(D,flow,fhigh,dt,Nmin,Nmax,verb,mode,f,eps)
+%  FXYMSSA_AUTO2: F-XY domain multichannel singular spectrum analysis (MSSA)
+%  with automatically selected rank
+%
+%  INmax   D:   	intput 3D data
+%       flow:   processing frequency range (lower)
+%       fhigh:  processing frequency range (higher)
+%       dt:     temporal sampling interval
+%       Nmin:      number of singular value to be preserved (low limit)
+%       Nmax:      number of singular value to be preserved (high limit)
+%       verb:   verbosity flag (default: 0)
+%       mode:   1 (amplitude difference)
+%               2 (ratio)
+%           f:  reference frequency for outputing singular values (energy)
+%           eps: threshold (fixed in default)
+%
+%  OUT  D1:  	output data
+%
+%  Copyright (C) 2013 The University of Texas at Austin
+%  Copyright (C) 2013 Yangkang Chen
+%  Modified 2015 by Yangkang Chen
+%  Modified 2017 by Yangkang Chen
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNmaxU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANmaxY WARRANmaxTY; without even the implied warranty of
+%  MERCHANmaxTABILITY or FITNmaxESS FOR A PARTICULAR PURPOSE.  See the
+%  GNmaxU General Public License for more details: http://www.gnu.org/licenses/
+%
+%  REFERENCES
+%  Wang et al., 2020, Separation and imaging of seismic diffractions using a localized rank-reduction method with adaptively selected ranks, 85, V497–V506.
[…]

### 2022-01-02 diffrlrra3d/matfun/fxymssa_win.m

@@ -1,0 +1,75 @@
+function [ D1 ] = fxymssa_win(D,flow,fhigh,dt,N,verb,n1win,n2win,n3win,r1,r2,r3)
+%  FXYMSSA_WIN: Local RR method
+%
+%  IN   D:   	intput 3D data
+%       flow:   processing frequency range (lower)
+%       fhigh:  processing frequency range (higher)
+%       dt:     temporal sampling interval
+%       N:      number of singular value to be preserved
+%       verb:   verbosity flag (default: 0)
+%
+%  OUT  D1:  	output data
+%
+%  Copyright (C) 2013 The University of Texas at Austin
+%  Copyright (C) 2013 Yangkang Chen
+%  Modified 2015 by Yangkang Chen
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details: http://www.gnu.org/licenses/
+%
+%  REFERENCES
+%  Wang et al., 2020, Separation and imaging of seismic diffractions using a localized rank-reduction method with adaptively selected ranks, 85, V497–V506.
+%  Chen et al., 2019, Obtaining free USArray data by multi-dimensional seismic reconstruction, Nature Communications, 10:4434.
+%  Bai et al., 2020, Seismic signal enhancement based on the lowrank methods, Geophysical Prospecting, 68, 2783-2807.
+%  Chen et al., 2020, Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method, Geophysical Journal International, 222, 1824-1845.
+%  Chen, Y., W. Huang, D. Zhang, W. Chen, 2016, An open-source matlab code package for improved rank-reduction 3D seismic data denoising and reconstruction, Computers & Geosciences, 95, 59-66.
[…]

### 2022-01-02 diffrlrra3d/matfun/fxymssa_win_auto.m

@@ -1,0 +1,77 @@
+function [ D1 ] = fxymssa_win_auto(D,flow,fhigh,dt,N,verb,n1win,n2win,n3win,r1,r2,r3,mode)
+%FXYMSSA_WIN_auto: local RR with automatically selected ranks
+%  
+%  IN   D:   	intput 3D data
+%       flow:   processing frequency range (lower)
+%       fhigh:  processing frequency range (higher)
+%       dt:     temporal sampling interval
+%       N:      number of singular value to be preserved
+%       verb:   verbosity flag (default: 0)
+%
+%  OUT  D1:  	output data
+%
+%  Copyright (C) 2013 The University of Texas at Austin
+%  Copyright (C) 2013 Yangkang Chen
+%  Modified 2015 by Yangkang Chen
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details: http://www.gnu.org/licenses/
+%
+%  REFERENCES
+%  Wang et al., 2020, Separation and imaging of seismic diffractions using a localized rank-reduction method with adaptively selected ranks, 85, V497–V506.
+%  Chen et al., 2019, Obtaining free USArray data by multi-dimensional seismic reconstruction, Nature Communications, 10:4434.
+%  Bai et al., 2020, Seismic signal enhancement based on the lowrank methods, Geophysical Prospecting, 68, 2783-2807.
+%  Chen et al., 2020, Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method, Geophysical Journal International, 222, 1824-1845.
+%  Chen, Y., W. Huang, D. Zhang, W. Chen, 2016, An open-source matlab code package for improved rank-reduction 3D seismic data denoising and reconstruction, Computers & Geosciences, 95, 59-66.
[…]

### 2022-01-02 diffrlrra3d/matfun/fxymssa_win_auto2.m

@@ -1,0 +1,79 @@
+function [ D1 ] = fxymssa_win_auto2(D,flow,fhigh,dt,N,N2,verb,n1win,n2win,n3win,r1,r2,r3,mode)
+%  FXYMSSA_WIN_auto2: local RR with automatically selected ranks
+%  
+%  IN   D:   	intput 3D data
+%       flow:   processing frequency range (lower)
+%       fhigh:  processing frequency range (higher)
+%       dt:     temporal sampling interval
+%       N:      number of singular value to be preserved
+%       verb:   verbosity flag (default: 0)
+%
+%  OUT  D1:  	output data
+%
+%  Copyright (C) 2013 The University of Texas at Austin
+%  Copyright (C) 2013 Yangkang Chen
+%  Modified 2015 by Yangkang Chen
+%
+%  This program is free software: you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published
+%  by the Free Software Foundation, either version 3 of the License, or
+%  any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details: http://www.gnu.org/licenses/
+%
+%  REFERENCES
+%  Wang et al., 2020, Separation and imaging of seismic diffractions using a localized rank-reduction method with adaptively selected ranks, 85, V497–V506.
+%  Chen et al., 2019, Obtaining free USArray data by multi-dimensional seismic reconstruction, Nature Communications, 10:4434.
+%  Bai et al., 2020, Seismic signal enhancement based on the lowrank methods, Geophysical Prospecting, 68, 2783-2807.
+%  Chen et al., 2020, Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method, Geophysical Journal International, 222, 1824-1845.
+%  Chen, Y., W. Huang, D. Zhang, W. Chen, 2016, An open-source matlab code package for improved rank-reduction 3D seismic data denoising and reconstruction, Computers & Geosciences, 95, 59-66.
[…]

### 2022-01-02 diffrlrra3d/matfun/localfxydmssa.m

@@ -1,0 +1,36 @@
+function [ DATA_out ] = localfxydmssa( DATA_in, param )
+% Local DRR
+%
+%  Copyright (C) 2020 Yangkang Chen
+% 
+% DATA_in:      input data
+% DATA_out:     output data
+% param:        parameters set
+% param.dt:     sampling interval in sec
+% param.lf:   	min  freq. in the data in Hz
+% param.hf:  	max  freq. in the data in Hz
+% param.N  	
+% param.NN  
+%
+%  REFERENCES
+%  Wang et al., 2020, Separation and imaging of seismic diffractions using a localized rank-reduction method with adaptively selected ranks, 85, V497–V506.
+%  Chen et al., 2019, Obtaining free USArray data by multi-dimensional seismic reconstruction, Nature Communications, 10:4434.
+%  Bai et al., 2020, Seismic signal enhancement based on the lowrank methods, Geophysical Prospecting, 68, 2783-2807.
+%  Chen et al., 2020, Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method, Geophysical Journal International, 222, 1824-1845.
+%  Chen, Y., W. Huang, D. Zhang, W. Chen, 2016, An open-source matlab code package for improved rank-reduction 3D seismic data denoising and reconstruction, Computers & Geosciences, 95, 59-66.
+%  Chen, Y., D. Zhang, Z. Jin, X. Chen, S. Zu, W. Huang, and S. Gan, 2016, Simultaneous denoising and reconstruction of 5D seismic data via damped rank-reduction method, Geophysical Journal International, 206, 1695-1717.
+%  Huang, W., R. Wang, Y. Chen, H. Li, and S. Gan, 2016, Damped multichannel singular spectrum analysis for 3D random noise attenuation, Geophysics, 81, V261-V270.
+%  Chen et al., 2017, Preserving the discontinuities in least-squares reverse time migration of simultaneous-source data, Geophysics, 82, S185-S196.
+%  
+dt=param.dt;
+N=param.N;
+NN=param.NN;
+flow=param.flow;
+fhigh=param.fhigh;
+verb=param.verb;
+
+DATA_out=fxydmssa(DATA_in,flow,fhigh,dt,N,NN,verb);
+
+return
+
+

### 2022-01-02 diffrlrra3d/paper.tex
Sun Jan  2 01:07:39 CST 2022

@@
-\documentclass[10pt]{IEEEtran}
-\usepackage{amsmath}
-\usepackage{cite}
-\usepackage{ifthen}
-\usepackage{seg}
-\usepackage{color}
-\usepackage{graphicx}
-\usepackage{subfigure}
+%\documentclass[10pt]{IEEEtran}
+%\usepackage{amsmath}
+%\usepackage{cite}
+%\usepackage{ifthen}
+%\usepackage{seg}
+%\usepackage{color}
+%\usepackage{graphicx}
+%\usepackage{subfigure}
+%
+
+%\begin{document}
 
@@
 \DeclareRobustCommand{\wen}[1]{#1}
-\DeclareRobustCommand{\old}[1]{}
-\DeclareRobustCommand{\new}[1]{#1}
-
-\begin{document}
 
@@
 \renewcommand{\thefootnote}{\fnsymbol{footnote}}
-\author{Wei Chen, Xingye Liu, Omar M. Saad, Yapo Abol{\'e} Serge Innocent Obou{\'e}, Liuqing Yang, Hang Wang, and Yangkang Chen
-\thanks{W.
+\author{Wei Chen, Xingye Liu, Omar M. Saad, Yapo Abol{\'e} Serge Innocent Obou{\'e}, Liuqing Yang, Hang Wang, and Yangkang Chen}
+%\thanks{W.
 Chen is with Cooperative Innovation Center of Unconventional Oil and Gas (Ministry of Education \& Hubei Province), Yangtze University, Wuhan, 430100, China, and Key Laboratory of Exploration Technologies for Oil and Gas Resources of Ministry of Education, Yangtze University, Wuhan, 430100, China}
-\thanks{X. Liu is with Chengdu University of Technology, Dongsanlu, Erxianqiao, Chengdu, 610059, China.}
-\thanks{O.M. Saad is with Seismology Department, National Research Institute of Astronomy and Geophysics (NRIAG), Helwan, 11731, Egypt.}
-\thanks{Y.A.S.I. Oboue and H. Wang are with School of Earth Sciences, Zhejiang University, Hangzhou, 310027, China.}
-\thanks{L. Yang is with State Key Laboratory of Petroleum Resource and Prospecting, China University of Petroleum (Beijing), Beijing, 102200, China.}
-\thanks{Y. Chen is with Bureau of Economic Geology, Jackson School of Geosciences, The University of Texas at Austin, Austin, Texas, 78713-8924, USA.}
-\thanks{The research is supported by the National Natural Science Foundation of China (Grant No.
+%\thanks{X. Liu is with Chengdu University of Technology, Dongsanlu, Erxianqiao, Chengdu, 610059, China.}
+%\thanks{O.M. Saad is with Seismology Department, National Research Institute of Astronomy and Geophysics (NRIAG), Helwan, 11731, Egypt.}
+%\thanks{Y.A.S.I. Oboue and H. Wang are with School of Earth Sciences, Zhejiang University, Hangzhou, 310027, China.}
+%\thanks{L. Yang is with State Key Laboratory of Petroleum Resource and Prospecting, China University of Petroleum (Beijing), Beijing, 102200, China.}
+%\thanks{Y. Chen is with Bureau of Economic Geology, Jackson School of Geosciences, The University of Texas at Austin, Austin, Texas, 78713-8924, USA.}
+%\thanks{The research is supported by the National Natural Science Foundation of China (Grant No.
 41804140) and the Open Fund of Cooperative Innovation Center of Unconventional Oil and Gas, Yangtze University (Ministry of Education \& Hubei Province) (Grant No.
@@
 
-\begin{keywords}
-Seismic signal separation, seismic denoising, seismic imaging, seismic diffraction
-\end{keywords}
-
 \section{Introduction}
-Seismic data contain various useful information that can reflect the geologic features of the subsurface \cite{shucai2020,guoyin2018}.
-In general, reflections are generated by large-scale geologic objects that are continuous and have smooth-reflecting boundaries, and their energy in the seismic records is relatively strong \cite{2010Imaging, Peng2018Accurate}.
+Seismic data contain various useful information that can reflect the geologic features of the subsurface \cite[]{shucai2020,guoyin2018}.
+In general, reflections are generated by large-scale geologic objects that are continuous and have smooth-reflecting boundaries, and their energy in the seismic records is relatively strong \cite[]{2010Imaging, Peng2018Accurate}.
 Reflections are preserved in conventional seismic exploration workflow, and are the most commonly used signals to detect large-scale geologic structures. 
@@
 These small-scale geologic bodies will scatter the energy that is expressed as diffractions in the seismic records, which are destroyed or removed by the traditional seismic processing techniques.
-However, diffractions are helpful to find unconventional reservoirs of oil and gas because they are associated with small-scale discontinuous objects \cite{2016Diffraction, 2020Separation}.
+However, diffractions are helpful to find unconventional reservoirs of oil and gas because they are associated with small-scale discontinuous objects \cite[]{2016Diffraction, 2020Separation}.
 
 Researchers use seismic diffraction to detect subsurface discontinuities, provided that the seismic diffraction is separated from the original data.  
-Nevertheless, it is a challenge because the energy of diffractions is weaker compared with the strong energy of reflections, which can even reach several orders of magnitude, i.e., diffractions are usually masked by reflections and noise \cite{1994Theory, 2007Post,omar2020geo1}.
+Nevertheless, it is a challenge because the energy of diffractions is weaker compared with the strong energy of reflections, which can even reach several orders of magnitude, i.e., diffractions are usually masked by reflections and noise \cite[]{1994Theory, 2007Post,omar2020geo1}.
 One of the most widely used methods is the path-summation-based method that uses the kinematic differences to separate reflections and diffractions.
-Based on the coherent summation of diffracted events according to the traveltime, \cite{1987A} and \cite{1988Imaging} achieve diffraction separation and imaging in common-offset and common-midpoint domains, respectively.
-\cite{2004Diffraction} separate and mute the reflection in the pseudodepth domain  by using the difference in properties of waves.
+Based on the coherent summation of diffracted events according to the traveltime, \cite[]{1987A} and \cite[]{1988Imaging} achieve diffraction separation and imaging in common-offset and common-midpoint domains, respectively.
+\cite[]{2004Diffraction} separate and mute the reflection in the pseudodepth domain  by using the difference in properties of waves.
 The most known diffraction separation and imaging method is based on a common-reflection-surface method that has been extended by many geophysicists.
- One of the advantages is that this method using several common midpoints to stack based on ray theory \cite{2013Recovering}.
-\cite{2009Diffraction} propose a multi-focusing algorithm to focus diffractions while scattering reflections.
-Similarly, \cite{2011Common} use the common-reflection-surface approach to achieve diffraction imaging.
-\cite{2012Separation} achieve diffraction imaging in the migrated dip-angle domain and pointed out that it was more advantageous to separate diffraction from seismic data.
-\cite{2013Diffraction} propose a method that can adaptively choose parameters to fit the diffraction trvaltime and accelerate the computation.
-\cite{Coimbra2018Enhancement} improve the accuracy of diffraction separation by a finite-offset double-square equation, and extended a fast version without losing accuracy.
-\cite{2018Fast} develop a robust and fast method to extract the parameters of common-reflection-surface by using the local slope attribute, and it could be used for the diffraction separation. 
-\cite{2018Common} point out that wavefront attributes of pre-stack seismic data could improve the illumination and are more appropriate for diffraction separation.
-\cite{20193D} construct a new traveltime difference gather to flatten the diffraction, then muted the upward reflection.
-For post-stack seismic data, \cite{2019Coherent} uses many wavefront filters to separate reflections and diffractions, and demonstrated its superiority in extracting diffractions masked by strong reflections.
+ One of the advantages is that this method using several common midpoints to stack based on ray theory \cite[]{2013Recovering}.
+\cite[]{2009Diffraction} propose a multi-focusing algorithm to focus diffractions while scattering reflections.
+Similarly, \cite[]{2011Common} use the common-reflection-surface approach to achieve diffraction imaging.
+\cite[]{2012Separation} achieve diffraction imaging in the migrated dip-angle domain and pointed out that it was more advantageous to separate diffraction from seismic data.
+\cite[]{2013Diffraction} propose a method that can adaptively choose parameters to fit the diffraction trvaltime and accelerate the computation.
+\cite[]{Coimbra2018Enhancement} improve the accuracy of diffraction separation by a finite-offset double-square equation, and extended a fast version without losing accuracy.
+\cite[]{2018Fast} develop a robust and fast method to extract the parameters of common-reflection-surface by using the local slope attribute, and it could be used for the diffraction separation. 
+\cite[]{2018Common} point out that wavefront attributes of pre-stack seismic data could improve the illumination and are more appropriate for diffraction separation.
+\cite[]{20193D} construct a new traveltime difference gather to flatten the diffraction, then muted the upward reflection.
+For post-stack seismic data, \cite[]{2019Coherent} uses many wavefront filters to separate reflections and diffractions, and demonstrated its superiority in extracting diffractions masked by strong reflections.
 
-Another effective diffraction separation and imaging method is based on the plane-wave destruction (PWD) proposed by \cite{Sergey2002Applications} and  \cite{2007Post}.
+Another effective diffraction separation and imaging method is based on the plane-wave destruction (PWD) proposed by \cite[]{Sergey2002Applications} and  \cite[]{2007Post}.
 Traveltimes of diffractions are quasi-hyperbolic-shaped while those of reflections are laterally continuous in the constant plane-wave slope sections.
@@
  After that, diffractions are migrated by selecting an optimal velocity.
-That is to say, the PWD-based method can simultaneously achieve velocity estimation and diffraction imaging \cite{2011Azimuthally}.
-\cite{2013Coal} utilize the PWD-based diffraction imaging method to detect the fractures in coals.
-\cite{Binzhong2018seismic} propose a local moving-average-error-filter to achieve diffraction separation and applied it to coal structures detection. 
-\cite{2018l1} developed an improved PWD-based method via wavelet transform and L1-norm, and achieved accurate diffraction separation.
-The PWD-based method depends on the local slopes, thus a wide range of approaches are developed to accurately estimate the local slopes, such as \cite{2008Separation, 2010Nonlinear, 2018Dip}.
-\cite{2020Least} achieve the diffraction separation by establishing an inversion objection and combining the PWD algorithm with other advanced techniques, such as Kirchhoff modeling, and path-summation-based methods.
+That is to say, the PWD-based method can simultaneously achieve velocity estimation and diffraction imaging \cite[]{2011Azimuthally}.
+\cite[]{2013Coal} utilize the PWD-based diffraction imaging method to detect the fractures in coals.
+\cite[]{Binzhong2018seismic} propose a local moving-average-error-filter to achieve diffraction separation and applied it to coal structures detection. 
+\cite[]{2018l1} developed an improved PWD-based method via wavelet transform and L1-norm, and achieved accurate diffraction separation.
+The PWD-based method depends on the local slopes, thus a wide range of approaches are developed to accurately estimate the local slopes, such as \cite[]{2008Separation, 2010Nonlinear, 2018Dip}.
+\cite[]{2020Least} achieve the diffraction separation by establishing an inversion objection and combining the PWD algorithm with other advanced techniques, such as Kirchhoff modeling, and path-summation-based methods.
 
 Most diffraction separation and imaging methods only take kinematic features of diffractions and reflections into consideration, and the dynamic differences between diffractions and reflections are ignored.
-However, the dynamic discrepancy is significant to diffraction imaging \cite{2015Diffraction, 20193D, 2020Diffraction}.
-\cite{2014Diffraction} update migration velocities according to shapes of reflections and diffractions in the migrated gathers by picking the angles related to reflections in the shot and opening-angle gathers, improving the accuracy.
-\cite{2015Diffraction} develop a least-squares fitting method by using double exponential functions to analyze the amplitude function of diffracted waves and improve the performance of diffraction separation.
-\cite{2016Imaging} develop a three-step diffraction separation and imaging approach based on wave-equation. It is computationally fast and resistant to random noise.
-Based on the fact that the dip direction of reflectors could not be observed in both left- and right-downgoing propagating waves, \cite{2019Efficient} develop an efficient wave-equation-based approach for diffraction separation.
-In frequency-wavenumber domain, \cite{2020Inspiration} use a double square root equation to simulate diffractions, and separated diffractions by using dip frequency filters.
-To improve the image quality of diffractions, \cite{2020Periodic} propose a periodic plane-wave least-squares reverse time migration method.
-\cite{2021Diffraction} applies a diffraction-angle filtering method to the virtual source in the acoustic full-waveform inversion to separate energy of reflections and transmissions.
+However, the dynamic discrepancy is significant to diffraction imaging \cite[]{2015Diffraction, 20193D, 2020Diffraction}.
+\cite[]{2014Diffraction} update migration velocities according to shapes of reflections and diffractions in the migrated gathers by picking the angles related to reflections in the shot and opening-angle gathers, improving the accuracy.
+\cite[]{2015Diffraction} develop a least-squares fitting method by using double exponential functions to analyze the amplitude function of diffracted waves and improve the performance of diffraction separation.
+\cite[]{2016Imaging} develop a three-step diffraction separation and imaging approach based on wave-equation. It is computationally fast and resistant to random noise.
+Based on the fact that the dip direction of reflectors could not be observed in both left- and right-downgoing propagating waves, \cite[]{2019Efficient} develop an efficient wave-equation-based approach for diffraction separation.
+In frequency-wavenumber domain, \cite[]{2020Inspiration} use a double square root equation to simulate diffractions, and separated diffractions by using dip frequency filters.
+To improve the image quality of diffractions, \cite[]{2020Periodic} propose a periodic plane-wave least-squares reverse time migration method.
+\cite[]{2021Diffraction} applies a diffraction-angle filtering method to the virtual source in the acoustic full-waveform inversion to separate energy of reflections and transmissions.
 Diffractions can be separated by designing many types of diffraction-angle filters.
@@
 Consequently, both kinematic and dynamic differences between reflections and diffractions are important for seismic diffraction separation and imaging.
-Jointly using kinematic and dynamic properties of wave fields is helpful for diffraction separation and imaging \cite{2010Separation}.
-\cite{2020Separation} propose a 2D diffraction separation method based on a local rank-reduction algorithm, in which the rank is optimized by an adaptive selection approach.
- \cite{2020Diffraction} utilize the multichannel singular-spectrum  analysis (MSSA) for diffraction separation and imaging.
+Jointly using kinematic and dynamic properties of wave fields is helpful for diffraction separation and imaging \cite[]{2010Separation}.
+\cite[]{2020Separation} propose a 2D diffraction separation method based on a local rank-reduction algorithm, in which the rank is optimized by an adaptive selection approach.
+ \cite[]{2020Diffraction} utilize the multichannel singular-spectrum  analysis (MSSA) for diffraction separation and imaging.
 Their implementation of the MSSA method does not consider the strong non-stationarity of seismic data and thus does not use local windows for the diffraction separation, which is referred to as a global rank-reduction (GRR) method.
@@
 Both kinematic and dynamic properties are considered.
-The rank-reduction filter is carried out in each local window to enhance the performance \cite{shaohuan2017gji,yangkang2017ieee,yangkang2019nc}.
+The rank-reduction filter is carried out in each local window to enhance the performance \cite[]{shaohuan2017gji,yangkang2017ieee,yangkang2019nc}.
 In this case, specifying an appropriate rank for different windows is necessary to make the result more promising.
@@
 
-\begin{figure}[htb!]
-\centering
-\includegraphics[width=\columnwidth]{Fig/demosigma}
-\caption{Singular value distribution.
+%\begin{figure}[htb!]
+%\centering
+%\includegraphics[width=\columnwidth]{Fig/demosigma}
+%\caption{Singular value distribution.
 (a) 3D reflection data containing three plane waves.
@@
 }
-\label{fig:demosigma}
-\end{figure}
+%\label{fig:demosigma}
+%\end{figure}
+\inputdir{./}
+\plot{demosigma}{width=\columnwidth}{Singular value distribution.
+(a) 3D reflection data containing three plane waves.
+(b) 3D seismic data containing reflections, diffractions and random noise.
+(c) 2D section extracted from (a).
+(d) 2D section extracted from (b).
+(e) Singular values distribution of the Hankel matrix in the 20 Hz slice of the data shown in (a).
+(f) Singular values distribution of the data shown in (b).
+}
+%\begin{figure}[htb!]
+% \centering
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/refl}
+%   \label{fig:refl}}
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/diffr}
+%   \label{fig:diffr}}   
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/syn}
+%   \label{fig:syn}}    
+%\caption{Benchmark dataset with groundtruth reflections and diffractions. (a) Reflection data. (b) Diffraction data. (c) Synthetic data. }
+%\label{fig:refl,diffr,syn}
+%\end{figure}
+%
+%\begin{figure}[htb!]
+% \centering
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-pwd-0}
+%   \label{fig:s-pwd-0}}
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-grr-0}
+%   \label{fig:s-grr-0}}   
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-lrra-0}
+%   \label{fig:s-lrra-0}}    
+%\caption{Separated reflections using (a) PWD method, (b) global rank-reduction method, and (c) proposed method.}
+%\label{fig:s-pwd-0,s-grr-0,s-lrra-0}
+%\end{figure}
+%
+%\begin{figure}[htb!]
+% \centering
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-pwd-n-0}
+%   \label{fig:s-pwd-n-0}}
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-grr-n-0}
+%   \label{fig:s-grr-n-0}}   
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-lrra-n-0}
+%   \label{fig:s-lrra-n-0}}    
+%\caption{Separated diffractions using (a) PWD method (SNR=6.52 dB), (b) global rank-reduction method (SNR=1.42 dB), and (c) proposed method (SNR=9.14 dB).}
+%\label{fig:s-pwd-n-0,s-grr-n-0,s-lrra-n-0}
+%\end{figure}
+%
+%\begin{figure}[htb!]
+%\centering
+%\subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-pwd-e-0}
+%  \label{fig:s-pwd-e-0}}
+%\subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-grr-e-0}
+%  \label{fig:s-grr-e-0}}   
+%\subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-lrra-e-0}
+%  \label{fig:s-lrra-e-0}}    
+%\caption{\new{Error of separated diffractions using (a) PWD method, (b) global rank-reduction method, and (c) proposed method.} \color{black}{}}
+%\label{fig:s-pwd-e-0,s-grr-e-0,s-lrra-e-0}
+%\end{figure}
 
-\begin{figure}[htb!]
- \centering
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/refl}
-   \label{fig:refl}}
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/diffr}
-   \label{fig:diffr}}   
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/syn}
-   \label{fig:syn}}    
-\caption{Benchmark dataset with groundtruth reflections and diffractions. (a) Reflection data. (b) Diffraction data. (c) Synthetic data. }
-\label{fig:refl,diffr,syn}
-\end{figure}
-
-\begin{figure}[htb!]
- \centering
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-pwd-0}
-   \label{fig:s-pwd-0}}
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-grr-0}
-   \label{fig:s-grr-0}}   
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-lrra-0}
-   \label{fig:s-lrra-0}}    
-\caption{Separated reflections using (a) PWD method, (b) global rank-reduction method, and (c) proposed method.}
-\label{fig:s-pwd-0,s-grr-0,s-lrra-0}
-\end{figure}
-
-\begin{figure}[htb!]
- \centering
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-pwd-n-0}
-   \label{fig:s-pwd-n-0}}
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-grr-n-0}
-   \label{fig:s-grr-n-0}}   
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-lrra-n-0}
-   \label{fig:s-lrra-n-0}}    
-\caption{Separated diffractions using (a) PWD method (SNR=6.52 dB), (b) global rank-reduction method (SNR=1.42 dB), and (c) proposed method (SNR=9.14 dB).}
-\label{fig:s-pwd-n-0,s-grr-n-0,s-lrra-n-0}
-\end{figure}
-
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-pwd-e-0}
-  \label{fig:s-pwd-e-0}}
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-grr-e-0}
-  \label{fig:s-grr-e-0}}   
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/s-lrra-e-0}
-  \label{fig:s-lrra-e-0}}    
-\caption{\new{Error of separated diffractions using (a) PWD method, (b) global rank-reduction method, and (c) proposed method.} \color{black}{}}
-\label{fig:s-pwd-e-0,s-grr-e-0,s-lrra-e-0}
-\end{figure}
+\inputdir{syn3d}
+\multiplot{3}{refll,diffrr,syn3d2}{width=0.45\columnwidth}{Benchmark dataset with groundtruth reflections and diffractions. (a) Reflection data. (b) Diffraction data. (c) Synthetic data. }
+\multiplot{3}{s-pwd-0,s-grr-0,s-lrra-0}{width=0.45\columnwidth}{Separated reflections using (a) PWD method, (b) global rank-reduction method, and (c) proposed method.}
+\multiplot{3}{s-pwd-n-0,s-grr-n-0,s-lrra-n-0}{width=0.45\columnwidth}{Separated reflections using (a) PWD method (SNR=6.52 dB), (b) global rank-reduction method (SNR=1.42 dB), and (c) proposed method (SNR=9.14 dB).}
+\multiplot{3}{s-pwd-e-0,s-grr-e-0,s-lrra-e-0}{width=0.45\columnwidth}{Error of separated diffractions using (a) PWD method, (b) global rank-reduction method, and (c) proposed method.}
 
@@
 Therefore, the contribution of the last few singular values is the smallest, while the first few singular values contribute more to reconstructing the data.
-The rank-reduction method also considers the energy discrepancy, i.e., the dynamic differences, to separate weak diffractions and strong reflections \cite{2010Separation, 2016Diffraction}.
+The rank-reduction method also considers the energy discrepancy, i.e., the dynamic differences, to separate weak diffractions and strong reflections \cite[]{2010Separation, 2016Diffraction}.
 
@@
 Let a 3D seismic data be denoted by $S(x, y, t)$, $x=1,\cdots, N_x$, $y=1,\cdots, N_y$, and $t=1,\cdots, N_t$, where $N_x$, $N_y$ and $N_t$ represent the numbers of samples in spatial and time axes, respectively.
-The rank-reduction method \cite{2011Simultaneous,weilin2016dmssa} is implemented in the frequency domain, thus the first step is to obtain the corresponding frequency-domain data $S(x, y,f )$  by forward Fourier transform $\mathcal{F}$.
+The rank-reduction method \cite[]{2011Simultaneous,weilin2016dmssa} is implemented in the frequency domain, thus the first step is to obtain the corresponding frequency-domain data $S(x, y,f )$  by forward Fourier transform $\mathcal{F}$.
 For a given frequency $f_0$, we construct the block Hankel matrix $\mathbf{{H}}$ by mapping the frequency-domain data into several Hankel matrices $\mathbf{\widetilde{H}}_i(f_0)$ through the Hankelization operator $\mathcal{H}$.
@@
 
-\cite{Zheng2014A} point out that the component with strong energy corresponds to a large singular value, i.e., the strong signals correspond to large singular values.
+\cite[]{Zheng2014A} point out that the component with strong energy corresponds to a large singular value, i.e., the strong signals correspond to large singular values.
 On the contrary, the smaller singular values represent the energy of diffractions and noise.
@@
 
-Thus, the problem of diffraction separation is transformed into estimating the reflection, which can be addressed by applying the singular-value decomposition (SVD) algorithm to the block Hankel matrix \cite{Chen2016An}.
+Thus, the problem of diffraction separation is transformed into estimating the reflection, which can be addressed by applying the singular-value decomposition (SVD) algorithm to the block Hankel matrix \cite[]{Chen2016An}.
 In particular, truncated singular-value decomposition (TSVD) is usually used to suppress the noise.
@@
 \end{equation}
-where $\mathbf{\hat{H}}$ denotes the denoised block Hankel matrix, i.e., the noise can be suppressed by ignoring some smaller singular values \cite{2020Diffraction}.
+where $\mathbf{\hat{H}}$ denotes the denoised block Hankel matrix, i.e., the noise can be suppressed by ignoring some smaller singular values \cite[]{2020Diffraction}.
 $\mathbf{\Sigma}=[{\sigma}_1,{\sigma}_2,\cdots,{\sigma}_N]$ is the diagonal singular matrix, $\mathbf{U}=[\mathbf{u}_1,\mathbf{u}_2,\cdots,\mathbf{u}_N]$ and $\mathbf{V}=[\mathbf{v}_1,\mathbf{v}_2,\cdots,\mathbf{v}_N]$ are left and right singular matrices, respectively.
@@
 
-\begin{figure}[htb!]
- \centering
- \subfigure[]{\includegraphics[width=0.6\columnwidth]{plot/Fig/ovp}
-   \label{fig:ovp}}
- \subfigure[]{\includegraphics[width=0.6\columnwidth]{plot/Fig/o}
-   \label{fig:o}}     
-\caption{(a) Velocity model of the first synthetic example. (b) Zero-offset data simulated from the velocity model.}
-\label{fig:ovp,o}
-\end{figure}
-
-\begin{figure}[htb!]
- \centering
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-pwd}
-   \label{fig:o-pwd}}
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrr}
-   \label{fig:o-lrr}}   
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrra}
-   \label{fig:o-lrra}} \\
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-pwd-n-0}
-   \label{fig:o-pwd-n-0}}
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrr-n-0}
-   \label{fig:o-lrr-n-0}}   
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrra-n-0}
-   \label{fig:o-lrra-n-0}}    
-\caption{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
+%\begin{figure}[htb!]
+% \centering
+% \subfigure[]{\includegraphics[width=0.6\columnwidth]{plot/Fig/ovp}
+%   \label{fig:ovp}}
+% \subfigure[]{\includegraphics[width=0.6\columnwidth]{plot/Fig/o}
+%   \label{fig:o}}     
+%\caption{(a) Velocity model of the first synthetic example. (b) Zero-offset data simulated from the velocity model.}
+%\label{fig:ovp,o}
+%\end{figure}
+%
+%\begin{figure}[htb!]
+% \centering
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-pwd}
+%   \label{fig:o-pwd}}
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrr}
+%   \label{fig:o-lrr}}   
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrra}
+%   \label{fig:o-lrra}} \\
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-pwd-n-0}
+%   \label{fig:o-pwd-n-0}}
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrr-n-0}
+%   \label{fig:o-lrr-n-0}}   
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrra-n-0}
+%   \label{fig:o-lrra-n-0}}    
+%\caption{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
 Second row: separated diffractions using (d) the PWD method, (e) the LRR method, and (f) the LRRA method.}
-\label{fig:o-pwd,o-lrr,o-lrra,o-pwd-n-0,o-lrr-n-0,o-lrra-n-0}
-\end{figure}
-
-\begin{figure}[htb!]
- \centering
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-pwd-imag-0}
-   \label{fig:o-pwd-imag-0}}
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrr-imag-0}
-   \label{fig:o-lrr-imag-0}}   
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrra-imag-0}
-   \label{fig:o-lrra-imag-0}}    
-\caption{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. The arrows indicate less reflection energy and higher resolution using the LRRA method.}
-\label{fig:o-pwd-imag-0,o-lrr-imag-0,o-lrra-imag-0}
-\end{figure}
+%\label{fig:o-pwd,o-lrr,o-lrra,o-pwd-n-0,o-lrr-n-0,o-lrra-n-0}
+%\end{figure}
+%
+%\begin{figure}[htb!]
+% \centering
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-pwd-imag-0}
+%   \label{fig:o-pwd-imag-0}}
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrr-imag-0}
+%   \label{fig:o-lrr-imag-0}}   
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/o-lrra-imag-0}
+%   \label{fig:o-lrra-imag-0}}    
+%\caption{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. The arrows indicate less reflection energy and higher resolution using the LRRA method.}
+%\label{fig:o-pwd-imag-0,o-lrr-imag-0,o-lrra-imag-0}
+%\end{figure}
 
@@
 A large value of threshold will damage the diffraction energy because a part of the diffraction energy is mixed in the  reconstructed reflections.
-Consequently,  the determination of rank values is challenging, and conventional strategies, such as  the difference curvature method \cite{Vicente2011Simultaneous}, may be artificial. 
+Consequently,  the determination of rank values is challenging, and conventional strategies, such as  the difference curvature method \cite[]{Vicente2011Simultaneous}, may be artificial. 
 Besides, it is difficult and time-consuming to manually specify a rank value in each local window.
@@
 
-\begin{figure}[htb!]
- \centering
- \subfigure[]{\includegraphics[width=0.6\columnwidth]{plot/Fig/kvp}
-   \label{fig:kvp}}
- \subfigure[]{\includegraphics[width=0.6\columnwidth]{plot/Fig/k}
-   \label{fig:k}}     
-\caption{(a) Velocity model of the second synthetic example. (b) Zero-offset data simulated from the velocity model.}
-\label{fig:kvp,k}
-\end{figure}
+%\begin{figure}[htb!]
+% \centering
+% \subfigure[]{\includegraphics[width=0.6\columnwidth]{plot/Fig/kvp}
+%   \label{fig:kvp}}
+% \subfigure[]{\includegraphics[width=0.6\columnwidth]{plot/Fig/k}
+%   \label{fig:k}}     
+%\caption{(a) Velocity model of the second synthetic example. (b) Zero-offset data simulated from the velocity model.}
+%\label{fig:kvp,k}
+%\end{figure}
+%
+%\begin{figure}[htb!]
+% \centering
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-pwd}
+%   \label{fig:k-pwd}}
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrr}
+%   \label{fig:k-lrr}}   
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrra}
+%   \label{fig:k-lrra}} \\
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-pwd-n-0}
+%   \label{fig:k-pwd-n-0}}
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrr-n-0}
+%   \label{fig:k-lrr-n-0}}   
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrra-n-0}
+%   \label{fig:k-lrra-n-0}}    
+%\caption{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
+Second row: separated diffractions using (d) the PWD method, (e) the LRR method, and (f) the LRRA method.}
+%\label{fig:k-pwd,k-lrr,k-lrra,k-pwd-n-0,k-lrr-n-0,k-lrra-n-0}
+%\end{figure}
+%
+%\begin{figure}[htb!]
+% \centering
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-pwd-imag-0}
+%   \label{fig:k-pwd-imag-0}}
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrr-imag-0}
+%   \label{fig:k-lrr-imag-0}}   
+% \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrra-imag-0}
+%   \label{fig:k-lrra-imag-0}}    
+%\caption{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. The arrows indicate less reflection energy and higher resolution using the LRRA method.}
+%\label{fig:k-pwd-imag-0,k-lrr-imag-0,k-lrra-imag-0}
+%\end{figure}
 
-\begin{figure}[htb!]
- \centering
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-pwd}
-   \label{fig:k-pwd}}
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrr}
-   \label{fig:k-lrr}}   
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrra}
-   \label{fig:k-lrra}} \\
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-pwd-n-0}
-   \label{fig:k-pwd-n-0}}
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrr-n-0}
-   \label{fig:k-lrr-n-0}}   
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrra-n-0}
-   \label{fig:k-lrra-n-0}}    
-\caption{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
+%uncomment
+%\inputdir{plot}
+%\multiplot{2}{ovp,o}{width=0.6\columnwidth}{(a) Velocity model of the first synthetic example. (b) Zero-offset data simulated from the velocity model.}
+%
+%\multiplot{6}{o-pwd,o-lrr,o-lrra,o-pwd-n-0,o-lrr-n-0,o-lrra-n-0}{width=0.3\columnwidth}{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
 Second row: separated diffractions using (d) the PWD method, (e) the LRR method, and (f) the LRRA method.}
-\label{fig:k-pwd,k-lrr,k-lrra,k-pwd-n-0,k-lrr-n-0,k-lrra-n-0}
-\end{figure}
+%
+%\multiplot{3}{o-pwd-imag-0,o-lrr-imag-0,o-lrra-imag-0}{width=0.45\columnwidth}{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
+The arrows indicate less reflection energy and higher resolution using the LRRA method.}
 
-\begin{figure}[htb!]
- \centering
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-pwd-imag-0}
-   \label{fig:k-pwd-imag-0}}
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrr-imag-0}
-   \label{fig:k-lrr-imag-0}}   
- \subfigure[]{\includegraphics[width=0.31\columnwidth]{plot/Fig/k-lrra-imag-0}
-   \label{fig:k-lrra-imag-0}}    
-\caption{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. The arrows indicate less reflection energy and higher resolution using the LRRA method.}
-\label{fig:k-pwd-imag-0,k-lrr-imag-0,k-lrra-imag-0}
-\end{figure}
+%\multiplot{2}{kvp,k}{width=0.6\columnwidth}{(a) Velocity model of the second synthetic example. (b) Zero-offset data simulated from the velocity model.}
+%
+%\multiplot{6}{k-pwd,k-lrr,k-lrra,k-pwd-n-0,k-lrr-n-0,k-lrra-n-0}{width=0.3\columnwidth}{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
+Second row: separated diffractions using (d) the PWD method, (e) the LRR method, and (f) the LRRA method.}
+%
+%\multiplot{3}{k-pwd-imag-0,k-lrr-imag-0,k-lrra-imag-0}{width=0.45\columnwidth}{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }
+%
 
 \section{Examples}
-In this part, we will first benchmark the proposed method with two state-of-the-art methods, i.e., the PWD method \cite{2007Post} and the global rank-reduction (GRR) method \cite{2020Diffraction}, based on a relatively simple but representative 3D dataset.
+In this part, we will first benchmark the proposed method with two state-of-the-art methods, i.e., the PWD method \cite[]{2007Post} and the global rank-reduction (GRR) method \cite[]{2020Diffraction}, based on a relatively simple but representative 3D dataset.
 Then, we will test the effects of the diffraction separation methods on diffraction imaging of two 3D synthetic models.
@@
 
-%\inputdir{plot}
-%\multiplot{3}{refl,diffr,syn}{width=0.45\columnwidth}{Benchmark dataset with groundtruth reflections and diffractions. (a) Reflection data. (b) Diffraction data. (c) Synthetic data. }
-%\multiplot{3}{s-pwd-0,s-grr-0,s-lrra-0}{width=0.45\columnwidth}{Separated reflections using (a) PWD method, (b) global rank-reduction method, and (c) proposed method.}
-%\multiplot{3}{s-pwd-n-0,s-grr-n-0,s-lrra-n-0}{width=0.45\columnwidth}{Separated reflections using (a) PWD method (SNR=6.52 dB), (b) global rank-reduction method (SNR=1.42 dB), and (c) proposed method (SNR=9.14 dB).}
-
 \subsection{Synthetic diffraction imaging test}
-The first diffraction imaging test is based on the Ordovician model \cite{decker2015carbonate,janson2010ultra,decker2015carbonate}. This model 
+The first diffraction imaging test is based on the Ordovician model \cite[]{decker2015carbonate,janson2010ultra,decker2015carbonate}. This model 
 is built based on the Ordovician limestone strata located in Tarim Basin, China, to test the diffraction imaging methods in characterizing paleokarst features in very deeply buried strata.
@@
 
-%\inputdir{plot}
-%\multiplot{2}{ovp,o}{width=0.6\columnwidth}{(a) Velocity model of the first synthetic example. (b) Zero-offset data simulated from the velocity model.}
-%
-%\multiplot{6}{o-pwd,o-lrr,o-lrra,o-pwd-n-0,o-lrr-n-0,o-lrra-n-0}{width=0.3\columnwidth}{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
-Second row: separated diffractions using (d) the PWD method, (e) the LRR method, and (f) the LRRA method.}
-%
-%\multiplot{3}{o-pwd-imag-0,o-lrr-imag-0,o-lrra-imag-0}{width=0.45\columnwidth}{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
-The arrows indicate less reflection energy and higher resolution using the LRRA method.}
-
-The second diffraction imaging test is based on the Khuff model \cite{decker2015carbonate,janson2013outcrop}, which corresponds to the Permian-Triassic Khuff reservoir that crops out in central Saudi Arabia near Buraydah.
-This model was originally built to study the influence of small-scale heterogeneities in carbonate reservoirs on the subsurface flow models \cite{janson2013outcrop}.
+The second diffraction imaging test is based on the Khuff model \cite[]{decker2015carbonate,janson2013outcrop}, which corresponds to the Permian-Triassic Khuff reservoir that crops out in central Saudi Arabia near Buraydah.
+This model was originally built to study the influence of small-scale heterogeneities in carbonate reservoirs on the subsurface flow models \cite[]{janson2013outcrop}.
 The velocity ($380\times200\times 128$) is plotted in Figure \ref{fig:kvp}.
@@
 
-%\multiplot{2}{kvp,k}{width=0.6\columnwidth}{(a) Velocity model of the second synthetic example. (b) Zero-offset data simulated from the velocity model.}
-%
-%\multiplot{6}{k-pwd,k-lrr,k-lrra,k-pwd-n-0,k-lrr-n-0,k-lrra-n-0}{width=0.3\columnwidth}{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
-Second row: separated diffractions using (d) the PWD method, (e) the LRR method, and (f) the LRRA method.}
-%
-%\multiplot{3}{k-pwd-imag-0,k-lrr-imag-0,k-lrra-imag-0}{width=0.45\columnwidth}{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }
-%
-
 \subsection{Field data example}
@@
 \new{It is a land seismic dataset from the Cooper Basin in Western Australia, which was used to characterize the tight-gas sand reservoir.
-Some previous studies regarding this dataset have been published in \cite{merzlikin2017analytical} and \cite{tyiasning2016comparison}.} \new{Detailed geological description of the area as well as the comparison of diffraction imaging results to discontinuity-type attributes is given by \cite{tyiasning2016comparison}.
+Some previous studies regarding this dataset have been published in \cite[]{merzlikin2017analytical} and \cite[]{tyiasning2016comparison}.} \new{Detailed geological description of the area as well as the comparison of diffraction imaging results to discontinuity-type attributes is given by \cite[]{tyiasning2016comparison}.
 \new{In particular, this dataset has fully azimuthal distribution of offsets and a far offset of 4000 m.
-The horizon maps shown below come from an interface between a pervasive sheet coal and fluvial Permian Patchawarra Sand at a depth of approximately 2500 m \cite{tyiasning2016comparison}.} The Patchawarra Sand is a tight-gas sand at this field.} The 3D post-stack dataset is plotted in Figure \ref{fig:b}.
+The horizon maps shown below come from an interface between a pervasive sheet coal and fluvial Permian Patchawarra Sand at a depth of approximately 2500 m \cite[]{tyiasning2016comparison}.} The Patchawarra Sand is a tight-gas sand at this field.} The 3D post-stack dataset is plotted in Figure \ref{fig:b}.
 Figures \ref{fig:b-pwd}-\ref{fig:b-lrra} plot the separated reflection data using the PWD, LRR, and LRRA methods, respectively.
@@
 To better visualize the difference of the separated diffractions in a horizontal slice, we extract a time slice (t=1.7 s) from the diffraction cubes and show the comparison in Figure \ref{fig:b-pwd-n-t-0,b-lrr-n-t-0,b-lrra-n-t-0}, where it is clearer to see the reflection energy using the PWD method.
-We migrate the separated diffractions using an analytical path-summation imaging method \cite{merzlikin2017analytical}, and show an extracted time slice in Figure \ref{fig:b-pwd-rimag-0,b-pwd-imag-0,b-lrr-imag-0,b-lrra-imag-0}.
+We migrate the separated diffractions using an analytical path-summation imaging method \cite[]{merzlikin2017analytical}, and show an extracted time slice in Figure \ref{fig:b-pwd-rimag-0,b-pwd-imag-0,b-lrr-imag-0,b-lrra-imag-0}.
 Apart from the diffraction images, we also show a conventional reflection image in Figure \ref{fig:b-pwd-rimag-0} for evaluating the advantage of the diffraction imaging in delineating small-scale heterogeneities.
@@
 It is known that the PWD method is based on the local slope calculation and the spatial coherency difference between the reflections and diffractions.
-On the one hand, the slope estimation based on the PWD method suffers from the noise sensitivity, as reported in many previous studies \cite{shaohuan2017,wanghang2020tgrs2,chenwei2021geo,chenwei2021tgrs2}.
+On the one hand, the slope estimation based on the PWD method suffers from the noise sensitivity, as reported in many previous studies \cite[]{shaohuan2017,wanghang2020tgrs2,chenwei2021geo,chenwei2021tgrs2}.
 The inaccurate slope estimation will affect the separation performance between diffractions and reflections, causing the coupling effect.
@@
 Thus, the assumption of the rank-reduction method is not valid for processing a large 3D realistic seismic dataset without applying the windowing strategy.
-Previous 2D diffraction imaging method based on the GRR method has shown some promising results \cite{2020Diffraction}, but causes significant artifacts due to the complication in the singular value distribution.
+Previous 2D diffraction imaging method based on the GRR method has shown some promising results \cite[]{2020Diffraction}, but causes significant artifacts due to the complication in the singular value distribution.
 The local rank-reduction method can help obtain better results because of the much-simplified data structure that follows the separation assumption.
-However, another problem arises due to the windowing strategy, i.e., the rank incoherency issue \cite{shaohuan2017gji,yangkang2017ieee}.
+However, another problem arises due to the windowing strategy, i.e., the rank incoherency issue \cite[]{shaohuan2017gji,yangkang2017ieee}.
 The adaptive rank selection method proposed in this paper well solves the rank incoherency problem by adapting the local structure with the automatically chosen rank parameter.
@@
 If the noise is random, it will be combined with the diffraction energy as the output of the local rank-reduction method.
-It is possible to further separate the random noise from the diffraction energy by leveraging their differences in the singular spectrum \cite{weilin2017dlsp,oboue2021geo1,oboue2021geo2}.
+It is possible to further separate the random noise from the diffraction energy by leveraging their differences in the singular spectrum \cite[]{weilin2017dlsp,oboue2021geo1,oboue2021geo2}.
 If the noise is random but linear, it will likely be considered as the diffraction energy, and could be interfering the separated diffraction energy when input to the imaging framework.
 However, it indeed depends on the spatial coherency difference between the linear noise and the diffraction energy.
-If the linear noise is steeply dipping and is more spatially incoherent than diffraction energy \cite{weilin2017mmf}, then the proposed method could still be effective in distinguishing the two components.
+If the linear noise is steeply dipping and is more spatially incoherent than diffraction energy \cite[]{weilin2017mmf}, then the proposed method could still be effective in distinguishing the two components.
 }
@@
 For the other three datasets, the global method is prohibitively expensive, thus we do not show the results.
-Note that to further increase the computational efficiency, a randomized SVD can also be used to obtain a large speedup but at the expense of degrading the performance \cite{li2014large}.
+Note that to further increase the computational efficiency, a randomized SVD can also be used to obtain a large speedup but at the expense of degrading the performance \cite[]{li2014large}.
 The automatic rank selection strategy almost adds no extra computational cost to the rank-reduction method, so the overall computational efficiency of the proposed method is acceptable.
 
-\begin{figure}[htb!]
- \centering
- \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b}
-   \label{fig:b}}
- \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-pwd}
-   \label{fig:b-pwd}}    \\
- \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrr}
-   \label{fig:b-lrr}}    
- \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrra}
-   \label{fig:b-lrra}} 
-\caption{Field data example. (a) A 3D field dataset. Separated reflection data using (b) the PWD method, (c) the LRR method, and (d) the LRRA method. }
-\label{fig:b,b-pwd,b-lrr,b-lrra}
-\end{figure}
-
-\begin{figure}[htb!]
- \centering
- \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-pwd-n-0}
-   \label{fig:b-pwd-n-0}}
- \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrr-n-0}
-   \label{fig:b-lrr-n-0}}   
- \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrra-n-0}
-   \label{fig:b-lrra-n-0}}    
-\caption{Separated diffraction data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.}
-\label{fig:b-pwd-n-0,b-lrr-n-0,b-lrra-n-0}
-\end{figure}
-
-\begin{figure}[htb!]
- \centering
- \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-pwd-n-t-0}
-   \label{fig:b-pwd-n-t-0}}
- \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrr-n-t-0}
-   \label{fig:b-lrr-n-t-0}}   
- \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrra-n-t-0}
-   \label{fig:b-lrra-n-t-0}}    
-\caption{A comparison of time slices extracted from the separated diffraction data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }
-\label{fig:b-pwd-n-t-0,b-lrr-n-t-0,b-lrra-n-t-0}
-\end{figure}
-
-\begin{figure}[htb!]
-\centering
-\subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-pwd-rimag-0}
-  \label{fig:b-pwd-rimag-0}}
-\subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-pwd-imag-0}
-  \label{fig:b-pwd-imag-0}} \\
-\subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrr-imag-0}
-  \label{fig:b-lrr-imag-0}}   
-\subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrra-imag-0}
-  \label{fig:b-lrra-imag-0}}    
-\caption{(a) Time slice of the reflection image.
+%\begin{figure}[htb!]
+% \centering
+% \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b}
+%   \label{fig:b}}
+% \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-pwd}
+%   \label{fig:b-pwd}}    \\
+% \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrr}
+%   \label{fig:b-lrr}}    
+% \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrra}
+%   \label{fig:b-lrra}} 
+%\caption{Field data example. (a) A 3D field dataset. Separated reflection data using (b) the PWD method, (c) the LRR method, and (d) the LRRA method. }
+%\label{fig:b,b-pwd,b-lrr,b-lrra}
+%\end{figure}
+%\begin{figure}[htb!]
+% \centering
+% \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-pwd-n-0}
+%   \label{fig:b-pwd-n-0}}
+% \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrr-n-0}
+%   \label{fig:b-lrr-n-0}}   
+% \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrra-n-0}
+%   \label{fig:b-lrra-n-0}}    
+%\caption{Separated diffraction data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.}
+%\label{fig:b-pwd-n-0,b-lrr-n-0,b-lrra-n-0}
+%\end{figure}
+%\begin{figure}[htb!]
+% \centering
+% \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-pwd-n-t-0}
+%   \label{fig:b-pwd-n-t-0}}
+% \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrr-n-t-0}
+%   \label{fig:b-lrr-n-t-0}}   
+% \subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrra-n-t-0}
+%   \label{fig:b-lrra-n-t-0}}    
+%\caption{A comparison of time slices extracted from the separated diffraction data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }
+%\label{fig:b-pwd-n-t-0,b-lrr-n-t-0,b-lrra-n-t-0}
+%\end{figure}
+%\begin{figure}[htb!]
+%\centering
+%\subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-pwd-rimag-0}
+%  \label{fig:b-pwd-rimag-0}}
+%\subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-pwd-imag-0}
+%  \label{fig:b-pwd-imag-0}} \\
+%\subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrr-imag-0}
+%  \label{fig:b-lrr-imag-0}}   
+%\subfigure[]{\includegraphics[width=0.48\columnwidth]{plot/Fig/b-lrra-imag-0}
+%  \label{fig:b-lrra-imag-0}}    
+%\caption{(a) Time slice of the reflection image.
 Time slices of the diffraction image using (b) the PWD method, (c) the LRR method, and (d) the LRRA method.
 The arrows indicate the higher resolution using the LRRA method and the lower resolution of the PWD method due to the consistency in depicting the crossline-oriented paleo-channel between the reflection and diffraction images.}
-\label{fig:b-pwd-rimag-0,b-pwd-imag-0,b-lrr-imag-0,b-lrra-imag-0}
-\end{figure}
+%\label{fig:b-pwd-rimag-0,b-pwd-imag-0,b-lrr-imag-0,b-lrra-imag-0}
+%\end{figure}
 
-%\plot{b}{width=0.6\columnwidth}{3D field dataset.}
+%% uncomment
 %\multiplot{4}{b,b-pwd,b-lrr,b-lrra}{width=0.45\columnwidth}{Field data example.
@@
 
-%\inputdir{./}
-%\plot{curve}{width=0.8\columnwidth}{SNR diagrams varying with different spatial window sizes.}
+\inputdir{./}
+\plot{curve}{width=0.8\columnwidth}{SNR diagrams varying with different spatial window sizes.}
 
-\begin{figure}[htb!]
-\centering
-\includegraphics[width=0.7\columnwidth]{Fig/curve}
-\caption{SNR diagrams varying with different spatial window sizes.}
-\label{fig:curve}
-\end{figure}
+\section{Acknowledgements}
+The research is supported by the National Natural Science Foundation of China (Grant No.
+41804140) and the Open Fund of Cooperative Innovation Center of Unconventional Oil and Gas, Yangtze University (Ministry of Education \& Hubei Province) (Grant No.
+UOG2021-01).
 
-%\section{Acknowledgements}
-%\section{DATA AND MATERIALS AVAILABILITY}
-%All datasets and source codes associated with this research will be made available online (www.ahay.org) as a reproducible article.
-
-\bibliographystyle{IEEEtran}
+\bibliographystyle{seg}
 \bibliography{diffr}
 
-\end{document}
+%\end{document}

### 2022-01-02 diffrlrra3d/matfun/LDRR.m

@@ -1,0 +1,77 @@
+function LDRR(din,d_lrr,d_lrra,n1,n2,n3,dt,lf,hf,N,N2,NN,n1win,n2win,n3win,r1,r2,r3,ifdamp,verb)
+% Author      : Yangkang Chen
+% Date        : March, 2020
+
+% Requirements: RSF (http://rsf.sourceforge.net/) with Matlab API
+
+%  Copyright (C) 2020 Zhejiang University
+%  Copyright (C) 2020 Yangkang Chen
+%  Modified by YC on Jan 24, 2021
+% 
+%  This program is free software; you can redistribute it and/or modify
+%  it under the terms of the GNU General Public License as published by
+%  the Free Software Foundation; either version 2 of the License, or
+%  (at your option) any later version.
+%
+%  This program is distributed in the hope that it will be useful,
+%  but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, write to the Free Software
+%  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307
+%
+%  REFERENCES
+%  Wang et al., 2020, Separation and imaging of seismic diffractions using a localized rank-reduction method with adaptively selected ranks, 85, V497–V506.
+%  Chen et al., 2019, Obtaining free USArray data by multi-dimensional seismic reconstruction, Nature Communications, 10:4434.
+%  Bai et al., 2020, Seismic signal enhancement based on the lowrank methods, Geophysical Prospecting, 68, 2783-2807.
+%  Chen et al., 2020, Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method, Geophysical Journal International, 222, 1824-1845.
[…]

### 2022-01-03 diffrlrra3d/paper.tex
Mon Jan  3 09:21:50 CST 2022

@@
 %uncomment
-%\inputdir{plot}
-%\multiplot{2}{ovp,o}{width=0.6\columnwidth}{(a) Velocity model of the first synthetic example. (b) Zero-offset data simulated from the velocity model.}
-%
-%\multiplot{6}{o-pwd,o-lrr,o-lrra,o-pwd-n-0,o-lrr-n-0,o-lrra-n-0}{width=0.3\columnwidth}{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
+\inputdir{o}
+\multiplot{2}{ovp,o}{width=0.6\columnwidth}{(a) Velocity model of the first synthetic example. (b) Zero-offset data simulated from the velocity model.}
+
+\multiplot{6}{o-pwd,o-lrr,o-lrra,o-pwd-n-0,o-lrr-n-0,o-lrra-n-0}{width=0.3\columnwidth}{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
 Second row: separated diffractions using (d) the PWD method, (e) the LRR method, and (f) the LRRA method.}
-%
-%\multiplot{3}{o-pwd-imag-0,o-lrr-imag-0,o-lrra-imag-0}{width=0.45\columnwidth}{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
+
+\multiplot{3}{o-pwd-imag-0,o-lrr-imag-0,o-lrra-imag-0}{width=0.45\columnwidth}{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
 The arrows indicate less reflection energy and higher resolution using the LRRA method.}
 
-%\multiplot{2}{kvp,k}{width=0.6\columnwidth}{(a) Velocity model of the second synthetic example. (b) Zero-offset data simulated from the velocity model.}
-%
-%\multiplot{6}{k-pwd,k-lrr,k-lrra,k-pwd-n-0,k-lrr-n-0,k-lrra-n-0}{width=0.3\columnwidth}{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
+\inputdir{k}
+\multiplot{2}{kvp,k}{width=0.6\columnwidth}{(a) Velocity model of the second synthetic example. (b) Zero-offset data simulated from the velocity model.}
+
+\multiplot{6}{k-pwd,k-lrr,k-lrra,k-pwd-n-0,k-lrr-n-0,k-lrra-n-0}{width=0.3\columnwidth}{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
 Second row: separated diffractions using (d) the PWD method, (e) the LRR method, and (f) the LRRA method.}
-%
-%\multiplot{3}{k-pwd-imag-0,k-lrr-imag-0,k-lrra-imag-0}{width=0.45\columnwidth}{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }
-%
+
+\multiplot{3}{k-pwd-imag-0,k-lrr-imag-0,k-lrra-imag-0}{width=0.45\columnwidth}{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }
 

### 2022-01-05 orthoa/paper.tex
Wed Jan  5 16:55:45 CST 2022

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}
\DeclareRobustCommand{\old}[1]{}
\DeclareRobustCommand{\new}[1]{#1}

\title{Accelerated signal-and-noise orthogonalization}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Guangtan Huang, Dong Zhang, Wei Chen, and Yangkang Chen}
%\author{Guangtan Huang, Dong Zhang, Wei Chen, and Yangkang Chen
%\thanks{G. Huang and Y. Chen are with Key Laboratory of Geoscience Big Data and Deep Resource of Zhejiang Province, School of Earth Sciences, Zhejiang University, Hangzhou 310027, China.}
%\thanks{D. Zhang is Department of Imaging Physics, Delft University of Technology, Lorentzweg 1, 2628 CJ, Delft, The Netherlands.}
%\thanks{W. Chen is with Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education, Yangtze University, Wuhan 430100, China.}
%\thanks{This work was supported in part by the Starting Fund from Zhejiang University, the National Natural Science Foundation of China under Grant 41804140, and the Open Fund of Key Laboratory of Exploration Technologies for Oil and Gas Resources (Yangtze University), Ministry of Education, under Grant PI2018-02. (Corresponding authors: Wei Chen)}}
\maketitle

\begin{abstract}
The local signal-to-noise orthogonalization algorithm has been widely used in the community of seismic processing and imaging. It helps orthogonalize the signal and noise components in an elegant way so that the noise does not contain the signal leakage in seismic denoising. %a denoising application.  or the wave components are better separated in a wavefield propagation problem. 
The traditional local signal-to-noise orthogonalization is based on solving a highly under-determined ill-posed inverse problem with local smoothness constraint. Due to the inversion nature, the local orthogonalization method requires a large number of iterations, and thus is computationally demanding in large-scale applications. Here, we proposed a much accelerated signal-and-noise orthogonalization method, where we design an efficient way for calculating the orthogonalization weight. When new samples are involved in the calculation, we calculate the orthogonalization weight of the new samples by connecting them with the calculated weights of previous samples. The orthogonalization weight needs to be smoothed and scaled after all samples have been processed to make the resulted orthogonalization weight smooth across the seismic data and match the amplitude level of the initially suppressed noise. In this way, we avoid iterations when calculating the orthogonalization weight. We apply the proposed method to several synthetic and field data examples, have a benchmark comparison with state-of-the-art algorithms, and demonstrate its much accelerated efficiency compared with the traditional local signal-and-noise orthogonalization.
\end{abstract}

%\begin{keywords}
%Denoising, local orthogonalization, seismic data processing
%\end{keywords}

\section{Introduction}
The seismic data profile is composed of different components, e.g., useful signals and unwanted noise. To enhance the useful components while rejecting those unwanted components has been an exclusively studied research topic \cite{canales1984,yangkang20141,yanan2014,yangkang20142,curveletieee2016,mostafa2016geo,weilin2016dmssa,xue2017full,shaohuan2018ieee,wang2019hankel,yangkang2019nc,wang2019efficient,omar2020geo1,wanghang2021geo}. Generally, such components play different roles depending on the purpose. In conventional processing, components other than the primary reflected waves are often considered as noise. However, with the development of exploration technology, many components that are considered noise have gradually been accepted and considered to be very useful. For instance, multiple waves, which have long been regarded as noise in conventional processing, are an important part of the full wavefield imaging and inversion \cite{verschuur2011}.  Such a relationship is also reflected in the diffracted wave to the diffraction imaging \cite{fomel2007}. Moreover, the interfering ambient noise can also be considered as signals when it comes to passive source seismic survey \cite{de2011ambient}. Thus, noise and signals themselves are not absolute concepts, which all depend on whether the signal component is needed for the undergoing work. Here, the signal is defined as those desired components in the seismic profiles, while noise is exploited to refer to the rest unwanted components. Therefore, how to separate the required and non-required components in the signal according to certain characteristics has an important role in the seismic data processing.

Chen and Fomel (2015) \cite{yangkang2015ortho} first proposed a secondary processing step, which is so-called the local signal-and-noise orthogonalization, to optimize the separation of signal and noise components after initial processing.  Such an algorithm effectively solve the signal leakage problem, which is a commonly existing problem in denoising processing. Local signal-and-noise orthogonalization makes use of the local orthogonality of signal and noise to separate the two without leakage. However, traditional methods always cause more or less signal leakage due to wrong parameter selection or insufficient denoising assumptions. Instead of using such a long name, here we use the local orthogonalization method to indicate this algorithm throughout this article for simplicity. The local orthogonalization method can retrieve the lost signal energy from the noise eliminated by a traditional denoising algorithm by using an element-wise weighting operator. Such an operator can be obtained by solving an inverse problem, where the model is constrained by a smoothing operator.

The local orthogonalization method has first demonstrated the performance via random noise attenuation \cite{yangkang2015ortho}. Although there are many methods for random noise suppression, the signal leakage problem still exists in these traditional methods. The local orthogonalization method effectively improves the denoising performance, and avoids the leakage of the effective signal as much as possible, and lays the foundation for subsequent imaging and inversion. Then, the algorithm has been widely exploited in some other seismic denoising processing, including ground roll noise removal, deblending, and demultiple, etc. Chen et al. (2015) \cite{yangkang2015orthogroll} then applied this method to help to suppress the ground roll noise. This approach is also based on the low-pass filtering based method to remove the ground roll noise, and then retrieve those reflection components that should not be suppressed from the removed noise.  In a similar way, Chen (2015) \cite{yangkang2015dbortho} introduced the algorithm into the iterative simultaneous-source separation framework \cite{yangkang20142,shaohuan2019} to improve the deblending effect. Introducing the local orthogonalization method in each iteration greatly improves the deblending performance and accelerates the convergency. \cite{zhangdong2019ortho} combined the algorithm with the surface-related multiple elimination (SRME) to retrieve the leaked multiples energy in the initially demultipled data, which effectively separate the primaries and multiples. \cite{zhangdong2020geo} further used the local orthogonalization method to suppress internel multiples from full-wavefield migrated images.

In addition to noise removal, the local orthogonalization method has also been widely used in wavefield decomposition. By compensating the amplitude leakage in each separated wave component, Sripanich et al. (2017) \cite{sripanich2017elastic} applied this method to better decompose the elastic wave modes in heterogeneous anisotropic media. Huang et al. (2018) \cite{weilin2018} better decomposed a microseismic trace via introducing the local orthogonalization method into a mathematical morphology algorithm. The improved algorithm decomposed the microseismic trace into quasi-orthogonal components, which can be exploited for weak microseismic signal detection.  Jeong et al. (2019) \cite{jeong2019enhanced} applied this method to the P- and S-components separation of elastic wave forward modeling, and further applied it to the multi-parameter full-waveform inversion (FWI). The inversion results demonstrate that the local orthogonalization method can not only decrease the residual energy or crosstalk caused by using conventional methods, but also accelerate the convergency of multi-parameter FWI and reduce likelihood of being trapped into local minima. Qu et al. (2020) \cite{qu2020robust} applied the local orthogonalization method to tackle the AVO effect in the joint migration inversion (JMI).

Due to the ill-posedness of the inverse problem, the objective function itself is also a function of the target parameters, thus a large number of iterations are required for solving the inverse problem. Similarly, the local orthogonalization method also requires a large number of iterations, and is computationally demanding in large-scale applications. Thus, the computational efficiency is an important bottleneck that limits the large-scale application of the local orthogonalization method in industrial use.  In this paper, to improve computing efficiency, we proposed a much accelerated signal-and-noise orthogonalization method, where we design an efficient way of calculating the orthogonalization weight. When new samples are involved in the calculation, we connect the orthogonalization weights of the new samples with the calculated weight of the previous samples to calculate the orthogonalization weights of the new samples. After processing all samples, the orthogonalization weights need to be smoothed and scaled so that the obtained orthogonalization weights are smoothed in the seismic data and matched with the amplitude level of the initial suppression noise. In this way, iteration is avoided when calculating the orthogonalization weights.

This paper is organized as follows. Firstly, we briefly review the theory of the conventional local signal-and-noise orthogonalization algorithm.  Then, the formula of the non-stationary triangle smoother and the iterative optimization method of adaptively obtaining a smooth radius map are introduced in detail. Next, the performance of the proposed method is proved by a set of representative examples. Finally, we draw some key conclusions.

\begin{figure}[htb!]
\centering
\includegraphics[width=0.45\textwidth]{Fig/demo_vec2}
\caption{Demonstration of the Gram-Schmidt orthogonalization.}
\label{fig:demo_vec2}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/c}
   \label{fig:c}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/n}
   \label{fig:n}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cn}
   \label{fig:cn}}\\
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cfx}
   \label{fig:cfx}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cfx2}
   \label{fig:cfx2}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cfx22}
   \label{fig:cfx22}}\\  
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cdifffx}
   \label{fig:cdifffx}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cdifffx2}
   \label{fig:cdifffx2}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cdifffx22}
   \label{fig:cdifffx22}}
\caption{Comparison of using the local-orthogonalization-based random noise attenuation approach for denoising test before and after. (a) Clean section. (b) Random noise section. (c) Noisy section (S/N=-0.75 dB). (d) Denoised result using $f$-$x$ deconvolution (S/N=9.21 dB). (e) Denoised result using the traditional orthogonalization method (S/N=10.99 dB). (f) Denoised result using the proposed method (S/N=10.40 dB). (g) Noise section using $f$-$x$ deconvolution. (h) Noise section using traditional orthogonalization method. (i) Noise section using the proposed method.}
\label{fig:c,n,cn,cfx,cfx2,cfx22,cdifffx,cdifffx2,cdifffx22}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/csimi-difffx}
   \label{fig:csimi-difffx}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/csimi-difffx2}
   \label{fig:csimi-difffx2}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/csimi-difffx22}
   \label{fig:csimi-difffx22}}
\caption{(a) Local similarity map using FX method. (b) Local similarity using the traditional orthogonalization method. (c) Local similarity using the proposed accelerated orthogonalization method.}
\label{fig:csimi-difffx,csimi-difffx2,csimi-difffx22}
\end{figure}

\section{Theory}
\subsection{Local signal-and-noise orthogonalization}
Given an input noisy seismic data $\mathbf{d}$, the signal and noise components after applying a normal denoising operator $\mathbf{P}$ can be expressed as:
\begin{align}
\label{eq:sn}
\mathbf{s} &= \mathbf{Pd}\\
\label{eq:snn}
\mathbf{n} &= \mathbf{d} -  \mathbf{Pd},
\end{align}
where $\mathbf{s}$ and $\mathbf{n}$ denote the initial signal and noise components after the initial denoising.

Due to inappropriate parameter selection or inadequacy of denoising assumptions \cite{yangkang2015ortho},  there will be still signal leakage in the noise component $\mathbf{n}$. The local signal-and-noise orthogonalization method was developed by \cite{yangkang2015ortho} to solve the signal leakage problem. The principle of the local signal-and-noise orthogonalization is to apply a weighting operator to retrieve the leaked signal component:
\begin{align}
\label{eq:sn1}
\hat{\mathbf{s}} &= \mathbf{s} + \tilde{\mathbf{s}},\\
\hat{\mathbf{n}} &= \mathbf{n} -  \tilde{\mathbf{s}},
\end{align}
where $\tilde{\mathbf{s}}$ denotes the leaked signal. The weight operator is expressed as a diagonal matrix composed of a weighting vector. The weighting vector can be obtained by extending the Gram-Schmidt orthogonalization \cite{gram} to a local version. An illustrative Fig. about the Gram-Schmidt orthogonalization is plotted in Fig. \ref{fig:demo_vec2}.  The vectors $\mathbf{s}$ and $\mathbf{n}$ can be orthogonalized by adding a scaled signal component $\mathbf{s}$ to the original signal component and subtracting the scale signal component from the noise component $\mathbf{n}$:
\begin{align}
\label{eq:sn2}
\hat{\mathbf{s}} &= \mathbf{s} + w\mathbf{s},\\
\label{eq:snn2}
\hat{\mathbf{n}} &= \mathbf{n} - w\mathbf{s},
\end{align}
where $\omega$ is a scalar denoting the orthogonalization weight. According to the principle of Gram-Schmidt orthogonalization, it is easy to derive that 
\begin{align}
\label{eq:sn3}
\omega=\frac{\mathbf{s}^T\mathbf{n}}{\mathbf{s}^T\mathbf{s}}.
\end{align}
In contrast to the local orthogonalization, we refer the orthogonalization weight in equation \ref{eq:sn3} as the global orthogonalization weight. The local orthogonalization weight indicates calculating the weight in a local way. The easiest way to define the local orthogonalization weight based on equation \ref{eq:sn3} is as follows:
\begin{align}
\label{eq:low}
w(x_1,x_2,x_3)=\frac{s(x_1,x_2,x_3)n(x_1,x_2,x_3)}{s(x_1,x_2,x_3)s(x_1,x_2,x_3)}=\frac{n(x_1,x_2,x_3)}{s(x_1,x_2,x_3)},
\end{align}
where $x_1,x_2,x_3$ denote the indices in the first, second, and third axes, respectively. Directly division between $n(x_1,x_2,x_3)$ and $s(x_1,x_2,x_3)$ is not stable. Instead, equation \ref{eq:low} can be transformed into an inverse problem as:
\begin{align}
\label{eq:low2}
w(x_1,x_2,x_3)s(x_1,x_2,x_3)=n(x_1,x_2,x_3).
\end{align}
Equation \ref{eq:low} can be solved via regularized least-squares inversion \cite{yangkang2015ortho}: 
\begin{equation}
\label{eq:low3}
\begin{split}
w_{k+1}(x_1,x_2,x_3)&= T(w_{k}+\lambda s_{k}(x_1,x_2,x_3)(n_{k}(x_1,x_2,x_3)\\
&-w_{k}(x_1,x_2,x_3)s_{k}(x_1,x_2,x_3))),
\end{split}
\end{equation}
where $T$ denotes a triangle-smoothing operator, and $\lambda$ denotes the step size for each model update.
\new{The triangle-smoothing operator is equivalent to applying a rectangle-smoothing operator twice.  The rectangle-smoothing operator can be expressed in the Z-transform form as follows:
\begin{equation}
\label{eq:box}
B(Z) = \frac{1}{N} ( 1+ Z + Z^2 +\cdots+Z^{N-1}) = \frac{1-Z^N}{N(1-Z)},
\end{equation}
where $N$ is the length for the rectangle-smoothing operator, or the radius for the triangle smoothing operator. The time-domain implementation of the rectangle-smoothing operator follows the recursive relation:
\begin{equation}
\label{eq:recur}
y_n = \frac{1}{N}(x_n - x_{n-N})+y_{n-1}
\end{equation}}
 Equation \ref{eq:low3} can be time-consuming for large-scale problems since it involves iterations. Besides, the smoothing operator applied in each iteration adds more computational cost to the orthogonalization process. The computational complexity of the inversion-based local orthogonalization method can be expressed as $O(N_{iter}N_d)$, where $N_{iter}$ denotes the number of iterations and $N_d$ denotes the data size. In a 3D problem, $N_d=N_1N_2N_3$, and $N_i$, $i\in\{1,2,3\}$, denotes the size of the $i$th dimension. In the traditional local orthogonalization method, the default number of iterations is 100. 
\new{The local orthogonalization is a two-step denoising method, which depends on effectiveness of the first-step denoising operator $\mathbf{P}$. The dependency of the initial denoising method is also the limitation of the orthogonalization method, i.e., the initial denoising operator should be able to remove sufficient noise without damaging much signal energy. When the initial denoising method completely removes the weak signal in the case of very strong noise, the local orthogonalization cannot be used to recover the completely lost signal. }

%\inputdir{complex}
%\multiplot{9}{c,n,cn,cfx,cfx2,cfx22,cdifffx,cdifffx2,cdifffx22}{width=0.2900\columnwidth}{Comparison of using the local-orthogonalization-based random noise attenuation approach for denoising test before and after. (a) Clean section. (b) Random noise section. (c) Noisy section (S/N=-0.75 dB). (d) Denoised result using $f$-$x$ deconvolution (S/N=9.21 dB). (e) Denoised result using the traditional orthogonalization method (S/N=10.99 dB). (f) Denoised result using the proposed method (S/N=10.40 dB). (g) Noise section using $f$-$x$ deconvolution. (h) Noise section using traditional orthogonalization method. (i) Noise section using the proposed method.}
%
%\multiplot{3}{csimi-difffx,csimi-difffx2,csimi-difffx22}{width=0.2900\columnwidth}{(a) Local similarity map using FX method. (b) Local similarity using the traditional orthogonalization method. (c) Local similarity using the proposed accelerated orthogonalization method. }
%

%\inputdir{csimul}
%\multiplot{9}{huo,huo-noise,huos,huos-mf,huos-ortho,huos-ortho2,huosdiff-mf,huosdiff-ortho,huosdiff-ortho2}{width=0.2900\columnwidth}{Comparison of using the local-orthogonalization-based blending noise attenuation approach for denoising test before and after. (a) Clean section. (b) Blending noise section. (c) Noisy section (S/N=0.78 dB). (d) Denoised result using median filtering (S/N=10.91 dB). (e) Denoised result using the traditional orthogonalization method (S/N=11.35 dB). (f) Denoised result using the proposed method (S/N=12.14 dB). (g) Noise section using median filtering. (h) Noise section using traditional orthogonalization method. (i) Noise section using the proposed method.}
%
%\multiplot{3}{huos-simi,huos-simi-ortho,huos-simi-ortho2}{width=0.2900\columnwidth}{(a) Local similarity map using median filtering. (b) Local similarity using the traditional orthogonalization method. (c) Local similarity using the proposed accelerated orthogonalization method. }
%

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huo}
   \label{fig:huo}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huo-noise}
   \label{fig:huo-noise}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos}
   \label{fig:huos}}\\
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-mf}
   \label{fig:huos-mf}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-ortho}
   \label{fig:huos-ortho}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-ortho2}
   \label{fig:huos-ortho2}}\\  
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huosdiff-mf}
   \label{fig:huosdiff-mf}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huosdiff-ortho}
   \label{fig:huosdiff-ortho}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huosdiff-ortho2}
   \label{fig:huosdiff-ortho2}}
\caption{Comparison of using the local-orthogonalization-based blending noise attenuation approach for denoising test before and after. (a) Clean section. (b) Blending noise section. (c) Noisy section (S/N=0.78 dB). (d) Denoised result using median filtering (S/N=10.91 dB). (e) Denoised result using the traditional orthogonalization method (S/N=11.35 dB). (f) Denoised result using the proposed method (S/N=12.14 dB). (g) Noise section using median filtering. (h) Noise section using traditional orthogonalization method. (i) Noise section using the proposed method.}
\label{fig:huo,huo-noise,huos,huos-mf,huos-ortho,huos-ortho2,huosdiff-mf,huosdiff-ortho,huosdiff-ortho2}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-simi}
   \label{fig:huos-simi}} 
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-simi-ortho}
   \label{fig:huos-simi-ortho}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-simi-ortho2}
   \label{fig:huos-simi-ortho2}}
\caption{(a) Local similarity map using median filtering. (b) Local similarity using the traditional orthogonalization method. (c) Local similarity using the proposed accelerated orthogonalization method.}
\label{fig:huos-simi,huos-simi-ortho,huos-simi-ortho2}
\end{figure}

%\inputdir{nine}
%\plot{pp}{width=0.5\columnwidth}{Field data example.}
%\multiplot{9}{pp-fx,pp-ortho,pp-ortho2,ppdiff-fx0,ppdiff-ortho0,ppdiff-ortho20,pp-simi,pp-simi-ortho,pp-simi-ortho2}{width=0.2900\columnwidth}{Denoising comparison. (a) Denoised data using $f$-$x$ deconvolution. (b) Denoised data using the traditional local orthogonalization. (c) Denoised data using the accelerated local orthogonalization. (d)-(f) Removed noise corresponding to (a)-(c), respectively. (g)-(i) Local similarity comparison corresponding to (a)-(c), respectively.  }
%

\begin{figure}[htb!]
\centering
\includegraphics[width=0.38\textwidth]{nine/Fig/pp}
\caption{Field data example.}
\label{fig:pp}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-fx}
   \label{fig:pp-fx}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-ortho}
   \label{fig:pp-ortho}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-ortho2}
   \label{fig:pp-ortho2}}\\
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/ppdiff-fx0}
   \label{fig:ppdiff-fx0}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/ppdiff-ortho0}
   \label{fig:ppdiff-ortho0}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/ppdiff-ortho20}
   \label{fig:ppdiff-ortho20}}\\  
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-simi}
   \label{fig:pp-simi}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-simi-ortho}
   \label{fig:pp-simi-ortho}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-simi-ortho2}
   \label{fig:pp-simi-ortho2}}
\caption{Denoising comparison. (a) Denoised data using $f$-$x$ deconvolution. (b) Denoised data using the traditional local orthogonalization. (c) Denoised data using the accelerated local orthogonalization. (d)-(f) Removed noise corresponding to (a)-(c), respectively. (g)-(i) Local similarity comparison corresponding to (a)-(c), respectively.}
\label{fig:pp-fx,pp-ortho,pp-ortho2,ppdiff-fx0,ppdiff-ortho0,ppdiff-ortho20,pp-simi,pp-simi-ortho,pp-simi-ortho2}
\end{figure}

%\inputdir{rna}
%\multiplot{1}{data0,zoom-data-a,zoom-data-b}{width=0.45\columnwidth}{Field data example. (a) Field data of the original scale. (b) Zoomed data corresponding to A. (c) Zoomed data corresponding to B. }
%

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.8\columnwidth]{rna/Fig/data0}
   \label{fig:data0}}\\
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-data-a}
   \label{fig:zoom-data-a}}
\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-data-b}
   \label{fig:zoom-data-b}} 
\caption{Field data example. (a) Field data of the original scale. (b) Zoomed data corresponding to A. (c) Zoomed data corresponding to B.}
\label{fig:data0,zoom-data-a,zoom-data-b}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/npre0}
   \label{fig:npre0}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-ortho0}
   \label{fig:rna-ortho0}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-ortho20}
   \label{fig:rna-ortho20}}\\
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/nprediff0}
   \label{fig:nprediff0}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rnadiff-ortho0}
   \label{fig:rnadiff-ortho0}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rnadiff-ortho20}
   \label{fig:rnadiff-ortho20}}\\  
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-simi}
   \label{fig:rna-simi}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-simi-ortho}
   \label{fig:rna-simi-ortho}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-simi-ortho2}
   \label{fig:rna-simi-ortho2}}
\caption{Denoising comparison. (a) Denoised data using $f$-$x$ regularized non-stationary autoregression. (b) Denoised data using the traditional local orthogonalization. (c) Denoised data using the accelerated local orthogonalization. (d)-(f) Removed noise corresponding to (a)-(c), respectively. (g)-(i) Local similarity comparison corresponding to (a)-(c), respectively.}
\label{fig:npre0,rna-ortho0,rna-ortho20,nprediff0,rnadiff-ortho0,rnadiff-ortho20,rna-simi,rna-simi-ortho,rna-simi-ortho2}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-npre-a}
   \label{fig:zoom-npre-a}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-npre-b}
   \label{fig:zoom-npre-b}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho-a}
   \label{fig:zoom-rna-ortho-a}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho2-b}
   \label{fig:zoom-rna-ortho-b}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho2-a}
   \label{fig:zoom-rna-ortho2-a}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho2-b}
   \label{fig:zoom-rna-ortho2-b}}\\  
\caption{Zoomed comparison of denoised sections. Left column: zoomed frame box A. Right column: zoomed frame box B.}
\label{fig:zoom-npre-a,zoom-npre-b,zoom-rna-ortho-a,zoom-rna-ortho-b,zoom-rna-ortho2-a,zoom-rna-ortho2-b}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rnadif-a}
   \label{fig:zoom-rnadif-a}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rnadif-b}
   \label{fig:zoom-rnadif-b}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-orthodif-a}
   \label{fig:zoom-orthodif-a}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-orthodif-b}
   \label{fig:zoom-orthodif-b}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-ortho2dif-a}
   \label{fig:zoom-ortho2dif-a}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-ortho2dif-b}
   \label{fig:zoom-ortho2dif-b}}\\  
\caption{Zoomed comparison of noise sections. Left column: zoomed frame box A. Right column: zoomed frame box B.}
\label{fig:zoom-rnadif-a,zoom-rnadif-b,zoom-orthodif-a,zoom-orthodif-b,zoom-ortho2dif-a,zoom-ortho2dif-b}
\end{figure}

\subsection{Accelerated signal-and-noise orthogonalization}
Considering the connection between the local orthogonalization weight of the current sample and the previous sample, we have the following constraints for the local orthogonalization weight at the location $(x_1,x_2,x_3)$ ($x_i=1,2,\cdots,N_i$, $i=1,2,3$, denotes index):
\begin{equation}
\label{eq:con}
\begin{split}
s(x_1,x_2,x_3) w(x_1,x_2,x_3) &= n(x_1,x_2,x_3), \\
 w(x_1,x_2,x_3) &\approx w(x_1-1,x_2,x_3), \\
 w(x_1,x_2,x_3) &\approx w(x_1,x_2-1,x_3), \\
 w(x_1,x_2,x_3) &\approx w(x_1,x_2,x_3-1). 
\end{split}
\end{equation}
We propose to formulate the equation \ref{eq:con} as a constrained least-squares problem as:
\begin{equation}
\label{eq:con1}
\begin{split}
\arg \min_w &\parallel s(x_1,x_2,x_3) w(x_1,x_2,x_3)-n(x_1,x_2,x_3) \parallel_2^2 \\
&+\alpha^2 \parallel w(x_1,x_2,x_3)- w(x_1-1,x_2,x_3) \parallel_2^2  \\
&+ \beta^2 \parallel w(x_1,x_2,x_3)- w(x_1,x_2-1,x_3) \parallel_2^2  \\
&+ \gamma^2 \parallel w(x_1,x_2,x_3)- w(x_1,x_2,x_3-1) \parallel_2^2,
\end{split}
\end{equation}
where $\alpha$, $ \beta$, and $\gamma$ are three trade-off parameters in the $x_1$, $x_2$, and $x_3$ axes, respectively.

The least-squares solution for equation \ref{eq:con1} can be derived as:
\begin{equation}
\label{eq:con2}
\overline{w}(x_1,x_2,x_3)=\frac{N}{D},
\end{equation}
where 
\begin{equation}
\label{eq:N}
\begin{split}
N&=s(x_1,x_2,x_3)n(x_1,x_2,x_3)+\alpha^2w(x_1-1,x_2,x_3) +\\
 &\beta^2w(x_1,x_2-1,x_3) + \gamma^2w(x_1,x_2,x_3-1),
\end{split}
\end{equation}
\begin{equation}
\label{eq:D}
D=s(x_1,x_2,x_3)s(x_1,x_2,x_3) + \alpha^2+\beta^2+\gamma^2.
\end{equation}

From equation \ref{eq:con2}, we can calculate the local orthogonalization weight without the need of inverting equation \ref{eq:low2}. Instead, the local orthogonalization weight is calculated in an online way, i.e., we can calculate the local orthogonalization weight sample by sample in a serial way and can obtain the new weights when the new samples come in.

The directly calculated orthogonalization weight based on equation \ref{eq:con2} might not be smooth, resulting a highly oscillating retrieval of leaked signals from the noise section, and could make the orthogonalization not stable. We propose to apply a secondary triangle smoothing to the analytically calculated orthogonalization weight:
\begin{equation}
\label{eq:con4}
\tilde{w}(x_1,x_2,x_3) = T(\overline{w}(x_1,x_2,x_3)).
\end{equation}
\new{In the case of spiky noise, it is also preferable to apply a median filter \cite{shuwei2016somf,sosvmf} to smooth the orthogonalization weight to alleviate the influence of the abnormal amplitude. }
Considering that the smoothing could affect the amplitude of the orthogonalization weight, the smoothed orthogonalization weight is then scaled to match the noise energy. The scale coefficient $\mu$ can be calculated as:
\begin{equation}
\label{eq:mu}
\mu = \frac{\max{|\tilde{n}(x_1,x_2,x_3)|}}{\max{|\tilde{w}(x_1,x_2,x_3)|}\max{|s(x_1,x_2,x_3)|}}.
\end{equation}
$\max{|\cdot|}$ denotes geting the absolute maximum of the input array. The definition of $\mu$ in equation \ref{eq:mu} is to ensure that the maximum level of retrieved signal is the complete noise component, indicating that no noise is removed for a specific sample after the orthogonalization operation. Without multiplying the scale $\mu$, the retrieved signal is either too weak (several orders of magnitude weaker than the noise), or too large (e.g., multiple times of the noise component), compared with the noise energy. The final orthogonalization weight in its analytical form without iterations can be expressed as:
\begin{equation}
\label{eq:alow}
\hat{w}(x_1,x_2,x_3) = \mu T(\overline{w}(x_1,x_2,x_3)).
\end{equation}
\new{Another strategy to alleviate the influence of abnormal amplitude is to calculate the coefficient $\mu$ in a window-based way. }Since equation \ref{eq:alow} is free of iterations, the complexity of the new orthogonalization method is $O(N_d)$, which is much accelerated compared with the traditional local orthogonalization method.

Inserting the expression of $\hat{w}$ into the orthogonalization equation, we can obtain the online signal-and-noise orthogonalization method as
\begin{equation}
\label{eq:con3}
\hat{s}(x_1,x_2,x_3) = s(x_1,x_2,x_3)+\hat{w}(x_1,x_2,x_3)s(x_1,x_2,x_3).
\end{equation}

\section{Examples}
We first use two synthetic examples to demonstrate the comparable denoising performance between the traditional and the accelerated signal-and-noise orthogonalization methods. At the same time, we demonstrate the much better denoising performance of the signal-and-noise orthogonalization methods compared with the traditional denoising methods. For evaluating the denoising performance, we use the signal-to-noise ratio (SNR) \cite{guochang2009,guochang2013,amir2017geo,amir2017,guochang2018weighted} defined as
\begin{equation}
\label{eq:diff}
SNR=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2^2}{\Arrowvert \hat{\mathbf{s}} -\mathbf{s}\Arrowvert_2^2},
\end{equation}
where $\mathbf{s}$ and $\hat{\mathbf{s}}$ denotes the true signal and the target signal for evaluating the quality. Besides, we quantitatively measure the signal leakage by using the local similarity metric \cite{yangkang2015ortho,fomel2007localattr}. \new{The local similarity $\mathbf{l}$ between $\mathbf{a}$ and $\mathbf{b}$ is defined as:
\begin{equation}
\label{eq:local}
\mathbf{l}=\sqrt{\mathbf{l}_1\circ\mathbf{l}_2}
\end{equation}
where $\circ$ denotes an element-wise product, $\mathbf{l}_1$ and $\mathbf{l}_2$ are solutions to the following minimization problems:
\begin{align}
\label{eq:local1}
\mathbf{l}_1 &=\arg\min_{\mathbf{l}_1}\Arrowvert \mathbf{a}-\mathbf{B}\mathbf{l}_1 \Arrowvert_2^2, \\
\label{eq:local2}
\mathbf{l}_2 &=\arg\min_{\mathbf{l}_2}\Arrowvert \mathbf{b}-\mathbf{A}\mathbf{l}_2 \Arrowvert_2^2,
\end{align}
where $\mathbf{A}$ is a diagonal operator constructed from $\mathbf{a}$ and $\mathbf{B}$ is a diagonal operator constructed from $\mathbf{b}$.
Optimization problems \ref{eq:local1} and \ref{eq:local2} can be solved using the shaping regularization method \cite{fomel2007localattr}.} The local similarity can be used to detect the locally similar components between initially denoised data and the removed noise. If there is signal leakage, the local similarity map will exhibit obviously high anomalies. \old{It is measured by solving two least-squares inverse problem, as detailed in ? and ?}.

The first synthetic example is shown in Fig. \ref{fig:c,n,cn,cfx,cfx2,cfx22,cdifffx,cdifffx2,cdifffx22}. This synthetic example is directly borrowed from \cite{yangkang2015ortho} for a benchmark comparison. Fig. \ref{fig:c} shows the clean data containing four linear events. Fig. \ref{fig:n} shows a noise section. Fig. \ref{fig:cn} plots the noisy data by summing Figs. \ref{fig:c} and \ref{fig:n}. The SNR of the noisy data is -0.75 dB. Figs. \ref{fig:cfx} shows the denoised data using a standard $f-x$ predictive filtering method \cite{canales1984}. Later, we will use FX method for briefly indicating the $f-x$ predictive filtering method. Fig. \ref{fig:cfx2} plots the denoised data using the traditional local signal-and-noise orthogonalization \cite{yangkang2015ortho}. Fig. \ref{fig:cfx22} plots the denoised data using the proposed accelerated signal-and-noise orthogonalization. By comparing the denoised data between the FX method and the local orthogonalization method, we find that the amplitude of the seismic events becomes obviously stronger after the orthogonalization operation, especially for the third horizontal event. The results of both orthogonalization methods are almost the same, but the proposed method is almost 100 times faster than the traditional local orthogonalization method. The signal leakage of the FX method can be observed from the noise section, as shown in Fig. \ref{fig:cdifffx}, where we can see clear spatially coherent energy around time 0.7s. The noise sections from the two orthogonalization methods show no obvious spatially coherent energy, as plotted in Figs. \ref{fig:cdifffx2} and \ref{fig:cdifffx22}. The SNR of the denoised data of FX method is 9.21 dB. The SNRs of the traditional and the accelerated orthogonalization methods are 10.99 dB and 10.40 dB, respectively. We can obtain two conclusions from the SNR comparison. First, the orthogonalization method can help significantly increase the SNR value. Secondly, although slightly worse, the proposed method can obtain comparable SNR value compared with the traditional orthogonalization method, but enjoy a much faster computational efficiency. The local similarity (between denoised data and removed noise) maps shown in Fig. \ref{fig:csimi-difffx,csimi-difffx2,csimi-difffx22} are used to evaluate the signal preservation performance of different methods. Fig. \ref{fig:csimi-difffx} shows obvious large similarity anomalies in the signal positions, which indicates a strong signal leakage problem for the FX method. The two orthogonalization methods significantly decrease the leaked signals, since the local similarity maps are almost zero throughout the profiles. Note that the proposed method causes a slightly worse signal leakage problem than the traditional method, as captured by the slightly larger local similarity values in Fig. \ref{fig:csimi-difffx22} than in Fig. \ref{fig:csimi-difffx2}.

The second synthetic example is presented in Fig. \ref{fig:huo,huo-noise,huos,huos-mf,huos-ortho,huos-ortho2,huosdiff-mf,huosdiff-ortho,huosdiff-ortho2}. This example is a deblending test. The noise in this dataset is spike-like blending noise, rather than the typical random noise. The deblending test was previously studied by \cite{yangkang2015ortho}. Fig. \ref{fig:huo} shows the clean data. Fig. \ref{fig:huo-noise} plots the blending noise simulated from a simultaneous-source acquisition survey \cite{yangkang20142}. The noisy data composed of the clean data and blending noise is shown in Fig. \ref{fig:huos}. The SNR of the noisy data is 0.78 dB. Figs. \ref{fig:huos-mf}, \ref{fig:huos-ortho}, and \ref{fig:huos-ortho2} plot the denoised data using the median filtering method \cite{justusson1981median}, the traditional orthogonalization method \cite{yangkang2015ortho}, and the proposed method, respectively. Here, since the median filtering method is most powerful in attenuating spike-like noise, we use it for comparison and as the initial denoising operator (i.e., $\mathbf{P}$ in equation \ref{eq:sn}).  Comparing the denoised data in Fig. \ref{fig:huo,huo-noise,huos,huos-mf,huos-ortho,huos-ortho2,huosdiff-mf,huosdiff-ortho,huosdiff-ortho2}, we can see that the median filtering greatly affects the amplitude of the dipping signals, and the traditional local orthogonalization greatly reduces the damages to dipping signals. However, the traditional local orthogonalization causes a spurious signal in the result, e.g., around 1.25-1.5s in the 120th trace. The proposed method reduces the signal damages but does not introduce spurious waveforms. The removed blending noise is plotted in the third row of Fig. \ref{fig:huo,huo-noise,huos,huos-mf,huos-ortho,huos-ortho2,huosdiff-mf,huosdiff-ortho,huosdiff-ortho2}. It is clear that a lot of dipping signals are leaked in Fig. \ref{fig:huosdiff-mf} and there are no observable signal waveforms in Figs. \ref{fig:huosdiff-ortho} and \ref{fig:huosdiff-ortho2}. The removed blending noise sections further confirm the effectiveness of the proposed method. The measured SNRs for the median filtering method, the traditional local orthogonalization method, and the proposed method are 10.91 dB, 11.35 dB, and 12.14 dB, respectively. In this example, the proposed method even obtains higher SNR than the traditional local orthogonalization method and obtains a speedup of almost 100 times. The local similarity between the denoised data and removed noise is calculated and displayed in Fig. \ref{fig:huos-simi,huos-simi-ortho,huos-simi-ortho2}, where the leaked signals of the median filter are clearly captured as high similarity anomalies. The two orthogonalization methods, however, cause negligible local similarity values.

The first field data example is shown in Figs. \ref{fig:pp} and \ref{fig:pp-fx,pp-ortho,pp-ortho2,ppdiff-fx0,ppdiff-ortho0,ppdiff-ortho20,pp-simi,pp-simi-ortho,pp-simi-ortho2}. This field data example has been studied by \cite{yangkang2015ortho} for demonstrating the performance of the traditional signal-and-noise orthogonalization method. Here, this example is used again for benchmarking the performance of the new accelerated orthogonalization method. The denoised data using three different methods, namely, the $f-x$ deconvolution $\new{(prediction)}$ method, the traditional orthogonalization, the proposed method, are shown in the top row of Fig. \ref{fig:pp-fx,pp-ortho,pp-ortho2,ppdiff-fx0,ppdiff-ortho0,ppdiff-ortho20,pp-simi,pp-simi-ortho,pp-simi-ortho2}. It seems that all three methods obtain satisfactory results for this field data. It is more useful to compare the noise sections as plotted in the second row of Fig. \ref{fig:pp-fx,pp-ortho,pp-ortho2,ppdiff-fx0,ppdiff-ortho0,ppdiff-ortho20,pp-simi,pp-simi-ortho,pp-simi-ortho2}. It is clear that the $f-x$ deconvolution method damages significant signals and leaves much coherent energy in the noise section, as highlighted by the green and pink frame boxes. The traditional orthogonalization method causes negligible signal leakage while the proposed method causes a slightly more signal leakage than the traditional method in the area highlighted by the pink frame box. The local similarity between the denoised data and removed noise is calculated and shown in the bottom row of Fig. \ref{fig:pp-fx,pp-ortho,pp-ortho2,ppdiff-fx0,ppdiff-ortho0,ppdiff-ortho20,pp-simi,pp-simi-ortho,pp-simi-ortho2} for the three methods. The local similarity maps further confirm that the $f-x$ deconvolution method causes the most serious signal leakage (as depicted by the high similarity values), which is followed by the proposed method, and then by the traditional local orthogonalization method.

The second field data is a complicated post-stack seismic profile, as plotted in Fig. \ref{fig:data0,zoom-data-a,zoom-data-b}. This data has been studied previously by \cite{guochang2012} and \cite{yangkang2015ortho}. The raw seismic data is plotted in Fig. \ref{fig:data0}, which contains very strong random noise. We zoomed in two areas from the raw data, highlighted by the two frame boxes A and B, in Figs. \ref{fig:zoom-data-a} and \ref{fig:zoom-data-b}. Fig. \ref{fig:npre0,rna-ortho0,rna-ortho20,nprediff0,rnadiff-ortho0,rnadiff-ortho20,rna-simi,rna-simi-ortho,rna-simi-ortho2} shows the denoising comparison for this example using different methods. The first row in Fig. \ref{fig:npre0,rna-ortho0,rna-ortho20,nprediff0,rnadiff-ortho0,rnadiff-ortho20,rna-simi,rna-simi-ortho,rna-simi-ortho2} compares the denoised data using three different methods. Apart from the traditional local orthogonalization method and the proposed accelerated orthogonalization method, we use the non-stationary predictive filtering method in the $f-x$ domain \cite{guochang2012} as a benchmark comparison. The non-stationary predictive filtering is the non-stationary extension of the standard FX method and thus can better deal with very complicated seismic datasets. From the comparison of denoised datasets, we can hardly find any difference, since all three methods seem to obtain very successful performance, i.e., removing most random noise while making the seismic reflection events cleaner and more coherent. We can see the difference between different methods from the removed noise sections, as displayed in the second row of Fig. \ref{fig:npre0,rna-ortho0,rna-ortho20,nprediff0,rnadiff-ortho0,rnadiff-ortho20,rna-simi,rna-simi-ortho,rna-simi-ortho2}. The removed noise using the non-stationary predictive filtering obviously causes some signal leakage, as highlighted by the two frame boxes A and B in Fig. \ref{fig:nprediff0}. The signal leakage is very clear and spatially coherent, and thus we are very sure it corresponds to signal energy. The removed noise corresponding to the two orthogonalization methods, however, does not show obvious signal leakage, demonstrating the effectiveness of both orthogonalization methods. In this example, the advantage of computational acceleration of the proposed method becomes more evident, since this dataset is much larger than the previous examples. Again, for this example, the proposed obtains a speedup of almost 100 times, assuming that 100 iterations are used in the traditional inversion-based local orthogonalization algorithm. The local similarity comparison as shown in the third row of Fig. \ref{fig:npre0,rna-ortho0,rna-ortho20,nprediff0,rnadiff-ortho0,rnadiff-ortho20,rna-simi,rna-simi-ortho,rna-simi-ortho2} further demonstrates both orthogonalization methods cause obviously less signal leakage compared with the non-stationary predictive filtering method. For a more detailed comparison of both denoised data and noise sections, we plot the zoomed sections (frame boxes A and B) in Figs. \ref{fig:zoom-npre-a,zoom-npre-b,zoom-rna-ortho-a,zoom-rna-ortho-b,zoom-rna-ortho2-a,zoom-rna-ortho2-b} and \ref{fig:zoom-rnadif-a,zoom-rnadif-b,zoom-orthodif-a,zoom-orthodif-b,zoom-ortho2dif-a,zoom-ortho2dif-b}. From the zoomed denoised data, compared with the zoomed raw data in Figs. \ref{fig:zoom-data-a} and \ref{fig:zoom-data-b}, we confirm the better signal preservation ability and the comparable performance of the two orthogonalization methods. The comparison of zoomed noise sections confirms that the signal leakage is much decreased using the orthogonalization methods, and the removed noise seems to be white after the orthogonalization operation.

\section{Discussions}
\new{In this section, we discuss the connection between the global/local orthogonalization and the $f-x$ projection filter \cite{sacchi2000fxproj}. The global orthogonalization operator is computed from a denoising operator ($\mathbf{P}$) by converting the denoised signal into a projection operator. Then the projection operator is applied onto the noise estimate to recover the leaked signal and adds it back to the signal estimate. This is equivalent to applying the projection operator (computed from the denoising operator) directly on to the noisy seismic data. To understand this, one can rearrange the equations \ref{eq:sn}, \ref{eq:snn}, \ref{eq:sn2}-\ref{eq:sn3}, and get:
\begin{equation}
%\hat{s} = s + (s*s’)/(s’*s) n = s + (s*s’)/(s’*s) (d-s) = (s*s’)/(s’*s) d
\begin{split}
\tilde{\mathbf{s}}&= \mathbf{s} + \mathbf{s}\frac{\mathbf{s}^T\mathbf{n}}{\mathbf{s}^T\mathbf{s}}=\mathbf{s} + \frac{\mathbf{s}\mathbf{s}^T}{\mathbf{s}^T\mathbf{s}}\mathbf{n} =\mathbf{s} + \frac{\mathbf{s}\mathbf{s}^T}{\mathbf{s}^T\mathbf{s}}(\mathbf{d}-\mathbf{s})\\
&=\frac{\mathbf{s}\mathbf{s}^T}{\mathbf{s}^T\mathbf{s}}\mathbf{d}
\end{split}
\end{equation}
where $\frac{\mathbf{s}\mathbf{s}^T}{\mathbf{s}^T\mathbf{s}}$ is the operator that projects data to the estimate signal subspace. The signal subspace estimate is computed from a leaky operator such as $f-x$ prediction filter, median filter, etc. Such interpretation shows why the global orthogonalization method preserves the signal better than an initial denoising algorithm, because the operator used by the initial denoising algorithm is not a projection operator. Hence, using an orthogonalized operator helps recovering the attenuated signal components. The local orthogonalization corresponds to a local projection operator from this viewpoint. However, the limitation of the orthogonalization method is that, if the original denoising operator completely misses some weak signal components (rather than recovering with a wrong amplitude), then the estimated signal subspace will be orthogonal to the missed signal. Consequently, the orthogonalization method would not be able to recover the lost signal components. It is meaningful to compare the $f-x$ prediction method, $f-x$ projection method and the hybrid $f-x$ prediction and orthogonalization method. Such a comparison is shown in Fig. \ref{fig:comp}. Figs. \ref{fig:c} and \ref{fig:cn} show the clean and noisy data of a crossing linear-event dataset, which meets the assumption of the $f-x$ prediction method. Figs. \ref{fig:c-fx} and \ref{fig:c-fx-n0} show the denoised data and noise section using the $f-x$ prediction method.  Figs. \ref{fig:c-fxp} and \ref{fig:c-fxp-n0} show the denoised data and noise section using the $f-x$ projection method. Figs. \ref{fig:c-fxortho} and \ref{fig:c-fxortho-n0} show the denoised data and noise section using the hybrid $f-x$ prediction and orthogonalization method. As indicated by the arrows (plotted on the noise sections), the signal preservation ability improves from the second row to the fourth row. It is also obvious that the $f-x$ projection method tends to better protect the low-dip-angle energy than the high-dip-angle energy.}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c}
   \label{fig:c}}
\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/cn}
   \label{fig:cn}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fx}
   \label{fig:c-fx}}
\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fx-n0}
   \label{fig:c-fx-n0}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fxp}
   \label{fig:c-fxp}}
\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fxp-n0}
   \label{fig:c-fxp-n0}}\\   
\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fxortho}
   \label{fig:c-fxortho}}
\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fxortho-n0}
   \label{fig:c-fxortho-n0}}\\    
\caption{\new{Comparison between the $f-x$ prediction method, $f-x$ projection method, and the hybrid $f-x$ prediction and orthogonalization method. First row: Clean and noisy data. Second row: denoised data and noise section using the $f-x$ prediction method.  Third row: denoised data and noise section using the $f-x$ projection method. Fourth row: denoised data and noise section using the hybrid method.}}
\label{fig:comp}
\end{figure}

\section{Conclusions}
The traditional local signal-and-noise orthogonalization method requires a large number of iterations to invert the orthogonalization weight and thus is not feasible for large-scale industrial applications. Since the orthogonalization weight of a sample is related to its neighbor samples, we can develop an orthogonalization method by connecting the current sample with previous samples with calculated orthogonalization weights. We solve the new optimization model via an analytical form of the least-squares method, and thus the new signal-and-noise orthogonalization method is free of iteration. The directly calculated weights, however, is not smooth enough and the secondary smoothing step needs to be applied. Since the orthogonalization weight is used to retrieve leaked signals from noise, to match the noise level, we need to apply a normalization step to the directly calculated orthogonalization weight. An exclusive analysis of different synthetic and real data examples is conducted to benchmark the proposed method with state-of-the-art approaches. It is concluded from the results that the proposed method can significantly accelerate the signal-and-noise orthogonalization without losing the effectiveness.

\bibliographystyle{IEEEtran}
\bibliography{ortho}

### 2022-01-05 orthoa/paper.tex
Wed Jan  5 17:26:27 CST 2022

@@
 \centering
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/c}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/c}
    \label{fig:c}}
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/n}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/n}
    \label{fig:n}}
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cn}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cn}
    \label{fig:cn}}\\
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cfx}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cfx}
    \label{fig:cfx}}
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cfx2}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cfx2}
    \label{fig:cfx2}}
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cfx22}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cfx22}
    \label{fig:cfx22}}\\  
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cdifffx}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cdifffx}
    \label{fig:cdifffx}}
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cdifffx2}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cdifffx2}
    \label{fig:cdifffx2}}
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cdifffx22}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cdifffx22}
    \label{fig:cdifffx22}}
@@
 \centering
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/csimi-difffx}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/csimi-difffx}
    \label{fig:csimi-difffx}}
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/csimi-difffx2}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/csimi-difffx2}
    \label{fig:csimi-difffx2}}
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/csimi-difffx22}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/csimi-difffx22}
    \label{fig:csimi-difffx22}}
@@
 \centering
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huo}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huo}
    \label{fig:huo}}
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huo-noise}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huo-noise}
    \label{fig:huo-noise}}
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos}
    \label{fig:huos}}\\
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-mf}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-mf}
    \label{fig:huos-mf}}
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-ortho}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-ortho}
    \label{fig:huos-ortho}}
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-ortho2}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-ortho2}
    \label{fig:huos-ortho2}}\\  
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huosdiff-mf}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huosdiff-mf}
    \label{fig:huosdiff-mf}}
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huosdiff-ortho}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huosdiff-ortho}
    \label{fig:huosdiff-ortho}}
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huosdiff-ortho2}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huosdiff-ortho2}
    \label{fig:huosdiff-ortho2}}
@@
 \centering
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-simi}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-simi}
    \label{fig:huos-simi}} 
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-simi-ortho}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-simi-ortho}
    \label{fig:huos-simi-ortho}}
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-simi-ortho2}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-simi-ortho2}
    \label{fig:huos-simi-ortho2}}
@@
 \centering
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-fx}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-fx}
    \label{fig:pp-fx}}
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-ortho}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-ortho}
    \label{fig:pp-ortho}}
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-ortho2}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-ortho2}
    \label{fig:pp-ortho2}}\\
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/ppdiff-fx0}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/ppdiff-fx0}
    \label{fig:ppdiff-fx0}}
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/ppdiff-ortho0}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/ppdiff-ortho0}
    \label{fig:ppdiff-ortho0}}
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/ppdiff-ortho20}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/ppdiff-ortho20}
    \label{fig:ppdiff-ortho20}}\\  
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-simi}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-simi}
    \label{fig:pp-simi}}
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-simi-ortho}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-simi-ortho}
    \label{fig:pp-simi-ortho}}
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-simi-ortho2}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-simi-ortho2}
    \label{fig:pp-simi-ortho2}}
@@
 \centering
-\subfigure[]{\includegraphics[width=0.8\columnwidth]{rna/Fig/data0}
+\subfloat[]{\includegraphics[width=0.8\columnwidth]{rna/Fig/data0}
    \label{fig:data0}}\\
-   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-data-a}
+   \subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-data-a}
    \label{fig:zoom-data-a}}
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-data-b}
+\subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-data-b}
    \label{fig:zoom-data-b}} 
@@
 \centering
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/npre0}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/npre0}
    \label{fig:npre0}}
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-ortho0}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-ortho0}
    \label{fig:rna-ortho0}}
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-ortho20}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-ortho20}
    \label{fig:rna-ortho20}}\\
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/nprediff0}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/nprediff0}
    \label{fig:nprediff0}}
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rnadiff-ortho0}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rnadiff-ortho0}
    \label{fig:rnadiff-ortho0}}
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rnadiff-ortho20}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rnadiff-ortho20}
    \label{fig:rnadiff-ortho20}}\\  
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-simi}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-simi}
    \label{fig:rna-simi}}
-\subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-simi-ortho}
+\subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-simi-ortho}
    \label{fig:rna-simi-ortho}}
-   \subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-simi-ortho2}
+   \subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-simi-ortho2}
    \label{fig:rna-simi-ortho2}}
@@
 \centering
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-npre-a}
+\subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-npre-a}
    \label{fig:zoom-npre-a}}
-   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-npre-b}
+   \subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-npre-b}
    \label{fig:zoom-npre-b}}\\
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho-a}
+\subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho-a}
    \label{fig:zoom-rna-ortho-a}}
-   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho2-b}
+   \subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho2-b}
    \label{fig:zoom-rna-ortho-b}}\\
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho2-a}
+\subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho2-a}
    \label{fig:zoom-rna-ortho2-a}}
-   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho2-b}
+   \subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho2-b}
    \label{fig:zoom-rna-ortho2-b}}\\  
@@
 \centering
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rnadif-a}
+\subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rnadif-a}
    \label{fig:zoom-rnadif-a}}
-   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rnadif-b}
+   \subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rnadif-b}
    \label{fig:zoom-rnadif-b}}\\
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-orthodif-a}
+\subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-orthodif-a}
    \label{fig:zoom-orthodif-a}}
-   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-orthodif-b}
+   \subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-orthodif-b}
    \label{fig:zoom-orthodif-b}}\\
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-ortho2dif-a}
+\subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-ortho2dif-a}
    \label{fig:zoom-ortho2dif-a}}
-   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-ortho2dif-b}
+   \subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-ortho2dif-b}
    \label{fig:zoom-ortho2dif-b}}\\  
@@
 \centering
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c}
+\subfloat[]{\includegraphics[width=0.22\columnwidth]{linear/Fig/c}
    \label{fig:c}}
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/cn}
+\subfloat[]{\includegraphics[width=0.22\columnwidth]{linear/Fig/cn}
    \label{fig:cn}}\\
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fx}
+\subfloat[]{\includegraphics[width=0.22\columnwidth]{linear/Fig/c-fx}
    \label{fig:c-fx}}
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fx-n0}
+\subfloat[]{\includegraphics[width=0.22\columnwidth]{linear/Fig/c-fx-n0}
    \label{fig:c-fx-n0}}\\
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fxp}
+\subfloat[]{\includegraphics[width=0.22\columnwidth]{linear/Fig/c-fxp}
    \label{fig:c-fxp}}
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fxp-n0}
+\subfloat[]{\includegraphics[width=0.22\columnwidth]{linear/Fig/c-fxp-n0}
    \label{fig:c-fxp-n0}}\\   
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fxortho}
+\subfloat[]{\includegraphics[width=0.22\columnwidth]{linear/Fig/c-fxortho}
    \label{fig:c-fxortho}}
-\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fxortho-n0}
+\subfloat[]{\includegraphics[width=0.22\columnwidth]{linear/Fig/c-fxortho-n0}
    \label{fig:c-fxortho-n0}}\\    
@@
 
-\bibliographystyle{IEEEtran}
+\bibliographystyle{seg}
 \bibliography{ortho}

### 2022-01-07 dipl/paper.tex
Thu Jan  6 23:31:21 CST 2022

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}
\DeclareRobustCommand{\old}[1]{}
\DeclareRobustCommand{\new}[1]{#1}

\title{Large dip calculation via robust non-stationary plane-wave destruction}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Wei Chen, Liuqing Yang, Xingye Liu, Hang Wang, and Yangkang Chen}
%\thanks{W. Chen is with the Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education, Yangtze University, Wuhan 430100, China, and also with the Cooperative Innovation Center of Unconventional Oil and Gas (Ministry of Education, Hubei Province), Yangtze University, Wuhan 430100, China (e-mail: chenwei2014@yangtzeu.edu.cn).}
%\thanks{L. Yang is with the College of Geophysics, China University of Petroleum, Beijing 102249, China.}
%\thanks{X. Liu is with the College of Geology and Environment, Shaanxi Provincial Key Laboratory of Geological Support for Coal Green Exploitation, Xi’an University of Science and Technology, Xi’an 710054, China.}
%\thanks{H. Wang and Y. Chen are with the Key Laboratory of Geoscience Big Data and Deep Resource of Zhejiang Province, School of Earth Sciences, Zhejiang University, Hangzhou 310027, China.}
%\thanks{This work was supported in part by the National Natural Science Foundation of China (NSFC) under Grant 41804140, and in part by the Open Fund of Cooperative Innovation Center of Unconventional Oil and Gas (Ministry of Education and Hubei Province), Yangtze University, under Grant UOG2020-01. (Corresponding author: Wei Chen.)}}
\maketitle

%\address{
%\footnotemark[1] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
%Yangtze University\\
%Daxue Road No.111\\
%Caidian District\\
%Wuhan, China, 430100 \\
%\footnotemark[2] Hubei Cooperative Innovation Center of Unconventional Oil and Gas\\
%Daxue Road No.111\\
%Caidian District\\
%Wuhan, China, 430100 \\
%\footnotemark[3]State Key Laboratory of Petroleum Resources and Prospecting \\
%China University of Petroleum \\
%Fuxue Road 18th\\
%Beijing, China, 102200 \\
%%hellowangyf@163.com \& chenxh@cup.edu.cn \\
%\footnotemark[4]College of Geology and Environment\\
%Xi’an University of Science and Technology\\
%Xi’an, Shaanxi Province, China, 710054 \\
%lwxwyh506673@126.com\\
%\footnotemark[5]
%School of Earth Sciences\\
%Zhejiang University\\
%Hangzhou, Zhejiang Province, China, 310027\\
%yangkang.chen@zju.edu.cn \\
%%Corresponding Author: Yangkang Chen (chenyk2016@gmail.com) 
%}
%

\begin{abstract}
The omnidirectional plane-wave destruction (OPWD) algorithm can estimate the large dip by using a circle-interpolating PWD filter but at the expense of causing potential instabilities due to the small values of the denominator in the regularized division problem. To mitigate the instability, one needs to use a relatively larger smoothing radius for a stronger regularization of the element-wise division, which however significantly decreases the resolution of dip estimation.  We propose a new OPWD method without compromising the dip resolution for the large dip calculation by applying a non-stationary smoothness constraint to the model. We use a larger smoothing radius for areas that tend to cause instabilities and vice versa. The non-stationary smoothing is carried out in a simple and efficient recursion way. The synthetic and real seismic data examples demonstrate the performance of the proposed algorithm.
\end{abstract}

%\begin{keywords}
%Large dip, non-stationary regularization, plane-wave destruction, filtering, noise
%\end{keywords}

\section{Introduction}
Seismic slope/dip is a widely used attribute in seismic processing and interpretation. 
The estimation of local slope is committed to detect the directionality of coherent events from the raw data. Compared with the global estimation methods, local slope estimation methods can be implemented quickly and rely slightly on a priori information \cite{Schleicher2008}.
The local slope has been successfully applied in a broad spectrum of geophysical tasks, ranging from velocity-independent imaging \cite{Kevin2004, Sergey2007, Matthew2020} to 
structural filtering \cite{liuyang2010, 2020Deblending, qushan2019geo, wanghang2020tgrs2}, passive seismic location \cite{Mohammad2015, Khoshnavaz2017}, initial model building \cite{guangtan2020tgrs1}, wavefield separation \cite{pwd}, and inversion-based seismic processing \cite{Sergey2007, Zhiguang2016}. 
During the past decades, many techniques and methods have been \old{invented}\new{proposed} to extract the local slope attribute.

The local slant stack algorithm is a traditional way of local slope extraction \cite{Ottolini1983}.  At first, the local coherence scanning is carried out at each point of the seismic data along all possible directions. Then, the slope value is determined by the direction with the highest coherence.  However, the calculation cost to find such an optimal direction by local slant stacking is extremely expensive. Besides, it is sensitive to the aperture of the local slant stack \cite{Schleicher2008, Santos2009}. Schleicher et al. (2008) \cite{Schleicher2008} developed an alternative, faster, and more reliable method to estimate local slopes by using \old{modern}\new{advanced} extraction techniques. \new{Besides, the local slope can also be calculated based on the prediction-error filter \cite{1991Earth, 1999Two}.}
\old{Another conventional method of local slope extraction is based on the prediction-error filter.}

The structural tensor algorithm is an excellent tool that has been widely used in geophysics applications, such as seismic structural analysis, fault interpretation, and structural-orientated filtering \new[]{\cite{wu2017directional}}.
It is an effective method to detect the flat region, edge region and corner region of an image.  
The structure tensor can also be employed to extract the directionality contained in seismic data \cite[]{1995Estimators, 1997A, Fehmers2003Fast}.   
The basic is that the orientation of seismic data can be represented by the structure vector. Computing the structure tensor contains two steps:  \old{at first}\new{first}, the orientation information is estimated at each point via orientation filtering. Then, \old{we map and average}\new{one maps and averages} the filtering result to the tensor representation \cite{1986Analyzing, 1991Computing, webmaster1992Adaptive}. The process is symmetric and semi-positive definite. In general, the dominant orientation corresponds to the maximum of the weighted average. Averaging the tensor suppresses the rapid changes of orientation in a seismic image caused by noise, and generates a smooth orientation result.
Nevertheless, the traditional structure tensor is usually second-order, thus only a single dominant slope can be computed. In addition, the maximum is not in agreement with the true orientation of an image when the  histogram of the orientation is multimodal \cite{image2002}.
\cite{2006An} proposed a multi-directional representation of gradient structure to extract high-order structures. They estimated the tensor via an asymmetric way by deriving parameters of multimodal directional distribution functions from discrete direction constraints. \cite{2007Representing} presented a specific method only for the case of two orientations  in the plane. 
\cite{2009A} extended the version of the second-order structure tensor to a higher-order one to capture the multiple orientations for more complex 3D data. 
\cite{2009Representing} developed an approach based on angular separable quadrature filters to estimate the local slope.  For multiple directionality estimation of seismic images, \cite{2013Extended} improved the structure
tensor by utilizing a one-way equation to deal with the problem of conflicting dips. 
However, these methods cost expensively in computation.
\cite{2015Compression} presented a high-efficiency method to detect multiple local slopes by the second-order structure tensor, which is suitable for the case of intersecting events.

Except for the aforementioned methods, \cite{1998Marfurt3} proposed a robust semblance-based coherency algorithm to improve the vertical resolution. 
The multiple window dip searching method is a more robust local slope estimation approach \cite{Kurt2006}. It uses a series of  multiple windows shifted in both space and time domains which contain each analysis point. As a result, the high-resolution  result of dip and azimuth is generated. \cite{2010Local} used a cross-correlation method to smoothly and locally estimate the slope attribute. The method does not require scanning operators and the cost is inexpensive. \cite{2013Consistent} introduced the single and joint dip constraints to the cross-correlation method to check the reciprocity, causality, consistency, vertical and lateral continuity during  the estimating process, improving the accuracy and fidelity of extracted local slopes. \cite{2015Seismicdip} proposed a structure-oriented polynomial fitting filter method that utilizes the relationship of the frequency response between 2D derivatives and 2D Hilbert transform. It is a non-iterative method for local dip estimation with a strong ability of anti-noise. \cite{Haibin2017} integrated the directions along the most and least apparent variations of the local waveforms to detect the local dip. \cite{2019Accurate} pointed out that the accuracy of the estimated dip attribute by the semblance scanning approach is usually impacted  by the dip of seismic reflectors. Then, they developed a method that combines the advantages of the gradient structure tensor analysis and multiple window Kuwahara scanning.

Nowadays, the plane-wave theory, firstly proposed by \cite{1991Earth}, has been utilized to estimate the local slope and shows promising performance. The finite difference is utilized to discrete the differential equation. Many plane-wave destruction filters are presented for the calculation of finite difference. Fomel (2002) \cite{pwd} used the Thiran’s filter \cite{1971Recursive} to replace the phase-shift operator, and simplified the plane-wave destruction (PWD) equation to a nonlinear form with respect to the slope. Then, he proposed an iterative algorithm to extract the local slope information. 
Subsequently, \cite{Sergey2007} proposed a shaping regularization method that could be applied to local slope estimation. The stability of extracted slope information is enhanced by the shaping regularization. \cite{dave2007} pointed out that local dip filters should be invertible, and proposed to extract a robust and invertible local dip filter based on directional derivative. \cite{2013Accelerated} confirmed that plane-wave destruction equation is actually polynomial of the slope. The iterative algorithm can be replaced by analytical solutions, which would accelerate the convergence and significantly save the calculation time. \cite{2013Omnidirectional} proved that the accuracy of estimated slope by the plane-wave destruction filter was unsatisfactory when it was applied to handle seismic data with steep structures. They introduced line-interpolating and circle-interpolating operators to avoid directional aliasing issues and boost the performance. 
However, the plane-wave destruction method is still unsatisfactory when the energy of noise is strong. In this case, a larger smoothing radius is required to eliminate the noise effect, whereas the fidelity will be negatively influenced. \new{Besides, eigenvectors of 3D structure tensor \cite{wu2017directional} can be used to derive the slope without the value range limitation and the instability issue, which is an advantage to the PWD method.}

The traditional PWD algorithm fails when the dip becomes very large because of the non-negligible error of the maxflat fractional delay filter in approximating the phase-shift operator in large dips. The omnidirectional plane-wave destruction (OPWD) algorithm can estimate the large dip due to a circle-interpolating PWD filter but at the expense of causing potential instabilities. The instability of the OPWD method is caused by the small values of the denominator in the regularized division problem. A simple way to solve the instability issue is to use a larger smoothing radius for a stronger constraint in the shaping regularization framework, which however significantly decreases the resolution of the estimated slope map. In this paper, we propose an effective way to compromise the stability and resolution of local slope estimation based on the PWD algorithm. We apply spatially non-stationary smoothing to regularize the slope inversion, e.g., applying a stronger smoothing in areas with a larger dip that tends to cause instability and aliasing, and a weaker smoothing in areas with less steep structures. The proposed robust slope estimation method is applied to a synthetic example to demonstrate the stable and high-resolution performance. It is then applied to different seismic processing and interpretation applications to test its wide applicability, including automatic event picking, 2D and 3D seismic structural filtering to enhance the signal-to-noise ratio.

\begin{figure}[htb!]
\centering
\includegraphics[width=0.6\columnwidth]{hyper/Fig/hyper}
\caption{Synthetic dataset. }
\label{fig:hyper}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.3\columnwidth]{hyper/Fig/hyper-dipl0-0}
  \label{fig:hyper-dipl0-0}}
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{hyper/Fig/hyper-dipl1-0}
  \label{fig:hyper-dipl1-0}}\\
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{hyper/Fig/hyper-dipl2-0}
  \label{fig:hyper-dipl2-0}}
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{hyper/Fig/hyper-dipln2-0}
  \label{fig:hyper-dipln2-0}}\\
  \subfloat[]{\includegraphics[width=0.3\columnwidth]{hyper/Fig/rect111}
  \label{fig:rect111}}
\caption{\old{Slope estimation results. (a) Traditional method with smoothing radius $R=5$. (b) Traditional method with smoothing radius $R=10$. (c) Traditional method with smoothing radius $R=15$. (d) Proposed method with non-stationary regularization.}\new{Slope estimation results using (a) traditional method with smoothing radius $R=5$, (b) traditional method with smoothing radius $R=10$, (c) traditional method with smoothing radius $R=15$, and (d) proposed method with non-stationary regularization. Note the evident instabilities in Figures \ref{fig:hyper-dipl0-0} and \ref{fig:hyper-dipl1-0}. (e) Non-stationary smoothing radius distribution, which is calculated based on the a priori information from the initial slope estimation of Figure \ref{fig:hyper-dipl2-0}. Note that the large dip areas are assigned an obviously larger smoothing radius. }}
\label{fig:hyper-dipl0-0,hyper-dipl1-0,hyper-dipl2-0,hyper-dipln2-0,rect111}
\end{figure}

%
%\begin{figure}[htb!]
%\centering
%\includegraphics[width=0.8\columnwidth]{real/Fig/r-data}
%\caption{Real seismic profile containing complex geological structures like faults and salts. }
%\label{fig:r-data}
%\end{figure}
%
%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real/Fig/r-dipl1-0}
%   \label{fig:r-dipl1-0}}
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real/Fig/r-dipl11-0}
%   \label{fig:r-dipl11-0}}\\
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real/Fig/r-dipl2-0}
%   \label{fig:r-dipl2-0}}
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real/Fig/r-dipln1-0}
%   \label{fig:r-dipln1-0}}   \\
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real/Fig/r-rect1}
%   \label{fig:r-rect1}}
%\caption{Slope estimation results. (a) Traditional method with smoothing radius $R=10$. (b) Traditional method with smoothing radius $R=20$. (c) Traditional method with smoothing radius $R=30$. (d) Proposed method with non-stationary regularization. \new{(e) Non-stationary smoothing radius distribution, which is calculated based on the a priori information from the initial slope estimation of Figure \ref{fig:r-dipl2-0}. Note that the large dip areas around the salt flanks are assigned an obviously larger smoothing radius.}}
%\label{fig:r-dipl1-0,r-dipl11-0,r-dipl2-0,r-dipln1-0,r-rect1}
%\end{figure}
%
%%\begin{figure}[htb!]
%%\centering
%%\includegraphics[width=0.5\textwidth]{real/Fig/r-rect1}
%%\caption{Non-stationary smoothing radius distribution, which is calculated based on the a priori information from the initial slope estimation of Figure \ref{fig:r-dipl2-0}. Note that the large dip areas around the salt flanks are assigned an obviously larger smoothing radius. }
%%\label{fig:r-rect1}
%%\end{figure}
%
%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.22\textwidth]{real/Fig/pick-r-dipl1-0}
%   \label{fig:pick-r-dipl1-0}}
%\subfloat[]{\includegraphics[width=0.22\textwidth]{real/Fig/pick-r-dipl11-0}
%   \label{fig:pick-r-dipl11-0}}\\
%\subfloat[]{\includegraphics[width=0.22\textwidth]{real/Fig/pick-r-dipl2-0}
%   \label{fig:pick-r-dipl2-0}}
%\subfloat[]{\includegraphics[width=0.22\textwidth]{real/Fig/pick-r-dipln1-0}
%   \label{fig:pick-r-dipln1-0}} 
%\caption{Comparison of automatically picked events using (a) traditional slope estimation method with smoothing radius $R=10$, (b) traditional slope estimation method with smoothing radius $R=20$, (c) traditional slope estimation method with smoothing radius $R=30$, and (d) proposed slope estimation method with non-stationary regularization. Note the unstable event picking performance in (a) and (b) and obviously better event painting using the proposed method. The black frame boxes are zoomed in Figure \ref{fig:pick-r-dipl2-win1,pick-r-dipln1-win1} for more detailed comparison. }
%\label{fig:pick-r-dipl1-0,pick-r-dipl11-0,pick-r-dipl2-0,pick-r-dipln1-0}
%\end{figure}
%
%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.22\textwidth]{real/Fig/pick-r-dipl2-win1}
%   \label{fig:pick-r-dipl2-win1}}
%\subfloat[]{\includegraphics[width=0.22\textwidth]{real/Fig/pick-r-dipln1-win1}
%   \label{fig:pick-r-dipln1-win1}} 
%\caption{Zoomed comparison of the automatically picked events using (a) traditional slope estimation method with smoothing radius $R=30$, and (b) proposed slope estimation method with non-stationary regularization, corresponding to Figures \ref{fig:pick-r-dipl2-0} and \ref{fig:pick-r-dipln1-0}, respectively. It is obvious that the proposed method obtains a better event picking.}
%\label{fig:pick-r-dipl2-win1,pick-r-dipln1-win1}
%\end{figure}
%
%
%\begin{figure}[htb!]
%\centering
%\includegraphics[width=0.4\textwidth]{real2d3/Fig/g}
%\caption{Real seismic profile containing complex geological structures like faults and salts. }
%\label{fig:g}
%\end{figure}
%
%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real2d3/Fig/g-dipl1-0}
%   \label{fig:g-dipl1-0}}
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real2d3/Fig/g-dipl11-0}
%   \label{fig:g-dipl11-0}}\\
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real2d3/Fig/g-dipl2-0}
%   \label{fig:g-dipl2-0}}
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real2d3/Fig/g-dipln1-0}
%   \label{fig:g-dipln1-0}} \\
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real2d3/Fig/g-rect1}
%   \label{fig:g-rect1}}
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real2d3/Fig/g-rect2}
%   \label{fig:g-rect2}}\\
%\caption{Slope estimation results. (a) Traditional method with smoothing radius $R=5$. (b) Traditional method with smoothing radius $R=20$. (c) Traditional method with smoothing radius $R=30$. (d) Proposed method with non-stationary regularization. \new{Non-stationary smoothing radius distribution \new{for the vertical smoothing (e) and the horizontal smoothing (f)}, which is calculated based on the a priori information from the initial slope estimation of Figure \ref{fig:g-dipl2-0}.}}
%\label{fig:g-dipl1-0,g-dipl11-0,g-dipl2-0,g-dipln1-0,g-rect1,g-rect2}
%\end{figure}
%
%%\begin{figure}[htb!]
%%\centering
%%\subfloat[]{\includegraphics[width=0.23\textwidth]{real2d3/Fig/g-rect1}
%%   \label{fig:g-rect1}}
%%\subfloat[]{\includegraphics[width=0.23\textwidth]{real2d3/Fig/g-rect2}
%%   \label{fig:g-rect2}}\\
%%\caption{Non-stationary smoothing radius distribution \new{for the vertical smoothing (a) and the horizontal smoothing (b)}, which is calculated based on the a priori information from the initial slope estimation of Figure \ref{fig:g-dipl2-0}.  }
%%\label{fig:g-rect1,g-rect2}
%%\end{figure}
%
%
%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real2d3/Fig/g-sm1-0}
%   \label{fig:g-sm1-0}}
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real2d3/Fig/g-sm2-0}
%   \label{fig:g-sm2-0}}\\
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real2d3/Fig/g-sm3-0}
%   \label{fig:g-sm3-0}}
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real2d3/Fig/g-sm4-0}
%   \label{fig:g-sm4-0}}
%\caption{Structure-oriented smoothing comparison. (a) Traditional method with smoothing radius $R=5$. (b) Traditional method with smoothing radius $R=20$. (c) Traditional method with smoothing radius $R=30$. (d) Proposed method with non-stationary regularization.}
%\label{fig:g-sm1-0,g-sm2-0,g-sm3-0,g-sm4-0}
%\end{figure}
%
%\begin{figure}[ht!]
%\centering
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real2d3/Fig/g-sm1-n-0}
%   \label{fig:g-sm1-n-0}}
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real2d3/Fig/g-sm2-n-0}
%   \label{fig:g-sm2-n-0}}\\
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real2d3/Fig/g-sm3-n-0}
%   \label{fig:g-sm3-n-0}}
%\subfloat[]{\includegraphics[width=0.23\textwidth]{real2d3/Fig/g-sm4-n-0}
%   \label{fig:g-sm4-n-0}}
%\caption{Removed noise comparison. (a) Traditional method with smoothing radius $R=5$. (b) Traditional method with smoothing radius $R=20$. (c) Traditional method with smoothing radius $R=30$. (d) Proposed method with non-stationary regularization.}
%\label{fig:g-sm1-n-0,g-sm2-n-0,g-sm3-n-0,g-sm4-n-0}
%\end{figure}
%
%
%\begin{figure}[htb!]
%\centering
%\includegraphics[width=0.40\textwidth]{real3d/Fig/real}
%\caption{Real seismic profile containing complex geological structure like faults and salts. }
%\label{fig:real}
%\end{figure}
%
%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.2\textwidth]{real3d/Fig/real-s2dip1}
%   \label{fig:real-s2dip1}}
%\subfloat[]{\includegraphics[width=0.2\textwidth]{real3d/Fig/real-s11dip1}
%   \label{fig:real-s11dip1}}\\
%\subfloat[]{\includegraphics[width=0.2\textwidth]{real3d/Fig/real-s1dip1}
%   \label{fig:real-s1dip1}}
%\subfloat[]{\includegraphics[width=0.2\textwidth]{real3d/Fig/real-ndip1}
%   \label{fig:real-ndip1}}   
%\subfloat[]{\includegraphics[width=0.2\textwidth]{real3d/Fig/real-rect1}
%   \label{fig:real-rect1}}   
%\caption{Slope estimation results. (a) Traditional method with smoothing radius $R=2$. (b) Traditional method with smoothing radius $R=10$. (c) Traditional method with smoothing radius $R=20$. (d) Proposed method with non-stationary regularization. \new{(e) Non-stationary smoothing radius distribution.}}
%\label{fig:real-s2dip1,real-s11dip1,real-s1dip1,real-ndip1,real-rect1}
%\end{figure}
%
%%\begin{figure}[htb!]
%%\centering
%%\includegraphics[width=0.22\textwidth]{real3d/Fig/real-rect1}
%%\caption{Non-stationary smoothing radius distribution. }
%%\label{fig:real-rect1}
%%\end{figure}
%
%
%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.22\textwidth]{real3d/Fig/real-pws2-0}
%   \label{fig:real-pws2-0}}
%\subfloat[]{\includegraphics[width=0.22\textwidth]{real3d/Fig/real-pws11-0}
%   \label{fig:real-pws11-0}}\\
%\subfloat[]{\includegraphics[width=0.22\textwidth]{real3d/Fig/real-pws1-0}
%   \label{fig:real-pws1-0}}
%\subfloat[]{\includegraphics[width=0.22\textwidth]{real3d/Fig/real-pws3-0}
%   \label{fig:real-pws3-0}}
%\caption{Structure-oriented smoothing comparison. (a) Traditional method with smoothing radius $R=2$. (b) Traditional method with smoothing radius $R=10$. (c) Traditional method with smoothing radius $R=20$. (d) Proposed method with non-stationary regularization.}
%\label{fig:real-pws2-0,real-pws11-0,real-pws1-0,real-pws3-0}
%\end{figure}
%
%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.22\textwidth]{real3d/Fig/real-pws2-n-0}
%   \label{fig:real-pws2-n-0}}
%\subfloat[]{\includegraphics[width=0.22\textwidth]{real3d/Fig/real-pws11-n-0}
%   \label{fig:real-pws11-n-0}}\\
%\subfloat[]{\includegraphics[width=0.22\textwidth]{real3d/Fig/real-pws1-n-0}
%   \label{fig:real-pws1-n-0}}
%\subfloat[]{\includegraphics[width=0.22\textwidth]{real3d/Fig/real-pws3-n-0}
%   \label{fig:real-pws3-n-0}}
%\caption{Removed noise comparison. (a) Traditional method with smoothing radius $R=2$. (b) Traditional method with smoothing radius $R=10$. (c) Traditional method with smoothing radius $R=20$. (d) Proposed method with non-stationary regularization.}
%\label{fig:real-pws2-n-0,real-pws11-n-0,real-pws1-n-0,real-pws3-n-0}
%\end{figure}
%

\section{Theory}
\subsection{Dip limitation of plane-wave destruction}
The plane-wave equation can be expressed analytically as:
\begin{equation}
\label{eq:pwe}
u(t,x)=w(t-\sigma x),
\end{equation}
where $u(t,x)$ denotes the plane-wave wavefield at location $(t,x)$. $w(t)$ denotes the wavelet. $\sigma$ is the local slope. The plane-wave equation in the frequency domain takes the form as
\begin{equation}
\label{eq:pwe2}
U(f,x)=W(f)e^{i2\pi f\sigma x},
\end{equation}
where $U(f,x)$ and $W(f)$ denote the spectrum of the wavefield and source wavelet, respectively.

Equation \ref{eq:pwe2} indicates that the plane waves can be predicted via the following phase-shift relation:
\new{\begin{equation}
\label{eq:pwe3}
U(f,x+\Delta x)=U(f,x)e^{i2\pi f\Delta x\sigma},
\end{equation}}
\new{where $\Delta x$ denotes the space interval.}

In the Z-transform domain, equation \ref{eq:pwe3} is equivalent to 
 \begin{equation}
\label{eq:pwe4}
U(Z_t,Z_x)(1-Z_t^{-\sigma}Z_x) = 0.
\end{equation}
To estimate the local slope $\sigma$ from the plane-wave equation, one needs to design a digital filter to approximate $Z_t^{-\sigma}$. \cite{pwd} used an all-pass (or maxflat fractional delay) filter to approximate the phase-shift operator:
 \begin{equation}
\label{eq:pwe5}
Z_t^{-\sigma} = \frac{A(Z_t)}{A(1/Z_t)}. 
\end{equation}
With a different order of accuracy, $A(Z_t)$ has the following form

\begin{equation}
\label{eq:3order}
Z_t^{-\sigma} \approx \frac{(1-\sigma)(2-\sigma)}{12} Z_t^{-1} + \frac{(2+\sigma)(2-\sigma)}{6} +  \frac{(1+\sigma)(2+\sigma)}{12} Z_t, 
\end{equation}
or
\begin{equation}
\label{eq:5order}
\begin{split}
Z_t^{-\sigma} \approx &\frac{(1-\sigma)(2-\sigma)(3-\sigma)(4-\sigma)}{1680} Z_t^{-2} + \\
&\frac{(4-\sigma)(2-\sigma)(3-\sigma)(4+\sigma)}{420} Z_t^{-1}+ \\
&\frac{(4-\sigma)(3-\sigma)(3+\sigma)(4+\sigma)}{280} + \\
&\frac{(4-\sigma)(2+\sigma)(3+\sigma)(4+\sigma)}{420} Z_t + \\
&\frac{(1+\sigma)(2+\sigma)(3+\sigma)(4+\sigma)}{1680} Z_t^{2}. 
\end{split}
\end{equation}
The third-order approximation in equation \ref{eq:3order} or the fifth-order approximation in equation \ref{eq:5order} is accurate only for small slopes. The approximation accuracy is very low for large slopes. Thus, the traditional PWD method suffers from the aliasing issue for large seismic slopes.
\subsection{Large dip calculation}
To solve the dip limitation issue of the traditional PWD method, the single phase-shift approximation is replaced by the double phase-shift approximation:
 \begin{equation}
\label{eq:pwe44}
U(Z_t,Z_x)(1-Z_t^{-\sigma_t}Z_x^{-\sigma_x}) = 0,
\end{equation}
where $\sigma_t$ and $\sigma_x$ denote the local slopes in the $t$ and $x$ directions, respectively. The PWD method based on the double phase-shift approximation strategy is called as the OPWD algorithm. The phase-shift approximations in both $t$ and $x$ directions take the same form as that in the traditional PWD method:
\begin{equation}
\label{eq:pwe55}
\begin{split}
Z_t^{-\sigma_t} &= \frac{A(Z_t)}{A(1/Z_t)},\\
Z_x^{-\sigma_x} &= \frac{A(Z_x)}{A(1/Z_x)}. 
\end{split}
\end{equation}
Inserting equation \ref{eq:pwe55} into equation \ref{eq:pwe44}, we obtain
 \begin{equation}
\label{eq:pwe442}
U(Z_t,Z_x)(1-\frac{A(Z_t)}{A(1/Z_t)}\frac{A(Z_x)}{A(1/Z_x)}) = 0,
\end{equation}
which can be further simplified as
 \begin{equation}
\label{eq:pwe442}
U(Z_t,Z_x)(A(1/Z_t)A(1/Z_x)-A(Z_t)A(Z_x)) = 0.
\end{equation}
Let $H(\sigma_t,\sigma_x)=A(1/Z_t)A(1/Z_x)-A(Z_t)A(Z_x)$, the target of the large dip calculation becomes
 \begin{equation}
\label{eq:pwe443}
H(\sigma_t,\sigma_x)U= 0,
\end{equation}
where $\sigma_t^2+\sigma_x^2=1$.

\subsection{Dip pre-conditioned inversion}
Instead of calculating $\sigma_t$ and $\sigma_x$ directly, the inverse problem can be better solved by pre-conditioning $\sigma_t$ and $\sigma_x$ via the dip angle $\theta$:
 \begin{equation}
\label{eq:pwe444}
H(\sigma_t(\theta),\sigma_x(\theta))U= 0,
\end{equation}
where $\sigma_t(\theta)=\sin(\theta)$ and $\sigma_x(\theta)=\cos(\theta)$.

Note that range of $\sigma_t$ is $\sigma_t\in[-\infty,+\infty]$, but the range of $\theta$ is $\theta\in[-90,+90]$, so equation \ref{eq:pwe444} is better pre-conditioned.

The non-linear inverse problem in Equation \ref{eq:pwe444} can be solved via the Gauss-Newton method. 
First, equation \ref{eq:pwe444} needs to be linearized as follows:
 \begin{equation}
\label{eq:pwe445}
H(\sigma_t(\theta_0),\sigma_x(\theta_0))U \approx \frac{\partial H}{\partial \sigma_t}U\sigma_t'(\theta_0)\Delta \theta + \frac{\partial H}{\partial \sigma_x}U\sigma_x'(\theta_0)\Delta \theta.
\end{equation}
Inserting equations $\sigma_t(\theta)=\sin(\theta)$ and $\sigma_x(\theta)=\cos(\theta)$ into \ref{eq:pwe445}, we obtain
\begin{equation}
\label{eq:pwe446}
H(\sigma_t(\theta_0),\sigma_x(\theta_0))U \approx \frac{\partial H}{\partial \sigma_t}U\cos(\theta_0)\Delta \theta - \frac{\partial H}{\partial \sigma_x}U\sin(\theta_0)\Delta \theta.
\end{equation}
$\theta_0$ in equations \ref{eq:pwe445} and \ref{eq:pwe446} denotes a fixed dip angle. $\Delta \theta$ denotes the dip angle perturbation during the linear inversion.

Secondly, the final local dip angle field is obtained via the non-linear iteration:
\begin{equation}
\label{eq:niter}
\theta_{n+1} = \theta_{n} + \Delta \theta. 
\end{equation}

\subsection{Non-stationary regularization}
Equation \ref{eq:pwe446} can be formulated as a matrix-vector linear inverse problem as
\begin{equation}
\label{eq:inv}
\mathbf{H}\Delta \boldsymbol{\theta}=\mathbf{u},
\end{equation}
where $\Delta \boldsymbol{\theta}$ denotes the vector form of the dip angle perturbation $\Delta \theta$, $\mathbf{H}$ is constructed from $\frac{\partial H}{\partial \sigma_t}U\cos(\theta_0) - \frac{\partial H}{\partial \sigma_x}U\sin(\theta_0)$, and $\mathbf{u}$ corresponds to $H(\sigma_t(\theta_0),\sigma_x(\theta_0))U$. It is worth noting that the forward operator $\mathbf{H}$ is a diagonal matrix. Thus, the nulls in the diagonal of $\mathbf{H}$ greatly affect the stability when solving equation \ref{eq:inv}. The traditional PWD method \cite{pwd} uses the shaping regularization method to solve equation \ref{eq:inv}:
\begin{equation}
\label{eq:inv}
\Delta \boldsymbol{\theta}_{n+1} = \mathbf{S}[\Delta \boldsymbol{\theta}+\mathbf{H}^T(\mathbf{u}-\mathbf{H}\Delta \boldsymbol{\theta}_n)],
\end{equation}
where $\mathbf{S}$ denotes a smoothing operator, used to contrain the slope update $\Delta \boldsymbol{\theta}$. Because of the singularity of the diagonal matrix $\mathbf{H}$, especially in the areas corresponding to the large dip angles, we need to use a strong smoothing (e.g., with a large smoothing radius) to ensure the stability. However, a strong smoothing will deteriorate the resolution of the estimated dip angle field. Here, we propose to apply a spatially non-stationary smoothing to constrain the linear inversion.  Considering that the Z-transform of a rectangle smoothing operator can be expressed as:
\begin{equation}
\label{eq:rec}
B(Z)=1+Z+Z^2+\cdots+Z^N = \frac{1-Z^N}{1-Z},
\end{equation}
the non-stationary smoothing can be implemented conveniently following equation \ref{eq:rec}, where the Z-transform of the smoothing filter is a function of smoothing radius $N$. The right side of equation \ref{eq:rec} can be understood as two independent steps, i.e., a simple recursion corresponding to $1-Z^N$ and a causal integration corresponding to $1/(1-Z)$.

To balance the stability requiring a large smoothing radius and the resolution requiring a small smoothing radius, we propose to design the non-stationary smoothing radius as a large value for large dip angle areas and as a small value for small dip angle areas. In this way, we can best compromise the inversion stability and resolution of the dip estimation result.

\section{Synthetic example}
We first apply the proposed method onto a synthetic seismic shot gather. The simple shot gather is plotted in Figure \ref{fig:hyper}. There are four hyperbolic events in this shot gather. Because of the large dips on the left and right sides of the shot gather, the traditional PWD algorithm cannot obtain a robust performance when a small smoothing radius is used. For example, when the smoothing radius $R=5$ (as shown in Figure \ref{fig:hyper-dipl0-0}), there are strong aliasing effects on the left and right sides of the data. When we increase the smoothing radius to $R=10$ (as shown in Figure \ref{fig:hyper-dipl1-0}), the aliasing effect becomes less serious, but the right flank of the first hyperbolic event still shows obvious aliasing and instability. In the traditional PWD method, only when increasing the smoothing radius to $R=15$ (as shown in Figure \ref{fig:hyper-dipl2-0}), the aliasing and unstable performance does not show up. However, as the smoothing radius increases, the resolution of the estimated slope map becomes lower. When $R=15$, although there is no stability issue, the resolution becomes unsatisfactory. Using the proposed robust PWD method, we obtain a high-resolution and stable slope estimation, as presented in Figure \ref{fig:hyper-dipln2-0}. The non-stationary smoothing radius used to regularize slope estimation is plotted in Figure \ref{fig:rect111}. This non-stationary smoothing radius map is calculated using the initial slope estimation with a relatively large smoothing radius $R=15$, based on the criterion that a higher slope value corresponds to a larger smoothing radius. As can be seen from Figure \ref{fig:rect111}, the smoothing radius varies from the minimum one point to the maximum 15 points. \new{Here, we consider the vertical and horizontal dimensions as the same length, so we do not use distinct radius value for the two directions. However, in practice, the size of the two dimensions may vary greatly. In that case, the smoothing radius should be adjusted correspondingly to match the relative size of different dimensions. }

%\section{Discussions}

\section{Real data applications}
To demonstrate the effectiveness of the proposed robust PWD method to slope-based applications, we use several real seismic data to show the performance of different applications, including automatic tracking, 2D and 3D seismic structural filterings.

We first apply the proposed method to a real seismic profile to demonstrate its application in automatic seismic event picking. The event picking is a necessary step in seismic interpretation. Traditionally, the event picking is done manually, which is time consuming and tedious. An automatic event picking method was proposed in Fomel (2010) \cite{fomel2010painting}, where the local slope of seismic data is first calculated and then used to predict the picking trajectory of the seismic events based on a reference trace. In the automatic event picking method, the seismic slope is the most important factor that affects the picking performance. The real seismic profile is plotted in Figure \ref{fig:r-data}, which contains several typical geological structures like faults, salts, and buried hills. Picking the events from this data is challenging because of the complicated structures. Due to the large dip of the faults and steeply dipping salt flanks, the traditional PWD method is not stable when using a relatively small smoothing radius. The seismic slopes estimated using different smoothing radii are plotted in Figure \ref{fig:r-dipl1-0,r-dipl11-0,r-dipl2-0,r-dipln1-0,r-rect1}. It is clear that when the constant smoothing radius $R=10$, there exists serious stability issues, as pointed out by the labeled arrow. The stability issue exists mostly on the steeper salt flank that is more aliasing. When increasing the smoothing radius  $R=20$, the stability issues becomes less serious, but it still suffers from the instability, as indicated by the arrow. When we increase the smoothing radius to $R=30$, the instability disappears, but the resolution of the slope map is seriously deteriorated.  The lower resolution of the local slope map will decrease the automatic event picker's ability to correctly track the seismic events in small-scale features. The proposed method, however, obtains a stable and high-resolution slope estimation result. The non-stationary smoothing radius is plotted in Figure \ref{fig:r-rect1}. From the scalebar of the smoothing radius map, it is clear that the smoothing radius varies from the minimum 10 points to the maximum 30 points. The large smoothing radius is mostly around the two flanks of the salt body, and the faults. We apply the automatic  event picking method \cite{fomel2010painting} to the seismic profile based on the estimated slope maps in Figure \ref{fig:r-dipl1-0,r-dipl11-0,r-dipl2-0,r-dipln1-0,r-rect1}, and obtain different event picking results shown in Figure \ref{fig:pick-r-dipl1-0,pick-r-dipl11-0,pick-r-dipl2-0,pick-r-dipln1-0}. The colorful curves in Figure \ref{fig:pick-r-dipl1-0,pick-r-dipl11-0,pick-r-dipl2-0,pick-r-dipln1-0} denote the automatically tracked seismic events. Note that the \old{resulted}\new{resulting} slopes contain ultra-high values because of the instability when estimating the local slopes shown in Figures \ref{fig:r-dipl1-0} and \ref{fig:r-dipl11-0}, which makes the automatic event picking method \cite{fomel2010painting} completely fail in Figures \ref{fig:pick-r-dipl1-0} and \ref{fig:pick-r-dipl11-0}. Figures \ref{fig:pick-r-dipl2-0} and \ref{fig:pick-r-dipln1-0}, however, show reasonable event tracking results. \new{In this example, as a quantitative comparison, the slopes shown in Figures \ref{fig:r-dipl1-0} and \ref{fig:r-dipl11-0} help pick zero events. The slopes shown in Figures \ref{fig:r-dipl2-0} and \ref{fig:r-dipln1-0} however help to pick 15 events.} To compare the event picking in detail, we magnify two areas in Figures \ref{fig:pick-r-dipl2-0} and \ref{fig:pick-r-dipln1-0}, and show the zoomed results in Figure \ref{fig:pick-r-dipl2-win1,pick-r-dipln1-win1}. It is clear that the event tracking result in Figure \ref{fig:pick-r-dipln1-win1} is more consistent with the actual seismic event and thus more accurate. This indicates that the proposed method helps obtain better event picking performance because of the higher resolution of the estimated slope map.

Then, we apply the proposed method to 2D structural filtering problem. The structural filtering method uses the local slope field to create a flattened dimension where a simple smoothing operator can be directly applied to remove the noise and make the seismic events more spatially coherent. The details of the structural filtering algorithm are introduced in \cite{liuyang2010}. The 2D real seismic data is plotted in Figure \ref{fig:g}. There are some steeply dipping events in the deep part of this profile. We first calculate different slope maps based on different smoothing options. 
The slope map using a small smoothing radius $R=10$ is plotted in Figure \ref{fig:g-dipl1-0}, where strong aliasing effect issues exist. An area of instability is indicated by the labeled arrow. Increasing the smoothing radius to $R=20$ (as shown in Figure \ref{fig:g-dipl11-0}) mitigates the effect but cannot solve the problem completely. The remaining instability effect is highlighted by the arrow. Increasing the smoothing radius further to $R=30$ will suffer from the instability issue, as indicated by the arrow in Figure \ref{fig:g-dipl2-0}. The proposed robust PWD method, however, solves this problem and make the slope estimation stable. In addition, it does not compromise the resolution of the slope map and maintains a comparable resolution as that of Figure \ref{fig:g-dipl1-0}. The \new{vertical} smoothing radius of this example is plotted in Figure \ref{fig:g-rect1}, where we can see clearly that the bottom half of the seismic profile is taken as the large-dip object and is assigned a large smoothing radius $R=35$, the other areas are mosty assigned a smaller radius $R=5$. \new{The horizontal smoothing radius of this example is plotted in Figure \ref{fig:g-rect2}. As we can see, the horizontal smoothing radius varies from 6 to 10 samples, which explains the higher resolution in Figure \ref{fig:g-dipln1-0} than \ref{fig:g-dipl2-0}. However, using small constant smoothing radius like 6 or 10 samples for Figure \ref{fig:g-dipl2-0}, the instability will be more serious.} The structural filtering results using these slope maps are plotted in Figure \ref{fig:g-sm1-0,g-sm2-0,g-sm3-0,g-sm4-0}. Figure \ref{fig:g-sm1-0} shows three distinct black traces, indicating the instability of the structural filtering due to the ultra high value of the slope estimation result in Figure \ref{fig:g-dipl1-0}. Figures \ref{fig:g-sm2-0}-\ref{fig:g-sm4-0} are more acceptable, but Figures \ref{fig:g-sm2-0}-\ref{fig:g-sm3-0} contain more or less distortion of the seismic events due to the over smoothing. It is clearer to compare the removed noise profiles presented in Figure \ref{fig:g-sm1-n-0,g-sm2-n-0,g-sm3-n-0,g-sm4-n-0}. From the noise comparison, it becomes clear that both Figures \ref{fig:g-sm2-n-0} and \ref{fig:g-sm3-n-0} show strong signal leakages \cite{yangkang2015ortho} in areas with a large dip. The noise of the proposed method, seems to be more random and contains negligible signal leakage. This example shows that although a larger smoothing radius will help mitigate the instability issue, the resulted low resolution will make the structural filtering result suffer from more serious signal leakage.

Finally, we apply the proposed method to a 3D structural filtering example. The 3D dataset is plotted in Figure \ref{fig:real}, which contains complicated structures. The principle of the 3D structural filtering is same as the 2D filtering. They differ in that the 3D structural filtering predicts the traces from both inline and cross line sections while the 2D structural filtering predicts the traces only from a 2D section. The estimated inline slope cubes using different smoothing radius options are plotted in Figure \new{\ref{fig:real-s2dip1,real-s11dip1,real-s1dip1,real-ndip1,real-rect1}}. Because of the small radius, the slope estimation is highly unstable. Figure \ref{fig:real-s2dip1} shows the result based on a small constant smoothing radius $R=2$. Figures \ref{fig:real-s11dip1} and \ref{fig:real-s1dip1} show the results corresponding to $R=10$ and $R=20$, respectively. 
As the smoothing radius increases, the slope estimation becomes more stable but has lower resolution. The proposed method, however, obtains a better compromise in resolution and stability. The resulted well-behaved slope result is plotted in Figure \ref{fig:real-ndip1}. We use a non-stationary smoothing radius cube as plotted in Figure \ref{fig:real-rect1}, which varies from the smallest two points to the largest 20 points. Figure \ref{fig:real-pws2-0,real-pws11-0,real-pws1-0,real-pws3-0} plots the structural filtering results using different slopes. As indicated by the arrows, as the smoothing radius increases, more noise is removed but more signals are damaged. The proposed method helps better compromise the noise removal and signal preservation, and obtains a good filtering result in Figure \ref{fig:real-pws3-0}. The removed noise cubes using different smoothing radii are plotted in Figure \ref{fig:real-pws2-n-0,real-pws11-n-0,real-pws1-n-0,real-pws3-n-0} to show a clearer comparison. It is obvious that the noise level in Figure \ref{fig:real-pws2-n-0} is a little weaker. As indicated by the arrows, all Figures \ref{fig:real-pws2-n-0}-\ref{fig:real-pws1-n-0} contain more or less signal leakage, showing some spatially coherent energy. The proposed method, however, removes a significant amount of noise without causing observable signal leakage.

\section{Discussion}
\new{Local dip estimation plays a crucial role in many geophysical applications when structural a priori information is needed. Due to the non-negligible error of the maxflat fractional delay filter in approximating the phase-shift operator, the traditional plane-wave destruction (PWD) algorithm fails when the dip becomes very large. The omnidirectional plane-wave destruction (OPWD) algorithm can estimate the large dip by using a circle-interpolating PWD filter but at the cost of causing potential instabilities. The instabilities can be mitigated by increasing the smoothing radius, which however will significantly decrease the resolution of the resulting slope.  So, there is an obvious contradiction between the resolution and instability. The new method is used to overcome this contradiction by designing non-stationary smoothing to constrain the slope.}

\new{The advantage of the adaptively smoothing approach is that it can use adaptive smoothing strength to adapt to the structural complexity thus is able to overcome the contradiction between resolution and stability. The disadvantage is that it may require some effort to design an appropriate spatial distribution of smoothing radius. However, the proposed method is better or equal to the traditional method, because the worst case of the proposed method will be equal to the traditional method (e.g., when the radius is spatially constant). One way to adjust the smoothing radius is completely based on the initial slope estimation. For example, we can define a threshold of slope values, above which we use a larger radius and under which we use a smaller radius. Another way is based on the instability effect in the initial slope estimation results. For example, for areas showing strong instability, we use a large smoothing radius.}

\new{The computational cost of the proposed method is almost equivalent to the traditional method. The difference between the two methods lays in the regularization step when inverting the slope map. In the new method, a non-stationary smoothing is applied instead of a constant-radius smoothing. In both traditional and new methods, we apply an efficient smoothing algorithm following equation \ref{eq:rec}. This smoothing method has been used extensively in the seismic community, e.g., recently by \cite{orthon2021}. Equation \ref{eq:rec} corresponds to a recursion formula in the time domain, which is a function of the smoothing radius $N$. So, implementing the stationary and non-stationary smoothing radius almost has no difference in the computational cost.}

\section{Conclusions}
The traditional PWD algorithm is not able to accurately estimate the large dips (e.g., slope larger than one) in the seismic section because of the phase-wrapping effect of the maxflat fractional delay filter. The OPWD algorithm could solve this problem by substituting the linear interpolation strategy with the circle interpolation scheme in the plane-wave construction filter. The OPWD algorithm, however, is less stable than the PWD algorithm since it tends to create extremely high values in the estimated local dip maps. To stabilize the inversion when calculating the local slope, a very large smoothing radius needs to be used, which however results in a low resolution and reversely decreases the accuracy of large dip estimation. The contradiction between stability and resolution makes the OPWD algorithm not differ from the traditional PWD algorithm too much. The non-stationary smoothness constrained slope estimation, however, only sacrifices the resolution of those areas that are easy to cause stability but preserves the accuracy and high resolution of other areas. Several examples have shown that the new PWD algorithm is able to estimate large dips with a high-resolution performance. Furthermore, the proposed method has a profound influence on a variety of seismic interpretation and processing applications.

\section{Acknowledgements}
The research in this article is partially supported by the National Natural Science Foundation of China (grant no. 41804140) and the Open Fund of Key Laboratory of Exploration Technologies for Oil and Gas Resources (Yangtze University), Ministry of Education (grant no. PI2018-02).

\bibliographystyle{seg}
\bibliography{dip}

### 2022-01-07 diffrlrra3d/paper.tex
up

@@
 %% uncomment
-%\multiplot{4}{b,b-pwd,b-lrr,b-lrra}{width=0.45\columnwidth}{Field data example.
+\inputdir{real3d}
+\multiplot{4}{b,b-pwd,b-lrr,b-lrra}{width=0.45\columnwidth}{Field data example.
 (a) A 3D field dataset.
@@
 }
-%\multiplot{3}{b-pwd-n-0,b-lrr-n-0,b-lrra-n-0}{width=0.45\columnwidth}{Separated diffraction data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }
+\multiplot{3}{b-pwd-n-0,b-lrr-n-0,b-lrra-n-0}{width=0.45\columnwidth}{Separated diffraction data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }
 
-%\multiplot{3}{b-pwd-n-t-0,b-lrr-n-t-0,b-lrra-n-t-0}{width=0.45\columnwidth}{A comparison of time slices extracted from the separated diffraction data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
+\multiplot{3}{b-pwd-n-t-0,b-lrr-n-t-0,b-lrra-n-t-0}{width=0.45\columnwidth}{A comparison of time slices extracted from the separated diffraction data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method.
 }
 
-%\multiplot{4}{b-pwd-rimag-0,b-pwd-imag-0,b-lrr-imag-0,b-lrra-imag-0}{width=0.45\columnwidth}{(a) Time slice of the reflection image.
+\multiplot{4}{b-pwd-rimag-0,b-pwd-imag-0,b-lrr-imag-0,b-lrra-imag-0}{width=0.45\columnwidth}{(a) Time slice of the reflection image.
 Time slices of the diffraction image using (b) the PWD method, (c) the LRR method, and (d) the LRRA method.

### 2022-01-15 qcomp/paper.tex
fix qcomp

--- 2020-09-16 qcomp/ieee_r1.tex
@@
 \renewcommand{\thefootnote}{\fnsymbol{footnote}}
-\author{Hang Wang, Guangtan Huang, Yangkang Chen, and Wei Chen
-\thanks{H. Wang, G. Huang, Y. Chen are with Zhejiang University.}
-\thanks{W. Chen is with Yangtze University (corresponding author).}
-\thanks{The research is supported by the National Natural Science Foundation of China (Grant No. 41804140).}}
+\author{Hang Wang, Guangtan Huang, Yangkang Chen, and Wei Chen}
+%\thanks{H. Wang, G. Huang, Y. Chen are with Zhejiang University.}
+%\thanks{W. Chen is with Yangtze University (corresponding author).}
+%\thanks{The research is supported by the National Natural Science Foundation of China (Grant No. 41804140).}}
 \maketitle
@@
 
-\begin{keywords}
-Q-compensation, denoising, and seismic data
-\end{keywords}
+%\begin{keywords}
+%Q-compensation, denoising, and seismic data
+%\end{keywords}
 
 \section{Introduction}
-Recovering the seismic signals from the strong background seismic noise, also known as seismic denoising, is of great importance of the whole seismic data processing chain \cite{yanan2014,yanhui2016,amir2017ieee,li2018multidimensional,wang2019hankel}.
-There have been a lot of classic denoising algorithms in the literature, e.g., the prediction-based denoising methods \cite{canales1984,abma1995}, \new{the sparse transform based denoising methods \cite{fomel2010seislet,mostafa2016geo,mostafa2016bssa,mousavi2017automatic}}, the mode decomposition based denoising methods \cite{chenwei2012}, the rank-reduction based denoising methods \cite{mssa,weilin2016dmssa,zhaoqiang2019tgrs}, etc.
+Recovering the seismic signals from the strong background seismic noise, also known as seismic denoising, is of great importance of the whole seismic data processing chain \cite[]{yanan2014,yanhui2016,amir2017ieee,li2018multidimensional,wang2019hankel}.
+There have been a lot of classic denoising algorithms in the literature, e.g., the prediction-based denoising methods \cite[]{canales1984,abma1995}, \new{the sparse transform based denoising methods \cite[]{fomel2010seislet,mostafa2016geo,mostafa2016bssa,mousavi2017automatic}}, the mode decomposition based denoising methods \cite[]{chenwei2012}, the rank-reduction based denoising methods \cite[]{mssa,weilin2016dmssa,zhaoqiang2019tgrs}, etc.
 Despite \old{of }the reported success in the field of seismic denoising, the traditional methods cannot resolve the problem of amplitude loss due to the anelastic attenuation when seismic waves are propagated in subsurface media.
@@
 The anelastic attenuation is usually described by the quality factor (Q).
-Kjartansson (1979) \cite{kjartansson1979constant} proposed a constant Q-model, which describes an attenuation medium \cite{bickel1985plane,wang2002stable,shen2018q,shen2018q2}.
-In the constant Q-model, the quality factor does not vary with frequency \cite{braginsky1989quality,dai2012multi}.
-The estimation of Q is important in a variety of geophysical inverse problems, e.g., Q-compensated seismic migration, high-fidelity seismic interpretation, reservoir fluid characterization, and seismic risk estimation \cite{mousavi2014jgr,shank2018image,cheng2018q,jyothi2017seismic,luo2019q,chen2019multichannel}.
-Q-compensation, a widely used method to seismic imaging, is becoming a \old{heated}\new{hot} researching topic in exploration geophysics \cite{guo2017adjoint,zhou2019viscoacoustic,aharchaou2019prestack}.
-\new{Besides, Q can also be used to interpret the large-scale geological features \cite{zhao2018lateral}.}
+Kjartansson (1979) \cite[]{kjartansson1979constant} proposed a constant Q-model, which describes an attenuation medium \cite[]{bickel1985plane,wang2002stable,shen2018q,shen2018q2}.
+In the constant Q-model, the quality factor does not vary with frequency \cite[]{braginsky1989quality,dai2012multi}.
+The estimation of Q is important in a variety of geophysical inverse problems, e.g., Q-compensated seismic migration, high-fidelity seismic interpretation, reservoir fluid characterization, and seismic risk estimation \cite[]{mousavi2014jgr,shank2018image,cheng2018q,jyothi2017seismic,luo2019q,chen2019multichannel}.
+Q-compensation, a widely used method to seismic imaging, is becoming a \old{heated}\new{hot} researching topic in exploration geophysics \cite[]{guo2017adjoint,zhou2019viscoacoustic,aharchaou2019prestack}.
+\new{Besides, Q can also be used to interpret the large-scale geological features \cite[]{zhao2018lateral}.}
 
-Reverse time migration (RTM) is thought as one of the most effective seismic imaging methods \cite{baysal1983reverse,yoon2004challenges,dai2012multi}.
+Reverse time migration (RTM) is thought as one of the most effective seismic imaging methods \cite[]{baysal1983reverse,yoon2004challenges,dai2012multi}.
 In recent years, Q-compensation research for different forms of reverse time migration has emerged.
-\cite{zhang2010compensating} proposed a Q-compensated RTM, where a \old{viscoelastic}\new{viscoacoustic} wave equation is used for compensating amplitude attenuation and phase dispersion effects.
-Researchers also used the separated fractional Laplace equation to approximate the constant-Q wave equation for viscous acoustic medium modeling and imaging tasks \cite{zhu2014q,fathalian2020approach}, which plays an important role in effectively using constant-Q in data processing \cite{harris2014q,wang2018adaptive}.\old{ The viscoelastic least-square inverse time migration (also known as Q-LSRTM) is a linear inversion of \new{a} subsurface reflectance model from lossy data ?.
+\cite[]{zhang2010compensating} proposed a Q-compensated RTM, where a \old{viscoelastic}\new{viscoacoustic} wave equation is used for compensating amplitude attenuation and phase dispersion effects.
+Researchers also used the separated fractional Laplace equation to approximate the constant-Q wave equation for viscous acoustic medium modeling and imaging tasks \cite[]{zhu2014q,fathalian2020approach}, which plays an important role in effectively using constant-Q in data processing \cite[]{harris2014q,wang2018adaptive}.\old{ The viscoelastic least-square inverse time migration (also known as Q-LSRTM) is a linear inversion of \new{a} subsurface reflectance model from lossy data ?.
 Compared with the traditional migration method, it could compensate for the amplitude loss of the migration image caused by the strong underground attenuation, and can produce the reflector accurately located at the depth.
 Researchers have developed different algorithms and demonstrate the Q-LSRTM method converges significantly faster than least-square reserve time migration ?.} Q-compensation can be utilized in full waveform inversion (FWI) as well.
-FWI provides a reliable method for the establishment of \new{a} high-resolution underground model, especially for the construction of \new{a} complex geological structure model, which has been \old{fully}\new{extensively} studied\old{ and developed} in the past decades \cite{tarantola2005inverse,virieux2009overview}.
-Q-compensated FWI has been proved to be highly effective \new{for building a reliable subsurface velocity model} \cite{xue2018accelerating}.
+FWI provides a reliable method for the establishment of \new{a} high-resolution underground model, especially for the construction of \new{a} complex geological structure model, which has been \old{fully}\new{extensively} studied\old{ and developed} in the past decades \cite[]{tarantola2005inverse,virieux2009overview}.
+Q-compensated FWI has been proved to be highly effective \new{for building a reliable subsurface velocity model} \cite[]{xue2018accelerating}.
 \old{By comparing the convergence rates of FWI with Q-compensated gradient and without Q-compensated gradient, we can know that the Q-compensation strategy can obviously improve the convergence of FWI, which is helpful for the fast inversion of \new{the} deep structure of velocity model ?.
@@
 %Q-compensation can be utilized in full waveform inversion (FWI) as well.
-FWI provides a reliable method for the establishment of \new{a} high-resolution underground model, especially for the construction of \new{a} complex geological structure model, which has been \old{fully}\new{extensively} studied\old{ and developed} in the past decades \cite{tarantola2005inverse,virieux2009overview}.
-Q-compensated FWI has been proved to be highly effective \new{for building a reliable subsurface velocity model} \cite{xue2017visco,xue2018accelerating}.
-By comparing the convergence rates of FWI with Q-compensated gradient and without Q-compensated gradient, we can know that the Q-compensation strategy can obviously improve the convergence of FWI, which is helpful for the fast inversion of \new{the} deep structure of velocity model \cite{alasmri2019towards,li2016application,xue2016q,wang2019q}.
+FWI provides a reliable method for the establishment of \new{a} high-resolution underground model, especially for the construction of \new{a} complex geological structure model, which has been \old{fully}\new{extensively} studied\old{ and developed} in the past decades \cite[]{tarantola2005inverse,virieux2009overview}.
+Q-compensated FWI has been proved to be highly effective \new{for building a reliable subsurface velocity model} \cite[]{xue2017visco,xue2018accelerating}.
+By comparing the convergence rates of FWI with Q-compensated gradient and without Q-compensated gradient, we can know that the Q-compensation strategy can obviously improve the convergence of FWI, which is helpful for the fast inversion of \new{the} deep structure of velocity model \cite[]{alasmri2019towards,li2016application,xue2016q,wang2019q}.
 \old{However, attenuation reconstruction is always an ill-posed problem.
-Because the reliability of attenuation reconstruction depends on the precision of \new{the} initial velocity model to a great extent, FWI has the advantages of being more robust and stable, but the calculation cost is very high ?.} \cite{xin20093} proposed a ray based Q-tomography, which can be incorporated into the traditional depth velocity modeling process.
+Because the reliability of attenuation reconstruction depends on the precision of \new{the} initial velocity model to a great extent, FWI has the advantages of being more robust and stable, but the calculation cost is very high ?.} \cite[]{xin20093} proposed a ray based Q-tomography, which can be incorporated into the traditional depth velocity modeling process.
 In order to compensate for the attenuation in RTM and FWI imaging, it is necessary to estimate the spatial change rate of attenuation from the dataset.
-Q-tomography based on frequency shift data is very useful in estimating the uniform attenuation rate \cite{harris2014q,he2012q,xin2014robust}.
+Q-tomography based on frequency shift data is very useful in estimating the uniform attenuation rate \cite[]{harris2014q,he2012q,xin2014robust}.
 
@@
 \end{equation}
-where $\mathbf{A}$ denotes the attenuation operator. In an integral form, equation \ref{eq:conva} can be expressed as \cite{margrave2011gabor,yufeng2018l12}:
+where $\mathbf{A}$ denotes the attenuation operator. In an integral form, equation \ref{eq:conva} can be expressed as \cite[]{margrave2011gabor,yufeng2018l12}:
 \begin{equation}
@@
 $r(t)$ is the reflectivity function in the time domain.
-The attenuation function can be defined based on the constant-Q theory as follows \cite{zhu2014q,yufeng2018l12}:
+The attenuation function can be defined based on the constant-Q theory as follows \cite[]{zhu2014q,yufeng2018l12}:
 \begin{equation}
@@
  \centering
- \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-dc}
+ \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-dc}
    \label{fig:syn-dc}}\\
- \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-da}
+ \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-da}
    \label{fig:syn-da}}
- \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-dn}
+ \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-dn}
    \label{fig:syn-dn}}
@@
  \centering
- \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d2}
+ \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d2}
    \label{fig:syn-d2}}
- \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d1}
+ \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d1}
    \label{fig:syn-d1}}
@@
  \centering
- \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-da-simi}
+ \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-da-simi}
    \label{fig:syn-da-simi}}
- \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-dn-simi}
+ \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-dn-simi}
    \label{fig:syn-dn-simi}}\\
- \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d2-simi}
+ \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d2-simi}
    \label{fig:syn-d2-simi}}
- \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d1-simi}
+ \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d1-simi}
    \label{fig:syn-d1-simi}}
@@
  \centering
- \subfigure[]{\includegraphics[width=0.5\textwidth]{synth/Fig/syn-ss0}
+ \subfloat[]{\includegraphics[width=0.5\textwidth]{synth/Fig/syn-ss0}
    \label{fig:syn-ss0}}
- \subfigure[]{\includegraphics[width=0.5\textwidth]{synth/Fig/syn-ss-z}
+ \subfloat[]{\includegraphics[width=0.5\textwidth]{synth/Fig/syn-ss-z}
    \label{fig:syn-ss-z}}
@@
  \centering
- \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-dn-0}
+ \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-dn-0}
    \label{fig:real-dn-0}}\\
- \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d2-0}
+ \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d2-0}
    \label{fig:real-d2-0}}
- \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d1-0}
+ \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d1-0}
    \label{fig:real-d1-0}}   
@@
 \end{equation}
-where $[\mathbf{W}_r]_{ii}=|r_i|^{-1/2}$. To avoid the singularity caused by too small $r_i$, a threshold needs to be defined \cite{amr2014}.
+where $[\mathbf{W}_r]_{ii}=|r_i|^{-1/2}$. To avoid the singularity caused by too small $r_i$, a threshold needs to be defined \cite[]{amr2014}.
 
@@
 $\mathbf{W}_r$ needs to be re-calculated during the iterations.
-\new{Following Daniel (2003) \cite{daniel2003}}, we ease the inconvenience in selecting the balancing parameter $\lambda$ by adjusting the sparsity constraint through the number of re-weighting iterations.
+\new{Following Daniel (2003) \cite[]{daniel2003}}, we ease the inconvenience in selecting the balancing parameter $\lambda$ by adjusting the sparsity constraint through the number of re-weighting iterations.
 A higher number of re-weighting iterations corresponds to a higher trade-off parameter $\lambda$ and vice versa.
@@
  \centering
- \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-dn-z1}
+ \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-dn-z1}
    \label{fig:real-dn-z1}}\\
- \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d2-z1}
+ \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d2-z1}
    \label{fig:real-d2-z1}}
- \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d1-z1}
+ \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d1-z1}
    \label{fig:real-d1-z1}}   
@@
  \centering
- \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-dn-z2}
+ \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-dn-z2}
    \label{fig:real-dn-z2}}\\
- \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d2-z2}
+ \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d2-z2}
    \label{fig:real-d2-z2}} 
- \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d1-z2}
+ \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d1-z2}
    \label{fig:real-d1-z2}}   
@@
  \centering
- \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q60-0}
+ \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q60-0}
    \label{fig:real-d1-q60-0}}
- \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q70-0}
+ \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q70-0}
    \label{fig:real-d1-q70-0}}   
- \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q80-0}
+ \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q80-0}
    \label{fig:real-d1-q80-0}}  \\
- \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q90-0}
+ \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q90-0}
    \label{fig:real-d1-q90-0}}
- \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q100-0}
+ \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q100-0}
    \label{fig:real-d1-q100-0}}   
- \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q120-0}
+ \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q120-0}
    \label{fig:real-d1-q120-0}}   
@@
  \centering
- \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q60-z1}
+ \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q60-z1}
    \label{fig:real-d1-q60-z1}}
- \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q70-z1}
+ \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q70-z1}
    \label{fig:real-d1-q70-z1}}   
- \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q80-z1}
+ \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q80-z1}
    \label{fig:real-d1-q80-z1}}  \\
- \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q90-z1}
+ \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q90-z1}
    \label{fig:real-d1-q90-z1}}
- \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q100-z1}
+ \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q100-z1}
    \label{fig:real-d1-q100-z1}}   
- \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q120-z1}
+ \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q120-z1}
    \label{fig:real-d1-q120-z1}}   
@@
  \centering
- \subfigure[]{\includegraphics[width=0.23\textwidth]{Fig/real3}
+ \subfloat[]{\includegraphics[width=0.23\textwidth]{Fig/real3}
    \label{fig:real3}}\\
- \subfigure[]{\includegraphics[width=0.23\textwidth]{Fig/real3-d2}
+ \subfloat[]{\includegraphics[width=0.23\textwidth]{Fig/real3-d2}
    \label{fig:real3-d2}}   
- \subfigure[]{\includegraphics[width=0.23\textwidth]{Fig/real3-d1}
+ \subfloat[]{\includegraphics[width=0.23\textwidth]{Fig/real3-d1}
    \label{fig:real3-d1}}   
@@
  \centering
- \subfigure[]{\includegraphics[width=0.23\textwidth]{Fig/real3-z}
+ \subfloat[]{\includegraphics[width=0.23\textwidth]{Fig/real3-z}
    \label{fig:real3-z}}\\
- \subfigure[]{\includegraphics[width=0.23\textwidth]{Fig/real3-d2-z}
+ \subfloat[]{\includegraphics[width=0.23\textwidth]{Fig/real3-d2-z}
    \label{fig:real3-d2-z}}   
- \subfigure[]{\includegraphics[width=0.23\textwidth]{Fig/real3-d1-z}
+ \subfloat[]{\includegraphics[width=0.23\textwidth]{Fig/real3-d1-z}
    \label{fig:real3-d1-z}}   
@@
  \centering
- \subfigure[]{\includegraphics[width=0.33\textwidth]{Fig/real3-s-0}
+ \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/real3-s-0}
    \label{fig:real3-s-0}}\\
- \subfigure[]{\includegraphics[width=0.33\textwidth]{Fig/real3-d2-s-0}
+ \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/real3-d2-s-0}
    \label{fig:real3-d2-s-0}} \\  
- \subfigure[]{\includegraphics[width=0.33\textwidth]{Fig/real3-d1-s-0}
+ \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/real3-d1-s-0}
    \label{fig:real3-d1-s-0}}   
@@
 \centering
-\subfigure[]{\includegraphics[width=0.5\textwidth]{Fig/real3-traces-0}}
+\subfloat[]{\includegraphics[width=0.5\textwidth]{Fig/real3-traces-0}}
 \caption{\new{Trace-by-trace comparison (middle traces of the zoomed seismic cubes in Fig.
@@
 \ref{fig:syn-dn}.
-We apply the FX method \cite{canales1984} and the proposed signal enhancing method to the noisy and attenuated data, and then show the results in Fig.
+We apply the FX method \cite[]{canales1984} and the proposed signal enhancing method to the noisy and attenuated data, and then show the results in Fig.
 \ref{fig:syn-d2,syn-d1}.
@@
 \ref{fig:syn-dc}.
-To evaluate the denoising and Q-compensation performance, we use the local similarity metric \cite{fomel2007localattr,yangkang2015ortho}.
+To evaluate the denoising and Q-compensation performance, we use the local similarity metric \cite[]{fomel2007localattr,yangkang2015ortho}.
 We calculate the local similarity between the ground-truth solution (Fig.
@@
 
-%\section{Discussions}
-%\section{Conclusions}
-%\section{Acknowledgements}
-
-\bibliographystyle{IEEEtran}
+\bibliographystyle{seg}
 \bibliography{q}
-
-%\begin{figure}[htb!]
-%	\centering
-%	\subfigure[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
-%	\caption{Caption.}
-%	\label{fig:fig}
-%\end{figure}
-
-%\begin{figure*}[ht!]
-%  \centering
-%  \subfigure[]{\includegraphics[width=0.45\textwidth]{path/Fig/fig1}
-%    \label{fig:fig1}}
-%  \subfigure[]{\includegraphics[width=0.35\textwidth]{path/Fig/fig2}
-%    \label{fig:fig2}}    
-%   \caption{caption goes here}
-%   \label{fig:fig1,fig2}
-%\end{figure*}
-
-%\begin{table}[h]
-%\caption{Table caption}
-%\begin{center}
-%     \begin{tabular}{|c|c|c|c|c|c|} 
-%	  \hline Column1 (unit)  & Column2 (unit) & Column3 (unit) \\ 
-%	  \hline 1 & 2  & 3 \\
-%       \hline
-%    \end{tabular} 
-%\end{center}
-%\label{tbl:table1}
-%\end{table}

### 2022-01-15 qcomp/matfun/mtx_oper.m

@@ -1,0 +1,22 @@
+function [ out ] = mtx_oper( in, Param, operator )
+% General form of matrix based operator
+% 
+% By Yangkang Chen, Feb, 2015
+% The University of Texas at Austin
+% 
+% operator = 1 : m->d (W )
+% operator = -1: d->m (W')
+
+W=Param.W;
+
+if operator == 1
+    out=W*in;
+end
+
+if operator == -1
+    out=W'*in;
+end
+    
+
+end
+

### 2022-01-17 erratic/paper.tex
erratic

\title{Erratic-noise suppression using iterative structure-oriented \wen{space-varying} median filtering with sparsity constraint}
\author{Guangtan Huang\footnotemark[1], Min Bai\footnotemark[3], Qiang Zhao\footnotemark[2], Wei Chen\footnotemark[3], and Yangkang Chen\footnotemark[1]}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\address{
\footnotemark[1]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
yangkang.chen@zju.edu.cn \\
\footnotemark[2]CNPC Key Laboratory of Geophysical Prospecting\\
China University of Petroleum (East China)\\
Qingdao 266580, China\\
zq\_clark@163.com\\
\footnotemark[3]Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
Yangtze University\\
Wuhan 430100, China\\
chenwei2014@yangtzeu.edu.cn
}

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}

\lefthead{Huang et al., 2020}
\righthead{Erratic noise suppression}

\begin{abstract}
\dlo{Erratic noise refers to those interfering components in the seismic data that correspond to isolated events with the non-Gaussian distribution. Erratic noise is usually of high amplitude, which makes the removal of this type of noise troublesome for many traditional denoising algorithms. We develop a new method to effectively suppress the erratic noise based on an iterative framework. We transform the data \dlo{with}\wen{including} erratic noise to a pseudodata with approximately Gaussian-type noise by \wen{using} a signal-preserving space-varying median filter. The pseudodata can thus be denoised based on a traditional least-squares based method with a sparsity-promoting constraint. Because of the constraint from the space-varying median filtering, strong erratic noise can be effectively suppressed during the iterative procedures. The space-varying filter is applied following the \dlo{morphological pattern of}\wen{slope direction of} the seismic data to further preserve the energy of useful signals. We apply the proposed robust denoising algorithm to a synthetic dataset and two field data examples and find it to be potentially advantageous for a range of industry applications.}Erratic noise often has high amplitudes and a non-Gaussian distribution. Least-squares based approaches therefore are not optimal. This can be handled better with non-least-squares approaches, e.g., based on Huber norm which is computationally expensive.  An alternative method has been published which involves transforming the data with erratic noise to pseudodata that has Gaussian distributed noise. It can then be \dlo{denoised}\wen{attenuated} using traditional least-squares approaches.  This alternative method has previously been used in combination with a curvelet transform in an iterative scheme. In this paper, we introduce a median filtering step in this iterative scheme. The median filter is applied following the slope direction of the seismic data to maximally preserve the energy of useful signals. The new method can suppress stronger erratic noise compared with the previous iterative method, and can better deal with random noise compared with the single-step implementation of the median filter. We apply the proposed robust denoising algorithm to a synthetic dataset and two field data examples and \dlo{find it to be potentially advantageous for a range of industry applications}\wen{demonstrate its advantages over three different noise attenuation algorithms}.   \par
\textbf{Key words:} Seismic signal processing, Erratic noise suppression, Median filtering, Sparsity-promoting constraint
\end{abstract}

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}

\section{Introduction}
Strong noise existing in the seismic data often deteriorates many processing and interpretation tasks in the whole seismic imaging workflow, thus the removal of \dlo{the }seismic noise is of great importance \cite[]{liuyang20091,guochang2012,shuwei2016,wangchong2018,zhaoqiang2018}.  According to the difference of spatial correlation in the seismic profiles, seismic noise is usually classified as coherent and incoherent\dlo{ noise}.  Because of the similarity between coherent noise and effective signals in the morphological features, it is usually inadequate to simply apply a one-step filtering method to remove the coherent noise.  Thus, coherent noise, e.g., \dlo{the }ground roll and multiple reflections, is often suppressed via a prediction-and-subtraction strategy \wen{\cite[]{verschuure1991,verschuur1992,karsli2004using,halliday2007,dondurur2012swell,karsli2018mean,zhangdong2020ortho}}. The incoherent noise, however, is mostly suppressed by applying some filters that best utilize the spatially correlative feature of the \dlo{noise}\wen{signal}. %In this paper, we focus on the suppression of incoherent noise.

Suppression of random noise has been studied extensively in recent years. \old{A wide variety of methods}\new{Many methods} have been introduced and applied for \dlo{the }seismic \wen{random-noise} suppression \cite[]{mssa,weilin2016dmssa}. One common \dlo{seismic signal }denoising strategy, \wen{also known as sparse coding}, is to transform the data into different domains in order to concisely represent the signal with a \dlo{few}\wen{limited} number of selected components that capture the useful information \wen{or to further randomize the incoherent components}. \dlo{It}\wen{This strategy} includes \dlo{the }methods based on the Fourier transform \wen{\cite[]{mousavi2016adaptive}}, wavelet transform \cite[]{mostafa2016bssa,mostafa2016geo}, seislet transform \cite[]{fomel2010seislet,yangkang20142}, curvelet transform \cite[]{mostafa2010}, shearlet transform \cite[]{jsedecon2016}, Radon transform \cite[]{beylkin1987discrete}, wavelet transform \cite[]{sweldens1995}, dictionary learning \cite[]{yangkang2017sgk,amir2017,amir2017geo}, and \wen{deep-learning techniques \cite[]{li2018large,zhu2019seismic}}. Another type of approaches for \wen{random-noise attenuation} focus\wen{es} on enhancing useful signals and suppressing random noise by utilizing \dlo{the}\wen{a} predictable property, such as\old{ the} $t-x$ predictive filtering \cite[]{abma1995}, $f-x$ predictive filtering \cite[]{canales1984,gulunay1986},  \new{the} complex-trace analysis method \cite[]{karsli2006application}, non-stationary predictive filtering \cite[]{guochang2012,guochang2013,guochang2018weighted,li2018multidimensional}, and the polynomial fitting-based approach \cite[]{yanhong2009}. \dlo{The decomposition-based denoising approaches consider the disparity of the seismic signal and random noise\wen{,} and attempt to extract useful information from the principal components of the noisy data. Typical methods include the empirical-mode decomposition (EMD) and its improvements ?, singular value decomposition (SVD)-based approaches ?, regularized non-stationary decomposition ?, the Cadzow filtering ?, singular spectrum analysis (SSA) ?, multichannel singular spectrum analysis (MSSA) ?, and damped singular spectrum analysis ?.}

%The decomposition-based denoising approaches consider the disparity of the seismic signal and random noise\wen{,} and attempt to extract useful information from the principal components of the noisy data. Typical methods include the empirical-mode decomposition (EMD) and its improvements \cite[]{chenwei2017emd}, singular value decomposition (SVD)-based approaches \cite[]{yatong2017ieee}, regularized non-stationary decomposition \cite[]{guoning2018}, the Cadzow filtering \cite[]{cadzow1988}, singular spectrum analysis (SSA) \cite[]{ssa,curveletieee2016,amir2017ieee}, multichannel singular spectrum analysis (MSSA) \cite[]{mssa}, and damped singular spectrum analysis \cite[]{weilin2016dmssa}.

Most of the aforementioned denoising algorithms are only effective for Gaussian-type noise. \dlo{The }Gaussian-type noise is usually easy to deal with by a transform-domain thresholding filter based on the least-squares criterion. \old{Erratic noise is also widely seen in many seismic datasets, which, however, is not easy to attenuate using a traditional denoising method.}\new{Erratic noise is also widely seen in many seismic datasets, but is not easy to attenuate using a traditional denoising method.} \dlo{The erratic}\wen{Erratic} noise is often caused by \dlo{a }power line\wen{s}, air blast\wen{s}, cultural noise, polarity reversals, poorly coupled geophones, recording and parity errors, wind, extreme weather conditions, etc \cite[]{trickett2012robust}. The most traditional method to attenuate \dlo{the }erratic noise is by first detecting the abnormal amplitudes and then correcting the amplitudes of the noise positions by interpolation or \dlo{proper }attenuation \cite[]{anderson1989automatic,schonewille2008swell}. A more convenient method is to directly suppress both erratic noise and Gaussian-type noise \dlo{by}\wen{in} a single step. In the past decade, some researchers have realized the necessity in developing algorithms specifically for erratic noise. Some robust denoising algorithms have been developed recently in the literature, such as the robust rank-reduction method \cite[]{chen2014robust} and robust principal component analysis \cite[]{candes2011robust}. The robust rank-reduction method substitutes the least-squares misfit with a more robust misfit function, such as the Tukeys bisquare function \cite[]{beaton1974fitting} or \wen{Huber function \cite[]{huber1964robust,sacchi1997reweighting}}. Both criteria can be connected with \wen{an} L1-norm misfit function to deal with the erratic noise effectively and can be solved with a classic L1 solver. In this way, the robust rank-reduction method is capable of estimating the signals when weakening the influence of \wen{the} erratic noise.  The robust \wen{principal-component} analysis method assumes that the useful signals are of low rank and the erratic noise is sparse. It is possible to construct a convex optimization problem for simultaneously obtaining the low-rank component, i.e., the signal, and the sparse erratic noise. \cite{chen2017robust} further developed an effective method to simultaneously remove erratic and random noise. The estimation of the prediction error filter and the additive noise\old{ sequence} are performed in an alternating fashion. First, the additive noise \old{sequence }is fixed, and the prediction error filter is estimated via the least-squares solution of a system of linear equations. Then, the prediction error filter is fixed, and the additive noise\old{ sequence} is estimated through a cost function containing a hybrid l1/l2-norm that prevents erratic noise to influence the final solution.

\dlo{However, computing}\wen{Computing} these robust criteria requires solving several optimization problems that are highly non-linear \dlo{and}\wen{which} is usually computationally expensive.  \cite{wong2017matrix} theoretically constructed a pseudodata and used the pseudodata to transform a minimization problem with a robust criterion into \dlo{some }well-known minimization problems that can be more easily solved \cite[]{zhaoqiang2018}. This general method has \dlo{a }great potential for transforming a variety of methods into their robust counterparts.  \dlo{Following  ?, we propose a robust version of a traditional sparsity-promoting filtering. To deal with the extremely strong erratic noise, we introduce an extra filtering operator to constrain the pseudodata that helps transform a non-robust minimization problem to a robust one. We apply \dlo{a powerful}\wen{an effective} median filter using a space-varying window size following the morphological pattern of the seismic events to constrain the erratic noise to be in the noise sections.} \wen{Following  \cite{wong2017matrix} and \cite{zhaoqiang2018}, we propose a more effective method to denoise seismic data that contain both erratic and random noise by applying a powerful structure-oriented space-varying median filter \cite[]{sosvmf} \old{into}\new{within} the iterative curvelet thresholding framework \cite[]{zhaoqiang2018}.}

In the proposed algorithm workflow, the \dlo{proposed}\wen{structure-oriented space-varying} median filtering method makes it unnecessary to use a large threshold for the curvelet method and thus makes the whole framework more flexible and reliable. Without the median filtering step, one needs to increase the threshold in the curvelet domain to constrain the erratic noise, thereby removing \dlo{a significant amount of }useful signals. We organize the paper as follows: we first \dlo{introduce}\wen{review} the robust inversion model for noise suppression that we use to suppress both Gaussian-type random noise and erratic noise. \dlo{Then, we introduce in detail a new type of median filter to constrain the pseudodata.}\wen{Then, we review a median filtering technique recently proposed by \cite{sosvmf}. We propose to use this filter to constrain the pseudodata.} Next, we comprehensively analyze the effectiveness and performance of the proposed method over both synthetic and real data examples\dlo{. Finally, some conclusions are made in the end}\wen{, before drawing some conclusions}.
%Some robust denois- ing methods considering erratic noise have been proposed in the past few years, such as robust principal component analysis [56] and robust reduced rank filtering [27], [57]–[61]. The robust principal component analysis supposes that the original data are the superposition of a noisy low-rank signal and a sparse erratic noise. Under this assumption, it is possible to recover both the low-rank and the sparse components exactly from random and erratic noise by solving a very convenient convex problem. Robust reduced rank filtering replaces the sensitive LS criterion by a robust criterion, such as Huber function [62] or Tukeys bisquare function [63]. Those robust criteria combine robust L1-norm treatment of a large erratic noise with Gaussian L2-norm treatment of a random noise [64], and can effectively weaken the influence of erratic noise during denoising. However, this approach suffers from a limitation for real signal in terms of the curve wavefronts that easily violate the low-rank assumption.
\section{Theory}
\wen{\subsection{Robust inversion}
%\subsection{Robust inversion model for noise suppression}
\old{A}\new{An} \wen{$L_1$-norm regularized} least-squares estimate for denoising can be expressed as:
\begin{equation}
\label{eq:ls}
\hat{\mathbf{m}} = \arg \min_{\mathbf{m}} \parallel \mathbf{d} - \mathbf{m} \parallel_2^2 + \gamma \parallel \mathbf{R}(\mathbf{m}) \parallel_1,
\end{equation}
\wen{where $\mathbf{d}$ and $\mathbf{m}$ denote the noisy data and denoised data, respectively, $\mathbf{R}$ is a regularization operator, and $\hat{\mathbf{m}}$ refers to the estimated model.} $\gamma$ is a tradeoff parameter that \dlo{compromise}\wen{compromises} the weight between the data misfit and model constraint.}

\wen{When erratic noise exists, a \dlo{huber}\wen{Huber} norm is better for the denoising problem \wen{\cite[]{wong2017matrix}}:
\begin{equation}
\label{eq:ls2}
\hat{\mathbf{m}} = \arg \min_{\mathbf{m}} \rho_c(\mathbf{d} - \mathbf{m}) + \gamma \parallel \mathbf{R}(\mathbf{m}) \parallel_1,
\end{equation}
where $\rho_c$ denotes the Huber norm. The Huber norm can be expressed as:
\wen{
\begin{equation}
\label{eq:huber}
\rho_c(y) = \left\{\begin{array}{ll}
\frac{1}{2} y^2 & |y|\le c,\\
c(|y|-\frac{1}{2}c) & |y|> c.
\end{array}
\right.
\end{equation}}
The idea of \dlo{constrained }pseudodata is inspired by the robust algorithm proposed in \cite{Oh2007}, where the concept of \emph{theoretical pseudodata} was proposed to transform a \wen{non-linear} optimization problem into a linear least-squares problem. \wen{The pseudodata is a temporary variable during the inversion process, and will be detailed later.} It is \dlo{easy to derive}\wen{easily derived} that, by substituting the raw data $\mathbf{d}$ with the pseudodata $\mathbf{p}$, the subgradient of the objective function with respect to $\mathbf{m}$ in optimization problem \ref{eq:ls} can be expressed as:
\begin{equation}
\label{eq:g1}
g_1=-2(\mathbf{p} - \mathbf{m}) + \gamma \partial_{\mathbf{m}} \parallel \mathbf{R}(\mathbf{m}) \parallel_1,
\end{equation}
where $\partial_{\mathbf{m}}$ denotes the partial derivative with respect to $\mathbf{m}$.}

\wen{Similarly, the subgradient of the objective function in optimization problem \wen{\ref{eq:ls2}} can be expressed as:
\wen{\begin{equation}
\label{eq:g2}
g_2=-\psi_c(\mathbf{d} - \mathbf{m}) + \gamma \partial_{\mathbf{m}} \parallel \mathbf{R}(\mathbf{m}) \parallel_1.
\end{equation}}
\wen{Here, $\psi_c$ denotes the derivative of $\rho_c$.} It is straightforward to derive that \wen{the} two subgradients expressed in \ref{eq:g1} and \ref{eq:g2} are equivalent when:
\wen{\begin{equation}
\label{eq:pseudo0}
\mathbf{p} = \mathbf{m} + \frac{1}{2}\psi_c(\mathbf{d}-\mathbf{m}).
\end{equation}}
}

\wen{$\psi_c$ denotes the derivative of the Huber criterion and can be expressed as:
\begin{equation}
\label{eq:psic}
\psi_c(y) = \left\{\begin{array}{ll}
y & |y|\le c,\\
\text{sign}(y)c &|y|>c.
\end{array}\right.
\end{equation}
\old{The symbol $\mathbf{S}$ denotes a constraining operator to ensure that no erratic noise exists in the pseudodata. In this paper, we propose to use a new type of median filter to filter out the spike-like noise. }The tuning parameter $c$ in equation \ref{eq:psic} can be empirically set as \wen{\cite[]{huber1964robust}}:
\begin{equation}
\label{eq:c}
c=1.345\sigma,
\end{equation}
where $\sigma$ is the approximated standard deviation of the Gaussian-type random noise. Following \cite{holland1977robust}, a robust estimate of $\sigma$ can be chosen as: 
\wen{\begin{equation}
\label{eq:sigma}
\sigma\approx \frac{\text{MAD}}{0.6745} = \frac{\text{Median}|x-\text{Median}(x)|}{0.6745}, 
\end{equation}}
\wen{where MAD denotes median absolute deviation.}}

\wen{\subsection{Iterative curvelet method}
\cite{zhaoqiang2018} proposed to apply the curvelet transform as the regularization operator, i.e., $\mathbf{R}=\mathbf{A}$. $\mathbf{A}$ denotes the curvelet transform. Then the robust inversion model is modified as:
\begin{equation}
\label{eq:ls22}
\hat{\mathbf{m}} = \arg \min_{\mathbf{m}} \rho_c(\mathbf{d} - \mathbf{m}) + \gamma \parallel \mathbf{A}\mathbf{m} \parallel_1.
\end{equation}
Equations \ref{eq:pseudo0} indicates that the minimization of the robust sparsity-promoting denoising model \dlo{equals}\wen{is equivalent} to the case when the input of \wen{a} conventional sparsity-promoting denoising model is a pseudodata expressed in equation \ref{eq:pseudo0}. The pseudodata serves as a bridge to solve a non-linear optimization problem via a linear solver. It is especially advantageous because a number of existing (non-robust) methods can be transformed to their robust counterparts for suppressing erratic noise.}

With $\mathbf{p}$ free of erratic noise, it is possible to use the least-squares model expressed in equation \ref{eq:ls} to remove the Gaussian-type random noise:
\begin{equation}
\label{eq:ls22}
\hat{\mathbf{m}} = \arg \min_{\mathbf{m}} \parallel \mathbf{p} - \mathbf{m} \parallel_2^2 + \gamma \parallel \mathbf{A}\mathbf{m} \parallel_1.
\end{equation}
This denoising problem can be solved simply by a thresholding step:
\begin{equation}
\label{eq:dn}
\hat{\mathbf{m}} = \mathbf{A}^{-1} \mathbf{T}_w \mathbf{A} \mathbf{p},
\end{equation}
where $\mathbf{A}^{-1}$ denotes the inverse sparse transform. $\mathbf{T}_w$ denotes a thresholding operator with an input threshold parameter $w$. The default choice of $w$ is the standard deviation $\sigma$ as approximated in equation \ref{eq:sigma}. In practice, $w$ can be adjusted several times in order to obtain the best performance. It also depends on the \old{sparsity degree}\new{degree of sparsity} in the transform domain. The algorithm formulated as equation \ref{eq:dn} is referred to as the curvelet thresholding method, which will be used in the benchmark comparison in the section of \dlo{EXAMPLES}\wen{examples}. To deal with the erratic noise, equation \ref{eq:ls} is solved iteratively by combining the pseudodata transformation expressed in equation \ref{eq:pseudo0} and the curvelet thresholding method expressed in equation \ref{eq:dn}. This iterative method is referred as the iterative curvelet method \cite[]{zhaoqiang2018}.

\subsection{Structure-oriented space-varying median filter}
Because seismic data is spatially correlative, the traditional median filter needs to be applied in the horizontal dimension of a 2D seismic data for rejecting the spiky erratic noise.  A traditional median filter, however, tends to damage signal energy when the seismic event is dipping. A better way to use the median filter is to apply it along the structural direction of seismic events. To apply the median filter along the structural direction, one needs to extract a 1D vector from the dipping seismic event for the 1D filtering of a median filter. This process is equivalent to flattening the curved seismic events so that the 1D median filter is used easily in the space direction of the flattened gather.

A critical part in the structure-oriented filtering is the creation of the flattened gather  \wen{in the time-space domain}. %\wen{The flattening process is closely related with the plane-wave destruction operation, which can be expressed briefly as
%\begin{equation}
%  \label{eq:pwd}
%  \mathbf{r} = \mathbf{D(\sigma)\,s},
%\end{equation}
%where $\sigma$ denotes the local slope map, $\mathbf{r}$ is the residual of the plane-wave destruction operation, and $\mathbf{D}$ denotes the plane-wave destruction operator. Equation \ref{eq:pwd} can be formulated as a matrix-vector form:
%\begin{equation}
%  \label{eq:d}
%  \left[\begin{array}{c}
%     \mathbf{r}_1 \\
%     \mathbf{r}_2 \\
%     \mathbf{r}_3 \\
%        \cdots \\
%     \mathbf{r}_N  \\
% \end{array}\right] =
%  \left[\begin{array}{ccccc}
%      \mathbf{I} & 0 & 0 & \cdots & 0 \\
%      - \mathbf{P}_{1,2}(\sigma_1) & \mathbf{I} & 0 & \cdots & 0 \\
%      0 & - \mathbf{P}_{2,3}(\sigma_2) & \mathbf{I} & \cdots & 0 \\
%      \cdots & \cdots & \cdots & \cdots & \cdots \\
%      0 & 0 & \cdots & - \mathbf{P}_{N-1,N}(\sigma_{N-1}) & \mathbf{I} \\
%    \end{array}\right]
%  \left[\begin{array}{c}
%     \mathbf{s}_1 \\
%     \mathbf{s}_2 \\
%     \mathbf{s}_3 \\
%        \cdots \\
%     \mathbf{s}_N  \\
% \end{array}\right]\;,
%\end{equation}
%where $\mathbf{I}$ is an identity operator, $\sigma_i$ denotes the $i$th local slope corresponding to $i$th trace, $\mathbf{s}_i$ denotes the $i$th seismic trace, and $\mathbf{P}_{i,i+1}(\sigma_i)$ denotes the operator that predicts trace $i+1$ from $i$. Prediction between two neighbor traces are achieved by shifting one of the two traces according to the local slope of seismic events. By minimizing equation \ref{eq:d}, the local slope map $\sigma$ can be obtained.}
%
\wen{We do the flattening via recursive prediction between seismic traces based on the estimated local slope.} Assuming that the flattened gather for filtering has a width of $2N+1$,  an arbitrary trace $\mathbf{x}_i$ can be predicted following the equation:
%the central trace $\mathbf{x}_i$ can be predicted from its $j$th ($j\le N$) right trace $\mathbf{x}_{i+j}$ in such a recursive manner,
\begin{equation}
\label{eq:recur}
\mathbf{x}_i=\mathbf{P}_{i+1,i}\cdots\mathbf{P}_{i+j-1,i+j-2}\mathbf{P}_{i+j,i+j-1}\mathbf{x}_{i+j}. 
\end{equation}
\dlo{where $\mathbf{P}_{i,j}$ is an operator, predicting the $i$th trace from the $j$th trace}\wen{Here, $\mathbf{P}_{i,i+1}(v_i)$ is briefly denoted as $\mathbf{P}_{i,i+1}$, where $v$ denotes the local slope at trace $i$}. A similar way can be used to recursively predict $\mathbf{x}_i$ from its left traces by:
\begin{equation}
\label{eq:recur}
\mathbf{x}_i=\mathbf{P}_{i-1,i}\cdots\mathbf{P}_{i-j+1,i-j+2}\mathbf{P}_{i-j,i-j+1}\mathbf{x}_{i-j}. 
\end{equation}

Figure \ref{fig:demo} demonstrates how to construct a structural gather containing flattened events based on the trace prediction strategy. In this sketch, $N=1$. It is obvious that a curved seismic event can be transformed into a flattened event and then the 1D median filter can be used to effectively reject erratic noise in the flattened domain. More details regarding the flattening can be found in \cite{liuyang2010}.

However, the structure-oriented filtering strategy requires the estimation of \wen{the} local slope of an input seismic profile. The challenge in the structure-oriented processing is that we need to obtain a sufficiently accurate slope field for creating \wen{well-flattened} local gathers \cite[]{sosvmf}. In seismic data with strong noise, especially with erratic noise, an accurate slope is difficult or even impossible to obtain.  When \wen{an} inaccurate local slope is obtained, the flattened gather will still contain curved events, which further results in inevitable damages to signals caused by a 1D median filter. In such \dlo{a }case, \dlo{we propose to apply}\wen{\cite{yangkang2015svmf} proposed to use} a space-varying median filter to attenuate the erratic noise in an approximately flattened gather without damaging the useful signals. The filter length $L$ is spatially variable in a space-varying median filter \cite[]{yangkang2015svmf}:
\wen{\begin{equation}
\label{eq:svmf1}
\hat{v}_{i,j}=\arg \min_{v_{m}\in U_{i,j} }\sum_{l=1}^{L_{i,j}} \Arrowvert v_{m} -v_l \Arrowvert_1,
\end{equation}}
where $\hat{v}_{i,j}$ is the output for position $x_{i,j}$. $U_{i,j}=\{v_1,v_2,\cdots,v_{L_{i,j}}\}$ corresponds to a local window for the 1D median filtering.
The spatially variable filter length $L_{i,j}$ can be adaptively chosen as:
\begin{equation}
\label{eq:svmf3}
L_{i,j}=\left\{\begin{array}{ll}
L+l_1,\quad 0\quad \le |x^L_{i,j}|\le T/2 \\
L+l_2,\quad T/2\quad <|x^L_{i,j}|\le T \\
L-l_3,\quad T \quad \le|x^L_{i,j}| < 2T\\
L-l_4,\quad |x^L_{i,j}| \ge 2T
\end{array}\right.,
\end{equation}
where $x^L_{i,j}$ denotes the initial signal estimate at position $x_{i,j}$, which is obtained by applying a median filter (with constant filter length $L$). $T$ denotes the average absolute value of the initial signal estimate. \wen{The variable filter length can better preserve the dipping signal energy since a larger filter length is more powerful in rejecting spiky noise but will damage more signal energy while a smaller filter length is less powerful but more amplitude-preserving, especially for dipping seismic events. The criteria for selecting the window parameters $l_1=2$, $l_2=0$, $l_3=2$, and $l_4=4$, are exactly the same as introduced in \cite{liuyang2009tvmf}. }\wen{It is worth noting that we iteratively calculate the slope and update the input slope for the structure-oriented filtering during the inversion.}

Figure \ref{fig:hyper,hyper-n,hyper-mf0,hyper-sosvmf0,hyper-mf-n,hyper-sosvmf-n} shows a synthetic test of the \dlo{proposed}\wen{enhanced} median filter on a synthetic dataset with hyperbolic events. 
Figures \ref{fig:hyper} and \ref{fig:hyper-n} show the clean and noisy data. Figure \ref{fig:hyper-mf0} and \ref{fig:hyper-sosvmf0} shows the denoising results using the enhanced median filter proposed in \cite{sosvmf}. Correspondingly, Figures \ref{fig:hyper-mf-n} and \ref{fig:hyper-sosvmf-n} show the removed noise. It is clear that the median filtering method proposed by \cite{sosvmf} obtains a successful preservation of seismic events while removing most of the erratic noise. The above mentioned median filter is referred as the structure-oriented space-varying median filter \cite[]{sosvmf}, which will also be used in the benchmark comparison in the section of \dlo{EXAMPLES}\wen{examples}.

\wen{\subsection{Robust inversion model with an extra constraining operator}
The pseudodata expressed in \ref{eq:pseudo0} depends on the initial estimates of the signal $\hat{\mathbf{m}}$ and noise $\mathbf{n}$. A better estimate of the signal helps obtain a more plausible estimate of $\mathbf{p}$. We propose to iterate the denoising procedures so that we can get the best estimate of the signal where both erratic and Gaussian-type noise are removed while useful signals \wen{remain} untouched.}

\wen{Thus, to}\dlo{To} solve the non-linear optimization problem expressed in equation \ref{eq:ls2}, we first define a \wen{constrained }pseudodata corresponding to the seismic data $\mathbf{d}$ as:
\wen{\begin{equation}
\label{eq:pseudo}
\mathbf{p} = \mathbf{S}(\hat{\mathbf{m}} + \frac{1}{2}\psi_c(\mathbf{n})),
\end{equation}}
where $\mathbf{n}=\mathbf{d}-\hat{\mathbf{m}}$ denotes the noise that corresponds to the signal estimate $\hat{\mathbf{m}}$. \old{$\mathbf{S}$ denotes a constraining operator.}\new{The symbol $\mathbf{S}$ denotes a constraining operator to ensure that no erratic noise exists in the pseudodata. In this paper, we propose to use structure-oriented space-varying median filter to filter out the spike-like noise. }

\dlo{, while} \dlo{Similarly, the subgradient of the objective function in optimization problem \wen{\ref{eq:ls2}} can be expressed as: $g_2=-\psi_c(\mathbf{d} - \mathbf{m}) + \gamma \partial_{\mathbf{m}} \parallel \mathbf{A}\mathbf{m} \parallel_1$.} \dlo{It is straightforward to derive that \wen{the} two subgradients expressed in \ref{eq:g1} and \ref{eq:g2} are equivalent when: $\mathbf{p} = \mathbf{m} + \frac{1}{2}\psi_c(\mathbf{d}-\mathbf{m})$. }
\dlo{Equations \ref{eq:g1}-\ref{eq:pseudo0} indicate that the minimization of the robust sparsity-promoting denoising model \dlo{equals}\wen{is equivalent} to the case when the input of \wen{a} conventional sparsity-promoting denoising model is a pseudodata expressed in equation \ref{eq:pseudo0}. The pseudodata serves as a bridge to solve a non-linear optimization problem via a linear solver. It is especially advantageous because a number of existing (non-robust) methods can be transformed to their robust counterparts for suppressing erratic noise. }

We follow the general framework of the robust matrix completion method developed in \cite{wong2017matrix}. However, the success of the \dlo{transformation by pseudodata}\wen{pseudodata transformation} depends on the selection of the tuning parameter shown in equation \ref{eq:psic}. The parameter $c$ makes the output value of the function $\psi_c$ restricted to $\text{sign}(x)c$, thus alleviating the influence of the outliers. The choice of $c$ is challenging as a large $c$ results in significant residual outliers (erratic noise) while a small $c$ tends to damage the energy of the useful signals. Thus, $c$ remains as an empirical parameter and may vary significantly in extreme cases. To achieve a better compromise between noise removal and signal preservation, we introduce an extra filter $\mathbf{S}$ to constrain the pseudodata, as expressed in equation \ref{eq:pseudo}. \old{With the constrained pseudodata, we can use a relatively large $c$, so that, increasing the variance estimation of Gaussian-type noise $\sigma$, and then use the constraining filter for removing the residual outliers without harming the useful signals.}\new{With the constrained pseudodata, we can use a relatively large $c$, that is, increasing the variance estimation of Gaussian-type noise $\sigma$ and then using the constraining filter for removing the residual outliers without damaging the useful signals.} \cite{zhaoqiang2018} extended this method to seismic data processing by combining the pseudodata transformation with a curvelet thresholding step. We further improve the iterative curvelet method in \cite{zhaoqiang2018} by applying an effective structure-oriented space-varying median filter\old{, which is introduced in detail in the last subsection,} to constrain the pseudodata. In the new framework, a relatively \old{larger}\new{large} $c$ ensures we preserves all signals and some erratic noise. The erratic noise can then be removed by the amplitude-preserving structure-oriented space-varying median filter. Although some signal damages caused by a relatively smaller $c$ can be retrieved during the later iterations, the mixture problem between the signal and erratic noise remains. \old{If some erratic noise has comparative energy as signals}\new{If the erratic noise has comparative energy as the signal}, then it is not possible to separate them using the simple derivative operator of Huber criterion $\psi_c$. In each iteration, the proposed method is better than the traditional method in separating the useful signals, erratic noise, and random noise, thanks to the amplitude-preserving property of the structure-oriented space-varying median filter, which results \new{in} a much better \old{overal}\new{overall} denoising performance.  Thus, selection of $c$ becomes much more convenient and the proposed algorithm framework is almost data adaptive.

\dlo{With $\mathbf{p}$ free of erratic noise, it is possible to use the least-squares model expressed in equation \ref{eq:ls} to remove the Gaussian-type random noise:
$\hat{\mathbf{m}} = \arg \min_{\mathbf{m}} \parallel \mathbf{p} - \mathbf{m} \parallel_2^2 + \gamma \parallel \mathbf{A}\mathbf{m} \parallel_1.$
This denoising problem can be solved simply by a thresholding step:
$\hat{\mathbf{m}} = \mathbf{A}^{-1} \mathbf{T}_w \mathbf{A} \mathbf{p}$,
where $\mathbf{A}^{-1}$ denotes the inverse sparse transform. $\mathbf{T}_w$ denotes a thresholding operator with an input threshold parameter $w$. The default choice of $w$ is the standard deviation $\sigma$ as approximated in equation \ref{eq:sigma}. In practice, $w$ can be adjusted several times in order to obtain the best performance.}

\dlo{However, the pseudodata depends on \dlo{an}\wen{the} initial estimates of the signal $\hat{\mathbf{m}}$ and noise $\mathbf{n}$. A better estimate of the signal helps obtain a more plausible estimate of $\mathbf{p}$. We propose to iterate the denoising procedures so that we can get the best estimate of the signal where both erratic and Gaussian-type noise are removed while useful signals \wen{remain} untouched.}

\begin{algorithm}[htb!]
   \caption{Iterative erratic noise suppression algorithm }
   \textbf{Input:} Noisy data $\mathbf{d}$, a pair of forward and inverse sparse transform $\mathbf{A}$ and $\mathbf{A}^{-1}$, a constraining operator $\mathbf{S}$.
    \begin{algorithmic}[1]
    \State \textbf{Initialize $\mathbf{m}_1$ with zero}: $\mathbf{m}_1=\mathbf{0}$
        \For{$i$ = $1,\cdots,N$}
     \State \textbf{Compute}: $\mathbf{n}=\mathbf{d}-\mathbf{m}_i$
     \State \textbf{Compute}: $\mathbf{p}=\mathbf{m}_i+\frac{1}{2}\psi(\mathbf{n})$
     \State \textbf{Compute}: $\mathbf{p}=\mathbf{S}(\mathbf{p})$
     \State \textbf{Solve}: $\mathbf{m}_{i+1}= \arg \min_{\mathbf{m}} \parallel \mathbf{p} - \mathbf{m} \parallel_2^2 + \gamma \parallel \mathbf{A}\mathbf{m} \parallel_1$
     	\If{$\parallel \mathbf{m}_{i+1} - \mathbf{m}_{i} \parallel<\epsilon$} 
     	\State	\textbf{Exit}
     	\EndIf

        \EndFor 
%         \State \textbf{1D inverse FFT}: $\hat{D}(x,t)=\text{IFFT}\left(\hat{D}(x,w)\right)$
\end{algorithmic}
   \textbf{Output:} Denoised result $\mathbf{m}_{i+1}$ and noise $\mathbf{n}=\mathbf{d}-\mathbf{m}$.
\label{alg:alg}
\end{algorithm}
Algorithm \ref{alg:alg} \old{detailed}\new{details} the complete workflow of the proposed method. In algorithm \ref{alg:alg}, $\epsilon$ denotes a convergence criterion. In this paper, we define the following convergence criterion:
\begin{equation}
\label{eq:eps}
\epsilon = C\sigma\sqrt{M},
\end{equation}
where $C$ is a gain factor fixed as 1.15 \cite[]{elad2006} and $M$ denotes the dimension of the noisy data $\mathbf{d}$. \wen{The variance} $\sigma$ is the approximated standard deviation of the Gaussian-type random noise, and can be chosen following equation \ref{eq:sigma}.

The proposed method is not simply a concatenation between a constraining operator (e.g., to remove the erratic noise) and a common random noise attenuation operator. Note that with the transformation expressed in equation \ref{eq:pseudo}, we can update the pseudodata by the current estimations of the model and rejected noise iteratively. For each update, we reformulate the denoising problem as a L1-norm regularized least-squares optimization problem, which can be solved via a standard denoising method. The key difference between the ``hybrid" method and the presented method is that the pseudodata is updated iteratively, thereby transforming the \wen{Huber}\dlo{huber}-norm regularized denoising model to L2-norm regularized denoising model. This strategy is very similar to that used in the well-known iterative re-weighted least-squares (IRLS) method \cite[]{sacchi1997reweighting}.

\dlo{The proposed framework can also be used to reconstruct missing seismic data. In the case of data reconstruction, problem \ref{eq:ls2} can be modified to:
$\hat{\mathbf{m}} = \arg \min_{\mathbf{m}} \rho_c(\mathbf{d} - \mathbf{M}\mathbf{m}) + \gamma \parallel \mathbf{A}\mathbf{m} \parallel_1$,
where $\mathbf{M}$ denotes the sampling operator. Solving the reconstruction problem follows a similar way as in the case of sole noise suppression. }

\dlo{The extension of the proposed iterative framework to the 3D version is straightforward. Since the 3D curvelet transform has been studied extensively in the literature ?, the main difficulty of the 3D extension comes from  the 3D version of the structure-oriented space-varying median filtering. The 3D structure-oriented space-varying median filtering requires the consideration of local slopes from two space directions (e.g., xline and inline) and a 2D median filter. We limit the algorithm tests and discussions in this paper to 2D problems. The 3D extension of the proposed method is now being investigated. }

\section{Examples}
In this section, a synthetic data with simulated Gaussian-type noise and erratic noise is used to \dlo{systematically }evaluate how effective the proposed method is. We also use a real pre-stack marine dataset to illustrate the performance of the proposed \wen{method} in \dlo{real-world applications}\wen{practice}. First, we need to define the metrics to evaluate the performance to quantitatively measure the denoising quality. We utilize the \dlo{SNR}\wen{signal-to-noise ratio} metric that is widely used in the literature. The definition is given as follows:
\wen{\begin{equation}
\label{eq:snr2}
\text{SNR}=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2}{\Arrowvert \mathbf{n} \Arrowvert_2},
\end{equation}}
where $\mathbf{s}$ is the vectorized signal and $\mathbf{n}$ is the vectorized noise. For denoised data, the difference between the exact solution $\mathbf{s}$ and the estimate $\hat{\mathbf{s}}$ is treated as the ``noise". Secondly, we use the local similarity metric as introduced in \wen{\cite{fomel2007localattr}} to evaluate the denoising performance in a local manner. The local similarity measures the correlation between two signals, in a local way. \dlo{For \wen{a} more detailed introduction, readers are referred to -. }\dlo{A higher}\wen{Higher} local similarity between \wen{the} exact solution and the estimate corresponds to \dlo{a }higher accuracy of the estimate, and vice versa.  We can also use the local similarity metric to evaluate the signal damages by calculating the similarity between denoised data and removed noise. A higher local similarity in this case indicates a higher level of signal leakage. This strategy is especially useful for quantifying the denoising performance of the real seismic data example, since there is no ground truth solution for real seismic data and it is \dlo{impossible}\wen{difficult} to use the SNR metric defined in equation \ref{eq:snr2}.  \wen{Thus, in this paper, we use SNR to measure the effectiveness of the methods when dealing with synthetic data and the local similarity metric when dealing with field data.}

The synthetic example is shown in Figure \ref{fig:l_dc,l_dn}. There are 501 time samples and 50 space samples. The sampling rate is 4 ms. Figure \ref{fig:l_dc} and \ref{fig:l_dn} display the noise-free and noise-corrupted data, respectively. There are four linear events in the data. \dlo{Then noisy}\wen{Then, the noise-free} data is corrupted by both Gaussian-type random noise and erratic noise (with \dlo{obviously }strong amplitude). The SNR for the noisy data is -1.25 dB. Figure \ref{fig:l_d} shows a comparison of four denoised results using four different methods. Figure \ref{fig:l_curv} shows the result from a classic curvelet thresholding method \wen{\cite[]{candes20061}}. Figure \ref{fig:l_sosvmf} shows the result from the single-step median filtering method \wen{\cite[]{sosvmf}}. Figure \ref{fig:l_curvi} displays the result from the curvelet method when applied iteratively \wen{\cite[]{zhaoqiang2018}}. Figure \ref{fig:l_sosvmfi} plots the result from the proposed method. The result from the proposed method (Figure \ref{fig:l_sosvmfi}) is obtained after 8 iterations. The result from the iterative curvelet method (Figure \ref{fig:l_curvi}) is obtained after 4 iterations, since more iterations will make the inversion unstable because of the strong erratic noise. The threshold in the curvelet-related methods \wen{(i.e., curvelet method, iterative curvelet method, and the proposed method)} is set as the default value, which is the standard deviation of $\sigma$ as approximated in equation \ref{eq:sigma}. The window length for the median filtering related methods is 9 points. Comparing the four results in Figure \ref{fig:l_d}, it is clear that both curvelet method and iterative curvelet method fail in removing all the high-amplitude erratic noise since there is still some residual erratic noise (especially in the 10th, 19th, 31st traces). The result from the simple median-filtering method does not contain obvious erratic noise but still contains a significant amount of residual Gaussian-type random noise. The result from the proposed method \dlo{obviously }outperforms all the other three methods. The SNRs of the four results are 7.37 dB for the curvelet method, 5.81 dB for the single-step median filtering method, 8.55 dB for the iterative curvelet method, and 9.61 dB for the proposed iterative method. \old{The SNRs of different dataset is also listed in Table \ref{tbl:table1}.}
%\begin{table}[h]
%\caption{SNRs of different method. Curvelet I means direct curvelet thresholding. SOSVMF means single-step median filtering method. Curvelet II means iterative curvelet thresholding.}
%\begin{center}
%    \begin{tabular}{|c|c|c|c|c|c|} 
%  \hline Noisy  & Curvelet I  & SOSVMF & Curvelet II  & Proposed\\ 
%  \hline -1.25 dB & 7.37 dB  & 5.81 dB  & 8.55 dB &  9.61 dB \\
%      \hline
%   \end{tabular} 
%\end{center}
%\label{tbl:table1}
%\end{table}
Figure \ref{fig:l_d_n} shows a comparison of noise removal for all four methods. The removed noise using \dlo{both curvelet-related methods}\wen{curvelet method and iterative curvelet method both} contain some \dlo{useful}\wen{signal} energy from the first dipping event. The removed noise using the proposed median filtering method is obviously weaker than that of the other three methods, especially around the positions of the four linear events. It is also discernible that there are some damages to the signals around the crossing point of the first two seismic events. The noise removed from the proposed method, however, is as strong as the \dlo{curvelet-related}\wen{curvelet and iterative curvelet} methods but does not \old{contains}\new{contain} any observable signal energy. In order to see the iteratively estimated clean signal during iterations, we plot the estimated signals after 1, 3, 5, and 7 iterations in Figure \ref{fig:l_ds}. From Figure \ref{fig:l_ds}, we can observe that the denoised data is getting cleaner and cleaner\old{, and with the amplitude of the first seismic event stronger and stronger}\new{, and that the ampltiude of the first seismic event is gettting stronger and stronger}. This observation can be confirmed from Figure \ref{fig:l_ns}, where the corresponding noise removals are plotted. From Figures \ref{fig:l_n_1} (after 1 iteration) to \ref{fig:l_n_7} (after 7 iterations), we can see clearly that the signal energy corresponding to the first event is getting weaker and weaker. In Figure \ref{fig:l_n_7}, the loss of useful energy is \dlo{barely seen}\wen{significantly less}.

\dlo{The proposed median filter is insensitive to the input slope map.}\wen{The proposed median filter is insensitive to strong variations in the slope map.} The main computational cost of structure-oriented space-varying median filter comes from calculation of the local slope, trace prediction and local similarity calculation required by space-varying median filter in each flattened local gather \cite[]{sosvmf}. \dlo{All these extra computational steps can be implemented via efficient algorithms based on shaping regularization ?, thus the application of this structure-oriented space-varying median filter is not expensive.} The slopes calculated from the noise-free and the noisy data are plotted in \wen{Figures \ref{fig:l_dip_dc} and \ref{fig:l_dip_dn}.} It is clear that the exact solution of \wen{the} local slope is very smooth and correlates \new{well} with the positions of the four seismic events\old{ very well}. The slope calculated from the noisy data, as shown in Figure \ref{fig:l_dn}, however, is highly oscillating and irregular. However, we use the practical slope calculated from the noisy data for the structure-oriented space-varying median filtering and the performance is still \dlo{successful}\wen{excellent}. It is worth mentioning that if we use a traditional structure-oriented space-varying median filtering method, the performance will highly \dlo{depends}\wen{depend} on the input slope map, which is very inaccurate in this example. We iteratively calculate the slope and update the input slope for the structure-oriented filtering during the inversion. The calculated slopes after 1, 3, 5, and 7 iterations are shown in Figure \ref{fig:l_dips}. From (a) to (b) in Figure \ref{fig:l_dips}, it is clear that the \dlo{slope}\wen{slopes} \dlo{becomes}\wen{become} smoother\dlo{ and smoother} and more accurate \dlo{as}\wen{when} compared with the exact solution in Figure \ref{fig:l_dip_dc}. \dlo{\dlo{But the}\wen{The} slope calculated after \dlo{7}\wen{seven} iterations is much better than the original input slope in Figure \ref{fig:l_dip_dn}, but is still a bit different \dlo{with}\wen{compared to} the exact solution.} We iteratively calculate the SNRs during the inversion and show the SNR diagram in Figure \ref{fig:l_snrs4}. In the first \dlo{6}\wen{six} iterations, the SNR increases from less than 6 dB of the initial estimate to around 10 dB. After \dlo{even}\wen{the} first iteration, the SNR has a dramatic change. After \dlo{6}\wen{six} iterations, however, the SNR goes through a small drop, which is explained by the fact that the proposed iterative \dlo{retrive}\wen{procedure retrieves} useful signals back from the removed noise while also \dlo{getting }\wen{re-introducing }some Gaussian-type noise\dlo{ back}. Although SNR decreases, the overall performance actually keeps increasing, as confirmed from the \dlo{iteratively}\wen{iterative} output results plotted in Figures \ref{fig:l_ds} and \ref{fig:l_ns}.

\wen{In Figure \ref{fig:l_dds}, we show iteratively obtained}\dlo{We also show iteratively obtained} results using the curvelet method, i.e., iteration without applying the proposed median filter as a constraining operator\dlo{, in Figure \ref{fig:l_dds}}. Figures \ref{fig:l_dds}a-\ref{fig:l_dds}d correspond to the output result after 1, 3, 5, and 7 iterations, respectively. From this comparison, we see that in the first 3 iterations, the iterative curvelet method is still stable, \dlo{then}\wen{following this} the iterative method becomes unstable because we iteratively retrieve the high-amplitude erratic noise from the noise profile without constraint to suppress the erratic noise. The corresponding noise profiles are shown in Figure \ref{fig:l_nns}, where we see that the removed noise becomes \dlo{weaker and weaker, indicating the fact that the iteration becomes less and less effective}\wen{weaker, indicating that progressive iterations become less effective}. The SNR comparison can only provide a global evaluation of the denoising performance. We then use the local similarity to evaluate the denoising performance\dlo{ locally}. The local \dlo{similar}\wen{similarity} maps between the noise-free data and the denoised data using different methods are shown in Figure \ref{fig:l_simi}. The high anomalies on the local similarity maps correlate with the seismic events very well. However, the amplitude of the local similarity anomaly is different for the four methods. While all the methods except for the proposed method have similar local similarity, the proposed method obtains \dlo{obviously }higher similarity values. To measure the signal leakages \cite[]{yangkang2015ortho}, the local similarity between the denoised data and removed noise for different methods are then calculated and shown in Figure \ref{fig:l_simi2}. It is clear that both \dlo{curvelet-related}\wen{curvelet and iterative curvelet} methods have some high similarity anomalies along the first seismic event, indicating the signal leakage of the first seismic event. The local similarity of the single-step median filtering method shows \dlo{obvious }high anomalies in the middle part of the profile. It is \dlo{salient}\wen{clear} that the local similarity corresponding to the proposed method is mostly zero and negligible across the whole profile. In order to test the denoising performance of different noise levels, e.g., in terms of random noise intensity and erratic noise density, we further conduct two tests. The first test is to explore the denoising performance of the proposed method in the cases of different noise intensities. We increase the noise variance gradually and apply the proposed method to compare the denoising performance. This test is illustrated in Figure \ref{fig:sigmas_d}. The top row of Figure \ref{fig:sigmas_d} show the noisy data with the same erratic noise but with increasing random noise intensity. The bottom row of Figure \ref{fig:sigmas_d}  shows the \old{correspondingly}\new{corresponding} removed noise sections. It is clear the denoising performance decreases as the noise variance increases. The denoising performance in the case of the strongest random noise is still acceptable, except for relatively more residual noise. Next, we conduct a similar test in terms of different erratic noise densities. This test is illustrated in Figure \ref{fig:dens_d}. The top row of Figure \ref{fig:dens_d} shows the noisy data with the same random noise but with increasing erratic noise density. The bottom row of Figure \ref{fig:dens_d} shows the \old{correspondingly}\new{corresponding} removed noise. It is obvious that the denoising performance decreases as the erratic noise density increases. When the erratic noise is the most dense, there is some residual noise in the result, but the general performance is still acceptable. These two tests show that the proposed method could perform robustly in cases when noise levels are high.

We further test the proposed method on a real seismic data as shown in Figure \ref{fig:f_dn}. This dataset is a \dlo{marin}\wen{marine} pre-stack shot gather, which contains both Gaussian-type random noise and erratic noise. There are 800 time samples and 220 space samples. The sampling rate is 4 ms. The results from the four aforementioned methods are shown in Figure \ref{fig:f_d}. From Figure \ref{fig:f_d}, it is clear that \dlo{both curvelet-related methods}\wen{both curvelet and iterative curvelet methods} have successfully \dlo{attenuate}\wen{attenuated} the Gaussian-type random noise but fail in \dlo{rejecting}\wen{removing} \dlo{those}\dlo{the}\wen{all} erratic noise. The iterative curvelet method seems to suppress more erratic noise than the simple curvelet thresholding method. The proposed median filter, although \wen{successfully rejecting} all the erratic noise, fails in attenuating much \wen{of} Gaussian-type random noise. The proposed method, as shown in Figure \ref{fig:f_sosvmfi_n}, obtains a very satisfying result with both \wen{the} Gaussian-type random noise and erratic noise effectively removed. In this example, both iteration-related methods use 8 iterations to obtain the result. The given window length for the median filters are both 9 points. A comparison of the removed noise profiles is shown in Figure \ref{fig:f_d_n}. It is obvious that both \dlo{curvelet-related}\wen{curvelet and iterative curvelet} methods tend to cause significant signal leakage.  The median filtering-related methods are very effective in preserving all the useful signals. \wen{However, it seems that the single-step median filtering removes less noise, compared with the proposed method.} Figure \ref{fig:f_ds} shows a comparison of \dlo{iteratively output}\wen{the iterative output} result after 1, 3, 5, and 7 iterations. It is clear that the high-amplitude erratic noise is well constrained during the iterations due to the effectiveness of the proposed median filter, and the amplitude of \wen{the} useful signals \dlo{becomes higher and higher}\wen{becomes progressively higher}. This observation can be further validated from the comparison of removed noise profiles during iterations in Figure \ref{fig:f_ns}. From (a) to (d) in Figure \ref{fig:f_ns}, it is clear that the signal leakage is gradually \dlo{retrieved}\wen{reduced} and the noise profile after 7 iterations \dlo{is almost not containing}\wen{contains almost no} discernable signal energy. In this example, because the exact solution for the noise-free data is unknown, we cannot use the SNR for evaluating the denoising performance. In this case, the local similarity is used to measure the signal damages of \wen{the} different methods. Here, we want to emphasize again that based on a similar level of removed noise, the local similarity can help measure how a method can preserve\dlo{/damage} the useful signals by simply checking the \dlo{high-anomalies}\wen{high-amplitude anomalies} in the similarity maps. The local similarity maps are plotted in Figure \ref{fig:f_simi2}, where we can observe that \dlo{both curvelet-related}\wen{both curvelet and iterative curvelet} methods cause significant signal leakages around the right side of the first arrivals. The single-step median filtering causes some damages in the areas around the first arrival. The proposed method does not cause observable signal leakage, indicating \dlo{a }\dlo{perfect}\wen{a very good} preservation of \wen{the} useful signals.

Next, we test the proposed method on another real data example, which is a post-stack seismic data. The raw data is plotted in Figure \ref{fig:f2_d}. There are 256 time samples and 256 space samples. The sampling rate is 4 ms. This example contains very strong string-like erratic noise and moderately strong Gaussian-type random noise.  The four results using four different methods are plotted in Figures \ref{fig:f2_curv}-\ref{fig:f2_sosvmfi}. The removed noise sections corresponding to different methods are plotted in Figure \ref{fig:f2_d_n}. The red arrows highlight the differences among the four methods. As emphasized by the red arrows, both \dlo{curvelet-related}\wen{curvelet and iterative curvelet} methods damage significant signal energy while the median filter-related methods preserve the useful signals well. Compared with the single-step filters, the two iterative methods remove more noise. Although the iterative curvelet method seems to be cleaner, \old{however, }it causes significant damages to the useful signals, as highlighted in Figure \ref{fig:f2_curvi}. \wen{It is also observable that the proposed method causes a few sporadic residual spikes. Considering the overall performance, these spikes are negligible.} It is intuitive that noise removal and signal preservation are always a compromise. \old{The traditional median filter is not as competent as the structure-oriented space-varying median filter in compromising the two things.}\new{The structure-oriented space-varying median filter better defines the tradeoff between the two than the traditional median filter.} Besides, the structure-oriented space-varying median filter \cite[]{sosvmf} \old{is more convenient to adapt}\new{more readily adapts} to the complexity of the input seismic data. More importantly, it is used in a data-driven way, i.e., insensitive to the noise levels or structural complexity (as elaborated in \cite{sosvmf}).

\section{Discussions}
\wen{The extension of the proposed iterative framework to the 3D version is straightforward. Since the 3D curvelet transform has been studied extensively in the literature \cite[]{ying20053d,jingjie2015jse}, the main difficulty of the 3D extension comes from  the 3D version of the structure-oriented space-varying median filtering. The 3D structure-oriented space-varying median filtering requires the consideration of local slopes from two space directions (e.g., xline and inline) and a 2D median filter. We limit the algorithm tests and discussions in this paper to 2D problems. The 3D extension of the proposed method is now being investigated. }

The proposed framework can also be used to reconstruct missing seismic data. In the case of data reconstruction, problem \ref{eq:ls2} can be modified to:
\begin{equation}
\label{eq:ls_recon}
\hat{\mathbf{m}} = \arg \min_{\mathbf{m}} \rho_c(\mathbf{d} - \mathbf{M}\mathbf{m}) + \gamma \parallel \mathbf{A}\mathbf{m} \parallel_1,
\end{equation} 
where $\mathbf{M}$ denotes the sampling operator. Solving the reconstruction problem follows a similar \old{way as in the case of sole noise suppression}\new{approach as the noise suppression problem}.

The proposed framework is more capable of compromising \new{between} the removal of erratic and random noise, and preservation of signal energy, thanks to the \old{superb amplitude-preserving  performance}\new{amplitude preservation} offerred by the structure-oriented space-varying median filtering. \old{The amplitude preserving property enables the proposed method useful for the amplitude-variation-with-offset analysis.}

\section{Conclusions}|

Most traditional denoising methods designed for Gaussian-type random noise may fail if the seismic data is also corrupted by erratic noise. To resolve this problem, in this paper, we combine the methods of \cite{wong2017matrix}, \cite{zhaoqiang2018} and \cite{sosvmf}. The general idea of pseudo-data transformation was from \cite{wong2017matrix}. Then, \cite{zhaoqiang2018} improved \cite{wong2017matrix}'s method by introducing the curvelet method. Next, we further improve \cite{zhaoqiang2018}'s method by introducing \old{a more }\new{an} advanced median filtering method \new{\cite[]{sosvmf}} to better cope with the structural complexity. On the other hand, the proposed method in this paper improves the structure-oriented space-varying median filtering method \cite[]{sosvmf} by better coping with the random noise. The proposed approach is tested on a synthetic and two real seismic data containing strong erratic noise. The comparison between the proposed method with traditional curvelet thresholding method, iterative curvelet method, and single-step median filtering method demonstrates the better performance of the new algorithm in separating useful signals, erratic noise, and random noise.

\section{Acknowledgements}
The research is supported by the Starting Funds from Zhejiang University. The authors are \dlo{appreciated}\wen{thankful} to Ke Chen and two anonymous reviewers for constructive comments.

\section{DATA AVAILABILITY STATEMENT}
All data included in this study are available upon request by contact with the corresponding author.

%\inputdir{test}
%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
%\multiplot{2}{test1,test2}{width=0.45\textwidth}{(a) Caption a. (b) Caption b.}

\bibliographystyle{seg}
\bibliography{noise}

\AtEndDocument{
\begin{figure}[htb!]
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/demo}
	\caption{Demonstration of the structural flattening process in structure-oriented filtering.}
	\label{fig:demo}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.32\textwidth]{hyper/Fig/hyper}
    \label{fig:hyper}}
    \subfloat[]{\includegraphics[width=0.32\textwidth]{hyper/Fig/hyper-n}
    \label{fig:hyper-n}}
	\subfloat[]{\includegraphics[width=0.32\textwidth]{hyper/Fig/hyper-mf0}
    \label{fig:hyper-mf0}}\\
    \subfloat[]{\includegraphics[width=0.32\textwidth]{hyper/Fig/hyper-sosvmf0}
    \label{fig:hyper-sosvmf0}}
	\subfloat[]{\includegraphics[width=0.32\textwidth]{hyper/Fig/hyper-mf-n}
    \label{fig:hyper-mf-n}}
    \subfloat[]{\includegraphics[width=0.32\textwidth]{hyper/Fig/hyper-sosvmf-n}
    \label{fig:hyper-sosvmf-n}}\\
	\caption{\wen{Synthetic test for comparing different median filters. (a) Clean data. (b) Noisy data with strong erratic noise. (c) Denoised data using MF. (d) Denoised data using SOSVMF. (e) Removed noise using MF. (f) Removed noise using SOSVMF.}}
	\label{fig:hyper,hyper-n,hyper-mf0,hyper-sosvmf0,hyper-mf-n,hyper-sosvmf-n}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_dc}
    \label{fig:l_dc}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_dn}
    \label{fig:l_dn}}\\
	\caption{Synthetic example. (a) Clean data. (b) Noisy data (SNR=-1.25 dB). }
	\label{fig:l_dc,l_dn}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_curv}
    \label{fig:l_curv}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_sosvmf}
    \label{fig:l_sosvmf}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_curvi}
    \label{fig:l_curvi}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_sosvmfi}
    \label{fig:l_sosvmfi}}
	\caption{Synthetic example. (a) Denoised data using the curvelet method \wen{developed in \cite{candes20061} }(SNR=7.37 dB). (b) Denoised data using the single-step median filtering method \wen{developed in \cite{sosvmf} }(SNR=5.81 dB). (c) Denoised data using the iterative curvelet method \wen{developed in \cite{zhaoqiang2018} }(SNR=8.55 dB). (d) Denoised data using the proposed method (SNR=9.61 dB). }
	\label{fig:l_d}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_curv_n}
    \label{fig:l_curv_n}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_sosvmf_n}
    \label{fig:l_sosvmf_n}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_curvi_n}
    \label{fig:l_curvi_n}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_sosvmfi_n}
    \label{fig:l_sosvmfi_n}}
	\caption{Synthetic example. (a) Removed noise using the curvelet method. (b) Removed noise using the single-step median filtering method. (c) Removed noise using the iterative curvelet method. (d) Removed noise using the proposed method. \old{It is clear that the curvelet-related methods cause serious signal leakage while the median filtering-related methods do not cause obvious damages to signals. The proposed method removes more Gaussian-type noise than the single-step median filtering method. } }
	\label{fig:l_d_n}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_d_1}
    \label{fig:l_d_1}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_d_3}
    \label{fig:l_d_3}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_d_5}
    \label{fig:l_d_5}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_d_7}
    \label{fig:l_d_7}}\\
	\caption{Synthetic example. (a) Denoised data after 1 iteration. (b) Denoised data after 3 iterations.  (c) Denoised data after 5 iterations. (d) Denoised data after 7 iterations. }
	\label{fig:l_ds}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_n_1}
    \label{fig:l_n_1}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_n_3}
    \label{fig:l_n_3}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_n_5}
    \label{fig:l_n_5}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_n_7}
    \label{fig:l_n_7}}\\
	\caption{Synthetic example. (a) Removed noise after 1 iteration. (b) Removed noise after 3 iterations.  (c) Removed noise after 5 iterations. (d) Removed noise after 7 iterations. }
	\label{fig:l_ns}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_dip_dc}
    \label{fig:l_dip_dc}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_dip_dn}
    \label{fig:l_dip_dn}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_dip_1}
    \label{fig:l_dip_1}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_dip_3}
    \label{fig:l_dip_3}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_dip_5}
    \label{fig:l_dip_5}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_dip_7}
    \label{fig:l_dip_7}}\\
	\caption{\wen{Synthetic example. (a) Slope calculated from the clean data. (b) Slope calculated from the noisy data. (c) Calculated slope after 1 iteration. (d) Calculated slope after 3 iterations.  (e) Calculated slope after 5 iterations. (f) Calculated slope after 7 iterations.} }
	\label{fig:l_dips}
\end{figure}

\begin{figure}[htb!]
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/l_snrs4}
	\caption{SNR variations during the iterative inversion.}
	\label{fig:l_snrs4}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_dd_1}
    \label{fig:l_dd_1}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_dd_3}
    \label{fig:l_dd_3}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_dd_5}
    \label{fig:l_dd_5}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_dd_7}
    \label{fig:l_dd_7}}\\
	\caption{Synthetic example (inversion without SOMF constraint). (a) Denoised data after 1 iteration. (b) Denoised data after 3 iterations.  (c) Denoised data after 5 iterations. (d) Denoised data after 7 iterations. }
	\label{fig:l_dds}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_nn_1}
    \label{fig:l_nn_1}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_nn_3}
    \label{fig:l_nn_3}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_nn_5}
    \label{fig:l_nn_5}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_nn_7}
    \label{fig:l_nn_7}}\\
	\caption{Synthetic example (inversion without SOMF constraint). (a) Removed noise after 1 iteration. (b) Removed noise after 3 iterations.  (c) Removed noise after 5 iterations. (d) Removed noise after 7 iterations. }
	\label{fig:l_nns}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_simi_curv}
    \label{fig:l_simi_curv}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_simi_sosvmf}
    \label{fig:l_simi_sosvmf}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_simi_curvi}
    \label{fig:l_simi_curvi}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_simi_sosvmfi}
    \label{fig:l_simi_sosvmfi}}
	\caption{Local similarity between clean data and denoised data. (a) Local similarity using the curvelet method. (b) Local similarity using the single-step median filtering method. (c) Local similarity using the iterative curvelet method. (d) Local similarity using the proposed method. }
	\label{fig:l_simi}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_simi2_curv}
    \label{fig:l_simi2_curv}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_simi2_sosvmf}
    \label{fig:l_simi2_sosvmf}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_simi2_curvi}
    \label{fig:l_simi2_curvi}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/l_simi2_sosvmfi}
    \label{fig:l_simi2_sosvmfi}}
	\caption{Local similarity between denoised data and removed noise. (a) Local similarity using the curvelet method. (b) Local similarity using the single-step median filtering method. (c) Local similarity using the iterative curvelet method. (d) Local similarity using the proposed method. }
	\label{fig:l_simi2}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/sigmas_dn1}
    \label{fig:sigmas_dn1}}
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/sigmas_dn2}
    \label{fig:sigmas_dn2}}
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/sigmas_dn3}
    \label{fig:sigmas_dn3}}
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/sigmas_dn4}
    \label{fig:sigmas_dn4}}\\
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/sigmas_d41}
    \label{fig:sigmas_d41}}
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/sigmas_d42}
    \label{fig:sigmas_d42}}
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/sigmas_d43}
    \label{fig:sigmas_d43}}
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/sigmas_d44}
    \label{fig:sigmas_d44}}\\ 
	\caption{\wen{Denoising test of different noise levels in terms of noise intensity. (a)-(d) Noisy data with the same erratic noise but with increasing random noise intensity. (e)-(h) \dlo{Removed noise}\wen{Denoised data} corresponding to (a)-(d), respectively. }}
	\label{fig:sigmas_d}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/dens_dn1}
    \label{fig:dens_dn1}}
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/dens_dn2}
    \label{fig:dens_dn2}}
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/dens_dn3}
    \label{fig:dens_dn3}}
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/dens_dn4}
    \label{fig:dens_dn4}}\\
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/dens_d41}
    \label{fig:dens_d41}}
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/dens_d42}
    \label{fig:dens_d42}}
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/dens_d43}
    \label{fig:dens_d43}}
	\subfloat[]{\includegraphics[width=0.22\textwidth]{Fig/dens_d44}
    \label{fig:dens_d44}}\\ 
	\caption{\wen{Denoising test of different noise levels in terms of density of erratic noise. (a)-(d) Noisy data with the same random noise but with increasing erratic noise density. (e)-(h) \dlo{Removed noise}\wen{Denoised data} corresponding to (a)-(d), respectively. }}
	\label{fig:dens_d}
\end{figure}

\begin{figure}[htb!]
	\centering
    \includegraphics[width=0.38\textwidth]{Fig/f_dn}
	\caption{\wen{First} field data example containing both Gaussian-type random noise and erratic noise.  }
	\label{fig:f_dn}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_curv}
    \label{fig:f_curv}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_sosvmf}
    \label{fig:f_sosvmf}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_curvi}
    \label{fig:f_curvi}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_sosvmfi}
    \label{fig:f_sosvmfi}}
	\caption{\wen{First} field data example. (a) Denoised data using the curvelet method. (b) Denoised data using the single-step median filtering method. (c) Denoised data using the iterative curvelet method. (d) Denoised data using the proposed method. }
	\label{fig:f_d}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_curv_n}
    \label{fig:f_curv_n}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_sosvmf_n}
    \label{fig:f_sosvmf_n}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_curvi_n}
    \label{fig:f_curvi_n}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_sosvmfi_n}
    \label{fig:f_sosvmfi_n}}
	\caption{\wen{First} field data example. (a) Removed noise using the curvelet method. (b) Removed noise using the single-step median filtering method. (c) Removed noise using the iterative curvelet method. (d) Removed noise using the proposed method. }
	\label{fig:f_d_n}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_d_1}
    \label{fig:f_d_1}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_d_3}
    \label{fig:f_d_3}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_d_5}
    \label{fig:f_d_5}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_d_7}
    \label{fig:f_d_7}}\\
	\caption{\wen{First} field data example. (a) Denoised data after 1 iteration. (b) Denoised data after 3 iterations.  (c) Denoised data after 5 iterations. (d) Denoised data after 7 iterations. }
	\label{fig:f_ds}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_n_1}
    \label{fig:f_n_1}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_n_3}
    \label{fig:f_n_3}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_n_5}
    \label{fig:f_n_5}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_n_7}
    \label{fig:f_n_7}}\\
	\caption{\wen{First} field data example. (a) Removed noise after 1 iteration. (b) Removed noise after 3 iterations.  (c) Removed noise after 5 iterations. (d) Removed noise after 7 iterations. }
	\label{fig:f_ns}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_simi2_curv}
    \label{fig:f_simi2_curv}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_simi2_sosvmf}
    \label{fig:f_simi2_sosvmf}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_simi2_curvi}
    \label{fig:f_simi2_curvi}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f_simi2_sosvmfi}
    \label{fig:f_simi2_sosvmfi}}
	\caption{Local similarity between denoised data and removed noise for the \wen{first} field data example. (a) Local similarity using the curvelet method. (b) Local similarity using the single-step median filtering method. (c) Local similarity using the iterative curvelet method. (d) Local similarity using the proposed method. }
	\label{fig:f_simi2}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f2_dn}
    \label{fig:f2_dn}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f2_curv}
    \label{fig:f2_curv}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f2_sosvmf}
    \label{fig:f2_sosvmf}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f2_curvi}
    \label{fig:f2_curvi}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f2_sosvmfi}
    \label{fig:f2_sosvmfi}}
	\caption{\wen{Second field data example. (a) Field data containing both Gaussian-type random noise and erratic noise. (b) Denoised data using the curvelet method. (c) Denoised data using the single-step median filtering method. (d) Denoised data using the iterative curvelet method. (e) Denoised data using the proposed method. \new{The two pink arrows indicate potential residual spikes.}} }
	\label{fig:f2_d}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f2_curv_n}
    \label{fig:f2_curv_n}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f2_sosvmf_n}
    \label{fig:f2_sosvmf_n}}\\
	\subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f2_curvi_n}
    \label{fig:f2_curvi_n}}
    \subfloat[]{\includegraphics[width=0.38\textwidth]{Fig/f2_sosvmfi_n}
    \label{fig:f2_sosvmfi_n}}
	\caption{\wen{Second field data example. (a) Removed noise using the curvelet method. (b) Removed noise using the single-step median filtering method. (c) Removed noise using the iterative curvelet method. (d) Removed noise using the proposed method.} }
	\label{fig:f2_d_n}
\end{figure}

}

\newpage
\listoffigures
\newpage

%\begin{figure}[htb!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
%	\caption{Caption.}
%	\label{fig:fig}
%\end{figure}

%\begin{figure}[htb!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
%    \label{fig:fig1}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
%    \label{fig:fig2}}\\
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure}

%\begin{figure*}[ht!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
%    \label{fig:fig1}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
%    \label{fig:fig2}}\\
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure*}

%\begin{table}[h]
%\caption{Table caption}
%\begin{center}
%     \begin{tabular}{|c|c|c|c|c|c|} 
%	  \hline Column1 (unit)  & Column2 (unit) & Column3 (unit) \\ 
%	  \hline 1 & 2  & 3 \\
%       \hline
%    \end{tabular} 
%\end{center}
%\label{tbl:table1}
%\end{table}
